Trickery [Combat]
You pull all sorts of crazy crap to get a leg up in combat.
This is a combat feat that scales with your base attack bonus.

Benefits: As a swift action, you may give yourself a +3 dodge bonus to AC, a +4 dodge bonus to one save of your choice, or resistance 4 against one energy type of your choice. This effect lasts one round.
+1: You gain a +4 bonus to your Feint attempts.
+6: Your BAB counts as one point higher for purposes of determining The Edge.
+11: As an immediate action, you may force one opponent in your threatened range about to make a d20 roll to roll twice and take the lower result.
+16: When you make a saving throw, you may take an immediate action to use your highest save bonus instead of the normal save type.


Multi-Weapon Fighting [Combat]
You are pointy in all directions.
This is a combat feat that scales with your base attack bonus.
Prerequisite: Must have the Two-Weapon Fighting feat.

Benefits: Whenever you make an attack or full-attack action, you may Feint once with each weapon you do not use in the attack.
+1: You have the Edge against opponents whose BAB plus number of wielded weapons (including natural weapons) is less than yours.
+6: Whenever you make an attack or full-attack action, you may make a number of attacks with your tertiary weapon equal to the number of attacks you are afforded with your primary weapon.
+11: You gain two extra attacks of opportunity each round for each weapon you wield beyond your second, these attacks of opportunity must be made with the corresponding weapons.
+16: Whenever you make an attack or full-attack action, you may make a number of attacks with your fourth weapon equal to the number of attacks you are afforded with your primary weapon.


\label{comm:feat:flurry}{}\babfeat{Flurry of Blows [Combat]}{ 
"...How many times did you hit him?" I asked. "I lost count at eight."
"Fourteen." he said.
"Whooaa..." }{
Flurry: You gain the ability to flurry as a full-round action. A flurry is a Full Attack action with additional "Flurry' attacks (see below). You have a number of Flurry attacks equal to your Dexterity modifier. 
Flurry attacks are similar to normal attacks, but have these differences:
-They can only be melee attacks.
-Their default attack bonus is BAB-5.
-You do not gain more Flurry attacks by wielding two weapons.
-Flurry attacks cannot be used to inflict bonus damage or additional effects. Therefore, none of the effects like a Rogue's Sneak Attack, a Barbarian's Rage Dice, or the myriad effects a Monk's Slam attack can have, apply to Flurry attacks.
-Flurry attacks cannot score critical hits. Instead, they inflict full weapon damage upon a critical threat (assuming their attack roll is high enough to hit).
}{Whenever you attack, you gain an extra attack at your full attack bonus. 
}{Improved Flurry: As a full-round action, your gain additional Flurry Attacks equal to 1 + [BAB/3]. These are in addition to the Flurry attacks granted by your dexterity modifier. 
}{Flurry is a standard action. 
}{Greater Flurry: When you use Flurry, all of the Flurry attacks are at your full attack bonus. You may use an Improved Flurry as a standard action. When you spend a full-round action to use Greater Flurry, you deal a number of Flurry attacks equal to [BAB/2], in addition to the ones granted by your Dex modifier.}

Intelligent Fighter [Combat]
You outsmart people...so you can stab them in the face.
+0: You have the Edge over opponents when your Intelligence is greater than both their Intelligence and their Dexterity.
+1: You may use your Int bonus on both melee and ranged attack rolls. Yes, you're very smart.
+6: Ghost Step: You may use your Int bonus in place of Charisma when you feint. Additionally, you may do a special feint, called a Ghost Step, when you take a move action to move around your opponent while staying in melee range. This feint may be based on BAB or your ranks in Bluff, plus your Int bonus. If it's successful, your opponent loses his Dex bonus (like normal) and you deal an additional Xd6 (X is equal to your Int Bonus) damage when you stab him in the ass, as long as the ass is stabbed before the enemy's next turn. This bonus damage is not multiplied on a critical hit, and Ghost Step may only be used once per round.
+11: You may use your Int bonus on both melee and ranged damage rolls.
+16: Manipulate: With your enormous brain, you're perfectly suited to tricking an enemy into doing what you want them to. You may do a special Feint as a swift action once a round.
If you succeed, designate an action, movement, or ability of the enemy. You must be aware of this ability, either by having seen it yourself or by succeeding on an appropriate knowledge check. On the enemy's turn, it performs the action you designated, as long the action does not violate its sense of self-preservation.
You may 'manipulate' the opponent into moving to a particular spot, or attacking you with a particular ability, weapon, or spell. Any attacks must be directed at you or one of your allies, although it is possible to trick an enemy into using, for example, a breath weapon on you while you're in the middle of its group of comrades. If you use this ability in consecutive rounds, take a -5 penalty for each round you've used this.
Common Manipulations include:
-Enemy follows you to keep melee distance (requires you to actually move)
-Enemy uses a spell-like ability on you or an ally of yours
-Enemy uses a particular weapon when it attacks.
-Enemy attacks you.
-Flying enemy lands to attack more directly.
-Enemy, for some inexplicable reason, decides they don't want to teleport for a round.


Improved Natural Weapons (Combat)
You have some really fierce natural means of stabbing people in the face.
Requirement:
One or more natural weapons. 

+0: Your natural weapons deal damage as though one size category larger
+1: All of your primary natural weapons can be used in one round without penalty. The secondary ones can be used with a mere -2 penalty, and deal damage like primary weapons.
+6: Your natural weapons tear at muscle, dealing 2 Strength damage each time they strike. Additionally, secondary weapons no longer receive a penalty to hit. In effect, all of your natural weapons are always primary.
+11: The reach of all of your natural weapons increases by 5 feet. Additionally, any time you successfully damage a foe with a natural weapon, they must make a Fortitude save (DC 10 + 1/2 your level + STR) or be Nauseated for one round.
+16: Your natural weapons all deal damage as though yet another size category larger, and gain bonus damage equal to half your Strength modifier again - if they dealt damage normally, it is now 1.5, if it was previously 1.5, it is now x2. Additionally, they all count as adamantine weapons and gain a +1 bonus per 5 character levels (round down) to hit and damage. Finally, if all of your natural weapons strike one foe at least once in the same round, the foe takes an additional 4d6 damage plus double your Strength modifier.

Master of Submissions
You're a great grappler, sure, but you specialise in breaking bones and choking people. Your victims either tap out or pass out.
+0: People take a -4 penalty to escape a grapple you begin. When you pin someone, you can also do basic unarmed damage.
+1: If you pin someone for two rounds in a row, they gain a penalty for one minute. This penalty varies based on the body part you describe the hold as hurting:
Arm: they get a -4 penalty to use that arm, -2 on grapple checks
Leg: speed is reduced by half, -5 against trip attempts
Head: they are blind for one round, then take a -2 penalty on Will saves
Spine: they are sickened with pain
Breathing: they become fatigued
Other: they take a -2 penalty on all attack rolls and skill checks
+6: If someone escapes from a grapple with you, you may immediately attempt to grapple them again, with a -4 penalty to do so. If you succeed, it does not count as maintaining the grapple - a new one is started. If they escape this one, they are safe.
+11: You can grapple two people at once and pin them both at once, without even taking a penalty. Also, every round that you have someone pinned, a cumulative 1d6 damage is taken (1d6 on the first round, 2d6 on the second, etc.)
+16: Your submission holds are now as painful as finishers. Anyone you pin for at least two rounds must make a Fortitude save (Dex or Str based). Failure causes a problem:
Arm: the arm breaks, becoming useless. They also take 3d8 damage.
Leg: the leg breaks, and they can no longer stand. They also take 3d8 damage.
Head: the skull fractures, and they are blind until healed, and stunned for 2 rounds.
Spine: They take 5d10 damage and are nauseated with pain for 2 rounds.
Breathing: They become exhausted. If failed again, they pass out.
Other: They take 4d6 damage and are stunned for 2 rounds.