Jack of All Trades [General]You know how to do a completely implausible number of things.This is a general feat that scales with your character level.Benefits: You suffer no penalties for being untrained in a skill.1: You retroactively gain 1 extra skill point per level (4 at 1st level). All skill points gained from this feat must be spent after you have spent other skill points gained for the same level, and cannot be used to raise a skill above your cross-class maximum rank.6: You immediately gain 1 rank in every core skill. For any skill where this would put you above your normal maximum ranks, you gain 1 extra skill point instead (subject to limitations given above).11: All core skills are considered class skills for you. Your synergy bonuses for having 5+ ranks in a skill are all doubled.16: You benefit from a +5 competence bonus to one skill at all times; you may change which skill as a swift action, but may only select a skill in which you have at least one rank.Ghostly Visage [General]People think you've already got one foot in the grave. They're right.This is a general feat that scales with your character level.Benefits: You may reroll your miss chance due to a target's incorporeality.1: When you attack or are targeted by an attack, you may take an immediate action to cause the attack to be resolved as if you were incorporeal, except that non-magical attacks still have a 50\% chance to hit you (as if they were magical). You must use this ability before the attack roll is made. You may not use this ability if you are denied your DEX bonus to AC.6: You gain lifesense, allowing you to locate living creatures within 60' as blindsense and sense the strength of their life force as if you had cast deathwatch.11: You may pass through solid objects as if incorporeal, but may not end your movement inside of one (if you do so by accident, you are shunted to the nearest open space and take 1d6 damage per 5' traveled).16: You are healed by negative energy as if undead (this does not interfere with any existing ability to be healed by positive energy). You do not lose XP when resurrected.Banter [General] You've turned talking into part of the Art of War Level:0: You may use your Charisma instead of your Dexterity modifier for calculating your dodge bonus. 1: Banter: If you engage an enemy in conversation, he focuses exclusively on you, which may be to his detriment. You and the enemy must understand each other’s language, and he must pass a Will Save (DC 10 + ? character level + Cha modifier), otherwise he is in Bantering mode for a number of rounds equal to your Charisma modifier. Both you and he take a -3 penalty to attack rolls, and if anyone other than you attacks him, he’s considered flat-footed—but it ends the bantering ends. This may be used a number of times a day equal to your Charisma modifier. 6: Flashy: Your attacks are considered to have the Edge against anyone who has less Charisma and Dexterity than you do. You also use your Charisma instead of your Str for melee damage rolls when you have the Edge. 11: Improved Banter: You don’t take the -3 penalty to attack rolls when Bantering. 16: The Curious Durability of Motormouths: You gain DR X/-, where X is your Charisma modifier + 3, while bantering. Setup: When you’re engaged with Banter with an enemy, the first ally’s attack to hit him is a full-damage critical hit.Coward (General)The feat of choice for Wizards and other scruffily-bearded cowards, everywhere! 1: Your run multiplier is increased by one for all levels of encumberance and armor. You also gain +3 to Initiative Rapid Linear Panic: +30 to your speed when you're running away from something. You're also moving so fast, you retain your dexterity bonus, gain a +8 Dodge bonus to AC and draw no AoO's. Ka-PWING If you act first, whether in a surprise round or through initiative, you can move your speed as a free action, drawing no attacks of opportunities for doing so. Legging It: After the initial mad rush to generate some distance, you settle into solid, ground-eating strides which can be kept up indefinitely. You can run for three times as long as you can normally. 6: RLP II: You get another +30 to your speed when running away from something. You also may use one of the following benefits during any given Rapid Linear Panic: -You may run up walls and across water without penalty to your movement speed. -You take no penalties for carrying one object or creature that would otherwise slow you down--even one as awkward as a Great Dane or another person. Armor doesn't slow you down, either. -Your RLP Dodge bonus increases by 4. -When in RLP, you may corner freely. I live with the fear: You're not immune to fear. Not by a long shot. But, on the other hand, being afraid doesn't make you lose your head. The worst state of fear you can experience is frightened, and when you're frightened, you don't take the penalties. You also keep your head enough that you can do other things not directly associated with fleeing the threat, as long as you can still do them while running away. 11: Look, A Distraction! With a bluff check (as a free action), you can bump other all enemies within 30 feet ten points down the initiative order. There he is! When you run from hostiles, they must make a will save ( DC 10 + your HD) or give chase exclusively to you. Yeah, the universe hates you like that. On the other hand, they're taking a -10 penalty to their Spot and Listen checks, and when they're attacked by someone other than you, they're surprised. 16: Your run multiplier goes up by 1 (again). You may also gain all of the benefits of RLP II at the same time, and may use any of these abilities, even when *not* running from something. After all, you can't run away in straight lines forever. You'll fall off the edge if keep it up enough.