%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Traps}\index{Traps}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Types of Traps:} A trap can be either mechanical or magic in nature. Mechanical 
traps include pits, arrow traps, falling blocks, water-filled rooms, whirling blades, 
and anything else that depends on a mechanism to operate. A mechanical trap can 
be constructed by a PC through successful use of the \linkskill{Craft} (trapmaking) skill (see 
Designing a Trap, below, and the skill description).

Magic traps are further divided into spell traps and magic device traps. Magic 
device traps initiate spell effects when activated, just as wands, rods, rings, 
and other magic items do. Creating a magic device trap requires the \linkfeat{Craft Wondrous Item}
feat (see Designing a Trap and the feat description).

Spell traps are simply spells that themselves function as traps. Creating 
a spell trap requires the services of a character who can cast the needed spell 
or spells, who is usually either the character creating the trap or an NPC spellcaster 
hired for the purpose.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mechanical Traps}
%%%%%%%%%%%%%%%%%%%%%%%%%

Dungeons are frequently equipped with deadly mechanical (nonmagical) traps. A trap 
typically is defined by its location and triggering conditions, how hard it is 
to spot before it goes off, how much damage it deals, and whether or not the heroes 
receive a saving throw to mitigate its effects. Traps that attack with arrows, 
sweeping blades, and other types of weaponry make normal attack rolls, with a specific 
attack bonus dictated by the trap's design.

Creatures who succeed on a DC 20 \linkskill{Search} check detect a simple mechanical trap before 
it is triggered. (A simple trap is a snare, a trap triggered by a tripwire, or 
a large trap such as a pit.)

A character with the trap sense class feature who succeeds on a DC 21 (or higher) 
Search check detects a well-hidden or complex mechanical trap before it is triggered. 
Complex traps are denoted by their triggering mechanisms and involve pressure plates, 
mechanisms linked to doors, changes in weight, disturbances in the air, vibrations, 
and other sorts of unusual triggers.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Magic Traps}
%%%%%%%%%%%%%%%%%%%%%%%%%

Many spells can be used to create dangerous traps. Unless the spell or item description 
states otherwise, assume the following to be true.

\begin{itemize}
\item A successful Search check (DC 25 + spell level) made by a rogue (and only a rogue) 
detects a magic trap before it goes off. Other characters have no chance to find 
a magic trap with a Search check.
\item Magic traps permit a saving throw in order to avoid the effect (DC 10 + spell level x 1.5).
\item Magic traps may be disarmed by a rogue (and only a rogue) with a successful Disable 
Device check (DC 25 + spell level).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Elements of a Trap}
%%%%%%%%%%%%%%%%%%%%%%%%%

All traps -- mechanical or magic -- have the following elements: trigger, reset, 
Search DC, Disable Device DC, attack bonus (or saving throw or onset delay), damage/effect, 
and Challenge Rating. Some traps may also include optional elements, such as poison 
or a bypass. These characteristics are described below.

%%%
\subsubsection{Trigger}
%%%

A trap's trigger determines how it is sprung.

\textbf{Location:} A location trigger springs a trap when someone stands in a particular 
square.

\textbf{Proximity:} This trigger activates the trap when a creature approaches 
within a certain distance of it. A proximity trigger differs from a location trigger 
in that the creature need not be standing in a particular square. Creatures that 
are flying can spring a trap with a proximity trigger but not one with a location 
trigger. Mechanical proximity triggers are extremely sensitive to the slightest 
change in the air. This makes them useful only in places such as crypts, where 
the air is unusually still.

The proximity trigger used most often for magic device traps is the \linkspell{Alarm} 
spell. Unlike when the spell is cast, an \textit{Alarm} spell used as a trigger 
can have an area that's no larger than the area the trap is meant to protect.

Some magic device traps have special proximity triggers that activate only when 
certain kinds of creatures approach. For example, a \linkspell{Detect Good} spell 
can serve as a proximity trigger on an evil altar, springing the attached trap 
only when someone of good alignment gets close enough to it.

\textbf{Sound:} This trigger springs a magic trap when it detects any sound. A 
sound trigger functions like an ear and has a +15 bonus on Listen checks. A successful 
Move Silently check, magical \linkspell{Silence}, and other effects that would negate 
hearing defeat it. A trap with a sound trigger requires the casting of \linkspell{Clairaudience} during its construction.

\textbf{Visual:} This trigger for magic traps works like an actual eye, springing 
the trap whenever it "sees" something. A trap with a visual trigger requires 
the casting of \linkspell{Arcane Eye}, \linkspell{Clairvoyance}, or \linkspell{True Seeing} during 
its construction. Sight range and the Spot bonus conferred on the trap depend on 
the spell chosen, as shown.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Spell Trap Spot Bonuses}
\centering
\begin{tabular}{lll}
\textbf{Spell} & \textbf{Sight Range} & \textbf{Spot Bonus}\\
Arcane Eye & Line of Sight (unlimited range) & +20\\
Clairvoyance & One preselected location & +15\\
True Seeing & Line of Sight (up to 120ft) & +30\\
\end{tabular}
\end{table}

If you want the trap to "see" in the dark, you must either choose the \textit{True Seeing}
option or add \textit{Darkvision} to the trap as well. (\textit{Darkvision}
limits the trap's sight range in the dark to 60 feet.) If invisibility, disguises, 
or illusions can fool the spell being used, they can fool the visual trigger as 
well. 

\textbf{Touch:} A touch trigger, which springs the trap when touched, is one of 
the simplest kinds of trigger to construct. This trigger may be physically attached 
to the part of the mechanism that deals the damage or it may not. You can make 
a magic touch trigger by adding \textit{Alarm} to the trap and reducing the area 
of the effect to cover only the trigger spot.

\textbf{Timed:} This trigger periodically springs the trap after a certain duration 
has passed.

\textbf{Spell:} All spell traps have this kind of trigger. The appropriate spell 
descriptions explain the trigger conditions for traps that contain spell 
triggers.

%%%
\subsubsection{Reset}
%%%

A reset element is the set of conditions under which a trap becomes ready to trigger 
again.

\textbf{No Reset:} Short of completely rebuilding the trap, there's no way to trigger 
it more than once. Spell traps have no reset element. 

\textbf{Repair:} To get the trap functioning again, you must repair it. 

\textbf{Manual:} Resetting the trap requires someone to move the parts back into 
place. This is the kind of reset element most mechanical traps have.

\textbf{Automatic:} The trap resets itself, either immediately or after a timed 
interval.

%%%
\subsubsection{Repairing and Resetting Mechanical Traps}
%%%

Repairing a mechanical trap requires a \linkskill{Craft} (trapmaking) check against a DC equal 
to the one for building it. The cost for raw materials is one-fifth of the trap's 
original market price. To calculate how long it takes to fix a trap, use the same 
calculations you would for building it, but use the cost of the raw materials required 
for repair in place of the market price.

Resetting a trap usually takes only a minute or so. For a trap with a more difficult 
reset method, you should set the time and labor required.

\vspace{12pt}
\textbf{Bypass (Optional Element)}

If the builder of a trap wants to be able to move past the trap after it is created 
or placed, it's a good idea to build in a bypass mechanism -- something that temporarily 
disarms the trap. Bypass elements are typically used only with mechanical traps; 
spell traps usually have built-in allowances for the caster to bypass them.

\textbf{Lock:} A lock bypass requires a DC 30 \linkskill{Open Lock} check to open. 

\textbf{Hidden Switch:} A hidden switch requires a DC 25 \linkskill{Search} check to locate.

\textbf{Hidden Lock:} A hidden lock combines the features above, requiring a DC 
25 Search check to locate and a DC 30 Open Lock check to open.

\vspace{12pt}
\textbf{Search and Disable Device DCs}

The builder sets the Search and Disable Device DCs for a mechanical trap. For a 
magic trap, the values depend on the highest-level spell used.

\textbf{Mechanical Trap:} The base DC for both Search and Disable Device checks 
is 20. Raising or lowering either of these DCs affects the base cost (Table: Cost 
Modifiers for Mechanical Traps) and possibly the CR (Table: CR Modifiers for Mechanical 
Traps). 

\textbf{Magic Trap:} The DC for both Search and Disable Device checks is equal 
to 25 + the spell level of the highest-level spell used. Only characters with the 
trap sense class feature can attempt a Search check or a Disable Device check involving 
a magic trap. These DCs do not affect the trap's cost or CR.

%%%
\subsubsection{Attack Bonus/Saving Throw DC}
%%%

A trap usually either makes an attack roll or forces a saving throw to avoid it. 
Occasionally a trap uses both of these options, or neither (see Never Miss).

\textbf{Pits:} These are holes (covered or not) that characters can fall into and 
take damage. A pit needs no attack roll, but a successful Reflex save (DC set by 
the builder) avoids it. Other save-dependent mechanical traps also fall into this 
category.

Pits in dungeons come in three basic varieties: uncovered, covered, and chasms. 
Pits and chasms can be defeated by judicious application of the Climb skill, the 
Jump skill, or various magical means.

Uncovered pits serve mainly to discourage intruders from going a certain way, although 
they cause much grief to characters who stumble into them in the dark, and they 
can greatly complicate a melee taking place nearby.

Covered pits are much more dangerous. They can be detected with a DC 20 Search 
check, but only if the character is taking the time to carefully examine the area 
before walking across it. A character who fails to detect a covered pit is still 
entitled to a DC 20 Reflex save to avoid falling into it. However, if she was running 
or moving recklessly at the time, she gets no saving throw and falls automatically.

Trap coverings can be as simple as piled refuse (straw, leaves, sticks, garbage), 
a large rug, or an actual trapdoor concealed to appear as a normal part of the 
floor. Such a trapdoor usually swings open when enough weight (usually about 50 
to 80 pounds) is placed upon it. Devious trap builders sometimes design trapdoors 
so that they spring back shut after they open. The trapdoor might lock once it's 
back in place, leaving the stranded character well and truly trapped. Opening such 
a trapdoor is just as difficult as opening a regular door (assuming the trapped 
character can reach it), and a DC 13 Strength check is needed to keep a spring-loaded 
door open.

Pit traps often have something nastier than just a hard floor at the bottom. A 
trap designer may put spikes, monsters, or a pool of acid, lava, or even water 
at the bottom. Spikes at the bottom of a pit deal damage as daggers with a +10 
attack bonus and a +1 bonus on damage for every 10 feet of the fall (to a maximum 
bonus on damage of +5). If the pit has multiple spikes, a falling victim is attacked 
by 1d4 of them. This damage is in addition to any damage from the fall itself. 

Monsters sometimes live in pits. Any monster that can fit into the pit might have 
been placed there by the dungeon's designer, or might simply have fallen in and 
not been able to climb back out. 

A secondary trap, mechanical or magical, at the bottom of a pit can be particularly 
deadly. Activated by a falling victim, the secondary trap attacks the already injured 
character when she's least ready for it.

\textbf{Ranged Attack Traps:} These traps fling darts, arrows, spears, or the like 
at whoever activated the trap. The builder sets the attack bonus. A ranged attack 
trap can be configured to simulate the effect of a composite bow with a high strength 
rating which provides the trap with a bonus on damage equal to its strength rating.

\textbf{Melee Attack Traps:} These traps feature such obstacles as sharp blades 
that emerge from walls and stone blocks that fall from ceilings. Once again, the 
builder sets the attack bonus.

%%%
\subsubsection{Damage/Effect}
%%%

The effect of a trap is what happens to those who spring it. Usually this takes 
the form of either damage or a spell effect, but some traps have special effects.

\textbf{Pits:} Falling into a pit deals 1d6 points of damage per 10 feet of depth. 

\textbf{Ranged Attack Traps:} These traps deal whatever damage their ammunition 
normally would. If a trap is constructed with a high strength rating, it has a 
corresponding bonus on damage.

\textbf{Melee Attack Traps:} These traps deal the same damage as the melee weapons 
they "wield." In the case of a falling stone block, you can assign any amount 
of bludgeoning damage you like, but remember that whoever resets the trap has to 
lift that stone back into place. 

A melee attack trap can be constructed with a built-in bonus on damage rolls, just 
as if the trap itself had a high Strength score. 

\textbf{Spell Traps:} Spell traps produce the spell's effect. Like all 
spells, a spell trap that allows a saving throw has a save DC of 10 + spell level 
+ caster's relevant ability modifier.

\textbf{Magic Device Traps:} These traps produce the effects of any spells included 
in their construction, as described in the appropriate entries. If the 
spell in a magic device trap allows a saving throw, its save DC is 10 + spell level 
x1.5. Some spells make attack rolls instead.

\textbf{Special:} Some traps have miscellaneous features that produce special effects, 
such as drowning for a water trap or ability damage for poison. Saving throws and 
damage depend on the poison or are set by the builder, as appropriate.

%%%
\subsubsection{Miscellaneous Trap Features}
%%%

Some traps include optional features that can make them considerably more deadly. 
The most common such features are discussed below.

\textbf{Alchemical Item:} Mechanical traps may incorporate alchemical devices or 
other special substances or items, such as tanglefoot bags, alchemist's fire, thunderstones, 
and the like. Some such items mimic spell effects. If the item mimics a spell effect, 
it increases the CR as shown on Table: CR Modifiers for Mechanical Traps.

\textbf{Gas:} With a gas trap, the danger is in the inhaled poison it delivers. 
Traps employing gas usually have the never miss and onset delay features (see below).

\textbf{Liquid:} Any trap that involves a danger of drowning is in this category. 
Traps employing liquid usually have the never miss and onset delay features (see 
below). 

\textbf{Multiple Target:} Traps with this feature can affect more than one character.

\textbf{Never Miss:} When the entire dungeon wall moves to crush you, your quick 
reflexes won't help, since the wall can't possibly miss. A trap with this feature 
has neither an attack bonus nor a saving throw to avoid, but it does have an onset 
delay (see below). Most traps involving liquid or gas are of the never miss variety. 

\textbf{Onset Delay:} An onset delay is the amount of time between when the trap 
is sprung and when it deals damage. A never miss trap always has an onset delay.

\textbf{Poison:} Traps that employ poison are deadlier than their nonpoisonous 
counterparts, so they have correspondingly higher CRs. To determine the CR modifier 
for a given poison, consult Table: CR Modifiers for Mechanical Traps. Only injury, 
contact, and inhaled poisons are suitable for traps; ingested types are not. Some 
traps simply deal the poison's damage. Others deal damage with ranged or melee 
attacks as well. 

\textbf{Pit Spikes:} Treat spikes at the bottom of a pit as daggers, each with 
a +10 attack bonus. The damage bonus for each spike is +1 per 10 feet of pit depth 
(to a maximum of +5). Each character who falls into the pit is attacked by 1d4 
spikes. Pit spikes do not add to the average damage of the trap (see \linksec{Challenge Rating of a Trap}{Average Damage}, 
below).

\textbf{Pit Bottom:} If something other than spikes waits at the bottom of a pit, 
it's best to treat that as a separate trap (see \linksec{Challenge Rating of a Trap}{Multiple Traps}, below) with a location 
trigger that activates on any significant impact, such as a falling character. 

\textbf{Touch Attack:} This feature applies to any trap that needs only a successful 
touch attack (melee or ranged) to hit.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sample Traps}
%%%%%%%%%%%%%%%%%%%%%%%%%

The costs listed for mechanical traps are market prices; those for magic traps 
are raw material costs. Caster level and class for the spells used to produce the 
trap effects are provided in the entries for magic device traps and spell traps. 
For all other spells used (in triggers, for example), the caster level is assumed 
to be the minimum required.

%%%
\subsubsection{CR 1 Traps}
%%%

\textbf{Basic Arrow Trap:} CR 1; mechanical; proximity trigger; manual reset; Atk 
+10 ranged (1d6/x3, arrow); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 2,000 gp.

\textbf{Camouflaged Pit Trap:} CR 1; mechanical; location trigger; manual reset; 
DC 20 Reflex save avoids; 10 ft. deep (1d6, fall); Search DC 24; Disable Device 
DC 20. \textit{Market Price:} 1,800 gp.

\textbf{Deeper Pit Trap:} CR 1; mechanical; location trigger; manual reset; hidden 
switch bypass (Search DC 25); DC 15 Reflex save avoids; 20 ft. deep (2d6, fall); 
multiple targets (first target in each of two adjacent 5-ft. squares); Search DC 
20; Disable Device DC 23. \textit{Market Price:} 1,300 gp.

\textbf{Fusillade of Darts:} CR 1; mechanical; location trigger; manual reset; 
Atk +10 ranged (1d4+1, dart); multiple targets (fires 1d4 darts at each target 
in two adjacent 5-ft. squares); Search DC 14; Disable Device DC 20. \textit{Market 
Price:} 500 gp.

\textbf{Poison Dart Trap:} CR 1; mechanical; location trigger; manual reset; Atk 
+8 ranged (1d4 plus poison, dart); poison (bloodroot, DC 12 Fortitude save resists, 
0/1d4 Con plus 1d3 Wis); Search DC 20; Disable Device DC 18. \textit{Market Price: 
}700 gp.

\textbf{Poison Needle Trap:} CR 1; mechanical; touch trigger; manual reset; Atk 
+8 ranged (1 plus greenblood oil poison); Search DC 22; Disable Device DC 20. \textit{Market 
Price:} 1,300 gp.

\textbf{Portcullis Trap:} CR 1; mechanical; location trigger; manual reset; Atk 
+10 melee (3d6); Search DC 20; Disable Device DC 20. \textit{Note:} Damage applies 
only to those underneath the portcullis. Portcullis blocks passageway. \textit{Market 
Price:} 1,400 gp.

\textbf{Razor-Wire across Hallway:} CR 1; mechanical; location trigger; no reset; 
Atk +10 melee (2d6, wire); multiple targets (first target in each of two adjacent 
5-ft. squares); Search DC 22; Disable Device DC 15. \textit{Market Price:} 400 
gp.

\textbf{Rolling Rock Trap:} CR 1; mechanical; location trigger; manual reset; Atk 
+10 melee (2d6, rock); Search DC 20; Disable Device DC 22. \textit{Market Price: 
}1,400 gp.

\textbf{Scything Blade Trap:} CR 1; mechanical; location trigger; automatic reset; 
Atk +8 melee (1d8/x3); Search DC 21; Disable Device DC 20. \textit{Market Price: 
}1,700 gp.

\textbf{Spear Trap:} CR 1; mechanical; location trigger; manual reset; Atk +12 
ranged (1d8/x3, spear); Search DC 20; Disable Device DC 20. \textit{Note:} 200-ft. 
max range, target determined randomly from those in its path. Market Price: 1,200 
gp.

\textbf{Swinging Block Trap:} CR 1; mechanical; touch trigger; manual reset; Atk 
+5 melee (4d6, stone block); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 500 gp.

\textbf{Wall Blade Trap:} CR 1; mechanical; touch trigger; automatic reset; hidden 
switch bypass (Search DC 25); Atk +10 melee (2d4/x4, scythe); Search DC 22; Disable 
Device DC 22. \textit{Market Price:} 2,500 gp.

%%%
\subsubsection{CR 2 Traps}
%%%

\textbf{Box of Brown Mold:} CR 2; mechanical; touch trigger (opening the box); 
automatic reset; 5-ft. cold aura (3d6, cold nonlethal); Search DC 22; Disable Device 
DC 16. \textit{Market Price:} 3,000 gp.

\textbf{Bricks from Ceiling:} CR 2; mechanical; touch trigger; repair reset; Atk 
+12 melee (2d6, bricks); multiple targets (all targets in two adjacent 5-ft. squares); 
Search DC 20; Disable Device DC 20. \textit{Market Price:} 2,400 gp.

\textbf{Burning Hands Trap:} CR 2; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Burning Hands}, 1st-level 
wizard, 1d4 fire, DC 11 Reflex save half damage); Search DC 26; Disable Device 
DC 26. \textit{Cost:} 500 gp, 40 XP.

\textbf{Camouflaged Pit Trap:} CR 2; mechanical; location trigger; manual reset; 
DC 20 Reflex save avoids; 20 ft. deep (2d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); Search DC 24; Disable Device DC 19. \textit{Market 
Price:} 3,400 gp.

\textbf{Inflict Light Wounds Trap:} CR 2; magic device; touch 
trigger; automatic reset; spell effect (\linkspell{Inflict Light Wounds}, 1st-level 
cleric, 1d8+1, DC 11 Will save half damage); Search DC 26; Disable Device DC 26. 
\textit{Cost:} 500 gp, 40 XP.

\textbf{Javelin Trap:} CR 2; mechanical; location trigger; manual reset; Atk +16 
ranged (1d6+4, javelin); Search DC 20; Disable Device DC 18. \textit{Market Price: 
}4,800 gp.

\textbf{Large Net Trap:} CR 2; mechanical; location trigger; manual reset; Atk 
+5 melee (see note); Search DC 20; Disable Device DC 25. \textit{Note:} Characters 
in 10-ft. square are grappled by net (Str 18) if they fail a DC 14 Reflex save. 
\textit{Market Price:} 3,000 gp.

\textbf{Pit Trap:} CR 2; mechanical, location trigger; manual reset; DC 20 Reflex 
save avoids; 40 ft. deep (4d6, fall); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 2,000 gp.

\textbf{Poison Needle Trap:} CR 2; mechanical; touch trigger; repair reset; lock 
bypass (Open Lock DC 30); Atk +17 melee (1 plus poison, needle); poison (blue whinnis, 
DC 14 Fortitude save resists (poison only), 1 Con/unconsciousness); Search DC 22; 
Disable Device DC 17. \textit{Market Price:} 4,720 gp.

\textbf{Spiked Pit Trap:} CR 2; mechanical; location trigger; automatic reset; 
DC 20 Reflex save avoids; 20 ft. deep (2d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); pit spikes (Atk +10 melee, 1d4 spikes per 
target for 1d4+2 each); Search DC 18; Disable Device DC 15. \textit{Market Price: 
}1,600 gp.

\textbf{Tripping Chain:} CR 2; mechanical; location trigger; automatic reset; multiple 
traps (tripping and melee attack); Atk +15 melee touch (trip), Atk +15 melee (2d4+2, 
spiked chain); Search DC 15; Disable Device DC 18. \textit{Market Price:} 3,800 
gp. \textit{Note:} This trap is really one CR 1 trap that trips and a second CR 
1 trap that attacks with a spiked chain. If the tripping attack succeeds, a +4 
bonus applies to the spiked chain attack because the opponent is prone.

\textbf{Well-Camouflaged Pit Trap:} CR 2; mechanical; location trigger; repair 
reset; DC 20 Reflex save avoids; 10 ft. deep (1d6, fall); Search DC 27; Disable 
Device DC 20. \textit{Market Price:} 4,400 gp.

%%%
\subsubsection{CR 3 Traps}
%%%

\textbf{Burning Hands Trap:} CR 3; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Burning Hands}, 5th-level 
wizard, 5d4 fire, DC 11 Reflex save half damage); Search DC 26; Disable Device 
DC 26. \textit{Cost:} 2,500 gp, 200 XP.

\textbf{Camouflaged Pit Trap:} CR 3; mechanical; location trigger; manual reset; 
DC 20 Reflex save avoids; 30 ft. deep (3d6, fall); multiple targets (first target 
in each of two adjacent squares); Search DC 24; Disable Device DC 18. \textit{Market 
Price:} 4,800 gp.

\textbf{Ceiling Pendulum:} CR 3; mechanical; timed trigger; automatic reset; Atk 
+15 melee (1d12+8/x3, greataxe); Search DC 15; Disable Device DC 27. \textit{Market 
Price:} 14,100 gp.

\textbf{Fire Trap:} CR 3; spell; spell trigger; no reset; spell 
effect (\linkspell{Fire Trap}, 3rd-level druid, 1d4+3 fire, DC 13 Reflex save half 
damage); Search DC 27; Disable Device DC 27. \textit{Cost:} 85 gp to hire NPC spellcaster.

\textbf{Extended Bane Trap:} CR 3; magic device; proximity 
trigger \textit{(detect good); }automatic reset; spell effect (extended \linkspell{Bane}, 
3rd-level cleric, DC 13 Will save negates); Search DC 27; Disable Device DC 27. 
\textit{Cost:} 3,500 gp, 280 XP.

\textbf{Ghoul Touch Trap:} CR 3; magic device; touch trigger; 
automatic reset; spell effect (\linkspell{Ghoul Touch}, 3rd-level wizard, DC 13 Fortitude 
save negates); Search DC 27; Disable Device DC 27. \textit{Cost:} 3,000 gp, 240 
XP. 

\textbf{Hail of Needles:} CR 3; mechanical; location trigger; manual reset; Atk 
+20 ranged (2d4); Search DC 22; Disable Device DC 22. \textit{Market Price:} 5,400 
gp.

\textbf{Acid Arrow Trap:} CR 3; magic device; proximity trigger 
\textit{(alarm); }automatic reset; Atk +2 ranged touch; spell effect (\linkspell{Acid Arrow},
3rd-level wizard, 2d4 acid/round for 2 rounds); Search DC 27; Disable Device 
DC 27. \textit{Cost:} 3,000 gp, 240 XP.

\textbf{Pit Trap:} CR 3; mechanical, location trigger; manual reset; DC 20 Reflex 
save avoids; 60 ft. deep (6d6, fall); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 3,000 gp.

\textbf{Poisoned Arrow Trap:} CR 3; mechanical; touch trigger; manual reset; lock 
bypass (Open Lock DC 30); Atk +12 ranged (1d8 plus poison, arrow); poison (Large 
monstrous scorpion venom, DC 14 Fortitude save resists, 1d4 Con/1d4 Con); Search 
DC 19; Disable Device DC 15. \textit{Market Price:} 2,900 gp.

\textbf{Spiked Pit Trap:} CR 3; mechanical; location trigger; manual reset; DC 
20 Reflex save avoids; 20 ft. deep (2d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); pit spikes (Atk +10 melee, 1d4 spikes per 
target for 1d4+2 each); Search DC 21; Disable Device DC 20. \textit{Market Price: 
}3,600 gp.

\textbf{Stone Blocks from Ceiling:} CR 3; mechanical; location trigger; repair 
reset; Atk +10 melee (4d6, stone blocks); Search DC 25; Disable Device DC 20. \textit{Market 
Price:} 5,400 gp.

%%%
\subsubsection{CR 4 Traps}
%%%

\textbf{Bestow Curse Trap:} CR 4; magic device; touch trigger 
\textit{(detect chaos); }automatic reset; spell effect (\linkspell{Bestow Curse}, 5th-level 
cleric, DC 14 Will save negates); Search DC 28; Disable Device DC 28. \textit{Cost: 
}8,000 gp, 640 XP.

\textbf{Camouflaged Pit Trap:} CR 4; mechanical; location trigger; manual reset; 
DC 20 Reflex save avoids; 40 ft. deep (4d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); Search DC 25; Disable Device DC 17. \textit{Market 
Price:} 6,800 gp. 

\textbf{Collapsing Column:} CR 4; mechanical; touch trigger (attached); no reset; 
Atk +15 melee (6d6, stone blocks); Search DC 20; Disable Device DC 24. \textit{Market 
Price:} 8,800 gp.

\textbf{Glyph of Warding (Blast):} CR 4; spell; spell trigger; 
no reset; spell effect (\linkspell{Glyph of Warding} [blast], 5th-level cleric, 2d8 
acid, DC 14 Reflex save half damage); multiple targets (all targets within 5 ft.); 
Search DC 28; Disable Device DC 28. \textit{Cost:} 350 gp to hire NPC spellcaster.

\textbf{Lightning Bolt Trap:} CR 4; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Lightning Bolt}, 5th-level 
wizard, 5d6 electricity, DC 14 Reflex save half damage); Search DC 28; Disable 
Device DC 28. \textit{Cost:} 7,500 gp, 600 XP.

\textbf{Pit Trap:} CR 4; mechanical, location trigger; manual reset; DC 20 Reflex 
save avoids; 80 ft. deep (8d6, fall); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 4,000 gp.

\textbf{Poisoned Dart Trap:} CR 4; mechanical; location trigger; manual reset; 
Atk +15 ranged (1d4+4 plus poison, dart); multiple targets (1 dart per target in 
a 10-ft.-by-10-ft. area); poison (Small monstrous centipede poison, DC 10 Fortitude 
save resists, 1d2 Dex/1d2 Dex); Search DC 21; Disable Device DC 22. \textit{Market 
Price:} 12,090 gp.

\textbf{Sepia Snake Sigil Trap:} CR 4; spell; spell trigger; 
no reset; spell effect (\linkspell{Sepia Snake Sigil}, 5th-level wizard, DC 14 Reflex 
save negates); Search DC 28; Disable Device DC 28. \textit{Cost:} 650 gp to hire 
NPC spellcaster.

\textbf{Spiked Pit Trap:} CR 4; mechanical; location trigger; automatic reset; 
DC 20 Reflex save avoids; 60 ft. deep (6d6, fall); pit spikes (Atk +10 melee, 1d4 
spikes per target for 1d4+5 each); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 4,000 gp. 

\textbf{Wall Scythe Trap:} CR 4; mechanical; location trigger; automatic reset; 
Atk +20 melee (2d4+8/x4, scythe); Search DC 21; Disable Device DC 18. \textit{Market 
Price:} 17,200 gp.

\textbf{Water-Filled Room Trap:} CR 4; mechanical; location trigger; automatic 
reset; multiple targets (all targets in a 10-ft.-by-10-ft. room); never miss; onset 
delay (5 rounds); liquid; Search DC 17; Disable Device DC 23. \textit{Market Price: 
}11,200 gp.

\textbf{Wide-Mouth Spiked Pit Trap:} CR 4; mechanical; location trigger; manual 
reset; DC 20 Reflex save avoids; 20 ft. deep (2d6, fall); multiple targets (first 
target in each of two adjacent 5-ft. squares); pit spikes (Atk +10 melee, 1d4 spikes 
per target for 1d4+2 each); Search DC 18; Disable Device DC 25. \textit{Market 
Price:} 7,200 gp.

%%%
\subsubsection{CR 5 Traps}
%%%

\textbf{Camouflaged Pit Trap:} CR 5; mechanical; location trigger; manual reset; 
DC 20 Reflex save avoids; 50 ft. deep (5d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); Search DC 25; Disable Device DC 17. \textit{Market 
Price:} 8,500 gp.

\textbf{Doorknob Smeared with Contact Poison:} CR 5; mechanical; touch trigger 
(attached); manual reset; poison (nitharit, DC 13 Fortitude save resists, 0/3d6 
Con); Search DC 25; Disable Device DC 19. \textit{Market Price:} 9,650 gp.

\textbf{Falling Block Trap:} CR 5; mechanical; location trigger; manual reset; 
Atk +15 melee (6d6); multiple targets (can strike all characters in two adjacent 
specified squares); Search DC 20; Disable Device DC 25. \textit{Market Price:} 15,000 
gp.

\textbf{Fire Trap:}CR 5; spell; spell trigger; no reset; spell effect 
(\linkspell{Fire Trap}, 7th-level wizard, 1d4+7 fire, DC 16 Reflex save half damage); 
Search DC 29; Disable Device DC 29. \textit{Cost:} 305 gp to hire NPC spellcaster.

\textbf{Fireball Trap:} CR 5; magic device; touch trigger; automatic 
reset; spell effect (\linkspell{Fireball}, 8th-level wizard, 8d6 fire, DC 14 Reflex 
save half damage); Search DC 28; Disable Device DC 28. \textit{Cost:} 12,000 gp, 
960 XP.

\textbf{Flooding Room Trap:} CR 5; mechanical; proximity trigger; automatic reset; 
no attack roll necessary (see note below); Search DC 20; Disable Device DC 25. 
\textit{Note:} Room floods in 4 rounds. \textit{Market Price:} 17,500 gp.

\textbf{Fusillade of Darts:} CR 5; mechanical; location trigger; manual reset; 
Atk +18 ranged (1d4+1, dart); multiple targets (1d8 darts per target in a 10-ft.-by-10-ft. 
area); Search DC 19; Disable Device DC 25. \textit{Market Price:} 18,000 gp.

\textbf{Moving Executioner Statue:} CR 5; mechanical; location trigger; automatic 
reset; hidden switch bypass (Search DC 25); Atk +16 melee (1d12+8/x3, greataxe); 
multiple targets (both arms attack); Search DC 25; Disable Device DC 18. \textit{Market 
Price:} 22,500 gp.

\textbf{Phantasmal Killer Trap:} CR 5; magic device; proximity 
trigger (\textit{alarm }covering the entire room); automatic reset; spell effect 
(\linkspell{Phantasmal Killer}, 7th-level wizard, DC 16 Will save for disbelief and 
DC 16 Fort save for partial effect); Search DC 29; Disable Device DC 29. \textit{Cost: 
}14,000 gp, 1,120 XP.

\textbf{Pit Trap:} CR 5; mechanical, location trigger; manual reset; DC 20 Reflex 
save avoids; 100 ft. deep (10d6, fall); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 5,000 gp.

\textbf{Poison Wall Spikes:} CR 5; mechanical; location trigger; manual reset; 
Atk +16 melee (1d8+4 plus poison, spike); multiple targets (closest target in each 
of two adjacent 5-ft. squares); poison (Medium monstrous spider venom, DC 12 Fortitude 
save resists, 1d4 Str/1d4 Str); Search DC 17; Disable Device DC 21. \textit{Market 
Price:} 12,650 gp.

\textbf{Spiked Pit Trap:} CR 5; mechanical; location trigger; manual reset; DC 
25 Reflex save avoids; 40 ft. deep (4d6, fall); multiple targets (first target 
in each of two adjacent 5-ft. squares); pit spikes (Atk +10 melee, 1d4 spikes per 
target for 1d4+4 each); Search DC 21; Disable Device DC 20. \textit{Market Price: 
}13,500 gp.

\textbf{Spiked Pit Trap (80 Ft. Deep):} CR 5; mechanical; location trigger, manual 
reset; DC 20 Reflex save avoids; 80 ft. deep (8d6, fall), pit spikes (Atk +10 melee, 
1d4 spikes for 1d4+5 each); Search DC 20; Disable Device DC 20. \textit{Market 
Price:} 5,000 gp. 

\textbf{Ungol Dust Vapor Trap:} CR 5; mechanical; location trigger; manual reset; 
gas; multiple targets (all targets in a 10-ft.-by-10-ft. room); never miss; onset 
delay (2 rounds); poison (ungol dust, DC 15 Fortitude save resists, 1 Cha/1d6 Cha 
plus 1 Cha drain); Search DC 20; Disable Device DC 16. \textit{Market Price:} 9,000 
gp.

%%%
\subsubsection{CR 6 Traps }
%%%

\textbf{Built-to-Collapse Wall:} CR 6; mechanical; proximity trigger; no reset; 
Atk +20 melee (8d6, stone blocks); multiple targets (all targets in a 10-ft.-by-10-ft. 
area); Search DC 14; Disable Device DC 16. \textit{Market Price:} 15,000 gp.

\textbf{Compacting Room:} CR 6; mechanical; timed trigger; automatic reset; hidden 
switch bypass (Search DC 25); walls move together (12d6, crush); multiple targets 
(all targets in a 10-ft.-by- 10-ft. room); never miss; onset delay (4 rounds); 
Search DC 20; Disable Device DC 22. \textit{Market Price:} 25,200 gp.

\textbf{Flame Strike Trap:} CR 6; magic device; proximity trigger 
\textit{(detect magic); }automatic reset; spell effect (\linkspell{Flame Strike}, 9th-level 
cleric, 9d6 fire, DC 17 Reflex save half damage); Search DC 30; Disable Device 
DC 30. \textit{Cost:} 22,750 gp, 1,820 XP.

\textbf{Fusillade of Spears:} CR 6; mechanical; proximity trigger; repair reset; 
Atk +21 ranged (1d8, spear); multiple targets (1d6 spears per target in a 10 ft.-by-10-ft. 
area); Search DC 26; Disable Device DC 20. \textit{Market Price:} 31,200 gp.

\textbf{Glyph of Warding (Blast):} CR 6; spell; spell trigger; 
no reset; spell effect (\linkspell{Glyph of Warding} [blast], 16th-level cleric, 8d8 
sonic, DC 14 Reflex save half damage); multiple targets (all targets within 5 ft.); 
Search DC 28; Disable Device DC 28. \textit{Cost:} 680 gp to hire NPC spellcaster.

\textbf{Lightning Bolt Trap:} CR 6; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Lightning Bolt}, 10th-level 
wizard, 10d6 electricity, DC 14 Reflex save half damage); Search DC 28; Disable 
Device DC 28. \textit{Cost:} 15,000 gp, 1,200 XP.

\textbf{Spiked Blocks from Ceiling:} CR 6; mechanical; location trigger; repair 
reset; Atk +20 melee (6d6, spikes); multiple targets (all targets in a 10-ft.-by-10-ft. 
area); Search DC 24; Disable Device DC 20. \textit{Market Price:} 21,600 gp.

\textbf{Spiked Pit Trap (100 Ft. Deep):} CR 6; mechanical; location trigger, manual 
reset; DC 20 Reflex save avoids; 100 ft. deep (10d6, fall); pit spikes (Atk +10 
melee, 1d4 spikes per target for 1d4+5 each); Search DC 20; Disable Device DC 20. 
\textit{Market Price:} 6,000 gp.

\textbf{Whirling Poison Blades:} CR 6; mechanical; timed trigger; automatic reset; 
hidden lock bypass (Search DC 25, Open Lock DC 30); Atk +10 melee (1d4+4/19-20 
plus poison, dagger); poison (purple worm poison, DC 24 Fortitude save resists, 
1d6 Str/2d6 Str); multiple targets (one target in each of three preselected 5-ft. 
squares); Search DC 20; Disable Device DC 20. \textit{Market Price:} 30,200 gp.

\textbf{Wide-Mouth Pit Trap:} CR 6; mechanical; location trigger, manual reset; 
DC 25 Reflex save avoids; 40 ft. deep (4d6, fall); multiple targets (all targets 
within a 10-ft.-by-10-ft. area); Search DC 26; Disable Device DC 25. \textit{Market 
Price:} 28,200 gp.

\textbf{Wyvern Arrow Trap:} CR 6; mechanical; proximity trigger; manual reset; 
Atk +14 ranged (1d8 plus poison, arrow); poison (wyvern poison, DC 17 Fortitude 
save resists, 2d6 Con/2d6 Con); Search DC 20; Disable Device DC 16. \textit{Market 
Price:} 17,400 gp. 

%%%
\subsubsection{CR 7 Traps}
%%%

\textbf{Acid Fog Trap:} CR 7; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Acid Fog}, 11th-level 
wizard, 2d6/round acid for 11 rounds); Search DC 31; Disable Device DC 31. \textit{Cost: 
}33,000 gp, 2,640 XP.

\textbf{Blade Barrier Trap:} CR 7; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Blade Barrier}, 11th-level 
cleric, 11d6 slashing, DC 19 Reflex save half damage); Search DC 31; Disable Device 
DC 31. \textit{Cost:} 33,000 gp, 2,640 XP.

\textbf{Burnt Othur Vapor Trap:} CR 7; mechanical; location trigger; repair reset; 
gas; multiple targets (all targets in a 10-ft.-by-10-ft. room); never miss; onset 
delay (3 rounds); poison (burnt othur fumes, DC 18 Fortitude save resists, 1 Con 
drain/3d6 Con); Search DC 21; Disable Device DC 21. \textit{Market Price:} 17,500 
gp.

\textbf{Chain Lightning Trap:} CR 7; magic device; proximity 
trigger \textit{(alarm); }automatic reset; spell effect (\linkspell{Chain Lightning}, 
11th-level wizard, 11d6 electricity to target nearest center of trigger area plus 
5d6 electricity to each of up to eleven secondary targets, DC 19 Reflex save half 
damage); Search DC 31; Disable Device DC 31. \textit{Cost:} 33,000 gp, 2,640 XP. 

\textbf{Black Tentacles Trap:} CR 7; magic device; proximity 
trigger \textit{(alarm); }no reset; spell effect (\linkspell{Black Tentacles}, 7th-level 
wizard, 1d4+7 tentacles, Atk +7 melee [1d6+4, tentacle]); multiple targets (up 
to six tentacles per target in each of two adjacent 5-ft. squares); Search DC 29; 
Disable Device DC 29. \textit{Cost:} 1,400 gp, 112 XP.

\textbf{Fusillade of Greenblood Oil Darts:} CR 7; mechanical; location trigger; 
manual reset; Atk +18 ranged (1d4+1 plus poison, dart); poison (greenblood oil, 
DC 13 Fortitude save resists, 1 Con/ 1d2 Con); multiple targets (1d8 darts per 
target in a 10-ft.-by-10-ft. area); Search DC 25; Disable Device DC 25. \textit{Market 
Price:} 33,000 gp.

\textbf{Lock Covered in Dragon Bile:} CR 7; mechanical; touch trigger (attached); 
no reset; poison (dragon bile, DC 26 Fortitude save resists, 3d6 Str/0); Search 
DC 27; Disable Device DC 16. \textit{Market Price:} 11,300 gp.

\textbf{Summon Monster VI Trap:} CR 7; magic device; proximity 
trigger \textit{(alarm); }no reset; spell effect (\linkspell{Summon Monster VI}, 11th-level 
wizard), Search DC 31; Disable Device DC 31. \textit{Cost:} 3,300 gp, 264 XP.

\textbf{Water-Filled Room:} CR 7; mechanical; location trigger; manual reset; multiple 
targets (all targets in a 10-ft.-by-10-ft. room); never miss; onset delay (3 rounds); 
water; Search DC 20; Disable Device DC 25. \textit{Market Price:} 21,000 gp. 

\textbf{Well-Camouflaged Pit Trap:} CR 7; mechanical; location trigger; repair 
reset; DC 25 Reflex save avoids; 70 ft. deep (7d6, fall); multiple targets (first 
target in each of two adjacent 5-ft. squares); Search DC 27; Disable Device DC 
18. \textit{Market Price:} 24,500 gp. 

%%%
\subsubsection{CR 8 Traps}
%%%

\textbf{Deathblade Wall Scythe:} CR 8; mechanical; touch trigger; manual reset; 
Atk +16 melee (2d4+8 plus poison, scythe); poison (deathblade, DC 20 Fortitude 
save resists, 1d6 Con/2d6 Con); Search DC 24; Disable Device DC 19. \textit{Market 
Price:} 31,400 gp.

\textbf{Destruction Trap:} CR 8; magic device; touch trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Destruction}, 13th-level 
cleric, DC 20 Fortitude save for 10d6 damage); Search DC 32; Disable Device DC 
32. \textit{Cost:} 45,500 gp, 3,640 XP.

\textbf{Earthquake Trap:} CR 8; magic device; proximity trigger 
\textit{(alarm); }automatic reset; spell effect (\linkspell{Earthquake}, 13th-level 
cleric, 65-ft. radius, DC 15 or 20 Reflex save, depending on terrain); Search DC 
32; Disable Device DC 32. \textit{Cost:} 45,500 gp, 3,640 XP.

\textbf{Insanity Mist Vapor Trap:} CR 8; mechanical; location trigger; repair reset; 
gas; never miss; onset delay (1 round); poison (insanity mist, DC 15 Fortitude 
save resists, 1d4 Wis/2d6 Wis); multiple targets (all targets in a 10-ft.-by-10-ft. 
room); Search DC 25; Disable Device DC 20. \textit{Market Price:} 23,900 gp.

\textbf{Acid Arrow Trap:} CR 8; magic device; visual trigger 
\textit{(true seeing); }automatic reset; multiple traps (two simultaneous \linkspell{Acid Arrow}
traps); Atk +9 ranged touch and +9 ranged touch; spell effect (\textit{acid 
arrow}, 18th-level wizard, 2d4 acid damage for 7 rounds); Search DC 27; Disable 
Device DC 27. \textit{Cost:} 83,500 gp, 4,680 XP. \textit{Note:} This trap is really 
two CR 6 \textit{acid arrow} traps that fire simultaneously, using the same trigger 
and reset.

\textbf{Power Word Stun Trap:} CR 8; magic device; touch trigger; 
no reset; spell effect (\linkspell{Power Word Stun}, 13th-level wizard), Search DC 
32; Disable Device DC 32. \textit{Cost:} 4,550 gp, 364 XP.

\textbf{Prismatic Spray Trap:} CR 8; magic device; proximity 
trigger \textit{(alarm); }automatic reset; spell effect (\linkspell{Prismatic Spray}, 
13th-level wizard, DC 20 Reflex, Fortitude, or Will save, depending on effect); 
Search DC 32; Disable Device DC 32. \textit{Cost:} 45,500 gp, 3,640 XP.

\textbf{Reverse Gravity Trap:} CR 8; magic device; proximity 
trigger (\textit{alarm, }10-ft. area); automatic reset; spell effect (\linkspell{Reverse Gravity},
13th-level wizard, 6d6 fall [upon hitting the ceiling of the 60-ft.- 
high room], then 6d6 fall [upon falling 60 ft. to the floor when the spell ends], 
DC 20 Reflex save avoids damage); Search DC 32; Disable Device DC 32. \textit{Cost: 
}45,500 gp, 3,640 XP.

\textbf{Well-Camouflaged Pit Trap:} CR 8; mechanical; location trigger; repair 
reset; DC 20 Reflex save avoids; 100 ft. deep (10d6, fall); Search DC 27; Disable 
Device DC 18. \textit{Market Price:} 16,000 gp.

\textbf{Word of Chaos Trap:} CR 8; magic device; proximity trigger 
\textit{(detect law); }automatic reset; spell effect (\linkspell{Word of Chaos}, 13th-level 
cleric); Search DC 32; Disable Device DC 32. \textit{Cost:} 46,000 gp, 3,680 XP.

%%%
\subsubsection{CR 9 Traps}
%%%

\textbf{Drawer Handle Smeared with Contact Poison:} CR 9; mechanical; touch trigger 
(attached); manual reset; poison (black lotus extract, DC 20 Fortitude save resists, 
3d6 Con/3d6 Con); Search DC 18; Disable Device DC 26. \textit{Market Price:} 21,600 
gp. 

\textbf{Dropping Ceiling:} CR 9; mechanical; location trigger; repair reset; ceiling 
moves down (12d6, crush); multiple targets (all targets in a 10-ft.-by-10-ft. room); 
never miss; onset delay (1 round); Search DC 20; Disable Device DC 16. \textit{Market 
Price:} 12,600 gp. 

\textbf{Incendiary Cloud Trap:} CR 9; magic device; proximity 
trigger \textit{(alarm); }automatic reset; spell effect (\linkspell{Incendiary Cloud}, 
15th-level wizard, 4d6/round for 15 rounds, DC 22 Reflex save half damage); Search 
DC 33; Disable Device DC 33. \textit{Cost:} 60,000 gp, 4,800 XP. 

\textbf{Wide-Mouth Pit Trap:} CR 9; mechanical; location trigger; manual reset; 
DC 25 Reflex save avoids; 100 ft. deep (10d6, fall); multiple targets (all targets 
within a 10-ft.-by-10-ft. area); Search DC 25; Disable Device DC 25. \textit{Market 
Price:} 40,500 gp. 

\textbf{Wide-Mouth Spiked Pit with Poisoned Spikes:} CR 9; mechanical; location 
trigger; manual reset; hidden lock bypass (Search DC 25, Open Lock DC 30); DC 
20 Reflex save avoids; 70 ft. deep (7d6, fall); multiple targets (all targets within 
a 10-ft.-by-10-ft. area); pit spikes (Atk +10 melee, 1d4 spikes per target for 
1d4+5 plus poison each); poison (giant wasp poison, DC 14 Fortitude save resists, 
1d6 Dex/1d6 Dex); Search DC 20; Disable Device DC 20. \textit{Market Price:} 11,910 
gp.

%%%
\subsubsection{CR 10 Traps}
%%%

\textbf{Crushing Room:} CR 10; mechanical; location trigger; automatic reset; walls 
move together (16d6, crush); multiple targets (all targets in a 10-ft.-by-10-ft. 
room); never miss; onset delay (2 rounds); Search DC 22; Disable Device DC 20. 
\textit{Market Price:} 29,000 gp.

\textbf{Crushing Wall Trap:} CR 10; mechanical; location trigger; automatic reset; 
no attack roll required (18d6, crush); Search DC 20; Disable Device DC 25. Market 
Price: 25,000 gp. 

\textbf{Energy Drain Trap:} CR 10; magic device; visual trigger 
(\textit{true seeing}); automatic reset; Atk +8 ranged touch; spell effect (\linkspell{Energy Drain}, 
17th-level wizard, 2d4 negative levels for 24 hours, DC 23 Fortitude save 
negates); Search DC 34; Disable Device DC 34. \textit{Cost:} 124,000 gp, 7,920 
XP.

\textbf{Forcecage and Summon Monster VII trap:} 
CR 10; magic device; proximity trigger \textit{(alarm); }automatic reset; multiple 
traps (one \linkspell{Forcecage} trap and one \linkspell{Summon Monster VII} trap that 
summons a hamatula); spell effect (\textit{Forcecage}, 13th-level wizard), spell 
effect (\textit{Summon Monster VII}, 13th-level wizard, hamatula); Search DC 32; 
Disable Device DC 32. \textit{Cost:} 241,000 gp, 7,280 XP. \textit{Note:} This 
trap is really one CR 8 trap that creates a \textit{Forcecage} and a second CR 
8 trap that summons a hamatula in the same area. If both succeed, the hamatula 
appears inside the \textit{Forcecage}. These effects are independent of each other.

\textbf{Poisoned Spiked Pit Trap:} CR 10; mechanical; location trigger; manual 
reset; hidden lock bypass (Search DC 25, Open Lock DC 30); DC 20 Reflex save avoids; 
50 ft. deep (5d6, fall); multiple targets (first target in each of two adjacent 
5-ft. squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+5 plus 
poison each); poison (purple worm poison, DC 24 Fortitude save resists, 1d6 Str/2d6 
Str); Search DC 16; Disable Device DC 25. \textit{Market Price:} 19,700 gp. 

\textbf{Wail of the Banshee Trap:} CR 10; magic device; proximity 
trigger \textit{(alarm); }automatic reset; spell effect (\linkspell{Wail of the Banshee},
17th-level wizard, DC 23 Fortitude save negates); multiple targets (up to 17 creatures); 
Search DC 34; Disable Device DC 34. \textit{Cost:} 76,500 gp, 6,120 XP.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Designing A Trap}
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Mechanical Traps:} Simply select the elements you want the trap to have 
and add up the adjustments to the trap's Challenge Rating that those elements require 
(see Table: CR Modifiers for Mechanical Traps) to arrive at the trap's final CR. 
From the CR you can derive the DC of the Craft (trapmaking) checks a character 
must make to construct the trap.

\textbf{Magic Traps:} As with mechanical traps, you don't have to do anything other 
than decide what elements you want and then determine the CR of the resulting trap 
(see Table: CR Modifiers for Magic Traps). If a player character wants to design 
and construct a magic trap, he must have the Craft Wondrous Item feat. In addition, 
he must be able to cast the spell or spells that the trap requires -- or, failing 
that, he must be able to hire an NPC to cast the spells for him.

%%%
\subsubsection{Challenge Rating of a Trap}
%%%

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{CR Modifiers for Mechanical Traps}
\centering
\begin{tabular}{l l}
\textbf{Feature} & \textbf{CR Modifier}\\
\textbf{Search DC}&\\
15 or lower &-1\\
25-29 &+1\\
30 or higher &+2\\
\textbf{Disable Device DC}&\\
15 or lower &-1\\
25-29 &+1\\
30 or higher &+2\\
\textbf{Reflex Save DC (Pit or Other Save-Dependent Trap)}&\\
15 or lower &-1\\
16-24 &+0\\
25-29 &+1\\
30 or higher &+2\\
\textbf{Attack Bonus (Melee or Ranged Attack Trap)}&\\
+0 or lower &-2\\
+1 to +5 &-1\\
+6 to +14 &+0\\
+15 to +19 &+1\\
+20 to +24 &+2\\
\textbf{Damage/Effect}&\\
Average damage &+1/7 points\textsuperscript{*}\\
\textbf{Miscellaneous Features}&\\
Alchemical device &Level of spell mimicked\\
Liquid &+5\\
Multiple target &+1 (or 0 if never miss)\\
Onset delay 1 round &+3\\
Onset delay 2 rounds &+2\\
Onset delay 3 rounds &+1\\
Onset delay 4+ rounds &-1\\
Poison & By poison (see below)\\
Pit spikes &+1\\
Touch attack &+1\\
\multicolumn{2}{l}{\textsuperscript{*} Rounded to the nearest multiple of 7 (round up for an average that lies exactly between two numbers).}\\
\end{tabular}
\end{table}

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Poison Modifers for Mechanical Trap CRs}
\centering
\begin{tabular}{l c l c}
Black adder venom &+1 &Large scorpion venom &+3\\
Black lotus extract &+8 &Malyss root paste &+3\\
Bloodroot &+1 &Medium spider venom &+2\\
Blue whinnis &+1 &Nitharit &+4\\
Burnt othur fumes &+6 &Purple worm poison &+4\\
Deathblade &+5 &Sassone leaf residue &+3\\
Dragon bile &+6 &Shadow essence &+3\\
Giant wasp poison &+3 &Small centipede poison &+1\\
Greenblood oil &+1 &Terinav root &+5\\
Insanity mist &+4 &Ungol dust &+3\\
Wyvern poison &+5 & &\\
\end{tabular}
\end{table}

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{CR Modifiers for Magic Traps}
\centering
\begin{tabular}{l l}
\textbf{Feature} & \textbf{Cost Modifier}\\
Highest-level spell & +Spell Level OR +1 per 7 points of average damage per round\textsuperscript{*}\\
\multicolumn{2}{l}{\textsuperscript{*}See the note following Table: CR Modifiers for Mechanical Traps.}\\
\end{tabular}
\end{table}

To calculate the Challenge Rating of a trap, add all the CR modifiers (see the 
tables below) to the base CR for the trap type.

\textbf{Mechanical Trap:} The base CR for a mechanical trap is 0. If your final 
CR is 0 or lower, add features until you get a CR of 1 or higher.

\textbf{Magic Trap:} For a spell trap or magic device trap, the base CR is 1. The 
highest-level spell used modifies the CR (see Table: CR Modifiers for Magic Traps).

\textbf{Average Damage:} If a trap (either mechanical or magic) does hit point 
damage, calculate the average damage for a successful hit and round that value 
to the nearest multiple of 7. Use this value to adjust the Challenge Rating of 
the trap, as indicated on the tables below. Damage from poisons and pit spikes 
does not count toward this value, but damage from a high strength rating and extra 
damage from multiple attacks does.

For a magic trap, only one modifier applies to the CR -- either the level of the 
highest-level spell used in the trap, or the average damage figure, whichever is 
larger.

\textbf{Multiple Traps:} If a trap is really two or more connected traps that affect 
approximately the same area, determine the CR of each one separately.

\textit{Multiple Dependent Traps:} If one trap depends on the success of the other 
(that is, you can avoid the second trap altogether by not falling victim to the 
first), they must be treated as separate traps.

\textit{Multiple Independent Traps:} If two or more traps act independently (that 
is, none depends on the success of another to activate), use their CRs to determine 
their combined Encounter Level as though they were monsters\textit{. }The resulting 
Encounter Level is the CR for the combined traps.

%%%
\subsubsection{Mechanical Trap Cost}
%%%

The base cost of a mechanical trap is 1,000 gp. Apply all the modifiers from Table: 
Cost Modifiers for Mechanical Traps for the various features you've added to the 
trap to get the modified base cost.

The final cost is equal to (modified base cost x Challenge Rating) + extra costs. 
The minimum cost for a mechanical trap is (CR x 100) gp.

After you've multiplied the modified base cost by the Challenge Rating, add the 
price of any alchemical items or poison you incorporated into the trap. If the 
trap uses one of these elements and has an automatic reset, multiply the poison 
or alchemical item cost by 20 to provide an adequate supply of doses.

\textbf{Multiple Traps:} If a trap is really two or more connected traps, determine 
the final cost of each separately, then add those values together. This holds for 
both multiple dependent and multiple independent traps (see the previous section).

%%%
\subsubsection{Magic Device Trap Cost}
%%%

Building a magic device trap involves the expenditure of experience points as well 
as gold pieces, and requires the services of a spellcaster. Table: Cost Modifiers 
for Magic Device Traps summarizes the cost information for magic device traps. 
If the trap uses more than one spell (for instance, a sound or visual trigger spell 
in addition to the main spell effect), the builder must pay for them all (except 
\textit{alarm}, which is free unless it must be cast by an NPC; see below).

The costs derived from Table: Cost Modifiers for Magic Device Traps assume that 
the builder is casting the necessary spells himself (or perhaps some other PC is 
providing the spells for free). If an NPC spellcaster must be hired to cast them 
those costs must be factored in as well.

A magic device trap takes one day to construct per 500 gp of its cost.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Cost Modifiers for Magic Device Traps}
\centering
\begin{tabular}{l l}
\textbf{Feature} & \textbf{Cost Modifier}\\
Alarm spell used in trigger & -\\
\textbf{One-Shot Trap}&\\
\hspace{.2cm}Each spell used in trap &\shortstack{+50 gp x caster level x spell level,\\+4 XP x caster level x spell level}\\
&\\
\hspace{.2cm}Material components &+ Cost of all material components\\
\hspace{.2cm}XP components &+ Total of XP components x 5 gp\\
\textbf{Automatic Reset Trap}&\\
\hspace{.2cm}Each spell used in trap &\shortstack{+500 gp x caster level x spell level,\\+40 XP x caster level x spell level}\\
&\\
\hspace{.2cm}Material components &+ Cost of all material components x 100 gp\\
\hspace{.2cm}XP components &+ Total of XP components x 500 gp\\
\end{tabular}
\end{table}

%%%
\subsubsection{Spell Trap Cost}
%%%

A spell trap has a cost only if the builder must hire an NPC spellcaster to cast 
it.

%%%
\subsubsection{Craft DCs for Mechanical Traps}
%%%

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Base Mechanical Craft (Trapmaking) DCs}
\centering
\begin{tabular}{l r}
\textbf{Trap CR} & \textbf{Base Craft (Trapmaking) DC}\\
1-3 & 20\\
4-6 & 25\\
7-10 & 30\\
\end{tabular}
\end{table}

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Mechanical Craft (Trapmaking) DC Modifiers}
\centering
\begin{tabular}{l r}
\textbf{Additional Components} & \textbf{DC Modifier}\\
Proximity Trigger & +5\\
Automatic Reset & +5\\
\end{tabular}
\end{table}

Once you know the Challenge Rating of a trap determine the Craft (trapmaking) DC 
by referring to the table and the modifiers given below.

\textbf{Making the Checks:} To determine how much progress a character makes on 
building a trap each week, that character makes a Craft (trapmaking) check. See 
the Craft skill description for details on Craft checks and the circumstances that 
can affect them.


\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Cost Modifiers for Mechanical Traps}
\centering
\begin{tabular}{l l}
\textbf{Feature} & \textbf{Cost Modifier}\\
\textbf{Trigger Type}&\\
Location &-\\
Proximity &+1,000 gp\\
Touch &-\\
Touch (attached) &-100 gp\\
Timed &+1,000 gp\\
\textbf{Reset Type}&\\
No reset &-500 gp\\
Repair &-200 gp\\
Manual &-\\
Automatic &+500 gp (or 0 if trap has timed trigger)\\
\textbf{Bypass Type}&\\
Lock &+100 gp (Open Lock DC 30)\\
Hidden switch &+200 gp (Search DC 25)\\
Hidden lock &+300 gp (Open Lock DC 30, Search DC 25)\\
\textbf{Search DC}&\\
19 or lower &-100 gp x (20 - DC)\\
20 &-\\
21 or higher &+200 gp x (DC - 20)\\
\textbf{Disable Device DC}&\\
19 or lower &-100 gp x (20 - DC)\\
20 &-\\
21 or higher &+200 gp x (DC - 20)\\
\textbf{Reflex Save DC (Pit or Other Save-Dependent Trap)}&\\
19 or lower &-100 gp x (20 - DC)\\
20 &-\\
21 or higher &+300 gp x (DC - 20)\\
\textbf{Attack Bonus (Melee or Ranged Attack Trap)}&\\
+9 or lower &-100 gp x (10 - bonus)\\
+10 &-\\
+11 or higher &+200 gp x (bonus - 10)\\
\textbf{Damage Bonus}&\\
High strength rating (ranged attack trap) &+100 gp x bonus (max +4)\\
High Strength bonus (melee attack trap) &+100 gp x bonus (max +8)\\
\textbf{Miscellaneous Features}&\\
Never miss &+1,000 gp\\
Poison &Cost of poison\textsuperscript{*}\\
Alchemical item &Cost of item\textsuperscript{*}\\
\multicolumn{2}{l}{\textsuperscript{*} Multiply cost by 20 if trap features automatic reset.}\\
\end{tabular}
\end{table}

\clearpage
