%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Urban Adventures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

At first glance, a city is much like a dungeon, made up of walls, doors, rooms, 
and corridors. Adventures that take place in cities have two salient differences 
from their dungeon counterparts, however. Characters have greater access to resources, 
and they must contend with law enforcement.

\textbf{Access to Resources:} Unlike in dungeons and the wilderness, characters 
can buy and sell gear quickly in a city. A large city or metropolis probably has 
high-level NPCs and experts in obscure fields of knowledge who can provide assistance 
and decipher clues. And when the PCs are battered and bruised, they can retreat 
to the comfort of a room at the inn.

The freedom to retreat and ready access to the marketplace means that the players 
have a greater degree of control over the pacing of an urban adventure.

\textbf{Law Enforcement:}\index{Law Enforcement} The other key distinctions between adventuring in a city 
and delving into a dungeon is that a dungeon is, almost by definition, a lawless 
place where the only law is that of the jungle: Kill or be killed. A city, on the 
other hand, is held together by a code of laws, many of which are explicitly designed 
to prevent the sort of behavior that adventurers engage in all the time: killing 
and looting. Even so, most cities' laws recognize monsters as a threat to the stability 
the city relies on, and prohibitions about murder rarely apply to monsters such 
as aberrations or evil outsiders. Most evil humanoids, however, are typically protected 
by the same laws that protect all the citizens of the city. Having an evil alignment 
is not a crime (except in some severely theocratic cities, perhaps, with the magical 
power to back up the law); only evil deeds are against the law. Even when adventurers 
encounter an evildoer in the act of perpetrating some heinous evil upon the populace 
of the city, the law tends to frown on the sort of vigilante justice that leaves 
the evildoer dead or otherwise unable to testify at a trial.

\textbf{Weapon And Spell Restrictions:} Different cities have different laws about such issues as carrying weapons in public 
and restricting spellcasters. The city's laws may not affect all characters equally. A monk isn't hampered at 
all by a law about peace-bonding weapons, but a cleric is reduced to a fraction 
of his power if all holy symbols are confiscated at the city's gates.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Urban Features}
%%%%%%%%%%%%%%%%%%%%%%%%%

Walls, doors, poor lighting, and uneven footing: In many ways a city is much like 
a dungeon. Some new considerations for an urban setting are covered below.

%%%
\subsubsection{Walls and Gates}
%%%

Many cities are surrounded by walls. A typical small city wall is a fortified stone 
wall 5 feet thick and 20 feet high. Such a wall is fairly smooth, requiring a DC 
30 \linkskill{Climb} check to scale. The walls are crenellated on one side to provide a low 
wall for the guards atop it, and there is just barely room for guards to walk along 
the top of the wall. A typical small city wall has AC 3, hardness 8, and 450 hp 
per 10-foot section.

A typical large city wall is 10 feet thick and 30 feet high, with crenellations 
on both sides for the guards on top of the wall. It is likewise smooth, requiring 
a DC 30 Climb check to scale. Such a wall has AC 3, hardness 8, and 720 hp per 
10-foot section.

A typical metropolis wall is 15 feet thick and 40 feet tall. It has crenellations 
on both sides and often has a tunnel and small rooms running through its interior. 
Metropolis walls have AC 3, hardness 8, and 1,170 hp per 10-foot section.

Unlike smaller cities, metropolises often have interior walls as well as surrounding 
walls -- either old walls that the city has outgrown, or walls dividing individual 
districts from each other. Sometimes these walls are as large and thick as the 
outer walls, but more often they have the characteristics of a large city's or 
small city's walls.

\textbf{Watch Towers:} Some city walls are adorned with watch towers set at irregular 
intervals. Few cities have enough guards to keep someone constantly stationed at 
every tower, unless the city is expecting attack from outside. The towers provide 
a superior view of the surrounding countryside as well as a point of defense against 
invaders.

Watch towers are typically 10 feet higher than the wall they adjoin, and their 
diameter is 5 times the thickness of the wall. Arrow slits line the outer sides 
of the upper stories of a tower, and the top is crenellated like the surrounding 
walls are. In a small tower (25 feet in diameter adjoining a 5-foot-thick wall), 
a simple ladder typically connect the tower's stories and the roof. In a larger 
tower, stairs serve that purpose. 

Heavy wooden doors, reinforced with iron and bearing good locks (\linkskill{Open Lock} DC 30), 
block entry to a tower, unless the tower is in regular use. As a rule, the captain 
of the guard keeps the key to the tower secured on her person, and a second copy 
is in the city's inner fortress or barracks.

\textbf{Gates:} A typical city gate is a gatehouse with two portcullises and murder 
holes above the space between them. In towns and some small cities, the primary 
entry is through iron double doors set into the city wall.

Gates are usually open during the day and locked or barred at night. Usually, one 
gate lets in travelers after sunset and is staffed by guards who will open it for 
someone who seems honest, presents proper papers, or offers a large enough bribe 
(depending on the city and the guards).

%%%
\subsubsection{Guards and Soldiers}
%%%

A city typically has full-time military personnel equal to 1\% of its adult population, 
in addition to militia or conscript soldiers equal to 5\% of the population. The 
full-time soldiers are city guards responsible for maintaining order within the 
city, similar to the role of modern police, and (to a lesser extent) for defending 
the city from outside assault. Conscript soldiers are called up to serve in case 
of an attack on the city.

A typical city guard force works on three eight-hour shifts, with 30\% of the force 
on a day shift (8am to 4pm), 
35\% on an evening shift (4pm to 12am), 
and 35\% on a night shift (12am to 8am). 
At any given time, 80\% of the guards on duty are on the streets patrolling, while 
the remaining 20\% are stationed at various posts throughout the city, where they 
can respond to nearby alarms. At least one such guard post is present within each 
neighborhood of a city (each neighborhood consisting of several districts).

The majority of a city guard force is made up of warriors, mostly 1st level. Officers 
include higher-level warriors, fighters, a fair number of clerics, and wizards 
or sorcerers, as well as multiclass fighter/spellcasters.

%%%
\subsubsection{Siege Engines}
%%%

Siege engines are large weapons, temporary structures, or pieces of equipment traditionally 
used in besieging a castle or fortress.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Seige Engines}
\centering
\begin{tabular}{l r c c c c}
\textbf{Item} & \textbf{Cost} & \textbf{Damage} & \textbf{Critical} & \textbf{Range Increment} & \textbf{Typical Crew}\\
Ballista & 500gp & 3d8 & 19-20 & 120ft & 1\\
Heavy Catapult & 800gp & 6d6 & -- & 200ft (100ft minimum) & 4\\
Light Catapult & 550gp & d6 & -- & 150ft (100ft minimum) & 2\\
Ram & 1,000gp & 3d6\textsuperscript{*} & -- & -- & 10\\
Seige Tower & 2,000gp & -- & -- & -- & 20\\
\multicolumn{6}{l}{\textsuperscript{*} See description for special rules.}\\
\end{tabular}
\end{table}

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Catapult Attack Modifiers}
\centering
\begin{tabular}{p{10cm} l}
\textbf{Condition} & \textbf{Modifier}\\
No line of sight to target square & -6\\
Successive Shots (crew can see where most recent misses landed) & Cumulative +2 per miss (Max +10)\\
Successive Shots (crew can't see where most recent miss landed, but observer is providing feedback) & Cumulative +1 per previous miss (Max +5)\\
\end{tabular}
\end{table}

\textbf{Ballista:} A ballista is essentially a Huge heavy crossbow fixed in place. 
Its size makes it hard for most creatures to aim it. Thus, a Medium creature 
takes a -4 penalty on attack rolls when using a ballista, and a Small creature 
takes a -6 penalty. It takes a creature smaller than Large two full-round actions 
to reload the ballista after firing.

A ballista takes up a space 5 feet across.

\textbf{Heavy Catapult:} A heavy catapult is a massive engine capable of throwing 
rocks or heavy objects with great force. Because the catapult throws its payload 
in a high arc, it can hit squares out of its line of sight. To fire a heavy catapult, 
the crew chief makes a special check against DC 15 using only his base attack bonus, 
Intelligence modifier, range increment penalty, and the appropriate modifiers from 
the lower section of Table 3-26. If the check succeeds, the catapult stone hits 
the square the catapult was aimed at, dealing the indicated damage to any object 
or character in the square. Characters who succeed on a DC 15 Reflex save take 
half damage. Once a catapult stone hits a square, subsequent shots hit the same 
square unless the catapult is re-aimed or the wind changes direction or speed.

If a catapult stone misses, roll 1d8 to determine where it lands. This determines 
the misdirection of the throw, with 1 being back toward the catapult and 2 through 
8 counting clockwise around the target square. Then, count 3 squares away from 
the target square for every range increment of the attack.

Loading a catapult requires a series of full-round actions. It takes a DC 15 Strength 
check to winch the throwing arm down; most catapults have wheels to allow up to 
two crew members to use the aid another action, assisting the main winch operator. 
A DC 15 Profession (siege engineer) check latches the arm into place, and then 
another DC 15 Profession (siege engineer) check loads the catapult ammunition. 
It takes four full-round actions to re-aim a heavy catapult (multiple crew members 
can perform these full-round actions in the same round, so it would take a crew 
of four only 1 round to re-aim the catapult).

A heavy catapult takes up a space 15 feet across.

\textbf{Light Catapult:} This is a smaller, lighter version of the heavy catapult. 
It functions as the heavy catapult, except that it takes a DC 10 Strength check 
to winch the arm into place, and only two full-round actions are required to re-aim 
the catapult.

A light catapult takes up a space 10 feet across.

\textbf{Ram:} This heavy pole is sometimes suspended from a movable scaffold that 
allows the crew to swing it back and forth against objects. As a full-round action, 
the character closest to the front of the ram makes an attack roll against the 
AC of the construction, applying the -4 penalty for lack of proficiency. (It's 
not possible to be proficient with this device.) In addition to the damage given 
on Table: Siege Engines, up to nine other characters holding the ram can add their 
Strength modifier to the ram's damage, if they devote an attack action to doing 
so. It takes at least one Huge or larger creature, two Large creatures, four Medium-size 
creatures, or eight Small creatures to swing a ram. (Tiny or smaller creatures 
can't use a ram.)

A ram is typically 30 feet long. In a battle, the creatures wielding the ram stand 
in two adjacent columns of equal length, with the ram between them.

\textbf{Siege Tower:} This device is a massive wooden tower on wheels or rollers 
that can be rolled up against a wall to allow attackers to scale the tower and 
thus to get to the top of the wall with cover. The wooden walls are usually 1 foot 
thick.

A typical siege tower takes up a space 15 feet across. The creatures inside push 
it at a speed of 10 feet (and a siege tower can't run). The eight creatures pushing 
on the ground floor have total cover, and those on higher floors get improved cover 
and can fire through arrow slits.

%%%
\subsubsection{City Streets}
%%%

Typical city streets are narrow and twisting. Most streets average 15 to 20 feet 
wide [(1d4+1)x5 feet)], while alleys range from 10 feet wide 
to only 5 feet. Cobblestones in good condition allow normal movement, but ones 
in poor repair and heavily rutted dirt streets are considered light rubble, increasing 
the DC of \linkskill{Balance} and \linkskill{Tumble} checks by 2.

Some cities have no larger thoroughfares, particularly cities that gradually grew 
from small settlements to larger cities. Cities that are planned, or perhaps have 
suffered a major fire that allowed authorities to construct new roads through formerly 
inhabited areas, might have a few larger streets through town. These main roads 
are 25 feet wide -- offering room for wagons to pass each other -- with 5-foot-wide 
sidewalks on either side.

\textbf{Crowds:} Urban streets are often full of people going about their daily 
lives. In most cases, it isn't necessary to put every 1st-level commoner on the 
map when a fight breaks out on the city's main thoroughfare. Instead just indicate 
which squares on the map contain crowds. If crowds see something obviously dangerous, 
they'll move away at 30 feet per round at initiative count 0. It takes 2 squares 
of movement to enter a square with crowds. The crowds provide cover for anyone 
who does so, enabling a Hide check and providing a bonus to Armor Class and on 
Reflex saves.

\textit{Directing Crowds:} It takes a DC 15 \linkskill{Diplomacy} check or DC 20 \linkskill{Intimidate} 
check to convince a crowd to move in a particular direction, and the crowd must 
be able to hear or see the character making the attempt. It takes a full-round 
action to make the Diplomacy check, but only a free action to make the Intimidate 
check.

If two or more characters are trying to direct a crowd in different directions, 
they make opposed Diplomacy or Intimidate checks to determine whom the crowd listens 
to. The crowd ignores everyone if none of the characters' check results beat the 
DCs given above.

%%%
\subsubsection{Above and beneath the Streets}
%%%

\textbf{Rooftops:} Getting to a roof usually requires climbing a wall (see the 
Walls section), unless the character can reach a roof by jumping down from a higher 
window, balcony, or bridge. Flat roofs, common only in warm climates (accumulated 
snow can cause a flat roof to collapse), are easy to run across. Moving along the 
peak of a roof requires a DC 20 Balance check. Moving on an angled roof surface 
without changing altitude (moving parallel to the peak, in other words) requires 
a DC 15 Balance check. Moving up and down across the peak of a roof requires a 
DC 10 Balance check.

Eventually a character runs out of roof, requiring a long jump across to the next 
roof or down to the ground. The distance to the next closest roof is usually 1d3x5 
feet horizontally, but the roof across the gap is equally likely to be 5 feet higher, 
5 feet lower, or the same height. Use the guidelines in the \linkskill{Jump} skill 
(a horizontal jump's peak height is one-fourth of the horizontal distance) to 
determine whether a character can make a jump.

\textbf{Sewers:} To get into the sewers, most characters open a grate (a full-round 
action) and jump down 10 feet. Sewers are built exactly like dungeons, except that 
they're much more likely to have floors that are slippery or covered with water. 
Sewers are also similar to dungeons in terms of creatures liable to be encountered 
therein. Some cities were built atop the ruins of older civilizations, so their 
sewers sometimes lead to treasures and dangers from a bygone age.

%%%
\subsubsection{City Buildings}
%%%

Most city buildings fall into three categories. The majority of buildings in the 
city are two to five stories high, built side by side to form long rows separated 
by secondary or main streets. These row houses usually have businesses on the ground 
floor, with offices or apartments above.

Inns, successful businesses, and large warehouses -- as well as millers, tanners, 
and other businesses that require extra space -- are generally large, free-standing 
buildings with up to five stories. 

Finally, small residences, shops, warehouses, or storage sheds are simple, one-story 
wooden buildings, especially if they're in poorer neighborhoods.

Most city buildings are made of a combination of stone or clay brick (on the lower 
one or two stories) and timbers (for the upper stories, interior walls, and floors). 
Roofs are a mixture of boards, thatch, and slates, sealed with pitch. A typical 
lower-story wall is 1 foot thick, with AC 3, hardness 8, 90 hp, and a Climb DC 
of 25. Upper-story walls are 6 inches thick, with AC 3, hardness 5, 60 hp, and 
a \linkskill{Climb} DC of 21. Exterior doors on most buildings are good wooden doors that are 
usually kept locked, except on public buildings such as shops and taverns.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buying Buildings}
%%%%%%%%%%%%%%%%%%%%%%%%%

Characters might want to buy their own buildings or even construct

their own castle. Use the prices in Table: Buildings directly, or as a guide when 
for extrapolating costs for more exotic structures.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Building Prices}
\centering
\begin{tabular}{l r}
\textbf{Building} & \textbf{Cost}\\
Simple House & 1,000gp\\
Grand House & 5,000gp\\
Mansion & 100,000gp\\
Tower & 50,000gp\\
Keep & 150,000gp\\
Castle & 500,000gp\\
Huge Castle & 1,000,000gp\\
Moat with Bridge & 50,000gp\\
\end{tabular}
\end{table}

\textit{Simple House:} This one- to three-room house is made of wood and has a 
thatched roof.

\textit{Grand House:} This four- to ten-room house is made of wood and has a thatched 
roof.

\textit{Mansion:} This ten- to twenty-room residence has two or three stories and 
is made of wood and brick. It has a slate roof.

\textit{Tower:} This round or square, three-level tower is made of stone.

\textit{Keep:} This fortified stone building has fifteen to twenty-five rooms.

\textit{Castle:} A castle is a keep surrounded by a 15-foot stone wall with four 
towers. The wall is 10 feet thick.

\textit{Huge Castle:} A huge castle is a particularly large keep with numerous 
associated buildings (stables, forge, granaries, and so on) and an elaborate 20-foot-high 
wall that creates bailey and courtyard areas. The wall has six towers and is 10 
feet thick.

\textit{Moat with Bridge:} The moat is 15 feet deep and 30 feet wide. The bridge 
may be a wooden drawbridge or a permanent stone structure.

%%%
\subsubsection{City Lights}
%%%

If a city has main thoroughfares, they are lined with lanterns hanging at a height 
of 7 feet from building awnings. These lanterns are spaced 60 feet apart, so their 
illumination is all but continuous. Secondary streets and alleys are not lit; it 
is common for citizens to hire lantern-bearers when going out after dark.

Alleys can be dark places even in daylight, thanks to the shadows of the tall buildings 
that surround them. A dark alley in daylight is rarely dark enough to afford true 
concealment, but it can lend a +2 circumstance bonus on \linkskill{Hide} checks.
