\subsubsection{Elemental Feats}

A feat with the [Elemental] tag can only be taken by a creature who is from an inner plane or any Elemental or Outsider with an elemental subtype. The abilities granted by feats with the [Elemental] tag are Extraordinary abilities unless otherwise stated. If the feat has another similar (such as [Fiend], [Celestial], or [Fey]), a creature who fulfills the criteria for the other tag may waive this requirement.

\descfeat{Abode of Earth[Elemental]}{You are at home within the earth.}
\ability{Prerequisites:}{(Earth) subtype, Burrow speed, Character level 3+}
\ability{Benefits:}{Your Burrow speed improves by 10' or to a minimum of 30', and you may burrow through rock.  You may leave a tunnel or leave the earth behind you undisturbed, as you choose.  If you leave the earth undisturbed, there is no sign of your passage unless you are in a square adjacent to a surface, except to creatures with Tremorsense or who make the Perception check to hear you.  The Perception check is not made more difficult by the earth you are in, just by distance through it.  Other rocks and earthen walls do interfere as normal.}

\descfeat{Adept Flyer[Elemental]}{You are a natural flyer.}
\ability{Prerequisites:}{(Air) subtype, Fly speed, Character level 5+}
\ability{Benefits:}{Your Fly speed improves to twice your base land speed (minimum 60'), or +10', whichever is more, and your maneuverability improves to Perfect.  Your Fly speed improves by 20' for every five character levels you gain beyond 5th.}

\descfeat{Binding Growth[Elemental]}{You grow on people.}
\ability{Prerequisite:}{Wood Elemental Creature (e.g., Psuedoelemental Being (Wood) feat)}
\ability{Benefit:}{After pinning or lifting a creature for a round, you may attempt to grow a Binding Growth on them with another grapple check against a DC of 10 + their Grapple modifier.  Once you do so, they are bound, losing their Dexterity bonus to AC and their ability to take physical actions other than try to escape, until they break the bonds.  The bonds can be broken by others with a slashing melee weapon capable of doing 5 + your hit dice points of damage against AC 5+your Constitution modifier, but a miss hurts the bound creature, or by a Strength check (DC 15 + your Constitution modifier) or Escape Artist check (DC 10 + your hit dice + your Constitution modifier).  Even once broken, they remain on for 1d4 rounds, entangling the bound creature.}

\descfeat{Blazing Speed[Elemental, Racial]}{You streak across the battlefield like a flaming meteor.}
\ability{Prerequisites:}{Burn, Firebodied}
\ability{Benefits:}{Your base land speed improves to 50', and your base Climb speed improves to 30'.  You gain a +4 dodge bonus to AC against attacks of opportunity provoked due to your movement through a threatened area.  You may also take a full round action to move twice your speed in any movement mode in a straight line.  When you do so, you may move through any number of enemies equal to or less than the number of attacks you would be allowed in a full attack.  You may not move through enemies more than one size larger than you.  When you do so, follow the following steps:

\begin{list}{}{\itemspace}
    \item 1) Opponent chooses to let you by?  Yes, go to 2.  No, go to 3.
    \item 2) Opponent makes Reflex save against your Burn ability.  You continue moving and may pick a new target. End.
    \item 3) Opponent makes an attack of opportunity provoked by your entering their space.  Go to 4.
    \item 4) You make a Trip attack.  You do not need to make an initial touch attack.  Your opponent is affected by your Burn ability as though by a failed save.  Did you trip them?  No: Go to 5.  Yes: Go to 6
    \item 5) Opponent makes attack of opportunity on you unless you have the Edge.  Did they hit you and either apply damage or make a successful combat maneuver (Disarm, Trip, Grapple, etc)?  Yes: You fall prone in the last space you were in before entering theirs.  No: You continue moving; this attack is completed.  End.
    \item 6) If you have the edge, you may make an attack of opportunity against them for falling (note that they are already on fire).  Regardless, you continue moving; this attack is resolved.  End.
\end{list}}

\descfeat{Breath of the Elements[Elemental]}{You have a breath weapon.}
\ability{Prerequisites:}{Resistance 10+ or immunity to an energy type.}
\ability{Benefits:}{Select an energy type that you meet this feat's prerequisite for and that you do not have a special vulnerability to (either the Vulnerability "ability," or an ability weakened/negated by taking that damage type, such as taking real damage through Regeneration).  You gain a Breath Weapon usable every 5 rounds that inflicts 1d6 damage per hit die you have of that energy type in a 30' cone.  Your Breath Weapon allows a reflex save for half damage, DC 10 + 1/2 your hit dice + your Constitution modifier.}

\descfeat{Burn[Elemental]}{You're hot. You're on fire. You like to burn things.}
\ability{Prerequisites:}{(Fire) Subtype}
\ability{Benefits:}{Anything you hit with your natural weapons or unarmed strikes must make a Reflex save (DC 10 + 1/2 your hit dice + your Constitution modifier) or catch fire until it is put out, taking 1d6 damage per round, plus 1d6 damage per round for five hit dice you have.  Creatures hitting you with natural weapons suffer the same effect.  Any creature grappling you, or that you grapple, is automatically on fire, and cannot be put out until it is no longer grappling you.  Any creature that fails a saving throw against one of your abilities that does fire damage suffers the same effect.}

\descfeat{Double Strike[Elemental]}{You can strike twice as fast.}
\ability{Prerequisites:}{Base Attack Bonus +4 or higher, one Slam natural weapon.}
\ability{Benefit:}{You gain a second Slam natural weapon, identical to the one you already have.  This feat has no effect if you already have two.  Your strength bonus to damage for your slam adjusts to be normal for the new situation.}

\descfeat{Drench[Elemental]}{Your body puts out fires.}
\ability{Prerequisites:}{(Water) Subtype}
\ability{Benefits:}{You can put out fires by touching them.  A nonmagical fire at least two size categories smaller than you can be put out automatically as a free action.  A nonmagical fire your size or smaller takes a standard action.  A magical fire is no action (if instantaneous), or a standard action (if it has a duration of one round or more), and requires a Dispel check (1d20 + your Character level against DC 11 + caster level).  Successfully drenching a fire ends it as \emph{dispel magic} (counterspell, if instantaneous, otherwise targeted).  If the source of the magical fire has multiple distinct parts (such as a \emph{meteor swarm}'s multiple meteors), you only put out the part touching you.  You take no damage from any fire you successfully put out.  Fire creatures are not subject to this effect unless summoned, in which case they behave as magical fires.}

\descfeat{Drowning Grasp[Elemental]}{You drown your enemies in your watery embrace.}
\ability{Prerequisites:}{(Water) Subtype, Character level 3+}
\ability{Benefits:}{You gain the Vortex ability of a Water Elemental.  You gain Improved Grab on one type of natural weapon that you have, such as Slam or Claw, which can only be used for the Hold Down grapple option; if you have no natural weapons, but gain them at a later level, this applies to the first natural weapon you gain and any alike to it.  Also, any creature you have Held Down or Lifted, or any creature Grabbing On to you, is considered to be underwater, and must breathe or hold its breath appropriately.}

\featname{Elemental Aura[Elemental]}
As the Fiend feat with the same name.

\descfeat{Elemental Resistance[Elemental]}{Your elemental heritage gives you the ability to resist energy attacks.}
\ability{Benefit:}{You gain Resistance 2 * Character level to one or two energy types, depending on your elemental subtype.
\begin{list}{}{\itemspace}
    \item Air: Electricity and Cold.
    \item Earth: Acid and Cold
    \item Fire: Cold.  This applies before your Cold Vulnerability is taken into account.
    \item Water: Acid and Electricity
\end{list}}
\ability{Special:}{If you have multiple elemental subtypes, pick one energy type from up to two of those subtypes' list.  If you have the Psuedoelemental Being feat and none of the above Subtypes, instead pick from the list below:
\begin{list}{}{\itemspace}
    \item Ice: Fire.  This applies before your Fire Vulnerability is taken into account.
    \item Shadow: Cold and Fire.
    \item Wood: Acid and Fire.
\end{list}}

\descfeat{Elemental Whirlwind[Elemental]}{You gain the signature ability of Air Elementals to transform into a Whirlwind.}
\ability{Prerequisites:}{(Air) Subtype, Character Level 5+}
\ability{Benefits:}{You gain the Air Elemental's Whirlwind ability.  It is sized, and does damage, as one of your size, but uses your hit dice for its duration.}

\featname{Extra Arms[Elemental]}
As the Fiend feat of the same name except as noted below.

\ability{Prerequsites:}{Character Level 9+, 15+ for 2nd pair.}

\descfeat{Extra Legs[Elemental]}{You are quadrupedal.}
\ability{Benefits:}{You gain +20' to your land speed, and Swim speed if you have one.  This does not affect other movement modes.  You also gain all of the benefits of being quadrupedal (stability and increased carrying capacity), and a +2 bonus on all checks to Trip or Bull Rush enemies.}

\descfeat{Hardiness of the Elements[Elemental, Racial]}{You have astounding physical fortitude due to your elemental nature.}
\ability{Prerequisites:}{Elemental-Bodied}
\ability{Benefits:}{You gain a +4 racial bonus to all saves against Stunning, are immune to Poison and Disease, and your racial bonus to saves against Paralysis improves by +4.  You also gain a 50\% chance to negate any critical hit or sneak attack made against you, instead of a 25\% chance due to your inherent Light Fortification.}

\featname{Huge Size[Elemental]}
As the Fiend feat of the same name, except that, optionally, if your element is Air, Fire, or Shadow, two points of the Strength boost and one point of the natural armor increase for the size increase may be traded to remove the reduction to Dexterity.  You may do this trade twice, giving a final total of STR +4, DEX +2, Natural Armor +1.

\descfeat{Ice Trail[Elemental]}{You leave a trail of ice where-ever you go.}
\ability{Prerequisite:}{Character Level 3+, (Cold) Subtype}
\ability{Benefit:}{Your square counts as if it had the \emph{Grease} spell cast on it, except that the slick is made of ice and has the (Cold) descriptor.  Any square you leave has this effect on it, lasting until the end of your next turn.  You never slip on ice, making you immune to this effect.}

\descfeat{Infusion of Elemental Essence}{You have been infused with the power of one of the elemental planes, granting you an affinity for that element and a small degree of magical power.}
\ability{Benefit:}{You may take any feat with the [Elemental] subtype that you qualify for; additionally, choose an elemental subtype (Air, Earth, Fire, or Water), and you may take [Elemental] feats as though you had that subtype. You also gain Resistance 10 to an energy type dependent on your element:

\begin{list}{}{\itemspace}
    \item Air or Earth: Acid or Electricity
    \item Fire: Fire
    \item Water: Acid or Cold
\end{list}
You may select this feat only once.}

\featname{Large Size[Elemental]}
As the Fiend feat of the same name, except that, optionally, two points of the Strength boost and one point of the Natural Armor increase for the size increase may be traded to remove the reduction to Dexterity. You may do this trade twice, for a final total of STR +4, Dex +2, Natural Armor +0.

\descfeat{Primal Armor[Elemental]}{Your body deflects blows off of itself.}
\ability{Benefit:}{You gain impenetrable Damage Reduction equal to half your character level, rounded up (1/- at first level, 2/- at 3rd, 5/- at 9th, 10/- at 19th).}

\descfeat{Primal Fortification[Elemental, Racial]}{Your body has become even more impenetrable.}
\ability{Prerequisite:}{Elemental-Bodied, Hardiness of the Elements}
\ability{Benefit:}{You gain immunity to Critical Hits.  You also cannot be flanked, as your undiffentiated body has no clear front or back.}

\descfeat{Psuedoelemental Being[Racial]}{You are a psuedoelemental being, with rare and unique powers.}
\ability{Prerequisite:}{Elemental-Bodied.}
\ability{Benefits:}{Instead of picking a normal elemental type as an elemental-bodied, select one of the following other planes: Ice, Magma, Shadow, or Wood.  You gain benefits as follows for the type you've picked:
\begin{list}{}{\itemspace}
    \item Ice: You gain the (Cold) subtype, a 30' base land speed, a 30' swim speed, and +2 to Str.  Your melee attacks do 1d6 bonus Cold damage.  You speak Aquan and Auran.
    \item Magma: You gain both the (Earth) and (Fire) subtypes. Your base land speed is 20', and you gain +2 Str. Otherwise you gain the full benefits of both elements.
    \item Shadow: You have a 30' base land speed and a Fly speed of 10', with good maneuverability, and gain +2 Dex. You are \emph{invisible} in any lighting less than bright light. You speak Common. Despite your affiliation to the Plane of Shadow instead of to the Inner Planes, you still qualify for [Elemental] feats.
    \item Wood: You have no elemental subtype, and gain +2 Con and a 10' Climb speed. You gain Regeneration 0, penetrable by Fire and Slashing weapons, which improves to Regeneration equal to your level in areas of natural daylight or equivalent brightness (such as a \emph{daylight} spell). You only gain natural healing if you spend at least 8 hours/day in such brightness. You count as a Plant, in addition to an Elemental, for all effects relating to type. You speak your choice of Sylvan or Treant, and any Elemental language.
\end{list}
Other Dual-element types than Magma, such as Ooze (Water and Earth), Smoke (Air and Fire), Vapor (Water and Air), and so on are possible.}
\ability{Special:}{This feat can only be taken at 1st level.}

\descfeat{Sphere Focus[Monstrous]}{You can draw on the power of a specific Sphere more easily.}
\ability{Prerequisite:}{Access to at least one Sphere}
\ability{Benefit:}{Select a Sphere that you know.  The DC of any saving throw against spell-like abilities from that Sphere increases by 1.}
\ability{Special:}{You may select this feat multiple times.  Its effects do not stack.  Each time you take this feat, it applies to a different Sphere.}

\featname{Stolen Breath[Elemental]}
As the [ Fiend ] feat of the same name, except where noted below.
\ability{Prerequisites:}{(Air) Subtype or Drowning Grasp, Character level 3+}

\descfeat{Tremorsense[Elemental]}{Your close connection to your home element gives you Tremorsense.}
\ability{Prerequisites:}{(Earth) or (Water) Subtype, Character level 6+}
\ability{Benefits:}{You gain Tremorsense out to 120'.  You gain Blindsight out to 30' against any creature you can Tremorsense.  If you have the (Water) subtype and not the (Earth) subtype, your Tremorsense works at its full range in liquids, but only to half range and you do not gain Blindsight through solids.}

\descfeat{Touch of Shadow[Elemental]}{Your shadowy touch can bypass armor.}
\ability{Prerequisite:}{Shadow Elemental Creature (Psuedoelemental Being (Shadow), Shadow Genasi, or similar), Natural weapon, Character Level 3+}
\ability{Benefit:}{You may choose to make natural weapon attacks as touch attacks.  Such attacks use your Dexterity bonus to hit, instead of Strength, and do not gain Strength to damage.}

\descfeat{Uncanny Flexibility[Elemental, Racial]}{Your body, being made of a material other than flesh, bends in directions and places that flesh neither can  nor should.}
\ability{Prerequisite:}{Airbodied, Firebodied, or Waterbodied; or Psuedoelemental Being (Magma or Shadow).}
\ability{Benefit:}{You gain a +4 bonus to Escape Artist checks, and Escape Artist is always a class skill for you.  You can compress your head to about half area for purposes of slipping through tight spaces, and may attempt to slip manacles, ropes, webs, nets, grapplers, and similar bonds as a free action.}

\descfeat{Unstoppable Force[Elemental, Racial]}{You cannot be stopped.}
\ability{Prerequisites:}{Elemental-Bodied, Hardiness of the Elements}
\ability{Benefit:}{You become immune to paralysis and stunning.}