%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

erial is Open Game Content, and is licensed for public use under 
the terms of the Open Game License v1.0a.}

\section*{{\LARGE SALIENT DIVINE ABILITIES}}

\vspace{12pt}
A salient divine ability is like a feat---it gives a deity a new capability or 
improves one that the deity already has. A deity has one salient divine ability 
for each divine rank the deity has, plus additional salient divine abilities reflecting 
its status: Demigods receive one bonus ability, lesser deities receive two bonus 
abilities, intermediate deities receive three, and greater deities receive five. 

Some salient divine abilities have prerequisites. Usually, the deity must have 
all the listed prerequisites to have the ability. A divine rank of 1 is a prerequisite 
for all salient divine abilities. The most common salient divine abilities are 
described here. A few deities have unique salient divine abilities that are described 
in the deity's individual entry.

\vspace{12pt}
\textbf{Using Salient Divine Abilities:} Using a salient divine ability is a standard 
action unless otherwise noted in the ability description. Using a salient divine 
ability does not provoke an attack of opportunity.

\vspace{12pt}
\textbf{Salient Divine Abilities and Antimagic:} A salient divine ability functions 
normally within an antimagic field, and is never subject to spell resistance.

\vspace{12pt}
\section*{Salient Divine Ability Descriptions}

Here is the format for salient divine ability descriptions.

\vspace{12pt}
\subsection*{Ability Name}

\textbf{Prerequisite:} A minimum divine rank, minimum ability score, another salient 
divine ability, a minimum base attack bonus, a feat, a skill, or some other condition 
that a deity must have in order to acquire this salient divine ability. This entry 
is absent if a salient divine ability has no prerequisite. An ability may have 
more than one prerequisite. All salient divine abilities have a minimum prerequisite 
of divine rank 1. Quasi-deities (rank 0) have no salient divine abilities.

\textbf{Benefit:} What the ability enables the deity to do. If a deity has the 
same ability more than once, its benefits do not stack unless indicated otherwise 
in the description. In general, having a salient divine ability twice is the same 
as having it once.

\textbf{Notes:} Additional facts about the ability that may be helpful when using 
the ability in play.

\textbf{Rest:} Some abilities require the deity to rest afterward. If no rest is 
required, the entry is absent. A resting deity can engage in light activities such 
as talking or walking at half speed. When attempting anything more strenuous than 
that, the deity can only take partial actions and suffers a -6 penalty on all attack 
rolls, saves, and checks. The deity cannot use another ability that requires rest 
until its current rest requirement is fulfilled. Any time the deity spends performing 
strenuous activities does not count toward the required rest time. 

\textbf{Suggested Portfolio Elements:} This entry gives one or more portfolio elements 
that are associated with the salient divine ability in question. The information 
is provided as guidance and should not be taken as a rule.

\vspace{24pt}
\section*{Alter Form}

This is an extraordinary ability.

\textbf{Prerequisite:} Alter Size salient divine ability.

\textbf{Benefit:} As a move-equivalent action, the deity can alter its form, including 
clothing and equipment. The assumed form must be corporeal. The deity's body can 
undergo a limited physical transmutation, including adding or subtracting one or 
two limbs. If the form selected has wings, the deity can fly. Likewise, the deity 
can swim if the form has fins, breathe water if the form has gills, and so on.

The deity can remain in the altered form indefinitely, but resumes its own form 
if slain.

\textbf{Notes:} The deity's attack bonus, Armor Class, and saves do not change. 
The deity does not gain any of the assumed form's special abilities, attack forms, 
defenses, ability scores, or mannerisms. The deity can change physical qualities 
(such as hair color, hair

texture, skin color, and gender). The deity can use this ability to create disguises, 
gaining a bonus of +10 on its Disguise checks. The deity can use its Alter Size 
ability simultaneously along with this one to become taller, shorter, thinner, 
or heavier.

\textbf{Suggested Portfolio Elements:} Nature, secrets, thieves.

\vspace{12pt}
\section*{Alter Reality}

\textbf{Prerequisite:} Cha 29.

\textbf{Benefit:} This ability is similar to the \textit{wish }spell. The deity 
merely thinks of something and then makes it so. Doing this requires at least a 
standard action.

\textbf{Notes:} The deity can duplicate any spell of 9th level or lower as a standard 
action. The duplicated spell has no material or XP component, and the DC of its 
saving throw (if one is allowed) is 20 + the deity's rank + the deity's Charisma 
modifier. 

The deity also can duplicate a spell with any metamagic feat (so long as the metamagic 
feat is available to characters of 20th level or lower). This use of the ability 
requires the deity to rest for 1 round for each level that the feat would normally 
add to the spell. It still takes a standard action to use this ability, so there 
is no point in using the ability to duplicate a quickened spell. 

The deity can render a magical or supernatural effect permanent. The rest requirement 
varies with the effect: 10 minutes per level of the effect times the number of 
subjects affected, 10 minutes per total Hit Dice of creatures affected, or 10 minutes 
per 10-foot cube affected. Use the highest applicable value. 

The deity can create temporary, nonmagical objects. This works like the Create 
Object ability (including the required rest period), except that the items last 
one day per rank.

The deity also can create permanent nonmagical objects as if using the Create Object 
ability except that all rest requirements are doubled and there is no reduction 
in rest time for being on an Outer Plane or in the deity's own realm. 

The deity can create temporary magic items or creatures. This works like the Divine 
Creation ability (including the required rest period), except that the items or 
creatures created last 1 hour per rank. This ability cannot create permanent magic 
items or creatures. 

The deity can reshape a landscape, creating any type of terrain the deity can imagine. 
Each 10-foot cube of material to be reshaped requires 1 round of effort, and the 
deity must rest for one day per 10-foot cube shaped after the work is completed.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Alter Size}

\textbf{Benefit:} As a free action, the deity can assume any size from Fine to 
Colossal. The deity also can change the size of up to 100 pounds of objects it 
touches. If the deity has a familiar, personal mount, or personal intelligent weapon, 
the creature can change size with the deity if the deity touches it, but its weight 
counts against the deity's weight limit. This is a supernatural ability.

\textbf{Notes:} This ability allows the deity to assume any proportions from the 
size of a grain of sand up or as much as 1,600 feet tall. A radical change in size 
can have great impact on the deity's combat ability. The deity's Strength, Armor 
Class, attack bonus, and damage dealt with weapons changes according to the size 
the deity assumes. The deity's Strength

score can never be reduced to less than 1 through this ability. Also note that 
use of this divine ability does not affect all the deities' characteristics.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Annihilating Strike}

\textbf{Prerequisites:} Divine rank 11, base attack bonus +20, Str 25.

\textbf{Benefit:} When the deity strikes with a weapon or natural weapon, the opponent 
struck might be obliterated. Creatures, attended objects, and magic items must 
make Fortitude saves (DC 20 + the deity's rank + the damage dealt) or be reduced 
to -10 hit points and killed outright. Unattended, nonmagical objects are obliterated. 
The deity can destroy up to 1,000 cubic feet (a 10-foot cube) of nonliving matter 
per rank, so the ability destroys only part of any very large object or structure 
targeted.

\textbf{Notes:} Deities with a rank equal to or greater than the attacking deity 
are not subject to this ability. This ability has no effect on objects or effects 
that are not subject to physical attacks.

\textbf{Suggested Portfolio Elements:} Death, justice, vengeance, war.

\vspace{12pt}
\section*{Arcane Mastery}

\textbf{Prerequisites:} Spellcaster level 1st, Int 29, Spell Mastery.

\textbf{Benefit:} The deity can prepare any wizard spell that it can cast without 
using a spellbook.

\textbf{Notes:} This ability gives the deity access to every spell on the sorcerer/wizard 
spell list, provided that the deity has sufficient wizard levels and a sufficient 
Intelligence score to cast them. The deity also can invent new sorcerer/wizard 
spells without researching them.

\textbf{Suggested Portfolio Elements:} Knowledge, magic.

\vspace{12pt}
\section*{Area Divine Shield}

\textbf{Prerequisites:} Divine rank 6, Cha 29, Divine Shield salient divine ability.

\textbf{Benefit:} Except where noted here, this ability works like the Divine Shield 
ability. The deity produces a transparent barrier whose area is up to one 10-foot 
square per rank, or a sphere or hemisphere with a radius of up to 1 foot per rank. 
The barrier can be placed anywhere within the deity's line of sight. The deity 
can place the barrier so that it is mobile with respect to some unattended object 
or willing creature. The barrier can be adjusted to ignore certain types of damage, 
just as a divine shield can. If the deity makes the shield mobile with respect 
to a willing creature, the deity also can make the barrier

one-way with respect to the creature and its allies, allowing them to attack through 
the shield and still use its protection.

\textbf{Notes:} The deity can shape the shield around itself or around a willing 
creature so that it is skintight, which prevents the subject from being touched.

\textbf{Suggested Portfolio Elements:} Mercy, protection.

\vspace{12pt}
\section*{Automatic Metamagic}

\textbf{Prerequisite:} Spellcaster level 1st.

\textbf{Benefit:} The deity chooses one metamagic feat. As a free action, the deity 
can apply the selected feat to the spells from any one spellcasting class the deity 
has or to its spell-like abilities. A spell altered by the use of this ability 
does not use up a higher-level slot.

\textbf{Notes:} The deity must obey all the limitations normally associated with 
the metamagic feat. Any metamagic feat selected cannot have a level requirement 
of 21st or higher. Feats that depend on making the spell's level higher, such as 
Heighten Spell, do not work with this ability. A deity can have this ability multiple 
times, choosing a metamagic feat and either a spellcasting class or spell-like 
abilities to which the ability will apply each time.

\textbf{Suggested Portfolio Elements:} Knowledge, magic.

\vspace{12pt}
\section*{Avatar}

\textbf{Prerequisites:} Divine rank 6, Cha 29.

\textbf{Benefit:} An avatar serves as a deity's alter ego, effectively allowing 
the deity to be in two or more places at the same time. An avatar is an extension 
of a deity. The deity senses and knows everything the avatar senses and knows and 
vice versa. Each avatar counts as a remote location where the deity is sensing 
and communicating. A lesser deity can have up to five avatars at once, an intermediate 
deity can have up to ten, and a greater deity can have up to twenty avatars at 
once. It takes a deity one year to create an avatar or replace a destroyed avatar. 
The process does not require any special effort on the deity's

part. An avatar must be created in the deity's own realm. If the deity has the 
Divine Creation salient divine ability, the deity can use it to create a new avatar 
anywhere. However, the deity must rest afterward as noted in the Divine Creation 
ability description. An avatar is a less powerful version of a deity, created by 
modifying the deity's statistics, that has the following characteristics.

\textit{Divine Rank:} The avatar's divine rank is half that of the deity (round 
down). This decrease in divine rank affects many of the avatar's statistics and 
abilities, including bonuses to attack rolls, damage, saves, checks, and Armor 
Class, damage reduction, resistances, number of salient divine abilities and bonus 
salient divine abilities, uses per day of domain powers, saving throw DCs against 
spell-like abilities, range of senses, automatic actions, magic items it can create, 
and extent of divine aura. The deity's ability scores, speed, class levels, and 
Hit Dice are unchanged.

\textit{Divine Abilities:} The avatar has salient divine abilities according to 
its own divine rank. The deity chooses which of its abilities the avatar has when 
creating the avatar. The avatar cannot have a salient divine ability that is not 
available to a deity of its own rank,

nor can it use a salient divine ability if it doesn't meet the prerequisites. An 
avatar cannot have the Avatar or Possess Mortal salient divine abilities.

An avatar does not have any remote sensing or remote communication powers.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Banestrike}

\textbf{Prerequisite:} Base attack bonus +20.

\textbf{Benefit:} Any weapon the deity weilds gains a bonus of +4 on attack rolls, 
and it deals an extra +4d6 points of damage against the designated foe. The bonus 
and extra damage stack with any other properties the weapon has.

\textbf{Notes:} The deity selects one kind of enemy from the list below.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Aberrations \end{minipage}} & \multicolumn{1}{p{2.006in}|}{\begin{minipage}[t]{2.006in}\raggedright
Oozes\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Animals \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Outsiders, chaotic\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Beasts \end{minipage}} & \multicolumn{1}{p{2.006in}|}{\begin{minipage}[t]{2.006in}\raggedright
Outsiders, evil\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Constructs \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Outsiders, good\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Dragons \end{minipage}} & \multicolumn{3}{p{2.144in}|}{\begin{minipage}[t]{2.144in}\raggedright
Outsiders, lawful\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Elementals\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Plants\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Fey \end{minipage}} & \multicolumn{3}{p{2.144in}|}{\begin{minipage}[t]{2.144in}\raggedright
Undead\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Giants \end{minipage}} & \multicolumn{3}{p{2.144in}|}{\begin{minipage}[t]{2.144in}\raggedright
Vermin\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.389in}|}{\begin{minipage}[t]{1.389in}\raggedright
Monstrous humanoids\end{minipage}} & \multicolumn{3}{p{2.144in}|}{\begin{minipage}[t]{2.144in}\raggedright
Humanoids (choose one subtype)\end{minipage}}\\
\hline
\end{longtable}

The ability functions only when the deity personally attacks with a melee weapon 
or ranged weapon. The deity can apply the Banestrike ability to any weapon or natural 
weapon, but not to a spell, spell-like ability, supernatural ability, or divine 
ability.

A deity can have this ability multiple times, choosing a different kind of foe 
each time. The deity can imbue only one bane special ability to a weapon at a time 
and can change among them once a round as a free action.

\textbf{Suggested Portfolio Elements:} Death, justice, vengeance, war.

\vspace{12pt}
\section*{Battlesense}

\textbf{Benefit:} The deity cannot be surprised or flanked except by a deity of 
higher rank. The deity retains its Dexterity bonus to Armor Class even if caught 
flat-footed or attacked by an invisible opponent, and is not subject to sneak attacks 
except by deities of higher rank.

\textbf{Notes:} If the deity has the uncanny dodge or improved uncanny dodge class 
feature, this ability replaces it.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Call Creatures}

\textbf{Benefit:} The kind of creature the deity can call is noted in the deity's 
description. Each creature called can have no more Hit Dice than the deity has 
divine ranks, and the deity cannot have more creatures serving it at any given 
time than the deity has ranks. The creatures are transported to the deity's presence 
through an interdimensional connection similar to that created by a \textit{gate 
}spell, except that it opens to the Material Plane. The creatures willingly serve 
to the best of their ability. The calling effect is otherwise similar

to the calling property of the \textit{gate }spell.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
kind of creature each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Clearsight}

\textbf{Prerequisites:} Divine rank 6, Wis 29.

\textbf{Benefit:} The deity can see illusions, transmuted creatures and objects, 
and disguised creatures or objects for what they really are, provided they are 
within 10 feet per divine rank of the deity. This ability is similar to the \textit{true 
seeing }spell, except that it does not reveal creatures' alignments and it does 
foil mundane disguises.

\textbf{Suggested Portfolio Elements:} Knowledge, truth.

\vspace{12pt}
\section*{Command Plants}

\textbf{Benefit:} The deity can make plants grow in a radius of up to one mile 
per divine rank once per day. The deity can use this ability even in a place where 
no plants grow, though in this case the plants wither and die after one day. This 
ability works like the \textit{plant growth }spell, except that it cannot be countered 
except by a deity of higher rank than the deity using the ability. 

Also once per day, the deity can charm plant creatures, animate plants, or make 
them entangle its foes. This ability functions like the \textit{command plants 
}spell, except that its maximum duration is one day no matter which option the 
deity chooses. At any one time, the deity can charm a number of plant creatures 
equal to its divine rank with this ability, regardless of Hit Dice.

\textbf{Suggested Portfolio Elements:} Agriculture, earth, fertility.

\vspace{12pt}
\section*{Control Creatures}

\textbf{Benefit:} The deity can command some kind of creature as noted in the deity's 
description. This ability is similar to the \textit{dominate monster }spell, but 
it is not a mind-affecting ability (the deity seizes direct control over the creature's 
body). Each day the deity can attempt to control a number of creature equal to 
its divine rank. The deity can attempt to take control of that number all at once, 
or in smaller numbers. All creatures to

be affected must be within the deity's line of sight when first affected. Once 
control is established, distance is not a factor and the deity can maintain control 
remotely, even across planes and through wards or barriers (except divine shields 
and warding spells cast by deities of higher rank than the deity using the ability). 
The subject is allowed a Will save (DC 10 + the deity's rank + the deity's Charisma 
modifier) to resist and is allowed a

new save if the deity commands the subject to do something against its nature.

At any given time, the deity cannot have more creatures under its control than 
10 times its divine rank. If the deity already has the maximum number of creatures 
under its control, it can still attempt to take control of other creatures, but 
must first release

one or more creatures already under its control. 

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
kind of creature each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Craft Artifact}

\textbf{Prerequisites:} Craft Magic Arms and Armor, Craft Rod, Craft Staff, Craft 
Wand, Craft Wondrous Item, Forge Ring, Scribe Scroll.

\textbf{Benefit:} The deity can craft magic arms and armor, staffs, wands, wondrous 
items, rings, and scrolls that exceed the normal limits for such items

\textbf{Suggested Portfolio Elements:} Crafts, knowledge, magic.

\vspace{12pt}
\section*{Create Object}

\textbf{Prerequisites:} Divine rank 6, Int 29.

\textbf{Benefit:} As a full-round action, the deity can create one or more simple, 
nonmagical objects with a total weight of up to 50 pounds per divine rank, or with 
a total volume of 10 cubic feet per rank. If the deity uses this ability on a divinely 
morphic plane or within its own godly realm, double the volume and weight the deity 
can create. If the deity's realm is located on a divinely morphic plane, triple 
the volume and weight the deity can create there.

\textbf{Notes:} For purposes of this ability, a simple object can have no moving 
parts more complex than a door hinge and must be composed of a single material. 
The material can be no more valuable than iron (1 sp per pound). Once created, 
the objects are permanent and nonmagical. If the deity has the appropriate Craft 
skill, the deity can make a Craft

check when creating the item to make it a masterwork item.

\textbf{Suggested Portfolio Elements:} Crafts, creation.

\vspace{12pt}
\section*{Create Greater Object}

\textbf{Prerequisites:} Divine rank 11, Int 29, Create Object salient divine ability.

\textbf{Benefit:} As a full-round action, the deity can create objects weighing 
up to 100 pounds per divine rank, or with a volume of 20 cubic feet per rank. If 
the deity uses this ability on a divinely morphic plane or within its own godly 
realm, double the volume and

weight the deity can create. If the deity's realm is located on a divinely morphic 
plane, triple the volume and weight the deity can create there.

\textbf{Notes:} This ability works like the Create Object ability, except as noted 
below. A deity can use this ability to create any kind of nonmagical object.

\textbf{Rest:} The deity must convert a considerable amount of its own energy into 
the object, which can leave the deity impaired. The deity can create an object 
with a value of up to 100 gp without impairment. For every additional 100 gp of 
value (or fraction of 100

gp), the deity must rest for 10 minutes. If the deity is creating an item on a 
divinely morphic plane or within its own godly realm, it can create a 200 gp item 
without resting. If the deity's realm is located on a divinely morphic plane, it 
can create a 300 gp item

there without having to rest.

\textbf{Suggested Portfolio Elements:} Crafts, creation.

\vspace{12pt}
\section*{Divine Air Mastery}

\textbf{Prerequisite:} Air domain.

\textbf{Benefit:} The deity gains a competence bonus on attack rolls, damage, and 
Armor Class equal to its divine rank if both the deity and its foe are airborne. 
The deity can fly with perfect maneuverability. When flying, the deity can automatically 
know the location of

any corporeal creature within 10 feet per divine rank, by sensing the disturbance 
in the air the creature causes.

\textbf{Suggested Portfolio Elements:} Air, wind.

\vspace{12pt}
\section*{Divine Archery}

\textbf{Prerequisites:} Base attack bonus +20, Dex 29, Point Blank Shot, Far Shot.

\textbf{Benefit:} The deity can fire a ranged weapon at any target within line 
of sight and within range of the deity's personal senses. No range increment applies 
to the attack. The deity does not incur any attacks of opportunity for firing a 
bow when threatened. As a full-round action, the deity may fire an arrow at her 
full base attack bonus at each opponent within 10 feet per divine rank. The deity 
must have the Weapon Focus feat with the type of bow she uses to perform this attack. 
When shooting a ranged weapon, the deity can ignore any cover bonus to the target's 
AC or any miss chance conferred by the

target's concealment.

\textbf{Suggested Portfolio Elements:} Archers, war.

\vspace{12pt}
\section*{Divine Armor Mastery}

\textbf{Prerequisites:} Armor Proficiency (light), Armor Proficiency (medium).

\textbf{Benefit:} The deity ignores the maximum Dexterity bonus limit for medium 
or light armor.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Divine Bard}

\textbf{Prerequisite:} Bard level 20th.

\textbf{Benefit:} This ability has several benefits:•

For the deity's bardic abilities that have a range (countersong, \textit{fascinate, 
}inspire competence, inspire greatness), that range is a number of miles equal 
to the deity's divine rank.•

The deity can use any bardic music inspiration ability as a standard action. The 
inspiration takes effect immediately after the deity concludes the action.•

The deity's bardic music abilities can affect even those normally immune to mind-affecting 
effects. However, such creatures gain a +10 bonus on their Will saves to resist 
such effects.•

The effects of all the deity's bardic music abilities are doubled. Inspire courage 
grants a +8 morale bonus on saving throws against charm and fear effects and a 
+8 morale bonus on attack and damage rolls; inspire competence grants a +4 competence 
bonus on skill checks; inspire greatness grants +4d10 Hit Dice, a +4 competence 
bonus on attack rolls, and a +2 competence bonus on Fortitude saves, and inspire 
heroics grants a +8 morale bonus on saving throws and a +8 dodge bonus to AC. The 
number of allies the deity can affect with inspire competence, inspire greatness, 
and inspire heroics doubles. When inspiring competence in multiple allies, the 
deity can choose different skills to inspire for different allies.•

The effects of the deity's bardic music inspiration abilities last for ten times 
as long as normal after the deity stops singing. This has no effect on inspiration 
abilities that have no duration after the bard stops singing.•

When any effect that is subject to countersong (any spell, supernatural ability, 
or spell-like effect that has the sonic or language-dependent desriptor) occurs 
within the deity's hearing, the deity can attempt a countersong as if it had prepared 
an action to do so.

\textbf{Suggested Portfolio Elements:} Art, bards, beauty, dance, love, music, 
poetry.

\vspace{12pt}
\section*{Divine Battle Mastery}

\textbf{Prerequisites:} Fighter level 20th, Combat Reflexes, Int 13, Dex 13, Dodge, 
Expertise, Mobility, Spring Attack, Whirlwind Attack, War domain.

\textbf{Benefit:} The deity can make an unlimited number of attacks of opportunity 
in one round. (The deity still can't make more than one attack of opportunity against 
a single opponent in a round.) As a full-round action, the deity may make one melee 
attack at its full base attack bonus against each opponent within reach. The deity 
does not incur any attacks of opportunity from this action.

\textbf{Suggested Portfolio Elements:} Justice, vengeance, war.

\vspace{12pt}
\section*{Divine Blast}

\textbf{Prerequisite:} Cha 29.

\textbf{Benefit:} The deity can use this ability a number of times per day equal 
to 3 + its Charisma bonus. The ray created can extend up to one mile per rank (the 
deity chooses the length). Targets the ray strikes take 1d12 points of damage per 
rank of the deity, plus 1d12

points of damage per point of Charisma bonus the deity has. There is no saving 
throw, but the deity must make a ranged touch attack to hit a target. The deity 
can make the ray look, sound, smell, and feel like any-thing it desires. Despite 
the appearance of the ray,

the damage it deals results directly from divine power and is therefore not subject 
to being reduced by \textit{protection from elements }and similar magic.

\textbf{Notes:} The ray destroys a \textit{wall of force, prismatic wall, }or \textit{prismatic 
sphere }it hits (all layers in a prismatic effect are destroyed). The ray itself 
is unaffected and can strike a target behind the \textit{wall of force }or prismatic 
effect.

A divine shield can stop the ray.

\textbf{Suggested Portfolio Elements:} Death, destruction, war.

\vspace{12pt}
\section*{Divine Blessing}

\textbf{Prerequisite:} Selected ability score 40.

\textbf{Benefit:} Choose one ability: Strength, Dexterity, Constitution, Intelligence, 
Wisdom, or Charisma. The deity must have a score of at least 40 in the selected 
ability. The deity can grant mortals a +6 enhancement bonus to that ability that 
lasts for one day. In a single day and at one time, the deity can affect a number 
of creatures equal to its divine rank.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
ability score each time.

\textbf{Suggested Portfolio Elements:} Agility, beauty, endurance, knowledge, strength, 
wisdom.

\vspace{12pt}
\section*{Divine Celerity}

\textbf{Prerequisite:} Dex 29.

\textbf{Benefit:} The deity acts as if \textit{hasted }for a number of minutes 
per day equal to its divine rank. The duration of the effect need not be consecutive 
rounds. Activating this ability is a free action.

\textbf{Suggested Portfolio Elements:} Travel, wind.

\vspace{12pt}
\section*{Divine Creation}

\textbf{Prerequisites:} Divine rank 16, Int 29, Create Object salient divine ability, 
Create Greater Object salient divine ability.

\textbf{Benefit:} As a full-round action, the deity can create mortal creatures 
or magic items whose total weight is up to 100 pounds per divine rank, or with 
a total volume of 20 cubic feet per rank. If the deity uses this ability on a divinely 
morphic plane or within its

own godly realm, double the volume and weight the deity can create. If the deity's 
realm is located on a divinely morphic plane, triple the volume and weight the 
deity can create there.

\textbf{Notes:} This ability works like the Create Greater Object ability, except 
as noted below.

A deity can use this ability to create any kind of creature that does not have 
a divine rank. The deity can create a creature with class levels, but never with 
more class levels than the deity has itself or the deity's divine rank, whichever 
is lower.

\textbf{Rest:} The deity must convert a considerable amount of its own energy into 
a creature, which always leaves the deity impaired. The deity must rest for 10 
minutes \ensuremath{\times}the creature's Hit Dice \ensuremath{\times}the creature's 
Challenge Rating for each creature created, with a minimum of 10 minutes per creature. 
If the creature has class levels, each level counts as an additional Hit Die. 

The deity can create any kind of magic item except an artifact.

The rest requirement for creating magic items is the same as for the Create Greater 
object ability.

\textbf{Suggested Portfolio Elements:} Crafts, creation, supreme.

\vspace{12pt}
\section*{Divine Dodge}

\textbf{Prerequisite:} Dex 29.

\textbf{Benefit:} Any physical attack or individually targeted spell directed at 
the deity has a percent miss chance equal to 50 + the deity's rank. Area effects 
that include the deity have a similar chance to be ineffective.

\textbf{Notes:} The ability is similar to the \textit{blink }spell, except that 
it is defensive only and the deity does not move to the Ethereal Plane, but simply 
exits from reality for a brief moment. This ability never interferes with the deity's 
own attacks. If an attack overcomes the miss chance, the deity still gets the benefit 
of a saving throw (if one is allowed).

\textbf{Suggested Portfolio Elements:} Agility, gambling, luck, protection.

\vspace{12pt}
\section*{Divine Druid}

\textbf{Prerequisites:} Druid level 20th.

\textbf{Benefit:} While in a \textit{wild shap}e, the deity gains all the extraordinary 
and supernatural abilities of the creature whose form it adopts. In addition to 
animal forms, the deity can take the form of magical beasts or plant creatures. 
Some deities can assume additional forms. These are specified in the deity's description.

The deity can assume the form of any animal, magical beast, or plant creature from 
Fine to Colossal in size.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Divine Earth Mastery}

\textbf{Prerequisites:} Earth domain.

\textbf{Benefit:} The deity gains a competence bonus on attack rolls, damage, and 
Armor Class equal to its divine rank if both the deity and its foe are touching 
the ground. The deity gains a burrow speed commensurate with its size (see Divine 
Characteristics), as well as the ability to glide through stone, dirt, or almost 
any other sort of earth except metal as easily as a fish swims through water. This 
burrowing leaves behind no tunnel or hole, nor does it create any ripple or other 
signs of its presence. The deity has tremorsense, allowing it to automatically 
sense the location of anything within 10 feet per divine rank that is in contact 
with the ground. The deity has complete control over all things made of earth (including 
stone and metal). It can alter the form of any amount of earth as a free action. 
The deity can duplicate the effects of the \textit{stone shape, move earth, rusting 
grasp, transmute rock to mud, transmute mud to rock, }and \textit{disintegrate 
}spells, with any earth, stone, or metal object as a target. The deity can also 
transmute any object made of earth,

stone, or metal into a different kind of earth, stone, or metal. The deity can 
affect any object it can see, but no more than one object per round.

\textbf{Suggested Portfolio Elements:} Earth.

\vspace{12pt}
\section*{Divine Fast Healing}

\textbf{Prerequisites:} Con 29 or the fast healing special quality.

\textbf{Benefit:} The deity gains fast healing of 20 + divine rank. Lost limbs 
or body parts reattach instantly when pressed against the wound on the body.

\textbf{Notes:} This ability does not stack with the fast healing special quality.

\textbf{Notes:} A deity can have this ability multiple times, and its effects stack. 
A deity with two applications of this ability improves its fast healing by 40 + 
(divine rank \ensuremath{\times}2).

\textbf{Suggested Portfolio Elements:} Endurance, healing.

\vspace{12pt}
\section*{Divine Fire Mastery}

\textbf{Prerequisites:} Fire domain.

\textbf{Benefit:} The deity gains a competence bonus on attack rolls, damage, and 
Armor Class equal to its divine rank if both the deity and its foe are touching 
fire or using weapons with the flaming or flaming burst special abilities.

The deity is immune to the effects of fire and heat.

The deity can automatically know the location of any corporeal creature within 
10 feet per divine rank by sensing the disturbance in the ambient temperature that 
the creature causes.

The deity has complete control over all nonmagical fire and can duplicate the effect 
of any spell with the fire descriptor as a standard action.

\textbf{Suggested Portfolio Elements:} Fire.

\vspace{12pt}
\section*{Divine Glibness}

\textbf{Prerequisites:} Cha 29, Bluff 40 ranks, Trickery domain.

\textbf{Benefit:} As a full-round action, the deity can speak and convince others 
to take some course of action. This works like a \textit{mass suggestion }spell 
cast at a level equal to 10 + the deity's divine rank, except that it affects up 
to (10 + divine rank) creatures, no two of

which can be more than (10 \ensuremath{\times}divine rank) feet apart. The save 
DC is 10 + the deity's Charisma modifier + the deity's divine rank.

\textbf{Suggested Portfolio Elements:} Commerce, lies, thieves.

\vspace{12pt}
\section*{Divine Inspiration}

\textbf{Benefit:} The deity can enchant creatures to create a specific emotion. 
The deity can affect one creature per divine rank at once, and up to the same number 
each day. All must be within the deity's line of sight when first affected. The 
specific effects depend on the

emotional state induced.

\textit{Courage:} The enchanted creatures become immune to fear effects and receive 
a +2 morale bonus on attack rolls, weapon damage rolls, skill checks, and Will 
saves.

\textit{Despair:} The enchanted creatures are affected as by an improved version 
of the \textit{crushing despair} spell: affected creatures suffer a -4 penalty 
on attack rolls, damage rolls, saves, and checks\textit{ }unless they make a successful 
Will save (DC 10 + deity's Charisma modifier + deity's divine rank). The effect 
lasts one day.

\textit{Dread:} The enchanted creatures must make successful Wisdom checks (DC 
= the deity's divine rank) to attack or fight. If the check fails, the creature 
flees in panic for 1d4 rounds. If the check succeeds, the creature does not have 
to check again for

10 minutes. The enchanted creatures also suffer a -2 morale penalty on attack rolls, 
weapon damage rolls, skill checks, and Will saves.

\textit{Frenzy:} Frenzied creatures spend themselves in drinking, feasting, and 
dancing unless provoked or incited to violence. Frenzied creatures turn violent 
if they are attacked or perceive a threat to their safety. Frenzied creatures receive 
a +4 morale bonus to Strength and Dexterity, a -4 penalty to Wisdom, and a -2 penalty 
to AC. Subjects can attempt Will saves (DC 10 + deity's Charisma modifier + deity's 
divine rank) to resist the effect. This is a mind-affecting compulsion.

\textit{Hope:} The enchanted creatures gain a +4 morale bonus on saving throws, 
attack rolls, ability checks, skill checks, and weapon damage rolls.

\textit{Rage:} The enchanted creatures receive a +4 morale bonus to Strength and 
Constitution scores, a +2 morale bonus on Will saves, and a -2 penalty to AC. They 
are compelled to fight heedless of danger. Subjects can attempt Will saves (DC 
10 + deity's Charisma

modifier + deity's divine rank) to resist the effect. This is a mind-affecting 
compulsion.

\textit{Love and Desire:} A love effect causes the target to fall in love with 
the specified creature, seeking every opportunity to be near that creature and 
making every effort to win the creature's affection. A desire effect is similar, 
but the target seeks any opportunity to

become physically intimate with the specified creature. Subjects can attempt Will 
saves (DC 10 + deity's Charisma modifier + deity's divine rank) to resist the effect. 
This is a mind-affecting compulsion effect.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Divine Monk}

\textbf{Prerequisites:} Monk level 20th.

\textbf{Benefit:} The deity's unarmed strikes are treated as a magic slashing weapon 
with an enhancement bonus of +5 and the keen, lawful, and vorpal qualities. If 
the deity chooses, a particular attack can be bludgeoning instead of slashing, 
but the keen and vorpal qualities do not apply to that attack. Any unarmed attack 
the deity makes has a base damage of 2d12.

The deity can use the Deflect Arrows feat to deflect any ranged attacks (including 
spells that require ranged touch attacks) as if they were arrows. The deity can 
deflect any number of attacks in a single round. When the deity deflects any attack, 
the attack is reflected upon the attacker, using the deity's base ranged attack 
bonus. When the deity deflects a spell, the spell's level is added to the DC to 
deflect the attack.  The deity only gains the second benefit of this ability if 
he or she has the Deflect Arrows feat.

\textbf{Suggested Portfolio Elements:} Law.

\vspace{12pt}
\section*{Divine Paladin}

\textbf{Prerequisites:} Paladin level 20th.

\textbf{Benefit:} The deity's aura of courage grants a +8 morale bonus on saving 
throws against fear effects and extends to all allies within 100 feet of the deity. 

The deity's special mount, if any, gains the celestial template. 

The deity can smite evil ten times per day, and gets an extra 3 points of damage 
per class level on a successful smite attempt.

\textbf{Suggested Portfolio Elements:} Good, justice, law, nobility, war.

\vspace{12pt}
\section*{Divine Radiance}

\textbf{Prerequisite:} Good alignment, Sun domain.

\textbf{Benefit:} The deity can shed light in a (10 feet \ensuremath{\times}divine 
rank) emanation from its body. This light counters and dispels all darkness effects 
(unless created by a deity of higher rank) and causes pain and damage to undead 
creatures, who take 2d8 points of damage per round with no save. As a full attack 
action, the deity can generate up to three rays of scorching light that can strike 
targets up to a number of miles away equal to the deity's divine rank. Each ray 
deals 1d6 points of damage per 2 divine ranks. Undead take 1d12 points of damage 
per 2 divine ranks.

\textbf{Suggested Portfolio Elements:} Good, light, sun.

\vspace{12pt}
\section*{Divine Rage}

\textbf{Prerequisite:} Barbarian level 20th.

\textbf{Benefit:} This ability is similar to the barbarian's rage ability (and 
it replaces the barbarian rage ability for the deity). The deity can activate this 
ability only after suffering damage from a weapon, and can use it a number of times 
per day equal to its divine rank. Once used, the ability lasts 1 hour (though the 
deity can end the rage at will). While raging, the deity gains +10 to Strength, 
+10 to Constitution, and a +5 morale bonus on Will saves. The deity's spell resistance 
and energy resistances each increase by +10. The deity also can make one extra 
attack, at its full attack bonus, whenever it uses the full attack action. While 
raging, the deity suffers a -5 penalty to Armor Class and cannot perform acts that 
require patience and concentration, such as moving silently, casting spells, and 
using salient divine abilities.

\textbf{Suggested Portfolio Elements:} Destruction, rage, strength, war.

\vspace{12pt}
\section*{Divine Ranger}

\textbf{Prerequisites:} Ranger level 20th, Wis 25, Wilderness Lore 40 ranks, Knowledge 
(nature) 30 ranks.

\textbf{Benefit:} Any weapon the deity wields against one of its favored enemies 
is treated as a bane weapon against that creature type. Thus, its enhancement bonus 
is increased by +2 and it deals +2d6 points of damage.

The deity can follow tracks at its normal land speed. It treats all normal terrain 
as very soft ground for purposes of tracking and ignores DC modifiers for time 
or weather. The deity can track creatures across water, underwater, or through 
the air by means of the minute disturbances they make and traces of their passage. 
The table below adds across water, underwater, and air to the list of surfaces 
found in the Track feat description.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.949in}|}{\begin{minipage}[t]{0.949in}\raggedright
\textbf{Surface}\end{minipage}} & \multicolumn{1}{p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedleft
\textbf{DC}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Across water\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
60\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.949in}|}{\begin{minipage}[t]{0.949in}\raggedleft
Underwater \end{minipage}} & \multicolumn{1}{p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedleft
80\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Air \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
120\end{minipage}}\\
\hline
\end{longtable}

\textbf{Suggested Portfolio Elements:} Archers, hunting, nature.

\vspace{12pt}
\section*{Divine Recall}

\textbf{Benefit:} The deity remembers every event of a certain type that has ever 
occurred. The type of event is specified in the deity description.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
type of event each time.

\textbf{Suggested Portfolio Elements:} Knowledge.

\vspace{12pt}
\section*{Divine Rogue}

\textbf{Prerequisites:} Rogue level 20th, Dodge, improved evasion, defensive roll.

\textbf{Benefit:} When struck by an attack from an opponent the deity has designated 
as its dodge target, the deity may make a Reflex save (DC 10 + damage dealt) to 
negate all damage from the attack.

If the deity passes within 5 feet of a trap, the deity is entitled to a Search 
check to notice it as if the deity were actively looking for it.

The deity can assess the exact value of any treasure it can see.

The deity also can immediately determine what any creature is carrying and where 
each carried item is.

\textbf{Suggested Portfolio Elements:} Thieves.

\vspace{12pt}
\section*{Divine Shield}

\textbf{Prerequisites:} Cha 29.

\textbf{Benefit:} As a free action, the deity can create a shield that lasts 10 
minutes and protects the deity's body and equipment from attacks. The shield stops 
10 points of damage per rank. Once the shield stops that much damage, it collapses. 
The damage can be from any source, including a divine blast attack. The deity can 
use this ability a number of times per day equal to 3 + its Constitution bonus.

\textbf{Notes:} The deity can adjust the shield so that it does not block damage 
the deity ignores anyway. The effects of multiple divine shields do not stack.

\textbf{Suggested Portfolio Elements:} Protection.

\vspace{12pt}
\section*{Divine Skill Focus}

\textbf{Prerequisites:} 23 ranks in the selected skill.

\textbf{Benefit:} The deity receives a bonus of 10 + its divine rank when using 
the skill selected.

\textbf{Notes:} This bonus stacks with the divine rank bonus deities normally receive 
on checks. If the selected skill is related to the deity's portfolio, add the deity's 
rank to the maximum DC for a free action.

A deity can have this ability multiple times, choosing a different skill each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Divine Sneak Attack}

\textbf{Prerequisites:} Sneak attack +10d6, crippling strike.

\textbf{Benefit:} The deity's sneak attacks deal an additional +3d6 points of damage.

Any attack of opportunity the deity makes is considered a sneak attack.

The deity can flank or catch flat-footed any opponent whose divine rank does not 
exceed the deity's and can sneak attack that opponent. The deity cannot deal sneak 
attack damage to opponents that are immune to critical hits. Any time the deity 
inflicts damage with a sneak attack, that target suffers damage equal to the deity's 
sneak attack bonus

damage on the deity's next turn as well. 

\textbf{Suggested Portfolio Elements:} Thieves.

\vspace{12pt}
\section*{Divine Spell Focus}

\textbf{Prerequisites:} Spell Focus, Greater Spell Focus.

\textbf{Benefit:} The deity chooses one school of magic. The save DC for any spell 
of that school increases by one-half the deity's divine rank. This bonus overlaps 
(does not stack with) the bonus from Spell Focus or Greater Spell Focus.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
school of magic each time.

\textbf{Suggested Portfolio Elements:} Magic.

\vspace{12pt}
\section*{Divine Spellcasting}

\textbf{Prerequisites:} Spellcaster level 20th.

\textbf{Benefit:} The deity can cast spells whose effective level is above 9th. 
The number of spells per day the deity can cast of each spell level above 9th depends 
on the deity's key ability score for spell-casting classes in which the deity has 
achieved 20th level, as shown

on Table: Divine Spellcasting. The numbers on that table represent one spell per 
day at each spell level above 9th in which it receives bonus spells from its key 
ability score, plus

bonus spells based on the key ability score. The deity can use these slots for 
spells prepared or cast with a metamagic feat, or for lower-level spells. 

If the deity has achieved 20th level in a spellcasting class with fewer than nine 
levels of spells (such as bard, paladin, or ranger), the deity can also cast one 
spell per day of each level between the maximum normal spell level and 9th, plus 
appropriate bonus spells

of each level based on the deity's key ability score. These spells are not shown 
on the table. 

The deity also doesn't incur attacks of opportunity for casting spells when threatened.

In addition, the deity receives the benefit of the Spell Focus feat on any spell 
it casts.

\textbf{Suggested Portfolio Elements:} Magic.

\vspace{12pt}
\subsection*{\textbf{Spell Slots Above 9th Level}}

The Divine Spellcasting ability grants deities access to spell slots above 9th 
level (which can be used to hold lower-level spells or spells whose level has been 
increased above 9th by the use of metamagic feats). The number of spell slots available 
to a deity depends on the deity's key ability score (Intelligence for wizards, 
Wisdom for clerics, druids, paladins, and rangers, and Charisma for bards and sorcerers), 
as shown on Table: Divine Spellcasting.

Even though the table only includes ability scores up to 61 and spell slots up 
to 25th level, the progression continues infinitely in both directions. For ability 
scores beyond 61, or for spell slots above 25th level, expand the table to follow 
the same patterns

as shown.

The numbers on this table include bonus spells that a deity receives for having 
a sufficiently high ability score, as well as one additional spell of each level 
at which the deity gains at least one bonus spell. This additional spell is one 
of the benefits of the

Divine Spellcasting salient divine ability.

\vspace{12pt}
\subsection*{\textbf{Table: Divine Spellcasting}}

\subsection*{\begin{longtable}{lllllllllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{3}{|p{0.577in}|}{\begin{minipage}[t]{0.577in}\centering
\end{minipage}} & \multicolumn{16}{p{3.301in}|}{\begin{minipage}[t]{3.301in}\centering
---------------------------------------------\textbf{ Spells per Day -----------------------------------------------------}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
\textbf{Score}\end{minipage}} & \multicolumn{17}{p{0.588in}|}{\begin{minipage}[t]{0.588in}\raggedright
\textbf{Modifier}\end{minipage}} & \multicolumn{1}{|p{0.240in}|}{\begin{minipage}[t]{0.240in}\raggedright
\textbf{10th}\end{minipage}} & \multicolumn{2}{p{0.336in}|}{\begin{minipage}[t]{0.336in}\raggedright
\textbf{11th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{12th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{13th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{14th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{15th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{16th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{17th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{18th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{19th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{20th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{21st}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{22nd}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
\textbf{23rd}\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
\textbf{24th}\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
\textbf{25th}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
10-11\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
+0\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
12-13\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+1\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
14-15\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
+2\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
16-17\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+3\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
18-19\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+4\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
20-21\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+5\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
22-23\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+6\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
24-25\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+7\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
26-27\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+8\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
28-29\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+9\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
30-31\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+10\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
32-33\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+11\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
34-35\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+12\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
36-37\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+13\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
38-39\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+14\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
40-41\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+15\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
42-43\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+16\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
44-45\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+17\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
46-47\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+18\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
48-49\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+19\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
50-51\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+20\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 24
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
52-53\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+21\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 25
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
54-55\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+22\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 26
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
56-57\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+23\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 27
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
58-59\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+24\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 28
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
60-61\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+25\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
2\end{minipage}}\\
\hline
% ROW 29
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
etc. . . \end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
\end{minipage}}\\
\hline
\end{longtable}
}

\vspace{12pt}
\section*{Divine Splendor}

\textbf{Prerequisites:} Divine rank 16, Cha 26.

\textbf{Benefit:} Any mortal who approaches within 10 feet per divine rank of the 
deity in its natural form dies immediately, with no saving throw.

\textbf{Suggested Portfolio Elements:} Supreme.

\vspace{12pt}
\section*{Divine Storm}

\textbf{Prerequisite:} Divine rank 11.

\textbf{Benefit:} The deity can surround itself with a vortex of holy or unholy 
force that manifests in different forms depending on the deity. The vortex extends 
from the deity in an emanation with a radius of 10 feet per divine rank. The effect 
stops attacks with thrown weapons and projectiles (they fail if made by creatures 
inside the area, or targeted at creatures within the area, or if their paths take 
them through the area).

In addition, the force expels creatures whose alignment on the ethical (lawful-chaotic) 
axis is opposite the deity's. If the deity's ethical alignment is neutral (neutral 
good or neutral evil), the force does not expel any creatures. Affected creatures 
in the area must make Fortitude saves (DC 10 + the deity's Charisma modifier + 
the deity's divine rank) or be picked up and thrown out, regardless of size. Such 
creatures suffer 1d6 points of

damage for each 10 feet they travel. Creatures that make successful saves are not 
affected by the vortex for one day, although the vortex still stops their thrown 
weapons and projectiles. Creatures that fail their saves can attempt to reenter 
the area, but must attempt new saves.

The force damages creatures whose alignment on the moral (good-evil) axis is opposite 
the deity's. If the deity's moral alignment is neutral (lawful neutral or chaotic 
neutral), the force does not damage any creatures. Affected creatures in the area 
must make Fortitude saves (DC 10 + the deity's Charisma modifier + the deity's 
divine rank) each round or suffer 1 point of holy damage per divine rank. A successful 
save negates the damage, but the creature must save again the next round if it 
is still within the area.

Creatures whose alignment is diametrically opposed to the deity's are subject to 
both effects.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Divine Water Mastery}

\textbf{Prerequisites:} Water domain.

\textbf{Benefit:} The deity gains a competence bonus on attack, damage, and Armor 
Class equal to its divine rank if both the deity and its foe are touching the same 
body of water.

The deity gains a swim speed commensurate with its size (see Divine Characteristics).

At will, as a full-round action, the deity can create a devastating tidal wave 
of water. On land, the wave has effects similar to a flash flood: Creatures caught 
in the water must

make a Fortitude save (DC 15). Large or smaller creatures that fail the save are 
swept

away, taking 1d6 points of subdual damage per round (1d3 points on a successful

Swim check against DC 20). Huge creatures that fail are knocked down, while Gar-gantuan 
and Colossal creatures are checked. The wave destroys all wooden buildings and

25\% of the stone buildings it comes into contact with. At sea, the tidal wave 
capsizes ships and crushes them to splinters. The wave affects a number of miles 
of coastland up to the deity's divine rank. 

When touching water, the deity can automatically sense the location of anything 
within 10 feet per divine rank that is in contact with the same body of water.

\textbf{Suggested Portfolio Elements:} Water.

\vspace{12pt}
\section*{Divine Weapon Focus}

\textbf{Benefit:} This ability works like the Weapon Focus feat except that the 
deity receives a bonus of +4 on attacks with the weapon. 

\textbf{Notes:} This bonus stacks with the divine rank bonus deities get on attack 
rolls, and with the Divine Weapon Mastery salient divine ability. It also stacks 
with the Weapon Focus and Greater Weapon Focus feats.

A deity can have this ability multiple times, choosing a different kind of weapon 
each time.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Divine Weapon Mastery}

\textbf{Prerequisites:} Fighter level 20th, War domain.

\textbf{Benefit:} The deity receives the benefits of the Weapon Focus, Weapon Specialization, 
and Improved Critical feats when wielding any simple or martial weapon. 

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Divine Weapon Specialization}

\textbf{Prerequisites:} Base attack bonus +20, Divine Weapon Focus salient divine 
ability with the selected weapon.

\textbf{Benefit:} This ability works like the fighter's Weapon Specialization feat, 
except that the deity receives a bonus on damage with the weapon equal to its divine 
rank.

\textbf{Notes:} If the selected weapon is a ranged weapon, the extra damage applies 
against any target the deity can see.

The damage bonus from this ability stacks with the damage bonus from the Divine 
Weapon Mastery ability and the Weapon Specialization and Greater Weapon Specialization 
feats.

A deity can have this ability multiple times, choosing a different kind of weapon 
each time.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Energy Burst}

\textbf{Benefit:} The deity can create an emanation of a specific type of energy 
(acid, cold, electricity, fire, or sonic energy, specified in the deity's description) 
with a radius of 10 feet per divine rank. Anything in the area takes 1d8 points 
of the appropriate energy damage per divine rank. Damage is halved for those who 
make successful saving throws (Reflex for acid, cold, electricity, or fire, or 
Fortitude for sonic energy; DC 10 + the deity's divine rank + the deity's Constitution 
modifier).

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
type of energy each time.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Energy Storm}

\textbf{Prerequisite:} Divine rank 11.

\textbf{Benefit:} The deity can surround itself with a vortex of energy (acid, 
cold, electricity, fire, sonic, positive, or negative energy, specified in the 
deity's description). The vortex extends from the deity in an emanation with a 
radius of 10 feet per divine rank. The effect

stops attacks with thrown weapons and projectiles. Such attacks fail if made by 
creatures inside the area, or targeted at creatures within the area, or if their 
paths take them through the area.

Energy storms that use acid, cold, electricity, fire, or sonic energy deal 1 point 
of energy damage and 1 point of holy damage per divine rank each round.

Positive energy deals 1 point of damage per divine rank to undead creatures, and 
heals the same amount of damage on living creatures.

Negative energy deals 1 point of negative energy per divine rank to living creatures, 
and heals the same amount of damage on undead creatures.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
type of energy each time.

\textbf{Suggested Portfolio Elements:} Fire, storms.

\vspace{12pt}
\section*{Extra Domain}

\textbf{Prerequisite:} Divine rank 6.

\textbf{Benefit:} The deity chooses one domain to add to its list of domains. The 
deity can grant spells and powers from that domain and use those spells and powers 
personally, just as it can the spells and powers of its other domains.

\textbf{Notes:} A deity can have this ability multiple times, choosing a new domain 
each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Extra Energy Immunity}

\textbf{Prerequisites:} Divine rank 6, resistance to the energy type selected.

\textbf{Benefit:} The deity gains immunity to acid, cold, electricity, fire, or 
sonic energy.

\textbf{Notes:} This ability is effective even if the attacker is a deity of higher 
rank.

A deity can have this ability multiple times, choosing a different form of energy 
each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Extra Sense Enhancement}

\textbf{Prerequisites:} Wis 29.

\textbf{Benefit:} The deity chooses one sense to enhance. The ability can extend 
a sense's range one mile per divine rank, or it can allow the sense to ignore one 
type of physical or magical blockage. The enhanced sense can penetrate 10 feet 
of a physical barrier per rank or 100 feet of a less tangible barrier (such as 
fog or smoke) per rank.

\textbf{Notes:} Some deities have specific applications of this ability that go 
beyond the normal senses.

A deity can have this ability multiple times, choosing a different sense each time.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Footsore}

\textbf{Prerequisites:} Travel domain.

\textbf{Benefit:} The deity can sap the energy from living creatures so that they 
feel tired. It can affect up to one creature per divine rank at once, but no more 
than one creature per divine rank each day. All must be within the deity's line 
of sight when first affected. Subjects

can attempt Fortitude saves (DC 10 + deity's Charisma modifier + deity's divine 
rank). Creatures who fail their saves become fatigued and their speed is reduced 
by half. Furthermore, any mount or vehicle they ride is likewise slowed. The effect 
lasts one day.

\textbf{Suggested Portfolio Elements:} Travel.

\vspace{12pt}
\section*{Free Move}

\textbf{Prerequisites:} Dex 29, Divine Celerity salient divine ability.

\textbf{Benefit:} The deity can move up to its speed once a round as a free action.

\textbf{Suggested Portfolio Elements:} Travel.

\vspace{12pt}
\section*{Frightful Presence}

\textbf{Prerequisites:} Cha 24.

\textbf{Benefit:} Whenever the deity performs a specific action specified in the 
deity's description (usually attacking, but sometimes making an intimidating gesture), 
foes within a 30-foot-radius burst must make Will saves (DC 10 + deity's Charisma 
modifier + deity's divine rank). Foes within the burst, but not the deity's immediate 
target, become shaken for 3d6 rounds if they fail their saves. Creatures the deity 
attacks when it activates the ability become panicked for 3d6 rounds if they fail 
their saves. Foes who make successful saving throws are unaffected by this ability 
for one day.

\textbf{Suggested Portfolio Elements:} Destruction, war.

\vspace{12pt}
\section*{Gift of Life}

\textbf{Benefit:} The deity restores the dead creature to life, no matter how long 
the creature has been dead or what the condition of the body.

\textbf{Notes:} This ability works like the \textit{true resurrection }spell, except 
that there is no material component and the amount of time the subject has been 
dead is irrelevant.

This ability can restore a creature to life against its will, but only with the 
permission of whatever deity rules the underworld or the divine realm where the 
mortal's soul resides. This ability can resurrect an elemental or outsider and 
can resurrect a creature whose soul is trapped, provided the soul is not held by 
a deity of higher rank than the one using this ability.

This ability cannot restore life to a creature that has been slain by the Hand 
of Death ability or the Life and Death ability of a deity with a higher rank.

\textbf{Suggested Portfolio Elements:} Healing, life.

\vspace{12pt}
\section*{Grow Creature}

\textbf{Benefit:} This ability works like the \textit{animal growth }spell, except 
that it can affect up to one creature of the specified type per divine rank each 
day, all of which must be within the deity's line of sight when first affected. 
The effect lasts one day.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
type of creature each time.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Hand of Death}

\textbf{Benefit:} The deity points to any mortal within the deity's sensory range 
and snuffs out its life. There must be an unbroken line of effect between the deity 
and the target.

\textbf{Notes:} This ability works like the \textit{destruction }spell, except 
that there is no material component. The mortal is allowed a Fortitude saving throw 
with a DC of 20 + the deity's Charisma bonus + the deity's divine rank. Even if 
the save succeeds, the subject takes 10d6 points of damage, which may kill it anyway. 
If the attack kills the mortal (either through a failed saving throw or through 
damage), the mortal cannot be raised or resurrected afterward, except by a deity 
of equal or higher rank using the Gift of Life, Life and Death, or Mass Life and 
Death salient divine ability.

\textbf{Suggested Portfolio Elements:} Death.

\vspace{12pt}
\section*{Increased Damage Reduction}

\textbf{Prerequisites:} Con 29.

\textbf{Benefit:} The deity's damage reduction increases 5 and adds an alignment 
requirement opposed to the deity's alignment to bypass the damage reduction. For 
example, a lawful good deity with DR25/epic would gain DR 30/epic and evil or DR 
30 epic and chaotic. 

\textbf{Notes:} A deity cannot chose this ability more than once.

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Increased Energy Resistance}

\textbf{Benefit:} The deity gains resistance equal to its divine rank to acid, 
cold, electricity, fire, or sonic energy. 

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
form of energy each time. The deity also can have this ability more than once for 
a single type of energy. When applied to an energy type that the deity already 
resists, this ability increases the resistance by 10. 

\textbf{Suggested Portfolio Elements:} Any.

\vspace{12pt}
\section*{Increased Spell Resistance}

\textbf{Benefit:} The deity's spell resistance increases by 20.

\textbf{Notes:} A deity can have this ability multiple times, and its effects stack. 
A deity with two applications of this ability improves its spell resistance by 
40.

\textbf{Suggested Portfolio Elements:} Magic.

\vspace{12pt}
\section*{Indomitable Strength}

\textbf{Prerequisite:} Str 40, Strength domain.

\textbf{Benefit:} If required to make an opposed roll involving Strength (including 
grapple checks), the deity receives a divine bonus of +25 on its roll. This bonus 
stacks with the normal divine rank bonus.

\textbf{Suggested Portfolio Elements:} Strength.

\vspace{12pt}
\section*{Instant Counterspell}

\textbf{Benefit:} When any spell is cast within the deity's line of sight, the 
deity can counterspell it as a free action, provided that the deity is capable 
of casting the spell immediately or has it as a spell-like ability and makes the 
required Spellcraft check. The use of Instant

Counterspell counts against the normal number of free actions the deity is allowed 
each round.

\textbf{Suggested Portfolio Elements:} Magic.

\vspace{12pt}
\section*{Instant Move}

\textbf{Prerequisites:} Divine rank 6, Dex 29.

\textbf{Benefit:} As a move action, the deity can travel up to 30 feet per divine 
rank, as though using the \textit{dimension door }spell, except that the deity 
never appears within a solid object and can act immediately after teleporting.

\textbf{Suggested Portfolio Elements:} Travel.

\vspace{12pt}
\section*{Irresistible Blows}

\textbf{Prerequisites:} Weapon Focus and Improved Critical with the selected melee 
weapon.

\textbf{Benefit:} When the deity makes a melee attack with the chosen weapon against 
a creature, resolve the attack as a melee touch attack (the weapon blow ignores 
armor and natural armor bonuses). If the weapon hits, the creature struck must 
make a Fortitude save (DC 10 + the deity's Constitution modifier + the deity's 
divine rank) or be stunned for 1d10 rounds. 

The deity's attacks with the chosen weapons are considered to be adamantine for 
purposes of bypassing damage reduction and hardness.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
kind of weapon each time.

\textbf{Suggested Portfolio Elements:} War.

\vspace{12pt}
\section*{Irresistible Performance}

\textbf{Prerequisites:} Perform 40 ranks.

\textbf{Benefit:} When the deity sings, plays a musical instrument, tells jokes, 
recites verse, or engages in any other type of performance as a full-round action, 
the deity has the option to create any of the following effects. The deity can 
use this ability a number of times per

day equal to its divine rank. It affects up to one creature per divine rank within 
a burst with a radius of 10 feet per divine rank, centered on the deity.•

Affected creatures become unable to take actions; instead, they dance, observe 
the performance with rapt attention, laugh, or applaud at the deity's option. The 
affected creatures also suffer a -4 penalty to Armor Class, cannot succeed at Reflex 
saves (except on a roll of 20), and cannot use shields. Creatures can resist this 
mind effect with a successful Will save (DC 10 + the deity's Charisma modifier 
+ the deity's divine rank). The effects last for as long as the deity performs 
and for up to 1 round per divine rank thereafter.•

Affected creatures become blissfully calm. They are immune to fear and compulsion 
effects except for those created by deities of higher rank than the performing 
deity and any such effects already operating on affected creatures are countered 
and dispelled. This ability also counters and dispels rage effects except for those 
created by deities of higher rank than the performing deity. Immunity to fear and 
compulsion last for as long as the deity performs and for up to 1 round per divine 
rank thereafter.•

Affected creatures fall asleep. This works like the \textit{sleep }spell, except 
that any living creature can be affected. Creatures can resist this mind effect 
with Will saves (DC 10 + the deity's Charisma modifier + the deity's divine rank). 
Affected creatures sleep for up to 1 hour per divine rank or until awakened. The 
deity can end the effect at will.•

Affected creatures are so deeply moved that they simply die. Only living creatures 
with Hit Dice equal to or less than the deity's divine rank are affected. Creatures 
can resist the effect with Fortitude saves (DC 10 + the deity's Charisma modifier 
+ the deity's divine rank).

Once a creature makes a successful save against one of the deity's performances, 
the creature cannot be affected again for one day.

Note: Not all deities with this ability can create all the mentioned effects, as 
specified in the deity descriptions.

\textbf{Suggested Portfolio Elements:} Art, bards, beauty, dance, love, music, 
poetry.

\vspace{12pt}
\section*{Know Death}

\textbf{Benefit:} The deity knows the exact moment and circumstances of any mortal 
creature's death just by looking at the creature.

\textbf{Suggested Portfolio Elements:} Death.

\vspace{12pt}
\section*{Know Secrets}

No secrets can be kept from the deity.

\textbf{Benefit:} The deity can learn a creature's entire history (including any 
embarrassing or vital secrets it might know) just by looking at it. This ability 
is similar to the \textit{legend lore }spell, except that it delivers instant results 
and the subject is allowed a Will save (DC 10 + the deity's Charisma modifier + 
the deity's divine rank) to avoid the effect.

\textbf{Suggested Portfolio Elements:} Knowledge, secrets.

\vspace{12pt}
\section*{Lay Curse}

\textbf{Benefit:} This ability works like the \textit{bestow curse }spell, except 
that mortals get no save. Deities of equal or lesser rank are subject to this ability, 
but are allowed Will saves (DC 10 + the deity's Charisma modifier + the deity's 
divine rank) to resist. The curse

can be removed only by a deity of equal or higher rank than the cursing deity.

The deity can affect up to one creature per divine rank at once, but no more than 
that number each day. All must be within the deity's line of sight when first affected.

\textbf{Suggested Portfolio Elements:} Evil.

\vspace{12pt}
\section*{Lay Quest}

\textbf{Benefit:} This ability works like the \textit{geas/quest }spell, except 
that it works only on mortals and it can be removed only by a deity of equal or 
higher rank than the deity who lays the quest. The deity can affect up to one creature 
per divine rank at once, but no more than that number each day. All must be within 
the deity's line of sight when first affected.

\textbf{Suggested Portfolio Elements:} Justice, law.

\vspace{12pt}
\section*{Life and Death}

\textbf{Prerequisites:} Divine rank 6, Gift of Life or Hand of Death salient divine 
ability.

\textbf{Benefit:} The deity designates any mortal and snuffs out its life. Or the 
deity can designate any dead mortal and restore it to life.

\textbf{Notes:} This ability works across planar boundaries and penetrates any 
barrier except a divine shield. However, the subject must be in a location the 
deity can sense, either within the deity's sense range or in a location the deity 
can perceive through its remote sensing ability. If the deity cannot see the subject, 
the deity must unambiguously identify the subject in some fashion. If the deity 
chooses to kill a mortal, the ability works like the

\textit{destruction }spell, except that there is no material component or saving 
throw. The mortal cannot be raised or resurrected afterward, except by a deity 
of equal or higher rank using the Gift of Life or Life and Death salient divine 
ability.

If the deity restores life to a mortal, this ability works like the \textit{true 
resurrection }spell, except that there is no material component and the amount 
of time the subject has been dead is irrelevant.

This ability cannot restore a creature to life against its will, but it can resurrect 
an elemental or outsider. It can resurrect a creature whose soul is trapped, provided 
the soul is not held by a deity of higher rank than the one using this ability.

This ability cannot restore life to a creature that has been slain by the Hand 
of Death, Life and Death, or Mass Life and Death ability of a deity with a higher 
rank.

\textbf{Rest:} After using either version of this ability, the deity must rest 
for 1 minute per level or Hit Die of the creature affected.

Deities whose portfolio includes death do not have to rest after using this ability.

\textbf{Suggested Portfolio Elements:} Death, supreme.

\vspace{12pt}
\section*{Life Drain}

\textbf{Prerequisites:} Death domain.

\textbf{Benefit:} As a free action, the deity can generate a cloud of darkness 
that rises from its body in a spread with a radius of 10 feet per divine rank and 
10 feet high. The cloud blocks sight as a \textit{deeper darkness }spell does, 
except that it cannot be countered by light

effects (other than those cast by deities of higher rank). Living creatures must 
make Will saves (DC 10 + the deity's Charisma modifier + the deity's divine rank) 
or die. Even with a successful save, living creatures still gain two negative levels 
(the save DC to remove the negative levels is the same as the first Will save). 
A single creature can be drained by the cloud only once per day, but the cloud's 
darkness remains effective.

\textbf{Suggested Portfolio Elements:} Death, undead.

\vspace{12pt}
\section*{Mass Divine Blast}

\textbf{Prerequisites:} Divine rank 6, Cha 29, Divine Blast salient divine ability.

\textbf{Benefit:} This ability works like the Divine Blast ability, except that 
the deity can specify up to five targets per rank, no two of which can be more 
than one mile apart per rank, or an area. The area can be a cone, burst, spread, 
or cylinder. A cone can be up to 100 feet long per rank. A burst or spread can 
have a radius of up to 50 feet per rank. A cylinder can have a radius of up to 
50 feet per rank and a height of up to 10 feet per rank. The deity chooses the 
attack's exact form and dimensions.

Each use of this ability counts as a use of the deity's Divine Blast ability.

\textbf{Suggested Portfolio Elements:} Death, destruction, war.

\vspace{12pt}
\section*{Mass Life and Death}

\textbf{Prerequisites:} Divine rank 16, Gift of Life or Hand of Death salient divine 
ability, Life and Death salient divine ability.

\textbf{Benefit:} The deity can designate any number of mortals and snuffs out 
their lives. Or the deity can designate any number of dead mortals and restore 
them to life.

\textbf{Notes:} No two mortals affected by a single use of this ability can be 
more than one mile apart per rank of the deity. The ability is otherwise identical 
with the Life and Death salient divine ability.

\textbf{Rest:} After using either version of this ability, the deity must rest 
for 1 minute per levels or Hit Dice of the creatures affected.

\textbf{Suggested Portfolio Elements:} Death, supreme.

\vspace{12pt}
\section*{Master Crafter}

\textbf{Prerequisites:} 23 ranks in two different Craft skills.

\textbf{Benefit:} Any object the deity creates is treated as a masterwork item, 
but uses the base item price (not the masterwork price) to determine time and cost 
required to create it. Any item the deity creates also has twice the hit points 
it would normally have, and its

break DC is increased by +10. These benefits apply to walls, doors, and other components 
of buildings the deity creates, as well as smaller items.

\textbf{Suggested Portfolio Elements:} Crafts, creation.

\vspace{12pt}
\section*{Mind of the Beast}

The deity can make plants and animals sentient, and it can reduce sentient creatures 
to animal or plant form.

\textbf{Benefit:} The deity can grant humanlike sentience to trees or animals. 
This sentience lasts a maximum of one day, and the sentient tree or animal obeys 
the deity's commands to the best of its ability. The deity can affect up to one 
creature per divine rank at once, but no more than that number each day. All must 
be within the deity's line of sight when first affected.

Also, the deity can transmute any creature into a plant or animal of approximately 
the same size or up to two size categories smaller. The subject is allowed a Fortitude 
save (DC 10 + the deity's Charisma modifier + the deity's divine rank) to resist. 
Subjects

turned into plants become objects. Subjects turned into animals have the same abilities 
and statistics of the kind of animal the deity chooses.

The Alter Reality ability can make either effect permanent.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Possess Mortal}

\textbf{Prerequisites:} Cha 29.

\textbf{Benefit:} The deity can possess any mortal in any location the deity can 
sense. Unwilling mortals can attempt Will saves (DC 10 + the deity's Charisma modifier 
+ the deity's rank).

\textbf{Notes:} Spells that prevent possession block this ability if the mortal 
is unwilling. Likewise, spells that end possession drive out the deity if the mortal 
is unwilling. If the mortal is willing, however, the deity cannot be blocked or 
driven out, except by a divine

shield or the use of the Alter Reality salient divine ability by a deity of higher 
rank.

The possessed mortal effectively becomes an avatar of the deity. The deity can 
draw on all the possessed mortal's memories, and the deity senses what the mortal 
senses. Each mortal possessed counts as a remote location where the deity is sensing 
and communicating. A demigod can possess up to two mortals at a time, a lesser 
deity can possess up to five mortals at once, an intermediate deity can possess 
up to ten, and a greater deity can possess up to twenty mortals at once.

While the deity is in possession, the mortal's abilities are unchanged, except 
as noted below.

\textit{Type:} Same as the deity.

\textit{Hit Points:} Same as the mortal, +1 for each rank of the deity.

\textit{Armor Clas}s: The mortal gains a divine bonus to Armor Class equal to half 
the deity's divine rank.

\textit{Ability Scores:} Strength, Dexterity, and Constitution are unchanged. Intelligence, 
Wisdom, and Charisma become 5 points lower than the deity's (or remain as the mortal's 
scores if they are higher).

\textit{Saves:} Fortitude and Reflex same as the mortal; Will adjusted if necessary 
for the mortal's new Wisdom score.

\textit{Skills:} The mortal can use its own skills and the deity's skills. If the 
mortal and the deity have the same skill, use the skill of whichever has more ranks 
in the skill. Use the mortal's effective ability scores to determine skill modifiers.

\textbf{Suggested Portfolio Elements:} Supreme.

\vspace{12pt}
\section*{Power of Luck}

\textbf{Prerequisites:} Luck domain.

\textbf{Benefit:} The deity can give creatures good or bad fortune. The deity can 
affect up to one creature per divine rank at once, but no more than that number 
each day. All must be within the deity's line of sight when first affected. Subjects 
receive a luck bonus of +1 per divine rank or a luck penalty of -1 per divine rank 
on attack rolls, saves, and checks for one day. Any creature that attacks the deity 
automatically suffers the luck penalty, and this does not count against the deity's 
daily uses of this ability.

\textbf{Suggested Portfolio Elements:} Fate, gambling, luck.

\vspace{12pt}
\section*{Power of Nature}

\textbf{Benefit:} The deity can perform any of the following in a radius of one 
mile per divine rank around the deity, at will, as a full-round action.•

Create or quell winds to produce anything from still air to tornado force winds.•

Set the temperature anywhere from -50°F to 120°F.•

Shake the earth, as the \textit{earthquake }spell.•

Create rain, sleet, hail, snow, or thunderstorms.

These effects last as long as the deity concentrates and for up to 1 minute per 
divine rank afterward. The deity can end an effect as a free action. 

\textbf{Suggested Portfolio Elements:} Nature, sea, weather.

\vspace{12pt}
\section*{Power of Truth}

\textbf{Benefit:} The deity knows when anyone (other than a deity of equal or higher 
rank) deliberately lies. This ability works like the \textit{discern lies }spell, 
except that it works continuously and applies to any creature the deity can perceive. 
The deity also can enchant creatures so they become truthful. The deity can affect 
up to one creature per divine rank at once, but no more than that number each day. 
All must be within the deity's line of sight when first affected. The enchanted 
creatures become unable to utter any deliberate falsehoods or evasions of truth 
for one day. The subject is allowed a Will save (DC 10 + the deity's Charisma modifier 
+ the deity's divine rank) to resist. Subjects who make successful saves become 
immune to this ability for one day. 

\textbf{Suggested Portfolio Elements:} Justice, law, truth.

\vspace{12pt}
\section*{Rejuvenation}

\textbf{Prerequisites:} Divine rank 11, Divine Fast Healing salient divine ability.

\textbf{Benefit:} When the deity suffers an attack that should destroy it, it simply 
disperses and reassembles later. Roll 10d10 to determine the number of days before 
the deity returns.

\textbf{Notes:} If the deity is killed in its own realm, subtract the deity's divine 
rank from the number of days it takes to return. If the deity's realm is on a divinely 
morphic Outer Plane, and the deity is killed there, subtract twice the deity's 
divine rank from

the number of days it takes to return. The return always takes at least one day.

This ability is ineffective if the deity is killed by another deity of equal or 
higher rank.

\textbf{Suggested Portfolio Elements:} Death, life, undead.

\vspace{12pt}
\section*{See Magic}

\textbf{Prerequisites:} Magic domain.

\textbf{Benefit:} This ability is similar to a constant \textit{greater arcane 
sight }spell, except that it covers the whole area the deity can see, and the deity 
immediately knows the number of auras present along with their locations and strengths. 
The deity needs to make a Spellcraft check to identify the school of each aura, 
but most deities with this ability can use Spellcraft as a free action.

\textbf{Suggested Portfolio Elements:} Magic.

\vspace{12pt}
\section*{Shapechange}

This is an extraordinary ability.

\textbf{Prerequisites:} Divine rank 11, Alter Size salient divine ability,

Alter Form salient divine ability.

\textbf{Benefit:} The deity can assume the form of an animal, beast, dragon, fey, 
giant, humanoid, magical beast, monstrous humanoid, or plant. The assumed form 
must be both living and corporeal. The deity can remain in the assumed form indefinitely, 
but it resumes its own form if slain.

\textbf{Notes:} This ability works like the Shift Form salient divine ability, 
except that the deity is not limited to a set number of forms and as noted here.

The deity can use its Alter Size ability simultaneously with this one to become 
as small as a grain of sand or as large as 1,600 feet in the assumed form's greatest 
dimension.

The deity can use this ability to create disguises, gaining a bonus of +20 on its 
Disguise checks.

\textbf{Suggested Portfolio Elements:} Nature, secrets, thieves.

\vspace{12pt}
\section*{Shift Form}

This is an extraordinary ability.

\textbf{Prerequisites:} Divine rank 6, Alter Size salient divine ability, Alter 
Form salient divine ability.

\textbf{Benefit:} The deity can assume the form of another creature. The forms 
a deity can assume are limited and vary with each deity. The forms allowed are 
listed in the deity's description. The deity can remain in the assumed form indefinitely, 
but it

resumes its own form if slain.

\textbf{Notes:} The deity acquires the physical, natural, and extraordinary abilities 
of the form it has assumed (but not spell-like or supernatural abilities) while 
retaining its own mind. Physical abilities include natural size and Strength, Dexterity, 
and Constitution scores. Natural abilities include armor, natural weapons (such 
as claws, bite, swoop and rake, and constriction; but not petrification, breath 
weapons, energy drain, energy effect, and the like), and similar gross physical 
qualities (presence or absence of wings, number of extremities, and so on). A body 
with extra limbs does not allow the deity to make more attacks (or more advantageous 
two-weapon attacks) than normal. Natural abilities also include mundane movement 
capabilities, such as walking, swimming, and flight with wings. The deity's speed 
is that of the assumed form or the deity's normal speed, whichever is higher.

In general, any part of the body or piece of equipment that is separated from the 
whole reverts to its original form. However, if the assumed form has an extraordinary 
ability that allows it to produce a substance or shed part of its body, then this 
ability also grants that ability. 

The deity retains its Intelligence, Wisdom, and Charisma scores, level and class, 
hit points (despite any change in its Constitution score), alignment, base attack 
bonus, and base saves. (New Strength, Dexterity, and Constitution scores may affect 
final attack and save bonuses.) The deity retains its outsider type, extraordinary 
abilities, spells, and spell-like abilities, but not its supernatural abilities.

The deity also retains its divine Armor Class bonus and divine qualities and abilities, 
provided they are not supernatural.

The deity can cast spells for which it has components. It needs a voice like that 
of a humanoid for verbal components and hands like those of a humanoid for somatic 
components, Likewise, the deity needs hands to use many of its powers, such as 
creating objects related to its portfolio.

When the shape shift occurs, the deity's equipment, if any, transforms to match 
the new form. If the new form is a creature that does not use equipment (aberration, 
animal, beast, magical beast, construct, dragon, elemental, ooze, some outsiders, 
plant, some undead creatures, some shapechangers, or vermin), the equipment melds 
into the new form and becomes nonfunctional.

Material components and focuses melded in this way cannot be used to cast spells. 
If the new form uses equipment (fey, giant, humanoid, some outsiders, many shapechangers, 
many undead creatures), the deity's equipment changes to match the new form and 
retains its properties.

This ability cannot confer class levels or class abilities.

The deity can change physical qualities such as hair color, hair texture, skin 
color, and gender. The deity can use this ability to create disguises, gaining 
a bonus of +15 on its Disguise checks.

The deity can use its Alter Size ability simultaneously with this one to become 
as small as a grain of sand or as large as 1,600 feet in the assumed form's greatest 
dimension.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Speak with Creatures}

\textbf{Benefit:} The deity has the supernatural ability to converse with the specified 
creature. This ability works like a permanent \textit{speak with animals }or \textit{speak 
with plants }spell, or like a \textit{tongues }spell that only allows the deity 
to converse with the specified type of creature.

\textbf{Notes:} A deity can have this ability multiple times, choosing a different 
type of creature each time.

\textbf{Suggested Portfolio Elements:} Nature.

\vspace{12pt}
\section*{Spontaneous Wizard Spells}

\textbf{Prerequisites:} Divine rank 6, Wizard level 1st, Int 29, Spell Mastery, 
Arcane Mastery salient divine ability.

\textbf{Benefit:} This ability works like a cleric's ability to cast \textit{cure 
}spells spontaneously, except that it applies to wizard spells. The deity must 
have a sufficient Intelligence score and wizard levels to cast the spell.

\textbf{Notes:} The deity still needs a spellbook for its wizard spells unless 
it also has the Divine Spellcasting ability.

\textbf{Suggested Portfolio Elements:} Knowledge, magic.

\vspace{12pt}
\section*{Stride}

\textbf{Prerequisites:} Travel domain.

\textbf{Benefit:} The deity's movement is doubled on the local or overland scales. 
Also, having this ability means that the deity's height does not limit the distance 
it can jump.

In addition, the deity can impart extra overland speed to living creatures. The 
deity can affect up to one creature per divine rank at once, but no more than that 
number each day. All must be within the deity's line of sight when first affected. 
Creatures who receive this boon double their speeds on the local or overland scales.

\textbf{Suggested Portfolio Elements:} Travel.

\vspace{12pt}
\section*{Sunder and Disjoin}

\textbf{Benefit:} If any weapon or item is used against the deity in combat, the 
deity can destroy it with a touch. Treat a successful touch as a combination of 
a \textit{disintegrate }spell and a 

\textit{disjunction }spell, both targeted exclusively at the touched item. The 
save DC for both effects is 19 + the deity's Charisma modifier. Anitem remains 
vulnerable to this ability for up to one day after being used against the deity.

\textbf{Suggested Portfolio Elements:} Victory, war.

\vspace{12pt}
\section*{Supreme Initiative}

This is an extraordinary ability.

\textbf{Prerequisites:} Dex 29, Improved Initiative.

\textbf{Benefit:} The deity goes first in the initiative order, no matter what 
its initiative result is or what initiative result anyone else in an encounter 
or battle has.

\textbf{Notes:} Determine initiative normally among any beings who don't have this 
ability, placing them in order after the deity. The deity can choose to delay or 
ready an action, just any other being can, and doing so changes the deity's initiative 
as normal. The deity also can refocus, thereby resuming its position at the beginning 
of the initiative order.

If two or more deities who have this ability are in the same battle, the deity 
with the highest divine rank gets the first position in the initiative order, the 
deity with the second highest rank gets the second position, and so on. Other beings 
then go in order after the last deity with the Supreme Initiative ability.

If two deities with this ability and the same divine rank are in a battle, make 
an initiative check for each deity, and the deity with the higher result goes first.

\textbf{Suggested Portfolio Elements:} Agility, thieves, war.

\vspace{12pt}
\section*{True Knowledge}

\textbf{Prerequisites:} Divine rank 11, Int 40, bardic knowledge or lore class 
feature and 10th level in the class that grants the ability, Knowledge domain.

\textbf{Benefit:} The deity never fails a bardic knowledge or lore check, no matter 
how obscure the knowledge involved. The deity speaks and understands all languages. 
The deity can use \textit{legend lore }and \textit{analyze dweomer }as free actions 
at will. These actions count against

the deity's maximum number of free actions per round.

\textbf{Suggested Portfolio Elements:} Knowledge.

\vspace{12pt}
\section*{True Shapechange}

This is an extraordinary ability.

\textbf{Prerequisites:} Divine rank 16, Alter Size salient divine ability, Alter 
Form salient divine ability, Shapechange salient divine ability.

\textbf{Benefit:} The deity can assume the form of any object or creature. The 
deity can remain in the assumed form indefinitely, but it resumes its own form 
if slain.

\textbf{Notes:} This ability works like the Shift Form salient divine ability, 
except as noted below.

The deity can take any form, living or unliving, corporal or incorporeal. The deity 
gains the supernatural abilities of the assumed form.

The deity can use this ability to create disguises, gaining a bonus of +20 on its 
Disguise checks.

The deity can use its Alter Size ability simultaneously with this one to become 
as small as a grain of sand or as large as 1,600 feet in the assumed form's greatest 
dimension.

\textbf{Suggested Portfolio Elements:} Nature, secrets, thieves.

\vspace{12pt}
\section*{Undead Mastery}

\textbf{Prerequisites:} Divine rank 14, Cleric level 17th.

\textbf{Benefit:} The deity can automatically command or destroy any undead creature, 
as desired, as a free action, though this counts against the normal limit of free 
actions per round. The deity can do this as often as desired, but it can command 
no more than one

undead creature per divine rank (regardless of the creatures' Hit Dice) at any 
one time.

\textbf{Suggested Portfolio Elements:} Death, life, undead.

\vspace{12pt}
\section*{Undead Qualities}

\textbf{Benefit:} The deity gains the qualities of the undead type:---

No Constitution score.---

Darkvision out to 60 feet.---

Immunity to all mind-affecting effects (charms, compulsions, phantasms, patterns, 
and morale effects).---

Immunity to poison, sleep effects, paralysis, stunning, disease, and death effects.---

Not subject to critical hits, nonlethal damage, ability drain, or energy drain. 
Immune to damage to its physical ability scores (Strength, Dexterity, and Constitution), 
as well as to fatigue and exhaustion effects.---

Cannot heal damage on its own if it has no Intelligence score, although it can 
be healed. Negative energy can heal undead creatures. The fast healing special 
quality works regardless of the creature's Intelligence score.---

Immunity to any effect that requires a Fortitude save (unless the effect also works 
on objects or is harmless).---

Uses its Charisma modifier for Concentration checks.---

Not at risk of death from massive damage, but when reduced to 0 hit points or less, 
it is immediately destroyed.---

Not affected by \textit{raise dead }and \textit{reincarnate }spells or abilities. 
\textit{Resurrection }and \textit{true resurrection }can affect undead creatures. 
These spells turn undead creatures back into the living creatures they were before 
becoming undead.---

Undead do not breathe, eat, or sleep.

\textbf{Suggested Portfolio Elements:} Death, undead.

\vspace{12pt}
\section*{Wave of Chaos}

\textbf{Prerequisites:} Chaotic alignment.

\textbf{Benefit:} The deity can create a wave of mental force that extends from 
the deity in a spread with a radius of 10 feet per divine rank. Creatures within 
the spread must make Will saves (DC 10 + the deity's Charisma modifier + the deity's 
divine rank) or

be forced to act unpredictably. This ability works like a \textit{confusion }spell 
cast by a sorcerer of level 10 + the deity's divine rank.

\textbf{Suggested Portfolio Elements:} Chaos.

\vspace{12pt}
\section*{Wound Enemy}

\textbf{Prerequisites:} Base attack bonus +20.

\textbf{Benefit:} The affected weapon deals damage to a creature such that a wound 
it causes deals 1d6 points of damage per round thereafter in addition to the normal 
damage from the weapon. Multiple wounds from the weapon result in cumulative bleeding 
loss (two

wounds for 2d6 points of damage per round, and so on). The bleeding can only be 
stopped by a successful Heal check (DC 15 + the deity's rank) or the application 
of any \textit{cure }spell or other healing spell \textit{(heal, healing circle, 
}and so on).

\textbf{Notes:} The ability functions only when the deity personally attacks with 
a physical weapon. The ability works with a ranged weapon, but not if someone else 
uses the weapon. The deity can apply to the ability to any weapon or natural weapon, 
but not to a

spell, spell-like ability, supernatural ability, or divine ability. A deity can 
have this ability multiple times, and its effects stack. 

\textbf{Suggested Portfolio Elements:} Death, pain, war.
