%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Barbarian}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Alignment:} Any nonlawful.

\textbf{Hit Die:} d12.

\textbf{Class Skills}

The barbarian's class skills (and the key ability for each skill) are \linkskill{Climb} (Str), 
\linkskill{Craft} (Int), \linkskill{Handle Animal} (Cha), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Ride} 
(Dex), \linkskill{Survival} (Wis), and \linkskill{Swim} (Str).

\textbf{Skill Points at 1st Level:} (4 + Int modifier) x4.

\textbf{Skill Points at Each Additional Level:} 4 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Barbarian}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} \\
1st & +1 & +2 & +0 & +0 & Fast Movement, Illiteracy, Rage 1/day \\
2nd & +2 & +3 & +0 & +0 & Uncanny Dodge \\
3rd & +3 & +3 & +1 & +1 & Trap Sense +1 \\
4th & +4 & +4 & +1 & +1 & Rage 2/day \\
5th & +5 & +4 & +1 & +1 & Improved Uncanny Dodge \\
6th & +6 & +5 & +2 & +2 & Trap Sense +2 \\
7th & +7 & +5 & +2 & +2 & Damage Reduction 1/- \\
8th & +8 & +6 & +2 & +2 & Rage 3/day \\
9th & +9 & +6 & +3 & +3 & Trap Sense +3 \\
10th & +10 & +7 & +3 & +3 & Damage Reduction 2/- \\
11th & +11 & +7 & +3 & +3 & Greater Rage \\
12th & +12 & +8 & +4 & +4 & Rage 4/day, Trap Sense +4 \\
13th & +13 & +8 & +4 & +4 & Damage Reduction 3/- \\
14th & +14 & +9 & +4 & +4 & Indomitable Will \\
15th & +15 & +9 & +5 & +5 & Trap Sense +5 \\
16th & +16 & +10 & +5 & +5 & Damage Reduction 4/-, Rage 5/day \\
17th & +17 & +10 & +5 & +5 & Tireless Rage \\
18th & +18 & +11 & +6 & +6 & Trap Sense +6 \\
19th & +19 & +11 & +6 & +6 & Damage Reduction 5/- \\
20th & +20 & +12 & +6 & +6 & Mighty Rage, Rage 6/day \\
\end{tabular}
\end{table}


%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are class features of the barbarian.

\textbf{Weapon and Armor Proficiency:} A barbarian is proficient with all simple 
and martial weapons, light armor, medium armor, and shields (except tower shields).

\textbf{Fast Movement (Ex):} A barbarian's land speed is faster than the norm for 
his race by +10 feet. This benefit applies only when he is wearing no armor, light 
armor, or medium armor and not carrying a heavy load. Apply this bonus before modifying 
the barbarian's speed because of any load carried or armor worn.

\textbf{Illiteracy:} Barbarians are the only characters who do not automatically 
know how to read and write. A barbarian may spend 2 skill points to gain the ability 
to read and write all languages he is able to speak.

A barbarian who gains a level in any other class automatically gains literacy. 
Any other character who gains a barbarian level does not lose the literacy he or 
she already had.

\textbf{Rage (Ex):} A barbarian can fly into a rage a certain number of times per 
day. In a rage, a barbarian temporarily gains a +4 bonus to Strength, a +4 bonus 
to Constitution, and a +2 morale bonus on Will saves, but he takes a -2 penalty 
to Armor Class. The increase in Constitution increases the barbarian's hit points 
by 2 points per level, but these hit points go away at the end of the rage when 
his Constitution score drops back to normal. (These extra hit points are not lost 
first the way temporary hit points are.) While raging, a barbarian cannot use any 
Charisma-, Dexterity-, or Intelligence-based skills (except for \linkskill{Balance}, \linkskill{Escape 
Artist}, \linkskill{Intimidate}, and \linkskill{Ride}), the \linkskill{Concentration} skill, or any abilities that require 
patience or concentration, nor can he cast spells or activate magic items that 
require a command word, a spell trigger (such as a wand), or spell completion (such 
as a scroll) to function. He can use any feat he has except \linkfeat{Combat Expertise}, item 
creation feats, and metamagic feats. A fit of rage lasts for a number of rounds 
equal to 3 + the character's (newly improved) Constitution modifier. A barbarian 
may prematurely end his rage. At the end of the rage, the barbarian loses the rage 
modifiers and restrictions and becomes fatigued (-2 penalty to Strength, -2 penalty 
to Dexterity, can't charge or run) for the duration of the current encounter (unless 
he is a 17th-level barbarian, at which point this limitation no longer applies; 
see below).

A barbarian can fly into a rage only once per encounter. At 1st level he can use 
his rage ability once per day. At 4th level and every four levels thereafter, he 
can use it one additional time per day (to a maximum of six times per day at 20th 
level). Entering a rage takes no time itself, but a barbarian can do it only during 
his action, not in response to someone else's action.

\textbf{Uncanny Dodge (Ex):} At 2nd level, a barbarian retains his Dexterity bonus 
to AC (if any) even if he is caught flat-footed or struck by an invisible attacker. 
However, he still loses his Dexterity bonus to AC if immobilized. If a barbarian 
already has uncanny dodge from a different class, he automatically gains improved 
uncanny dodge (see below) instead.

\textbf{Trap Sense (Ex):} Starting at 3rd level, a barbarian gains a +1 bonus on 
Reflex saves made to avoid traps and a +1 dodge bonus to AC against attacks made 
by traps. These bonuses rise by +1 every three barbarian levels thereafter (6th, 
9th, 12th, 15th, and 18th level). Trap sense bonuses gained from multiple classes 
stack.

\textbf{Improved Uncanny Dodge (Ex):} At 5th level and higher, a barbarian can 
no longer be flanked. This defense denies a rogue the ability to sneak attack the 
barbarian by flanking him, unless the attacker has at least four more rogue levels 
than the target has barbarian levels. If a character already has uncanny dodge 
(see above) from a second class, the character automatically gains improved uncanny 
dodge instead, and the levels from the classes that grant uncanny dodge stack to 
determine the minimum level a rogue must be to flank the character.

\textbf{Damage Reduction (Ex):} At 7th level, a barbarian gains Damage Reduction. 
Subtract 1 from the damage the barbarian takes each time he is dealt damage from 
a weapon or a natural attack. At 10th level, and every three barbarian levels thereafter 
(13th, 16th, and 19th level), this damage reduction rises by 1 point. Damage reduction 
can reduce damage to 0 but not below 0.

\textbf{Greater Rage (Ex):} At 11th level, a barbarian's bonuses to Strength and 
Constitution during his rage each increase to +6, and his morale bonus on Will 
saves increases to +3. The penalty to AC remains at -2.

\textbf{Indomitable Will (Ex):} While in a rage, a barbarian of 14th level or higher 
gains a +4 bonus on Will saves to resist enchantment spells. This bonus stacks 
with all other modifiers, including the morale bonus on Will saves he also receives 
during his rage.

\textbf{Tireless Rage (Ex):} At 17th level and higher, a barbarian no longer becomes 
fatigued at the end of his rage.

\textbf{Mighty Rage (Ex):} At 20th level, a barbarian's bonuses to Strength and 
Constitution during his rage each increase to +8, and his morale bonus on Will 
saves increases to +4. The penalty to AC remains at -2.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ex-Barbarians}
%%%%%%%%%%%%%%%%%%%%%%%%%

A barbarian who becomes lawful loses the ability to rage and cannot gain more levels 
as a barbarian. He retains all the other benefits of the class (damage reduction, 
fast movement, trap sense, and uncanny dodge).