%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Cleric}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Alignment:} A cleric's alignment must be within one step of his deity's 
(that is, it may be one step away on either the lawful-chaotic axis or the good-evil 
axis, but not both). A cleric may not be neutral unless his deity's alignment is 
also neutral.

\textbf{Hit Die:} d8.

\textbf{Class Skills}

The cleric's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Heal} (Wis), \linkskill{Knowledge} (arcana) (Int), \linkskill{Knowledge} 
(history) (Int), \linkskill{Knowledge} (religion) (Int), \linkskill{Knowledge} (the planes) (Int), \linkskill{Profession} 
(Wis), and \linkskill{Spellcraft} (Int). 

\textbf{Domains and Class Skills:} A cleric who chooses the Animal or Plant domain 
adds \linkskill{Knowledge} (nature) (Int) to the cleric class skills listed above. A cleric 
who chooses the \linkskill{Knowledge} domain adds all \linkskill{Knowledge} (Int) skills to the list. A 
cleric who chooses the Travel domain adds \linkskill{Survival} (Wis) to the list. A cleric 
who chooses the Trickery domain adds \linkskill{Bluff} (Cha), \linkskill{Disguise} (Cha), and \linkskill{Hide} (Dex) 
to the list. See Deity, Domains, and Domain Spells, below, for more information.

\textbf{Skill Points at 1st Level:} (2 + Int modifier) x4.

\textbf{Skill Points at Each Additional Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Cleric}
\centering
\begin{tabular}{*{5}{l}p{1.5cm}*{10}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{0th} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
1st & +0 & +2 & +0 & +2 & \raggedright{}Turn or Rebuke Undead & 3 & 1 & -- & -- & -- & -- & -- & -- & -- & --\\
2nd & +1 & +3 & +0 & +3 & -- & 4 & 2 & -- & -- & -- & -- & -- & -- & -- & --\\
3rd & +2 & +3 & +1 & +3 & -- & 4 & 2 & 1 & -- & -- & -- & -- & -- & -- & --\\
4th & +3 & +4 & +1 & +4 & -- & 5 & 3 & 2 & -- & -- & -- & -- & -- & -- & --\\
5th & +3 & +4 & +1 & +4 & -- & 5 & 3 & 2 & 1 & -- & -- & -- & -- & -- & --\\
6th & +4 & +5 & +2 & +5 & -- & 5 & 3 & 3 & 2 & -- & -- & -- & -- & -- & --\\
7th & +5 & +5 & +2 & +5 & -- & 6 & 4 & 3 & 2 & 1 & -- & -- & -- & -- & --\\
8th & +6 & +6 & +2 & +6 & -- & 6 & 4 & 3 & 3 & 2 & -- & -- & -- & -- & --\\
9th & +6 & +6 & +3 & +6 & -- & 6 & 4 & 4 & 3 & 2 & 1 & -- & -- & -- & --\\
10th & +7 & +7 & +3 & +7 & -- & 6 & 4 & 4 & 3 & 3 & 2 & -- & -- & -- & --\\
11th & +8 & +7 & +3 & +7 & -- & 6 & 5 & 4 & 3 & 3 & 2 & 1 & -- & -- & --\\
12th & +9 & +8 & +4 & +8 & -- & 6 & 5 & 4 & 4 & 3 & 3 & 2 & -- & -- & --\\
13th & +9 & +8 & +4 & +8 & -- & 6 & 5 & 5 & 4 & 4 & 3 & 2 & 1 & -- & --\\
14th & +10 & +9 & +4 & +9 & -- & 6 & 5 & 5 & 4 & 4 & 4 & 3 & 2 & -- & --\\
15th & +11 & +9 & +5 & +9 & -- & 6 & 5 & 5 & 4 & 4 & 4 & 3 & 2 & 1 & --\\
16th & +12 & +10 & +5 & +10 & -- & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & --\\
17th & +12 & +10 & +5 & +10 & -- & 6 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 2 & 1\\
18th & +13 & +11 & +6 & +11 & -- & 6 & 5 & 5 & 5 & 5 & 5 & 4 & 3 & 3 & 2\\
19th & +14 & +11 & +6 & +11 & -- & 6 & 5 & 5 & 5 & 5 & 5 & 4 & 4 & 3 & 3\\
20th & +15 & +12 & +6 & +12 & -- & 6 & 5 & 5 & 5 & 5 & 5 & 4 & 4 & 4 & 4\\
\end{tabular}
\end{table}

In addition to the stated number of spells per day for 1st through 9th level spells, a cleric gets a domain spell for each spell level, starting at 1st. The Domain spells are in addition to any bonus spells that the cleric might receice for having a high Wisdom score.

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are class features of the cleric.

\textbf{Weapon and Armor Proficiency:} Clerics are proficient with all simple weapons, 
with all types of armor (light, medium, and heavy), and with shields (except tower 
shields).

A cleric who chooses the War domain receives the \linkfeat{Weapon Focus} feat related to his 
deity's weapon as a bonus feat. He also receives the appropriate Martial Weapon 
Proficiency feat as a bonus feat, if the weapon falls into that category.

\textbf{Aura (Ex):} A cleric of a chaotic, evil, good, or lawful deity has a particularly 
powerful aura corresponding to the deity's alignment (see the \linkspell{Detect Evil}
spell for details). Clerics who don't worship a specific deity but choose the 
Chaotic, Evil, Good, or Lawful domain have a similarly powerful aura of the corresponding 
alignment.

\textbf{Spells:} A cleric casts divine spells, which are drawn from the cleric 
spell list. However, his alignment may restrict him from casting certain spells 
opposed to his moral or ethical beliefs; see Chaotic, Evil, Good, and Lawful Spells, 
below. A cleric must choose and prepare his spells in advance (see below).

To prepare or cast a spell, a cleric must have a Wisdom score equal to at least 
10 + the spell level. The Difficulty Class for a saving throw against a cleric's 
spell is 10 + the spell level + the cleric's Wisdom modifier.

Like other spellcasters, a cleric can cast only a certain number of spells of each 
spell level per day. His base daily spell allotment is given on Table: The Cleric. 
In addition, he receives bonus spells per day if he has a high Wisdom score. A 
cleric also gets one domain spell of each spell level he can cast, starting at 
1st level. When a cleric prepares a spell in a domain spell slot, it must come 
from one of his two domains (see Deities, Domains, and Domain Spells, below).

Clerics meditate or pray for their spells. Each cleric must choose a time at which 
he must spend 1 hour each day in quiet contemplation or supplication to regain 
his daily allotment of spells. Time spent resting has no effect on whether a cleric 
can prepare spells. A cleric may prepare and cast any spell on the cleric spell 
list, provided that he can cast spells of that level, but he must choose which 
spells to prepare during his daily meditation.

\textbf{Deity, Domains, and Domain Spells:} A cleric's deity influences his alignment, 
what magic he can perform, his values, and how others see him. A cleric chooses 
two domains from among those belonging to his deity. A cleric can select an alignment 
domain (Chaos, Evil, Good, or Law) only if his alignment matches that domain.

If a cleric is not devoted to a particular deity, he still selects two domains 
to represent his spiritual inclinations and abilities. The restriction on alignment 
domains still applies.

Each domain gives the cleric access to a domain spell at each spell level he can 
cast, from 1st on up, as well as a granted power. The cleric gets the granted powers 
of both the domains selected.

With access to two domain spells at a given spell level, a cleric prepares one 
or the other each day in his domain spell slot. If a domain spell is not on the 
cleric spell list, a cleric can prepare it only in his domain spell slot.

\textbf{Spontaneous Casting:} A good cleric (or a neutral cleric of a good deity) 
can channel stored spell energy into healing spells that the cleric did not prepare 
ahead of time. The cleric can "lose" any prepared spell that is not a domain 
spell in order to cast any \textit{cure} spell of the same spell level or lower 
(a \textit{cure} spell is any spell with "cure" in its name). 

An evil cleric (or a neutral cleric of an evil deity), can't convert prepared spells 
to \textit{cure} spells but can convert them to \textit{inflict} spells (an \textit{inflict}
spell is one with "inflict" in its name).

A cleric who is neither good nor evil and whose deity is neither good nor evil 
can convert spells to either \textit{cure} spells or \textit{inflict} spells (player's 
choice). Once the player makes this choice, it cannot be reversed. This choice 
also determines whether the cleric turns or commands undead (see below).

\textbf{Chaotic, Evil, Good, and Lawful Spells:} A cleric can't cast spells of 
an alignment opposed to his own or his deity's (if he has one). Spells associated 
with particular alignments are indicated by the chaos, evil, good, and law descriptors 
in their spell descriptions.

\textbf{Turn or Rebuke Undead (Su):} Any cleric, regardless of alignment, has the 
power to affect undead creatures by channeling the power of his faith through his 
holy (or unholy) symbol (see Turn or Rebuke Undead).

A good cleric (or a neutral cleric who worships a good deity) can turn or destroy 
undead creatures. An evil cleric (or a neutral cleric who worships an evil deity) 
instead rebukes or commands such creatures. A neutral cleric of a neutral deity 
must choose whether his turning ability functions as that of a good cleric or an 
evil cleric. Once this choice is made, it cannot be reversed. This decision also 
determines whether the cleric can cast spontaneous \textit{cure} or \textit{inflict}
spells (see above).

A cleric may attempt to turn undead a number of times per day equal to 3 + his 
Charisma modifier. A cleric with 5 or more ranks in \linkskill{Knowledge} (religion) gets a 
+2 bonus on turning checks against undead.

\textbf{Bonus Languages:} A cleric's bonus language options include Celestial, 
Abyssal, and Infernal (the languages of good, chaotic evil, and lawful evil outsiders, 
respectively). These choices are in addition to the bonus languages available to 
the character because of his race.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ex-Clerics}
%%%%%%%%%%%%%%%%%%%%%%%%%

A cleric who grossly violates the code of conduct required by his god loses all 
spells and class features, except for armor and shield proficiencies and proficiency 
with simple weapons. He cannot thereafter gain levels as a cleric of that god until 
he atones (see the \linkspell{Atonement} spell description).