%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Fighter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Alignment:} Any.

\textbf{Hit Die:} d10.

\textbf{Class Skills}

The fighter's class skills (and the key ability for each skill) are \linkskill{Climb} (Str), 
\linkskill{Craft} (Int), \linkskill{Handle Animal} (Cha), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Ride} (Dex), and 
\linkskill{Swim} (Str).

\textbf{Skill Points at 1st Level:} (2 + Int modifier) x4.

\textbf{Skill Points at Each Additional Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Fighter}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} \\
1st & +1 & +2 & +0 & +0 & Bonus Feat \\
2nd & +2 & +3 & +0 & +0 & Bonus Feat \\
3rd & +3 & +3 & +1 & +1 & -- \\
4th & +4 & +4 & +1 & +1 & Bonus Feat \\
5th & +5 & +4 & +1 & +1 & -- \\
6th & +6 & +5 & +2 & +2 & Bonus Feat \\
7th & +7 & +5 & +2 & +2 & -- \\
8th & +8 & +6 & +2 & +2 & Bonus Feat \\
9th & +9 & +6 & +3 & +3 & -- \\
10th & +10 & +7 & +3 & +3 & Bonus Feat \\
11th & +11 & +7 & +3 & +3 & -- \\
12th & +12 & +8 & +4 & +4 & Bonus Feat \\
13th & +13 & +8 & +4 & +4 & -- \\
14th & +14 & +9 & +4 & +4 & Bonus Feat \\
15th & +15 & +9 & +5 & +5 & -- \\
16th & +16 & +10 & +5 & +5 & Bonus Feat \\
17th & +17 & +10 & +5 & +5 & -- \\
18th & +18 & +11 & +6 & +6 & Bonus Feat \\
19th & +19 & +11 & +6 & +6 & -- \\
20th & +20 & +12 & +6 & +6 & Bonus Feat \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are class features of the fighter.

\textbf{Weapon and Armor Proficiency:} A fighter is proficient with all simple 
and martial weapons and with all armor (heavy, medium, and light) and shields (including 
tower shields).

\textbf{Bonus Feats:} At 1st level, a fighter gets a bonus combat-oriented feat 
in addition to the feat that any 1st-level character gets and the bonus feat granted 
to a human character. The fighter gains an additional bonus feat at 2nd level and 
every two fighter levels thereafter (4th, 6th, 8th, 10th, 12th, 14th, 16th, 18th, 
and 20th). These bonus feats must be drawn from the feats noted as fighter bonus 
feats. A fighter must still meet all prerequisites for a bonus feat, including 
ability score and base attack bonus minimums.

These bonus feats are in addition to the feat that a character of any class gets 
from advancing levels. A fighter is not limited to the list of fighter bonus feats 
when choosing these feats.