%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Sorcerer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Alignment:} Any.

\textbf{Hit Die:} d4.

\textbf{Class Skills}

The sorcerer's class skills (and the key ability for each skill) are \linkskill{Bluff} (Cha), 
\linkskill{Concentration} (Con), \linkskill{Craft} (Int), \linkskill{Knowledge} (arcana) (Int), \linkskill{Profession} (Wis), and 
\linkskill{Spellcraft} (Int).

\textbf{Skill Points at 1st Level:} (2 + Int modifier) x4.

\textbf{Skill Points at Each Additional Level: }2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Sorcerer}
\centering
\begin{tabular}{*{5}{l}p{1.5cm}*{10}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{0th} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
1st & +0 & +0 & +0 & +2 & Summon Familiar & 5 & 3 & -- & -- & -- & -- & -- & -- & -- & --\\
2nd & +1 & +0 & +0 & +3 & -- & 6 & 4 & -- & -- & -- & -- & -- & -- & -- & --\\
3rd & +1 & +1 & +1 & +3 & -- & 6 & 5 & -- & -- & -- & -- & -- & -- & -- & --\\
4th & +2 & +1 & +1 & +4 & -- & 6 & 6 & 3 & -- & -- & -- & -- & -- & -- & --\\
5th & +2 & +1 & +1 & +4 & -- & 6 & 6 & 4 & -- & -- & -- & -- & -- & -- & --\\
6th & +3 & +2 & +2 & +5 & -- & 6 & 6 & 5 & 3 & -- & -- & -- & -- & -- & --\\
7th & +3 & +2 & +2 & +5 & -- & 6 & 6 & 6 & 4 & -- & -- & -- & -- & -- & --\\
8th & +4 & +2 & +2 & +6 & -- & 6 & 6 & 6 & 5 & 3 & -- & -- & -- & -- & --\\
9th & +4 & +3 & +3 & +6 & -- & 6 & 6 & 6 & 6 & 4 & -- & -- & -- & -- & --\\
10th & +5 & +3 & +3 & +7 & -- & 6 & 6 & 6 & 6 & 5 & 3 & -- & -- & -- & --\\
11th & +5 & +3 & +3 & +7 & -- & 6 & 6 & 6 & 6 & 6 & 4 & -- & -- & -- & --\\
12th & +6 & +4 & +4 & +8 & -- & 6 & 6 & 6 & 6 & 6 & 5 & 3 & -- & -- & --\\
13th & +6 & +4 & +4 & +8 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 4 & -- & -- & --\\
14th & +7 & +4 & +4 & +9 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 5 & 3 & -- & --\\
15th & +7 & +5 & +5 & +9 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 4 & -- & --\\
16th & +8 & +5 & +5 & +10 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 5 & 3 & --\\
17th & +8 & +5 & +5 & +10 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 4 & --\\
18th & +9 & +6 & +6 & +11 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 5 & 3\\
19th & +9 & +6 & +6 & +11 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 4\\
20th & +10 & +6 & +6 & +12 & -- & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 5\\
\end{tabular}
\end{table}

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Sorcerer Spells Known}
\centering
\begin{tabular}{l*{11}{c}}
\textbf{Level} & \textbf{0th} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th} & \textbf{6th} & \textbf{7th} & \textbf{8th} & \textbf{9th} \\
1st & 4 & 2 & -- & -- & -- & -- & -- & -- & -- & -- \\
2nd & 5 & 2 & -- & -- & -- & -- & -- & -- & -- & -- \\
3rd & 5 & 3 & -- & -- & -- & -- & -- & -- & -- & -- \\
4th & 6 & 3 & 1 & -- & -- & -- & -- & -- & -- & -- \\
5th & 6 & 4 & 2 & -- & -- & -- & -- & -- & -- & -- \\
6th & 7 & 4 & 2 & 1 & -- & -- & -- & -- & -- & -- \\
7th & 7 & 5 & 3 & 2 & -- & -- & -- & -- & -- & -- \\
8th & 8 & 5 & 3 & 2 & 1 & -- & -- & -- & -- & -- \\
9th & 8 & 5 & 4 & 3 & 2 & -- & -- & -- & -- & -- \\
10th & 9 & 5 & 4 & 3 & 2 & 1 & -- & -- & -- & -- \\
11th & 9 & 5 & 5 & 4 & 3 & 2 & -- & -- & -- & -- \\
12th & 9 & 5 & 5 & 4 & 3 & 2 & 1 & -- & -- & -- \\
13th & 9 & 5 & 5 & 4 & 4 & 3 & 2 & -- & -- & -- \\
14th & 9 & 5 & 5 & 4 & 4 & 3 & 2 & 1 & -- & -- \\
15th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 2 & -- & -- \\
16th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 2 & 1 & -- \\
17th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 3 & 2 & -- \\
18th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 3 & 2 & 1 \\
19th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 3 & 3 & 2 \\
20th & 9 & 5 & 5 & 4 & 4 & 4 & 3 & 3 & 3 & 3 \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are class features of the sorcerer.

\textbf{Weapon and Armor Proficiency:} Sorcerers are proficient with all simple 
weapons. They are not proficient with any type of armor or shield. Armor of any 
type interferes with a sorcerer's gestures, which can cause his spells with somatic 
components to fail.

\textbf{Spells:} A sorcerer casts arcane spells which are drawn primarily from 
the sorcerer/wizard spell list. He can cast any spell he knows without preparing 
it ahead of time, the way a wizard or a cleric must (see below).

To learn or cast a spell, a sorcerer must have a Charisma score equal to at least 
10 + the spell level. The Difficulty Class for a saving throw against a sorcerer's 
spell is 10 + the spell level + the sorcerer's Charisma modifier.

Like other spellcasters, a sorcerer can cast only a certain number of spells of 
each spell level per day. His base daily spell allotment is given on Table: The 
Sorcerer. In addition, he receives bonus spells per day if he has a high Charisma 
score.

A sorcerer's selection of spells is extremely limited. A sorcerer begins play knowing 
four 0-level spells and two 1st-level spells of your choice. At each new sorcerer 
level, he gains one or more new spells, as indicated on Table: Sorcerer Spells 
Known. (Unlike spells per day, the number of spells a sorcerer knows is not affected 
by his Charisma score; the numbers on Table: Sorcerer Spells Known are fixed.) 
These new spells can be common spells chosen from the sorcerer/wizard spell list, 
or they can be unusual spells that the sorcerer has gained some understanding of 
by study. The sorcerer can't use this method of spell acquisition to learn spells 
at a faster rate, however.

Upon reaching 4th level, and at every even-numbered sorcerer level after that (6th, 
8th, and so on), a sorcerer can choose to learn a new spell in place of one he 
already knows. In effect, the sorcerer "loses" the old spell in exchange for 
the new one. The new spell's level must be the same as that of the spell being 
exchanged, and it must be at least two levels lower than the highest-level sorcerer 
spell the sorcerer can cast. A sorcerer may swap only a single spell at any given 
level, and must choose whether or not to swap the spell at the same time that he 
gains new spells known for the level.

Unlike a wizard or a cleric, a sorcerer need not prepare his spells in advance. 
He can cast any spell he knows at any time, assuming he has not yet used up his 
spells per day for that spell level. He does not have to decide ahead of time which 
spells he'll cast.

\textbf{Familiar:} A sorcerer can obtain a familiar (see below). Doing so takes 
24 hours and uses up magical materials that cost 100 gp. A familiar is a magical 
beast that resembles a small animal and is unusually tough and intelligent. The 
creature serves as a companion and servant.

The sorcerer chooses the kind of familiar he gets. As the sorcerer advances in 
level, his familiar also increases in power.

If the familiar dies or is dismissed by the sorcerer, the sorcerer must attempt 
a DC 15 Fortitude saving throw. Failure means he loses 200 experience points per 
sorcerer level; success reduces the loss to one-half that amount. However, a sorcerer's 
experience point total can never go below 0 as the result of a familiar's demise 
or dismissal. A slain or dismissed familiar cannot be replaced for a year and day. 
A slain familiar can be raised from the dead just as a character can be, and it 
does not lose a level or a Constitution point when this happy event occurs.

A character with more than one class that grants a familiar may have only one familiar 
at a time.
