
\section{Artifacts}

Artifacts are extremely powerful. Rather than merely another form of magic equipment, 
they are the sorts of legendary relics that whole campaigns can be based on. Each 
could be the center of a whole set of adventures---a quest to recover it, a fight 
against a opponent wielding it, a mission to cause its destruction, and so on.

No table has been included to randomly generate specific artifacts, since these 
items should only enter a campaign through deliberate choice on your part.

\vspace{12pt}
MINOR ARTIFACTS

Minor artifacts are not necessarily unique items. Even so, they are magic items 
that no longer can be created, at least by common mortal means.

\vspace{12pt}
Minor Artifact Descriptions

Described below is a selection of the most well-known (not necessarily the most 
numerous) minor artifacts.

\vspace{12pt}
\textbf{Book of Infinite Spells:} This work bestows upon any character of any class 
the ability to use the spells within its pages. However, any character not already 
able to use spells gains one negative level for as long as the book is in her possession 
or while she uses its power. A \textit{book of infinite spells }contains 1d8+22 
pages. The nature of each page is determined by a dice roll: 01-50, arcane spell; 
51-100, divine spell.

Determine the exact spell by using the tables for determining major scroll spells.

Once a page is turned, it can never be flipped back---paging through a \textit{book 
of infinite spells }is a one-way trip. If the book is closed, it always opens again 
to the page it was on before the book was closed. When the last page is turned, 
the book vanishes.

Once per day the owner of the book can cast the spell to which the book is opened. 
If that spell happens to be one that is on the character's class spell list, she 
can cast it up to four times per day. The pages cannot be ripped out without destroying 
the book. Similarly, the spells cannot be cast as scroll spells, nor can they be 
copied into a spellbook---their magic is bound up permanently within the book itself.

The owner of the book need not have the book on her person in order to use its 
power. The book can be stored in a place of safety while the owner is adventuring 
and still allow its owner to cast spells by means of its power.

Each time a spell is cast, there is a chance that the energy connected with its 
use causes the page to magically turn despite all precautions. The owner knows 
this and may even benefit from the turning by gaining access to a new spell. The 
chance of a page turning depends on the spell the page contains and what sort of 
spellcaster the owner is.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{3.355in}|}{\begin{minipage}[t]{3.355in}\raggedright
\textbf{Condition}\end{minipage}} & \multicolumn{1}{p{1.009in}|}{\begin{minipage}[t]{1.009in}\centering
\textbf{Chance of Page Turning}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
Caster employing a spell usable by own class and level\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
10\%\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{3.355in}|}{\begin{minipage}[t]{3.355in}\centering
Caster employing a spell not usable by own class and level\end{minipage}} & \multicolumn{1}{p{1.009in}|}{\begin{minipage}[t]{1.009in}\centering
20\%\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
Nonspellcaster employing divine spell\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
25\%\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{3.355in}|}{\begin{minipage}[t]{3.355in}\centering
Nonspellcaster employing arcane spell\end{minipage}} & \multicolumn{3}{p{1.145in}|}{\begin{minipage}[t]{1.145in}\centering
30\%\end{minipage}}\\
\hline
\end{longtable}

Treat each spell use as if a scroll were being employed, for purposes of determining 
casting time, spell failure, and so on.

Strong (all schools); CL 18th;Weight 3 lb.

\vspace{12pt}
\textbf{Deck of Many Things: }A \textit{deck of many things }(both beneficial and 
baneful) is usually found in a box or leather pouch. Each deck contains a number 
of cards or plaques made of ivory or vellum. Each is engraved with glyphs, characters, 
and sigils. As soon as one of these cards is drawn from the pack, its magic is 
bestowed upon the person who drew it, for better or worse.

The character with a \textit{deck of many things }who wishes to draw a card must 
announce how many cards she will draw before she begins. Cards must be drawn within 
1 hour of each other, and a character can never again draw from this deck any more 
cards than she has announced. If the character does not willingly draw her allotted 
number (or if she is somehow prevented from doing so), the cards flip out of the 
deck on their own. \textit{Exception: }If the jester is drawn, the possessor of 
the deck may elect to draw two additional cards.

Each time a card is taken from the deck, it is replaced (making it possible to 
draw the same card twice) unless the draw is the jester or the fool, in which case 
the card is discarded from the pack. A \textit{deck of many things }contains 22 
cards. To simulate the magic cards, you may want to use tarot cards, as indicated 
in the second column of the accompanying table. If no tarot deck is available, 
substitute ordinary playing cards instead, as indicated in the third column. The 
effects of each card, summarized on the table, are fully described below.

\vspace{12pt}
\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{4}{|p{4.330in}|}{\begin{minipage}[t]{4.330in}\raggedright
\textbf{Deck of Many Things}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{4}{p{0.170in}|}{\begin{minipage}[t]{0.170in}\raggedright
\textbf{Plaque}\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
\textbf{Tarot Card}\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
\textbf{Playing Card}\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
\textbf{Summary of Effect}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.998in}|}{\begin{minipage}[t]{1.998in}\raggedright
Balance\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
XI. Justice\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Two of spades\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Change alignment instantly.\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Comet\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Two of swords\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Two of diamonds\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Defeat the next monster you meet to gain one level.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Donjon\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Four of swords\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Ace of spades\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
You are \textit{imprisoned}.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Euryale\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Ten of swords\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Queen of spades\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
-1 penalty on all saving throws henceforth.\end{minipage}}\\
\hline
% ROW 7
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
The Fates\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Three of cups\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Ace of hearts\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Avoid any situation you choose . . . once.\end{minipage}}\\
\hline
% ROW 8
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Flames\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XV. The Devil\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Queen of clubs\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Enmity between you and an outsider.\end{minipage}}\\
\hline
% ROW 9
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Fool\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
0. The Fool\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Joker (with trademark)\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Lose 10,000 experience points and you must draw again.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Gem\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Seven of cups\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Two of hearts\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain your choice of twenty-five pieces of jewelry or fifty gems.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Idiot\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Two of pentacles\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Two of clubs\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Lose Intelligence (permanent drain). You may draw again.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Jester\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XII. The Hanged Man\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Joker (without trademark)\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain 10,000 XP or two more draws from the deck.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Key\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
V. The Hierophant\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Queen of hearts\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain a major magic weapon.\end{minipage}}\\
\hline
% ROW 14
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Knight\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Page of swords\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Jack of hearts\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain the service of a 4th-level fighter.\end{minipage}}\\
\hline
% ROW 15
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Moon\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XVIII. The Moon\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Queen of diamonds\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
You are granted 1d4 wishes.\end{minipage}}\\
\hline
% ROW 16
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Rogue\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Five of swords\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Jack of spades\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
One of your friends turns against you.\end{minipage}}\\
\hline
% ROW 17
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Ruin\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XVI. The Tower\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
King of spades\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Immediately lose all wealth and real property.\end{minipage}}\\
\hline
% ROW 18
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Skull\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XIII. Death\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Jack of clubs\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Defeat dread wraith or be forever destroyed.\end{minipage}}\\
\hline
% ROW 19
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Star\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XVII. The Star\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Jack of diamonds\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Immediately gain a +2 inherent bonus to one ability score.\end{minipage}}\\
\hline
% ROW 20
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Sun\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
XIX. The Sun\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
King of diamonds\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain beneficial medium wondrous item and 50,000 XP.\end{minipage}}\\
\hline
% ROW 21
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Talons\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Queen of pentacles\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Ace of clubs\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
All magic items you possess disappear permanently.\end{minipage}}\\
\hline
% ROW 22
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Throne\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Four of staves\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
King of hearts\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Gain a +6 bonus on Diplomacy checks plus a small keep.\end{minipage}}\\
\hline
% ROW 23
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
Vizier\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
IX. The Hermit\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
Ace of diamonds\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Know the answer to your next dilemma.\end{minipage}}\\
\hline
% ROW 24
\multicolumn{5}{p{2.168in}|}{\begin{minipage}[t]{2.168in}\raggedright
The Void\end{minipage}} & \multicolumn{1}{|p{0.460in}|}{\begin{minipage}[t]{0.460in}\raggedright
Eight of swords\end{minipage}} & \multicolumn{1}{p{0.872in}|}{\begin{minipage}[t]{0.872in}\raggedright
King of clubs\end{minipage}} & \multicolumn{1}{p{1.000in}|}{\begin{minipage}[t]{1.000in}\raggedright
Body functions, but soul is trapped elsewhere.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\textit{Balance: }The character must change to a radically different alignment. 
If the character fails to act according to the new alignment, she gains a negative 
level.

\textit{Comet: }The character must single-handedly defeat the next hostile monster 
or monsters encountered, or the benefit is lost. If successful, the character gains 
enough XP to attain the next experience level.

\textit{Donjon: }This card signifies imprisonment--- either by the \textit{imprisonment 
}spell or by some powerful being. All gear and spells are stripped from the victim 
in any case. Draw no more cards.

\textit{Euryale: }The medusalike visage of this card brings a curse that only the 
fates card or a deity can remove. The -1 penalty on all saving throws is otherwise 
permanent.

\textit{Fates: }This card enables the character to avoid even an instantaneous 
occurrence if so desired, for the fabric of reality is unraveled and respun. Note 
that it does not enable something to happen. It can only stop something from happening 
or reverse a past occurrence. The reversal is only for the character who drew the 
card; other party members may have to endure the situation.

\textit{Flames: }Hot anger, jealousy, and envy are but a few of the possible motivational 
forces for the enmity. The enmity of the outsider can't be ended until one of the 
parties has been slain. Determine the outsider randomly, and assume that it attacks 
the character (or plagues her life in some way) within 1d20 days.

\textit{Fool: }The payment of XP and the redraw are mandatory. This card is always 
discarded when drawn, unlike all others except the jester.

\textit{Gem: }This card indicates wealth. The jewelry is all gold set with gems, 
each piece worth 2,000 gp, the gems 1,000 gp value each. 

\textit{Idiot: }This card causes the drain of 1d4+1 points of Intelligence immediately. 
The additional draw is optional.

\textit{Jester: }This card is always discarded when drawn, unlike all others except 
the fool. The redraws are optional.

\textit{Key: }The magic weapon granted must be one usable by the character. It 
suddenly appears out of nowhere in the character's hand.

\textit{Knight: }The fighter appears out of nowhere and serves loyally until death. 
He or she is of the same race (or kind) and gender as the character.

\textit{Moon: }This card sometimes bears the image of a moonstone gem with the 
appropriate number of \textit{wishes }shown as gleams therein; sometimes it depicts 
a moon with its phase indicating the number of \textit{wishes }(full = four; gibbous 
= three; half = two; quarter = one). These \textit{wishes }are the same as those 
granted by the 9th-level wizard spell and must be used within a number of minutes 
equal to the number received.

\textit{Rogue: }When this card is drawn, one of the character's NPC friends (preferably 
a cohort) is totally alienated and forever after

hostile. If the character has no cohorts, the enmity of some powerful personage 
(or community, or religious order) can be substituted. The hatred is secret until 
the time is ripe for it to be revealed with devastating effect.

\textit{Ruin: }As implied by its name, when this card is drawn, all nonmagical 
possessions of the drawer are lost.

\textit{Skull: }A dread wraith appears. Treat this creature as an unturnable undead. 
The character must fight it alone---if others help, they get dread wraiths to fight 
as well. If the character is slain, she is slain forever and cannot be revived, 
even with a \textit{wish }or a \textit{miracle}.

\textit{Star: }The 2 points are added to any ability the character chooses. They 
cannot be divided among two abilities. 

\textit{Sun: }Roll for a medium wondrous item until a useful item is indicated.

\textit{Talons: }When this card is drawn, every magic item owned or possessed by 
the character is instantly and irrevocably gone.

\textit{Throne: }The character becomes a true leader in people's eyes. The castle 
gained appears in any open area she wishes (but the decision where to place it 
must be made within 1 hour).

\textit{Vizier: }This card empowers the character drawing it with the one-time 
ability to call upon a source of wisdom to solve any

single problem or answer fully any question upon her request. The query or request 
must be made within one year. Whether the information gained can be successfully 
acted upon is another question entirely.

\textit{The Void: }This black card spells instant disaster. The character's body 
continues to function, as though comatose, but her psyche is trapped in a prison 
somewhere---in an object on a far plane or planet, possibly in the possession of 
an outsider. A \textit{wish }or a \textit{miracle }does not bring the character 
back, instead merely revealing the plane of entrapment. Draw no more cards.

Strong (all schools); CL 20th.

\vspace{12pt}
\textbf{Hammer of Thunderbolts:} This \textit{+3 Large returning warhammer }deals 
4d6 points of damage on any hit. Further, if the wielder wears a \textit{belt of 
giant Strength }and \textit{gauntlets of ogre power }and he knows that the hammer 
is a \textit{hammer of thunderbolts }(not just a \textit{+3 warhammer}), the weapon 
can be used to full effect: It gains a total +5 enhancement bonus, allows all \textit{belt 
}and \textit{gauntlet }bonuses to stack (only when using this weapon), and strikes 
dead any giant upon whom it scores a hit (Fortitude DC 20 negates the death effect 
but not the damage).

When hurled, on a successful attack the hammer emits a great noise, like a clap 
of thunder, causing all creatures within 90 feet to be stunned for 1 round (Fortitude 
DC 15 negates). The hammer's range increment is 30 feet.

Strong evocation, necromancy, and transmutation; CL 20th; Weight 15 lb.

\vspace{12pt}
\textbf{Philosopher's Stone:} This rare substance appears to be an ordinary, sooty 
piece of blackish rock. If the stone is broken open (break DC 20), a cavity is 
revealed at the stone's heart. This cavity is lined with a magical type of quicksilver 
that enables any arcane spellcaster to transmute base metals (iron and lead) into 
silver and gold. A single \textit{philosopher's stone }can turn from up to 5,000 
pounds of iron into silver, or up to 1,000 pounds of lead into gold. However, the 
quicksilver becomes unstable once the stone is opened and loses its potency within 
24 hours, so all transmutations must take place within that period.

The quicksilver found in the center of the stone may also be put to another use. 
If mixed with any \textit{cure }potion while the substance is still potent, it 
creates a special \textit{oil of life }that acts as a \textit{true resurrection 
}spell for any dead body it is sprinkled upon.

Strong transmutation; CL 20th;Weight 3 lb.

\vspace{12pt}
\textbf{Sphere of Annihilation:} A \textit{sphere of annihilation }is a globe of 
absolute blackness, a ball of nothingness 2 feet in diameter. The object is actually 
a hole in the continuity of the multiverse. Any matter that comes in contact with 
a sphere is instantly sucked into the void, gone, and utterly destroyed. Only the 
direct intervention of a deity can restore an annihilated character.

A \textit{sphere of annihilation }is static, resting in some spot as if it were 
a normal hole. It can be caused to move, however, by mental effort (think of this 
as a mundane form of telekinesis, too weak to move actual objects but a force to 
which the sphere, being weightless, is sensitive). A character's ability to gain 
control of a \textit{sphere of annihilation }(or to keep controlling one) is based 
on the result of a control check against DC 30 (a move action). A control check 
is 1d20 + character level + character Int modifier. If the check succeeds, the 
character can move the sphere (perhaps to bring it into contact with an enemy) 
as a free action.

Control of a sphere can be established from as far away as 40 feet (the character 
need not approach too closely). Once control is established, it must be maintained 
by continuing to make control checks (all DC 30) each round. For as long as a character 
maintains control (does not fail a check) in subsequent rounds, he can control 
the sphere from a distance of 40 feet + 10 feet per character level. The sphere's 
speed in a round is 10 feet +5 feet for every 5 points by which the character's 
control check result in that round exceeded 30.

If a control check fails, the sphere slides 10 feet in the direction of the character 
attempting to move it.

If two or more creatures vie for control of a \textit{sphere of annihilation, }the 
rolls are opposed. If none are successful, the sphere slips toward the one who 
rolled lowest.

Should a \textit{gate }spell be cast upon a \textit{sphere of annihilation}, there 
is a 50\% chance (01-50 on d\%) that the spell destroys it, a 35\% chance (51-85) 
that the spell does nothing, and a 15\% chance (86-100) that a gap is torn in the 
spatial fabric, catapulting everything within a 180-foot radius into another plane. 
If a \textit{rod of cancellation }touches a \textit{sphere of annihilation},

they negate each other in a tremendous explosion. Everything within a 60-foot radius 
takes 2d6x10 points of damage. \textit{Dispel}

\textit{magic }and \textit{mage's disjunction }have no effect on a sphere.

See also \textit{talisman of the sphere }(below).

Strong transmutation; CL 20th.

\vspace{12pt}
\textbf{Staff of the Magi:} A long wooden staff, shod in iron and inscribed with 
sigils and runes of all types, this potent artifact contains many spell powers 
and other functions. Some of its powers use charges, while others don't. The following 
powers do not use charges:•

\textit{Detect magic•}

\textit{Enlarge person (}Fortitude DC 15 negates)•

\textit{Hold portal•}

\textit{Light•}

\textit{Mage armor•}

\textit{Mage hand}

The following powers drain 1 charge per usage:•

\textit{Dispel magic•}

\textit{Fireball }(10d6 damage, Reflex DC 17 half )•

\textit{Ice storm•}

\textit{Invisibility•}

\textit{Knock•}

\textit{Lightning bolt }(10d6 damage, Reflex DC 17 half )•

\textit{Passwall•}

\textit{Pyrotechnics }(Will or Fortitude DC 16 negates)•

\textit{Wall of fire•}

\textit{Web}

These powers drain 2 charges per usage:•

\textit{Monster summoning IX•}

\textit{Plane shift }(Will DC 21 negates)•

\textit{Telekinesis }(400 lb. maximum weight; Will DC 19 negates)

A \textit{staff of the magi }gives the wielder spell resistance 23. If this is 
willingly lowered, however, the staff can also be used to absorb arcane spell energy 
directed at its wielder, as a \textit{rod of absorption} does. Unlike the rod, 
this staff converts spell levels into charges rather than retaining them as spell 
energy usable by a spellcaster. If the staff absorbs enough spell levels to exceed 
its limit of 50 charges, it explodes as if a retributive strike had been performed 
(see below). The wielder has no idea how many spell levels are cast at her, for 
the staff does not communicate this knowledge as a \textit{rod of absorption }does. 
(Thus, absorbing spells can be risky.)

\textit{Retributive Strike: }A \textit{staff of the magi }can be broken for a retributive 
strike. Such an act must be purposeful and declared by the wielder. All charges 
in the staff are released in a 30-foot spread. All within 10 feet of the broken 
staff take hit points of damage equal to 8 times the number of charges in the staff, 
those between 11 feet and 20 feet away take points equal to 6 times the number 
of charges, and those 21 feet to 30 feet distant take 4 times the number of charges. 
A DC 17 Reflex save reduces damage by half. 

The character breaking the staff has a 50\% chance (01-50 on d\%) of traveling 
to another plane of existence, but if she does not (51-100), the explosive release 
of spell energy destroys her. Only specific items, including the \textit{staff 
of the magi }and the \textit{staff of power} are capable of a retributive strike.

Strong (all schools); CL 20th;Weight 5 lb.

\vspace{12pt}
\textbf{Talisman of Pure Good:} A good (LG, NG, CG) divine spellcaster who possesses 
this item can cause a flaming crack to open at the feet of an evil (LE, NE, CE) 
divine spellcaster who is up to 100 feet away. The intended victim is swallowed 
up forever and sent hurtling to the center of the earth. The wielder of the talisman 
must be good, and if he is not exceptionally pure in thought and deed the evil 
character gains a DC 19 Reflex saving throw to leap away from the crack. Obviously, 
the target must be standing on solid ground for this item to function. 

A \textit{talisman of pure good }has 6 charges. If a neutral (LN, N, CN) divine 
spellcaster touches one of these stones, he takes 6d6 points of damage. If an evil 
divine spellcaster touches one, he takes 8d6 points of damage. All other characters 
are unaffected by the device.

Strong evocation [good]; CL 18th.

\vspace{12pt}
\textbf{Talisman of the Sphere:} This small adamantine loop and handle are useless 
to those unable to cast arcane spells. Characters

who cannot cast arcane spells take 5d6 points of damage merely from picking up 
and holding a talisman of this sort. However, when held by an arcane spellcaster 
who is concentrating on control of a \textit{sphere of annihilation, }a \textit{talisman 
of the sphere }doubles the character's modifier on his control check (doubling 
both his Intelligence bonus and his character level for this purpose).

If the wielder of a talisman establishes control, he need check for maintaining 
control only every other round thereafter. If control is not established, the sphere 
moves toward him. Note that while many spells and effects of cancellation have 
no effect upon a \textit{sphere of annihilation, }the talisman's power of control 
can be suppressed or canceled.

Strong transmutation; CL 16th;Weight 1 lb.

\vspace{12pt}
\textbf{Talisman of Reluctant Wishes: }A talisman of this sort appears the same 
as a \textit{stone of controlling earth elementals. }Its powers are quite different, 
however, and dependent on the Charisma of the individual holding the talisman. 
Whenever a character touches a \textit{talisman of reluctant wishes, }he must make 
a DC 15 Charisma check. 

If he fails, the device acts as a \textit{stone of weight}. Discarding or destroying 
it results in 5d6 points of damage to the character and the disappearance of the 
talisman. 

If he succeeds, the talisman remains with the character for 5d6 hours, or until 
a \textit{wish }is made with it, whichever comes first. It then disappears.

If he rolls a natural 20, the character finds it impossible to be rid of the talisman 
for as many months as he has points of Charisma. In addition, the artifact grants 
him one \textit{wish }for every 6 points of the character's Charisma. It also grows 
warm and throbs whenever its possessor comes within 20 feet of a mechanical or 
magic trap. (If the talisman is not held, its warning heat and pulses are of no 
avail.)

Regardless of which reaction results, a \textit{talisman of reluctant wishes }disappears 
when its time period expires, leaving behind a 10,000 gp diamond in its stead.

Strong conjuration; CL 20th;Weight 1 lb.

\vspace{12pt}
\textbf{Talisman of Ultimate Evil:} An evil (LE, NE, CE) divine spellcaster who 
possesses this item can cause a flaming crack to open at the feet of a good (LG, 
NG, CG) divine spellcaster who is up to 100 feet away. The intended victim is swallowed 
up forever and sent hurtling to the center of the earth. The wielder of the talisman 
must be evil, and if she is not exceptionally foul and perverse in the sights of 
her evil deity the good character gains a DC 19 Reflex save to leap away from the 
crack. Obviously, the target must be standing on solid ground for this item to 
function. 

A \textit{talisman of ultimate evil }has 6 charges. If a neutral (LN, N, CN) divine 
spellcaster touches one of these stones, she takes 6d6 points of damage. If a good 
divine spellcaster touches one, she takes 8d6 points of damage. All other characters 
are unaffected by the device. 

Strong evocation [evil]; CL 18th.

\vspace{12pt}
MAJOR ARTIFACTS

Major artifacts are unique items---only one of each such item exists. These are 
the most potent of magic items, capable of altering the balance of a campaign.

Unlike all other magic items, major artifacts are not easily destroyed. Each should 
have only a single, specific means of destruction.

\vspace{12pt}
Major Artifact Descriptions

\vspace{12pt}
\textbf{The Moaning Diamond:} The \textit{Moaning Diamond }appears to be an uncut 
diamond the size of a human fist. At all times, it gives forth a baleful moaning 
sound, as if in pain. Despite the noise, the \textit{Moaning Diamond }is not evil. 
The wielder of the stone can, three times per day, call upon it to reshape earth 
and stone as if by the spell \textit{stone shape, }affecting 5,000 cubic feet of 
material. The \textit{Moaning Diamond }can summon an elder earth elemental with 
maximum hit points that serves the caster until it is slain. Only one such elemental 
can be summoned at a time; if it is slain, a new creature cannot be summoned for 
24 hours. 

\vspace{12pt}
\textbf{The Orbs of Dragonkind:} Each of these fabled orbs contains the essence 
and personality of an ancient dragon of a different variety (one for each of the 
major ten different chromatic and metallic dragons). The bearer of an \textit{Orb 
}can \textit{dominate }dragons of its particular variety within 500 feet (as \textit{dominate 
monster}), the dragon being forced to make a DC 25 Will save to resist. (Spell 
resistance is not useful against this effect.) Each \textit{Orb of Dragonkind }bestows 
upon the wielder the AC and saving throw bonuses of the dragon within. These values 
replace whatever values the character would otherwise have, whether they are better 
or worse. These values cannot be modified by any means short of ridding the character 
of the \textit{Orb. }A character possessing an \textit{Orb of Dragonkind }is immune 
to the breath weapon---but only the breath weapon---of the dragon variety keyed 
to the \textit{Orb. }Finally, a character possessing an \textit{Orb }can herself 
use the breath weapon of the dragon in the \textit{Orb }three times per day.

All \textit{Orbs of Dragonkind }can be used to communicate verbally and visually 
with the possessors of the other \textit{Orbs. }The owner of an \textit{Orb }knows 
whether there are dragons within 10 miles at all times. For dragons of the \textit{Orb'}s 
particular variety, the range is 100 miles. If within 1 mile of a dragon of the 
\textit{Orb'}s variety, the wielder can determine the exact location and age of 
the creature. The bearer of one of these \textit{Orbs }earns the enmity forever 
of all dragonkind for profiting by the enslavement of one of their kin, even if 
she later loses the item. 

Each \textit{Orb }also has an individual power that can be invoked once per round 
at 10th caster level.•

\textit{Black Dragon Orb: Fly }(Will DC 17 negates).•

\textit{Blue Dragon Orb: Haste }(Fortitude DC 17 negates)\textit{.•}

\textit{Brass Dragon Orb: Teleport }(Will DC 19 negates)\textit{.•}

\textit{Bronze Dragon Orb: Scrying }(Will DC 18 negates)\textit{.•}

\textit{Copper Dragon Orb: Suggestion }(Will DC 17 negates)\textit{.•}

\textit{Gold Dragon Orb: }The owner of the gold \textit{Orb }can call upon any 
power possessed by one of the other \textit{Orbs---}including the \textit{dominate 
}and breath weapon abilities but not AC, save bonuses, or breath weapon immunity---but 
can only use an individual

power once per day. She can use \textit{dominate }on any other possessor of an 
\textit{Orb }within 1 mile (Will DC 23 negates).•

\textit{Green Dragon Orb: Spectral hand.•}

\textit{Red Dragon Orb: Wall of fire.•}

\textit{Silver Dragon Orb: Cure critical wounds }(Will DC 18 half )\textit{.•}

\textit{White Dragon Orb: Protection from energy (cold) }(Fortitude DC 17 negates)\textit{.}

\vspace{12pt}
\textbf{The Saint's Mace: }This relic appears to be a simple, well-used cudgel, 
but its simple appearance hides great power. The \textit{saint's mace }has a +5 
enhancement bonus and functions as a heavy mace with the holy, lawful, and disruption 
special abilities. The wielder can project \textit{searing light }from the mace 
at will, at caster level 20th.

\vspace{12pt}
\textbf{The Shadowstaff:} This artifact was crafted centuries ago, weaving together 
the wispy strands of shadow itself into a twisted black staff. The \textit{Shadowstaff 
}makes the wielder slightly shadowy and incorporeal, granting him a +4 bonus to 
AC and Reflex saves (which stacks with any other bonuses). However, in bright light 
(such as that of the sun, but not a torch) or in absolute darkness, the wielder 
takes a -2 penalty on all attack rolls, saves, and checks. 

The \textit{Shadowstaff }also has these powers.•

\textit{Summon Shadows: }Three times per day the staff may summon 2d4 shadows. 
Immune to turning, they serve the wielder as if called by a \textit{summon monster 
V }spell cast at 20th level.•

\textit{Summon Nightshade: }Once per month, the staff can summon a nightcrawler 
nightshade that serves the wielder as if called by a \textit{summon monster IX 
}spell cast at 20th level.•

\textit{Shadow Form: }Three times per day the wielder can become a living shadow, 
with all the movement powers granted by the

\textit{gaseous form }spell. •

\textit{Shadow Bolt: }Three times per day the staff can project a ray attack that 
deals 10d6 points of cold damage to a single target. The shadow bolt has a range 
of 100 feet.

\vspace{12pt}
The Shield of the Sun: This \textit{+5 large shield, }emblazoned with the symbol 
of the sun, allows the wielder to cast spells as if she were a 20th-level paladin 
with a Wisdom score of 20. The spells gained are cumulative with any existing spells 
per day that the character might have, even if she's already a paladin. The \textit{Shield 
of the Sun }also grants spell resistance 15 to its wielder. It absorbs the first 
10 points of damage from any energy attack (fire, cold, acid, electricity, or sonic). 
In return for all this, once per year the shield's owner must undertake a quest 
(no saving throw to avoid) at the behest of a lawful good deity. 

A character who is evil or chaotic (LE, NE, CE, CN, CG) gains four negative levels 
if she attempts to use this artifact. Although these negative levels never results 
in actual level loss, they remain as long as the shield is in hand and cannot be 
overcome in any way (including \textit{restoration }spells). The negative levels 
disappear when the shield is stowed or leaves the wearer's possession.
