\section{Staves}

A staff is a long shaft of wood that stores several spells. Unlike wands, which 
can contain a wide variety of spells, each staff is of a certain kind and holds 
specific spells. A staff has 50 charges when created.

\textbf{Physical Description:} A typical staff is 4 feet to 7 feet long and 2 inches 
to 3 inches thick, weighing about 5 pounds. Most staffs are wood, but a rare few 
are bone, metal, or even glass. (These are extremely exotic.) Staffs often have 
a gem or some device at their tip or are shod in metal at one or both ends. Staffs 
are often decorated with carvings or runes. A typical staff is like a walking stick, 
quarterstaff, or cudgel. It has AC 7, 10 hit points, hardness 5, and a break DC 
of 24.

\textbf{Activation:} Staffs use the spell trigger activation method, so casting 
a spell from a staff is usually a standard action that doesn't provoke attacks 
of opportunity. (If the spell being cast, however, has a longer casting time than 
1 standard action, it takes that long to cast the spell from a staff.) To activate 
a staff, a character must hold it forth in at least one hand (or whatever passes 
for a hand, for nonhumanoid creatures).

\textbf{Special Qualities:} Roll d\%. A 01-30 result indicates that something (a 
design, inscription, or the like) provides some clue to the staff 's function, 
and 31-100 indicates no special qualities.

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{4}{|p{3.575in}|}{\begin{minipage}[t]{3.575in}\raggedright
\textbf{Table: Staffs}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{4}{p{0.278in}|}{\begin{minipage}[t]{0.278in}\centering
\textbf{Medium}\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textbf{Staff}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.013in}|}{\begin{minipage}[t]{1.013in}\centering
01-15\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
01-03\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Charming}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
16,500 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
16-30\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
04-09\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Fire}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
17,750 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
31-40\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
10-11\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Swarming insects}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
24,750 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
41-60\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
12-17\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Healing}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
27,750 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
61-75\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
18-19\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Size alteration}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
29,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
76-90\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
20-24\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Illumination}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
48,250 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
91-95\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
25-31\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Frost}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
56,250 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
96-100\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
32-38\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Defense}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
58,250 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
39-43\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Abjuration}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
44-48\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Conjuration}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 13
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
49-53\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Enchantment}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
54-58\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Evocation}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
59-63\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Illusion}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 16
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
64-68\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Necromancy}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 17
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
69-73\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Transmutation}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
65,000 gp\end{minipage}}\\
\hline
% ROW 18
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
74-77\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Divination}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
73,500 gp\end{minipage}}\\
\hline
% ROW 19
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
78-82\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Earth and stone}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
80,500 gp\end{minipage}}\\
\hline
% ROW 20
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
83-87\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Woodlands}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
101,250 gp\end{minipage}}\\
\hline
% ROW 21
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
88-92\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Life}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
155,750 gp\end{minipage}}\\
\hline
% ROW 22
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
93-97\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Passage}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
170,500 gp\end{minipage}}\\
\hline
% ROW 23
\multicolumn{5}{p{1.291in}|}{\begin{minipage}[t]{1.291in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.724in}|}{\begin{minipage}[t]{0.724in}\centering
98-100\end{minipage}} & \multicolumn{1}{p{0.639in}|}{\begin{minipage}[t]{0.639in}\centering
\textit{Power}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
211,000 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
Staff Descriptions

Staffs use the wielder's ability score and relevant feats to set the DC for saves 
against their spells. Unlike with other sorts of magic items, the wielder can use 
his caster level when activating the power of a staff if it's higher than the caster 
level of the staff. 

This means that staffs are far more potent in the hands of a powerful spellcaster. 
Because they use the wielder's ability score to set the save DC for the spell, 
spells from a staff are often harder to resist than ones from other magic items, 
which use the minimum ability score required to cast the spell.  Not only are aspects 
of the spell dependant on caster level (range, duration, and so on) potentially 
higher, but spells from a staff are harder to dispel and have a better chance of 
overcoming a target's spell resistance.

Furthermore, a staff can hold a spell of any level, unlike a wand, which is limited 
to spells of 4th level or lower. The minimum caster level of a staff is 8th. Standard 
staffs are described below.

\textbf{Abjuration:} Usually carved from the heartwood of an ancient oak or other 
large tree, this staff allows use of the following spells:•

\textit{Shield }(1 charge)•

\textit{Resist energy }(1 charge)•

\textit{Dispel magic }(1 charge)•

\textit{Lesser globe of invulnerability }(2 charges)•

\textit{Dismissal }(2 charges)•

\textit{Repulsion }(3 charges)

Strong abjuration; CL 13th; Craft Staff, \textit{dismissal, dispel magic, lesser 
globe of invulnerability, resist energy, repulsion, shield; }Price 65,000 gp.

\textbf{Charming:} Made of twisting wood ornately shaped and carved, this staff 
allows use of the following spells:•

\textit{Charm person }(1 charge)•

\textit{Charm monster }(2 charges)

Moderate enchantment; CL 8th; Craft Staff, \textit{charm person, charm monster; 
}Price 16,500 gp.

\textbf{Conjuration:} This staff is usually made of ash or walnut and bears ornate 
carvings of many different kinds of creatures. It allows use of the following spells:•

\textit{Unseen servant }(1 charge)•

\textit{Summon swarm }(1 charge)•

\textit{Stinking cloud }(1 charge)•

\textit{Minor creation }(2 charges)•

\textit{Cloudkill }(2 charges)•

\textit{Summon monster VI }(3 charges)

Strong conjuration; CL 13th; Craft Staff, \textit{cloudkill, stinking cloud, summon 
monster VI, summon swarm, unseen servant; }Price 65,000 gp.

\textbf{Defense: }The \textit{staff of defense }is a simple-looking staff that 
throbs with power when held defensively. It allows use of the following spells:•

\textit{Shield }(1 charge)•

\textit{Shield of faith }(1 charge)•

\textit{Shield other }(1 charge)•

\textit{Shield of law }(3 charges)

Strong abjuration; CL 15th; Craft Staff, \textit{shield, shield of faith, shield 
of law, shield other}, creator must be lawful; Price 58,250 gp.

\textbf{Divination:} Made from a supple length of willow, often with a forked tip, 
this staff allows use of the following spells:•

\textit{Detect secret doors }(1 charge)•

\textit{Locate object }(1 charge)•

\textit{Tongues }(1 charge)•

\textit{Locate creature }(2 charges)•

\textit{Prying eyes }(2 charges)•

\textit{True seeing }(3 charges)

Strong divination; CL 13th; Craft Staff, \textit{detect secret doors}, \textit{locate 
creature, locate object, prying eyes, tongues}, \textit{true seeing}; Price 73,500 
gp.

\textbf{Earth and Stone:} This staff is topped with a fist-sized emerald that gleams 
with smoldering power. It allows the use of the following spells: •

\textit{Passwall }(1 charge)•

\textit{Move earth }(1 charge)

Moderate transmutation; CL 11th; Craft Staff, \textit{move earth, passwall}; Price 
80,500 gp.

\textbf{Enchantment:} Often made from applewood and topped with a clear crystal, 
this staff allows use of the following spells:•

\textit{Sleep }(1 charge)•

\textit{Hideous laughter }(1 charge)•

\textit{Suggestion }(1 charge)•

\textit{Crushing despair }(2 charges)•

\textit{Mind fog }(2 charges)•

\textit{Suggestion, mass }(3 charges)

Strong enchantment; CL 13th; Craft Staff, c\textit{rushing despair, mass suggestion, 
mind fog, sleep, suggestion, hideous laughter; }Price 65,000 gp.

\textbf{Evocation: }Usually very smooth and carved from hickory, willow, or yew, 
this staff allows use of the following spells:•

\textit{Magic missile }(1 charge)•

\textit{Shatter }(1 charge)•

\textit{Fireball }(1 charge)•

\textit{Ice storm }(2 charges)•

\textit{Wall of force }(2 charges)•

\textit{Chain lightning }(3 charges)

Strong evocation; CL 13th; Craft Staff\textit{, chain lightning, fireball, ice 
storm, magic missile,}

\textit{shatter, wall of force; }Price 65,000 gp.

\textbf{Fire:} Crafted from bronzewood with brass bindings, this staff allows use 
of the following spells:•

\textit{Burning hands }(1 charge)•

\textit{Fireball }(1 charge)•

\textit{Wall of fire }(2 charges)

Moderate evocation; CL 8th; Craft Staff, \textit{burning hands, fireball, wall 
of fire}; Price 17,750 gp.

\textbf{Frost:} Tipped on either end with a glistening diamond, this rune-covered 
staff allows use of the following spells:•

\textit{Ice storm }(1 charge)•

\textit{Wall of ice }(1 charge)•

\textit{Cone of cold }(2 charge)

Moderate evocation; CL 10th; Craft Staff\textit{, cone of cold}, \textit{ice storm, 
wall of ice; }Price 56,250 gp.

\textbf{Healing: }This white ash staff, with inlaid silver runes, allows use of 
the following spells:•

\textit{Lesser restoration }(1 charge)•

\textit{Cure serious wounds }(1 charge)•

\textit{Remove blindness/deafness }(2 charges)•

\textit{Remove disease }(3 charges)

Moderate conjuration; CL 8th; Craft Staff, \textit{cure serious wounds, lesser 
restoration, remove blindness/deafness, remove disease}; Price 27,750 gp.

\textbf{Illusion:} This staff is made from ebony or other dark wood and carved 
into an intricately twisted, fluted, or spiral shape. It allows use of the following 
spells:•

\textit{Disguise self }(1 charge)•

\textit{Mirror image }(1 charge)•

\textit{Major image }(1 charge)•

\textit{Rainbow pattern }(2 charges)•

\textit{Persistent image }(2 charges)•

\textit{Mislead }(3 charges)

Strong illusion; CL 13th; Craft Staff, \textit{disguise self, major image, mirror 
image, persistent image, project image, rainbow pattern; }Price 65,000 gp.

\textbf{Illumination: }This staff is usually sheathed in silver and decorated with 
sunbursts. It allows use of the following spells:•

\textit{Dancing lights }(1 charge)•

\textit{Flare }(1 charge)•

\textit{Daylight }(2 charges)•

\textit{Sunburst }(3 charges)

Strong evocation; CL 15th; Craft Staff, \textit{dancing lights, daylight, flare, 
sunburst}; Price 48,250 gp.

\textbf{Life:} Made of thick oak shod in gold, this staff allows use of the following 
spells:•

\textit{Heal }(1 charge)•

\textit{Raise dead }(5 charges)

Moderate conjuration; CL 11th; Craft Staff, \textit{heal, resurrection}; Price 
155,750 gp.

\textbf{Necromancy: }This staff is made from ebony or other dark wood and carved 
with the images of bones and skulls. It allows use of the following spells:•

\textit{Cause fear }(1 charge)•

\textit{Ghoul touch }(1 charge)•

\textit{Halt undead }(1 charge)•

\textit{Enervation }(2 charges)•

\textit{Waves of fatigue }(2 charges)•

\textit{Circle of death }(3 charges)

Strong necromancy; CL 13th; Craft Staff, \textit{cause fear, circle of death, enervation, 
ghoul touch, halt undead, waves of fatigue; }Price 65,000 gp.

\textbf{Passage:} This potent item allows use of the following spells: •

\textit{Dimension door }(1 charge)•

\textit{Passwall }(1 charge)•

\textit{Phase door }(2 charges)•

\textit{Greater teleport }(2 charges)•

\textit{Astral projection }(2 charges)

Strong varied; CL 17th; Craft Staff, \textit{astral projection, dimension door, 
greater teleport, passwall, phase door}; Price 170,500 gp.

\textbf{Power:} The \textit{staff of power }is a very potent magic item, with offensive 
and defensive abilities. It is usually topped with a glistening gem, its shaft 
straight and smooth. It has the following powers:•

\textit{Magic missile }(1 charge)•

\textit{Ray of enfeeblement }(heightened to 5th level) (1 charge)•

\textit{Continual flame }(1 charge)•

\textit{Levitate }(1 charge)•

\textit{Lightning bolt }(heightened to 5th level) (1 charge)•

\textit{Fireball }(heightened to 5th level) (1 charge)•

\textit{Cone of cold }(2 charges)•

\textit{Hold monster }(2 charges)•

\textit{Wall of force }(in a 10-ft.-diameter hemisphere around the caster only) 
(2 charges)•

\textit{Globe of invulnerability }(2 charges)

The wielder of a \textit{staff of power }gains a +2 luck bonus to AC and saving 
throws. The staff is also a \textit{+2 quarterstaff, }and its wielder may use it 
to smite opponents. If 1 charge is expended (as a free action), the staff causes 
double damage (x3 on a critical hit) for 1 round.

A \textit{staff of power }can be used for a retributive strike, requiring it to 
be broken by its wielder. (If this breaking of the staff is purposeful and declared 
by the wielder, it can be performed as a standard action that does not require 
the wielder to make a Strength check.) All charges currently in the staff are instantly 
released in a 30-foot radius. All within 2 squares of the broken staff take points 
of damage equal to 8 x the number of charges in the staff, those 3 or 4 squares 
away take 6 x the number of charges in damage, and those 5 or 6 squares distant 
take 4 x the number of charges in damage. All those affected can make DC 17 Reflex 
saves to reduce the damage by half.

The character breaking the staff has a 50\% chance of traveling to another plane 
of existence, but if he does not, the explosive release of spell energy destroys 
him. Only certain items, including the \textit{staff of the magi} and the \textit{staff 
of power, }are capable of being used for a retributive strike.

After all charges are used up from the staff, it remains a \textit{+2 quarterstaff}. 
(Once empty of charges, it cannot be used for a retributive strike.)

Strong varied; CL 15th; Craft Staff, Craft Magic Arms and Armor, \textit{magic 
missile, }heightened \textit{ray of enfeeblement, continual flame, levitate, }heightened 
\textit{fireball, }heightened \textit{lightning bolt, cone of cold, hold monster, 
wall of force, globe of invulnerability; }Price 211,000 gp.

\textbf{Size Alteration:} Stout and sturdy, this staff of dark wood allows use 
of the following spells:•

\textit{Enlarge person }(1 charge)•

\textit{Reduce person }(1 charge)•

\textit{Shrink item }(1 charge)•

\textit{Enlarge person, mass }(1 charge)•

\textit{Reduce person, mass }(1 charge)

Faint conjuration; CL 8th; Craft Staff, \textit{enlarge person, mass enlarge person, 
reduce person, mass reduce person, shrink item}; Price 29,000 gp.

\textbf{Swarming Insects:} Made of twisted dark wood with dark spots resembling 
crawling insects (which occasionally seem to move), this staff allows use of the 
following spells:•

\textit{Summon swarm }(1 charge)•

\textit{Insect plague }(3 charges)

Moderate conjuration; CL 9th; Craft Staff, \textit{insect plague, summon swarm}; 
Price 24,750 gp.

\textbf{Transmutation:} This staff is generally carved from or decorated with petrified 
wood and allows use of the following spells:•

\textit{Expeditious retreat }(1 charge)•

\textit{Alter self }(1 charge)•

\textit{Blink }(1 charge)•

\textit{Polymorph }(2 charges)•

\textit{Baleful polymorph }(2 charges)•

\textit{Disintegrate }(3 charges)

Strong transmutation; CL 13th; Craft Staff, \textit{alter self, baleful polymorph, 
blink, disintegrate, expeditious retreat, polymorph; }Price 65,000 gp.

\textbf{Woodlands:} Appearing to have grown naturally into its shape, this oak, 
ash, or yew staff allows use of the following spells:•

\textit{Charm animal }(1 charge)•

\textit{Speak with animals }(1 charge)•

\textit{Barkskin }(2 charges)•

\textit{Wall of thorns }(3 charges)•

\textit{Summon nature's ally VI }(3 charges)•

\textit{Animate plants }(4 charges)

The staff may be used as a weapon, functioning as a \textit{+2 quarterstaff}. The 
\textit{staff of the woodlands }also allows its wielder to \textit{pass without 
trace }at will, with no charge cost. These two attributes continue to function 
after all the charges are expended.

Moderate varied; CL 13th; Craft Staff, Craft Magic Arms and Armor, \textit{animate 
plants, barkskin, charm animal, pass without trace, speak with animals, summon 
nature's ally VI, wall of thorns; }Price 101,250 gp.
