
\classname{Fiendish Brute [Fiend]}
\vspace*{-8pt}
\quot{"Rowwr!"}



\desc{The power of a fiend goes beyond mere magical power: it is a transformation into a form that most suits one's evil. For some fiends, physical power is the route by which they work their will on the world, and fangs and claws are just a few of the weapons that fiends develop in order to rend the helpless flesh of their prey. Physical transformations like stingers, wings, poisons, and vile diseases all find their way into the armaments of fiends, but do not think that these are the limits of their evil; fiends are nothing if not creative in the pursuit of their own particular brand of evil.}

\ability{Alignment:}{A character must be non-good to take any levels in Fiendish Brute. Nothing happens to a Fiendish Brute if he becomes Good, save that he must look elsewhere for class advancing.}

\ability{Races:}{The Fiendish Brute is \emph{only} available to Outsiders with a plane of origin in the Lower Planes. Creatures from the prime material plane whose ancestors were from a Lower Plane may take this class, but they must have the Outsider type.}

\ability{Starting Gold:}{4d4x10 gp (100 gold)}

\ability{Starting Age:}{As Warforged Rogue.}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{The Fiendish Brute's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Hide (Dex), Jump (Str), Listen (Wis), Move Silently (Dex), Sense Motive (Wis), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}



\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{8cm}}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2 &+0 &Natural Weapons, Natural Armor, Attribute Boost\\
2nd &+1 &+3 &+3 &+0 &Bonus Feat\\
3rd &+1 &+3 &+3 &+1 &Attribute Boost\\
4th &+2 &+4 &+4 &+1 &Bonus Feat\\
5th &+2 &+4 &+4 &+1 &Attribute Boost\\
6th &+3 &+5 &+5 &+2 &Bonus Feat\\
7th &+3 &+5 &+5 &+2 &Attribute Boost\\
8th &+4 &+6 &+6 &+2 &Bonus Feat\\
9th &+4 &+6 &+6 &+3 &Attribute Boost\\
10th &+5 &+7 &+7 &+3 &Bonus Feat\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Fiendish Brute class.

\ability{Weapon and Armor Proficiency:}{Fiendish Brutes are proficient only with armor spikes, and aren't inherently proficient with any armor.}

\ability{Natural Weapons:}{A Fiendish Brute has 2 claw attacks, one attached to each arm (or its two front legs if it is a quadruped, if it has no limbs at all it grows two vestigial arms that have claws at the end). These claws are natural weapons and inflict damage normal for the creature's size.}

\ability{Natural Armor:}{A Fiendish Brute has a natural armor bonus of 3 plus its class level. So a 7th level Fiendish Brute has a natural armor bonus of +10.}

\ability{Attribute Boost:}{At 1st level and every odd numbered level afterwards, the Fiendish Brute's physical attributes improve, as if it had gained several character levels. Every time the Fiendish Brute gains an attribute boost, two of his physical attributes irrevocably increase by 1.}

\ability{Bonus Feat:}{At every even numbered level, the Fiendish Brute gains a bonus feat. This feat may be any [Fiend], [Monstrous], or [General] feat, and the Fiendish Brute must meet the prerequisites.}
