\classname{Marshall} \label{class:marshall}
\vspace*{-8pt}
\quot{"The Jarls of Niefelheim think to banish our summers to a land of darkness. If they succeed there will be no second chances, no future generations. We will stop them here. For if our children's children are to even exist, they must remember our bravery on this day!"}

\desc{The Marshall is a leader of men. Whether a member of a squad of Halfling special forces or the head of a rampaging horde of Bugbears, the Marshall's true home is the battlefield.}

\ability{Alignment:}{Leaders arise on every aspect of the wheel. From the hordes of the Orcs to the formations of the Dwarves, there is almost always a charismatic leader at the head of any serious army. Serious armies are often employed by the forces of Law, as the forces of Chaos are often wont to be embodied by individuals pillaging without reference one to another. But the forces of Chaos have their share of tyrants as well.}

\ability{Races:}{Almost all Marshalls are humanoids. There are few races of Giants or Magical Beasts that form warbands sufficient to warrant military leadership.}

\ability{Attributes:}{Charisma is of prime importance to a Marshall. Other than that, a Marshall spends a lot of time yelling in plain view of enemies, so Constitution is of perhaps greater importance for them than it is to many other classes.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{As Paladin.}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Marshall's class skills (and the key ability for each skill) are Bluff (Cha), Climb (Str), Craft (Int), Concentration (Con), Diplomacy (Cha), Disguise (Cha), Gather Information (Cha), Handle Animal (Cha), Heal (Wis), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge [Any] (Int), Listen (Wis), Move Silently (Dex), Profession (-), Ride (Dex), Search (Int), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Survival (Wis), Swim (Str), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1 &+1 &+2 &+2 &+2 &Battle Shout, \spell{Heal Injuries}, Inspire Bravery\\
2 &+2 &+3 &+3 &+3 &Untiring, Magic Circle\\
3 &+3 &+3 &+3 &+3 &Dispelling Glare, War Shout\\
4 &+4 &+4 &+4 &+4 &Bolster Allies, Inspire Heroism\\
5 &+5 &+4 &+4 &+4 &\spell{Aura of Healing}, Project Voice\\
6 &+6/+1 &+5 &+5 &+5 &Leadership, \spell{Restoration}\\
7 &+7/+2 &+5 &+5 &+5 &\spell{Heal}, Terrible Shout\\
8 &+8/+3 &+6 &+6 &+6 &Inspire Foolishness, Delaying Shout\\
9 &+9/+4 &+6 &+6 &+6 &Inspire the Masses, \spell{Revive the Dead}\\
10 &+10/+5 &+7 &+7 &+7 &\spell{Mass Heal}, Command Enemies\\
11 &+11/+6/+6 &+7 &+7 &+7 &Massive Presence, Inspire Greater Heroism\\
12 &+12/+7/+7 &+8 &+8 &+8 &Convert Opponents
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Marshall class.

\ability{Weapon and Armor Proficiency:}{Marshalls are proficient with all simple and Marshall weapons, as well as any Exotic Weapons appropriate to their race, religion, or culture. Marshalls are proficient with light, Medium, and Heavy armor as well as Shields and Great Shields.}

\ability{Battle Shout (Ex):}{With a Swift Action, a Marshall may scream super loud and work up his allies for battle. All allies within short range gain a Morale Bonus to attack and damage rolls for 10 rounds. This bonus is half the Marshall's class level (rounded up) or the Marshall's Charisma modifier, whichever is less. Allies must be able to see and hear the Marshall for this bonus to take effect.}

\ability{Heal Injuries (Sp):}{The blood of an army is the life of its men, and soldiers who cannot fight are less than worthless. With a one minute ritual, a Marshall can heal a number of characters equal to his class level of a number of hit points of damage equal to his ranks in the Heal skill. This action may be taken a number of times per day equal to 3 + the Marshall's Charisma Modifier (if any), and all affected characters must be within close range of the Marshall or the entire period.}

\ability{Inspire Bravery (Ex):}{A Marshall's mere presence is a boon to the morale of his compatriots. All allies within short range of a Marshall may add the Marshall's Charisma modifier to their saves against [Fear] effects.}

\ability{Untiring (Ex):}{A 2nd level Marshall need not ever sleep and is immune to any effects which cause \condition{fatigue}, \condition{exhaustion}, or \condition{sleep}.}

\ability{Magic Circle (Su):}{A 2nd level Marshall radiates a \spell{magic circle} against an alignment of his choice at all times. He can end, resume, or change the alignment of his circle as a Swift action.}

\ability{Dispelling Glare (Su):}{A 3rd level Marshall can attempt to destroy a magical effect by staring at it really hard. As a Swift Action, the Marshall may attempt to dispel a single magical effect or suppress a single magical item within medium range and line of sight. The dispelling effect and DC is as per \spell{dispel magic}, and the Marshall's check is a d20 + Marshall Level.}

\ability{War Shout (Ex):}{At 3rd level, a Marshall's Battle Shout effects all allies within Long Range. The allies must still be able to hear and see the Marshall as normal.}

\ability{Bolster Allies (Ex):}{With a Swift action, a 4th level Marshall may assist all allies within short range of himself. These allies may each reroll one die roll made before the Marshall's next turn. They must be able to see and hear the Marshall when the reroll is called for.}

\ability{Inspire Heroism (Ex):}{The allies of a 4th level Marshall are capable of heroic, even improbable feats so long as they can see and hear the Marshall. All allies within Short Range of the Marshall gain a +1 Luck bonus on attack rolls, skill and ability checks, and saves.}

\ability{Aura of Healing (Su):}{A 5th level Marshall can activate an Aura of Healing as a Swift Action. This aura lasts for 10 rounds and may be activated a number of times per day equal to the Marshall's Charisma modifier. All allies within short range heal a number of hit points equal to the Marshall's ranks in Heal during the Marshall's turn while the aura is in effect.}

\ability{Project Voice (Ex):}{The voice of a 5th level Marshall carries super far. In anything approaching normal conditions, the Marshall can project his voice out for a mile. The Marshall can automatically dispel a \spell{silence} or similar effect as a Swift action.}

\ability{Leadership:}{At 6th level, a Marshall gains a Leadership feat that he qualifies for as an additional feat.}

\ability{Restoration (Sp):}{A 6th level Marshall can cast \spell{restoration} as a spell-like abilty at will.}

\ability{Heal (Sp):}{A 7th level Marshall may use \spell{heal} as a spell-like ability with a caster level equal to his Character Level. This may be used a number of times per day equal to his Charisma modifier.}

\ability{Terrible Shout (Ex):}{A 7th level Marshall can spook all enemies within Medium range with a terrible war howl. Enemies who can see and hear the Marshall within range must make a Will save (DC 10 + \half Level + Charisma Modifier) or become \condition{frightened} for 10 rounds. This is a [Fear] effect and only affects creatures with an Intelligence score. Creatures who succeed in their save are unaffected for the next 24 hours.}

\ability{Inspire Foolishness (Ex):}{People do dumb stuff for an 8th level Marshall. All allies within Short Range of a Marshall are immune to Fear so long as they can see and hear the Marshall.}

\ability{Delaying Glare (Ex):}{An 8th level Marshall can trip up and delay enemies with a steady Glare and an intimidating stance. With a Swift Action, the Marshall may force all enemies within Medium Range to make a Will save (DC 10 + \half Level + Charisma Modifier) or become \spell{slowed} for 10 rounds. Enemies must be able to see the Marshall, but they need not hear him.}

\ability{Inspire the Masses (Ex):}{The Inspiration abiilties of a 9th level Marshall extend to Long range, provided that the allies can still see and hear the Marshall.}

\ability{Revive the Dead (Sp):}{A 9th level Marshall can refill the ranks of his army by returning the fallen to life. With a 10 minute ritual, the Marshall can return a dead creature back to life so long as it has died within a number of days equal to the Marshall's ranks in the Heal skill. The newly alive awaken with a number of hit points as if they had had zero and then rested for 1 day (usually 2 hit points per hit die). The Marshall may do this a number of times per day equal to his Charisma modifier. This abiilty does not affect a character's level, nor does it restore removed body parts.}

\ability{Mass Heal (Sp):}{A 10th level Marshall can cast \spell{mass heal} as a spell-like ability a number of times per day equal to his Charisma modifier.}

\ability{Command Enemies (Ex):}{With a standard action, a Marshall can issue commands to opponents as the spell \spell{greater command}. Unless enemies make a Will Save (DC 10 + \half Level + Charisma Modifier), these commands are obeyed. This is a [Mind Affecting] [Language Dependant] ability.}

\ability{Massive Presence (Su):}{An 11th level Marshall can grow one size category and emit light as a bonfire at will. In addition to making the Marshall stronger and more powerful as normal, the Marshall is of course much easier to see. This effect may be begun or ended as a Swift Action.}

\ability{Inspire Greater Heroism (Ex):}{At 11th level, the Luck bonus provided by Inspire Heroism increases to +2. It still affects all allies who can see and hear him within Long Range (because of the Inspire the Masses ability).}

\ability{Convert Opponents (Ex):}{A 12th level Marshall can make an opponent within Medium Range Friendly to himself and his cause with a Standard Action unless the creature makes a Will Save (DC 10 + \half Level + Charisma Modifier). This is a [Mind Affecting] [Compulsion] effect, but any changes in attitude caused by subsequent Diplomacy or actions are not. In all other respects, this functions as \spell{charm monster}. This ability may be used at will.}
