\classname{Puppeteer} \label{class:puppeteer}
\vspace*{-8pt}
\quot{"This time, I think they'll stay up longer - I used more juice."}

\desc{It is well known to those who investigate such things that electrical energy can bring animation to the freshly dead in much the same way as positive or negative energy can. Those who have a natural inclination towards commanding the lightning can live out their life in obscurity or they can investigate their own abilities.

Those of a particularly investigative bent can accomplish much towards animating the dead and even creating new life. The puppeteer is one such person.}

\ability{Alignment:}{Electricity is a destructive force, but it is also the source of life. The Puppeteer focuses on the animating aspects, and a lot of them are Lawful. But they don't have to be.}

\ability{Races:}{Puppeteers appear in all races, though significant portions of many races live in areas where being a Puppeteer is illegal.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d8}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}p{9cm}}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2 &+2 &Electricity Resistance, Jolt, Electric Bolts, Puppet the Dead, Electric Magic\\
2nd &+1 &+3 &+3 &+3 &Disrupting Shock, Familiar\\
3rd &+2 &+3 &+3 &+3 &Greased Lightning, Repair Construct\\
4th &+3 &+4 &+4 &+4 &Electricity Immunity, Arc Light, Devastating Thunder\\
5th &+3 &+4 &+4 &+4 &Perpetual Storm, Corpse Quickening\\
6th &+4 &+5 &+5 &+5 &Persistent Puppets\\
7th &+5 &+5 &+5 &+5 &Lightning Bolts\\
8th &+6/+1 &+6 &+6 &+6 &Create Golem\\
9th &+6/+1 &+6 &+6 &+6 &Army of Puppets\\
10th &+7/+2 &+7 &+7 &+7 &Tunneling\\
11th &+8/+3 &+7 &+7 &+7 &Magnetism\\
12th &+9/+4 &+8 &+8 &+8 &Life Anew\\
\end{tabular}
\end{small}
\end{table}

\ability{Class Skills:}{The Puppeteer's class skills (and the key ability for each skill) are Bluff (Cha), Craft (Int), Concentration (Con), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Handle Animal (Cha), Intimidate (Cha), Knowledge (Each skill individually, Int), Listen (Wis), Move Silently (Dex), Profession (-), Ride (Dex), Search (Int), Spellcraft (Int), Spot (Wis), Survival (Wis), and Use Rope (Dex).}

\ability{Skills/Level:}{ 4 + Intelligence Bonus}

\smallskip\noindent All of the following are Class Features of the Puppeteer class:

\ability{Weapon and Armor Proficiency:}{Puppeteers are proficient with all simple weapons, as well as the whip, all martial spears, and all sizes and varieties of chain (including spiked chains). Puppeteers are proficient with light armor but not with shields of any kind.}

\ability{Electricity Resistance (Ex):}{A Puppeteer has a Resistance to Electricity equal to twice his level.}

\ability{Jolt (Su):}{As a standard action, a Puppeteer can electrify his body, shocking the next creature which he touches or which touches him during the next minute. This shock inflicts 1d6 of electricity damage, with an allowed Fortitude Save for half (DC 10 + 1/2 Level + Charisma Modifier).}

\ability{Electric Bolts (Sp):}{A Puppeteer can throw bolts of electricity as an attack action. A Lightning Bolt tavels out to short range, and inflicts 1d6 of Fire damage per level. A Lightning Bolt strikes its target with a ranged touch attack.}

\ability{Puppet the Dead (Su):}{If the Puppeteer can inflict electricity damage on a corpse, he can can it to rise as a zombie. This zombie can't have more than 4 hit dice for every level of puppeteer he possesses, and it immediately collapses if it has been active for more than 10 minutes or if the puppeteer animates a second corpse.
\begin{list}{}{\itemspace}\item These zombies are of the construct type rather than being true undead, and are healed by electricity damage. Otherwise use the normal zombie template\end{list}}

\ability{Electric Magic (Ex):}{A Puppeteer is considered to have every spell with the Electricity Descriptor on his spell list for the purpose of activating magic items.}

\ability{Disrupting Shock (Sp):}{As a standard action, a 2nd level Puppeteer can create an electrical discharge inside another creature's body. This effect causes a d6 of damage and stuns the target for one round. The victim is entitled to a Fortitude save (DC 10 + 1/2 Level + the Puppeteer's Intelligence bonus) to halve the damage and negate the stunning effect. This ability can be used out to Medium range, and it always hits.}

\ability{Familiar:}{At 2nd level, a Puppeteer is entitled to a familiar. They may choose a corpse familiar or a construct familiar, but not a normal living animal.}

\ability{Greased Lightning (Ex):}{From 3rd level on, a Puppeteer's Electricity cuts through Electricity Resistance, hardness, and Immunity. No more than 1/2 of the damage inflicted by his electrical damage can be negated by hardness or immunity or resistance to electricity. In addition, the Puppeteer ignores the first 5 points of Electricity Resistance that a target has.}

\ability{Repair Construct (Sp):}{A 3rd level Puppeteer can energize a construct with a touch. This touch heals 2d8+Level hit points, and is be usable at any time.}

\ability{Electricity Immunity (Ex):}{A 4th level Puppeteer is immune to Electricity.}

\ability{Arc Light (Sp):}{A 4th level Puppeteer may shed light like a \emph{daylight} spell from his own body. The clearly electrical light emanates from any portion of the character's body and can be begun or ended as a move action.}

\ability{Devastating Thunder (Ex):}{When a 4th level Puppeteer inflicts electrical damage on any target, he inflicts an additional amount of that damage equal to his Intelligence modifier or his class level, whichever is less.}

\ability{Perpetual Storm (Sp):}{A 5th level Puppeteer benefits from \emph{call lightning} at all times.}

\ability{Corpse Quickening (Ex):}{When a 5th level Puppeteer animates a corpse, it is not limited to a single standard action.}

\ability{Persistent Puppets (Su):}{A 6th level Puppeteer can create lightning zombies which last an entire day before falling apart on their own.}

\ability{Lightning Bolts (Sp):}{At 7th level, the Puppeteer can send forth a \emph{lightning bolt} as the sorcerer/wizard spell, at will. This spell-like ability has a save DC of 10 + 1/2 Level + Intelligence Modifier. Unlike the normal spell, a Puppeteer's Lightning Bolt has no damage cap.}

\ability{Create Golem (Su):}{An 8th level Puppeteer can create Flesh Golems. These do not require the expenditure of XP. The latest creation, and \emph{only} the last one created by the Puppeteer is immune to the berserking trait as it is fully under his control.}

\ability{Army of Puppets (Sp):}{A 9th level Puppeteer's animated corpses no longer collapse when he raises another puppet, so long as his total number of puppet's is less than his class level.}

\ability{Tunneling (Sp):}{At 10th level, a Puppeteer can teleport short distances, as per \emph{dimension door}. This ability is usable at will.}

\ability{Magnetism (Sp):}{An 11th level Puppeteer can hurl metal objects around at high speed for no discernible reason. This acts like \emph{telekinesis}, which is usable at will, save that only creatures and objects made primarily of ferrous metals may be lifted and thrown.}

\ability{Life Anew (Su):}{A 12th level Puppeteer can create Corpse Creatures with lightning. This is like using \emph{create undead} save that the creatures are Constructs instead of Undead, are healed by Electrical damage, and don't have any action reduction.}