\classname{Soldier} \label{class:soldier}
\vspace{-8pt}
\quot{I got so much style, my styles got style.}

\noindent\desc{The worlds of Dungeons \& Dragons have dozens or even hundreds of sapient races, all of whom have distinctive methods of combat and warfare. And yet, it is demonstrably true that an individual warrior of one species is pretty much interchangeable for one of any other. The true tactical uniqueness comes from the exemplar soldiers of these empires, and those are the dudes who have the actual Soldier \emph{class}. However, even that only usually applies to low level Soldiers. Those who've fought in many battles get a grasp on the special tactics of the other races and start using them in battle. It is to be noted that some races (such as Osyluth) don't really engage in battle, and instead direct minions to do battle on their behalf. The secrets of battle for these races are then the tricks they drum into soldiers working for them, rather than into their own warriors.}

\noindent\desc{The Soldier is a vaguely Book of Weaboo Fightan Magic class, and as such has Maneuvers, Stances, and an initiator level and stuff like that. However, while they have these things, they also have a very simple system for using their abilities: they can use any of them they know whenever they want. A Soldier gets a lot of Stances (one per level) and relatively less Maneuvers (one every other level). Deal with it.}

\noindent\desc{A Soldier has multiple attribute dependency of Intelligence and Constitution, also they have only a \nicefrac{3}{4} BAB progression. Nonetheless they are serviceable combatants even though Strength and Dexterity are probably like their 3rd or 4th best attributes.}

\ability{Starting Gold:}{8d4x10 gp (200 Gold)}

\ability{Starting Age:}{As Fighter}

\ability{Alignment:}{Soldiers can and do fight for any cause, sometimes for ideology and other times for pure mercenary interest. A Soldier can be of any alignment, and the class is no marker for level's of fanaticism. The player can choose how strongly they detect their alignment.}\medskip

\ability{Hit Die}{d8}

\ability{Class Skills:}{Balance, Climb, Craft, Diplomacy, Disguise, Gather Information, Handle Animal, Hide, Intimidate, Jump, Knowledge (Any), Linguistics, Listen, Move Silently, Perform, Profession, Ride, Search, Sleight of Hand, Spot, Survival, Swim.}

\ability{Skill Points/Level:}{4 + Int mod}

\begin{table}[htb]
\begin{small}
\begin{tabular}[h]{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{9cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special& Maneuvers\\
1st&  +0&  +2&  +0& +0&  Stances, Soldier Maneuvers, Secrets of Battle& 1\\
2nd&  +1&  +3&  +0& +0&  Hardened Survivor& 1\\
3rd&  +2&  +3&  +1& +1&  Wearing Shoes, Lucky& 2\\
4th&  +3&  +4&  +1& +1&  Mighty Stances& 2\\
5th&  +3&  +4&  +1& +1&  Veteran's Experience& 3\\
6th&  +4&  +5&  +2& +2&  Leader of Men& 3\\
7th&  +5&  +5&  +2& +2&  Boots Keep Walking& 4\\
8th&  +6&  +6&  +2& +2&  Fantastic Stances& 4\\
9th&  +6&  +6&  +3& +3&  Boots Keep Walking& 5\\
10th& +7&  +7&  +3& +3&  Meet Interesting People& 5\\
11th& +8&  +7&  +3& +3&  Boots Keep Walking& 6\\
12th& +9&  +8&  +4& +4&  Giant Stances& 6\\
13th& +9&  +8&  +4& +4&  Boots Keep Walking& 7\\
14th& +10& +9&  +4& +4&  Logistics Master& 7\\
15th& +11& +9&  +5& +5&  Going Places& 8\\
16th& +12& +10& +5& +5&  Epic Stances& 8\\
17th& +12& +10& +5& +5&  & 9\\
18th& +13& +11& +6& +6&  Mass Desertion& 9\\
19th& +14& +11& +6& +6&  & 10\\
20th& +15& +12& +6& +6&  World Conquest& 10\\
\end{tabular}
\end{small}
\end{table}\smallskip\noindent All of the following are Class Features of the Soldier class.

\ability{Weapon and Armor Proficiency:}{A Soldier is proficient with all simple and martial weapons, as well as the racial weapons of any race mentioned in one of their Combat Styles. A Soldier is proficient with Light, Medium, and Heavy Armors in addition to Shields and Tower Shields.}

\ability{Soldier Maneuvers:}{As a Soldier gains class levels they learn how to perform amazing maneuvers of daring-do and general badassery which are collectively called "Maneuvers." A Maneuver takes a Standard Action and is an Extraordinary Ability. Many of the Soldier's Stances specifically impact the Soldier's special Soldier Maneuvers, and that refers to these and not just any attack action or full attack they happen to make. A Soldier has an Initiator level equal to their class level. A Soldier learns one maneuver each odd-numbered Soldier level, but they can also abandon any number of maneuvers they already learned whenever they gain a level of any class and learn new maneuvers that they qualify for. Most Soldier Maneuvers allow the character to make a standard attack modified in some fashion. If they are using a double weapon with which they are proficient or two finesseable weapons, they may instead make one standard attack with each weapon (adding only half their Strength bonus to the off-hand weapon), but any special maneuver effects that trigger on damage only trigger once if either or both attacks hit.}

\ability{Secrets of Battle:}{A Soldier adds their Intelligence Modifier (if positive) to their attack rolls, up to a maximum bonus equal to their Soldier Level.}

\ability{Stances:}{While the Soldier is not flatfooted, they may engage a Stance at the cost of one Swift Action per round. Each Stance is usually based on the unique fighting techniques of one of the world's armies that the Soldier has trained in, fought with, or researched. Each Stance is procedurally generated, allowing the character to gain the benefit of their Intelligence bonus to something they don't normally get to do \emph{and} get a special additional bonus based on the racial combat styles they are emulating. Each Stance also needs a \emph{name}, which can be generated on the chart at the end of this document.}

\begin{list}{}{\itemspace}
\item \textbf{Basic Bonuses}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Add Intelligence Modifier to Armor Class.
\item Add Intelligence Modifier to Saving Throws.
\item Add Intelligence Modifier to Strength and Dexterity based Skill Checks.
\item Gain Spell Resistance of 5 + Level + Intelligence Modifier.\end{list}

\begin{list}{}{\itemspace}
\item \textbf{Basic Race List}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Orc: The character is considered to be one size category larger for purposes where that would be good such as carrying capacity, using weapons one handed, and tripping.
\item Drow: If the Soldier inflicts damage on a target, they may convert all the damage to Subdual and cause 2 points of Strength Damage.
\item Dwarf: The Soldier resists things with great facility. If presented with a Fortitude or Will save for Partial, the character receives the Partial effect on a \emph{failed} save and no effect at all on a successful save.
\item Elf: The Soldier can take their Standard Action in the middle of their Move Action, continuing their movement after the Standard Action is resolved.
\item Goblin: The Soldier can redirect any attacks against their mount to themselves, and may choose to have their mount discounted from an area of effect if they are are still within it.
\item Hobgoblin: The Soldier does not generate the -10 penalty to Move Silently for moving quickly, nor do they suffer the -20 penalty to Move Silently for engaging in combat.
\item Halfling: The Soldier can throw any weapon they are proficient with to full effect as if they had made a melee attack with it – even for Manuvers that require a melee attack to function. A light weapon has a range increment of 30', a one-handed weapon has a range of 20', and a two handed weapon has a range increment of 10' (multiplied by the creature's base reach). A weapon thrown in this way gains a +2 to-hit for the what-the-crap factor.
\item Gnome: When the Soldier inflicts damage onto a creature, that creature cannot see the Soldier until the beginning of the Soldier's next turn. It's like they were invisible, or crawling around underneath them or something.
\item Kobold: When the soldier inflicts damage on a target they may as a free action place something that they have as a stored item in the target's square. Common choices include smoke sticks, thunderstones, caltrops, and feather tokens.
\item Human: The Soldier can use any weapon or armor no matter how obscure without problem. The character is considered proficient with any weapons or armors even if exotic or improvised. The character also ignores armor check penalties and armor stealth penalties.
\item Aasimar: The Soldier ignores Concealment (but not Full Concealment) unless that Concealment comes from poor lighting. Full Concealment is treated as regular Concealment unless it comes from total darkness.
\item Tiefling: The Soldier has Full Concealment if poor lighting would give them Concealment.
\end{list}

\ability{Hardened Survivor (Ex):}{A 2nd level Soldier has resigned themselves to living in crappy conditions on both sides of a siege, and resigned themselves to eating things that a less martially oriented person would refuse out of hand. They may add their Constitution modifier to their Survival checks instead of their Wisdom Modifier. They also increase their Death Margin by their ranks in Survival.}

\ability{Wearing Shoes (Ex):}{A 3rd level Soldier really understands how Charlie thinks. Also how K'zrtlk thinks. And they can totally emulate those dudes. The Soldier gains a bonus to Disguise equal to their ranks in Disguise, and suffers no penalty for disguising themselves as a different race.}

\ability{Lucky (Ex):}{It's amazing how a lucky veteran keeps coming back from amazingly dangerous situations. A 3rd level Soldier gains a Luck bonus to their Saving Throws equal to their Constitution Modifier, to a maximum of their Class Level. They also never have to make saves against massive damage.}

\ability{Mighty Stances:}{From 4th level on, a Soldier can select their racial bonuses for their stances from the Mighty Races list.}

\begin{list}{}{\itemspace}
\item \textbf{Mighty Races}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Dark Creeper: The Soldier sees in any darkness, even magical darkness, like a frickin Devil.
\item Gnoll: Enemies who are \emph{flanked} by the Soldier are considered to be in difficult terrain and cannot take a 5' step.
\item Skulk: The Soldier has Concealment, and people have to deal with a 20\% miss chance. This provides a +4 bonus to Hide checks.
\item Kuo-Toa: Whenever the Soldier is attacked in melee with a weapon, they may make a free melee attack roll. If they score higher on their roll than the attacker did, the attacker drops their weapon. The original attack still hits or misses normally.
\item Lizardfolk: When attacking from Concealment or Cover, the target is denied their Dexterity bonus as if the Soldier was attacking from Full Concealment.
\item Myconid: If the Soldier inflicts damage on a target, they may convert all the damage to Subdual and force the target to make a Will Save (DC 10 + \half Level + Int Modifier) or be \emph{confused} for 1 round / level.
\item Bugbear: If the Soldier hits a target with a Maneuver and that opponent is denied their Dexterity bonus to AC or flanked, the Soldier inflicts an extra d6 of sneak attack damage per 2 class levels.
\item Thri-Kreen: The Soldier can leap for stupidly ridiculous distances. Each round, the Soldier can make an additional jump with a bonus equal to their level as a free action. This jump is not limited by height and any movement is completed that round, does not provoke attacks of opportunities, and does not count against the character's normal movement.
\item Sahuagin: The Soldier can breathe water or air as whichever one would be preferable, and has a Land and Swim Speed equal to their highest of either. 
\item Troglodyte: Opponents who are \emph{nauseated} in your threatened range do not get a Move Action and all attacks against them receive a +2 bonus to-hit and damage.
\end{list}

\ability{Veteran's Experience (Ex):}{A 5th level Soldier has seen crazy crap and come out craftier for it. They gain an Enhancement bonus to their Intelligence equal to one third of their character level (round up).}

\ability{Leader of Men:}{At 6th level, a Soldier gains Command as a bonus feat. If they already have Command, they can take another [Leadership] Feat that they qualify for instead.}

\ability{Boots Keep Walking (Ex):}{At level 7 and again at levels 9, 11, and 13 a Soldier's experience fighting on the battlefields of the Heavy Metalish terrain that dots the D\&D landscape grants them special abilities related to that terrain experience. Every time the Soldier gains one of these Terrain-based abilities they also gain a cumulative +2 bonus to all Survival tests as they are able to generalize their specific experiences into relevancies in other circumstances.}

\begin{list}{}{\itemspace}
\item \textbf{Terrain Powers}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Cave Crawler: The Soldier suffers no penalty for squeezing. The Soldier's movement speed is not reduced during poor visibility.
\item Cliff Jumper: The Soldier gains a Climb Speed equal to half their land speed. The Soldier ignores difficult terrain caused by uneven stone.
\item Ice Skater: The Soldier gains Energy Resistance to Cold equal to their Character Level. They ignore the effects of any decreased temperatures.
\item Inferno Commando: The Soldier gains Energy Resistance to Fire equal to their Character Level. They ignore the effects of any increased temperatures.
\item Jungle Fighter: The Soldier can move through difficult terrain caused by vegetation as if it wasn't there, counts cover from vegetation as if it was one stage better in both directions (so 50\% cover would provide them a +6 AC bonus but only a +2 AC bonus to enemies), and does not take damage or get \emph{entangled} from enchanted vegetation such as \emph{entangle} or \emph{briar web}.
\item Planar Champion: The Soldier ignores Planar Traits that would suck for them such as "Lawfully Aligned" or "Prison Plane" - not the Gravity or Time traits.
\item Swamp Beast: The Soldier is able to ignore difficult terrain that is caused by an area being water logged. Also they are immune to the \emph{nauseated} condition.
\item Waste Warrior: The Soldier takes twice as long to dehydrate and takes half damage from dessication effects. Also they take no damage from and their visibility is not impaired by dust storms, smoke clouds, ash rains, and any similar stuff.
\end{list}

\ability{Fantastic Stances:}{From 8th level on, a Soldier can select their racial bonuses for their stances from the Fantastic Races list.}

\begin{list}{}{\itemspace}
\item \textbf{Fantastic Races}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Ogre: If the Soldier inflicts damage with an attack of opportunity, the action that provoked the attack of opportunity is not completed.
\item Gith: If any creature uses a [Teleport] or plane shift effect within the Soldier's line of sight, they may elect to immediately teleport to a point that is adjacent to the creature's new location. Creatures cannot use Psionic abilities defensively within the Soldier's threatened area.
\item Yakfolk: All spells are considered to be on the Soldier's list for purposes of activating Spell Trigger items.
\item Pixie: If the Soldier inflicts damage on a target, they may convert all the damage to Subdual and force the target to make a Will Save (DC 10 + ½ Level + Int Modifier) or fall \emph{asleep} for 1 minute / level.
\item Kyton: The Soldier's threatened area extends for an extra 20' in all directions.
\item Yuan-Ti: All of the Soldier's maneuvers come with a poison rider if they inflict damage at all. Victim's suffer 2d4 of Constitution damage from poison, with a Fortitude Save (DC 10 + ½ Level + Con Modifier) for half damage.
\item Doppelganger:If the Soldier inflicts damage on a target, they may convert all the damage to Subdual and force the target to make a Will Save (DC 10 + \half Level + Int Modifier) or give up their surface thoughts \emph{detect thoughts} style. Also the character can change shape into the target as per whatever version of \emph{alter self} you're using.
\item Abeil: All enemies within the Soldier's threatened area suffer a penalty to their Will saves equal to the Soldier's Intelligence Modifier.
\item Succubus: If the Soldier inflicts damage on a target, they may convert all the damage to Subdual and force the target to make a Will Save (DC 10 + ½ Level + Int Modifier), or accept a \emph{suggestion}.
\item Nerra: Any time the Soldier successfully negates a spell, or supernatural or spell-like ability targeted against them with a successful Saving Throw or Spell Resistance, the spell is reflected against the caster of the spell as per \emph{spell turning}.
\end{list}

\ability{Meet Interesting People:}{At 10th level, the Soldier can add their Intelligence Modifier to Charisma checks.}

\ability{Giant Stances:}{From 12th level on, a Soldier can select their racial bonuses for their stances from the Giant Races list.}

\begin{list}{}{\itemspace}
\item \textbf{Giant Races}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Ilithid: The Soldier can \emph{coup de grace} a target who is \emph{stunned} as a standard action that does not provoke an attack of opportunity.
\item Ettin: The Soldier can attack with two weapons when using a Maneuver, and they don't even have to be light or finesseable weapons. If both attacks hit, any special effects that trigger on damage may occur twice. Both weapons use the Soldier's full Strength bonus.
\item Stone Giant: The Soldier may catch or deflect a number of ranged weapons equal to their Intelligence modifier each turn.
\item Fire Giant: The Soldier can cause a burst of fire damage every time they inflict damage with a Maneuver. This is a 15' burst that inflicts half as much damage as the attack inflicted and is centered on the target. It's all fire damage, and a Reflex Save halves that damage.
\item Slaad: The Soldier can giant frog at will.
%\item Eladrin: 
\item Troll: The Soldier has Regeneration of 1 hit point per round per level. Acid, Fire, starvation, and suffocation do normal damage.
\item Vrock: When the Soldier performs a maneuver, all other creatures within 40' suffer 3d20 of ultima damage, Fortitude Save for half (DC 10 + ½ Level + Int Modifier).
\item Osyluth: The Soldier sees through illusions and shape changing as per \emph{true seeing}.
\item Justicator: The Soldier can redirect the target of a single target effect or attack to themselves if the original target is within the Soldier's Reach.
\end{list}

\ability{Logistics Master (Ex):}{A 14th level Soldier is a master of War and can manage supply lines intuitively. The Soldier can use their Survival skill to manage Logistics on any scale from the personal to the Imperial.}

\ability{Going Places (Sp):}{A 15th level Soldier can follow anything to anywhere. By touching something from another plane, they may \emph{planeshift} to the plane of the creature or object's origin. Since it is easy to touch yourself in D\&D, a Soldier can always return to their own plane of origin. This can also be used to banish things to their home plane of existence, if they fail a Will save.}

\ability{Epic Stances:}{From 16th level on, a Soldier can select their racial bonuses for their stances from the Epic Races list.}

\begin{list}{}{\itemspace}
\item \textbf{Epic Races}
\end{list}
\begin{list}{$\bullet$}{\itemspace}
\item Rakshasa: The Soldier is unaffected by spells, supernatural abilities, and spell-like abilities of 6th level or less, as if they were carrying a \emph{greater orb of invulnerability} around.
\item Storm Giant: The Soldier is unaffected by Weather effects. Also, whenever the Soldier inflicts damage with a Maneuver, they may strike any other targets (of their choice) within 60' with a lightning bolt that does half that much damage (Reflex Save for Half again).
\item Ethergaunt: Any time the Soldier strikes a target with a Maneuver, they may create an \emph{antimagic field} that fills the 5' square they struck for one round.
\item Archon: The damage inflicted by the Soldier's maneuvers may be converted entirely to Light damage.
\item Deva: The Soldier may choose to cancel immunities to \emph{stun}, \emph{sleep}, or \emph{fear} on targets within 30' of themselves.
\item Marilith: The Soldier makes a number of additional standard attacks equal to their Intelligence modifier when they perform a maneuver. Any special effect that takes place if the maneuver inflicts damage takes place if at least one of the attacks inflicts damage.
\item Gelugon: Any target damaged by the Soldier's Maneuvers is \emph{slowed} for 1 round. Any time the Solder strikes a target who is \emph{shaken} or worse, the attack is a critical hit.
\item Nycoloth: If the Soldier inflicts damage with a maneuver, they may use their attack or damage result as their Grapple result to immediately start a grapple against the same target.
\item Quarut: The Soldier can take actions normally during time disturbances, and continues to get turns during \emph{time stop} (if cast within long range of the Soldier). They may interact with things that are frozen in time (so they could, for example, perform a coup de grace on a target that was in \emph{temporal stasis}.
\item Anathema: The Soldier can generate an \emph{antipathy} effect as a free action, once per round.
\end{list}

\ability{Mass Desertion (Ex):}{An 18th level Soldier is a dreaded thing. When  he takes to the field, enemies know their cause is hopeless. Enemies of CR 8 or less who see the Soldier in the fray simply give up. They retreat or surrender as appropriate. This is not a fear effect, and extends to line of sight.}

\ability{World Conquest (Ex):}{At 20th level, the Soldier wins D\&D.}

\clearpage
\noindent\begin{large}\textbf{Soldier Maneuvers:}\end{large}

\noindent\desc{In order to take a specific Strike you must have an Initiator Level sufficient to use it, meaning that half your Initiator Level (rounded up) must be at least the level of the proposed Maneuver.}

\noindent\desc{If there is a Save offered by a Soldier Strike, the DC is 10 + ½ Character Level + Constitution Modifier.}

\maneuver{Brutal Strike}{1}
{The Soldier hits someone super hard with a melee attack. The attack does an extra d6 of damage. This bonus increases to 2d6 at 3rd level, 3d6 at 4th level, 4d6 at 6th level, 5d6 at 7th level, 7d6 at 8th level, 9d6 at 9th level, 11d6 at 10th level, 14d6 at 11th level, 16d6 at 12th level, 20d6 at 13th level, 100 points at 14th level, 110 points at 15th level, 125 points at 16th level, 150 points at 17th level, 175 points at 18th level, 200 points at 19th level, and 250 points of damage at 20th level.}

\maneuver{Turtle World}{1}
{The Soldier attacks normally but hides themselves from harm. The Solider makes a standard attack and has energy resistance to all energy types and DR X/- equal to their Constitution Modifier plus their Character level until the beginning of their next turn if the attack inflicts damage.}

\maneuver{Looting Strike}{1}
{The Soldier stabs a fool and pockets their things. The Soldier makes a standard melee attack and if it inflicts damage they can force the target to drop a weapon or other carried item. The Soldier can grab and store that item if they wish.}

\maneuver{Blinding Blow}{2}
{The Soldier strikes a foe in their eyes or whatever they see with. They make a standard attack and if they inflict damage the target must make a Fortitude Save or be \emph{blinded}.}

\maneuver{Runaround}{2}
{The Soldier runs around and stabs someone from an unconventional direction. The Soldier moves their speed and then makes a standard melee attack at +2 to-hit. The Soldier gains a +2 bonus to AC until the beginning of their next turn.}

\maneuver{Knockdown}{2}
{The Soldier strikes someone in a manner that knocks them right down. The Soldier makes a standard attack and if it inflicts damage, the target becomes \emph{prone}.}

\maneuver{Whirlwind}{3}
{The Soldier flips out and stabs everyone. The soldier makes a standard melee attack against every opponent they can reach. They may gain no more bonus cleave attacks than they have Intelligence Modifier.}

\maneuver{Executioner}{3}
{The Soldier chops a dude's head right off and spits down the hole in the stump. The Soldier makes a standard melee attack and if he does any damage the target makes a Fortitude Save or they die.}

\maneuver{Delaying Tactics}{3}
{The Soldier feints and draws things out, unraveling time. The Soldier makes a standard attack. Every creature adjacent to the Soldier is \emph{slowed} for Level/Rounds.}

\maneuver{Mind Thwack}{4}
{The Soldier beats someone in the brain so hard that it creates a psychic resonance the incapacitates others. The Soldier makes a standard attack against a living, non-mindless creature and if he does any damage, all creatures except the Soldier within 10' of the target must make a Will save or be \emph{stunned} for a d4 rounds.}

\maneuver{Lingering Strike}{4}
{The Soldier hits the target with a cruel and lingering wound that disrupts their concentration. The Soldier makes a standard attack. The attack does double damage, and is considered to be ongoing damage for purposes of Concentration checks made in the following round.}

\maneuver{Hurl Away}{4}
{The Soldier strikes an opponent and hurls them away from themselves. The Soldier makes a standard melee attack, and if it does any damage the target is also pushed away 5' for every point of Constition bonus the Soldier has. This works like a successful Bullrush except that the Soldier doesn't need to move to keep the victim moving.}

\maneuver{Dimensional Strike}{5}
{The Soldier reaches into the ether and tears the target a new one. The Soldier sees the invisible and then makes a standard attack that ignore Incorporeality and can strike Ethereal creatures. If the attack does any damage, the target is moved to the plane of existence that the Soldier is on and is no longer incorporeal for the next 2d4 rounds.}

\maneuver{Meteor Smash}{5}
{The Soldier strikes the ground so hard that everything just fucking explodes. All other creatures within 30' suffer d8/level of physical bludgeoning damage, Reflex Save for half.}

\maneuver{Demoralizing Strike}{5}
{The Soldier hits a target so ugly that it freaks out all of their allies. If the target takes any damage they are \emph{sickened} for the next minute. All enemies within line of sight must make a Will save or become \emph{shakened} for one round.}

\maneuver{Critical Strike}{6}
{The Soldier strikes an opponent perfectly. The Soldier makes a standard attack, and if it hits it is a critical as if it had rolled a natural 20 and then confirmed.}

\maneuver{Hydra Strike}{6}
{The Soldier makes a flurry of attacks. The character makes a number of standard attacks equal to their Intelligence Modifier. These don't even have to be against the same target. Every time they get a critical hit, they get an additional attack.}

\maneuver{Blade Rush}{6}
{The Soldier runs around his opponents and jacks them up. The Soldier moves their full move without provoking attacks of opportunity and makes a standard melee attack against every opponent who is within their threatened area at any point during their move. Each attack inflicts bonus damage equal to the maximum damage inflicted by the weapon's damage die (for example: 8 damage for a longsword or falchion). The character cannot gain bonus attacks from Cleave during this maneuver.}

\maneuver{Doom Tunnel}{7}
{The Soldier hacks a corridor through whatever happens to be in front of him, whether that be air, rock or other people. He may move out to his full charge range and attack everyone who is in his path. If he fails to kill a target, they are shoved aside so he can keep moving. Any nonliving thing in the path is \emph{Disintegrated}, as per the spell.}

\maneuver{Heaven Piercer}{7}
{The Soldier stabs the sky hard enough to split it open and cause death to rain down upon everyone around. This requires line of sight to the sky, and causes all within 50 feet to take 1d8 Electricity damage per level (Reflex half). Additionally, the general other-dimensional doom raining down pushes creatures over, negates ranged attacks, and impedes flight within 50' of the Soldier until his next turn as per a Hurricane-Force Wind. In some planes of existence, a wounded sky may leak damage types other than lightning, such as fire or acid.}

\maneuver{Earth Shaker}{7}
{The Soldier strikes the ground and the ground strikes everyone else. All other creatures touching the ground within 60' of the soldier take 1d8 of Bludgeoning damage per level (Fortitude Half). Those creatures that fail their saves are also partially buried in dirt. They are \emph{prone} and \emph{entangled} until they can make an Escape Artist or Size Modified Strength test with a DC of 15 + the Soldier's Constitution modifier as a Full Round Action (or burrow or teleport out).}

\maneuver{Banishing Strike}{8}
{The Soldier smashes the target out of existence. The Soldier makes a standard attack, and if the target suffers any damage it is sent to its home plane, where it is then \emph{dimensional anchored} for a day. The soldier may travel with the target if they choose.}

\maneuver{Harrying Strike}{8}
{The Soldier may take a 5' step that teleports to a space adjacent to a creature that was within short range of the Soldier \emph{last turn}. The Soldier need not know where the target has gone since then, and can follow any distance to any plane of existence without fail. The Soldier then makes a standard attack.}

\maneuver{Hamster Strike}{8}
{The Soldier strikes the target in such a manner that they become a small rodent. The soldier makes a standard attack, and if any damage is inflicted, the target is now a harmless hamster, as per \emph{baleful polymorph}. Some Soldiers learn similar attacks that transform the target into other things.}

\maneuver{Perfect Killer}{9}
{The Soldier strikes an enemy and they die. The Soldier makes a standard attack against a target, if the target suffers any damage it dies. This is a [Death] effect.}

\maneuver{Extra Strike}{9}
{The Soldier makes a standard attack as a free action. This may be used once per round, and may be used on other creatures' initiative counts.}

\maneuver{World Slaying Strike}{9}
{The Soldier attacks every creature they can see. The Soldier makes a standard attack, and this attack is resolved against every target they choose to designate out to line of sight. Make one attack roll and compare to each target's AC, but if miss chances apply, roll for each separately.}


\noindent\desc{\begin{large}\textbf{Naming Your Stances:}\end{large}}

\noindent\desc{When you name your styles, be sure to have the representative species name in there somewhere, and also generate an adjective and a noun to name the stance. The racial word can go in the first, second, or third position depending on what sounds better. So when making a Drow style, you could have the "Underhanded Grandeur of the Drow" or the "Drow Invincible Method" or the "Informal Drow Approach."}

\noindent\begin{tabular}[h]{lll}
\textbf{Roll or Choose}& \textbf{Adjective}& \textbf{Noun}\\
\textbf{1}& Rising& Stance\\
\textbf{2}& Sweltering& Dance\\
\textbf{3}& Sneaky& Technique\\
\textbf{4}& Underhanded& Style\\
\textbf{5}& Virtuous& Grandeur\\
\textbf{6}& Wonderful& Defense\\
\textbf{7}& Glorious& Manner\\
\textbf{8}& Fantastic& Attack\\
\textbf{9}& Dark& Idiosyncrasy\\
\textbf{10}& Wicked& Tactic\\
\textbf{11}& Awesome& Maneuver\\
\textbf{12}& Splendid& Pattern\\
\textbf{13}& Informal& Mode\\
\textbf{14}& Shadow& Method\\
\textbf{15}& Sexy& Mean\\
\textbf{16}& Impenetrable& System\\
\textbf{17}& Invincible& Way\\
\textbf{18}& Inflammable& Approach\\
\textbf{19}& Sordid& Attitude\\
\textbf{20}& Wrathful& Craft\\
\end{tabular}
