\classname{Spirit Shaman}
\vspace*{-8pt}
\quot{"The fat one hates us... He knows too much. You'll have to do something about that..."}

\desc{The Spirit Shaman is the team player of the natural world. They work with spirits great and small, the incorporeal spark of life within all things. From pacts and oaths, the shaman gains the camaraderie and power of these beings, allowing them to etch their will within the worlds of the living and the dead. As such, they are divine casters of a different bent than clerics and druids. While the cleric's powers come through faith and the druid's comes through [s]yiffing[/s] communion, the shaman is more pragmatic, gaining their powers from whatever is nearby.}

\desc{A Spirit Shaman is meant for two things: charming spirits and punching people in the face with said spirits. For this, the most important aspects are Wisdom and Charisma: Wisdom to understand what the spirits are going on about and Charisma to convince those spirits to crush things for you.}

\ability{Starting Gold:}{2d4x10 gp (50 Gold)}

\ability{Starting Age:}{As Druid}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{Athletics, Concentration, Craft, Diplomacy, Handle Animal, Heal, Knowledge (Any), Perception, Profession, Ride, Survival.}

\ability{Skills/Level:}{4 + Int modifier.}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+2 &+2 &Spellcasting, Spirit Guide, Detect Spirits, Resist Nature's Lure\\
2nd &+1 &+0 &+3 &+3 &Strength of Spirit, Woodland Stride\\
3rd &+1 &+1 &+3 &+3 &See the Unseen, Animism (Speak in Tongues)\\
4th &+2 &+1 &+4 &+4 &\emph{Remove Curse}\\
5th &+2 &+1 &+4 &+4 &Animism (Speak with Monsters)\\
6th &+3 &+2 &+5 &+5 &\emph{Break Enchantment}\\
7th &+3 &+2 &+5 &+5 &Animism (Speak with Plants)\\
8th &+4 &+2 &+6 &+6 &Ether Gate\\
9th &+4 &+3 &+6 &+6 &Animism (Speak with Magic), See Pockets\\
10th &+5 &+3 &+7 &+7 &Answering Spirits, Material Shift\\
11th &+5 &+3 &+7 &+7 &Animism (Speak with Stones)\\
12th &+6/+1 &+4 &+8 &+8 &Empty Pockets\\
13th &+6/+1 &+4 &+8 &+8 &Animism (Speak with Air), See Deeper Pockets\\
14th &+7/+2 &+4 &+9 &+9 &End Magic\\
15th &+7/+2 &+5 &+9 &+9 &Live Forever\\
16th &+8/+3 &+5 &+10 &+10 &Dual Nature\\
17th &+8/+3 &+5 &+10 &+10 &Sculpt the Spirit Realm\\
18th &+9/+4 &+6 &+11 &+11 &Banishment\\
19th &+9/+4 &+6 &+11 &+11 &All Sight\\
20th &+10/+5 &+6 &+12 &+12 &Victory\\
\end{tabular}
\end{small}
\end{table}

\begin{table}[htb]
\begin{small}
\noindent\begin{tabular}{lllllllllll}
 & \multicolumn{10}{c}{Spirit Shaman Spells Per Day}\\
 &0 &1 &2 &3 &4 &5 &6 &7 &8 &9\\
1 &4 &2 &- &- &- &- &- &- &- &-\\
2 &5 &3 &- &- &- &- &- &- &- &-\\
3 &6 &4 &2 &- &- &- &- &- &- &-\\
4 &6 &5 &3 &- &- &- &- &- &- &-\\
5 &6 &6 &4 &2 &- &- &- &- &- &-\\
6 &6 &6 &5 &3 &- &- &- &- &- &-\\
7 &6 &6 &6 &4 &2 &- &- &- &- &-\\
8 &6 &6 &6 &5 &3 &- &- &- &- &-\\
9 &6 &6 &6 &6 &4 &2 &- &- &- &-\\
10 &6 &6 &6 &6 &5 &3 &- &- &- &-\\
11 &6 &6 &6 &6 &6 &4 &2 &- &- &-\\
12 &6 &6 &6 &6 &6 &5 &3 &- &- &-\\
13 &6 &6 &6 &6 &6 &6 &4 &2 &- &-\\
14 &6 &6 &6 &6 &6 &6 &5 &3 &- &-\\
15 &6 &6 &6 &6 &6 &6 &6 &4 &2 &-\\
16 &6 &6 &6 &6 &6 &6 &6 &5 &3 &-\\
17 &6 &6 &6 &6 &6 &6 &6 &6 &4 &2\\
18 &6 &6 &6 &6 &6 &6 &6 &6 &5 &3\\
19 &6 &6 &6 &6 &6 &6 &6 &6 &6 &4\\
20 &6 &6 &6 &6 &6 &6 &6 &6 &6 &5\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All of the following are class features of the Spirit Shaman class.

\ability{Weapon and Armor Proficiency:}{Spirit Shamans are proficient with all Simple and Martial Weapons, and with Light and Medium Armor}

\ability{Armor and Casting:}{If you are proficient, it will come.}

\ability{Spellcasting:}{The spirit shaman casts divine spells. Once between times that the sun sets, a spirit shaman may commune with the spirit world for an hour. During this communion, the Spirit Shaman regains their spell slots and may select 4 spells from the Spirit Shaman list of each level she can cast spells from. These spells may be cast spontaneously by the Spirit Shaman. Applying metamagic never takes any extra time. The Spirit Shaman's save DCs are Charisma based, and their bonus spells are Wisdom based.}

\ability{Spirit Guide:}{The Spirit Shaman has a spirit guide, some kind of freaky critter that guides them from the Ethereal plane. The spirit guide has the form of a monster with a CR equal to the spirit shaman's level, but always has an Intelligence equal to the spirit shaman's Wisdom and has the same alignment as they do. The spirit guide exists only on the ethereal plane, but the spirit shaman can see and hear it as if it were on the same plane as they are. The spirit guide takes a new form every time the spirit shaman changes level, chosen by the DM.}

\ability{Detect Spirits (Su):}{A Spirit Shaman knows when there are incorporeal creatures, astral creatures, ethereal creatures, or fey within 60 feet of themselves. One of these creatures that has remained within 60' of the spirit shaman for a second round has their five foot square known by the spirit shaman. A spirit shaman knows roughly how many hit dice such a creature has if they stay within 60 feet for a third consecutive round.}

\ability{Resist Nature's Lure (Ex):}{A spirit shaman gains a +4 bonus on saves against the spell like abilities of Fey.}

\ability{Strength of Spirit (Su):}{At 2nd level, a spirit shaman hulks out whenever they are on the ethereal plane. Add their Charisma bonus (if any) to their Strength, their Wisdom bonus (if any) to their Constitution, and their Intelligence bonus (if any) to their Dexterity. The spirit shaman also has a Deflection bonus to AC equal to their Wisdom modifier while they are on the Ethereal Plane.}

\ability{Woodland Stride (Su):}{At 2nd level, a spirit shaman can move through natural surroundings unimpeded. The spirit shaman treats difficult terrain caused by vegetation as if it was not difficult terrain.}

\ability{See the Unseen (Su):}{A spirit shaman of 3rd level sees invisible, astral, and ethereal things within 60 feet of themselves.}

\ability{Animism (Ex):}{A spirit shaman can listen and speak directly to the spirit in all living things. Also they have a really expansive idea of what constitutes a living thing. At 3rd level, a spirit shaman can speak with any living creature that has a language. At 5th level, they can speak with any living creature \emph{as if} they had a language and a language in common with the spirit shaman at that. At 7th level, they can speak with plants. At 9th level, they can speak with magic items and constructs. At 11th level, they can speak with earth and stone. At 13th level they can speak with the air itself, which coincidentally allows them to mimic \emph{message} or \emph{whispering winds} whenever they want. Note that as described in \emph{speak with plants} and \emph{stone tell}, that inanimate objects can be kind of uninteresting conversationalists.}

\ability{\emph{Remove Curse} (Sp):}{At 4th level, a spirit shaman may cast \emph{remove curse} as a spell like ability a number of times per day equal to their Wisdom modifier. Caster level is their character level.}

\ability{\emph{Break Enchantment} (Sp):}{At 6th level, a spirit shaman may cast \emph{break enchantment} as a spell like ability a number of times per day equal to their Wisdom modifier. Caster level is their character level.}

\ability{Ether Gate (Su):}{An 8th level Spirit Shaman may open up a gateway between the ethereal plane and the physical world. The gate stays open as long as the spirit shaman concentrates. For every five feet wide the shaman makes the portal, they suffer 2 points of damage for every round they hold it open.}

\ability{See Pockets (Su):}{A spirit shaman of 9th level or more can see what's inside any pocket dimensions whose egress is within 60 feet of themselves. The place the pocket dimension connects with the rest of reality is obvious (to the spirit shaman). At 13th level, the range extends to 120 feet.}

\ability{Answering Spirits (Su):}{At 10th level, a spirit shaman can ask questions of the spirit world that will actually be answered. This is like \emph{contact other plane}, but there is no chance of going insane. The shaman may ask a number of questions per day equal to their Wisdom modifier.}

\ability{Material Shift (Su):}{At 10th level, the spirit shaman can draw things into the material world from coterminous planes.}

\ability{Empty Pockets (Su):}{A spirit shaman of 12th level or more can have any number of things they are aware of pushed into the material plane from extradimensionsal spaces as a standard action.}

\ability{End Magic (Su):}{With a standard action, a 14th level spirit shaman can automatically dispel an effect or suppress an item within medium range.}

\ability{Live Forever (Ex):}{A 15th level spirit shaman lives forever and never suffers any penalties for old age, nor loses any XP for being reincarnated. Also, their type changes to Fey.}

\ability{Dual Nature (Ex):}{At 16th level, the spirit shaman can be in the ethereal plane and whatever other plane at the same time. They count as being on the ethereal plane or their coterminus plane both. Which means that they do get the benefits of strength of spirits while picking up physical objects. Woo-hoo.}

\ability{Sculpt the Spirit Realm (Su):}{At 17th level, a spirit shaman can fill up the ethereal realm with stuff just by thinking about it. Five minutes meditating mimics a \emph{true creation}.}

\ability{Banishment (Su):}{An 18th level spirit shaman can send any target within medium range to any plane of existence they choose with a standard action. The victim may make a Will save against a DC of 10 + ½ Level + Charisma Modifier to avoid being transported. If the victim is transported, the spirit shaman may additionally \emph{dimensional anchor} them to their destination plane for 24 hours.}

\ability{All Sight (Ex):}{At 19th level, a spirit shaman can perceive everything within medium range of themselves, even if that thing might be invisible or on a coterminus plane, or in an extradimensional space. Just because somethng can be perceived does not mean it is \emph{noticed}, and stealth and perception checks still apply (although distance and visibility modifiers do not).}

\ability{Victory:}{At 20th level, the Spirit Shaman wins D\&D.}

\spelllist{Spirit Shaman Spell List:}

\small\ability{0th level:}{\emph{DAlarm, Cure Minor Wounds, Detect Magic, Dancing Lights, Fleeting Flame, Prestidigitation, Light, Darkness, Detect Poison}}

      \ability{Level 1:}{\emph{Animate Fire, Charm Person, Cure Light Wounds, Disguise Self, Endue Elements, Entangle, Make Manifest (SC), Pass Without Trace, Protection from Chaos, Protection from Law, Sleep, Summon Spirits I}}

      \ability{Level 2:}{\emph{Blink, Control Plants, Detect Thoughts, Ethereal Jaunt, Glitterdust, Invisibility, See Invisibility, Summon Spirits II, Tasha's Uncontrollable Hideous Laughter, Stone Tell, Treestride, Warp Wood, Wood Shape}}

      \ability{Level 3:}{\emph{Animate Objects, Animate Plants, Clairvoyance, Consecrate, Deep Slumber, Desecrate, Etherealness, Improved Invisibility, Magic Circle Against Chaos, Magic Circle Against Law, Plant Growth, Remove Disease, Summon Spirits III, Transport via Plants}}

      \ability{Level 4:}{\emph{Baleful Polymorph, Charm Monster, Cloak of the Sea (SC), Command Plants, Dimension Door, Dimensional Anchor, Feeblemind, Ghostform (SC), Illusory Feast (SC), Neutralize Poison, Reincarnation, Scry, Stone Shape, Summon Spirits IV, True Sight}}

      \ability{Level 5:}{\emph{Break Enchantment, Circle of Death, Find the Path, Magic Jar, Move Earth, Sirine's Grace (SC), Plane Shift, Regenerate, Repel Wood, Summon Spirits V, Wall of Thorns}}

      \ability{Level 6:}{\emph{Hallow, Heal, Insanity, Mass Drown (SC), Nightmare, Otto's Irresistible Dance, Summon Spirits VI, Unhallow}}

      \ability{Level 7:}{\emph{Dimensional Lock, Finger of Death, Foresight, Greater Plane Shift (SC), Planar Bubble (SC), Solipsism (SC), Summon Spirits VII}}

      \ability{Level 8:}{\emph{Fimbulwinter (ICO), Frostfell (ICO), Maddening Whispers (SC), Mass Charm, Maze, Summon Spirits VIII, True Reincarnate (MotW)}}

      \ability{Level 9:}{\emph{Mass Heal, Mind Blank, Programmed Amnesia (SC), Reality Maelstrom (SC), Reaving Dispel, Soul Bind, Summon Spirits IX, Trap the Soul, Weird}}
\normalsize
