\classname{Summoner} \label{class:summoner}
\vspace{-8pt}
\quot{"Watch me pull a rhinoceros out of my hat."}

\ability{Alignment:}{A Summoner may be of any alignment.}

\ability{Races:}{Summoners appear in every race. Halflings in particular are very likely to adopt the way of the Summoner.}

\ability{Starting Gold:}{4d4x10 gp (100 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Summoner's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Escape Artist (Dex), Handle Animal (Cha), Intimidate (Cha), Knowledge (arcana) (Int), Knowledge (nature) (Int), Knowledge (the planes) (Int), Profession (Wis), Ride (Dex), Sense Motive (Cha), and Spellcraft (Int).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.2cm}p{0.7cm}p{0.7cm}p{0.7cm}p{4.7cm}llllllllll}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special & \multicolumn{10}{c}{Spells Per Day}\\
&&&&&& 0 &1 &2 &3 &4 &5 &6 &7 &8 &9\\
1st &+0 &+0 &+2 &+2 &Rapid Summoning, Summoned Cohort, Armored Casting, Aura &5 &3 &- &- &- &- &- &- &- &-\\
2nd &+1 &+0 &+3 &+3 &Sudden Extend &6 &4 &- &- &- &- &- &- &- &-\\
3rd &+1 &+1 &+3 &+3 &Advanced Learning &6 &5 &- &- &- &- &- &- &- &-\\
4th &+2 &+1 &+4 &+4 &Extended Summoning: 1st level &6 &6 &3 &- &- &- &- &- &- &-\\
5th &+2 &+1 &+4 &+4 &Advanced Learning &6 &6 &4 &- &- &- &- &- &- &-\\
6th &+3 &+2 &+5 &+5 &Master Tactician &6 &6 &5 &3 &- &- &- &- &- &-\\
7th &+3 &+2 &+5 &+5 &Advanced Learning, Summon &6 &6 &6 &4 &- &- &- &- &- &-\\
8th &+4 &+2 &+6 &+6 &  &6 &6 &6 &5 &3 &- &- &- &- &-\\
9th &+4 &+3 &+6 &+6 &Advanced Learning, Extended Summoning: 2nd level &6 &6 &6 &6 &4 &- &- &- &- &-\\
10th &+5 &+3 &+7 &+7 &Medium Armor Proficiency &6 &6 &6 &6 &5 &3 &- &- &- &-\\
11th &+5 &+3 &+7 &+7 &Advanced Learning, Improved Summoning &6 &6 &6 &6 &6 &4 &- &- &- &-\\
12th &+6/+1 &+4 &+8 &+8 &Advanced Aid &6 &6 &6 &6 &6 &5 &3 &- &- &-\\
13th &+6/+1 &+4 &+8 &+8 &Advanced Learning &6 &6 &6 &6 &6 &6 &4 &- &- &-\\
14th &+7/+2 &+4 &+9 &+9 &Extended Summoning: 3rd level &6 &6 &6 &6 &6 &6 &5 &3 &- &-\\
15th &+7/+2 &+5 &+9 &+9 &Advanced Learning, Improved Summoning &6 &6 &6 &6 &6 &6 &6 &4 &- &-\\
16th &+8/+3 &+5 &+10 &+10 &Shield Proficiency &6 &6 &6 &6 &6 &6 &6 &5 &3 &-\\
17th &+8/+3 &+5 &+10 &+10 &Advanced Learning &6 &6 &6 &6 &6 &6 &6 &6 &4 &-\\
18th &+9/+4 &+6 &+11 &+11 &  &6 &6 &6 &6 &6 &6 &6 &6 &5 &3\\
19th &+9/+4 &+6 &+11 &+11 &Advanced Learning, Extended Summoning: 4th level &6 &6 &6 &6 &6 &6 &6 &6 &6 &4\\
20th &+10/+5 &+6 &+12 &+12 &Perfect Summon &6 &6 &6 &6 &6 &6 &6 &6 &6 &6\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Summoner class.

\ability{Weapon and Armor Proficiency:}{Summoners are proficient with all simple weapons, as well as the bola, the whip, the net, and the harpoon. Summoners are proficient with light armor but not with shields of any kind. At 10th level, a Summoner gains proficiency with Medium Armor. At 16th level, the Summoner gains proficiency with shields.}

\ability{Spellcasting:}{The Summoner is an Arcane Spellcaster with the same spells per day progression as a Sorcerer. A Summoner casts spells from the Summoner Spell List (below). A Summoner automatically knows every spell on her spell list. She can cast any spell she knows without preparing them ahead of time, provided that spell slots of an appropriate level are still available.To cast a Summoner spell, she must have a Charisma at least equal to 10 + the Spell level. The DC and bonus spells of the Summoner's spells is Charisma based.}

\ability{Rapid Summoning:}{A Summoner can cast summoning spells in less time than most other casters. Any Conjuration spell of the [Summoning] subschool that a Summoner casts that would have a casting time of one full round have a casting time of 1 standard action instead. This ability has no effect on spells which already require less than one full round to cast, nor does it affect spells with a casting time greater than one full round.}

\ability{Summoned Cohort:}{Once per day when a Summoner casts a Conjuration spell of the [Summoning] subschool, she may extend its duration to 24 hours. This ability is not cumulative with other effects that increase the duration of a spell.}

\ability{Armored Casting:}{A Summoner casts arcane spells, but she is not affected by the arcane spell failure of any armor or shield she is proficient with. This ability only applies to her Summoner spells, if she is able to cast any other arcane spells, they are affected by arcane spell failure normally.}

\ability{Aura:}{A Summoner's strong connection to the outer planes causes them to be detected very strongly of whatever alignment she has. For purposes of spells like \spell{detect chaos}, levels in Summoner count as Outsider hit dice.}

\ability{Sudden Extend:}{At 2nd level, the Summoner gains Sudden Extend as a bonus feat. If she already has Sudden Extend, she may gain any metamagic feat that she qualifies for instead.}

\ability{Advanced Learning:}{At 3rd level and every two levels afterwards, the Summoner may permanently add one spell to her spell list. This spell must be of a level she can already cast, and it must be of the Conjuration school. Only spells from the Cleric, Druid, or Wizard spell list may be added in this way.}

\ability{Extend Summoning:}{Conjuration spells of the [Summoning] subschool that the Summoner casts can be affected by the Extend Spell metamagic for free. At 4th level, the Summoner may apply this free spell extending to spells of 1st level or lower. At 9th level, she may apply it to 2nd level spells, at 14th level she may apply it to 3rd level spells, and at 19th level she may apply Extend Spell for free to 4th level spells.}

\ability{Master Tactician:}{A Summoner learns to fight with many allies. At 6th level, any ally within 30 feet of her may gain a +4 bonus for flanking instead of the normal +2 bonus as long as they can perceive the Summoner.}

\ability{\spell{Summon (Sp)}:}{At 7th level, a Summoner can attempt to summon outsiders with an alignment identical to her own. Summoning another creature of the same character level has a 40\% chance of success, and summoning a creature of a lower level increases the chances of success by 10\% for every level the Summoner's level exceeds the CR of the target.}

\ability{Advanced Aid (Ex):}{A Summoner of 12th level may take the Aid Another action as a free action once per round.}

\ability{Improved \spell{Summoning}:}{At 11th level, the Summoner's chances to \spell{summon} an outsider increase by 10\%. This chance increases by another 10\% at 15th level.}

\ability{Perfect \spell{Summon}:}{At 20th level, the Summoner's \spell{summon} power has a 100\% chance of success, even when summoning a creature of equal level to herself.}


\spelllist{Summoner Spell List:}
\small

\ability{0th level:}{\emph{Anticipate Teleportation, Caltrops, Darkness, Detect Magic, Detect Poison, Light, Protection from Alignment, Read Magic, Resist Planar Alignment}}

\ability{1st level:}{\emph{Avoid Planar Effects, Comprehend Languages, Grease, Portal Beacon, Summon Frost Beast I, Summon Monster I, Summon Nature's Ally I, Summon Undead I, Wall of Smoke}}

\ability{2nd level:}{\emph{Analyze Portal, Baleful Transposition, Dimension Hop, Daylight, Deeper Darkness, Entangle, Phantom Steed, Planar Tolerance, Portal Alarm, Regroup, Sleet Storm, Summon Frost Beast II, Summon Monster II, Summon Nature's Ally II, Summon Undead II, Tongues, Web, Wind Wall}}

\ability{3rd level:}{\emph{Clairaudience/Clairvoyance, Dimension Step, Dimensional anchor, Greater Anticipate Teleportation, Magic Circle Against Alignment, Plant Growth, Stinking Cloud, Summon Frost Beast III, Summon Monster III, Summon Nature's Ally III, Summon Undead III, Vipergout, Wall of Ice}}

\ability{4th level:}{\emph{Dimension Door, Dismissal, Drawmij's Instant Summons, Lesser planar ally, lesser planar binding, Summon Frost Beast IV, Summon Monster IV, Summon Nature's Ally IV, Summon Undead IV, Wall of Fire}}

\ability{5th level:}{\emph{Dimension Shuffle, Dimensional Lock, Evard's Black Tentacles, Greater Dimension Door, Planeshift, Summon Frost Beast V, Summon Monster V, Summon Nature's Ally V, Summon Undead V, Teleport, Wall of Iron, Wall of Stone, Word of Recall}}

\ability{6th level:}{\emph{Antipathy, Greater Planeshift, Planar Ally, Planar Binding, Planar Bubble, Summon Frost Beast VI, Summon Monster VI, Summon Nature's Ally VI, Sympathy, Wall of Thorns}}

\ability{7th level:}{\emph{Binding, Forcecage, Greater Teleport, Maze, Shadowwalk, Summon Frost Beast VII, Summon Monster VII, Summon Nature's Ally VII, Teleport Object}}

\ability{8th level:}{\emph{Freedom, Greater Planar Ally, Greater Planar Binding, Shades, Summon Frost Beast VIII, Summon Golem, Summon Monster VIII, Summon Nature's Ally VIII}}

\ability{9th level:}{\emph{Elemental Swarm, Gate, Imprisonment, Refuge, Summon Elemental Monolith, Summon Frost Beast IX, Summon Monster IX, Summon Nature's Ally IX, Teleportation Circle, Unbinding}}
\normalsize
