\classname{Warrior [NPC]}
\vspace{-8pt}
\quot{"Guards! Get them!"}

\desc{The worlds of D\&D have a multitude of powerful champions who slay dragons with their swords and break necromancers over their knees. But while these characters are often the primary focus of the D\&D game, the fact remains that the way of the sword is traveled quite frequently by orcs and elves alike, and the vast majority of those who do so are not actually capable of performing such awesome displays of martial prowess. These are the Warriors -- the people who wield weapons in a manner that is entirely unlikely to get their names told in lasting song and story.}

\desc{Warriors in the Game: Warriors aren't playable as PCs. They lack the depth and tactical versatility to be an interesting character and they are not powerful enough to pull their weight in any real adventuring setup. They have a CR equal to half their Warrior level and don't get multiclassed with real classes at all. In order to keep this from being potentially unbalanced, we strongly suggest that warriors show up in groups. So while a 4th level Warrior is nominally a CR 2 opponent, he's not really a good challenge for a 2nd level party. But 2 of them are an appropriate challenge for a 4th level party. And that's really what the Warrior is for -- showing up in groups and getting smacked around anyway.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Warrior's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Craft (Int), Escape Artist (Dex), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Listen (Wis), Profession (Wis), Ride (Dex), Spot (Wis), Survival (Wis), Swim (Str), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+0 &+0 &+2 &Replacable\\
2nd &+2 &+0 &+0 &+3 &Signature Weaponry\\
3rd &+3 &+1 &+1 &+3 &Loyal to Death\\
4th &+4 &+1 &+1 &+4 &Rank\\
5th &+5 &+1 &+1 &+4 &Unshakable Morale\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Warrior class.

\ability{Weapon and Armor Proficiency:}{A Warrior is proficient with all simple and martial weapons, as well as Light and Medium Armor and Shields. In addition, a Warrior is proficient with either Heavy Armor or an Exotic Weapon.}

\ability{Replaceable:}{Warriors represent the faceless hordes of grunts, guards, and mooks. They are intended to be easy to use, and very easy to replace. Instead of worrying about the feats that a Warrior has, simply give Warriors +1 to-hit for each feat they would be eligible for.}

\ability{Signature Weaponry:}{2nd level warriors are proficient with all racial and cultural weapons and armor of their people. For example, 2nd level Dwarven Warriors are proficient with the Dwarven Waraxe and Stone Plate armor, while 2nd level Elven Warriors are proficient with Elven Thinblades and Darkleaf Armor.}

\ability{Loyal to Death:}{3rd level Warriors will fight to the death and remain conscious when below 0 hit points (they are still staggered as normal).}

\ability{Rank:}{4th level Warriors are qualified to lead troops, and have a Command Rating equivalent to being a Sergeant.}

\ability{Unshakable Morale:}{5th level Warriors never have to make Morale checks and receive a +2 bonus on saves vs. Fear.}

\ability{Trading Out Warrior Levels:}{Warrior levels aren't capable of doing anything good. If for some reason a Warrior became a named character, he becomes a member of a real character class. That is, simply trade levels of Warrior for levels in a real class that has a full BAB progression.}
