\classname{Defender} \label{class:defender}
\vspace{-8pt}
\quot{"One step closer, and your master will be receiving your head on a silver platter."}

\desc{Defenders are able warriors that prioritize the safety of their allies over the destruction of their enemies. Of course, destroying their enemies helps protect their allies, so most Defenders pursue this objective as well. Some Defenders are noble and idealistic and strive to protect the helpless; others just figure that keeping their current allies alive is easier than finding new ones.}

\desc{Defenders focus on martial combat and do not practice any traditional form of spellcasting, but they can't exactly ignore magic, given the number of magical threats in the world. Consequently, Defenders learn to manipulate the magic around them.}

\ability{Alignment:}{Any. Usually (but not always) similar to the alignment of the people the Defender wants to protect.}

\ability{Races:}{Races that don't value staying alive tend not to last very long. Defenders may be of any race.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{As Fighter.}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{The Defender's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Escape Artist (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), Spot (Wis), Survival (Wis), Swim (Str), Tumble (Dex), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Immediate Aid, Aura of Safety, Phalanx Fighter\\
2nd &+2 &+3 &+3 &+3 &Devoted Defense, Anticipate Opportunity, Uncanny Rescue\\
3rd &+3 &+3 &+3 &+3 &Danger Sense, Expert Reflexes, Armor Mastery\\
4th &+4 &+4 &+4 &+4 &Quick Lift, Tight Formation, Unresting Guard\\
5th &+5 &+4 &+4 &+4 &Positional Advantage, Improved Aid, Empowered Saves\\
6th &+6/+1 &+5 &+5 &+5 &Spell Static, Lasting Aid, Radiate Courage\\
7th &+7/+2 &+5 &+5 &+5 &Retaliatory Strike, Diverting Offense\\
8th &+8/+3 &+6 &+6 &+6 &Spell Stretch, Improved Withdraw, Greater Aura of Safety\\
9th &+9/+4 &+6 &+6 &+6 &Distracting Blows, Deadly Defense\\
10th &+10/+5 &+7 &+7 &+7 &Defender's Resilience, Opportunity Cost\\
11th &+11/+6/+6 &+7 &+7 &+7 &Ranged Aid, Greater Defensive Perimeter\\
12th &+12/+7/+7 &+8 &+8 &+8 &Spell Simulacrum, Aggressive Defense\\
13th &+13/+8/+8 &+8 &+8 &+8 &Effortless Motion, Instant Aura of Safety\\
14th &+14/+9/+9 &+9 &+9 &+9 &Superior Save, Improved Retaliatory Strike\\
15th &+15/+10/+10 &+9 &+9 &+9 &Reflect Woes\\
16th &+16/+11/+11/+11 &+10 &+10 &+10 &Spell Snare\\
17th &+17/+12/+12/+12 &+10 &+10 &+10 &General Aid\\
18th &+18/+13/+13/+13 &+11 &+11 &+11 &Unerring Sentinel, Supreme Defensive Perimeter\\
19th &+19/+14/+14/+14 &+11 &+11 &+11 &Warped Reach\\
20th &+20/+15/+15/+15 &+12 &+12 &+12 &Eternal Aura of Safety, Greater Aid\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Defender class.

\ability{Weapon and Armor Proficiency:}{Defenders are proficient with all Simple and Martial Weapons. Defenders are proficient with Light, Medium, and Heavy Armor, Shields and Great Shields.}

\ability{Immediate Aid (Ex):}{A Defender is aware of the plight of his allies at all times. He may Aid Another as an immediate action.}

\ability{Aura of Safety (Su):}{As a swift action, a Defender may project an Aura of Safety to protect himself and his allies. Roll a d20 and add the Defender's highest save to the result. For one round, the Defender and all allies he can see automatically succeed on the save against any spell or spell-like ability whose DC is less than or equal to the result (if the DC is higher, the target may still attempt a save as normal). This ability may be used a number of times per day equal to 3 + his charisma modifier.}

\desc{At 8th level, Aura of Safety works against any effect that allows a save. It is now usable a number of times per day equal to half the Defender's class levels + his charisma modifier.}

\desc{At 13th level, using Aura of Safety becomes a free action, instead of a Swift action.}

\desc{At 20th level, there is no longer a limit to the number of times per day the Defender may project an Aura of Safety.}

\ability{Phalanx Fighter:}{A Defender gains Phalanx Fighter as a bonus feat. If he already has this feat, he may instead select any [Combat] feat for which he meets the prerequisites.}

\ability{Devoted Defense (Ex):}{At 2nd level, when a Defender takes a Total Defense action, he gains a dodge bonus to AC equal to half his class level, in addition to the usual +4. In addition, the Defender may still make attacks of opportunity during a round that he takes a Total Defense action; in fact, he may make a number of extra attacks of opportunity equal to the number of attacks he can make during a Full Attack.}

\ability{Anticipate Opportunity (Ex):}{By 2nd level, a Defender has honed his ability to anticipate and exploit openings in enemy defenses. If an enemy takes an action that would provoke an attack of opportunity from the Defender (including a movement), but the Defender does not threaten the target, the Defender may forfeit one of his attacks of opportunity for the round to move 5' to a position where he threatens that enemy (and may then perform the attack of opportunity as normal). This movement provokes attacks of opportunity as normal.}

\ability{Uncanny Rescue (Ex):}{A Defender is always vigilant for threats to his allies. Once a Defender has attained 2nd level, any ally the Defender can reach benefits from Uncanny Dodge (though the Defender himself does not). Any allies the Defender can reach that already have Uncanny Dodge benefit from Improved Uncanny Dodge (the Defender himself does not). }

\ability{Danger Sense:}{At 3rd level, a Defender receives Danger Sense as a bonus feat. If he already has Danger Sense, he may select any [Combat] feat for which he meets the prerequisites.}

\ability{Expert Reflexes (Ex):}{Beginning at 3rd level, a Defender can make a number of additional attacks of opportunity each round equal to half his class level.}

\ability{Armor Mastery (Ex):}{A Defender acts as a shield for his allies, and must be strong enough to withstand mortal blows while remaining swift enough to intercept them. At 3rd level, the armor check penalty of any armor or shield being used by a Defender is reduced by 4.}

\ability{Quick Lift (Ex):}{Often the best way to protect someone is simply to separate them from the threat. Upon reaching 4th level, a Defender may make a Lift grapple attempt as a swift action. If the Defender moves on the same turn, this may be done at any point during the movement, and the Defender may continue moving afterwards.}

\ability{Tight Formation (Ex):}{Defenders never assume they are anyone's primary target, and learn to position themselves accordingly. At 4th level, a Defender may choose to count as being 5' in any direction from his actual position for purposes of determining whether he provides cover or dodge bonuses to another creature.}

\ability{Unresting Guard (Ex):}{Once the Defender has reached 4th level, he never becomes fatigued and no longer requires sleep. He is now immune to magical sleep effects.}

\ability{Positional Advantage (Ex):}{A Defender considers danger to others more important than danger to himself. As an immediate action, a Defender of 5th level may move one touched creature (but not himself) five feet in any direction. This movement does not provoke attacks of opportunity. If the target is unwilling, the Defender must succeed at a touch attack to move the target, and provokes an attack of opportunity from the target unless he has the Edge against that target.}

\ability{Improved Aid (Ex):}{Whenever a Defender of 5th level performs an Aid Another action, he provides double the usual bonus.}

\ability{Empowered Saves (Su):}{After reaching 5th level, a Defender always benefits from a resistance bonus to his saves equal to one third his character level, rounded up.}

\ability{Spell Static (Su):}{Magic doesn't behave entirely normally near a Defender. Once the Defender has reached 6th level, he gains spell resistance equal to 10 + his level. Any allies the Defender can reach also benefit from this spell resistance.}

\ability{Lasting Aid (Ex):}{When a Defender of 6th level uses an Aid Another action to provide an ally with a bonus, that bonus applies to every relevant roll within the next round, instead of only to the first one.}

\ability{Radiate Courage (Ex):}{At 6th level, a Defender becomes immune to [Fear] effects, and all [Fear] effects are suppressed on any ally benefitting from his Aura of Safety.}

\ability{Retaliatory Strike (Ex):}{A 7th-level Defender zealously protects his allies. A creature provokes an attack of opportunity from the Defender whenever it makes an attack that does not target him. If the attack would already provoke an attack of opportunity, it provokes a second one. At 14th level, attacks of opportunity made with this ability do not count against the Defender's limit of attacks of opportunity per round.}

\ability{Diverting Offense (Ex):}{Once a Defender has reached 7th level, any creature within a Defender's reach can neither grant nor receive flanking bonuses, unless he allows it.}

\ability{Spell Stretch (Su):}{At 8th level, a Defender learns to manipulate the duration of magical effects. Whenever the Defender or any creature within his reach is affected by a spell or spell-like ability with a duration other than instantaneous, concentration, or permanent, the Defender automatically knows the effect's duration, and may opt to increase or decrease it by up to 50\%. This is not an action.}

\ability{Improved Withdraw (Ex):}{Defenders prefer a tactical retreat to mutually-assured destruction. When a Defender of 8th level performs a Withdraw action, he provokes no attacks of opportunity from any opponents he can see for any movement taken during the action.}

\ability{Distracting Blows (Su):}{A Defender of 9th level has learned to momentarily disrupt the focus of opponents with his attacks. Whenever the Defender makes a successful attack against an opponent currently performing an action (normally only possible as a readied attack or attack or opportunity), the target must make a Will save (DC 10 + \half\ level + CHA) or lose the action. If the action was a movement and the target fails the save, he remains in the last square he occupied before the attack was triggered.}

\ability{Deadly Defense (Ex):}{By 9th level, a Defender has learned to goad enemies into mistakes through care and patience. When the Defender takes a Total Defense action, anyone attacking him before his next turn provokes an attack of opportunity from the Defender. If the attacker has the Edge, the Defender's attack of opportunity is resolved after the initial attack (and therefore does not benefit from Distracting Blows).}

\ability{Defender's Resilience:}{At 10th level, a Defender receives any one of Great Fortitude, Iron Will, or Lightning Reflexes as a bonus feat. If he already has all three of these feats, he may select any feat for which he meets the prerequisites.}

\ability{Opportunity Cost (Ex):}{By 10th level, a Defender has gained insight into the flow of battle and can anticipate the reactions of less experienced warriors. If the Defender has the Edge on an opponent, he may make an attack of opportunity against that opponent whenever the opponent makes an attack of opportunity.}

\ability{Ranged Aid (Ex):}{A Defender of 11th level may use Aid Another actions to hinder any opponent he can see within 60 feet, rather than just opponents within his reach.}

\ability{Greater Defensive Perimeter (Ex):}{Upon reaching 11th level, all of the Defender's class features whose range is dependent on his reach also extend 5' beyond his reach. Alternately, if he is armed with a ranged weapon, these effects extend out to 30'.}

\ability{Spell Simulacrum (Su):}{When a Defender of 12th level is targeted by a spell (or within the area affected by an area spell), he may choose for that spell to also affect the caster (the caster is entitled to saves or spell resistance as normal for the spell). This is not an action.}

\ability{Aggressive Defense (Ex):}{At 12th level, a Defender always has the Edge against any opponent currently threatening any of his allies. Additionally, he may make an attack of opportunity against any opponent that enters his threatened range if that opponent could threaten any of the Defender's allies from the space being entered. These attacks of opportunity do not benefit from the Defender's Distracting Blows ability.}

\ability{Effortless Motion (Ex):}{Defenders are expected to adapt their tactics to any situation without wasted effort. Upon reaching 13th level, a Defender may forfeit a swift action to take a move action, or vice versa. The move action from the Defender's current or next turn may be forfeited to perform an immediate action, just as is normally possible with a swift action (and thus the Defender can potentially take two immediate actions in a round).}

\ability{Superior Save (Ex):}{When a Defender attains 14th level, one of his saves (Fortitude, Reflex, or Will) becomes a Superior Save. Whenever he uses that save, he may add his highest attribute modifier (whichever it is at the time) instead of the usual attribute (CON, DEX, or WIS, respectively).}

\ability{Reflect Woes (Su):}{When a Defender of 15th level makes a successful attack, at his option, all poisons, diseases, negative levels, and ability damage afflicting the Defender or any ally within his reach are transferred (with their remaining durations) to the target. This transfer bypasses the target's immunity to any effect he is capable of inflicting.}

\ability{Spell Snare (Su):}{A Defender of 16th level has learned to entrap magical effects as they pass by. Whenever a spell or spell-like ability with a range of at least 5' and no more than "Long" is cast such that its line of effect passes within the Defender's reach, he automatically knows the spell being cast and its target (though not necessarily the caster). If the spell targets a creature, object, point, or area, the Defender may choose for the spell to target himself, one of his held items, or his position (as appropriate) instead. If he snares a spell that requires an attack roll, the attack automatically succeeds, but the Defender is still entitled to a saving throw or spell resistance as appropriate for the spell. This is not an action.}

\ability{General Aid (Ex):}{When a Defender of 17th level uses Aid Another to hinder an opponent and provide an attack or AC bonus to an ally, he provide bonuses to both attack and AC (rather than just one), and that bonus applies to all allies (rather than just one).}

\ability{Unerring Sentinel (Ex):}{Once the Defender has reached 18th level, he suppresses all of the following conditions on any allies within his reach: dazed, confused, entangled, and all fear and sleep effects. Additionally, any ally within the Defender's reach that is helpless is treated as being stunned instead.}

\ability{Supreme Defensive Perimeter (Ex):}{Upon reaching 18th level, all of the Defender's class features whose range is dependent on his reach also extend 10' beyond his reach. Alternately, if he is armed with a ranged weapon, these effects extend out to 60'.}

\ability{Warped Reach (Su):}{At 19th level, a Defender armed with any melee weapon can reach every square that is occupied or threatened by any ally within 100 feet, even if he does not have line of effect to those squares. The Defender also provides a flanking bonus to any ally attacking any creature the Defender threatens, regardless of relative position.}

\ability{Greater Aid (Ex):}{Whenever a Defender of 20th level performs an Aid Another action, he provides triple the usual bonus (instead of double from Improved Aid).}
