\classname{Dread Necromancer} \label{class:dreadnecro}
\vspace{-8pt}
\quot{"Why, yes milady, you are rather beautiful. I am afraid, however, that that is not why I want your body."}

\desc{Contrary to what many believe, Death is not an agent of evil. Often it is an agent of mercy for the sick, or an agent of change for the old. A Dread Necromancer is neither of those things. He is an agent of suffering and affliction, an agent of permanency and rot. He is not an agent of Death, but of Unlife. Cursing his mortal frame for its weakness, he seeks the twisted power of that which dies but is not dead, preferring an eternity of decay to the finality of Death, and as he masters the dark arts, he will achieve his end.}

\ability{Alignment:}{Although Necromancy is not generally an evil thing, it is even less a good thing. A Dread Necromancer can be any alignment, but don't expect orphanages to welcome you to their bake sales.}

\ability{Races:}{Dread Necromancers appear in all races, but Humans make up the majority of those out in the world.}

\ability{Starting Gold:}{3d6x10 gp (105 gold)}

\ability{Starting Age:}{As Sorcerer.}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Dread Necromancer's class skills (and the key ability for each skill) are Bluff (Cha), Craft (Int), Concentration (Con), Decipher Script (Int), Disguise (Cha), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Knowledge (any) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Search (Int), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus} (x4 at 1st level).

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{2cm}p{0.7cm}p{0.7cm}p{0.7cm}p{4.7cm}lllllllll}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special & \multicolumn{9}{c}{Spells Per Day}\\
&&&&&															  &1 &2 &3 &4 &5 &6 &7 &8 &9 \\
1st    &+0              &+2  &+0  &+2  & Body Assemblage, Practiced Caster, Rebuke Undead, Spell Casting, Touch of Death  &3 &- &- &- &- &- &- &- &- \\
2nd    &+1              &+3  &+0  &+3  & Unholy Toughness								  &4 &- &- &- &- &- &- &- &- \\
3rd    &+2              &+3  &+1  &+3  & Dead Inside									  &5 &- &- &- &- &- &- &- &- \\
4th    &+3              &+4  &+1  &+4  & 										  &6 &3 &- &- &- &- &- &- &- \\
5th    &+3              &+4  &+1  &+4  & Undead Creation Feat								  &6 &4 &- &- &- &- &- &- &- \\
6th    &+4              &+5  &+2  &+5  & 										  &6 &5 &3 &- &- &- &- &- &- \\
7th    &+5              &+5  &+2  &+5  & Undead Mastery									  &6 &6 &4 &- &- &- &- &- &- \\
8th    &+6/+1           &+6  &+2  &+6  & 										  &6 &6 &5 &3 &- &- &- &- &- \\
9th    &+6/+1           &+6  &+3  &+6  & Undead Creation Feat								  &6 &6 &6 &4 &- &- &- &- &- \\
10th   &+7/+2           &+7  &+3  &+7  & 										  &6 &6 &6 &5 &3 &- &- &- &- \\
11th   &+8/+3           &+7  &+3  &+7  & Phylactery									  &6 &6 &6 &6 &4 &- &- &- &- \\
12th   &+8/+3           &+8  &+4  &+8  & 										  &6 &6 &6 &6 &5 &3 &- &- &- \\
13th   &+9/+4           &+8  &+4  &+8  & Undead Creation Feat								  &6 &6 &6 &6 &6 &4 &- &- &- \\
14th   &+10/+5          &+9  &+4  &+9  & 										  &6 &6 &6 &6 &6 &5 &3 &- &- \\
15th   &+11/+6/+6       &+9  &+5  &+9  & Aura of Malevolence								  &6 &6 &6 &6 &6 &6 &4 &- &- \\
16th   &+12/+7/+7       &+10 &+5  &+10 & 										  &6 &6 &6 &6 &6 &6 &5 &3 &- \\
17th   &+12/+7/+7       &+10 &+5  &+10 & Undead Creation Feat								  &6 &6 &6 &6 &6 &6 &6 &4 &- \\
18th   &+13/+8/+8       &+11 &+6  &+11 & 										  &6 &6 &6 &6 &6 &6 &6 &5 &3 \\
19th   &+14/+9/+9       &+11 &+6  &+11 & Abomination									  &6 &6 &6 &6 &6 &6 &6 &6 &4 \\
20th   &+15/+10/+10     &+12 &+6  &+12 & Without Number									  &6 &6 &6 &6 &6 &6 &6 &6 &6 \\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the Dread Necromancer.

\ability{Weapon and Armor Proficiency:}{A Dread Necromancer is proficient with all simple weapons, his Death Touch, and 1 martial weapon of his choice; he is not proficient with any armor or shield.}

\ability{Body Assemblage (Ex):}{At first level, a Dread Necromancer receives the Body Assemblage necromantic creation feat as a bonus feat.}

\ability{Practiced Caster (Ex):}{Due to the extreme specialization of a Dread Necromancer’s craft, you never suffer any arcane spell failure while wearing an armor or shield you are proficient with.}

\ability{Rebuke Undead (Su):}{A Dread Necromancer may Rebuke Undead as a Cleric of equal level 3 + his Charisma Modifier (if positive) times per day.}

\ability{Spell Casting:}{A Dread Necromancer is an arcane caster whose spell list is every spell from the Necromancy school on the Cleric, Druid, and Wizard spell list in the players handbook. A spell appearing on multiple spell lists with a different spell level is considered to be the lowest level available on the Dread Necromancer’s spell list, which is provided for your convenience below. His caster level is equal to his class level. A Dread Necromancer knows all spells on his spell list (as a Cleric), and may cast them spontaneously a number of times per day as a Sorcerer of equal level, except that a dread necromancer has no 0 level spell slots. A Dread Necromancer must have a Charisma Score of at least 10 + the spell’s level to cast a spell of that level. The DC of a Dread Necromancer spell you cast is 10 + the spell’s level + your Charisma Modifier. At first level and each level thereafter, you may permanently add one Cleric, Druid, or Wizard spell with a spell level equal to or less than the highest you may cast from any school to your spell list. At 5th level and every odd level thereafter, you may switch out one spell you know for another Cleric, Druid, or Wizard spell of the same spell level}

\ability{Touch of Death (Su):}{Anytime a Dread Necromancer makes a melee attack, he may do an additional 1d6 per class level of negative energy damage in addition to whatever else he does. He may also just do the negative energy damage as a melee touch attack as an attack action.}

\ability{Unholy Toughness (Su):}{At second level, a Dread Necromancer may substitute their Charisma Modifier for Fortitude Saves, Concentration Checks, and bonus HP per hit die. Additionally you gain DR/Magic equal to their character level that stacks with any other sources of DR you possess.}

\ability{Dead Inside (Ex):}{At third level, change the Dread Necromancer’s creature type to Undead (if it was not already), and gains the [dark minded] and [augmented *whatever previous creature type you were*] subtypes. You also get +4 Turn Resistance, happy Deathday.}

\ability{Undead Creation Feat (Ex):}{At fifth, ninth, thirteenth, and seventeenth level, a Dread Necromancer receives a necromantic creation feat as a bonus feat. He must still meet all prerequisites for these bonus feats, which are granted in addition to the feats that a character of any class gets from advancing levels.}

\ability{Undead Mastery (Su):}{At seventh level, a Dread Necromancer’s Charisma Modifier is added to the number of Hit Dice He may have animated (now 4 + his Charisma Modifier per level) or controlled through Rebuking (now 2 + his Charisma Modifier per level) at one time. Additionally, any undead he creates gain DR/Magic equal to their Hit dice, receive a +1 enchantment bonus to all their ability scores per 3 character levels of the Dread Necromancer, and a number of additional HP equal to that granted by the Unholy Toughness of the Dread Necromancer for no reason. The bonus HP granted by Undead Mastery does not stack with that granted by the Unholy Toughness special quality an undead already possess.}

\ability{Phylactery (Su):}{At 11th level, a Dread necromancer creates and stores his soul within a Phylactery, and unless it is destroyed, a Dread Necromancer is never slain when his body is destroyed. Instead, the body re-appears 1d10 days later where the phylactery was located with the phylactery around its neck. The Phylactery is a diminutive object with a Hardness equal to the DR you possess, and has a number of hit points equal to your hit point total. If the Phylactery is destroyed, you are also slain, and go on to the afterlife you deserve. Your Phylactery counts against your 8 magic item limit. Additionally, you gain DR/Bludgeoning equal to your character level that stacks with any other sources of DR you possess.}

\ability{Aura of Malevolence (Su):}{Just in case nobody figured it out already, a Dread Necromancer is worse than a dark alley in a dark alley. At fifteenth level, at the beginning of any creature’s turn who is within medium range of you (100 ft. + 10 ft. for each character level you possess) and not considered an ally by you must make a Will Save (DC 10 + half the your character level + the your Charisma Modifier) or be Shaken for a number of rounds equal to the your Charisma Modifier.}

\ability{Abomination (Su):}{Really, you should have seen this coming. At nineteenth level, A Dread Necromancer becomes so abhorrent to creation that it partially shunts you from existence. You gain the Incorporeal Subtype. It takes an act of will to manifest physically as a corporeal creature, and requires a move action on your part to do so for a number of rounds equal to your Charisma Modifier. Also, you gain DR/Good equal to your character level that stacks with any other sources of DR you possess.}

\ability{Without Number (Ex):}{At twentieth level, a Dread Necromancer becomes an Aspected Necromantic Intelligence, which radiates out from your body a number of miles equal to you Charisma Modifier. You may change your Aspect as an Immediate Action to any Undead whose CR is equal to your level or less; and no, you can’t aspect Slay Mates. You may see and hear as if you were standing where any undead created by the Intelligence is (using your spot and listen modifiers, as well as any perceptive abilities you possess). The Dread Necromancer’s Phylactery is considered the Focus of the Necromantic Intelligence.}

\spelllist{Dread Necromancer Spells:}
\small

      \ability{1st Level:}{\emph{Cause Fear, Chill Touch, Curse Water, Death Watch, Doom, Inflict Light Wounds, Ray of Enfeeblement}}

			\ability{2nd Level:}{\emph{Blindness/Deafness, Command Undead, Death Knell, False Life, Gentle Repose, Ghoul Touch, Inflict Moderate Wounds, Scare, Spectral Hand}}

      \ability{3rd Level:}{\emph{Animate Dead, Contagion, Halt Undead, Inflict Serious Wounds, Poison, Ray of Exhaustion, Speak with Dead, Vampiric Touch}}

      \ability{4th Level:}{\emph{Blight, Death Ward, Enervation, Fear, Inflict Critical Wounds}}

      \ability{5th Level:}{\emph{Mass Inflict Light Wounds, Magic Jar, Mark of Justice, Slay Living, Symbol of Pain, Waves of Fatigue}}

      \ability{6th Level:}{\emph{Circle of Death, Create Undead, Eyebite, Harm, Mass Inflict Moderate Wounds, Symbol of Fear, Undeath to Death}}

      \ability{7th Level:}{\emph{Control Undead, Finger of Death, Mass Inflict Serious Wounds, Symbol of Weakness, Waves of Exhaustion}}

      \ability{8th Level:}{\emph{Clone, Create Greater Undead, Horrid Wilting, Mass Inflict Critical Wounds, Symbol of Death}}

      \ability{9th Level:}{\emph{Astral Projection, Energy Drain, Soul Bind, Wail of the Banshee}}
\normalsize