\classname{Ninja}
\vspace{-8pt}
\quot{"Did you see that army roll I just did? Course not, I'm a fucking ninja!"}

\ability{Alignment:}{Totally Sweet (Any)}

\ability{Starting Gold:}{4d4*10 gp (100 gp)}

\ability{Starting Age:}{As Rogue}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The ninja's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (Any) (Int), Listen (Wis), Move Silently (Dex), Perform (Dance/Stage Theatre) (Cha), Search (Int), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Swim (Str), Tumble (Dex), Use Rope (Dex)}

\ability{Skills/Level:}{4 + Int Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}p{7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &AC Bonus\\
1st    &+1              &+0 &+2  &+2  & Armored in Life, Surprise!, Too Fast By Half &+4\\
2nd    &+2              &+0 &+3  &+3  & Wall Jump, Ninja'd  &+5\\
3rd    &+3              &+1 &+3  &+3  & Invisible, Speed of Thought, Cowabunga!  &+5\\
4th    &+4              &+1 &+4  &+4  & Dark Stalker, Seductive Gaze  &+6\\
5th    &+5              &+1 &+4  &+4  & Master of Disguise, Summon Mist, Kidney Punch  &+6\\
6th    &+6/+1           &+2 &+5  &+5  & Double-Jump, Join the Clan  &+7\\
7th    &+7/+2           &+2 &+5  &+5  & Scuttler, Anti-Noise Aura, Sexy No Justsu  &+7\\
8th    &+8/+3           &+2 &+6  &+6  & Log Trick, Go Ninja Go Ninja Go  &+8\\
9th    &+9/+4           &+3 &+6  &+6  & Master of Escape, All Ninjas Fly, Flying Kick  &+8\\
10th   &+10/+5          &+3 &+7  &+7  & Not Visible, Close Combat  &+9\\
11th   &+11/+6/+6       &+3 &+7  &+7  & Shadow Lands, Shadow Clone, Too Fast By \textthreequarters &+9\\
12th   &+12/+7/+7       &+4 &+8  &+8  & Secret Bedroom Technique, Get Over Here!  &+10\\
13th   &+13/+8/+8       &+4 &+8  &+8  & Trap Setter, Spirit Blade, Time to Death  &+10\\
14th   &+14/+9/+9       &+4 &+9  &+9  & Perfect Disguise, Pirate Killer  &+11\\
15th   &+15/+10/+10     &+5 &+9  &+9  & Spell Stowaway, Secret Scrolls, Perpetual Distraction  &+11\\
16th   &+16/+11/+11/+11 &+5 &+10 &+10 & Honor is Babbies, Disregard Me  &+12\\
17th   &+17/+12/+12/+12 &+5 &+10 &+10 & Murder Punch, Harem No Jutsu, FINISH HIM!  &+12\\
18th   &+18/+13/+13/+13 &+6 &+11 &+11 & Me First!, You Can't See Me  &+13\\
19th   &+19/+14/+14/+14 &+6 &+11 &+11 & Clan Master, Forbidden Technique, Nightmare Realm  &+13\\
20th   &+20/+15/+15/+15 &+6 &+12 &+12 & Fully Too Fast, Back In Black  &+14\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the ninja. 

\ability{Weapon and Armor Proficiency:}{Ninjas are proficient with all simple weapons, all martial weapons, and with two exotic weapons of the players choice}

\ability{Armored in Life (Su):}{A Ninja has a special Armor bonus whenever they are not using armor or shields that he is not proficient in. This Armor Bonus applies against Touch Attacks and Incorporeal Touch Attacks, and has a value of +4. Every even numbered class level, the Armored in Life bonus increases by 1. If the Ninja wears armor which he is proficient in (for example: normal clothing) that has an enhancement bonus, that enhancement bonus applies to his Armored in Life Armor Bonus.}

\ability{Surprise! (Ex):}{If the Ninja should catch a foe flat-footed, then all successful attacks she makes against that foe are automatic critical hits. I have no idea why ninjas carry scythes.}

\ability{Too Fast By Half (Ex):}{The Ninja multiplies her base speed by 1.5 (round down), particularly when doing a "Ninja Run" pose.}

\ability{Wall Jump (Ex):}{Ninjas are great at using the walls to propel themselves. Not only does she suffer no falling damage when next to a wall, she may also double her jumping height and distance when starting off next to a wall, and if between two walls, gains a Climb speed equal to her land speed.}

\ability{Ninja'd (Ex):}{Ninja always seize the initiative at the last moment and do things before anyone else can react. In combat, if there is no Surprise round, the Ninja gains her own Surprise round. If there \textit{is} a Surprise round, the Ninja can act in it, going first. The Ninja can only access this ability if she possesses more levels of Ninja than any other class.}

\ability{Invisible (Su):}{The Ninja may become Invisible at will, as per the spell \spell{invisibility}.}

\ability{Speed of Thought (Ex):}{Ninja move so fast they get speed lines when they move. The Ninja may add her Int bonus to her Initiative, and to all melee attack and damage rolls made against flat-footed or flanked opponents.}

\ability{Cowabunga! (Su):}{Ninja are possibly the best surfers in the world. She may move on water as though it were a solid surface, and is immune to the effects of Grease and similar spells and effects. If she stops on water, she must make a DC 40 Balance check to remain on top.}

\ability{Dark Stalker (Ex):}{The Ninja can see and hear incorporeal/ethereal creatures normally, so they must make Hide/Move Silently checks to sneak up on her.}

\ability{Seductive Gaze (Su):}{The Ninja gains a Charm Monster gaze attack at will, with an Int-based save DC.}

\ability{Master of Disguise (Su):}{With a DC 15 Disguise check, a Ninja can effectively cast Disguise Self. With a DC 20 check, she can effectively cast Alter Self.}

\ability{Summon Mist (Su):}{Mist is a Ninja's best friend. She can call upon it, as per the spell \textit{Obscuring Mist}, at will, though only one such effect can be active at a time.}

\ability{Kidney Punch (Ex):}{When the Ninja punches someone who is flat-footed or flanked, they are crippled by pain. The foe becomes Staggered and Prone unless they can pass a Fortitude save (Int-based). Staggered lasts for one full round, Prone lasts until they stand up.}

\ability{Double-Jump (Ex):}{You would think a Ninja can fly by looking at them jump. Double the Jumping height and distance of the Ninja. This stacks with Wall Jump. Additionally, she gains a Fly speed (half her base speed, Clumsy, flat-footed while flying).}

\ability{Join the Clan (Ex, see below):}{The Ninja becomes a member of a very secret Ninja clan. As benefits, she can call upon their assistance for information, and is taught the secret techniques: she may cast \textit{Knock}, \textit{Detect Traps} and \textit{Identify} as Spell-like abilities at will. These only require Swift actions.}

\ability{Scuttler (Ex):}{The Ninja is great at moving about in all situations. She may move at regular speed while being stealthy, and does not suffer penalties for difficult terrain.}

\ability{Anti-Noise Aura (Su):}{Have you ever heard a Ninja, as opposed to the short scream of their victim? I didn't think so. But sometimes, a Ninja has to travel with a plate-armoured Cleric, a Dire Bear (Druid) and a Knight on a steam engine. She may, at will, radiate a 20' Aura of silence, masking all noises made.}

\ability{Sexy No Jutsu (Su):}{By spending a Full Round Action making indecent gestures, the Ninja may cause a Suggestion or Hold Person effect on a target who can see her and fails a Will save (Int-based). Additionally, if the target passes the save, they still take a -3 penalty on Will saves for one round and suffer 5d6 Non-lethal damage.}

\ability{Log Trick (Ex):}{Just when you think you have a Ninja, you actually have a log. The Ninja is behind you. As an Immediate action, the Ninja may Dimension Door to any location up to 30' away, leaving a puff of smoke and a wooden log behind. Additionally, she may spend a Standard Action to Dimension Door 30' away, leaving a Mirror Image behind for 4 rounds. When the image ends, a log appears.}

\ability{Go Ninja Go Ninja Go (Ex):}{The Ninja may make a Full Round action (or two Partial actions) and a Swift action in the Surprise round, as opposed to just one Partial action.}

\ability{Master of Escape (Ex):}{The Ninja can never be pinned down. Any Escape Artist check may be made as a Standard action that does not provoke, and she may make Epic checks at the following DCs: Extremely Tight Space (a chimney, a glass jar, someone's anus) DC 30, Walls of Force DC 40 or Caster Level + 5, whichever is higher. She also gains a +8 bonus to escape a grapple. None of this applies when wearing heavy armour or when heavily encumbered.}

\ability{All Ninjas Fly (Su):}{The Ninja gains a Fly speed (Average) equal to her base speed.}

\ability{Flying Kick (Ex):}{When flying or jumping, the Ninja may make a special charge attack. She moves in a straight line, up to twice her movement speed, and attacks everyone in this line. She gains the charge bonus and penalty, and additionally, anyone struck is Dazed for one round if they fail a Fort save (Dex-based DC).}

\ability{Not Visible (Ex):}{The Ninja cannot be seen when she doesn't want to be. This is like Invisibility, except that it is (Ex) and True Seeing doesn't cut it. The only way to see her is to know what you're looking for and beat her Hide with a Spot check with no bonuses to the Spot check from equipment, spells or effects - only 1d20 + ranks + ability score + feats. Or if she ends the effect voluntarily or by attacking or passing out.}

\ability{Close Combat (Ex):}{I bet you think you're really smart for trying to grapple the Ninja. You won't for long. Ninja can act normally while being grappled, even if lifted or pinned - including movement (the grappler can hold on and be moved with her or can let go), and doesn't lose her Dex bonus to AC. Furthermore, her opponent IS flat-footed against her attacks.}

\ability{Shadow Lands (Su):}{The Ninja can conjure a Hallucinatory Terrain effect at will. Only one such effect can be active at a time.}

\ability{Shadow Clone (Su):}{The Ninja can cast Mirror Image at will, however cannot use it while even a single image still remains - she can't even refresh it, having to wait until the final clone vanishes. Additionally, when attacking foes in melee combat, she deals +2d6 damage for every remaining image.}

\ability{Too Fast By \textthreequarters (Ex):}{The Ninja becomes even faster. She may make a Move action as an Immediate action, and makes 10' steps of adjustment instead of 5' steps (unless she only wants to move 5'). With a DC 25 Balance check she can instead make 15' steps of adjustment.}

\ability{Secret Bedroom Technique (Su):}{The Ninja learns secret Ninja skills that would be forbidden if Ninjas didn't find them so funny. Firstly she may, with a Standard action, create a magic dust that if inhaled or consumed (it dissolves in liquid) creates an Emotion: Love (or Lust or Trust) effect. The save DC is Int-based, and the powder becomes useless after one hour if not used. Secondly, no sexual encounter with her ever needs to be played out, as the partner(s) automatically have "a very good time" and their attitude changes to Fanatical.}

\ability{Get Over Here! (Ex):}{With a Swift action, the Ninja may call out to a foe who understands her language and can hear her. The foe must pass a Will save (Int-based DC) or immediately make a Move action directly towards the Ninja, regardless of obstacles or provoking. Alternatively she may force them to, on their next action, attempt to charge her instead of whatever they were going to do, but this must be decided when she uses the ability.}

\ability{Trap Setter (Ex):}{If the Ninja has a trap on hand, she can set it in one Standard action, she's that fast. The DC to spot it is equal to a Sleight of Hand check she makes, and the DC to disarm is is that plus five. The DC to avoid being horribly maimed is normal for the trap, however.}

\ability{Spirit Blade (Su):}{The Ninja can even cut ghosts. All of her attacks affect incorporeal and ethereal creatures as though they were neither, and ignore Armour and Shield bonuses to AC as well as all kinds of Damage Reduction (including DR X/-).}

\ability{Time To Death (Ex):}{Those who would normally be staggered upon failing a save against the Ninja's Kidney Punch instead become Nauseated for 1d4 rounds, although they do still get the save.}

\ability{Perfect Disguise (Su):}{The Ninja may, with a DC 35 Disguise check, Polymorph as per the spell. True Seeing does not trump this.}

\ability{Pirate Killer (Ex):}{Shouting "YARR!" provokes an Attack of Opportunity from the Ninja. Additionally, she gains a +4 bonus to Hit and 4d6+4 Bonus Damage against Swashbucklers, Dread Pirates and all ship-owners, and enjoys a doubled critical threat multiplier against them.}

\ability{Spell Stowaway (Su):}{If someone within 30' casts a spell on himself, the Ninja may elect to, as not an action, gain the effects as well. Note that if the Lich turns out to have been casting Harm, it gets healed whereas she is damaged as normal (unless Negative energy heals her normally).}

\ability{Secret Scrolls (Ex, see below):}{Having risen through the ranks, the Ninja is shown the secret scrolls and gains special abilities. She may cast Disintegrate, Utterdark and Hold Monster once each per minute.}

\ability{Perpetual Distraction (Su):}{People are always distracted while fighting the Ninja. She always counts as flanking enemies.}

\ability{Honour is Babbies (Ex):}{The Ninja does not care for honour, and makes a hobby out of putting the boot in when facing an enemy. If a foe has fallen Prone, her attacks automatically hit them. If she focuses all attacks against this fallen foe, they must make a Fort save (Dex-based DC) or become Helpless from pain for 1 round.}

\ability{Disregard Me (Ex):}{The Ninja gains the ability to not be noticed. It becomes impossible to detect her with Divinations unless she wants to be, and she never provokes Attacks of Opportunity. Likewise enemies can't use readied actions against her. However, if an enemy has an ability that lets them take Attacks of Opportunity on someone who hasn't provoked, or lets them force foes to provoke, it still works against her.}

\ability{Murder Punch (Ex):}{People die when they are killed. All attacks made by the Ninja ignore Fast Healing and Regeneration - the damage is there until healed (such as by magic) or the very long recovery of X per day. Anyone slain by the Ninja can never come back without a True Resurrection or a Wish.}

\ability{Harem No Jutsu (Su):}{This ability works like Sexy no Jutsu, except every foe within 50' is affected. If anyone is successfully affected for 3 rounds in a row they must make a Fort save (same DC) or die, but they will die happy. The Ninja gains a +9,001 bonus to Perform (Dance) checks.}

\ability{FINISH HIM! (Ex):}{If the Ninja makes a full attack against a single foe denied their Dex bonus, and every attack hits, then instead of any other effects requiring saving throws, she may force them to make a single Fort save (Int-based DC, +1 for every hit beyond the first) or die, exploding in a shower of gore.}

\ability{Me First! (Ex):}{If someone casts a spell within 30' of the Ninja, she may spend an Immediate action to steal the effects. The spell is still cast, but all effects are resolved against the Ninja. She can do this after identifying a spell being cast.}

\ability{You Can't See Me (Su):}{The Ninja may, as an Immediate action, cause an attack, spell or effect directed at her to instead target the attacker. They must continue to use it at full force with the full bonus used against her and cannot attempt to force the attack to miss or fail.}

\ability{Clan Master (Ex, see below):}{The Ninja becomes the master of her clan, gaining the final secret arts: she gains Immunity to a single school of magic of her choice, and ceases ageing, though bonuses will still accrue. Additionally her Int, Wis and Cha scores all suddenly increase by +4.}

\ability{Forbidden Technique (Su):}{The Ninja learns a trick that is forbidden to all but the most experienced Ninjas. Rumour has it the last person who tried it was sent home in a matchbox. She may, as a Full Round action, gaze upon a foe, who is entitled to a Will save (Int-based). If they fail, they cease to exist, permanently wiped from the face of the earth. Only a major quest can bring them back. If they succeed, they still suffer 2d6 negative levels. The Ninja may elect to sacrifice herself with this power, but can never be compelled to do so via magic or trickery: if she does, the foe receives no save and is simply destroyed, but the same applies to her. They are both gone forever, for a given value of "forever".}

\ability{Nightmare Realm (Su):}{The Ninja may cast Nightmare Terrain at will, though only one such effect may be in play at a time. Additionally, every round, one target of her choice in the area can be targeted with a Shadow Well effect.}

\ability{Fully Too Fast (Ex):}{The speed of the Ninja now increases to double the base speed. Additionally, she may move as though by teleportation, ignoring all barriers and such, and leaves a thunderclap behind when doing this. The thunderclap affects all within 10' of where she previously stood, knocking them Prone and Dazing them for one round if they fail a Fort save (Dex-based DC).}

\ability{Back In Black (Su):}{If the Ninja is ever killed, as long as the body is not destroyed and the soul is not consumed/bound/destroyed, she simply comes back 24 hours later, none the worse for wear.}