\classname{Snowscaper}
\quot{"I think you need to chill out."}

\desc{Snowscapers tap into the Plane of Ice, and may create ice and cold and snow when they want to. They're better on their home turf (cold snowfields), but the mark of a powerful snowscaper is being able to make their own snow and ice.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d8}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2 &+2 &Cold Resistance, Cold Magic, Pall of Frost, Frozen Heart\\
2nd &+1 &+3 &+3 &+3 &Brittling, Create Ice, Skate\\
3rd &+2 &+3 &+3 &+3 &Frost’s Bite, Ice Skating, Ground Freeze.\\
4th &+3 &+4 &+4 &+4 &Cold Immunity, Encumber\\
5th &+3 &+4 &+4 &+4 &Icebeam, Let It Snow\\
6th &+4 &+5 &+5 &+5 &Freeze, Never-melt Ice\\
7th &+5 &+5 &+5 &+5 &Skate on Air, Create More Ice\\
8th &+6/+1 &+6 &+6 &+6 &Wall of Ice\\
9th &+6/+1 &+6 &+6 &+6 &Blizzard, Mirror Mirror On The Wall\\
10th &+7/+2 &+7 &+7 &+7 &Through the Looking Glass\\
11th &+8/+3 &+7 &+7 &+7 &Animate Snow\\
12th &+9/+4 &+8 &+8 &+8 &Create Tons of Ice\\
13th &+9/+4 &+8 &+8 &+8 &Wintersmith, The Great Blizzard of '52.\\
\end{tabular}
\end{small}
\end{table}

\ability{Class Skills:}{The Snowscaper's class skills (and the key ability for each skill) are Bluff (Cha), Climb (Str), Craft (Int), Concentration (Con), Disguise (Cha), Escape Artist (Dex), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Profession (-), Ride (Dex), Search (Int), Spellcraft (Int), Spot (Wis), Survival (Wis), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\ability{Weapon and Armor Proficiency:}{The Snowscaper is proficient with all simple weapons, all martial swords and piercing weapons, and any three exotic piercing or slashing weapons he wants. The Snowscaper is proficient with light armor but not with shields.}

\ability{Cold Resistance (Ex):}{At level 1, the Snowscaper gains Cold Resistance equal to her character level.}

\ability{Cold Magic (Ex):}{All Cold spells are considered spells known for the purposes of magic item activation.}

\ability{Coldfire (Su):}{At level 1, the Snowscaper may form a semi-solid ball of pure cold energy and then throw it at an enemy as an standard action, where it'll burst upon impact. This is a ranged touch attack with a Short range, and does 1d6 cold damage per level.}

\ability{Pall of Frost (Su):}{At level 1, the Snowscaper may frost herself over and chill the air around herself within 10 feet, inflicting 1d6 cold damage to everyone within the radius. While frosted, the Snowscaper is considered armed, and all of her melee attacks do 1d6 extra cold damage.}

\ability{Frozen Heart (Su):}{A Snowscaper gets her Charisma bonus or her character level (whichever is lower) to Cold damage.}

\ability{Brittling (Su):}{At level 2 the Snowscaper may concentrate her will upon a person or object within medium range, and chill the target. This always hits, and does 1d6 cold damage, and makes the target lose their Dex bonus to AC for one round (two if the target is Cold-vulnerable). Objects have their hardness halved for 1d4 rounds; this goes for any creature which also has a Hardness score.}

\ability{Create Ice Object (Su):}{At level 2 a Snowscaper may use a standard action to create any object or objects she's seen seen before--out of ice. They may be created in the air or in a square of your choice (within range), 10 lbs per character level, short range, a number of objects equal to your character level. Hardness equal to 10 + ½ Character level + Charisma Modifier, but takes 1d6 damage each round it’s in non-freezing temperature (which the Snowscaper can get around). Treat it as having the HP of a material of a similar hardness, if you care that much about sundering. Also, creating your maximum amount is a full-round action.}

\ability{Skate (Su):}{At level 2, The Snowscaper may [i]skate[/i] at will, as per the psionic power, on a line of ice she creates ahead of her as she moves. The trail remains iced over for one round. This may also be used on natural ice.}

\ability{Frost’s Bite (Su):}{At level 3, the Snowscaper’s ice abilities generate a bitter cold. Her cold abilities penetrate Cold immunity, resistance, and hardness.}

\ability{Ice Skating (Su):}{At level 3, you may use Skate to cross liquid surfaces. The ice trail still disappears after a round, so you'd better keep moving, especially if you're crossing lava or acid.}

\ability{Ground Freeze (Su):}{At level 3, the Snowscaper may freeze four 5-foot squares per character level as a standard action. The ice in any square can be thawed using a fire spell. Also, the Snowscaper may now fix Ice objects onto horizontal and vertical surfaces and be sure they'll support a decent amount of weight.}

\ability{Cold Immunity (Su):}{At level 4, the Snowscaper does not fear cold, and is immune to it.}

\ability{Encumber (Su):}{At level 4, the Snowscaper’s creation abilities are getting better, allowing her to do more and more things. She may spend a standard action to attempt to wrap someone in heavy, restricting ice—as much as she can make with Create Ice--encumbering them with the weight, with a Reflex save for half the weight.}

\ability{Icebeam (Su):}{The Snowscaper's mastery of coldfire has expanded to allow her to fire a ray of it. Long-range ray as a standard action, 1d6 Cold Damage per character level.}

\ability{Let It Snow (Su):}{As a standard action, the Snowscaper may it snow in a medium-range radius, in as wide or as small an area as you want (within the radius). It starts off with a foot of snow, and goes up a foot every round until you tell it to stop.}

\ability{Freeze (Su):}{At level 6, the Snowscaper may bind someone or something up with ice. Treat as a Hold Monster, but with a Reflex save instead.}

\ability{Never-melt Ice (Su):}{At level 6, the Snowscaper’s ice creations are immune to all fire and won’t melt unless the Snowscaper allows it or the Snowscaper dies.}

\ability{Skate In Air (Su):}{At level 7, the Snowscaper may now skate through the air by creating a sheet of ice to travel across. The largest angle at which the Snowscaper can travel upwards is 45 degrees (as per Air Walk).}

\ability{Create More Ice (Su):}{At level 7, the Snowscaper may create 100 lbs of ice per character level within medium range. She may now make three separate objects per character level.}

\ability{Wall of Ice (Sp):}{At level 8, the Snowscaper gains Wall of Ice as an at-will spell-like ability.}

\ability{Blizzard (Sp):}{At level 9 the Snowscaper may use a standard action to produce a howling gale of freezing wind carrying shards of ice and snow. It does 1d6 Cold damage per character level, and also does 1d6 Slashing and Piercing damage/three character levels. A Blizzard is a short-range Cone.}

\ability{Mirror Mirror on the Wall (Su):}{All of the Snowscaper’s ice creations come from the Plane of Ice, and, as such, are linked and can be linked. At level 9, a Snowscaper has gained enough mastery to link any two smooth reflective surfaces made from her ice like a window as standard action.

\noindent That is to say, the Snowscaper stands in front of a mirror, chooses one of her other mirrors, wherever it may be, and then may see out the other mirror as if looking through a window.

\noindent Anyone or anything present on the other side can likewise see and communicate through their mirror. This effect lasts until the ice mage dismisses it as a free action (or until they're knocked out or killed or what-have-you). Only two surfaces may be linked as such at a time.}

\ability{Through the Looking Glass (Su):}{At level 9, a Snowscaper using her [i]Mirror Mirror On The Wall[/i] ability may pass through the mirrors as easily as climbing through a window, stepping through an open door, or falling down a hole. Others may also come, as long they form a chain by holding hands and the first person through is the Snowscaper. It is not advisable to let go of the chain when you're halfway through the mirror, because now your body parts will be separated by the distance between the mirrors.}

\ability{Animate Snow (Sp):}{At level 11, the Snowscaper may use Animate Snow, as the spell, at will.}

\ability{Create Tons of Ice (Su):}{At level 12, the Snowscaper can create 1,000 lbs of ice per character level as full-round action. It can be created within long range, but must be created on the ground.}

\ability{Wintersmith (Su):}{At level 13, The Snowscaper may now plunge an area into winter. When she first gets this ability, she may create large amounts of snow and icicles and all that, out to Long Range, for one day per character level. This can have effects like Let it Snow and Ground Freeze. Unlike most of her creations, this is not Never-melt Ice. At character level 15, she may do it as far as she can see. At level 17, the wintery conditions she creates do not melt normally and last until she relents and lets them thaw away, or until she is killed.}

\ability{The Great Blizzard of '52 (Sp):}{The Snowscaper's blizzards are now of legendary proportions. She may create a blizzard which is a Medium-ranged Cone. It inflicts (Character Level + Cha Modifier)d6 in Cold damage, and (1/3 Character Level + Cha Modifier) in Slashing and Piercing damage.}