\classname{Sohei} \label{class:comm:sohei}
\vspace{-8pt}
\quot{``Don't you dare hurt my friends.''}

\desc{The Sohei is a bit like the Monk, but with a little more influence (in theory, at least) on being virtuous and enlightened. They also tend to use weapons and armour, but it's by no means necessary.}

\desc{Note that this isn't just a description of the class I have written, it's basically what the Sohei seems to be. To be honest, they're not as well known as, say, the ninja (although at least there's less argument as to what they actually do).}

\desc{As a Sohei, a good Int is not a bad idea, but what you really want is a high Wisdom, and without ignoring your physical abilities. Although, I hear there are feats that could in fact allow you to ignore your physical scores. It has the potential to get around annoying things like walls of force at later levels, and gets a free ticket into the Wish Based Economy. It probably has cool tricks for the advanced player to exploit, but I don't really see anything that stops it being available to beginners.}

\ability{Alignment:}{Anything they could argue as being virtuous (Any Good)}

\ability{Races:}{Any}

\ability{Starting Gold:}{2d4x10 gp (50 gold)}

\ability{Starting Age:}{As Monk.}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{Make your own, since Koumei doesn't believe in cross-class skills.}
%This should really have a set of class skills to comply with the rest of the classes.

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}p{9cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Improved Unarmed Strike, Divine Flurry\\
2nd &+2 &+3 &+3 &+3 &Unforeseen Strike, Virtuous Writings\\
3rd &+3 &+3 &+3 &+3 &Power Slide, Speed: +10'\\
4th &+4 &+4 &+4 &+4 &Counter Attack\\
5th &+5 &+4 &+4 &+4 &Enlightenment: Perfect Understanding\\
6th &+6/+1 &+5 &+5 &+5 &Super Gauge, Divine Go Stone Placement of Perfection\\
7th &+7/+2 &+5 &+5 &+5 &Divine Frenzy\\
8th &+8/+3 &+6 &+6 &+6 &Speed: +15', C-C-C-COMBO BREAKER\\
9th &+9/+4 &+6 &+6 &+6 &Divine Perfection\\
10th &+10/+5 &+7 &+7 &+7 &Enlightenment: Eschew Worldly Possessions, Divine Dodge\\
11th &+11/+6/+6 &+7 &+7 &+7 &One Hand Clapping\\
12th &+12/+7/+7 &+8 &+8 &+8 &Shadow Run\\
13th &+13/+8/+8 &+8 &+8 &+8 &Weight of Thought, Speed: +20'\\
14th &+14/+9/+9 &+9 &+9 &+9 &Divine Meditation\\
15th &+15/+10/+10 &+9 &+9 &+9 &Enlightenment: We Are All Connected\\
16th &+16/+11/+11/+11 &+10 &+10 &+10 &Poetry in Motion\\
17th &+17/+12/+12/+12 &+10 &+10 &+10 &Zen Fist\\
18th &+18/+13/+13/+13 &+11 &+11 &+11 &Speed: +25', Formation of the Eight Trigrams\\
19th &+19/+14/+14/+14 &+11 &+11 &+11 &Deadly Finishing Move\\
20th &+20/+15/+15/+15 &+12 &+12 &+12 &Enlightenment: Transcendence, Secret Scroll \\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Sohei class.

\ability{Weapon and Armor Proficiency:}{Sohei are proficient with all Simple Weapons, All Polearms, Light Armor, Medium Armor, and Heavy Armor.}

\ability{Improved Unarmed Strike:}{The Sohei gains a natural Slam attack that deals 1d8 damage if Medium sized. This gains an enhancement bonus equal to one quarter of their level (round down), and can be used to make full attack actions if no other weapons are used.}

\ability{Divine Flurry:}{When making a Full Attack action with any weapon or combination thereof, the Sohei may make one additional attack, and all attacks are made at their highest attack bonus, however all of them take a crippling -2 penalty to hit.}

\ability{Unforeseen Strike:}{Those struck by the Attacks of Opportunity of the Sohei must make a Fortitude save (DC 10 + half the Sohei's HD + their Wisdom modifier) or be Stunned for 1 round.}

\ability{Virtuous Writings:}{The Sohei may cast spells from Divine scrolls as though they had the spells on their class list. Yes, even if a jerk of a Warlock takes a spell that isn't Divine (are there any that aren't on some obscure domain?) and makes a Divine scroll of it. Additionally, they may create scrolls of spells on the Cleric*, Good, Nobility, Oracle or Purification spell lists, as though a Cleric (with the listed domains) of a level equal to their Sohei level. Casting the spells are not required for this process.\smallskip
*Does not include [Evil] spells.}

\ability{Power Slide:}{If a 3rd level Sohei takes damage from an attack, she may allow herself to be flung backwards, thereby lessening the impact. She may make a Balance check with a DC equal to the damage inflicted and if she succeeds, she suffers only half damage. This is a skill check, not a Saving Throw, so abilities such as Evasion do not apply. She is moved away from the source of damage by 5' for every 5 points of damage (or part there of) negated in this way. If there is not enough space for her to move, she suffers a d6 of damage for each square not moved. If she passes through an occupied square, the Sohei would have to make a tumble check to avoid attacks of opportunity. \smallskip

If this ability is gained from another class, then the Sohei may choose to increase or decrease the total distance moved by 50\% (so a Power Slide that negated 12 points of damage can cause him to move 5', 10', or 15' at her choice).}

\ability{Speed:}{The Sohei gains an increasing enhancement bonus to Speed. This is reduced by 5 feet when wearing Medium Armour, or 10' when wearing Heavy Armor.}

\ability{Counter Attack:}{Enemies provoke attacks of opportunity from the Sohei whenever they make melee attacks against the Sohei's allies.}

\ability{Enlightenment: Perfect Understanding:}{The Sohei reaches a plateu of enlightenment and understanding. At this stage, they can never be Confused, and always know when a person is lying. Additionally, they can choose to automagically disbelieve illusions and can see the invisible.}

\ability{Super Gauge:}{Whenever the Sohei successfully strikes a foe or is struck by a foe, they gain a point of Tension against that foe. This lasts for a number of rounds equal to their Wisdom modifier, until they gain Tension against anyone else, until the foe they have Tension against is defeated or until used (whichever comes first).
\smallskip
5 Tension points may be spent to gain an additional melee attack as a Free Action or to Empower a spell being cast from a scroll. 10 points may be used to unleash a Super Move, a Full Attack where each hit deals an additional amount of damage equal to 5d6 plus the Sohei's BAB. It should be compulsory that the player shout out the name of the attack.}

\ability{Divine Go Stone Placement of Perfection:}{Whenever combat begins, before Initiative is actually rolled, the Sohei may freeze time for one round. In this time, the Sohei and their allies may each make a Move Action to get into superior positions. Initiative is then rolled, and combat resumes. They may also use this ability once per minute during combat as an Immediate Action.}

\ability{Divine Frenzy:}{Whenever someone deals damage to the Sohei, they may enter a Divine Frenzy. This lasts for as long as they have Tension, and during the effect they may act completely normally and use items normally - they can even cast spells if they have spellcasting ability from another class. The Divine Flurry gains another bonus attack, with every strike gaining +2d6 damage of any Energy Type, and the Sohei's Attacks of Opportunity may, at the Sohei's option, knock the targets away 5' per 5 damage dealt, in a straight line in the direction of their choice. This movement provokes Attacks of Opportunity, but not from the Sohei.}

\ability{C-C-C-COMBO BREAKER:}{Each foe is unable to successfully make more than one attack against each of the Sohei's allies during their turn, as long as the Sohei is not flat-footed. This includes spells and similar effects, as long as they are not Harmless, but does not include attacks of opportunity, as they do not take place during the foe's turn (unless they do, in which case they do count). For multiple-target or area effects, only the targets they already attacked are immune.\smallskip

Linked effects such as Improved Grab, the Trip ability of wolves and Poison will take effect as normal. Even taking continuing damage from an ongoing effect is fine. The enemies are free to take turns beating on the same guy, and one enemy splitting attacks up amongst the team is still fine, but one foe focusing their attacks on one target triggers this ability. For example, a Disintegrate followed by a Quickened Fireball will mean one guy gets hit for Disintegration, and everyone else takes the fire damage. \smallskip

The ally in question must be in a square the Sohei threatens, otherwise they are exempt from this effect.}

\ability{Divine Perfection:}{The Sohei becomes immune to Death Effects, Disease and Poison, and gains Spell Resistance equal to their Hit Dice + 5}

\ability{Enlightenment: Eschew Worldly Possessions:}{At this stage, the Sohei can create items worth up to 15,000 GP as per a Wish, at will, requiring only a minute of meditation. They also need not eat or drink. To use this ability, the Sohei must not own any currency or precious metals. Personal equipment is exempted from the restriction. This is a flavor thing, so use common sense.}

\ability{Divine Dodge:}{Once per minute, as an Immediate Action, the Sohei may suddenly move 10' away without provoking Attacks of Opportunity. If this brings the Sohei out of range for an attack that was about to be resolved, the attack automatically misses, likewise if it brings the Sohei out of the area of effect for a spell that was about to go off. \smallskip

It may be used again before the minute is up, at the cost of 10 Tension. However, this must be against an attack performed by the one who earned the Tension.}

\ability{One Hand Clapping:}{The Sohei cannot be Dazed, Deafened or Stunned. Additionally, their unarmed strikes deal +2d6 Sonic damage when they strike, and by spending 10 Tension as a Swift action, they may cause each blow to unleash a Sonic Pulse: all enemies within 10' take 1d6+BAB Sonic damage (no save), and the foes actually struck must pass a Fortitude save at the end of the Sohei's turn or be knocked Prone, Deaf and Paralyzed for 1d4 rounds. \smallskip

Furthermore, if an ally provokes an Attack of Opportunity, and is in a square the Sohei threatens, they may educate the ally in the wisdom of not provoking, by smacking them upside the head. This uses a single Attack of Opportunity but has no effect on the ally. However, no enemy may take an Attack of Opportunity against the ally for that action.}

\ability{Shadow Run:}{The Sohei can step onto the Ethereal Plane, and thus may walk on water or, for that matter, thin air as long as they end their turn standing on something solid. It can be a flimsy tree branch or a bamboo pole, mind you, as long as it is a solid object. Furthermore, they may step through Walls of Force, treating them merely as 10' movement per wall, and can add their Intelligence modifier to their Initiative.}

\ability{Weight of Thought:}{The Sohei may subtract their Wisdom modifier from armour penalties. If this reduces the penalty to zero, then they may move as if unarmoured, including being able to run at full speed in Heavy armour and tumble and everything.}

\ability{Divine Meditation:}{If the Sohei spends one minute meditating, they gain insight into future events, and may add a +10 Insight bonus on the next d20 roll they make. Additionally, doing so lets them regain Hit Points equal to the sum of all of their ranks in Knowledge skills.}

\ability{Enlightenment: We Are All Connected:}{The Sohei gains an even greater understanding of life, and how hatred is a weapon we forge for others that only hurts ourselves, that the air they exhale is inhaled by their enemies, and that everything is linked together.\smallskip

Any beneficial spell or effect granted to the Sohei or any of their allies they can see is instead, at the Sohei's option, granted to the Sohei and any number of their allies they can see. Additionally, any foe who subjects the Sohei (or any ally the Sohei can reach) to an ongoing condition such as Poison, Disease, Fear, Blindness or Nausea must make a Will save (DC 10 + half the Sohei's Hit Dice + their Wisdom modifier) or also receive the same affliction, for the same duration.}

\ability{Poetry in Motion:}{The Sohei may make a Move Action in addition to any other actions they perform in a turn. This movement may be broken up so as to walk around while making a Full Attack. Additionally, the Sohei counts as being in every square they move through until their turn is over, allowing them to flank with themselves and knock enemies past herself to provoke attacks of opportunity.}

\ability{Zen Fist:}{The actions of the Sohei cannot be interrupted by Immediate Actions, readied actions or attacks of opportunity. Instead, the Sohei declares their intent (such as "to make three attacks against the Hobgoblin Warlord and three against its Dragon mount"), the dice are rolled, and no attacks are actually made. However, at the end of the Sohei's turn, the targets have been attacked, actions performed and so on, just without there being a moment in time in which the actions were made. If you are confused by this, you're not Zen enough. \smallskip

Additionally, they may elect to move as by teleporting - the journey has been made without a single footstep having fallen. Doing this, however, does not allow for Poetry in Motion.}

\ability{Formation of the Eight Trigrams:}{Whenever the Sohei uses the Divine Go Stone Placement of Perfection ability, they form a strong barrier of defence with their allies. Draw an imaginary line between every pair of allies, including the Sohei. These form Walls of Force for one round, and are filled with Acid Fog that does not affect the Sohei or their allies. \smallskip

Additionally, the Sohei and their allies gain the benefits (but not the drawbacks) of a Stoneskin effect for one round. Any foe who attacks the Sohei or any of her allies during this time but fails to deal any damage automatically becomes Exhausted for one minute. In this case, allies are only those within 50' of the Sohei, not those back home in Kansas.}

\ability{Deadly Finishing Move:}{By spending 20 Tension as a Standard Action, the Sohei may unleash a killer Destroyer move. This attack deals an additional 2d6 damage per Hit Die of the Sohei, and bypasses all Damage Reduction (?including /-) and Regeneration. \smallskip

It also deals Strength Damage equal to the Sohei's Wisdom modifier, and the target must make either a Fortitude save or a Will save (Sohei's choice) or be slain instantly and completely destroyed. Not even ashes remain, and the soul is transported to the centre of the planet, on another plane (probably Hell). \smallskip

It should be mandated that the player name this move and either shout it out before unleashing it, or quietly state the name after the effects take place.}

\ability{Enlightenment: Transcendence:}{The Sohei is no longer a normal mortal creature. They become Ageless, and can only die by being killed. However, they are so hardcore they wouldn't die even if you killed them: they rise again 24 hours later unless the body is hacked apart and burned, the ashes then scattered into an Unhallowed land.}

\ability{Secret Scroll:}{The Sohei writes out the secret scrolls to enlightenment and, as they no longer have any goals of their own, having reached transcendence, must now strive to lead others to the door of knowledge. Anyone who reads the scrolls gains a permanent +5 Inherent bonus to Wisdom (the Sohei gains this when writing the scrolls), however from this point on they take a -5 penalty to hit the Sohei, due to having been influenced enough that the Sohei can predict their every move.}
