\classname{Warlock} \label{comm:class:spherelock}
\vspace*{-8pt}
\quot{"I have all the powers of Hell at my disposal. Who are you to question me?"}

\desc{Some people want power, and are crazy enough to offer their soul to various not nice people to get it. Others are simply (un)lucky enough to be descendants of those same people. However they managed to get their abilities, Warlocks wield the powers of the lower planes, which include powerful magic spells and the ability to shoot hellfire out of their hands.}

\ability{Alignment:}{Warlocks who bargain away their souls for power tend to be Evil, though nothing requires them to be. In fact, demons and devils will jump on the chance to corrupt someone Good to Team Evil, but such instances are rare. People whose power comes from their blood can be any alignment.}

\ability{Races:}{Warlocks can be any non-Outsider. Actual Outsiders don't bargain away their souls because they already have the ability to use the powers they would get, and that is represented by them having access to classes like \hyperref[class:truefiend]{True Fiend} or \hyperref[class:conduit]{Conduit of the Lower Planes}. However, a Warlock who later becomes an Outsider can still be a Warlock.}

\ability{Starting Gold:}{4d4x10 gp (100 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Warlock's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Disguise (Cha), Hide (Dex), Intimidate (Cha), Knowledge (all, taken individually) (Int), Listen (Wis), Move Silently (Dex), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Use Magic Device (Cha).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+2 &+2 &Sphere, Eldritch Blast\\
2nd &+1 &+0 &+3 &+3 &Fiendish Similarities\\
3rd &+2 &+1 &+3 &+3 &Sphere\\
4th &+3 &+1 &+4 &+4 &Call Fiends\\
5th &+3 &+1 &+4 &+4 &Hellfire Blast\\
6th &+4 &+2 &+5 &+5 &Sphere\\
7th &+5 &+2 &+5 &+5 &Damage Reduction\\
8th &+6/+1 &+2 &+6 &+6 &Bonus Feat\\
9th &+6/+1 &+3 &+6 &+6 &Sphere\\
10th &+7/+2 &+3 &+7 &+7 &Dark Blast\\
11th &+8/+3 &+3 &+7 &+7 &Fiendish Servant\\
12th &+9/+4 &+4 &+8 &+8 &Sphere\\
13th &+9/+4 &+4 &+4 &+8 &Energy Resistance\\
14th &+10/+5 &+4 &+9 &+9 &Fear Aura\\
15th &+11/+6/+6 &+5 &+9 &+9 &Sphere, Fiendish Apotheosis
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Warlock class.

\ability{Weapon and Armor Proficiency:}{Warlocks are proficient in light armor, shields (but not great shields), and simple weapons.}

\ability{Sphere:}{A Warlock gains basic access to a \hyperref[spheres]{sphere} at every third level. If the Warlock selects a sphere that he already has basic access to, he upgrades it to advanced access. If he already had advanced access, he gains expert access.}

\ability{Eldritch Blast (Su):}{As an attack action, a Warlock may fire a blast of fire at his foes. This has a range of Close (25 feet +5 ft./2 levels), does 1d6 damage per level of Warlock, and requires a ranged touch attack to hit.}

\ability{Fiendish Simularities}{A 2nd level Warlock may qualify for and take feats with the \hyperref[feats:fiend]{[Fiend]} or \hyperref[feats:necromantic]{[Necromantic]} tag, as long as he meets the other requirements. For [Necromantic] feats, he may use his character level as his caster level.}

\ability{Call Fiends (Sp):}{At 4th level, a Warlock can Summon an Outsider with the [Evil] subtype once per day, as long as the Outsider's Challenge Rating is 3 less than his character level or lower. He can also choose to double the number of creatures summoned by reducing the max CR of the creatures by 2 per doubling (a 9th level Warlock could summon one CR 6 fiend, two CR 4 fiends, 4 CR 2 fiends, or 8 CR 1 fiends). This is treated as a spell of one half the Warlock's level, rounded down, with a caster level equal to his levels in Warlock.}

\ability{Hellfire Blast (Su):}{At 5th level, a Warlock may choose to fire a blast of hellfire instead of normal fire, at the cost of 2d6 points of damage (i.e. a 5th level Warlock could use a 5d6 fire blast or a 3d6 hellfire blast). This blast bypasses fire resistance and deals half damage to creatures with fire immunity.}

\ability{Damage Reduction (Ex):}{At 7th level, a Warlock gains damage reduction equal to one half his class level, rounded up. This damage reduction is bypasses by whatever material is baneful to the Warlock's fiendish patron or ancestor (silver for Baatezu, wood for Yugoloths, stone for Demodands, and iron for Tanar'ri) or Good aligned weapons. At 13th level, it is bypassed only by one of those, which the Warlock chooses upon taking the level. If a Warlock later takes levels in \hyperref[class:truefiend]{True Fiend}, the damage reduction stacks and, at the third level of True Fiend, is bypassed only by weapons that are both Good and made of a baneful substance.}

\ability{Bonus Feat:}{At 8th level, a Warlock gains one bonus feat, which can be any \hyperref[feats:fiend]{[Fiend]} feat he qualifies for.}

\ability{Dark Blast (Su):}{At 10th level, a Warlock may choose to change the damage of his Eldritch Blast to Unholy damage by reducing the damage it deals by 4d6 (a 10th level Warlock could opt to fire a 10d6 fire blast, 8d6 hellfire blast, or 6d6 unholy blast).}

\ability{Fiendish Servant:}{An 11th level Warlock is followed by a cohort whose CR is 2 less than his level, but the cohort can only have levels in True Fiend, Fiendish Brute, or Conduit of the Lower Planes (they can also have racial hit dice).}

\ability{Energy Resistance:}{At 13th level, a Warlock gains resistance 10 to two energy types of his choice, and resistance 5 to a third.}

\ability{Fear Aura (Su):}{At 14th level, a Warlock can radiate a 20 foot aura of \spell{fear} (as per the spell) at will with a caster level equal to his character level. Save DC is 10+1/2 HD+Cha modifier.}

\ability{Fiendish Apotheosis:}{A 15th level Warlock becomes an Outsider with the [Evil] subtype, even if his own alignment is not evil. He is immortal and does not age. This allows him to qualify for the Fiend classes, which can be used to fill out his last 5 levels.}
