\classname{Storm Lord} \label{class:stormlord}
\vspace{-8pt}
\quot{"My fury will leave you soaking wet."}

\desc{A Storm Lord is really in touch with the primal power of a big ass storm. He can channel it into baddassery. Storm Lords are more prevalent in races that deal with storms. Storms take many forms, and Storm Lords can be in touch with some or all of them, and may prefer one type to another.}

\ability{Alignment:}{Storm Lords can be any alignment, but most strongly favor chaos over order. Doesn't stop Bob the Stormlord from talking about how Storms are really nature putting shit back into it's proper place though. (And see Tome of Trees, that's actually what Nature is doing.) }

\ability{Starting Gold:}{5d4x10gp  (125 gold)}

\ability{Starting Age:}{As Sorceror.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Storm Lord's class skills (and the key ability for each skill) are Balance (Dex), Concentration (Con), Disable Device (Int), Escape Artist (Dex), Handle Animal (Cha), Knowledge (Nature) (Int), Listen (Wis), Sense Motive (Wis), Spellcraft (Int), Ssurvival (Wis), Swim (Str), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st  &+0          &+2 &+2  &+0 & Call of the Storm, Angry Hands, Approaching Doom \\
2nd  &+1          &+3 &+3  &+0 & Inevitable Tide, Storm Hound, Winds of Change \\
3rd  &+2          &+3 &+3  &+1 & Loud Noises, Blown Away, Lightning Bolt \\
4th  &+3          &+4 &+4  &+1 & Storm Immunities, Windwall \\
5th  &+3          &+4 &+4  &+1 & Majesty, Storm Hound (Fog) \\
6th  &+4          &+5 &+5  &+2 & Long Arm of the Storm, Rain Season \\
7th  &+5          &+5 &+5  &+2 & Dust Storm, Sleet Storm \\
8th  &+6/+1       &+6 &+6  &+2 & Lightning is My Middle Name, Increased Approaching Doom \\
9th  &+6/+1       &+6 &+6  &+3 & Control Weather, Swift Winds \\
10th &+7/+2       &+7 &+7  &+3 & Storm Hound (Winds), Wind Walk \\
11th &+8/+3       &+7 &+7  &+3 & Eye of the Storm, Share the Storm \\
12th &+8/+3       &+8 &+8  &+4 & Control Winds \\
13th &+9/+4       &+8 &+8  &+4 & Earthquake, Wall of Lightning \\
14th &+10/+5      &+9 &+9  &+4 & Tornado \\
15th &+11/+6/+6   &+9 &+9  &+5 & Storm Hound (Solid Fog) \\
16th &+12/+7/+7   &+10 &+10 &+5 & Tsunami \\
17th &+12/+7/+7   &+10 &+10 &+5 & Tornado Accompaniment \\
18th &+13/+8/+8   &+11 &+11 &+6 & Let the World Weep \\
19th &+14/+9/+9   &+11 &+11 &+6 & Storm Hound (Control Winds) \\
20th &+15/+10/+10 &+12 &+12 &+6 & Captain Planet \\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the storm lord.

\ability{Weapon and Armor Proficiency:}{Storm Lords are proficient with Tridents, Simple Weapons, Martial Weapons, and Anything made out of Lightning. They are also Proficient with Light Armor.}

\ability{Call of the Storm (Su):}{A Storm Lord may cast \spell{message}, \spell{sending}, \spell{whispering wind}, and \spell{ghost sound} as SLAs at will. He also treats anything with the [Earth], [Water], [Air], or [Electricity] descriptors as being on his class list for the purposes of items.}

\ability{Angry Hands (Su):}{As an attack action the Storm Lord throws Lightning from his fists. This is a Ranged Touch Attack within Short Range. It strikes for 1d4 Lightning Damage per Storm Lord level and \condition{entangles} the target until the end of your next turn.}

\ability{Approaching Doom (Sp):}{The Storm Lord may cast \spell{omen of peril} at will.}

\ability{Inevitable Tide (Ex):}{\spell{freedom of movement} does not apply to wind effects regardless of if your DM thinks it does, or you do. The Storm Lord's wind effects still limit your movement anyway. Deal. Also, Storm Lords have weathered the most terrible of storms, and aren't afraid of that crap. They are immune to fear.}

\ability{Storm Hound (Su):}{The Storm Lord is followed by a piece of wayward storm. This is an Obscuring Mist effect that moves 100 ft per round as directed by the Storm Lord. It can be directed as a free action, and dismissed, recalled, or both with a full round action. It can never be more than medium range away from the Storm Lord, and he cannot direct it if he does not have line of effect to some part of it. The Storm Hound is immune to any wind affect created by the Storm Lord, but if dispersed through another wind affect, is treated as dismissed. You may recall any level of Storm Lord you like, as long as you have reached that level.}

\smallskip\noindent At level 5 this becomes a Fog Cloud.

\smallskip\noindent At level 10 a 20 ft radius patch of wind blowing either inward or outward at Windstorm Speed (Use saving throw of 10 + \half level + Wisdom modifier).

\smallskip\noindent At level 15 a Solid Fog effect.

\smallskip\noindent At level 19 a Control Winds effect at CL = Storm Lord Level. Its radius can be changed with a full round action.

\ability{Winds of Change (Ex):}{The Storm Lord has winds whip around him, granting a +4 deflection bonus to AC and Reflex saves that increases by 1 every 3 levels (5 at 4th, 6 at 7th, ect.).}

\ability{Loud Noises (Su):}{The Storm Lord may cause whipping wind to become very loud in a 20 ft radius at medium range. This forces a fort save (10 + \half level + Wisdom modifier) against deafness and does 2d6 Sonic damage. At level 10 a failed save also results in being stunned for 1 round.}

\ability{Blown Away (Su):}{The Storm Lord may use \spell{gust of wind} as an immediate action.}

\ability{Lightning Bolt (Sp):}{The Storm Lord may use \spell{lightning bolt} as an at will SLA at CL equal to his character level. The save DC is 10 + \half level + Wisdom mod, and there is no damage dice cap.}

\ability{Storm Immunities (Ex):}{A Storm Lord becomes immune to Sonic, Electricity, and all effects outlined under the heading "Weather" in the DMG. This includes being able to see through weather effects such as Sleet, Fog, etc, including his own. This applies even if created by a spell, but does not apply to spell effects not outlined in the DMG, such as the Solid part of a Solid Fog spell.}

\ability{Wind Wall (Sp):}{The Storm Lord may use \spell{wind wall} as an SLA at CL = Storm Lord Level at will. Saving throw of 10+\half level+Wis mod.}

\ability{Majesty (Su):}{The Storm Lord flies on the winds that whip around him. He flies at average maneuverability with a speed of 40ft. He may also use \spell{Telekinesis} at will but only Sustained Force and Combat Maneuver, using his Wisdom modifier for combat maneuver and a DC of 10 + \half level + Wis mod for sustained force.}

\ability{Long Arm of the Storm (Ex):}{Both Loud Noises and Angry Hands extend to Long range. His Gust of Wind and Lightning Bolt SLAs double their range.}

\ability{Rain Season (Su):}{The Storm Lord can make it Rain in a 100 mile radius emanation. He can make it keep raining forever. The emanation is always centered on him. He can also stop making it rain at will.}

\ability{Sleet Storm (Sp):}{As the spell, at will, save DC is 10 + \half level + Wis mod, CL = Storm Lord level.}

\ability{Dust Storm (Su):}{A Raging Dust Storm is manifested in a 60ft Cone in front of the Storm Lord. It does 1d6 Slashing Damage per Storm Lord level, Ref save for half (10 + \half level + Wis mod). The dust lingers in the air, mimicking the effects of Solid Fog for one round.}

\ability{Lightning is My Middle Name (Su):}{The Storm Lord can use \spell{Chain Lightning} as an SLA at CL = Storm Lord level at will. Unlike the spell, it offers no saving throw, does not halve damage on successive targets, and has no dice cap.}

\smallskip\noindent Additionally, all Storm Lord powers that do electricity damage bypass all resistance and do half damage to immune creatures. And Lightning Bolt no longer offers a save.

\ability{Improved Approaching Doom: Electric Boogaloo (Su):}{The Storm Lord may sit down and meditate for an hour, during which lots of electricity crackles around him. At the end of this hour, he obtains an answer to one question as the \spell{Divination} spell with CL = Storm Lord level. He may do this a number of time per day equal to his Wisdom mod.}

\ability{Control Weather (Sp):}{\spell{Control Weather}, as the spell, at will SLA. CL = Storm Lord level. Wisdom based. DC 10 + \half level + Wis. the usual. The same is true of all future SLAs.}

\ability{Swift Winds (Ex):}{\spell{Gust of Wind} increases to Wind Storm level winds. \spell{Wind Wall} becomes an immediate action. \spell{Telekinesis} becomes a swift action, and maintaining it is also a swift action. Also, the Storm Lord's fly speed increases to 120 ft, and his maneuverability increases to perfect.}

\ability{Wind Walk (Sp):}{As the spell, Wisdom, CL yadda.}

\ability{Eye of the Storm (Su):}{As a standard action, a Storm Lord can lock someone in a whirling vortex. They are paralyzed for one round per level. Reflex save to avoid. He can also use \spell{Wind Wall} to wrap himself in protection, and have it move with him.}

\ability{Share the Storm (Su):}{By performing a ritual of anointment, the Storm Lord can bless up to five creatures at a time. If he blesses a sixth, the first loses it. The ritual lasts about one hour. Those so blessed gain all the advantages of the Storm Lords "Storm Immunities" class ability. Also, he gets a +7 Fuck You RNG bonus to checks to overcome spell resistance, dispel checks against things he made exist, and anything involving someone trying to control a magic effect that he has control over.}

\ability{Control Winds (Sp):}{\spell{Control Winds}, SLA, as the spell, DC 10+\half level+Wis mod. CL = character level.}

\ability{Earthquake (Sp):}{\spell{Earthquake}, SLA, as the spell, DC 10 + \half level + Wis mod. CL = character level.}

\ability{Wall of Lighting (Sp):}{The Storm Lord may summon a wall of lightning within medium range that lasts for 1 minute per Storm Lord level. It fills four 5ft squares per Storm Lord level. It blocks line of sight and line of effect. Any creature or object attempting to enter the wall or move within it must make a DC 10 + \half level + Wis mod reflex save to time their movement. A failure deals 10 Electricity damage per Storm Lord level, and they lose whatever action they used to move. Success allows them to move freely for that round at half speed. CL equals Storm Lord level.}

\ability{Tornado (Sp):}{As a standard action, the Storm Lord can summon a Tornado that lasts for 1 round per Storm Lord level within medium range. It is at CL = Storm Lord level and the Save DC is 10 + \half level + Wis mod. The effect is a 40 ft radius Whirlwind as the Air Elemental Special ability. It does 1d4 damage per two Storm Lord levels.}

\ability{Tsunami (Sp):}{Storm Lords summon big ass walls of water. Everyone in the area of effect (a Cone out to Long Range) gets fucked up for 400 bludgeoning damage, and knocked prone. A successful reflex save of DC 10 + \half level + Wis mod halves damage and negates the prone condition. The Tsunami also does double damage to objects and automatically bypasses hardness. CL = Storm Lord level.}

\ability{Tornado Accompaniment (Su):}{In addition to summoning Tornadoes, the Storm Lord can totally fucking be a dick and have a Tornado that surrounds him at all times and doesn't cost any actions.}

\ability{Let the World Weep (Sp):}{The Storm Lord may cast \spell{Storm of Vengeance} at will as an SLA, same stuff as usual applies. He may also be more badass, and summon a Storm of Please Die, which is just like his Rain Season ability except the effects are:}

It is either in the lowest or highest possible temperature band everywhere, and it changes daily.
Every volcano is constantly erupting.
Some kind of precipitation is falling, and it covers the ground and probably most buildings.
Winds never decrease below Severe.
Earthquakes occur randomly.
Any Ocean boils, and occasionally sends of giant raging tsunamis of boiling water.

\ability{Captain Planet (Rl):}{Having mastered the powers of Earth, Wind, Water, and Fire, you must now master the power of Heart. Your character is retired, and you may not create another one until you go out and get a girlfriend. If you already have a girlfriend, you get another one at no charge.}