\classname{Swashbuckler} \label{class:swashbuckler}
\vspace{-8pt}
\quot{"Yes, I'm a pirate. No I don't have a fucking copy of Spore."}

\ability{Alignment:}{Any}

\ability{Starting Gold:}{8d4x10 gp (200 Gold)}

\ability{Starting Age:}{As Rogue}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The swashbucklers's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Disable Device (Int), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Intimidate (Cha), Jump (Str), Knowledge (Your Mum, in the Biblical sense) (Int), Spot (Wis), Survival (Wis), Tumble (Dex), Use Rope (Dex)}

\ability{Skill Points at 1st Level:}{(6 + Int modifier) x 4}

\ability{Skill Points at Each Additional Level:}{6 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st  &+1              &+0 &+2  &+0 & Fencing, Your Opponent is Me! \\
2nd  &+2              &+0 &+3  &+0 & Combat Climbing, Tie-Down \\
3rd  &+3              &+1 &+3  &+1 & Acrobatic Charge, Stylish Hat \\
4th  &+4              &+1 &+4  &+1 & I'm Not Left Handed, Combat Sidle \\
5th  &+5              &+1 &+4  &+1 & Power Slide, Constant Cover \\
6th  &+6/+1           &+2 &+5  &+2 & Evasion, Close Quarters Fighting \\
7th  &+7/+2           &+2 &+5  &+2 & Distraction, Ridiculous Attire \\
8th  &+8/+3           &+2 &+6  &+2 & I Had Three Knives, Death Parrot \\
9th  &+9/+4           &+3 &+6  &+3 & Master of Escape, Whirlwind \\
10th &+10/+5          &+3 &+7  &+3 & Witty Repartee, Thrice Keelhauled \\
11th &+11/+6/+6       &+3 &+7  &+3 & Control Ropes and Rigging \\
12th &+12/+7/+7       &+4 &+8  &+4 & Dread Pirate Tales, Legendary Booty \\
13th &+13/+8/+8       &+4 &+8  &+4 & Arm's Length, Catch Me If You Can \\
14th &+14/+9/+9       &+4 &+9  &+4 & Menacing Visage, En Garde! \\
15th &+15/+10/+10     &+5 &+9  &+5 & Foil Action, Rapier Wit \\
16th &+16/+11/+11/+11 &+5 &+10 &+5 & Razor Wind \\
17th &+17/+12/+12/+12 &+5 &+10 &+5 & Razor's Edge \\
18th &+18/+13/+13/+13 &+6 &+11 &+6 & Bladestorm \\
19th &+19/+14/+14/+14 &+6 &+11 &+6 & One More Thing \\
20th &+20/+15/+15/+15 &+6 &+12 &+6 & The Immortal Dread Pirate Lives On! \\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the swashbuckler. 

\ability{Weapon and Armor Proficiency:}{Swashbucklers are proficient with all simple weapons, all martial weapons, one exotic weapon of the players choice, and all light armors.}

\ability{Fencing (Ex):}{Swashbucklers are good at keeping themselves safe from injury. Once per round, as a Not An Action, a Swashbuckler may make a melee attack roll when attacked. If the Swashbuckler rolls higher, the attack is parried and she is safe from harm. This does not work in heavy armour.}

\ability{Your Opponent Is Me! (Ex):}{You have to pay attention to a Swashbuckler when fighting her, as even losing concentration for a moment will mean your kidneys get turned into kebabs. Whenever the Swashbuckler successfully strikes a foe in melee combat on her own turn, they must either successfully attack her or take the Full Defence Action before her next turn. Otherwise, when she attacks, she treats them as flat-footed and deals bonus damage equal to three times her class level per hit.}

\ability{Combat Climbing (Ex):}{The Swashbuckler gains a Climb speed equal to her land speed, along with all the benefits. She needn't even hang on with her hands, and can fight just fine hanging upside-down. When she fights while climbing, enemies who lack a Climb speed take a -4 penalty to strike her, due to being unaccustomed to such a fighting style. This does not work in any armour heavier than light.}

\ability{Tie-Down (Ex):}{it's hard to move about when fighting a swashbuckler. Anyone she strikes in melee combat during her turn must make an Escape Artist check, opposed by her attack roll. If they fail, they are treated as Entangled until the start of her next turn. If they fail by 10 or more, they are also unable to move around (but can still act, they just can't move from one square to another).}

\ability{Acrobatic Charge (Ex):}{With a DC 15 Tumble or Balance check (her choice), the Swashbuckler can charge in a zig-zag or curve, ignoring hazards lying in the path. This ability does not work in heavy armour or when heavily encumbered.}

\ability{Stylish Hat (Ex):}{Pirates wear stylish hats. This grants a +4 "You're Shitting Me" bonus on Bluff, Diplomacy, Gather Information and Perform checks. Furthermore, if she throws the hat (a Swift action), everyone paying attention to her (foes in squares she threatens or vice versa) must make a Reflex save (Charisma-based) or lose their concentration for a moment, provoking an Attack of Opportunity.}

\ability{I'm Not Left Handed (Ex):}{The Swashbuckler gains the benefits of the Two Weapon Fighting feat. If she already has this feat, or gets it later, she gains the ability to use the Fencing parry at the cost of an Attack of Opportunity (even if the foe does not provoke - this just limits the number of parries or AoOs that could be used per turn).}

\ability{Combat Sidle (Ex):}{Once per round, when a foe starts in a square she threatens and makes a 5' step, the swashbuckler may move as well, to keep up with the foe. Additionally, her normal 5' steps become 10' steps, and can be increased to 15' with a DC 25 Balance check.}

\ability{Power Slide (Ex):}{Just like the Jester/Thief-Acrobat ability. Does not work in heavy armour or when heavily encumbered.}

\ability{Constant Cover (Ex):}{There is always some kind of cover to protect the swashbuckler. She benefits from 1/4 cover at all times, unless there is more cover, in which case she uses that instead. With a DC 35 Tumble check as an Immediate action, she can increase this to 1/2 cover for the duration of the attack she interrupts.}

\ability{Evasion (Ex):}{If a 6th level swashbucker succeeds in a Reflex Save to halve damage, they suffer no damage instead. This ability does not work if heavily encumbered or wearing medium or heavy armour.}

\ability{Close Quarters Fighting (Ex):}{Swashbucklers can fight normally when grappled or pinned, and do not lose their Dex bonus to AC. Effectively it's like not being grappled, except she can still be chokeslammed. Additionally, she can fight without penalty in cramped conditions. These abilities do not work when wearing medium or heavy armour.}

\ability{Distraction (Ex):}{If someone is in a square the swashbuckler threatens, then she is considered to be flanking them, no matter what direction an attack comes from. Additionally, whenever she strikes a foe, she gains the Edge against them until they strike her.}

\ability{Ridiculous Attire (Ex):}{All pirates, by law, are required to dress in a ridiculous manner, with the exception of female pirates, who must dress both ridiculous and sexy. At either rate, enemies have a hard time actually taking their garb seriously. During the first round of combat, as well as the surprise round if there is one, all foes take a penalty to attack rolls equal to the swashbuckler's Charisma modifier.}

\ability{I Had Three Knives (Ex):}{Swashbucklers always have another weapon. They gain a special "Other weapon" attack in melee combat, unless very carefully searched beforehand, involving 10 minutes, rubber gloves and a Search check (DC 25 + Swashbuckler's level + her Dex mod). This attack is made at her highest attack bonus, and deals damage as a +1 dagger, though it always catches foes flat-footed. This becomes a +1 Keen weapon at level 12, a +2 Keen weapon at level 16, and a +2 Keen Wounding weapon at level 20. As if you cared. The weapon can not be pulled out and used when wearing medium or heavy armour.}

\ability{Death Parrot:}{The swashbuckler gains a parrot as an animal companion. If it dies, another takes its place the next day. Use the stats for a raven, except that it gains +3d6 Sneak Attack damage and a special Rake attack that deals 2d4 damage and, on a critical hit, permanently Blinds the target. It has Improved Evasion when sharing the swashbuckler's square.}

\ability{Master of Escape (Ex):}{The swashbuckler can never be pinned down. Any Escape Artist check may be made as a Standard action that does not provoke, and she may make Epic checks at the following DCs: Extremely Tight Space (a chimney, a glass jar, someone's anus) DC 30, Walls of Force DC 40 or Caster Level + 5, whichever is higher. She also gains a +8 bonus to escape a grapple. None of this applies when wearing heavy armour or when heavily encumbered.}

\ability{Whirlwind:}{The swashbuckler Whirlwind as a bonus feat. If she already has this feat she may select another [Combat] feat instead.}

\ability{Witty Repartee (Ex):}{When making a melee attack, as long as she can speak, the swashbuckler can utilise Witty Repartee. A single foe must be designated, and attacks against this foe receive additional damage equal to a Bluff check (make the check once at the start of the round). The opponent can only nullify this by making a higher Bluff check than her original one.}

\ability{Thrice Keelhauled (Su):}{Pirates are used to being keelhauled, it's a hobby to them. The Swashbuckler can breathe underwater and on land, and gains a Swim speed equal to double her land speed, along with all the usual benefits. While in the water, when fighting foes who do not have a Swim speed - even if they are on land - she always has the Edge.}

\ability{Control Ropes and Rigging (Su):}{Every swashbuckler carries a stout rope some 50 feet long that entangles opponents of any size as an animate rope spell (caster level 16th). A swashbuckler can hurl its rope 30 feet with no range penalty. .}

\ability{Dread Pirate Tales (Ex):}{Word has spread of the terrors of the swashbuckler. When a swashbuckler makes it known who she is, she may immediately make an Intimidate check against everyone within 60'. Against those who would be merely impressed, she may make a Diplomacy check instead. Any person can only be targeted once per day by this.}

\ability{Legendary Booty (Ex):}{Whenever there's treasure, someone knows about it, and it's usually the treasure hunter that does. Whenever the issue of a particular cache of treasure or legendary item is raised, the swashbuckler may make a check to remember tales of its location: roll 1d20 + class level + Int mod, against a DC of 10 (mundane treasure you don't care about at this level), 20 (minor magic items), 25 (good stuff for your level) or 30 (artefacts, plot items and crazy-good items).

Additionally, many swashbucklers have legendary booty of another kind, if you know what I mean. Everyone wants to plunder this booty, if you know what I mean. As long as she wears tight-fitting pants (or foregoes them), foes of a swashbuckler are subject to Fascination if they fail a Will save (CHA-based). This lasts until she leaves their sight or someone attacks them. Those who would find her physically unattractive (pre-established criteria aside, assume every NPC is straight and easy) or who also have this ability gain a +4 bonus to the save. Those who meet both requirements or are around her on a daily basis are immune.}

\ability{Arm's Length (Ex):}{The swashbuckler is good at holding people at sword-point. Entering a square she threatens provokes attacks of opportunity from her, subject to all the same conditions as leaving a threatened square. If the AoO hits by more than 5, the target is forced back.}

\ability{Catch Me If You Can (Ex):}{The swashbuckler gains a +10' Enhancement bonus to all movement speeds when wearing Light or no armour, and only lightly encumbered. Additionally, with a Partial action she may gain the benefits of Freedom of Movement for one full round.}

\ability{Menacing Visage (Su):}{It's not that the pirate necessarily looks scary, but her reputation is so fierce that people associate her face with terror. When she reveals her face to enemies, they must make a Will save (CHA based) or Panic for 1d4 rounds, then Cower for a number of rounds equal to her Charisma modifier. Once someone passes the save, they are immune for 24 hours.}

\ability{En Garde! (Ex):}{Swashbucklers are amazing at duelling with their foes. Whenever they successfully strike a flat-footed, they must make an opposed BAB+Dex check or drop their weapons (or anything else they are carrying). They then grant her the Edge for the rest of the encounter.}

\ability{Foil Action (Ex):}{At 15th level a swashbuckler may attempt to monkeywrench any action an opponent is taking. The swashbuckler may throw sand into a beholder's eye, bat aside a key spell component, or strike a weapon hand with a thrown object, but the result is the same: the opponent's action is wasted, and any spell slots, limited ability uses, or the like used to power it are expended. A swashbuckler must be within 30 feet of his opponent to use this ability, and must hit with a touch attack or ranged touch attack. Using Foil Action is an Immediate action. This ability does not work when wearing Heavy armour.}

\ability{Rapier Wit (Ex):}{When attacking a foe she has the Edge against and using Witty Repartee, the swashbuckler may make Bluff checks instead of Attack rolls, and enjoys a doubled threat range (which does not stack with Improved Critical or similar feats, but DOES stack with Keen).}

\ability{Razor Wind (Ex):}{When running at full speed, the swashbuckler may make a single attack roll and use this roll to make an attack against every single enemy she threatens at any point in the movement. Any foes who attempt Attacks of Opportunity but miss or are parried automatically fall prone. This cannot be done if encumbered at all or if wearing Medium or Heavy armour.}

\ability{Razor's Edge (Ex):}{Now, when foes leave themselves open to the extra damage from "Your Opponent is Me!," they take more damage than normal: five times her level, plus Strength damage.}

\ability{Bladestorm (Su):}{As a full round action, the Swashbuckler may make a full attack against each adjacent foe. Additionally, she gains a number of extra attacks against each foe equal to her Dexterity modifier minus the number of foes she is attacking (minimum zero). Foes who suffer the extra damage from "Your Opponent Is Me!" must, at the end of this action, make a Fort save (Dex-based) or be Stunned for one round.}

\ability{One More Thing (Ex):}{At the end of the swashbuckler's turn, make a note of every foe she successfully hit. She may make one additional attack against each of them, regardless of how often she hit any given target.}

\ability{The Immortal Dread Pirate Lives On! (Su):}{When killed, a swashbuckler continues to fight while dead. Feel free to continue tracking damage, but it doesn't actually do anything (and she gains a Hardness rating, being a dead body). After one minute, she reverts to actually being dead, but becomes a Ghost for free. Enjoy your capstone.}