\classname{Warmage}
\vspace{-8pt}
\quot{TACTICAL GENIUS!}

\desc{Wizards in general are pretty good on the battlefield. When it comes to killing lots of people at a time, casters excel at that if they feel like it. Not that a single great warrior can't hack through an army by the time everyone else has done their shoes up, but it's always the explosions of flame that people remember.}

\desc{But some casters are specifically designed for the battlefield. Not only do they call ordinance down, annihilating large numbers of people at a time, but they can also take care of the stuff that only the good commanders think of: food, drink, digging trenches, building fortifications, gathering intel, making the battlefield conditions perfect. When you need someone like that, you turn to the Warmage.}

\ability{Starting Gold:}{5d4x10 gp (125 Gold)}

\ability{Starting Age:}{As Wizard}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{}

\ability{Skills/Level:}{4 + Int modifier.}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+2 &+2 &Elemental Exchange (Fire and Cold), Spellcasting, Armored Casting\\
2nd &+1 &+0 &+3 &+3 &Create Water, Create Food\\
3rd &+1 &+1 &+3 &+3 &Purify Food and Drink\\
4th &+2 &+1 &+4 &+4 &Energy Effect\\
5th &+2 &+1 &+4 &+4 &Swift Cast 1/day, Elemental Exchange (Acid and Electricity)\\
6th &+3 &+2 &+5 &+5 &Limitless Spell Force\\
7th &+3 &+2 &+5 &+5 &Explosive Spell\\
8th &+4 &+2 &+6 &+6 &Energy Surge\\
9th &+4 &+3 &+6 &+6 &Weaken Defences, Elemental Exchange (Sonic)\\
10th &+5 &+3 &+7 &+7 &Swift Cast 2/day, Chain Spell\\
11th &+5 &+3 &+7 &+7 &Rallying Spell\\
12th &+6/+1 &+4 &+8 &+8 &Energy Blitz\\
13th &+6/+1 &+4 &+8 &+8 &Heroes Feast, Elemental Exchange (Force and Negative)\\
14th &+7/+2 &+4 &+9 &+9 &Instant Fortress\\
15th &+7/+2 &+5 &+9 &+9 &Swift Cast 3/day, Arcane Ordinance\\
16th &+8/+3 &+5 &+10 &+10 &Energy Mastery\\
17th &+8/+3 &+5 &+10 &+10 &Dimensional Fortress\\
18th &+9/+4 &+6 &+11 &+11 &Hellstorm\\
19th &+9/+4 &+6 &+11 &+11 &Dragonflight Bombardment\\
20th &+10/+5 &+6 &+12 &+12 &Swift Cast 4/day, Arcane Siege, Win\\
\end{tabular}
\end{small}
\end{table}

\begin{table}[htb]
\begin{small}
\noindent\begin{tabular}{lllllllllll}
 & \multicolumn{10}{c}{Warmage Spells Per Day}\\
 &0 &1 &2 &3 &4 &5 &6 &7 &8 &9\\
1 &4 &2 &- &- &- &- &- &- &- &-\\
2 &5 &3 &- &- &- &- &- &- &- &-\\
3 &6 &4 &2 &- &- &- &- &- &- &-\\
4 &6 &5 &3 &- &- &- &- &- &- &-\\
5 &6 &6 &4 &2 &- &- &- &- &- &-\\
6 &6 &6 &5 &3 &- &- &- &- &- &-\\
7 &6 &6 &6 &4 &2 &- &- &- &- &-\\
8 &6 &6 &6 &5 &3 &- &- &- &- &-\\
9 &6 &6 &6 &6 &4 &2 &- &- &- &-\\
10 &6 &6 &6 &6 &5 &3 &- &- &- &-\\
11 &6 &6 &6 &6 &6 &4 &2 &- &- &-\\
12 &6 &6 &6 &6 &6 &5 &3 &- &- &-\\
13 &6 &6 &6 &6 &6 &6 &4 &2 &- &-\\
14 &6 &6 &6 &6 &6 &6 &5 &3 &- &-\\
15 &6 &6 &6 &6 &6 &6 &6 &4 &2 &-\\
16 &6 &6 &6 &6 &6 &6 &6 &5 &3 &-\\
17 &6 &6 &6 &6 &6 &6 &6 &6 &4 &2\\
18 &6 &6 &6 &6 &6 &6 &6 &6 &5 &3\\
19 &6 &6 &6 &6 &6 &6 &6 &6 &6 &4\\
20 &6 &6 &6 &6 &6 &6 &6 &6 &6 &5\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Warmage class.

\ability{Weapon and Armor Proficiency:}{Warmages are proficient with all simple and martial weapons. Warmages are proficient with light armor and medium armor but not with shields of any kind.}

\ability{Spellcasting:}{The Warmage automatically knows every spell on their class list that they are a high enough level to cast. They cast spells spontaneously, without preparation. The ability score that determines their spellcasting is Intelligence. Unless stated otherwise, any Warmage class features that affect her spells will only affect those gained from Warmage levels, not other classes.}

\ability{Armored Casting:}{A Warmage casts arcane spells, but she is not affected by the arcane spell failure of any armor or shield she is proficient with. This ability only applies to her Warmage spells, if she is able to cast any other arcane spells, they are affected by arcane spell failure normally.}

\ability{Elemental Exchange:}{If a spell deals a specific type of energy damage (Acid, Cold, Electricity, Fire, Sonic, Force, Negative, Dessication), the Warmage can elect to swap it to Fire or Cold damage - later, more energy types become available. This is not an action and does not affect the spell in any other way, unless the spell has an energy descriptor, in which case it changes to match the new one (so you won't have a Cold Fireball being a [Fire] spell). This applies to any spells the Warmage can cast, not just her Warmage ones.}

\ability{Create Water (Sp):}{The Warmage can Create Water as a Spell-like ability at will. The Caster Level is equal to her class level.}

\ability{Create Food (Sp):}{The Warmage can Create Food as a Spell-like ability at will. This creates one pound of nutritious, if bland, non-descript food per class level and uses a Standard Action. Consider it the equivalent of a military MRE designed to keep for long times. Yeah, I can see you salivating already.}

\ability{Purify Food and Drink (Sp):}{The Warmage can purify food and drink as a Spell-like ability at will.}

\ability{Energy Effect:}{When casting spells that deal energy damage, a special effect occurs, based on the energy type:

\noindent\begin{tabular}{|l|l|}
\hline
Energy: &Effect:\\
\hline
Acid &the target becomes Sickened for 1d4 rounds\\
\hline
Cold &the target becomes numb, dropping whatever they are holding\\
\hline
Electricity &the target is momentarily shocked, becoming Staggered for 1 round\\
\hline
Fire &the target catches fire\\
\hline
Sonic &the target is Deafened for 1 minute\\
\hline
\end{tabular}

The effects only occur if the target is damaged. If a spell causes multiple damage types, only one effect can be chosen per target. Targets are entitled to a Fortitude save to negate this effect (DC 10 + half the Warmage's HD + her Int modifier). If the original spell allows a saving throw, then passing that save negates the effect instead of making someone roll two saves.}

\ability{Swift Cast:}{Once per day per five class levels, the Warmage can cast a spell as a Swift Action. This only applies to spells that can be cast as a full round or less, however it does not change the spell level or any other aspect. It DOES change the casting time, in the exact manner that I just stated.}

\ability{Limitless Spell Force:}{If a spell has effects that increase with caster level (one ray per 4 levels beyond 3rd, 1d6 per level, 2 targets per level etc.) and usually has a limit on this increase, ignore the limit: the effects increase with the Warmage's caster level indefinitely.}

\ability{Explosive Spell:}{When casting a damaging spell with an area of effect, the Warmage may elect to make it an Explosive spell. All targets who take damage must succeed on a Fortitude save or be sent flying. The DC is 10 + half the Warmage's HD + her Int modifier. They are hurled in the direction the spell struck them from, moving to the outer edge, and half the distance travelled again (so if they would need to move 10' to leave the area of effect they would be moved 10+5 = 15'. If they had to move 100' they would end up being knocked 150'), then land prone. If a solid barrier prevents their movement, they take 1d6 Bludgeoning damage for every 10' of movement denied. Yes, the Warmage may pinball people with a bouncing Lightning Bolt.}

\ability{Energy Surge:}{Even greater effects apply to Warmage spells that deal energy damage.

\begin{tabular}[h]{|l|l|}
\hline
Energy: &Effect:\\
\hline
Acid &The target takes 1d4 Str damage as their muscle tissue is eaten away\\
\hline
Cold &The target becomes Slowed for 2d4 rounds as their joints freeze\\
\hline
Electricity &The target is Stunned for 1 round\\
\hline
Fire &The target becomes Exhausted for 2d4 rounds\\
\hline
Sonic &The target is knocked prone and Dazed for 1 round\\
\hline
\end{tabular}

The Warmage may elect to apply Energy Effect or Energy Surge, but not both at once. As with Energy Effect, there is a saving throw.}

\ability{Weaken Defences:}{Any foe who suffers damage from a spell cast by a Warmage takes a penalty on their Armour Class, Damage Reduction, Spell Resistance and Energy Resistances until the beginning of the Warmage's next turn. This penalty is equal to the spell level.}

\ability{Chain Spell:}{When casting a single-target spell (whether a single target is designated or it is a ray, orb etc. - even if multiple targets can be selected but only one is chosen, but not for area-of-effect spells) with a casting time of one round or less, the Warmage can make it chain out to other targets. This increases the casting time to take up one round and then a full round action on the following turn. The spell will then chain out, with half of its original effect, to a number of secondary targets up to half her caster level. They are still entitled to any saving throws, and no-one may be targeted multiple times (additional chains are wasted if there are too few targets). The maximum distance from primary to secondary target is equal to half the original range.

By adding yet another full round to the casting time, the secondary targets will then chain out to tertiary targets (but they can't all chain back to each other. Again, any given person is effected only once per casting).}

\ability{Rallying Spell:}{Whenever the Warmage casts a spell that successfully takes a foe out of combat, she may elect for it to become a rallying spell. There is a blast of loud noise and she lights up (suppressing any Darkness effects) for one round, and all allies within 30' gain a morale bonus on Attack rolls and Will saves equal to the spell level, lasting for one round.}

\ability{Energy Blitz:}{Incredible effects apply to Warmage spells that deal energy damage.

\begin{tabular}[h]{|l|p{12cm}|}
\hline
Energy: &Effect:\\
\hline
Acid &All of the target's non-magical equipment on their person is dissolved immediately, and they are Blinded for the rest of the encounter\\
\hline
Cold &The target is Paralysed for 1 round, then Slowed for 2 more\\
\hline
Electricity &The target becomes Confused and Entangled for the rest of the encounter\\
\hline
Fire &The target becomes a raging inferno, as though set on fire for 5d6 Fire damage per round, setting adjacent subjects on fire as well\\
\hline
Sonic &The target is knocked prone and rendered Staggered and unable to stand for 4 rounds\\
\hline
\end{tabular}

The Warmage may elect to apply Energy Effect, Energy Surge or Energy Blitz, but no combination of the three at a time. As with Energy Effect and Surge, there is a saving throw.}

\ability{Heroes Feast:}{Once per day, the Warmage may cast Heroes Feast as a Spell-like Ability, except that it can affect three times as many people. This may be cast again if a major victory is scored (such as the defeat of an enemy army or capture of a large castle. Ask your DM).}

\ability{Instant Fortress:}{The Warmage may summon a Fortress as a Spell-like Ability. The fortress appears after three consecutive rounds of concentration, and then functions like the item of the same name. If packed up, then it regenerates all damage within 24 hours. If destroyed, it takes a week for another to be called forth. If the concentration time is extended out to one minute, then the fortress appears as two towers connected by a wall 25' tall, 10' thick and 50' long, with arrow slits and battlements at the top. If extended out to ten minutes, it becomes four towers, each connected by one such wall in a square formation, with a 60' tall tower in the centre, connected to the walls by 10' thick, 10' tall, 20' long corridors.

The fortress requires as much time to pack up as to set up.}

\ability{Arcane Ordinance:}{By focusing for two full rounds in addition to the original casting time, the Warmage may quadruple the area of effect of an area spell. By focusing for five rounds in addition to the original casting time, she may multiply the area by ten. However, either benefit will only apply to the first round (unless Instantaneous), unless the Warmage maintains concentration on the spell.}

\ability{Energy Mastery:}{Whenever the Warmage kills a target with a spell that deals a type of Energy damage that she could change a spell to do (Acid, Cold, Electricity, Fire, Force, Negative, Sonic), there is an explosion of energy. Everyone adjacent to the target takes 1d4 damage of the same type per caster level (Reflex half, DC 10 + half the Warmage's HD + her Int modifier), with no Effects, Surges or Blitzes applied to this. This is not a spell, so anyone slain by this does [b]not[/b] also explode, creating an infinite peasant chain of ordinance.}

\ability{Dimensional Fortress:}{Once per day, the Warmage may cast Mordenkainen's Magnificent Mansion. Anyone who attempts to gain entry uninvited triggers an alarm and  a Disintegrate effect. The DC of this effect is 10 + half the Warmage's hit dice + her Caster Level.}

\ability{Hellstorm:}{Once per day, the Warmage may call a devastating blitz of arcane power upon her foes, designed to force everyone to stay in cover, but also doing a reasonable job of tearing buildings apart so the battle can truly begin. 

The Warmage must spend a full round action concentrating, and then designate the area of effect: two 10x10' squares per caster level. After this, the effect is out of her hands - even if she wants to, she cant stop it. The area is struck by an Earthquake that lasts for one minute, and every round, a single meteor (as per Meteor Swarm) strikes the location of her choosing (if she does not make a selection, a random area is picked, generally large or tall targets such as buildings go first) until the meteor is up. Anyone inside a structure that is not destroyed by the earthquake/meteor is perfectly safe from this damage.

Additionally, anyone who is not enjoying physical cover of at least 50\% takes Acid damage and Fire damage, each equal to the Warmage's class level, every round. The only way to avoid this (aside from energy resistance/immunity) is to gain cover or leave the area of effect.

At the end of the minute, all effects stop, except for the pits and difficult ground, which is instantaneous and thus doesn't go away, and everyone within the area must make a Fort save (DC 10 + half the Warmage's hit dice + her Int modifier) or be Stunned for 3 rounds, allowing the invading army to rush in and start the violence.}

\ability{Dragonflight Bombardment:}{The Warmage gains a loyal ally: a Dragon with a true CR that must be at least 3 less than the Warmage's character level. If it dies, another turns up in 1d6+6 days. This dragon acts as a mount, and will gladly fight in melee or rain its breath weapon down upon the battlefield. Additionally, as long as both are in physical contact, the Warmage may cast any damaging spell through the dragon, affecting everyone in the Area of Effect of the breath weapon. If the duration was more than Instantaneous, it becomes "one round".}

\ability{Arcane Siege:}{Three times per day, the Warmage may target a building she can see and, as a Supernatural Ability, cause it to crack open. If the building fails a Fortitude save (use the best save of the inhabitants, if none it automatically fails) it splits apart, tumbling to the ground and dealing 20d6 damage to all of the inhabitants who are likely trapped and unable to escape. Clouds of dust equal to a Sandstorm are churned up for 1 minute, as well.}

\ability{Win:}{The Warmage wins the game. There is no saving throw for this. Note that this doesn't actually affect the game.}

\spelllist{Warmage Spell List:}

\small\ability{0th level:}{\emph{Dancing Lights, Darkness, Detect Magic, Detect Poison, Disrupt Undead, Ghost Sound, Light, Magic Missile, Mending, Message, Purify Food and Drink, Rouse, Stand}}

      \ability{Level 1:}{\emph{Alarm, Detect Scrying, Detect Secret Doors, Disguise Self, Endure Elements, Entangle, Firespray, Grease, Mass Rouse, Mass Stand, Mount, Obscuring Mist, Shocking Grasp, Silent Image, Ventriloquism}}

      \ability{Level 2:}{\emph{Arcane Lock, Continual Flame, Fireball, Jet of Steam, Gust of Wind, Incendiary Slime, Locate Object, Mass Enlarge Person, Mass Reduce Person, Misdirection, Protection From Arrows, Pyrotechnics, Resist Energy, Scare, Scorching Ray, See Invisibility, Whispering Wind}}

      \ability{Level 3:}{\emph{Caustic Mire, Caustic Smoke, Deep Slumber, Dispel Magic, Flame Arrow, Fly, Horrid Sickness, Invisibility Sphere, Lightning Bolt, Major Image, Mass Resist Energy, Mordenkainen's Faithful Hound, Nondetection, Protection From Energy, Rage, Sleet Storm, Stinking Cloud, Wall of Fire, Water Breathing, Wind Wall}}

      \ability{Level 4:}{\emph{Confusion, Dimension Door, Dimensional Anchor, Evard's Black Tentacles, Fear, Fire Shield, Fire Trap, Hallucinatory Terrain, Ice Storm, Move Earth, Scrying, Shout, Solid Fog, Stone Shape, Wall of Fire, Wall of Ice}}

      \ability{Level 5:}{\emph{Cloudkill, Cone of Cold, Deltane's Fiery Tentacles, Fire and Brimstone, Fire Seeds, Greater Dispel, Dismissal, Fabricate, Lightning Leap, Mind Fog, Mirage Arcana, Nightmare Terrain, Prying Eyes, Seeming, Sending, Tactical Teleportation, Telepathic Bond, Transmute Mud to Rock, Transmute Rock to Mud, Wall of Force, Wall of Stone, Waves of Fatigue}}

      \ability{Level 6:}{\emph{Acid Fog, Chain Lightning, Contingency, Guards and Wards, Mass (Bull's Strength, Cat's Grace, Bear's Endurance), Mass Suggestion, Storm of Fire and Ice, Sunburst, True Seeing, Veil, Wall of Iron, Wall of Thorns}}

      \ability{Level 7:}{\emph{Banishment, Control Weather, Deadly Lahar, Earthquake, Forcecage, Greater Teleport, Incendiary Cloud, Mass Hold Person, Mass Invisibility, Mordenkainen's Sword, Phase Door, Planeshift, Prismatic Spray, Reverse Gravity, Waves of Exhaustion, Whirlwind}}

      \ability{Level 8:}{\emph{Deadly Sunstroke, Dimensional Lock, Greater Prying Eyes, Greater Shout, Horrid Wilting, Mass Charm Monster, Mass Polymorph, Prismatic Wall, Storm of Vengeance}}

      \ability{Level 9:}{\emph{Astral Projection, Elemental Swarm, Etherealness, Firestorm, Foresight, Mass Hold Monster, Meteor Swarm, Prismatic Deluge, Prismatic Sphere, Timestop, Towering Thunderhead, Wail of the Banshee}}
\normalsize

\spelllist{Altered Spells:}
\ability{Chain Lightning:}{This acts as a Lightning Bolt (and may be bounced, as below), except that every time a target takes damage from it (whether they make the save or not), another smaller bolt shoots out to another target of your choice within 50 feet. This requires a Ranged Touch Attack, and if the target is struck, they take half the original damage. If a bolt bounces over someone multiple times, multiple secondary bolts are launched. An individual can be hit by the primary bolt and one or more secondary bolts (though not secondary bolts that are caused by them getting struck) in the same casting.}

\ability{Cone of Cold:}{This works like normal, except the entire area of effect is coated in ice (functioning like a Grease spell that is automatically Dispelled, square-by-square, by Fire effects) and anyone who fails the save takes 1d6 Dexterity damage.}

\ability{Firestorm:}{This spell functions as normal, except that it lasts for as long as the Warmage concentrates. The area of effect cannot be moved, however.}

\ability{Flame Arrow:}{When cast, all arrows fired from within 50' of the caster during the next round deal an additional amount of Fire Damage equal to 2d6 plus her Caster Level.}

\ability{Lightning Bolt:}{When cast by a Warmage, Lightning Bolts may bounce off surfaces, either at a 90 degree angle or 180 degrees straight back at the caster, caster's choice.}

\ability{Mass X:}{The spell works just as normal, except it affects one subject per caster level.}

\ability{Mass Polymorph:}{This works only on willing targets, affecting two subjects per caster level. The subjects are transformed into Trolls, effectively replacing their character sheets with the MM entry. They can think like themselves, retaining their alignments and memories, but don't actually retain their skills, feats, ability scores (even mental ones) or anything else. You don't get troll wizards and troll knights and troll thief-acrobats, you get trolls.

These trolls may, however, utter "Hurr hurr, I'm a (their original class)" as a free action. Troll wizards can be said to cast sleep (range: touch, material focus: a club, somatic component: make an attack roll) and Knock (range: touch, material focus: a club, somatic component: make a break check), likewise Troll Rogues can be said to be able to pick locks (with a club) and disable devices (with a club).}

\ability{Meteor Swarm:}{this causes four meteors to rain down from the sky, all at different points. Make a ranged touch attack against four different targets (including sections of ground). The targets, if hit, take 10d6 Bludgeoning Damage. Then, all within a 20' radius of each meteor takes 1d6 Fire damage per caster level (if multiple blasts hit the same person, they are damaged multiple times) with a Ref save for half (each time, if struck multiple times). If the targets of the meteors were hit by the attacks, they automatically fail the save.

The area then becomes difficult ground, with the 5' square points of impact becoming deep craters (10' deep pits).}
