\classname{Enlightened Disciple of Wel Hung Temple, Long Wang Province} \label{comm:prestige:enlighteneddisciple}
\vspace*{-8pt}
\quot{``I am Enlightened. You are not."}

You came from Wel Hung Temple, in the province that was named after its residents' most significant feature. Because of this, you're special. Plus you're enlightened.

\ability{Prerequisites:}{}
\listprereq
	\itemability{Skills:}{Knowledge (Religion) or Knowledge (the Planes) 8 ranks }
	\itemability{Feats:}{Insightful Strike or Zen Archery }
	\itemability{Special:}{Must have one Enlightenment ability }
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skills/Level:}{8 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{8.5cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+2&Wings of Flight, Hair of Vines\\
2&+2&+3&+3&+3&Daylight, Halo of Flames\\
3&+3&+3&+3&+3&Enlightenment: Eschew Worldly Possessions, Dig a Hole\\
4&+4&+4&+4&+4&Wings of Deflection, Koan of the One-Eyed Monk\\
5&+5&+4&+4&+4&Koan of the Inquisitive Student, Quantum Stance\\
6&+6&+5&+5&+5&Enlightenment: We Are All Connected, Fill it Up\\
7&+7&+5&+5&+5&Tibetan Butterfly Technique, Wings of Searing Light\\
8&+8&+6&+6&+6&Beating of Enlightenment, Quantum Cat Mantra\\
9&+9&+6&+6&+6&Enlightenment: Transcendence, Zen Fist\\
10&+10&+7&+7&+7&The Barrier That Wasn't, Kill Buddha\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Enlightened Disciple of Wel Hung Temple, Long Wang Province prestige class.

\ability{Weapon and Armor Proficiency:}{The Enlightened Disciple gains no proficiency with armor or weapons.}

\ability{Wings of Flight:}{The Enlightened Disciple gains a pair of ethereal wings that grant Good Flight at a speed of 40' per round. For every additional set of wings gained, add +20' of speed.}

\ability{Hair of Vines:}{the hair of the Enlightened Disciple becomes vines and flowers. Animals and Plants will never attack her.}

\ability{Daylight:}{the Disciple constantly emits Daylight as per the spell, as a Supernatural Ability. She may choose to suppress this ability at will.}

\ability{Halo of Flames:}{a halo of fire forms over the head of the Enlightened Disciple. Anyone who grapples with her or strikes her with a melee weapon takes fire damage equal to 1d6 plus her character level, plus her Wisdom modifier.}

\ability{Enlightenment: Eschew Worldly Possessions:}{at this stage, the Disciple can create items worth up to 15,000 GP as per a Wish, at will, requiring only a minute of meditation. They also need not eat or drink. To use this ability, the Disciple must not own any currency or precious metals. Personal equipment is exempted from the restriction. This is a flavour thing, so use common sense.}

\ability{Dig a Hole:}{By touching an unattended object, the Disciple may cause a Disintegrate effect as a Supernatural ability at will. This only affects objects and terrain, not creatures. Doing this removes all mental ability damage and ability drain, as the act of digging a hole for no purpose other than to dig a hole helps them reach a state of peace.}

\ability{Wings of Deflection:}{The Enlightened Disciple grows a second pair of ethereal wings. She gains a +4 Deflection bonus to Armour Class, +2 for having another pair of wings already, and this improves by another +2 for every other pair of wings she gains.}

\ability{Koan of the One-Eyed Monk:}{By threatening people with violence, the Disciple is able to cause others to reach their own Enlightenment. If she can beat the foe's modified level check with an Intimidate check, then even if the foe is immune to Fear or Intimidation, she still bestows a Suggestion upon them, however they are entitled to a save. \smallskip

Any time she is able to make a Demoralise check (such as demoralising foes who see her slaughter an enemy, if she has the relevant feat), she may use this ability, rolling once and applying the result to the check of every foe who could be affected.}

\ability{Koan of the Inquisitive Student:}{Upon successfully striking a foe in melee combat, the Disciple may merely rap them on the head. This causes zero damage, but causes them to lose their Dexterity bonus to AC for one round. Within the same encounter, the Disciple may, upon successfully hitting that foe a second time, automatically turn the hit into a confirmed critical hit. They must perform the harmless rap on the head again in order to automatically critical again.}

\ability{Quantum Stance:}{Observe the Enlightened Disciple. She is not really there, merely more likely to be there than not there. Nothing is truly where we perceive it to be. The Disciple takes this to the logical conclusion: any attack against the Disciple suffers a 50\% miss chance. True Seeing and such abilities to not get around this; the only way to prevent it is to have a higher Wisdom score than the Disciple.}

\ability{Enlightenment: We Are All Connected:}{The Disciple gains an even greater understanding of life, and how hatred is a weapon we forge for others that only hurts ourselves, that the air they exhale is inhaled by their enemies, and that everything is linked together. \smallskip

Any beneficial spell or effect granted to the Disciple or any of her allies she can see is instead, at the Disciple's option, granted to the Disciple and any number of her allies she can see. Additionally, any foe who subjects the Disciple (or any ally in a square the Disciple threatens) to an ongoing condition such as Poison, Disease, Fear, Blindness or Nausea must make a Will save (DC 10 + half the Disciple's Hit Dice + her Wisdom modifier) or also receive the same affliction, for the same duration. If the original target is immune to the effect, then the attacker takes the effect but the target does not. The target may then, as a Free Action, tell the attacker to fellate them.}

\ability{Fill It Up:}{As a Supernatural Ability at will, the Disciple may conjure earth and minerals to fill holes, repair damaged buildings or alter the terrain. This functions as a Creation that only makes wood, earth, mud, sand, clay, non-precious stone and non-precious metal, and Fabricate that applies only to the above materials. Once per day, if the Disciple uses this ability to fill a hole created by ``Dig a Hole", she gains the benefits of a Moment of Prescience.}

\ability{Tibetan Butterfly Technique:}{Once per 5 minutes of meditation (or digging holes and filling them up), the Disciple may create a Wings of Flurry (Dragon Cock? I Walk) effect in the shape of a hurricane. This may either function as normal, or be placed anywhere within 250 feet, as though the Disciple were standing at that point. The save DC is 10 + \half HD + her Wisdom modifier.}

\ability{Wings of Searing Light:}{The Disciple grows a third pair of wings. As a Supernatural Ability at will, she may use a Standard Action to fire one ray of light per wing possessed, out to 250' each, as ranged touch attacks. Upon hitting, they each deal Fire damage equal to 1d6 + her class level + her Wisdom modifier. Undead take double damage.}

\ability{Beating of Enlightenment:}{Upon automatically scoring a critical hit with Koan of the Inquisitive Student, the Disciple can teach the foe a valuable lesson. They must make a Will save (DC 10 + \half HD + her Wis mod) or be Stunned with realisation for 1 round, and then Cowering until someone makes an attack against them or the combat ends. \smallskip

If the combat ends before they are attacked, the Disciple may elect to set the target on the path of Enlightenment, forcing another Will save (same DC) against a Suggestion to leave immediately, searching for Enlightenment. They will undertake this vague task for 1 hour per class level.}

\ability{Quantum Cat Mantra:}{No one can really be sure if the Disciple is dead or alive. It's not that she necessarily looks unhealthy, or is in a box, it's just that no-one can actually know for certain. The Disciple may treat herself as dead or alive or undead or any combination thereof when being subject to abilities. So she is immune to Physical Ability Damage/Drain, Energy Drain/Negative Levels, Fatigue, Poison, Disease, Death Effects and Critical Hits and so on, and is healed by Inflict spells, yet is also healed by Cure spells, and cannot be Turned/Rebuked.}

\ability{Enlightenment: Transcendence:}{The Disciple is no longer a normal mortal creature. She becomes Ageless, and can only die by being killed. However, she is so hardcore she wouldn't die even if you killed her: she rises again 24 hours later unless the body is hacked apart and burned, the ashes then scattered into an Unhallowed land.}

\ability{Zen Fist:}{The actions of the Disciple cannot be interrupted by Immediate Actions, readied actions or attacks of opportunity. Instead, the Disciple declares her intent (such as "to make three attacks against the Hobgoblin Warlord and three against its Dragon mount"), the dice are rolled, and no attacks are actually made. However, at the end of the Disciple's turn, the targets have been attacked, actions performed and so on, just without there being a moment in time in which the actions were made. If you are confused by this, you're not Zen enough. \smallskip

Additionally, she may elect to move as by teleporting - the journey has been made without a single footstep having fallen. Doing this, however, does not allow for Poetry in Motion (if she gains that class feature from another source).}

\ability{The Barrier That Wasn't:}{The Disciple may ignore all Entanglement, Difficult Ground, Walls of Force and physical barriers. Indeed, she cannot be impeded by the terrain (yet is able to stand on solid ground, and swim in water) or Wall spells (although they can still deal damage). She can still be grappled, but gains a +8 bonus to escape the grapple.}

\ability{Kill Buddha:}{It is said that if you should see Buddha, you must kill him. People do not become Enlightened by repeating what was done before them, they only attain Enlightenment in their own manner. The Disciple at this point becomes the Enlightened Master of Wel Hung Temple, Long Wang Province (replace all references of ``Disciple" to ``Master"), and gains the Half Celestial template without the Level Adjustment. The wings from the template are added to those already possessed, increasing the bonuses.}
