\classname{Defender of the Woods} \label{comm:prestige:defenderofwoods}
\vspace*{-8pt}
\quot{``In Sovjet Faerun, trees cut down YOU!''}

\ability{Requirements:}{}
\listprereq
\itemability{BAB:}{+7}
\itemability{Skills:}{Knowledge: Nature 10 ranks, Sense Motive 10 ranks}
\itemability{Special:}{Must be a Plant, Magical Beast or Fey, or have made peaceful contact with a creature of one of the above types. Must not be fond of deforestation. Fey Knights needn't meet the Sense Motive requirement.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d10}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skill Points at Each Level:}{6 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+0 &+2 &+2 &Tree Stride, Monstrous Mount, Diamondwood Armour\\
2nd &+2 &+0 &+3 &+3 &Speak With Animals, Resist Nature's Lure, Entangle\\
3rd &+3 &+1 &+3 &+3 &I Talk To The Trees, Designate Opponent\\
4th &+4 &+1 &+4 &+4 &The Trees Have Eyes, Turn Flames, Briar Web\\
5th &+5 &+1 &+4 &+4 &Primal Rage, Enchanted Forest\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Defender of the Woods prestige class.

\ability{Weapon and Armor Proficiency:}{Defender of the Woods gain no proficiency with any weapon or armor.}

\ability{Tree Stride:}{The Defender of the Woods may Dimension Door between any two trees in the same general forest/jungle/clump of woodland. This is a Spell-like ability that may be performed at will.}

\ability{Monstrous Mount:}{A great beast of a mount is granted for the Defender of the Woods to ride. They should select a Plant, Animal or Magical Beast with a CR equal to their own level minus 3, and it serves them loyally. If slain, another replaces it after 24 hours.

Instead of a specific creature, a generic one may be custom-built:
\listone
    \item CR equal to Magical Beast hit dice
    \item Huge Size (Long), 50' movement
    \item Either Fly 30' (Average), Swim 100', Climb 40' or Burrow 40'.
    \item Quadrupedal and Stable
    \item Natural Armour equal to hit dice
    \item Str 20, Dex 15, Con 18, Int 5, Wis 12, Cha 9. Add +1 to any one ability score for every hit die.
    \item 2 Claws (3d6+Str) and a Bite (4d6+1/2 Str) or 2 Claws (3d6+1/2 Str) and a Tail Slap (4d6+Str+1/2) or 4 Tendrils (2d6+Str) or Bite (4d6+Str) and Gore (4d6+Str, double on a charge)
    \item Damage Reduction/iron and Fire and Cold Resistance equal to Hit Dice
    \item May cast 1 Druid spell each of levels 1, 3 and 5, three times per day, as spell-like abilities (DC = 10 + half HD + Wisdom modifier).
\end{list}}

\ability{Diamondwood Armour:}{The Defender of the Woods is blessed by the creatures of the forest. Their armour turns into Wood, but is considered as strong as Adamantine and allows them to add their class level as a bonus on saving throws against [Fire] effects and Poison. Furthermore, the armour grows one Goodberry per class level per day, sprouting in the morning.}

\ability{Speak With Animals:}{As a Supernatural ability at will, the Defender of the Woods can communicate with animals.}

\ability{Resist Nature's Lure:}{The Defender of the Woods becomes gains a +5 bonus to saves against the Spell-like and Supernatural abilities of Fey. This is good, because protecting them doesn't mean they won't put you to sleep and draw a dick on your face, just for laughs.}

\ability{Entangle:}{The Defender of the Woods may cast Entangle as a Spell-like ability at will. The DC is equal to 10 + \half Hit Dice + Charisma modifier.}

\ability{I Talk To The Trees:}{The Defender of the Woods can speak with plants as a Supernatural ability. Regular plants usually don't have much to say (and indeed, can't speak, requiring telepathy or just giving vague impressions). Plant creatures might have means of verbal communication.}

\ability{Designate Opponent:}{The Defender of the Woods, if already possessing Knight Levels, may add their Defender level minus 2 to their effective Knight level for the purpose of bonus damage against Designated Opponents.}

\ability{The Trees Have Eyes:}{Whenever the Defender is within 1 mile of a forest, jungle or other large collection of trees, they are able to tell when hostile forces are within 1 mile of the same group of trees, as well as the general location and a rough idea of how many there are.}

\ability{Turn Flames:}{Fire spells cast within 20' of the Defender of the Woods must make a Spell Penetration check against 15 + \half the Defender's Hit Dice, otherwise they fail. Additionally, with a Swift Action, the Defender may automatically extinguish all non-magical flames within 50'. \smallskip

Both abilities are Supernatural.}

\ability{Briar Web:}{Anyone caught in the Entangle effect created by the Defender also takes Magical Wooden Piercing Damage equal to 2d6 plus the hit dice of the Defender, every round they remain in the area. This does not count as attacking them, so it's okay if they fall over or lose their Dex bonus to AC.}

\ability{Primal Rage:}{Once per hour, the Defender of the Woods may assume a beastly form, resembling a werebear. They increase one size category, gain 2 Claw Attacks that deal 2d6+Str damage for a Large Creature and a Bite Attack that deals 3d6 + \half Str damage for a Large Creature, and gain +6 Str, +2 Dex and +4 Con instead of the usual changes to ability scores based on size. They also gain +5 natural armour and the Improved Grab ability when they hit with a bite attack. The natural weapons are treated as having a Greater Magic Fang (Caster Level = Hit Dice) cast on them.

This lasts for 1 minute. While in this form, they may not cast any spells or spell-like abilities. If they should reach 20 Hit Dice total, the beastly form also gains the Greenbound template (and may use the spell-like abilities inherent to the template).}

\ability{Enchanted Forest:}{When in an area with a large group of trees, the Defender is aided by the very woods themselves. Once per hour they may cast \spell{sleep} as a Supernatural Ability with no limit on Hit Dice (but may not take advantage of the situation to attack the sleeping foes, if a Knight), and additionally, constantly radiate a 250' radius Nightmare Terrain that only affects hostile creatures. Those who are in the area and fail to disbelieve take 1d6 + Defender's Hit Dice in damage at the start of their turn. This is also a Supernatural ability, and the save DC for both effects is Charisma based.}

