\classname{Drunken Master} \label{comm:prestige:drunkenmaster}
\vspace*{-8pt}
\quot{``Listen, you uppity orc-spawned barely-brained lout, I've had a really bad couple of decades, and only two things makes me feel better. One comes in a bottle. The other is fighting. And you, trying to come in here and be the big man, just broke all the bottles. Except the one in my hand... *Dook...dook...dook* ...Ready f'...f'...f'...for yer whippin', m'boy?" }

\desc{Sometimes, a man suffers or sees an event so terrible, all he can do is start drinking. And drink. And drink. And drink. Sometimes, he's the kind of drunk that enjoys a fight. And even more rarely, he's the kind of drunk whose alcohol consumption lets him push his body to extraordinary feats. Someday, maybe he'll extricate himself from the bottle, but right now, he goes into fights with a noticeable sway and big grin. }

\desc{There are very few people who seek to become a true Drunken Master. That path means a hangover most mornings, and bruises and broken bones you don't remember acquiring, and stabbing pains from your liver. However, sometimes, the world goes so bad, all a warrior can do is find a town and just start drinking. Often in silence, often staring at the drink for a long time before he actually drinks it. He'll participate in bar fights, because they let him forget for a little while, but it's only a temporary reprieve. However, when he does fight, he throws himself whole-heartedly into the fight, performing feats that no one would attempt while sober and allowing the alcohol to push his body past its normal physical limits. }

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+3}
\itemability{Skills:}{Tumble 8 ranks}
\itemability{Special:}{The character must to be an alcoholic and not care if he lives or dies.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Drunken Master’s class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Escape Artist (Dex), Gather Information (Int), Hide (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Sense Motive (Wis), Spot (Wis), Swim (Str), and Tumble (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{8cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+0&Drink Like A Devil, Loosened Up, Fighting Style\\
2&+2&+3&+3&+0&Gulp It Down, Drunken Habit\\
3&+3&+3&+3&+1&Drink Like Two Devils, Drunken Habit, Liquid Power\\
4&+4&+4&+4&+1&*Dook Dook Dook*, Drunken Habit, Fighting Style\\
5&+5&+4&+4&+1&Drunken Habit, Drunken Habit\\
6&+6&+5&+5&+2&Drunken Habit, More Liquid Power\\
7&+7&+5&+5&+2&Drunken Habit, Master Fighting Style\\
8&+8&+6&+6&+2&Drunken Habit, Drunken Habit\\
9&+9&+6&+6&+3&Drunken Habit, I Remember Now\\
10&+10&+6&+6&+3&Drunken Habit, Grandmaster Fighting Style.\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Drunken Master prestige class.

\ability{Weapon and Armor Proficiency:}{The Drunken Master takes no penalty with improvised weapons, and gains no armor proficiency.}

\ability{Drink Like a Devil (Ex):}{A Drunken Master may spend either move or standard action to drink a tankard of ale, a glass of wine, or a mouthful of liquor. Doing so gives him a +2 bonus to a physical stat of his choice, at the price of a -2 penalty to a mental stat of his choice. This lasts for 1 hour for each ‘drink’ the Drunken Master has consumed, and he may consume a number of drinks equal to half his character level plus his unenhanced Constitution modifier.}

\ability{Loosened Up (Ex):}{As the Monk’s Armored in Life, except only when under the effects of Drink Like a Devil. Levels of Drunken Master stack with levels of Monk for determining the armor bonus, but if the character does not have Armored in Life, he gains that ability--when drinking.}

\ability{Fighting Style (Su):}{At levels 1 and 4, the Drunken Master gains a Fighting Style, as the Dungeonomicon Monk does. If he does not already have a Slam attack, he gets one. He may only use these fighting styles when under the influence.}

\ability{Drunken Habit:}{The Drunken Master has traits that only come out when he drinks. They are not very pretty. Each time a new Drunken Habit is acquired, pick one of the below as long as the requirements are met before getting this Habit.}
\begin{itemize}

    \item{\textit{Mean Drunk (Ex):} The Drunken Master is a mean drunk. When under the influence, he hits even harder than he does when he's sober. He gains +1d6 bonus damage as long as he's had a drink. It applies to melee and thrown attacks and Attacks of Opportunity (If using Races of War AoO rules, it applies to AoO's granted by BAB, but not to those granted by feats). Mean Drunk can be taken more than once, and the bonus damage stacks, but may be taken only up to a number of times equal to one-half class level (Maximum +5d6).}

\item{\textit{Noxious Breath (Ex):} The Drunken Master may, as a standard action, breathe in the face of a target whose face is within five feet of his. Doing so forces a Fort save, DC 10 + ? character level + Number Of Drinks He’s Had In The Past Hour. If it fails, the target is nauseated for one round. If passed, the target is instead sickened for one round. If the target has Scent, it takes a penalty to his Fort Save equal to the Survival bonus granted by Scent.}

\item{\textit{Vile Breath (Ex):} The DC on Noxious Breath goes up by 2. Also, Mettle can’t get someone off the hook this time. Requirement: Noxious Breath}

\item{\textit{Evil Breath (Ex):} The DC on Noxious Breath goes up by 3. This ability may be taken up to three times. The bonus stacks. Requirement: Vile Breath.}
 
\item{\textit{Really Loose (Ex):} For every two drinks the Drunken Master has active, his Loosen Up bonus increases by 1.}

\item{\textit{Dodgy Drunk (Ex):} When something attacks the Drunken Master and misses, he may take a 5-foot step. Requirement: Really Loose.}

\item{\textit{Painkiller (Su):} When the Drunken Master adds Painkiller to his list of Liquid Powers. Painkiller makes you take half-damage for 5 rounds. Requirement: Liquid Power.}

\item{\textit{Funny Drunk (Ex):} If the Drunken Master fails a skill check or misses someone he’s attacking, he does so in a way that is classic physical comedy. Those watching, including the target, must make a Will save versus Tasha’s Hideous Laughter (DC 10 +\half character level + Number of Drinks Consumed In The Past Hour).}

\item{\textit{Drunken Savant (Ex):} Select three skills. Each drink you have gives you a +2 enhancement bonus to those skills.}

\item{\textit{I did what? (Ex):} The Drunken Master may expend a Drunken Habit to gain a bonus Skill or Combat feat which can only be used while drunk. This may be taken twice, selecting a new feat each time.}

\item{\textit{Where'd He Go Now? (Ex):} If a drunken master is under the influence of at least 4 drinks, he sometimes doesn't  remember how he got somewhere. As long as no one is paying attention to him, he may move forty feet as a free action once a minute, even through walls, locked doors, or thin air. Upon arrival, he won’t remember how he got there, and no one will have seen him do it. “Paying Attention” is defined as actively watching, listening to, or being engaged in combat. Things that can break attention to allow the drunken master an opportunity to use this power include looking away momentarily, speaking to someone else, or being attacked by someone else.}

\item{\textit{Recuperating Coma (Ex):} If a drunken master is afflicted by abilty damage, ability drain, disease, poison fatigue, exhaustion, blindness, deafness, curse, or negative level he may opt to enter a Recuperating Coma. He keels over and stays asleep until all his drinks have worn off (One hour per drink). Each hour, he is cured of one affliction (a disease’s or poison’s effects are considered a single affliction, as are fatigue and exhaustion). If he is completely cured of afflictions before he wakes up, he is healed as though by a Cure Critical Wounds each hour. Requirement: Liquid Power.}
\end{itemize}

\ability{Gulp It Down (Ex):}{At second level, when consuming alcohol, a drunken master may take in a drink as a swift action rather than a move action.}

\ability{Drink Like Two Devils (Ex):}{At third level, if a drunken master spends a move or a standard action to consume a drink, you instead get the effects of two drinks. This may be used in conjunction with Gulp It Down.}

\ability{Liquid Power (Su):}{At level 3, the drunken master reacts to alcohol in strange ways. Choose two out of Bull’s Strength, Cat’s Grace, Bear’s Endurance, or Cure Moderate Wounds. From now on, when the Drunken Master takes a drink, he may instead receive the benefit as if he’d drunk an appropriate potion.}

\ability{*Dook Dook Dook* (Ex):}{At fourth level, if the drunken master spends a full-round action drinking, he gains the equivalent of 5 drinks. }

\ability{More Liquid Power (Su):}{At level 6, the drunken master adds another Liquid Power to his repertoire. The bonuses also increase to +6, except for Cure Moderate Wounds, which becomes Cure Critical Wounds. He may use Drink Like Two Devils or *Dook Dook Dook* in conjunction with this ability, and divide up the bonuses between drinks and Liquid Powers as he chooses..}

\ability{Master Fighting Style (Su):}{At level 7, a drunken master gains a Master Fighting Style. Again, he may only use it when drunk.}

\ability{I Remember Now (Ex):}{At level 9, a drunken master gains a degree of clarity that makes him all the more terrifying, and may use certain of his abilities even while not drunk. He may use any of his Fighting Styles, his Master Fighting Style, Mean Drunk, Noxious Breath (and its improvements), Funny Drunk, and Where’d He Go Now?, his bonus feats, and Loosened Up becomes Armored in Life. For Noxious Breath’s DC while sober, use the Monk’s Constitution modifier. For Funny Drunk’s DC, use his Charisma modifier.}

\ability{Grandmaster Fighting Style (Su):}{The drunken master gains a Grandmaster Fighting Style. Thanks to I Remember Now, he may use it at any time.}