%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Classes}\label{chapter:Classes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{classes-base/barbarian}
\input{classes-base/bard}
\input{classes-base/cleric}
\input{classes-base/druid}
\input{classes-base/fighter}
\input{classes-base/monk}
\input{classes-base/paladin}
\input{classes-base/ranger}
\input{classes-base/rogue}
\input{classes-base/sorcerer}
\input{classes-base/wizard}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multiclass Characters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A character may add new classes as he or she progresses in level, thus becoming 
a multiclass character. The class abilities from a character's different classes 
combine to determine a multiclass character's overall abilities. Multiclassing 
improves a character's versatility at the expense of focus.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Class And Level Features}
%%%%%%%%%%%%%%%%%%%%%%%%%

As a general rule, the abilities of a multiclass character are the sum of the abilities 
of each of the character's classes.

\textbf{\gameterm{Level}:} "\gameterm{Character Level}" is a character's total number of levels. It 
is used to determine when feats and ability score boosts are gained.

"\gameterm{Class Level}" is a character's level in a particular class. For a character whose 
levels are all in the same class, character level and class level are the same.

\textbf{\gameterm{Hit Points}:} A character gains hit points from each class as his or her 
class level increases, adding the new hit points to the previous total. 

\textbf{\gameterm{Base Attack Bonus}:} Add the base attack bonuses acquired for each class 
to get the character's base attack bonus. A resulting value of +6 or higher provides 
the character with multiple attacks. 

\textbf{\gameterm{Saving Throws}:} Add the base save bonuses for each class together.

\textbf{\gameterm{Skills}:} If a skill is a class skill for any of a multiclass character's 
classes, then character level determines a skill's maximum rank. (The maximum rank 
for a class skill is 3 + character level.)

If a skill is not a class skill for any of a multiclass character's classes, the 
maximum rank for that skill is one-half the maximum for a class skill.

\textbf{Class Features:} A multiclass character gets all the class features of 
all his or her classes but must also suffer the consequences of the special restrictions 
of all his or her classes. (\textit{Exception:} A character who acquires the barbarian 
class does not become illiterate.) 

In the special case of turning undead, both clerics and experienced paladins have 
the same ability. If the character's paladin level is 4th or higher, her effective 
turning level is her cleric level plus her paladin level minus 3. 

In the special case of uncanny dodge, both experienced barbarians and experienced 
rogues have the same ability. When a barbarian/rogue would gain uncanny dodge a 
second time (for her second class), she instead gains improved uncanny dodge, if 
she does not already have it. Her barbarian and rogue levels stack to determine 
the rogue level an attacker needs to flank her. 

In the special case of obtaining a familiar, both wizards and sorcerers have the 
same ability. A sorcerer/wizard stacks his sorcerer and wizard levels to determine 
the familiar's natural armor, Intelligence score, and special abilities.

\textbf{Feats:} A multiclass character gains feats based on character levels, regardless 
of individual class level

\textbf{Ability Increases:} A multiclass character gains ability score increases 
based on character level, regardless of individual class level.

\textbf{Spells:} The character gains spells from all of his or her spellcasting 
classes and keeps a separate spell list for each class. If a spell's effect is 
based on the class level of the caster, the player must keep track of which class's 
spell list the character is casting the spell from.

