%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Skills}\label{chapter:Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If you buy a class skill, your character gets 1 rank (equal to a +1 bonus on checks 
with that skill) for each skill point. If you buy other classes' skills (cross-class 
skills), you get 1/2 rank per skill point.

Your maximum rank in a class skill is your character level + 3.

Your maximum rank in a cross-class skill is one-half of this number (do not round 
up or down).

\textbf{Using Skills:} To make a skill check, roll: 1d20 + skill modifier (Skill 
modifier = skill rank + ability modifier + miscellaneous modifiers)

This roll works just like an attack roll or a saving throw -- the higher the roll, 
the better. Either you're trying to match or exceed a certain Difficulty Class 
(DC), or you're trying to beat another character's check result.

\textbf{Skill Ranks:} A character's number of ranks in a skill is based on how 
many skill points a character has invested in a skill. Many skills can be used 
even if the character has no ranks in them; doing this is called making an untrained 
skill check.

\textbf{Ability Modifier:} The ability modifier used in a skill check is the modifier 
for the skill's key ability (the ability associated with the skill's use). The 
key ability of each skill is noted in its description.

\textbf{Miscellaneous Modifiers:} Miscellaneous modifiers include racial bonuses, 
armor check penalties, and bonuses provided by feats, among others.

Each skill point you spend on a class skill gets you 1 rank in that skill. Class 
skills are the skills found on your character's class skill list. Each skill point 
you spend on a cross-class skill gets your character 1/2 rank in that skill. Cross-class 
skills are skills not found on your character's class skill list. (Half ranks do 
not improve your skill check, but two 1/2 ranks make 1 rank.) You can't save skill 
points to spend later.

The maximum rank in a class skill is the character's level + 3. If it's a cross-class 
skill, the maximum rank is half of that number (do not round up or down).

Regardless of whether a skill is purchased as a class skill or a cross-class skill, 
if it is a class skill for any of your classes, your maximum rank equals your total 
character level + 3.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Using Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

When your character uses a skill, you make a skill check to see how well he or 
she does. The higher the result of the skill check, the better. Based on the circumstances, 
your result must match or beat a particular number (a DC or the result of an opposed 
skill check) for the check to be successful. The harder the task, the higher the 
number you need to roll.

Circumstances can affect your check. A character who is free to work without distractions 
can make a careful attempt and avoid simple mistakes. A character who has lots 
of time can try over and over again, thereby assuring the best outcome. If others 
help, the character may succeed where otherwise he or she would fail.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Skill Checks}
%%%%%%%%%%%%%%%%%%%%%%%%%

A skill check takes into account a character's training (skill rank), natural talent 
(ability modifier), and luck (the die roll). It may also take into account his 
or her race's knack for doing certain things (racial bonus) or what armor he or 
she is wearing (armor check penalty), or a certain feat the character possesses, 
among other things. 

To make a skill check, roll 1d20 and add your character's skill modifier for that 
skill. The skill modifier incorporates the character's ranks in that skill and 
the ability modifier for that skill's key ability, plus any other miscellaneous 
modifiers that may apply, including racial bonuses and armor check penalties. The 
higher the result, the better. Unlike with attack rolls and saving throws, a natural 
roll of 20 on the d20 is not an automatic success, and a natural roll of 1 is not 
an automatic failure.

%%%
\subsubsection{Difficulty Class}
%%%

Some checks are made against a Difficulty Class (DC). The DC is a number (set using 
the skill rules as a guideline) that you must score as a result on your skill check 
in order to succeed.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Difficulty Class Examples}
\centering
\begin{tabular}{l l}
\textbf{Difficulty (DC)} & \textbf{Example (Skill Used)}\\
Very Easy (0) & Notice Something large in plain sight (\linkskill{Spot})\\
Easy (5) & Climb a knotted rope (\linkskill{Climb})\\
Average (10) & Hear an approaching guard (\linkskill{Listen})\\
Tough (15) & Rig a wagon wheel to fall off (\linkskill{Disable Device})\\
Challenging (20) & Swim in stormy water (\linkskill{Swim})\\
Formidable (25) & Open an average lock (\linkskill{Open Lock})\\
Heroic (30) & Leap across a 30-foot chasm (\linkskill{Jump})\\
Nearly Impossible (40) & Track a squad of orcs across hard ground acter 24 hours of rainfall (\linkskill{Survival})\\
\end{tabular}
\end{table}

%%%
\subsubsection{Opposed Checks}
%%%

An opposed check is a check whose success or failure is determined by comparing 
the check result to another character's check result. In an opposed check, the 
higher result succeeds, while the lower result fails. In case of a tie, the higher 
skill modifier wins. If these scores are the same, roll again to break the tie.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Example Opposed Checks}
\centering
\begin{tabular}{l l l}
\textbf{Task} & \textbf{Skills (Key Ability)} & \textbf{Opposing Skill (Key Ability)}\\
Con someone & \linkskill{Bluff} (Cha) & \linkskill{Sense Motive} (Wis)\\
Pretend to be someone else & \linkskill{Disguise} (Cha) & \linkskill{Spot} (Wis)\\
Create a false map & \linkskill{Forgery} (Int) & \linkskill{Forgery} (Int)\\
Hide form someone & \linkskill{Hide} (Dex) & \linkskill{Spot} (Wis)\\
Make a bully back down & \linkskill{Intimidate} (Cha) & Special\textsuperscript{1}\\
Sneak up on someone & \linkskill{Move Silently} (Dex) & \linkskill{Listen} (Wis)\\
Steal a coin pouch & \linkskill{Sleight of Hand} (Dex) & \linkskill{Spot} (Wis)\\
Tie a prisoner securely & \linkskill{Use Rope} (Dex) & \linkskill{Escape Artist} (Dex)\\
\multicolumn{3}{p{11cm}}{\textsuperscript{1} An Intimidate check is opposed by the target's level check, not a skill check. See the Intimidate skill description for ore information.}\\
\end{tabular}
\end{table}

%%%
\subsubsection{Trying Again}
%%%

In general, you can try a skill check again if you fail, and you can keep trying 
indefinitely. Some skills, however, have consequences of failure that must be taken 
into account. A few skills are virtually useless once a check has failed on an 
attempt to accomplish a particular task. For most skills, when a character has 
succeeded once at a given task, additional successes are meaningless.

%%%
\subsubsection{Untrained Skill Checks}
%%%

Generally, if your character attempts to use a skill he or she does not possess, 
you make a skill check as normal. The skill modifier doesn't have a skill rank 
added in because the character has no ranks in the skill. Any other applicable 
modifiers, such as the modifier for the skill's key ability, are applied to the 
check.

Many skills can be used only by someone who is trained in them.

%%%
\subsubsection{Favorable and Unfavorable Conditions}
%%%

Some situations may make a skill easier or harder to use, resulting in a bonus 
or penalty to the skill modifier for a skill check or a change to the DC of the 
skill check.

The chance of success can be altered in four ways to take into account exceptional 
circumstances.

\begin{enumerate*}
\item Give the skill user a +2 circumstance bonus to represent conditions that improve 
performance, such as having the perfect tool for the job, getting help from another 
character (see \linksec{Combining Skill Attempts}), or possessing unusually accurate information. 

\item Give the skill user a -2 circumstance penalty to represent conditions that hamper 
performance, such as being forced to use improvised tools or having misleading 
information.

\item Reduce the DC by 2 to represent circumstances that make the task easier, such 
as having a friendly audience or doing work that can be subpar.

\item Increase the DC by 2 to represent circumstances that make the task harder, such 
as having an uncooperative audience or doing work that must be flawless.
\end{enumerate*}

Conditions that affect your character's ability to perform the skill change the 
skill modifier. Conditions that modify how well the character has to perform the 
skill to succeed change the DC. A bonus to the skill modifier and a reduction in 
the check's DC have the same result: They create a better chance of success. But 
they represent different circumstances, and sometimes that difference is important.



Using a skill might take a round, take no time, or take several rounds or even 
longer. Most skill uses are standard actions, move actions, or full-round actions. 
Types of actions define how long activities take to perform within the framework 
of a combat round (6 seconds) and how movement is treated with respect to the activity. 
Some skill checks are instant and represent reactions to an event, or are included 
as part of an action.

These skill checks are not actions. Other skill checks represent part of movement.

%%%
\subsubsection{Checks without Rolls}
%%%

A skill check represents an attempt to accomplish some goal, usually while under 
some sort of time pressure or distraction. Sometimes, though, a character can use 
a skill under more favorable conditions and eliminate the luck factor.

\textbf{Taking 10:} When your character is not being threatened or distracted, 
you may choose to take 10. Instead of rolling 1d20 for the skill check, calculate 
your result as if you had rolled a 10. For many routine tasks, taking 10 makes 
them automatically successful. Distractions or threats (such as combat) make it 
impossible for a character to take 10. In most cases, taking 10 is purely a safety 
measure -- you know (or expect) that an average roll will succeed but fear that 
a poor roll might fail, so you elect to settle for the average roll (a 10). Taking 
10 is especially useful in situations where a particularly high roll wouldn't help.

\textbf{Taking 20:} When you have plenty of time (generally 2 minutes for a skill 
that can normally be checked in 1 round, one full-round action, or one standard 
action), you are faced with no threats or distractions, and the skill being attempted 
carries no penalties for failure, you can take 20. In other words, eventually you 
will get a 20 on 1d20 if you roll enough times. Instead of rolling 1d20 for the 
skill check, just calculate your result as if you had rolled a 20.

Taking 20 means you are trying until you get it right, and it assumes that you 
fail many times before succeeding. Taking 20 takes twenty times as long as making 
a single check would take.

Since taking 20 assumes that the character will fail many times before succeeding, 
if you did attempt to take 20 on a skill that carries penalties for failure, your 
character would automatically incur those penalties before he or she could complete 
the task. Common "take 20" skills include Escape Artist, Open Lock, and Search.

\textbf{Ability Checks and Caster Level Checks:} The normal take 10 and take 20 
rules apply for ability checks. Neither rule applies to caster level checks.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Combining Skill Attempts}
%%%%%%%%%%%%%%%%%%%%%%%%%

When more than one character tries the same skill at the same time and for the 
same purpose, their efforts may overlap.

%%%
\subsubsection{Individual Events}
%%%

Often, several characters attempt some action and each succeeds or fails independently. 
 The result of one character's Climb check does not influence the results of other 
characters Climb check.

%%%
\subsubsection{Aid Another and Skills}
%%%

You can help another character achieve success on his or her skill check by making 
the same kind of skill check in a cooperative effort. If you roll a 10 or higher 
on your check, the character you are helping gets a +2 bonus to his or her check, 
as per the rule for favorable conditions. (You can't take 10 on a skill check to 
aid another.) In many cases, a character's help won't be beneficial, or only a 
limited number of characters can help at once. 

In cases where the skill restricts who can achieve certain results you can't aid 
another to grant a bonus to a task that your character couldn't achieve alone.

%%%
\subsubsection{Skill Synergy}
%%%

It's possible for a character to have two skills that work well together. In general, 
having 5 or more ranks in one skill gives the character a +2 bonus on skill checks 
with each of its synergistic skills, as noted in the skill description. In some 
cases, this bonus applies only to specific uses of the skill in question, and not 
to all checks. Some skills provide benefits on other checks made by a character, 
such as those checks required to use certain class features.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ability Checks}
%%%%%%%%%%%%%%%%%%%%%%%%%

Sometimes a character tries to do something to which no specific skill really applies. 
In these cases, you make an ability check. An ability check is a roll of 1d20 plus 
the appropriate ability modifier. Essentially, you're making an untrained skill 
check. 

In some cases, an action is a straight test of one's ability with no luck involved. 
Just as you wouldn't make a height check to see who is taller, you don't make a 
Strength check to see who is stronger.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skill Descriptions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section describes each skill, including common uses and typical modifiers. 
Characters can sometimes use skills for purposes other than those noted here.

Here is the format for skill descriptions.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Skill Name}
%%%%%%%%%%%%%%%%%%%%%%%%%

The skill name line includes (in addition to the name of the skill) the following 
information.

\textbf{Key Ability:} The abbreviation of the ability whose modifier applies to 
the skill check. \textit{Exception:} Speak Language has "None" as its key ability 
because the use of this skill does not require a check.

\textbf{Trained Only:} If this notation is included in the skill name line, you 
must have at least 1 rank in the skill to use it. If it is omitted, the skill can 
be used untrained (with a rank of 0). If any special notes apply to trained or 
untrained use, they are covered in the Untrained section (see below).

\textbf{Armor Check Penalty:} If this notation is included in the skill name line, 
an armor check penalty applies (when appropriate) to checks using this skill. If 
this entry is absent, an armor check penalty does not apply.

\vspace{12pt}
The skill name line is followed by a general description of what using the skill 
represents. After the description are a few other types of information:

\textbf{Check:} What a character ("you" in the skill description) can do with 
a successful skill check and the check's DC.

\textbf{Action:} The type of action using the skill requires, or the amount of 
time required for a check.

\textbf{Try Again:} Any conditions that apply to successive attempts to use the 
skill successfully. If the skill doesn't allow you to attempt the same task more 
than once, or if failure carries an inherent penalty (such as with the Climb skill), 
you can't take 20. If this paragraph is omitted, the skill can be retried without 
any inherent penalty, other than the additional time required.

\textbf{Special:} Any extra facts that apply to the skill, such as special effects 
deriving from its use or bonuses that certain characters receive because of class, 
feat choices, or race.

\textbf{Synergy:} Some skills grant a bonus to the use of one or more other skills 
because of a synergistic effect. This entry, when present, indicates what bonuses 
this skill may grant or receive because of such synergies. See Table 4-5 for a 
complete list of bonuses granted by synergy between skills (or between a skill 
and a class feature).

\textbf{Restriction:} The full utility of certain skills is restricted to characters 
of certain classes or characters who possess certain feats. This entry indicates 
whether any such restrictions exist for the skill.

\textbf{Untrained:} This entry indicates what a character without at least 1 rank 
in the skill can do with it. If this entry doesn't appear, it means that the skill 
functions normally for untrained characters (if it can be used untrained) or that 
an untrained character can't attempt checks with this skill (for skills that are 
designated as "Trained Only").

\input{skills/appraise}
\input{skills/balance}
\input{skills/bluff}
\input{skills/climb}
\input{skills/concentration}
\input{skills/craft}
\input{skills/decipher-script}
\input{skills/diplomacy}
\input{skills/disable-device}
\input{skills/disguise}
\input{skills/escape-artist}
\input{skills/forgery}
\input{skills/gather-information}
\input{skills/handle-animal}
\input{skills/heal}
\input{skills/hide}
\input{skills/intimidate}
\input{skills/jump}
\input{skills/knowledge}
\input{skills/listen}
\input{skills/move-silently}
\input{skills/open-lock}
\input{skills/perform}
\input{skills/profession}
\input{skills/ride}
\input{skills/search}
\input{skills/sense-motive}
\input{skills/sleight-of-hand}
\input{skills/speak-language}
\input{skills/spellcraft}
\input{skills/spot}
\input{skills/survival}
\input{skills/swim}
\input{skills/tumble}
\input{skills/use-magic-device}
\input{skills/use-rope}
