%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Description}\label{chapter:Description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Alignment}\index{Alignment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A creature's general moral and personal attitudes are represented by its alignment: 
lawful good, neutral good, chaotic good, lawful neutral, neutral, chaotic neutral, 
lawful evil, neutral evil, or chaotic evil.

Alignment is a tool for developing your character's identity. It is not a straitjacket 
for restricting your character. Each alignment represents a broad range of personality 
types or personal philosophies, so two characters of the same alignment can still 
be quite different from each other. In addition, few people are completely consistent.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Good vs Evil}
%%%%%%%%%%%%%%%%%%%%%%%%%

Good characters and creatures protect innocent life. Evil characters and creatures 
debase or destroy innocent life, whether for fun or profit.

"Good" implies altruism, respect for life, and a concern for the dignity of sentient 
beings. Good characters make personal sacrifices to help others.

"Evil" implies hurting, oppressing, and killing others. Some evil creatures simply 
have no compassion for others and kill without qualms if doing so is convenient. 
Others actively pursue evil, killing for sport or out of duty to some evil deity 
or master. 

People who are neutral with respect to good and evil have compunctions against 
killing the innocent but lack the commitment to make sacrifices to protect or help 
others. Neutral people are committed to others by personal relationships. 

Being good or evil can be a conscious choice. For most people, though, being good 
or evil is an attitude that one recognizes but does not choose. Being neutral on 
the good-evil axis usually represents a lack of commitment one way or the other, 
but for some it represents a positive commitment to a balanced view. While acknowledging 
that good and evil are objective states, not just opinions, these folk maintain 
that a balance between the two is the proper place for people, or at least for 
them.

Animals and other creatures incapable of moral action are neutral rather than good 
or evil. Even deadly vipers and tigers that eat people are neutral because they 
lack the capacity for morally right or wrong behavior.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Law vs Chaos}
%%%%%%%%%%%%%%%%%%%%%%%%%

Lawful characters tell the truth, keep their word, respect authority, honor tradition, 
and judge those who fall short of their duties. 

Chaotic characters follow their consciences, resent being told what to do, favor 
new ideas over tradition, and do what they promise if they feel like it.

"Law" implies honor, trustworthiness, obedience to authority, and reliability. 
On the downside, lawfulness can include close-mindedness, reactionary adherence 
to tradition, judgmentalness, and a lack of adaptability. Those who consciously 
promote lawfulness say that only lawful behavior creates a society in which people 
can depend on each other and make the right decisions in full confidence that others 
will act as they should.

"Chaos" implies freedom, adaptability, and flexibility. On the downside, chaos 
can include recklessness, resentment toward legitimate authority, arbitrary actions, 
and irresponsibility. Those who promote chaotic behavior say that only unfettered 
personal freedom allows people to express themselves fully and lets society benefit 
from the potential that its individuals have within them.

Someone who is neutral with respect to law and chaos has a normal respect for authority 
and feels neither a compulsion to obey nor a compulsion to rebel. She is honest 
but can be tempted into lying or deceiving others.

Devotion to law or chaos may be a conscious choice, but more often it is a personality 
trait that is recognized rather than being chosen. Neutrality on the lawful-chaotic 
axis is usually simply a middle state, a state of not feeling compelled toward 
one side or the other. Some few such neutrals, however, espouse neutrality as superior 
to law or chaos, regarding each as an extreme with its own blind spots and drawbacks.

Animals and other creatures incapable of moral action are neutral. Dogs may be 
obedient and cats free-spirited, but they do not have the moral capacity to be 
truly lawful or chaotic.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Nine Alignments}
%%%%%%%%%%%%%%%%%%%%%%%%%

Nine distinct alignments define all the possible combinations of the lawful-chaotic 
axis with the good-evil axis. Each alignment description below depicts a typical 
character of that alignment. Remember that individuals vary from this norm, and 
that a given character may act more or less in accord with his or her alignment 
from day to day. Use these descriptions as guidelines, not as scripts.

The first six alignments, lawful good through chaotic neutral, are the standard 
alignments for player characters. The three evil alignments are for monsters and 
villains.

%%%
\subsubsection{Lawful Good, "Crusader"}
%%%
A lawful good character acts as a good person 
is expected or required to act. She combines a commitment to oppose evil with the 
discipline to fight relentlessly. She tells the truth, keeps her word, helps those 
in need, and speaks out against injustice. A lawful good character hates to see 
the guilty go unpunished.

Lawful good is the best alignment you can be because it combines honor and compassion.

%%%
\subsubsection{Neutral Good, "Benefactor"}
%%%
A neutral good character does the best that 
a good person can do. He is devoted to helping others. He works with kings and 
magistrates but does not feel beholden to them.

Neutral good is the best alignment you can be because it means doing what is good 
without bias for or against order.

%%%
\subsubsection{Chaotic Good, "Rebel"}
%%%
A chaotic good character acts as his conscience 
directs him with little regard for what others expect of him. He makes his own 
way, but he's kind and benevolent. He believes in goodness and right but has little 
use for laws and regulations. He hates it when people try to intimidate others 
and tell them what to do. He follows his own moral compass, which, although good, 
may not agree with that of society.

Chaotic good is the best alignment you can be because it combines a good heart 
with a free spirit.

%%%
\subsubsection{Lawful Neutral, "Judge"}
%%%
A lawful neutral character acts as law, tradition, 
or a personal code directs her. Order and organization are paramount to her. She 
may believe in personal order and live by a code or standard, or she may believe 
in order for all and favor a strong, organized government.

Lawful neutral is the best alignment you can be because it means you are reliable 
and honorable without being a zealot.

%%%
\subsubsection{Neutral, "Undecided"}
%%%
A neutral character does what seems to be a good 
idea. She doesn't feel strongly one way or the other when it comes to good vs. 
evil or law vs. chaos. Most neutral characters exhibit a lack of conviction or 
bias rather than a commitment to neutrality. Such a character thinks of good as 
better than evil -- after all, she would rather have good neighbors and rulers than 
evil ones. Still, she's not personally committed to upholding good in any abstract 
or universal way.

Some neutral characters, on the other hand, commit themselves philosophically to 
neutrality. They see good, evil, law, and chaos as prejudices and dangerous extremes. 
They advocate the middle way of neutrality as the best, most balanced road in the 
long run.

Neutral is the best alignment you can be because it means you act naturally, without 
prejudice or compulsion.

%%%
\subsubsection{Chaotic Neutral, "Free Spirit"}
%%%
A chaotic neutral character follows 
his whims. He is an individualist first and last. He values his own liberty but 
doesn't strive to protect others' freedom. He avoids authority, resents restrictions, 
and challenges traditions. A chaotic neutral character does not intentionally disrupt 
organizations as part of a campaign of anarchy. To do so, he would have to be motivated 
either by good (and a desire to liberate others) or evil (and a desire to make 
those different from himself suffer). A chaotic neutral character may be unpredictable, 
but his behavior is not totally random. He is not as likely to jump off a bridge 
as to cross it.

Chaotic neutral is the best alignment you can be because it represents true freedom 
from both society's restrictions and a do-gooder's zeal.

%%%
\subsubsection{Lawful Evil, "Dominator"}
%%%
A lawful evil villain methodically takes what 
he wants within the limits of his code of conduct without regard for whom it hurts. 
He cares about tradition, loyalty, and order but not about freedom, dignity, or 
life. He plays by the rules but without mercy or compassion. He is comfortable 
in a hierarchy and would like to rule, but is willing to serve. He condemns others 
not according to their actions but according to race, religion, homeland, or social 
rank. He is loath to break laws or promises.

This reluctance comes partly from his nature and partly because he depends on order 
to protect himself from those who oppose him on moral grounds. Some lawful evil 
villains have particular taboos, such as not killing in cold blood (but having 
underlings do it) or not letting children come to harm (if it can be helped). They 
imagine that these compunctions put them above unprincipled villains.

Some lawful evil people and creatures commit themselves to evil with a zeal like 
that of a crusader committed to good. Beyond being willing to hurt others for their 
own ends, they take pleasure in spreading evil as an end unto itself. They may 
also see doing evil as part of a duty to an evil deity or master.

Lawful evil is sometimes called "diabolical," because devils are the epitome 
of lawful evil.

Lawful evil is the most dangerous alignment because it represents methodical, intentional, 
and frequently successful evil.

%%%
\subsubsection{Neutral Evil, "Malefactor"}
%%%
A neutral evil villain does whatever she 
can get away with. She is out for herself, pure and simple. She sheds no tears 
for those she kills, whether for profit, sport, or convenience. She has no love 
of order and holds no illusion that following laws, traditions, or codes would 
make her any better or more noble. On the other hand, she doesn't have the restless 
nature or love of conflict that a chaotic evil villain has.

Some neutral evil villains hold up evil as an ideal, committing evil for its own 
sake. Most often, such villains are devoted to evil deities or secret societies.

Neutral evil is the most dangerous alignment because it represents pure evil without 
honor and without variation.

%%%
\subsubsection{Chaotic Evil, "Destroyer"}
%%%
A chaotic evil character does whatever his 
greed, hatred, and lust for destruction drive him to do. He is hot-tempered, vicious, 
arbitrarily violent, and unpredictable. If he is simply out for whatever he can 
get, he is ruthless and brutal. If he is committed to the spread of evil and chaos, 
he is even worse. Thankfully, his plans are haphazard, and any groups he joins 
or forms are poorly organized. Typically, chaotic evil people can be made to work 
together only by force, and their leader lasts only as long as he can thwart attempts 
to topple or assassinate him.

Chaotic evil is sometimes called "demonic" because demons are the epitome of 
chaotic evil.

Chaotic evil is the most dangerous alignment because it represents the destruction 
not only of beauty and life but also of the order on which beauty and life depend.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Vital Stats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Age}
%%%%%%%%%%%%%%%%%%%%%%%%%

You can choose or randomly generate your character's age. If you choose it, it 
must be at least the minimum age for the character's race and class (see Table: 
Random Starting Ages). Your character's minimum starting age is the adulthood age 
of his or her race plus the number of dice indicated in the entry corresponding 
to the character's race and class on Table: Random Starting Ages.

Alternatively, refer to Table: Random Starting Ages and roll dice to determine 
how old your character is.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Random Starting Ages}
\centering
\begin{tabular}{l c p{2.5cm} p{2.5cm} p{2.2cm}}
\textbf{Race}  &  \textbf{Adulthood}  &  \textbf{Barbarian, Rogue, Sorcerer}  &  \textbf{Bard, Fighter, Paladin, Ranger}  &  {\raggedright{}\textbf{Cleric, Druid, Monk, Wizard}}\\
Human & 15 years & +1d4 & +1d6 & +2d6\\
Dwarf & 40 years & +3d6 & +5d6 & +7d6\\
Elf & 110 years & +4d6 & +6d6 & +10d6\\
Gnome & 40 years & +4d6 & +6d6 & +9d6\\
Half-elf & 20 years & +1d6 & +2d6 & +3d6\\
Half-orc & 14 years & +1d4 & +1d6 & +2d6\\
Halfling & 20 years & +2d4 & +3d6 & +4d6\\
\end{tabular}
\end{table}

With age, a character's physical ability scores decrease and his or her mental 
ability scores increase (see Table: Aging Effects). The effects of each aging step 
are cumulative. However, none of a character's ability scores can be reduced below 
1 in this way.

When a character reaches venerable age, secretly roll his or her maximum age, which 
is the number from the Venerable column on Table: Aging Effects plus the result 
of the dice roll indicated on the Maximum Age column on that table, and records 
the result, which the player does not know. A character who reaches his or her 
maximum age dies of old age at some time during the following year.

The maximum ages are for player characters. Most people in the world at large die 
from pestilence, accidents, infections, or violence before getting to venerable 
age.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Aging Effects}
\centering
\begin{tabular}{l c c c c}
\textbf{Race} & \textbf{Middle Age\textsuperscript{1}} & \textbf{Old\textsuperscript{2}} & \textbf{Venerable\textsuperscript{3}} & \textbf{Maximum Age}\\
Human & 35 years & 53 years & 70 years & +2d20 years\\
Dwarf & 125 years & 188 years & 250 years & +2d100 years\\
Elf & 175 years & 263 years & 350 years & +4d100 years\\
Gnome & 100 years & 150 years & 200 years & +3d100 years\\
Half-elf & 62 years & 93 years & 125 years & +3d20 years\\
Half-orc & 30 years & 45 years & 60 years & +2d10 years\\
Halfling & 50 years & 75 years & 100 years & +5d20 years\\
\multicolumn{5}{l}{\textsuperscript{1} At middle age, -1 to Str, Dex, and Con; +1 to Int, Wis, and Cha.}\\
\multicolumn{5}{l}{\textsuperscript{2} At old age, -2 to Str, Dex, and Con; +1 to Int, Wis, and Cha.}\\
\multicolumn{5}{l}{\textsuperscript{3} At venerable age, -3 to Str, Dex, and Con; +1 to Int, Wis, and Cha.}\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Height and Weight}
%%%%%%%%%%%%%%%%%%%%%%%%%

The dice roll given in the Height Modifier column determines the character's extra 
height beyond the base height. That same number multiplied by the dice roll or 
quantity given in the Weight Modifier column determines the character's extra weight 
beyond the base weight.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Random Height and Weight}
\centering
\begin{tabular}{l c c c c}
\textbf{Race} & \textbf{Base Height} & \textbf{Height Modifier} & \textbf{Base Weight} & \textbf{Weight Modifier}\\
Human, male & 4' 10" & +2d10 & 120 lb. & x (2d4) lb.\\
Human, female & 4' 5" & +2d10 & 85 lb. & x (2d4) lb.\\
Dwarf, male & 3' 9" & +2d4 & 130 lb. & x (2d6) lb.\\
Dwarf, female & 3' 7" & +2d4 & 100 lb. & x (2d6) lb.\\
Elf, male & 4' 5" & +2d6 & 85 lb. & x (1d6) lb.\\
Elf, female & 4' 5" & +2d6 & 80 lb. & x (1d6) lb.\\
Gnome, male & 3' 0" & +2d4 & 40 lb. & x 1 lb.\\
Gnome, female & 2' 10" & +2d4 & 35 lb. & x 1 lb.\\
Half-elf, male & 4' 7" & +2d8 & 100 lb. & x (2d4) lb.\\
Half-elf, female & 4' 5" & +2d8 & 80 lb. & x (2d4) lb.\\
Half-orc, male & 4' 10" & +2d12 & 150 lb. & x (2d6) lb.\\
Half-orc, female & 4' 5" & +2d12 & 110 lb. & x (2d6) lb.\\
Halfling, male & 2' 8" & +2d4 & 30 lb. & x 1 lb.\\
Halfling, female & 2' 6" & +2d4 & 25 lb. & x 1 lb.\\
\end{tabular}
\end{table}
