\begin{minipage}[][][t]{0.5\linewidth}
\raceentry{Aasimar}
%\vspace{-2\baselineskip}
\textit{``My ancestors were more beautiful than you can imagine."}\\
~\\*
Aasimar are humans that have a beautiful outsider, usually but not always a celestial, somewhere in their ancestry.\\
\ability{Personality:}{Though mostly human, an aasimar's immortal heritage influences their mental development. Aasimar tend toward more extreme personalities, being especially quiet and introspective or particularly loud and boisterous. Most aasimar are very opinionated, and have strongly held beleifs.}\\
\ability{Physical Description:}{Aasimar look like especially beautiful humans, though they sometimes bear vestiges of their ancestry that denote them as being different (strangely colored eyes, silver-blonder or white hair, slightly `off' facial features).}\\
\ability{Society:}{Aasimar are typically born and raised in human societies, and gain the same customs of that culture.}\\
\ability{Alignment:}{Most aasimar are the descendants of celestials, and tend towards the good alignments. Rarely, an aasimar might instead have an infernal heritage, being the descendant of an erinyes or succubus. Such aasimar instead tend towards an evil alignment.}\\
\end{minipage}
\begin{minipage}{0.5\linewidth}
\rowcolors{1}{colorone}{colortwo}
\begin{tabu}to \linewidth{X[1, l, b]}
\header Aasimar Racial Traits \\
\ability{Type:}{Outsider (Native and Human Subtype)} \\
\ability{Size:}{Medium}\\
\ability{Speed }{30 foot}\\
\ability{Racial Ability Score Modifiers:}{+2 Wisdom, +2 Charisma}\\
\textbullet ~Aasimar with a Charisma of at least 10 may cast light as a spell-like ability with a caster level equal to their character level once per day.\\
\textbullet  ~+2 bonus to Spot, and Listen checks.\\
\ability{Automatic Languages:}{Common}\\
\ability{Bonus Languages:}{Abyssal, Aquan, Auran, Celestial, Formian, Ignan, Slaad, Sylvan, Terran.}\\
\ability{Favored Classes:}{Paladin and Sorcerer}\\
\end{tabu}
\rowcolors{1}{colorone}{colortwo}
\begin{tabularx}{\linewidth}{XXXX}
\header\multicolumn{4}{l}{Aasimar Starting Age}\\
\textbf{Adulthood:}&\textbf{Simple:}&\textbf{Moderate:}&\textbf{Complex:}\\
20 Years&+1d6&+2d6&+3d6\\
\end{tabularx}
\rowcolors{1}{colorone}{colortwo}
\begin{tabularx}{\linewidth}{XXXXX}
\header\multicolumn{5}{l}{Aasimar Height and Weight}\\
\textbf{Gender}&\textbf{Base Height}&\textbf{Height Mod.}&\textbf{Base Weight}&\textbf{Weight Mod.}\\
Male&4' 7"&+2d8&90 lb.&x(2d4) lb.\\
Female&4' 5"&+2d8&80 lb.&x(2d4) lb.\\
\end{tabularx}
\end{minipage}