%\begin{racebox}
\raceentry{Drow}{``Time to die for the Spider Queen."}

No description until we either obtain or write one.

\racedescription{NYW}

\racepersonality{NYW}

\racesociety{NYW}

\racealignment{NYW}

\racedatastart
\begin{racetable}
\type{Humanoid (Elf Subtype)}
\size{Medium}
\scores{+2 Dexterity, -2 Constitution}
\speed{30}
\senses{Darkvision 120'}
\autolanguages{Elvish}
\bonuslanguages{Abyssal, Beholder, Common, Draconic, Drow Sign Language, Dwarvish, Gnome, Kuo-Toa, Terran, Undercommon}
\favoredclasses{Cleric and Wizard}
\end{racetable}

\vspace{\baselineskip}
\agetable{20}{+1d6}{+2d6}{+3d6}

\vspace{\baselineskip}
\begin{heightweighttable}
\male{4' 7"}{+2d8}{90 lb.}{x(2d4)}
\female{4' 5"}{+2d8}{80 lb.}{x(2d4)}
\end{heightweighttable}
\racedataend

\racialtraits{
\racetrait{Daylight Sensitivity}{While in brightly lit surroundings (such as a daylight spell), a Drow suffers a -2 penalty to attack rolls and precision-based skill checks.}
\racetrait{Innate Magic}{Drow with a Charisma of at least 10 may cast deeper darkness (duration 4 hours), and fairie fire as spell-like abilities with a caster level equal to their character level once per day each.}
\racetrait{Magic Resistant}{+2 bonus to saving throws against spells and spell-like abilities.}
\racetrait{Skill Bonus}{+2 bonus to Spot and Listen checks.}
\racetrait{Elven Trance}{Drow never sleep and are immune to sleep effects. Drow must still perform their 4 hour daily trance to stay coherent and rested.}
\racetrait{Interesting Times}{Drow live an exceedingly interesting life and every Drow has proficiency with the rapier and an exotic ranged weapon of their choice.}
}
%\end{racebox}