%\begin{racebox}
\raceentry{Dwarf}{``I remember that..."}

Dwarves are (unfinished sentence, because I'm guessing that descriptive info is not OGL so this needs to be written wholecloth).

\racedescription{NYW}

\racepersonality{NYW}

\racesociety{NYW}

\racealignment{NYW}

\racedatastart
\begin{racetable}
\type{Humanoid (Dwarf subtype)}
\size{Medium}
\scores{+2 Constitution, --2 Charisma}
\speed{20}
\senses{Darkvision}
\autolanguages{Common, Dwarven}
\bonuslanguages{Giant, Gnome, Goblin, Orc, Terran, and Undercommon}
\favoredclasses{Fighter}
\end{racetable}

\vspace{\baselineskip}
\agetable{40}{+3d6}{+5d6}{+7d6}

\vspace{\baselineskip}
\begin{heightweighttable}
\male{3' 9"}{+2d4}{130 lb.}{x(2d6)}
\female{3' 7"}{+2d4}{100 lb.}{x(2d6)}
\end{heightweighttable}
\racedataend

\racialtraits{
\racetrait{Load Bearing}{Dwarves can move up to their full speed even when wearing medium or heavy armor or when carrying a medium or heavy load.}
\racetrait{Stonecunning}{This ability grants a dwarf a +2 racial bonus on Search checks to notice unusual stonework, such as sliding walls, stonework traps, new construction (even when built to match the old), unsafe stone surfaces, shaky stone ceilings, and the like. Something that isn’t stone but that is disguised as stone also counts as unusual stonework. A dwarf who merely comes within 10 feet of unusual stonework can make a Search check as if he or she were actively searching, and a dwarf can use the Search skill to find stonework traps as a rogue can. A dwarf can also intuit depth, sensing his or her approximate depth underground as naturally as a human can sense which way is up.}
\racetrait{Weapon Familiarity}{Dwarves may treat dwarven waraxes and dwarven urgroshes as martial weapons, rather than exotic weapons.}
\racetrait{Dwarven Stability}{A dwarf gains a +4 bonus on ability checks made to resist being bull rushed or tripped when standing on the ground (but not when climbing, flying, riding, or otherwise not standing firmly on the ground).}
\racetrait{Poison Resistant}{+2 racial bonus on saving throws against poison.}
\racetrait{Magic Resistant}{+2 racial bonus on saving throws against spells and spell-like effects.}
\racetrait{Racial Enmity}{+1 racial bonus on attack rolls against orcs and goblinoids.}
\racetrait{Giant Dodger}{+4 dodge bonus to Armor Class against monsters of the giant type.}
\racetrait{Forge Eye}{+2 racial bonus on Appraise checks that are related to stone or metal items.}
\racetrait{Forge Arm}{+2 racial bonus on Craft checks that are related to stone or metal.}
}
%\end{racebox}