%\begin{racebox}
\raceentry{Gnome}{``What's that you say little mole? Kobolds in the well!?"}

Nothing until we find or write it.

\racedescription{NYW}

\racepersonality{NYW}

\racesociety{NYW}

\racealignment{NYW}

\racedatastart
\begin{racetable}
\type{Humanoid (Gnome subtype)}
\size{Small}
\scores{+2 Constitution, --2 Strength}
\speed{20}
\senses{Low Light Vision}
\autolanguages{Common and Gnome}
\bonuslanguages{Draconic, Dwarven, Elven, Giant, Goblin, and Orc. In addition, a gnome can speak with a burrowing mammal (a badger, fox, rabbit, or the like).}
\favoredclasses{Bard}
\end{racetable}

\vspace{\baselineskip}
\agetable{40}{+4d6}{+6d6}{+9d6}

\vspace{\baselineskip}
\begin{heightweighttable}
\male{3' 0"}{+2d4}{40 lb.}{x(1)}
\female{2' 10"}{+2d4}{35 lb.}{x(1)}
\end{heightweighttable}
\racedataend

\racialtraits{
\racetrait{Weapon Familiarity}{Gnomes may treat gnome hooked hammers as martial weapons rather than exotic weapons.}
\racetrait{Desensitized to Illusions}{+2 racial bonus on saving throws against illusions.}
\racetrait{Practiced Illusions}{Add +1 to the Difficulty Class for all saving throws against illusion spells cast by gnomes. This adjustment stacks with those from similar effects.}
\racetrait{Racial Enmity}{+1 racial bonus on attack rolls against kobolds and goblinoids.}
\racetrait{+4 dodge bonus to Armor Class against monsters of the giant type.}
\racetrait{Big Ears}{+2 racial bonus on Listen checks.}
\racetrait{Gnomish Alchemy}{+2 racial bonus on Craft (alchemy) checks.}
\racetrait{Burrowers Tongue \sla}{Gnomes may cast \spell{speak with animals} once per day, though they may only speak with burrowing mammals and only for one minute).}
\racetrait{Innate Illusions \sla}{A gnome with a Charisma score of at least 10 may cast \spell{dancing lights}, \spell{ghost sound}, and \spell{prestidigitation} each once per day, with a caster level equal to their character level.}
}


%\end{racebox}