\classname{Arcane Strategist} \label{comm:prestige:arcanestrategist}
\vspace*{-8pt}
\quot{"Did they think they could fool a strategist like me? I have specialised in the use of fire all my life!"}

You plan things out ahead of time. In excruciating detail. And then kill people. With your plans.

\ability{Requirements:}{}
\listprereq
\itemability{Skills:}{Knowledge (Engineering) 8 ranks, Knowledge (Nature) 8 ranks and Knowledge (Tactics) 8 ranks }
\itemability{Spells:}{must be able to cast 3rd level Arcane spells}
\itemability{Special:}{must have followers or an army or a [Leadership] feat.}
\end{list} \vspace*{8pt}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Move Earth, Expert Tactician&+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Delay Spell, Mass Spell 1/Day &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Signal&+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Spell Trap, Mass Spell 2/Day &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Retributive Spell &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Spell Beacon, Mass Spell 3/Day &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Eight Trigrams Formation &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Artillery, Mass Spell 4/Day &+1 spellcaster level\\
9th &+4 &+3 &+3 &+6 &Conjure Battlefield &+1 spellcaster level\\
10th &+5 &+3 &+3 &+7 &TACTICAL GENIUS!, Mass Spell 5/Day &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Arcane Strategist prestige class.

\ability{Weapon and Armor Proficiency:}{Arcane Strategists gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, the Arcane Strategist casts spells (including gaining any new spell slots and spell knowledge) as if they had also gained a level in an arcane spellcasting class they had previous to gaining that level.}

\ability{Move Earth:}{The Arcane Strategist may cast Move Earth as a spell-like ability a number of times per day equal to her Int modifier.}

\ability{Expert Tactician:}{This feat is gained as a bonus feat.}

\ability{Delay Spell:}{The Arcane Strategist may Delay any spell they cast, except for the spells of their highest level available. A spell may be delayed by up to 3 rounds, chosen at the time of casting. After this delay, the spell goes off, just as if it had been cast only then.}

\ability{Mass Spell:}{Once per day, the Arcane Strategist may cast a Mass version of a spell, using the same spell slot as the original. This takes a full round action if it would normally take less time, or an extra full round action if it would take one round or more. The spell must be one that affects one or more targets, not an area of effect. It now affects one target per caster level. Every 2 levels, another daily use of this is granted.}

\ability{Signal Spell:}{With a full round action, the Arcane Strategist may declare a special strategy. All allies within hearing distance can be blessed with a Contingency for when the Arcane Strategist casts a specific spell, causing them to perform a Standard, Move or Full Round Action (stated at time of preparation) as an Immediate Action. This lasts until activated, the upcoming Dawn/Dusk/Noon/Midnight or the ability is used again (it overwrites current contingencies). \smallskip

An example could be "When I cast a Mass Haste, everyone make a Full Attack Action against an enemy you can reach." or "When I Fireball the enemies, everyone Charge them."}

\ability{Spell Trap:}{The Arcane Strategist may cast a spell as a Trap, as long as the spell usually affects an area of effect. The Trap is placed onto a 5' square and lasts until the upcoming Dawn/Dusk/Noon/Midnight, or until triggered, or until the maximum allowed is exceeded, where the oldest are removed first. The maximum allowed is the Arcane Strategist's Intelligence modifier. \smallskip

Enemies can detect the trap with a Search check equal to the save DC of the spell (if it doesn't have one normally, it is 10 + spell level + Int modifier). If someone steps into the square without Disabling it first, the spell goes off, only affecting the one square. All other effects are the same, and the square being trapped has to be adjacent to the Arcane Strategist.}

\ability{Retributive Spell:}{The Arcane Strategist may cast any Single Target spell as a Retributive spell, but may only have one up at a time. She becomes wreathed in magic for 1 minute or until struck in melee combat. If the latter occurs, the spell activates, affecting the attacker as though they were the original target of the spell.}

\ability{Spell Beacon:}{The Arcane Strategist may cast a spell as a Spell Beacon at a range of up to 20' per class level. The square targeted glows with a pillar of light, helping to direct allies to it. Whenever one of her allies touches the square, the spell is activated. This may be any multiple target, single target or area of effect spell, and is usually used to place buffs at vital objectives to help allies hold the positions. Some strategists are not above making the spells harmful, however, effectively setting orbital bombardments on their allies.}

\ability{Eight Trigrams Formation:}{With a Full Round Action, the Arcane Strategist can create a defensive barrier for her allies. Draw an imaginary line between every pair of allies, including the Arcane Strategist. These form Walls of Force for one round, and are filled with Acid Fog that does not affect her or her allies. \smallskip

Additionally, the Arcane Strategist and her allies gain the benefits (but not the drawbacks) of a Stoneskin effect for one round. Any foe who attacks the Arcane Strategist or any of her allies during this time but fails to deal any damage automatically becomes Exhausted for one minute. In this case, allies are only those within 50' of the Arcane Strategist, not those back home in Kansas.}

\ability{Artillery:}{Damaging spells cast by the Arcane Strategist begin to have tell-tale signs of their destructive capacity. When the Arcane Strategist casts Area of Effect spells that allow a save and primarily deal damage, her enemies may elect to dive for cover, becoming Prone and Cowering for 1 round, but automatically passing all saving throws. They can do this after rolling and failing, but doing so extends the Cowering to 2 rounds. While they remain Prone and Cowering, they continue to automatically pass saving throws against such spells cast by her.}

\ability{Conjure Battlefield:}{Once per day, the Arcane Strategist may transform the landscape into a favourable battlefield. One square mile gains the effects of Nightmare Terrain (the Arcane Strategist and her allies ignore this effect), and a trench network covers a third of the battlefield - the third closest the Strategist, providing Full Cover. Additionally, a full fortress set (as per the Warmage "Instant Fortress" ability) is conjured on her side, and spits out one Fireball per round. Finally, the middle third of the area is filled with a Stone Spikes effect. Should a major victory be scored, this ability may be used once more on that day.}

\ability{TACTICAL GENIUS!}{Once per day, the Arcane Strategist may perform a great tactical move, selecting one of two effects:
\begin{itemize}
  	\item{1) She and her allies are instantly Teleported Without Error or Gated to the precise point they wish to be, with a Timestop effect taking place upon arrival.}

	\item{2) A powerful magical ally is summoned, appearing anywhere the Arcane Strategist can see. Typical creatures include:}
		\begin{itemize}
  			\item{a Remorhaz with additional HD}
			\item{a Purple Worm (no sniggering there!) with additional HD}
			\item{a Colossal Adamantine Animated Siege Tower with a Catapult on top}
			\item{a Colossal Monstrous Vermin with additional HD}
		\end{itemize} 
\end{itemize}

The CR may be any amount up to your character level -2. The creature hangs around until one minute has passed, and usually just goes on a rampage, trying to deal as much damage to the enemy forces as possible.

This ability may be used once more in the day if a great victory is achieved.}

\ability{Great Victories:}{A decisive martial victory on the scale of annexing a decently-sized kingdom, or in lieu of conquest, a terror that was plaguing aforementioned decently-sized kingdom and threatened it with destruction/enslavement/more than just the heebiejeebies.

Optionally anything that involves great tactical coordination and represents the culmination of months if not years of planning and maneuvering might also qualify (for instance, courting, seducing and having sex with eight princesses at once, or convincing the entire planet to play a game of The Floor Is Lava (this can of course be really simple by actually turning the floor into lava)).}