\classname{Big Nob}  \label{comm:prestige:bignob}
\vspace*{-8pt}
\quot{"MY NAME IS HUGE!"}


In some cultures, being the biggest seriously makes you the best. You are viewed as the leader, and if someone smaller disagrees, they have to kill you. Even then, everyone is cheering for you, because you're bigger.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+1}
\itemability{Size:}{Large or larger}
\itemability{Feats:}{Leadership}
\itemability{Special:}{Must lead an army, or have led an army, in which you are/were the biggest.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Big Nob's class skills (and the key ability for each skill) have not yet been written}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{10cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+0&+0&Command Rating +1, Look Out Sir!\\
2&+2&+3&+0&+0&+1 Natural Armour, Intimidating Battlecry\\
3&+3&+3&+1&+1&Big Morale +1, Warstride\\
4&+4&+4&+1&+1&+1 Natural Armour, Minion See Minion Do\\
5&+5&+4&+1&+1&Command Rating +1, WAAAAAGH!\\
6&+6&+5&+2&+2&+1 Natural Armour, Get Over Here!\\
7&+7&+5&+2&+2&Big Morale +2, More WAAAAAGH!\\
8&+8&+6&+2&+2&+1 Natural Armour, Who's Scarier?\\
9&+9&+6&+3&+3&Command Rating +1, Worthy Sacrifice, My Name Is Huge\\
10&+10&+6&+3&+3&+1 Natural Armour, The Most WAAAAAGH!\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Big Nob class.

\ability{Weapon and Armor Proficiency:}{You gain proficiency with all armour and shields.}

\ability{Look Out, Sir!:}{As long as you have at least one minion, cohort or follower within your reach, you gain the benefits of Improved Evasion. However, if you elect to use it, one minion, cohort or follower within reach is killed. This does not result in a penalty or reduction to your Leadership score.}

\ability{Intimidating Battlecry:}{As a Swift action, when charging you can let out a battlecry. This allows you to make a demoralise attempt against all foes within 60' who can hear you. You receive a +2 bonus for every size category above Medium. Additionally, all allies within 60' gain a +20 ' bonus to their speed for one turn.}

\ability{Warstride:}{You can ignore all difficult terrain, and are in no way impeded by the corpses of your allies and/or enemies. You never slip on blood, or are blinded by sprays of blood, should such things ever be relevant (see: Kobold feats).}

\ability{Minion See, Minion Do:}{Whenever you attack a foe, all allies who could reach the foe by making a charge attack may do so as an Immediate action.}

\ability{WAAAAAGH!:}{You have such legend surrounding you, and your minions have so much faith in you, that you grow one size category, gaining all relevant bonuses and penalties.}

\ability{Get Over Here!:}{When you bellow at a foe, issuing a challenge, you scare them into approaching you so you can hit them. As a move action, you may issue this challenge to a foe who can see and hear you. If they fail a Will save (10 + \half HD + Cha) then they are Shakened and have to approach you (spending at least one move action getting nearer. They can totally charge you to do this, though). If they pass, they are not subject to the fear effect and can elect to pass on your challenge. Doing this, however, gives all of their underlings a -2 morale penalty for 1 minute because their leader is a chickenshit.}

\ability{More WAAAAAGH!:}{Your Leadership rating is unable to be lowered by anything, even if you personally elect to slaughter half your followers. Additionally, every follower within 30' may spend a standard action praising you, empowering your blows with the power of WAAAAAGH! This grants you +1d6 to all melee damage per simpering minion on your next turn.}

\ability{Who's Scarier?:}{You are immune to fear, as you are the scariest thing you know of. Your minions are also immune to fear from any source other than you.}

\ability{Worthy Sacrifice:}{Any time you take damage, you may elect for a minion, follower or cohort within reach to take this damage for you. This only works once per round, however. If ever you are rendered prone or shoved to another square, you can sacrifice a minion or follower within reach to negate this effect, squishing them flat.}

\ability{My Name Is Huge:}{You may elect to now have a very large, impressive name and title that all feel obliged to say in full. Any ability that could involve speaking your name, such as a Knight's challenge, any Truenaming effect, or similar, takes longer to perform, along this chart:
Less than Swift $\Rightarrow$ Swift $\Rightarrow$ Move $\Rightarrow$ Standard $\Rightarrow$ Full $\Rightarrow$ Minute $\Rightarrow$ *2}

\ability{The Most WAAAAAGH!:}{You gain another size category, along with all relevant bonuses and penalties. }