\classname{Bladesinger} \label{comm:prestige:bladesinger}
\vspace*{-8pt}
\quot{"They say my voice is terrible. Fortunately for you, I'm going to kill you with my sword instead."}

Unlike the arcane archer, which survived with its class abilities intact from 3.0 despite radical changes in the environment, the bladesinger has the singular honor of being one of the most-revised PrCs in third edition.  It's gone through no fewer than four distinct versions, first in Tome and Blood, then in the Tome and Blood web errata, then in Races of Faerun, and most recently in Complete Warrior.  It's varied from being about as effective as any full-BAB class (that is to say, not very) to complete and total uselessness.

\ability{Prerequisites:}{}
\listprereq
	\itemability{BAB:}{+3}
	\itemability{Race:}{Elf or half-elf}
	\itemability{Feats:}{Elusive Target}
	\itemability{Proficiencies:}{Proficient with all martial weapons and light armor.}
	\itemability{Skills:}{Balance 4 ranks, Concentration 4 ranks, Perform (dance) 2 ranks, Perform (sing) 2 ranks, Tumble 4 ranks.}
	\itemability{Spells:}{Ability to cast 1st-level arcane spells.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The bladesinger's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Escape Artist (Dex), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Ride (Dex), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Swim (Str), and Tumble (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+1&+0&+2&+2&Bladesong School, Minor Spellsong&+1 spellcasting level\\
2&+2&+0&+3&+3&Dance of Air, Lesser Spellsong&+1 spellcasting level\\
3&+3&+1&+3&+3&Blind Fighting&+1 spellcasting level\\
4&+4&+1&+4&+4&Dance of Blades&+1 spellcasting level\\
5&+5&+1&+4&+4&Insightful Strike&+1 spellcasting level\\
6&+6&+2&+5&+5&Dance of Death, Major Spellsong&+1 spellcasting level\\
7&+7&+2&+5&+5&Subtle Cut&+1 spellcasting level\\
8&+8&+2&+6&+6&Dance of Fury, Song of Celerity&+1 spellcasting level\\
9&+9&+3&+6&+6&Whirlwind&+1 spellcasting level\\
10&+10&+3&+7&+7&Bladesong Master, Martial Mage&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the bladesinger prestige class.

\ability{Weapon and Armor Proficiency:}{Bladesingers gain no new proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, a bladesinger casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in an arcane spellcasting class he had previous to gaining that level.}

\ability{Bladesong School:}{Bladesingers devote themselves to the study of a single type of weapon above all others.  Almost all bladesingers select light or one-handed weapons so they can wield them while also casting spells, but the exact weapon depends on a bladesinger's school, with swords the most popular choice.  They gain the Combat School feat for their chosen weapon.}

\ability{Minor Spellsong (Ex):}{A bladesinger does not suffer arcane spell failure from light armor.}

\ability{Dance of Air (Ex):}{Beginning at 2nd level, while wearing light or no armor and wielding his chosen weapon, a bladesinger gains a dodge bonus to AC equal to the level of the highest-level arcane spell he has prepared or the highest-level arcane spell slot he has unused.}

\ability{Lesser Spellsong (Ex):}{Starting at 2nd level, while wearing light or no armor and wielding his chosen weapon, a bladesinger may take 10 on Concentration checks to cast defensively.}

\ability{Blind Fighting:}{At 3rd level, a bladesinger gains Blind Fighting as a bonus feat.  If he already has it, he may select any Combat, Skill, or metamagic feat he meets the prerequisites for as a bonus feat instead.}

\ability{Dance of Blades (Ex):}{Beginning at 4th level, while wearing light or no armor, a bladesinger gains a bonus equal to one-half his class level when using or defending against trips, disarms, sunders, or feints with his chosen weapon.  He has the Edge against any opponent whose Dexterity, Intelligence, and Charisma are less than his Intelligence or his Charisma.}

\ability{Greater Spellsong (Ex):}{Starting at 4th level, when a bladesinger casts a spell while wearing light or no armor and wielding his chosen weapon, he does not provoke an attack of opportunity.}

\ability{Insightful Strike:}{At 5th level, a bladesinger gains Insightful Strike as a bonus feat. If he already has it, he may select any Combat, Skill, or metamagic feat he meets the prerequisites for as a bonus feat instead.}

\ability{Dance of Death (Su):}{Beginning at 6th level, a bladesinger's magic guides his blows to deadly accuracy.  While wearing light or no armor, as an immediate action after confirming a critical hit with his chosen weapon, a bladesinger can sacrifice a prepared spell or spell slot, as if he had cast it, and add the level of the spell to his critical multiplier for that hit.}

\ability{Major Spellsong (Ex):}{Starting at 6th level, whenever a bladesinger casts a spell while wearing light or no armor and wielding his chosen weapon, he gains a +3 dodge bonus to AC until the beginning of his next turn.}

\ability{Subtle Cut:}{At 7th level, a bladesinger gains Subtle Cut as a bonus feat.  If he already has it, he may select any Combat, Skill, or metamagic feat he meets the prerequisites for as a bonus feat instead.}

\ability{Dance of Fury (Ex):}{Beginning at 8th level, whenever a bladesinger makes a full attack with his chosen weapon while wearing light or no armor, he gains an additional attack at his full attack bonus.}

\ability{Song of Celerity (Ex):}{Starting at 8th level, while wearing light or no armor and wielding his chosen weapon, a bladesinger may cast spells at least four levels lower than the highest level he can cast as swift actions, as if he had applied the Quicken Spell feat to them.  In addition, he gains Quicken Spell as a bonus feat; if he already has it, he may select any Combat, Skill, or metamagic feat he meets the prerequisites for as a bonus feat instead.}

\ability{Whirlwind:}{At 9th level, a bladesinger gains Whirlwind as a bonus feat.  If he already has it, he may select any Combat, Skill, or metamagic feat he meets the prerequisites for as a bonus feat instead.}

\ability{Bladesong Master:}{At 10th level, a bladesinger masters his art and starts his own bladesong school.  He gains a +3 bonus to attack rolls and Armor Class against anyone wielding his chosen weapon; also, if he takes any Leadership feat [Leadership, for those not using RoW] he gains a +3 bonus to his Leadership score provided he takes a bladesinger as a cohort.}

\ability{Martial Mage (Ex):}{Beginning at 10th level, a bladesinger's Base Attack Bonus is equal to her highest arcane caster level, regardless of what class levels she has, but can't in any event be greater than her Hit Dice.}
