\classname{Crusader of the Elemental Forces} \label{comm:prestige:crusaderelemental}
\vspace*{-8pt}
\quot{"GOOOOOO, PLANET!"}

You have devoted your Knightly pursuits to the study of how to kill people with fire. And water. And air. And sometimes, for something different, with earth.

\ability{Requirements:}{}
\listprereq
\itemability{BAB:}{+10}
\itemability{Skills:}{Knowledge (the Planes) 13 ranks, Knowledge (Nature) 13 ranks}
\itemability{Special:}{Must have some form of attack that deals Fire, Electricity, Cold or Acid damage. Elemental Knights qualify by dint of existing.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skill Points at Each Level:}{4 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Elemental Resistances, Elemental Strike\\
2nd &+2 &+3 &+3 &+3 &Heart of Water, Drench, Elemental Mount\\
3rd &+3 &+3 &+3 &+3 &Heart of Earth, Earthen Grasp, Elemental Rage\\
4th &+4 &+4 &+4 &+4 &Heart of Air, Whirlwind, Storm of Elemental Fury\\
5th &+5 &+4 &+4 &+4 &Heart of Fire, Fiery Skin, Storm of Vengeance\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Crusader of the Elemental Forces prestige class.

\ability{Weapon and Armor Proficiency:}{Crusader of the Elemental Forces gain no proficiency with any weapon or armor.}

\ability{Elemental Resistances:}{The Crusader of the Elemental Forces receives Energy Resistance equal to 5 times their class level against Fire, Acid, Cold and Electricity. They are also unaffected by reasonably strong wind, fog, rain, muddy ground, quicksand, sandstorms, random lightning strikes, particularly hot weather or particularly cold weather.}

\ability{Elemental Strike:}{When dealing additional damage to a Designated Opponent, the Crusader may, on a successful hit, elect to either Soak the target (making them count as Entangled until dried), set them on fire, knock them prone with earthly might or cause the wind to carry them into the air, moving them up to 50' away. If multiple hits are made, multiple effects may be caused in the same round.}

\ability{Heart of Water:}{The Crusader has a permanent Heart of Water effect (Swim speed equal to Land Speed, Breathe Underwater, +5 enhancement bonus to Escape Artist). At any rime, the Crusader can elect to be affected by Freedom of Movement instead. This is a Swift Action to decide, and lasts until they change it back with another Swift Action. This is a Supernatural Ability.}

\ability{Drench:}{The Crusader gains the ability to drench others (and flames), just like a Water Elemental. This is a Supernatural ability.}

\ability{Elemental Mount:}{The Crusader gains a Mount to ride. This mount is loyal, and if it dies, another appears a day later. It can be any Elemental with a CR at least 3 less than the Crusader's character level. It can be ridden even if logic says otherwise, and causes no harm at all to the Crusader.}

\ability{Heart of Earth:}{The Crusader has a permanent Heart of Earth effect (+8 bonus to resist Trip/Overrun/Bull Rush and increased maximum HP of 30). Alternatively, with a Swift Action they may lose these effects and instead gain a Stoneskin effect that lasts until they use a Swift Action to change back. As long as both original Heart effects are active (not the alternate spell effects), the Crusader gains Light Fortification. This is a Supernatural Ability.}

\ability{Earthen Grasp:}{The Crusader can make the ground grab people who are standing on it. This is a Supernatural Ability that requires a Standard Action. She may use her own BAB and Strength to make a grapple attempt at a target within 50', but counts as a Colossal creature. If the foe is grappled, the Crusader can Concentrate to sustain this effect, constricting them and dealing 10d6 Crushing damage every round until the foe escapes.}

\ability{Elemental Rage:}{The Elemental Strike ability is enhanced. If the Crusader sets an enemy on fire, they burn brilliantly, taking 5d6 Fire damage per round and the DC to put the flames out becomes 10 + half the Crusader's Hit Dice + her Charisma modifier. If she soaks them, water floods their lungs and they drown enough to become Exhausted. If she knocks them prone they are Stunned for 1 round, and if she knocks them into the air, they are held in place as though by a Telekinetic Sphere, air whirling all about them.}

\ability{Heart of Air:}{The Crusader of the Elements gains a permanent Heart of Air effect (+10 enhancement bonus to Jump checks, 30' Flight (Average)). She may at any time unleash a Gust of Wind as a Swift action, but doing so deactivates the Heart of Air until her next turn. This is a Supernatural ability.}

\ability{Whirlwind:}{The Crusader may, with a Standard Action, transform into a tornado of sorts. Her ability scores and attributes all remain the same, however she has a constant 50\% Concealment and gains a Slam attack that deals 1d8+Str*1.5 Bludgeoning for a Medium Creature and buffets the target 20' away. She may also trap enemies inside the vortex like an Air Elemental. However, she does lose the ability to cast any spells and loses the benefits of Heart of Earth, Fire and Water. Changing back just requires a Swift Action.}

\ability{Storm of Elemental Fury:}{The Crusader may cast Storm of Elemental Fury three times per day as a Spell-like Ability, as long as she designated an opponent who did not strike her in the last turn. The opponent must be in the area of effect. The DC is 10 + half her hit dice + her Charisma modifier.}

\ability{Heart of Fire:}{The Crusader gains a permanent Heart of Fire effect (Fire Immunity, +10' enhancement bonus to speed). Alternatively, with a Swift Action she may swap it out for a Fire Shield, and change it back with another Swift action. If all four Hearts are active, she becomes immune to critical hits.}

\ability{Fiery Skin:}{Anyone who Grapples with the Crusader or strikes her with a melee weapon catches fire instantly.}

\ability{Storm of Vengeance:}{Once per day, the Crusader may cast Storm of Vengeance as a Supernatural Ability. It will last until the next dawn, dusk, noon or midnight (whichever comes first). Seriously.}