\classname{Eldritch Knight} \label{comm:prestige:eldritchknight}
\vspace*{-8pt}
\quot{``Yes, I do know how to use this sword I'm carrying.  Would you like me to prove it to you?"}

Unlike the arcane trickster, the Eldritch Knight is not based on a playable class at all, but rather on the ridiculous idea that full BAB is worth something.  Of course, anyone with even a cursory understanding of the game's mechanics realizes that full BAB is worth close to nothing at all, particularly when the alternative is undiluted awesomeness like full spellcasting.  However, people want a hybrid arcane-caster/melee class, judging by the number of times the concept's been reinvented, so I guess something like it ought to exist.

The basic problem with making this class work is that if you offered a wizard gestalt with the core fighter or barbarian, at the cost of a level of wizard casting, the wizard would \i{not be crazy} if they said no.  Any class that makes a wizard drop a level of casting to get into it, therefore, has to have not only full BAB, but class features better than core fighter or barbarian offers.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+1}
\itemability{Feats:}{Still Spell}
\itemability{Spells:}{Ability to cast 1st-level arcane spells.}
\itemability{Proficiencies:}{Must be proficient with all martial weapons, light armor, and shields.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Eldritch Knight's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+1&+2&+0&+2&Familiar, Martial Focus, Somatic Skill&+1 spellcasting level\\
2&+2&+3&+0&+3&Arcane Strike&+1 spellcasting level\\
3&+3&+3&+1&+3&Bonus Feat&+1 spellcasting level\\
4&+4&+4&+1&+4&Channel Spell&+1 spellcasting level\\
5&+5&+4&+1&+4&Enduring Spells&+1 spellcasting level\\
6&+6&+5&+2&+5&Improved Familiar&+1 spellcasting level\\
7&+7&+5&+2&+5&Stilled Casting&+1 spellcasting level\\
8&+8&+6&+2&+6&Bonus Feat&+1 spellcasting level\\
9&+9&+6&+3&+6&Sudden Quicken&+1 spellcasting level\\
10&+10&+7&+3&+7&Martial Mage&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the Eldritch Knight prestige class:

\ability{Weapon and Armor Proficiency:}{Eldritch Knights gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, a Eldritch Knight casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in an arcane spellcasting class he had previous to gaining that level.}

\ability{Familiar):}{Eldritch Knight levels stack with any other class levels that grant a familiar.  If an Eldritch Knight does not already have a familiar, he may summon one; his Eldritch Knight level determines its abilities.}

\ability{Martial Focus (Ex):}{An Eldritch Knight may imbue a masterwork melee weapon with magic, allowing it to act as a focus for his spells. Creating a martial focus requires a 24-hour ritual and 100 gp in magical enameling and gems to make the weapon suitable for this purpose.  Once finished, an Eldritch Knight wielding his martial focus may cast any spell that has a material component or arcane focus with a cost less than 1 gp without needing that component or focus.  For spells with foci or components that cost more than 1 gp, he must still have the component or focus at hand, as normal.  An Eldritch Knight may only have one martial focus at a time, but may recreate or change it by repeating the ritual.}

\ability{Somatic Skill (Ex):}{An Eldritch Knight has mastered using somatic components in armor and does not suffer arcane spell failure with any armor or shield he is proficient with.}

\ability{Arcane Strike (Ex):}{Beginning at 2nd level, an Eldritch Knight deals 1d6 bonus damage in melee for each level of the highest-level arcane spell he has prepared or the highest-level arcane spell slot he has unused, or his level in Eldritch Knight, whichever is lower. These bonus damage dice only apply to attacks granted by Base Attack Bonus.  He has the Edge on any opponents without spells or spell-like abilities.}

\ability{Bonus Feat (Ex):}{At 3rd and 8th levels, an Eldritch Knight gains a bonus metamagic or Combat feat; he must meet all prerequisites for this feat.}

\ability{Channel Spell(Ex):}{Starting at 4th level, an Eldritch Knight may channel spells through his martial focus.  For an Eldritch Knight to channel a spell, it must have a target, be a ray spell, or be an area spell that affects certain kinds of targets.  The Eldritch Knight takes a single standard action to cast the spell and make a single melee attack that, if it hits, causes the spell to take effect.  Spell resistance applies, and the channeled spell offers the same save or saves as the original spell; however, the Eldritch Knight gets a +3 bonus to penetrate spell resistance and a +2 bonus to save DCs with a channeled spell.  An Eldritch Knight may hold the charge on a channeled spell, as normal for touch spells.}

\ability{Enduring Spells(Ex):}{Beginning at 5th level, all of an Eldritch Knight's arcane spells have their durations doubled, as if he had applied the Extend Spell metamagic feat to them.  This does not change their level or casting time.  If he also has the Extend Spell metamagic feat, he can apply it to triple their durations.}

\ability{Improved Familiar (Ex):}{At 6th level, an Eldritch Knight gains Improved Familiar as a bonus feat.  If he already has Improved Familiar, he insteads gains a bonus metamagic or fighter [Combat, for those using RoW rules] feat he meets the prerequisities for.}

\ability{Stilled Casting (Ex):}{Starting at 7th level, all of an Eldritch Knight's arcane spells are stilled, as if he had applied the Still Spell metamagic feat to them.  This does not change their level or casting time.}

\ability{Sudden Quicken (Ex):}{At 9th level, an Eldritch Knight gains Sudden Quicken as a bonus feat.  If he already has Sudden Quicken, he insteads gains a bonus metamagic or fighter [Combat, for those using RoW rules] feat he meets the prerequisities for.}

\ability{Martial Mage (Ex):}{Beginning at 10th level, an Eldritch Knight's Base Attack Bonus is equal to his highest arcane caster level, regardless of what class levels he has, but can't in any event be greater than his Hit Dice.}