\classname{Holy Crusader} \label{comm:prestige:holycrusader}
\vspace*{-8pt}
\quot{"Through great action, we may make a difference. It is only through inaction under the guise of pacifism that we lose to the great evils."}

\ability{Requirements:}{}
\listprereq
\itemability{BAB:}{+5}
\itemability{Skills:}{Knowledge (the planes) 8 ranks, Knowledge (religion) 8 ranks}
\itemability{Feats:}{Blitz}
\itemability{Alignment:}{Any Good}
\itemability{Spellcasting:}{Must be able to form a Protection From or Magic Circle Against Evil at least once per day, as a spell or otherwise.}
\itemability{Special:}{Must have \emph{started} a fight with an Evil Outsider. Angelic Knights need only meet one of the two skill requirements (but still must be Good and have the Blitz feat).}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skill Points at Each Level:}{4 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+0 &+2 &Aura of Daylight, Celestial Plate, Take The Burden\\
2nd &+2 &+3 &+0 &+3 &Aura of Menace, Divine Mount, Incite Vigilance\\
3rd &+3 &+3 &+1 &+3 &Fiend Slayer, Commanding Voice, Angel Wings\\
4th &+4 &+4 &+1 &+4 &Holy Word, Smite Evil, Empower the Helpless\\
5th &+5 &+4 &+1 &+4 &Resurrection, Decry the Wicked, Angel Wings\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Holy Crusader prestige class.

\ability{Weapon and Armor Proficiency:}{Holy Crusaders gain no proficiency with any weapon or armor.}

\ability{Aura of Daylight:}{The Holy Crusader constantly emits Daylight, dealing damage to Undead within 30' equal to 1d6+Cha every round. They may suppress this ability at will if they want to sneak about or, you know, sleep.}

\ability{Celestial Plate:}{The Angels are so impressed by the Crusader that they give her a set of Adamantine Full Plate with an Enhancement bonus equal to her level divided by 4 (round down). Additionally, it grants DR 10/Good (making it useful when fighting Evil), and adds its Enhancement Bonus to armour to any damage rolls against creatures with the [Evil] subtype. Additionally, if the character has flight, they may still fly when wearing this, despite the weight.}

\ability{Take the Burden:}{With a Standard Action, the Holy Crusader may make a touch attack against an ally and ease their suffering. They may Cure 1d6 damage per hit die, receiving half the damage themselves, or may transfer one affliction (such as Nausea, a Poison or Disease, negative levels or Stunning) from the target to themselves. If they are immune to the affliction, they luck out and the affliction is just cured.}

\ability{Aura of Menace:}{A righteous aura surrounds Holy Crusaders that fight or get angry. Any hostile creature within a 20-foot radius of a Holy Crusader must succeed on a Will save (DC 10 + \half Hit Die + Charisma modifier) to resist its effects. Those who fail take a -2 penalty on attacks, AC, and saves for 24 hours or until they successfully hit the Holy Crusader that generated the aura. A creature that has resisted or broken the effect cannot be affected again by the same Holy Crusader’s aura for 24 hours.}

\ability{Divine Mount:}{The Holy Crusader is blessed with a special mount to ride. It is completely loyal, and if slain, another replaces it after 24 hours. The mount may be any [Good] Magical Beast (including Celestial Animals/Vermin), or a Half-Celestial Animal or Vermin, with a CR at least 3 less than the Crusader's hit dice.}

\ability{Incite Vigilance:}{As a Supernatural Ability once per hour, the Holy Crusader may drive allies to their limits, creating a Mass Haste effect. This is a verbal ability that requires a Move-Equivalent Action. The benefits also apply to the Crusader herself.}

\ability{Fiend Slayer:}{The Holy Crusader is especially trained to kill fiends, somewhere between an occupation, hobby and driving goal. When the Crusader strikes an [Evil, Extraplanar] Outsider, they lose access to one Spell-like or Supernatural ability of the Crusader's choice for one round per class level. Multiple strikes remove multiple abilities. If the fiend is left with no abilities and is struck again, they must make a Fortitude save (DC 10 + \half the Crusader's HD + their Charisma modifier) or be Destroyed (as per "Destruction").}

\ability{Commanding Voice:}{The Holy Crusader may caste Greater Command as a Spell-like Ability at will to anyone who failed to save against their Aura of Menace. The Save DC is equal to 10 + \half the Crusader's Hit Dice + their Charisma modifier.}

\ability{Angel Wings:}{At levels 3 and 5, the Holy Crusader receives a bonus [Celestial] feat. This must be a feat that grants wings.}

\ability{Holy Word:}{Three times per day, the Holy Crusader may cast Holy Word as a Supernatural Ability. Caster level equals hit dice and cannot be augmented beyond this.}

\ability{Smite Evil:}{Once per hour, the Holy Crusader may Smite Evil. This is a non-action that alters an attack that is about to be made, adding their Charisma modifier to the attack roll and hit dice to the damage roll. These benefits only apply to Evil enemies. Furthermore, Divine flames consume the target, treating them as on fire, except the damage is Holy.}

\ability{Empower the Helpless:}{Once per day as a Supernatural Ability, a Holy Crusader may grant great power to up to 2 NPCs per class level. The NPCs must have a CR of no more than 1 each. Once blessed, they become a frenzied mob of righteousness for 1 hour per class level. Treat them as a single Human Barbarian that happens to take up more space than usual and has the [Swarm] subtype, with a number of levels equal to the combined hit dice of all of the NPCs. They gain Strength and Constitution scores equal to 10 plus the class level of the Crusader, Dexterity 12, and the average Intelligence, Wisdom and Charisma of the mob.}

\ability{Resurrection:}{Once per day as a Supernatural Ability, the Holy Crusader may create a True Resurrection effect.}

\ability{Decry the Wicked:}{As a Standard Action at will, the Holy Crusader can shout out the sins of an Evil aligned foe. This is a verbal Supernatural Ability that extends out to 100 feet. The target must make a Will save or suffer from Heavy Encumbrance and become Fatigued for 1 minute. Every round, they suffer nonlethal damage equal to 2d6 plus the Crusader's hit dice.}
