\classname{Maelstrom of Fiery Ki} \label{comm:prestige:maelstrom}
\vspace*{-8pt}
\quot{"It was a mistake to make me unhappy.... SHI SHI HOUKUDAN!"}

You get very tense. It helps you fight better. Sometimes, you get so tense you explode and everyone dies.

\ability{Prerequisites:}{}
\listprereq
	\itemability{BAB:}{+7}
	\itemability{Special:}{Must posses a Super Gauge.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+2&Trouble Brewing, Rageblade\\
2&+2&+3&+3&+3&Ki Burst, Taste Your Own Blood\\
3&+3&+3&+3&+3&Tempest in a Tea Cup, Shadowrun\\
4&+4&+4&+4&+4&Flow of Violence, Overflowing Cup of Ki\\
5&+5&+4&+4&+4&Deadly Finishing Move, Ki Eruption\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Maelstrom of Fiery Ki prestige class.

\ability{Weapon and Armor Proficiency:}{The Maelstrom of Fiery Ki gains no proficiency with armor or weapons.}

\ability{Trouble Brewing:}{The Maelstrom of Fiery Ki builds up a lot of Tension, the kind that can only be eased off by applying violence to other people. In the face. Whenever struck, or striking an enemy, they gain 2 Tension instead of 1.}

\ability{Rageblade:}{When striking the subject of their Tension, the Maelstrom adds their current Tension to melee damage rolls. This is multiplied by critical hits, Leap Attack and so on.}

\ability{Ki Burst:}{As a Standard Action, the Maelstrom may unleash a wave of burning Ki energy at her foes. This has a radius of 5' per 2 points of Tension spent, and everyone in the area takes 1d6 Fire damage per Tension spent, up to a maximum of the Maelstrom's hit dice. Only half of this may be resisted/negated. Everyone in the area is subject to a Ref save for half damage (DC 10 + 1/2 the Maelstrom's HD + her Wis mod). Spending an additional 10 Tension transforms this into a Swift action.}

\ability{Taste Your Own Blood:}{The Maelstrom practically enjoys getting smacked around now. When suffering a critical hit, a sneak attack, any [Pain] effect, or any hit that reduces her to 25\% or less (including multiple little hits when already in the danger zone), she gains another 5 Tension.}

\ability{Tempest in a Tea Cup:}{The Maelstrom of Fiery Ki may now ignore attacks from others, focusing exclusively on the one building her Super Gauge. By doing so, she gains no Tension against anyone other than the designated foe, but as a result does not lose her Tension just because someone else slaps her up. If she turns and attacks them, the Tension is lost as normal. She can opt not to use this ability at any time. \smallskip

One side effect of this ability is she no longer loses her Tension after attacking a different target - the Tension is lost when the decision is made, thus preventing her from possibly being able to charge up against one person and release against another.}

\ability{Shadowrun:}{The Maelstrom can step onto the Ethereal Plane, and thus may walk on water or, for that matter, thin air as long as she ends her turn standing on something solid. It can be a flimsy tree branch or a bamboo pole, mind you, as long as it is a solid object. Furthermore, she may step through Walls of Force, treating them merely as 10' movement per wall, and can add her Intelligence modifier to her Initiative. \smallskip

If she already possesses this ability or later on gets it from continuing their life as a Sohei, she instead gains Poetry in Motion. If she manages to get that as well, then she gets a round of applause.}

\ability{Flow of Violence:}{Pain is a great teacher: it teaches us not to get hurt, usually. With a Swift Action, the Maelstrom may spend 10 Tension to gain the benefits of a single [Combat] feat for a number of rounds equal to her Wisdom modifier. Only one feat may be gained at a time in this manner.}

\ability{Overflowing Cup of Ki:}{The Maelstrom is such a tornado of fury that she gains twice as much Tension from all sources (10 from critical hits, sneak attacks, [Pain] effects and dangerously low health, 4 from hitting or getting hit).}

\ability{Deadly Finishing Move:}{By spending 20 Tension as a Standard Action, the Maelstrom may unleash a killer Destroyer move. This attack deals an additional 2d6 damage per Hit Die of the Maelstrom, and bypasses all Damage Reduction (including /-) and Regeneration. \smallskip

It also deals Strength Damage equal to the Maelstrom's Wisdom modifier, and the target must make either a Fortitude save or a Will save (Maelstrom's choice) or be slain instantly and completely destroyed. Not even ashes remain, and the soul is transported to the centre of the planet, on another plane (probably Hell). \smallskip

It should be mandated that the player name this move and either shout it out before unleashing it, or quietly state the name after the effects take place. And adopts a cool pose, with the name written in Kanji on pieces of paper and held up next to their head by another player. \smallskip

The target, if slain, does gain enough time to compose and recite a poem, however they cannot use this time for anything else. It's a poem and death, or death without sauce.}

\ability{Ki Eruption:}{At the cost of 20 additional Tension, Ki Burst may be used as an Immediate Action, interrupting enemy actions. If an interrupted enemy takes damage from this, their action automatically fails.}
