\classname{Meteor Ninja} \label{comm:prestige:meteorninja}
\vspace*{-8pt}
\quot{"Float like a butterfly, sting like an elephant"}

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+5}
\itemability{Size:}{Large or larger}
\itemability{Special:}{Either 8 or more ranks in Hide, or the ability to become Invisible.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Meteor Ninja's class skills (and the key ability for each skill) have not been written}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2&+0 &Sneak Attack +1d6, Hide in Plain Sight \\
2nd &+1 &+3 &+3 &+0 &Shadow Clone Technique\\
3rd &+2 &+3&+3 &+1&Sneak Attack +2d6, Blend In\\
4th &+3 &+4 &+4 &+1 &Aura of Silence, Assassin's Grasp\\
5th &+3 &+4 &+4 &+1 &Sneak Attack +3d6, Always Invisible\\
6th &+4 &+5 &+5 &+2 &Crushing Assassination, Who's Next?\\
7th &+5 &+5 &+5&+2&Sneak Attack +4d6, Meteor Dance\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Meteor Ninja class:

\ability{Sneak Attack:}{As per the Rogue. If you already have Sneak Attack, it stacks.}

\ability{Hide in Plain Sight:}{You can use the Hide skill even while being observed. As long as you are within 10 feet of some sort of shadow, you can hide yourself from view in the open without anything to actually hide behind. You cannot, however, hide in your own shadow. }

\ability{Shadow Clone Technique:}{As a standard action, you may conjure up shadow clones, using "Mirror Image" as a Supernatural ability. You may do this once per day per class level with a caster level equal to your character level.}

\ability{Blend In:}{As a mind-affecting effect, people forget that you are actually a giant, and forget that you don't belong where you are. As long as you are within 20' of at least 5 other people, you may cause all who see you to believe you are the same size as those other people and part of the group.}

\ability{Aura of Silence:}{This supernatural ability can be activated at will. It causes Silence to extend in an aura, filling the squares you occupy and extending 5' further in each direction.}

\ability{Assassin's Grasp:}{If you elect to grapple a flat-footed foe who is smaller than you, and succeed in the grapple attempt, you may cover their mouth to prevent them from making noise, and hide them against your body. If you are hidden, you remain hidden. Additionally, you may use your size to your advantage in strangling/crushing them. You deal normal unarmed damage, plus sneak attack, plus double your Strength bonus.
Additionally, you deal 2d6 damage per size category of difference.}

\ability{Always Invisible:}{As a Supernatural ability, you may make yourself Invisible at will with a standard action. You become visible as soon as you attack someone, but may spend a swift action to hide in plain sight once this happens.}

\ability{Crushing Assassination:}{You may, as a standard action, make a brutal attack against a flat-footed foe who is smaller than you. If you hit, the attack is automatically a critical hit, and the target is knocked prone. They are also hurled 5' for every 10 points of damage you deal. If they strike a wall, roll 1d6 for every 5' they are prevented from moving. If that is enough to destroy the wall, then it is destroyed and they continue to move. Otherwise, they take the damage.

Whether they make the full movement or not, the target then has to make a Fortitude save (DC is 10 + half your HD + your Str modifier) or be Stunned for 1d4 rounds.}

\ability{Who's Next?:}{When you deliver a Crushing Assassination, the Assassin's Grasp or a killing blow, every foe who can see you must make a Will save (DC 10 + half your HD + your Cha modifier) or cower for one round and be unable to attack you for one minute. If they are already suffering from any fear effect, or fail the save by 5 or more, they panic for 5 rounds. If they are under a fear effect AND fail the save by 5 or more, they fall comatose from fear for 3 rounds, and wake up frightened.}

\ability{Meteor Dance:}{You gain a limited form of flight, based on jumping. You gain a flight speed equal to your land speed, however this cannot be used to charge or run, and you must both start and end your movement on a solid surface.

If you use this flight to move into the square of a foe, then you may make a Jump check. Should this beat the attack roll they make for an Attack of Opportunity, you avoid the AoO entirely. Additionally, by leaping into their square (AoO hitting or otherwise), you slam your momentum-charged body into them, knocking them prone and delivering 3d6 damage per size category above Medium, plus double your Strength modifier.}
