\classname{Ogre Mage}  \label{comm:prestige:ogremage}
\vspace*{-8pt}
\quot{"BIG MAN CASTS BIG SPELLS!"}


The Ogre-Mage monster in the MM can fuck right off. Seriously, it has several "run away" abilities, a few other random spells and no general theme. It also stops trying to be a closet troll (despite Invisibility being ideal for that) and so doesn't hit as hard as you'd think a creature of its CR does. So here's a new one, as a Prestige Class.


\ability{Prerequisites:}{}
\listprereq
\itemability{Size:}{Large or larger}
\itemability{Feats:}{Enlarge Spell}
\itemability{Spellcasting:}{must be able to cast 3rd level Arcane Spells}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{I don't care, and neither should you.}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+2 &+0 &+2 &Big Magic &+1 spellcaster level\\
2nd &+1 &+3 &+0 &+3 &Extend Spell, Heighten Spell &+1 spellcaster level\\
3rd &+1 &+3 &+1 &+3 &Large Familiar, Widen Spell&+1 spellcaster level\\
4th &+2 &+4 &+1 &+4 &Empower Spell, Reach Spell &+1 spellcaster level\\
5th &+2 &+4 &+1 &+4 &Gargantuan Magic &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\ability{Big Magic:}{The Ogre Mage may apply any of the following meta-magic feats (Enlarge Spell, Empower Spell, Extend Spell, Reach Spell, Widen Spell) without adjusting the casting time or spell level, a total number of times per day equal to 3 plus its Charisma modifier.}

\ability{Bonus Feats:}{The various metamagic feats are gained as bonus feats.}

\ability{Large Familiar:}{the Ogre Mage gains a familiar at level 3. Unlike normal familiars, if it dies the Ogre Mage suffers no penalty other than a -2 morale penalty to attack rolls and Will saves for one hour. Another familiar can be summoned the very next day. The familiar can be any creature with a CR at least 4 less than the Ogre Mage's character level, and must be no smaller than one size category smaller than the Ogre Mage, and no larger than the Ogre Mage itself.}

\ability{Gargantuan Magic:}{Once per day, a 5th level Ogre Mage may enter a trance where its size helps launch gigantic waves of magical power. This trance lasts for one minute, and changes the range for all touch attack and targeted spells to "within sight," and changes all burst, spread, cylinder and emanation ranges to a radius of one mile per character level. Cones find their area tripled, and lines continue as far as the Ogre Mage can see.

Additionally, whenever a 5th level Ogre Mage casts a spell, any targets that are damaged must make a Fortitude save (with a DC equal to 10 + half its character level + Con modifier) or be knocked prone. }