\descfeat{Apprenticeship}
{New Mentor Types for the Lower Planes:}
While the race of a mentor is usually irrelevant, some mentors draw their knowledge and experience solely from their racial heritage and the magical radiations of their home plane. To choose one of these extraplanar mentors, the character must have at least 2 ranks in Knowledge (planes).\vspace*{\baselineskip}

	\shortability{Devil:}{A devil mentor is a powerful baatezu from the Nine Hells of Baator that has decided to share its knowledge with a worthy apprentice. An apprentice of this mentor gains an innate understanding of infernal contracts, and may use Knowledge(planes) to influence the attitude of any native of a plane that is aligned to law and evil, or any subject of a calling spell.}
	 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Knowledge (any one)\end{list} \vspace*{\baselineskip}

	\shortability{Demon:}{A demon mentor is a powerful tanar'ri from the Abyss, and it has forced his apprentices to hide a portion of his power. Once per month, you may use one of its spell-like abilities of a 2nd level effect or less.}
	 \vspace*{-\baselineskip}\listone \item Bluff \item Knowledge (Planes)\end{list} \vspace*{\baselineskip}

	\shortability{Yugoloth:}{While utterly evil, Yugoloth mentors are honorable in their own way and have been known to train apprentices in the dark arts. Apprentices of these fiends learn the true nature of evil, and may choose to count as evil for the prerequisites of feats or prestige classes, and for magical effects like spells or magic items.}
	 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Diplomacy\end{list} \vspace*{\baselineskip}

	\shortability{Demondand:}{A demondand mentor is a powerful fiend from Carceri. An apprentice of this mentor learns the arts of punishment at the hands of these extraplanar jailors, and may use Intimidate to influence a creature's attitude to Helpful by accepting a +10 to the DC of the check.}
	 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Intimidate\end{list} \vspace*{\baselineskip}