\classname{Ghoul Paragon}\label{class:ghoulparagon}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Ghoul Paragon's class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (local) (Int), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha), and Use Rope (Dex).}

\ability{Skills/Level:}{6 + Intelligence Bonus}\\

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort  Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+0 &Paralysis\\
2nd &+2 &+3 &+3 &+0 &Pestilence, +1d6 Sneak Attack\\
3rd &+3 &+3 &+3 &+1 &Stench, Improved Pestilence\\
\end{tabular}
\end{small}
\end{table}

\noindent All of the following are Class Features of the Ghoul Paragon class.

\ability{Weapon and Armor Proficiencies:}{The Ghoul Paragon gains no new armor or weapon proficiencies.}

\ability{Paralysis (Ex):}{Characters struck by a Ghoul Paragon's unarmed strikes or natural weapons must make a Fortitude save or become paralyzed for 1d4+1 rounds. The Save DC is Charisma based. Elves are immune to this effect.}

\ability{Pestilence (Ex):}{A Ghoul Paragon of 2nd level is immune to disease, but spreads it quite easily. Every disease the Ghoul Paragon is ever exposed to is retained within his body (at the very least, this includes ghoul fever), and every time the Ghoul Paragon inflicts lethal damage with an unarmed strike or natural weapon, he also exposes the target to one of those diseases.}

\ability{Sneak Attack (Ex):}{At 2nd level, the Ghoul Paragon gains a die of Sneak Attack as a Rogue. Levels of Ghoul Paragon stack with Rogue and similar classes for purposes of overcoming Uncanny Dodge.}

\ability{Stench (Ex):}{A Ghoul Paragon of 3rd level stinks so dreadfully that all other creatures within 10 feet must make a Fortitude save or become sickened for 10 minutes. A creature which successfully saves may not be affected by the Ghoul Paragon's stench for 24 hours. This is a Poison effect, the save is Constitution based.}

\ability{Improved Pestilence (Su):}{At 3rd level a Ghoul Paragon becomes able to magically speed up the disease process in his victims. The initial incubation period for any disease he passes with the Pestilence power becomes 1 round, and the save DC of any such disease is now Charisma based.}
