\descfeat{Psuedoelemental Being [Racial]}{You are a psuedoelemental being, with rare and unique powers.}
\shortability{Prerequisite:}{Elemental-Bodied.}
\shortability{Benefits:}{Instead of picking a normal elemental type as an elemental-bodied, select one of the following other planes: Ice, Magma, Shadow, or Wood.  You gain benefits as follows for the type you've picked:
\begin{list}{}{\itemspace}
    \item Ice: You gain the (Cold) subtype, a 30' base land speed, a 30' swim speed, and +2 to Str.  Your melee attacks do 1d6 bonus Cold damage.  You speak Aquan and Auran.
    \item Magma: You gain both the (Earth) and (Fire) subtypes. Your base land speed is 20', and you gain +2 Str. Otherwise you gain the full benefits of both elements.
    \item Shadow: You have a 30' base land speed and a Fly speed of 10', with good maneuverability, and gain +2 Dex. You are \emph{invisible} in any lighting less than bright light. You speak Common. Despite your affiliation to the Plane of Shadow instead of to the Inner Planes, you still qualify for [Elemental] feats.
    \item Wood: You have no elemental subtype, and gain +2 Con and a 10' Climb speed. You gain Regeneration 0, penetrable by Fire and Slashing weapons, which improves to Regeneration equal to your level in areas of natural daylight or equivalent brightness (such as a \emph{daylight} spell). You only gain natural healing if you spend at least 8 hours/day in such brightness. You count as a Plant, in addition to an Elemental, for all effects relating to type. You speak your choice of Sylvan or Treant, and any Elemental language.
\end{list}
Other Dual-element types than Magma, such as Ooze (Water and Earth), Smoke (Air and Fire), Vapor (Water and Air), and so on are possible.}
\shortability{Special:}{This feat can only be taken at 1st level.}


