\newcommand{\spelldesc}[3]{\featname{#1}
\begin{small}
#2
\end{small}

#3
\vspace{12pt}}

\spelldesc{Mass Righteous Might}
{\shortability{Transmutation}{}
\shortability{Level:}{Courage 9}
\shortability{Range:}{Close}
\shortability{Targets:}{One or more allies, no two of which can be more than 30ft apart}
\shortability{Duration:}{1 minute/level}}
{This spell functions identically to righteous might, except as noted above.}

\spelldesc{Mnemonic Enhancer}
{\shortability{Transmutation}{}
\shortability{Level:}{Wiz 4}
\shortability{Components:}{V, S, M, F}
\shortability{Casting Time:}{10 minutes}
\shortability{Range:}{Personal}
\shortability{Target:}{You}
\shortability{Duration:}{Instantaneous}}
{Casting this spell allows you to prepare additional spells or retain spells recently cast. Pick one of these two versions when the spell is cast.

\listone
    \itemability{Prepare}{\\You prepare up to three additional levels of spells, as a wizard. A cantrip counts as ½ level for this purpose. You cast these spells using the same caster level and attributes as the mnemonic enhancer. Later castings of the prepare effect completely supercede earlier ones.}

    \itemability{Retain}{\\You retain any spell of 3rd level or lower that you had cast up to 1 round before you started casting the mnemonic enhancer. This restores the previously cast spell to your mind.}
\end{list}

In either event, the spell or spells prepared or retained fade after 24 hours (if not cast).

\ability{Material Component:}{A piece of string, and ink consisting of squid secretion with black dragon’s blood.}

\shortability{Focus:}{An ivory plaque of at least 50 gp value.}}