%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Arcane Archer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become an arcane archer, a character must fulfill all the following 
criteria.

\textbf{Race:} Elf or half-elf.

\textbf{Base Attack Bonus:} +6.

\textbf{Feats:} Point Blank Shot, Precise Shot, Weapon Focus (longbow or shortbow).

\textbf{Spells:} Ability to cast 1st-level arcane spells.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d8.

\textbf{Class Skills}

The arcane archer's class skills (and the key ability for each skill) are \linkskill{Craft} 
(Int), \linkskill{Hide} (Dex), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Ride} (Dex), \linkskill{Spot} (Wis), \linkskill{Survival} 
(Wis), and \linkskill{Use Rope} (Dex).

\textbf{Skill Points at Each Level:} 4 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Arcane Archer}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} \\
1st & +1 & +2 & +2 & +0 & Enhance Arrow +1 \\
2nd & +2 & +3 & +3 & +0 & Imbue Arrow \\
3rd & +3 & +3 & +3 & +1 & Enhance Arrow +2 \\
4th & +4 & +4 & +4 & +1 & Seeker Arrow \\
5th & +5 & +4 & +4 & +1 & Enhance Arrow +2 \\
6th & +6 & +5 & +5 & +2 & Phase Arrow \\
7th & +7 & +5 & +5 & +2 & Enhance Arrow +2 \\
8th & +8 & +6 & +6 & +2 & Hail of Arrows\\
9th & +9 & +6 & +6 & +3 & Enhance Arrow +2 \\
10th & +10 & +7 & +7 & +3 & Arrow of Death\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the arcane archer prestige class.

\textbf{Weapon and Armor Proficiency:} An arcane archer is proficient with all 
simple and martial weapons, light armor, medium armor, and shields.

\textbf{Enhance Arrow (Su):} At 1st level, every nonmagical arrow an arcane archer 
nocks and lets fly becomes magical, gaining a +1 enhancement bonus. Unlike magic 
weapons created by normal means, the archer need not spend experience points or 
gold pieces to accomplish this task. However, an archer's magic arrows only function 
for her. For every two levels the character advances past 1st level in the prestige 
class, the magic arrows she creates gain +1 greater potency (+1 at 1st level, +2 
at 3rd level, +3 at 5th level, +4 at 7th level, and +5 at 9th level).

\textbf{Imbue Arrow (Sp):} At 2nd level, an arcane archer gains 
the ability to place an area spell upon an arrow. When the arrow is fired, the 
spell's area is centered on where the arrow lands, even if the spell could normally 
be centered only on the caster. This ability allows the archer to use the bow's 
range rather than the spell's range. It takes a standard action to cast the spell 
and fire the arrow. The arrow must be fired in the round the spell is cast, or 
the spell is wasted.

\textbf{Seeker Arrow (Sp):} At 4th level, an arcane archer can 
launch an arrow once per day at a target known to her within range, and the arrow 
travels to the target, even around corners. Only an unavoidable obstacle or the 
limit of the arrow's range prevents the arrow's flight. This ability negates cover 
and concealment modifiers, but otherwise the attack is rolled normally. Using this 
ability is a standard action (and shooting the arrow is part of the action).

\textbf{Phase Arrow (Sp):} At 6th level, an arcane archer can 
launch an arrow once per day at a target known to her within range, and the arrow 
travels to the target in a straight path, passing through any nonmagical barrier 
or wall in its way. (Any magical barrier stops the arrow.) This ability negates 
cover, concealment, and even armor modifiers, but otherwise the attack is rolled 
normally.

Using this ability is a standard action (and shooting the arrow is part of the 
action).

\textbf{Hail of Arrows (Sp):} In lieu of her regular attacks, 
once per day an arcane archer of 8th level or higher can fire an arrow at each 
and every target within range, to a maximum of one target for every arcane archer 
level she has earned. Each attack uses the archer's primary attack bonus, and each 
enemy may only be targeted by a single arrow.

\textbf{Arrow of Death (Sp):} At 10th level, an arcane archer 
can create an \textit{arrow of death} that forces the target, if damaged by the 
arrow's attack, to make a DC 20 Fortitude save or be slain immediately. It takes 
one day to make an \textit{arrow of death}, and the arrow only functions for the 
arcane archer who created it. The \textit{arrow of death} lasts no longer than 
one year, and the archer can only have one such arrow in existence at a time.
