%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Assassin}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become an assassin, a character must fulfill all the following criteria.

\textbf{Alignment:} Any evil.

\textbf{Skills:} \linkskill{Disguise} 4 ranks, \linkskill{Hide} 8 ranks, \linkskill{Move Silently} 8 ranks.

\textbf{Special:} The character must kill someone for no other reason than to join 
the assassins.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d6.

\textbf{Class Skills}

The assassin's class skills (and the key ability for each skill) are \linkskill{Balance} (Dex), 
\linkskill{Bluff} (Cha), \linkskill{Climb} (Str), \linkskill{Craft} (Int), \linkskill{Decipher Script} (Int), \linkskill{Diplomacy} (Cha), 
\linkskill{Disable Device} (Int), \linkskill{Disguise} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Forgery} (Int),
\linkskill{Gather Information} (Cha), \linkskill{Hide} (Dex), \linkskill{Intimidate} (Cha), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Open Lock} (Dex), \linkskill{Search} (Int), \linkskill{Sense Motive} (Wis), \linkskill{Sleight of Hand} 
(Dex), \linkskill{Spot} (Wis), \linkskill{Swim} (Str), \linkskill{Tumble} (Dex), \linkskill{Use Magic Device} (Cha), and \linkskill{Use Rope} 
(Dex). 

\textbf{Skill Points at Each Level:} 4 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Assassin}
\centering
\begin{tabular}{*{6}{l}*{4}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} \\
1st & +0 & +0 & +2 & +0 & Sneak Attack +1d6, Death Attack, Poison Use, Spells & 0 & - & - & - \\
2nd & +1 & +0 & +3 & +0 & +1 save against poison, Uncanny Dodge & 1 & - & - & - \\
3rd & +2 & +1 & +3 & +1 & Sneak Attack +2d6 & 2 & 0 & - & - \\
4th & +3 & +1 & +4 & +1 & +2 save against poison & 3 & 1 & - & - \\
5th & +3 & +1 & +4 & +1 & Sneak Attack +3d6, Improved Uncanny Dodge & 3 & 2 & 0 & - \\
6th & +4 & +2 & +5 & +2 & +3 save against poison & 3 & 3 & 1 & - \\
7th & +5 & +2 & +5 & +2 & Sneak Attack +4d6 & 3 & 3 & 2 & 0 \\
8th & +6 & +2 & +6 & +2 & +4 save against poison, Hide In Plain Sight & 3 & 3 & 3 & 1 \\
9th & +6 & +3 & +6 & +3 & Sneak Attack +5d6 & 3 & 3 & 3 & 2 \\
10th & +7 & +3 & +7 & +3 & +5 save against poison & 3 & 3 & 3 & 3 \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the assassin prestige class.

\textbf{Weapon and Armor Proficiency:} Assassins are proficient with the crossbow 
(hand, light, or heavy), dagger (any type), dart, rapier, sap, shortbow (normal 
and composite), and short sword. Assassins are proficient with light armor but 
not with shields.

\textbf{Sneak Attack:} This is exactly like the rogue ability of the same name. 
The extra damage dealt increases by +1d6 every other level (2nd, 4th, 6th, 8th, 
and 10th). If an assassin gets a sneak attack bonus from another source the bonuses 
on damage stack.

\textbf{Death Attack:} If an assassin studies his victim for 3 rounds and then 
makes a sneak attack with a melee weapon that successfully deals damage, the sneak 
attack has the additional effect of possibly either paralyzing or killing the target 
(assassin's choice). While studying the victim, the assassin can undertake other 
actions so long as his attention stays focused on the target and the target does 
not detect the assassin or recognize the assassin as an enemy. If the victim of 
such an attack fails a Fortitude save (DC 10 + the assassin's class level + the 
assassin's Int modifier) against the kill effect, she dies. If the saving throw 
fails against the paralysis effect, the victim is rendered helpless and unable 
to act for 1d6 rounds plus 1 round per level of the assassin. If the victim's saving 
throw succeeds, the attack is just a normal sneak attack. Once the assassin has 
completed the 3 rounds of study, he must make the death attack within the next 
3 rounds.

If a death attack is attempted and fails (the victim makes her save) or if the 
assassin does not launch the attack within 3 rounds of completing the study, 3 
new rounds of study are required before he can attempt another death attack.

\textbf{Poison Use:} Assassins are trained in the use of poison and never risk 
accidentally poisoning themselves when applying poison to a blade.

\textbf{Spells:} Beginning at 1st level, an assassin gains the ability to cast 
a number of arcane spells. To cast a spell, an assassin must have an Intelligence 
score of at least 10 + the spell's level, so an assassin with an Intelligence of 
10 or lower cannot cast these spells. Assassin bonus spells are based on Intelligence, 
and saving throws against these spells have a DC of 10 + spell level + the assassin's 
Intelligence bonus. When the assassin gets 0 spells per day of a given spell level 
he gains only the bonus spells he would be entitled to based on his Intelligence 
score for that spell level.

The assassin's spell list appears below. An assassin casts spells just as a bard 
does.

Upon reaching 6th level, at every even-numbered level after that (8th and 10th), 
an assassin can choose to learn a new spell in place of one he already knows. The 
new spell's level must be the same as that of the spell being exchanged, and it 
must be at least two levels lower than the highest-level assassin spell the assassin 
can cast. An assassin may swap only a single spell at any given level, and must 
choose whether or not to swap the spell at the same time that he gains new spells 
known for that level.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Assassin Spells Known}
\centering
\begin{tabular}{l*{4}{c}}
\textbf{Level} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th}\\
1st & 2\textsuperscript{1} & - & - & -\\
2nd & 3 & - & - & -\\
3rd & 3 & 2\textsuperscript{1} & - & -\\
4th & 4 & 3 & - & -\\
5th & 4 & 3 & 2\textsuperscript{1} & -\\
6th & 4 & 4 & 3 & -\\
7th & 4 & 4 & 3 & 2\textsuperscript{1}\\
8th & 4 & 4 & 4 & 3\\
9th & 4 & 4 & 4 & 3\\
10th & 4 & 4 & 4 & 4\\
\multicolumn{5}{p{7cm}}{\textsuperscript{1}Provided the assassin has sufficient Intelligence to have a bonus spell of this level.}\\
\end{tabular}
\end{table}

\textbf{Save Bonus against Poison:} The assassin gains a natural saving throw bonus 
to all poisons gained at 2nd level that increases by +1 for every two additional 
levels the assassin gains.

\textbf{Uncanny Dodge (Ex):} Starting at 2nd level, an assassin retains his Dexterity 
bonus to AC (if any) regardless of being caught flat-footed or struck by an invisible 
attacker. (He still loses any Dexterity bonus to AC if immobilized.)

If a character gains uncanny dodge from a second class the character automatically 
gains improved uncanny dodge (see below).

\textbf{Improved Uncanny Dodge (Ex):} At 5th level, an assassin can no longer be 
flanked, since he can react to opponents on opposite sides of him as easily as 
he can react to a single attacker. This defense denies rogues the ability to use 
flank attacks to sneak attack the assassin. The exception to this defense is that 
a rogue at least four levels higher than the assassin can flank him (and thus sneak 
attack him).

If a character gains uncanny dodge (see above) from a second class the character 
automatically gains improved uncanny dodge, and the levels from those classes stack 
to determine the minimum rogue level required to flank the character.

\textbf{Hide in Plain Sight (Su):} At 8th level, an assassin can use the Hide skill 
even while being observed. As long as he is within 10 feet of some sort of shadow, 
an assassin can hide himself from view in the open without having anything to actually 
hide behind.

He cannot, however, hide in his own shadow.

%%%
\subsubsection{Assassin Spell List}
%%%

Assassins choose their spells from the following list:

\textbf{1st Level:} \linkspell{Disguise Self}, \linkspell{Detect Poison}, \linkspell{Feather Fall}, \linkspell{Ghost Sound}, \linkspell{Jump}, \linkspell{Obscuring Mist}, \linkspell{Sleep}, \linkspell{True Strike}.

\textbf{2nd Level:} \linkspell{Alter Self}, \linkspell{Cat's Grace}, \linkspell{Darkness}, \linkspell{Fox's Cunning}, \linkspell{Illusory Script}, \linkspell{Invisibility}, \linkspell{Pass Without Trace}, \linkspell{Spider Climb}, \linkspell{Undetectable Alignment}.

\textbf{3rd Level:} \linkspell{Deep Slumber}, \linkspell{Deeper Darkness}, \linkspell{False Life}, \linkspell{Magic Circle Against Good}, \linkspell{Misdirection}, \linkspell{Nondetection}.

\textbf{4th Level:} \linkspell{Clairaudience/Clairvoyance}, \linkspell{Dimension Door}, \linkspell{Freedom of Movement}, \linkspell{Glibness}, \linkspell{Greater Invisibility}, \linkspell{Locate Creature}, \linkspell{Modify Memory}, \linkspell{Poison}.
