%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Blackguard}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a blackguard, a character must fulfill all the following criteria.

\textbf{Alignment:} Any evil.

\textbf{Base Attack Bonus:} +6.

\textbf{Skills:} \linkskill{Hide} 5 ranks, \linkskill{Knowledge} (religion) 2 ranks. 

\textbf{Feats:} \linkfeat{Cleave}, \linkfeat{Improved Sunder}, \linkfeat{Power Attack}.

\textbf{Special:} The character must have made peaceful contact with an evil outsider 
who was summoned by him or someone else.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d10.

\textbf{Class Skills}

The blackguard's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Handle Animal} (Cha), \linkskill{Heal} (Wis), \linkskill{Hide} (Dex), 
\linkskill{Intimidate} (Cha), \linkskill{Knowledge} (religion) (Int), \linkskill{Profession} (Wis), and \linkskill{Ride} (Dex). 

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Assassin}
\centering
\begin{tabular}{*{6}{l}*{4}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} \\
1st & +1 & +2 & +0 & +0 & Aura of Evil, Detect Good, Poison Use & 0 & - & - & - \\
2nd & +2 & +3 & +0 & +0 & Dark Blessing, Smite Good 1/day & 1 & - & - & - \\
3rd & +3 & +3 & +1 & +1 & Command Undead, Aura of Despair & 1 & 0 & - & - \\
4th & +4 & +4 & +1 & +1 & Sneak Attack +1d6 & 1 & 1 & - & - \\
5th & +5 & +4 & +1 & +1 & Fiendish Servant, Smite Good 2/day & 1 & 1 & 0 & - \\
6th & +6 & +5 & +2 & +2 & -- & 1 & 1 & 1 & - \\
7th & +7 & +5 & +2 & +2 & Sneak Attack +2d6 & 2 & 1 & 1 & 0 \\
8th & +8 & +6 & +2 & +2 & -- & 2 & 1 & 1 & 1 \\
9th & +9 & +6 & +3 & +3 & -- & 2 & 2 & 1 & 1 \\
10th & +10 & +7 & +3 & +3 & Sneak Attack +3d6, Smite Good 3/day & 2 & 2 & 2 & 1 \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the blackguard prestige class.

\textbf{Weapon and Armor Proficiency:} Blackguards are proficient with all simple 
and martial weapons, with all types of armor, and with shields.

\textbf{Aura of Evil (Ex):} The power of a blackguard's aura of evil (see the \linkspell{Detect Evil} spell) is equal to his class level plus his cleric level, if any.

\textbf{Detect Good (Sp):} At will, a blackguard can use \linkspell{Detect Good} as a spell-like ability, duplicating the effect of the \textit{detect good} spell.

\textbf{Poison Use:} Blackguards are skilled in the use of poison and never risk 
accidentally poisoning themselves when applying poison to a blade.

\textbf{Dark Blessing (Su):} A blackguard applies his Charisma modifier (if positive) 
as a bonus on all saving throws.

\textbf{Spells:} A blackguard has the ability to cast a small number of divine 
spells. To cast a blackguard spell, a blackguard must have a Wisdom score of at 
least 10 + the spell's level, so a blackguard with a Wisdom of 10 or lower cannot 
cast these spells.

Blackguard bonus spells are based on Wisdom, and saving throws against these spells 
have a DC of 10 + spell level + the blackguard's Wisdom modifier. When the blackguard 
gets 0 spells per day of a given spell level he gains only the bonus spells he 
would be entitled to based on his Wisdom score for that spell level. The blackguard's 
spell list appears below. A blackguard has access to any spell on the list and 
can freely choose which to prepare, just as a cleric. A blackguard prepares and 
casts spells just as a cleric does (though a blackguard cannot spontaneously cast 
\textit{cure} or \textit{inflict} spells).

\textbf{Smite Good (Su):} Once a day, a blackguard of 2nd level or higher may attempt 
to smite good with one normal melee attack.

He adds his Charisma modifier (if positive) to his attack roll and deals 1 extra 
point of damage per class level. If a blackguard accidentally smites a creature 
that is not good, the smite has no effect but it is still used up for that day.

At 5th level, and again at 10th level, a blackguard may smite good one additional 
time per day.

\textbf{Aura of Despair (Su):} Beginning at 3rd level, the blackguard radiates 
a malign aura that causes enemies within 10 feet of him to take a -2 penalty on 
all saving throws.

\textbf{Command Undead (Su):} When a blackguard reaches 3rd level, he gains the 
supernatural ability to command and rebuke undead. He commands undead as would 
a cleric of two levels lower.

\textbf{Sneak Attack:} This ability, gained at 4th level, is like the rogue ability 
of the same name. The extra damage increases by +1d6 every third level beyond 4th 
(7th and 10th). If a blackguard gets a sneak attack bonus from another source the 
bonuses on damage stack.

%%%
\subsubsection{Blackguard Spell List}
%%%

Blackguards choose their spells from the following list:

\textbf{1st Level:} \linkspell{Cause Fear}, \textit{Corrupt Weapon}, \linkspell{Cure Light Wounds}, \linkspell{Doom}, \linkspell{Inflict Light Wounds}, \linkspell{Magic Weapon}, \linkspell{Summon Monster I}*.

\textbf{2nd Level:} \linkspell{Bull's Strength}, \linkspell{Cure Moderate Wounds}, \linkspell{Darkness}, \linkspell{Death Knell}, \linkspell{Eagle's Splendor}, \linkspell{Inflict Moderate Wounds}, \linkspell{Shatter}, \linkspell{Summon Monster II}*.

\textbf{3rd Level:} \linkspell{Contagion}, \linkspell{Cure Serious Wounds}, \linkspell{Deeper Darkness}, \linkspell{Protection From Energy}, \linkspell{Inflict Serious Wounds}, \linkspell{Summon Monster III}*.

\textbf{4th Level:} \linkspell{Cure Critical Wounds}, \linkspell{Freedom of Movement}, \linkspell{Inflict Critical Wounds}, \linkspell{Poison}, \linkspell{Summon Monster IV}*.

*Evil creatures only.

%%%
\subsubsection{Corrupt Weapon}
%%%

Blackguards have access to a special spell, \textit{Corrupt Weapon}, which is the 
opposing counterpart of the paladin spell \linkspell{Bless Weapon}. Instead of improving 
a weapon's effectiveness against evil foes \textit{Corrupt Weapon} makes a weapon 
more effective against good foes.

%%%
\subsubsection{Fallen Paladins}
%%%

Blackguards who have levels in the paladin class (that is to say, are now ex-paladins) 
gain extra abilities the more levels of paladin they have.

A fallen paladin who becomes a blackguard gains all of the following abilities 
that apply, according to the number of paladin levels the character has.

1-2: Smite good 1/day. (This is in addition to the ability granted to all blackguards 
at 2nd level.

3-4: Lay on hands. Once per day, the blackguard can use this supernatural ability 
to cure himself or his fiendish servant of damage equal to his Charisma bonus x 
his level.

5-6: Sneak attack damage increased by +1d6. Smite good 2/day.

7-8: Fiendish summoning. Once per day, the blackguard can use a \linkspell{Summon Monster I} spell to call forth an evil creature. For this spell, the caster level 
is double the blackguard's class level.

9-10: Undead companion. In addition to the fiendish servant, the blackguard gains 
(at 5th level) a Medium-size skeleton or zombie as a companion. This companion 
cannot be turned or rebuked and gains all special bonuses as a fiendish servant 
when the blackguard gains levels. Smite good 3/day.

11 or more: A fallen paladin of this stature immediately gains a blackguard level 
for each level of paladin he trades in. 

The character level of the character does not change. With the loss of paladin 
levels, the character no longer gains as many extra abilities for being a fallen 
paladin. 

%%%
\subsubsection{The Blackguard's Fiendish Servant}
%%%

Upon or after reaching 5th level, a blackguard can call a fiendish bat, cat, dire 
rat, horse, pony, raven, or toad to serve him. The blackguard's servant further 
gains HD and special abilities based on the blackguard's character level (see the 
table below).

A blackguard may have only one fiendish servant at a time.

Should the blackguard's servant die, he may call for another one after a year and 
a day. The new fiendish servant has all the accumulated abilities due a servant 
of the blackguard's current level.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Blackguard Fiendish Servant Progression}
\centering
\begin{tabular}{l c c c c p{5cm}}
\textbf{Character Level} & \textbf{Bonus HD} & \textbf{Nat Armor} & \textbf{Str} & \textbf{Int} & \textbf{Special}\\
12th or lower & +2 & +1 & +1 & 6 & Empathic Link, Improved Evasion, Share Spells, Share Saving Throws\\
13th-15th & +4 & +3 & +2 & 7 & Speak with Blackguard\\
16th-18th & +6 & +5 & +3 & 8 & Blood Bond\\
19th-20th & +8 & +7 & +4 & 9 & Spell Resistance\\
\end{tabular}
\end{table}

\textit{Character Level:} The character level of the blackguard (his blackguard 
level plus his original class level).

\textit{Bonus HD:} Extra eight-sided (d8) Hit Dice, each of which gains a Constitution 
modifier, as normal. Extra Hit Dice improve the servant's base attack and base 
save bonuses, as normal.

\textit{Natural Armor Adj.:} This is an improvement to the servant's existing natural 
armor bonus.

\textit{Str Adj.:} Add this figure to the servant's Strength score.

\textit{Int:} The servant's Intelligence score. (A fiendish servant is smarter 
than normal animals of its kind.)

\vspace{12pt}
The abilities mentioned in the "Special" column of the accompanying table are 
described below.

\textbf{Empathic Link (Su):} The blackguard has an empathic link with his servant 
out to a distance of up to 1 mile. The blackguard cannot see through the servant's 
eyes, but they can communicate empathically. Because of the limited nature of the 
link, only general emotional content can be communicated.

Because of the empathic link between the servant and the blackguard, the blackguard 
has the same connection to a place or an item that the servant does.

\textbf{Improved Evasion (Ex):} If the servant is subjected to an attack that normally 
allows a Reflex saving throw for half damage, it takes no damage on a successful 
saving throw and only half damage on a failed saving throw. Improved evasion is 
an extraordinary ability.

\textbf{Share Saving Throws:} For each of its saving throws, the servant uses either 
its own base save bonus or the blackguard's, whichever is higher. The servant applies 
its own ability modifiers to saves, and it doesn't share any other bonuses on saves 
that the blackguard might have.

\textbf{Share Spells:} At the blackguard's option, he may have any spell (but not 
any spell-like ability) he casts on himself also affect his servant. The servant 
must be within 5 feet at the time of casting to receive the benefit. If the spell 
has a duration other than instantaneous, it stops affecting the servant if it moves 
farther than 5 feet away and will not affect the servant again even if the servant 
returns to the blackguard before the duration expires. Additionally, the blackguard 
may cast a spell with a target of "You" on his servant (as a touch range spell) 
instead of on himself. A blackguard and his servant can share spells even if the 
spells normally do not affect creatures of the servant's type (magical beast).

\textbf{Speak with Blackguard (Ex):} If the blackguard's character level is 13th 
or higher, the blackguard and servant can communicate verbally as if they were 
using a common language. Other creatures do not understand the communication without 
magical help.

\textbf{Blood Bond (Ex):} If the blackguard's character level is 16th or higher, 
the servant gains a +2 bonus on all attack rolls, checks, and saves if it witnesses 
the blackguard being threatened or harmed.

This bonus lasts as long as the threat is immediate and apparent.

\textbf{Spell Resistance (Ex):} If the blackguard's character level is 19th or 
higher, the servant gains spell resistance equal to the blackguard's level + 5. 
To affect the servant with a spell, another spellcaster must get a result on a 
caster level check (1d20 + caster level) that equals or exceeds the servant's spell 
resistance.
