%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Dragon Disciple}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a dragon disciple, a character must fulfill all the following 
criteria.

\textbf{Race:} Any nondragon (cannot already be a half-dragon).

\textbf{Skills:} Knowledge (arcana) 8 ranks.

\textbf{Languages:} Draconic.

\textbf{Spellcasting:} Ability to cast arcane spells without preparation.

\textbf{Special:} The player chooses a dragon variety when taking the first level 
in this prestige class.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d12.

\textbf{Class Skills}

The dragon disciple's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Gather Information} (Cha), 
\linkskill{Knowledge} (all skills, taken individually) (Int) \linkskill{Listen} (Wis), \linkskill{Profession} (Wis), 
\linkskill{Search} (Int), \linkskill{Speak Language} (Int), \linkskill{Spellcraft} (Int), and \linkskill{Spot} (Wis). 

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Dragon Disciple}
\centering
\begin{tabular}{*{6}{l}c}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{Bonus Spells} \\
1st & +0 & +2 & +0 & +2 & Natural Armor Increase (+1) & 1\\
2nd & +1 & +3 & +0 & +3 & Ability Boost (Str +2), Claws and Bite & 1\\
3rd & +2 & +3 & +1 & +3 & Breath Weapon (2d8) & 0\\
4th & +3 & +4 & +1 & +4 & Ability Boost (Str +2), Natural Armor Increase (+2) & 1\\
5th & +3 & +4 & +1 & +4 & Blindsense 30ft & 1\\
6th & +4 & +5 & +2 & +5 & Ability Boost (Con +2) & 1\\
7th & +5 & +5 & +2 & +5 & Breath Weapon (4d8), Natural Armor Increase (+3) & 0\\
8th & +6 & +6 & +2 & +6 & Ability Boost (Int +2) & 1\\
9th & +6 & +6 & +3 & +6 & Wings & 1\\
10th & +7 & +7 & +3 & +7 & Blindsense 60ft, Dragon Apotheosis & 0\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the dragon disciple prestige class.

\textbf{Weapon and Armor Proficiency:} Dragon disciples gain no proficiency with 
any weapon or armor.

\textbf{Bonus Spells:} Dragon disciples gain bonus spells as they gain levels in 
this prestige class, as if from having a high ability score, as given on Table: 
The Dragon Disciple. A bonus spell can be added to any level of spells the disciple 
already has the ability to cast.

If a character has more than one spellcasting class, he must decide to which class 
he adds each bonus spell as it is gained. Once a bonus spell has been applied, 
it cannot be shifted.

\textbf{Natural Armor Increase (Ex):} At 1st, 4th, and 7th level, a gains an increase 
to the character's existing natural armor (if any), as indicated on Table: The 
Dragon Disciple (the numbers represent the total increase gained to that point). 
As his skin thickens, a dragon disciple takes on more and more of his progenitor's 
physical aspect.

\textbf{Claws and Bite (Ex):} At 2nd level, a dragon disciple gains claw and bite 
attacks if he does not already have them. Use the values below or the disciple's 
base claw and bite damage values, whichever are greater.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Dragon Disciple Natural Weapons}
\centering
\begin{tabular}{l c c}
\textbf{Size} & \textbf{Bite Damage} & \textbf{Claw Damage}\\
Small & 1d4 & 1d3\\
Medium & 1d6 & 1d4\\
Large & 1d8 & 1d6\\
\end{tabular}
\end{table}

A dragon disciple is considered proficient with these attacks. When making a full 
attack, a dragon disciple uses his full base attack bonus with his bite attack 
but takes a -5 penalty on claw attacks. The Multiattack feat reduces this penalty 
to only -2.

\textbf{Ability Boost (Ex):} As a dragon disciple gains levels in this prestige 
class, his ability scores increase as noted on Table: The Dragon Disciple.

These increases stack and are gained as if through level advancement.

\textbf{Breath Weapon (Su):} At 3rd level, a dragon disciple gains a minor breath 
weapon. The type and shape depend on the dragon variety whose heritage he enjoys 
(see below). Regardless of the ancestor, the breath weapon deals 2d8 points of 
damage of the appropriate energy type.

At 7th level, the damage increases to 4d8, and when a disciple attains dragon apotheosis 
at 10th level it reaches its full power at 6d8. Regardless of its strength, the 
breath weapon can be used only once per day. Use all the rules for dragon breath 
weapons except as specified here.

The DC of the breath weapon is 10 + class level + Con modifier.

A line-shaped breath weapon is 5 feet high, 5 feet wide, and 60 feet long. A cone-shaped 
breath weapon is 30 feet long.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Dragon Disciple Breath Weapons}
\centering
\begin{tabular}{l l}
\textbf{Dragon Variety\textsuperscript{1}} & \textbf{Breath Weapon}\\
Black & Line of acid\\
Blue & Line of lightning\\
Green & Cone of corrosive gas (acid)\\
Red & Cone of fire\\
White & Cone of cold\\
Brass & Line of fire\\
Bronze & Line of lightning\\
Copper & Line of acid\\
Gold & Cone of fire\\
Silver & Cone of cold\\
\multicolumn{2}{p{7cm}}{\textsuperscript{1}Other varieties of dragon disciple are possible, using other dragon varieties as ancestors.}\\
\end{tabular}
\end{table}

\textbf{Blindsense (Ex):} At 5th level, the dragon disciple gains blindsense with 
a range of 30 feet. Using nonvisual senses the dragon disciple notices things it 
cannot see. He usually does not need to make Spot or Listen checks to notice and 
pinpoint the location of creatures within range of his blindsense ability, provided 
that he has line of effect to that creature.

Any opponent the dragon disciple cannot see still has total concealment against 
him, and the dragon disciple still has the normal miss chance when attacking foes 
that have concealment. Visibility still affects the movement of a creature with 
blindsense. A creature with blindsense is still denied its Dexterity bonus to Armor 
Class against attacks from creatures it cannot see. At 10th level, the range of 
this ability increases to 60 feet.

\textbf{Wings (Ex):} At 9th level, a dragon disciple grows a set of draconic wings. 
He may now fly at a speed equal to his normal land speed, with average maneuverability.

\textbf{Dragon Apotheosis:} At 10th level, a dragon disciple takes on the half-dragon 
template. His breath weapon reaches full strength (as noted above), and he gains 
+4 to Strength and +2 to Charisma. His natural armor bonus increases to +4, and 
he acquires low-light vision, 60-foot darkvision, immunity to \linkspell{Sleep} and 
paralysis effects, and immunity to the energy type used by his breath weapon (see 
above).
