%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Duelist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a duelist, a character must fulfill all the following criteria.

\textbf{Base Attack Bonus:} +6.

\textbf{Skills:} \linkskill{Perform} 3 ranks, \linkskill{Tumble} 5 ranks.

\textbf{Feats:} \linkfeat{Dodge}, \linkfeat{Mobility}, \linkfeat{Weapon Finesse}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d10.

\textbf{Class Skills}

The duelist's class skills (and the key ability for each skill) are \linkskill{Balance} (Dex), 
\linkskill{Bluff} (Cha), \linkskill{Escape Artist} (Dex), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Perform} (Cha),
\linkskill{Sense Motive} (Wis), \linkskill{Spot} (Wis), and \linkskill{Tumble} (Dex).

\textbf{Skill Points at Each Level:} 4 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Duelist}
\centering
\begin{tabular}{*{6}{l}*{4}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +1 & +0 & +2 & +0 & Canny Defense \\
2nd & +2 & +0 & +3 & +0 & Improved Reaction +2\\
3rd & +3 & +1 & +3 & +1 & Enhanced Mobility\\
4th & +4 & +1 & +4 & +1 & Grace\\
5th & +5 & +1 & +4 & +1 & Precise Strike +1d6\\
6th & +6 & +2 & +5 & +2 & Acrobatic Charge\\
7th & +7 & +2 & +5 & +2 & Elaborate Parry\\
8th & +8 & +2 & +6 & +2 & Improved Reaction +4\\
9th & +9 & +3 & +6 & +3 & Deflect Arrows\\
10th & +10 & +3 & +7 & +3 & Precise Strike +1d6\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Weapon and Armor Proficiency:} The duelist is proficient with all simple 
and martial weapons, but no type of armor or shield.

\textbf{Canny Defense (Ex):} When not wearing armor or using a shield, a duelist 
adds 1 point of Intelligence bonus (if any) per duelist class level to her Dexterity 
bonus to modify Armor Class while wielding a melee weapon. If a duelist is caught 
flat-footed or otherwise denied her Dexterity bonus, she also loses this bonus.

\textbf{Improved Reaction (Ex):} At 2nd level, a duelist gains a +2 bonus on initiative 
checks.

At 8th level, the bonus increases to +4. This bonus stacks with the benefit provided 
by the Improved Initiative feat.

\textbf{Enhanced Mobility (Ex):} When wearing no armor and not using a shield, 
a duelist gains an additional +4 bonus to AC against attacks of opportunity caused 
when she moves out of a threatened square.

\textbf{Grace (Ex):} At 4th level, a duelist gains an additional +2 competence 
bonus on all Reflex saving throws. This ability functions for a duelist only when 
she is wearing no armor and not using a shield.

\textbf{Precise Strike (Ex):} At 5th level, a duelist gains the ability to strike 
precisely with a light or one-handed piercing weapon, gaining an extra 1d6 damage 
added to her normal damage roll.

When making a precise strike, a duelist cannot attack with a weapon in her other 
hand or use a shield. A duelist's precise strike only works against living creatures 
with discernible anatomies. Any creature that is immune to critical hits is not 
vulnerable to a precise strike, and any item or ability that protects a creature 
from critical hits also protects a creature from a precise strike. At 
10th level, the extra damage on a precise strike increases to +2d6.

\textbf{Acrobatic Charge (Ex):} At 6th level, a duelist gains the ability to charge 
in situations where others cannot. She may charge over difficult terrain that normally 
slows movement. Depending on the circumstance, she may still need to make appropriate 
checks to successfully move over the terrain.

\textbf{Elaborate Parry (Ex):} At 7th level and higher, if a duelist chooses to 
fight defensively or use total defense in melee combat, she gains an additional 
+1 dodge bonus to AC for each level of duelist she has.

Deflect Arrows: At 9th level, a duelist gains the benefit of the Deflect Arrows 
feat when using a light or one-handed piercing weapon.
