%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Dwarven Defender}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a defender, a character must fulfill all the following criteria.

\textbf{Race:} \linkrace{Dwarf}.

\textbf{Alignment:} Any lawful.

\textbf{Base Attack Bonus:} +7.

\textbf{Feats:} \linkfeat{Dodge}, \linkfeat{Endurance}, \linkfeat{Toughness}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d12.

\textbf{Class Skills}

The defender's class skills (and the key ability for each skill) are \linkskill{Craft} (Int), 
\linkskill{Listen} (Wis), \linkskill{Sense Motive} (Wis), and \linkskill{Spot} (Wis).

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Dwarven Defender}
\centering
\begin{tabular}{*{6}{l}c}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{AC Boost} \\
1st & +1 & +2 & +0 & +2 & Defensive Stance 1/day & +1\\
2nd & +2 & +3 & +0 & +3 & Uncanny Dodge & +1\\
3rd & +3 & +3 & +1 & +3 & Defensive Stance 2/day & +1\\
4th & +4 & +4 & +1 & +4 & Trap Sense +1 & +2\\
5th & +5 & +4 & +1 & +4 & Defensive Stance 3/day & +2\\
6th & +6 & +5 & +2 & +5 & Damage Reduction 3/-, Improved Uncanny Dodge & +2\\
7th & +7 & +5 & +2 & +5 & Defensive Stance 4/day & +3\\
8th & +8 & +6 & +2 & +6 & Mobile Defense, Trap Sense +2 & +3\\
9th & +9 & +6 & +3 & +6 & Defensive Stance 5/day & +3\\
10th & +10 & +7 & +3 & +7 & Damage Reduction 6/- & +4\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the dwarven defender prestige class.

\textbf{AC Bonus (Ex):} The dwarven defender receives a dodge bonus to Armor Class 
that starts at +1 and improves as the defender gains levels, until it reaches +4 
at 10th level.

\textbf{Weapon and Armor Proficiency:} A dwarven defender is proficient with all 
simple and martial weapons, all types of armor, and shields.

\textbf{Defensive Stance:} When he adopts a defensive stance, a defender gains 
phenomenal strength and durability, but he cannot move from the spot he is defending. 
He gains +2 to Strength, +4 to Constitution, a +2 resistance bonus on all saves, 
and a +4 dodge bonus to AC. The increase in Constitution increases the defender's 
hit points by 2 points per level, but these hit points go away at the end of the 
defensive stance when the Constitution score drops back 4 points. These extra hit 
points are not lost first the way temporary hit points are. While in a defensive 
stance, a defender cannot use skills or abilities that would require him to shift 
his position. A defensive stance lasts for a number of rounds equal to 3 + the 
character's (newly improved) Constitution modifier. A defender may end his defensive 
stance voluntarily prior to this limit. At the end of the defensive stance, the 
defender is winded and takes a -2 penalty to Strength for the duration of that 
encounter. A defender can only use his defensive stance a certain number of times 
per day as determined by his level (see Table: The Dwarven Defender). Using the 
defensive stance takes no time itself, but a defender can only do so during his 
action.

\textbf{Uncanny Dodge (Ex):} Starting at 2nd level, a dwarven defender retains 
his Dexterity bonus to AC (if any) regardless of being caught flat-footed or struck 
by an invisible attacker. (He still loses any Dexterity bonus to AC if immobilized.)

If a character gains uncanny dodge from a second class, the character automatically 
gains improved uncanny dodge (see below).

\textbf{Trap Sense (Ex):} At 4th level, a dwarven defender gains a +1 bonus on 
Reflex saves made to avoid traps and a +1 dodge bonus to AC against attacks by 
traps. At 8th level, these bonuses rise to +2. These bonuses stack with trap sense 
bonuses gained from other classes.

\textbf{Damage Reduction (Ex):} At 6th level, a dwarven defender gains damage reduction. 
Subtract 3 points from the damage the dwarven defender takes each time he is dealt 
damage. At 10th level, this damage reduction rises to 6/-. Damage reduction can 
reduce damage to 0 but not below 0.

\textbf{Improved Uncanny Dodge (Ex):} At 6th level, a dwarven defender can no longer 
be flanked. This defense denies rogues the ability to use flank attacks to sneak 
attack the dwarven defender.

The exception to this defense is that a rogue at least four levels higher than 
the dwarven defender can flank him (and thus sneak attack him).

If a character gains uncanny dodge (see above) from a second class the character 
automatically gains improved uncanny dodge, and the levels from those classes stack 
to determine the minimum rogue level required to flank the character.

\textbf{Mobile Defense (Ex):} At 8th level, a dwarven defender can adjust his position 
while maintaining a defensive stance. While in a defensive stance, he can take 
one 5-foot step each round without losing the benefit of the stance.
