%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Eldritch Knight}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become an eldritch knight, a character must fulfill all the following 
criteria.

\textbf{Weapon Proficiency:} Must be proficient with all martial weapons.

\textbf{Spells:} Able to cast 3rd-level arcane spells.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d6.

\textbf{Class Skills}

The eldritch knight's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Decipher Script} (Int), \linkskill{Jump} (Str), \linkskill{Knowledge} (arcana) (Int), 
\linkskill{Knowledge} (nobility and royalty) (Int), \linkskill{Ride} (Dex), \linkskill{Sense Motive} (Wis), \linkskill{Spellcraft} 
(Int), and \linkskill{Swim} (Str). 

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Eldritch Knight}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +1 & +2 & +0 & +0 & Bonus Feat\\
2nd & +2 & +3 & +0 & +0 & Spells\\
3rd & +3 & +3 & +1 & +1 & - \\
4th & +4 & +4 & +1 & +1 & - \\
5th & +5 & +4 & +1 & +1 & - \\
6th & +6 & +5 & +2 & +2 & - \\
7th & +7 & +5 & +2 & +2 & - \\
8th & +8 & +6 & +2 & +2 & - \\
9th & +9 & +6 & +3 & +3 & - \\
10th & +10 & +7 & +3 & +3 & - \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are features of the eldritch knight prestige class.

\textbf{Weapon and Armor Proficiency:} Eldritch knights gain no proficiency with 
any weapon or armor.

\textbf{Bonus Feat:} At 1st level, an eldritch knight may choose a bonus feat from 
the list of feats available to \linkclass{Fighter}{Fighters}. This is in addition to the feats that 
a character of any class normally gets from advancing levels. The character must 
still meet any prerequisites for these bonus feats, including levels of fighter 
for the \linkfeat{Weapon Specialization}, \linkfeat{Greater Weapon Focus}, and \linkfeat{Greater Weapon Specialization} 
feats.

\textbf{Spells per Day:} From 2nd level on, when a new eldritch knight level is 
gained, the character gains new spells per day as if she had also gained a level 
in whatever arcane spellcasting class she belonged to before she added the prestige 
class. She does not, however, gain any other benefit a character of that class 
would have gained. This essentially means that she adds the level of eldritch knight 
to the level of whatever other arcane spellcasting class the character has, then 
determines spells per day and caster level accordingly.

If a character had more than one arcane spellcasting class before she became an 
eldritch knight, she must decide to which class she adds each level of eldritch 
knight for the purpose of determining spells per day.
