%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Hierophant}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a hierophant, a character must fulfill all the following criteria.

\textbf{Skills:} \linkskill{Knowledge} (religion) 15 ranks.

\textbf{Feats:} Any metamagic feat.

\textbf{Spells:} Able to cast 7th-level divine spells.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d8.

\textbf{Class Skills}

The hierophant's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Heal} (Wis), \linkskill{Knowledge} (arcana) (Int), \linkskill{Knowledge} 
(religion) (Int), \linkskill{Profession} (Wis), and \linkskill{Spellcraft} (Int). 

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Hierophant}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +0 & +2 & +0 & +2 & Special Ability\\
2nd & +1 & +3 & +0 & +3 & Special Ability\\
3rd & +1 & +3 & +1 & +3 & Special Ability\\
4th & +2 & +4 & +1 & +4 & Special Ability\\
5th & +2 & +4 & +1 & +4 & Special Ability\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All the following are Class Features of the hierophant prestige class.

\textbf{Weapon and Armor Proficiency:} Hierophants gain no proficiency with any 
weapon or armor.

\textbf{Spells and Caster Level:} Levels in the hierophant prestige class, even 
though they do not advance spell progression in the character's base class, still 
stack with the character's base spellcasting levels to determine caster level.

\textbf{Special Ability:} Every level, a hierophant gains a special ability of 
his choice from among the following.

\textit{Blast Infidel (Su):} A hierophant can use negative energy spells to their 
maximum effect on creatures with an alignment opposed to the hierophant. (See the 
table below for a list of which alignments are opposed to each alignment.) Any 
spell with a description that involves inflicting or channeling negative energy 
cast on a creature of the opposed alignment works as if under the effect of a Maximize 
Spell feat (without using a higher-level spell slot). Undead affected by this ability 
heal the maximized amount of damage.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Hierophant Opposed Alignments}
\centering
\begin{tabular}{*{6}{l}c}
\textbf{Hierophant Alignment} & \textbf{Opposed Alignment}\\
Lawful Good & Chaotic Evil\\
Neutral Good & Neutral Evil\\
Chaotic Good & Lawful Evil\\
Lawful Neutral & Chaotic Neutral\\
Neutral & Lawful Good, Chaotic Good, Lawful Evil, Chaotic Evil\textsuperscript{1}\\
Chaotic Neutral & Lawful Neutral\\
Lawful Evil & Chaotic Good\\
Neutral Evil & Neutral Good\\
Chaotic Evil & Lawful Good\\
\multicolumn{2}{p{10cm}}{\textsuperscript{1}A neutral hierophant chooses one of these alignments to be the one that he opposes, for the purposes of this special ability.}\\
\end{tabular}
\end{table}

\textit{Divine Reach (Su):} A hierophant with this ability can use touch spells 
on targets up to 30 feet away. If the spell requires a melee touch attack, the 
hierophant must make a ranged touch attack instead. Divine reach can be selected 
a second time as a special ability, in which case the range increases to 60 feet.

\textit{Faith Healing (Su):} A hierophant can use healing spells to their maximum 
effect on creatures of the same alignment as the hierophant (including the hierophant 
himself ). Any spell with the healing descriptor cast on such creatures works as 
if under the effects of a Maximize Spell feat (without using a higher-level spell 
slot).

\textit{Gift of the Divine (Su):} Available only to hierophants with cleric levels, 
this ability allows a hierophant to transfer one or more uses of his turn undead 
ability to a willing creature. (Hierophants who rebuke undead transfer uses of 
rebuke undead instead.) The transfer lasts anywhere from 24 hours to one week (chosen 
at the time of transfer), and while the transfer is in effect, the number of turning 
attempts per day allowed to the hierophant is reduced by the number transferred. 
The recipient turns undead as a cleric of the hierophant's cleric level but uses 
her own Charisma modifier.

\textit{Mastery of Energy (Su):} Available only to hierophants with cleric levels, 
this ability allows a hierophant to channel positive or negative energy much more 
effectively, increasing his ability to affect undead. Add a +4 bonus to the hierophant's 
turning checks and turning damage rolls. This ability only affects undead, even 
if the hierophant can turn other creatures, such as with a granted power of a domain.

\textit{Metamagic Feat:} A hierophant can choose a metamagic feat in place of one 
of the special abilities described here if desired.

\textit{Power of Nature (Su):} Available only to hierophants with druid levels, 
this ability allows a hierophant to temporarily transfer one or more of his druid 
Class Features to a willing creature. The transfer lasts anywhere from 24 hours 
to one week (chosen at the time of transfer), and while the transfer is in effect, 
the hierophant cannot use the transferred power. He can transfer any of his druid 
powers except spellcasting and the ability to have an animal companion.

The druid's wild shape ability can be partially or completely transferred. The 
heirophant choses how many uses of wild shape per day to give to transfer and retains 
the rest of the uses for himself. If the hierophant can assume the form of Tiny 
or Huge animals, the recipient can as well.

As with the \linkspell{Imbue With Spell Ability} spell, the hierophant remains responsible 
to his deity for any use to which the recipient puts the transferred abilities.

\textit{Spell Power:} This special ability increases a hierophant's effective caster 
level by 1 for purposes of determining level-dependent spell variables and for 
caster level checks. This ability can be selected more than once, and changes to 
effective caster level are cumulative.

\textit{Spell-Like Ability:} A hierophant who selects this special ability can 
use one of his divine spell slots to permanently prepare one of his divine spells 
as a spell-like ability that can be used twice per day. The hierophant does not 
use any components when casting the spell, although a spell that costs XP to cast 
still does so, and a spell with a costly material component instead costs him 10 
times that amount in XP.

The spell normally uses a spell slot of the spell's level (or higher, if the hierophant 
chooses to permanently attach a metamagic feat to the spell chosen). The hierophant 
can use an available higher-level spell slot to use the spell-like ability more 
than once per day. Allocating a slot three levels higher allows him to cast the 
spell four times per day, and a slot six levels higher lets him cast it six times 
per day. If selected more than one time as a special ability, this ability can 
apply to the same spell (increasing the number of times per day it can be used) 
or to a different spell.
