%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Loremaster}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a loremaster, a character must fulfill all the following criteria.

\textbf{Skills:} \linkskill{Knowledge} (any two) 10 ranks in each.

\textbf{Feats:} Any three metamagic or item creation feats, plus \linkfeat{Skill Focus} (Knowledge 
[any individual Knowledge skill]).

\textbf{Spells:} Able to cast seven different divination spells, one of which must 
be 3rd level or higher.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d4.

\textbf{Class Skills}

The loremaster's class skills (and the key ability for each skill) are \linkskill{Appraise} 
(Int), \linkskill{Concentration} (Con), \linkskill{Craft} (alchemy) (Int), \linkskill{Decipher Script} (Int), \linkskill{Gather Information}
(Cha), \linkskill{Handle Animal} (Cha), \linkskill{Heal} (Wis), \linkskill{Knowledge} (all skills taken 
individually) (Int), \linkskill{Perform} (Cha), \linkskill{Profession} (Wis), \linkskill{Speak Language}, \linkskill{Spellcraft} 
(Int), and \linkskill{Use Magic Device} (Cha). 

\textbf{Skill Points at Each Level:} 4 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Loremaster}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +0 & +0 & +0 & +2 & Secret, Spells\\
2nd & +1 & +0 & +0 & +3 & Lore\\
3rd & +1 & +1 & +1 & +3 & Secret \\
4th & +2 & +1 & +1 & +4 & Bonus Language \\
5th & +2 & +1 & +1 & +4 & Secret \\
6th & +3 & +2 & +2 & +5 & Greater Lore \\
7th & +3 & +2 & +2 & +5 & Secret \\
8th & +4 & +2 & +2 & +6 & Bonus Language \\
9th & +4 & +3 & +3 & +6 & Secret \\
10th & +5 & +3 & +3 & +7 & True Lore \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are Class Features of the loremaster prestige class.

\textbf{Weapon and Armor Proficiency:} Loremasters gain no proficiency with any 
weapon or armor.

\textbf{Spells per Day/Spells Known:} When a new loremaster level is gained, the 
character gains new spells per day (and spells known, if applicable) as if she 
had also gained a level in a spellcasting class she belonged to before she added 
the prestige class. She does not, however, gain any other benefit a character of 
that class would have gained. This essentially means that she adds the level of 
loremaster to the level of some other spellcasting class the character has, then 
determines spells per day, spells known, and caster level accordingly.

\textbf{Secret:} At 1st level and every two levels higher than 1st (3rd, 5th, 7th, 
and 9th), the loremaster chooses one

secret from the table below. Her level plus Intelligence modifier determines the 
total number of secrets she can choose. She can't choose the same secret twice.

\textbf{Lore:} At 2nd level, a loremaster gains the ability to know legends or 
information regarding various topics, just as a bard can with bardic knowledge. 
The loremaster adds her level and her Intelligence modifier to the lore check, 
which functions otherwise exactly like a bardic knowledge check.

\textbf{Bonus Languages:} A loremaster can choose any new language at 4th and 8th 
level.

\textbf{Greater Lore (Ex):} At 6th level, a loremaster gains the ability to understand 
magic items, as with the \linkspell{Identify} spell.

\textbf{True Lore (Ex):} At 10th level, once per day a loremaster can use her knowledge 
to gain the effect of a \linkspell{Legend Lore} spell or an \linkspell{Analyze Dweomer} spell.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Loremaster Secrets}
\centering
\begin{tabular}{l l l}
\textbf{Level + Int Mod} & \textbf{Secret} & \textbf{Effect} \\
1 & Instant Mastery & 4 ranks in a skill that the character has no ranks in\\
2 & Secret Health & +3 hit points\\
3 & Secrets of Inner Strength & +2 on Will saves\\
4 & The Lore of True Stamina & +2 on Fort saves\\
5 & Secret Knowledge of Avoidance & +2 on Reflex saves\\
6 & Weapon Trick & +1 on attack rolls\\
7 & Dodge Trick & +1 Dodge bonus to AC\\
8 & Applicable Knowledge & Any one feat\\
9 & Newfound Arcana & one bonus 1st level spell slot\textsuperscript{1}\\
10 & More Newfound Arcana & one bonus 2nd level spell slot\textsuperscript{1}\\
\multicolumn{3}{l}{\textsuperscript{1} As if gained through a high ability score}\\
\end{tabular}
\end{table}
