%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Mystic Theurge}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a mystic theurge, a character must fulfill all the following 
criteria.

\textbf{Skills:} \linkskill{Knowledge} (arcana) 6 ranks, \linkskill{Knowledge} (religion) 6 ranks.

\textbf{Spells:} Able to cast 2nd-level divine spells and 2nd-level arcane spells.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d4.

\textbf{Class Skills}

The mystic theurge's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Decipher Script} (Int), \linkskill{Knowledge} (arcana) (Int), \linkskill{Knowledge} 
(religion) (Int), \linkskill{Profession} (Wis), \linkskill{Sense Motive} (Wis), and \linkskill{Spellcraft} (Int). 

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Loremaster}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +0 & +0 & +0 & +2 & Arcane Spells, Divine Spells\\
2nd & +1 & +0 & +0 & +3 & -\\
3rd & +1 & +1 & +1 & +3 & -\\
4th & +2 & +1 & +1 & +4 & -\\
5th & +2 & +1 & +1 & +4 & -\\
6th & +3 & +2 & +2 & +5 & -\\
7th & +3 & +2 & +2 & +5 & -\\
8th & +4 & +2 & +2 & +6 & -\\
9th & +4 & +3 & +3 & +6 & -\\
10th & +5 & +3 & +3 & +7 & -\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are features of the mystic theurge prestige class.

\textbf{Weapon and Armor Proficiency:} Mystic theurges gain no proficiency with 
any weapon or armor.

\textbf{Spells per Day: }When a new mystic theurge level is gained, the character 
gains new spells per day as if he had also gained a level in any one arcane spellcasting 
class he belonged to before he added the prestige class and any one divine spellcasting 
class he belonged to previously. He does not, however, gain any other benefit a 
character of that class would have gained. This essentially means that he adds 
the level of mystic theurge to the level of whatever other arcane spellcasting 
class and divine spellcasting class the character has, then determines spells per 
day and caster level accordingly. If a character had more than one arcane spellcasting 
class or more than one divine spellcasting class before he became a mystic theurge, 
he must decide to which class he adds each level of mystic theurge for the purpose 
of determining spells per day.
