%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Shadow Dancer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a shadowdancer, a character must fulfill all the following 
criteria.

\textbf{Skills:} \linkskill{Move Silently} 8 ranks, \linkskill{Hide} 10 ranks, \linkskill{Perform} (dance) 5 ranks.

\textbf{Feats:} \linkfeat{Combat Reflexes}, \linkfeat{Dodge}, \linkfeat{Mobility}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d8.

\textbf{Class Skills}

The shadowdancer's class skills (and the key ability for each skill) are \linkskill{Balance} 
(Dex), \linkskill{Bluff} (Cha), \linkskill{Decipher Script} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Disguise} (Cha), \linkskill{Escape Artist}
(Dex), \linkskill{Hide} (Dex), \linkskill{Jump} (Str), \linkskill{Listen} (Wis), \linkskill{Move Silently} (Dex), \linkskill{Perform}
(Cha), \linkskill{Profession} (Wis), \linkskill{Search} (Int), \linkskill{Sleight of Hand} (Dex), \linkskill{Spot} (Wis), \linkskill{Tumble} 
(Dex), and \linkskill{Use Rope} (Dex).

\textbf{Skill Points at Each Level:} 6 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Duelist}
\centering
\begin{tabular}{*{6}{l}*{4}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +0 & +0 & +2 & +0 & Hide In Plain Sight \\
2nd & +1 & +0 & +3 & +0 & Evasion, Darkvision, Uncanny Dodge\\
3rd & +2 & +1 & +3 & +1 & Shadow Illusion, Summon Shadow\\
4th & +3 & +1 & +4 & +1 & Shadow Jump (20ft)\\
5th & +3 & +1 & +4 & +1 & Defensive Roll, Improved Uncanny Dodge\\
6th & +4 & +2 & +5 & +2 & Shadow Jump (40ft), Summon Shadow (+2HD)\\
7th & +5 & +2 & +5 & +2 & Slippery Mind\\
8th & +6 & +2 & +6 & +2 & Shadow Jump (80ft)\\
9th & +6 & +3 & +6 & +3 & Summon Shadow (+2HD)\\
10th & +7 & +3 & +7 & +3 & Shadow Jump (160ft), Improved Evasion\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are features of the shadowdancer prestige class.

\textbf{Weapon and Armor Proficiency:} Shadowdancers are proficient with the club, 
crossbow (hand, light, or heavy), dagger (any type), dart, mace, morningstar, quarterstaff, 
rapier, sap, shortbow (normal and composite), and short sword. Shadowdancers are 
proficient with light armor but not with shields.

\textbf{Hide in Plain Sight (Su):} A shadowdancer can use the Hide skill even while 
being observed. As long as she is within 10 feet of some sort of shadow, a shadowdancer 
can hide herself from view in the open without anything to actually hide behind. 
She cannot, however, hide in her own shadow.

\textbf{Evasion (Ex):} At 2nd level, a shadowdancer gains evasion. If exposed to 
any effect that normally allows her to attempt a Reflex saving throw for half damage, 
she takes no damage with a successful saving throw. The evasion ability can only 
be used if the shadowdancer is wearing light armor or no armor.

\textbf{Darkvision (Su):} At 2nd level, a shadowdancer can see in the dark as though 
she were permanently under the effect of a \linkspell{Darkvision} spell.

\textbf{Uncanny Dodge (Ex):} Starting at 2nd level, a shadowdancer retains her 
Dexterity bonus to AC (if any) regardless of being caught flat-footed or struck 
by an invisible attacker. (She still loses any Dexterity bonus to AC if immobilized.)

If a character gains uncanny dodge from a second class, the character automatically 
gains improved uncanny dodge (see below).

\textbf{Shadow Illusion (Sp):} When a shadowdancer reaches 3rd 
level, she can create visual illusions. This ability's effect is identical to that 
of the arcane spell \textit{silent image} and may be employed once per day.

\textbf{Summon Shadow (Su):} At 3rd level, a shadowdancer can summon a shadow, 
an undead shade. Unlike a normal shadow, this shadow's alignment matches that of 
the shadowdancer, and the creature cannot create spawn. The summoned shadow cannot 
be turned, rebuked, or commanded by any third party. This shadow serves as a companion 
to the shadowdancer and can communicate intelligibly with the shadowdancer. Every 
third level gained by the shadowdancer adds +2 HD (and the requisite base attack 
and base save bonus increases) to her shadow companion.

If a shadow companion is destroyed, or the shadowdancer chooses to dismiss it, 
the shadowdancer must attempt a DC 15 Fortitude save. If the saving throw fails, 
the shadowdancer loses 200 experience points per shadowdancer level. A successful 
saving throw reduces the loss by half, to 100 XP per prestige class level. The 
shadowdancer's XP total can never go below 0 as the result of a shadow's dismissal 
or destruction. A destroyed or dismissed shadow companion cannot be replaced for 
30 days.

\textbf{Shadow Jump (Su):} At 4th level, a shadowdancer gains the ability to travel 
between shadows as if by means of a \linkspell{Dimension Door} spell. The limitation 
is that the magical transport must begin and end in an area with at least some 
shadow. A shadowdancer can jump up to a total of 20 feet each day in this way; 
this may be a single jump of 20 feet or two jumps of 10 feet each. Every two levels 
higher than 4th, the distance a shadowdancer can jump each day doubles (40 feet 
at 6th, 80 feet at 8th, and 160 feet at 10th). This amount can be split among many 
jumps, but each one, no matter how small, counts as a 10-foot increment.

\textbf{Defensive Roll (Ex):} Starting at 5th level, once per day, when a shadowdancer 
would be reduced to 0 hit points or less by damage in combat (from a weapon or 
other blow, not a spell or special ability), she can attempt to roll with the damage. 
She makes a Reflex saving throw (DC = damage dealt) and, if successful, takes only 
half damage from the blow. She must be aware of the attack and able to react to 
it in order to execute her defensive roll. If she is in a situation that would 
deny her any Dexterity bonus to AC, she can't attempt a defensive roll.

\textbf{Improved Uncanny Dodge (Ex):} At 5th level, a shadowdancer can no longer 
be flanked. This defense denies rogues the ability to use flank attacks to sneak 
attack the shadowdancer. The exception to this defense is that a rogue at least 
four levels higher than the shadowdancer can flank her (and thus sneak attack her).

If a character gains uncanny dodge (see above) from a second class the character 
automatically gains improved uncanny dodge, and the levels from those classes stack 
to determine the minimum rogue level required to flank the character.

\textbf{Slippery Mind (Ex):} At 7th level, if a shadowdancer is affected by an 
enchantment and fails her saving throw, 1 round later she can attempt her saving 
throw again. She only gets this one extra chance to succeed at her saving throw. 
If it fails as well, the spell's effects occur normally.

\textbf{Improved Evasion (Ex):} This ability, gained at 10th level, works like 
evasion (see above). A shadowdancer takes no damage at all on successful saving 
throws against attacks that allow a Reflex saving throw for half damage. What's 
more, she takes only half damage even if she fails her saving throw.
