%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Thaumaturgist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\Requirements
%%%%%%%%%%%%%%%%%%%%%%%%%

To qualify to become a thaumaturgist, a character must fulfill all the following 
criteria.

\textbf{Feats:} \linkfeat{Spell Focus} (conjuration).

\textbf{Spells:} Able to cast \linkspell{Lesser Planar Ally}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\Basics
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d4.

\textbf{Class Skills}

The thaumaturgist's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Diplomacy} (Cha), \linkskill{Knowledge} (religion) (Int), \linkskill{Knowledge} (the 
planes) (Int), \linkskill{Profession} (Wis), \linkskill{Sense Motive} (Wis), \linkskill{Speak Language} (none), and 
\linkskill{Spellcraft} (Int).

\textbf{Skill Points at Each Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Thaumaturgist}
\centering
\begin{tabular}{*{6}{l}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special}\\
1st & +0 & +0 & +0 & +2 & Improved Ally, Spells\\
2nd & +1 & +0 & +0 & +3 & Augment Summoning\\
3rd & +1 & +1 & +1 & +3 & Extended Summoning\\
4th & +2 & +1 & +1 & +4 & Contingent Conjuration\\
5th & +2 & +1 & +1 & +4 & Planar Cohort\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are features of the thaumaturgist prestige class.

\textbf{Weapon and Armor Proficiency:} Thaumaturgists gain no proficiency with 
any weapon or armor.

\textbf{Spells per Day:} When a new thaumaturgist level is gained, the character 
gains new spells per day as if he had also gained a level in whatever spellcasting 
class he belonged to before he added the prestige class. He does not, however, 
gain any other benefit a character of that class would have gained. This essentially 
means that he adds the level of thaumaturgist to the level of whatever other spellcasting 
class the character has, then determines spells per day and caster level accordingly.

If a character had more than one spellcasting class before he became a thaumaturgist, 
he must decide to which class he adds each level of thaumaturgist for the purpose 
of determining spells per day.

\textbf{Improved Ally:} When a thaumaturgist casts a \linkspell{Planar Ally} spell 
(including the \linkspell{Lesser Planar Ally}{Lesser} and \linkspell{Greater Planar Ally}{Greater} versions), he makes a \linkskill{Diplomacy} 
check to convince the creature to aid him for a reduced payment. If the thaumaturgist's 
Diplomacy check adjusts the creature's attitude to helpful the creature will work 
for 50\% of the standard fee, as long as the task is one that is not against its 
nature. 

The thaumaturgist's improved ally class feature only works when the planar ally 
shares at least one aspect of alignment with the thaumaturgist.

A thaumaturgist can have only one such ally at a time, but he may bargain for tasks 
from other planar allies normally.

\textbf{Augment Summoning:} At 2nd level, a thaumaturgist gains the \linkfeat{Augment Summoning} 
feat.

\textbf{Extended Summoning:} At 3rd level and higher, all spells from the summoning 
subschool that the thaumaturgist casts have their durations doubled, as if the 
\linkfeat{Extend Spell} feat had been applied to them. The levels of the summoning spells 
don't change, however. This ability stacks with the effect of the Extend Spell 
feat, which does change the spell's level.

\textbf{Contingent Conjuration:} A 4th-level thaumaturgist can prepare a summoning 
or calling spell ahead of time to be triggered by some other event. This functions 
as described for the \linkspell{Contingency} spell, including having the thaumaturgist 
cast the summoning or calling spell beforehand. The spell is cast instantly when 
the trigger event occurs. 

The conditions needed to bring the spell into effect must be clear, although they 
can be general. If complicated or convoluted condition as are prescribed, the contingent 
conjuration may fail when triggered. The conjuration spell occurs based solely 
on the stated conditions, regardless of whether the thaumaturgist wants it to, 
although most conjurations can be dismissed normally. A thaumaturgist can have 
only one contingent conjuration active at a time.

\textbf{Planar Cohort:} A 5th-level thaumaturgist can use any of the \linkspell{Planar Ally}
spells to call a creature to act as his cohort. The called creature serves 
loyally and well as long as the thaumaturgist continues to advance a cause important 
to the creature. 

To call a planar cohort, the thaumaturgist must cast the relevant spell, paying 
the XP costs normally. It takes an offering of 1,000 gp x the HD of the creature 
to convince it to serve as a planar cohort, and the improved ally class feature 
can't be used to reduce or eliminate this cost. The planar cohort can't have more 
Hit Dice than the thaumaturgist has, and must have an ECL no higher than the thaumaturgist's 
character level -2.

A thaumaturgist can have only one planar cohort at a time, but he can continue 
to make agreements with other called creatures normally. A planar cohort replaces 
a thaumaturgist's existing cohort, if he has one by virtue of the \linkfeat{Leadership} feat.
