\spellentry{Alarm}

Abjuration

\textbf{Level:} Brd 1, Rgr 1, Sor/Wiz 1

\textbf{Components:} V, S, F/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} 20-ft.-radius emanation centered on a point in space

\textbf{Duration:} 2 hours/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

A\textit{larm} sounds a mental or audible alarm each time a creature of Tiny or 
larger size enters the warded area or touches it. A creature that speaks the password 
(determined by you at the time of casting) does not set off the alarm. 
You decide at the time of casting whether the alarm will be mental or 
audible.

\textit{Mental Alarm:} A mental alarm alerts you (and only you) so long 
as you remain within 1 mile of the warded area. You note a single mental "ping" 
that awakens you from normal sleep but does not otherwise disturb concentration. 
A \linkspell{Silence} spell has no effect on a mental alarm.

\textit{Audible Alarm:} An audible alarm produces the sound of a hand 
bell, and anyone within 60 feet of the warded area can hear it clearly. Reduce 
the distance by 10 feet for each interposing closed door and by 20 feet for each 
substantial interposing wall.

In quiet conditions, the ringing can be heard faintly as far as 180 feet away. 
The sound lasts for 1 round. Creatures within a \linkspell{Silence} spell cannot hear 
the ringing.

Ethereal or astral creatures do not trigger the alarm.

\textit{Alarm} can be made permanent with a \linkspell{Permanency} spell.

\textit{Arcane Focus:} A tiny bell and a piece of very fine silver wire

