\spellentry{Animal Messenger}

Enchantment (Compulsion) [Mind-Affecting]

\textbf{Level:} Brd 2, Drd 2, Rgr 1

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One Tiny animal

\textbf{Duration:} One day/level

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} Yes

You compel a Tiny animal to go to a spot you designate. The most common use for 
this spell is to get an animal to carry a message to your allies. The animal cannot 
be one tamed or trained by someone else, including such creatures as familiars 
and animal companions.

Using some type of food desirable to the animal as a lure, you call the animal 
to you. It advances and awaits your bidding. You can mentally impress on the animal 
a certain place well known to you or an obvious landmark. The directions must be 
simple, because the animal depends on your knowledge and can't find a destination 
on its own. You can attach some small item or note to the messenger. The animal 
then goes to the designated location and waits there until the duration of the 
spell expires, whereupon it resumes its normal activities.

During this period of waiting, the messenger allows others to approach it and remove 
any scroll or token it carries. The intended recipient gains no special ability 
to communicate with the animal or read any attached message (if it's written in 
a language he or she doesn't know, for example).

\textit{Material Component:} A morsel of food the animal likes.

