\spellentry{Animate Dead}

Necromancy [Evil]

\textbf{Level:} Clr 3, Death 3, Sor/Wiz 4

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Targets:} One or more corpses touched

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

This spell turns the bones or bodies of dead creatures into undead skeletons or 
zombies that follow your spoken commands.

The undead can follow you, or they can remain in an area and attack any creature 
(or just a specific kind of creature) entering the place. They remain animated 
until they are destroyed. (A destroyed skeleton or zombie can't be animated again.)

Regardless of the type of undead you create with this spell, you can't create more 
HD of undead than twice your caster level with a single casting of Animate Dead. (The \linkspell{Desecrate} spell doubles this limit)

The undead you create remain under your control indefinitely. No matter how many 
times you use this spell, however, you can control only 4 HD worth of undead creatures 
per caster level. If you exceed this number, all the newly created creatures fall 
under your control, and any excess undead from previous castings become uncontrolled. 
(You choose which creatures are released.) If you are a cleric, any undead you 
might command by virtue of your power to command or rebuke undead do not count 
toward the limit.

\textit{Skeletons:} A skeleton can be created only from a mostly intact corpse 
or skeleton. The corpse must have bones. If a skeleton is made from a corpse, the 
flesh falls off the bones. 

\textit{Zombies:} A zombie can be created only from a mostly intact corpse. The 
corpse must be that of a creature with a true anatomy.

\textit{Material Component:} You must place a black onyx gem worth at least 25 
gp per Hit Die of the undead into the mouth or eye socket of each corpse you intend 
to animate. The magic of the spell turns these gems into worthless, burned-out 
shells.

