\spellentry{Animate Plants}

Transmutation

\textbf{Level:} Drd 7, Plant 7

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} One Large plant per three caster levels or all plants within 
range; see text

\textbf{Duration:} 1 round/level or 1 hour/level; see text

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You imbue inanimate plants with mobility and a semblance of life. Each animated 
plant then immediately attacks whomever or whatever you initially designate as 
though it were an animated object of the appropriate size category. You may animate 
one Large or smaller plant, or an equivalent number of larger plants, per three 
caster levels. A Huge plant counts as two Large or smaller plants, a Gargantuan 
plant as four, and a Colossal plant as eight. You can change the designated target 
or targets as a move action, as if directing an active spell.

Use the statistics for animated objects, except that plants smaller than 
Large usually don't have hardness.

Animate plants cannot affect plant creatures, nor does it affect nonliving 
vegetable material.

\textit{Entangle:} Alternatively, you may imbue all plants within range with a 
degree of mobility, which allows them to entwine around creatures in the area. 
This usage of the spell duplicates the effect of an \linkspell{Entangle} spell. Spell 
resistance does not keep creatures from being entangled. This effect lasts 1 hour 
per caster level.

