\spellentry{Astral Projection}

Necromancy

\textbf{Level:} Clr 9, Sor/Wiz 9, Travel 9

\textbf{Components:} V, S, M

\textbf{Casting Time:} 30 minutes

\textbf{Range:} Touch

\textbf{Targets:} You plus one additional willing creature touched per two caster 
levels

\textbf{Duration:} See text

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

By freeing your spirit from your physical body, this spell allows you to project 
an astral body onto another plane altogether.

You can bring the astral forms of other willing creatures with you, provided that 
these subjects are linked in a circle with you at the time of the casting. These 
fellow travelers are dependent upon you and must accompany you at all times. If 
something happens to you during the journey, your companions are stranded wherever 
you left them.

You project your astral self onto the Astral Plane, leaving your physical body 
behind on the Material Plane in a state of suspended animation. The spell projects 
an astral copy of you and all you wear or carry onto the Astral Plane. Since the 
Astral Plane touches upon other planes, you can travel astrally to any of these 
other planes as you will. To enter one, you leave the Astral Plane, forming a new 
physical body (and equipment) on the plane of existence you have chosen to enter.

While you are on the Astral Plane, your astral body is connected at all times to 
your physical body by a silvery cord. If the cord is broken, you are killed, astrally 
and physically. Luckily, very few things can destroy a silver cord. When a second 
body is formed on a different plane, the incorporeal silvery cord remains invisibly 
attached to the new body. If the second body or the astral form is slain, the cord 
simply returns to your body where it rests on the Material Plane, thereby reviving 
it from its state of suspended animation. Although astral projections are able 
to function on the Astral Plane, their actions affect only creatures existing on 
the Astral Plane; a physical body must be materialized on other planes.

You and your companions may travel through the Astral Plane indefinitely. Your 
bodies simply wait behind in a state of suspended animation until you choose to 
return your spirits to them. The spell lasts until you desire to end it, or until 
it is terminated by some outside means, such as \linkspell{Dispel Magic} cast upon 
either the physical body or the astral form, the breaking of the silver cord, or 
the destruction of your body back on the Material Plane (which kills you).

\textit{Material Component:} A jacinth worth at least 1,000 gp, plus a silver bar 
worth 5 gp for each person to be affected.

