\spellentry{Augury}

Divination

\textbf{Level:} Clr 2

\textbf{Components:} V, S, M, F

\textbf{Casting Time:} 1 minute

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

An Augury can tell you whether a particular action will bring good or 
bad results for you in the immediate future.

The base chance for receiving a meaningful reply is 70\% + 1\% per caster level, 
to a maximum of 90\%; this roll is made secretly. A question may be so straightforward 
that a successful result is automatic, or so vague as to have no chance of success. 
If the \textit{augury} succeeds, you get one of four results:

\begin{itemize*}
\item Weal (if the action will probably bring good results).
\item Woe (for bad results).
\item Weal and woe (for both).
\item Nothing (for actions that don't have especially good or bad results).
\end{itemize*}

If the spell fails, you get the "nothing" result. A cleric who gets the "nothing" 
result has no way to tell whether it was the consequence of a failed or successful 
augury.

The augury can see into the future only about half an hour, so anything 
that might happen after that does not affect the result. Thus, the result might 
not take into account the long-term consequences of a contemplated action. All 
auguries cast by the same person about the same topic use the same dice 
result as the first casting.

\textit{Material Component:} Incense worth at least 25 gp.

\textit{Focus:} A set of marked sticks, bones, or similar tokens of at least 25 
gp value.

