\spellentry{Black Tentacles}

Conjuration (Creation)

\textbf{Level:} Sor/Wiz 4

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Area:} 20-ft.-radius spread

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

This spell conjures a field of rubbery black tentacles, each 10 feet long. These 
waving members seem to spring forth from the earth, floor, or whatever surface 
is underfoot -- including water. They grasp and entwine around creatures that enter 
the area, holding them fast and crushing them with great strength.

Every creature within the area of the spell must make a grapple check, opposed 
by the grapple check of the tentacles. Treat the tentacles attacking a particular 
target as a Large creature with a base attack bonus equal to your caster level 
and a Strength score of 19. Thus, its grapple check modifier is equal to your caster 
level +8. The tentacles are immune to all types of damage.

Once the tentacles grapple an opponent, they may make a grapple check each round 
on your turn to deal 1d6+4 points of bludgeoning damage. The tentacles continue 
to crush the opponent until the spell ends or the opponent escapes.

Any creature that enters the area of the spell is immediately attacked by the tentacles. 
Even creatures who aren't grappling with the tentacles may move through the area 
at only half normal speed.

\textit{Material Component:} A piece of tentacle from a giant octopus or a giant 
squid.

