\spellentry{Blasphemy}

Evocation [Evil, Sonic]

\textbf{Level:} Clr 7, Evil 7

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 40 ft.

\textbf{Area:} Nonevil creatures in a 40-ft.-radius spread centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None or Will negates; see text

\textbf{Spell Resistance:} Yes

Any nonevil creature within the area of a Blasphemy spell suffers the 
following ill effects.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Blastphemy Effects}
\centering
\begin{tabular}{c l}
\textbf{HD} & \textbf{Effect} \\
Equal to caster level & Dazed\\
Up to caster level -1 & Weakened, Dazed\\
Up to caster level -5 & Paralyzed, Weakened, Dazed\\
Up to caster level -10 & Killed, Paralyzed, Weakened, Dazed\\
\end{tabular}
\end{table}

The effects are cumulative and concurrent.

No saving throw is allowed against these effects.

\textit{Dazed:} The creature can take no actions for 1 round, though it defends itself normally.

\textit{Weakened:} The creature's Strength score decreases by 2d6 points for 2d4 rounds.

\textit{Paralyzed:} The creature is paralyzed and helpless for 1d10 minutes.

\textit{Killed:} Living creatures die. Undead creatures are destroyed.

Furthermore, if you are on your home plane when you cast this spell, nonevil extraplanar 
creatures within the area are instantly banished back to their home planes. Creatures 
so banished cannot return for at least 24 hours. This effect takes place regardless 
of whether the creatures hear the blasphemy. The banishment effect allows 
a Will save (at a -4 penalty) to negate.

Creatures whose Hit Dice exceed your caster level are unaffected by blasphemy.

