\spellentry{Clone}

Necromancy

\textbf{Level:} Sor/Wiz 8

\textbf{Components:} V, S, M, F

\textbf{Casting Time:} 10 minutes

\textbf{Range:} 0 ft.

\textbf{Effect:} One clone

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

This spell makes an inert duplicate of a creature. If the original individual has 
been slain, its soul immediately transfers to the clone, creating a replacement 
(provided that the soul is free and willing to return). The original's physical 
remains, should they still exist, become inert and cannot thereafter be restored 
to life. If the original creature has reached the end of its natural life span 
(that is, it has died of natural causes), any cloning attempt fails.

To create the duplicate, you must have a piece of flesh (not hair, nails, scales, 
or the like) with a volume of at least 1 cubic inch that was taken from the original 
creature's living body. The piece of flesh need not be fresh, but it must be kept 
from rotting. Once the spell is cast, the duplicate must be grown in a laboratory 
for 2d4 months.

When the clone is completed, the original's soul enters it immediately, if that 
creature is already dead. The clone is physically identical with the original and 
possesses the same personality and memories as the original. In other respects, 
treat the clone as if it were the original character raised from the dead, including 
the loss of one level or 2 points of Constitution (if the original was a 1st-level 
character). If this Constitution adjustment would give the clone a Constitution 
score of 0, the spell fails. If the original creature has lost levels since the 
flesh sample was taken and died at a lower level than the clone would otherwise 
be, the clone is one level below the level at which the original died.

The spell duplicates only the original's body and mind, not its equipment.

A duplicate can be grown while the original still lives, or when the original soul 
is unavailable, but the resulting body is merely a soulless bit of inert flesh, 
which rots if not preserved.

\textit{Material Component:} The piece of flesh and various laboratory supplies 
(cost 1,000 gp).

\textit{Focus:} Special laboratory equipment (cost 500 gp).

