\spellentry{Contact Other Plane}

Divination

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Concentration

You send your mind to another plane of existence (an Elemental Plane or some plane 
farther removed) in order to receive advice and information from powers there. 
(See the accompanying table for possible consequences and results of the attempt.) 
The powers reply in a language you understand, but they resent such contact and 
give only brief answers to your questions. (All questions are answered with "yes", 
"no", "maybe", "never", "irrelevant", or some other one-word answer.)

You must concentrate on maintaining the spell (a standard action) in order to ask 
questions at the rate of one per round. A question is answered by the power during 
the same round. For every two caster levels, you may ask one question.

Contact with minds far removed from your home plane increases the probability that 
you will incur a decrease to Intelligence and Charisma, but the chance of the power 
knowing the answer, as well as the probability of the entity answering correctly, 
are likewise increased by moving to distant planes.

Once the Outer Planes are reached, the power of the deity contacted determines 
the effects. (Random results obtained from the table are subject to the personalities 
of individual deities.)

On rare occasions, this divination may be blocked by an act of certain deities 
or forces.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Contact Other Plane Results}
\centering
\begin{tabular}{l l cccc}
\textbf{Plane Contacted} & \textbf{Avoid Int/Cha Decrease} & \textbf{True Answer} & \textbf{Don't Know} & \textbf{Lie} & \textbf{Random}\\
Elemental Plane & DC 7 / 1 week & 01-34 & 35-62 & 63-83 & 84-100\\
(Element Appropriate) & DC 7 / 1 week & 01-68 & 69-75 & 76-98 & 99-100\\
Positive / Negative Energy Plane & DC 8 / 1 week & 01-39 & 40-65 & 66-86 & 87-100\\
Astral Plane & DC 9 / 1 week & 01-44 & 45-67 & 68-88 & 89-100\\
Outer Plane, demideity & DC 10 / 2 weeks & 01-49 & 50-70 & 71-91 & 92-100\\
Outer Plane, lesser deity & DC 12 / 3 weeks & 01-60 & 61-75 & 76-95 & 96-100\\
Outer Plane, intermediate deity & DC 14 / 4 weeks & 01-73 & 74-81 & 82-98 & 99-100\\
Outer Plane, greater deity & DC 16 / 5 weeks & 01-88 & 89-90 & 91-99 & 100\\
\end{tabular}
\end{table}

\textit{Avoid Int/Cha Decrease:} You must succeed on an Intelligence check against 
this DC to avoid a decrease in Intelligence and Charisma. If the check fails, your 
Intelligence and Charisma scores each fall to 8 for the stated duration, and you 
become unable to cast arcane spells. If you lose Intelligence and Charisma, the 
effect strikes as soon as the first question is asked, and no answer is received. 
(The entries in parentheses are for questions that pertain to the appropriate Elemental 
Plane.)

\textbf{Results of a Successful Contact:} d\% is rolled for the result shown on 
the table:

\textit{True Answer:} You get a true, one-word answer. Questions that cannot be 
answered in this way are answered randomly.

\textit{Don't Know:} The entity tells you that it doesn't know.

\textit{Lie:} The entity intentionally lies to you.

\textit{Random:} The entity tries to lie but doesn't know the answer, so 
it makes one up.

