\spellentry{Contingency}

Evocation

\textbf{Level:} Sor/Wiz 6

\textbf{Components:} V, S, M, F

\textbf{Casting Time:} At least 10 minutes; see text

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} One day/level (D) or until discharged

You can place another spell upon your person so that it comes into effect under 
some condition you dictate when casting \textit{contingency}. The \textit{contingency 
}spell and the companion spell are cast at the same time. The 10-minute casting 
time is the minimum total for both castings; if the companion spell has a casting 
time longer than 10 minutes, use that instead.

The spell to be brought into effect by the \textit{contingency} must be one that 
affects your person and be of a spell level no higher than one-third your caster 
level (rounded down, maximum 6th level).

The conditions needed to bring the spell into effect must be clear, although they 
can be general. In all cases, the \textit{contingency} immediately brings into 
effect the companion spell, the latter being "cast" instantaneously when the 
prescribed circumstances occur. If complicated or convoluted conditions are prescribed, 
the whole spell combination (\textit{contingency} and the companion magic) may 
fail when called on. The companion spell occurs based solely on the stated conditions, 
regardless of whether you want it to.

You can use only one \textit{contingency} spell at a time; if a second is cast, 
the first one (if still active) is dispelled.

\textit{Material Component:} That of the companion spell, plus quicksilver and 
an eyelash of an ogre mage, rakshasa, or similar spell-using creature.

\textit{Focus:} A statuette of you carved from elephant ivory and decorated with 
gems (worth at least 1,500 gp). You must carry the focus for the \textit{contingency 
}to work.

