\spellentry{Control Water}

Transmutation [Water]

\textbf{Level:} Clr 4, Drd 4, Sor/Wiz 6, Water 4

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Area:} Water in a volume of 10 ft./level by 10 ft./level by 2 ft./level 
(S)

\textbf{Duration:} 10 min./level (D)

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} No

Depending on the version you choose, the \textit{control water} spell raises or 
lowers water.

\textit{Lower Water:} This causes water or similar liquid to reduce its depth by 
as much as 2 feet per caster level (to a minimum depth of 1 inch). The water is 
lowered within a squarish depression whose sides are up to caster level x 10 feet 
long. In extremely large and deep bodies of water, such as a deep ocean, the spell 
creates a whirlpool that sweeps ships and similar craft downward, putting them 
at risk and rendering them unable to leave by normal movement for the duration 
of the spell. When cast on water elementals and other water-based creatures, this 
spell acts as a \textit{slow} spell (Will negates). The spell has no effect on 
other creatures.

\textit{Raise Water:} This causes water or similar liquid to rise in height, just 
as the \textit{lower water} version causes it to lower. Boats raised in this way 
slide down the sides of the hump that the spell creates. If the area affected by 
the spell includes riverbanks, a beach, or other land nearby, the water can spill 
over onto dry land.

With either version, you may reduce one horizontal dimension by half and double 
the other horizontal dimension.

\textit{Arcane Material Component:} A drop of water (for \textit{raise water}) 
or a pinch of dust (for \textit{lower water}).

