\spellentry{Create Undead}

Necromancy [Evil]

\textbf{Level:} Clr 6, Death 6, Evil 6, Sor/Wiz 6

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 hour

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One corpse

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

A much more potent spell than \textit{animate dead}, this evil spell allows you 
to create more powerful sorts of undead: ghouls, ghasts, mummies, and mohrgs. The 
type or types of undead you can create is based on your caster level, as shown 
on the table below.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
\textbf{Caster Level}\end{minipage}} & \multicolumn{1}{p{1.126in}|}{\begin{minipage}[t]{1.126in}\raggedright
\textbf{Undead Created}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
11th or lower\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Ghoul\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
12th-14th\end{minipage}} & \multicolumn{1}{p{1.126in}|}{\begin{minipage}[t]{1.126in}\raggedright
Ghast\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
15th-17th\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Mummy\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
18th or higher\end{minipage}} & \multicolumn{3}{p{1.265in}|}{\begin{minipage}[t]{1.265in}\raggedright
Mohrg\end{minipage}}\\
\hline
\end{longtable}

You may create less powerful undead than your level would allow if you choose. 
Created undead are not automatically under the control of their animator. If you 
are capable of commanding undead, you may attempt to command the undead creature 
as it forms.

This spell must be cast at night.

\textit{Material Component:} A clay pot filled with grave dirt and another filled 
with brackish water. The spell must be cast on a dead body. You must place a black 
onyx gem worth at least 50 gp per HD of the undead to be created into the mouth 
or eye socket of each corpse. The magic of the spell turns these gems into worthless 
shells.

