\spellentry{Crown of Glory}

Evocation

\textbf{Level:} Glory 8

\textbf{Components:} V, S , M, D F

\textbf{Casting Time:} 1 full round

\textbf{Range:} Personal

\textbf{Area:} 120-ft.-radius emanation centered on you

\textbf{Duration:} 1 minute/level

\textbf{Saving Throw:} Will negates

\textbf{Spell Resistance:} Yes

The caster is imbued with an aura of celestial authority, inspiring awe in all 
lesser creatures.

The caster gains a +4 enhancement bonus to his or her Charisma score for the duration 
of the spell. All creatures with fewer than 8 HD or levels cease whatever they 
are doing and are compelled to pay attention to the caster. Any such creature that 
wants to take hostile action against the caster must make a successful Will save 
to do so. Any creature that does not make this saving throw the first time it attempts 
a hostile action is \textit{enthralled} for the duration of the spell (as the \textit{enthrall 
}spell), as long as it is in the spell's area, nor will it try to leave the area 
on its own. Creatures with 8 HD or more may pay attention to the caster, but are 
not affected by this spell.

When the caster speaks, all listeners telepathically understand him or her, even 
if they do not understand the language. While the spell lasts, the caster can make 
up to three suggestions to creatures of fewer than 8 HD in range, as if using the 
\textit{mass suggestion} spell (Will save negates); creatures with 8 HD or more 
aren't affected by this power. Only creatures within range at the time a \textit{suggestion 
}is given are subject to it.

\textit{Material Component:} worth at least 200 gp.
