\spellentry{Detect Thoughts}

Divination [Mind-Affecting]

\textbf{Level:} Brd 2, Knowledge 2, Sor/Wiz 2

\textbf{Components:} V, S, F/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Area:} Cone-shaped emanation

\textbf{Duration:} Concentration, up to 1 min./level (D)

\textbf{Saving Throw:} Will negates; see text

\textbf{Spell Resistance:} No

You detect surface thoughts. The amount of information revealed depends on how 
long you study a particular area or subject.

\textit{1st Round:} Presence or absence of thoughts (from conscious creatures with 
Intelligence scores of 1 or higher).

\textit{2nd Round:} Number of thinking minds and the Intelligence score of each. 
If the highest Intelligence is 26 or higher (and at least 10 points higher than 
your own Intelligence score), you are stunned for 1 round and the spell ends. This 
spell does not let you determine the location of the thinking minds if you can't 
see the creatures whose thoughts you are detecting.

\textit{3rd Round:} Surface thoughts of any mind in the area. A target's Will save 
prevents you from reading its thoughts, and you must cast \textit{detect thoughts 
}again to have another chance. Creatures of animal intelligence (Int 1 or 2) have 
simple, instinctual thoughts that you can pick up.

Each round, you can turn to detect thoughts in a new area. The spell can penetrate 
barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 
3 feet of wood or dirt blocks it.

\textit{Arcane Focus:} A copper piece.

