\spellentry{Detect Magic}

Divination

\textbf{Level:} Brd 0, Clr 0, Drd 0, Sor/Wiz 0

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Area:} Cone-shaped emanation

\textbf{Duration:} Concentration, up to 1 min./level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You detect magical auras. The amount of information revealed depends on how long 
you study a particular area or subject.

\textit{1st Round:} Presence or absence of magical auras.

\textit{2nd Round:} Number of different magical auras and the power of the most 
potent aura.

\textit{3rd Round:} The strength and location of each aura. If the items or creatures 
bearing the auras are in line of sight, you can make Spellcraft skill checks to 
determine the school of magic involved in each. (Make one check per aura; DC 15 
+ spell level, or 15 + half caster level for a nonspell effect.)

Magical areas, multiple types of magic, or strong local magical emanations may 
distort or conceal weaker auras.

\textit{Aura Strength:} An aura's power depends on a spell's functioning spell 
level or an item's caster level. If an aura falls into more than one category, 
\textit{detect magic} indicates the stronger of the two.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{1}{|p{1.448in}|}{\begin{minipage}[t]{1.448in}\raggedright
\textbf{} \end{minipage}} & \multicolumn{4}{p{2.775in}|}{\begin{minipage}[t]{2.775in}\centering
 --  --  --  --  --  --  --  --  -- \textbf{ Aura Power  --  --  --  --  --  --  --  --  -- }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
\textbf{Spell or Object}\end{minipage}} & \multicolumn{4}{p{0.222in}|}{\begin{minipage}[t]{0.222in}\centering
\textbf{Faint}\end{minipage}} & \multicolumn{1}{|p{1.448in}|}{\begin{minipage}[t]{1.448in}\centering
\textbf{Moderate}\end{minipage}} & \multicolumn{1}{p{0.668in}|}{\begin{minipage}[t]{0.668in}\centering
\textbf{Strong}\end{minipage}} & \multicolumn{1}{p{0.582in}|}{\begin{minipage}[t]{0.582in}\centering
\textbf{Overwhelming}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.570in}|}{\begin{minipage}[t]{0.570in}\centering
Functioning spell (spell level)\end{minipage}} & \multicolumn{1}{p{0.955in}|}{\begin{minipage}[t]{0.955in}\centering
3rd or lower\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
4th-6th\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
7th-9th\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
10th+ (deity-level)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
Magic item (caster level)\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\centering
5th or lower\end{minipage}} & \multicolumn{1}{|p{1.448in}|}{\begin{minipage}[t]{1.448in}\centering
6th-11th\end{minipage}} & \multicolumn{1}{p{0.668in}|}{\begin{minipage}[t]{0.668in}\centering
12th-20th\end{minipage}} & \multicolumn{1}{p{0.582in}|}{\begin{minipage}[t]{0.582in}\centering
21st+ (artifact)\end{minipage}}\\
\hline
\end{longtable}

\textit{Lingering Aura:} A magical aura lingers after its original source dissipates 
(in the case of a spell) or is destroyed (in the case of a magic item). If \textit{detect 
magic} is cast and directed at such a location, the spell indicates an aura strength 
of dim (even weaker than a faint aura). How long the aura lingers at this dim level 
depends on its original power:

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
\textbf{Original Strength}\end{minipage}} & \multicolumn{1}{p{1.806in}|}{\begin{minipage}[t]{1.806in}\raggedright
\textbf{Duration of Lingering Aura}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Faint\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d6 rounds\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
Moderate\end{minipage}} & \multicolumn{1}{p{1.806in}|}{\begin{minipage}[t]{1.806in}\raggedright
1d6 minutes\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Strong\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d6x10 minutes\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
Overwhelming\end{minipage}} & \multicolumn{3}{p{1.944in}|}{\begin{minipage}[t]{1.944in}\raggedright
1d6 days\end{minipage}}\\
\hline
\end{longtable}

Outsiders and elementals are not magical in themselves, but if they are summoned, 
the conjuration spell registers.

Each round, you can turn to detect magic in a new area. The spell can penetrate 
barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 
3 feet of wood or dirt blocks it.

\textit{Detect magic} can be made permanent with a \textit{permanency} spell.

