\spellentry{Detect Undead}

Divination

\textbf{Level:} Clr 1, Pal 1, Sor/Wiz 1

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Area:} Cone-shaped emanation

\textbf{Duration:} Concentration, up to 1 minute/ level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You can detect the aura that surrounds undead creatures. The amount of information 
revealed depends on how long you study a particular area.

\textit{1st Round:} Presence or absence of undead auras.

\textit{2nd Round:} Number of undead auras in the area and the strength of the 
strongest undead aura present. If you are of good alignment, and the strongest 
undead aura's strength is overwhelming (see below), and the creature has HD of 
at least twice your character level, you are stunned for 1 round and the spell 
ends.

\textit{3rd Round:} The strength and location of each undead aura. If an aura is 
outside your line of sight, then you discern its direction but not its exact location.

\textit{Aura Strength:} The strength of an undead aura is determined by the HD 
of the undead creature, as given on the following table:

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.829in}|}{\begin{minipage}[t]{0.829in}\raggedright
\textbf{HD}\end{minipage}} & \multicolumn{1}{p{0.983in}|}{\begin{minipage}[t]{0.983in}\raggedright
\textbf{Strength}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1 or lower\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Faint\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.829in}|}{\begin{minipage}[t]{0.829in}\raggedright
2-4\end{minipage}} & \multicolumn{1}{p{0.983in}|}{\begin{minipage}[t]{0.983in}\raggedright
Moderate\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
5-10\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Strong\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.829in}|}{\begin{minipage}[t]{0.829in}\raggedright
11 or higher\end{minipage}} & \multicolumn{3}{p{1.122in}|}{\begin{minipage}[t]{1.122in}\raggedright
Overwhelming\end{minipage}}\\
\hline
\end{longtable}

\textit{Lingering Aura:} An undead aura lingers after its original source is destroyed. 
If \textit{detect undead} is cast and directed at such a location, the spell indicates 
an aura strength of dim (even weaker than a faint aura). How long the aura lingers 
at this dim level depends on its original power:

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
\textbf{Original Strength}\end{minipage}} & \multicolumn{1}{p{1.806in}|}{\begin{minipage}[t]{1.806in}\raggedright
\textbf{Duration of Lingering Aura}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Faint\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d6 rounds\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
Moderate\end{minipage}} & \multicolumn{1}{p{1.806in}|}{\begin{minipage}[t]{1.806in}\raggedright
1d6 minutes\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Strong\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d6x10 minutes\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.203in}|}{\begin{minipage}[t]{1.203in}\raggedright
Overwhelming\end{minipage}} & \multicolumn{3}{p{1.944in}|}{\begin{minipage}[t]{1.944in}\raggedright
1d6 days\end{minipage}}\\
\hline
\end{longtable}

Each round, you can turn to detect undead in a new area. The spell can penetrate 
barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 
3 feet of wood or dirt blocks it.

\textit{Arcane Material Component:} A bit of earth from a grave.

