\spellentry{Dictum}

Evocation [Lawful, Sonic]

\textbf{Level:} Clr 7, Law 7

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 40 ft.

\textbf{Area:} Nonlawful creatures in a 40-ft.-radius spread centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None or Will negates; see text

\textbf{Spell Resistance:} Yes

Any nonlawful creature within the area of a \textit{dictum} spell suffers the following 
ill effects.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
\textbf{HD}\end{minipage}} & \multicolumn{1}{p{2.133in}|}{\begin{minipage}[t]{2.133in}\raggedright
\textbf{Effect}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Equal to caster level\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Deafened\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
Up to caster level -1\end{minipage}} & \multicolumn{1}{p{2.133in}|}{\begin{minipage}[t]{2.133in}\raggedright
\textit{Slowed}, deafened\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Up to caster level -5\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Paralyzed, \textit{slowed}, deafened\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
Up to caster level -10\end{minipage}} & \multicolumn{3}{p{2.272in}|}{\begin{minipage}[t]{2.272in}\raggedright
Killed, paralyzed, \textit{slowed}, deafened\end{minipage}}\\
\hline
\end{longtable}

The effects are cumulative and concurrent. No saving throw is allowed against these 
effects.

\textit{Deafened:} The creature is deafened for 1d4 rounds.

\textit{Slowed:} The creature is \textit{slowed}, as by the \textit{slow} spell, 
for 2d4 rounds.

\textit{Paralyzed:} The creature is paralyzed and helpless for 1d10 minutes.

\textit{Killed:} Living creatures die. Undead creatures are destroyed.

Furthermore, if you are on your home plane when you cast this spell, nonlawful 
extraplanar creatures within the area are instantly banished back to their home 
planes. Creatures so banished cannot return for at least 24 hours. This effect 
takes place regardless of whether the creatures hear the \textit{dictum}. The banishment 
effect allows a Will save (at a -4 penalty) to negate.

Creatures whose HD exceed your caster level are unaffected by \textit{dictum}.

