\spellentry{Dimension Door}

Conjuration (Teleportation)

\textbf{Level:} Brd 4, Sor/Wiz 4, Travel 4

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Target:} You and touched objects or other touched willing creatures

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None and Will negates (object)

\textbf{Spell Resistance:} No and Yes (object)

You instantly transfer yourself from your current location to any other spot within 
range. You always arrive at exactly the spot desired -- whether by simply visualizing 
the area or by stating direction. After using this spell, you can't take any other 
actions until your next turn. You can bring along objects as long as their weight 
doesn't exceed your maximum load. You may also bring one additional willing Medium 
or smaller creature (carrying gear or objects up to its maximum load) or its equivalent 
per three caster levels. A Large creature counts as two Medium creatures, a Huge 
creature counts as two Large creatures, and so forth. All creatures to be transported 
must be in contact with one another, and at least one of those creatures must be 
in contact with you.

If you arrive in a place that is already occupied by a solid body, you and each 
creature traveling with you take 1d6 points of damage and are shunted to a random 
open space on a suitable surface within 100 feet of the intended location.

If there is no free space within 100 feet, you and each creature traveling with 
you take an additional 2d6 points of damage and are shunted to a free space within 
1,000 feet. If there is no free space within 1,000 feet, you and each creature 
travelling with you take an additional 4d6 points of damage and the spell simply 
fails.

