\spellentry{Disintegrate}

Transmutation

\textbf{Level:} Destruction 7, Sor/Wiz 6

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Ray

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Fortitude partial (object)

\textbf{Spell Resistance:} Yes

A thin, green ray springs from your pointing finger. You must make a successful 
ranged touch attack to hit. Any creature struck by the ray takes 2d6 points of 
damage per caster level (to a maximum of 40d6). Any creature reduced to 0 or fewer 
hit points by this spell is entirely disintegrated, leaving behind only a trace 
of fine dust. A disintegrated creature's equipment is unaffected.

When used against an object, the ray simply disintegrates as much as one 10- foot 
cube of nonliving matter. Thus, the spell disintegrates only part of any very large 
object or structure targeted. The ray affects even objects constructed entirely 
of force, such as \textit{forceful hand} or a \textit{wall of force}, but not magical 
effects such as a \textit{globe of invulnerability} or an \textit{antimagic field}.

A creature or object that makes a successful Fortitude save is partially affected, 
taking only 5d6 points of damage. If this damage reduces the creature or object 
to 0 or fewer hit points, it is entirely disintegrated.

Only the first creature or object struck can be affected; that is, the ray affects 
only one target per casting.

\textit{Arcane Material Component:} A lodestone and a pinch of dust.

