\spellentry{Dominate Person}

Enchantment (Compulsion) [Mind-Affecting]

\textbf{Level:} Brd 4, Sor/Wiz 5

\textbf{Components:} V, S

\textbf{Casting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One humanoid

\textbf{Duration:} One day/level

\textbf{Saving Throw:} Will negates

\textbf{Spell Resistance:} Yes

You can control the actions of any humanoid creature through a telepathic link 
that you establish with the subject's mind.

If you and the subject have a common language, you can generally force the subject 
to perform as you desire, within the limits of its abilities. If no common language 
exists, you can communicate only basic commands, such as "Come here," "Go there," 
"Fight," and "Stand still." You know what the subject is experiencing, but 
you do not receive direct sensory input from it, nor can it communicate with you 
telepathically.

Once you have given a \textit{dominated} creature a command, it continues to attempt 
to carry out that command to the exclusion of all other activities except those 
necessary for day-to-day survival (such as sleeping, eating, and so forth). Because 
of this limited range of activity, a Sense Motive check against DC 15 (rather than 
DC 25) can determine that the subject's behavior is being influenced by an enchantment 
effect (see the Sense Motive skill description).

Changing your instructions or giving a \textit{dominated} creature a new command 
is the equivalent of redirecting a spell, so it is a move action.

By concentrating fully on the spell (a standard action), you can receive full sensory 
input as interpreted by the mind of the subject, though it still can't communicate 
with you. You can't actually see through the subject's eyes, so it's not as good 
as being there yourself, but you still get a good idea of what's going on.

Subjects resist this control, and any subject forced to take actions against its 
nature receives a new saving throw with a +2 bonus. Obviously self-destructive 
orders are not carried out. Once control is established, the range at which it 
can be exercised is unlimited, as long as you and the subject are on the same plane. 
You need not see the subject to control it.

If you don't spend at least 1 round concentrating on the spell each day, the subject 
receives a new saving throw to throw off the domination.

\textit{Protection from evil} or a similar spell can prevent you from exercising 
control or using the telepathic link while the subject is so warded, but such an 
effect neither prevents the establishment of domination nor dispels it.

