\spellentry{Dream}

Illusion (Phantasm) [Mind-Affecting]

\textbf{Level:} Brd 5, Sor/Wiz 5

\textbf{Components:} V, S

\textbf{Casting Time:} 1 minute

\textbf{Range:} Unlimited

\textbf{Target:} One living creature touched

\textbf{Duration:} See text

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

You, or a messenger touched by you, sends a phantasmal message to others in the 
form of a dream. At the beginning of the spell, you must name the recipient or 
identify him or her by some title that leaves no doubt as to identity. The messenger 
then enters a trance, appears in the intended recipient's dream, and delivers the 
message. The message can be of any length, and the recipient remembers it perfectly 
upon waking. The communication is one-way. The recipient cannot ask questions or 
offer information, nor can the messenger gain any information by observing the 
dreams of the recipient.

Once the message is delivered, the messenger's mind returns instantly to its body. 
The duration of the spell is the time required for the messenger to enter the recipient's 
dream and deliver the message.

If the recipient is awake when the spell begins, the messenger can choose to wake 
up (ending the spell) or remain in the trance. The messenger can remain in the 
trance until the recipient goes to sleep, then enter the recipient's dream and 
deliver the message as normal. A messenger that is disturbed during the trance 
comes awake, ending the spell.

Creatures who don't sleep (such as elves, but not half-elves) or don't dream cannot 
be contacted by this spell.

The messenger is unaware of its own surroundings or of the activities around it 
while in the trance. It is defenseless both physically and mentally (always fails 
any saving throw) while in the trance.

