\spellentry{Earthquake}

Evocation [Earth]

\textbf{Level:} Clr 8, Destruction 8, Drd 8, Earth 7

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Area:} 80-ft.-radius spread (S)

\textbf{Duration:} 1 round

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} No

When you cast \textit{earthquake}, an intense but highly localized tremor rips 
the ground. The shock knocks creatures down, collapses structures, opens cracks 
in the ground, and more. The effect lasts for 1 round, during which time creatures 
on the ground can't move or attack. A spellcaster on the ground must make a Concentration 
check (DC 20 + spell level) or lose any spell he or she tries to cast. The earthquake 
affects all terrain, vegetation, structures, and creatures in the area. The specific 
effect of an \textit{earthquake} spell depends on the nature of the terrain where 
it is cast.

\textit{Cave, Cavern, or Tunnel:} The spell collapses the roof, dealing 8d6 points 
of bludgeoning damage to any creature caught under the cave-in (Reflex DC 15 half 
) and pinning that creature beneath the rubble (see below). An \textit{earthquake 
}cast on the roof of a very large cavern could also endanger those outside the 
actual area but below the falling debris.

\textit{Cliffs: Earthquake} causes a cliff to crumble, creating a landslide that 
travels horizontally as far as it fell vertically. Any creature in the path takes 
8d6 points of bludgeoning damage (Reflex DC 15 half ) and is pinned beneath the 
rubble (see below).

\textit{Open Ground:} Each creature standing in the area must make a DC 15 Reflex 
save or fall down. Fissures open in the earth, and every creature on the ground 
has a 25\% chance to fall into one (Reflex DC 20 to avoid a fissure). At the end 
of the spell, all fissures grind shut, killing any creatures still trapped within.

\textit{Structure:} Any structure standing on open ground takes 100 points of damage, 
enough to collapse a typical wooden or masonry building, but not a structure built 
of stone or reinforced masonry. Hardness does not reduce this damage, nor is it 
halved as damage dealt to objects normally is. Any creature caught inside a collapsing 
structure takes 8d6 points of bludgeoning damage (Reflex DC 15 half ) and is pinned 
beneath the rubble (see below).

\textit{River, Lake, or Marsh:} Fissures open underneath the water, draining away 
the water from that area and forming muddy ground. Soggy marsh or swampland becomes 
quicksand for the duration of the spell, sucking down creatures and structures. 
Each creature in the area must make a DC 15 Reflex save or sink down in the mud 
and quicksand. At the end of the spell, the rest of the body of water rushes in 
to replace the drained water, possibly drowning those caught in the mud.

\textit{Pinned beneath Rubble:} Any creature pinned beneath rubble takes 1d6 points 
of nonlethal damage per minute while pinned. If a pinned character falls unconscious, 
he or she must make a DC 15 Constitution check or take 1d6 points of lethal damage 
each minute thereafter until freed or dead.

