\spellentry{Enlarge Person}

Transmutation

\textbf{Level:} Sor/Wiz 1, Strength 1

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One humanoid creature

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Fortitude negates

\textbf{Spell Resistance:} Yes

This spell causes instant growth of a humanoid creature, doubling its height and 
multiplying its weight by 8. This increase changes the creature's size category 
to the next larger one. The target gains a +2 size bonus to Strength, a -2 size 
penalty to Dexterity (to a minimum of 1), and a -1 penalty on attack rolls and 
AC due to its increased size.

A humanoid creature whose size increases to Large has a space of 10 feet and a 
natural reach of 10 feet. This spell does not change the target's speed.

If insufficient room is available for the desired growth, the creature attains 
the maximum possible size and may make a Strength check (using its increased Strength) 
to burst any enclosures in the process. If it fails, it is constrained without 
harm by the materials enclosing it --  the spell cannot be used to crush a creature 
by increasing its size.

All equipment worn or carried by a creature is similarly enlarged by the spell. 
Melee and projectile weapons affected by this spell deal more damage. Other magical 
properties are not affected by this spell. Any \textit{enlarged} item that leaves 
an \textit{enlarged} creature's possession (including a projectile or thrown weapon) 
instantly returns to its normal size. This means that thrown weapons deal their 
normal damage, and projectiles deal damage based on the size of the weapon that 
fired them. Magical properties of \textit{enlarged} items are not increased by 
this spell.

Multiple magical effects that increase size do not stack,.

\textit{Enlarge person} counters and dispels \textit{reduce person}.

\textit{Enlarge person} can be made permanent with a \textit{permanency} spell.

\textit{Material Component:} A pinch of powdered iron.

