\spellentry{Enthrall}

Enchantment (Charm) [Language Dependent, Mind-Affecting, Sonic]

\textbf{Level:} Brd 2, Clr 2

\textbf{Components:} V, S

\textbf{Casting Time:} 1 round

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Targets:} Any number of creatures

\textbf{Duration:} 1 hour or less

\textbf{Saving Throw:} Will negates; see text

\textbf{Spell Resistance:} Yes

If you have the attention of a group of creatures, you can use this spell to hold 
them spellbound. To cast the spell, you must speak or sing without interruption 
for 1 full round. Thereafter, those affected give you their undivided attention, 
ignoring their surroundings. They are considered to have an attitude of friendly 
while under the effect of the spell. Any potentially affected creature of a race 
or religion unfriendly to yours gets a +4 bonus on the saving throw.

A creature with 4 or more HD or with a Wisdom score of 16 or higher remains aware 
of its surroundings and has an attitude of indifferent. It gains a new saving throw 
if it witnesses actions that it opposes.

The effect lasts as long as you speak or sing, to a maximum of 1 hour. Those \textit{enthralled 
}by your words take no action while you speak or sing and for 1d3 rounds thereafter 
while they discuss the topic or performance. Those entering the area during the 
performance must also successfully save or become \textit{enthralled}. The speech 
ends (but the 1d3-round delay still applies) if you lose concentration or do anything 
other than speak or sing.

If those not \textit{enthralled} have unfriendly or hostile attitudes toward you, 
they can collectively make a Charisma check to try to end the spell by jeering 
and heckling. For this check, use the Charisma bonus of the creature with the highest 
Charisma in the group; others may make Charisma checks to assist. The heckling 
ends the spell if this check result beats your Charisma check result. Only one 
such challenge is allowed per use of the spell.

If any member of the audience is attacked or subjected to some other overtly hostile 
act, the spell ends and the previously \textit{enthralled} members become immediately 
unfriendly toward you. Each creature with 4 or more HD or with a Wisdom score of 
16 or higher becomes hostile.

