\spellentry{Ethereal Jaunt}

Transmutation

\textbf{Level:} Clr 7, Sor/Wiz 7

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level (D)

You become ethereal, along with your equipment. For the duration of the spell, 
you are in a place called the Ethereal Plane, which overlaps the normal, physical, 
Material Plane. When the spell expires, you return to material existence.

An ethereal creature is invisible, insubstantial, and capable of moving in any 
direction, even up or down, albeit at half normal speed. As an insubstantial creature, 
you can move through solid objects, including living creatures. An ethereal creature 
can see and hear on the Material Plane, but everything looks gray and ephemeral. 
Sight and hearing onto the Material Plane are limited to 60 feet.

Force effects and abjurations affect an ethereal creature normally. Their effects 
extend onto the Ethereal Plane from the Material Plane, but not vice versa. An 
ethereal creature can't attack material creatures, and spells you cast while ethereal 
affect only other ethereal things. Certain material creatures or objects have attacks 
or effects that work on the Ethereal Plane.

Treat other ethereal creatures and ethereal objects as if they were material. 

If you end the spell and become material while inside a material object (such as 
a solid wall), you are shunted off to the nearest open space and take 1d6 points 
of damage per 5 feet that you so travel.

