\spellentry{Feather Fall}

Transmutation

\textbf{Level:} Brd 1, Sor/Wiz 1

\textbf{Components:} V

\textbf{Casting Time:} 1 free action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} One Medium or smaller freefalling object or creature/level, no 
two of which may be more than 20 ft. apart

\textbf{Duration:} Until landing or 1 round/level

\textbf{Saving Throw:} Will negates (harmless) or Will negates (object)

\textbf{Spell Resistance:} Yes (object)

The affected creatures or objects fall slowly. \textit{Feather fall} instantly 
changes the rate at which the targets fall to a mere 60 feet per round (equivalent 
to the end of a fall from a few feet), and the subjects take no damage upon landing 
while the spell is in effect. However, when the spell duration expires, a normal 
rate of falling resumes.

The spell affects one or more Medium or smaller creatures (including gear and carried 
objects up to each creature's maximum load) or objects, or the equivalent in larger 
creatures: A Large creature or object counts as two Medium creatures or objects, 
a Huge creature or object counts as two Large creatures or objects, and so forth.

You can cast this spell with an instant utterance, quickly enough to save yourself 
if you unexpectedly fall. Casting the spell is a free action, like casting a quickened 
spell, and it counts toward the normal limit of one quickened spell per round. 
You may even cast this spell when it isn't your turn.

This spell has no special effect on ranged weapons unless they are falling quite 
a distance. If the spell is cast on a falling item the object does half normal 
damage based on its weight, with no bonus for the height of the drop.

\textit{Feather fall} works only upon free-falling objects. It does not affect 
a sword blow or a charging or flying creature.

