\spellentry{Find the Path}

Divination

\textbf{Level:} Brd 6, Clr 6, Drd 6, Knowledge 6, Travel 6

\textbf{Components:} V, S, F

\textbf{Casting Time:} 3 rounds

\textbf{Range:} Personal or touch

\textbf{Target:} You or creature touched

\textbf{Duration:} 10 min./level

\textbf{Saving Throw:} None or Will negates (harmless)

\textbf{Spell Resistance:} No or Yes (harmless)

The recipient of this spell can find the shortest, most direct physical route to 
a specified destination, be it the way into or out of a locale. The locale can 
be outdoors, underground, or even inside a \textit{maze} spell. \textit{Find the 
path} works with respect to locations, not objects or creatures at a locale. The 
location must be on the same plane as you are at the time of casting.

The spell enables the subject to sense the correct direction that will eventually 
lead it to its destination, indicating at appropriate times the exact path to follow 
or physical actions to take. For example, the spell enables the subject to sense 
trip wires or the proper word to bypass a \textit{glyph of warding}. The spell 
ends when the destination is reached or the duration expires, whichever comes first. 
\textit{Find the path} can be used to remove the subject and its companions from 
the effect of a \textit{maze} spell in a single round.

This divination is keyed to the recipient, not its companions, and its effect does 
not predict or allow for the actions of creatures (including guardians).

\textit{Focus:} A set of divination counters of the sort you favor.

