\spellentry{Fire Shield}

Evocation [Fire or Cold]

\textbf{Level:} Fire 5, Sor/Wiz 4, Sun 4

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level (D)

This spell wreathes you in flame and causes damage to each creature that attacks 
you in melee. The flames also protect you from either cold-based or fire-based 
attacks (your choice).

Any creature striking you with its body or a handheld weapon deals normal damage, 
but at the same time the attacker takes 1d6 points of damage +1 point per caster 
level (maximum +15). This damage is either cold damage (if the \textit{shield} protects 
against fire-based attacks) or fire damage (if the \textit{shield} protects against 
cold-based attacks). If the attacker has spell resistance, it applies to this effect. 
Creatures wielding weapons with exceptional reach are not subject to this damage 
if they attack you.

When casting this spell, you appear to immolate yourself, but the flames are thin 
and wispy, giving off light equal to only half the illumination of a normal torch 
(10 feet). The color of the flames is determined randomly (50\% chance of either 
color) -- blue or green if the \textit{chill shield} is cast, violet or blue if 
the \textit{warm shield} is employed. The special powers of each version are as 
follows.

\textit{Warm Shield:} The flames are warm to the touch. You take only half damage 
from cold-based attacks. If such an attack allows a Reflex save for half damage, 
you take no damage on a successful save.

\textit{Chill Shield:} The flames are cool to the touch. You take only half damage 
from fire-based attacks. If such an attack allows a Reflex save for half damage, 
you take no damage on a successful save.

\textit{Arcane Material Component:} A bit of phosphorus for the \textit{warm shield; 
}a live firefly or glowworm or the tail portions of four dead ones for the \textit{chill 
shield}.

