\spellentry{Fire Seeds}

Conjuration (Creation) [Fire]

\textbf{Level:} Drd 6, Fire 6, Sun 6

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Targets:} Up to four touched acorns or up to eight touched holly berries

\textbf{Duration:} 10 min./level or until used

\textbf{Saving Throw:} None or Reflex half; see text

\textbf{Spell Resistance:} No

Depending on the version of \textit{fire seeds} you choose, you turn acorns into 
splash weapons that you or another character can throw, or you turn holly berries 
into bombs that you can detonate on command.

\textit{Acorn Grenades:} As many as four acorns turn into special splash weapons 
that can be hurled as far as 100 feet. A ranged touch attack roll is required to 
strike the intended target. Together, the acorns are capable of dealing 1d6 points 
of fire damage per caster level (maximum 20d6), divided up among the acorns as 
you wish.

Each acorn explodes upon striking any hard surface. In addition to its regular 
fire damage, it deals 1 point of splash damage per die, and it ignites any combustible 
materials within 10 feet. A creature within this area that makes a successful Reflex 
saving throw takes only half damage; a creature struck directly is not allowed 
a saving throw.

\textit{Holly Berry Bombs:} You turn as many as eight holly berries into special 
bombs. The holly berries are usually placed by hand, since they are too light to 
make effective thrown weapons (they can be tossed only 5 feet). If you are within 
200 feet and speak a word of command, each berry instantly bursts into flame, causing 
1d8 points of fire damage +1 point per caster level to every creature in a 5-foot 
radius burst and igniting any combustible materials within 5 feet. A creature in 
the area that makes a successful Reflex saving throw takes only half damage.

\textit{Material Component:} The acorns or holly berries.

