\spellentry{Forcecage}

Evocation [Force]

\textbf{Level:} Sor/Wiz 7

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} Barred cage (20-ft. cube) or windowless cell (10-ft. cube)

\textbf{Duration:} 2 hours/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

This powerful spell brings into being an immobile, invisible cubical prison composed 
of either bars of force or solid walls of force (your choice).

Creatures within the area are caught and contained unless they are too big to fit 
inside, in which case the spell automatically fails. Teleportation and other forms 
of astral travel provide a means of escape, but the force walls or bars extend 
into the Ethereal Plane, blocking ethereal travel.

Like a \textit{wall of force} spell, a \textit{forcecage} resists \textit{dispel 
magic}, but it is vulnerable to a \textit{disintegrate} spell, and it can be destroyed 
by a \textit{sphere of annihilation} or a \textit{rod of cancellation}.

\textit{Barred Cage:} This version of the spell produces a 20-foot cube made of 
bands of force (similar to a \textit{wall of force} spell) for bars. The bands 
are a half-inch wide, with half-inch gaps between them. Any creature capable of 
passing through such a small space can escape; others are confined. You can't attack 
a creature in a barred cage with a weapon unless the weapon can fit between the 
gaps. Even against such weapons (including arrows and similar ranged attacks), 
a creature in the barred cage has cover. All spells and breath weapons can pass 
through the gaps in the bars.

\textit{Windowless Cell:} This version of the spell produces a 10-foot cube with 
no way in and no way out. Solid walls of force form its six sides.

\textit{Material Component:} Ruby dust worth 1,500 gp, which is tossed into the 
air and disappears when you cast the spell.

