\spellentry{Geas, Lesser}\label{spell:Lesser Geas}

Enchantment (Compulsion) [Language-Dependent, Mind-Affecting]

\textbf{Level:} Brd 3, Sor/Wiz 4

\textbf{Components:} V

\textbf{Casting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One living creature with 7 HD or less

\textbf{Duration:} One day/level or until discharged (D)

\textbf{Saving Throw:} Will negates

\textbf{Spell Resistance:} Yes

A \textit{lesser geas} places a magical command on a creature to carry out some 
service or to refrain from some action or course of activity, as desired by you. 
The creature must have 7 or fewer Hit Dice and be able to understand you. While 
a \textit{geas} cannot compel a creature to kill itself or perform acts that would 
result in certain death, it can cause almost any other course of activity.

The \textit{geased} creature must follow the given instructions until the \textit{geas 
}is completed, no matter how long it takes.

If the instructions involve some open-ended task that the recipient cannot complete 
through his own actions the spell remains in effect for a maximum of one day per 
caster level. A clever recipient can subvert some instructions:

If the subject is prevented from obeying the \textit{lesser geas} for 24 hours, 
it takes a -2 penalty to each of its ability scores. Each day, another -2 penalty 
accumulates, up to a total of -8. No ability score can be reduced to less than 
1 by this effect. The ability score penalties are removed 24 hours after the subject 
resumes obeying the \textit{lesser geas}.

A \textit{lesser geas} (and all ability score penalties) can be ended by \textit{break 
enchantment}, \textit{limited wish}, \textit{remove curse}, \textit{miracle}, or 
\textit{wish}. \textit{Dispel magic} does not affect a \textit{lesser geas}.

