\spellentry{Genesis}

Conjuration (Creation)

\textbf{Level:} Sor/Wiz 9, Creation 9

\textbf{Components:} V, S , M, X P

\textbf{Casting Time:} 1 week (8 hours/day)

\textbf{Range:} 180 ft. (see text)

\textbf{Effect:} A demiplane on the Ethereal Plane, centered on your location

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

The spellcaster creates a finite plane with limited access: a demiplane. Demiplanes created by this power are very small, very minor planes.

A character can only cast this spell while on the Ethereal Plane. When he or she casts the spell, a local density fluctuation precipitates the creation of a demiplane. At first, the fledgling plane grows at a rate of 1 foot in radius per day to an initial maximum radius of 180 feet as it rapidly draws substance from surrounding ethereal vapors and protomatter.

The spellcaster determines the environment within the demiplane when he or she first casts genesis, reflecting most any desire the spellcaster can visualize. The spellcaster determines factors such as atmosphere, water, temperature, and the general shape of the terrain. This spell cannot create life (including vegetation), nor can it create construction (such as buildings, roads, wells, dungeons, and so forth). The spellcaster must add these things in some other fashion if he or she desires. Once the basic demiplane reaches its maximum size, the spellcaster can continue to cast this spell to enlarge the demiplane, adding another 180 feet of radius to the demiplane each time.

\textit{Material Component:} A crystalline sphere

\textit{XP Cost:} 5,000 XP.
