\spellentry{Giant Vermin}

Transmutation

\textbf{Level:} Clr 4, Drd 4

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} Up to three vermin, no two of which can be more than 30 ft. apart

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

You turn three normal-sized centipedes, two normal-sized spiders, or a single normal-sized 
scorpion into larger forms. Only one type of vermin can be transmuted (so a single 
casting cannot affect both a centipede and a spider), and all must be grown to 
the same size. The size to which the vermin can be grown depends on your level; 
see the table below.

Any giant vermin created by this spell do not attempt to harm you, but your control 
of such creatures is limited to simple commands ("Attack," "Defend," "Stop," 
and so forth). Orders to attack a certain creature when it appears or guard against 
a particular occurrence are too complex for the vermin to understand. Unless commanded 
to do otherwise, the giant vermin attack whoever or whatever is near them.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
\textbf{Caster Level}\end{minipage}} & \multicolumn{1}{p{0.879in}|}{\begin{minipage}[t]{0.879in}\raggedright
\textbf{Vermin Size}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
9th or lower\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Medium\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
10th-13th\end{minipage}} & \multicolumn{1}{p{0.879in}|}{\begin{minipage}[t]{0.879in}\raggedright
Large\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
14th-17th\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Huge\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.938in}|}{\begin{minipage}[t]{0.938in}\raggedright
18th-19th\end{minipage}} & \multicolumn{3}{p{1.018in}|}{\begin{minipage}[t]{1.018in}\raggedright
Gargantuan\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
20th or higher\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Colossal\end{minipage}}\\
\hline
\end{longtable}

