\spellentry{Glyph of Warding}

Abjuration

\textbf{Level:} Clr 3

\textbf{Components:} V, S, M

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Touch

\textbf{Target or Area:} Object touched or up to 5 sq. ft./level

\textbf{Duration:} Permanent until discharged (D)

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} No (object) and Yes; see text

This powerful inscription harms those who enter, pass, or open the warded area 
or object. A \textit{glyph of warding} can guard a bridge or passage, ward a portal, 
trap a chest or box, and so on.

You set the conditions of the ward. Typically, any creature entering the warded 
area or opening the warded object without speaking a password (which you set when 
casting the spell) is subject to the magic it stores. Alternatively or in addition 
to a password trigger, \textit{glyphs} can be set according to physical characteristics 
(such as height or weight) or creature type, subtype, or kind. \textit{Glyphs} can 
also be set with respect to good, evil, law, or chaos, or to pass those of your 
religion. They cannot be set according to class, Hit Dice, or level. \textit{Glyphs 
}respond to invisible creatures normally but are not triggered by those who travel 
past them ethereally. Multiple \textit{glyphs} cannot be cast on the same area. 
However, if a cabinet has three drawers, each can be separately warded.

When casting the spell, you weave a tracery of faintly glowing lines around the 
warding sigil. A \textit{glyph} can be placed to conform to any shape up to the 
limitations of your total square footage. When the spell is completed, the \textit{glyph 
}and tracery become nearly invisible.

\textit{Glyphs} cannot be affected or bypassed by such means as physical or magical 
probing, though they can be dispelled. \textit{Mislead}, \textit{polymorph}, and 
\textit{nondetection} (and similar magical effects) can fool a \textit{glyph}, 
though nonmagical disguises and the like can't. \textit{Read magic} allows you 
to identify a \textit{glyph of warding} with a DC 13 Spellcraft check. Identifying 
the \textit{glyph} does not discharge it and allows you to know the basic nature 
of the \textit{glyph} (version, type of damage caused, what spell is stored).

\textit{Note:} Magic traps such as \textit{glyph of warding} are hard to detect 
and disable. A rogue (only) can use the Search skill to find the \textit{glyph 
}and Disable Device to thwart it. The DC in each case is 25 + spell level, or 28 
for \textit{glyph of warding}.

Depending on the version selected, a \textit{glyph} either blasts the intruder 
or activates a spell.

\textit{Blast Glyph:} A \textit{blast glyph} deals 1d8 points of damage per two 
caster levels (maximum 5d8) to the intruder and to all within 5 feet of him or 
her. This damage is acid, cold, fire, electricity, or sonic (caster's choice, made 
at time of casting). Each creature affected can attempt a Reflex save to take half 
damage. Spell resistance applies against this effect.

\textit{Spell Glyph:} You can store any harmful spell of 3rd level or lower that 
you know. All level-dependent features of the spell are based on your caster level 
at the time of casting the \textit{glyph}. If the spell has a target, it targets 
the intruder. If the spell has an area or an amorphous effect the area or effect 
is centered on the intruder. If the spell summons creatures, they appear as close 
as possible to the intruder and attack. Saving throws and spell resistance operate 
as normal, except that the DC is based on the level of the spell stored in the 
\textit{glyph}.

\textit{Material Component:} You trace the \textit{glyph} with incense, which must 
first be sprinkled with powdered diamond worth at least 200 gp.

