\spellentry{Grease}

Conjuration (Creation)

\textbf{Level:} Brd 1, Sor/Wiz 1

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target or Area:} One object or a 10-ft. square

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} No

A \textit{grease} spell covers a solid surface with a layer of slippery grease. 
Any creature in the area when the spell is cast must make a successful Reflex save 
or fall. This save is repeated on your turn each round that the creature remains 
within the area. A creature can walk within or through the area of grease at half 
normal speed with a DC 10 Balance check. Failure means it can't move that round 
(and must then make a Reflex save or fall), while failure by 5 or more means it 
falls (see the Balance skill for details).

The spell can also be used to create a greasy coating on an item. Material objects 
not in use are always affected by this spell, while an object wielded or employed 
by a creature receives a Reflex saving throw to avoid the effect. If the initial 
saving throw fails, the creature immediately drops the item. A saving throw must 
be made in each round that the creature attempts to pick up or use the \textit{greased 
}item. A creature wearing \textit{greased} armor or clothing gains a +10 circumstance 
bonus on Escape Artist checks and on grapple checks made to resist or escape a 
grapple or to escape a pin.

\textit{Material Component:} A bit of pork rind or butter.

