\spellentry{Guards and Wards}

Abjuration

\textbf{Level:} Sor/Wiz 6

\textbf{Components:} V, S, M, F

\textbf{Casting Time:} 30 minutes

\textbf{Range:} Anywhere within the area to be warded

\textbf{Area:} Up to 200 sq. ft./level (S)

\textbf{Duration:} 2 hours/level (D)

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} See text

This powerful spell is primarily used to defend your stronghold. The ward protects 
200 square feet per caster level. The warded area can be as much as 20 feet high, 
and shaped as you desire. You can ward several stories of a stronghold by dividing 
the area among them; you must be somewhere within the area to be warded to cast 
the spell. The spell creates the following magical effects within the warded area.

\textit{Fog:} Fog fills all corridors, obscuring all sight, including darkvision, 
beyond 5 feet. A creature within 5 feet has concealment (attacks have a 20\% miss 
chance). Creatures farther away have total concealment (50\% miss chance, and the 
attacker cannot use sight to locate the target). Saving Throw: None. Spell Resistance: 
No.

\textit{Arcane Locks:} All doors in the warded area are \textit{arcane locked. 
}Saving Throw: None. Spell Resistance: No.

\textit{Webs:} Webs fill all stairs from top to bottom. These strands are identical 
with those created by the \textit{web} spell, except that they regrow in 10 minutes 
if they are burned or torn away while the \textit{guards and wards} spell lasts. 
Saving Throw: Reflex negates; see text for \textit{web}. Spell Resistance: No.

\textit{Confusion:} Where there are choices in direction -- such as a corridor intersection 
or side passage -- a minor \textit{confusion-}type effect functions so as to make 
it 50\% probable that intruders believe they are going in the opposite direction 
from the one they actually chose. This is an enchantment, mind-affecting effect. 
Saving Throw: None. Spell Resistance: Yes.

\textit{Lost Doors:} One door per caster level is covered by a \textit{silent image 
}to appear as if it were a plain wall. Saving Throw: Will disbelief (if interacted 
with). Spell Resistance: No.

In addition, you can place your choice of one of the following five magical effects.

1. \textit{Dancing lights} in four corridors. You can designate a simple program 
that causes the lights to repeat as long as the \textit{guards and wards} spell 
lasts. Saving Throw: None. Spell Resistance: No.

2. A \textit{magic mouth} in two places. Saving Throw: None. Spell Resistance: 
No.

3. A \textit{stinking cloud} in two places. The vapors appear in the places you 
designate; they return within 10 minutes if dispersed by wind while the \textit{guards 
and wards} spell lasts. Saving Throw: Fortitude negates; see text for \textit{stinking 
cloud}. Spell Resistance: No.

4. A \textit{gust of wind} in one corridor or room. Saving Throw: Fortitude negates. 
Spell Resistance: Yes.

5. A \textit{suggestion} in one place. You select an area of up to 5 feet square, 
and any creature who enters or passes through the area receives the \textit{suggestion 
}mentally. Saving Throw: Will negates. Spell Resistance: Yes.

The whole warded area radiates strong magic of the abjuration school. A \textit{dispel 
magic} cast on a specific effect, if successful, removes only that effect. A successful 
\textit{Mage's disjunction} destroys the entire \textit{guards and wards} effect.

\textit{Material Component:} Burning incense, a small measure of brimstone and 
oil, a knotted string, and a small amount of blood.

\textit{Focus:} A small silver rod.

