\spellentry{Gust of Wind}

Evocation [Air]

\textbf{Level:} Drd 2, Sor/Wiz 2

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Effect:} Line-shaped gust of severe wind emanating out from you to the 
extreme of the range

\textbf{Duration:} 1 round

\textbf{Saving Throw:} Fortitude negates

\textbf{Spell Resistance:} Yes

This spell creates a severe blast of air (approximately 50 mph) that originates 
from you, affecting all creatures in its path.

A Tiny or smaller creature on the ground is knocked down and rolled 1d4x10 feet, 
taking 1d4 points of nonlethal damage per 10 feet. If flying, a Tiny or smaller 
creature is blown back 2d6x10 feet and takes 2d6 points of nonlethal damage due 
to battering and buffeting.

Small creatures are knocked prone by the force of the wind, or if flying are blown 
back 1d6x10 feet.

Medium creatures are unable to move forward against the force of the wind, or if 
flying are blown back 1d6x5 feet.

Large or larger creatures may move normally within a \textit{gust of wind} effect.

A \textit{gust of wind} can't move a creature beyond the limit of its range.

Any creature, regardless of size, takes a -4 penalty on ranged attacks and Listen 
checks in the area of a \textit{gust of wind}.

The force of the \textit{gust} automatically extinguishes candles, torches, and 
similar unprotected flames. It causes protected flames, such as those of lanterns, 
to dance wildly and has a 50\% chance to extinguish those lights.

In addition to the effects noted, a \textit{gust of wind} can do anything that 
a sudden blast of wind would be expected to do. It can create a stinging spray 
of sand or dust, fan a large fire, overturn delicate awnings or hangings, heel 
over a small boat, and blow gases or vapors to the edge of its range.

\textit{Gust of wind} can be made permanent with a \textit{permanency} spell.




