\spellentry{Hallow}

Evocation [Good]

\textbf{Level:} Clr 5, Drd 5

\textbf{Components:} V, S, M, DF

\textbf{Casting Time:} 24 hours

\textbf{Range:} Touch

\textbf{Area:} 40-ft. radius emanating from the touched point

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} See text

\textit{Hallow} makes a particular site, building, or structure a holy site. This 
has four major effects.

First, the site or structure is guarded by a \textit{magic circle against evil}
effect.

Second, all Charisma checks made to turn undead gain a +4 sacred bonus, and Charisma 
checks to command undead take a -4 penalty. Spell resistance does not apply to 
this effect. (This provision does not apply to the druid version of the spell.)

Third, any dead body interred in a \textit{hallowed} site cannot be turned into 
an undead creature.

Finally, you may choose to fix a single spell effect to the \textit{hallowed} site. 
The spell effect lasts for one year and functions throughout the entire site, regardless 
of the normal duration and area or effect. You may designate whether the effect 
applies to all creatures, creatures who share your faith or alignment, or creatures 
who adhere to another faith or alignment. At the end of the year, the chosen effect 
lapses, but it can be renewed or replaced simply by casting \textit{hallow} again.

Spell effects that may be tied to a \textit{hallowed} site include \textit{aid, 
bane, bless, cause fear, darkness, daylight, death ward, deeper darkness, detect 
evil, detect magic, dimensional anchor, discern lies, dispel magic, endure elements, 
freedom of movement, invisibility purge, protection from energy, remove fear, resist 
energy, silence, tongues}, and \textit{zone of truth}. Saving throws and spell 
resistance might apply to these spells' effects. (See the individual spell descriptions 
for details.)

An area can receive only one \textit{hallow} spell (and its associated spell effect) 
at a time. \textit{Hallow} counters but does not dispel \textit{unhallow}.

\textit{Material Component:} Herbs, oils, and incense worth at least 1,000 gp, 
plus 1,000 gp per level of the spell to be included in the \textit{hallowed} area.

