\spellentry{Haste}

Transmutation

\textbf{Level:} Brd 3, Sor/Wiz 3

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} One creature/level, no two of which can be more than 30 ft. apart

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} Fortitude negates (harmless)

\textbf{Spell Resistance:} Yes (harmless)

The transmuted creatures move and act more quickly than normal. This extra speed 
has several effects.

When making a full attack action, a hasted creature may make one extra attack with 
any weapon he is holding. The attack is made using the creature's full base attack 
bonus, plus any modifiers appropriate to the situation. (This effect is not cumulative 
with similar effects, such as that provided by a weapon of speed, nor does it actually 
grant an extra action, so you can't use it to cast a second spell or otherwise 
take an extra action in the round.)

A \textit{hasted} creature gains a +1 bonus on attack rolls and a +1 dodge bonus 
to AC and Reflex saves. Any condition that makes you lose your Dexterity bonus 
to Armor Class (if any) also makes you lose dodge bonuses.

All of the \textit{hasted} creature's modes of movement (including land movement, 
burrow, climb, fly, and swim) increase by 30 feet, to a maximum of twice the subject's 
normal speed using that form of movement. This increase counts as an enhancement 
bonus, and it affects the creature's jumping distance as normal for increased speed.

Multiple \textit{haste} effects don't stack. \textit{Haste} dispels and counters 
\textit{slow}.

\textit{Material Component:} A shaving of licorice root.

