\spellentry{Illusory Script}

Illusion (Phantasm) [Mind-Affecting]

\textbf{Level:} Brd 3, Sor/Wiz 3

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 minute or longer; see text

\textbf{Range:} Touch

\textbf{Target:} One touched object weighing no more than 10 lb.

\textbf{Duration:} One day/level (D)

\textbf{Saving Throw:} Will negates; see text

\textbf{Spell Resistance:} Yes

You write instructions or other information on parchment, paper, or any suitable 
writing material. The \textit{illusory script} appears to be some form of foreign 
or magical writing. Only the person (or people) designated by you at the time of 
the casting are able to read the writing; it's unintelligible to any other character, 
although an illusionist recognizes it as \textit{illusory script}.

Any unauthorized creature attempting to read the script triggers a potent illusory 
effect and must make a saving throw. A successful saving throw means the creature 
can look away with only a mild sense of disorientation. Failure means the creature 
is subject to a suggestion implanted in the script by you at the time the illusory 
script spell was cast. The suggestion lasts only 30 minutes. Typical suggestions 
include "Close the book and leave," "Forget the existence of the book," and 
so forth. If successfully dispelled by \textit{dispel magic}, the \textit{illusory 
script} and its secret message disappear. The hidden message can be read by a combination 
of the \textit{true seeing} spell with the \textit{read magic} or \textit{comprehend 
languages} spell.

The casting time depends on how long a message you wish to write, but it is always 
at least 1 minute.

\textit{Material Component:} A lead-based ink (cost of not less than 50 gp).

