\spellentry{Interposing Hand}

Evocation [Force]

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V, S, F

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} 10-ft. hand

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

\textit{Interposing hand} creates a Large magic hand that appears between you and 
one opponent. This floating, disembodied hand then moves to remain between the 
two of you, regardless of where you move or how the opponent tries to get around 
it, providing cover (+4 AC) for you against that opponent. Nothing can fool the 
hand -- it sticks with the selected opponent in spite of darkness, invisibility, 
polymorphing, or any other attempt at hiding or disguise. The hand does not pursue 
an opponent, however.

An \textit{interposing hand} is 10 feet long and about that wide with its fingers 
outstretched. It has as many hit points as you do when you're undamaged, and its 
AC is 20 (-1 size, +11 natural). It takes damage as a normal creature, but most 
magical effects that don't cause damage do not affect it.

The hand never provokes attacks of opportunity from opponents. It cannot push through 
a \textit{wall of force} or enter an \textit{antimagic field}, but it suffers the 
full effect of a \textit{prismatic wall} or \textit{prismatic sphere}. The hand 
makes saving throws as its caster.

\textit{Disintegrate} or a successful \textit{dispel magic} destroys it.

Any creature weighing 2,000 pounds or less that tries to push past the hand is 
slowed to half its normal speed. The hand cannot reduce the speed of a creature 
weighing more than 2,000 pounds, but it still affects the creature's attacks.

Directing the spell to a new target is a move action.

\textit{Focus:} A soft glove.

