\spellentry{Invisibility}

Illusion (Glamer)

\textbf{Level:} Brd 2, Sor/Wiz 2, Trickery 2

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal or touch

\textbf{Target:} You or a creature or object weighing no more than 100 lb./level

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Will negates (harmless) or Will negates (harmless, object)

\textbf{Spell Resistance:} Yes (harmless) or Yes (harmless, object)

The creature or object touched becomes invisible, vanishing from sight, even from 
darkvision. If the recipient is a creature carrying gear, that vanishes, too. If 
you cast the spell on someone else, neither you nor your allies can see the subject, 
unless you can normally see invisible things or you employ magic to do so.

Items dropped or put down by an invisible creature become visible; items picked 
up disappear if tucked into the clothing or pouches worn by the creature. Light, 
however, never becomes invisible, although a source of light can become so (thus, 
the effect is that of a light with no visible source). Any part of an item that 
the subject carries but that extends more than 10 feet from it becomes visible.

Of course, the subject is not magically \textit{silenced}, and certain other conditions 
can render the recipient detectable (such as stepping in a puddle). The spell ends 
if the subject attacks any creature. For purposes of this spell, an attack includes 
any spell targeting a foe or whose area or effect includes a foe. (Exactly who 
is a foe depends on the invisible character's perceptions.) Actions directed at 
unattended objects do not break the spell. Causing harm indirectly is not an attack. 
Thus, an invisible being can open doors, talk, eat, climb stairs, summon monsters 
and have them attack, cut the ropes holding a rope bridge while enemies are on 
the bridge, remotely trigger traps, open a portcullis to release attack dogs, and 
so forth. If the subject attacks directly, however, it immediately becomes visible 
along with all its gear. Spells such as \textit{bless} that specifically affect 
allies but not foes are not attacks for this purpose, even when they include foes 
in their area.

\textit{Invisibility} can be made permanent (on objects only) with a \textit{permanency 
}spell.

\textit{Arcane Material Component:} An eyelash encased in a bit of gum arabic.

