\spellentry{Iron Body}

Transmutation

\textbf{Level:} Earth 8, Sor/Wiz 8

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level (D)

This spell transforms your body into living iron, which grants you several powerful 
resistances and abilities.

You gain damage reduction 15/adamantine. You are immune to blindness, critical 
hits, ability score damage, deafness, disease, drowning, electricity, poison, stunning, 
and all spells or attacks that affect your physiology or respiration, because you 
have no physiology or respiration while this spell is in effect. You take only 
half damage from acid and fire of all kinds. However, you also become vulnerable 
to all special attacks that affect iron golems.

You gain a +6 enhancement bonus to your Strength score, but you take a -6 penalty 
to Dexterity as well (to a minimum Dexterity score of 1), and your speed is reduced 
to half normal. You have an arcane spell failure chance of 50\% and a -8 armor 
check penalty, just as if you were clad in full plate armor. You cannot drink (and 
thus can't use potions) or play wind instruments.

Your unarmed attacks deal damage equal to a club sized for you (1d4 for Small characters 
or 1d6 for Medium characters), and you are considered armed when making unarmed 
attacks.

Your weight increases by a factor of ten, causing you to sink in water like a stone. 
However, you could survive the crushing pressure and lack of air at the bottom 
of the ocean -- at least until the spell duration expires.

\textit{Arcane Material Component:} A small piece of iron that was once part of 
either an iron golem, a hero's armor, or a war machine.

