\spellentry{Limited Wish}

Universal

\textbf{Level:} Sor/Wiz 7

\textbf{Components:} V, S, XP

\textbf{Casting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Target, Effect, or Area:} See text

\textbf{Duration:} See text

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} Yes

A \textit{limited wish} lets you create nearly any type of effect. For example, 
a \textit{limited wish} can do any of the following things.%\item

Duplicate any sorcerer/wizard spell of 6th level or lower, provided the spell is 
not of a school prohibited to you.%\item

Duplicate any other spell of 5th level or lower, provided the spell is not of a 
school prohibited to you.%\item

Duplicate any sorcerer/wizard spell of 5th level or lower, even if it's of a prohibited 
school.%\item

Duplicate any other spell of 4th level or lower, even if it's of a prohibited school.%\item

Undo the harmful effects of many spells, such as \textit{geas/quest} or \textit{insanity}.%\item

Produce any other effect whose power level is in line with the above effects, such 
as a single creature automatically hitting on its next attack or taking a -7 penalty 
on its next saving throw.

A duplicated spell allows saving throws and spell resistance as normal (but the 
save DC is for a 7th-level spell). When a \textit{limited wish} duplicates a spell 
that has an XP cost, you must pay that cost or 300 XP, whichever is more. When 
a \textit{limited wish} spell duplicates a spell with a material component that 
costs more than 1,000 gp, you must provide that component.

\textit{XP Cost:} 300 XP or more (see above).

