\spellentry{Mage's Disjunction}

Abjuration

\textbf{Level:} Magic 9, Sor/Wiz 9

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} All magical effects and magic items within a 40-ft.-radius burst

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates (object)

\textbf{Spell Resistance:} No

All magical effects and magic items within the radius of the spell, except for 
those that you carry or touch, are disjoined. That is, spells and spell-like effects 
are separated into their individual components (ending the effect as a \textit{dispel 
magic} spell does), and each permanent magic item must make a successful Will save 
or be turned into a normal item. An item in a creature's possession uses its own 
Will save bonus or its possessor's Will save bonus, whichever is higher.

You also have a 1\% chance per caster level of destroying an \textit{antimagic 
field}. If the \textit{antimagic field} survives the \textit{disjunction}, no items 
within it are disjoined.

Even artifacts are subject to \textit{disjunction}, though there is only a 1\% 
chance per caster level of actually affecting such powerful items. Additionally, 
if an artifact is destroyed, you must make a DC 25 Will save or permanently lose 
all spellcasting abilities. (These abilities cannot be recovered by mortal magic, 
not even \textit{miracle} or \textit{wish}.)

\textit{Note:} Destroying artifacts is a dangerous business, and it is 95\% likely 
to attract the attention of some powerful being who has an interest in or connection 
with the device.

