\spellentry{Mage's Sword}

Evocation [Force]

\textbf{Level:} Sor/Wiz 7

\textbf{Components:} V, S, F

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} One sword

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

This spell brings into being a shimmering, swordlike plane of force. The sword 
strikes at any opponent within its range, as you desire, starting in the round 
that you cast the spell. The sword attacks its designated target once each round 
on your turn. Its attack bonus is equal to your caster level + your Int bonus or 
your Cha bonus (for wizards or sorcerers, respectively) with an additional +3 enhancement 
bonus. As a force effect, it can strike ethereal and incorporeal creatures. It 
deals 4d6+3 points of force damage, with a threat range of 19-20 and a critical 
multiplier of x2.

The sword always strikes from your direction. It does not get a bonus for flanking 
or help a combatant get one. If the sword goes beyond the spell range from you, 
if it goes out of your sight, or if you are not directing it, the sword returns 
to you and hovers.

Each round after the first, you can use a standard action to switch the sword to 
a new target. If you do not, the sword continues to attack the previous round's 
target.

The sword cannot be attacked or harmed by physical attacks, but \textit{dispel 
magic}, \textit{disintegrate}, a \textit{sphere of annihilation}, or a \textit{rod 
of cancellation} affects it. The sword's AC is 13 (10, +0 size bonus for Medium 
object, +3 deflection bonus).

If an attacked creature has spell resistance, the resistance is checked the first 
time \textit{Mage's sword} strikes it. If the sword is successfully resisted, the 
spell is dispelled. If not, the sword has its normal full effect on that creature 
for the duration of the spell.

\textit{Focus:} A miniature platinum sword with a grip and pommel of copper and 
zinc. It costs 250 gp to construct.

