\spellentry{Mage's Magnificent Mansion}

Conjuration (Creation)

\textbf{Level:} Sor/Wiz 7

\textbf{Components:} V, S, F

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} Extradimensional mansion, up to three 10-ft. cubes/level (S)

\textbf{Duration:} 2 hours/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You conjure up an extradimensional dwelling that has a single entrance on the plane 
from which the spell was cast. The entry point looks like a faint shimmering in 
the air that is 4 feet wide and 8 feet high. Only those you designate may enter 
the mansion, and the portal is shut and made invisible behind you when you enter. 
You may open it again from your own side at will. Once observers have passed beyond 
the entrance, they are in a magnificent foyer with numerous chambers beyond. The 
atmosphere is clean, fresh, and warm.

You can create any floor plan you desire to the limit of the spell's effect. The 
place is furnished and contains sufficient foodstuffs to serve a nine-course banquet 
to a dozen people per caster level. A staff of near-transparent servants (as many 
as two per caster level), liveried and obedient, wait upon all who enter. The servants 
function as \textit{unseen servant} spells except that they are visible and can 
go anywhere in the mansion.

Since the place can be entered only through its special portal, outside conditions 
do not affect the mansion, nor do conditions inside it pass to the plane beyond.

\textit{Focus:} A miniature portal carved from ivory, a small piece of polished 
marble, and a tiny silver spoon (each item worth 5 gp).

