\spellentry{Magic Mouth}

Illusion (Glamer)

\textbf{Level:} Brd 1, Sor/Wiz 2

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature or object

\textbf{Duration:} Permanent until discharged

\textbf{Saving Throw:} Will negates (object)

\textbf{Spell Resistance:} Yes (object)

This spell imbues the chosen object or creature with an enchanted mouth that suddenly 
appears and speaks its message the next time a specified event occurs. The message, 
which must be twenty-five or fewer words long, can be in any language known by 
you and can be delivered over a period of 10 minutes. The mouth cannot utter verbal 
components, use command words, or activate magical effects. It does, however, move 
according to the words articulated; if it were placed upon a statue, the mouth 
of the statue would move and appear to speak. Of course, \textit{magic mouth} can 
be placed upon a tree, rock, or any other object or creature.

The spell functions when specific conditions are fulfilled according to your command 
as set in the spell. Commands can be as general or as detailed as desired, although 
only visual and audible triggers can be used. Triggers react to what appears to 
be the case. Disguises and illusions can fool them. Normal darkness does not defeat 
a visual trigger, but magical \textit{darkness} or \textit{invisibility} does. 
Silent movement or magical \textit{silence} defeats audible triggers. Audible triggers 
can be keyed to general types of noises or to a specific noise or spoken word. 
Actions can serve as triggers if they are visible or audible. A \textit{magic mouth 
}cannot distinguish alignment, level, Hit Dice, or class except by external garb.

The range limit of a trigger is 15 feet per caster level, so a 6th-level caster 
can command a \textit{magic mouth} to respond to triggers as far as 90 feet away. 
Regardless of range, the mouth can respond only to visible or audible triggers 
and actions in line of sight or within hearing distance.

\textit{Magic mouth} can be made permanent with a \textit{permanency} spell.

\textit{Material Component:} A small bit of honeycomb and jade dust worth 10 gp.

