\spellentry{Meld into Stone}

Transmutation [Earth]

\textbf{Level:} Clr 3, Drd 3

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level

\textit{Meld into stone} enables you to meld your body and possessions into a single 
block of stone. The stone must be large enough to accommodate your body in all 
three dimensions. When the casting is complete, you and not more than 100 pounds 
of nonliving gear merge with the stone. If either condition is violated, the spell 
fails and is wasted.

While in the stone, you remain in contact, however tenuous, with the face of the 
stone through which you melded. You remain aware of the passage of time and can 
cast spells on yourself while hiding in the stone. Nothing that goes on outside 
the stone can be seen, but you can still hear what happens around you. Minor physical 
damage to the stone does not harm you, but its partial destruction (to the extent 
that you no longer fit within it) expels you and deals you 5d6 points of damage. 
The stone's complete destruction expels you and slays you instantly unless you 
make a DC 18 Fortitude save.

Any time before the duration expires, you can step out of the stone through the 
surface that you entered. If the spell's duration expires or the effect is dispelled 
before you voluntarily exit the stone, you are violently expelled and take 5d6 
points of damage.

The following spells harm you if cast upon the stone that you are occupying: \textit{Stone 
to flesh} expels you and deals you 5d6 points of damage. \textit{Stone shape} deals 
you 3d6 points of damage but does not expel you. \textit{Transmute rock to mud 
}expels you and then slays you instantly unless you make a DC 18 Fortitude save, 
in which case you are merely expelled. Finally, \textit{passwall} expels you without 
damage.

