\spellentry{Miracle}

Evocation

\textbf{Level:} Clr 9, Luck 9

\textbf{Components:} V, S, XP; see text

\textbf{Casting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Target, Effect, or Area:} See text

\textbf{Duration:} See text

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} Yes

You don't so much cast a \textit{miracle} as request one. You state what you would 
like to have happen and request that your deity (or the power you pray to for spells) 
intercede.

A \textit{miracle} can do any of the following things.%\item

Duplicate any cleric spell of 8th level or lower (including spells to which you 
have access because of your domains). %\item

Duplicate any other spell of 7th level or lower.%\item

Undo the harmful effects of certain spells, such as \textit{feeblemind} or \textit{insanity}.%\item

Have any effect whose power level is in line with the above effects.

If the \textit{miracle} has any of the above effects, casting it has no experience 
point cost.

Alternatively, a cleric can make a very powerful request. Casting such a \textit{miracle 
}costs the cleric 5,000 XP because of the powerful divine energies involved. Examples 
of especially powerful \textit{miracles} of this sort could include the following.%\item

Swinging the tide of a battle in your favor by raising fallen allies to continue 
fighting.%\item

Moving you and your allies, with all your and their gear, from one plane to another 
through planar barriers to a specific locale with no chance of error.%\item

Protecting a city from an earthquake, volcanic eruption, flood, or other major 
natural disaster.

In any event, a request that is out of line with the deity's (or alignment's) nature 
is refused.

A duplicated spell allows saving throws and spell resistance as normal, but the 
save DCs are as for a 9th-level spell. When a \textit{miracle} duplicates a spell 
that has an XP cost, you must pay that cost. When a \textit{miracle} spell duplicates 
a spell with a material component that costs more than 100 gp, you must provide 
that component.

\textit{XP Cost:} 5,000 XP (for some uses of the \textit{miracle} spell; see above).

