\spellentry{Mirror Image}

Illusion (Figment)

\textbf{Level:} Brd 2, Sor/Wiz 2

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal; see text

\textbf{Target:} You

\textbf{Duration:} 1 min./level (D)

Several illusory duplicates of you pop into being, making it difficult for enemies 
to know which target to attack. The figments stay near you and disappear when struck.

\textit{Mirror image} creates 1d4 images plus one image per three caster levels 
(maximum eight images total). These figments separate from you and remain in a 
cluster, each within 5 feet of at least one other figment or you. You can move 
into and through a \textit{mirror image}. When you and the \textit{mirror image 
}separate, observers can't use vision or hearing to tell which one is you and which 
the image. The figments may also move through each other. The figments mimic your 
actions, pretending to cast spells when you cast a spell, drink potions when you 
drink a potion, levitate when you levitate, and so on.

Enemies attempting to attack you or cast spells at you must select from among indistinguishable 
targets. Generally, roll randomly to see whether the selected target is real or 
a figment. Any successful attack against an image destroys it. An image's AC is 
10 + your size modifier + your Dex modifier. Figments seem to react normally to 
area spells (such as looking like they're burned or dead after being hit by a \textit{fireball}).

While moving, you can merge with and split off from figments so that enemies who 
have learned which image is real are again confounded.

An attacker must be able to see the images to be fooled. If you are invisible or 
an attacker shuts his or her eyes, the spell has no effect. (Being unable to see 
carries the same penalties as being blinded.)

