\spellentry{Modify Memory}

Enchantment (Compulsion) [Mind-Affecting]

\textbf{Level:} Brd 4

\textbf{Components:} V, S

\textbf{Casting Time:} 1 round; see text

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One living creature

\textbf{Duration:} Permanent

\textbf{Saving Throw:} Will negates

\textbf{Spell Resistance:} Yes

You reach into the subject's mind and modify as many as 5 minutes of its memories 
in one of the following ways.%\item

Eliminate all memory of an event the subject actually experienced. This spell cannot 
negate \textit{charm, geas/quest, suggestion}, or similar spells.%\item

Allow the subject to recall with perfect clarity an event it actually experienced.%\item

Change the details of an event the subject actually experienced.%\item

Implant a memory of an event the subject never experienced.

Casting the spell takes 1 round. If the subject fails to save, you proceed with 
the spell by spending as much as 5 minutes (a period of time equal to the amount 
of memory time you want to modify) visualizing the memory you wish to modify in 
the subject. If your concentration is disturbed before the visualization is complete, 
or if the subject is ever beyond the spell's range during this time, the spell 
is lost.

A modified memory does not necessarily affect the subject's actions, particularly 
if it contradicts the creature's natural inclinations. An illogical modified memory 
is dismissed by the creature as a bad dream or a memory muddied by too much wine. 

