\spellentry{Nightmare}

Illusion (Phantasm) [Mind-Affecting, Evil]

\textbf{Level:} Brd 5, Sor/Wiz 5

\textbf{Components:} V, S

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Unlimited

\textbf{Target:} One living creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates; see text

\textbf{Spell Resistance:} Yes

You send a hideous and unsettling phantasmal vision to a specific creature that 
you name or otherwise specifically designate.

The \textit{nightmare} prevents restful sleep and causes 1d10 points of damage. 
The \textit{nightmare} leaves the subject fatigued and unable to regain arcane 
spells for the next 24 hours.

The difficulty of the save depends on how well you know the subject and what sort 
of physical connection (if any) you have to that creature.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{3.076in}|}{\begin{minipage}[t]{3.076in}\raggedright
\textbf{Knowledge}\end{minipage}} & \multicolumn{1}{p{1.295in}|}{\begin{minipage}[t]{1.295in}\raggedright
\textbf{Will Save Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
None\textsuperscript{\textbf{1}}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
+10\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{3.076in}|}{\begin{minipage}[t]{3.076in}\raggedleft
Secondhand (you have heard of the subject)\end{minipage}} & \multicolumn{1}{p{1.295in}|}{\begin{minipage}[t]{1.295in}\raggedleft
+5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
Firsthand (you have met the subject)\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{3.076in}|}{\begin{minipage}[t]{3.076in}\raggedleft
Familiar (you know the subject well)\end{minipage}} & \multicolumn{3}{p{1.424in}|}{\begin{minipage}[t]{1.424in}\raggedleft
-5\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
1 You must have some sort of connection to a creature you have no knowledge of.\end{minipage}}\\
\hline
\end{longtable}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{2.287in}|}{\begin{minipage}[t]{2.287in}\raggedright
\textbf{Connection}\end{minipage}} & \multicolumn{1}{p{1.276in}|}{\begin{minipage}[t]{1.276in}\raggedright
\textbf{Will Save Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Likeness or picture\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
-2\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{2.287in}|}{\begin{minipage}[t]{2.287in}\raggedleft
Possession or garment\end{minipage}} & \multicolumn{1}{p{1.276in}|}{\begin{minipage}[t]{1.276in}\raggedleft
-4\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Body part, lock of hair, bit of nail, etc.\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
-10\end{minipage}}\\
\hline
\end{longtable}

\textit{Dispel evil} cast on the subject while you are casting the spell dispels 
the \textit{nightmare} and causes you to be stunned for 10 minutes per caster level 
of the \textit{dispel evil}.

If the recipient is awake when the spell begins, you can choose to cease casting 
(ending the spell) or to enter a trance until the recipient goes to sleep, whereupon 
you become alert again and complete the casting. If you are disturbed during the 
trance, you must succeed on a Concentration check as if you were in the midst of 
casting a spell or the spell ends.

If you choose to enter a trance, you are not aware of your surroundings or the 
activities around you while in the trance.

You are defenseless, both physically and mentally, while in the trance. (You always 
fail any saving throw, for example.)

Creatures who don't sleep (such as elves, but not half-elves) or dream are immune 
to this spell.

