\spellentry{Phantom Steed}

Conjuration (Creation)

\textbf{Level:} Brd 3, Sor/Wiz 3

\textbf{Components:} V, S

\textbf{Casting Time:} 10 minutes

\textbf{Range:} 0 ft.

\textbf{Effect:} One quasi-real, horselike creature

\textbf{Duration:} 1 hour/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You conjure a Large, quasi-real, horselike creature. The steed can be ridden only 
by you or by the one person for whom you specifically created the mount. A phantom 
steed has a black head and body, gray mane and tail, and smoke-colored, insubstantial 
hooves that make no sound. It has what seems to be a saddle, bit, and bridle. It 
does not fight, but animals shun it and refuse to attack it.

The mount has an AC of 18 (-1 size, +4 natural armor, +5 Dex) and 7 hit points 
+1 hit point per caster level. If it loses all its hit points, the phantom steed 
disappears. A phantom steed has a speed of 20 feet per caster level, to a maximum 
of 240 feet. It can bear its rider's weight plus up to 10 pounds per caster level.

These mounts gain certain powers according to caster level. A mount's abilities 
include those of mounts of lower caster levels. 

\textit{8th Level:} The mount can ride over sandy, muddy, or even swampy ground 
without difficulty or decrease in speed.

\textit{10th Level:} The mount can use \textit{water walk} at will (as the spell, 
no action required to activate this ability).

\textit{12th Level:} The mount can use \textit{air walk} at will (as the spell, 
no action required to activate this ability) for up to 1 round at a time, after 
which it falls to the ground.

\textit{14th Level:} The mount can fly at its speed (average maneuverability).

