\spellentry{Planar Binding, Lesser}\label{spell:Lesser Planar Binding}

Conjuration (Calling) [see text]

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V, S

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Close (25 ft. + 5 ft./2 levels); see text

\textbf{Target:} One elemental or outsider with 6 HD or less

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates

\textbf{Spell Resistance:} No and Yes; see text

Casting this spell attempts a dangerous act: to lure a creature from another plane 
to a specifically prepared trap, which must lie within the spell's range. The called 
creature is held in the trap until it agrees to perform one service in return for 
its freedom.

To create the trap, you must use a \textit{magic circle} spell, focused inward. 
The kind of creature to be bound must be known and stated. If you wish to call 
a specific individual, you must use that individual's proper name in casting the 
spell.

The target creature is allowed a Will saving throw. If the saving throw succeeds, 
the creature resists the spell. If the saving throw fails, the creature is immediately 
drawn to the trap (spell resistance does not keep it from being called). The creature 
can escape from the trap with by successfully pitting its spell resistance against 
your caster level check, by dimensional travel, or with a successful Charisma check 
(DC 15 + 1/2 your caster level + your Cha modifier). It can try each method once 
per day. If it breaks loose, it can flee or attack you. A \textit{dimensional anchor 
}cast on the creature prevents its escape via dimensional travel. You can also 
employ a calling diagram (see \textit{magic circle against evil}) to make the trap 
more secure.

If the creature does not break free of the trap, you can keep it bound for as long 
as you dare. You can attempt to compel the creature to perform a service by describing 
the service and perhaps offering some sort of reward. You make a Charisma check 
opposed by the creature's Charisma check. The check is assigned a bonus of +0 to 
+6 based on the nature of the service and the reward. If the creature wins the 
opposed check, it refuses service. New offers, bribes, and the like can be made 
or the old ones reoffered every 24 hours. This process can be repeated until the 
creature promises to serve, until it breaks free, or until you decide to get rid 
of it by means of some other spell. Impossible demands or unreasonable commands 
are never agreed to. If you roll a 1 on the Charisma check, the creature breaks 
free of the binding and can escape or attack you.

Once the requested service is completed, the creature need only so inform you to 
be instantly sent back whence it came. The creature might later seek revenge. If 
you assign some open-ended task that the creature cannot complete though its own 
actions the spell remains in effect for a maximum of one day per caster level, 
and the creature gains an immediate chance to break free. Note that a clever recipient 
can subvert some instructions.

When you use a calling spell to call an air, chaotic, earth, evil, fire, good, 
lawful, or water creature, it is a spell of that type. 

