\spellentry{Polymorph Any Object}

Transmutation

\textbf{Level:} Sor/Wiz 8, Trickery 8

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature, or one nonmagical object of up to 100 cu. ft./level

\textbf{Duration:} See text

\textbf{Saving Throw:} Fortitude negates (object); see text

\textbf{Spell Resistance:} Yes (object)

This spell functions like \textit{polymorph}, except that it changes one object 
or creature into another. The duration of the spell depends on how radical a change 
is made from the original state to its enchanted state. The duration is determined 
by using the following guidelines.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{2.870in}|}{\begin{minipage}[t]{2.870in}\raggedright
\textbf{Changed Subject Is:}\end{minipage}} & \multicolumn{1}{p{1.205in}|}{\begin{minipage}[t]{1.205in}\raggedleft
\textbf{Increase to Duration Factor}\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Same kingdom (animal, vegetable, mineral)\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
+5\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{2.870in}|}{\begin{minipage}[t]{2.870in}\raggedleft
Same class (mammals, fungi, metals, etc.)\end{minipage}} & \multicolumn{1}{p{1.205in}|}{\begin{minipage}[t]{1.205in}\raggedleft
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Same size\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
+2\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{2.870in}|}{\begin{minipage}[t]{2.870in}\raggedleft
Related (twig is to tree, wolf fur is to wolf, etc.)\end{minipage}} & \multicolumn{3}{p{1.344in}|}{\begin{minipage}[t]{1.344in}\raggedleft
+2\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Same or lower Intelligence\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
+2\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{2.870in}|}{\begin{minipage}[t]{2.870in}\raggedleft
1 Add all that apply. Look up the total on the next table.\end{minipage}}\\
\hline
\end{longtable}

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.700in}|}{\begin{minipage}[t]{0.700in}\centering
\textbf{Duration Factor}\end{minipage}} & \multicolumn{1}{p{0.826in}|}{\begin{minipage}[t]{0.826in}\centering
\textbf{Duration}\end{minipage}} & \multicolumn{1}{p{1.393in}|}{\begin{minipage}[t]{1.393in}\centering
\textbf{Example}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
0\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
20 minutes\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Pebble to human\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.700in}|}{\begin{minipage}[t]{0.700in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.826in}|}{\begin{minipage}[t]{0.826in}\centering
1 hour\end{minipage}} & \multicolumn{1}{p{1.393in}|}{\begin{minipage}[t]{1.393in}\centering
Marionette to human\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
3 hours\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Human to marionette\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.700in}|}{\begin{minipage}[t]{0.700in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.826in}|}{\begin{minipage}[t]{0.826in}\centering
12 hours\end{minipage}} & \multicolumn{4}{p{1.601in}|}{\begin{minipage}[t]{1.601in}\centering
Lizard to manticore\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
2 days\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Sheep to wool coat\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.700in}|}{\begin{minipage}[t]{0.700in}\centering
7\end{minipage}} & \multicolumn{1}{p{0.826in}|}{\begin{minipage}[t]{0.826in}\centering
1 week\end{minipage}} & \multicolumn{4}{p{1.601in}|}{\begin{minipage}[t]{1.601in}\centering
Shrew to manticore\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.700in}|}{\begin{minipage}[t]{0.700in}\centering
9+\end{minipage}} & \multicolumn{1}{p{0.826in}|}{\begin{minipage}[t]{0.826in}\centering
Permanent\end{minipage}} & \multicolumn{4}{p{1.601in}|}{\begin{minipage}[t]{1.601in}\centering
Manticore to shrew\end{minipage}}\\
\hline
\end{longtable}

Unlike \textit{polymorph, polymorph any object} does grant the creature the Intelligence 
score of its new form. If the original form didn't have a Wisdom or Charisma score, 
it gains those scores as appropriate for the new form.

Damage taken by the new form can result in the injury or death of the polymorphed 
creature. In general, damage occurs when the new form is changed through physical 
force.

A nonmagical object cannot be made into a magic item with this spell. Magic items 
aren't affected by this spell.

This spell cannot create material of great intrinsic value, such as copper, silver, 
gems, silk, gold, platinum, mithral, or adamantine. It also cannot reproduce the 
special properties of cold iron in order to overcome the damage reduction of certain 
creatures.

This spell can also be used to duplicate the effects of \textit{baleful polymorph, 
polymorph, flesh to stone}, \textit{stone to flesh}, \textit{transmute mud to rock}, 
\textit{transmute metal to wood}, or \textit{transmute rock to mud}.

\textit{Arcane Material Component:} Mercury, gum arabic, and smoke.

