\spellentry{Protection From Evil}

Abjuration [Good]

\textbf{Level:} Clr 1, Good 1, Pal 1, Sor/Wiz 1

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} Creature touched

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Will negates (harmless)

\textbf{Spell Resistance:} No; see text

This spell wards a creature from attacks by evil creatures, from mental control, 
and from summoned creatures. It creates a magical barrier around the subject at 
a distance of 1 foot. The barrier moves with the subject and has three major effects.

First, the subject gains a +2 deflection bonus to AC and a +2 resistance bonus 
on saves. Both these bonuses apply against attacks made or effects created by evil 
creatures.

Second, the barrier blocks any attempt to possess the warded creature (by a \textit{magic 
jar} attack, for example) or to exercise mental control over the creature (including 
enchantment (charm) effects and enchantment (compulsion) effects that grant the 
caster ongoing control over the subject, such as \textit{dominate person}). The 
protection does not prevent such effects from targeting the protected creature, 
but it suppresses the effect for the duration of the \textit{protection from evil 
}effect. If the \textit{protection from evil} effect ends before the effect granting 
mental control does, the would-be controller would then be able to mentally command 
the controlled creature. Likewise, the barrier keeps out a possessing life force 
but does not expel one if it is in place before the spell is cast. This second 
effect works regardless of alignment.

Third, the spell prevents bodily contact by summoned creatures. This causes the 
natural weapon attacks of such creatures to fail and the creatures to recoil if 
such attacks require touching the warded creature. Good summoned creatures are 
immune to this effect. The protection against contact by summoned creatures ends 
if the warded creature makes an attack against or tries to force the barrier against 
the blocked creature. Spell resistance can allow a creature to overcome this protection 
and touch the warded creature.

\textit{Arcane Material Component:} A little powdered silver with which you trace 
a 3-foot -diameter circle on the floor (or ground) around the creature to be warded.

