\spellentry{Pyrotechnics}

Transmutation

\textbf{Level:} Brd 2, Sor/Wiz 2

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Target:} One fire source, up to a 20-ft. cube

\textbf{Duration:} 1d4+1 rounds, or 1d4+1 rounds after creatures leave the smoke 
cloud; see text

\textbf{Saving Throw:} Will negates or Fortitude negates; see text

\textbf{Spell Resistance:} Yes or No; see text

\textit{Pyrotechnics} turns a fire into either a burst of blinding fireworks or 
a thick cloud of choking smoke, depending on the version you choose.

\textit{Fireworks:} The fireworks are a flashing, fiery, momentary burst of glowing, 
colored aerial lights. This effect causes creatures within 120 feet of the fire 
source to become blinded for 1d4+1 rounds (Will negates). These creatures must 
have line of sight to the fire to be affected. Spell resistance can prevent blindness.

\textit{Smoke Cloud:} A writhing stream of smoke billows out from the source, forming 
a choking cloud. The cloud spreads 20 feet in all directions and lasts for 1 round 
per caster level. All sight, even darkvision, is ineffective in or through the 
cloud. All within the cloud take -4 penalties to Strength and Dexterity (Fortitude 
negates). These effects last for 1d4+1 rounds after the cloud dissipates or after 
the creature leaves the area of the cloud. Spell resistance does not apply.

\textit{Material Component:} The spell uses one fire source, which is immediately 
extinguished. A fire so large that it exceeds a 20-foot cube is only partly extinguished. 
Magical fires are not extinguished, although a fire-based creature used as a source 
takes 1 point of damage per caster level.

