\spellentry{Raise Dead}

Conjuration (Healing)

\textbf{Level:} Clr 5

\textbf{Components:} V, S, M, DF

\textbf{Casting Time:} 1 minute

\textbf{Range:} Touch

\textbf{Target:} Dead creature touched

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} Yes (harmless)

You restore life to a deceased creature. You can raise a creature that has been 
dead for no longer than one day per caster level. In addition, the subject's soul 
must be free and willing to return. If the subject's soul is not willing to return, 
the spell does not work; therefore, a subject that wants to return receives no 
saving throw.

Coming back from the dead is an ordeal. The subject of the spell loses one level 
(or 1 Hit Die) when it is raised, just as if it had lost a level or a Hit Die to 
an energy-draining creature. If the subject is 1st level, it loses 2 points of 
Constitution instead (if this would reduce its Con to 0 or less, it can't be raised). 
This level/HD loss or Constitution loss cannot be repaired by any means. A character 
who died with spells prepared has a 50\% chance of losing any given spell upon 
being raised, in addition to losing spells for losing a level. A spellcasting creature 
that doesn't prepare spells (such as a sorcerer) has a 50\% chance of losing any 
given unused spell slot as if it had been used to cast a spell, in addition to 
losing spell slots for losing a level.

A raised creature has a number of hit points equal to its current Hit Dice. Any 
ability scores damaged to 0 are raised to 1. Normal poison and normal disease are 
cured in the process of raising the subject, but magical diseases and curses are 
not undone. While the spell closes mortal wounds and repairs lethal damage of most 
kinds, the body of the creature to be raised must be whole. Otherwise, missing 
parts are still missing when the creature is brought back to life. None of the 
dead creature's equipment or possessions are affected in any way by this spell.

A creature who has been turned into an undead creature or killed by a death effect 
can't be raised by this spell. Constructs, elementals, outsiders, and undead creatures 
can't be raised. The spell cannot bring back a creature that has died of old age.

\textit{Material Component:} Diamonds worth a total of least 5,000 gp.

