\spellentry{Refuge}

Conjuration (Teleportation)

\textbf{Level:} Clr 7, Sor/Wiz 9

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} Object touched

\textbf{Duration:} Permanent until discharged

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You create powerful magic in some specially prepared object. This object contains 
the power to instantly transport its possessor across any distance within the same 
plane to your abode. Once the item is transmuted, you must give it willingly to 
a creature and at the same time inform it of a command word to be spoken when the 
item is used. To make use of the item, the subject speaks the command word at the 
same time that it rends or breaks the item (a standard action). When this is done, 
the individual and all objects it is wearing and carrying (to a maximum of the 
character's heavy load) are instantly transported to your abode. No other creatures 
are affected (aside from a familiar that is touching the subject).

You can alter the spell when casting it so that it transports you to within 10 
feet of the possessor of the item when it is broken and the command word spoken. 
You will have a general idea of the location and situation of the item possessor 
at the time the \textit{refuge} spell is discharged, but once you decide to alter 
the spell in this fashion, you have no choice whether or not to be transported.

\textit{Material Component:} The specially prepared object, whose construction 
requires gems worth 1,500 gp.

