\spellentry{Reincarnate}

Transmutation

\textbf{Level:} Drd 4

\textbf{Components:} V, S, M, DF

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Touch

\textbf{Target:} Dead creature touched

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} Yes (harmless)

With this spell, you bring back a dead creature in another body, provided that 
its death occurred no more than one week before the casting of the spell and the 
subject's soul is free and willing to return. If the subject's soul is not willing 
to return, the spell does not work; therefore, a subject that wants to return receives 
no saving throw.

Since the dead creature is returning in a new body, all physical ills and afflictions 
are repaired. The condition of the remains is not a factor. So long as some small 
portion of the creature's body still exists, it can be reincarnated, but the portion 
receiving the spell must have been part of the creature's body at the time of death. 
The magic of the spell creates an entirely new young adult body for the soul to 
inhabit from the natural elements at hand. This process takes 1 hour to complete. 
 When the body is ready, the subject is reincarnated.

A reincarnated creature recalls the majority of its former life and form. It retains 
any class abilities, feats, or skill ranks it formerly possessed. Its class, base 
attack bonus, base save bonuses, and hit points are unchanged. Strength, Dexterity, 
and Constitution scores depend partly on the new body. First eliminate the subject's 
racial adjustments (since it is no longer of his previous race) and then apply 
the adjustments found below to its remaining ability scores. The subject's level 
(or Hit Dice) is reduced by 1. If the subject was 1st level, its new Constitution 
score is reduced by 2. (If this reduction would put its Con at 0 or lower, it can't 
be reincarnated). This level/HD loss or Constitution loss cannot be repaired by 
any means.

It's possible for the change in the subject's ability scores to make it difficult 
for it to pursue its previous character class. If this is the case, the subject 
is well advised to become a multiclass character.

For a humanoid creature, the new incarnation is determined using the following 
table. For nonhumanoid creatures, a similar table of creatures of the same type 
should be created.

A creature that has been turned into an undead creature or killed by a death effect 
can't be returned to life by this spell.  Constructs, elementals, outsiders, and 
undead creatures can't be reincarnated. The spell cannot bring back a creature 
who has died of old age.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Reincarnation Results}
\centering
\begin{tabular}{c l c c c}
\textbf{d\%} & \textbf{Incarnation} & \textbf{Str} & \textbf{Dex} & \textbf{Con}\\
01 & Bugbear & +4 & +2 & +2\\
02-13 & Dwarf & +0 & +0 & +2\\
14-25 & Elf & +0 & +2 & -2\\
26 & Gnoll & +4 & +0 & +2\\
27-38 & Gnome & -2 & +0 & +2\\
39-42 & Goblin & -2 & +2 & +0\\
43-52 & Half-elf & +0 & +0 & +0\\
53-62 & Half-orc & +2 & +0 & +0\\
63-74 & Halfling & -2 & +2 & +0\\
75-89 & Human & +0 & +0 & +0\\
90-93 & Kobold & -4 & +2 & -2\\
94 & Lizardfolk & +2 & +0 & +2\\
95-98 & Orc & +4 & +0 & +0\\
99 & Troglodyte & +0 & -2 & +4\\
100 & Other & ? & ? & ?\\
\end{tabular}
\end{table}

The reincarnated creature gains all abilities associated with its new form, including 
forms of movement and speeds, natural armor, natural attacks, extraordinary abilities, 
and the like, but it doesn't automatically speak the language of the new form. 

A \textit{wish} or a \textit{miracle} spell can restore a reincarnated character 
to his or her original form.

\textit{Material Component:} Rare oils and unguents worth a total of least 1,000 
gp, spread over the remains.

