\spellentry{Rope Trick}

Transmutation

\textbf{Level:} Sor/Wiz 2

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} One touched piece of rope from 5 ft. to 30 ft. long

\textbf{Duration:} 1 hour/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

When this spell is cast upon a piece of rope from 5 to 30 feet long, one end of 
the rope rises into the air until the whole rope hangs perpendicular to the ground, 
as if affixed at the upper end. The upper end is, in fact, fastened to an extradimensional 
space that is outside the multiverse of extradimensional spaces ("planes"). Creatures 
in the extradimensional space are hidden, beyond the reach of spells (including 
divinations), unless those spells work across planes. The space holds as many as 
eight creatures (of any size). Creatures in the space can pull the rope up into 
the space, making the rope "disappear." In that case, the rope counts as one 
of the eight creatures that can fit in the space. The rope can support up to 16,000 
pounds. A weight greater than that can pull the rope free.

Spells cannot be cast across the extradimensional interface, nor can area effects 
cross it. Those in the extradimensional space can see out of it as if a 3-foot-by- 
5-foot window were centered on the rope. The window is present on the Material 
Plane, but it's invisible, and even creatures that can see the window can't see 
through it. Anything inside the extradimensional space drops out when the spell 
ends. The rope can be climbed by only one person at a time. The \textit{rope trick 
}spell enables climbers to reach a normal place if they do not climb all the way 
to the extradimensional space.

\textit{Note:} It is hazardous to create an extradimensional space within an existing 
extradimensional space or to take an extradimensional space into an existing one.

\textit{Material Component:} Powdered corn extract and a twisted loop of parchment.

