\spellentry{Rusting Grasp}

Transmutation

\textbf{Level:} Drd 4

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} One nonmagical ferrous object (or the volume of the object within 
3 ft. of the touched point) or one ferrous creature

\textbf{Duration:} See text

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

Any iron or iron alloy item you touch becomes instantaneously rusted, pitted, and 
worthless, effectively destroyed. If the item is so large that it cannot fit within 
a 3-foot radius a 3-foot-radius volume of the metal is rusted and destroyed. Magic 
items made of metal are immune to this spell.

You may employ \textit{rusting grasp} in combat with a successful melee touch attack. 
\textit{Rusting grasp} used in this way instantaneously destroys 1d6 points of 
Armor Class gained from metal armor (to the maximum amount of protection the armor 
offered) through corrosion. 

Weapons in use by an opponent targeted by the spell are more difficult to grasp. 
You must succeed on a melee touch attack against the weapon. A metal weapon that 
is hit is destroyed.

\textit{Note:} Striking at an opponent's weapon provokes an attack of opportunity. 
Also, you must touch the weapon and not the other way around.

Against a ferrous creature, \textit{rusting grasp} instantaneously deals 3d6 points 
of damage +1 per caster level (maximum +15) per successful attack. The spell lasts 
for 1 round per level, and you can make one melee touch attack per round.




