\spellentry{Secret Chest}

Conjuration (Summoning)

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V, S, F

\textbf{Casting Time:} 10 minutes

\textbf{Range:} See text

\textbf{Target:} One chest and up to 1 cu. ft. of goods/caster level

\textbf{Duration:} Sixty days or until discharged

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You hide a chest on the Ethereal Plane for as long as sixty days and can retrieve 
it at will. The chest can contain up to 1 cubic foot of material per caster level 
(regardless of the chest's actual size, which is about 3 feet by 2 feet by 2 feet). 
If any living creatures are in the chest, there is a 75\% chance that the spell 
simply fails. Once the chest is hidden, you can retrieve it by concentrating (a 
standard action), and it appears next to you.

The chest must be exceptionally well crafted and expensive, constructed for you 
by master crafters. The cost of such a chest is never less than 5,000 gp. Once 
it is constructed, you must make a tiny replica (of the same materials and perfect 
in every detail), so that the miniature of the chest appears to be a perfect copy. 
(The replica costs 50 gp.) You can have but one pair of these chests at any given 
time -- even a \textit{wish} spell does not allow more. The chests are nonmagical 
and can be fitted with locks, wards, and so on, just as any normal chest can be.

To hide the chest, you cast the spell while touching both the chest and the replica. 
The chest vanishes into the Ethereal Plane. You need the replica to recall the 
chest. After sixty days, there is a cumulative chance of 5\% per day that the chest 
is irretrievably lost. If the miniature of the chest is lost or destroyed, there 
is no way, not even with a \textit{wish} spell, that the large chest can be summoned 
back, although an extraplanar expedition might be mounted to find it.

Living things in the chest eat, sleep, and age normally, and they die if they run 
out of food, air, water, or whatever they need to survive.

\textit{Focus:} The chest and its replica.

