\spellentry{Secure Shelter}

Conjuration (Creation)

\textbf{Level:} Brd 4, Sor/Wiz 4

\textbf{Components:} V, S, M, F; see text

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} 20-ft.-square structure

\textbf{Duration:} 2 hours/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You conjure a sturdy cottage or lodge made of material that is common in the area 
where the spell is cast. The floor is level, clean, and dry. In all respects the 
lodging resembles a normal cottage, with a sturdy door, two shuttered windows, 
and a small fireplace.

The shelter has no heating or cooling source (other than natural insulation qualities). 
Therefore, it must be heated as a normal dwelling, and extreme heat adversely affects 
it and its occupants. The dwelling does, however, provide considerable security 
otherwise -- it is as strong as a normal stone building, regardless of its material 
composition. The dwelling resists flames and fire as if it were stone. It is impervious 
to normal missiles (but not the sort cast by siege engines or giants).

The door, shutters, and even chimney are secure against intrusion, the former two 
being \textit{arcane locked} and the latter secured by an iron grate at the top 
and a narrow flue. In addition, these three areas are protected by an \textit{alarm 
}spell. Finally, an \textit{unseen servant} is conjured to provide service to you 
for the duration of the shelter.

The \textit{secure shelter} contains rude furnishings  -- eight bunks, a trestle 
table, eight stools, and a writing desk.

\textit{Material Component:} A square chip of stone, crushed lime, a few grains 
of sand, a sprinkling of water, and several splinters of wood. These must be augmented 
by the components of the \textit{unseen servant} spell (string and a bit of wood) 
if this benefit is to be included.

\textit{Focus:} The focus of the \textit{alarm} spell (silver wire and a tiny bell) 
if this benefit is to be included.

