\spellentry{Sepia Snake Sigil}

Conjuration (Creation) [Force]

\textbf{Level:} Brd 3, Sor/Wiz 3

\textbf{Components:} V, S, M

\textbf{Casting Time:} 10 minutes

\textbf{Range:} Touch

\textbf{Target:} One touched book or written work

\textbf{Duration:} Permanent or until discharged; until released or 1d4 days + 
one day/level; see text

\textbf{Saving Throw:} Reflex negates

\textbf{Spell Resistance:} No

When you cast \textit{sepia snake sigil}, a small symbol appears in the text of 
one written work such as a book, scroll, or map. The text containing the symbol 
must be at least twenty-five words long. When anyone reads the text containing 
the symbol, the \textit{sepia snake} springs into being and strikes the reader, 
provided there is line of effect between the symbol and the reader.

Simply seeing the enspelled text is not sufficient to trigger the spell; the subject 
must deliberately read it. The target is entitled to a save to evade the snake's 
strike. If it succeeds, the \textit{sepia snake} dissipates in a flash of brown 
light accompanied by a puff of dun-colored smoke and a loud noise. If the target 
fails its save, it is engulfed in a shimmering amber field of force and immobilized 
until released, either at your command or when 1d4 days + one day per caster level 
have elapsed.

While trapped in the amber field of force, the subject does not age, breathe, grow 
hungry, sleep, or regain spells. It is preserved in a state of suspended animation, 
unaware of its surroundings. It can be damaged by outside forces (and perhaps even 
killed), since the field provides no protection against physical injury. However, 
a dying subject does not lose hit points or become stable until the spell ends.

The hidden sigil cannot be detected by normal observation, and \textit{detect magic 
}reveals only that the entire text is magical.

A \textit{dispel magic} can remove the sigil. An \textit{erase} spell destroys 
the entire page of text.

\textit{Sepia snake sigil} can be cast in combination with other spells that hide 
or garble text, such as \textit{secret page}.

\textit{Material Component:} 500 gp worth of powdered amber, a scale from any snake, 
and a pinch of mushroom spores.

