\spellentry{Shadow Conjuration}

Illusion (Shadow)

\textbf{Level:} Brd 4, Sor/Wiz 4

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Effect:} See text

\textbf{Duration:} See text

\textbf{Saving Throw:} Will disbelief (if interacted with); varies; see text

\textbf{Spell Resistance:} Yes; see text

You use material from the Plane of Shadow to shape quasi-real illusions of one 
or more creatures, objects, or forces. \textit{Shadow conjuration} can mimic any 
sorcerer or wizard conjuration (summoning) or conjuration (creation) spell of 3rd 
level or lower.

\textit{Shadow conjurations} are actually one-fifth (20\%) as strong as the real 
things, though creatures who believe the \textit{shadow conjurations} to be real 
are affected by them at full strength.

Any creature that interacts with the conjured object, force, or creature can make 
a Will save to recognize its true nature.

Spells that deal damage have normal effects unless the affected creature succeeds 
on a Will save. Each disbelieving creature takes only one-fifth (20\%) damage from 
the attack. If the disbelieved attack has a special effect other than damage, that 
effect is only 20\% likely to occur. Regardless of the result of the save to disbelieve, 
an affected creature is also allowed any save that the spell being simulated allows, 
but the save DC is set according to \textit{shadow conjuration'}s level (4th) rather 
than the spell's normal level. In addition, any effect created by \textit{shadow 
conjuration} allows spell resistance, even if the spell it is simulating does not. 
Shadow objects or substances have normal effects except against those who disbelieve 
them.

Against disbelievers, they are 20\% likely to work.

A shadow creature has one-fifth the hit points of a normal creature of its kind 
(regardless of whether it's recognized as shadowy). It deals normal damage and 
has all normal abilities and weaknesses. Against a creature that recognizes it 
as a shadow creature, however, the shadow creature's damage is one-fifth (20\%) 
normal, and all special abilities that do not deal lethal damage are only 20\% 
likely to work. (Roll for each use and each affected character separately.) Furthermore, 
the shadow creature's AC bonuses are one-fifth as large.

A creature that succeeds on its save sees the \textit{shadow conjurations} as transparent 
images superimposed on vague, shadowy forms.

Objects automatically succeed on their Will saves against this spell.

