\spellentry{Simulacrum}

Illusion (Shadow)

\textbf{Level:} Sor/Wiz 7

\textbf{Components:} V, S, M, XP

\textbf{Casting Time:} 12 hours

\textbf{Range:} 0 ft.

\textbf{Effect:} One duplicate creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

\textit{Simulacrum} creates an illusory duplicate of any creature. The duplicate 
creature is partially real and formed from ice or snow. It appears to be the same 
as the original, but it has only one-half of the real creature's levels or Hit 
Dice (and the appropriate hit points, feats, skill ranks, and special abilities 
for a creature of that level or HD). You can't create a simulacrum of a creature 
whose Hit Dice or levels exceed twice your caster level. You must make a Disguise 
check when you cast the spell to determine how good the likeness is. A creature 
familiar with the original might detect the ruse with a successful Spot check (opposed 
by the caster's Disguise check) or a DC 20 Sense Motive check.

At all times the simulacrum remains under your absolute command. No special telepathic 
link exists, so command must be exercised in some other manner. A simulacrum has 
no ability to become more powerful. It cannot increase its level or abilities. 
If reduced to 0 hit points or otherwise destroyed, it reverts to snow and melts 
instantly into nothingness. A complex process requiring at least 24 hours, 100 
gp per hit point, and a fully equipped magical laboratory can repair damage to 
a simulacrum.

\textit{Material Component:} The spell is cast over the rough snow or ice form, 
and some piece of the creature to be duplicated (hair, nail, or the like) must 
be placed inside the snow or ice. Additionally, the spell requires powdered ruby 
worth 100 gp per HD of the simulacrum to be created.

\textit{XP Cost:} 100 XP per HD of the simulacrum to be created (minimum 1,000 
XP).

