\spellentry{Soften Earth and Stone}

Transmutation [Earth]

\textbf{Level:} Drd 2, Earth 2

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} 10-ft. square/level; see text

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

When this spell is cast, all natural, undressed earth or stone in the spell's area 
is softened. Wet earth becomes thick mud, dry earth becomes loose sand or dirt, 
and stone becomes soft clay that is easily molded or chopped. You affect a 10-footsquare 
area to a depth of 1 to 4 feet, depending on the toughness or resilience of the 
ground at that spot. Magical, enchanted, dressed, or worked stone cannot be affected. 
Earth or stone creatures are not affected.

A creature in mud must succeed on a Reflex save or be caught for 1d2 rounds and 
unable to move, attack, or cast spells. A creature that succeeds on its save can 
move through the mud at half speed, and it can't run or charge.

Loose dirt is not as troublesome as mud, but all creatures in the area can move 
at only half their normal speed and can't run or charge over the surface.

Stone softened into clay does not hinder movement, but it does allow characters 
to cut, shape, or excavate areas they may not have been able to affect before.

While \textit{soften earth and stone} does not affect dressed or worked stone, 
cavern ceilings or vertical surfaces such as cliff faces can be affected. Usually, 
this causes a moderate collapse or landslide as the loosened material peels away 
from the face of the wall or roof and falls.

A moderate amount of structural damage can be dealt to a manufactured structure 
by softening the ground beneath it, causing it to settle. However, most well-built 
structures will only be damaged by this spell, not destroyed.

