\spellentry{Speak With Dead}

Necromancy [Language-Dependent]

\textbf{Level:} Clr 3

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 10 minutes

\textbf{Range:} 10 ft.

\textbf{Target:} One dead creature

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} Will negates; see text

\textbf{Spell Resistance:} No

You grant the semblance of life and intellect to a corpse, allowing it to answer 
several questions that you put to it. You may ask one question per two caster levels. 
Unasked questions are wasted if the duration expires. The corpse's knowledge is 
limited to what the creature knew during life, including the languages it spoke 
(if any). Answers are usually brief, cryptic, or repetitive. If the creature's 
alignment was different from yours, the corpse gets a Will save to resist the spell 
as if it were alive.

If the corpse has been subject to \textit{speak with dead} within the past week, 
the new spell fails. You can cast this spell on a corpse that has been deceased 
for any amount of time, but the body must be mostly intact to be able to respond. 
A damaged corpse may be able to give partial answers or partially correct answers, 
but it must at least have a mouth in order to speak at all. 

This spell does not let you actually speak to the person (whose soul has departed). 
It instead draws on the imprinted knowledge stored in the corpse. The partially 
animated body retains the imprint of the soul that once inhabited it, and thus 
it can speak with all the knowledge that the creature had while alive. The corpse, 
however, cannot learn new information.

Indeed, it can't even remember being questioned.

This spell does not affect a corpse that has been turned into an undead creature.

