\spellentry{Spell Turning}

Abjuration

\textbf{Level:} Luck 7, Magic 7, Sor/Wiz 7

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Until expended or 10 min./level

Spells and spell-like effects targeted on you are turned back upon the original 
caster. The abjuration turns only spells that have you as a target. Effect and 
area spells are not affected. \textit{Spell turning} also fails to stop touch range 
spells. 

From seven to ten (1d4+6) spell levels are affected by the turning. The exact number 
is rolled secretly.

When you are targeted by a spell of higher level than the amount of spell turning 
you have left, that spell is partially turned. The subtract the amount of spell 
turning left from the spell level of the incoming spell, then divide the result 
by the spell level of the incoming spell to see what fraction of the effect gets 
through. For damaging spells, you and the caster each take a fraction of the damage. 
For nondamaging spells, each of you has a proportional chance to be affected.

If you and a spellcasting attacker are both warded by \textit{spell turning} effects 
in operation, a resonating field is created.

Roll randomly to determine the result.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
\textbf{d\%}\end{minipage}} & \multicolumn{1}{p{3.741in}|}{\begin{minipage}[t]{3.741in}\raggedright
\textbf{Effect}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
01-70\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Spell drains away without effect.\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
71-80\end{minipage}} & \multicolumn{1}{p{3.741in}|}{\begin{minipage}[t]{3.741in}\raggedright
Spell affects both of you equally at full effect.\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
81-97\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Both turning effects are rendered nonfunctional for 1d4 minutes.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
98-100\end{minipage}} & \multicolumn{3}{p{3.880in}|}{\begin{minipage}[t]{3.880in}\raggedright
Both of you go through a rift into another plane.\end{minipage}}\\
\hline
\end{longtable}

\textit{Arcane Material Component:} A small silver mirror.

