\spellentry{Storm of Vengeance}

Conjuration (Summoning)

\textbf{Level:} Drd 9, Clr 9

\textbf{Components:} V, S

\textbf{Casting Time:} 1 round

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Effect:} 360-ft.-radius storm cloud

\textbf{Duration:} Concentration (maximum 10 rounds) (D)

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} Yes

This spell creates an enormous black storm cloud. Lightning and crashing claps 
of thunder appear within the storm. Each creature beneath the cloud must succeed 
on a Fortitude save or be deafened for 1d4x10 minutes.

If you do not maintain concentration on the spell after casting it, the spell ends. 
 If you continue to concentrate, the spell generates additional effects in each 
following round, as noted below. Each effect occurs during your turn.

\textit{2nd Round:} Acid rains down in the area, dealing 1d6 points of acid damage 
(no save).

\textit{3rd Round:} You call six bolts of lightning down from the cloud. You decide 
where the bolts strike. No two bolts may be directed at the same target. Each bolt 
deals 10d6 points of electricity damage. A creature struck can attempt a Reflex 
save for half damage.

\textit{4th Round:} Hailstones rain down in the area, dealing 5d6 points of bludgeoning 
damage (no save).

\textit{5th through 10th Rounds:} Violent rain and wind gusts reduce visibility. 
The rain obscures all sight, including darkvision, beyond 5 feet. A creature 5 
feet away has concealment (attacks have a 20\% miss chance). Creatures farther 
away have total concealment (50\% miss chance, and the attacker cannot use sight 
to locate the target). Speed is reduced by three-quarters.

Ranged attacks within the area of the storm are impossible. Spells cast within 
the area are disrupted unless the caster succeeds on a Concentration check against 
a DC equal to the \textit{storm of vengeance'}s save DC + the level of the spell 
the caster is trying to cast.

