\spellentry{Summon Monster I}

Conjuration (Summoning) [see text]

\textbf{Level:} Brd 1, Clr 1, Sor/Wiz 1

\textbf{Components:} V, S, F/DF

\textbf{Casting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} One summoned creature

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

This spell summons an extraplanar creature (typically an outsider, elemental, or 
magical beast native to another plane). It appears where you designate and acts 
immediately, on your turn. It attacks your opponents to the best of its ability. 
If you can communicate with the creature, you can direct it not to attack, to attack 
particular enemies, or to perform other actions.

The spell conjures one of the creatures from the 1st-level list on the accompanying 
Summon Monster table. You choose which kind of creature to summon, and you can 
change that choice each time you cast the spell.

A summoned monster cannot summon or otherwise conjure another creature, nor can 
it use any teleportation or planar travel abilities. Creatures cannot be summoned 
into an environment that cannot support them.

When you use a summoning spell to summon an air, chaotic, earth, evil, fire, good, 
lawful, or water creature, it is a spell of that type.

\textit{Summon Monster I List (and alignment):} Celestial dog LG, Celestial owl LG, Celestial giant fire beetle NG, Celestial porpoise NG (aquatic environments only), Celestial badger CG, Celestial monkey CG, Fiendish dire rat LE, Fiendish raven LE, Fiendish medium monstrous centipede NE, Fiendish small monstrous scorpion NE, Fiendish hawk CE, Fiendish small monstrous spider CE, Fiendish octopus CE (aquatic environments only), Fiendish small viper CE

\textit{Arcane Focus:} A tiny bag and a small (not necessarily lit) candle.

