\spellentry{Symbol of Death}

Necromancy [Death]

\textbf{Level:} Clr 8, Sor/Wiz 8

\textbf{Components:} V, S, M

\textbf{Casting Time:} 10 minutes

\textbf{Range:} 0 ft.; see text

\textbf{Effect:} One symbol

\textbf{Duration:} See text

\textbf{Saving Throw:} Fortitude negates

\textbf{Spell Resistance:} Yes

This spell allows you to scribe a potent rune of power upon a surface. When triggered, 
a \textit{symbol of death} slays one or more creatures within 60 feet of the symbol 
(treat as a burst) whose combined total current hit points do not exceed 150. The 
\textit{symbol of death} affects the closest creatures first, skipping creatures 
with too many hit points to affect. Once triggered, the \textit{symbol} becomes 
active and glows, lasting for 10 minutes per caster level or until it has affected 
150 hit points' worth of creatures, whichever comes first. Any creature that enters 
the area while the \textit{symbol of death} is active is subject to its effect, 
whether or not that creature was in the area when it was triggered. A creature 
need save against the \textit{symbol} only once as long as it remains within the 
area, though if it leaves the area and returns while the \textit{symbol} is still 
active, it must save again.

Until it is triggered, the \textit{symbol of death} is inactive (though visible 
and legible at a distance of 60 feet). To be effective, a \textit{symbol of death 
}must always be placed in plain sight and in a prominent location. Covering or 
hiding the rune renders the \textit{symbol of death} ineffective, unless a creature 
removes the covering, in which case the \textit{symbol of death} works normally.

As a default, a \textit{symbol of death} is triggered whenever a creature does 
one or more of the following, as you select: looks at the rune; reads the rune; 
touches the rune; passes over the rune; or passes through a portal bearing the 
rune. Regardless of the trigger method or methods chosen, a creature more than 
60 feet from a symbol of death can't trigger it (even if it meets one or more of 
the triggering conditions, such as reading the rune). Once the spell is cast, a 
\textit{symbol of death'}s triggering conditions cannot be changed.

In this case, "reading" the rune means any attempt to study it, identify it, 
or fathom its meaning. Throwing a cover over a \textit{symbol of death} to render 
it inoperative triggers it if the symbol reacts to touch. You can't use a \textit{symbol 
of death} offensively; for instance, a touch-triggered symbol of death remains 
untriggered if an item bearing the \textit{symbol of death} is used to touch a 
creature. Likewise, a \textit{symbol of death} cannot be placed on a weapon and 
set to activate when the weapon strikes a foe.

You can also set special triggering limitations of your own. These can be as simple 
or elaborate as you desire. Special conditions for triggering a \textit{symbol 
of death} can be based on a creature's name, identity, or alignment, but otherwise 
must be based on observable actions or qualities. Intangibles such as level, class, 
Hit Dice, and hit points don't qualify. 

When scribing a \textit{symbol of death}, you can specify a password or phrase 
that prevents a creature using it from triggering the effect. Anyone using 
the password remains immune to that particular rune's effects so long as the creature 
remains within 60 feet of the rune. If the creature leaves the radius and returns 
later, it must use the password again.

You also can attune any number of creatures to the \textit{symbol of death}, but 
doing this can extend the casting time. Attuning one or two creatures takes negligible 
time, and attuning a small group (as many as ten creatures) extends the casting 
time to 1 hour. Attuning a large group (as many as twenty-five creatures) takes 
24 hours. Attuning larger groups takes proportionately longer. Any creature attuned 
to a \textit{symbol of death} cannot trigger it and is immune to its effects, even 
if within its radius when triggered. You are automatically considered attuned to 
your own \textit{symbols of death}, and thus always ignore the effects and cannot 
inadvertently trigger them.

\textit{Read magic} allows you to identify a \textit{symbol of death} with a DC 
19 Spellcraft check. Of course, if the \textit{symbol of death} is set to be triggered 
by reading it, this will trigger the symbol.

A \textit{symbol of death} can be removed by a successful \textit{dispel magic 
}targeted solely on the rune. An \textit{erase} spell has no effect on a \textit{symbol 
of death}. Destruction of the surface where a \textit{symbol of death} is inscribed 
destroys the \textit{symbol} but also triggers it.

\textit{Symbol of death} can be made permanent with a \textit{permanency} spell. 
A permanent \textit{symbol of death} that is disabled or that has affected its 
maximum number of hit points becomes inactive for 10 minutes, then can be triggered 
again as normal.

\textit{Note:} Magic traps such as \textit{symbol of death} are hard to detect 
and disable. A rogue (only) can use the Search skill to find a \textit{symbol of 
death} and Disable Device to thwart it. The DC in each case is 25 + spell level, 
or 33 for \textit{symbol of death}.

\textit{Material Component:} Mercury and phosphorus, plus powdered diamond and 
opal with a total value of at least 5,000 gp each.

