\spellentry{Telekinesis}

Transmutation

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Target or Targets:} See text

\textbf{Duration:} Concentration (up to 1 round/ level) or instantaneous; see text

\textbf{Saving Throw:} Will negates (object) or None; see text

\textbf{Spell Resistance:} Yes (object); see text

You move objects or creatures by concentrating on them. Depending on the version 
selected, the spell can provide a gentle, sustained force, perform a variety of 
combat maneuvers, or exert a single short, violent thrust.

\textit{Sustained Force:} A sustained force moves an object weighing no more than 
25 pounds per caster level (maximum 375 pounds at 15th level) up to 20 feet per 
round. A creature can negate the effect on an object it possesses with a successful 
Will save or with spell resistance.

This version of the spell can last 1 round per caster level, but it ends if you 
cease concentration. The weight can be moved vertically, horizontally, or in both 
directions. An object cannot be moved beyond your range. The spell ends if the 
object is forced beyond the range. If you cease concentration for any reason, the 
object falls or stops.

An object can be telekinetically manipulated as if with one hand. For example, 
a lever or rope can be pulled, a key can be turned, an object rotated, and so on, 
if the force required is within the weight limitation. You might even be able to 
untie simple knots, though delicate activities such as these require Intelligence 
checks.

\textit{Combat Maneuver:} Alternatively, once per round, you can use \textit{telekinesis 
}to perform a bull rush, disarm, grapple (including pin), or trip. Resolve these 
attempts as normal, except that they don't provoke attacks of opportunity, you 
use your caster level in place of your base attack bonus (for disarm and grapple), 
you use your Intelligence modifier (if a wizard) or Charisma modifier (if a sorcerer) 
in place of your Strength or Dexterity modifier, and a failed attempt doesn't allow 
a reactive attempt by the target (such as for disarm or trip). No save is allowed 
against these attempts, but spell resistance applies normally. This version of 
the spell can last 1 round per caster level, but it ends if you cease concentration.

\textit{Violent Thrust:} Alternatively, the spell energy can be spent in a single 
round. You can hurl one object or creature per caster level (maximum 15) that are 
within range and all within 10 feet of each other toward any target within 10 feet 
per level of all the objects. You can hurl up to a total weight of 25 pounds per 
caster level (maximum 375 pounds at 15th level).

You must succeed on attack rolls (one per creature or object thrown) to hit the 
target with the items, using your base attack bonus + your Intelligence modifier 
(if a wizard) or Charisma modifier (if a sorcerer). Weapons cause standard damage 
(with no Strength bonus; note that arrows or bolts deal damage as daggers of their 
size when used in this manner). Other objects cause damage ranging from 1 point 
per 25 pounds (for less dangerous objects) to 1d6 points of damage per 25 pounds 
(for hard, dense objects).

Creatures who fall within the weight capacity of the spell can be hurled, but they 
are allowed Will saves (and spell resistance) to negate the effect, as are those 
whose held possessions are targeted by the spell. If a telekinesed creature is 
hurled against a solid surface, it takes damage as if it had fallen 10 feet (1d6 
points).

