\spellentry{Teleport}

Conjuration (Teleportation)

\textbf{Level:} Sor/Wiz 5, Travel 5

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal and touch

\textbf{Target:} You and touched objects or other touched willing creatures

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None and Will negates (object)

\textbf{Spell Resistance:} No and Yes (object)

This spell instantly transports you to a designated destination, which may be as 
distant as 100 miles per caster level. Interplanar travel is not possible. You 
can bring along objects as long as their weight doesn't exceed your maximum load. 
You may also bring one additional willing Medium or smaller creature (carrying 
gear or objects up to its maximum load) or its equivalent (see below) per three 
caster levels. A Large creature counts as two Medium creatures, a Huge creature 
counts as two Large creatures, and so forth. All creatures to be transported must 
be in contact with one another, and at least one of those creatures must be in 
contact with you. As with all spells where the range is personal and the target 
is you, you need not make a saving throw, nor is spell resistance applicable to 
you. Only objects held or in use (attended) by another person receive saving throws 
and spell resistance.

You must have some clear idea of the location and layout of the destination. The 
clearer your mental image, the more likely the teleportation works. Areas of strong 
physical or magical energy may make teleportation more hazardous or even impossible.

To see how well the teleportation works, roll d\% and consult the Teleport table. 
Refer to the following information for definitions of the terms on the table.

\textit{Familiarity:} "Very familiar" is a place where you have been very often 
and where you feel at home. "Studied carefully" is a place you know well, either 
because you can currently see it, you've been there often, or you have used other 
means (such as \textit{scrying}) to study the place for at least one hour. "Seen 
casually" is a place that you have seen more than once but with which you are 
not very familiar. "Viewed once" is a place that you have seen once, possibly 
using magic. 

"False destination" is a place that does not truly exist or if you are teleporting 
to an otherwise familiar location that no longer exists as such or has been so 
completely altered as to no longer be familiar to you. When traveling to a false 
destination, roll 1d20+80 to obtain results on the table, rather than rolling d\%, 
since there is no real destination for you to hope to arrive at or even be off 
target from.

\textit{On Target:} You appear where you want to be.

\textit{Off Target:} You appear safely a random distance away from the destination 
in a random direction. Distance off target is 1d10x1d10\% of the distance that 
was to be traveled. The direction off target is determined randomly

\textit{Similar Area:} You wind up in an area that's visually or thematically similar 
to the target area.

Generally, you appear in the closest similar place within range. If no such area 
exists within the spell's range, the spell simply fails instead.

\textit{Mishap:} You and anyone else teleporting with you have gotten "scrambled." 
You each take 1d10 points of damage, and you reroll on the chart to see where you 
wind up. For these rerolls, roll 1d20+80. Each time "Mishap" comes up, the characters 
take more damage and must reroll.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{1}{|p{1.499in}|}{\begin{minipage}[t]{1.499in}\raggedright
\textbf{Familiarity}\end{minipage}} & \multicolumn{1}{p{0.677in}|}{\begin{minipage}[t]{0.677in}\centering
\textbf{On Target}\end{minipage}} & \multicolumn{1}{p{0.690in}|}{\begin{minipage}[t]{0.690in}\centering
\textbf{Off Target}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\centering
\textbf{Similar Area}\end{minipage}} & \multicolumn{1}{p{0.524in}|}{\begin{minipage}[t]{0.524in}\centering
\textbf{Mishap}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
Very familiar\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
01-97\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
98-99\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
100\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
 -- \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.499in}|}{\begin{minipage}[t]{1.499in}\centering
Studied carefully\end{minipage}} & \multicolumn{1}{p{0.677in}|}{\begin{minipage}[t]{0.677in}\centering
01-94\end{minipage}} & \multicolumn{1}{p{0.690in}|}{\begin{minipage}[t]{0.690in}\centering
95-97\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\centering
98-99\end{minipage}} & \multicolumn{1}{p{0.524in}|}{\begin{minipage}[t]{0.524in}\centering
100\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
Seen casually\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
01-88\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
89-94\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
95-98\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
99-100\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.499in}|}{\begin{minipage}[t]{1.499in}\centering
Viewed once\end{minipage}} & \multicolumn{1}{p{0.677in}|}{\begin{minipage}[t]{0.677in}\centering
01-76\end{minipage}} & \multicolumn{1}{p{0.690in}|}{\begin{minipage}[t]{0.690in}\centering
77-88\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\centering
89-96\end{minipage}} & \multicolumn{6}{p{0.829in}|}{\begin{minipage}[t]{0.829in}\centering
97-100\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
False destination (1d20+80)\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
 -- \end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
 -- \end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
81-92\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
93-100\end{minipage}}\\
\hline
\end{longtable}

