\spellentry{Telekinetic Sphere}

Evocation [Force]

\textbf{Level:} Sor/Wiz 8

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} 1-ft.-diameter/level sphere, centered around creatures or objects

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Reflex negates (object)

\textbf{Spell Resistance:} Yes (object)

This spell functions like \textit{resilient sphere}, with the addition that the 
creatures or objects inside the globe are nearly weightless. Anything contained 
within an \textit{telekinetic sphere} weighs only one-sixteenth of its normal weight. 
You can telekinetically lift anything in the sphere that normally weighs 5,000 
pounds or less. The telekinetic control extends from you out to medium range (100 
feet + 10 feet per caster level) after the sphere has succeeded in encapsulating 
its contents.

You can move objects or creatures in the sphere that weigh a total of 5,000 pounds 
or less by concentrating on the sphere. You can begin moving a sphere in the round 
after casting the spell. If you concentrate on doing so (a standard action), you 
can move the sphere as much as 30 feet in a round. If you cease concentrating, 
the sphere does not move in that round (if on a level surface) or descends at its 
falling rate (if aloft) until it reaches a level surface, or the spell's duration 
expires, or you begin concentrating again. If you cease concentrating (voluntarily 
or due to failing a Concentration check), you can resume concentrating on your 
next turn or any later turn during the spell's duration.

The sphere falls at a rate of only 60 feet per round, which is not fast enough 
to cause damage to the contents of the sphere.

You can move the sphere telekinetically even if you are in it.

\textit{Material Component:} A hemispherical piece of clear crystal, a matching 
hemispherical piece of gum arabic, and a pair of small bar magnets.

