\spellentry{Transport Via Plants}

Conjuration (Teleportation)

\textbf{Level:} Drd 6

\textbf{Components:} V, S

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Unlimited

\textbf{Target:} You and touched objects or other touched willing creatures

\textbf{Duration:} 1 round

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

You can enter any normal plant (Medium or larger) and pass any distance to a plant 
of the same kind in a single round, regardless of the distance separating the two. 
The entry plant must be alive. The destination plant need not be familiar to you, 
but it also must be alive. If you are uncertain of the location of a particular 
kind of destination plant, you need merely designate direction and distance and 
the \textit{transport via plants} spell moves you as close as possible to the desired 
location. If a particular destination plant is desired but the plant is not living, 
the spell fails and you are ejected from the entry plant.

You can bring along objects as long as their weight doesn't exceed your maximum 
load. You may also bring one additional willing Medium or smaller creature (carrying 
gear or objects up to its maximum load) or its equivalent per three caster levels. 
Use the following equivalents to determine the maximum number of larger creatures 
you can bring along: A Large creature counts as two Medium creatures, a Huge creature 
counts as two Large creatures, and so forth. All creatures to be transported must 
be in contact with one another, and at least one of those creatures must be in 
contact with you.

You can't use this spell to travel through plant creatures.

The destruction of an occupied plant slays you and any creatures you have brought 
along, and ejects the bodies and all carried objects from the tree.

