\spellentry{Trap the Soul}

Conjuration (Summoning)

\textbf{Level:} Sor/Wiz 8

\textbf{Components:} V, S, M, (F); see text

\textbf{Casting Time:} 1 standard action or see text

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} Permanent; see text

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} Yes; see text

\textit{Trap the soul} forces a creature's life force (and its material body) into 
a gem. The gem holds the trapped entity indefinitely or until the gem is broken 
and the life force is released, which allows the material body to reform. If the 
trapped creature is a powerful creature from another plane it can be required to 
perform a service immediately upon being freed. Otherwise, the creature can go 
free once the gem imprisoning it is broken.

Depending on the version selected, the spell can be triggered in one of two ways.

\textit{Spell Completion:} First, the spell can be completed by speaking its final 
word as a standard action as if you were casting a regular spell at the subject. 
This allows spell resistance (if any) and a Will save to avoid the effect. If the 
creature's name is spoken as well, any spell resistance is ignored and the save 
DC increases by 2. If the save or spell resistance is successful, the gem shatters.

\textit{Trigger Object:} The second method is far more insidious, for it tricks 
the subject into accepting a trigger object inscribed with the final spell word, 
automatically placing the creature's soul in the trap. To use this method, both 
the creature's name and the trigger word must be inscribed on the trigger object 
when the gem is enspelled. A \textit{sympathy} spell can also be placed on the 
trigger object. As soon as the subject picks up or accepts the trigger object, 
its life force is automatically transferred to the gem without the benefit of spell 
resistance or a save.

\textit{Material Component:} Before the actual casting of \textit{trap the soul, 
}you must procure a gem of at least 1,000 gp value for every Hit Die possessed 
by the creature to be trapped. If the gem is not valuable enough, it shatters when 
the entrapment is attempted. (While creatures have no concept of level or Hit Dice 
as such, the value of the gem needed to trap an individual can be researched. Remember 
that this value can change over time as creatures gain more Hit Dice.)

\textit{Focus (Trigger Object Only):} If the trigger object method is used, a special 
trigger object, prepared as described above, is needed.

