\spellentry{Tree Stride}

Conjuration (Teleportation)

\textbf{Level:} Drd 5, Rgr 4

\textbf{Components:} V, S, DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 hour/level or until expended; see text

You gain the ability to enter trees and move from inside one tree to inside another 
tree. The first tree you enter and all others you enter must be of the same kind, 
must be living, and must have girth at least equal to yours. By moving into an 
oak tree (for example), you instantly know the location of all other oak trees 
within transport range (see below) and may choose whether you want to pass into 
one or simply step back out of the tree you moved into. You may choose to pass 
to any tree of the appropriate kind within the transport range as shown on the 
following table.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
\textbf{Type of Tree}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
\textbf{Transport Range}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Oak, ash, yew\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
3,000 feet\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
Elm, linden\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
2,000 feet\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Other deciduous\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1,500 feet\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
Any coniferous\end{minipage}} & \multicolumn{3}{p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
1,000 feet\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
All other trees\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
500 feet\end{minipage}}\\
\hline
\end{longtable}

You may move into a tree up to one time per caster level (passing from one tree 
to another counts only as moving into one tree). The spell lasts until the duration 
expires or you exit a tree. Each transport is a full-round action.

You can, at your option, remain within a tree without transporting yourself, but 
you are forced out when the spell ends. If the tree in which you are concealed 
is chopped down or burned, you are slain if you do not exit before the process 
is complete.

