\spellentry{True Seeing}

Divination

\textbf{Level:} Clr 5, Drd 7, Knowledge 5, Sor/Wiz 6

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} Creature touched

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} Will negates (harmless)

\textbf{Spell Resistance:} Yes (harmless)

You confer on the subject the ability to see all things as they actually are. The 
subject sees through normal and magical darkness, notices secret doors hidden by 
magic, sees the exact locations of creatures or objects under \textit{blur} or 
\textit{displacement} effects, sees invisible creatures or objects normally, sees 
through illusions, and sees the true form of polymorphed, changed, or transmuted 
things. Further, the subject can focus its vision to see into the Ethereal Plane 
(but not into extradimensional spaces). The range of \textit{true seeing} conferred 
is 120 feet.

\textit{True seeing}, however, does not penetrate solid objects. It in no way confers 
X-ray vision or its equivalent. It does not negate concealment, including that 
caused by fog and the like. \textit{True seeing} does not help the viewer see through 
mundane disguises, spot creatures who are simply hiding, or notice secret doors 
hidden by mundane means. In addition, the spell effects cannot be further enhanced 
with known magic, so one cannot use \textit{true seeing} through a \textit{crystal 
ball} or in conjunction with \textit{clairaudience/clairvoyance}.

\textit{Material Component:} An ointment for the eyes that costs 250 gp and is 
made from mushroom powder, saffron, and fat.

