\spellentry{Unhallow}

Evocation [Evil]

\textbf{Level:} Clr 5, Drd 5

\textbf{Components:} V, S, M

\textbf{Casting Time:} 24 hours

\textbf{Range:} Touch

\textbf{Area:} 40-ft. radius emanating from the touched point

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} See text

\textit{Unhallow} makes a particular site, building, or structure an unholy site. 
This has three major effects.

First, the site or structure is guarded by a \textit{magic circle against good 
}effect.

Second, all turning checks made to turn undead take a -4 penalty, and turning checks 
to rebuke undead gain a +4 profane bonus. Spell resistance does not apply to this 
effect. (This provision does not apply to the druid version of the spell.)

Finally, you may choose to fix a single spell effect to the \textit{unhallowed 
}site. The spell effect lasts for one year and functions throughout the entire 
site, regardless of its normal duration and area or effect. You may designate whether 
the effect applies to all creatures, creatures that share your faith or alignment, 
or creatures that adhere to another faith or alignment. At the end of the year, 
the chosen effect lapses, but it can be renewed or replaced simply by casting \textit{unhallow 
}again.

Spell effects that may be tied to an \textit{unhallowed} site include \textit{aid, 
bane, bless, cause fear, darkness, daylight, death ward, deeper darkness, detect 
magic, detect good, dimensional anchor, discern lies, dispel magic, endure elements, 
freedom of movement, invisibility purge, protection from energy, remove fear, resist 
energy, silence, tongues}, and \textit{zone of truth}.

Saving throws and spell resistance might apply to these spells' effects. (See the 
individual spell descriptions for details.)

An area can receive only one \textit{unhallow} spell (and its associated spell 
effect) at a time.

\textit{Unhallow} counters but does not dispel \textit{hallow}.

\textit{Material Component:} Herbs, oils, and incense worth at least 1,000 gp, 
plus 1,000 gp per level of the spell to be tied to the \textit{unhallowed} area.

