\spellentry{Wall of Iron}

Conjuration (Creation)

\textbf{Level:} Sor/Wiz 6

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Iron wall whose area is up to one 5-ft. square/level; see text

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} No

You cause a flat, vertical iron wall to spring into being. The wall inserts itself 
into any surrounding nonliving material if its area is sufficient to do so. The 
wall cannot be conjured so that it occupies the same space as a creature or another 
object. It must always be a flat plane, though you can shape its edges to fit the 
available space.

A \textit{wall of iron} is 1 inch thick per four caster levels. You can double 
the wall's area by halving its thickness. Each 5- foot square of the wall has 30 
hit points per inch of thickness and hardness 10. A section of wall whose hit points 
drop to 0 is breached. If a creature tries to break through the wall with a single 
attack, the DC for the Strength check is 25 + 2 per inch of thickness.

If you desire, the wall can be created vertically resting on a flat surface but 
not attached to the surface, so that it can be tipped over to fall on and crush 
creatures beneath it. The wall is 50\% likely to tip in either direction if left 
unpushed. Creatures can push the wall in one direction rather than letting it fall 
randomly. A creature must make a DC 40 Strength check to push the wall over. Creatures 
with room to flee the falling wall may do so by making successful Reflex saves. 
Any Large or smaller creature that fails takes 10d6 points of damage. The wall 
cannot crush Huge and larger creatures.

Like any iron wall, this wall is subject to rust, perforation, and other natural 
phenomena.

\textit{Material Component:} A small piece of sheet iron plus gold dust worth 50 
gp (1 pound of gold dust).

