\spellentry{Wall of Fire}

Evocation [Fire]

\textbf{Level:} Drd 5, Fire 4, Sor/Wiz 4

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Opaque sheet of flame up to 20 ft. long/level or a ring of fire 
with a radius of up to 5 ft. per two levels; either form 20 ft. high

\textbf{Duration:} Concentration + 1 round/level

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} Yes

An immobile, blazing curtain of shimmering violet fire springs into existence. 
One side of the wall, selected by you, sends forth waves of heat, dealing 2d4 points 
of fire damage to creatures within 10 feet and 1d4 points of fire damage to those 
past 10 feet but within 20 feet. The wall deals this damage when it appears and 
on your turn each round to all creatures in the area. In addition, the wall deals 
2d6 points of fire damage +1 point of fire damage per caster level (maximum +20) 
to any creature passing through it. The wall deals double damage to undead creatures.

If you evoke the wall so that it appears where creatures are, each creature takes 
damage as if passing through the wall. If any 5-foot length of wall takes 20 points 
of cold damage or more in 1 round, that length goes out. (Do not divide cold damage 
by 4, as normal for objects.)

\textit{Wall of fire} can be made permanent with a \textit{permanency} spell. A 
permanent \textit{wall of fire} that is extinguished by cold damage becomes inactive 
for 10 minutes, then reforms at normal strength.

\textit{Arcane Material Component:} A small piece of phosphorus.

