\spellentry{Wall of Ice}

Evocation [Cold]

\textbf{Level:} Sor/Wiz 4

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Anchored plane of ice, up to one 10-ft. square/level, or hemisphere 
of ice with a radius of up to 3 ft. + 1 ft./level

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} Reflex negates; see text

\textbf{Spell Resistance:} Yes

This spell creates an anchored plane of ice or a hemisphere of ice, depending on 
the version selected. A \textit{wall of ice} cannot form in an area occupied by 
physical objects or creatures. Its surface must be smooth and unbroken when created. 
Any creature adjacent to the wall when it is created may attempt a Reflex save 
to disrupt the wall as it is being formed. A successful save indicates that the 
spell automatically fails. Fire can melt a \textit{wall of ice}, and it deals full 
damage to the wall (instead of the normal half damage taken by objects). Suddenly 
melting a \textit{wall of ice} creates a great cloud of steamy fog that lasts for 
10 minutes.

\textit{Ice Plane:} A sheet of strong, hard ice appears. The wall is 1 inch thick 
per caster level. It covers up to a 10-foot-square area per caster level (so a 
10th-level wizard can create a wall of ice 100 feet long and 10 feet high, a wall 
50 feet long and 20 feet high, or some other combination of length and height that 
does not exceed 1,000 square feet). The plane can be oriented in any fashion as 
long as it is anchored. A vertical wall need only be anchored on the floor, while 
a horizontal or slanting wall must be anchored on two opposite sides.

Each 10-foot square of wall has 3 hit points per inch of thickness. Creatures can 
hit the wall automatically. A section of wall whose hit points drop to 0 is breached. 
If a creature tries to break through the wall with a single attack, the DC for 
the Strength check is 15 + caster level.

Even when the ice has been broken through, a sheet of frigid air remains. Any creature 
stepping through it (including the one who broke through the wall) takes 1d6 points 
of cold damage +1 point per caster level (no save).

\textit{Hemisphere:} The wall takes the form of a hemisphere whose maximum radius 
is 3 feet + 1 foot per caster level. The \textit{hemisphere} is as hard to break 
through as the \textit{ice plane} form, but it does not deal damage to those who 
go through a breach.

\textit{Material Component:} A small piece of quartz or similar rock crystal.

