\spellentry{Wall of Stone}

Conjuration (Creation) [Earth]

\textbf{Level:} Clr 5, Drd 6, Earth 5, Sor/Wiz 5

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Stone wall whose area is up to one 5-ft. square/level (S)

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} No

This spell creates a wall of rock that merges into adjoining rock surfaces. A \textit{wall 
of stone} is 1 inch thick per four caster levels and composed of up to one 5-foot 
square per level. You can double the wall's area by halving its thickness. The 
wall cannot be conjured so that it occupies the same space as a creature or another 
object.

Unlike a \textit{wall of iron}, you can create a \textit{wall of stone} in almost 
any shape you desire. The wall created need not be vertical, nor rest upon any 
firm foundation; however, it must merge with and be solidly supported by existing 
stone. It can be used to bridge a chasm, for instance, or as a ramp. For this use, 
if the span is more than 20 feet, the wall must be arched and buttressed. This 
requirement reduces the spell's area by half. The wall can be crudely shaped to 
allow crenellations, battlements, and so forth by likewise reducing the area.

Like any other stone wall, this one can be destroyed by a \textit{disintegrate 
}spell or by normal means such as breaking and chipping. Each 5-foot square of 
the wall has 15 hit points per inch of thickness and hardness 8. A section of wall 
whose hit points drop to 0 is breached. If a creature tries to break through the 
wall with a single attack, the DC for the Strength check is 20 + 2 per inch of 
thickness.

It is possible, but difficult, to trap mobile opponents within or under a \textit{wall 
of stone}, provided the wall is shaped so it can hold the creatures. Creatures 
can avoid entrapment with successful Reflex saves.

\textit{Arcane Material Component:} A small block of granite.

