\spellentry{Wall of Force}

Evocation [Force]

\textbf{Level:} Sor/Wiz 5

\textbf{Components:} V, S, M

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} Wall whose area is up to one 10-ft. square/level

\textbf{Duration:} 1 round /level (D)

\textbf{Saving Throw:} None

\textbf{Spell Resistance:} No

A \textit{wall of force} spell creates an invisible wall of force. The wall cannot 
move, it is immune to damage of all kinds, and it is unaffected by most spells, 
including \textit{dispel magic}. However, \textit{disintegrate} immediately destroys 
it, as does a \textit{rod of cancellation}, a \textit{sphere of annihilation}, or 
a \textit{mage's disjunction} spell. Breath weapons and spells cannot pass through 
the wall in either direction, although \textit{dimension door, teleport}, and similar 
effects can bypass the barrier. It blocks ethereal creatures as well as material 
ones (though ethereal creatures can usually get around the wall by floating under 
or over it through material floors and ceilings). Gaze attacks can operate through 
a \textit{wall of force}.

The caster can form the wall into a flat, vertical plane whose area is up to one 
10- foot square per level. The wall must be continuous and unbroken when formed. 
If its surface is broken by any object or creature, the spell fails.

\textit{Wall of force} can be made permanent with a \textit{permanency} spell.

\textit{Material Component:} A pinch of powder made from a clear gem.

