\spellentry{Wind Wall}

Evocation [Air]

\textbf{Level:} Air 2, Clr 3, Drd 3, Rgr 2, Sor/Wiz 3

\textbf{Components:} V, S, M/DF

\textbf{Casting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Effect:} Wall up to 10 ft./level long and 5 ft./level high (S)

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} None; see text

\textbf{Spell Resistance:} Yes

An invisible vertical curtain of wind appears. It is 2 feet thick and of considerable 
strength. It is a roaring blast sufficient to blow away any bird smaller than an 
eagle, or tear papers and similar materials from unsuspecting hands. (A Reflex 
save allows a creature to maintain its grasp on an object.) Tiny and Small flying 
creatures cannot pass through the barrier. Loose materials and cloth garments fly 
upward when caught in a \textit{wind wall}. Arrows and bolts are deflected upward 
and miss, while any other normal ranged weapon passing through the wall has a 30\% 
miss chance. (A giant-thrown boulder, a siege engine projectile, and other massive 
ranged weapons are not affected.) Gases, most gaseous breath weapons, and creatures 
in gaseous form cannot pass through the wall (although it is no barrier to incorporeal 
creatures).

While the wall must be vertical, you can shape it in any continuous path along 
the ground that you like. It is possible to create cylindrical or square wind walls 
to enclose specific points. 

\textit{Arcane Material Component:} A tiny fan and a feather of exotic origin.

