\spellentry{Wish}

Universal

\textbf{Level:} Sor/Wiz 9

\textbf{Components:} V, XP

\textbf{Casting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Target, Effect, or Area:} See text

\textbf{Duration:} See text

\textbf{Saving Throw:} See text

\textbf{Spell Resistance:} Yes

\textit{Wish} is the mightiest spell a wizard or sorcerer can cast. By simply speaking 
aloud, you can alter reality to better suit you.

Even \textit{wish}, however, has its limits.

A \textit{wish} can produce any one of the following effects.%\item

Duplicate any wizard or sorcerer spell of 8th level or lower, provided the spell 
is not of a school prohibited to you.%\item

Duplicate any other spell of 6th level or lower, provided the spell is not of a 
school prohibited to you.%\item

Duplicate any wizard or sorcerer spell of 7th level or lower even if it's of a 
prohibited school.%\item

Duplicate any other spell of 5th level or lower even if it's of a prohibited school. 
%\item
Undo the harmful effects of many other spells, such as \textit{geas/quest} or \textit{insanity}.%\item

Create a nonmagical item of up to 25,000 gp in value.%\item

Create a magic item, or add to the powers of an existing magic item.%\item

Grant a creature a +1 inherent bonus to an ability score. Two to five \textit{wish 
}spells cast in immediate succession can grant a creature a +2 to +5 inherent bonus 
to an ability score (two wishes for a +2 inherent bonus, three for a +3 inherent 
bonus, and so on). Inherent bonuses are instantaneous, so they cannot be dispelled. 
\textit{Note:} An inherent bonus may not exceed +5 for a single ability score, 
and inherent bonuses to a particular ability score do not stack, so only the best 
one applies.%\item

Remove injuries and afflictions. A single \textit{wish} can aid one creature per 
caster level, and all subjects are cured of the same kind of affliction. For example, 
you could heal all the damage you and your companions have taken, or remove all 
poison effects from everyone in the party, but not do both with the same \textit{wish}. 
A \textit{wish} can never restore the experience point loss from casting a spell 
or the level or Constitution loss from being raised from the dead.%\item

Revive the dead. A \textit{wish} can bring a dead creature back to life by duplicating 
a \textit{resurrection} spell. A \textit{wish} can revive a dead creature whose 
body has been destroyed, but the task takes two \textit{wishes}, one to recreate 
the body and another to infuse the body with life again. A \textit{wish} cannot 
prevent a character who was brought back to life from losing an experience level.%\item

Transport travelers. A \textit{wish} can lift one creature per caster level from 
anywhere on any plane and place those creatures anywhere else on any plane regardless 
of local conditions. An unwilling target gets a Will save to negate the effect, 
and spell resistance (if any) applies.%\item

Undo misfortune. A \textit{wish} can undo a single recent event. The \textit{wish 
}forces a reroll of any roll made within the last round (including your last turn). 
Reality reshapes itself to accommodate the new result. For example, a \textit{wish 
}could undo an opponent's successful save, a foe's successful critical hit (either 
the attack roll or the critical roll), a friend's failed save, and so on. The reroll, 
however, may be as bad as or worse than the original roll. An unwilling target 
gets a Will save to negate the effect, and spell resistance (if any) applies.

You may try to use a \textit{wish} to produce greater effects than these, but doing 
so is dangerous. (The \textit{wish} may pervert your intent into a literal but 
undesirable fulfillment or only a partial fulfillment.)

Duplicated spells allow saves and spell resistance as normal (but save DCs are 
for 9th-level spells).

\textit{Material Component:} When a \textit{wish} duplicates a spell with a material 
component that costs more than 10,000 gp, you must provide that component.

\textit{XP Cost:} The minimum XP cost for casting \textit{wish} is 5,000 XP. When 
a \textit{wish} duplicates a spell that has an XP cost, you must pay 5,000 XP or 
that cost, whichever is more. When a \textit{wish} creates or improves a magic 
item, you must pay twice the normal XP cost for crafting or improving the item, 
plus an additional 5,000 XP.

