\spellentry{Word of Chaos}

Evocation [Chaotic, Sonic]

\textbf{Level:} Chaos 7, Clr 7

\textbf{Components:} V

\textbf{Casting Time:} 1 standard action

\textbf{Range:} 40 ft.

\textbf{Area:} Nonchaotic creatures in a 40-ft.- radius spread centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None or Will negates; see text

\textbf{Spell Resistance:} Yes

Any nonchaotic creature within the area who hears the \textit{word of chaos} suffers 
the following ill effects.

The effects are cumulative and concurrent. No saving throw is allowed against these 
effects.

\textit{Deafened:} The creature is deafened for 1d4 rounds.

\textit{Stunned:} The creature is stunned for 1 round.

\textit{Confused:} The creature is \textit{confused}, as by the \textit{confusion 
}spell, for 1d10 minutes. This is a mind-affecting enchantment effect.

\textit{Killed:} Living creatures die. Undead creatures are destroyed.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
\textbf{HD}\end{minipage}} & \multicolumn{1}{p{2.133in}|}{\begin{minipage}[t]{2.133in}\raggedright
\textbf{Effect}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Equal to caster level\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Deafened\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
Up to caster level -1\end{minipage}} & \multicolumn{1}{p{2.133in}|}{\begin{minipage}[t]{2.133in}\raggedright
Stunned, deafened\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Up to caster level -5\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textit{Confused}, stunned, deafened\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.369in}|}{\begin{minipage}[t]{1.369in}\raggedright
Up to caster level -10\end{minipage}} & \multicolumn{3}{p{2.272in}|}{\begin{minipage}[t]{2.272in}\raggedright
Killed, \textit{confused}, stunned, deafened\end{minipage}}\\
\hline
\end{longtable}

Furthermore, if you are on your home plane when you cast this spell, nonchaotic 
extraplanar creatures within the area are instantly banished back to their home 
planes. Creatures so banished cannot return for at least 24 hours. This effect 
takes place regardless of whether the creatures hear the \textit{word of chaos. 
}The banishment effect allows a Will save (at a -4 penalty) to negate.

Creatures whose HD exceed your caster level are unaffected by \textit{word of chaos}.

