\subsection{Genasi}
\vspace*{-8pt}
\quote {``Fire burns in my veins. And soon, in yours."}

Genasi are the descendents of mortals and genies of various kinds.  Mortals with minor infusions of elemental essense before birth, or descended from those with stronger infusions, also appear as Genasi.  Their physical traits are influenced by the elements they are descended from.

Depending on their elemental influences, Genasi are likely to become every kind of adventurer.

Genasi have the following racial traits:
\listone
    \item Medium Size. Genasi fall into the human height and weight ranges, although Earth Genasi tend to be squat and Air Genasi willowy.
    \item 30' movement
    \item Outsider Type (Native and Human subtypes)
    \item Elemental Subtype of the appropriate element: (Air), (Earth), (Fire), or (Water).
    \item Darkvision 60'
    \item +2 Strength
    \item +1 to the DC to save against any spells or spell-like abilities cast by the Genasi with a descriptor matching the Genasi's elemental subtype.
    \item Favored Class: Genie and by element: Air: Thief-Acrobat.  Earth: Knight.  Fire: Elementalist.  Water: Monk.
    \item Automatic Languages: Common
    \item Bonus Languages: Abyssal, Aquan, Auran, Celestial, Draconic, Formian, Ignan, Infernal, Slaad, Terran
\end{list}

Genasi also gain another ability that reflects their elemental origin:
\listone
    \item Air: Fly speed of 10' with Good maneuverability
    \item Earth: Burrow speed of 10'
    \item Fire: \spell{Produce flame} as a spell-like ability three times per day, cast at the Genasi's character level.  
    \item Water: Swim speed of 30' and ability to breathe water as easily as air.
\end{list}

\textbf{Fire Genasi Genie Substitution Class Feature:}

\desc{Instead of getting Immunity to Fire as a Genie at 1st level, the Fire Genasi instead loses their Cold Vulnerability.}

\textbf{Material and Shadow Genasi:}

\textbf{Material Genasi} are the descendents of Jann and mortals.  A Material Genasi does not get an elemental subtype, but instead receives a +1 to their saving throw against all spells of any elemental subtype.  Their favored classes are Druid and Genie.

\textbf{Shadow Genasi} are the descendents of Khayal Genies (see the Tome of Magic) and mortals.  A Shadow Genasi gains a bonus to Constitution instead of Strength, no elemental subtype, Spell Focus (Illusion) as a bonus feat, which also applies to any spell-like abilities it may have, and the ability to cast \spell{invisibility} once per day as a spell-like ability with a caster level equal to their character level).  Their favored classes are Beguiler and Genie.