The Spheres available to the Curator do not follow the thematic restrictions given in the Tome of Fiends, and therefore are not available to Fiendish Sphere users, such as the True Fiend, Conduit of the Lower Planes, and Warlock. Additionally, these Spheres do not impart fiendish traits as the Fiendish Spheres do. However, they follow all other mechanics for Fiendish Spheres.

Exorcism Sphere
(Created by Doctus)

Special: You gain the ability to turn undead three times per day as a good-aligned cleric of the same level as the class that granted you this sphere. You cannot use these turning attempts to power divine feats.

Level, Benefits
1 Protection from Evil
3 Consecrate
5 Magic Circle against Evil
7 Dispel Evil
9 Disrupting Weapon
11 Banishment
13 Holy Word
15 Sunburst
17 Undeath's Eternal Foe (SpC)
19 Freedom


Mystery Sphere

Special: You benefit from a constant undetectable alignment effect.

Level, Benefits
1 Disguise Self
3 Silence
5 Blacklight
7 Greater Invisibility
9 Mirage Arcana
11 Forbiddance
13 Screen
15 Mind Blank
17 Etherealness
19 Time Stop


Piety Sphere

Special: If you succeed on a Sense Motive check (opposed by Bluff), you know the target's alignment. If you fail, you cannot make another attempt until you gain another rank of Sense Motive.

Level, Benefits
1 Bless
3 Aid
5 Prayer
7 Lesser Globe of Invulnerability
9 Hallow
11 Heroes' Feast
13 Refuge
15 Holy Aura
17 Gate (Calling version only)
19 Miracle


Restraint Sphere

Special: You gain a +3 bonus on saves against mind-affecting effects.

Level, Benefits
1 Entangle
3 Web
5 Stinking Cloud
7 Black Tentacles
9 Wall of Stone
11 Repulsion
13 Forcecage
15 Prismatic Wall
17 Temporal Stasis
19 Imprisonment


Revelation Sphere

Special: You receive a +2 bonus on all Knowledge checks, and never count as untrained in any Knowledge skill.

Level, Benefits
1 Detect Evil
3 Detect Thoughts
5 Clairaudience/Clairvoyance
7 Divination
9 True Seeing
11 Find the Path
13 Legend Lore
15 Discern Location
17 Foresight
19 Astral Projection


Splendor Sphere

Special: You gain a +2 bonus to Diplomacy, Intimidate, and Sense Motive

Level, Benefits
1 Charm Person
3 Eagle's Splendor
5 Flame Strike
7 Glorious Form (as Monstrous Form in the Dungeonomicon, except the new form appears glorious instead of monstrous)
9 Sympathy
11 Greater Heroism
13 Planar Ally
15 Sunburst
17 Weird
19 Implosion


Vigor Sphere

Special: Whenever you heal someone with a spell-like ability, they recover additional HP equal to your ranks in the Heal skill.

Level, Benefits
1 Cure Light Wounds
3 Shield Other
5 Cure Serious Wounds
7 Death Ward
9 Raise Dead
11 Heal
13 Greater Restoration
15 Greater Spell Immunity
17 Mass Heal
19 True Resurrection 