\featname{\hypertarget{sphere:aegis}{Aegis}}
\textbf{Special:}{You radiate an aura of protection out to 10 feet. All allies in this aura receive a resistance bonus to saves OR a deflection bonus to AC equal to character level / 3, rounding up.}
\textbf{Special Bonus:}{If you upgrade this Sphere to Advanced access, your aura of protection grants a resistance bonus to saves AND a deflection bonus to AC.}
\textbf{Special Bonus:}{If you upgrade this Sphere to Expert access, your aura of protection goes out to Short range instead of 10 feet.}
\sphere
{Mage Armor}
{Resist Energy}
{Protection From Energy}
{Stoneskin}
{Extended Globe of Invulnerability, Lesser}
{Energy Immunity (As Resist Energy, but grants Immunity instead of resistance)}
{Spell Turning}
{Protection from Spells}
{Foresight}
\spherecont{19 Double Extended (lasts for 3 times as long as normal) Mind Blank}

\featname{\hypertarget{sphere:courage}{Courage}}
\textbf{Special:}{You are immune to fear.}
\sphere
{Bless (can be used as a swift action)}
{Heroism}
{Remove Fear}
{Heroes' Feast}
{Righteous Might}
{Greater Heroism}
{Break Enchantment (can be used as a swift action)}
{Freedom}
{Mass Righteous Might*}
\spherecont{Greater Heroism (can be used as an immediate action)}

\featname{\hypertarget{sphere:exorcim}{Exorcism}}
\textbf{Special:}{You gain the ability to turn undead three times per day as a good-aligned cleric of the same level as the class that granted you this sphere. You cannot use these turning attempts to power divine feats.}
\sphere
{Protection from Evil}
{Consecrate}
{Magic Circle against Evil}
{Dispel Evil}
{Disrupting Weapon}
{Banishment}
{Holy Word}
{Sunburst}
{Undeath's Eternal Foe (SpC)}
\spherecont{Freedom}

\featname{\hypertarget{sphere:healing}{Healing}}
\textbf{Special:}{Any spells of the Healing subschool that you cast (including SLAs) have a range of 30ft, unless it would normally be longer.}
\sphere
{Cure Moderate Wounds}
{Lesser Restoration}
{Cure Critical Wounds}
{Mass Cure Critical Wounds}
{Heal}
{Restoration}
{Ressurection}
{Mass Heal}
{Heal (can be used as an immediate action)}
\spherecont{Greater Restoration (can be used as an immediate action)}

\featname{\hypertarget{sphere:judgement}{Judgement}}
\textbf{Special:}{You gain Intimidate as a class skill, and may demoralise an opponent as a swift action.}
\sphere
{Doom}
{Mark of the Outcast [SC]}
{Awaken Sin [SC]}
{Castigate [SC]}
{Sicken Evil [BoED]}
{Wages of Sin [BoED]}
{Tomb of Light [BoED]}
{Last Judgement [BoED]}
{Rain of Black Tulips [BoED]}
\spherecont{Sanctify the Wicked [BoED]}

\featname{\hypertarget{sphere:light}{Light}}
\textbf{Special:}{You shed light like a torch, and can suppress or resume this ability at-will. This ability is considered extraordinary.}
\sphere
{Faerie Fire}
{Searing Light}
{Daylight}
{Sunbeam}
{Sunburst}
{True Seeing}
{Power Word Blind}
{Prismatic Wall}
{Prismatic Sphere}
\spherecont{Sunburst (can be used as an immediate action)}

\featname{\hypertarget{sphere:magic}{Magic}}
\textbf{Special:}{You gain the Scribe Scroll feat. You can treat scrolls as spellbooks.}
\sphere
{Magic Missile}
{Arcane Sight}
{Anyspell}
{Mnemonic Enhancer}
{Lesser Spell Matrix}
{Greater Anyspell}
{Limited Wish}
{Spell Engine}
{Antimagic Field}
\spherecont{Wish}

\featname{\hypertarget{sphere:majesty}{Majesty}}
\textbf{Special:}{You gain Diplomacy as a class skill. Additionally, you may use your Charisma modifier on any skills dependant on Wisdom or Intelligence instead.}
\sphere
{Lantern Light [BoED]}
{Glorious Raiment [BoED]}
{Crown of Flame [BoED]}
{Luminous Armor [BoED]}
{Sicken Evil [BoED]}
{Crown of Brilliance [BoED] }
{Heaven's Trumpet [BoED]}
{Crown of Glory [SC]}
{Blinding Glory [BoED]}
\spherecont{Greater Aspect of the Deity [BoED]}

\featname{\hypertarget{sphere:themartyr}{The Martyr}}
\textbf{Special:}{You never lose experience, levels, or attribute points from death or ressurection.}
\sphere
{Divine Sacrifice [SC]}
{Shield Other}
{Consecrated Masochism [BoVD, Consecrate Spell from BoED]}
{Blood of the Martyr (immediate action) [BoED]}
{Renewal Pact [SC]}
{Karmic Retribution [CM]}
{Tomb of Light [BoED]}
{Phoenix Fire [BoED]}
{Transcend Mortality [CM]}
\spherecont{Exalted Fury [BoED]}

\featname{\hypertarget{sphere:mystery}{Mystery}}
\textbf{Special:}{You benefit from a constant undetectable alignment effect.}
\sphere
{Disguise Self}
{Silence}
{Blacklight}
{Greater Invisibility}
{Mirage Arcana}
{Forbiddance}
{Screen}
{Mind Blank}
{Etherealness}
\spherecont{Time Stop}

\featname{\hypertarget{sphere:prayer}{Prayer}}
\textbf{Special:}{You gain Perform (oratory) as a class skill. Additionally, any spell or SLA with the [Sonic] descriptor that you use has its area of effect doubled.}
\sphere
{Prayer}
{Shout}
{Dismissal}
{Greater Shout}
{Commune}
{Word of Recall}
{Power Word Stun}
{Blasphemy/Holy Word/Dictum/Word of Chaos (choose one when you gain this level, and you cannot choose one of opposite alignment to your own)}
{Wail of the Banshee}
\spherecont{19: Power Word Kill (can be used as a swift action)}

\featname{\hypertarget{sphere:piety}{Piety}}
\textbf{Special:}{If you succeed on a Sense Motive check (opposed by Bluff), you know the target's alignment. If you fail, you cannot make another attempt until you gain another rank of Sense Motive.}
\sphere
{Bless}
{Aid}
{Prayer}
{Lesser Globe of Invulnerability}
{Hallow}
{Heroes' Feast}
{Refuge}
{Holy Aura}
{Gate (Calling version only)}
\spherecont{Miracle}

\featname{\hypertarget{sphere:restraint}{Restraint}}
\textbf{Special:}{You gain a +3 bonus on saves against mind-affecting effects.}
\sphere
{Entangle}
{Web}
{Stinking Cloud}
{Black Tentacles}
{Wall of Stone}
{Repulsion}
{Forcecage}
{Prismatic Wall}
{Temporal Stasis}
\spherecont{Imprisonment}

\featname{\hypertarget{sphere:revelation}{Revelation}}
\textbf{Special:}{You receive a +2 bonus on all Knowledge checks, and never count as untrained in any Knowledge skill.}
\sphere
{Detect Evil}
{Detect Thoughts}
{Clairaudience/Clairvoyance}
{Divination}
{True Seeing}
{Find the Path}
{Legend Lore}
{Discern Location}
{Foresight}
\spherecont{Astral Projection}

\featname{\hypertarget{sphere:splendor}{Splendor}}
\textbf{Special:}{You gain a +2 bonus to Diplomacy, Intimidate, and Sense Motive}
\sphere
{Charm Person}
{Eagle's Splendor}
{Flame Strike}
{Glorious Form (as Monstrous Form in the Dungeonomicon, except the new form appears glorious instead of monstrous)}
{Sympathy}
{Greater Heroism}
{Planar Ally}
{Sunburst}
{Weird}
\spherecont{Implosion}

\featname{\hypertarget{sphere:vigor}{Vigor Sphere}}
\textbf{Special:}{Whenever you heal someone with a spell-like ability, they recover additional HP equal to your ranks in the Heal skill.}
\sphere
{Cure Light Wounds}
{Shield Other}
{Cure Serious Wounds}
{Death Ward}
{Raise Dead}
{Heal}
{Greater Restoration}
{Greater Spell Immunity}
{Mass Heal}
\spherecont{True Resurrection}