\classname{Arcane Archer} \label{comm:prestige:arcanearcher}
\vspace*{-8pt}
\quot{``I kill people with arrows. Special arrows.''}

\desc{The arcane archer isn't, strictly speaking, a hybrid, since in itself it's a pure combat class that just requires multiclassing into a casting class as a prerequisite.  However, it's close enough so that I want to discuss it in this section.}

\desc{Back when the 3.0 DMG was released, arcane archer wasn't playable, since it was still a full BAB class, which meant it didn't have any abilities anyone cared about.  However, it was less unplayable than it is now, because it received two huge nerfs in 3.5: \spell{greater magic weapon} came into the core and arrow and bow enhancements changed so they no longer stacked with each other.  As it stands, a core 3rd-level spell replaces most of the class's features, another spell (\spell{arrow storm}) duplicates hail of arrows and is available much earlier with less investment, arrow of death isn't even remotely level-appropriate (a DC 20 Fort save at 17th level?  Please.), and phase and seeker arrow do far too little damage to be relevant.  The only mildly interesting ability is imbue arrow, since it opens up the possibility of firing AMFs at your enemies from miles away, but because of the PrC's prerequisites and the required two levels of lost casting, it's also all but useless.}

\ability{Prerequisites:}{}
\listprereq
	\itemability{BAB:}{+3}
	\itemability{Race:}{Elf or half-elf}
	\itemability{Feats:}{Point Blank Shot}
	\itemability{Proficiencies:}{Proficient with the longbow, the shortbow, or a similar weapon}
	\itemability{Spells:}{Ability to cast \spell{greater magic weapon} and \spell{true strike} as arcane spells.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Arcane Archer's class skills (and the key ability for each skill) are Balance (Dex), Concentration (Con), Craft (Int), Handle Animal (Cha), Hide (Dex), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{5cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+1&+0&+2&+2&Imbue Arrow, Magic Arrows&--\\
2&+2&+0&+3&+3&Enhanced Arrows, \spell{Hawkeye}&+1 spellcasting level\\
3&+3&+1&+3&+3&Enduring Spells, \spell{Hunter's Mercy}&+1 spellcasting level\\
4&+4&+1&+4&+4&Hunter&+1 spellcasting level\\
5&+5&+1&+4&+4&True Shot&+1 spellcasting level\\
6&+6&+2&+5&+5&\spell{Arrow Storm}&+1 spellcasting level\\
7&+7&+2&+5&+5&Prepare Arrow&+1 spellcasting level\\
8&+8&+2&+6&+6&Swift Enhancement&+1 spellcasting level\\
9&+9&+3&+6&+6&Sniper&+1 spellcasting level\\
10&+10&+3&+7&+7&Martial Mage&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the Arcane Archer prestige class.

\ability{Weapon and Armor Proficiency:}{Arcane archers gain no new proficiency with any weapon or armor.}

\ability{Spellcasting:}{At every level except 1st, an arcane archer casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in an arcane spellcasting class she had previous to gaining that level.}

\ability{Imbue Arrow (Su):}{An arcane archer can cast an area, touch, ray, targeted, or effect (that affects an area) spell into an arrow as she fires it, with a single standard action.  If it's an area or effect spell, it takes effect where the arrow lands, even if the spell could normally only be centered on the caster.  If it's a targeted, ray, or touch spell, if the arrow hits its target (with a normal attack roll), the spell affects that target as normal, offering spell resistance and a saving throw or throws as usual.  Any spell she imbues into an arrow gets +1 to its saving throw DCs and +2 bonus to penetrate spell resistance.}

\ability{Magic Arrows (Su):}{Any arrow an arcane archer fires has an enhancement bonus equal to one-third her character level, to a maximum of +5 before 21st level.}

\ability{Enhanced Arrows (Su):}{Starting at 2nd level, any arrow an arcane archer fires gains a special ability or abilities: she selects any ability or combination of abilities from the following list that sum to one-third her highest arcane caster level.  She can change which ability her arrows gain as a move-equivalent action; beginning at 8th level, she can change abilities as a swift action.

Example: General Ielenia, an elf wizard 2/arcane archer 8, is leading the elves against a goblin army, so before the armies meet, she selects goblinoidbane and superior seeking for her enhanced arrows ability.  However, during the battle she discovers that the goblins have hired some ogre mercenaries led by an ogre mage, so she takes a move-equivalent action to switch her arrows to giantbane and flaming burst.
\begin{itemize}
 \item{Bane +1}
 \item{Flaming +1}
 \item{Freezing +1}
 \item{Ghost Touch +1}
 \item{Magebane (Complete Arcane) +1}
 \item{Merciful +1}
 \item{Seeking +1}
 \item{Shocking +1}
 \item{Thundering +1}
 \item{Flaming Burst +2}
 \item{Icy Burst +2}
 \item{Shocking Burst +2}
 \item{Wounding +2}
 \item{Superior Seeking +2}
 \item{Explosive (Complete Warrior) +3}
 \item{Phasing +3}
 \item{Brilliant Energy +4}
\end{itemize}

\textit{Superior Seeking:} A superior seeking arrow flies unerringly to its target, even going around corners, but the arcane archer must know that an enemy is in a square; the arrow negates any miss chances from concealment or cover.  Her attack is rolled as normal. \smallskip

\textit{Phasing:} A phasing arrow goes ethereal and only returns to material existence as it's about to strike its target.  Thus, it can pass through solid objects and even spells (but not force effects) on the way to its target, though the arcane archer must still target the right square.  Her attack is rolled as normal.}

\ability{\spell{Hawkeye}:}{At 2nd level, an archer archer who prepares spells adds \spell{hawkeye} (Spell Compendium) to her spellbook for free, and may lose a prepared spell to cast it like a cleric casting a \spell{cure} spell.  An arcane archer who casts spontaneously adds it to her spells known for free.}

\ability{Enduring Spells (Su):}{Starting at 3rd level, all of an arcane archer's arcane spells have their durations doubled, as if she had applied the Extend Spell metamagic feat to them.  This does not change their level or casting time.  If she has the Extend Spell metamagic feat, she can apply it to triple their durations.}

\ability{\spell{Hunter's Mercy}:}{At 3rd level, an archer archer who prepares spells adds \spell{hunter's mercy} (Spell Compendium) to her spellbook for free, and may lose a prepared spell to cast it like a cleric casting a \spell{cure} spell.  An arcane archer who casts spontaneously adds it to her spells known for free.}

\ability{Hunter:}{At 4th level, an arcane archer gains Hunter as a bonus feat.  If she already has it, she may select any Combat or metamagic feat she meets the prerequisites for as a bonus feat instead.}

\ability{\spell{Arrow Storm}:}{At 5th level, an archer archer who prepares spells adds \spell{arrow storm} (Spell Compendium) to her spellbook for free, and may lose a prepared spell to cast it like a cleric casting a \spell{cure} spell.  An arcane archer who casts spontaneously adds it to her spells known for free.}

\ability{True Shot (Su):}{Beginning at 5th level, an arcane archer able to cast \spell{true strike} (either has it prepared, or knows it and has an appropriate unused spell slot) can cast the spell and fire an arrow that benefits from it as a single standard action.  If she prepares spells, she may lose a prepared spell to cast \spell{true strike} like a cleric casting a \spell{cure} spell.}

\ability{Prepare Arrow:}{Beginning at 7th level, as a standard action, an arcane archer can place a spell into an arrow as if using imbue, and the arrow holds the spell until it's fired.  She may only have one such arrow prepared at a time.}

\ability{Sniper:}{At 9th level, an arcane archer gains Sniper as a bonus feat.  If she already has it, she may select any Combat or metamagic feat she meets the prerequisites for as a bonus feat instead.}

\ability{Martial Mage (Ex):}{Beginning at 10th level, an arcane archer's Base Attack Bonus is equal to her highest arcane caster level, regardless of what class levels she has, but can't in any event be greater than her Hit Dice.}
