\classname{Golem-Knight of Mechanus} \label{comm:prestige:golemknight}
\vspace*{-8pt}
\quot{``GIGA-KNIGHT! GIGA-KNIGHT!''}

\ability{Requirements:}{}
\listprereq
\itemability{BAB:}{+7}
\itemability{Skills:}{Knowledge (engineering) 10 ranks}
\itemability{Special:}{Must have spent time learning the art of construction in Mechanus. A Knight who is of an appropriate Order need not possess the ranks in Knowledge (engineering) or spend time learning in Mechanus.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d12}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skill Points at Each Level:}{6 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+0 &+0 &Craft Mechanus Armor, Amplifiers\\
2nd &+2 &+3 &+0 &+0 &Mechanus Mount, Rocket Lance\\
3rd &+3 &+3 &+1 &+1 &Artificer's Secret Weapon, Fuel Lines\\
4th &+4 &+4 &+1 &+1 &Craft Grenades, Boomstick\\
5th &+5 &+4 &+1 &+1 &Golem Body, Craft Servo-Arm\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Golem Knight prestige class.

\ability{Weapon and Armor Proficiency:}{The Golem Knight is considered proficient with any weapon she personally crafts.}

\ability{Craft Mechanus armor:}{The Golem Knight can, given about a day and enough scrap materials, construct a suit of Mechanus Armor. This is extra heavy Adamantine Full Plate that has an Enhancement bonus equal to one quarter of the Knight's character level. However, it only gains this effect when worn by the Knight who crafted it.

Additionally, the wearer gains all Construct traits (but ability scores remain unchanged), along with the ability to add the armor's Enhancement bonus to all Break attempts and damage rolls.}

\ability{Amplifiers:}{The Golem Knight has a booming voice that can carry on for miles. Additionally, they may cast Command at will as an Extraordinary ability.}

\ability{Mechanus Mount:}{The Golem Knight may, given enough scrap material and about a day, craft a mighty steed that looks like a warhorse with too many layers of plate barding. This counts as a Cauchemar Nightmare of the Construct type (ability scores are unchanged) and no actual alignment. It loses its Spell-like abilities (but retains the smoke, breath weapon and fire damage) and Subtypes, and has hit dice equal to the Knight's character level.

It possesses a Natural armor bonus of +0 but an armor bonus equal to its hit dice and an Enhancement bonus to Strength and AC equal to the class level of the Golem Knight. It is completely loyal to the Golem Knight, but when not being ridden, it stands motionless, unable to act.

It can be crafted to any size that the Golem Knight could ride, and the Knight can see through its Smoke.}

\ability{Rocket Lance:}{The Golem Knight may, with an hour of work, modify a lance to be fired as though from a cannon. It can be used as a ranged weapon with range increments of 15' and counts as charging when fired. It still adds the Strength modifier of the Knight to damage, but does not multiply the Strength by one and a half.}

\ability{Artificer's Secret Weapon:}{With a day of hard work, the Golem Knight can craft special weapons. They are treated as though magical (with a Greater Magic Weapon effect), though may trade the bonuses out for special abilities. However, they are in no way magical and thus function normally in an AMF and cannot be disjoined. They still bypass DR/magic and can strike incorporeal targets.}

\ability{Fuel Lines:}{Special fuel pipes can be built into the Mechanus armor with a whole hour of work. This allows the Golem Knight to drink any potion they have as a Swift Action.}

\ability{Craft Grenades:}{With an hour and some random materials, the Golem Knight may craft 1d4+1 special grenades. Sadly, they are unstable and will be unusable after 24 hours. Until then, they may be thrown as grenade weapons (duh), exploding in a 30' radius. The save DC is 10 + half the Knight's HD + their Int modifier. The Golem Knight may choose the effects upon creation:

\listone
    \item Incendiary: all in the area take 1d6 Fire damage per character level of the Golem Knight. A successful Ref save halves this damage, but those who fail the save catch fire.
    \item Frost Cloud: all in the area take 1d6 Cold damage per character level of the Golem Knight and are Slowed for 1 round. A successful Fort save halves the damage and negates the Slow effect.
    \item Flash Bang: all in the area are Blinded and Deafened for 1d4 rounds on a failed Ref save.
    \item Concussion: all in the area are knocked prone automatically, and Dazed for 1 round on a failed Fort save.
    \item Electro Pulse: all in the area take 1d6 Electricity damage per character level of the Golem Knight. A successful Ref save halves this, but those who fail the save count as Entangled for 1 round as their limbs spasm.
    \item Sleep Gas: all in the area become drowsy for 2 rounds on a failed Fort save. Drowsy characters count as Fatigued and take a -6 penalty on saves against Sleep effects.
    \item Corrosive Gas: all in the area take 1d6 Acid damage per character level of the Golem Knight. A Ref save halves this. Those who fail the save take damage equal to the Golem Knight's character level on the following round.
    \item Disruption Pulse: all Constructs and Undead in the area take 1d8 untyped damage per character level of the Golem Knight. A Fort save halves this, and they are not immune to this effect.
\end{list}
\vspace{6pt}

Grenades are not magical.}

\ability{Boomstick:}{With half a day of work, the Golem Knight can craft a double-barrelled shotgun of sorts. Firing this two-handed weapon is an Attack action and it takes a Partial Action to reload (Swift with Rapid Reload or Sleight of Hand 10 ranks, Free with both of the above), but can fire twice before needing to be reloaded. 1d6+1 rounds can be crafted with an hour of work.

\listone
    \item Solid Shot: 40' range increments, 3d6 Bludgeoning damage, critical 20/x4.
    \item Scatter Shot: 40' cone, 3d6 Bludgeoning damage, Ref half (same DC as grenades). Those who fail are knocked Prone.
    \item Incendiary: 40' cone, 2d6 Fire damage, Ref half. Those who fail catch fire.
    \item Flash-Bang Powder: 40' cone, all in the area are Blinded and Deafened for 1 round, Ref negates.
    \item Explosive Shells: 20' range increments, 1d10 bludgeoning damage and 3d6 Fire damage, sets the target on fire. Crit 20/x3 (only multiplies the Bludgeoning damage).
    \item Meltdown Shells: 20' range increments, 1d10 bludgeoning damage and 3d6 Acid damage, with 2d6 Acid damage the following round. Crit 20/x3 (only multiplies the Bludgeoning damage).
    \item Executioner Seeker Rounds: creates a non-magical Magic Missile (try not to think too hard about it) effect with a CL equal to the class level of the Golem Knight.
\end{list}
\vspace{6pt}

This weapon is not magical.}

\ability{Golem Body:}{With a week of work and enough materials, the Golem Knight may construct their very own actual golem body. This can be a giant chunk of baked clay that looks like a few rocks stacked together, or it could be an intricate suit of many plates of armor. Whatever. It takes a whole hour to don this "body", or to escape it, but when worn, the following benefits are gained, in addition to those that would be gained if the Knight was wearing their Mechanus armor (they can't wear armor while wearing this):
\newline Size: 1 category larger (you may wish to construct a bigger horse)
\newline Ability Scores: +8 Strength, -4 Dexterity, +4 Constitution
\newline Speed: Remains the same
\newline Reach: Extends by 5'
\newline Armor: As the Mechanus armor +5
\newline Attacks: May wield weapons, or gains 2 slams (2d6+Str for a Large creature). \newline May also use a Bite attack (3d6+\half Str for a Large creature).
\newline Special:
\listone
    \item Trample (4d6 for a Large creature)
    \item Improved Grab
    \item Spell Resistance equal to 10 + hit dice
    \item Furnace Blast (Ex): 50' breath weapon deals 2d6 Fire damage per hit die, Ref half (Con-based). Can be used once per minute, and those who fail the save catch fire. May instead be focused on a character hit by a Bite attack, as a Swift action. This hits automatically as though they had failed the save, but no-one else is affected.
\end{list}
\smallskip

This ``armor'' is not magical.}

\ability{Craft Servo Arm:}{The Golem Knight may, with a day's work, craft an additional arm to connect to a mount, Mechanus armor, or the Golem Body. This arm reaches out to 10' further than the subject normally could, and can manipulate objects like a Telekinesis spell (CL = HD), or may be used to attack foes like a Bigby's Crushing Fist spell (CL = HD). It also has a form of blow-torch and saw added, which helps it assist the Knight in creating items (halving the time), but also is very unfortunate for those grappled by the arm. They take an additional 2d6 Adamantine Slashing damage and 5d6 Fire damage per round.
\smallskip
The Servo Arm is also not magical.}
