%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Prestige Classes}\label{chapter:Prestige Classes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Prestige classes offer a new form of multiclassing. Unlike the basic classes, characters must meet Requirements before they can take their first level of a prestige class. The rules for level advancement apply to this system, meaning the first step of advancement is always choosing a class. If a character does not meet the Requirements for a prestige class before that first step, that character cannot take the first level of that prestige class.  Taking a prestige class does not incur the experience point penalties normally associated with multiclassing.

%%%
\subsubsection{Definitions of Terms}
%%%

Here are definitions of some terms used in this section.

\textbf{\gameterm{Base Class}:} One of the standard eleven classes.

\textbf{\gameterm{Caster Level}:} Generally equal to the number of class levels (see below) in a spellcasting class. Some prestige classes add caster levels to an existing class.

\textbf{\gameterm{Character Level}:} The total level of the character, which is the sum of all class levels held by that character.

\textbf{\gameterm{Class Level}:} The level of a character in a particular class. For a character with levels in only one class, class level and character level are the same.

\input{classes-prestige/arcane-archer}
\clearpage
\input{classes-prestige/arcane-trickster}
\input{classes-prestige/archmage}
\input{classes-prestige/assassin}
\input{classes-prestige/blackguard}
\input{classes-prestige/dragon-disciple}
\input{classes-prestige/duelist}
\input{classes-prestige/dwarven-defender}
\input{classes-prestige/eldritch-knight}
\input{classes-prestige/hierophant}
\input{classes-prestige/horizon-walker}
\input{classes-prestige/loremaster}
\input{classes-prestige/mystic-theurge}
\input{classes-prestige/shadowdancer}
\input{classes-prestige/thaumaturgist}
