%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Casting Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Whether a spell is arcane or divine, and whether a character prepares spells in 
advance or chooses them on the spot, casting a spell works the same way.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choosing A Spell}
%%%%%%%%%%%%%%%%%%%%%%%%%

First you must choose which spell to cast. If you're a \linkclass{Cleric}, \linkclass{Druid}, experienced 
\linkclass{Paladin}, experienced \linkclass{Ranger}, or \linkclass{Wizard}, you select from among spells prepared earlier 
in the day and not yet cast (see \linksec{Preparing Wizard Spells} and \linksec{Preparing Divine Spells}).

If you're a bard or sorcerer, you can select any spell you know, provided you are 
capable of casting spells of that level or higher.

To cast a spell, you must be able to speak (if the spell has a verbal component), 
gesture (if it has a somatic component), and manipulate the material components 
or focus (if any). Additionally, you must concentrate to cast a spell.

If a spell has multiple versions, you choose which version to use when you cast 
it. You don't have to prepare (or learn, in the case of a bard or sorcerer) a specific 
version of the spell.

Once you've cast a prepared spell, you can't cast it again until you prepare it 
again. (If you've prepared multiple copies of a single spell, you can cast each 
copy once.) If you're a bard or sorcerer, casting a spell counts against your daily 
limit for spells of that spell level, but you can cast the same spell again if 
you haven't reached your limit.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Concentration}
%%%%%%%%%%%%%%%%%%%%%%%%%

To cast a spell, you must concentrate. If something interrupts your concentration 
while you're casting, you must make a \linkskill{Concentration} check or lose the spell. The 
more distracting the interruption and the higher the level of the spell you are 
trying to cast, the higher the DC is. If you fail the check, you lose the spell 
just as if you had cast it to no effect.

\textbf{Injury:} If while trying to cast a spell you take damage, you must make 
a Concentration check (DC 10 + points of damage taken + the level of the spell 
you're casting). If you fail the check, you lose the spell without effect. The 
interrupting event strikes during spellcasting if it comes between when you start 
and when you complete a spell (for a spell with a casting time of 1 full round 
or more) or if it comes in response to your casting the spell (such as an attack 
of opportunity provoked by the spell or a contingent attack, such as a readied 
action).

If you are taking continuous damage half the damage is considered to take place 
while you are casting a spell. You must make a Concentration check (DC 10 + 1/2 
the damage that the continuous source last dealt + the level of the spell you're 
casting). If the last damage dealt was the last damage that the effect could deal 
then the damage is over, and it does not distract you.

Repeated damage does not count as continuous damage.

\textbf{Spell:} If you are affected by a spell while attempting to cast a spell 
of your own, you must make a Concentration check or lose the spell you are casting. 
If the spell affecting you deals damage, the DC is 10 + points of damage + the 
level of the spell you're casting.

If the spell interferes with you or distracts you in some other way, the DC is 
the spell's saving throw DC + the level of the spell you're casting. For a spell 
with no saving throw, it's the DC that the spell's saving throw would have if a 
save were allowed.

\textbf{Grappling or Pinned:} The only spells you can cast while grappling or pinned 
are those without somatic components and whose material components (if any) you 
have in hand. Even so, you must make a Concentration check (DC 20 + the level of 
the spell you're casting) or lose the spell.

\textbf{Vigorous Motion:} If you are riding on a moving mount, taking a bouncy 
ride in a wagon, on a small boat in rough water, below-decks in a storm-tossed 
ship, or simply being jostled in a similar fashion, you must make a Concentration 
check (DC 10 + the level of the spell you're casting) or lose the spell. 

\textbf{Violent Motion:} If you are on a galloping horse, taking a very rough ride 
in a wagon, on a small boat in rapids or in a storm, on deck in a storm-tossed 
ship, or being tossed roughly about in a similar fashion, you must make a Concentration 
check (DC 15 + the level of the spell you're casting) or lose the spell.

\textbf{Violent Weather:} You must make a Concentration check if you try to cast 
a spell in violent weather. If you are in a high wind carrying blinding rain or 
sleet, the DC is 5 + the level of the spell you're casting. If you are in wind-driven 
hail, dust, or debris, the DC is 10 + the level of the spell you're casting. In 
either case, you lose the spell if you fail the Concentration check. If the weather 
is caused by a spell, use the rules in the Spell subsection above.

\textbf{Casting Defensively:} If you want to cast a spell without provoking any 
attacks of opportunity, you must make a Concentration check (DC 15 + the level 
of the spell you're casting) to succeed. You lose the spell if you fail.

\textbf{Entangled:} If you want to cast a spell while entangled in a net or by 
a tanglefoot bag or while you're affected by a spell with similar effects, you 
must make a DC 15 Concentration check to cast the spell. You lose the spell if 
you fail.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Counterspells}\index{Counterspelling}
%%%%%%%%%%%%%%%%%%%%%%%%%

It is possible to cast any spell as a counterspell. By doing so, you are using 
the spell's energy to disrupt the casting of the same spell by another character. 
Counterspelling works even if one spell is divine and the other arcane.

\textbf{How Counterspells Work:} To use a counterspell, you must select an opponent 
as the target of the counterspell. You do this by choosing the ready action. In 
doing so, you elect to wait to complete your action until your opponent tries to 
cast a spell. (You may still move your speed, since ready is a standard action.)

If the target of your counterspell tries to cast a spell, make a \linkskill{Spellcraft} check 
(DC 15 + the spell's level). This check is a free action. If the check succeeds, 
you correctly identify the opponent's spell and can attempt to counter it. If the 
check fails, you can't do either of these things.

To complete the action, you must then cast the correct spell. As a general rule, 
a spell can only counter itself. If you are able to cast the same spell and you 
have it prepared (if you prepare spells), you cast it, altering it slightly to 
create a counterspell effect. If the target is within range, both spells automatically 
negate each other with no other results.

\textbf{Counterspelling Metamagic Spells:} Metamagic feats are not taken into account 
when determining whether a spell can be countered

\textbf{Specific Exceptions:} Some spells specifically counter each other, especially 
when they have diametrically opposed effects.

\textbf{Dispel Magic as a Counterspell:} You can use \linkspell{Dispel Magic}
to counterspell another spellcaster, and you don't need to identify the 
spell he or she is casting. However, \textit{Dispel Magic} doesn't always work 
as a counterspell (see the spell description).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Caster Level}
%%%%%%%%%%%%%%%%%%%%%%%%%

A spell's power often depends on its caster level, which for most spellcasting 
characters is equal to your class level in the class you're using to cast the spell. 

You can cast a spell at a lower caster level than normal, but the caster level 
you choose must be high enough for you to cast the spell in question, and all level-dependent 
features must be based on the same caster level. 

In the event that a class feature, domain granted power, or other special ability 
provides an adjustment to your caster level, that adjustment applies not only to 
effects based on caster level (such as range, duration, and damage dealt) but also 
to your caster level check to overcome your target's spell resistance and to the 
caster level used in dispel checks (both the dispel check and the DC of the check). 

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spell Failure}\index{Spell Failure}
%%%%%%%%%%%%%%%%%%%%%%%%%

If you ever try to cast a spell in conditions where the characteristics of the 
spell cannot be made to conform, the casting fails and the spell is wasted.

Spells also fail if your concentration is broken and might fail if you're wearing 
armor while casting a spell with somatic components.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Spell's Result}
%%%%%%%%%%%%%%%%%%%%%%%%%

Once you know which creatures (or objects or areas) are affected, and whether those 
creatures have made successful saving throws (if any were allowed), you can apply 
whatever results a spell entails.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Special Spell Effects}
%%%%%%%%%%%%%%%%%%%%%%%%%

Many special spell effects are handled according to the school of the spells in 
question Certain other special spell features are found across spell schools.

\textbf{Attacks:} Some spell descriptions refer to attacking. All offensive combat 
actions, even those that don't damage opponents are considered attacks. Attempts 
to turn or rebuke undead count as attacks. All spells that opponents resist with 
saving throws, that deal damage, or that otherwise harm or hamper subjects are 
attacks. Spells that summon monsters or other allies are not attacks because the 
spells themselves don't harm anyone.

\textbf{Bonus Types:}\index{Bonus Types} Usually, a bonus has a type that indicates how the spell 
grants the bonus. The important aspect of bonus types is that two bonuses of the 
same type don't generally stack. With the exception of dodge bonuses, most circumstance 
bonuses, and racial bonuses, only the better bonus works (see \linksec{Combining Magical Effects},
below). The same principle applies to penalties -- a character taking two 
or more penalties of the same type applies only the worst one.

\textbf{\gameterm{Bringing Back the Dead}:} Several spells have the power to restore slain 
characters to life.

When a living creature dies, its soul departs its body, leaves the Material Plane, 
travels through the Astral Plane, and goes to abide on the plane where the creature's 
deity resides. If the creature did not worship a deity, its soul departs to the 
plane corresponding to its alignment. Bringing someone back from the dead means 
retrieving his or her soul and returning it to his or her body.

\textit{Level Loss:} Any creature brought back to life usually loses one level 
of experience. The character's new XP total is midway between the minimum needed 
for his or her new (reduced) level and the minimum needed for the next one. If 
the character was 1st level at the time of death, he or she loses 2 points of Constitution 
instead of losing a level.

This level loss or Constitution loss cannot be repaired by any mortal means, even 
\linkspell{Wish} or \linkspell{Miracle}. A revived character can regain a lost level 
by earning XP through further adventuring. A revived character who was 1st level 
at the time of death can regain lost points of Constitution by improving his or 
her Constitution score when he or she attains a level that allows an ability score 
increase.

\textit{Preventing Revivification:} Enemies can take steps to make it more difficult 
for a character to be returned from the dead. Keeping the body prevents others 
from using \linkspell{Raise Dead} or \linkspell{Resurrection} to restore the slain character 
to life. Casting \linkspell{Trap the Soul} prevents any sort of revivification unless 
the soul is first released.

\textit{Revivification against One's Will:} A soul cannot be returned to life if 
it does not wish to be. A soul knows the name, alignment, and patron deity (if 
any) of the character attempting to revive it and may refuse to return on that 
basis.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Combining Magical Effects}
%%%%%%%%%%%%%%%%%%%%%%%%%

Spells or magical effects usually work as described, no matter how many other spells 
or magical effects happen to be operating in the same area or on the same recipient. 
Except in special cases, a spell does not affect the way another spell operates. 
Whenever a spell has a specific effect on other spells, the spell description explains 
that effect. Several other general rules apply when spells or magical effects operate 
in the same place:

\textbf{Stacking Effects:} Spells that provide bonuses or penalties on attack rolls, 
damage rolls, saving throws, and other attributes usually do not stack with themselves. 
More generally, two bonuses of the same type don't stack even if they come from 
different spells (or from effects other than spells; see \linksec{Special Spell Effects}{Bonus Types}, above). 

\textit{Different Bonus Names:} The bonuses or penalties from two different spells 
stack if the modifiers are of different types. A bonus that isn't named stacks 
with any bonus.

\textit{Same Effect More than Once in Different Strengths:} In cases when two or 
more identical spells are operating in the same area or on the same target, but 
at different strengths, only the best one applies.

\textit{Same Effect with Differing Results:} The same spell can sometimes produce 
varying effects if applied to the same recipient more than once. Usually the last 
spell in the series trumps the others. None of the previous spells are actually 
removed or dispelled, but their effects become irrelevant while the final spell 
in the series lasts.

\textit{One Effect Makes Another Irrelevant:} Sometimes, one spell can render a 
later spell irrelevant. Both spells are still active, but one has rendered the 
other useless in some fashion.

\textit{Multiple Mental Control Effects:} Sometimes magical effects that establish 
mental control render each other irrelevant, such as a spell that removes the subjects 
ability to act. Mental controls that don't remove the recipient's ability to act 
usually do not interfere with each other. If a creature is under the mental control 
of two or more creatures, it tends to obey each to the best of its ability, and 
to the extent of the control each effect allows. If the controlled creature receives 
conflicting orders simultaneously, the competing controllers must make opposed 
Charisma checks to determine which one the creature obeys.

\textbf{Spells with Opposite Effects:} Spells with opposite effects apply normally, 
with all bonuses, penalties, or changes accruing in the order that they apply. 
Some spells negate or counter each other. This is a special effect that is noted 
in a spell's description. 

\textbf{Instantaneous Effects:} Two or more spells with instantaneous durations 
work cumulatively when they affect the same target.
