%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spell Lists}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An \textsuperscript{M} or \textsuperscript{F} appearing 
at the end of a spell's name in the spell lists denotes a spell with a material 
or focus component, respectively, that is not normally included in a spell component 
pouch. An \textsuperscript{X} denotes a spell with an XP component 
paid by the caster.

\textbf{Order of Presentation:} In the spell lists and the spell descriptions that 
follow them, the spells are presented in alphabetical order by name except for 
those belonging to certain spell chains.

When a spell's name begins with "lesser", "greater", or "mass", the spell 
description is alphabetized under the second word of the spell name instead.

\textbf{Hit Dice:} The term "Hit Dice" is used synonymously with "character 
levels" for effects that affect a number of Hit Dice of creatures. Creatures with 
Hit Dice only from their race, not from classes, have character levels equal to 
their Hit Dice.

\textbf{Caster Level:} A spell's power often depends on caster level, which is 
defined as the caster's class level for the purpose of casting a particular spell. 
A creature with no classes has a caster level equal to its Hit Dice unless otherwise 
specified. The word "level" in the spell lists that follow always refers to caster 
level.

\textbf{Creatures and Characters:} The words "creature" and "character" are 
used synonymously in the spell descriptions.


%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bard Spells}\index{Bard Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{0th Level Bard Spells (Cantrips)}
%%%

\linkspell{Dancing Lights}: Creates torches or other lights.

\linkspell{Daze}: Humanoid creature of 4 HD or less loses next action.

\linkspell{Detect Magic}: Detects spells and magic items within 60 ft.

\linkspell{Flare}: Dazzles one creature (-1 on attack rolls).

\linkspell{Ghost Sound}: Figment sounds.

\linkspell{Know Direction}: You discern north.

\linkspell{Light}: Object shines like a torch.

\linkspell{Lullaby}: Makes subject drowsy; -5 on Spot and Listen checks, -2 on Will saves against \linkspell{Sleep}.

\linkspell{Mage Hand}: 5-pound telekinesis.

\linkspell{Mending}: Makes minor repairs on an object.

\linkspell{Message}: Whispered conversation at distance.

\linkspell{Open/Close}: Opens or closes small or light things.

\linkspell{Prestidigitation}: Performs minor tricks.

\linkspell{Read Magic}: Read scrolls and spellbooks.

\linkspell{Resistance}: Subject gains +1 on saving throws.

\linkspell{Summon Instrument}: Summons one instrument of the caster's choice.

%%%
\subsubsection{1st Level Bard Spells}
%%%

\linkspell{Alarm}: Wards an area for 2 hours/level.

\linkspell{Animate Rope}: Makes a rope move at your command.

\linkspell{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\linkspell{Charm Person}: Makes one person your friend.

\linkspell{Comprehend Languages}: You understand all spoken and written languages.

\linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\linkspell{Detect Secret Doors}: Reveals hidden doors within 60 ft.

\linkspell{Disguise Self}: Changes your appearance.

\linkspell{Erase}: Mundane or magical writing vanishes.

\linkspell{Expeditious Retreat}: Your speed increases by 30 ft.

\linkspell{Feather Fall}: Objects or creatures fall slowly.

\linkspell{Grease}: Makes 10-ft. square or one object slippery.

\linkspell{Hideous Laughter}: Subject loses actions for 1 round/ level.

\linkspell{Hypnotism}: Fascinates 2d4 HD of creatures.

\linkspell{Identify}\textsuperscript{M}: Determines properties of magic item.

\linkspell{Lesser Confusion}: One creature is \linksec{Confused} for 1 round.

\linkspell{Magic Mouth}\textsuperscript{M}: Speaks once when triggered.

\linkspell{Magic Aura}: Alters object's magic aura.

\linkspell{Obscure Object}: Masks object against scrying.

\linkspell{Remove Fear}: Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.

\linkspell{Silent Image}: Creates minor illusion of your design.

\linkspell{Sleep}: Puts 4 HD of creatures into magical slumber.

\linkspell{Summon Monster I}: Calls extraplanar creature to fight for you.

\linkspell{Undetectable Alignment}: Conceals alignment for 24 hours.

\linkspell{Unseen Servant}: Invisible force obeys your commands.

\linkspell{Ventriloquism}: Throws voice for 1 min./level.

%%%
\subsubsection{2nd Level Bard Spells}
%%%

\linkspell{Alter Self}: Assume form of a similar creature.

\linkspell{Animal Messenger}: Sends a Tiny animal to a specific place.

\linkspell{Animal Trance}: Fascinates 2d6 HD of animals.

\linkspell{Blindness/Deafness}: Makes subject blind or deaf.

\linkspell{Blur}: Attacks miss subject 20\% of the time.

\linkspell{Calm Emotions}: Calms creatures, negating emotion effects.

\linkspell{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\linkspell{Darkness}: 20-ft. radius of supernatural shadow.

\linkspell{Daze Monster}: Living creature of 6 HD or less loses next action.

\linkspell{Delay Poison}: Stops poison from harming subject for 1 hour/ level.

\linkspell{Detect Thoughts}: Allows "listening" to surface thoughts.

\linkspell{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\linkspell{Enthrall}: Captivates all within 100 ft. + 10 ft./level.

\linkspell{Fox's Cunning}: Subject gains +4 to Int for 1 min./level.

\linkspell{Glitterdust}: Blinds creatures, outlines invisible creatures.

\linkspell{Heroism}: Gives +2 on attack rolls, saves, skill checks.

\linkspell{Hold Person}: Paralyzes one humanoid for 1 round/level.

\linkspell{Hypnotic Pattern}: Fascinates (2d4 + level) HD of creatures.

\linkspell{Invisibility}: Subject is invisible for 1 min./level or until it attacks.

\linkspell{Locate Object}: Senses direction toward object (specific or type).

\linkspell{Minor Image}: As \linkspell{Silent Image}, plus some sound.

\linkspell{Mirror Image}: Creates decoy duplicates of you (1d4 +1 per three levels, max 8).

\linkspell{Misdirection}: Misleads divinations for one creature or object.

\linkspell{Pyrotechnics}: Turns fire into blinding light or choking smoke.

\linkspell{Rage}: Gives +2 to Str and Con, +1 on Will saves, -2 to AC.

\linkspell{Scare}: Panics creatures of less than 6 HD.

\linkspell{Shatter}: Sonic vibration damages objects or crystalline creatures.

\linkspell{Silence}: Negates sound in 20-ft. radius.

\linkspell{Sound Burst}: Deals 1d8 sonic damage to subjects; may stun them.

\linkspell{Suggestion}: Compels subject to follow stated course of action.

\linkspell{Summon Monster II}: Calls extraplanar creature to fight for you.

\linkspell{Summon Swarm}: Summons swarm of bats, rats, or spiders.

\linkspell{Tongues}: Speak any language.

\linkspell{Whispering Wind}: Sends a short message 1 mile/level.

%%%
\subsubsection{3rd Level Bard Spells}
%%%

\linkspell{Blink}: You randomly vanish and reappear for 1 round/level.

\linkspell{Charm Monster}: Makes monster believe it is your ally.

\linkspell{Clairaudience/Clairvoyance}: Hear or see at a distance for 1 min./level.

\linkspell{Confusion}: Subjects behave oddly for 1 round/level.

\linkspell{Crushing Despair}: Subjects take -2 on attack rolls, damage rolls, saves, and checks.

\linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\linkspell{Daylight}: 60-ft. radius of bright light.

\linkspell{Deep Slumber}: Puts 10 HD of creatures to sleep.

\linkspell{Dispel Magic}: Cancels magical spells and effects.

\linkspell{Displacement}: Attacks miss subject 50\%.

\linkspell{Fear}: Subjects within cone flee for 1 round/level.

\linkspell{Gaseous Form}: Subject becomes insubstantial and can fly slowly.

\linkspell{Glibness}: You gain +30 bonus on Bluff checks, and your lies can escape magical discernment.

\linkspell{Good Hope}: Subjects gain +2 on attack rolls, damage rolls, saves, and checks.

\linkspell{Haste}: One creature/level moves faster, +1 on attack rolls, AC, and Reflex saves.

\linkspell{Illusory Script}\textsuperscript{M}: Only intended reader can decipher.

\linkspell{Invisibility Sphere}: Makes everyone within 10 ft. invisible.

\linkspell{Lesser Geas}: Commands subject of 7 HD or less.

\linkspell{Major Image}: As \linkspell{Silent Image}, plus sound, smell and thermal effects.

\linkspell{Phantom Steed}: Magic horse appears for 1 hour/level.

\linkspell{Remove Curse}: Frees object or person from curse.

\linkspell{Scrying}\textsuperscript{F}: Spies on subject from a distance.

\linkspell{Sculpt Sound}: Creates new sounds or changes existing ones.

\linkspell{Secret Page}: Changes one page to hide its real content.

\linkspell{See Invisibility}: Reveals invisible creatures or objects.

\linkspell{Sepia Snake Sigil}\textsuperscript{M}: Creates text symbol that immobilizes reader.

\linkspell{Slow}: One subject/level takes only one action/round, -1 to AC, reflex saves, and attack rolls.

\linkspell{Speak With Animals}: You can communicate with animals.

\linkspell{Summon Monster III}: Calls extraplanar creature to fight for you.

\linkspell{Tiny Hut}: Creates shelter for ten creatures.

%%%
\subsubsection{4th Level Bard Spells}
%%%

\linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\linkspell{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\linkspell{Detect Scrying}: Alerts you of magical eavesdropping.

\linkspell{Dimension Door}: Teleports you short distance.

\linkspell{Dominate Person}: Controls humanoid telepathically.

\linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\linkspell{Greater Invisibility}: As \linkspell{Invisibility}, but subject can attack and stay invisible.

\linkspell{Hallucinatory Terrain}: Makes one type of terrain appear like another (field into forest, or the like).

\linkspell{Hold Monster}: As \linkspell{Hold Person}, but any creature.

\linkspell{Legend Lore}\textsuperscript{M}\textsuperscript{F}: Lets you learn tales about a person, place, or thing.

\linkspell{Locate Creature}: Indicates direction to familiar creature.

\linkspell{Modify Memory}: Changes 5 minutes of subject's memories.

\linkspell{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\linkspell{Rainbow Pattern}: Lights fascinate 24 HD of creatures.

\linkspell{Repel Vermin}: Insects, spiders, and other vermin stay 10 ft. away.

\linkspell{Secure Shelter}: Creates sturdy cottage.

\linkspell{Shadow Conjuration}: Mimics conjuring below 4th level, but only 20\% real.

\linkspell{Shout}: Deafens all within cone and deals 5d6 sonic damage.

\linkspell{Speak with Plants}: You can talk to normal plants and plant creatures.

\linkspell{Summon Monster IV}: Calls extraplanar creature to fight for you.

\linkspell{Zone of Silence}: Keeps eavesdroppers from overhearing conversations.

%%%
\subsubsection{5th Level Bard Spells}
%%%

\linkspell{Dream}: Sends message to anyone sleeping.

\linkspell{False Vision}\textsuperscript{M}: Fools scrying with an illusion.

\linkspell{Greater Dispel Magic}: As \linkspell{Dispel Magic}, but +20 on check.

\linkspell{Greater Heroism}: Gives +4 bonus on attack rolls, saves, skill checks; immunity to fear; temporary hp.

\linkspell{Mass Cure Light Wounds}: Cures 1d8 damage +1/level for many creatures.

\linkspell{Mass Suggestion}: As \linkspell{Suggestion}, plus one subject/level.

\linkspell{Mind Fog}: Subjects in fog get -10 to Wis and Will checks.

\linkspell{Mirage Arcana}: As \linkspell{Hallucinatory Terrain}, plus structures.

\linkspell{Mislead}: Turns you invisible and creates illusory double.

\linkspell{Nightmare}: Sends vision dealing 1d10 damage, fatigue.

\linkspell{Persistent Image}: As \linkspell{Major Image}, but no concentration required.

\linkspell{Seeming}: Changes appearance of one person per two levels.

\linkspell{Shadow Evocation}: Mimics evocation of lower than 5th level, but only 20\% real.

\linkspell{Shadow Walk}: Step into shadow to travel rapidly.

\linkspell{Song of Discord}: Forces targets to attack each other.

\linkspell{Summon Monster V}: Calls extraplanar creature to fight for you.

%%%
\subsubsection{6th Level Bard Spells}
%%%

\linkspell{Analyze Dweomer}\textsuperscript{F}: Reveals magical aspects of subject.

\linkspell{Animate Objects}: Objects attack your foes.

\linkspell{Eyebite}: Target becomes panicked, sickened, and comatose.

\linkspell{Find the Path}: Shows most direct way to a location.

\linkspell{Geas/Quest}{Geas}: As \linkspell{Lesser Geas}, plus it affects any creature.

\linkspell{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.

\linkspell{Irresistible Dance}: Forces subject to dance.

\linkspell{Mass Cat's Grace}: As \linkspell{Cat's Grace}, affects one subject/level.

\linkspell{Mass Charm Monster}: As \linkspell{Charm Monster}, but all within 30 ft.

\linkspell{Mass Cure Moderate Wounds}: Cures 2d8 damage +1/level for many creatures.

\linkspell{Mass Eagle's Splendor}: As \linkspell{Eagle's Splendor}, affects one subject/level.

\linkspell{Mass Fox's Cunning}: As \linkspell{Fox's Cunning}, affects one subject/level.

\linkspell{Permanent Image}: Includes sight, sound, and smell.

\linkspell{Programmed Image}\textsuperscript{M}: As \linkspell{Major Image}, plus triggered by event.

\linkspell{Project Image}: Illusory double can talk and cast spells.

\linkspell{Greater Scrying}: As \linkspell{Scrying}, but faster and longer.

\linkspell{Greater Shout}: Devastating yell deals 10d6 sonic damage; stuns creatures, damages objects.

\linkspell{Summon Monster VI}: Calls extraplanar creature to fight for you.

\linkspell{Sympathetic Vibration}: Deals 2d10 damage/round to freestanding structure.

\linkspell{Veil}: Changes appearance of group of creatures.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cleric Spells}\index{Cleric Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{0th Level Cleric Spells (Orisons)}
%%%

\linkspell{Create Water}: Creates 2 gallons/level of pure water.

\linkspell{Cure Minor Wounds}: Cures 1 point of damage.

\linkspell{Detect Magic}: Detects spells and magic items within 60 ft.

\linkspell{Detect Poison}: Detects poison in one creature or object.

\linkspell{Guidance}: +1 on one attack roll, saving throw, or skill check.

\linkspell{Inflict Minor Wounds}: Touch attack, 1 point of damage.

\linkspell{Light}: Object shines like a torch.

\linkspell{Mending}: Makes minor repairs on an object.

\linkspell{Purify Food and Drink}: Purifies 1 cu. ft./level of food or water.

\linkspell{Read Magic}: Read scrolls and spellbooks.

\linkspell{Resistance}: Subject gains +1 on saving throws.

\linkspell{Virtue}: Subject gains 1 temporary hp.

%%%
\subsubsection{1st Level Cleric Spells}
%%%

\linkspell{Bane}: Enemies take -1 on attack rolls and saves against fear.

\linkspell{Bless}: Allies gain +1 on attack rolls and saves against fear.

\linkspell{Bless Water}\textsuperscript{M}: Makes holy water.

\linkspell{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\linkspell{Command}: One subject obeys selected command for 1 round.

\linkspell{Comprehend Languages}: You understand all spoken and written languages.

\linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\linkspell{Curse Water}\textsuperscript{M}: Makes unholy water.

\linkspell{Deathwatch}: Reveals how near death subjects within 30 ft. are.

\linkspell{Detect Chaos}/\linkspell{Detect Evil}{Evil}/\linkspell{Detect Good}{Good}/\linkspell{Detect Law}{Law}: Reveals creatures, spells, or objects of selected alignment.

\linkspell{Detect Undead}: Reveals undead within 60 ft.

\linkspell{Divine Favor}: You gain +1 per three levels on attack and damage rolls.

\linkspell{Doom}: One subject takes -2 on attack rolls, damage rolls, saves, and checks.

\linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\linkspell{Entropic Shield}: Ranged attacks against you have 20\% miss chance.

\linkspell{Hide from Undead}: Undead can't perceive one subject/level.

\linkspell{Inflict Light Wounds}: Touch deals 1d8 damage +1/level (max +5).

\linkspell{Magic Stone}: Three stones gain +1 on attack, deal 1d6 +1 damage.

\linkspell{Magic Weapon}: Weapon gains +1 bonus.

\linkspell{Obscuring Mist}: Fog surrounds you.

\linkspell{Protection From Chaos}/\linkspell{Protection From Evil}{Evil}/\linkspell{Protection From Good}{Good}/\linkspell{Protection From Law}{Law}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\linkspell{Remove Fear}: Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.

\linkspell{Sanctuary}: Opponents can't attack you, and you can't attack.

\linkspell{Shield of Faith}: Aura grants +2 or higher deflection bonus.

\linkspell{Summon Monster I}: Calls extraplanar creature to fight for you.

%%%
\subsubsection{2nd Level Cleric Spells}
%%%

\linkspell{Aid}: +1 on attack rolls and saves against fear, 1d8 temporary hp +1/level 
(max +10).

\linkspell{Align Weapon}: Weapon becomes good, evil, lawful, or chaotic.

\linkspell{Augury}\textsuperscript{M}\textsuperscript{F}: Learns whether an action will be good or bad.

\linkspell{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\linkspell{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\linkspell{Calm Emotions}: Calms creatures, negating emotion effects.

\linkspell{Consecrate}\textsuperscript{M}: Fills area with positive energy, making undead weaker.

\linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\linkspell{Darkness}: 20-ft. radius of supernatural shadow.

\linkspell{Death Knell}: Kills dying creature; you gain 1d8 temporary hp, +2 to Str, and +1 level.

\linkspell{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\linkspell{Desecrate}\textsuperscript{M}: Fills area with negative energy, making undead stronger.

\linkspell{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\linkspell{Enthrall}: Captivates all within 100 ft. + 10 ft./level.

\linkspell{Find Traps}: Notice traps as a rogue does.

\linkspell{Gentle Repose}: Preserves one corpse.

\linkspell{Hold Person}: Paralyzes one humanoid for 1 round/level.

\linkspell{Inflict Moderate Wounds}: Touch attack, 2d8 damage +1/level (max +10).

\linkspell{Lesser Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.

\linkspell{Make Whole}: Repairs an object.

\linkspell{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\linkspell{Remove Paralysis}: Frees one or more creatures from paralysis or \linkspell{Slow} effect.

\linkspell{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\linkspell{Shatter}: Sonic vibration damages objects or crystalline creatures.

\linkspell{Shield Other}\textsuperscript{F}: You take half of subject's damage.

\linkspell{Silence}: Negates sound in 20-ft. radius.

\linkspell{Sound Burst}: Deals 1d8 sonic damage to subjects; may stun them.

\linkspell{Spiritual Weapon}: Magic weapon attacks on its own.

\linkspell{Status}: Monitors condition, position of allies.

\linkspell{Summon Monster II}: Calls extraplanar creature to fight for you.

\linkspell{Undetectable Alignment}: Conceals alignment for 24 hours.

\linkspell{Zone of Truth}: Subjects within range cannot lie.

%%%
\subsubsection{3rd Level Cleric Spells}
%%%

\linkspell{Animate Dead}\textsuperscript{M}: Creates undead skeletons and zombies.

\linkspell{Bestow Curse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.

\linkspell{Blindness/Deafness}: Makes subject blinded or deafened.

\linkspell{Contagion}: Infects subject with chosen disease.

\linkspell{Continual Flame}\textsuperscript{M}: Makes a permanent, heatless torch.

\linkspell{Create Food and Water}: Feeds three humans (or one horse)/level.

\linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\linkspell{Daylight}: 60-ft. radius of bright light.

\linkspell{Deeper Darkness}: Object sheds supernatural shadow in 60-ft. radius.

\linkspell{Dispel Magic}: Cancels spells and magical effects.

\linkspell{Glyph of Warding}\textsuperscript{M}: Inscription harms those who pass it.

\linkspell{Helping Hand}: Ghostly hand leads subject to you.

\linkspell{Inflict Serious Wounds}: Touch attack, 3d8 damage +1/level (max +15).

\linkspell{Invisibility Purge}: Dispels invisibility within 5 ft./level.

\linkspell{Locate Object}: Senses direction toward object (specific or type).

\linkspell{Magic Circle Against Chaos}/\linkspell{Magic Circle Against Evil}{Evil}/\linkspell{Magic Circle Against Good}{Good}/\linkspell{Magic Circle Against Law}{Law}: As \textit{protection} spells, but 10-ft. radius and 10 min./level.

\linkspell{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

\linkspell{Meld into Stone}: You and your gear merge with stone.

\linkspell{Obscure Object}: Masks object against scrying.

\linkspell{Prayer}: Allies +1 bonus on most rolls, enemies -1 penalty.

\linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

\linkspell{Remove Blindness/Deafness}: Cures normal or magical conditions.

\linkspell{Remove Curse}: Frees object or person from curse.

\linkspell{Remove Disease}: Cures all diseases affecting subject.

\linkspell{Searing Light}: Ray deals 1d8/two levels damage, more against undead.

\linkspell{Speak With Dead}: Corpse answers one question/two levels.

\linkspell{Stone Shape}: Sculpts stone into any shape.

\linkspell{Summon Monster III}: Calls extraplanar creature to fight for you.

\linkspell{Water Breathing}: Subjects can breathe underwater.

\linkspell{Water Walk}: Subject treads on water as if solid.

\linkspell{Wind Wall}: Deflects arrows, smaller creatures, and gases.

%%%
\subsubsection{4th Level Cleric Spells}
%%%

\linkspell{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

\linkspell{Control Water}: Raises or lowers bodies of water.

\linkspell{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\linkspell{Death Ward}: Grants immunity to death spells and negative energy effects.

\linkspell{Dimensional Anchor}: Bars extradimensional movement.

\linkspell{Discern Lies}: Reveals deliberate falsehoods.

\linkspell{Dismissal}: Forces a creature to return to native plane.

\linkspell{Divination}\textsuperscript{M}: Provides useful advice for specific proposed actions.

\linkspell{Divine Power}: You gain attack bonus, +6 to Str, and 1 hp/level.

\linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\linkspell{Giant Vermin}: Turns centipedes, scorpions, or spiders into giant vermin.

\linkspell{Imbue With Spell Ability}: Transfer spells to subject.

\linkspell{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).

\linkspell{Lesser Planar Ally}\textsuperscript{X}: Exchange services with a 6 HD extraplanar creature.

\linkspell{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\linkspell{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\linkspell{Repel Vermin}: Insects, spiders, and other vermin stay 10 ft. away.

\linkspell{Restoration}\textsuperscript{M}: Restores level and ability score drains.

\linkspell{Sending}: Delivers short message anywhere, instantly.

\linkspell{Spell Immunity}: Subject is immune to one spell per four levels.

\linkspell{Summon Monster IV}: Calls extraplanar creature to fight for you.

\linkspell{Tongues}: Speak any language.

%%%
\subsubsection{5th Level Cleric Spells}
%%%

\linkspell{Atonement}\textsuperscript{F}\textsuperscript{X}: Removes burden of misdeeds from subject.

\linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\linkspell{Commune}\textsuperscript{X}: Deity answers one yes-or-no question/level.

\linkspell{Mass Cure Light Wounds}: Cures 1d8 damage +1/level for many creatures.

\linkspell{Dispel Chaos}/\linkspell{Dispel Evil}{Evil}/\linkspell{Dispel Good}{Good}/\linkspell{Dispel Law}{Law}: +4 bonus against attacks.

\linkspell{Disrupting Weapon}: Melee weapon destroys undead.

\linkspell{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\linkspell{Greater Command}: As \linkspell{Command}, but affects one subject/level.

\linkspell{Hallow}\textsuperscript{M}: Designates location as holy.

\linkspell{Insect Plague}: Locust swarms attack creatures.

\linkspell{Mark of Justice}: Designates action that will trigger \textit{curse} on subject.

\linkspell{Mass Inflict Light Wounds}: Deals 1d8 damage +1/level to many creatures.

\linkspell{Plane Shift}\textsuperscript{F}: As many as eight subjects travel to another plane.

\linkspell{Raise Dead}\textsuperscript{M}: Restores life to subject who died as long as one day/level ago.

\linkspell{Righteous Might}: Your size increases, and you gain combat bonuses.

\linkspell{Scrying}\textsuperscript{F}: Spies on subject from a distance.

\linkspell{Slay Living}: Touch attack kills subject.

\linkspell{Spell Resistance}: Subject gains SR 12 + level.

\linkspell{Summon Monster V}: Calls extraplanar creature to fight for you.

\linkspell{Symbol of Pain}\textsuperscript{M}: Triggered rune wracks nearby creatures with pain.

\linkspell{Symbol of Sleep}\textsuperscript{M}: Triggered rune puts nearby creatures into catatonic slumber.

\linkspell{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.

\linkspell{Unhallow}\textsuperscript{M}: Designates location as unholy.

\linkspell{Wall of Stone}: Creates a stone wall that can be shaped.

%%%
\subsubsection{6th Level Cleric Spells}
%%%

\linkspell{Animate Objects}: Objects attack your foes.

\linkspell{Antilife Shell}: 10-ft. field hedges out living creatures.

\linkspell{Banishment}: Banishes 2 HD/level of extraplanar creatures.

\linkspell{Blade Barrier}: Wall of blades deals 1d6/level damage.

\linkspell{Create Undead}: Create ghouls, ghasts, mummies, or mohrgs.

\linkspell{Find the Path}: Shows most direct way to a location.

\linkspell{Forbiddance}\textsuperscript{M}: Blocks planar travel, damages creatures of different alignment.

\linkspell{Greater Dispel Magic}: As \linkspell{Dispel Magic}, but up to +20 on check.

\linkspell{Greater Glyph of Warding}: As \linkspell{Glyph of Warding}, but up to 10d8 damage or 6th-level spell.

\linkspell{Harm}: Deals 10 points/level damage to target.

\linkspell{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.

\linkspell{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.

\linkspell{Mass Bear's Endurance}: As \linkspell{Bear's Endurance}, affects one subject/ level.

\linkspell{Mass Bull's Strength}: As \linkspell{Bull's Strength}, affects one subject/level.

\linkspell{Mass Cure Moderate Wounds}: Cures 2d8 damage +1/level for many creatures.

\linkspell{Mass Eagle's Splendor}: As \linkspell{Eagle's Splendor}, affects one subject/level.

\linkspell{Mass Inflict Moderate Wounds}: Deals 2d8 damage +1/level to many creatures.

\linkspell{Mass Owl's Wisdom}: As \linkspell{Owl's Wisdom}, affects one subject/level.

\linkspell{Planar Ally}\textsuperscript{X}: As \linkspell{Lesser Planar Ally}, but up to 12 HD.

\linkspell{Geas/Quest}{Quest}: As \linkspell{Lesser Geas}, plus it affects any creature.

\linkspell{Summon Monster VI}: Calls extraplanar creature to fight for you.

\linkspell{Symbol of Fear}\textsuperscript{M}: Triggered rune panics nearby creatures.

\linkspell{Symbol of Persuasion}\textsuperscript{M}: Triggered rune charms nearby creatures.

\linkspell{Undeath to Death}\textsuperscript{M}: Destroys 1d4 HD/level undead (max 20d4).

\linkspell{Wind Walk}: You and your allies turn vaporous and travel fast.

\linkspell{Word of Recall}: Teleports you back to designated place.

%%%
\subsubsection{7th Level Cleric Spells}
%%%

\linkspell{Blasphemy}: Kills, paralyzes, weakens, or dazes nonevil subjects.

\linkspell{Control Weather}: Changes weather in local area.

\linkspell{Destruction}\textsuperscript{F}: Kills subject and destroys remains.

\linkspell{Dictum}: Kills, paralyzes, slows, or deafens nonlawful subjects.

\linkspell{Ethereal Jaunt}: You become ethereal for 1 round/level.

\linkspell{Greater Restoration}\textsuperscript{X}: As \linkspell{Restoration}, plus restores all levels and ability scores.

\linkspell{Greater Scrying}: As \linkspell{Scrying}, but faster and longer.

\linkspell{Holy Word}: Kills, paralyzes, blinds, or deafens nongood subjects.

\linkspell{Mass Cure Serious Wounds}: Cures 3d8 damage +1/level for many creatures.

\linkspell{Mass Inflict Serious Wounds}: Deals 3d8 damage +1/level to many creatures.

\linkspell{Refuge}\textsuperscript{M}: Alters item to transport its possessor to you.

\linkspell{Regenerate}: Subject's severed limbs grow back, cures 4d8 damage +1/level (max +35).

\linkspell{Repulsion}: Creatures can't approach you.

\linkspell{Resurrection}\textsuperscript{M}: Fully restore dead subject.

\linkspell{Summon Monster VII}: Calls extraplanar creature to fight for you.

\linkspell{Symbol of Stunning}\textsuperscript{M}: Triggered rune stuns nearby creatures.

\linkspell{Symbol of Weakness}\textsuperscript{M}: Triggered rune weakens nearby creatures.

\linkspell{Word of Chaos}: Kills, \linksec{Confused}{Confuses}, \linksec{Stunned}{Stuns}, or \linksec{Deafened}{Deafens} nonchaotic subjects.

%%%
\subsubsection{8th Level Cleric Spells}
%%%

\linkspell{Antimagic Field}: Negates magic within 10 ft.

\linkspell{Cloak of Chaos}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against lawful spells.

\linkspell{Create Greater Undead}\textsuperscript{M}: Create shadows, wraiths, spectres, or devourers.

\linkspell{Dimensional Lock}: Teleportation and interplanar travel blocked for one day/level.

\linkspell{Discern Location}: Reveals exact location of creature or object.

\linkspell{Earthquake}: Intense tremor shakes 80-ft.-radius.

\linkspell{Fire Storm}: Deals 1d6/level fire damage.

\linkspell{Greater Planar Ally}\textsuperscript{X}: As \linkspell{Lesser Planar Ally}, but up to 18 HD.

\linkspell{Greater Spell Immunity}: As \linkspell{Spell Immunity}, but up to 8th-level spells.

\linkspell{Holy Aura}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against evil spells.

\linkspell{Mass Cure Critical Wounds}: Cures 4d8 damage +1/level for many creatures.

\linkspell{Mass Inflict Critical Wounds}: Deals 4d8 damage +1/level to many creatures.

\linkspell{Shield of Law}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against chaotic spells.

\linkspell{Summon Monster VIII}: Calls extraplanar creature to fight for you.

\linkspell{Symbol of Death}\textsuperscript{M}: Triggered rune slays nearby creatures.

\linkspell{Symbol of Insanity}\textsuperscript{M}: Triggered rune renders nearby creatures insane.

\linkspell{Unholy Aura}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against good spells.

%%%
\subsubsection{9th Level Cleric Spells}
%%%

\linkspell{Astral Projection}\textsuperscript{M}: Projects you and companions onto Astral Plane.

\linkspell{Energy Drain}: Subject gains 2d4 negative levels.

\linkspell{Etherealness}: Travel to Ethereal Plane with companions.

\linkspell{Gate}\textsuperscript{X}: Connects two planes for travel or summoning.

\linkspell{Implosion}: Kills one creature/round.

\linkspell{Mass Heal}: As \linkspell{Heal}, but with several subjects.

\linkspell{Miracle}\textsuperscript{X}: Requests a deity's intercession.

\linkspell{Soul Bind}\textsuperscript{F}: Traps newly dead soul to prevent \linkspell{Resurrection}.

\linkspell{Storm of Vengeance}: Storm rains acid, lightning, and hail.

\linkspell{Summon Monster IX}: Calls extraplanar creature to fight for you.

\linkspell{True Resurrection}\textsuperscript{M}: As \linkspell{Resurrection}, plus remains aren't needed.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cleric Domains}\index{Cleric Domains}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{Air Domain}
%%%

\textbf{Granted Powers}: Turn or destroy earth creatures as a good cleric turns undead. Rebuke, command, or bolster air creatures as an evil cleric rebukes undead. Use these abilities a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

\textbf{Air Domain Spells}

\textbf{1} \linkspell{Obscuring Mist}: Fog surrounds you.

\textbf{2} \linkspell{Wind Wall}: Deflects arrows, smaller creatures, and gases.

\textbf{3} \linkspell{Gaseous Form}: Subject becomes insubstantial and can fly slowly.

\textbf{4} \linkspell{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

\textbf{5} \linkspell{Control Winds}: Change wind direction and speed.

\textbf{6} \linkspell{Chain Lightning}: 1d6/level damage; 1 secondary bolt/level each deals half damage.

\textbf{7} \linkspell{Control Weather}: Changes weather in local area.

\textbf{8} \linkspell{Whirlwind}: Cyclone deals damage and can pick up creatures.

\textbf{9} \linkspell{Elemental Swarm}\textsuperscript{*}: Summons multiple elementals.

\textsuperscript{*}Cast as an air spell only.

%%%
\subsubsection{Animal Domain}
%%%

\textbf{Granted Powers}: You can use \linkspell{Speak With Animals} once per day as a spell-like ability.

Add \linkskill{Knowledge} (nature) to your list of cleric class skills.

\textbf{Animal Domain Spells}

\textbf{1} \linkspell{Calm Animals}: Calms (2d4 + level) HD of animals.

\textbf{2} \linkspell{Hold Animal}: Paralyzes one animal for 1 round/level.

\textbf{3} \linkspell{Dominate Animal}: Subject animal obeys silent mental commands.

\textbf{4} \linkspell{Summon Nature's Ally IV}\textsuperscript{*}: Calls creature to fight.

\textbf{5} \linkspell{Commune with Nature}: Learn about terrain for 1 mile/level.

\textbf{6} \linkspell{Antilife Shell}: 10-ft. field hedges out living creatures.

\textbf{7} \linkspell{Animal Shapes}: One ally/level polymorphs into chosen animal.

\textbf{8} \linkspell{Summon Nature's Ally VIII}\textsuperscript{*}: Calls creature to fight.

\textbf{9} \linkspell{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.

\textsuperscript{*}Can only summon animals.

%%%
\subsubsection{Artifice Domain}
%%%

\textbf{Granted Power}: Gain +4 bonus on \linkskill{Craft} checks. The character casts Conjuration (creation) spells at +1 caster level. (Those with access to both the Artifice and \linksec{Creation Domain}{Creation} domains cast Conjuration (creation) spells at +3 caster level.)

\textbf{Artifice Domain Spells}

\textbf{1} \linkspell{Animate Rope}: Makes a rope move at your command.

\textbf{2} \linkspell{Wood Shape}: Rearranges wooden objects to suit you.

\textbf{3} \linkspell{Stone Shape}: Sculpts stone into any shape.

\textbf{4} \linkspell{Minor Creation}: Creates one cloth or wood object.

\textbf{5} \linkspell{Fabricate}: Transforms raw materials into finished items.

\textbf{6} \linkspell{Major Creation}: As \linkspell{Minor Creation}, plus stone and metal.

\textbf{7} \linkspell{Hardening}: Object permanently gains 1 Hardness per 2 caster levels.

\textbf{8} \linkspell{True Creation}\textsuperscript{X}: Instantly create a nonmagical unattended object.

\textbf{9} \linkspell{Prismatic Sphere}: As \linkspell{Prismatic Wall}, but surrounds on all sides.

%%%
\subsubsection{Chaos Domain}
%%%

\textbf{Granted Power}: You cast chaos spells at +1 caster level.

\textbf{Chaos Domain Spells}

\textbf{1} \linkspell{Protection From Law}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\textbf{2} \linkspell{Shatter}: Sonic vibration damages objects or crystalline creatures.

\textbf{3} \linkspell{Magic Circle Against Law}: As \linkspell{Protection From Law}{Protection} spells, but 10-ft. radius and 10 min./level.

\textbf{4} \linkspell{Chaos Hammer}: Damages and staggers lawful creatures.

\textbf{5} \linkspell{Dispel Law}: +4 bonus against attacks by lawful creatures.

\textbf{6} \linkspell{Animate Objects}: Objects attack your foes.

\textbf{7} \linkspell{Word of Chaos}: Kills, \linkspell{Confusion}{Confuses}, stuns, or deafens nonchaotic subjects.

\textbf{8} \linkspell{Cloak of Chaos}\textsuperscript{F}: +4 to AC, +4 resistance, SR 25 against lawful spells.

\textbf{9} \linkspell{Summon Monster IX}\textsuperscript{*}: Calls extraplanar creature to fight for you.

\textsuperscript{*}Cast as a chaos spell only.

%%%
\subsubsection{Charm Domain}
%%%

\textbf{Granted Power}: The character can boost his or her Charisma by 4 points once per day. Activating this power is a free action. The Charisma increase lasts 1 minute.

\textbf{Charm Domain Spells}

\textbf{1} \linkspell{Charm Person}: Makes one person your friend.

\textbf{2} \linkspell{Calm Emotions}: Calms creatures, negating emotion effects.

\textbf{3} \linkspell{Suggestion}: Compels subject to follow stated course of action.

\textbf{4} \linkspell{Heroism}: Gives +2 bonus on attack rolls, saves, skill checks.

\textbf{5} \linkspell{Charm Monster}: Makes monster believe it is your ally.

\textbf{6} \linkspell{Geas/Quest}{Quest}: As \linkspell{Lesser Geas}, plus it affects any creature.

\textbf{7} \linkspell{Insanity}: Subject suffers continuous \linkspell{Confusion}.

\textbf{8} \linkspell{Demand}: As \linkspell{Sending}, plus you can send \linkspell{Suggestion}.

\textbf{9} \linkspell{Dominate Monster}: As \linkspell{Dominate Person}, but any creature.

%%%
\subsubsection{Community Domain}
%%%

\textbf{Granted Power}: Use \linkspell{Calm Emotions} as a spell-like ability once per day. Gain a +2 competence bonus on \linkskill{Diplomacy} checks.

\textbf{Community Domain Spells}

\textbf{1} \linkspell{Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.

\textbf{2} \linkspell{Shield Other}\textsuperscript{F}: You take half of subject's damage.

\textbf{3} \linkspell{Prayer}: Allies +1 bonus on most rolls, enemies -1 penalty.

\textbf{4} \linkspell{Status}: Monitors condition, position of allies.

\textbf{5} \linkspell{Telepathic Bond}:  Link lets allies communicate.

\textbf{6} \linkspell{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.

\textbf{7} \linkspell{Refuge}\textsuperscript{M}: Alters item to transport its possessor to you.

\textbf{8} \linkspell{Heal, Mass}: As \linkspell{Heal}, but with several subjects.

\textbf{9} \linkspell{Miracle}\textsuperscript{X}: Requests a deity's intercession.

%%%
\subsubsection{Creation Domain}
%%%

\textbf{Granted Power}: Cast Conjuration (creation) spells at +2 caster level. (Those with access to both the \linksec{Artifice Domain}{Artifice} and Creation domains cast Conjuration (creation) spells at +3 caster level.)

\textbf{Creation Domain Spells}

\textbf{1} \linkspell{Create Water}: Creates 2 gallons/level of pure water.

\textbf{2} \linkspell{Minor Image}: As \linkspell{Silent Image}, plus some sound.

\textbf{3} \linkspell{Create Food and Water}: Feeds three humans (or one horse)/level.

\textbf{4} \linkspell{Minor Creation}: Creates one cloth or wood object.

\textbf{5} \linkspell{Major Creation}: As \linkspell{Minor Creation}, plus stone and metal.

\textbf{6} \linkspell{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.

\textbf{7} \linkspell{Permanent Image}: Includes sight, sound, and smell.

\textbf{8} \linkspell{True Creation}\textsuperscript{X}: Instantly create a nonmagical unattended object.

\textbf{9} \linkspell{Genesis}\textsuperscript{X}: Creates a deimiplane on the Ethereal Plane.

%%%
\subsubsection{Darkness Domain}
%%%

\textbf{Granted Power}: Free \linkfeat{Blind-Fight} feat.

\textbf{Darkness Domain Spells}

\textbf{1} \linkspell{Obscuring Mist}: Fog surrounds you.

\textbf{2} \linkspell{Blindness}: Makes subject blind.

\textbf{3} \linkspell{Blacklight}: Creates area of absolute darkness.

\textbf{4} \linkspell{Armor of Darkness}: Darkness shroud grants deflection bonus, Darkvision, and save bonus.

\textbf{5} \linkspell{Summon Monster V} (only summons 1d3 shadows): Calls extraplanar creature to fight for you.

\textbf{6} \linkspell{Prying Eyes}: 1d4 +1/level floating eyes scout for you.

\textbf{7} \linkspell{Nightmare}: Sends vision dealing 1d10 damage, fatigue.

\textbf{8} \linkspell{Power Word Blind}: Blinds creature with 200 hp or less.

\textbf{9} \linkspell{Power Word Kill}: Kills creature with 100 hp or less.

%%%
\subsubsection{Death Domain}
%%%

\textbf{Granted Power}: You may use a death touch once per day. Your death touch is a supernatural ability that produces a death effect. You must succeed on a melee touch attack against a living creature (using the rules for touch spells). When you touch, roll 1d6 per cleric level you possess. If the total at least equals the creature's current hit points, it dies (no save).

\textbf{Death Domain Spells}

\textbf{1} \linkspell{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\textbf{2} \linkspell{Death Knell}: Kill dying creature and gain 1d8 temporary hp, +2 to Str, and +1 caster level.

\textbf{3} \linkspell{Animate Dead}\textsuperscript{M}: Creates undead skeletons and zombies.

\textbf{4} \linkspell{Death Ward}: Grants immunity to death spells and negative energy effects.

\textbf{5} \linkspell{Slay Living}: Touch attack kills subject.

\textbf{6} \linkspell{Create Undead}\textsuperscript{M}: Create ghouls, ghasts, mummies, or mohrgs.

\textbf{7} \linkspell{Destruction}\textsuperscript{F}: Kills subject and destroys remains.

\textbf{8} \linkspell{Create Greater Undead}\textsuperscript{M}: Create shadows, wraiths, spectres, r devourers.

\textbf{9} \linkspell{Wail of the Banshee}: Kills one creature/level.

%%%
\subsubsection{Destruction Domain}
%%%

\textbf{Granted Power}: You gain the smite power, the supernatural ability to make a single melee attack with a +4 bonus on attack rolls and a bonus on damage rolls equal to your cleric level (if you hit). You must declare the smite before making the attack. This ability is usable once per day.

\textbf{Destruction Domain Spells}

\textbf{1} \linkspell{Inflict Light Wounds}: Touch attack, 1d8 damage +1/level (max +5).

\textbf{2} \linkspell{Shatter}: Sonic vibration damages objects or crystalline creatures.

\textbf{3} \linkspell{Contagion}: Infects subject with chosen disease.

\textbf{4} \linkspell{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).

\textbf{5} \linkspell{Inflict Light Wounds, Mass}: Deals 1d8 damage +1/level to any creatures.

\textbf{6} \linkspell{Harm}: Deals 10 points/level damage to target.

\textbf{7} \linkspell{Disintegrate}: Makes one creature or object vanish.

\textbf{8} \linkspell{Earthquake}: Intense tremor shakes 80-ft.-radius.

\textbf{9} \linkspell{Implosion}: Kills one creature/round.

%%%
\subsubsection{Earth Domain}
%%%

\textbf{Granted Power}: Turn or destroy air creatures as a good cleric turns undead. Rebuke, command, or bolster earth creatures as an evil cleric rebukes undead. Use these abilities a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

\textbf{Earth Domain Spells}

\textbf{1} \linkspell{Magic Stone}: Three stones become +1 projectiles, 1d6 +1 damage.

\textbf{2} \linkspell{Soften Earth and Stone}: Turns stone to clay or dirt to sand or mud.

\textbf{3} \linkspell{Stone Shape}: Sculpts stone into any shape.

\textbf{4} \linkspell{Spike Stones}: Creatures in area take 1d8 damage, may be \linkspell{Slow}{Slowed}.

\textbf{5} \linkspell{Wall of Stone}: Creates a stone wall that can be shaped.

\textbf{6} \linkspell{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.

\textbf{7} \linkspell{Earthquake}: Intense tremor shakes 80-ft.-radius.

\textbf{8} \linkspell{Iron Body}: Your body becomes living iron.

\textbf{9} \linkspell{Elemental Swarm}\textsuperscript{*}: Summons multiple elementals.

\textsuperscript{*}Cast as an earth spell only.

%%%
\subsubsection{Evil Domain}
%%%

\textbf{Granted Power}: You cast evil spells at +1 caster level.

\textbf{Evil Domain Spells}

\textbf{1} \linkspell{Protection From Good}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\textbf{2} \linkspell{Desecrate}\textsuperscript{M}: Fills area with negative energy, making undead stronger.

\textbf{3} \linkspell{Magic Circle Against Good}: As \linkspell{Protection From Good}{Protection} spell, but 10-ft. radius and 10 min./level.

\textbf{4} \linkspell{Unholy Blight}: Damages and sickens good creatures.

\textbf{5} \linkspell{Dispel Good}: +4 bonus against attacks by good creatures.

\textbf{6} \linkspell{Create Undead}\textsuperscript{M}: Create ghouls, ghasts, mummies, or mohrgs.

\textbf{7} \linkspell{Blasphemy}: Kills, paralyzes, weakens, or dazes nonevil subjects.

\textbf{8} \linkspell{Unholy Aura}\textsuperscript{F}: +4 to AC, +4 resistance, SR 25 against good spells.

\textbf{9} \linkspell{Summon Monster IX}\textsuperscript{*}: Calls extraplanar creature to fight for you.

\textsuperscript{*}Cast as an evil spell only.

%%%
\subsubsection{Fire Domain}
%%%

\textbf{Granted Power}: Turn or destroy water creatures as a good cleric turns undead. Rebuke, command, or bolster fire creatures as an evil cleric rebukes undead. Use these abilities a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

\textbf{Fire Domain Spells}

\textbf{1} \linkspell{Burning Hands}: 1d4/level fire damage (max 5d4).

\textbf{2} \linkspell{Produce Flame}: 1d6 damage +1/ level, touch or thrown.

\textbf{3} \linkspell{Resist Energy}\textsuperscript{*}: Ignores 10 (or more) points of damage/attack from specified energy type.

\textbf{4} \linkspell{Wall of Fire}: Deals 2d4 fire damage out to 10 ft. and 1d4 out to 20 ft. Passing through wall deals 2d6 damage +1/level.

\textbf{5} \linkspell{Fire Shield}: Creatures attacking you take fire damage; you're protected from heat or cold.

\textbf{6} \linkspell{Fire Seeds}: Acorns and berries become grenades and bombs.

\textbf{7} \linkspell{Fire Storm}: Deals 1d6/level fire damage.

\textbf{8} \linkspell{Incendiary Cloud}: Cloud deals 4d6 fire damage/round.

\textbf{9} \linkspell{Elemental Swarm}\textsuperscript{*}\textsuperscript{*}: Summons multiple elementals.

\textsuperscript{*}Resist cold or fire only.

\textsuperscript{*}\textsuperscript{*}Cast as a fire spell only.

%%%
\subsubsection{Glory Domain}
%%%

\textbf{Granted Power}: Turn undead with a +2 bonus on the turning check and +1d6 to the turning damage roll.

\textbf{Glory Domain Spells}

\textbf{1} \linkspell{Disrupt Undead}: Deals 1d6 damage to one undead.

\textbf{2} \linkspell{Bless Weapon}: Weapon strikes true against evil foes.

\textbf{3} \linkspell{Searing Light}: Ray deals 1d8/two levels, more against undead.

\textbf{4} \linkspell{Holy Smite}: Damages and blinds evil creatures.

\textbf{5} \linkspell{Holy Sword}: Weapon becomes +5, deals +2d6 damage against evil.

\textbf{6} \linkspell{Bolt of Glory}: Positive Energy bolt deals various effects to target based on their home plane.

\textbf{7} \linkspell{Sunbeam}: Beam blinds and deals 4d6 damage.

\textbf{8} \linkspell{Crown of Glory}: Celestial aura of authority grants various bonuses.

\textbf{9} \linkspell{Gate}\textsuperscript{X}: Connects two planes for travel or summoning.

%%%
\subsubsection{Good Domain}
%%%

\textbf{Granted Power}: You cast good spells at +1 caster level.

\textbf{Good Domain Spells}

\textbf{1} \linkspell{Protection From Evil}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\textbf{2} \linkspell{Aid}: +1 on attack rolls, +1 on saves against fear, 1d8 temporary hp +1/level (max +10).

\textbf{3} \linkspell{Magic Circle Against Evil}: As \linkspell{Protection From Evil}{Protection} spell, but 10-ft. radius and 10 min./level.

\textbf{4} \linkspell{Holy Smite}: Damages and blinds evil creatures.

\textbf{5} \linkspell{Dispel Evil}: +4 bonus against attacks by evil creatures.

\textbf{6} \linkspell{Blade Barrier}: Wall of blades deals 1d6/level damage.

\textbf{7} \linkspell{Holy Word}\textsuperscript{F}: Kills, paralyzes, slows, or deafens nongood subjects.

\textbf{8} \linkspell{Holy Aura}: +4 to AC, +4 resistance, and SR 25 against evil spells.

\textbf{9} \linkspell{Summon Monster IX}\textsuperscript{*}: Calls extraplanar creature to fight for you.

\textsuperscript{*}Cast as a good spell only.

%%%
\subsubsection{Healing Domain}
%%%

\textbf{Granted Power}: You cast healing spells at +1 caster level.

\textbf{Healing Domain Spells}

\textbf{1} \linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\textbf{2} \linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\textbf{3} \linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\textbf{4} \linkspell{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\textbf{5} \linkspell{Cure Light Wounds, Mass}: Cures 1d8 damage +1/level (max +25) for many creatures.

\textbf{6} \linkspell{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.

\textbf{7} \linkspell{Regenerate}: Subject's severed limbs grow back, cures 4d8 damage +1/level (max +35).

\textbf{8} \linkspell{Mass Cure Critical Wounds}: Cures 4d8 damage +1/level (max +40) for many creatures.

\textbf{9} \linkspell{Heal, Mass}: As \linkspell{Heal}, but with several subjects.

%%%
\subsubsection{Knowledge Domain}
%%%

\textbf{Granted Power}: Add all Knowledge skills to your list of cleric class skills.

You cast divination spells at +1 caster level.

\textbf{Knowledge Domain Spells}

\textbf{1} \linkspell{Detect Secret Doors}: Reveals hidden doors within 60 ft.

\textbf{2} \linkspell{Detect Thoughts}: Allows "listening" to surface thoughts.

\textbf{3} \linkspell{Clairaudience/Clairvoyance}: Hear or see at a distance for 1 min./level.

\textbf{4} \linkspell{Divination}\textsuperscript{M}: Provides useful advice for specific proposed actions.

\textbf{5} \linkspell{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.

\textbf{6} \linkspell{Find the Path}: Shows most direct way to a location.

\textbf{7} \linkspell{Legend Lore}\textsuperscript{M}\textsuperscript{F}: Lets you learn tales about a person, place, or thing.

\textbf{8} \linkspell{Discern Location}: Reveals exact location of creature or object.

\textbf{9} \linkspell{Foresight}: "Sixth sense" warns of impending danger.

%%%
\subsubsection{Law Domain}
%%%

\textbf{Granted Power}: You cast law spells at +1 caster level.

\textbf{Law Domain Spells}

\textbf{1} \linkspell{Protection From Chaos}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\textbf{2} \linkspell{Calm Emotions}: Calms creatures, negating emotion effects.

\textbf{3} \linkspell{Magic Circle Against Chaos}: As \linkspell{Protection From Chaos}{Protection} spell, but 10-ft. radius and 10 min./level.

\textbf{4} \linkspell{Order's Wrath}: Damages and dazes chaotic creatures.

\textbf{5} \linkspell{Dispel Chaos}: +4 bonus against attacks by chaotic creatures.

\textbf{6} \linkspell{Hold Monster}: As \linkspell{Hold Person}, but any creature.

\textbf{7} \linkspell{Dictum}: Kills, paralyzes, slows, or deafens nonlawful subjects.

\textbf{8} \linkspell{Shield of Law}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against chaotic spells.

\textbf{9} \linkspell{Summon Monster IX}\textsuperscript{*}: Calls extraplanar creature to fight for you.

\textsuperscript{*}Cast as a law spell only.

%%%
\subsubsection{Liberation Domain}
%%%

\textbf{Granted Power}: The character gains a +2 morale bonus on all saving throws against enchantment spells or effects.

\textbf{Liberation Domain Spells}

\textbf{1} \linkspell{Remove Fear}: Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.

\textbf{2} \linkspell{Remove Paralysis}:  Frees one or more creatures from paralysis or \linkspell{Slow} effect.

\textbf{3} \linkspell{Remove Curse}: Frees object or person from curse.

\textbf{4} \linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\textbf{5} \linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\textbf{6} \linkspell{Greater Dispel Magic}: As \linkspell{Dispel Magic}, but +20 on check.

\textbf{7} \linkspell{Refuge}\textsuperscript{M}: Alters item to transport its possessor to you.

\textbf{8} \linkspell{Mind Blank}: Subject is immune to mental/emotional magic and scrying.

\textbf{9} \linkspell{Freedom}: Releases creature from \linkspell{Imprisonment}.

%%%
\subsubsection{Luck Domain}
%%%

\textbf{Granted Power}: You gain the power of good fortune, which is usable once per day. This extraordinary ability allows you to reroll one roll that you have just made before the DM declares whether the roll results in success or failure. 
You must take the result of the reroll, even if it's worse than the original roll.

\textbf{Luck Domain Spells}

\textbf{1} \linkspell{Entropic Shield}: Ranged attacks against you have 20\% miss chance.

\textbf{2} \linkspell{Aid}: +1 on attack rolls, +1 against fear, 1d8 temporary hp +1/level 
(max +10).

\textbf{3} \linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

\textbf{4} \linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\textbf{5} \linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\textbf{6} \linkspell{Mislead}: Turns you invisible and creates illusory double.

\textbf{7} \linkspell{Spell Turning}: Reflect 1d4+6 spell levels back at caster.

\textbf{8} \linkspell{Moment of Prescience}: You gain insight bonus on single attack roll, check, or save.

\textbf{9} \linkspell{Miracle}\textsuperscript{X}: Requests a deity's intercession.

%%%
\subsubsection{Madness Domain}
%%%

\textbf{Granted Power}: The character gains an Insanity score equal to half his or her class level. For spellcasting (determining bonus spells and DCs), the character uses his or her Wisdom score plus his or her Insanity score in place of Wisdom alone.

For all other purposes, such as skills and saves, use Wisdom minus Insanity in place of Wisdom. 

Once per day, the character can see and act with the clarity of true madness. Use the character's Insanity score as a positive rather than a negative modifier on a single roll involving Wisdom. Choose to use this power before the roll is made.

\textbf{Madness Domain Spells}

\textbf{1} \linkspell{Lesser Confusion}: One creature is \linkspell{Confusion}{Confused} for 1 round.

\textbf{2} \linkspell{Touch of Madness}: Touch attack dazes target for 1round/level.

\textbf{3} \linkspell{Rage}: Gives +2 to Str and Con, +1 on Will saves, -2 to AC.

\textbf{4} \linkspell{Confusion}: Subjects behave oddly for 1 round/level.

\textbf{5} \linkspell{Bolts of Bedevilment}: Launch rays that daze for 1d3 rounds each for 1round/level.

\textbf{6} \linkspell{Phantasmal Killer}: Fearsome illusion kills subject or deals 3d6 damage.

\textbf{7} \linkspell{Insanity}: Subject suffers continuous \linksec{Confused}{Confusion}.

\textbf{8} \linkspell{Maddening Scream}: Forces target to uncontrollably run around screaming.

\textbf{9} \linkspell{Weird}: As \linkspell{Phantasmal Killer}, but affects all within 30 ft.

%%%
\subsubsection{Magic Domain}
%%%

\textbf{Granted Power}: Use scrolls, wands, and other devices with spell completion or spell trigger activation as a \linkclass{Wizard} of one-half your cleric level (at least 1st level). For the purpose of using a scroll or other magic device, if you are also a wizard, actual wizard levels and these effective wizard levels stack.

\textbf{Magic Domain Spells}

\textbf{1} \linkspell{Magic Aura}: Alters object's magic aura.

\textbf{2} \linkspell{Identify}: Determines properties of magic item.

\textbf{3} \linkspell{Dispel Magic}: Cancels magical spells and effects.

\textbf{4} \linkspell{Imbue With Spell Ability}: Transfer spells to subject.

\textbf{5} \linkspell{Spell Resistance}: Subject gains SR 12 + level.

\textbf{6} \linkspell{Antimagic Field}: Negates magic within 10 ft.

\textbf{7} \linkspell{Spell Turning}: Reflect 1d4+6 spell levels back at caster.

\textbf{8} \linkspell{Protection From Spells}\textsuperscript{M}\textsuperscript{F}: Confers +8 resistance bonus.

\textbf{9} \linkspell{Mage's Disjunction}: Dispels magic, disenchants magic items.

%%%
\subsubsection{Nobility Domain}
%%%

\textbf{Granted Power}: The character has the spell-like ability to inspire allies, giving them a +2 morale bonus on saving throws, attack rolls, ability checks, skill checks, and weapon damage rolls. Allies must be able to hear the character speak for 1 round. Using this ability is a standard action. It lasts a number of rounds equal to the character's Charisma bonus and can be used once per day.

\textbf{Nobility Domain Spells}

\textbf{1} \linkspell{Divine Favor}: You gain +1 per three levels on attack and damage rolls.

\textbf{2} \linkspell{Enthrall}: Captivates all within 100 ft. + 10 ft./level.

\textbf{3} \linkspell{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

\textbf{4} \linkspell{Discern Lies}: Reveals deliberate falsehoods.

\textbf{5} \linkspell{Greater Command}: As \linkspell{Command}, but affects one subject/level.

\textbf{6} \linkspell{Geas/Quest}{Quest}: As \linkspell{Lesser Geas}, plus it affects any creature.

\textbf{7} \linkspell{Repulsion}: Creatures can't approach you.

\textbf{8} \linkspell{Demand}: As \linkspell{Sending}, plus you can send \linkspell{Suggestion}.

\textbf{9} \linkspell{Storm of Vengeance}: Storm rains acid, lightning, and hail.

%%%
\subsubsection{Plant Domain}
%%%

\textbf{Granted Powers}: Rebuke or command plant creatures as an evil cleric rebukes or commands undead. Use this ability a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

Add \linkskill{Knowledge} (nature) to your list of cleric class skills.

\textbf{Plant Domain Spells}

\textbf{1} \linkspell{Entangle}: Plants entangle everyone in 40-ft.-radius.

\textbf{2} \linkspell{Barkskin}: Grants +2 (or higher) enhancement to natural armor.

\textbf{3} \linkspell{Plant Growth}: Grows vegetation, improves crops.

\textbf{4} \linkspell{Command Plants}: Sway the actions of one or more plant creatures.

\textbf{5} \linkspell{Wall of Thorns}: Thorns damage anyone who tries to pass.

\textbf{6} \linkspell{Repel Wood}: Pushes away wooden objects.

\textbf{7} \linkspell{Animate Plants}: One or more trees animate and fight for you.

\textbf{8} \linkspell{Control Plants}: Control actions of one or more plant creatures.

\textbf{9} \linkspell{Shambler}: Summons 1d4+2 shambling mounds to fight for you.

%%%
\subsubsection{Protection}
%%%

\textbf{Granted Power}: You can generate a protective ward as a supernatural ability. Granting someone you touch a resistance bonus equal to your cleric level on his or her next saving throw. Activating this power is a standard action. The protective ward is an abjuration effect with a duration of 1 hour that is usable once per day.

\textbf{Protection Domain Spells}

\textbf{1} \linkspell{Sanctuary}: Opponents can't attack you, and you can't attack.

\textbf{2} \linkspell{Shield Other}\textsuperscript{F}: You take half of subject's damage.

\textbf{3} \linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

\textbf{4} \linkspell{Spell Immunity}: Subject is immune to one spell per four levels.

\textbf{5} \linkspell{Spell Resistance}: Subject gains SR 12 + level.

\textbf{6} \linkspell{Antimagic Field}: Negates magic within 10 ft.

\textbf{7} \linkspell{Repulsion}: Creatures can't approach you.

\textbf{8} \linkspell{Mind Blank}: Subject is immune to mental/emotional magic and scrying.

\textbf{9} \linkspell{Prismatic Sphere}: As \linkspell{Prismatic Wall}, but surrounds on all sides.

%%%
\subsubsection{Repose Domain}
%%%

The Repose domain is similar to the Death domain, but is granted by good-aligned deities whose clerics are barred from casting evil spells.

\textbf{Granted Power}: The character may use a \textit{Death Touch} once per day. The \textit{Death Touch} is a spell-like ability that is a death effect. The character must succeed at a melee touch attack against a living creature (using the rules for touch spells). When the character touches, roll 1d6 per his or her cleric level. If the total at least equals the creature's current hit points, it dies.

\textbf{Repose Domain Spells}

\textbf{1} \linkspell{Deathwatch}: Reveals how near death subjects within 30 ft. are.

\textbf{2} \linkspell{Gentle Repose}: Preserves one corpse.

\textbf{3} \linkspell{Speak With Dead}: Corpse answers one question/two levels.

\textbf{4} \linkspell{Death Ward}: Grants immunity to death spells and negative energy effects.

\textbf{5} \linkspell{Slay Living}: Touch attack kills subject.

\textbf{6} \linkspell{Undeath to Death}: \textsuperscript{M}: Destroys 1d4/level HD of undead (max 20d4).

\textbf{7} \linkspell{Destruction}: \textsuperscript{F}: Kills subject and destroys remains.

\textbf{8} \linkspell{Surelife}: Protect yourself against non-magical, non-creature forms of certain death (swimming in lava, airless rooms, etc)

\textbf{9} \linkspell{Wail of the Banshee}: Kills one creature/level.

%%%
\subsubsection{Rune Domain}
%%%

\textbf{Granted Power}: Free Scribe Scroll feat.

\textbf{Rune Domain Spells}

\textbf{1} \linkspell{Erase}: Mundane or magical writing vanishes.

\textbf{2} \linkspell{Secret Page}: Changes one page to hide its real content.

\textbf{3} \linkspell{Glyph of Warding}: \textsuperscript{M}: Inscription harms those who pass it.

\textbf{4} \linkspell{Explosive Runes}: Deals 6d6 damage when read.

\textbf{5} \linkspell{Lesser Planar Binding}: Traps extraplanar creature of 6 HD or less until it performs a task.

\textbf{6} \linkspell{Greater Glyph of Warding}: As \linkspell{Glyph of Warding}, but up to 10d8 damage or 6th-level spell.

\linkspell{Instant Summons}\textsuperscript{M}: Prepared object appears in your hand.

\textbf{8} \linkspell{Symbol of Death}{Symbol} (any type): \textsuperscript{M}: Triggered rune has various effects

\textbf{9} \linkspell{Teleportation Circle}\textsuperscript{M}: Circle teleports any creature inside to designated spot.

%%%
\subsubsection{Scalykind Domain}
%%%

\textbf{Granted Power}: Rebuke or command animals (reptilian creatures and snakes only) as an evil cleric rebukes or commands undead. Use this ability a total number of times per day equal to 3 + Charisma modifier.

\textbf{Scalykind Domain Spells}

\textbf{1} \linkspell{Magic Fang}: One natural weapon of subject creature gets +1 on attack and damage rolls.

\textbf{2} \linkspell{Animal Trance}\textsuperscript{*}: Fascinates 2d6 HD of animals.

\textbf{3} \linkspell{Greater Magic Fang}: One natural weapon of subject creature gets +1/four levels on attack and damage rolls (max +5).

\textbf{4} \linkspell{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\textbf{5} \linkspell{Animal Growth}\textsuperscript{*}: One animal/two levels doubles in size.

\textbf{6} \linkspell{Eyebite}: Target becomes panicked, sickened, and comatose.

\textbf{7} \linkspell{Creeping Doom}: Swarms of \sout{centipedes} \textit{tiny snakes} attack at your command.

\textbf{8} \linkspell{Animal Shapes}\textsuperscript{*}: One ally/level polymorphs into chosen animal.

\textbf{9} \linkspell{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.

\textsuperscript{*}Affects ophidian or reptilian creatures only.

%%%
\subsubsection{Strength Domain}
%%%

\textbf{Granted Power}: You can perform a feat of strength as a supernatural ability. You gain an enhancement bonus to Strength equal to your cleric level. Activating the power is a free action, the power lasts 1 round, and it is usable once per day.

\textbf{Strength Domain Spells}

\textbf{1} \linkspell{Enlarge Person}: Humanoid creature doubles in size.

\textbf{2} \linkspell{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\textbf{3} \linkspell{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

\textbf{4} \linkspell{Spell Immunity}: Subject is immune to one spell per four levels.

\textbf{5} \linkspell{Righteous Might}: Your size increases, and you gain combat bonuses.

\textbf{6} \linkspell{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.

\textbf{7} \linkspell{Grasping Hand}: Large hand provides cover, pushes, or grapples.

\textbf{8} \linkspell{Clenched Fist}: Large hand provides cover, pushes, or attacks your foes.

\textbf{9} \linkspell{Crushing Hand}: Large hand provides cover, pushes, or crushes your foes.

%%%
\subsubsection{Sun Domain}
%%%

\textbf{Granted Power}: Once per day, you can perform a greater turning against undead in place of a regular turning. The greater turning is like a normal turning except that the undead creatures that would be turned are destroyed instead.

\textbf{Sun Domain Spells}

\textbf{1} \linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\textbf{2} \linkspell{Heat Metal}: Make metal so hot it damages those who touch it.

\textbf{3} \linkspell{Searing Light}: Ray deals 1d8/two levels, more against undead.

\textbf{4} \linkspell{Fire Shield}: Creatures attacking you take fire damage; you're protected from heat or cold.

\textbf{5} \linkspell{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\textbf{6} \linkspell{Fire Seeds}: Acorns and berries become grenades and bombs.

\textbf{7} \linkspell{Sunbeam}: Beam blinds and deals 4d6 damage.

\textbf{8} \linkspell{Sunburst}: Blinds all within 10 ft., deals 6d6 damage.

\textbf{9} \linkspell{Prismatic Sphere}: As \linkspell{Prismatic Wall}, but surrounds on all sides.

%%%
\subsubsection{Travel Domain}
%%%

\textbf{Granted Powers}: For a total time per day of 1 round per cleric level you possess, you can act normally regardless of magical effects that impede movement as if you were affected by the spell \linkspell{Freedom of Movement}. This effect occurs automatically as soon as it applies, lasts until it runs out or is no longer needed, and can operate multiple times per day (up to the total daily limit of rounds). This granted power is a supernatural ability.

Add \linkskill{Survival} to your list of cleric class skills.

\textbf{Travel Domain Spells}

\textbf{1} \linkspell{Longstrider}: Increases your speed.

\textbf{2} \linkspell{Locate Object}: Senses direction toward object (specific or type).

\textbf{3} \linkspell{Fly}: Subject flies at speed of 60 ft.

\textbf{4} \linkspell{Dimension Door}: Teleports you short distance.

\textbf{5} \linkspell{Teleport}: Instantly transports you as far as 100 miles/level.

\textbf{6} \linkspell{Find the Path}: Shows most direct way to a location.

\textbf{7} \linkspell{Teleport, Greater}: As \linkspell{Teleport}, but no range limit and no off-target arrival.

\textbf{8} \linkspell{Phase Door}: Creates an invisible passage through wood or stone.

\textbf{9} \linkspell{Astral Projection}\textsuperscript{M}: Projects you and companions onto Astral Plane.

%%%
\subsubsection{Tickery Domain}
%%%

\textbf{Granted Power}: Add \linkskill{Bluff}, \linkskill{Disguise}, and \linkskill{Hide} to your list of cleric class skills.

\textbf{Trickery Domain Spells}

\textbf{1} \linkspell{Disguise Self}: Disguise own appearance.

\textbf{2} \linkspell{Invisibility}: Subject invisible 1 min./level or until it attacks.

\textbf{3} \linkspell{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.

\textbf{4} \linkspell{Confusion}: Subjects behave oddly for 1 round/level.

\textbf{5} \linkspell{False Vision}\textsuperscript{M}: Fools scrying with an illusion.

\textbf{6} \linkspell{Mislead}: Turns you invisible and creates illusory double.

\textbf{7} \linkspell{Screen}: Illusion hides area from vision, scrying.

\textbf{8} \linkspell{Polymorph Any Object}: Changes any subject into anything else.

\textbf{9} \linkspell{Time Stop}: You act freely for 1d4+1 rounds.

%%%
\subsubsection{War Domain}
%%%

\textbf{Granted Power}: Free \linkfeat{Martial Weapon Proficiency} with deity's favored weapon (if necessary) and \linkfeat{Weapon Focus} with the deity's favored weapon.

\textbf{War Domain Spells}

\textbf{1} \linkspell{Magic Weapon}: Weapon gains +1 bonus.

\textbf{2} \linkspell{Spiritual Weapon}: Magical weapon attacks on its own.

\textbf{3} \linkspell{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

\textbf{4} \linkspell{Divine Power}: You gain attack bonus, +6 to Str, and 1 hp/level.

\textbf{5} \linkspell{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\textbf{6} \linkspell{Blade Barrier}: Wall of blades deals 1d6/level damage.

\textbf{7} \linkspell{Power Word Blind}: Blinds creature with 200 hp or less.

\textbf{8} \linkspell{Power Word Stun}: Stuns creature with 150 hp or less.

\textbf{9} \linkspell{Power Word Kill}: Kills creature with 100 hp or less.

%%%
\subsubsection{Water Domain}
%%%

\textbf{Granted Power}: Turn or destroy fire creatures as a good cleric turns undead. Rebuke, command, or bolster water creatures as an evil cleric rebukes undead. Use these abilities a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

\textbf{Water Domain Spells}

\textbf{1} \linkspell{Obscuring Mist}: Fog surrounds you.

\textbf{2} \linkspell{Fog Cloud}: Fog obscures vision.

\textbf{3} \linkspell{Water Breathing}: Subjects can breathe underwater.

\textbf{4} \linkspell{Control Water}: Raises or lowers bodies of water.

\textbf{5} \linkspell{Ice Storm}: Hail deals 5d6 damage in cylinder 40 ft. across.

\textbf{6} \linkspell{Cone of Cold}: 1d6/level cold damage.

\textbf{7} \linkspell{Acid Fog}: Fog deals acid damage.

\textbf{8} \linkspell{Horrid Wilting}: Deals 1d6/level damage within 30 ft.

\textbf{9} \linkspell{Elemental Swarm}\textsuperscript{*}: Summons multiple elementals.

\textsuperscript{*}Cast as a water spell only.

%%%
\subsubsection{Weather Domain}
%%%

\textbf{Granted Power}: \linkskill{Survival} is a class skill.

\textbf{Weather Domain Spells}

\textbf{1} \linkspell{Obscuring Mist}: Fog surrounds you.

\textbf{2} \linkspell{Fog Cloud}: Fog obscures vision.

\textbf{3} \linkspell{Call Lightning}: Calls down lightning bolts (3d6 per bolt) from sky.

\textbf{4} \linkspell{Sleet Storm}: Hampers vision and movement.

\textbf{5} \linkspell{Ice Storm}: Hail deals 5d6 damage in cylinder 40 ft. across.

\textbf{6} \linkspell{Control Winds}: Change wind direction and speed.

\textbf{7} \linkspell{Control Weather}: Cyclone deals damage and can pick up creatures.

\textbf{8} \linkspell{Whirlwind}: Cyclone deals damage and can pick up creatures.

\textbf{9} \linkspell{Storm of Vengeance}: Storm rains acid, lightning, and hail.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Druid Spells}\index{Druid Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{0th Level Druid Spells (Orisons)}
%%%

\linkspell{Create Water}: Creates 2 gallons/level of pure water.

\linkspell{Cure Minor Wounds}: Cures 1 point of damage.

\linkspell{Detect Magic}: Detects spells and magic items within 60 ft.

\linkspell{Detect Poison}: Detects poison in one creature or object.

\linkspell{Flare}: Dazzles one creature (-1 penalty on attack rolls).

\linkspell{Guidance}: +1 on one attack roll, saving throw, or skill check.

\linkspell{Know Direction}: You discern north.

\linkspell{Light}: Object shines like a torch.

\linkspell{Mending}: Makes minor repairs on an object.

\linkspell{Purify Food and Drink}: Purifies 1 cu. ft./level of food or water.

\linkspell{Read Magic}: Read scrolls and spellbooks.

\linkspell{Resistance}: Subject gains +1 bonus on saving throws.

\linkspell{Virtue}: Subject gains 1 temporary hp.

%%%
\subsubsection{1st Level Druid Spells}
%%%

\linkspell{Calm Animals}: Calms (2d4 + level) HD of animals.

\linkspell{Charm Animal}: Makes one animal your friend.

\linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\linkspell{Detect Animals or Plants}: Detects kinds of animals or plants.

\linkspell{Detect Snares and Pits}: Reveals natural or primitive traps.

\linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\linkspell{Entangle}: Plants entangle everyone in 40-ft.-radius.

\linkspell{Faerie Fire}: Outlines subjects with light, canceling \linkspell{Blur}, concealment, and the like.

\linkspell{Goodberry}: 2d4 berries each cure 1 hp (max 8 hp/24 hours).

\linkspell{Hide from Animals}: Animals can't perceive one subject/level.

\linkspell{Jump}: Subject gets bonus on Jump checks.

\linkspell{Longstrider}: Your speed increases by 10 ft.

\linkspell{Magic Fang}: One natural weapon of subject creature gets +1 on attack and damage rolls.

\linkspell{Magic Stone}: Three stones gain +1 on attack rolls, deal 1d6+1 damage.

\linkspell{Obscuring Mist}: Fog surrounds you.

\linkspell{Pass Without Trace}: One subject/level leaves no tracks.

\linkspell{Produce Flame}: 1d6 damage +1/level, touch or thrown.

\linkspell{Shillelagh}: Cudgel or quarterstaff becomes +1 weapon (1d10 damage) for 1 min./level.

\linkspell{Speak With Animals}: You can communicate with animals.

\linkspell{Summon Nature's Ally I}: Calls creature to fight.

%%%
\subsubsection{2nd Level Druid Spells}
%%%

\linkspell{Animal Messenger}: Sends a Tiny animal to a specific place.

\linkspell{Animal Trance}: Fascinates 2d6 HD of animals.

\linkspell{Barkskin}: Grants +2 (or higher) enhancement to natural armor.

\linkspell{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\linkspell{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\linkspell{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\linkspell{Chill Metal}: Cold metal damages those who touch it.

\linkspell{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\linkspell{Fire Trap}\textsuperscript{M}: Opened object deals 1d4+1/level damage.

\linkspell{Flame Blade}: Touch attack deals 1d8 +1/two levels damage.

\linkspell{Flaming Sphere}: Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.

\linkspell{Fog Cloud}: Fog obscures vision.

\linkspell{Gust of Wind}: Blows away or knocks down smaller creatures.

\linkspell{Heat Metal}: Make metal so hot it damages those who touch it.

\linkspell{Hold Animal}: Paralyzes one animal for 1 round/level.

\linkspell{Lesser Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.

\linkspell{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\linkspell{Reduce Animal}: Shrinks one willing animal.

\linkspell{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\linkspell{Soften Earth and Stone}: Turns stone to clay or dirt to sand or mud.

\linkspell{Spider Climb}: Grants ability to walk on walls and ceilings.

\linkspell{Summon Nature's Ally II}: Calls creature to fight.

\linkspell{Summon Swarm}: Summons swarm of bats, rats, or spiders.

\linkspell{Tree Shape}: You look exactly like a tree for 1 hour/level.

\linkspell{Warp Wood}: Bends wood (shaft, handle, door, plank).

\linkspell{Wood Shape}: Rearranges wooden objects to suit you.

%%%
\subsubsection{3rd Level Druid Spells}
%%%

\linkspell{Call Lightning}: Calls down lightning bolts (3d6 per bolt) from sky.

\linkspell{Contagion}: Infects subject with chosen disease.

\linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\linkspell{Daylight}: 60-ft. radius of bright light.

\linkspell{Diminish Plants}: Reduces size or blights growth of normal plants.

\linkspell{Dominate Animal}: Subject animal obeys silent mental commands.

\linkspell{Greater Magic Fang}: One natural weapon of subject creature gets +1/four levels on attack and damage rolls (max +5).

\linkspell{Meld into Stone}: You and your gear merge with stone.

\linkspell{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\linkspell{Plant Growth}: Grows vegetation, improves crops.

\linkspell{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

\linkspell{Quench}: Extinguishes nonmagical fires or one magic item.

\linkspell{Remove Disease}: Cures all diseases affecting subject.

\linkspell{Sleet Storm}: Hampers vision and movement.

\linkspell{Snare}: Creates a magic booby trap.

\linkspell{Speak with Plants}: You can talk to normal plants and plant creatures.

\linkspell{Spike Growth}: Creatures in area take 1d4 damage, may be \linkspell{Slow}{Slowed}.

\linkspell{Stone Shape}: Sculpts stone into any shape.

\linkspell{Summon Nature's Ally III}: Calls creature to fight.

\linkspell{Water Breathing}: Subjects can breathe underwater.

\linkspell{Wind Wall}: Deflects arrows, smaller creatures, and gases.

%%%
\subsubsection{4th Level Druid Spells}
%%%

\linkspell{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

\linkspell{Antiplant Shell}: Keeps animated plants at bay.

\linkspell{Blight}: Withers one plant or deals 1d6/level damage to plant creature.

\linkspell{Command Plants}: Sway the actions of one or more plant creatures.

\linkspell{Control Water}: Raises or lowers bodies of water.

\linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\linkspell{Dispel Magic}: Cancels spells and magical effects.

\linkspell{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\linkspell{Giant Vermin}: Turns centipedes, scorpions, or spiders into giant vermin.

\linkspell{Ice Storm}: Hail deals 5d6 damage in cylinder 40 ft. across.

\linkspell{Reincarnate}: Brings dead subject back in a random body.

\linkspell{Repel Vermin}: Insects, spiders, and other vermin stay 10 ft. away.

\linkspell{Rusting Grasp}: Your touch corrodes iron and alloys.

\linkspell{Scrying}\textsuperscript{F}: Spies on subject from a distance.

\linkspell{Spike Stones}: Creatures in area take 1d8 damage, may be \linkspell{Slow}{Slowed}.

\linkspell{Summon Nature's Ally IV}: Calls creature to fight.

%%%
\subsubsection{5th Level Druid Spells}
%%%

\linkspell{Animal Growth}: One animal/two levels doubles in size.

\linkspell{Atonement}: Removes burden of misdeeds from subject.

\linkspell{Awaken}\textsuperscript{X}: Animal or tree gains human intellect.

\linkspell{Baleful Polymorph}: Transforms subject into harmless animal.

\linkspell{Call Lightning Storm}: As \linkspell{Call Lightning}, but 5d6 damage per bolt.

\linkspell{Commune with Nature}: Learn about terrain for 1 mile/level.

\linkspell{Control Winds}: Change wind direction and speed.

\linkspell{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\linkspell{Death Ward}: Grants immunity to all death spells and negative energy effects.

\linkspell{Hallow}\textsuperscript{M}: Designates location as holy.

\linkspell{Insect Plague}: Locust swarms attack creatures.

\linkspell{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.

\linkspell{Summon Nature's Ally V}: Calls creature to fight.

\linkspell{Transmute Mud to Rock}: Transforms two 10-ft. cubes per level.

\linkspell{Transmute Rock to Mud}: Transforms two 10-ft. cubes per level.

\linkspell{Tree Stride}: Step from one tree to another far away.

\linkspell{Unhallow}\textsuperscript{M}: Designates location as unholy.

\linkspell{Wall of Fire}: Deals 2d4 fire damage out to 10 ft. and 1d4 out to 20 ft. 
Passing through wall deals 2d6 damage +1/level.

\linkspell{Wall of Thorns}: Thorns damage anyone who tries to pass.

%%%
\subsubsection{6th Level Druid Spells}
%%%

\linkspell{Antilife Shell}: 10-ft.-radius field hedges out living creatures.

\linkspell{Find the Path}: Shows most direct way to a location.

\linkspell{Fire Seeds}: Acorns and berries become grenades and bombs.

\linkspell{Greater Dispel Magic}: As \linkspell{Dispel Magic}, but +20 on check.

\linkspell{Ironwood}: Magic wood is strong as steel.

\linkspell{Liveoak}: Oak becomes treant guardian.

\linkspell{Move Earth}: Digs trenches and builds hills.

\linkspell{Mass Bear's Endurance}: As \linkspell{Bear's Endurance}, affects one subject/ level.

\linkspell{Mass Bull's Strength}: As \linkspell{Bull's Strength}, affects one subject/level.

\linkspell{Mass Cat's Grace}: As \linkspell{Cat's Grace}, affects one subject/level.

\linkspell{Mass Cure Light Wounds}: Cures 1d8 damage +1/level for many creatures.

\linkspell{Mass Owl's Wisdom}: As \linkspell{Owl's Wisdom}, affects one subject/level.

\linkspell{Repel Wood}: Pushes away wooden objects.

\linkspell{Spellstaff}: Stores one spell in wooden quarterstaff.

\linkspell{Stone Tell}: Talk to natural or worked stone.

\linkspell{Summon Nature's Ally VI}: Calls creature to fight.

\linkspell{Transport Via Plants}: Move instantly from one plant to another of the same kind.

\linkspell{Wall of Stone}: Creates a stone wall that can be shaped.

%%%
\subsubsection{7th Level Druid Spells}
%%%

\linkspell{Animate Plants}: One or more plants animate and fight for you.

\linkspell{Changestaff}: Your staff becomes a treant on command.

\linkspell{Control Weather}: Cyclone deals damage and can pick up creatures.

\linkspell{Creeping Doom}: Swarms of centipedes attack at your command.

\linkspell{Mass Cure Moderate Wounds}: Cures 2d8 damage +1/level for many creatures.

\linkspell{Fire Storm}: Deals 1d6/level fire damage.

\linkspell{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.

\linkspell{Greater Scrying}: As \linkspell{Scrying}, but faster and longer.

\linkspell{Summon Nature's Ally VII}: Calls creature to fight.

\linkspell{Sunbeam}: Beam blinds and deals 4d6 damage.

\linkspell{Transmute Metal to Wood}: Metal within 40 ft. becomes wood.

\linkspell{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.

\linkspell{Wind Walk}: You and your allies turn vaporous and travel fast.

%%%
\subsubsection{8th Level Druid Spells}
%%%

\linkspell{Animal Shapes}: One ally/level polymorphs into chosen animal.

\linkspell{Control Plants}: Control actions of one or more plant creatures.

\linkspell{Mass Cure Serious Wounds}: Cures 3d8 damage +1/level for many creatures.

\linkspell{Earthquake}: Intense tremor shakes 80-ft.-radius.

\linkspell{Finger of Death}: Kills one subject.

\linkspell{Repel Metal or Stone}: Pushes away metal and stone.

\linkspell{Reverse Gravity}: Objects and creatures fall upward.

\linkspell{Summon Nature's Ally VIII}: Calls creature to fight.

\linkspell{Sunburst}: Blinds all within 10 ft., deals 6d6 damage.

\linkspell{Whirlwind}: Cyclone deals damage and can pick up creatures.

\linkspell{Word of Recall}: Teleports you back to designated place.

%%%
\subsubsection{9th Level Druid Spells}
%%%

\linkspell{Antipathy}: Object or location affected by spell repels certain creatures.

\linkspell{Mass Cure Critical Wounds}: Cures 4d8 damage +1/level for many creatures.

\linkspell{Elemental Swarm}: Summons multiple elementals.

\linkspell{Foresight}: "Sixth sense" warns of impending danger.

\linkspell{Regenerate}: Subject's severed limbs grow back, cures 4d8 damage +1/level (max +35).

\linkspell{Shambler}: Summons 1d4+2 shambling mounds to fight for you.

\linkspell{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.

\linkspell{Storm of Vengeance}: Storm rains acid, lightning, and hail.

\linkspell{Summon Nature's Ally IX}: Calls creature to fight.

\linkspell{Sympathy}\textsuperscript{M}: Object or location attracts certain creatures.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Paladin Spells}\index{Paladin Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{1st Level Paladin Spells}
%%%

\linkspell{Bless}: Allies gain +1 on attack rolls and +1 on saves against fear.

\linkspell{Bless Water}: Makes holy water.

\linkspell{Bless Weapon}: Weapon strikes true against evil foes.

\linkspell{Create Water}: Creates 2 gallons/level of pure water.

\linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\linkspell{Detect Poison}: Detects poison in one creature or small object.

\linkspell{Detect Undead}: Reveals undead within 60 ft.

\linkspell{Divine Favor}: You gain +1 per three levels on attack and damage rolls.

\linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\linkspell{Lesser Restoration}: Dispels magical ability penalty or repairs 1d4 ability damage.

\linkspell{Magic Weapon}: Weapon gains +1 bonus.

\linkspell{Protection From Chaos}/\linkspell{Protection From Evil}{Evil}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\linkspell{Read Magic}: Read scrolls and spellbooks.

\linkspell{Resistance}: Subject gains +1 on saving throws.

\linkspell{Virtue}: Subject gains 1 temporary hp.

%%%
\subsubsection{2nd Level Paladin Spells}
%%%

\linkspell{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\linkspell{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\linkspell{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\linkspell{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\linkspell{Remove Paralysis}: Frees one or more creatures from paralysis or \linkspell{Slow} effect.

\linkspell{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\linkspell{Shield Other}\textsuperscript{F}: You take half of subject's damage.

\linkspell{Undetectable Alignment}: Conceals alignment for 24 hours.

\linkspell{Zone of Truth}: Subjects within range cannot lie.

%%%
\subsubsection{3rd Level Paladin Spells}
%%%

\linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\linkspell{Daylight}: 60-ft. radius of bright light.

\linkspell{Discern Lies}: Reveals deliberate falsehoods.

\linkspell{Dispel Magic}: Cancels spells and magical effects.

\linkspell{Greater Magic Weapon}: +1 bonus/four levels (max +5).

\linkspell{Heal Mount}: As \linkspell{Heal} on warhorse or other special mount.

\linkspell{Magic Circle Against Chaos}: As \linkspell{Protection From Chaos}, but 10-ft. radius and 10 min./level.

\linkspell{Magic Circle Against Evil}: As \linkspell{Protection From Evil}, but 10-ft. radius and 10 min./level.

\linkspell{Prayer}: Allies +1 bonus on most rolls, enemies -1 penalty.

\linkspell{Remove Blindness/Deafness}: Cures normal or magical conditions.

\linkspell{Remove Curse}: Frees object or person from curse.

%%%
\subsubsection{4th Level Paladin Spells}
%%%

\linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\linkspell{Death Ward}: Grants immunity to death spells and negative energy effects.

\linkspell{Dispel Chaos}: +4 bonus against attacks by chaotic creatures.

\linkspell{Dispel Evil}: +4 bonus against attacks by evil creatures.

\linkspell{Holy Sword}: Weapon becomes +5, deals +2d6 damage against evil.

\linkspell{Mark of Justice}: Designates action that will trigger curse on subject.

\linkspell{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\linkspell{Restoration}\textsuperscript{M}: Restores level and ability score drains.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ranger Spells}\index{Ranger Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{1st Level Ranger Spells}
%%%

\linkspell{Alarm}: Wards an area for 2 hours/level.

\linkspell{Animal Messenger}: Sends a Tiny animal to a specific place.

\linkspell{Calm Animals}: Calms (2d4 + level) HD of animals.

\linkspell{Charm Animal}: Makes one animal your friend.

\linkspell{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\linkspell{Detect Animals or Plants}: Detects kinds of animals or plants.

\linkspell{Detect Poison}: Detects poison in one creature or object.

\linkspell{Detect Snares and Pits}: Reveals natural or primitive traps.

\linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\linkspell{Entangle}: Plants entangle everyone in 40-ft.-radius circle.

\linkspell{Hide from Animals}: Animals can't perceive one subject/level.

\linkspell{Jump}: Subject gets bonus on Jump checks.

\linkspell{Longstrider}: Increases your speed.

\linkspell{Magic Fang}: One natural weapon of subject creature gets +1 on attack and damage rolls.

\linkspell{Pass Without Trace}: One subject/level leaves no tracks.

\linkspell{Read Magic}: Read scrolls and spellbooks.

\linkspell{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\linkspell{Speak With Animals}: You can communicate with animals.

\linkspell{Summon Nature's Ally I}: Calls animal to fight for you.

%%%
\subsubsection{2nd Level Ranger Spells}
%%%

\linkspell{Barkskin}: Grants +2 (or higher) enhancement to natural armor.

\linkspell{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\linkspell{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\linkspell{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\linkspell{Hold Animal}: Paralyzes one animal for 1 round/level.

\linkspell{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

\linkspell{Snare}: Creates a magic booby trap.

\linkspell{Speak with Plants}: You can talk to normal plants and plant creatures.

\linkspell{Spike Growth}: Creatures in area take 1d4 damage, may be \linkspell{Slow}{Slowed}.

\linkspell{Summon Nature's Ally II}: Calls animal to fight for you.

\linkspell{Wind Wall}: Deflects arrows, smaller creatures, and gases.

%%%
\subsubsection{3rd Level Ranger Spells}
%%%

\linkspell{Command Plants}: Sway the actions of one or more plant creatures.

\linkspell{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\linkspell{Darkvision}: See 60 ft. in total darkness.

\linkspell{Diminish Plants}: Reduces size or blights growth of normal plants.

\linkspell{Greater Magic Fang}: One natural weapon of subject creature gets +1/three caster levels on attack and damage rolls (max +5).

\linkspell{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\linkspell{Plant Growth}: Grows vegetation, improves crops.

\linkspell{Reduce Animal}: Shrinks one willing animal.

\linkspell{Remove Disease}: Cures all diseases affecting subject.

\linkspell{Repel Vermin}: Insects, spiders, and other vermin stay 10 ft. away.

\linkspell{Summon Nature's Ally III}: Calls animal to fight for you.

\linkspell{Tree Shape}: You look exactly like a tree for 1 hour/level.

\linkspell{Water Walk}: Subject treads on water as if solid.

%%%
\subsubsection{4th Level Ranger Spells}
%%%

\linkspell{Animal Growth}: One animal/two levels doubles in size.

\linkspell{Commune with Nature}: Learn about terrain for 1 mile/level.

\linkspell{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\linkspell{Freedom of Movement}: Subject moves normally despite impediments.

\linkspell{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.

\linkspell{Summon Nature's Ally IV}: Calls animal to fight for you.

\linkspell{Tree Stride}: Step from one tree to another far away.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sorcerer / Wizard Spells}\index{Sorcerer Spells}\index{Wizard Spells}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{0th Level Sorcerer / Wizard Spells (Cantrips)}
%%%

Abjur

\linkspell{Resistance}: Subject gains +1 on saving throws.

Conj

\linkspell{Acid Splash}: Orb deals 1d3 acid damage.

Div

\linkspell{Detect Poison}: Detects poison in one creature or small object.

\linkspell{Detect Magic}: Detects spells and magic items within 60 ft.

\linkspell{Read Magic}: Read scrolls and spellbooks.

Ench

\linkspell{Daze}: Humanoid creature of 4 HD or less loses next action.

Evoc

\linkspell{Dancing Lights}: Creates torches or other lights.

\linkspell{Flare}: Dazzles one creature (-1 on attack rolls).

\linkspell{Light}: Object shines like a torch.

\linkspell{Ray of Frost}: Ray deals 1d3 cold damage.

Illus

\linkspell{Ghost Sound}: Figment sounds.

Necro

\linkspell{Disrupt Undead}: Deals 1d6 damage to one undead.

\linkspell{Touch of Fatigue}: Touch attack fatigues target.

Trans

\linkspell{Mage Hand}: 5-pound telekinesis.

\linkspell{Mending}: Makes minor repairs on an object.

\linkspell{Message}: Whispered conversation at distance.

\linkspell{Open/Close}: Opens or closes small or light things.

Univ

\linkspell{Arcane Mark}: Inscribes a personal rune (visible or invisible).

\linkspell{Prestidigitation}: Performs minor tricks.

%%%
\subsubsection{1st Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Alarm}: Wards an area for 2 hours/level.

\linkspell{Endure Elements}: Exist comfortably in hot or cold environments.

\linkspell{Hold Portal}: Holds door shut.

\linkspell{Protection From Chaos}/\linkspell{Protection From Evil}{Evil}/\linkspell{Protection From Good}{Good}/\linkspell{Protection From Law}{Law}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\linkspell{Shield}: Invisible disc gives +4 to AC, blocks \linkspell{Magic Missile}{Magic Missiles}.

Conj

\linkspell{Grease}: Makes 10-ft. square or one object slippery.

\linkspell{Mage Armor}: Gives subject +4 armor bonus.

\linkspell{Mount}: Summons riding horse for 2 hours/level.

\linkspell{Obscuring Mist}: Fog surrounds you.

\linkspell{Summon Monster I}: Calls extraplanar creature to fight for you.

\linkspell{Unseen Servant}: Invisible force obeys your commands.

Div

\linkspell{Comprehend Languages}: You understand all spoken and written languages.

\linkspell{Detect Secret Doors}: Reveals hidden doors within 60 ft.

\linkspell{Detect Undead}: Reveals undead within 60 ft.

\linkspell{Identify}\textsuperscript{M}: Determines properties of magic item.

\linkspell{True Strike}: +20 on your next attack roll.

Ench

\linkspell{Charm Person}: Makes one person your friend.

\linkspell{Hypnotism}: Fascinates 2d4 HD of creatures.

\linkspell{Sleep}: Puts 4 HD of creatures into magical slumber.

Evoc

\linkspell{Burning Hands}: 1d4/level fire damage (max 5d4).

\linkspell{Floating Disk}: Creates 3-ft.-diameter horizontal disk that holds 100 lb./level.

\linkspell{Magic Missile}: 1d4+1 damage; +1 missile per two levels above 1st (max 5).

\linkspell{Shocking Grasp}: Touch delivers 1d6/level electricity damage (max 5d6).

Illus

\linkspell{Color Spray}: Knocks unconscious, blinds, and/or stuns weak creatures.

\linkspell{Disguise Self}: Changes your appearance.

\linkspell{Magic Aura}: Alters object's magic aura.

\linkspell{Silent Image}: Creates minor illusion of your design.

\linkspell{Ventriloquism}: Throws voice for 1 min./level.

Necro

\linkspell{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\linkspell{Chill Touch}: One touch/level deals 1d6 damage and possibly 1 Str damage.

\linkspell{Ray of Enfeeblement}: Ray deals 1d6 +1 per two levels Str damage.

Trans

\linkspell{Animate Rope}: Makes a rope move at your command.

\linkspell{Enlarge Person}: Humanoid creature doubles in size.

\linkspell{Erase}: Mundane or magical writing vanishes.

\linkspell{Expeditious Retreat}: Your speed increases by 30 ft.

\linkspell{Feather Fall}: Objects or creatures fall slowly.

\linkspell{Jump}: Subject gets bonus on Jump checks.

\linkspell{Magic Weapon}: Weapon gains +1 bonus.

\linkspell{Reduce Person}: Humanoid creature halves in size.

%%%
\subsubsection{2nd Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Arcane Lock}\textsuperscript{M}: Magically locks a portal or chest.

\linkspell{Obscure Object}: Masks object against scrying.

\linkspell{Protection From Arrows}: Subject immune to most ranged attacks.

\linkspell{Resist Energy}: Ignores first 10 (or more) points of damage/attack from specified energy type.

Conj

\linkspell{Acid Arrow}: Ranged touch attack; 2d4 damage for 1 round +1 round/three levels.

\linkspell{Fog Cloud}: Fog obscures vision.

\linkspell{Glitterdust}: Blinds creatures, outlines invisible creatures.

\linkspell{Summon Monster II}: Calls extraplanar creature to fight for you.

\linkspell{Summon Swarm}: Summons swarm of bats, rats, or spiders.

\linkspell{Web}: Fills 20-ft.-radius spread with sticky spiderwebs.

Div

\linkspell{Detect Thoughts}: Allows "listening" to surface thoughts.

\linkspell{Locate Object}: Senses direction toward object (specific or type).

\linkspell{See Invisibility}: Reveals invisible creatures or objects.

Ench

\linkspell{Daze Monster}: Living creature of 6 HD or less loses next action.

\linkspell{Hideous Laughter}: Subject loses actions for 1 round/level.

\linkspell{Touch of Idiocy}: Subject takes 1d6 points of Int, Wis, and Cha damage.

Evoc

\linkspell{Continual Flame}\textsuperscript{M}: Makes a permanent, heatless torch.

\linkspell{Darkness}: 20-ft. radius of supernatural shadow.

\linkspell{Flaming Sphere}: Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.

\linkspell{Gust of Wind}: Blows away or knocks down smaller creatures.

\linkspell{Scorching Ray}: Ranged touch attack deals 4d6 fire damage, +1 ray/four levels (max 3).

\linkspell{Shatter}: Sonic vibration damages objects or crystalline creatures.

Illus

\linkspell{Blur}: Attacks miss subject 20\% of the time.

\linkspell{Hypnotic Pattern}: Fascinates (2d4 + level) HD of creatures.

\linkspell{Invisibility}: Subject is invisible for 1 min./level or until it attacks.

\linkspell{Magic Mouth}\textsuperscript{M}: Speaks once when triggered.

\linkspell{Minor Image}: As \linkspell{Silent Image}, plus some sound.

\linkspell{Mirror Image}: Creates decoy duplicates of you (1d4 +1 per three levels, max 8).

\linkspell{Misdirection}: Misleads divinations for one creature or object.

\linkspell{Phantom Trap}\textsuperscript{M}: Makes item seem trapped.

Necro

\linkspell{Blindness/Deafness}: Makes subject blinded or deafened.

\linkspell{Command Undead}: Undead creature obeys your commands.

\linkspell{False Life}: Gain 1d10 temporary hp +1/level (max +10).

\linkspell{Ghoul Touch}: Paralyzes one subject, which exudes stench that makes those nearby sickened.

\linkspell{Scare}: Panics creatures of less than 6 HD.

\linkspell{Spectral Hand}: Creates disembodied glowing hand to deliver touch attacks.

Trans

\linkspell{Alter Self}: Assume form of a similar creature.

\linkspell{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\linkspell{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\linkspell{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\linkspell{Darkvision}: See 60 ft. in total darkness.

\linkspell{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\linkspell{Fox's Cunning}: Subject gains +4 Int for 1 min./level.

\linkspell{Knock}: Opens locked or magically sealed door.

\linkspell{Levitate}: Subject moves up and down at your direction.

\linkspell{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\linkspell{Pyrotechnics}: Turns fire into blinding light or choking smoke.

\linkspell{Rope Trick}: As many as eight creatures hide in extradimensional space.

\linkspell{Spider Climb}: Grants ability to walk on walls and ceilings.

\linkspell{Whispering Wind}: Sends a short message 1 mile/level.

%%%
\subsubsection{3rd Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Dispel Magic}: Cancels magical spells and effects.

\linkspell{Explosive Runes}: Deals 6d6 damage when read.

\linkspell{Magic Circle Against Chaos}/\linkspell{Magic Circle Against Evil}{Evil}/\linkspell{Magic Circle Against Good}{Good}/\linkspell{Magic Circle Against Law}{Law}: As \textit{Protection} spells, but 10-ft. radius and 10 min./level.

\linkspell{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.

\linkspell{Protection From Energy}: Absorb 12 points/level of damage from one kind of energy.

Conj

\linkspell{Phantom Steed}: Magic horse appears for 1 hour/level.

\linkspell{Sepia Snake Sigil}\textsuperscript{M}: Creates text symbol that immobilizes reader.

\linkspell{Sleet Storm}: Hampers vision and movement.

\linkspell{Stinking Cloud}: Nauseating vapors, 1 round/level.

\linkspell{Summon Monster III}: Calls extraplanar creature to fight for you.

Div

\linkspell{Arcane Sight}: Magical auras become visible to you.

\linkspell{Clairaudience/Clairvoyance}: Hear or see at a distance for 1 min./level.

\linkspell{Tongues}: Speak any language.

Ench

\linkspell{Deep Slumber}: Puts 10 HD of creatures to sleep.

\linkspell{Heroism}: Gives +2 bonus on attack rolls, saves, skill checks.

\linkspell{Hold Person}: Paralyzes one humanoid for 1 round/level.

\linkspell{Rage}: Subjects gains +2 to Str and Con, +1 on Will saves, -2 to AC.

\linkspell{Suggestion}: Compels subject to follow stated course of action.

Evoc

\linkspell{Daylight}: 60-ft. radius of bright light.

\linkspell{Fireball}: 1d6 damage per level, 20-ft. radius.

\linkspell{Lightning Bolt}: Electricity deals 1d6/level damage.

\linkspell{Tiny Hut}: Creates shelter for ten creatures.

\linkspell{Wind Wall}: Deflects arrows, smaller creatures, and gases.

Illus

\linkspell{Displacement}: Attacks miss subject 50\%.

\linkspell{Illusory Script}\textsuperscript{M}: Only intended reader can decipher.

\linkspell{Invisibility Sphere}: Makes everyone within 10 ft. invisible.

\linkspell{Major Image}: As \linkspell{Silent Image}, plus sound, smell and thermal effects.

Necro

\linkspell{Gentle Repose}: Preserves one corpse.

\linkspell{Halt Undead}: Immobilizes undead for 1 round/level.

\linkspell{Ray of Exhaustion}: Ray makes subject exhausted.

\linkspell{Vampiric Touch}: Touch deals 1d6/two levels damage; caster gains damage as hp.

Trans

\linkspell{Blink}: You randomly vanish and reappear for 1 round/level.

\linkspell{Flame Arrow}: Arrows deal +1d6 fire damage.

\linkspell{Fly}: Subject flies at speed of 60 ft.

\linkspell{Gaseous Form}: Subject becomes insubstantial and can fly slowly.

\linkspell{Haste}: One creature/level moves faster, +1 on attack rolls, AC, and Reflex saves.

\linkspell{Keen Edge}: Doubles normal weapon's threat range.

\linkspell{Greater Magic Weapon}: +1/four levels (max +5).

\linkspell{Secret Page}: Changes one page to hide its real content.

\linkspell{Shrink Item}: Object shrinks to one-sixteenth size.

\linkspell{Slow}: One subject/level takes only one action/round, -1 to AC, reflex saves, and attack rolls.

\linkspell{Water Breathing}: Subjects can breathe underwater.

%%%
\subsubsection{4th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Dimensional Anchor}: Bars extradimensional movement.

\linkspell{Fire Trap}\textsuperscript{M}: Opened object deals 1d4 damage +1/level.

\linkspell{Lesser Globe of Invulnerability}: Stops 1st- through 3rd-level spell effects.

\linkspell{Remove Curse}: Frees object or person from curse.

\linkspell{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.

Conj

\linkspell{Black Tentacles}: Tentacles grapple all within 20 ft. spread.

\linkspell{Dimension Door}: Teleports you short distance.

\linkspell{Minor Creation}: Creates one cloth or wood object.

\linkspell{Secure Shelter}: Creates sturdy cottage.

\linkspell{Solid Fog}: Blocks vision and slows movement.

\linkspell{Summon Monster IV}: Calls extraplanar creature to fight for you.

Div

\linkspell{Arcane Eye}: Invisible floating eye moves 30 ft./round.

\linkspell{Detect Scrying}: Alerts you of magical eavesdropping.

\linkspell{Locate Creature}: Indicates direction to familiar creature.

\linkspell{Scrying}\textsuperscript{F}: Spies on subject from a distance.

Ench

\linkspell{Charm Monster}: Makes monster believe it is your ally.

\linkspell{Confusion}: Subjects behave oddly for 1 round/level.

\linkspell{Crushing Despair}: Subjects take -2 on attack rolls, damage rolls, saves, and checks.

\linkspell{Lesser Geas}: Commands subject of 7 HD or less.

Evoc

\linkspell{Fire Shield}: Creatures attacking you take fire damage; you're protected from heat or cold.

\linkspell{Ice Storm}: Hail deals 5d6 damage in cylinder 40 ft. across.

\linkspell{Resilient Sphere}: Force globe protects but traps one subject.

\linkspell{Shout}: Deafens all within cone and deals 5d6 sonic damage.

\linkspell{Wall of Fire}: Deals 2d4 fire damage out to 10 ft. and 1d4 out to 20 ft. Passing through wall deals 2d6 damage +1/level.

\linkspell{Wall of Ice}: Ice plane creates wall with 15 hp +1/level, or hemisphere can trap creatures inside.

Illus

\linkspell{Hallucinatory Terrain}: Makes one type of terrain appear like another (field into forest, or the like).

\linkspell{Greater Invisibility}: As \linkspell{Invisibility}, but subject can attack and stay invisible.

\linkspell{Illusory Wall}: Wall, floor, or ceiling looks real, but anything can pass through.

\linkspell{Phantasmal Killer}: Fearsome illusion kills subject or deals 3d6 damage.

\linkspell{Rainbow Pattern}: Lights fascinate 24 HD of creatures.

\linkspell{Shadow Conjuration}: Mimics conjuration below 4th level, but only 20\% real.

Necro

\linkspell{Animate Dead}\textsuperscript{M}: Creates undead skeletons and zombies.

\linkspell{Bestow Curse}: -6 to an ability score; -4 on attack rolls, saves, and checks; or 50\% chance of losing each action.

\linkspell{Contagion}: Infects subject with chosen disease.

\linkspell{Enervation}: Subject gains 1d4 negative levels.

\linkspell{Fear}: Subjects within cone flee for 1 round/level.

Trans

\linkspell{Enlarge Person, Mass}: Enlarges several creatures.

\linkspell{Mnemonic Enhancer}\textsuperscript{F}: \textit{Wizard only}. Prepares extra spells or retains one just cast.

\linkspell{Polymorph}: Gives one willing subject a new form.

\linkspell{Mass Reduce Person}: Reduces several creatures.

\linkspell{Stone Shape}: Sculpts stone into any shape.

%%%
\subsubsection{5th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\linkspell{Dismissal}: Forces a creature to return to native plane.

\linkspell{Mage's Private Sanctum}: Prevents anyone from viewing or scrying an area for 24 hours.

Conj

\linkspell{Cloudkill}: Kills 3 HD or less; 4-6 HD save or die, 6+ HD take Con damage.

\linkspell{Mage's Faithful Hound}: Phantom dog can guard, attack.

\linkspell{Major Creation}: As \linkspell{Minor Creation}, plus stone and metal.

\linkspell{Lesser Planar Binding}: Traps extraplanar creature of 6 HD or less until it performs a task.

\linkspell{Secret Chest}\textsuperscript{F}: Hides expensive chest on Ethereal Plane; you retrieve it at will.

\linkspell{Summon Monster V}: Calls extraplanar creature to fight for you.

\linkspell{Teleport}: Instantly transports you as far as 100 miles/level.

\linkspell{Wall of Stone}: Creates a stone wall that can be shaped.

Div

\linkspell{Contact Other Plane}: Lets you ask question of extraplanar entity.

\linkspell{Prying Eyes}: 1d4 +1/level floating eyes scout for you.

\linkspell{Telepathic Bond}: Link lets allies communicate.

Ench

\linkspell{Dominate Person}: Controls humanoid telepathically.

\linkspell{Feeblemind}: Subject's Int and Cha drop to 1.

\linkspell{Hold Monster}: As \linkspell{Hold Person}, but any creature.

\linkspell{Mind Fog}: Subjects in fog get -10 to Wis and Will checks.

\linkspell{Symbol of Sleep}\textsuperscript{M}: Triggered rune puts nearby creatures into catatonic slumber.

Evoc

\linkspell{Cone of Cold}: 1d6/level cold damage.

\linkspell{Interposing Hand}: Hand provides cover against one opponent.

\linkspell{Sending}: Delivers short message anywhere, instantly.

\linkspell{Wall of Force}: Wall is immune to damage.

Illus

\linkspell{Dream}: Sends message to anyone sleeping.

\linkspell{False Vision}\textsuperscript{M}: Fools scrying with an illusion.

\linkspell{Mirage Arcana}: As \linkspell{Hallucinatory Terrain}, plus structures.

\linkspell{Nightmare}: Sends vision dealing 1d10 damage, fatigue.

\linkspell{Persistent Image}: As \linkspell{Major Image}, but no concentration required.

\linkspell{Seeming}: Changes appearance of one person per two levels.

\linkspell{Shadow Evocation}: Mimics evocation below 5th level, but only 20\% real.

Necro

\linkspell{Blight}: Withers one plant or deals 1d6/level damage to plant creature.

\linkspell{Magic Jar}\textsuperscript{F}: Enables possession of another creature.

\linkspell{Symbol of Pain}\textsuperscript{M}: Triggered rune wracks nearby creatures with pain.

\linkspell{Waves of Fatigue}: Several targets become fatigued.

Trans

\linkspell{Animal Growth}: One animal/two levels doubles in size.

\linkspell{Baleful Polymorph}: Transforms subject into harmless animal.

\linkspell{Fabricate}: Transforms raw materials into finished items.

\linkspell{Overland Flight}: You fly at a speed of 40 ft. and can hustle over long distances.

\linkspell{Passwall}: Creates passage through wood or stone wall.

\linkspell{Telekinesis}: Moves object, attacks creature, or hurls object or creature.

\linkspell{Transmute Mud to Rock}: Transforms two 10-ft. cubes per level.

\linkspell{Transmute Rock to Mud}: Transforms two 10-ft. cubes per level.

Univ

\linkspell{Permanency}\textsuperscript{X}: Makes certain spells permanent.

%%%
\subsubsection{6th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Antimagic Field}: Negates magic within 10 ft.

\linkspell{Greater Dispel Magic}: As \linkspell{Dispel Magic}, but +20 on check.

\linkspell{Globe of Invulnerability}: As \linkspell{Lesser Globe of Invulnerability}, plus 4th-level spell effects.

\linkspell{Guards and Wards}: Array of magic effects protect area.

\linkspell{Repulsion}: Creatures can't approach you.

Conj

\linkspell{Acid Fog}: Fog deals acid damage.

\linkspell{Planar Binding}: As \linkspell{Lesser Planar Binding}, but up to 12 HD.

\linkspell{Summon Monster VI}: Calls extraplanar creature to fight for you.

\linkspell{Wall of Iron}\textsuperscript{M}: 30 hp/four levels; can topple onto foes.

Div

\linkspell{Analyze Dweomer}\textsuperscript{F}: Reveals magical aspects of subject.

\linkspell{Legend Lore}\textsuperscript{M}\textsuperscript{F}: Lets you learn tales about a person, place, or thing.

\linkspell{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.

Ench

\linkspell{Geas/Quest}: As \linkspell{Lesser Geas}, plus it affects any creature.

\linkspell{Greater Heroism}: Gives +4 bonus on attack rolls, saves, skill checks; immunity to fear; temporary hp.

\linkspell{Mass Suggestion}: As \linkspell{Suggestion}, plus one subject/level.

\linkspell{Symbol of Persuasion}\textsuperscript{M}: Triggered rune charms nearby creatures.

Evoc

\linkspell{Chain Lightning}: 1d6/level damage; 1 secondary bolt/level each deals half damage.

\linkspell{Contingency}\textsuperscript{F}: Sets trigger condition for another spell.

\linkspell{Forceful Hand}: Hand pushes creatures away.

\linkspell{Freezing Sphere}: Freezes water or deals cold damage.

Illus

\linkspell{Mislead}: Turns you invisible and creates illusory double.

\linkspell{Permanent Image}: Includes sight, sound, and smell.

\linkspell{Programmed Image}\textsuperscript{M}: As \linkspell{Major Image}, plus triggered by event.

\linkspell{Shadow Walk}: Step into shadow to travel rapidly.

\linkspell{Veil}: Changes appearance of group of creatures.

Necro

\linkspell{Circle of Death}\textsuperscript{M}: Kills 1d4/level 
HD of creatures.

\linkspell{Create Undead}\textsuperscript{M}: Creates ghouls, ghasts, mummies, or mohrgs.

\linkspell{Eyebite}: Target becomes panicked, sickened, and comatose.

\linkspell{Symbol of Fear}\textsuperscript{M}: Triggered rune panics nearby creatures.

\linkspell{Undeath to Death}\textsuperscript{M}: Destroys 1d4/level HD of undead (max 20d4).

Trans

\linkspell{Control Water}: Raises or lowers bodies of water.

\linkspell{Disintegrate}: Makes one creature or object vanish.

\linkspell{Flesh to Stone}: Turns subject creature into statue.

\linkspell{Hardening}: Object permanently gains 1 Hardness per 2 caster levels.

\linkspell{Mage's Lucubration}: \textit{Wizard only}. Recalls spell of 5th level or lower.

\linkspell{Mass Bear's Endurance}: As \linkspell{Bear's Endurance}, affects one subject/level.

\linkspell{Mass Bull's Strength}: As \linkspell{Bull's Strength}, affects one subject/ level.

\linkspell{Mass Cat's Grace}: As \linkspell{Cat's Grace}, affects one subject/level.

\linkspell{Mass Eagle's Splendor}: As \linkspell{Eagle's Splendor}, affects one subject/level.

\linkspell{Mass Fox's Cunning}: As \linkspell{Fox's Cunning}, affects one subject/ level.

\linkspell{Mass Owl's Wisdom}: As \linkspell{Owl's Wisdom}, affects one subject/ level.

\linkspell{Move Earth}: Digs trenches and build hills.

\linkspell{Stone to Flesh}: Restores petrified creature.

\linkspell{Transformation}\textsuperscript{M}: You gain combat bonuses.

%%%
\subsubsection{7th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Banishment}: Banishes 2 HD/level of extraplanar creatures.

\linkspell{Sequester}: Subject is invisible to sight and scrying; renders creature comatose.

\linkspell{Spell Turning}: Reflect 1d4+6 spell levels back at caster.

Conj

\linkspell{Instant Summons}\textsuperscript{M}: Prepared object appears in your hand.

\linkspell{Mage's Magnificent Mansion}\textsuperscript{F}: Door leads to extradimensional mansion.

\linkspell{Phase Door}: Creates an invisible passage through wood or stone.

\linkspell{Plane Shift}\textsuperscript{F}: As many as eight subjects travel to another plane.

\linkspell{Summon Monster VII}: Calls extraplanar creature to fight for you.

\linkspell{Greater Teleport}: As \linkspell{Teleport}, but no range limit and no off-target arrival.

\linkspell{Teleport Object}: As \linkspell{Teleport}, but affects a touched object.

Div

\linkspell{Arcane Sight, Greater}: As \linkspell{Arcane Sight}, but also reveals magic effects on creatures and objects.

\linkspell{Greater Scrying}: As \linkspell{Scrying}, but faster and longer.

\linkspell{Vision}\textsuperscript{M}\textsuperscript{X}: As \linkspell{Legend Lore}, but quicker and strenuous.

Ench

\linkspell{Hold Person, Mass}: As \linkspell{Hold Person}, but all within 30 ft.

\linkspell{Insanity}: Subject suffers continuous \linkspell{Confusion}.

\linkspell{Power Word Blind}: Blinds creature with 200 hp or less.

\linkspell{Symbol of Stunning}\textsuperscript{M}: Triggered rune stuns nearby creatures.

Evoc

\linkspell{Delayed Blast Fireball}: 1d6/level fire damage; you can postpone blast for 5 rounds.

\linkspell{Forcecage}\textsuperscript{M}: Cube or cage of force imprisons all inside.

\linkspell{Grasping Hand}: Hand provides cover, pushes, or grapples.

\linkspell{Mage's Sword}\textsuperscript{F}: Floating magic blade strikes opponents.

\linkspell{Prismatic Spray}: Rays hit subjects with variety of effects.

Illus

\linkspell{Invisibility, Mass}: As \linkspell{Invisibility}, but affects all in range.

\linkspell{Project Image}: Illusory double can talk and cast spells.

\linkspell{Greater Shadow Conjuration}: As \linkspell{Shadow Conjuration}, but up to 6th level and 60\% real.

\linkspell{Simulacrum}\textsuperscript{M}\textsuperscript{X}: Creates partially real double of a creature.

Necro

\linkspell{Control Undead}: Undead don't attack you while under your command.

\linkspell{Finger of Death}: Kills one subject.

\linkspell{Symbol of Weakness}\textsuperscript{M}: Triggered rune weakens nearby creatures.

\linkspell{Waves of Exhaustion}: Several targets become exhausted.

Trans

\linkspell{Control Weather}: Changes weather in local area.

\linkspell{Ethereal Jaunt}: You become ethereal for 1 round/level.

\linkspell{Reverse Gravity}: Objects and creatures fall upward.

\linkspell{Statue}: Subject can become a statue at will.

Univ

\linkspell{Limited Wish}\textsuperscript{X}: Alters reality -- within spell limits.

%%%
\subsubsection{8th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Dimensional Lock}: Teleportation and interplanar travel blocked for one day/level.

\linkspell{Mind Blank}: Subject is immune to mental/emotional magic and scrying.

\linkspell{Prismatic Wall}: Wall's colors have array of effects.

\linkspell{Protection From Spells}\textsuperscript{M}\textsuperscript{F}: Confers +8 resistance bonus.

Conj

\linkspell{Incendiary Cloud}: Cloud deals 4d6 fire damage/round.

\linkspell{Maze}: Traps subject in extradimensional maze.

\linkspell{Greater Planar Binding}: As \linkspell{Lesser Planar Binding}, but up to 18 HD.

\linkspell{Summon Monster VIII}: Calls extraplanar creature to fight for you.

\linkspell{Trap the Soul}\textsuperscript{M}\textsuperscript{F}: Imprisons subject within gem.

Div

\linkspell{Discern Location}: Reveals exact location of creature or object.

\linkspell{Moment of Prescience}: You gain insight bonus on single attack roll, check, or save.

\linkspell{Greater Prying Eyes}: As \linkspell{Prying Eyes}, but eyes have \linkspell{True Seeing}.

Ench

\linkspell{Antipathy}: Object or location affected by spell repels certain creatures.

\linkspell{Binding}\textsuperscript{M}: Utilizes an array of techniques to imprison a creature.

\linkspell{Mass Charm Monster}: As \linkspell{Charm Monster}, but all within 30 ft.

\linkspell{Demand}: As \linkspell{Sending}, plus you can send \linkspell{Suggestion}.

\linkspell{Irresistible Dance}: Forces subject to dance.

\linkspell{Maddening Scream}: Forces target to uncontrollably run around screaming.

\linkspell{Power Word Stun}: Stuns creature with 150 hp or less.

\linkspell{Symbol of Insanity}\textsuperscript{M}: Triggered rune renders nearby creatures insane.

\linkspell{Sympathy}\textsuperscript{F}: Object or location attracts certain creatures.

Evoc

\linkspell{Clenched Fist}: Large hand provides cover, pushes, or attacks your foes.

\linkspell{Polar Ray}: Ranged touch attack deals 1d6/level cold damage.

\linkspell{Greater Shout}: Devastating yell deals 10d6 sonic damage; stuns creatures, damages objects.

\linkspell{Sunburst}: Blinds all within 10 ft., deals 6d6 damage.

Illus

\linkspell{Scintillating Pattern}: Twisting colors \linksec{Confused}{Confuse}, \linksec{Stunned}{Stun}, or render \linksec{Unconscious}.

\linkspell{Screen}: Illusion hides area from vision, scrying.

\linkspell{Greater Shadow Evocation}: As \linkspell{Shadow Evocation}, but up to 7th level and 60\% real.

\linkspell{Telekinetic Sphere}: As \linkspell{Resilient Sphere}, but you move sphere telekinetically.

Necro

\linkspell{Clone}\textsuperscript{M}\textsuperscript{F}: Duplicate awakens when original dies.

\linkspell{Create Greater Undead}\textsuperscript{M}: Create shadows, wraiths, spectres, or devourers.

\linkspell{Horrid Wilting}: Deals 1d6/level damage within 30 ft.

\linkspell{Symbol of Death}\textsuperscript{M}: Triggered rune slays nearby creatures.

Trans

\linkspell{Iron Body}: Your body becomes living iron.

\linkspell{Polymorph Any Object}: Changes any subject into anything else.

\linkspell{Temporal Stasis}\textsuperscript{M}: Puts subject into suspended animation.

%%%
\subsubsection{9th Level Sorcerer / Wizard Spells}
%%%

Abjur

\linkspell{Freedom}: Releases creature from \linkspell{Imprisonment}.

\linkspell{Imprisonment}: Entombs subject beneath the earth.

\linkspell{Mage's Disjunction}: Dispels magic, disenchants magic items.

\linkspell{Prismatic Sphere}: As \linkspell{Prismatic Wall}, but surrounds on all sides.

Conj

\linkspell{Gate}\textsuperscript{X}: Connects two planes for travel or summoning.

\linkspell{Genesis}\textsuperscript{X}: Creates a deimiplane on the Ethereal Plane

\linkspell{Refuge}\textsuperscript{M}: Alters item to transport its possessor to you.

\linkspell{Summon Monster IX}: Calls extraplanar creature to fight for you.

\linkspell{Teleportation Circle}\textsuperscript{M}: Circle teleports any creature inside to designated spot.

Div

\linkspell{Foresight}: "Sixth sense" warns of impending danger.

Ench

\linkspell{Dominate Monster}: As \linkspell{Dominate Person}, but any creature.

\linkspell{Mass Hold Monster}: As \linkspell{Hold Monster}, but all within 30 ft.

\linkspell{Power Word Kill}: Kills one creature with 100 hp or less.

Evoc

\linkspell{Crushing Hand}: Large hand provides cover, pushes, or crushes your foes.

\linkspell{Meteor Swarm}: Four exploding spheres each deal 6d6 fire damage.

Illus

\linkspell{Shades}: As \linkspell{Shadow Conjuration}, but up to 8th level and 80\% real.

\linkspell{Weird}: As \linkspell{Phantasmal Killer}, but affects all within 30 ft.

Necro

\linkspell{Astral Projection}\textsuperscript{M}: Projects you and companions onto Astral Plane.

\linkspell{Energy Drain}: Subject gains 2d4 negative levels.

\linkspell{Soul Bind}\textsuperscript{F}: Traps newly dead soul to prevent \linkspell{Resurrection}.

\linkspell{Wail of the Banshee}: Kills one creature/level.

Trans

\linkspell{Etherealness}: Travel to Ethereal Plane with companions.

\linkspell{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.

\linkspell{Time Stop}: You act freely for 1d4+1 rounds.

Univ

\linkspell{Wish}\textsuperscript{X}: As \linkspell{Limited Wish}, but with fewer limits.
