\classname{Master of the Seven Necromantic Mysteries}\label{class:masterofnecromanticmysteries}
\vspace*{-8pt}
\quot{``Did you think that you could oppose me? Death itself is no mystery to one such as I."}

The Master of the Seven Necromantic Mysteries is a necromancer extraordinaire, a grandmaster of the necromantic arts. He transcends the normal limitations of magic and finds the common threads that link all Necromancy magic. Great is his power and terrible is his anger, as he wields the powers of life and death with terrible skill. Both the living and the dead fear him, as he wields powers from beyond life. All those who study the arts of necromancy acknowledge his skill.

\ability{Prerequisites:}{}
\listprereq
\itemability{Feats:}{Spell Focus(Necromancy), Greater Spell Focus (Necromancy), two necromantic creation feats}
\itemability{Skills:}{Knowledge (Arcana) 12 ranks, Knowledge (Religion) 12 ranks}
\itemability{Spells:}{Must be able to cast 5th level Necromancy spells and must be able to cast one Necromancy spell at each spell level available.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Master of the Seven Necromantic Mysteries? class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Knowledge (All Skills Individually) (Int), Profession (Wis), Sense Motive (Wis), Spellcraft (Int), and Use Magic Device (Cha).}

\ability{Skills/Level:}{2 + Intelligence modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+2 &+0 &+2 &Master of Necromancy, First Mystery: Secrets of Commanding &+1 spellcaster level\\
2nd &+1 &+3 &+0 &+3 &Second Mystery: Secrets of Necromantic Spells &+1 spellcaster level\\
3rd &+1 &+3 &+1 &+3 &Third Mystery: Secrets of Negative Energy &+1 spellcaster level\\
4th &+2 &+4 &+1 &+4 &Fourth Mystery: Secrets of Undead Creation &+1 spellcaster level\\
5th &+2 &+4 &+1 &+4 &Fifth Mystery: Secrets of Life Draining &+1 spellcaster level\\
6th &+3 &+5 &+2 &+5 &Sixth Mystery: Secrets of the Soul &+1 spellcaster level\\
7th &+3 &+5 &+2 &+5 &Seventh Mystery: Secrets of Eternal Life &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All the following are Class Features of the Master of the Seven Necromantic Mysteries prestige class.

\ability{Weapon and Armor Proficiency:}{A Master of the Seven Necromantic Mysteries gain no proficiency with any weapon or armor.}

\ability{Master of Necromancy:}{The Master of the Seven Necromantic Mysteries gains a bonus to his caster level when casting spells of the school of Necromancy equal to his class level.}

\ability{Secrets of Commanding (Su):}{The Master of the Seven Necromantic Mysteries can Rebuke Undead as a cleric of his character level plus his Master of the Seven Necromantic Mysteries class level. This does not stack with any Rebuking the Master may have gained from other classes with grant Rebuking (such as Cleric or Dread Necromancer). He may also ignore the turning resistance of any undead creature he has already successfully rebuked (so a Ghoul counts as only 2 commanded hit dice instead of 4).}

\ability{Secrets of Necromancy Spells:}{At 2nd level, The Master of the Seven Necromantic Mysteries can learn any Necromancy spell from any list provided he has deciphered the spell in written form. If he is of a class that has a limited number of spells known, he must sacrifice one of his other spells known of an equal level.

In addition, the Master of the Seven Necromantic Mysteries learns one additional free spell from the school of Necromancy every level (including this one). This spell may be from any list, but must be of a level he can cast.}

\ability{Secrets of Negative Energy (Su):}{At 3rd level, The Master of the Seven Necromantic Mysteries may convert the damage from any spell with the cold, ice, fire, or acid subtype to instead inflict negative energy damage.}

\ability{Secrets of Undead Creation (Su):}{At 4th level, The Master of the Seven Necromantic Mysteries gains the feat Feed the Dark Gods as a bonus feat.

In addition, the Master may choose three undead creation spells per day to cast as spell-like abilities usable once per day.}

\ability{Secrets of Life Draining (Su):}{At 5th level, The Master of the Seven Necromantic Mysteries gains the ability to draw life from his spells that inflict negative levels or ability drain. For every negative level bestowed of point of ability damage inflicted, the Master gains 5 temporary hit points. These temporary hit points vanish after one hour, and cannot cause the Master to have more temporary hit point than twice his fully healed number of hit points.}

\ability{Secrets of the Soul:}{At 6th level, The Master of the Seven Necromantic Mysteries may cast \spell{magic jar} at will as a Supernatural ability. Any body that he possesses counts as a second receptacle, meaning that he gains the benefits of being in a receptacle while in another?s body, and he still has an object receptacle to return to if the body he is possessing is killed or destroyed.}

\ability{Secrets of Eternal Life:}{At 7th level, The Master of the Seven Necromantic Mysteries becomes immortal. He no longer ages, and if killed he becomes a ghost. As a ghost, he automatically succeeds on his Rejuvenation check.}

