\classname{Soul Merchant}
\vspace*{8pt}

Upon death, souls pass to the Outer Planes. Evil souls go to the Lower Planes while good souls go the Upper Planes, and some souls wander the places between, but each has a value to the beings that live in those place.

Where there is value and profit to be made there is a merchant; in the soul trade, that man is the Soul Merchant. Slaver, procurer, and arbitrator, the Soul Merchant is ultimate middle-man in the market of stealing, selling, and buying souls. Like any successful merchant, he enjoys special privileges with his clients.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{Knowledge(planes) 10 ranks, Knowledge(religion) 10 ranks}
\itemability{Spells:}{Must be able to cast \spell{lesser planar binding}}
\itemability{Feats:}{Leadership}
\end{list}\vspace*{8pt}


\ability{Hide Dice:}{d4}

\ability{Class Skills:}{The Soul Merchant's class skills (and the key ability for each skill) are Appraise (Int), Bluff (Cha), Concentration (Con), Craft (Int), Decipher Script (Int), Knowledge (all skills, taken individually) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skill Points/Level:}{2 + Int modifier}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Extract Soul, Extended Contract &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Escort to the Promenade &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Craft Soul Contract &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Soulless Spawn &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Bargain &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Notable Investments &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Credit &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Lifetime Warranty &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All the following are Class Features of the Soul Merchant prestige class.

\ability{Weapon and Armor Proficiency:}{The Soul Merchant gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Soul Merchant casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Extract Soul(Su):}{The Soul Merchant may cast \spell{soul bind} as a spell like ability a number of times per day equal to his intelligence bonus. He must use a gem to hold the soul, and it must be worth at least 100gp.}

\ability{Extended Contract(Su):}{Due to his extensive web of contacts in the Outer Planes, he can call spirits from beyond the grave. He may call undead creatures with his \spell{planar binding} spells in addition to the usual creatures.}

\ability{Escort to the Promenade(Su):}{At 2nd level, the Soul Merchant may call an Escort with a casting of the \spell{lesser planar binding} spell. Treat this creature as a Erinyes, but with the additional ability to use \spell{gate} (travel version only, and only to Finality and the last location it was bound to). This Escort will take a Soul Merchant to Finality, a planar metropolis that has a prominent economy in the buying selling of souls (see Finality in the Locations of Necromantic Importance section).}

\ability{Craft Soul Contract(Su):}{At 3rd level, the Soul Merchant may craft a Soul Contract. This is an item that details the conditions of an agreement or bargain where one party has put up his soul as collateral. Should this party default on the contract, his soul is forced into a gem as detailed in the contract (the gem need not have line of effect to the victim for this to occur). Should the other contractee default, the contract is rendered powerless. If the physical paper of contract is destroyed, the magical effects of the contract are also ended.}

\ability{Soulless Spawn:}{Should a 4th level Soul Merchant gain someone's soul with a Soul Contract, he may turn their body (if it still lives) into a unique form of spawn called a Soulless. These creatures have all of their normal abilities, but also have the Mindless trait, and must be commanded by the Soul Merchant to perform any action.}

\ability{Bargain:}{By 5th level, the Soul Merchant has become a trusted (or at least known) middle-man in the soul trade. He may sell lesser souls to gain souls of greater value. In effect, he may buy souls in Finality by exchanging enough souls to equal the value of a more powerful soul. The Soul Merchant also gains the ability to increase the HD limitation of any planar binding spells he casts by +2 HD.}

\ability{Notable Investments:}{A Soul Merchant of 6th level has performed substantial dealings in the oft maligned (yet potentially lucrative) trade in souls. The character can act as a fixer for one of the major interested parties. The character gains one ability from the following list: Angelic Favor, Baatezu Favor, Demonic Favor, or Lich's Favor.}

\listone
\itemability{Angelic Favor (Sp):}{Due to outstanding effort in the recovery of good-aligned souls and destruction of evil-aligned souls, several celestials owe you favors. Once per day you may cast \spell{Greater Planar Ally} as a spell-like ability. This effect only calls a good-aligned celestial, and it only accepts souls as payment.}
\itemability{Baatezu Favor (Sp):}{Due to preexisting deals with several Devils, the Soul Merchant may destroy a soul for infernal power. Once per day, the Soul Merchant may gain DR of 15/good and silver for 10 minutes per CR of the creature destroyed. During this time, the Soul Merchant may see in darkness (including magical darkness) and is immune to fire.}
\itemability{Demonic Favor (Sp):}{After hurling a number of notable souls into forgotten maelstroms of torment in the Abyss, the Soul Merchant has gained agreements in principle to issue commands to Tanar'ri legions that are nominally under the control of his business associates. The Soul Merchant no longer has to pay Demons that have a CR at least 6 less than his own for their services.}
\itemability{Lich's Favor (Sp):}{Due to preexisting deals with several Liches, the Soul Merchant level may destroy a soul for magical power. Once per day, the Soul Merchant may recover a spell slot by destroying a soul of a CR equal to twice the level of the spell.}
\end{list}\vspace*{8pt}

\ability{Credit:}{Due to his outstanding record, a 7th level Soul Merchant can use his abilities on credit (without expending souls); however, if he does not pay for these uses with twice as many souls (two souls of the correct value for each ability he used) in one month, his own soul is taken. If for any reason the Soul Merchant's soul cannot be taken, the merchants of Acheron will not extend him any more credit.}

\ability{Lifetime Warranty:}{At 8th level the Soul Merchant may store souls with certain powerful outsiders in the Finality. Should he ever die, these outsiders will sell his souls for the magic objects necessary to return him to life (such as \spell{true resurrection}, \spell{cloning}, or \spell{true reincarnation} magic). If he should ever run out of souls, he can still be brought back on credit\ldots }
