
\classname{Assassin} \label{class:assassin}
\vspace{-8pt}
\quot{``I kill people. Individually, you are a person. Collectively, I think you count as people.''}

\desc{An assassin is a master of the art of killing, a vicious weapon honed by experience and inclination to learn the myriad ways to end a life. Unlike common warriors or rogues, an Assassin does not study various fighting arts or muddle his training with martial dirty tricks, he instead studies the anatomy of the various creatures of wildly different anatomies and forms of existence, and he uses this knowledge to place his blows in areas vital for biological or mystical reasons. Stealth and sudden violence are his hallmarks, and various exotic tools and killing methods become his tools.}

\desc{While most societies consider assassination to be a vile art, or at best a dishonorable or unvalorous one, the reasons that drive these killers vary. Cold-hearted mercenaries share a skill set with dedicated demon-hunters, differing only in the application of their skills. Only the most na\"ive student of ethics believes that all killing is evil, or that nobility cannot be found in a mercifully quick death.}

\ability{Alignment:}{An Assassin may be of any alignment.}

\ability{Races:}{Any}

\ability{Starting Gold:}{6d4x10 gp (150 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Assassin's skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Swim (Str), Tumble (Dex), and Use Magic Device (Cha).}

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2 &+0 &Poison Use, Death Attack +3d6, Personal Immunity, Spellcasting\\
2nd &+1 &+3 &+3 &+0 &Uncanny Dodge, Death Attack +4d6\\
3rd &+2 &+3 &+3 &+1 &Hide in Plain Sight, Death Attack +5d6\\
4th &+3 &+4 &+4 &+1 &Cloak of Discretion, Death Attack +6d6\\
5th &+3 &+4 &+4 &+1 &Traps, Trapmaking, Death Attack +7d6\\
6th &+4 &+5 &+5 &+2 &Palm Weapon, Death Attack +8d6\\
7th &+5 &+5 &+5 &+2 &Full Death Attack, Death Attack +9d6\\
8th &+6/+1 &+6 &+6 &+2 &Nerve of the Assassin, Death Attack +10d6\\
9th &+6/+1 &+6 &+6 &+3 &Improved Uncanny Dodge, Death Attack +11d6\\
10th &+7/+2 &+7 &+7 &+3 &Skill Mastery, Death Attack +12d6\\
11th &+8/+3 &+7 &+7 &+3 &Poisonmaster, Death Attack +13d6\\
12th &+8/+3 &+8 &+8 &+4 &Personal Immunity, Death Attack +14d6\\
13th &+9/+4 &+8 &+8 &+4 &Exotic Method, Death Attack +15d6\\
14th &+10/+5 &+9 &+9 &+4 &Personal Immunity, Death Attack +16d6\\
15th &+11/+6/+6 &+9 &+9 &+5 &Killer's Proof, Death Attack +17d6\\
16th &+12/+7/+7 &+10 &+10 &+5 &Exotic Method, Death Attack +18d6\\
17th &+12/+7/+7 &+10 &+10 &+5 &Death by a Thousand Cuts, Death Attack +19d6\\
18th &+13/+8/+8 &+11 &+11 &+6 &Mind Blank, Death Attack +20d6\\
19th &+14/+9/+9 &+11 &+11 &+6 &Exotic Method, Death Attack +21d6\\
20th &+15/+10/+10 &+12 &+12 &+6 &Killing Strike, Death Attack +22d6\\
\end{tabular}
\end{small}
\end{table}

\begin{floatingfigure}{3.9in}
\begin{small}
\noindent\begin{tabular}{lllllllllllllllll}
 & \multicolumn{7}{c}{Assassin Spells Per Day}  &   &\multicolumn{7}{c}{Assassin Spells Known}\\
  &0 &1 &2 &3 &4 &5 &6 &  &  &0 &1 &2 &3 &4 &5 &6\\
1 &2 &- &- &- &- &- &- &  &1 &4 &- &- &- &- &- &-\\
2 &3 &0 &- &- &- &- &- &  &2 &5 &2 &- &- &- &- &-\\
3 &3 &1 &- &- &- &- &- &  &3 &6 &3 &- &- &- &- &-\\
4 &3 &2 &0 &- &- &- &- &  &4 &6 &3 &2 &- &- &- &-\\
5 &3 &3 &1 &- &- &- &- &  &5 &6 &4 &3 &- &- &- &-\\
6 &3 &3 &2 &- &- &- &- &  &6 &6 &4 &3 &- &- &- &-\\
7 &3 &3 &2 &0 &- &- &- &  &7 &6 &4 &4 &2 &- &- &-\\
8 &3 &3 &3 &1 &- &- &- &  &8 &6 &4 &4 &3 &- &- &-\\
9 &3 &3 &3 &2 &- &- &- &  &9 &6 &4 &4 &3 &- &- &-\\
10 &3 &3 &3 &2 &0 &- &- &  &10 &6 &4 &4 &4 &2 &- &-\\
11 &3 &3 &3 &3 &1 &- &- &  &11 &6 &4 &4 &4 &3 &- &-\\
12 &3 &3 &3 &3 &2 &- &- &  &12 &6 &4 &4 &4 &3 &- &-\\
13 &3 &3 &3 &3 &2 &0 &- &  &13 &6 &4 &4 &4 &4 &2 &-\\
14 &3 &3 &3 &3 &3 &1 &- &  &14 &6 &4 &4 &4 &4 &3 &-\\
15 &3 &3 &3 &3 &3 &2 &- &  &15 &6 &4 &4 &4 &4 &3 &-\\
16 &3 &3 &3 &3 &3 &2 &0 &  &16 &6 &5 &4 &4 &4 &4 &2\\
17 &3 &3 &3 &3 &3 &3 &1 &  &17 &6 &5 &5 &4 &4 &4 &3\\
18 &3 &3 &3 &3 &3 &3 &2 &  &18 &6 &5 &5 &5 &4 &4 &3\\
19 &3 &3 &3 &3 &3 &3 &3 &  &19 &6 &5 &5 &5 &5 &4 &4\\
20 &3 &3 &3 &3 &3 &3 &3 &  &20 &6 &5 &5 &5 &5 &5 &4\\
\end{tabular}
\end{small}
\end{floatingfigure}

\smallskip\noindent All of the following are Class Features of the Assassin class.

\ability{Weapon and Armor Proficiency:}{Assassins are proficient with all Light Weapons, as well as simple weapons, repeating crossbows, and hand crossbows. At first level, an Assassin gains proficiency with one Exotic Weapon of her choice. Assassins are proficient with Light Armor but not with shields.}

\ability{Spellcasting:}{The Assassin is an Arcane Spellcaster with the same spells per day and spells known progression as a Bard, except that he gains no more than three spell slots per level. An Assassin's spells known may be chosen from the Sorcerer/Wizard list, and must be from the schools of Divination, Illusion, or Necromancy. To cast an Assassin spell, she must have an Intelligence at least equal to 10 + the Spell level. The DC of the Assassin's spells is Intelligence based and the bonus spells are Intelligence based.}

\ability{Poison Use (Ex):}{An Assassin may prepare, apply, and use poison without any chance of poisoning herself.}

\ability{Death Attack (Ex):}{An Assassin may spend a full-round action to study an opponent who would be denied their Dexterity bonus if she instead attacked that target. If she does so, her next attack is a Death Attack if she makes it within 1 round. A Death Attack inflicts a number of extra dice of damage equal to her Assassin level plus two dice, but only if the target is denied its Dexterity Bonus to AC against that attack. Special attacks such as a coup de grace may be a Death Attack. Assassins are well trained in eliminating magical or distant opponents, and do not have to meet the stringent requirements of a sneak attack, though if a character has both sneak attack and death attack, they stack if the character meets the requirements of both. As long as the victim is denied their dexterity against attacks from the assassin during the study action and the attack itself, it counts as a death attack. An Assassin may load a crossbow simultaneously with his action to study his target if he has a Base Attack Bonus of +1 or more.}

\ability{Personal Immunity (Ex):}{Choose four poisons, an Assassin is immune to all four of those poisons, even if they are made available in a stronger strength. At levels 5, 7, and 12 the Assassin may choose one more type of poison to become immune to. At level 14, an Assassin becomes immune to all poisons.}

\ability{Uncanny Dodge (Ex):}{Starting at 2nd level, an Assassin can react to danger before his senses would normally allow him to do so. He retains her Dexterity bonus to AC (if any) even if she is caught flat-footed or struck by an invisible attacker. However, he still loses her Dexterity bonus to AC if immobilized. If an Assassin already has uncanny dodge from a different class he automatically gains improved uncanny dodge (see below) instead.}

\ability{Hide in Plain Sight (Ex):}{A 3rd level Assassin can hide in unusual locations, and may hide in areas without cover or concealment without penalty. An Assassin may even hide while being observed. This ability does not remove the -10 penalty for moving at full speed, or the -20 penalty for running or fighting.}

\ability{Cloak of Discretion (Su):}{At 4th level, an Assassin is protected by a constant \emph{nondetection} effect, with a caster level equal to his character level.}

\ability{Trapfinding:}{At 5th level, Assassins can use the Search skill to locate traps when the task has a Difficulty Class higher than 20. Finding a nonmagical trap has a DC of at least 20, or higher if it is well hidden. Finding a magic trap has a DC of 25 + the level of the spell used to create it. Assassins can use the Disable Device skill to disarm magic traps. A magic trap generally has a DC of 25 + the level of the spell used to create it. An Assassin who beats a trap's DC by 10 or more with a Disable Device check can study a trap, figure out how it works, and bypass it (with her party) without disarming it.}

\ability{Trapmaking:}{At 5th level, the Assassin learns to build simple mechanical traps in out of common materials. As long as has access to ropes, flexible material like green wood, and weapon-grade materials like sharpened wooden sticks or steel weapons, he can build an improvised trap in 10 minutes. He can build any non-magical trap on the ``CR 1" trap list that doesn't involve a pit. These traps have a Search DC equal to 20 + the Assassin's level, have a BAB equal to his own, and are always single-use traps. He may add poison to these traps, if he has access to it, but it will dry out in an hour.}

\ability{Palm Weapon (Su):}{At 6th level, the Assassin learns to conceal weapons with supernatural skill. Any weapon successfully concealed with Sleight of Hand cannot be found with divination magic.}

\ability{Full Death Attack:}{At 7th level, if the Assassin studies an opponent to perform a Death Attack, she can make a full attack during the next round where every attack inflicts Death Attack damage as long as the target was denied their Dexterity bonus to AC against the first attack in the full attack action.}

\ability{Nerve of the Killer:}{At 8th level, an Assassin gains a limited immunity to compulsion and charm effects. While studying a target for a Death Attack, and for one round afterward, he counts as if he were within a \spell{protection from evil} effect. This does not confer a deflection bonus to AC.}

\ability{Improved Uncanny Dodge (Ex):}{An Assassin of 9th level or higher can no longer be flanked. This defense denies another character the ability to sneak attack the character by flanking him, unless the attacker has at least four more levels in a class that provides sneak attack than the target. If a character already has uncanny dodge (see above) from a second class, the character automatically gains improved uncanny dodge instead, and the levels from the classes that grant uncanny dodge stack to determine the minimum level required to flank the character.}

\ability{Skill Mastery (Ex):}{At 10th level, an Assassin becomes so certain in the use of certain skills that she can use them reliably even under adverse conditions. When making a skill check with Climb, Disable Device, Hide, Move Silently, Search, Spellcraft, Use Magic Device, Use Rope, or Swim, she may take 10 even if stress and distractions would normally prevent her from doing so.}

\ability{Poisonmaster:}{At 11th level, the Assassin learns alchemic secrets for creating short-term poisons. By expending an entire healer's kit worth of materials and an hour of time, he can synthesize one dose of any poison in the DMG. This poison degrades to uselessness in one week.}

\ability{Exotic Method:}{At 13th, 16th, and 19th level the Assassin learns an exotic form of killing from the list below. Once chosen, this ability does not change:}
\listone

    \item \ability{Carrier:}{Three times per day, the Assassin can cast \spell{contagion} as a swift action spell-like ability.}
    \item \ability{Poison of the Cockatrice:}{Twice per day, the Assassin can cast \spell{flesh to stone} as a swift action spell-like ability.}
    \item \ability{Killer Faerie Arts:}{Twice per day, the Assassin can cast \spell{polymorph other} as a swift action spell-like ability.}
    \item \ability{Proxy Assassin:}{Twice per day, the Assassin can cast \spell{summon monster VII} as a spell-like ability. This effect lasts 10 minutes.}
    \item \ability{Death By Plane:}{Once per day, the Assassin can cast \spell{plane shift} as a spell-like ability.}
    \item \ability{Dimesional Rip:}{Once per day, the Assassin can cast \spell{implosion} as a spell-like ability. The duration of this effect is three rounds.}
    \item \ability{New School:}{The Assassin may now choose spells known from a new school.}
\end{list}
\vspace{8pt}

\ability{Killer's Proof (Su):}{At 15th level, the Assassin learns to steal the souls of those he kills. If he is holding an onyx worth at least 100 GP when he kills an enemy, he may place their soul within the gem as if he has cast \spell{soul bind} on them at the moment of their death.}

\ability{Death by a Thousand Cuts:}{At 17th level, the assassin has learned to kill even the hardiest of foes by reducing their physical form to shambles. Every successful Death attack inflicts a cumulative -2 Dexterity penalty to the Assassin's victim. These penalties last one day.}

\ability{Mind Blank (Su):}{At 18th level, the Assassin is protected by a constant \spell{mind blank} effect.}

\ability{Killing Strike (Su):}{At 20th level, the Assassin's Death Attacks bypass his victim's DR and hardness.}
