\classname{Elementalist}
\vspace{-8pt}
\quot{``Feel the wrath of the natural order you have angered!"}

\ability{Alignment:}{An prospective Elementalist must be of a neutral alignment (N, NG, NE, LN, or CN) in order to learn the secrets of Elementalism. Once a character already has at least one level of Elementalist, nothing prevents her from changing alignment.}

\ability{Races:}{Every race has elementalists, but races that have more draconic heritage mixed in have decidedly more elementalists. Dwarves have a natural affinity for stone and often choose the route of the Elementalist. Kobolds are naturally inclined towards elementalism and only jealous guarding of the secrets of elementalism by}

\ability{Starting Gold:}{4d4x10 gp (100 gold)}

\ability{Starting Age:}{As Druid.}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Elementalist's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Escape Artist (Dex), Handle Animal (Cha), Heal (Wis), Intimidate (Cha), Knowledge (arcana) (Int), Knowledge (nature) (Int), Knowledge (the planes) (Int), Profession (Wis), Ride (Dex), Search (Int), and Spellcraft (Int).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
&   Base Attack Bonus&  Fort Save&  Ref Save&   Will Save&  Special\\
1&  +0& +0& +0& +2&  Armored Casting, \spell{Create Water} \\
2&  +1& +0& +0& +3&  Elemental Survival\\
3&  +1& +1& +1& +3&  Advanced Learning\\
4&  +2& +1& +1& +4&  \spell{Create Air}\\
5&  +2& +1& +1& +4&  Elemental Faminilar, Advanced Learning\\
6&  +3& +2& +2& +5&  \\
7&  +3& +2& +2& +5&  Resistance to Energy: 5, Advanced Learning\\
8&  +4& +2& +2& +6&   \\
9&  +4& +3& +3& +6&  \spell{Create Fire}, Advanced Learning\\
10& +5& +3& +3& +7&  Timelessness  \\
11& +5& +3& +3& +7&  Advanced Learning, Elemental Traits   \\
12& +6& +4& +4& +8&   \\
13& +6& +4& +4& +8&  Resistance to Energy: 10, Advanced Learning   \\
14& +7& +4& +4& +9&  \spell{Create Wood}   \\
15& +7& +5& +5& +9&  Advanced Learning, Improved Summoning \\
16& +8& +5& +5& +10&     Elemental Wildshape 1/day \\
17& +8& +5& +5& +10&     \spell{Create Earth}, Advanced Learning   \\
18& +9& +6& +6& +11&     Elemental Wildshape 2/day \\
19& +9& +6& +6& +11&     Resistance to Energy: 15, Advanced Learning   \\
20& +10&    +6& +6& +12&     Elemental Wildshape 3/day \\

\end{tabular}
\end{small}
\end{table}



\smallskip\noindent All of the following are Class Features of the Elementalist class.

\ability{Weapon and Armor Proficiency:}{Elementalists are proficient with all simple weapons, as well as the scimitar, the battle axe, the trident, the pick (heavy and light), and the longbow (including composite longbows). Elementalists are proficient with light armor but not with shields of any kind.}

\ability{Spellcasting:}{The Elementalist is an Arcane Spellcaster with the same spells per day progression as a Sorcerer. An Elementalist casts spells from the Elementalist Spell List (below). An Elementalist automatically knows every spell on her spell list. She can cast any spell she knows without preparing them ahead of time, provided that spell slots of an appropriate level are still available.

To cast an Elementalist spell, she must have an Intelligence at least equal to 10 + the Spell level. The DC of the Elementalist's spells is Wisdom based and the bonus spells are Intelligence based.}

\ability{\spell{Create Water (Su)}:}{An Elementalist can create water as a standard action at will as the spell create water with a caster level equal to her character level.}

\ability{Armored Casting:}{An Elementalist casts arcane spells, but she is not affected by the arcane spell failure of any armor or shield she is proficient with. This ability only applies to her Elementalist spells, if she is able to cast any other arcane spells, they are affected by arcane spell failure normally.}

\ability{Elemental Survival (Ex):}{An Elementalist of 2nd level or higher survives in elemental planes as easily as on the prime. Whenever on any elemental, paraelemental, or energy plane, she is able to ignore any harmful planar traits and moves through any of these planes without impediment.}

\ability{Advanced Learning:}{At 3rd level and every two levels afterwards, the Elementalist may permanently add one spell to her spell list. This spell must be of a level she can already cast, and may not be of the Illusion or Necromancy school. Only spells from the Druid or Wu Jen spell list may be added in this way.}

\ability{\spell{Create Air (Su)}:}{At 4th level an Elementalist can create air at will as if she was an open Bottle of Air.}

\ability{Elemental Familiar:}{At 5th level, an Elementalist can acquire a familiar in the same manner as a Sorcerer. Unlike a Sorcerer, the Elementalist has only 5 choices for her familiar:}

\listone
    \item \ability{Small Air Elemental:}{+2 to Tumble and Jump Checks.}
    \item \ability{Small Earth Elemental:}{+3 on Bullrush checks, whether the attacker or defender.}
    \item \ability{Small Fire Elemental:}{+3 to Intimidate checks.}
    \item \ability{Small Water Elemental:}{+4 bonus to Swim checks, you may take 10 on swim checks at any time.}
    \item \ability{Small Wood Elemental:}{+2 to Survival and Climb checks.}
\end{list}


\ability{Resistance to Energy (Ex):}{At 7th level, an Elementalist has accumulated an inherent resilience in the face of all manners of elemental adversity. She has an Energy Resistance of 5 against any form of energy damage she is exposed to. At 13th level, this general resistance increases to 10 points. At 19th level, the resistance increases to 15.}

\ability{\spell{Create Fire (Su)}:}{At 9th level, an Elementalist can set a creature or object on fire at will as a standard action. The target must be within short range, and suffers 2d6 of fire damage every round until the fire is extinguished. A victim can attempt to extinguish itself as a full-round action by making a Reflex Save (DC 15). The flames, once begun, are non-magical.}

\ability{Timeless:}{At 10th level, an Elementalist is infused with the uncompromising nature of the raw elements themselves. Se stops aging and never dies of old age.}

\ability{Elemental Traits:}{At 11th level, an Elementalist attunes herself to a specific element, becoming in some way like the element of her choice:}

\listone
    \item \ability{Air Elemental:}{Gains Air Mastery and a Flight Speed (perfect maneuverability) equal to her walking speed.}
    \item \ability{Earth Elemental:}{Gains Earth Mastery, a 30' Tremorsense, and a Burrowing Speed equal to half her walking speed.}
    \item \ability{Fire Elemental:}{Gains Immunity to Fire, and her body immolates whenever desired inflicting an additional 4d6 of fire damage on any creature struck with her unarmed strikes or which strike her with an unarmed strike.}
    \item \ability{Water Elemental:}{Gains Water Mastery, the [Aquatic] subtype, and a swim speed equal to her walking speed.}
    \item \ability{Wood Elemental:}{Gains Immunity to Polymorphing, a 60 foot Woodsense, and a Climb Speed equal to her walking speed.}
\end{list}


\ability{\spell{Create Wood (Su)}:}{At 14th level, an Elementalist can create a full sized tree as a standard action, as if using a Quaal's Feather Token (Tree). This is an at-will ability.}

\ability{Elemental Wildshape (Su):}{At 16th level, the Elementalist can actually become an Elemental in a manner simply to wildshape. Once per day, an Elementalist can assume an Alternate Form of an Air Elemental, an Earth Elemental, a Fire Elemental, a Water Elemental, or a Wood Elemental as a standard action. The alternate form may be dismissed at will, but otherwise persists for 24 hours. Only True Elemental forms may be assumed, and the forms in question must be smaller than Elder (Small to Huge Size is acceptable). Every 2 levels, the Elemental Wildshape may be activated an extra time each day.}

\ability{\spell{Create Earth (Su)}:}{At 17th level, an Elementalist can create a wall of stone at any time as a standard action.}

\spelllist{Elementalist Spell List:}

\small\ability{0th level:}{\emph{Attune Form, Caltrops, Detect Magic, Detect Poison, Light}}

      \ability{1st level:}{\emph{Air Breathing, Entangle, Gust of Wind, Obscuring Mist, Pass Without Trace, Produce Flame, Speak With Plants, Stone Shatter, Summon Elemental I, Wall of Smoke, Water Breathing}}

      \ability{2nd level:}{\emph{Binding Winds, Command Plants, Creeping Cold, Earth Bind, Earthen Grace, Fog Cloud, Heat Metal, Protection From Arrows, Soften Earth and Stones, Summon Elemental II*, Wall of Sand, Warp Wood, Wood Shape}}

      \ability{3rd level:}{\emph{Blight, Control Water, Earth Reaver, Fire Shield, Fly, Plant Growth, Stone Shape, Stone Skin, Summon Elemental III*, Wall of Fire, Wall of Water, Wind Wall}}

      \ability{4th level:}{\emph{Briar Web, Greater Stone Shape, Scry, Summon Elemental IV*, Wall of Stone}}

      \ability{5th level:}{\emph{Animate Plants, Move Earth, Stone Tell, Summon Elemental V*, Wall of Thorns}}

      \ability{6th level:}{\emph{Control Plants, Energy Immunity, Flesh to Stone, Stone to Flesh, Summon Elemental VI*}}

      \ability{7th level:}{\emph{Greater Scrying, Summon Elemental VII*, Transmute Rock to Lava}}

      \ability{8th level:}{\emph{Summon Elemental VIII*}}

      \ability{9th level:}{\emph{Elemental Swarm, Summon Elemental IX*, Summon Elemental Monolith}}
\normalsize
