\classname{Genie} \label{class:genie}
\vspace*{-8pt}
\quot{``Who controls the past, controls the future. Who controls the \spell{wishes}, controls the past.''}

\desc{Djinn, Efreet, Marid, Dao\ldots these are the names that inspire terror and greed throughout the planes, and with good reason. These Genies are far more powerful than the other denizens of the Elemental Sultanates, and it is for this reason that they rule them. They control the wishes, and for many they may as well control the \textit{universe}.}

\desc{The Genies are universally accomplished, but this doesn't make them more powerful at any particular level than any other character. Indeed, level is a measure of power. The most powerful denizens of the Elemental Planes are Genies \textit{and higher level} than mere elementals. The Genie advances in everything all at once, and thus gains new abilities relatively slowly compared to what other, more focused Outsider progressions are capable of.}

\ability{Alignment:}{While the Elemental Planes are Neutral, the denizens often are not. Genies can be of any alignment and often are.}

\ability{Races:}{The Genie is \textit{only} available to Outsiders with a plane of origin in the Elemental Planes. Creatures from the prime material plane whose ancestors were from an Elemental Plane may take this class, but they must have the Outsider type.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{Since a Genie is immortal and never ages, a character may claim any starting age she wishes.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Genie's class skills (and the key ability for each skill) are Appraise (Int, Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Disguise (Cha), Escape Artist (Dex), Hide (Dex), Intimidate (Cha), Knowledge (all skills taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (-), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Speak Language (-), Spellcraft (Int), Spot (Wis), Survival (Wis), Use Magic Device (Cha), and Use Rope (Dex).}

\ability{Skills/Level:}{8 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3.5cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Immortality, Planar Traits\\
2nd &+2 &+3 &+3 &+3 &Telepathy, Lesser Genie Powers\\
3rd &+3 &+3 &+3 &+3 &Genie Powers\\
4th &+4 &+4 &+4 &+4 &Sphere\\
5th &+5 &+4 &+4 &+4 &Greater Planar Traits\\
6th &+6/+1 &+5 &+5 &+5 &\\
7th &+7/+2 &+5 &+5 &+5 &Greater Genie Powers\\
8th &+8/+3 &+6 &+6 &+6 &Sphere\\
9th &+9/+4 &+6 &+6 &+6 &\textit{Summon}\\
10th &+10/+5 &+7 &+7 &+7 &\\
11th &+11/+6/+6 &+7 &+7 &+7 &Grant Wishes\\
12th &+12/+7/+7 &+8 &+8 &+8 &Sphere\\
13th &+13/+8/+8 &+8 &+8 &+8 &Damage Reduction\\
14th &+14/+9/+9 &+9 &+9 &+9 &Awesome Planar Traits\\
15th &+15/+10/+10 &+9 &+9 &+9 &Greater Summoning\\
16th &+16/+11/+11/+11 &+10 &+10 &+10 &Sphere\\
17th &+17/+12/+12/+12 &+10 &+10 &+10 &Elemental Power\\
18th &+18/+13/+13/+13 &+11 &+11 &+11 &\textit{Gate}\\
19th &+19/+14/+14/+14 &+11 &+11 &+11 &Epic Damage Reduction\\
20th &+20/+15/+15/+15 &+12 &+12 &+12 &Sphere\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Genie class.

\ability{Weapon and Armor Proficiency:}{Genies are proficient with all simple and martial weapons, as well as the whip, the net, and the lajatang. Genies are proficient with light armor but not with shields of any kind.}

\ability{Immortality (Ex):}{Ageless as the earth and endless as the sky, the True Genie never ages and retains a youthful appearance unto a thousand thousand generations.}

\ability{Planar Traits:}{A Genie is a member of one of the iconic aristocracies of the Elemental Conflux. Starting at first level she may travel on any elemental plane without suffering the baleful effects of those extreme environments, in addition she gains access to the distinctive abilities of her race, as befits her plane of origin:}

\listone
	\itemability{Fire:}{Efreet Traits:}
	\listtwo
		\itemability{Heat(Ex):}{Any time an Efreet hits an opponent with a melee attack or she is struck with a natural weapon she inflicts her Constitution Modifier in Fire Damage in addition to whatever else she does. This ability may be suppressed as a standard action and resumed as a Swift action.}
		\itemability{Immunity to Fire:}{An Efreet takes no damage from fire of any kind.}
	\end{list}
	\itemability{Air:}{Djinn Traits:}
	\listtwo
		\itemability{Air Mastery (Ex):}{Airborne creatures suffer a -1 penalty to attack and damage rolls against a Djinn.}
		\itemability{Immunity to Acid:}{A Djinn takes no damage from Acid of any kind.}
	\end{list}
	\itemability{Water:}{Marid Traits:}
	\listtwo
		\itemability{Water Mastery (Ex):}{A Marid gains a +1 bonus to attack and damage rolls against opponents touching water.}
		\itemability{Water Breathing (Ex):}{A Marid benefits as per \spell{water breathing}, but non-magical and all the time.}
		\itemability{Immunity to Cold:}{A Marid takes no damage from cold of any kind.}
	\end{list}
	\itemability{Earth:}{Dao Traits:}
	\listtwo
		\itemability{Earth Mastery (Ex):}{A Dao recieves a +1 bonus to attack and damage rolls if both it and its opponent are touching the ground.}
		\itemability{Immunity to Electricity:}{A Dao takes no damage from electricity of any kind.}
	\end{list}
\end{list}

\ability{Telepathy (Su):}{At 2nd level, a Genie gains the ability to communicate telepathically with any creature that speaks a language within 100 feet.}

\ability{Genie Powers (Sp):}{At 2nd level, a Genie may cast \spell{create food and water} once per day. At 3rd level, the Genie can \spell{planeshift} at will. The only planes which can be accessed in this manner are the Elemental planes and the prime material. Only willing creatures may be transported. At 7th level, a Genie may cast \spell{major creation} 3 times a day. Any objects created which last more than 12 hours are permanent.}

\ability{Sphere:}{The Genie gains basic access to a sphere at 4th level, and gains a new sphere at every fourth level afterwards. If the Genie selects a sphere that she already has basic access to, she upgrades it to advanced access. If she already had advanced access, she gains expert access.}

\ability{Greater Planar Traits:}{A Genie of 5th level or more gains access to more of the distinctive abilities of her race, as befits her plane of origin:}

\listone
	\itemability{Fire:}{Efreet Traits:}
	\listtwo
		\itemability{Size Changing (Sp):}{An Efreet can change a creature's size up or down one size category for an hour, and can do this twice per day. This can be used offensively, and the save DC is Charisma based. This is the equivalent of a 2nd level spell.}
		\itemability{Start Fires (Su):}{An Efreet can set anything she can see on fire as a standard action.}
	\end{list}
	\itemability{Air:}{Djinn Traits:}
	\listtwo
		\itemability{Whirlwind (Ex):}{A Djinn can assume the form of a whirlwind, as described in the description of the Air Elemental.}
		\itemability{Gust of Wind (Sp):}{A Djinn can use \spell{gust of wind} at will.}
	\end{list}
	\itemability{Water:}{Marid Traits:}
	\listtwo
		\itemability{Drench (Ex):}{A Marid can extinguish normal or magical fires with a touch. This always works.}
		\itemability{Resistances:}{A Marid has Sonic, Fire, and Acid Resistance 10.}
	\end{list}
	\itemability{Earth:}{Dao Traits:}
	\listtwo
		\itemability{Earth Glide:}{At 5th level, a Dao is able to move through solid stone as if it were open space. She may take any non-living objects she can carry with her.}
	\end{list}
\end{list}

\ability{Summon (Sp):}{At 9th level, a Genie can attempt to \spell{summon} vassals and others of its kind (for example: a Djinn could summon other denizens of the Plane of Air). Summoning another creature of the same character level has a 40\% chance of success, and summoning a creature of a lower level increases the chances of success by 10\% for every level the summoner's level exceeds the CR of the target.}

\ability{Grant Wishes (Sp):}{At 11th level, a Genie bcomes a steward of the \spell{wish} economy. She may grant up to three mortal wishes each day. Doing so takes a few minutes to word the \spell{wish} properly and any costs are paid by the recipient (remember that many wishes do not have a special cost).}

\ability{Damage Reduction (Su):}{A 13th level Genie has Damage Reduction of Level/Adamantine. At 19th level this becomes DR of Level/Epic.}

\ability{Awesome Planar Traits:}{A Genie of 14th level or more gains access to more of the distinctive abilities of her race, as befits her plane of origin:}

\listone
	\itemability{Fire:}{Efreet Traits:}
	\listtwo
		\itemability{Firestorm (Sp):}{An Efreet can use \spell{firestorm} at will.}
	\end{list}
	\itemability{Air:}{Djinn Traits:}
	\listtwo
		\itemability{Telekinesis (Sp):}{A Djinn can use \spell{telekinesis} at will.}
	\end{list}
	\itemability{Water:}{Marid Traits:}
	\listtwo
		\itemability{Acid Fog (Sp):}{A Marid can use \spell{acid fog} once per hour.}
	\end{list}
	\itemability{Earth:}{Dao Traits:}
	\listtwo
		\itemability{Transmute Rock and Mud (Sp):}{A Dao can use \spell{transmute rock to mud} and \spell{transmute mud to rock} at will.}
	\end{list}
\end{list}

\ability{Greater Summoning:}{A Genie of 15th level may attempt to use her summon power to summon a creature of a level higher than her own, though doing so carries only a 30\% chance of success.}

\ability{Elemental Power:}{The powers of the lower planes are awesome to behold. At 17th level, the True Fiend gains a +10 bonus to defeating Spell Resistance with the spell-like abilities granted by her spheres.}

\ability{Gate (Sp):}{At 18th level, a Genie can open a \spell{gate} (transport version) whenever she wants.}
