\classname{Fire Mage} \label{class:firemage}
\vspace*{-8pt}
\quot{``Burn, baby, burn.''}

A Fire Mage is someone who burns their own soul out to burn the bodies of others. Tactically, they shine against groups of enemies, because fires spread across the battlefield like a plague. Oddly, they tend to have trouble when facing off against furnishings. 

\ability{Playing a Fire Mage:}{The Fire Mage is a user of magic, and that magic is based on Charisma. But they are also a heavy user of ranged attacks, and at low to mid levels have some tricks that can be effective in melee, so a fire mage also wants a decent Dexterity and possibly Strength.}

\ability{Alignment:}{Fire is a destructive force, and a lot of Fire Mages are Chaotic. But they don't have to be.}

\ability{Races:}{Fire Mages appear in all races, though significant portions of many races live in areas where being a Fire Mage is illegal.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Fire Mage's class skills (and the key ability for each skill) are Bluff (Cha), Climb (Str), Craft (Int), Concentration (Con), Disguise (Cha), Escape Artist (Dex), Handle Animal (Cha), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Profession (-), Ride (Dex), Search (Int), Spellcraft (Int), Spot (Wis), Survival (Wis), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st  &+0          &+2  &+2  &+2  &Fire Resistance, Fire Burst, Fire Bolts, Impress Flames, Fire Magic\\
2nd  &+1          &+3  &+3  &+3  &Ignite, Friend to Flames\\
3rd  &+2          &+3  &+3  &+3  &Piercing Flames, Hand of Fire\\
4th  &+3          &+4  &+4  &+4  &Fire Immunity, Smokeless Flame\\
5th  &+3          &+4  &+4  &+4  &Great Balls of Fire\\
6th  &+4          &+5  &+5  &+5  &Mindfire\\
7th  &+5          &+5  &+5  &+5  &Visions of Flame, Fiery Reach\\
8th  &+6/+1       &+6  &+6  &+6  &Soul of Cinders\\
9th  &+6/+1       &+6  &+6  &+6  &Sculpt Flames\\
10th &+7/+2       &+7  &+7  &+7  &Conflagration\\
11th &+8/+3       &+7  &+7  &+7  &Beacon, Firewalk\\
12th &+9/+4       &+8  &+8  &+8  &Bond of Fire\\
13th &+9/+4       &+8  &+8  &+8  &Fire Clouds\\
14th &+10/+5      &+9  &+9  &+9  &Fiery Dawn, Ray of Light\\
15th &+11/+6/+6   &+9  &+9  &+9  &Sending, Rain of Fire\\
16th &+12/+7/+7   &+10 &+10 &+10 &Brain Burn, Blazing Speed\\
17th &+12/+7/+7   &+10 &+10 &+10 &Lord of Flames\\
18th &+13/+8/+8   &+11 &+11 &+11 &The Unforgettable Fire\\
19th &+14/+9/+9   &+11 &+11 &+11 &Spontaneous Combustion\\
20th &+15/+10/+10 &+12 &+12 &+12 &End in Flames, Holocaust
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Fire Mage class.

\ability{Weapon and Armor Proficiency:}{Fire Mages are proficient with all simple weapons, as well as the whip, all martial axes, and all sizes and varieties of scimitar (including falchions). Fire Mages are proficient with light armor but not with shields of any kind.}

\ability{Fire Resistance (Ex):}{A Fire Mage has a Resistance to Fire equal to twice his level.}

\ability{Fire Burst (Sp):}{As a standard action, a Fire Mage can emit a burst of flame from her body, striking all creatures and objects within 10' of her position except herself. This burst of flames inflicts 1d6 of fire damage + an additional 1d6 per two character levels beyond 1st (2d6 at 3rd, 3d6 at 5th, 4d6 at 7th, etc) with an allowed Reflex Save for half (DC 10 + ½ Level + Charisma Modifier).}

\ability{Fire Bolts (Sp):}{A Fire Mage can throw bolts of fire as an attack action. A Fire Bolt tavels out to short range, and inflicts 1d6 of Fire damage per character level. A Fire Bolt strikes its target with a ranged touch attack.}

\ability{Impress Flames (Ex):}{: Every time a Fire Mage inflicts Fire damage on any target, whether with her class abilities or another source of fire, she inflicts an amount of extra Fire Damage equal to her character level or her Charisma bonus, whichever is less.}

\ability{Fire Magic (Ex):}{A Fire Mage is considered to have every spell with the Fire Descriptor on her spell list for the purpose of activating magic items or entering Prestige Classes. Spell-Like Abilities granted by the Fire Mage class are the equivalent level of the spell they duplicate, or if they do not duplicate a specific spell, they are the equivalent of a spell equal to half the class level at which they are gained (maximum 9th level).}

\ability{Ignite (Sp):}{As a standard action, a 2nd level Fire Mage can cause any creature or object to burst into flame. A creature on fire suffers 1d6 of Fire damage per round (the Mage's Impress Flames ability applies to each round of course), and the creature can attempt to put itself out with a DC 15 Reflex save (see the DMG, p. 303). This ability can be used out to Medium range, and it always hits.}

\ability{Friend to Flames (Ex):}{A fire mage of at least 2nd level adds half of her level to any Bluff, Diplomacy, Handle Animal, Intimidate, or Sense Motive check made to interact with a [Fire] creature.}

\ability{Piercing Flames (Ex):}{From 3rd level on, a Fire Mage may chose to make any fire damage she deals into Piercing Flames. When she does so her fire damage cuts through Fire Resistance, hardness, and Immunity. No more than ½ of the damage inflicted by her Piercing Flames can be negated by hardness or immunity or resistance to Fire. In addition, Piercing Flames ignores the first 5 points of Fire Resistance that a target has.}

\ability{Hand of Fire (Su):}{A 3rd level Fire Mage can, as an immediate action, set fire to her own body, causing her to count as armed at all times, even with unarmed attacks. While using this ability the Fire Mage also causes an extra 1d6 of Fire damage with all melee attacks. She may dismiss this ability as a free action, but otherwise it lasts 1 round per character level.}

\ability{Fire Immunity (Ex):}{At 4th level the Fire Mage becomes immune to Fire.}

\ability{Smokeless Flames (Sp):}{A 4th level Fire Mage can create fires that produce no heat and do not burn. These fires can be anything from the size of a torch to a bonfire, and produce light accordingly. Each lasts until the next time the sun rises. Smokeless Flame can be created anywhere within Medium range.}

\ability{Great Balls of Fire (Sp):}{A 5th level Fire Mage can hurl explosive fire anywhere within Long Range as a Full Round Action. This Fire explodes into a 20' radius burst and inflicts 1d6 of Fire Damage per character level. All creatures within the area are entitled to Reflex saves to halve damage (DC 10 + ½ Level + Charisma Modifier).}

\ability{Mindfire (Sp):}{A 6th level Fire Mage can start a Fire in a creature's mind, duplicating the effects of rage or confusion for a number of minutes equal to her Level. The victim must be within Medium Range, and is entitled to a Will Save to negate this effect (DC 10 + ½ Level + Charisma Modifier). This is a Mind influencing Compulsion effect.}

\ability{Visions of Flames (Sp):}{A 7th level Fire Mage can see through smoke and flame. She ignores any concealment or total concealment due to smoke, flame or [Fire] effects. Also, she see into the heart of flames and may use \spell{contact other plane} at will to communicate with the denizens of the Elemental Plane of Fire. A Fire Mage is in no danger of becoming insane or damaged by this experience.}

\ability{Fiery Reach (Ex):}{At 7th level a fire mage gains an extra 5' of reach with any flaming melee weapon. This applies to magic weapons with the Flaming ability, flame blade and similar spells, and also to any of her own melee weapons while she is using her hand of fire ability.}

\ability{Soul of Cinders (Sp):}{An 8th level Fire Mage has tempered her soul in fires hotter than Battor, and is no longer susceptible to Energy Drain or Fear.}

\ability{Sculpt Flames (Sp):}{A 9th level Fire Mage can create delicate shapes and walls made of fire. The Fire is fully shapeable, but cannot pass through more than 2 squares per level. Any creature passing through a square with fire in it suffers 1d6 of fire damage per character level. A creature which is in a square that is being filled with fire is entitled to a Reflex Save (DC 10 + ½ Level + Charisma Modifier) to move to the nearest non-flaming square as an immediate action. These fires persist for 1 round per level. Alternately, the Fire Mage can replicate a wall of fire which persists for 1 minute per level.}

\ability{Conflagration (Sp):}{At 10th level, a Fire Mage can surround herself with a nimbus of flames that extends for 10' in all directions from his person. All other targets in this area suffer a d10 of Fire Damage per character level, but are entitled to a Reflex Save (DC 10 + ½ Level + Charisma Modifier). In addition, a 10th level Fire Mage is permanently treated as having a fireshield Warm Shield version upon her person whenever she wants.}

\ability{Beacon (Sp):}{An 11th level Fire Mage can create a magically permanent bonfire as a standard action. She always knows exactly where each Beacon she has created is and will know if it is put out by any means.}

\ability{Firewalk (Sp):}{At 11th level a Fire Mage can walk into any fire large enough to fit her person and appear in any other fire that is likewise of sufficient size anywhere on any plane of existence. The Fire Mage must know where the target fire is. The Fire Mage can take along any number of willing creatures or carried objects that are also able to fit in both flames.}

\ability{Bonds of Fire (Sp):}{A 12th level Fire Mage can craft solid fire into restraints and entrap target within short range. The bonds will immobilize a creature which fails a Reflex Save (DC 10 + ½ Level + Charisma Modifier), and will entangle the creature unless it succeeds in its save by more than 5. A creature can attempt to escape by taking a Full round action to make a Strength or Escape Artist test with a DC equal to the Use Rope Skill Result of the Fire Mage. The victim suffers 20 points of Fire Damage per round, and the bonds of fire last until the victim escapes or the Fire Mage dismisses them.}

\ability{Fire Clouds (Sp):}{As a Full Round Action, a 13th level Fire Mage can create huge billowing clouds of Fire. The Fire Clouds must be created within Long range, and persist for 3 rounds whether they are still in range or not. The cloud is shapeable, and covers at most 3 10' cubes per Level. Each round, everyone and everything inside the cloud suffers 1d6 of Fire damage per character level, but is entitled to a Reflex save for half damage (DC 10 + ½ Level + Charisma Modifier).}

\ability{Fiery Dawn (Sp):}{A 14th level Fire Mage can call levels of illumination that are painful and destructive as the unmitigated baleful glare of the sun itself. All darkness within 5 miles is dispelled, and everything is illuminated. All undead suffer a 10 points of damage per round. All creatures specifically vulnerable to light suffer 10 damage per round (thus, vampires suffer 20 damage per round). All creatures are dazzled. Creatures must pass a Fortitude save (DC 10 + ½ Level + Charisma Modifier) every minute or become blind for the remainder of the effect. Creatures that are blinded when the effect ends are entitled to another Fort save to get their vision back, but if they fail this save the blinding is permanent. This effect lasts until the Fire Mage dismisses it or becomes incapacitated.}

\ability{Ray of Light (Sp):}{As an attack action, a 14th level Fire Mage can fire a ray of Light at any target within Short Range. It inflicts 1d6 of Light Damage per character level if it hits with a Ranged Touch Attack. Undead take 10 extra damage. Creatures specifically vulnerable to Light suffer an additional 10 damage.}

\ability{Sending (Sp):}{A 15th level Fire Mage can send a message, as the sending spell to any creature on any plane of existence with a standard action and receive a reply even if they are on different planes of existence.}

\ability{Rain of Fire (Sp):}{At 15th level, the Fire Mage can open the skies and dump raw inferno upon all who would oppose her. The fires inflict 1d6 of Fire Damage per character level, and victims are permitted a Reflex save (DC 10 + ½ level + Charisma Modifier) for half damage. The Fire Mage chooses which squares are struck with fire, and the only limits to how many squares can burn is how many squares the Fire Mage can see. There are no range limits to this power save line of sight.}

\ability{Brain Burn (Sp):}{A 16th level Fire Mage can set a creature's mind ablaze, with a standard action, she may duplicate the effects of greater heroism or insanity The target must be within Medium Range, and is entitled to a Will Save to negate this effect (DC 10 + ½ Level + Charisma Modifier). This is a Mind influencing Compulsion effect.}

\ability{Blazing Speed (Ex):}{At 16th level, the Fire Mage gains the ability to use her abilities with the speed of a wildfire. She may now use an immediate action to activate any Fire Mage class ability which would otherwise recquire a Standard or Attack Action to activate.}

\ability{Lord of Flames (Sp):}{At 17th level, the Fire Mage gains the ability to compel creatures of fire. This works as per dominate monster save that it can only effect creatures of the [Fire] subtype but can effect [Fire] subtype creature types normally immune to mind-affecting effects, such as Undead and Constructs. A target may negate this with a Will Save (DC 10 + 1/2 Level + Charisma Modifier) a creature that successfully saves cannot be affected again by the same Fire Mage's use of this ability for 24 hours.}

\ability{The Unforgettable Fire (Sp):}{At 18th level, the Fire Mage gains the ability to use discern location at will to learn the location of any creature or object to whom she has previously dealt fire damage.}

\ability{Spontaneous Combustion (Sp):}{At 19th level, the Fire Mage gains the ability to make enemies 'asplode with a thought. As a standard action she forces one creature or object in short range to make a Fortitude Save (DC 10 + 1/2 Level + Charisma Modifier). Creatures who fail this save die instantly, objects which fail are reduced to smoke and ash. Creatures and objects who succeed on this save still take 1d6 Fire damage per character level. Any creatures slain by this ability can only be restored to life via true resurrection, miracle, or using a wish followed by resurrection.}

\ability{End in Fire (Su):}{At 20th level, the Fire Mage exhibits a splendor like the radiance of a thousand suns bursting at once and has become a shatterer of worlds. As a full round action, she may destroy any demiplane she occupies. Doing this shunts all occupants of the demiplane to the parent plane, but utterly destroys any non-attended object of less than artifact status (no save).}

\ability{Holocaust:}{at 20th level, the Fire Mage Wins D\&D.}
