\classname{The Witch}

\desc{Fantasy literature has always had witches. Usually they are evil and fly on broomsticks, cackling and cursing/poisoning the heroines into a coma or death, so that the prince charming can save them and fuck them, hopefully in that order. Occasionally they're just generically evil -- they're bad because they're witches, but they don't particularly do anything that evil, and sometimes there are good witches.}

\desc{The witch in D\&D draws upon the various fantasy sources, along with an option to be a good, nature-friendly, curse-removing witch for all the hippy wicca kids out there. They gain the ability to fly, they can use cauldrons to scry and make magic potions, they have a ritual under the full moon, and they have a scary evil eye. Also, there is the mandatory Monty Python reference, and they have spellcasting which is by no means shabby.}

\desc{The witch can happily be played by beginners: they have Save or Lose spells and save-penalising spells. It's as simple as ``pump your DCs up high and go wild''. By the same token, they have enough oddball spells there that more experienced players can go around turning the forest into their personal army, or turning a room of people into statues, reshaping them into other objects, then covering them in symbols and adding sympathy so people go and touch them. Maybe even turning the morphed statues back into flesh. Did you ever want a vase made of human flesh?}

\ability{Starting Gold:}{3d4x10 gp (75 Gold)}

\ability{Starting Age:}{As Sorcerer}

\ability{Hit Die:}{1d6}

\ability{Class Skills:}{}

\ability{Skill Points:}{6 + Int modifier.}

\ability{Ability Scores:}{The Witch wants a reasonably high Charisma, for the spell-like and Supernatural abilities, but also wants a good Intelligence or Wisdom, for spellcasting (they can choose which one). Maintaining both should not be hard, and the physical ability scores are practically optional.}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+0 &+2 &Evil Eye, Spellcasting, Armored Casting\\
2nd &+1 &+3 &+0 &+3 &Animal Form or Familiar, Wild Empathy\\
3rd &+1 &+3 &+1 &+3 &Brew Potion\\
4th &+2 &+4 &+1 &+4 &Trickery, Float on Water\\
5th &+2 &+4 &+1 &+4 &Evil Eyes\\
6th &+3 &+5 &+2 &+5 &Mass Brewing, Pluck Poison\\
7th &+3 &+5 &+2 &+5 &Dream Mastery\\
8th &+4 &+6 &+2 &+6 &Trickery\\
9th &+4 &+6 &+3 &+6 &Evil Gaze\\
10th &+5 &+7 &+3 &+7 &Cauldron Scrying\\
11th &+5 &+7 &+3 &+7 &Flight\\
12th &+6/+1 &+8 &+4 &+8 &Trickery, Hag Bite [b]or[/b] Bibbity Bobbity Boo\\
13th &+6/+1 &+8 &+4 &+8 &Ritual of Youth\\
14th &+7/+2 &+9 &+4 &+9 &Eye of Newt\\
15th &+7/+2 &+9 &+5 &+9 &Presence of Witchery\\
16th &+8/+3 &+10 &+5 &+10 &Trickery\\
17th &+8/+3 &+10 &+5 &+10 &Craft Heartstone\\
18th &+9/+4 &+11 &+6 &+11 &Hag Laughter or Rise of the Triffids\\
19th &+9/+4 &+11 &+6 &+11 &Elixer of Life and Death\\
20th &+10/+5 &+12 &+6 &+12 &Trickery\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Witch class.

\ability{Weapon and Armor Proficiency:}{Witches are proficient with all simple weapons and with light armor, but not with shields of any kind.}

\ability{Evil Eye:}{As a Swift action, the Witch may use this Supernatural ability at will. They must target an enemy within Close Range that they can see, although spells like Mirror Image, Blink and Displacement have no effect -- the target can still be seen. The target must then make a Will save (DC 10 + half the Witches' HD plus the Witches' Charisma modifier) or be Shaken for as long as they can see the Witch. If already Shaken, they become Frightened. If Frightened, they Cower. If Cowering or Panicked, they fall Comatose. If they pass the save, they take a -2 penalty on Saving Throws until the end of the Witches' turn.
This is a [Mind Affecting, Fear] effect.}

\ability{Spellcasting:}{The Witch instinctively knows all spells on the Witch spell list. They cast spells per day as per the Wizard, gaining bonus spells per day for a high Wisdom or Intelligence score (select at first level, it cannot change). The same ability score determines the save DCs. Spells are cast spontaneously from the Witch spell list.}

\ability{Armored Casting:}{A Witch casts arcane spells, but she is not affected by the arcane spell failure of any armor or shield she is proficient with. This ability only applies to her Witch spells, if she is able to cast any other arcane spells, they are affected by arcane spell failure normally.}

\ability{Animal Form:}{At 2nd level the Witch may transform into a Tiny, non-offensive animal as a Supernatural ability at will. This lasts until the upcoming midday, dusk, midnight or dawn (whichever comes first), or until dismissed, and gives the Witch the physical ability scores of the animal in question, however they may not cast spells in this form. The Witch may choose either Animal Form or Familiar, but not both.}

\ability{Familiar:}{Alternatively, the Witch may opt to gain a familiar. This works like the Sorcerer and Wizard, except if it dies then the Witch merely becomes sad for a little while, and another one can be summoned the following day. If the Witch gains a cohort, it may be any form of animal or monstrous creature (subject to the usual limitations) and can be treated as a familiar. Yes, that polar bear that sits outside the cafe ``begging'' for food? That's a familiar, waiting to steal your soul.}

\ability{Wild Empathy:}{Just like a Druid.}

\ability{Brew Potion:}{Using a Cauldron, a 3rd-level Witch may brew a potion of any spell level they can cast. This uses the spell slot, and takes one hour but has no expensive components or XP cost. The potion lasts for 24 hours before returning to brackish water.}

\ability{Trickery:}{At every 4th level, one ability may be chosen from the following list to allow the Witch to cheat death.

\listone
    \item Energy Resistance 10 + Hit Dice to any one energy type. This may be taken multiple times, either granting resistance to another energy or adding +10 to all energy resistances (which will apply to future energy resistances gained).
    \item Damage Reduction 3 + Half Hit Dice, overcome by Iron. This may be taken multiple times, adding +6 to the DR each time.
    \item Spell Resistance 5 + Hit Dice. This may be taken twice more, each adding +3 to the SR.
    \item Immune to Detect spells and True Seeing
    \item A +4 bonus on saving throws against [Mind Affecting] Effects. This may be taken twice more, increasing the bonus by +4 each time.
    \item Immune to Poison
    \item Immune to Disease
    \item A +4 bonus on saving throws against the spell-like and supernatural effects of Outsiders, Elementals and Fey. This may be taken twice more, increasing the bonus by +4 each time.
\end{list}}

\ability{Float on Water:}{The Witch weighs as much as a duck at 4th level, so may float on water, never sinking or drowning.}

\ability{Evil Eyes:}{At 5th level the Witch may now target two people at the same time with the Evil Eye ability. Alternatively, both eyes may be focused on the one person, causing them to instead be Sickened on a failed save, or Nauseated if already Sickened, or to immediately contract Demon Fever if already Nauseated. This option is neither [Mind Affecting] nor a [Fear] effect.}

\ability{Mass Brewing:}{When Brewing a Potion, a 6th level Witch may make a number of potions equal to their Charisma modifier, although these will only last for four hours each. But it still takes only one hour to brew in total, and uses the one spell slot.}

\ability{Pluck Poison:}{Thrice per day at 6th level, the Witch may pluck a berry or fruit from a tree, or a mushroom from the ground. It becomes tainted with any ingested poison of the Witches' choice, with a save DC equal to 10 + half their HD + their Charisma modifier, or may neutralise poison. This lasts for 12 hours.}

\ability{Dream Mastery:}{At 7th level the Witch may cast Nightmare as a Supernatural ability at will. The save DC is Charisma based. They may also Planeshift into (and out from) the dreamscape of anyone sleeping within 30', also at will.}

\ability{Evil Gaze:}{The Evil Eye (either variant) may, at 9th level, be used similar to a Gaze attack that affects all in a 50' cone. It still requires a Swift Action to activate, as it is not always active. Everyone must attempt to save, but may elect to avert their eyes -- they lose their Dexterity bonus to their AC for 1 round, but are allowed a Reflex save. If this save is passed, they are immune to all effects. If it is failed, they are entitled to the Will save as normal. Alternatively, the regular Evil Eye or Evil Eyes may be used to make those who fail the save Fatigued. If already Fatigued they become Exhausted, and if already Exhausted they pass out.}

\ability{Cauldron Scrying:}{The Witch may Scry once per day at 10th level, using a cauldron to see through. This is a Spell-like ability, with a DC equal to 10 + half their HD + their Charisma modifier.}

\ability{Flight:}{Upon reaching 11th level, the Witch may fly at will, with an unlimited duration, as per the spell. Some form of object is required for this, such as a broomstick, carpet, bathtub or vacuum cleaner.}

\ability{Hag Bite:}{At 12th level the Witch gains a bite attack that deals 2d6 damage plus one and a half times their Strength modifier, if Medium. This also causes Demon Fever. A Good Witch probably shouldn't choose this ability.}

\ability{Bibbity Bobbity Boo:}{Alternatively, if the Witch is not Evil, they may prefer the ability to cast Animate Objects at will, lasting until the upcoming dawn, midday, dusk or midnight (whichever comes first). This works only on plants, however it can also change their form to a moderate degree. Examples include turning pumpkins into carriages, flowers into cleaning objects and [s]pineapples into thermonuclear weapons[/s] cabbages into horses. But they'll still look something like the original object, and can still be eaten.}

\ability{Ritual of Youth:}{The Witch may perform an 8 hour ritual under the light of a full moon. This involves chanting, dancing, and probably a campfire. Successfully completing the ritual changes the Witch to the Adult age category, and lasts for 2 months. Performing it again in the meantime resets the timer. After it ends, they change back to their true age, so eventually this becomes essential to prevent death by old age. Yes, it effects physical ability score modifiers.}

\ability{Eye of Newt:}{The Witch may harvest organs from creatures they assist in slaying, for use in item creation. This grants an XP component equal to the CR of the creature, squared.}

\ability{Presence of Witchery:}{Any place a Witch resides in for one month or more gains a 100' radius aura. This aura then extends out to 1 mile after another month. Either the land becomes blighted, affected by an Unhallow effect, with all water tasting foul and killing all small fish residing therein and all plants withering and dying, or the land becomes fruitful, affected by a Hallow effect, the water becoming sweet and free of disease and all crops yielding a full harvest.}

\ability{Craft Heartstone:}{By performing a ritual under a full moon, requiring at least two other willing participants (both must be familiars, witches or Night Hags) and four hours, the witch may create a Heartstone. They gain all benefits and are treated as a Night Hag, being able to turn Ethereal and haunt dreams like a Night Hag. If the witch is a good witch, they may ``haunt'' the dreams of Non-Evil creatures, protecting them from Nightmares, Dream Haunting, and any intruders into a Dreamscape. The target will wake up fully refreshed and with a Good Hope effect that lasts for the rest of the day.}

\ability{Hag Laughter:}{Three times per day, an 18th level Witch may emit a cackling laugh as a Standard Action. One target per level who can hear this must make a Fortitude save (DC 10 + half the Witches' HD + their Cha modifier) or immediately contract Cackle Fever, taking 3d6 Wisdom damage instantly. Good Witches probably don't want to do this. A Witch may select either Hag Laughter or Rise of the Triffids, but not both.}

\ability{Rise of the Triffids:}{Instead of Hag Laughter, the Witch may elect to be able to call vegetation to their aid. As long as there is at least a 10'x10' square of plant matter, it may rise up to aid the Witch as a Battlebriar, with Hit Dice equal to the Witch. This may be done once per day, requiring a Standard Action, and lasts until the upcoming dawn, midday, dusk or midnight (whichever comes first). The summoned plant life is completely loyal to the Witch. A Witch may select either Hag Laughter or Rise of the Triffids, but not both.}

\ability{Elixer of Life and Death:}{At 19th level, the Witch may brew a special Elixer under the light of the full moon, requiring 6 hours. Doing so makes a single dose of this potent brew, which will last for 24 hours before becoming useless. If force-fed to the dead, they return to life with no level loss, full regeneration of limbs and no lasting problems. If given to the living, then at the option of the Witch, they either must immediately make a Fortitude save against being slain, or are freed from any ailments. This can even be used to suppress the transformation of a Werewolf (no save against this) or return the Sentient Undead to life (again, no save), both lasting for 24 hours.}
[/spoiler]

\spelllist{Witch Spell List:}

\small\ability{0th level:}{\emph{Arcane Mark, Bestow Curse 0 Dancing Lights, Detect Magic, Detect Poison, Remove Curse 0, Touch of Fatigue}}

      \ability{Level 1:}{\emph{Animate Rope, Bane, Bestow Curse I, Cause Fear, Charm Person, Command, Curse Water, Faerie Fire, Magic Mouth, Message, Ray of Enfeeblement, Reduce Person, Remove Curse I, Remove Fear, Sleep}}

      \ability{Level 2:}{\emph{Augury, Bestow Curse II, Blindness/Deafness, Calm Emotions, Command Undead, Delay Poison, Desecrate, False Life, Hideous Laughter, Reduce Animal, Remove Curse II, Remove Paralysis, Speak With Animals, Summon Swarm, Touch of Idiocy, Warp Wood}}

      \ability{Level 3:}{\emph{Bestow Curse III, Charm Monster, Contagion, Deep Slumber, Fear, Plant Growth, Ray of Exhaustion, Remove Blindness/Deafness, Remove Curse III, Remove Disease, Secret Page, Sepia Snake Sigil, Shrink Item, Tiny Hut*}}

      \ability{Level 4:}{\emph{Baleful Polymorph, Bestow Curse IV, Blight, Command Plants, Confusion, Insect Plague, Neutralize Poison, Phantasmal Killer, Poison, Mass Reduce Person, Remove Curse IV, Unholy Blight}}

      \ability{Level 5:}{\emph{Animal Growth, Awaken, Bestow Curse V, Crushing Despair, Dream, Feeblemind, Mirage Arcana, Remove Curse V, Repel Vermin, Symbol of Pain, Transmute Rock to Mud, Transmute Mud to Rock, Unhallow, Waves of Fatigue}}

      \ability{Level 6:}{\emph{Animate Objects, Bestow Curse VI, Greater Command, Commune With Nature, Eyebite, Flesh to Stone, Stone to Flesh, Remove Curse VI, Symbol of Fear, Wall of Thorns}}

      \ability{Level 7:}{\emph{Animal Shapes, Animate Plants, Bestow Curse VII, Creeping Doom, Insanity, Power Word: Stun, Remove Curse VII, Symbol of Insanity, Symbol of Stunning, Symbol of Weakness, Waves of Exhaustion}}

      \ability{Level 8:}{\emph{Antipathy, Bestow Curse VIII, Binding, Control Undead, Horrid Wilting, Irresistable Dance, Magnificent Mansion*, Maze, Remove Curse VIII, Symbol of Death, Sympathy, Trap the Soul}}

      \ability{Level 9:}{\emph{Bestow Curse IX, Control Plants, Imprisonment, Remove Curse IX, Wail of the Banshee}}
\normalsize

New and Altered Spells:

\ability{Mordenkainen's Tiny Hut:}{this may work as normal, or it may create an actual physical gingerbread cottage. It is immune to normal weather and remains edible for the duration, however it tends to lure animals and children to it.}

\ability{Mordenkainen's Magnificent Mansion:}{This creates a physical gingerbread mansion, rather than forming a demiplane and transporting you there. Otherwise it acts like the spell. Remember that it is edible.

Yes, you could totally fill it with radishes and then Bibbity Bobbity Boo them into prostitutes and create a very unique brothel, unless Frank is going to tell me that's a famous myth/story somewhere in the world.}

\ability{Remove Curse 0-IX}{Basically have the same effect: they remove curses applied by Bestow Curse of equal or lower level, and of Supernatural/Spell-like Curse/Evil Eye abilities that have a Caster Level (or Hit Dice of the creator) of no more than double the level of the Remove Spell. Remove Curse VII and higher also function as Break Enchantment for spells of equal or lower level, and Remove Curse IX can also grant the effects of Freedom.}

\ability{Bestow Curse 0-IX}{Requires a touch attack, but allows no saving throw when cast by the Witch. The duration depends on the spell level: 0-I is ``for the rest of the encounter'', II-III is ``until the next dawn, dusk, midday or midnight (whichever comes first)'', IV-VI is ``for one day'', VII-VIII is ``until the next full moon (does not count the current one if currently during a full moon)'' and IX is ``permanent''.

Spell Resistance still applies. The effects vary by level (and any version may use the effect of a lower level, with the new DC and duration):}

\begin{list}{}{\itemspace}
\itemability{0:}{The target becomes Sickened or takes a -4 penalty on all Skill Checks}
\itemability{I:}{The target suffers 20\% action failure on all actions or takes a -4 penalty on all d20 rolls or becomes fascinating to animals and vermin, who are attracted to the character within a 1 mile radius and are all determined to share the character's occupied space.}
\itemability{II:}{The target suffers 50\% action failure on all actions or takes a -8 penalty to one ability score, or all of their equipment instantly falls to the ground, even things that really shouldn't fall off. Even bags spill open.}
\itemability{III:}{The target suddenly ages, taking a -6 penalty to Strength, Dexterity and Constitution and has poor vision, gaining a -6 penalty to Spot and Search and treating everyone as though they had Concealment.}
\itemability{IV:}{the target is rendered unable to speak, or enters a Rage but has a 50\% chance of not being able to tell enemy from ally. Alternatively, they become terribly allergic to either Plants, Animals or Vermin (caster chooses), taking a -10 penalty on all attack rolls, Fort saves and skill checks when within 10' of one.}
\itemability{V:}{the target forgets a single class feature of the caster's choice, or is treated as having zero ranks in any of their skills, or a Centipede Swarm appears within their stomach and attacks, requiring disembowelment (50\% of their HP or more) to remove. Every morning, another swarm will appear there. Oh joy. If cast as the level 8 or 9 version, enjoy Hellwasps instead.}
\itemability{VI:}{the target is rendered Blind and Deaf and also enters a Rage, charging in random directions and attacking whatever they bump into, or their clothing all animates (as per Animate Object) and tries to kill them.}
\itemability{VII:}{The target becomes suicidal, attempting to find ways to end their own life, or is rendered unable to sleep, suffering all of the effects of sleep deprivation. Alternatively, their hands turn into Small Monstrous Spiders (with HD equal to the Caster Level) which immediately try to bite them until hacked off (dealing the damage of the injury to the target) and then slain. They then turn back into hands, but are detached. This will happen every morning for the duration, as well.}
\itemability{VIII:}{The target becomes Stunned or Nauseated, or despite all logic is targeted by a single Comet once per day for the entire duration. What are the odds? Alternatively, they contract a disease, and contract another one every morning they wake up.}
\itemability{IX:}{The target suffers an Eternity of Torture effect, or their weapons turn into snakes (Half Fiend or Half Celestial, with +1 Outsider hit die per Caster Level) and immediately attack them, treating their natural weapons as though they had all the special abilities and enhancement bonuses of the original weapon. If it is a weapon of 3 Wishes, you can expect the snake to waste them, going ``I wish I was out in the desert somewhere. I wish I had a pond of cool water. I wish I had a mouse. Yeeeeeeah, I'm so happy.''

Moses has nothing on this.}
\end{list}