\classname{Curator} \label{comm:class:curator}
\vspace*{-8pt}
\quot{``These people are under my stewardship. Please handle them with care.''}

%\desc{}

%\ability{Alignment:}{}

%\ability{Races:}{}

\ability{Starting Gold:}{4d4*10 gp (100 gold)}

\ability{Starting Age:}{As Cleric.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Curator's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Heal (Wis), Listen (Wis), Knowledge (arcana) (Int), Knowledge (local) (Int), Knowledge (religion) (Int), Profession (Wis), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Survival (Wis), and Use Magic Device (Cha)}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+0 &+2 &Luminous Bolt, Benediction\\
2nd &+1 &+3 &+0 &+3 &Sphere\\
3rd &+2 &+3 &+1 &+3 &Benediction\\
4th &+3 &+4 &+1 &+4 &Heal Injuries\\
5th &+3 &+4 &+1 &+4 &Benediction\\
6th &+4 &+5 &+2 &+5 &Sphere\\
7th &+5 &+5 &+2 &+5 &Benediction\\
8th &+6/+1 &+6 &+2 &+6 &One and All, Greater Luminous Bolt\\
9th &+6/+1 &+6 &+3 &+6 &Greater Benediction\\
10th &+7/+2 &+7 &+3 &+7 &Sphere\\
11th &+8/+3 &+7 &+3 &+7 &Greater Benediction\\
12th &+8/+3 &+8 &+4 &+8 &Perfect Preservation\\
13th &+9/+4 &+8 &+4 &+8 &Greater Benediction\\
14th &+10/+5 &+9 &+4 &+9 &Sphere\\
15th &+11/+6/+6 &+9 &+5 &+9 &Supreme Benediction\\
16th &+12/+7/+7 &+10 &+5 &+10 &Supreme Luminous Bolt\\
17th &+12/+7/+7 &+10 &+5 &+10 &Supreme Benediction\\
18th &+13/+8/+8 &+11 &+6 &+11 &Sphere\\
19th &+14/+9/+9 &+11 &+6 &+11 &Supreme Benediction\\
20th &+15/+10/+10 &+12 &+6 &+12 &Eternity\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Curator class.

\ability{Weapon and Armor Proficiency:}{A Curator is proficient with simple weapons, with light and medium armor, and with shields (but not great shields).}

\ability{Luminous Bolt (Su):}{As an attack action, a Curator may fire a bolt of light at her foes. This has a range of Close (25 feet +5 ft./2 levels), does 1d6 light damage per two levels of Curator (rounded up), and requires a ranged touch attack to hit. Any creature damaged by this attack must make a Fortitude save (DC 10 + CHA + \half your level) or be dazzled for one round. Undead and creatures specifically vulnerable to light take double damage, and incorporeal undead targeted by this effect have no miss chance due to incorporeality.

Once a Curator reaches 8th level, any creature that fails the Fortitude save when struck by her Luminous Bolt also becomes blinded for one round. When she reaches 16th level, a creature failing the save also becomes stunned for one round. }

\ability{Benedictions (Su):}{At levels 1, 3, 5, and 7, a Curator learns a Benediction. Each Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a faint glow while its effects persist.

Each Benediction has two effects, chosen from the following list:}

\begin{itemize}\itemspace\begin{small}
    \item{The target of your Benediction receives an amount of temporary HP equal to your ranks in the Heal skill.}
    \item{The target of your Benediction is cured of one of the following status effects: dazzled, shaken, sickened, or magical fatigue (your choice at time of use).}
    \item{The target of your Benediction receives a +2 morale bonus to AC.}
    \item{The target of your Benediction receives a +2 morale bonus to all saves.}
    \item{The target of your Benediction receives spell resistance equal to 5 + your character level.}
    \item{The target of your Benediction gains a +3 insight bonus to resist enemy bullrush, disarm, grapple, and trip attempts.}
    \item{The target of your Benediction gains a +5 insight bonus to Balance, Escape Artist, and Tumble checks.}
    \item{The target of your Benediction gains a +5 insight bonus to Climb, Jump, and Swim checks.}
    \item{The target of your Benediction gains a +5 insight bonus to Listen and Spot checks, and to resist enemy feints.}
    \item{The target of your Benediction gains blindsense out to 15'.}
    \item{The target of your Benediction gains a +10' insight bonus to move speed.}
    \item{Anyone attacking the target of your Benediction in melee must make a Fortitude save (DC 10 + CHA + \half your level) or be sickened for one round. This occurs before the attack is resolved.}
    \item{Anyone attacking the target of your Benediction in melee must make a Will save (DC 10 + CHA + \half your level) or be shaken for one round. This occurs before the attack is resolved.}
\end{small}\end{itemize}

\ability{Spheres:}{At 2nd level, and every 4 levels thereafter, the Curator gains basic access to a Sphere, which must be one of: Exorcism, Mystery, Piety, Restraint, Revelation, Splendor, or Vigor. If she selects a Sphere in which she already has basic access, she gains advanced access; if she already has advanced accesss, she gains expert access.}

\ability{Heal Injuries (Sp):}{With a one minute ritual, a Curator of 4th level can heal a number of characters equal to her class level of a number of hit points of damage equal to her ranks in the Heal skill. This action may be taken a number of times per day equal to 3 + the Curator’s Charisma Modifier (if any), and all affected characters must be within close range of the Curator for the entire period.}

\ability{One and All (Su):}{At 8th level, a Curator takes on wider responsibilities. Once per day, when she activates one of her Benedictions, she may apply its effects to herself and all allies within range, rather than just one target.}

\ability{Greater Benedictions (Su):}{At levels 9, 11, and 13, a Curator learns a Greater Benediction. Each Greater Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Greater Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a warm glow while its effects persist.

When a Curator gains a Greater Benediction, she may replace one of her Benedictions with a different Benediction.

Each Greater Benediction has two effects, chosen from the following list:}

\begin{itemize}\itemspace\begin{small}
    \item{The target of your Greater Benediction receives DR 8/-.}
    \item{The target of your Greater Benediction gains energy resistance 15 against one energy type you select at the time of use.}
    \item{The target of your Greater Benediction cannot be affected by poison, disease, fear or charm effects (this does not suppress or remove effects already present).}
    \item{The target of your Greater Benediction gains the benefits of a protection from alignment effect, using an alignment you choose at the time of use.}
    \item{The target of your Greater Benediction benefits from Evasion and Improved Uncanny Dodge.}
    \item{The target of your Greater Benediction benefits from blindsight out to 30'.}
    \item{The target of your Greater Benediction does not provoke the normal attacks of opportunity for movement, ranged attacks, spells, spell-like abilities, or using items.}
    \item{The target of your Greater Benediction benefits from a freedom of movement effect.}
    \item{Anyone attacking the target of your Greater Benediction in melee must make a Reflex save or be struck by a luminous pulse for 5d6 light damage (undead and light-vulnerable creatures take double damage). Each attacker is subjected to this effect only once per round.}
    \item{Anyone attacking the target of your Greater Benediction must make a Will save (DC 10 + CHA + \half your level) or fail, losing the action but not any resources (spell slots, components, XP, and the like) used to power it.}
    \item{Your Greater Benediction affects one additional target within range.}
    \item{Your Greater Benediction bestows any two effects from the Benediction Effects list.}
\end{small} \end{itemize}

\ability{Perfect Preservation(Ex):}{Once she reaches 12th level, a Curator is immortal. She may also care for a number of willing creatures equal to her charisma modifier, and prevent them from aging for as long as they receive care. Additionally, neither the Curator nor any creature under her care will lose a level if they die and are resurrected.}

\ability{Supreme Benedictions (Su):}{At levels 15, 17, and 19, a Curator learns a Supreme Benediction. Each Supreme Benediction requires an immediate action to activate, may target any creature the Curator can see within Close range (including herself), and is usable at will. The effects of a Supreme Benediction end at the start of the Curator's next turn, and the affected creature is surrounded by a strong glow while its effects persist.

When a Curator gains a Supreme Benediction, she may replace one of her Benedictions or Greater Benedictions with a different Benediction of the same type.

Each Supreme Benediction has two effects, chosen from the following list:}

\begin{itemize}\itemspace\begin{small}
    \item{The target of your Supreme Benediction is immune to fire, cold, electricity, acid, sonic, negative energy, and death effects.}
    \item{The target of your Supreme Benediction is immune to fatigue, exhaustion, fear affects, mind-affecting effects, dazing, stunning, sickening, and nausea, and all such effects are immediately removed from him.}
    \item{The target of your Supreme Benediction has total concealment.}
    \item{The target of your Supreme Benediction benefits from true seeing and blindsight to 120', and his attacks never suffer a miss chance due to concealment.}
    \item{The target of your Supreme Benediction may choose to teleport himself and everything he is physically carrying up to 100' in any direction as a free action once per round.}
    \item{Any creature damaging the target of your Supreme Benediction also damages itself for half that amount (this includes ability damage).}
    \item{Any creature forcing the target of your Supreme Benediction to make a saving throw must itself make a Fortitude save (DC 10 + CHA + \half your level) or be knocked unconscious for two rounds.}
    \item{Any hostile creature that meets the gaze of the target of your Supreme Benediction must make a Reflex save (DC 10 + CHA + \half your level) or be cowered until it loses sight of him.}
    \item{Any creature coming within 60' of the target of your Supreme Benediction with hostile intent must make a Will save (DC 10 + CHA + \half your level) or become helpless for one round. Each creature is only subjected to this effect once per round.}
    \item{The effects of your Supreme Benediction persist for one extra round.}
    \item{Your Supreme Benediction bestows any two effects from the Greater Benediction Effects list.}
\end{small}\end{itemize}

\ability{Eternity(Ex):}{Upon reaching 20th level, a Curator selects one Benediction or Greater Benediction that she knows. Thereafter, she enjoys its effects unceasingly and at all times.}