Tamed Lightning (One/Two Handed)
Proficiency: Spear, lance or greatspear.
Reach: 5-10' like a spiked chain
Damage: 1d6 Lightning damage per 2 levels. Strength modifier still applies. Remember that it's 2-handed.
Critical: 20 x3
Special:
The Tamed Lightning's attacks ignore metal armor and shields, as well as all natural armor possessed by metallic foes (iron golems, copper dragons, whatever).

Every 5 rounds, it builds up enough electricity that it can cast Lightning Bolt as a Supernatural ability (Dex-based DC).

Once per round when you strike a foe in melee, one additional foe within 10' of that foe can also be targeted. Use the same attack roll.

Deals an additional amount of damage to creatures with the [Water] subtype equal to your BAB.


Mirrorshard Sword (One Handed)
Proficiency: Any kind of sword.
Reach: 5'
Damage: 1d6 slashing per two levels and 1 point of Constitution damage due to blood loss.
Critical: 18-20 x2 (the Con damage is also multiplied)
Special:
Reflection: As an Immediate action, you may make an attack against any ray fired at you. If your attack roll beats the attack roll used to hit you (or the Save DC), you reflect the ray back at the caster.

Blinding Light: As a Move action, the wielder can reflect any nearby light, causing all within 30' to make a Fortitude save (Dex-based DC) or be Blinded for 3 rounds. Creatures with Light sensitivity take a -4 penalty to their save and are permanently blinded if they fail the save. If they pass, Light sensitive creatures are Dazzled for three rounds.

Image of the Hero: The wielder always has a single mirror image.


Giant Scorpion Claws (One Handed)
Proficiency: Exotic Weapon Proficiency (scorpion claws), or Improved Unarmed Strike. If you have your own set of claws as a natural weapon, you're proficient enough with these to count, too. Whatever.
Reach: 5'
Damage: 1d6 (Piercing OR Slashing) per 2 levels.
Critical: 20 x3
Special:
These provide a +6 bonus on Grapple and Disarm checks. You also gain Improved Grab when using these.

You gain a special Eviscerate attack whenever you elect to deal damage in a Grapple. You needn't roll to hit, and automatically deal claw damage for each claw you possess. The opponent also takes 2 points of Strength damage per claw you use, due to muscles being torn.

Once per minute you can transform into a Monstrous Scorpion with a CR up to your BAB minus 1. You gain the size, natural armour, Strength, Dexterity, Constitution, DR, speed, natural attacks (replacing the claws with your own weapon ones), poison and any other physical feature.

You also gain immunity to nonlethal heat when wearing these.


Demon Whip (One Handed)
Proficiency: Whip. 
Reach: 5-15', actually threatens.
Damage: 1d6 slashing per 2 levels. Real damage, not ignored by armour, use doesn't provoke AoO. 
Critical: 20 x2 (special)
Special:
As a full-round action, you can attach the whip to your own body, at the shoulder, spine or whatever. You now have it as a "natural attack" in addition to any other attacks you make. You may detach the whip as a move action.

You can cast damning darkness and deeper darkness as spell-like abilities at will. Once per hour, you may cast summon monster X, where X equals half your BAB, minus 1. You may only summon Chaotic Evil creatures. The fiend lasts for one minute per level.

On a critical hit, the whip attaches to the target and begins strangling them. You immediately may begin a grapple, and can even elect to let go of the whip and let it get to work. It will deal regular damage every round, as well as forcing the victim to make a Fort save (Str-based DC) or be Nauseated for the round.


Wings of the Vampire Bat (One/Two Handed)
Proficiency: These require Exotic Weapon Proficiency. Alternatively, if the wielder possesses wing attacks, they count as proficient.
Reach: 5'
Damage: 1d6 bludgeoning per 2 levels.
Critical: 20 x2
Special:
When wielded as a pair, these allow the user to fly at 60' with Average maneuverability.

As a Supernatural ability at will, the wielder may summon a swarm of bats for one minute.

Every time the wings deal damage, the user regains hit points equal to their BAB (up to the damage dealt as a maximum). Excess damage converts into Temporary hit points, which last for one minute.

Once per minute, the wielder may cast Energy Drain as a Spell-like ability (Str-based DC).


Armour of the Exterminator
Heavy armour
Armour Bonus: +10 (+5 against touch attacks)
Max Dex: +1
Armour check penalty: -6
ASF: 60\%

Special:
So bulky is this armour that it provides the benefits of the Powerful Build trait. Additionally, it grants extra force behind blows, increasing the multiplier of power attack (assuming it is being used) by 1 (for instance, regular PA becomes +2 damage for each -1 to hit, a two-handed weapon becomes +3 per -1, a two-handed leap-attack weapon becomes +4 per -1 and a six-handed weapon becomes +7 per -1).

Also, this armour provides additional protection to vital organs. It has a 60\% chance of negating any critical hit (resulting in normal damage), sneak attack, ability damage/drain, death effect or negative level. If the attack used to deliver the effect/damage was a touch attack, the chance of negation is only 30\%.



Helm of the Exterminator
Uses the helmet/hat/circlet "slot".
Adds 5\% Arcane Spell Failure

Special:
This filters air and protects the entire head and throat, thus providing immunity to silence, deafening, blindness and gases. Furthermore, it enhances vision, providing low-light vision and dark vision out to 120'.

Also, the baleful glare of the ruby eyes grants a gaze attack. All who approach within 30' must make a Will save (Charisma-based) or cower for 1 round, then be shaken for 1 minute. Any given person is only affected once per day.

Finally, this may be combined with the Armour of Extermination, providing the following benefits:
+2 to the armour bonus (+1 against touch attacks)
+10\% to the negation of critical hits etc. (even against touch attacks)


Ghost-Powered Boots of the Exterminator
Uses the footwear "slot".
To utilise the kick attacks without penalty, either proficiency with natural weapons or the Improved Unarmed Strike feat is needed.

Special:
These help lift the body and other evenly-adjusted weight, although they are bulky in their own right. No movement penalty is suffered for wearing Medium or Heavy armour, however the wearer still cannot run in heavy armour.

2 kick attacks are gained with these soul-infused boots, dealing 2d6+Str bludgeoning damage and forcing a Fortitude save (Str-based) against being knocked prone. They threaten on a 20 and deal double damage on a critical hit. A "free" kick attack may be made as an immediate action against any adjacent foe who is knocked prone by anyone other than yourself.

Trample: The Trample ability is gained, dealing 1d6 damage per 2 levels and forcing a Fortitude save (Strength-based) against being dazed for one round.

When worn with the Armour of Extermination, the following benefits are gained:
+2 to the armour bonus (+1 against touch attacks)
+5\% to the negation ability (even against touch attacks)



"Rip" and "Tear", the Exterminating Gauntlets

These are two weapons. The stats given are for a single one, though they are designed to be used as a pair.

Proficiency: claws, spiked gauntlets or Improved Unarmed Strike
Reach: 5'
Damage: 1d6 per 2 levels, plus double your Strength modifier. The damage is bludgeoning and electric.
Critical: 20/x2

Special:
The claws in these gauntlets are designed for grasping foes, latching on and crushing them. The Improved Grab ability is applied to them.

When choosing to deal damage in a grapple, as long as you succeed on the grapple check, the gauntlet deals automatic damage (without any Power Attack), as well as an additional 4d6 piercing/slashing damage from the whirling teeth that jut out of the palms.

When a foe escapes from a grapple, the teeth latch on and tear at their flesh, dealing an additional 4d8 piercing/slashing damage, plus 2 Constitution damage.

The gauntlets contain lightning and trapped ghosts, and these can be used to launch small bolts of energy. Ten magic missiles can be launched at once, as per the spell, as a standard action. There is no limit to these.

As a pair, both can be used at once - dealing damage for each in a grapple, and to an escaping foe. Likewise, the full twenty magic missiles can be fired each round as a standard action.

If the entire set of Exterminator Armour is worn, including the gauntlets, additional benefits are granted:

Damage Reduction equal to your BAB, negated by nothing.
+2 to the DC of your gaze attack.
The ability to teleport 50' without error as a move action at will.
A +4 enhancement bonus to Strength.




Blessed Incense Burner (Two Handed)
Proficiency: Morning Star/Flail, though you could probably get away with any chain weapon at all.
Reach: 5-10' like a spiked chain
Damage: 2d8+Strength modifier bludgeoning damage, and 1d6 Fire damage per two levels.
Critical: 20 x3
Special:
Due to the holy incense surrounding them, the wielder constantly gains the benefits of a Blur effect.

Once per three rounds they may unleash a 30' cone of Fire as a Standard action, dealing 1d6 damage (half Fire, half Holy) per character level to all in the area. A Ref save (DC = attack roll) halves this.

As a Move action, the wielder may create a solid fog effect.

Once per hour, they may cast scorching ray as a Standard Action. One ray per two points of BAB is fired, each dealing 2d6 Fire damage and 2d6 Holy damage.


Wightskin Gloves (Light)
Proficiency: Counts as Unarmed Strike, claw/slam attack or Spiked Gauntlet.
Reach: 5'
Damage: 1d6 Negative energy per 2 levels, and 1 Negative Level
Critical: 20 x2
Special:
Anyone slain with them becomes a Wight under the user's control, to a maximum of 1 per character level. They have the same number of hit dice they had in life.

Once per three rounds, ennervation may be cast as a Spell-like ability. At 17th level, energy drain may be cast instead.

Inflict spells cure the wielder, though cure spells still cure (unless they already took damage from cure spells).



The Eldritch Glaive (Two Handed)
That's right, forget Warlocks, this is the daemonic weapon the invocation was based on. Proficiency: Glaive, but any polearm probably works. 
Reach: 5-10'
Damage: 1d6 Eldritch damage per two levels. Touch attacks for the win.
Critical: 20 x3
Special:
Anyone struck must pass a Fortitude Save (STR-based) or be Sickened for one minute. At 15th level, this instead becomes a save vs Nausea for 1 minute and on a successful save they are merely Sickened. They need only save once per round.

Anyone struck must also pass a Will Save (STR-based) or be Shaken for one minute. It stacks, but they are only subject to one of these per round. At 15th level, they Cower for 3 rounds if they fail the save.

Anyone slain by the Glaive is trapped in the Abyss, and can only be brought back by:
True resurrection
wish
miracle
A deity deciding to do so
freedom then raise dead/resurrection
Travelling to the layer of Hell in question, kicking the crap out of the level-appropriate demonic guards, then bringing the soul back and pouring it back into the body ("liquid" soul in a bottle by default, but tablets, gas and suppository forms are available via prescription, requiring a journey to Baator and proving you're not a soul addict) before resurrecting or raising them.


Deep Emerald
(A fist-sized flower carved from emerald, shining a lovely aquamarine colour)
Proficiency: Any ranged weapon (or weapon that can be thrown normally) works well enough for this.
Reach: None.
Ranged Touch Attack: 60'
Damage: 1d6 Cold damage per 2 levels
Critical: 20 x2
Special:
Piercing Cold - deals half damage to those immune to Cold. Reduces any Cold Resistance by half.

Can cast "Drown" and "Cone of Cold" once each per 4 rounds as a Spell-like ability.

Can cast "Wall of Water", "Acid Fog" and "Ice Storm" once each per hour as a Spell-like ability.



God-Kicking Boots (Light)
These finely crafted boots often come in pairs. While not designed to actually attack true gods (As the name suggests), they do prove useful against creatures whom lesser mortals would consider gods.
Proficiency: Gauntlet or Unarmed Strike
Reach: 5
Damage: As the Unarmed Damage of a Monk of your Character Level
Critical: 19-20 x3
Special:
The God-Kicking Boots can affect immaterial creatures as though they possessed the ghost touch property and ignore the first 5 points of any damage reduction.

On a critical hit, creatures not native to the current plane is affected by a Dismissal spell as cast by a Sorcerer of your character level, except the save DC is (10 + ? Character Level + Strength Mod).


Grand Goremaul (Two-Handed)
This oversized war hammer is a necromantic creation made of semi-solid blood attached to a handle of bone and flesh. It calls to the blood of those it strikes, and carries with it disease.
Proficiency: Any kind of hammer.
Reach: 10'
Damage: 1d6 bludgeoning and 1d6 negative energy per four levels.
Critical: 19-20 x3
Special:
Living creatures hit by a Grand Goremaul take 1 point of constitution damage.

A Grand Goremaul gives you the ability to Rebuke Undead once per day as a Cleric of your Character Level -3.

On a critical hit, a Living target must save or be affected by Mummy Rot.


Divine Reflector (One-Handed)
This oversized, razor-edged shield blurs and burns with holy (or unholy) light. They are well suited to both offense and defense, and are preferred by clerics and other divine casters.
Proficiency: Large shield 
Reach: 5'
Damage: 1d6 bludgeoning per 2 levels.
Critical: 20 x3
Special: Divine Reflectors count as large shields for the purposes of defense. Shield Bashing with the shield does damage as above, and does not negate the shields bonus to AC.

Whenever you could make an attack, in place of that attack you may designate a “Parry Attempt.” Any time before the beginning of your next turn, you may make an attack roll with the Divine Reflector and use the roll result in place of your AC against a single attack.

Divine spellcasters can, as an immediate action, expend one prepared spell or available spell slot to imbue the Divine Reflector with energy. Doing so grants a bonus to attack or AC on a single attack (Made by or against the spellcaster, respectively) equal to the sacrificed spell’s level. This ability affects a single attack made by or targeting the wielder.


Giant Rosary (Two-Handed)
Giant Rosaries are weapons designed to crush undead, often used by paladins and clerics. Those who use them tend to follow the creed of “Disarm and Dismantle”, which means to render the opponent’s offense ineffective (Through Tripping, Disarmament, Sundering, and similar methods) before destroying them.
Proficiency: Spiked Chain
Reach: 5-10', actually threatens.
Damage: 1d6 bludgeoning per 2 levels.
Critical: 19-20 x2
Special:
Giant Rosaries can be used to trip and disarm as a spiked chain.

In the hands of a character who can cast spells, Giant Rosaries have a threat range of 17-20/x2.

Giant Rosaries deal an extra 1d6 points of damage to Undead creatures, and can be used to sneak attack or critical hit an Undead. Giant Rosaries also affect immaterial creatures as though they possessed the ghost touch property.


Hat of Dragon Slaying:
Anyone with hands is considered proficient, as a hat is just waved about.
Reach: normal
Damage: 1d6 bludgeoning damage per 2 levels, plus STR mod.
Critical Hit: 20 x3

Special:
Dragon-Slayer: Every time it strikes a dragon, the hat instead deals 1d6 damage per level, plus STR mod. Additionally, dragons hit by this weapon are unable to fly or use their breath weapons for 5 rounds. There is no saving throw against this effect.

Invisibility From Dragons: Once per hour, the hat may project a Sphere of Invisibility effect, however those in the area are only invisible to dragons.

Stylish: The wearer enjoys a +4 bullshit bonus to Diplomacy checks while wearing this stylish hat, along with a +2 bullshit bonus to Bluff and Disguise (as the target is distracted by the stylish hat).

Shame: Should any dragon be knocked unconscious or killed by the hat, they suffer from a deep shame. They no longer have the right to be called a dragon, changing their type to Magical Beast. They lose the immunity to sleep and paralysis, and are affected by a Crushing Despair effect until they either kill the wielder, destroy the hat or have a Wish used to remove the shame. Seriously, they got defeated with a hat.


Khyt, the Whip of Dragon Slaying:
Proficiency: Whips
Reach: 5-15'
Damage: 1d6 bludgeoning/slashing damage per 2 levels, plus STR mod.
Critical Hit: 20 x2

Special:
Being a proper Russian knout, there is none of this "nonlethal damage, it provokes to use it, and armour ignores it" nonsense. It will tear flesh away with ease, or pulverise the bones.

Dragon Slayer: Against dragons, this weapon deals 1d6 damage per level, plus the STR modifier. Additionally, the dragon is unable to use its breath weapon or flight for three rounds upon getting hit. There is no save against this effect.

Kinky: You gain a +4 bullshit bonus to Diplomacy when dealing with clerics of Loviatar or other people in the BDSM realm, but a +4 bullshit bonus to Intimidate with everyone else.

Blood Spray: Every time damage is dealt to something that can bleed, this weapon causes a spray of blood, complete with bits of muscle hanging from the exposed wires in it. The target must make a Fortitude save (DC 10 + half your level + your STR mod) or be nauseated for 1 round, and all other targets must make a Will save (same DC) or be sickened for 3 rounds.

Special: Anyone who possesses both of the above weapons at the same time gains a +4 bullshit bonus to hit and damage dragons, and all enemies take a -3 morale penalty to strike the wielder.


Plane of Force:
For the purposes of proficiency, this counts as a Long Sword, Battle Axe, or Scimitar. Select which whenever you pick it up.
Reach: Melee
Damage: 1d20 slashing damage per 6 levels. Strength modifier still applies. Cannot be wielded with more than one hand.
Critical Hit: 18-20 x2

Special:
A Plane of Force ignores Natural Armor and Non-Magical Armor/Shields.

A Plane of Force ignores hardness and bypasses material damage reduction.

On a confirmed critical threat(roll to confirm even against a creature immune to critical hits) the creature struck must pass a fortitude save or lose a limb as if the weapon had the Sharpness special quality.

A Plane of Force is a Force affect and thus can strike Incorporeal and Ethereal targets without the miss chance normally inherent in attacking something Incorporeal or Ethereal.


Amphisbaena:
For the purposes of proficiency, this counts as a morning star or a spiked chain. Select which whenever you pick it up.
Reach(M): 5’-10’ threatens
Damage: 1d6 piercing damage per 2 levels.
Critical Hit: 18-20 x2

Special:
Two Headed: Can be used as a double weapon with 5’ reach.

Poison: Initial and Secondary Damage is 1d6 Con per 4 levels; Fort Save DC10+? HD+? BAB.

Death Gaze: During the Full Moon you can aim the two heads of the snake as a full-round action and force any 2 creatures within 30ft. to make a Fort Save(DC10+? HD+Cha Mod) or die. When not under the full moon you can use this power to Confuse instead of kill. The snake’s lantern-like eyes also function as a pair of bullseye lanterns that require no oil and can be used under water.

Bite Footprints*: You can attack the ground in any square a creature moved through on their last turn in order to inflict base weapon damage, but not poison, on that creature. You can also harm a creature in this manner if you have a clear and complete footprint belonging to the target, regardless of how old it is or how far away the creature is.

Spit Venom: As a Swift action you may take a ranged touch attack against any two creatures within 30ft., if you succeed these creatures are blinded for one minute.

*I didn’t find any reference to this in the mythology, though I didn’t look very hard, but I’m including it because angelfromanotherpin suggested it.

This is a really cool idea Koumei had and more people should contribute.










Dagger of Dargon-Slaying [One-Handed]

...it's got a +5 against Dragons!

Proficiency: Daggers
Reach: melee
Damage: 1d4 piercing or slashing for a medium creature
Critical Hit: 19-20/x2

This simple looking dagger is made with a smooth bone handle and it's blade has a crude etching on it. The etching is of a figure stabbing at a massive serpent that has encoiled the figure.

The blade is extremely sharp for such a crude looking blade and the handle fits right into your hand, even if it seemed a bit too small before you wrapped your fingers around it.

Special: You count as if you are five levels higher when you are within charging range of a Dragon that is Hostile to you (the dragon is able to charge you, not you able to charge it).

Your BaB and Saves all count as if you are five levels higher. You may only apply these if you are attacking a hostile Dragon that you are within the charging range of or if such a Dragon uses an effect that would force you to make a Saving Throw.

Additionally you count as if you had the class abilities of the class you took at first level as if your character were Five levels higher in that class.

These newly granted class abilities can only be used against the hostile Dragon and do not work against any other targets.

You always have The Edge when facing a dragon in combat, whether it is hostile to you or not. 

