\classname{Barrister of the Nine}
\vspace*{-8pt}
\quot{"Perhaps unfortunately, your contract actually does not allow that."}

The rules governing planar contracts are inviolate, but they are not written down in their entirety in any book of laws or treatise on the planes. Only the most agile, creative, and logical of minds can grasp the entirety of the mystical laws governing contracts between the planes, and these individual find service among power brokers and demon princes of the Nine Hells. If they survive this term of service, they eventually learn all the ways to abuse and exploit the unclear language and loopholes in the contract agreements of the planes.

\ability{Requirements:}{}
\listprereq
%To qualify to become an Barrister of the Nine, a character must fulfill all the following criteria.
\itemability{Skills:}{Knowledge (planes) 10 ranks, Profession (Infernal Lawyer) 10 ranks, Diplomacy 4 ranks, Intimidate 4 ranks.}
\itemability{Feats:}{Broker of the Infernal, Apprentice(Devil)}
\itemability{Spells:}{Ability to cast 5th-level arcane spells, and the spell \spell{lesser planar binding}}
\itemability{Special:}{Must be a native of the Prime Material Plane}
\itemability{Special:}{Must be lawful and cannot be good.}
\end{list} \vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Barrister of the Nine class skills (and the key ability for each skill) are Bluff(Cha), Concentration (Con), Craft (Int), Diplomacy (Cha), Intimidate(Cha), Knowledge (all) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Seal the Contract, Corner Office, Immunity Deal &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Penalized &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Pacts: Stability Pact &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Contractual Obligations &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Pacts: Renewal Pact &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Proof of Payment &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Pacts: Death Pact &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Inheritance Clause &+1 spellcaster level\\
9th &+4 &+3 &+3 &+6 &Pacts: Contingency &+1 spellcaster level\\
10th &+5 &+3 &+3 &+7 &Loophole &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Barrister of the Nine prestige class. Any use of the Barrister of the Nine's class abilities (except Corner Office) creates a written contract. If this written contract is destroyed, the spell modified by the Barrister's class ability ends.

\ability{Weapon and Armor Proficiency:}{Barristers of the Nine gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, the Barrister casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Seal the Contract(Su):}{At first level, a Barrister of the Nine may use any of the planar binding spells to seal an agreement between any two individuals. While the Barrister must cast the spell, one of the two individuals becomes the caster for the purposes of services owed and payments.}

\ability{Corner Office (Sp):}{At 1st level, the Barrister gains an extraplanar office for his dealings. This effects may be used at will, and is in effect a magnificent mansion, except that it is the same location between castings, meaning that when the duration ends this extradimensional space is inaccessible, but items and creatures still be there when this ability is used again (effectively trapped unless planar travel magic is used) . This location counts as the Prime for calling spells, and has a permanent calling circle and an unchanging layout.}

\ability{Immunity Deal (Ex):}{A Barrister of the Nine is immune to energy drain and wisdom drain.}

\ability{Penalized:}{At 2nd level, the Barrister of the Nine has learned to incorporate double-talk and legal trickery in his calling spells, meaning that if called creatures survive to complete their service(s), they must return half the GP value treasure used to buy their services. Note: If a creature accepted the caster's services in return for their service, they must instead pay half the value of such services in GP or magic items.}

\ability{Pacts (Sp):}{At 3rd level, the Barrister of the Nine can cast \spell{Stability Pact} as a spell-like ability one per day.
At 5th level, he may cast \spell{Renewal Pact} once per day as a spell-like ability.
At 7th level, he may cast \spell{Death Pact} once per day as a spell-like ability.
At 9th level, he may cast \spell{Contingency} once per day as a spell-like ability.}

\ability{Contractual Obligations:}{When making a bargain with a extraplanar being, the Barrister can gain one additional service for every +5 added to the DC of bargaining check.}

\ability{Proof of Payment:}{At 6th level, the Barrister of the Nine has learned to add in clauses to his planar binding spells that delays payment for services until those services are completed. If the called creature is killed before the service is complete, the Barrister does not need to pay for services.}

\ability{Inheritance Clause:}{A Barrister of the Nine of 8th level can transfer services owed him by creatures he has bound to other creatures, even if those creatures are not present at the time a calling spell is cast.}

\ability{Loophole:}{At 10th level, the Barrister of the Nine has learned to word his agreements is such a way as to avoid payment. He no longer needs to pay for any agreements made with his calling spells.}
