\classname{Boatman of Styx}

The River Styx is a planar path winding its way along the Lower Planes servicing the myriad planes of evil, and its waters rob mortals and immortals of their memories. Ferrymen ply these waters, offering safe passage and travel between the planes, but most are con-men looking to make a quick silver, predators in disguise, or well-meaning fools. Few beings know the truly safe routes along the River Styx, thus earning the title of boatmen, and even fewer have accepted its nature into their very body.

\ability{Requirements:}{}
%To qualify to become a Boatman of Styx, a character must fulfill all the following criteria.
\listprereq
\itemability{Skills:}{Knowledge (Planes) 8 ranks, Survival 4 ranks, Profession (boatman) 4 ranks.}
\itemability{Feats:}{Quickdraw}
\itemability{Special:}{Must have visited every Lower Plane via the River Styx, and lived at least one year on a boat on the River Styx.}
\itemability{Special:}{+2d6 sneak attack, skirmish, or sudden strike}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Boatman of the Styx's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (planes) (Int), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex), Use Magic Device (Cha), and Use Rope (Dex).}

\ability{Skill Points at Each Level:}{6 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+2 &+2 &+0 &Safe Passage, Stygian Blood\\
2nd &+1 &+3 &+3 &+0 &River-born, +1d6 sneak attack dice\\
3rd &+2 &+3 &+3 &+1 &Stygian Tears\\
4th &+3 &+4 &+4 &+1 &River-marked, +2d6 sneak attack dice\\
5th &+3 &+4 &+4 &+1 &Kiss of Lethe\\
6th &+4 &+5 &+5 &+2 &Eternal Boatman, +3d6 sneak attack dice\\
7th &+5 &+5 &+5 &+2 &Bonus Feat\\
8th &+6 &+6 &+6 &+2 &Knowledgeable, +4d6 sneak attack dice\\
9th &+6 &+6 &+6 &+3 &Stygian Tributary\\
10th &+7 &+7 &+7 &+3 &Xirfilstyx Dance, +5d6 sneak attack dice\\
\end{tabular}
\end{small}
\end{table}



\smallskip \noindent All of the following are Class Features of the Boatman of Styx prestige class.

\ability{Weapon and Armor Proficiency:}{A Boatman of Styx gains proficiency in the Long Staff, but does not gain any other weapon or armor proficiency.}

\ability{Safe Passage (Su):}{At 1st level, the Boatman of Styx learns to navigate the River Styx. When leading a boat or ship, the Boatman can lead a craft to any other planar location that contains some portion of the River Styx. This journey takes 1d6 hours, and is uneventful.}

\ability{Stygian Blood(Ex):}{At 1st level, the Boatman of Styx has absorbed small amounts of the River Styx into his blood, and from this point forward he is immune to mind-affecting effects and the effects of the River Styx.}

\ability{River-born:}{At 2nd level, the Boatman of Styx gains a swim speed of 60', and he may take 10 on any Swim check. He also does not need to breathe while submersed in water.}

\ability{Sneak Attack:}{A Boatman of Styx gains an additional die of Sneak Attack at every even numbered level.}

\ability{Stygian Tears:}{At 3rd level, the Boatman of Styx's tears gain the effects of the River Styx. He may collect up to one vial of tears per day. Being struck by a vial of these tears has the same effects as an exposure to the waters of the River Styx (DM's option). If kept stoppered, these vials of tears last indefinitely.}

\ability{River-marked:}{At 4th level, the Boatman of Styx's continues exposure to the River Styx grants a +8 to Swim checks, a +6 to Disguise checks, and a +4 to Bluff checks.}

\ability{Kiss of Lethe(Su):}{At 5th level, the Boatman of Styx may kiss an enemy on an opposed Grapple check. This kiss has the same effects as an exposure to the River Styx (DMs option).}

\ability{Eternal Boatman(Sp):}{At 6th level, the Boatman of Styx may summon a normal wooden boat once per day. This boat is large enough to carry the Boatman and up to eight Medium sized passengers. This boat lasts 24 hours, then falls apart into pieces of rotted wood.}

\ability{Bonus Feat:}{At 7th level, the Boatman of Styx gains a bonus feat. He must meet any prerequisites of this feat to choose it.}

\ability{Knowledgeable:}{At 8th level, the Boatman of Styx's has absorbed a critical mass of memories from swimming in the River Styx. He always has at least 10 ranks in all Knowledges, and may expend skill points to raise these Knowledges as if they were class skills. The Boatman also gains the ability to speak, read, and write any language.}

\ability{Stygian Tributary(Sp):}{At 9th level, the Boatman of Styx learns a secret about the River Styx: it sometimes touches rivers on planes other than the Lower Planes. Once per day, a Boatman of Styx may cast a \spell{gate} (travel version only) as a spell-like ability, but only while standing on a boat in a river. This portal leads to any other river on any plane.}

\ability{Xirfilstyx Dance(Su):}{At 10th level, the Boatman of Styx has studied these fiends of the River Styx and learned a secret fighting art. Any creature struck a Boatman of Styx's sneak attack must make a Will save or be dazed for 1d4 rounds. Any affected creature does not remember any events while dazed.}
