\classname{Bone Rider}
\vspace{-8pt}
\quot{"We can make it; we'll just have to ride all night..."}

The desire for a steed that will not tire or balk is instantly understandable by anyone who has ridden for even a short time. Still, while the dark arts can provide, there are few who are willing to take steps down that path. The Bone Rider is one who has chosen to sacrifice the luxury of acceptance for the power and convenience of using the raw power of death for transportation and war.

\ability{Prerequisites:}{}
\listprereq
\itemability{Feats:}{Mounted Combat}
\itemability{BAB:}{+3}
\itemability{Skills:}{Ride 7 ranks, Knowledge (Religion) 3 ranks, Diplomacy 4 ranks}
\itemability{Special:}{Must have proficiency with all martial weapons.}
\end{list}\vspace*{8pt}

\ability{Hit Dice:}{d10}

\ability{Class Skills:}{The Bone Rider's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Handle Animal (Cha), Heal (Wis), Knowledge all skills taken individually) (Int), Profession (Wis), Ride (Dex), and Sense Motive (Wis).}

\ability{Skill Points/Level:}{2 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+0 &+2 &Mount the Dead, Turn/Rebuke Undead, Spellcasting\\
2nd &+2 &+3 &+0 &+3 &Versatile Riding, Deadly Touch\\
3rd &+3 &+3 &+1 &+3 &Bonus Feat, Animate Dead\\
4th &+4 &+4 &+1 &+4 &Speed of the Dead, Hunger of the Dead\\
5th &+5 &+4 &+1 &+4 &Bonus Feat, Eternal Faithfulness\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Bone Rider class.

\ability{Weapon and Armor Proficiency:}{The Bone Rider gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level of Bone Rider counts as two levels of Blackguard for the purposes of spells per day and available spells. A Bone Rider's caster level for these Blackguard spells is her character level.}

\ability{Mount the Dead (Su):}{A Bone Rider can summon an undead creature to serve her for up to her character level in hours each day. The Bone Rider traditionally rides this creature, though it is fanatically loyal and she can use it for any other task it is capable of. Summoning or dismissing the mount is a standard action, and it appears within close range of the Bone Rider. If the Bone Rider's mount is destroyed, she may not summon it again for 24 hours.

The mount is an undead creature, but is often much more intelligent and loyal than a normal example of its type. The undead mount has an Intelligence of 10 if it would normally be less than that (including creatures which usually have an Intelligence of "--"). The Bone Rider is immune to any harmful effects of touching or being within the presence of her mount. The Mount gains Turn Resistance equal to the Bone Rider's class level.}

\ability{Sample Mounts:}{A Bone Rider of sufficiently high level can select her mount from the following list, if her character level is at least equal to the minimum level of the beast in question. If a Bone Rider is higher level than necessary, she adds the difference to the undead beast's hit dice. The DM is welcome to allow alternative undead steeds, the following list is intended only as an example.}

\begin{tabular}{rlrl}
\textbf{Level} & \textbf{Mount} & \textbf{Level} & \textbf{Mount}\\
1  & Skeleton Wolf &13  & Ulgurstasta (FF)\\
3  & Skeleton Warhorse & 15  & Charnel Hound (MM3)\\
5  & Skeleton Manticore &16  & Nightwing\\
7  & Zombie Wyvern &17  & Hullathoin (FF)\\
9  & Revived Fossil Behir (LM) & 20  & Nightcrawler\\
11  & Young Adult White Zombie Dragon (Draconomicon) &&\\
\end{tabular}

\ability{Turn/Rebuke Undead (Su):}{If the Bone Rider already has turning or rebuking, she may add her levels of Bone Rider to her level for the purposes of turning or rebuking.}

\ability{Versatile Riding (Ex):}{At 2nd level, the Bone Rider's Mount gains the special bonuses of a \spell{phantom steed} cast with a caster level equal to her caster level.}

\ability{Deadly Touch (Su):}{At 2nd level, a Bone Rider can inflict negative energy damage with a touch. The total amount of damage which can be used each day is equal to her Charisma bonus times her class level. As this is negative energy, this damage heals undead. The Bone Rider can use as much or as little of this ability with a single touch as she chooses.}

\ability{Bonus feat:}{At 3rd level, the Bone Rider gains a Bonus Feat that she qualifies for. The feat must have Mounted Combat or Point Blank Shot as one of its prerequisites. She gains another similar Bonus Feat at level 5.}

\ability{Animate Dead (Sp):}{Once per week, a 3rd level Bone Rider may use \spell{animate dead} as a spell-like ability. Her caster level is equal to her character level.}

\ability{Speed of the Dead:}{At 4th level, the Bone Rider's mount gains a +100' enhancement bonus to its speed with every movement it has. The mount also gains Evasion.}

\ability{Hunger of the Dead:}{The mount of a 4th level Bone Rider can consume the flesh of a fallen corporeal enemy and heal itself completely in doing so. Devouring a helpless or dead opponent is a standard action if the target creature is at least one size smaller than the undead beast.}

\ability{Eternal Faithfulness (Su):}{At 5th level, a Bone Rider's Mount will sacrifice itself to save the Bone Rider's life. If the Bone Rider is ever affected by an effect or attack that would kill her while she is touching her mount, her mount suffers the effects instead. If the effect covered an area, it is entirely possible that the mount will be affected twice.}

\ability{Paladin Bone Riders:}{In games using the Playing With Fire Necromancy option, it is entirely possibly for a Paladin to become a Bone Rider and use their abilities without adversely affecting their standing as Paladins. However, many of the spells on the Blackguard list are not conducive to retaining a Good alignment. It is suggested therefore, that a Bone Rider with any levels in Paladin be allowed to prepare spells from the Paladin list in her Blackguard spell slots in addition to the regular Blackguard spells.}

\ability{Special Mounts and Cohorts:}{A game master may allow a Bone Rider with leadership to have an undead mount as a cohort. This undead Cohort may be any creature of a CR at least 2 less than the Bone Rider's character level, and may remain in the world 24 hours a day if desired. The undead cohort is a special creature initially attracted like a normal cohort, and has the Elite stat array (Undead creatures which normally have an Intelligence less than 10 or "--" have an Int modifier of +0 when they are a cohort special mount).}
