\classname{Corpselight Whisperer}
\vspace*{-8pt}
\quot{"Come into my house, it is warm and the nights are both cool and damp in the swamp."}

The bogs of the Bane Mires are stagnant and reek with the stench of decay. But while they are a boundless well of sickness and death, they are also part of nature, at least according to the merciless will-o-wisps that live there. There are few even among the druids who are willing to make their home in such an inhospitable land. But there are secrets to be learned, for those who with a keen ear and a light step. For while the corpse lights may share their secrets, they may also lead one into the fast bogs from which there is no escape.

There is a side of nature that few admit the existence of, and even fewer have seen first hand. It is dangerous and cruel, filled with moldering corpses and rank spoilage. But it is perhaps not as different from the forests of home as the elders would have one believe...

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{Knowledge(Nature) 4 ranks, Listen 4 ranks, Survival 9 ranks}
\itemability{Special:}{Ability to wild shape}
\itemability{Special:}{Must have made friendly contact with a Will-o-Wisp.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{Concentration (Con), Climb (Str), Craft (Int), Handle Animal (Cha), Heal (Wis), Hide (Dex), Intimidate (Cha), Knowledge (nature) (Int), Knowledge (religion) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Spellcraft (Int), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Skill Points/Level:}{4 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+2 &+2 &Spell-like Abilities: Animate Dead &+1 spellcaster level\\
2nd &+1 &+0 &+3 &+3 &Wildshape: Will-O-Wisp, +1 Wildshape Use &+1 spellcaster level\\
3rd &+2 &+1 &+3 &+3 &Spell-like Abilities: Dancing Lights, Terrible Nectar &+1 spellcaster level\\
4th &+3 &+1 &+4 &+4 &Summon Wisps, +1 Wildshape Use &+1 spellcaster level\\
5th &+3 &+1 &+4 &+4 &Wildshape: Large Plant, Sanctum Spell &+1 spellcaster level\\
6th &+4 &+2 &+5 &+5 &Bonus Domain (Deathbound) &+1 spellcaster level\\
7th &+5 &+2 &+5 &+5 &Spell-like Abilities: Programmed Image, +1 Wildshape Use &+1 spellcaster level\\
8th &+6 &+2 &+6 &+6 &Bog's Heart, Bonus Necromantic Feat &+1 spellcaster level\\
9th &+6 &+3 &+6 &+6 &Hands of the Corpselight &+1 spellcaster level\\
10th &+7 &+3 &+7 &+7 &Incorporeal Wildshape 1/day &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All the following are Class Features of the Corpselight Whisperer prestige class.

\ability{Weapon and Armor Proficiencies:}{The Corpselight Whisperer gains no new armor or weapon proficiencies.}

\ability{Spellcasting:}{Every level, the Corpselight Whisperer casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in a spellcasting class she had previous to gaining that level.}

\ability{Spell-like Abilities (Sp):}{A Corpselight Whisperer can use \spell{animate dead} as a spell-like ability. At 3rd level, she is able to use \spell{dancing lights}, and at 7th level she is able to use \spell{programmed image}.  Her caster level is equal to her hit dice, and these abilities are usable at will.}

\ability{Wildshape:}{At 2nd level, a Corpselight Whisperer can use her Wildshape ability to assume the form of a Will-o-Wisp, regardless of the allowed size, type, or hit dice of her Wildshape ability. Becoming a Will-o-Wisp in this manner gives the Whisperer all of the Will-o-wisp's Extraordinary abilities and \hyperlink{feat:weaponfinesse}{Weapon Finesse} as a bonus feat. At level 7, the Whisperer can use her Wildshape ability to assume the form of a Plant of up to Large size. Becoming a Plant in this fashion uses the normal rules for a Druid's Wildshape ability. The Corpselight Whisperer may use her Wildshape ability one extra time per day at levels 2, 4, and 7. Levels in Corpselight Whisperer stack with levels in other Wildshaping classes for the purposes of maximum hit dice and duration.}

\ability{Terrible Nectar (Su):}{At 3rd level the Corpselight Whisperer gains sustenance from the terror of others. If she is within 60 feet of an intelligent creature that is affected by a [Fear] effect, she needs one less meal that day and can get by with 2 hours less sleep. If such a creature is killed while under the influence of a [Fear] effect and within 60 feet of her, she does not need to eat or sleep that day at all.}

\ability{Summon Wisps (Su):}{A Whisperer of 4th level or higher can summon Will-O-Wisps to aid her. The wisps serve faithfully for one hour and then vanish. The Whisperer can summon one wisp for every two class levels each day, and can choose to summon all of them at once or to conjure them in smaller groups as desired.}

\ability{Bonus Feat:}{At 5th level, the Corpselight Whisperer gains Sanctum Spell as a bonus feat. A magical sanctum created in this manner must be in a marshy natural setting (though it does not have to be a structure). At 8th level, the Corpselight Whisperer gains an additional Necromantic Creation Feat that she meets the prerequisites for as a bonus feat.}

\ability{Bonus Domain:}{At 6th level, the Whisperer gains the Deathbound Domain as a bonus domain. She gains the granted ability (to animate 50\% more undead with each use of \spell{animate dead}), and can prepare one extra domain spell at every spell level using the normal rules for domain spell preparation.}

\ability{Bog's Heart (Su):}{A Corpselight Whisperer of 8th level or higher who dies is \spell{reincarnated} 1d10 days later in the middle of her magical sanctum, provided that no one has cut off her magical sanctum in the meantime (either by physically making the area into something other than a swamp, or through magic such as \spell{desecrate}). Being reincarnated in this fashion does not result in level loss and costs no XP. Unlike the normal spell, the Corpselight Whisperer will return with a new young adult body if he dies by reaching his maximum age.}

\ability{Hands of the Corpselight (Ex):}{Like a Will-o-Wisp, a Corpselight Whisperer of 9th level can deliver powerful electric shocks. Any touch or natural weapon attack of the Corpselight Whisperer can also inflict 2d8 of electricity damage (even if it would already inflict electricity damage).}

\ability{Incorporeal Wildshape (Su):}{A Corpselight Whisperer of 10th level or higher can Wildshape into an Undead creature with the Incorporeal subtype. The Whisperer gains all of the assumed form's Extraordinary, Supernatural, and Spell-like abilities. The Corpselight Whisperer may only Wildshape in this manner once per day, but if she would gain additional uses of Elemental Wildshape for any reason, she gains an equal number of additional uses of Incorporeal Wildshape.}
