\classname{Death King}\label{class:deathking}
\vspace*{-8pt}
\quot{"I have returned."}\nopagebreak

The will of the people is great, and their need for heroes is sometimes greater. Sometimes, it is so great as to keep a great warrior from dying. Living but dead, these heroes of the people are pulled back from the dead time and time again, feeling the pain of each death but unable to end the cycle.

Some seek vengeance, while others seek redemption, but all have death in their eyes. Each has returned from death and been changed. Each has grown crueler and harder, and known the bliss of death. None have given up, though many have been destroyed. Underestimate them, and they will destroy you.

\ability{Prerequisites:}{}\nopagebreak
\listprereq
\itemability{Feats:}{Power Attack, Expertise, Leadership}
\itemability{BAB:}{+8}
\itemability{Special:}{Must have proficiency with all martial weapons.}
\itemability{Special:}{Must have been returned from the dead.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{Unknown}

\ability{Class Skills:}{The Death King's class skills (and the key ability for each skill) are Climb (Str), Concentration(Con), Craft (Int), Intimidate (Cha), Jump (Str), Ride (Dex), and Swim (Str).}

\ability{Skill Points/Level:}{2 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+1 &+2 &+0 &+2 &Mantle of Death &+1 spellcaster level\\
2nd &+2 &+3 &+0 &+3 &+1 Natural Armor, Gaze of the Terrible &+1 spellcaster level\\
3rd &+3 &+3 &+1 &+3 &+2 Natural Armor, Fast Healing 1 &+1 spellcaster level\\
4th &+4 &+4 &+1 &+4 &+3 Natural Armor, Regeneration 1 &+1 spellcaster level\\
5th &+5 &+4 &+1 &+4 &+4 Natural Armor, Horrors from Beyond &+1 spellcaster level\\
6th &+6 &+5 &+2 &+5 &+5 Natural Armor, Eternal Hero &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Death King class.

\ability{Weapon and Armor Proficiency:}{The Death King gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Death King casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level. If the character does not have any levels in any spellcasting classes when he takes his first level of Death King, this class feature gives him levels in Sorcerer spellcasting.}

\ability{Mantle of Death:}{The Death King's type changes to Undead (and he gains the augmented subtype for his original type) and he gains the \hyperref[undead:darkminded]{Dark Minded} and \hyperref[undead:unliving]{Unliving} subtypes.}

\ability{Natural Armor:}{Every level past 1st, the Death King's natural armor increases by 1.}

\ability{Gaze of the Terrible (Su):}{As a swift action, a 2nd level Death King can target an opponent within short range who meets its gaze with a \spell{fear} effect. This effect is handled as the spell, but targets only a single opponent.}

\ability{Fast Healing 1 (Ex):}{The Death King gains Fast Healing 1 at 3rd level.}

\ability{Regeneration 1 (Ex):}{The Death King gains Regeneration 1 at 4th level. Non-magical weapons do normal damage to the Death King.}

\ability{Horrors from Beyond (Su):}{As a swift action, a 5th level Death King can target an opponent within short range with a \spell{phantasmal killer} effect. This effect is handled as the spell.}

\ability{Eternal Hero (Ex):}{Should a 6th level Death King be destroyed and his remains interred in a Tomb, he is restored to life in one week with no level loss.}
