\classname{Death Knight}
\vspace*{-8pt}
\quot{"There is no horror you have known that can prepare you for what I am about to reveal."}

Those who take up the black sword of the Death Knights in the name of powerful evil gods are not all undead. They aren't even all evil, since sometimes evil gods simply curse warriors in order to screw with them. But a lot of them are evil and undead, and that gives the Death Knight his classic image.


\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+6}
\itemability{Skills:}{Knowledge (Religion) 4 ranks}
\itemability{Special:}{Must have proficiency with all martial weapons.}
\itemability{Special:}{Must have had nonviolent contact with a Fiend.}
\end{list}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Death Knight's class skills (and the key ability for each skill) are Climb (Str), Concentration (Con), Craft (Int), Intimidate (Cha), Jump (Str), Knowledge (all skills individually) (Int), Listen (Wis), Move Silently (Dex), Spot (Wis), Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+0&+0&+2&Sword of Death, Life and Death\\
2&+2&+0&+0&+3&Army of the Dead\\
3&+3&+1&+1&+3&Sphere: Bone\\
4&+4&+1&+1&+4&Bonus Feat\\
5&+5&+1&+1&+4&Sphere: Fire\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Death Knight class.

\ability{Weapon and Armor Proficiency:}{The Death Knight gains no proficiency with armor or weapons.}

\ability{Sword of Death (Su):}{A Death Knight can transform his blade into a black instrument of destruction. His melee attacks inflict 2d6 of Unholy damage against living creatures.}

\ability{Life and Death:}{A Death Knight can transform himself into a Vampire, Ghoul, Revenant, or Swordwraith if he chooses either upon becoming a Death Knight or at some later date. Rules for being these undead creatures are found in the Tome of Necromancy. In addition, a Death Knight may qualify for and use Necromantic Feats using his Base Attack Bonus instead of a caster level.}

\ability{Army of the Dead (Su):}{A 2nd level Death Knight may raise undead as per animate dead or create undead with a caster level equal to his hit dice.}

\ability{Spheres:}{At 3rd level, a Death Knight gains the \hyperlink{sphere:bone}{Sphere of Bone}. At 5th level, he gains the \hyperlink{sphere:fire}{Sphere of Fire}.}

\ability{Bonus Feat:}{At 4th level a Death Knight gains a bonus feat. This may be any \hyperref[feats:combat]{[Combat]} feat or \hyperref[feats:fiend]{[Fiend]} feat he meets the prerequisites for.}
