\classname{Defiler of Temples}\label{class:defiler}
\vspace*{-8pt}
\quot{"That stuff is all sacred to Nerull, so we should desecrate it thoroughly. I'm going to need more beer."}

The gods are jealous creatures and demand that their followers forsake the other gods. More over, they ask their most devoted followers to destroy the icons and worshippers of their peers. A Defiler of Temples is one who has taken up that cause and seeks to destroy the gods that oppose his own.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{9 ranks in Knowledge (Religion), 4 ranks in Knowledge (Dungeoneering)}
\itemability{Spellcasting:}{Must be able to cast Divine Spells.}
\itemability{Special:}{Must have slain a divine caster following a god other than your own or a cleric dedicated to a philosophy you find abhorrent.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Defiler of Temples' class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Gather Information (Cha), Hide (Dex), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Swim (Str), and Use Magic Device (Cha).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+0&+0&+2&+2&\spell{Find traps}, Avoid Divine Wrath&+1 spellcasting level\\
2&+1&+0&+3&+3&Unreproachable Alignment, Divine Spell Resistance&+1 spellcasting level\\
3&+2&+1&+3&+3&\spell{Desecrate}&+1 spellcasting level\\
4&+3&+1&+4&+4&Stolen Power&+1 spellcasting level\\
5&+3&+1&+4&+4&\spell{Mindblank}&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Defiler of Temples class.

\ability{Weapon and Armor Proficiency:}{A Defiler of Temples gains proficiency with no new weapons or armor.}

\ability{Spellcasting:}{Every level, the Defiler of Temples casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Find Traps (Sp):}{A Defiler of Temples can cast \spell{find traps} as a spell-like ability with a caster level equal to his character level. This ability is usable at will.}

\ability{Avoid Divine Wrath (Ex):}{Magical effects created by divine magic are unable to perceive a Defiler of Temples, so a contingent effect such as a \spell{glyph of warding} will not activate in the Defiler of Temples' presence. A Defiler of Temples can still be affected by a divine spell which targets him or for which he is in the area of effect. Only divine contingent effects are incapable of acting upon him.}

\ability{Unreproachable Alignment (Ex):}{All effects that have any effect dependent upon the alignment of a character affect a 2nd level Defiler of Temples as if he had or lacked whatever alignment would cause the least possible effect. So a \spell{blasphemy} would not affect him as if he was Evil, while an \spell{order's wrath} would not affect him as a non-Chaotic individual.}

\ability{Divine Spell Resistance (Ex):}{The powers of the gods roll off the back of a Defiler of Temples like butter off a warm sofa. At 2nd level a Defiler of Temples gains Spell Resistance of 15 + Character level. This Spell Resistance only applies against Divine spells.}

\ability{Desecrate (Sp):}{A Defiler of Temples loves nothing more than to defile the temples of his enemies. It's what he lives for. At 3rd level, he can do it reflexively with whatever he has on hand. A Defiler of Temples is then able to cast \spell{desecrate} as a spell-like ability with a caster level equal to his character level. This ability is usable at will.}

\ability{Stolen Power:}{By 4th level, the Defiler of Temples has captured enough of the divine power from his enemies that he can use it himself. The Defiler of Temples gains one bonus domain that must be one not offered by his deity or consistent with his own philosophy. Spells can be prepared and cast from this extra domain in precisely the same manner as a normal Cleric's Domains.}

\ability{\spell{Mindblank (Su)}:}{At 5th level, the Defiler of Temples benefits from the effects of the spell \spell{mindblank}. Even the gods themselves cannot find him with their magic.}
