\classname{Demon Samurai}\label{class:demonsamurai}
\vspace*{-8pt}
\quot{"The Oni Lords have granted me great power, and in return I shall give them a world of blood."}

Samurai are men of honor and duty, but are men nonetheless, and they have needs and desires that may not be understood by their fellows. To attain these desires, some samurai pledge their loyalty to powerful fiends, and in return they are invested with demonic power. Cruel, dangerous, and loyal to a force of primal evil, Demon Samurai wander the land or lead armies of their lesser fellows, seeking to restructure the world to fit their own deviant desires.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+5}
\itemability{Skills:}{4 ranks in Knowledge(Religion)}
\itemability{Special:}{Must have the ability to have an Ancestral Weapon by class ability or feat.}
\itemability{Alignment:}{Must be Evil.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{The Demon Samurai's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Hide (Dex), Intimidate(Cha), Jump (Str), Knowledge (Religion) (Int), Listen (Wis), Move Silently (Dex), Ride (Wis), Sense Motive (Wis), Spot (Wis), and Survival (Wis).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+0 &+2 &Mantle of Dark One, Code of Conduct\\
2nd &+2 &+3 &+0 &+3 &Face of Evil\\
3rd &+3 &+3 &+1 &+3 &Talons\\
4th &+4 &+4 &+1 &+4 &Sphere\\
5th &+5 &+4 &+1 &+4 &Usurp the Darkness\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Demon Samurai class.

\ability{Weapon and Armor Proficiency:}{A Demon Samurai gains proficiency with one fiendish weapon, and Demon Armor.}

\ability{Mantle of Dark One(Su):}{At 1st level, a Demon Samurai becomes so tied to thbe forces of darkness that he can no longer hide his taint. After donning any armor, it transforms into Demon Armor after 10 minutes have passed, retaining any existing magical abilities or bonuses. If the armor would normally inflict negative levels due to the Demon Samurai's alignment, it no longer does so after transforming into Demon Armor. The Demon Armor generally looks the same with every transformation, but generally becomes more stylized as the Demon Samurai grow in power.

This transformation to the armor ends if the Demon Samurai removes it, unless the Demon Samurai has worn that armor continuously for at least one year.}

\ability{Code of Conduct:}{On first day of the new year, a Demon Samurai must sacrifice a magic item or collection of souls worth more than 15,000 gp to his Patron, or else lose all Demon Samurai class abilities for one year.}

\ability{Face of Evil (Su):}{As a swift action, the Demon Samurai may cast \spell{fear} as a spell-like ability usable at will. When he uses this ability, his face transforms into a demonic visage, and creatures which do not meet his gaze are not affected. This demonic visage is the same every time, and is a reflection of the Demon Samurai's particular sins. If a character makes their saving throw against this effect, they may not be affected by it again for 24 hours.}

\ability{Talons:}{At 3rd level, a Demon Samurai gains two claw attacks for his size and Multiattack as a bonus feat. He may choose feats with the [Fiend] descriptor.}

\ability{Sphere:}{At 4th level, a Demon Samurai gains access to a Sphere of his choice. He may now take levels in True Fiend or other Fiendish classes. See the Tome of Fiends for further information.}

\ability{Usurp the Darkness(Sp):}{At 5th level, the Demon Samurai gains the ability to cast \spell{plane shift} as a spell-like ability, but he may only travel to the home plane of his Patron.}\\

Should the Demon Samurai defeat his Patron in single combat, he is no longer bound by his Code of Conduct, and no longer needs to retain an Evil alignment to maintain class abilities.

\ability{Former Demon Samurais:}{Any character that changes his alignment from Evil loses all class abilities until he returns to Evil, unless he has attained the 5th level of this class and defeated his Patron in single combat.}
