\classname{Dragon Lancer}\label{class:dragonlancer}
\vspace*{-8pt}
\quot{"She is not my steed, she is my companion."}

Fantasy worlds are filled with people who ride around on all kinds of stuff, but none is more immediately iconic than that of the Dragon Rider. Every fantasy world has warriors who ride around on dragons. Even ones that don't fit into D\&D methodology in any other way. At some level it resonates.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{Diplomacy 12 ranks, Ride 12 Ranks, Language (Draconic)}
\itemability{Feats:}{Mounted combat}
\itemability{Special:}{Must have made friendly contact with a Dragon.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d10}

\ability{Class Skills:}{The Dragon Rider's class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Diplomacy (Cha), Escape Artist (Dex), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all skills individually) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &  Base Attack  Bonus  & Fort Save &   Ref Save    &Will Save    &Special\\
1st&+1&+2&+2&+2&Dragon Mount, Dragon Skills, Dragon Resistances\\
2nd&+2&+3&+3&+3&Dragon Armor\\
3rd&+3&+3&+3&+3&Dragon Immunities\\
4th&+4&+4&+4 &+4&Dragon Fighting, Dragon Senses\\
5th&+5&+4&+4 &+4&Destroy Property\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Dragon Lancer prestige class.

\ability{Weapon and Armor Proficiency:}{The Dragon Rider gains no proficiency with armor or weapons.}

\ability{Dragon Mount:}{A Dragon Rider always has a level appropriate Dragon to ride around on. A level appropriate Dragon is 2 levels lower than the Dragon Rider's character level.}

\ability{Dragon Skills:}{Whatever a Dragon Rider does with her life, the special skills of her Dragon Mount's race are class skills for her, and she gains a +3 bonus on them (Balance and Climb for White, Hide and Swim for Black, Bluff and Listen for Blue, Survival and Diplomacy for Green, Sense Motive and Appraise for Red).}

\ability{Dragon Resistances (Ex):}{A Dragon Rider is naturally resilient to whatever it is that her dragon breathes. She gains Energy Resistance equal to her BAB to that energy type.}

\ability{Dragon Armor:}{A Dragon Rider can fashion armor and shield for herself from the discarded scales of her mount. This is appropriate Dragonscale equipment that does not require the skinning of a live Dragon. While the Dragonrider is using it, this Dragonscale equipment has an enhancement bonus equal to one third of her character level.}

\ability{Dragon Immunities (Ex):}{At 3rd level, a Dragon Rider gains immunity to whatever energy type her Dragon Mount breathes. Also she has the immunities granted by being a Dragon -- immunity to Paralysis and Aging.}

\ability{Dragon Fighting (Ex):}{A 4th level Dragon Rider knows the tricks of fighting with and against Dragons. Both the Dragon Rider and her mount have the Edge for any attack they make against a Dragon. Also, any attack she makes against a Dragon inflict an extra 2d6 of damage.}

\ability{Dragon Senses (Ex):}{A 4th level Dragon Rider has Blindsight out to 30', as well as Darkvision out to 60' and Lowlight Vision.}

\ability{Destroy Property (Ex):}{At 5th level, a Dragon Rider may ride her mount straight through objects that obstruct her path. While flying at full speed, her mount may crash through objects even as structurally sound as Force effects without slowing down.}

First of all, we know that the Dragons in the Monster Manual make you sad. They make us sad too. Not just because they are all color coded by philosophy and that's really dumb, but also because Dragons are way too small. Seriously, the proper challenge for most adventurers is a Dragon the size of my dog, and you just can't ride around on those things at all. Most characters want to ride around on a dragon that is at least two sizes larger than they are, and under the normal rules that's just not available until epic levels (by which time you no longer care).

Naturally of course, complete rules for making a Dragon that is scaleable and a decent challenge while being substantially larger than my cat will be introduced in the Tome of Tiamat. But since we know that won't be out for a while, let's throw in a preview mount for Vayn to have when she's an 11th level character:

\ability{Mitzraicha}{}\\
\emph{Dragon (White) 7 / Metallic Paragon 2}\\
\ability{Large Dragon (Cold)}{ -- 100 Hit Points}\\
\ability{Speed:}{60 ft., Burrow 10 ft., Fly 200 ft. (average)}\\
\ability{Stats:}{Strength 23, Dexterity 8, Constitution 18, Intelligence 14, Wisdom 13, Charisma 15}\\
\ability{Skills:}{Balance +14, Concentration +16, Diplomacy +16, Listen +13, Sense Motive +13, Spellcraft +14, Spot +13, Survival +13}\\
\ability{Attacks:}{Bite +14 (2d6+9) and 2 Claws +12 (d8+3)}\\
\ability{Special Actions:}{Breath Weapon (9d6 Cold or paralyzing gas) -- DC 18. Fear DC, human form, fog cloud.}\\
\ability{Special Qualities:}{Blind Sense 60', Immunity to Cold and Paralysis, DR 5/Magic, Fire Vulnerability, Ice Walking, SR 14.}\\
\ability{Saves:}{Fort: +11, Reflex +6, Will +8}\\
