\classname{Dungeon Veteran}\label{class:dungeonveteran}
\vspace*{-8pt}
\quot{"No. If the floor looks like a chessboard, don't walk on it."}

Dungeons are dangerous places, and those who venture into them develop a certain paranoia that is readily identifiable. Who else would take a ten foot pole to the privy to prod the ceiling before entering?

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{9 ranks in Climb, 4 ranks in Knowledge (Dungeoneering)}
\itemability{Feat:}{Power Attack, Cleave}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Dungeon Veteran's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Craft (Int), Disable Device (Int), Handle Animal (Cha), Heal (Wis), Hide (Dex), Jump (Str), Knowledge (dungeoneering) (Int), Knowledge (geography) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Search (Int), Spot (Wis), Survival (Wis), Swim (Str), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+0&+2&+2&Evasion, Dramatic Attack\\
2&+2&+0&+3&+3&Darkvision, Trap Sense\\
3&+3&+1&+3&+3&Loyal Steel, Improved Property Damage\\
4&+4&+1&+4&+4&Looking For Trouble, Exotic Weapon\\
5&+5&+1&+4&+4&\spell{Antimagic Field}, Treasure Sense\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Dungeon Veteran class.

\ability{Weapon and Armor Proficiency:}{A Dungeon Veteran gains proficiency with no new weapons or armor.}

\ability{Evasion (Ex):}{If a Dungeon Veteran succeeds in a Reflex Save to halve damage, he suffers no damage instead. If he already has the Evasion class feature, he gains Improved Evasion instead.}

\ability{Dramatic Attack (Ex):}{Dungeon Veterans fight with flair and gusto and take full advantage of the exotic and dangerous surroundings their battles take place in. When a Dungeon Veteran strikes an opponent with a weapon for 10 or more damage, they may elect to perform a Bullrush against that opponent. This Bullrush maneuver does not provoke an attack of opportunity and is considered to automatically touch the opponent. The Dungeon Veteran does not move with this Bullrush.}

\ability{Darkvision (Ex):}{A 2nd level Dungeon Veteran gains Darkvision with a range of 120 feet.}

\ability{Trap Sense (Ex):}{At 2nd level, a Dungeon Veteran gains a Dodge bonus to AC and Saves against Traps equal to his Class Level.}

\ability{Loyal Steel (Ex):}{Every weapon the Dungeon Veteran throws or fires is treated as having the Returning quality once the Dungeon Veteran achieves 3rd level.}

\ability{Improved Property Damage (Ex):}{Sometimes, it's safer just to go through the wall. A 3rd level Dungeon Veteran's attacks ignore the hardness of unattended objects.}

\ability{Looking for Trouble (Ex):}{Dungeon Veterans spend their lives in a constant state of readiness and are unphased by attacks from any direction. When a Dungeon Veteran reaches 4th level he adds his class level to his Spot, Listen, Search, and Initiative checks.}

\ability{Exotic Weapon:}{At 4th level, a Dungeon Veteran gains Exotic Weapon Proficiency in a weapon of his choice as a bonus feat.}

\ability{\spell{Antimagic Field (Sp)}:}{Once per day, a 5th level Dungeon Veteran can cast antimagic field as a spell-like ability. Caster Level is equal to character level.}

\ability{Treasure Sense (Su):}{The greed of those who venture into dungeons is legendary. When a Dungeon Veteran reaches 5th level, he can detect very valuable items. The presence of an item or pile of coins can be felt by the Dungeon Veteran for 5' for every 1,000 gp in value of the item or hoard in question.}
