\classname{Elothar Warrior of Bladereach}
\vspace*{-8pt}
\quot{"My name is Elothar. Your name is unimportant, for you shall soon be dead."}

The city of Bladereach sits at the mouth of the Typhon River that flows from the Bane Mires into Ferrin's Bay. The elves of Celentian's caravan come every year to trade with the largely human inhabitants of Bladereach and sometimes they leave more than the wares of the Black Orchard Hills when they leave. The results of these dalliances find that they never fit in amongst the people of Bladereach, and are taught the hard secrets of battle that the children of Bladereach have to offer. Often, these half-elven warriors turn to adventuring.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{Use Rope 9 ranks.}
\itemability{Race:}{Half-elf.}
\itemability{Region:}{Must be from Bladereach.}
\itemability{Special:}{Name must be Elothar.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Elothar Warrior of Bladereach's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Craft (Int), Handle Animal (Cha), Heal (Wis), Hide (Dex), Jump (Str), Knowledge (all skills taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Search (Int), Spot (Wis), Survival (Wis), Swim (Str), and Use Rope (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+0 &+0 &+2 &Way of Two Swords\\
2nd &+2 &+0 &+0 &+3 &Tommy, Legacy of the Water Stone\\
3rd &+3 &+1 &+1 &+3 &Magic Swords, Immunity to Petrification\\
4th &+4 &+1 &+1 &+4 &I've Got That!\\
5th &+5 &+1 &+1 &+4 &Double Riposte, Fistful of Rubies\\
6th &+6 &+2 &+2 &+5 &Der'renya the Ruby Sorceress\\
7th &+7 &+2 &+2 &+5 &Ways and Paths\\
8th &+8 &+2 &+2 &+6 &Name of the First Eagle\\
9th &+9 &+3 &+3 &+6 &Blessing of the Gnome King\\
10th &+10 &+3 &+3 &+7 &Flying Ship, Your Money is No Good Here\\
11th &+11 &+3 &+3 &+7 &Demesne of Tralathon\\
12th &+12 &+4 &+4 &+8 &Mark of Ruin\\
13th &+13 &+4 &+4 &+8 &Sword of Kas, Dwarf Friend\\
14th &+14 &+4 &+4 &+9 &Happily Ever After, Khadrimarh\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Elothar Warrior of Bladereach prestige class.

\ability{Weapon and Armor Proficiency:}{An Elothar Warrior of Bladereach gains proficiency with the Nerra Shard Sword, the Kaorti Ribbon Dagger, and the Shuriken.}

\ability{Way of Two Swords (Ex):}{With a single standard action, an Elothar Warrior of Bladreach may attack with a one-handed or light weapon in each hand at no penalties to-hit or damage for the weapon in his primary or off-hand.}

\ability{Tommy:}{At 2nd level, an Elothar Warrior of Bladereach is joined in his adventures by Tommy, a 5th level Halfling Rogue from Figmountain. Tommy is a loyal cohort and gains levels when the Elothar Warrior of Bladereach does. Other Halflings will be impressed by Tommy's apparent loyalty and the Elothar Warrior of Bladereach gains a +3 bonus to his Diplomacy checks when dealing with Halflings if Tommy is present.}

\ability{Legacy of the Water Stone (Sp):}{An Elothar Warrior of Bladereach of 2nd level has touched the fabled Water Stone, and gleaned a portion of its powers thereby. He may cast \spell{create water} as a spell-like ability at will. The caster level for this ability is 5.}

\ability{Magic Swords (Su):}{Any sword a 3rd level Elothar Warrior of Bladereach holds has an enhancement bonus equal to \third of his character level (round down, no maximum). The enhancement bonus fades one round after the Elothar Warrior of Bladereach stops touching the weapons.}

\ability{Immunity to Petrification (Ex):}{At 3rd level, an Elothar Warrior of Bladereach cannot be petrified.}

\ability{I've Got That! (Sp):}{At 4th level, an Elothar Warrior of Bladereach can mimic the effects of a \spell{drawmij's instant summons} at will. The Elothar Warrior of Bladereach does not need an \spell{arcane mark} on the item, nor does he need a sapphire to call the item in question.}

\ability{Double Riposte (Ex):}{If an opponent provokes an attack of opportunity from a 5th level Elothar Warrior of Bladereach, the Elothar Warrior of Bladereach may attack with a weapon in each hand at no penalty. This is considered a single attack of opportunity for purposes of how many attacks of opportunity the Elothar Warrior of Bladereach is allowed in a turn.}

\ability{Fistful of Rubies:}{At 5th level, an Elothar Warrior of Bladereach finds 10,000 gp worth of rubies.}

\ability{Der'renya the Ruby Sorceress:}{At 6th level, an Elothar Warrior of Bladereach is joined in his travels by Der'renya the Ruby Sorceress, a beautiful Drow magician. She is a Wizard 6/ Seeker of the Lost Wizard Traditions 4, and gains levels when he does. Other dark elves will be angered by Der'renya's betrayal, and will be if anything even less friendly with the Elothar Warrior of Bladereach if encountered with her.}

\ability{Ways and Paths (Su):}{At 7th level, an Elothar Warrior of Bladereach can make his way back to any plane he's ever been to. By wandering around in the wilderness for three days, he can make a Survival check (DC 25) to shift himself and anyone traveling with him to another plane.}

\ability{Name of the First Eagle (Sp):}{At 8th level, an Elothar Warrior of Bladereach can speak the name of the first eagle, which summons a powerful giant eagle that has the attributes of a Roc (though it is only large sized). The eagle appears for one hour, and may be summoned once per day.}

\ability{Blessing of the Gnome King (Su):}{At 9th level, an Elothar Warrior of Bladereach has pleased the king of the Gnomes so thoroughly that he is granted a portion of the gnomish power. The Elothar Warrior of Bladereach can speak with burrowing animals and sees through illusions as if he had \spell{true seeing cast} upon him by a 20th level Sorcerer.}

\ability{Flying Ship:}{At 10th level, an Elothar Warrior of Bladereach finds a Flying Ship from the Eberron setting. And can pilot it around.}

\ability{Your Money is no Good Here:}{An Elothar Warrior of Bladereach of 10th level gets free drinks and food at The Wandering Eye, a tavern in Sigil.}

\ability{Demesne of Tralathon}{At 11th level, an Elothar Warrior of Bladereach gains sole control of Tralathon, a small demiplane that appears to be an abandoned Githyanki outpost. Tralathon has several one-way portals that exit onto places on the Astral Plane, the Prime Material, and Limbo. The Elothar Warrior of Bladereach may planeshift to Tralathon at will as a spell-like ability.}

\ability{Mark of Ruin (Su):}{At 12th level, an Elothar Warrior of Bladereach is permanently marked with the Mark of Ruin, which causes all of his melee attacks to ignore hardness and damage reduction.}

\ability{Sword of Kas:}{An Elothar Warrior of Bladereach finds the Sword of Kas at level 13.}

\ability{Dwarf Friend (Ex):}{The deeds of an Elothar Warrior of Bladereach are well remembered by Dwarves when he reaches level 13. Dwarves he encounters are treated as Friendly.}

\ability{Happily Ever After:}{At 14th level, an Elothar Warrior of Bladereach becomes king of Bladereach with Der'renya as his queen. The castle of Halan Shador, that used to belong to the Lichking Hadrach is his to rule from.}

\ability{Khadrimarh:}{A 14th level, an Elothar Warrior of Bladereach has a young adult white dragon named Khadrimarh as a pet.}

\abox{Elothar Warriors of Bladereach in your campaign}{You may want to adapt this prestige class to the specifics of your campaign. In other campaign worlds, the race, region, and name requirements of this class may need to be changed to fit with the overall narrative.}
