\classname{Half Dragon}
\vspace*{-8pt}
\quot{"Also, dragons are pretty! Very pretty."}

Half Dragon is a character class that can be used to make a monster into a more "dragon-like" monster. It can also be taken by player characters who want to be more dragon-like, for whatever reason. Maybe they got spilled with dragon blood and became dragon-like themselves. Maybe their mother slept with a dragon in disguise. Maybe the dragon wasn't in disguise. I don't want to hear about it.

\ability{Prerequisites:}
\listprereq
\itemability{Special:}{Must have some reason why you're more draconic than everyone else. Maybe it's inherited, maybe it's not. Something. Just don't go into too much detail, I probably don't even want to know.}
\itemability{Special:}{Must choose one appropriate dragon type to be more like.}
\end{list}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Half Dragon's class skills (and the key ability for each skill) are Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all skills individually) (Int), Listen (Wis), Move Silently (Dex), Move Silently (Dex), Search (Int), Spot (Wis), Swim (Str).}

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1  & +1 & ++2 & +2 & +2 & Breath Weapon, Scales of the Dragon, Dragon Sight\\
2  & +2 & +2 & +2 & +2 &  Wings of the Dragon, Subtypes, Immunities, Strength of the Dragon\\
3  & +3 & +3 & +3 & +3 &  Sphere, Spell Resistance\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Half Dragon prestige class.

\ability{Weapon and Armor Proficiency:}{The Half Dragon gains no proficiency with armor or weapons.}

\ability{Breath Weapon (Su):}{A Half Dragon is able to emit a deadly breath weapon. The energy type of the weapon is appropriate to whatever dragon type is involved in the dragon-half. As appropriate, it will either come out as a cone with short range, or a line which is twice that long. The breath weapon does 1d6 of damage per character level (or CR) of the Half Dragon and the Reflex save DC is 10 + \half Hit Dice + Con Modifier. Using this breath weapon is a Standard action, and once used it cannot be used again for 2d4 rounds.}

\ability{Scales of the dragon (Ex):}{Half Dragons gain an Enhancement Bonus equal to \third of their Hit Dice (rounded up) to their Natural Armor Bonus to AC.}

\ability{Dragon Sight (Ex):}{Half Dragons gain 60' of Darkvision and see 3 times as far in limited light conditions as per Low Light Vision.}

\ability{Wings of the Dragon (Ex):}{At second level, a half dragon grows dragon wings. They may be small and cute or huge and cloak-like. But regardless of size or mass ratios, they allow the character to fly half again as fast as their land movement rate with average maneuverability.}

\ability{Subtypes:}{A Half Dragon of second level has the Dragon Subtype, as well as whatever elemental or energy subtypes is appropriate for whatever kind of dragon is manifest within her. For example: a Half Black Dragon would gain subtypes of [Dragon, Water].}

\ability{Immunities (Ex):}{2nd level Half Dragons are immune to sleep and paralysis effects, as well as the energy type that they themselves breathe on people.}

\ability{Strength of the Dragon (Ex):}{Upon achieving 2nd level, a Half Dragon is blessed with increased Strength. She gains an Enhancement Bonus equal to \third of her hit dice (rounded up) to her Strength score.}

\ability{Sphere:}{A 3rd level Half Dragon gains a single Sphere.}

\ability{Spell Resistance (Ex):}{3rd level Half Dragons have Spell Resistance of 2 + Character Level (yes, only 2 + Character Level, I'm not even kidding).} 