\classname{Initiate of the Black Tower}
\vspace*{-8pt}
\quot{"Bow before your new Master!"}

Fiends and mortals have played the slavery game for eons, each tempting the other with promises of greater power and threats of greater tortures. In this game, there are favored playing pieces, and they are The Initiates of the Black Tower. These fiend-trained conjurers are weapons in the Blood War, aimed at rival fiends and upstart mortals who have little respect for the scions of the Lower Planes. In exchange for otherworldly secrets, these casters pay a terrible price in service to the fiends of the Black Tower.

\ability{Requirements:}{}
\listprereq %To qualify to become an Initiate of the Black Tower, a character must fulfill all the following criteria.
\itemability{Skills:}{Knowledge (planes) 10 ranks, Spellcraft 10 ranks, Diplomacy 4 ranks, Intimidate 4 ranks.}
\itemability{Feats:}{Broker of the Infernal}
\itemability{Spells:}{Ability to cast 5th-level arcane spells, and the spell \spell{lesser planar binding}}
\itemability{Special:}{Must be a native of the Prime Material Plane, and must either specialize in the conjuration school or have one [summoning] or [calling] spell known at each spell level available.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Initiate of the Black Tower's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Diplomacy(Cha), Intimidate(Cha), Knowledge (all skills taken individually) (Int), Profession (Wis), Search (Int), and Spellcraft (Int).}

\ability{Skill Points at Each Level:}{2 + Int modifier.}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Access to the Registrar, Binding Sense &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Dispel the Chains of Service &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Marks of the Black Tower &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &True Scrying &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Usurp Services &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Share Name &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Calling Ruse &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Unnamed &+1 spellcaster level\\
9th &+4 &+3 &+3 &+6 &Recall the Servant &+1 spellcaster level\\
10th &+5 &+3 &+3 &+7 &Master of the Black Tower &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip \noindent All of the following are Class Features of the Initiate of the Black Tower prestige class.

\ability{Weapon and Armor Proficiency:}{Initiates of the Black Tower gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, the Initiate casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Access to the Registrar:}{At 1st level, the Initiate gains access to The Registrar, a library of True Names of extraplanar beings. For each level in this class, he learns one True Name of a creature of a CR equal to his character level at the time this ability is gained, minus two.}

\ability{Binding Sense(Su):}{At 1st level, an Initiate of the Black Tower may make a Spellcraft check to identify a [calling] or [summoning] effect as if it was a spell being cast whenever he come within of 100' of such an effect. Also, he is alerted whenever a creature whose True Name he knows is called or summoned.}

\ability{\spell{Dispel the Chains of Service}:}{at 2nd level, this spell is added to the Initiate of the Black Tower's list of spells known as a 3rd level spell. This spell functions in all ways as \spell{Dispel Evil}, but it affects [calling] and [summoning] effects instead of evil effects.}

\ability{Marks of the Black Tower (Ex):}{By scratching runes and magical diagrams into the walls, ceilings, and floors of a building, an Initiate of the Black Tower of 3rd level can ward an area from the effects of [calling] and [summoning] spells used by other casters. No creature can be called from the area unless a True Name is used, and no other caster can use [summoning] spells in the area. To create these marks, chalks or paints must be used to inscribe the marks, and a Spellcraft check must be made (DC equals 10 + 5 for every 20' radius). Up to one 10' by 10' area in each Marked area can be free of chalk or paint and still have the Marks be effective. If any markings are disturbed, the effect ends. It takes 10 minutes per 10' radius to scribe these Marks.

If the character uses 100 GP in magical reagents and silver per 10' radius, these markings can be made more difficult to disturb. A Disable Device check is needed to disturb these Marks (DC 25).}

\ability{True Scrying (Sp):}{At 4th level, the Initiate gains the ability to scry on creatures whose True Name he knows as a spell-like ability usable at-will. By casting this effect on any reflective service, the Initiate of the Black Tower can \spell{Scry} on any creature whose True Name he knows with no chance of failure. This also gives enough information to cast \spell{teleport} or other transportation magic as if the location of creature was a well known location.}

\ability{Usurp Services (Sp):}{At 5th level, an Initiate of the Black Tower may make a caster level check as swift action to Usurp a [calling] or [summoning] effect. If this check is successful, the Initiate becomes the caster of the spell for that effect, gaining services, control over summoned monsters, etc.}

\ability{Share Name (Sp):}{At 6th level, the Initiate of the Black Tower may Share Spells with a creature whose True Name he knows as if the creature was a Familiar of the Initiate.}

\ability{Calling Ruse:}{At 7th level, the Initiate of the Black Tower may substitute himself whenever a creature whose True Name he knows is called by a summoning or calling effect. Instead of the creature, he appears and he has three rounds to act as he pleases before the spell affects him as if he were the original creature called.}

\ability{Unnamed (Sp):}{At 8th level, the Initiate of the Black Tower's knowledge of True Names has become so great that he has learned a way to remove True Names from creatures without removing them from existence. He may use this ability once per month, and for all effects, they no longer have a True Name, and can no longer be a target for [summoning] or [calling] spells.}

\ability{Recall the Servant (Sp):}{At 9th level, the Initiate of the Black Tower gains the ability to cast a special version of \spell{gate} to call any creature whose True Name he knows. This may be used three times per day, and it ends any preexisting [calling] or [summoning] effects.}

\ability{Master of the Black Tower:}{At 10th level, the Initiate of the Black Tower has mastered the secrets of the Black Tower. He may now use his Unnamed ability once per day, except that when he uses this ability he can instead takes their True Names. Taking a True Name means that these creatures are now immune to any [calling] or [summoning] effects, except for effects cast by the Initiate.}
