\classname{Legendary Strategist}\label{class:legendarystrategist}
\vspace*{-8pt}
\quot{"We can do this."}

Every group of people has a leader. Some leaders go on to fame in history as total bad asses. That's the Legendary Commander right there.

\ability{Prerequisites:}
\listprereq
\itemability{Skills:}{Knowledge (History) 9 ranks, Bluff 4 ranks, Sense Motive 4 ranks}
\itemability{Feats:}{Must have at least one Leadership feat.}
\itemability{Special:}{Must hold or have held a Rank.}
\itemability{Special:}{Must have been on the winning side of a battle with at least 100 participants.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Legendary Strategist's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Concentration (Con), Craft (Int), Diplomacy (Cha), Disable Device (Int), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (all skills individually) (Int), Listen (Wis), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Swim (Str), and Use Rope.}

\ability{Skills/Level:}{8 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+0 &+0 &+0 &A World of Opportunity, Assistance, Legacies of Command\\
2nd &+2 &+0 &+0 &+0 &Rousing Speech, Trapmaker\\
3rd &+3 &+1 &+1 &+1 &Sending, Trick Opponent\\
4th &+4 &+1 &+1 &+1 &Rally Troops\\
5th &+5 &+1 &+1 &+1 &Heroes' Feast, Best Efforts\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Legendary Strategist prestige class.


\ability{Weapon and Armor Proficiency:}{The Legendary Strategist gains proficiency with any Siege Weapons he happens to come across.}

\ability{A World of Opportunity (Ex):}{Once per turn, a Legendary Strategist may take an Immediate Action without using up his swift action next round.}

\ability{Assistance (Ex):}{A Legendary Strategist may lend assistance and direction to his compatriots. As an immediate action he may allow an ally to reroll one die roll. The ally must be within Medium Range. This is a language dependent ability.}

\ability{Legacies of Command (Ex):}{A Legendary Strategist adds his class level to his Commander rating and his Leadership score(s).}

\ability{Rousing Speech (Ex):}{With a 10 minute tirade, a 2nd level Legendary Strategist may grant all allies who can hear him a Morale Bonus equal to his class level to Damage Rolls and saves vs. Fear. These bonuses last until the sun next rises or sets.}

\ability{Trapmaker (Ex):}{A 2nd level Legendary Strategist is adept at getting traps made. He may allow other characters to use his Craft skill when making Traps so long as they benefit from the effects of his rousing speech.}

\ability{Sending (Sp):}{At 3rd level, a Legendary Strategist may cast \spell{sending} at will as a spell-like ability.}

\ability{Trick Opponent (Ex):}{A 3rd level Legendary Strategist can trick people into doing all kinds of stupid crap on the battlefield. With an Immediate Action, the Legendary Strategist can force any character within Medium Range to reroll a die roll. This is a Language Dependent ability.}

\ability{Rally Troops (Ex):}{With an Immediate Action, a 4th level Legendary Strategist can negate any [Fear] status currently on any allies within Medium Range. This is a Language Dependent ability.}

\ability{Heroes' Feast (Sp):}{At 5th level, a Legendary Strategist may cast \spell{heroes' feast} as a spell-like ability at will.}

\ability{Best Efforts (Ex):}{A 5th level Legendary Strategist can inspire any plebian to perform at their best. Any character who has at least 6 less hit dice than he does who is under the effects of his Rousing Speech gains a +5 Morale bonus on any skill or ability check it makes.}
