\classname{The Monitor}\label{class:monitor}
\vspace*{-8pt}
\quot{"In time\ldots\  even the sun will die. Until then\ldots\  I shall content myself with your demise."}

Kuo-Toans are a depressing group to hang with at the best of times. Their relentless downbeat attitude can turn even the most festive of occasions into a dirge. But perhaps the most depressing of all Kuo-Toa are the Monitors. These monks of Kuo-Toa society are dedicated to a strict regimen of martial training and meditation on the complete futility of all things. Discussions with Monitors have been known to drive even other Kuo-Toa to suicide.




\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{9 ranks in Balance}
\itemability{Feat:}{Multiattack}
\itemability{Alignment:}{Any Evil.}
\itemability{Special:}{Must have at least one Fighting Style class feature.}
\itemability{Special:}{Must be trained in the Kuo-Toa Monasteries.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Monitor's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Craft (Int), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (Religion) (Int), Knowledge (Dungeoneering) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Sense Motive (Wis), Spot (Wis), Swim (Str), and Tumble (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\ability{BAB:}{Good (1/1), Saves: Fort: Good; Reflex: Good; Will: Good}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+2&Fighting Style, Armored in Life, Powerful Observation\\
2&+2&+3&+3&+3&Strike the Intangible\\
3&+3&+3&+3&+3& Master Fighting Style\\
4&+4&+4&+4&+4& Wait for Death\\
5&+5&+4&+4&+4& Master Fighting Style\\
6&+6&+5&+5&+5&Depressing Monologue\\
7&+7&+5&+5&+5&Master Fighting Style\\
8&+8&+6&+6&+6&Sticky Hands, Apathy\\
9&+9&+6&+6&+6& Grand Master Fighting Style\\
\end{tabular}
\end{small}
\end{table}



\noindent All of the following are Class Features of the Monitor class.

\ability{Weapon and Armor Proficiency:}{A Monitor gains no proficiency with any weapons or armor.}

\ability{Fighting Style:}{The Monitor gains a Fighting Style as a Monk at first level.}

\ability{Armored in Life:}{Levels of Monitor stack with levels in Monk for the purposes of the Monk's Armored in Life ability.}

\ability{Powerful Observation:}{A Monitor adds his class level as a bonus to his Spot and Sense Motive checks.}

\ability{Strike the Intangible:}{At 2nd level, a Monitor gains the ability to strike the invisible creatures he can see. His natural weapon attacks can hurt incorporeal and ethereal targets without a miss chance related to intangibility.}

\ability{Master Fighting Style:}{At 3rd, 5th, and 7th level a Monitor gains a Master Fighting Style, as a Monk.}

\ability{Wait for Death (Su):}{A Monitor looks forward only to death, but this can be a very long wait indeed. A Monitor of 4th level does not age, sleep, need nutrition, or breathe. Furthermore, a Monitor of 4th level no longer loses hit points when he has 0 hit points or less.}

\ability{Depressing Monologue (Su):}{Any creature that speaks to a 6th level Monitor for more than five minutes must make a Willpower Save (DC 10 + \half hit dice + Charisma Modifier) or be affected by \spell{abject despair} and \spell{curse of crumbling conviction.}}

\ability{Sticky Hands (Ex):}{A Monitor of 8th level makes great use of sticky Kuo-Toa secretions and gains a +4 bonus on Disarm tests, whether he is the attacker or the defender.}

\ability{Apathy (Su):}{At 8th level, a Monitor is able to draw upon supernatural reserves of ennui and ambivalence, rendering him immune to mind affecting effects.}

\ability{Grand Master Fighting Style:}{At 9th level, a Monitor gains a Grand Master Fighting Style as a Monk.}
