\classname{Ninja of Gax}\label{class:ninjaofgax}
\vspace*{-8pt}
\quot{"Of course I'm not a ninja."}

In a world of gates, planar travel, and teleportation, cultural cross-pollination is a sure result. One such product is the Ninja Of Gax, a figure of stealth and deception born of an oriental tradition adopted by outsiders in order to gain access to mystical arts of disguise and obfuscation. Unlike common rogues or assassins, these covert operatives are part of an ancient tradition of ninjas passed from wily teacher to ambitious student, steeped in secrets gained from generations of practice and discipline. Unlike the originators of this tradition, these students do not hold allegiance to lords or owe loyalty to family or dynasty, making them among the most dangerous deceivers and spies. Their skills are their own to command, and they are free to pursue adventure or wealth as they see fit, unbound by the ties that enslave common ninja clans.

\ability{Prerequisites:}
\listprereq
\itemability{Skills:}{9 ranks in Concentration, 4 ranks in Disguise, 4 ranks in Knowledge Dungeoneering}
\itemability{Race:}{Must have the [Human] subtype.}
\itemability{Feat:}{Must have proficiency with at least one exotic weapon.}
\itemability{Spellcasting:}{Must be able to cast Arcane Spells.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Ninja of Gax's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Sense Motive (Wis), Sleight of Hand (Dex), Spellcraft (Int), Swim (Str), Tumble (Dex), and Use Magic Device (Cha).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{7cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+0&+0&+2&+2&Trapfinding, Good in Black, Cover Identity&+1 spellcasting level\\
2&+1&+0&+3&+3&Ki Breath, +1d6 Sneak Attack&+1 spellcasting level\\
3&+1&+1&+3&+3&Touch of the Ring, Ki Stride&+1 spellcasting level\\
4&+2&+1&+4&+4&+2d6 Sneak Attack&+1 spellcasting level\\
5&+2&+1&+4&+4&Ki Transport, Great in Black&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Ninja of Gax class.

\ability{Weapon and Armor Proficiency:}{A Ninja of Gax gains proficiency with the katana, the shuriken, the sai, the long staff, and the nunchaku.}

\ability{Good in Black:}{A Ninja looks good in black, and knows it. While he's wearing only black clothing, he gains a +2 circumstance bonus to his Charisma.}

\ability{Cover Identity:}{A Ninja of Gax rarely admits that he is a member of an ancient Ninja Tradition. The Ninja of Gax gains a +10 bonus to his disguise checks to convince people that he is not a Ninja and is instead an ordinary arcane Spellcaster.}

\ability{Spellcasting:}{Every level, the Ninja of Gax casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Ki Breath (Su):}{A Ninja of 2nd level gains the ability to hold his breath for an additional minute each day for each level of the Ninja of Gax class.}

\ability{Sneak Attack (Ex):}{At 2nd and 4th level, the Ninja of Gax gains a die of Sneak Attack as a Rogue.}

\ability{Touch of the Ring (Ex):}{A Ninja of Gax of 3rd level suffers no non-lethal damage from the Ring of Gax.}

\ability{Ki Stride (Su):}{At 3rd level, the Ninja of Gax may walk on water for 1 round per class level per day.}

\ability{Ki Transport (Su):}{At 5th level, a Ninja of Gax may walk through walls. By spending three rounds concentrating, the Ninja of Gax may transport himself up to 5 feet in any direction, completely bypassing any intervening obstructions. This ability may not be used if the Ninja of Gax has previously used his ability to hold his breath or walk on water that day.}

\ability{Great in Black:}{At 5th level, the Ninja of Gax looks great in black and his self confidence is bolstered enormously when he is clothed entirely in that color. His circumstance bonus to his Charisma increases to +4.}
