\classname{Progenitor of the Gith}\label{class:progenitor}
\vspace*{-8pt}
\quot{"I've spent five years as a slave to brain-eating geniuses, fighting every day in the pits for their amusement, killing beings culled from dozens of planes. Do you really think this crap impresses me?"}

The Illithid are slavers extraordinaire, masters of the mind control and capable of traveling far in their search for slaves. To escape their clutches, one must become a creature as powerful as them, and some do so by absorbing the ambient psionic radiations of their cities and becoming a more than mortal creature. In this way, the Githzerai and Githyanki earned their freedom, and this route is still open to those willing and capable of surrendering their essence in exchange for communion with the Astral Plane.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+4}
\itemability{Race:}{Human}
\itemability{Special:}{Must have spent at least five years as a slave in an illithid city.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Progenitor of Gith's skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Handle Animal (Cha), Hide (Dex), Intimidate (Cha), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Search (Int), Sense Motive (Wis), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1&+1&+2&+2&+2&Thoughtful Warrior, Endurance of the Mind\\
2&+2&+3&+3&+3&Ideas Made Form\\
3&+3&+3&+3&+3&Movement of the Mind\\
4&+4&+4&+4&+4&Astral Strike\\
5&+5&+4&+4&+4&Native of the Silver Sky\\
\end{tabular}
\end{small}
\end{table}



\noindent All of the following are Class Features of the Progenitor of Gith class.

\ability{Weapon and Armor Proficiency:}{Progenitors of Gith gain proficiency in the composite long bow, and gain no armor proficiencies.}

\ability{Thoughtful Warrior (Sp):}{At 1st level, a Progenitor gains the ability to cast \spell{daze}, \spell{mage hand}, and \spell{feather fall} at will as a spell-like ability}

\ability{Endurance of the Mind (Su):}{A Progenitor has likely been mind blasted and charmed many times in his life. If he is currently the subject of an ongoing effect that allows a Willpower save, he may retest that saving throw every round. Success is treated as if he had passed the initial Willpower save.}

\ability{Ideas Made Form (Sp):}{At 2nd level, the Progenitor gains the ability to cast \spell{clairaudience/clairvoyance} and \spell{shatter} at will as a spell-like ability}

\ability{Movement of the Mind (Sp):}{At 3rd level, the Progenitor gains the ability to cast \spell{dimension door} at will as a spell-like ability.}

\ability{Astral Strike (Sp):}{At 4th level, a Progenitor can cast \spell{Telekinesis} at will as a spell-like ability.}

\ability{Native of the Silver Sky (Ex):}{At 5th level, the energies of the Astral Plane now bolster the physical form of the Progenitor, and he gains becomes an Outsider native to the Astral Plane and he gains Spell Resistance equal to his character level +5, a +4 armor bonus to AC, and the ability to cast \spell{plane shift} twice a day as a spell-like ability.

If he breeds with a githzerai or githyanki, any offspring will be of that race.}
