\classname{Pumpkin King}
\vspace*{-8pt}
\quot{"Rise my children, and taste the fruits of our enemies."}

The sight of the ghostly green pumpkin fires has haunted many a soul. The light it casts reveals not the world beneath the cloak of shadows, but a world of nightmares and terror. The children of the vine are called into service by it. The light calls to them, and they rise to obey their Pumpkin King.

\ability{Requirements:}{}
\listprereq
%To qualify to become a Pumpkin King, a character must fulfill all the following criteria.
\itemability{Skills:}{Knowledge (religion) 8 ranks, Knowledge (nature) 4 ranks.}
\itemability{Feats:}{Body Assemblage [Necromantic].}
\itemability{Spells:}{Able to cast 3rd level spells and cast necromancy spells from every spell level available.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d8.}

\ability{Class Skills:}{The Pumpkin King's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Heal (Wis), Intimidate (Cha), Knowledge (all) (Int), Perform (Cha), Profession (Wis), and Spellcraft (Int).}

\ability{Skill Points at Each Level:}{2 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Children of the Vine, Grow Vines &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Pumpkin Bomb, Plant Spells &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Pluck the Ripe, Soul of the Harvest &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Pumpkin Men &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Reap the Unworthy, Soul of the Pumpkin &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Patch of Doom &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Dark Harvest &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Cornucopia of Death &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip \noindent All the following are Class Features of the Pumpkin King prestige class.

\ability{Weapon and Armor Proficiency:}{Pumpkin Kings gain proficiency in the scythe, but otherwise gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{Every level, the Pumpkin King casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Children of the Vine (Sp):}{At first level, the Pumpkin King has learned to create the Children of the Vine. As an at-will spell-like ability, you may cast a special version of \spell{animate dead} to create skeletons, and only skeletons, from bones or corpses. To use this effect, you must place a pumpkin seed in the mouth or eyes of the skulls used. Vines then creep out of the eyes and wrap themselves around the newly created skeleton's bones. These Children of the Vine last until the next dawn, and this ability shares a control pool with \spell{animate dead}. Children of the Vine that fall inert with the Sun's rise may be reanimated as normal. If a corpse has any flesh remaining upon its bones when animated by this effect, that flesh is scrubbed clean by the vines.}

\ability{Grow Vines (Sp):}{A Pumpkin king can grow pumpkin seeds into lush vines with fully ripened fruit at will.

Also at this level, leaves and small vines start to grow out of your hair. If you are an undead creature, these vines and leaves appear brown and dried; otherwise, they are dark green.}

\ability{Pumpkin Bomb (Su):}{A 2nd level Pumpkin King may throw a Pumpkin Bomb up to fifty feet. He conjures a pumpkin blazing with green and black flames that detonates with unholy energy when it reaches its target. The explosion is 15 feet in radius and inflicts 1d6 per character level of Unholy Damage. A successful Reflex save halves the damage and the Save DC is Charisma based. Throwing a bomb is a full-round action that may be used at will.}

\ability{Plant Spells:}{At 2nd level, the spells \spell{entangle}, \spell{command plants}, \spell{control plants}, \spell{plant growth}, and \spell{wall of thorns} are added to the Pumpkin King's spells known. The spells are known at the level they appear on the Druid spell list.}

\ability{Pluck the Ripe (Ex):}{At 3rd level, any undead you create with spells, class features, or feats have vines and leaves protruding from their bodies. This infestation means that your skeletons have a minimum natural armor bonus equal to your levels in the Pumpkin King class, and they gain immunity to unholy damage.}

\ability{Soul of the Harvest:}{At 3rd level, the irises of your eyes become orange and seem to have an inner light. You gain immunity to unholy damage.}

\ability{Pumpkin Men (Sp):}{At 4th level, you may replace the heads of existing skeletons or Children of the Vine with specially carved pumpkins, creating Pumpkin Men. Pumpkin Men are equal to normal skeletons that have had the \spell{awaken undead} effect used on them, that have a minimum natural armor bonus equal to your level in Pumpkin King, immunity to unholy damage and the Woodland Stride ability of a 2nd level Druid. The holes in the pumpkins that are their eyes and mouths glow with the sickly fires of a Pumpkin Bomb.

You may simultaneously control up to your Pumpkin King level in Pumpkin Men. If you try to convert another skeleton or corpse into a Pumpkin Man beyond your control limit, the Pumpkin Man you have controlled the longest is destroyed. This is an at-will spell-like ability, but properly carving such a pumpkin takes 10 minutes.}

\ability{Reap the Unworthy (Ex):}{At 5th level, any creature damaged by one of your Pumpkin Bombs also must make a Willpower save or become frightened.}

\ability{Soul of the Pumpkin:}{At 5th level, the Pumpkin King's form becomes gaunt and stick-like. He gains immunity to energy drain, negative levels, ability damage, and ability drain.}

\ability{Patch of Doom (Sp):}{At 6th level, a Pumpkin King may create a Patch of Doom one per day as a spell-like ability. A Patch of Doom is a necromantically-charged pumpkin patch. He creates a 10' by 10 area covered in vines, leaves, and pumpkins, and he and his undead in this area gain Fast Healing 1 and immunity to Turning (but not Rebuking). A Patch of Doom is a permanent effect until it is burned clean and the area has a consecrate effect cast on it.

Several uses of this ability can create a single and contiguous Patch of Doom covering a large area. The area of the patch is considered desecrated.

Anyone eating these pumpkins is poisoned as if he had eaten Black Lotus. A Patch of Doom radiates moderate evil, and does not need light, water, soil, or nutrients to survive, but its effects are suppressed if it is covered in ice or snow.}

\ability{Dark Harvest(Su):}{At 7th level, any creature killed in a Patch of Doom created by you becomes a Pumpkin Man that is not under your control (and does not count towards your control pool). This Pumpkin Man will not attack the creator of his Patch of Doom, but will attack any other living creature entering any Patch of Doom contiguous to his own Patch of Doom.}

\ability{Cornucopia of Death(Su):}{At 8th level, the Pumpkin King will return to life if killed. On the next full moon, a body will be created for him in a Patch of Doom of his choice that he has created. He loses a level as normal for returning from the dead, unless there is already one or more pumpkin man in that patch, in which case one of the pumpkin men is destroyed to create the new body and the Pumpkin King loses no levels.

Once he has used this ability, his head will have been replaced with a pumpkin with eyes and mouth glowing with sickly greenish-yellow fires. This has no game effect.}
