\classname{Seeker of the Lost Wizard Traditions}\label{class:seekerofthelosttraditions}
\vspace*{-8pt}
\quot{"The old ways are the best ways. Magic in the past was capable of things you can't even comprehend."}

Empires have risen and fallen many times in history, and each time new magics are discovered and old magics are lost. The Seeker of the Lost Wizard Traditions is a user of magic who is convinced that the way magic was used in the past is better in some important fashion. Whether they are correct or not is something that the Mages of the Arcane Order would probably be willing to argue for days or weeks. But it is undeniable that much of the magic used by the Seeker are beyond the comprehension of those who have not taken the time to explore its ancient ways.

Previous generations have largely picked the surface clean of ancient magic power, and now those who wish to find the remnants of the ancient civilizations must journey deeper and deeper beneath the earth to find items that are protected from scrying.

\ability{Prerequisites:}
\listprereq
\itemability{Skills:}{Spellcraft 9 ranks; Knowledge (Dungeoneering) 9 ranks}
\itemability{Spellcasting:}{Must be able to prepare arcane spells of at least 2nd level.}
\itemability{Race:}{Human, Elf, or Gnome}
\itemability{Special:}{Must not be specialized in a school of magic other than Illusion.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Seeker of the Lost Wizard Traditions' class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Knowledge (all skills, taken individually) (Int), Profession (Wis), and Spellcraft (Int)).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+0&+0&+0&+2&Spell Reflection, Scroll Preparation&+1 spellcasting level\\
2&+1&+0&+0&+3&Uncapped Magic&+1 spellcasting level\\
3&+1&+1&+1&+3&Burst Conservancy&+1 spellcasting level\\
4&+2&+1&+1&+4&Harvest Magic&+1 spellcasting level\\
5&+2&+1&+1&+4&Expanse of the Sky&+1 spellcasting level\\
6&+3&+2&+2&+5&Temporary Portal&+1 spellcasting level\\
7&+3&+2&+2&+5&Unbreachable Stone Defense&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Seeker of the Lost Wizard Traditions class.

\ability{Weapon and Armor Proficiency:}{A Seeker of the Lost Wizard Traditions gains no proficiency with any weapons or armor. However, a Seeker of the Lost Wizard Traditions is considered proficient with any magic sword he holds.}

\ability{Spellcasting:}{Every level, the Seeker of the Lost Wizard Traditions casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Spell Reflection (Su):}{A Seeker of the Lost Wizard Traditions may reflect spells with a line area of effect off of walls. The spell may either bounce off at an appropriate angle (angle of incidence equals angle of refraction) or straight back towards the caster at his whim. Creatures whose spaces are entered twice by a bouncing spell effect are affected twice.}

\ability{Scroll Preparation:}{A Seeker of the Lost Wizard Traditions may prepare his daily spells from any magical writing that he has deciphered without harming himself or the magical writing. Many Seekers take magical scrolls and bind them together into book form because magical scrolls take up less room in a book than do normal pages of spell formulae.}

\ability{Uncapped Magic:}{At 2nd level, spells cast by a Seeker of the Lost Wizard Traditions do not have maximum level-dependent effects.}

\ability{Burst Conservancy (Su):}{At 3rd level, the spells cast by a Seeker of the Lost Wizard Traditions attempt to fill all available space. Every square that a spell with a burst area of effect is prevented from occupying because of a wall or similar obstruction is added to the other side of the effect's area. For example, a fireball takes up 44 squares when used without obstructions. When used in a long, 10' wide hallway by a Seeker of the Lost Wizard Traditions, the fireball would extend to be 110' long.}

\ability{Harvest Magic (Ex):}{A 4th level Seeker of the Lost Wizard Traditions can cut pieces out of recently killed monsters that are useful in item creation. An Aberration, Dragon, Magical Beast, Ooze, or Outsider that has been successfully identified with the appropriate knowledge skill by the Seeker of the Lost Wizard Traditions and killed within the last hour can have one of its organs harvested by the Seeker in a 10 minute procedure that preserves some of the magical power of the creature. The magical portions of such a creature are worth 50 gp and 2 XP towards item creation per CR of the monster.}

\ability{Expanse of the Sky (Su):}{At 5th level, a Seeker of the Lost Wizard Traditions may double the ranges and areas of his spell effects when he is outdoors. As long as the Seeker of the Lost Wizard Traditions has an open sky over his head, every 10' cube in a spell description is a 20' cube, every 30' cone is a 60' cone, and so on and so on. Essentially, all of his spells benefit from Widen and Enlarge Spell}

\ability{Temporary Portal (Su):}{When a 6th level Seeker of the Lost Wizard Traditions casts a [Teleportation] spell that would normally change his own location, he can create a portal from the target location to a location adjacent to himself instead of moving himself. This portal can be seen through and line of effect for spells can be drawn through it. The Seeker of the Lost Wizard Traditions may dismiss the portal at any time as a free action, and it otherwise lasts 1 round per caster level of the Seeker.}

\ability{Unbreachable Stone Defense (Su):}{When a 7th level Seeker of the Lost Wizard Traditions benefits from the spell \spell{stoneskin}, his damage reduction is increased to Unlimited/Adamantine. The hit point reserve of the stone skin is still only reduced by a maximum of 10 points per attack.}
