\classname{Seer of the Tempest}
\vspace*{-8pt}
\quot{"Aaaah! AAAAAAAH! AAAAAAH!"}

The Windswept Depths of Pandemonium breed a special kind of magician. Driven half-mad by the eternal darkness and thunderous din of the eternal windstorm, they walk the battlefields of the multiverse bringing the terrors they know to those who do not.

Most characters who become Seers of the Tempest are Warmages, though sometimes this path appeals to Wizards of a particularly martial bent.

\ability{Requirements:}{}
\listprereq
%To qualify to become a Seer of the Tempest, a character must fulfill all the following criteria:
\itemability{Skills:}{Intimidate 9 ranks.}
\itemability{Alignment:}{Non-Lawful}
\itemability{Spells:}{Must be able to cast 3rd level Arcane spells, and must be able to cast Evocations of every level she can cast.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Seer of the Tempest's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Intimidate (Cha), Knowledge (all skills taken individually) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Increased Edge, Sonic Spells, Suffer the Firmament &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Scary Noises &+1 spellcaster level\\
3rd &+2 &+1 &+1 &+3 &Winds &+1 spellcaster level\\
4th &+3 &+1 &+1 &+4 &Attune Domain: Storm &+1 spellcaster level\\
5th &+3 &+1 &+1 &+4 &Swift Winds &+1 spellcaster level\\
6th &+4 &+2 &+2 &+5 &Uproar &+1 spellcaster level\\
7th &+5 &+2 &+2 &+5 &Sense the Winds &+1 spellcaster level\\
8th &+6 &+2 &+2 &+6 &Attune Domain: Darkness &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Seer of the Tempest class.

\ability{Weapon and Armor Proficiency:}{The Seer of the Tempest gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Seer of the Tempest casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in a spellcasting class she had previous to gaining that level.}

\ability{Increased Edge:}{If the Seer of the Tempest has the Edge class feature, she may add her class level to the Edge bonus. This has no effect if she does not have the Edge class feature.}

\ability{Sonic Spells:}{Every spell that the Seer of the Tempest casts that inflicts any damage may inflict Sonic damage instead at her option when the spell is cast. No other effects of the spell are changed, nor is the casting time of the spell. Spells that are made to inflict Sonic damage in this way gain the [Sonic] descriptor.}

\ability{Suffer the Firmament (Ex):}{A Seer of the Tempest is at home in a tornado as a calm day. She is unaffected by winds of any strength, and suffers no penalties to her listen checks in even the stiffest gale.}

\ability{Scary Noises (Su):}{At 2nd level, the booming destruction of the Seer's magical attacks channels the haunting terrors of Pandemonium. Any creature damaged by a [Sonic] spell cast by the Seer must make a Willpower Save or become shaken. If a creature becomes shaken twice, she becomes frightened. The Save DC is Charisma based, and this is considered a [Fear] effect.}

\ability{Winds (Sp):}{A Seer of the Tempest who has reached 3rd level may use \spell{gust of wind} as a spell-like ability at will. At 5th level, using this ability becomes an Immediate action.}

\ability{Attune Domain:}{At 4th level, the Seer of the Tempest gains Attune Domain (Storm Domain) as a bonus feat. At 8th level she gains Attune Domain (Darkness Domain) as a bonus feat.}

\ability{Uproar (Su):}{As a free action, a Seer of the Tempest of 6th level can attempt to Intimidate all creatures she can target within line of effect that are within an area afflicted by Severe (or worse) winds.}

\ability{Sense the Winds (Su):}{At 7th level, a Seer of the Tempest can feel the disturbances caused by creatures and objects within the wind. She can perceive and target any creature or object within 120 feet of herself so long as there is at least a Light Breeze.}
