\classname{Skindancer}
\vspace*{-8pt}
\quot{"It was Elothar... but it wasn't Elothar. It was like someone wearing an Elothar suit."}

Skindancers are a rare breed of assassin, working their way into a community, shedding identities as they shed skins, with each murder moving closer their targets. The Skindancer is a thief of forms, a powerful Necromancer who has transcended mere shapeshifting magic and mastered the techniques of drawing supernatural power from wearing the living skins of his enemies. They are paragons of disguise and infiltration, dark souls hiding among their enemies while sowing discord and chaos in their wake.

\ability{Prerequisites:}{}
\listprereq
\itemability{Feats:}{A Feast Unknown, Still Spell, Silent Spell}
\itemability{Spellcasting:}{Must be able to cast 4th level Necromancy spells}
\itemability{Special:}{Must not be good.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Skindancer's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Disquise(Cha), Hide(Dex), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently(Dex), Profession (Wis), Sense Motive(Wis), Spot(Wis), and Spellcraft (Int).}

\ability{Skill Points/Level:}{6 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+2 &+0 &+0 &Wear Skin, Taking Lives &+1 spellcaster level\\
2nd &+1 &+3 &+0 &+0 &Likeness &+1 spellcaster level\\
3rd &+1 &+3 &+1 &+1 &Death Attack &+1 spellcaster level\\
4th &+2 &+4 &+1 &+1 &Flexible Hide &+1 spellcaster level\\
5th &+2 &+4 &+1 &+1 &Hide the Evidence &+1 spellcaster level\\
6th &+3 &+5 &+2 &+2 &Fill the Shell &+1 spellcaster level\\
7th &+3 &+5 &+2 &+2 &Aura Steal &+1 spellcaster level\\
8th &+4 &+6 &+2 &+2 &Art of Preservation &+1 spellcaster level\\
9th &+4 &+6 &+3 &+3 &Skin Reincarnation &+1 spellcaster level\\
10th &+5 &+7 &+3 &+3 &Skin Puppets &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All the following are Class Features of the Skin Dancer prestige class.

\ability{Wear Skin (Ex):}{The Skindancer may wear any Skin that has been prepared by the Taking Lives ability of a Skindancer. While wearing this Skin, the Skindancer has the form of the creature whose skin he is wearing as if he had cast \spell{shapechange} and become that creature. This effect lasts as long as he wears the Skin. In addition, he also gains one use of each spell-like ability of that creature's race. Once used, the spell-like abilities of a particular skin are forever expended.

The Skindancer may only wear the Skin of a creature whose CR is three less than his character level, and who has the same size as him. Using this ability on the Skin of a sentient creature (Int of 5 or better) is an evil act.

If the Skindancer dies while wearing a Skin, that Skin is destroyed.}

\ability{Taking Lives (Ex):}{To use this power, the Skindancer must have the fresh and undamaged body of a creature. It cannot have been taken HP damage from any fire or acid effect, piercing or slashing damage, or any other effect that would damage, tear, or destroy its skin (DM's judgment). If the creature was killed within ten minutes (or preserved with magic ten minutes from its death by an effect like \spell{gentle repose}), the Skindancer may begin a one hour ritual to turn the outer flesh of the body into a Skin. Once completed, the skinless body remains. Using this ability on the body of a sentient creature (Int of 5 or better) is an evil act. Any Skin that has not been worn by a Skindancer for one hour rots away to uselessness. Skins cannot be made from Undead, Plants, Oozes, Swarms, Constructs, or any other creature that does not have a skin (DM's option).}

\ability{Likeness (Ex):}{While wearing a creature's Skin, the Skindancer gains a +10 to Bluff and Disguise checks to impersonate that creature (this stacks with the bonuses gained by shapeshifting or disguise spells).}

\ability{Death Attack (Ex):}{At 3rd level, the Skindancer gains the Death Attack ability of an Assassin. Levels in this class stack with levels of any other class that offers Death Attack for the purposes of this class feature. Any creature killed by a bludgeoning Death Attack is suitable for the Taking Lives ability.}

\ability{Flexible Hide:}{At 4th level, the Skindancer can wear the Skin of a creature who is within one size category of his own size.}

\ability{Hide the Evidence (Su):}{At 5th level, the Skindancer can completely devour the skinless body of any victim that he uses the Taking Lives ability on.}

\ability{Fill the Shell:}{At 6th level, the Skindancer can wear the Skin of a body that is up to two sizes larger than his own.}

\ability{Aura Steal(Su):}{For the purposes of divination magic, the Skindancer is the creature whose Skin he is wearing.}

\ability{Art of the Preservation (Su):}{The Skindancer has learned the art of preserving Skins for later use in briny pools. By spending 500 gp per CR of the creature the pool will hold and one day, the Skindancer can build a briny pool that will preserve a Skin inside it and indefinitely maintain the Skin's ability to be worn. Once taken out of the pool, the skin rots to uselessness within one hour as usual, unless it is worn.}

\ability{Skin Reincarnation(Su):}{If killed, a Skindancer will be reincarnated (as the spell) into the form of one of the Skins he is preserving with the Art of Preservation ability (if he does not have a preserved Skin of his own size and race, randomly determine which Skin is used). The Skin used by this ability is destroyed in the process.}

\ability{Skin Puppets:}{The Skindancer can create Skins that can be worn by others by expending 2,000 gp per CR of the creature. Each creature wearing one of these Skins gains one use of the Wear Skin ability, and counts as if the Skindancer had successfully cast \spell{charm monster} on them.}
