\classname{Speaker for the Dead}\label{class:speakerfordead}
\vspace*{-8pt}
\quot{"For ten thousand years our ancestors have lived and died in this land and not once has the world been swallowed by an unending chasm into the Abyss. They tell me that they are disappointed in your actions, and I am here to make their displeasure known."}

The souls of those that die are drawn inexorably towards the outer planes to await their punishment or rewards as befits the whim of the powerful beings that dwell there -- outsiders and the gods themselves. A few get drawn back to the world of the living, but the vast majority become petitioners, and the memories of these lives beyond counting are gradually forgotten and lost to time.

Or they would be, if the Speakers did not endeavor to catch these memories and keep them safe against a time in the future when they may be needed again.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills:}{Diplomacy 4 Ranks, Knowledge (History) 9 ranks}
\itemability{Languages:}{Must know at least 4 languages}
\itemability{Spellcasting:}{Must be able to cast Divination and Necromancy spells of levels 1 through 3.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Speaker for the Dead's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy(Cha), Knowledge (all skills, taken individually) (Int), Profession (Wis), Speak Language, and Spellcraft (Int).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}ll}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Speak With Dead &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Call Spirits, Well of Knowledge &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Taste of Lethe, Hear the Hungry Spirit &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Education of the Dead &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Proxy of the Dead &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Revenge of the Fallen &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Avenging Souls &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Library of Lost Memories &+1 spellcaster level\\
9th &+4 &+3 &+3 &+6 &Usurp Death's Kingdom &+1 spellcaster level\\
10th &+5 &+3 &+3 &+7 &Vengeance of the Dead &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Speaker for the Dead prestige class.

\ability{Spellcasting:}{Every level, the Speaker for the Dead casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in a spellcasting class she had previous to gaining that level.}

\ability{Speak With Dead (Sp):}{A Speaker for the Dead can use \spell{speak with dead} as a spell-like ability at will. Unlike a normal caster, they can successfully use the spell more than once on the same corpse, though if a corpse of a creature with a hostile alignment makes its save, speak with dead may not be used again on that corpse for an entire week.}

\ability{Call Spirits (Su):}{The Speaker for the Dead is able to telepathically communicate with any undead creature. She gains a +4 to all Diplomacy, Bluff, Sense Motive, or Intimidate checks when used on undead.  In addition, all the of \spell{summon undead} spells are considered spells known for her.}

\ability{Well of Knowledge:}{By 2nd level, the Speaker for the Dead has begun to have long conversations with the dead, gaining all sorts of odd knowledge. The speaker's levels count as Bard levels for the purposes of Bardic Knowledge. If she does not already have Bardic Knowledge, she gains that ability using only her levels in Speaker for the Dead.}

\ability{Hear the Hungry Spirit(Su):}{The Speaker for the Dead can sense of the presence or absence of undead within 1 mile. She knows their general direction, but cannot pinpoint distance, power, or numbers of undead.}

\ability{Taste of Lethe (Ex):}{A Speaker of 3rd level or higher has honed her skills of remembrance to the point where she is able to draw upon the unending mind of the undead. She is not completely immune to mind affecting magic as an undead is, but her memories are. The Speaker is immune to effects such as \spell{modify memory} and \spell{mind rape}, and is even able to drink the waters of the River Styx without losing any precious memories.}

\ability{Education of the Dead:}{The Speaker for the Dead has absorbed vast amounts of information from the spirits of the dead. She is considered to have a minimum of 10 ranks in all Knowledge skills. To surpass the 10 rank minimum, the Speaker must assign skill points as normal to gain a skill at a higher ranks.}

\ability{Proxy of the Dead:}{Undead creatures cannot attack a Speaker for the Dead unless they make a DC 25 Will save (they may make a new save each round). If she casts a spell or attacks them, they automatically make their next save. Unintelligent undead get no save.}

\ability{Revenge of the Fallen:}{At 6th level, the Speaker for the Dead gains the ability to cast \spell{animate dead} as a spell-like ability at will. Whenever she does so, these undead are not controlled. They form a weak Necromantic Intelligence that has a purpose of finding the people that killed them. This effect cannot create any individual zombies or skeleton with more than 4 HD.}

\ability{Avenging Soul:}{At 7th level, the Speaker for the Dead gains the ability to cast \spell{greater create undead} as a spell-like ability once per day. Whenever she does so, these undead are not controlled. Each has a weak Necromantic Intelligence that has a purpose of finding the people that killed them.}

\ability{Library of Lost Memories:}{The Speaker for the Dead may cast \spell{contact other plane} or \spell{legend lore} as a spell-like ability once per day at 8th level.}

\ability{Usurp Death's Kingdom (Su):}{A 9th level Speaker for the Dead may alter the purpose of a Necromantic Intelligence. She must perform a ritual that takes 24 hours at the location of the Focus of the Necromantic Intelligence, and this ritual provokes the same response as a Cleansing.

When she is done, the Necromantic Intelligence's purpose changes to anything the Speaker desires. If this is not possible, the Necromantic Intelligence is destroyed.}

\ability{Vengeance of the Dead:}{At 10th level, the Speaker for the Dead may create a Necromantic Intelligence with a purpose of her choosing. This costs 20,000 gp in materials, and circumstances must be appropriate for a Necromantic Intelligence to form.}
