\classname{Thief of Souls}\label{class:thiefofsouls}
\vspace*{-8pt}
\quot{"What would I possibly want with your money?"}

Jewels, gold, and magical trinkets fill the dreams of most thieves, but the Thief of Souls wants only the most treasured possession of all: your very soul. Charming, wicked, and stealthy, they're the enemy of the gods, preventing believer's souls from entering their rightful place in the afterlife.

From souls come power, and these dangerous individuals have learned to tap into that power for their own ends. The fact that this process destroys the souls does not matter to them as they know the world is full of souls, waiting to be taken.

\ability{Prerequisites:}
\listprereq
\itemability{Skills:}{Use Magic Device 9 ranks, Knowledge(Religion) 4 ranks, Craft (alchemy) 4 ranks}
\itemability{Spellcasting:}{Ability to cast 1st level Arcane Spells.}
\itemability{Alignment:}{Cannot be good.}
\itemability{Special:}{Sneak Attack, Sudden Strike, or Skirmish +2d6}
\itemability{Special:}{Must have owned and used a dagger made from thinaun.}
\end{list}\vspace*{8pt}

\ability{Hit Dice:}{d6}

\ability{Class Skills:}{The Thief of Soul's class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all) (Int), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex), and Use Magic Device (Cha).}

\ability{Skill Points/Level:}{6 + Int modifier}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+2 &+2 &Soul Taker, Thinaun Alchemy &+1 spellcaster level\\
2nd &+1 &+0 &+3 &+3 &Sneak Attack +1d6 &+1 spellcaster level\\
3rd &+1 &+1 &+3 &+3 &Fuel Magic &+1 spellcaster level\\
4th &+2 &+1 &+4 &+4 &Sneak Attack +2d6 &+1 spellcaster level\\
5th &+2 &+1 &+4 &+4 &Soulfire &+1 spellcaster level\\
6th &+3 &+2 &+5 &+5 &Sneak Attack +3d6 &+1 spellcaster level\\
7th &+3 &+2 &+5 &+5 &Steal Magical Essence &+1 spellcaster level\\
8th &+4 &+2 &+6 &+6 &Sneak Attack +4d6 &+1 spellcaster level\\
9th &+4 &+3 &+6 &+6 &Reap Soul &+1 spellcaster level\\
10th &+5 &+3 &+7 &+7 &Fuel Life, Sneak Attack +5d6 &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Thief of Souls prestige class.

\ability{Weapon and Armor Proficiency:}{The Thief of Souls gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Thief of Souls casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Soul Taker(Su):}{At 1st level, a Thief of Souls may extract a soul from a thinaun dagger and place it within a gem worth at least 100 gp. This process takes one minute, and the soul in the gem is held inside it indefinitely. If the soul gem is smashed, the soul inside is released. If the soul gem is used to fuel any of the Thief of Soul's class features, the gem and soul inside are destroyed and the creature whose soul was taken cannot be returned from the dead.}

\ability{Thinaun Alchemy(Ex):}{The Thief of Souls learns alchemic secrets that teach him how to convert iron into thinaun, the legendary soul stealing metal. He may construct new blades using this technique, the process take one day and expends 5000 gp in materials.}

\ability{Sneak Attack (Ex):}{At 2nd level, the Thief of Soul's Sneak Attack Damage increases by 1d6. His sneak attack damage increases by another d6 at every even level. If the Thief of Souls has the Skirmish ability, he can increase his Skirmish Damage instead of his Sneak Attack.}

\ability{Fuel Magic(Su):}{When activating a charged magic item, a 3rd level Thief of Souls may destroy a gem containing a soul (destroying the soul) instead of using charge(s) from that item. The soul used must have a HD equal to the caster level of the effect.}

\ability{Soulfire (Su):}{A 5th level Thief of Souls may destroy a gem containing a soul (destroying the soul) in exchange for a ranged touch attacking deal 1d6 points of damage per HD of the soul with the gem. This is an attack action with a medium range, and the character need not be within 30 feet of the target for the attack to count as a Sneak Attack (other restrictions of sneak attacks apply).}

\ability{Steal Magical Essence (Su):}{Any time a Thief of Souls of 7th level or higher uses his Soul Taker ability, he can also extract one spell from the soul that it had prepared at the time of its death (his choice). This effect keeps the spell in the gem, and any character who makes a DC 20 Use Magic Device check may use this spell as if casting it from a Spell Storing item. Once the spell is cast, the gem no longer functions as a spell storing item, but is not otherwise damaged.}

\ability{Reap Soul (Su):}{Any time the Thief of Souls successfully uses his sneak attack on an enemy with a thinaun weapon, the victim must make a Fortitude save or die. The save is Charisma based, and this is a Necromantic Death Effect. The Thief of Soul's thinaun blade can take the soul as normal.}

\ability{Fuel Life (Ex):}{At 10th level, the Thief of Souls may destroy any soul gem with a CR equal to his character level in exchange for reverting himself to a young adult age. Doing so has no effect on his mental attributes, and when the soul gem is destroyed the character may choose to alter his appearance to match that of the creature whose soul was destroyed. This gives a +10 bonus to Disguise checks to impersonate the victim.}
