\classname{Vampire Paragon Class}\label{class:vampireparagon}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Vampire Paragon's class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disguise (Cha), Escape Artist (Dex), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Sense Motive (Wis), Sleight of Hand (Dex), Speak Language (n/a), Spellcraft (Int), and Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}\\

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{0.7cm}p{0.7cm}p{0.7cm}ll}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+2 &+2 &Blood Pool, Gaseous Form, Flaw &+1 spellcaster level\\
2nd &+1 &+0 &+3 &+3 &Hypnotic Gaze &+1 spellcaster level\\
3rd &+1 &+1 &+3 &+3 &Command Spawn, Regeneration, Flaw &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\noindent All of the following are Class Features of the Vampire Paragon class.

\ability{Weapon and Armor Proficiencies:}{The Vampire Paragon gains no new armor or weapon proficiencies.}

\ability{Spellcasting:}{Every level, the Vampire Paragon casts spells (including gaining any new spell slots and spell knowledge) as if she had also gained a level in a spellcasting class she had previous to gaining that level. If the character does not have any levels in any spellcasting classes when she takes her first level of Vampire, this class feature gives her levels in Sorcerer spellcasting.}

\ability{Blood Pool (Ex):}{A Vampire Paragon may "store" blood she has drained from intelligent creatures against future need and draw upon this blood to power her body or her magic. If a Vampire Paragon consumes the Constitution of an intelligent creature after she has already fed for the day, excess Constitution drained adds to her Blood Pool. A Vampire Paragon's Blood Pool can never exceed her character level plus her class level of Vampire Paragon. Constitution drained after the Blood Pool is filled is wasted.

A Vampire Paragon may spend a point of her Blood Pool to heal herself of five points of damage. She may spend 4 points of Blood Pool to forgo needing to feed for one day. A spell being cast may be enhanced with any metamagic feat the Vampire Paragon knows by spending a number of points of Blood Pool equal to the number of extra levels the metamagic would add to the spell. Using Blood Pool is a free action, but no more than 4 points may be spent in a single round.}

\ability{Gaseous Form (Su):}{A Vampire Paragon can assume \spell{gaseous form} as the spell at will.}

\ability{Flaw:}{Increasing the power of the blood within a Vampire is not without difficulties. As the potency of the Vampire's blood grows, so too does the power of her curse. At 1st and 3rd level of Vampire Paragon, the vampire gains an additional weakness related to her blood. Appropriate vampiric weaknesses are too numerous to be listed here, but could include: Inability to enter consecrated or hallowed ground; helplessness in water; \spell{repulsion} (as the spell) by garlic; vulnerability to silver; daylight powerlessness (as a specter); dazed by spilled grains (2d4 rounds); nauseated by Holy Water (1d4 rounds); Inability to enter a hearth unless invited.}

\ability{Hypnotic Gaze (Su):}{At 2nd level, a Vampire Paragon gains the ability to hypnotize creatures which meet its gaze. The Vampire Paragon may make use its gaze on one creature within short range each round as a Swift action. Creatures are affected as by a \spell{hypnotism} spell except that there is no hit die cap. The hypnotism effect ends if the Vampire Paragon no longer maintains the gaze (for example, by attempting to hypnotize a new victim). This is a Mind Affecting Enchantment effect, the DC is Charisma based.}

\ability{Command Spawn:}{Vampire Spawn created by a Vampire Paragon of 3rd level are under the Vampire Paragon's control.}

\ability{Regeneration (Ex):}{At 3rd level a Vampire Paragon regenerates, healing subdual damage every round equal to her character level. Damage from critical hits, fire, positive energy, aligned weapons, or wood inflict lethal damage on a Vampire Paragon.}
