\classname{Stranger with the Burning Eyes}

One of the greatest necromantic mysteries is the ability to move souls from one body to another, and to use this trick to inhabit the flesh of a stranger, gaining a twisted and parasitic form of immortality. Usually this art is as dangerous as it is powerful, but for the Stranger with the Burning Eyes the experience is a way of life. They have abandoned their true form and now only move from body to body like a virus, taking with them knowledge and power, working their way through the world using the bodies of others as proxies.

When they transfer to a new body, their eyes glow with the fires of their souls, as they have fanned the flames of their spirits until they can survive without a material form. They are the consummate strangers in strange land, and often acquire habits from the many unusual body forms they have inhabited. One thing is certain: they have little regard for the people they inhabit.

\ability{Prerequisites:}{}
\listprereq
\itemability{Feats:}{Still Spell, Silent Spell}
\itemability{Skills:}{Knowledge (Religion) 9 ranks, Concentration 9 ranks}
\itemability{Spellcasting:}{Must be able to spontaneously cast 5th level spells, and the spell \spell{magic jar}.}
\itemability{Special:}{Your true body must have been destroyed.}
\itemability{Special:}{You cannot be good.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d4}

\ability{Class Skills:}{The Stranger with the Burning Eyes' class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Hide(Dex), Intimidate (Cha), Knowledge (all skills, taken individually) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+1 &+0 &+0 &+2 &Burning Soul, Token &+1 spellcaster level\\
2nd &+2 &+0 &+0 &+3 &Consume &+1 spellcaster level\\
3rd &+3 &+1 &+1 &+3 &Firewall of the Soul &+1 spellcaster level\\
4th &+4 &+1 &+1 &+4 &Explosive Reaction &+1 spellcaster level\\
5th &+5 &+1 &+1 &+4 &Inferno &+1 spellcaster level\\
6th &+6 &+2 &+2 &+5 &Lore of the Burning Flame &+1 spellcaster level\\
7th &+7 &+2 &+2 &+5 &Slow Burn &+1 spellcaster level\\
8th &+8 &+2 &+2 &+6 &Wildfire &+1 spellcaster level\\
9th &+9 &+3 &+3 &+6 &Conflagration &+1 spellcaster level\\
10th &+10 &+3 &+3 &+7 &Hellfire &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All the following are Class Features of the Stranger with the Burning Eyes prestige class.

\ability{Spellcasting:}{Every level, the Stranger with the Burning Eyes casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Burning Soul (Su):}{At 1st level, the Stranger with the Burning Eyes has mastered the ability to move between bodies. He may use \spell{magic jar} at will as a Supernatural ability with an indefinite duration. For the purposes of this spell, any body he is possessing also counts as a receptacle, so he may use the senses granted by being in a \spell{magic jar} receptacle and possess new bodies from this form, and he returns to the last body he possessed if his current body is killed, if it is within range (it gets a save as usual). If it is not within range, he is killed. Since bodies count as receptacles for this effect, the Stranger does not need line of effect to possess a new body.

The Stranger with the Burning Eyes no longer ages, though bodies he is possessing will age.}

\ability{Token:}{At 1st level, the Stranger with the Burning Eyes is magically followed by a token whenever he changes bodies. This is a simple piece of jewelry worth at least 1,000 gp, and it can be enchanted with any enchantment suitable for rings, rods, wonderous items, and armor (but it cannot be intelligent). This item is a tiny object with hardness 20 and 20 hp, and if removed from a body the Stranger with the Burning eyes is possessing he is immediately forced to possess a new body (he cannot possess that body ever again). If he cannot possess a new body, he dies. (Note: if the victim of the Stranger's possession attack is ever given a second Will save to resist his possession from an effect like Slippery Mind, a successful save means the victim removes the token).

The token is magically recreated or moved each time the Stranger possesses a new body, so as long as he lives it continues to exist.}

\ability{Consume (Su):}{At second level, the Stranger with the Burning Eyes may ``lose" a prepared spell or spell slot to perform a Wisdom draining touch attack as a standard action. The touch attack does as much Wisdom drain as the spell level that is lost, and a successful Will save halves this drain.}

\ability{Firewall of the Soul:}{At 3rd level, the Stranger with the burning Eyes is immune to any effect that moves his soul or would end his possession of a body (other than removing his token). Any effect that traps his soul in his current body still works, and he will die if such an effect is cast on him and the body he is possessing dies. The Stranger may also remain in a body if he is in an \spell{antimagic field} or other magic destroying effect, though he is effectively trapped in that body until he can leave that effect.}

\ability{Explosive Reaction (Su):}{At 4th level, when the Stranger with a Burning Soul is in a body that is killed, he may take an immediate action to possess a new body (or return to his last body, as usual).}

\ability{Inferno(Su):}{While in a possessed body, the Stranger may use any of its feats once he has attained 5th level.}

\ability{Lore of the Burning Flame:}{While in a possessed body, the Stranger may use any of its skills or personal knowledge once he has attained 6th level.}

\ability{Slow Burn(Su):}{Once the Stranger with the Burning Eyes has achieved 7th level, if he is in a body that is killed, and he cannot successfully possess any body, his soul is instead transferred into his Token and it counts as a receptacle. Should the Token be destroyed while it holds the soul of the Stranger, he immediately dies without a chance to possess new bodies.}

\ability{Wildfire(Su):}{At 8th level, the Stranger with the Burning Eyes may use his \spell{magic jar} ability a number of times a round equal to his Charisma modifier as a full round action. This enable to make possession attempts very quickly and even travel large distances in heavily populated areas.}

\ability{Conflagration(Su):}{As a standard action, a 9th level Stranger with the Burning Eyes can combine a use of his Consume ability with his \spell{magic jar} ability. The person he attempts to possess is affected by the Consume ability as if he had been successfully touched. The Consume effect uses spells or spell slots as normal.}

\ability{Hellfire:}{Should the Stranger with the Burning Eyes ever he killed once he has achieved 10th level, he returns to life with his soul in his Token one year later (it is recreated 1d4 miles from the location of his death). He does not lose a level from this return from the dead.}
