Dragoon
“ 	"You can fly?!?" 	”
—A blue dragon simultaneously discovering the existance and capabilities of Dragoons

The Dragoons are a group of warriors dedicated to slaying large monsters. Of course, they are most famous for taking on dragons, to the point that many of them have a definite dragon motif to their armor. Armed with a spear to be able to reach vital points on barn-sized creatures with hides like rock, Dragoons leap fearlessly into battle. And I do mean leap.

It is hypothesized that the amazing physical abilities shown by a Dragoon are the result of natural talent for magic combined it with a strict training regimen, and channeled towards something other than spells.
[edit] Becoming a Dragoon

Generally, Dragoons are recruited and trained as a sort of public service; even Evil civilizations have a problem with big monsters, so Dragoons can hail from those places, too.


Entry Requirements Skills: 	Jump 8 Ranks
Feats: 	Giant Slayer for those using Races of War (DnD Other) rules, Skill Focus: Jump for those who aren't.
Special: 	Heavy armor proficiency, and proficiency with a spear, lance, or similar weapon.

Hit Die: d10

Level 	Base
Attack Bonus 	Saving Throws 	Special
Fort 	Ref 	Will
1st 	+1 	+2 	+2 	+0 	Evasion, Jump Attack, Jump Good
2nd 	+2 	+3 	+3 	+0 	Spear Mastery
3rd 	+3 	+3 	+3 	+1 	Dragonbreath
4th 	+4 	+4 	+4 	+1 	Killer Jump
5th 	+5 	+4 	+4 	+1 	Dragonbreath
6th 	+6 	+5 	+5 	+2 	Giantkiller
7th 	+7 	+5 	+5 	+2 	Dragonbreath
8th 	+8 	+6 	+6 	+2 	Dragonheart, Improved Evasion
9th 	+9 	+6 	+6 	+3 	Dragonbreath
10th 	+10 	+7 	+7 	+3 	Double Jump

Class Skills (4 + Int modifier per level)
Balance, Climb, Intimidate, Jump, Knowledge (all), Listen, Spot, Survival, Swim, Tumble

Overtrained: While not exactly a Code of Conduct, Dragoons do have a few things drilled into their head by their teacher: Defend the People From Monsters, Especially Big Monsters.

The majority of their training is concerned with finding ways to stab monsters in the face when it seems improbable that the Dragoon would be able to reach that high. Naturally, a Dragoon first reaction upon seeing a monster chewing on a few cows in the street and hearing people scream, would be to heft his spear and then endeavor to stab the monster in the face. I'm not saying they *must* do it, but it will be their first, second, and third thought.

Jump Attack (Ex): At first level Dragoons learn a specialized mode of attack—death from above. As long as one falls at least thirty feet and attacks at the end of the fall, he does double damage on a successful hit; if he's wielding a spear or a lance of some kind, he does triple damage and ignores either armor or natural armor (whichever is higher). Should he score a critical hit with a Jump Attack, damage is caculated by adding 1 onto the weapon's critical multiplier, or 2 if using a spear or a lance or similar weapon.

Jump Good (Su): At 1st level, A Dragoon's Jump DCs are halved, and the formula for figuring vertical jump height is the same as for horizontal jump height (one foot per point on the check). Dragoons jump extraordinarily quickly, letting them complete an entire jump, no matter how far it is, as a move action, and their Armor Check penalty does not apply to their Jump checks; they are always considered to benefit from a running start on Jump checks. They also gain immunity to falling damage as long as they’re conscious and always land on their feet.

Evasion (Ex): Really big creatures can often unleash really big blasts of fire or acid or some other unpleasantness. For this reason, Dragoons are trained in the arts of evasion. Should a Dragoon already have Evasion, this stacks to Improved Evasion.

Spear Mastery (Ex): Dragoons like spears. They’re simple to use, and the reach makes it easier to damage vital points on their chosen foes—big, big monsters. At 2nd level, A Dragoon may use a reach weapon as if it were not a reach weapon with no penalty and the critical threat range with spears and lances and other piercing polearms is increased by 1 (this stacks with anything that doubles the critical threat range, but is added after the doubling).

Dragonbreath (Su): Dragoons have a career fighting monsters who tend to have breath weapons or some ability to turn an entire area into pain. Naturally, there is a desire to get even, and at 3rd level it's become strong enough to take over more of the Dragoon's natural magical talent and grant him a breath weapon known as Dragonbreath.

At levels 3, 5, 7, and 9, select an energy type out of fire, electricity, cold, acid, and sonic. The Dragoon can use his Dragonbreath with any of his repertoire of energy types. Dragonbreath is a 15-foot cone which inflicts 1d8 per character level of the energy type (selected when used), Reflex save DC 10 + 1/2 Character level + Con mod for half. After Dragonbreath is used, it may not be used again for 1d4 rounds.

Killer Jump (Su): If a Dragoon has learned anything by 4th level, it’s that there is a huge amount of energy to be gained from falling.

Killer Jump is full-round action. It begins when the Dragoon makes a Jump check to land on a target, and with this particular check he may travel travel up to 10 feet (vertically and/or horizontally) for every two points on the check.

When he lands on the target, he makes a touch attack roll. It is like a normal Jump Attack (does double damage on a successful hit (triple if using a spear)) but an additional d6 of damage for every 10 feet he fell, and is considered a critical threat and resolved as such; the bonus falling damage is not multiplied. He may do this every 1d4 rounds.

Giantkiller (Ex): A 6th-level Dragoon has some experience with killing big creatures, and has discovered a very interesting fact—big creatures have big vital areas. Of course, having a long weapon helps in exploiting these areas.

A Dragoon gets a doubled critical range for spear-like weapons, as long as the target is Large size or larger. He also gets a +2 on his attack rolls to confirm critical hits for each size the creature is above medium.

Improved Evasion (Ex): As the Rogue. If the Dragoon already has Improved Evasion, he gets a bonus feat for which he meets the prerequisites.

Dragonheart (Su): A Dragoon who hits his stride will enter a state of mind. It's a good place for him, and a bad place for his enemies.

If a Dragoon succeeds on a saving throw or confirms a natural critical hit (the auto-threat from Killer Jump does not count, unless the attack roll was naturally in the threat range), Dragonheart activates as a free action. The Dragoon gains Fast Healing equal to 1/2 his character level + his Con modifier, and becomes immune to mind-affecting effects, ability damage or drain, and morale and fear effects. Dragonheart lasts for a number of rounds equal to his class level.

Double Jump (Su): The Dragoon is now a master of jumping on things to kill them. When he connects with a Jump Attack or a Killer Jump, he may make an swift action to perform another Jump Attack on the same target.
[edit] Ex-Dragoon

Generally, Dragoons only retire when old age makes fighting giant monsters risky. Most of them, though, default to being Dragoons and, as such, seek out, recruit, and train suitable people to replace themselves in the ranks. 