\classname{Berzerker} \label{comm:prestige:berzerker}
\vspace*{-8pt}
\quot{"Maim! Kill! Burn! Maim! Kill! Burn! Maim! Kill! Burn! Maim! Kill! Burn! Maim! Kill! Burn!"  "Attack! Is the only other word you need to know."}

Some people fight, some few of those that fight can kill, a very select few are concerned with nothing so long as they can fight. Preferably in hand to hand combat, preferably now.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB}{+5}
\itemability{Skill:}{Intimidate 8 Ranks}
\itemability{Proficiency:}{Must be proficient with at least one slashing or piercing weapon.}
\itemability{Special:}{Must have attacked a creature for lethal damage for no reason other than to get into a fight (i.e. there must not be any foreknown reward or accomplishment that the character can know about aside from "I got into a fight with that creature").}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d12}

\ability{Class Skills:}{The Berzerker's class skills have not yet been written.}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1&+1&+2&+0&+0&Natural Wearer of Armour, Rage, Ferocious Healing\\
2&+2&+3&+0&+0&+1&Hate Magic, MAIM! KILL! BURN!,\\
3&+3&+3&+1&+1&Skulls for the Skull Throne! Disdain for No Weapon\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Berzerker class.

\ability{Weapon and Armor Proficiency:}{A Berzerker gains proficiency with all slashing and piercing melee weapons.}

\ability{Rage:}{As the Barbarian Class feature, Berzerker levels stack with Barbarian levels for determining the effects of the Rage feature and Rage Dice.}

\ability{Natural Wearer of Armour:}{A Berzerker is always ready for the spilling of blood. As such, they nearly never remove their armour, becoming so accustomed to its presence that it begins to act as if it were a second skin. Some Berzerkers even wear extra armour. Merely because they can.

As long as the Berzerker is wearing one suit of armour that they are proficient with, the Armour Bonus instead counts as a Natural Armour bonus. They may wear an other suit of armour so long as it has a lower Armour Check Penalty than the suit of armour that is underneath. The Armour Check and Stealth Check penalties of both armours are added together.

[Yes, that means that the 1/2 of your lowest armour value rule from Book of Gears is voided].}

\ability{Ferocious Healing:}{If a Berzerker deals lethal damage to an other creature they gain Fast Healing for a number of rounds equal to their levels in classes that provide Rage or Rage-like abilities combined.}

\ability{Hate Magic:}{Berzerkers hate magical effects as well as anyone who uses them. They willingly use magical equipment (often stolen from magic using characters, usually by force) in order to even the odds. However, they must always make a Saving Throw against any spell that is cast on them (even beneficial ones) that allows for a saving throw, and they gain Spell Resistance equal to 15 + Hit Dice. This spell resistance can not be willingly lowered by the Berzerker.}

\ability{MAIM! KILL! BURN!:}{A Berzerker can go into an unending chant to encourage herself to spill even more blood.

As a swift action, a Berzerker may begin ranting and raving at the top of their lung at their enemies. The Berzerker's lethal attacks deal an additional amount of damage equal to their character level in [Energy] damage. This benefit lasts until the beginning of the Berzerker's next round.

[Energy is  `Baskin Robbins' damage flavours (i.e. Holy, Anti-holy, Acid, Dope, Fire, Cold, Electricity, Sonic, Hedgehogs, Force etc.) or "Fire" if `Sane' damage flavours are used.]}

\ability{Skulls for the Skull Throne!:}{A Bloodspiller's weapon acts as if it has the BoG's \spell{sharpness} weapon property at all times. This can be suppressed as a non-action and can be re-activated as part of an attack action. A weapon with \spell{shaprness} cuts off a target's limb if they are attacked and damaged that round unless they make a Reflex save against a DC of 10 + 1/2 the Berzerker's Hit Dice + The Berzerker's Charisma Modifier.}

\ability{Disdain for No Weapon:}{Sometimes a Berzerker only has a soup cup, often that is more than enough.

A Berzerker suffers no penalties for using an improvised weapon. Also, they can use any sized melee weapon, so long as it is a light load for them, without any penalty. This weapon deals damage as if it were an appropriate weapon of a size category that corresponds with its weight. }