\classname{Blade Fighter} \label{class:comm:bladefighter}
\vspace*{-8pt}
\quot{"It takes skill to kill with the blade, but don't be afraid to use the point."}

Fighting is not a pleasant thing. You are trying to physically exert your will upon an other creature, usually trying to end their life.

Some people who do this sort of thing on a regular basis learn that certain methods and techniques are effective at surviving fights. If these people live long enough, they eventually have others learn from them. If enough people become students of a single person's methods, then a fighting style is born.

Fighting styles range in both methodology and tools; from the use of turning non-weapons into weapons, to using obvious weapons in a fashion that they were not expected to be used.

Fighting with knives is very common, and thus many different fighting styles deal with how to use a relatively short piece of hard substance in a manner that both keeps you alive and also makes the other creature dead.

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+6}
\itemability{Skills:}{Craft 8 ranks, Knowledge (Nature) 8 ranks}
\itemability{Feats:}{Combat School (Light Slashing or Piercing weapons)}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Blade Fighter's class skills (and the key ability for each skill) are Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Diplomacy (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Listen (Wis), Move Silently (Dex), Profession (Wis), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Swim (Str), Tumble (Dex). }

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+0&Train the Body and Mind, Bend Like a Reed in the Wind, Hone the Blade, Distracting Strike\\
2&+2&+3&+3&+0&Blade Lore, Killing With the Edge Takes Skill, Pragmatic Point\\
3&+3&+3&+3&+1&Push the Body and Mind, Crippling Strike\\
4&+4&+4&+4&+1&Predilection for Blade-fighting, Blinding Strike\\
5&+5&+4&+4&+2&Break the Body and Mind, May Your Blade Chip and Shatter\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Blade Fighter class:

\ability{Weapon and Armor Proficiency:}{A Blade Fighter gains proficiency with no new weapons or armor.}

\ability{Train the Body and Mind (Ex):}{+2 on Will and Fort saves.}

\ability{Bend Like a Reed in the Wind (Ex):}{As long as you are not denied your Dexterity modifier to your Armour Class, and you are wearing armour that does not give you an armour check penalty (or light armour or no armour if not using RoW) you may add your intelligence modifier to your armour class; if it is positive.}

\ability{Hone the Blade (Ex):}{With 1 hour's time and 10 GP, you can turn any light slashing and/ piercing weapon into a masterwork weapon. You may do this while performing an other action, if it is possible to do both at the same time (cooking or smithing a horseshoe = no; walking or talking with someone = yes).
With 8 hours time and access to a forge, you can turn any object into an appropriate masterwork light slashing and/or Piercing weapon. If this changed object was a weapon, it retains any unique or special properties that the original weapon had.}

\ability{Distracting Swipe (Ex):}{You may elect to deal no damage with any of your attacks with light slashing/piercing weapons. If you do so, your target is Cowered. This Cowered effect lasts until the target takes damage from any source or at the end of the turn that the action was performed in (Eg. If you performed this while making an AoO on your target, the effect ends once your target's turn is over; if performed in your turn, the effect ends when your turn is over).}

\ability{Blade Lore (Ex):}{Any masterwork light slashing/piercing weapon you wield may count as if it were a Magic weapon. If you have used this weapon before, making your wielded weapon Magic is a non-action. If you have just picked up this weapon, making your wielded weapon Magic is a standard action.}

\ability{Killing With the Edge Takes Skill (Ex):}{You may add the Enhancement bonus of one light slashing/piercing weapon that you are wielding to your results in Grapple checks. If you have the edge in a Grapple, you may attack with a light slashing/piercing weapon as soon as you can attack in the grapple.}

\ability{Pragmatic Point (Ex):}{Your range increments with all light slashing/piercing weapons is doubled. You may add your one half your Character level to your attack rolls with light slashing/piercing weapons; if you do so, your damage is reduced to the weapon's base damage.}

\ability{Push the Body and Mind (Ex):}{As an immediate action, take 1 Con and 1 Wis damage; gain up to your class level on all Attack and Damage rolls, Skill checks, Saving Throws and Armour Class. This bonus lasts until the encounter ends.}

\ability{Blinding Strike (Ex):}{If you attack a Cowered opponent, you may choose to blind them, if you do so your attack deals no damage. A creature blinded in this manner can make a full round action to clear their eyes, clearing ones eyes is an action that provokes an attack of opportunity.}

\ability{Predilection for Blade-fighting (Ex):}{Gain DR X/-, where X is 2+ \half your character level.}

\ability{Crippling Strike (Ex):}{If you deal damage to a grappled opponent with a light slashing or piercing weapon, you may embed your weapon in your target. If you do so, the target receives the weapons last enhancement bonus as a penalty to all of their attack rolls, damage rolls, grapple checks, skill checks and saving throws.
Pulling out the weapon is a full round action that provokes an Attack of Opportunity. The embedded weapon counts against your maximum equippable magic items as long as it is in your target and is giving them the penalty to rolls.}

\ability{Break the Body and Mind (Ex):}{As an immediate action, take 1 Con and 1 Wis damage; gain up to your character level on all Attack and Damage rolls, Skill checks, Saving Throws and Armour Class. This bonus lasts until the encounter ends.

If this Ability damage is healed before the current adventure ends (either naturally or through magical means), then you receive a penalty to your Con and Wis equal to the amount of times you have used this ability on your current adventure. This penalty lasts until the current adventure is complete, after which it is removed.}

\ability{May Your Blade Chip and Shatter (Ex):}{As a standard action you may crack any light slashing/piercing that you wield.

If you deal damage to a creature, the weapon is destroyed. The weapons last enhancement bonus is given as a penalty to all of the target's attack rolls, damage rolls, grapple checks, skill checks and saving throws. This effect lasts until the encounter ends.

The cracked weapon counts against your maximum equippable magic items as long as it is in your target and is giving them the penalty to rolls.}