\classname{Elemental Brute}
\vspace*{-8pt}
\quot{"Wind etches cliff walls.\\
A landslide falls to the sea.\\
Raindrops douse spring fires."}

\desc{The powers of the elements are more than just a source for mages to tap, but the building blocks out of which everything else is made.  By combining more of the elements onto one's self, an elemental can become a being of immense physical power.  Elemental Brutes not only grow this power, but also use it to control the battlefield around them.}

\desc{Elemental Brutes are heavy hitters in melee, and use their abilities to make the battlefield a more difficult place for their opponents and to protect their allies.}

\ability{Alignment:}{Elemental Brutes can be any alignment, and often are.}

\ability{Races:}{Only Outsiders and Elementals from the Elemental Planes may take levels in Elemental Brute.  Those from the Material plane whose ancestors come from the Elemental Planes may take levels in Elemental Brute, but they must have the Outsider or Elemental type.}

\ability{Starting Gold:}{4d4x10 GP}

\ability{Starting Age:}{As Rogue.}

\ability{Hit Die:}{d10}

\ability{Base Attack Bonus:}{Medium (as Cleric)}

\ability{Saving Throws:}{Good Fortitude and either Reflex (Air, Fire) or Will (Earth, Water)}

\ability{Class Skills:}{Balance (Dex), Climb (Str), Hide (Dex), Jump (Str), Listen (Wis), Move Silently (Dex), Sense Motive (Wis), Spot (Wis), Survival (Wis), and Swim (Str).}

\ability{Nice Skills:}{Acrobatics (Dex), Athletics (Con), Jump (Str), Perception (Wis), Sense Motive (Wis), Survival (Wis), and Stealth (Dex)}

\ability{Skill Points per Level:}{4 + Int Mod (x4 at 1st level)}

\begin{table}[htb]
\begin{small}
\begin{tabular}[h]{lp{1.9cm}p{0.7cm}p{1.5cm}p{0.7cm}p{9cm}}
&   Base Attack Bonus&  Fort Save&  Ref Save&   Will Save&  Special\\
1&  +0& +2& +2/+0& +0/+2&  Elemental Origin, Natural Armor, Natural Weapon, Bonus Feat, Combat Talent +1\\
2&  +1& +3& +3/+0& +0/+3&  Attribute Boost\\
3&  +2& +3& +3/+1& +1/+3&  Elemental Mastery\\
4&  +3& +4& +4/+1& +1/+4&  Attribute Boost\\
5&  +3& +4& +4/+1& +1/+4&  Bonus Feat, Combat Talent +2\\
6&  +4& +5& +5/+2& +2/+5&  Attribute Boost\\
7&  +5& +5& +5/+2& +2/+5&  Horde Breaker\\
8&  +6/+1& +6& +6/+2& +2/+6&  Attribute Boost\\
9&  +6/+1& +6& +6/+3& +3/+6&  Bonus Feat, Combat Talent +3\\
10& +7/+2& +7& +7/+3& +3/+7&  Attribute Boost\\
\end{tabular}
\end{small}
\end{table}

\ability{Weapon and Armor Proficiency:}{Elemental Brutes are proficient only with their natural weapons, and with no armor.}

\ability{Elemental Origin:}{An Elemental Brute grows from the material of one of the elemental planes.  It has the most obvious connection available (Genasi (except Material Genasi) and Elemental-Bodied all indicate a connection with one of the planes, as do all elemental monsters in the Monster Manual).  If none suggests itself, such as for a Material Genasi, the Elemental Brute gets to pick one of the four elemental planes.  Certain abilities come in different forms depending on elemental origin.  Air, Fire, and Shadow Brutes gain the General Feat version of Weapon Finesse as a bonus feat.}

\ability{Natural Weapon:}{An Elemental Brute gains a Slam attack for 1d8 damage (if medium), plus strength and a half.}

\ability{Natural Armor:}{Elemental Brutes gain a natural armor bonus to AC equal to their level.}

\ability{Bonus Feat:}{At 1st, 5th, and 9th level, the Elemental Brute gains a bonus [Elemental], [Monstrous], or [General] feat that it qualifies for.  At 7th level it gains Horde Breaker.  If it already has Horde Breaker, it may gain another bonus feat, or another Combat feat that it qualifies for.}

\ability{Combat Talent (ex):}{You may add the listed number to your base attack bonus for purposes of unlocking abilities of [Combat] Feats.  If playing with fractional BAB, instead count the Elemental Brute as providing full BAB for purposes of unlocking [Combat] Feat abilities}

\ability{Attribute Boost:}{At 2nd level and every even numbered level afterward, the Elemental Brute's physical attributes improve, as if it had gained several character levels. Every time the Elemental Brute gains an attribute boost, its Constitution and one other physycial attribute dependent on Elemental Origin irrevocably increase by 1.

\noindent\begin{tabular}[h]{ll}
\emph{Strength}: &Earth, Water, Ice, Magma, Wood\\
\emph{Dexterity:} &Air, Fire, Shadow\\
\end{tabular}}

\ability{Elemental Mastery (ex):}{An Elemental Brute of 3rd level or higher gains The Edge against opponents in its element.

\noindent\begin{tabular}[h]{ll}
\emph{Air:} &An Air Brute gains The Edge against flying opponents.\\
\emph{Earth:} &An Earth Brute gains The Edge as long as its weight and its opponent's weight are both on the ground.\\
\emph{Fire:} &A Fire Brute gains The Edge against any opponent that is presently on fire or otherwise taking continuous fire damage when it makes its attack.\\
\emph{Water:} &A Water Brute gains The Edge against any opponent immersed at least halfway in water.\\
\end{tabular}

Exotic elemental types also gain this ability:

\noindent\begin{tabular}[h]{ll}
\emph{Ice:} &An Ice Brute gains The Edge against any opponent standing on ice.\\
\emph{Magma:} &A Magma Brute behaves like a Fire Brute.\\
\emph{Shadow:} &A Shadow Brute gains The Edge against any opponent against whose attacks it has concealment or total concealment.\\
\emph{Wood:} &A Wood Brute gains The Edge against any opponent who ended their last turn adjacent to it without attacking it.\\
\end{tabular}}

\subsubsection*{Playing an Elemental Brute}
\ability{Religion:}{Elemental Brutes are seldom particularly religious, although they may follow an Elemental deity of their appropriate kind.  Recently, a cult of evil Elemental Brutes was found worshipping the Elder Elemental Eye.}

\ability{Other Classes:}{Elemental Brutes get along well with Elemental Weirds of like element, as their abilities complement eachother well.  They do not necessarily get along well with Genies, as many Genies expect to be lords over the Elemental Brutes.  Elemental Brutes get along well with Druids, and with properly respectful Elementalists, whose magic complements the Elemental Brute's physical power.  Stealthy types often appreciate the distraction that an Elemental Brute can provide, and warriors may appreciate having an Elemental Brute to spar with.  Casters may view an Elemental Brute as little higher than their summoned minion, earning the Brute's wariness.}

\ability{Combat:}{Elemental Brutes are effective at controlling the battlefield to force enemies into melee with them. Air Brutes often take an air superiority role, tripping flying opponents to cause them to stall and drop them to where their allies can reach them, while Earth and Water Brutes control a section of battlefield with their bulk. Fire Brutes make effective skirmishers, especially with the Whirlwind feat to allow them to attack several creatures at once, and Burn to allow them the Edge against any creature they've already hit. Exotic Brutes gain other abilities to match.}

\ability{Advancement:}{An Elemental Brute, after completing the class, may take levels in Elemental Weird, or in another combat-focused class, or may become a Genie.  A few levels of Elemental Brute can add quite a bit to many melee Genasi or Elemental-Bodied builds, especially to gain the Large Size and Huge Size feats, granting the character a greater reach and the ability to use bigger weapons.  Other melee classes grant the Elemental Brute the ability to use better weapons and shields, and multiclassing into Monk would give the Brute the ability to use fighting styles with its elemental Slams.}