\classname{Elemental Weird}
\vspace*{-8pt}
\quot{"The guardian of the Temple of the Seas shall not allow you to pass"}

\desc{The Elements are known as one of the many primal sources of magic.  Mortal mages and even beings of the outer planes draw on the energies of the Inner Planes to fuel their magic, but Elemental Weirds, as beings of the elements themselves, surpass them all at drawing on raw elemental power.  For an elemental to become an Elemental Weird is to drink deep from the wellspring of magic, soar on the winds of fate, cast sorceries as the roots of the mountains, and burn with the fires of power, fully seizing their birthright as elementals.  Those Elementals and Genasi who walk this path gain a terrifying mastery of the magics of the elements.}

\ability{Alignment:}{Most Elemental Weirds tend toward at least some form of Neutrality, but it takes all kinds.}

\ability{Races:}{Only Outsiders and Elementals from the Elemental Planes may take levels in Elemental Weird.  Those from the Material Plane whose ancestors come from the Elemental Planes may take levels in Elemental Weird, but they must have the Outsider or Elemental type.}

\ability{Starting Gold:}{4d4 x 10 GP (100 GP)}

\ability{Starting Age:}{Complex (as Wizard)}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{Concentration (Con), Craft (Int), Diplomacy (Cha), Knowledge (All skills, taken individually) (Int), Spellcraft (Int)}
\ability{Skill Points per Level:}{2 + Int Mod}

\begin{table}[htb]
\begin{small}
\begin{tabular}[h]{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
&   Base Attack Bonus&  Fort Save&  Ref Save&   Will Save&  Special\\
1&  +0& +0& +0& +2&  Elemental Origin, Sphere\\
2&  +1& +0& +0& +3&  Enhanced Sphere Access\\
3&  +1& +1& +1& +3&  Sphere\\
4&  +2& +1& +1& +4&  Hardiness of the Elements\\
5&  +2& +1& +1& +4&  Sphere\\
6&  +3& +2& +2& +5&  Elemental Skills\\
7&  +3& +2& +2& +5&  Sphere\\
8&  +4& +2& +2& +6&  Unstoppable Force\\
9&  +4& +3& +3& +6&  Sphere\\
10& +5& +3& +3& +7&  Magical Training\\
\end{tabular}
\end{small}
\end{table}

\ability{Weapon and Armor Proficiency:}{An Elemental Weird is proficient with all Simple weapons, and a martial weapon dependent on Elemental Origin, and Light armor, but not with shields of any kind.
Origin Proficiency:
\begin{tabular}[h]{ll}
\emph{Air} &Bolas, Throwing Axe\\
\emph{Earth} &Light and Heavy pick\\
\emph{Water} &Trident, Net\\
\emph{Fire} &Spiked Chain\\
\end{tabular}
Exotic origins also grant a weapon proficiency:
\begin{tabular}[h]{ll}
\emph{Ice} &Handaxe, Battleaxe\\
\emph{Magma} &Light Hammer, Warhammer\\
\emph{Shadow} &Shortsword, Kukri\\
\emph{Wood} &Glaive, Greatclub\\
\end{tabular}}

\ability{Elemental Origin:}{An Elemental Weird's power originates with one of the elemental planes, typically one of the four classical planes.  They have the most obvious connection available (Genasi (except Material Genasi) and Elemental-Bodied all indicate a connection with one of the planes, as do all elemental monsters in the Monster Manual). If none suggests itself, such as for a Material Genasi, the Elemental Brute gets to pick one of the four elemental planes.  The Elemental Weird's origin determines the Spheres to which it gains access.}

\ability{Sphere:}{The Elemental Weird gains basic access to a Sphere at every odd numbered level. If the Elemental Weird selects a sphere that it already has basic access to, it upgrades its access to advanced access. If it already had advanced access, it gains expert access.}

\ability{Enhanced Sphere Access:}{At 2nd level, the Elemental Weird gains extra uses of the spell-like abilities that it gains from it Spheres. The Elemental Weird gains a number of extra uses of any spell-like ability equal to half the number by which its character level exceeds the minimum character level to use the spell-like ability (rounded up). So if the Elemental Weird has a character level of 4, it would gain 1 extra use of a spell-like ability that is granted by one of it spheres at character level 3 and 2 extra uses of any spell-like from one of its spheres with a minimum level of 1.  The Elemental Weird gains a +1 bonus to caster level for all spell-like abilities cast from Spheres to which it has Expert acess, and saving throws against such abilities are made against a DC of 11 + 1/2 the Weird's character level (rounded up) + the Weird's charisma modifier (the highest save DC it would have, plus one).}

\ability{Bonus Feats:}{An Elemental Weird gains the Hardiness of the Elements feat as a bonus feat at level 4, and Unstoppable Force as a bonus feat at level 8.  If it already has Hardiness of the Elements at level 4, it gains Unstoppable Force then instead.  If it already has Unstoppable Force when it is given that as a bonus feat, it gains its choice of any [ Elemental ] or [ Item Creation ] feat instead.}

\ability{Elemental Skills:}{An Elemental Weird gains a +10 Competence bonus to a skill depending on their elemental origin:
\begin{tabular}[h]{ll}
\emph{Air} &Tumble\\
\emph{Earth} &Knowledge (Dungeoneering)\\
\emph{Fire} &Jump\\
\emph{Water} &Escape Artist\\
\end{tabular}
Exotic origins gain the following:
\begin{tabular}[h]{ll}
\emph{Ice} &Sense Motive\\
\emph{Magma} &Intimidate\\
\emph{Shadow} &Sleight of Hand\\
\emph{Wood} &Search\\
\end{tabular}}

\ability{Magical Training:}{An Elemental Weird of 10th level is able to cast magic in a more traditional fashion.  It has the Spells per day and spells known (including Advanced Learning) of a 6th level Elementalist, and a caster level of 10.  At its option, it may use Charisma instead of Intelligence to determine the highest level of spells it may cast and its bonus spells per day, or instead of Wisdom to determine spell save DCs, but not both.  It may take classes that improve spellcasting of existing classes in order to advance its spellcasting ability.}