\classname{Invisible Blade} \label{comm:prestige:invisibleblade}
\vspace*{-8pt}
\quot{"Flavor Text Here"}

Insert more flavor text here.

\ability{Prerequisites:}{}
\listprereq
\itemability{Skills}{Deception 7 ranks, Legerdemain 3 ranks}
\itemability{Special:}{A prospective Invisible Blade must be proficient in a light bladed weapon.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Invisible Blade's class skills (and the key ability for each skill) are Acrobatics (Dex), Arcana (Int), Athletics (Str), Concentration (Cha), Craft (Int), Deception (Cha), Empathy (Wis), Legerdemain (Dex), Spot (Wis).}

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1&+1&+0&+2&+0&Invisible Blade, See Invisible\\
2&+2&+0&+3&+0&Sneak attack +1d6\\
3&+3&+1&+3&+1&Phase Blade\\
4&+4&+1&+4&+1&Sneak attack +2d6\\
5&+5&+1&+4&+1&Imaginary Blade\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Invisible Blade class.

\ability{Weapon and Armor Proficiency:}{The invisible Blade does gain proficiency with any new weapons or armor.}

\ability{Invisible Blade (Sp):}{As a swift action, the Invisible Blade may turn any weapons she wields invisible. Any any target attacked by such a weapon is considered flat-footed unless the target is able to see it (though detect invisible, blindsight, or a similar ability).}

\ability{See Invisible (Su):}{The Invisible Blade can see invisible, as the spell, except that it is always active.}

\ability{Phase Blade (Sp):}{The Invisible Blade can use \spell{wraithstrike} a number of times per day equal to her class level plus 1/2 her character level.}

\ability{Imaginary Blade (Su):}{As a swift action, the Invisible Blade create an invisible weapons of force. These take the form of any light, bladed, non-reach weapon that the Invisible Blade is proficient in, save that they are a force effects and deal force damage. An Imaginary Blade gains an enhancement bonus as a magical weapon. An Imaginary Blade is invisible as the Invisible Blade's eponymous ability.}
