\classname{Celestial Beacon}\label{class:celestialbeacon}

The Lower Planes are realms of evil of such magnitude that the good are oppressed in such a place. Those whose goodness is so strong that it radiates from them are beacons to the denizens of these realms, and some have learned to harness this light to burn away the unclean presence of the fiends.

\ability{Requirements}{}
\listprereq
%To qualify to become a Celestial Beacon, a character must fulfill all the following criteria.
\itemability{Skills:}{Knowledge (Planes) 4 ranks, Knowledge (Religion) 9 ranks.}
\itemability{BAB:}{+5}
\itemability{Special:}{Must radiate moderate good.}
\itemability{Special:}{Must be proficient in heavy armor.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Celestial Beacon's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Intimidate(Cha), Heal(Wis), Knowledge (Religion) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+1 &+2 &+0 &+2 &Aura of Good, Smite Evil &+1 spellcaster level\\
2nd &+2 &+3 &+0 &+3 &Halo of the Righteous &+1 spellcaster level\\
3rd &+3 &+3 &+1 &+3 &Arms of the Holy &+1 spellcaster level\\
4th &+4 &+4 &+1 &+4 &Armament of the Holy &+1 spellcaster level\\
5th &+5 &+4 &+1 &+4 &Death Ward &+1 spellcaster level\\
6th &+6 &+5 &+2 &+5 &Flare of Goodness &+1 spellcaster level\\
7th &+7 &+5 &+2 &+5 &Light of Peace &+1 spellcaster level\\
8th &+8 &+6 &+2 &+6 &Holyfire Shield &+1 spellcaster level\\
9th &+9 &+6 &+3 &+6 &Celestial Aspect &+1 spellcaster level\\
10th &+10 &+7 &+3 &+7 &Ward Against Evil Magic &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Celestial Beacon prestige class.

\ability{Weapon and Armor Proficiency:}{Celestial Beacons gain no proficiency with any weapon or armor, but do gain proficiency in the Tower Shield.}

\ability{Aura of Good (Ex):}{The power of a Celestial Beacon's aura of good (see the \spell{detect good} spell) is equal to her Celestial Beacon level. This stacks with any other Aura of Good Ability gained from other sources.}

\ability{Smite Evil (Su):}{As a free action, a Celestial Beacon may attempt to smite evil with one normal melee attack. She adds her Charisma bonus (if any) to her attack roll and deals 1 extra point of damage per Celestial Beacon level. If the Celestial Beacon accidentally smites a creature that is not evil, the smite has no effect, but a use of the ability is expended for that day. The Celestial Beacon may use this ability once for every level of Celestial Beacon, and uses per day and bonuses of this effect stacks with any Smite Evil gained from other classes.}

\ability{Halo of the Righteous(Su):}{At 2nd level, the Celestial Beacon emanates a \spell{Magic Circle Against Evil} effect, as the spell.}

\ability{Arms of the Holy:}{At 3rd level, any melee attack performed by a Celestial Beacon counts as good-aligned for the purposes by bypassing damage reduction.}

\ability{Armament of the Holy (Su):}{At 4th level, any armor worn by the Celestial Beacon takes on a silvery of golden shine, and it is one category lighter than normal for purposes of movement and other limitations. Heavy armors are treated as medium, and medium armors are treated as light, but light armors are still treated as light. Spell failure chances for armors and shields worn by a Celestial Beacon are decreased by 10\%, maximum Dexterity bonus is increased by 2, and armor check penalties are lessened by 3 (to a minimum of 0). The Celestial Beacon gains DR 5/evil}

\ability{Death Ward(Su) :}{At 5th level, the Celestial Beacon is continuously under the effects of a \spell{death ward}, as the spell. The irises of his eyes become gold or silver.}

\ability{Flare of Goodness (Su):}{At 6th level, the Celestial Beacon may perform a Flare of Goodness as an immediate action. This has the effects of a \spell{Sunburst} spell, and any evil magic in the radius is automatically dispelled. After using this ability, all class features gained from Celestial Beacon levels cease functioning for 1d4+1 rounds.}

\ability{Light of Peace:}{Upon reaching 7th level, the Celestial Beacon is continuously under the effects of a \spell{sanctuary} spell. If the Celestial Beacon attacks during a round, this effect ends for 1d4 rounds, then renews itself.

The Celestial Beacons also gains the ability to shine as brightly as a torch. He may suppress or renew this ability as a swift action.}

\ability{Holyfire Shield (Sp):}{As a swift action, an 8th level Celestial Beacon can cast use a spell-like ability called Holyfire Shield at will. This effect is like a golden-colored \spell{fire shield}, but the damage it inflicts is holy damage and it grants immunity to unholy damage.}

\ability{Celestial Aspect:}{At 9th level, the Celestial Beacon becomes an Outsider, and gains a +2 to Str, +2 to Wis, and +2 to Cha. He may be restored to life according to his previous type.}

\ability{Ward Against Evil Magic:}{At 10th level, the Celestial Beacon gains SR of 15 + character level, but only against [evil] spells and spell-like abilities and the spells and spell-like abilities cast by evil-aligned creatures.}
