\classname{Uttercold Assault Necromancer}\label{class:uttercold}
\vspace*{-8pt}
\quot{``Coooooooobraaaaaaaaa!"}

The living dead can make terrifically efficient soldiers, fearless and untiring. However, mindless undead are less than ideal in many respects, being unable to take initiative or respond to changing battlefield conditions. Sentient undead are therefore the pinnacle of soldiering, but since they are not mindless, they must be lead.

For political reasons, the living dead are seldom permitted to serve as their own officers; instead, fearful mortal authorities insist that they must be placed under the command of the living. However, if such officers hope to win the respect of their troops, they must be magically powerful in their own right, as well as charismatic and subtly tainted by the touch of death. Such officers learn not only to lead and motivate sentient undead on the battlefield, but to support their forces with cold and death related magic.

Not only are the undead fearless, but they are also perfectly disciplined, do not do damage to the civilian infrastructure, and do not require forage to survive. In order to maintain discipline, and in response to the hatred and fear in which their forces are held, these officers hold themselves to the highest standard of military ethics. A degree of political aptitude also serves such officers well, as their forces are almost guaranteed to be given the most dangerous and least desirable missions. The stringent requirements of this class demand commitment from a young age, so most Uttercold Assault Necromancers are apprenticed in their teens. Being in such scarce supply, they are absolutely required to train apprentices in turn to join the officer corp.

\ability{Prerequisites:}{}
\listprereq
\itemability{Feats:}{Energy Substitution (Cold), Lord of the Uttercold, Tomb Tainted Soul, Mentor (exchanged for apprentice).}
\itemability{Spells:}{Must be able to cast at least three spells from the Necromancy school, of which at least one must be third level or higher, and at least one spell with the cold descriptor.}
\itemability{Skills:}{Concentration 9 Ranks, Knowledge (Planes) 9 Ranks, Language (Battle Signals), Speak Language (Semaphore Battle Signals).}
\itemability{Alignment:}{Cannot be chaotic.}
\itemability{Special:}{Must hold officer's rank (Rank 3+, see Heroes of Battle) in a military or paramilitary organization that includes elite units of sentient undead.}
\itemability{Special:}{Your apprentices (from the Mentor feat) must also be junior officers in your military organization (Rank 1+).}
\itemability{Note:}{If you are using Playing with Fire, the Necromantic Commander aura does not have an alignment requirement, and neither does Tomb Tainted Soul.}
\end{list}\vspace*{8pt}

\ability{Hit Dice:}{d4}

\ability{Class Skills:}{The Uttercold Assault Necromancer's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Diplomacy (Cha), Knowledge (All Skills Individually) (Int), Profession (Wis), Sense Motive (Wis) and Spellcraft (Int).}

\ability{Skill Points/Level:}{2 + Int modifier}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+0 &+0 &+2 &Uttercold Assault!:20, Undead General, Rebuke Undead, Officer and a Gentleman, Undead Leadership &+1 spellcaster level\\
2nd &+1 &+0 &+0 &+3 &Necromantic Commander &+1 spellcaster level\\
3rd &+1 &+1 &+1 &+3 &Exceptional Leadership &+1 spellcaster level\\
4th &+2 &+1 &+1 &+4 &Uttercold Assault!: 30, Bonus Feat &+1 spellcaster level\\
5th &+2 &+1 &+1 &+4 &Elite Followers &+1 spellcaster level\\
6th &+3 &+2 &+2 &+5 &Rallying Cry &+1 spellcaster level\\
7th &+3 &+2 &+2 &+5 &Uttercold Assault!: 40, Bonus Feat &+1 spellcaster level\\
8th &+4 &+2 &+2 &+6 &Fearsome Charge &+1 spellcaster level\\
9th &+4 &+3 &+3 &+6 &Crush Them &+1 spellcaster level\\
10th &+5 &+3 &+3 &+7 &Uttercold Assault!: 50, Bonus Feat, Elite Followers &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Uttercold Assault Necromancer class.

\ability{Weapon and Armor Proficiency:}{The Uttercold Assault Necromancer gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Uttercold Assault Necromancer casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Unit:}{An Uttercold Assault Necromancer trains rigorously as part of an elite unit. For purposes of his class abilities, his ``unit" includes himself and all of his cohorts, followers, and apprentices, as well as any undead creature summoned, commanded, or controlled by members of his unit. Other characters (such as other PCs and hirelings) can train and become part of his unit if they are healed by negative energy.}

\ability{Uttercold Assault! (Su):}{All members of your unit within your Commander Aura (see Heroes of Battle, pg. 75, this is normally 30 ft.), all gain Cold Resistance: 20. At levels 4, 7 and 10 the cold resistance rises by an additional 10 points. Note that you still do not otherwise benefit from your own Commander Aura, you just get cold resistance.}

\ability{Undead General (Ex):}{Instead of skeletal warriors as undead followers, your undead followers have the \hyperref[undead:darkminded]{Dark Minded} subtype and levels in any class; ignore the Exceptional Followers rule from the Epic Handbook. These are ordinarily Human \hyperref[undead:swordwraith]{Swordwraith} \hyperref[class:fighter]{Fighters}, but other equivalent units may be substituted if apropos for the military organization you represent (the cannibal-hobbits of the Kankomar Foreign Legions are Ghoul-Halfling Rangers, for example).

Any morale bonuses, which you would otherwise provide from class features, commander auras, or spells, can be competence bonuses instead, at your discretion.

Undead can learn to savor victory, but death holds no fear for them. Your leadership score, when leading the undead, is not penalized when you suffer casualties. Casualties do penalize your leadership if you try to lead living followers, however.

Your apprentices do not penalize your leadership score when attracting undead cohorts.}

\ability{Rebuke Undead (Su):}{If an Uttercold Assault Necromancer already has the ability to rebuke/command undead, levels of Uttercold Assault Necromancer stack with levels in other classes to determine Rebuking Level. He gains no ability to rebuke undead if he does not already have it.}

\ability{Officer and a Gentleman (Ex):}{An Uttercold Assault Necromancer must conduct his villainous acts with restraint, good manners and aplomb. Your code of conduct includes the following:

\listone
    \item  Avoid harming innocents and civilians, when feasible.
    \item  Be courteous and dignified of bearing (and towards the opposite sex, gallant) at all times.
    \item  Graciously accept the surrender of a defeated foe, and treat them with decorum and respect, which means absolutely no torture.
    \item  Captured foes may not be summarily slain. You are permitted to test their worthiness by placing them in elaborate conditions almost certain to kill them, as long as those of sufficient character or cleverness might survive.
    \item  Always keep your word of honor.
\end{list}\vspace*{8pt}

You are also expected to ensure that all of your subordinates (``minions") obey this code, and to discipline them if they do not. Note that other ``dishonorable" actions, including attacks from ambush, torture of captured spies, and the use of poison, are perfectly permissible under your code. If you violate this code in a minor way (GM discretion) you lose all remaining usages of your Exceptional Leadership class ability for the day. Severe violations cause you to lose your Exceptional Leadership and Uttercold Assault! class features until you Atone. As long as you are known to keep to your code you are entitled to a +2 bonus to your Leadership score, stacking with other leadership bonuses.}

\ability{Undead Leadership (Ex):}{You gain Undead Leadership as a bonus feat, even if you do not meet the requirements. You will immediately ``attract" the largest unit of Undead followers that you can lead (see Undead General above). You must attract cohorts as normal. If you already have Undead Leadership, take a Bonus Feat (see the list below) instead.}

\ability{Necromantic Commander (Ex):}{At 2nd level, you gain the Necromantic Commander aura (see pg. 75 of Heroes of Battle,) in addition to your existing Commander Aura, even if you do not meet the requirements. Your followers benefit from both commander aura effects. If you already have Necromantic Commander as your aura, immediately select an additional aura for which you qualify.}

\ability{Exceptional Leadership (Ex):}{At 3rd level, you can exert Exceptional Leadership as an immediate action. A number of members of your unit equal to your class level gain these benefits until your next action: a +2 competence bonus to AC, will and reflex saves, as well as to-hit and damage rolls. The targets must all be within your command radius. If the targets are currently under an effect that requires a will save, they are allowed an immediate additional will save to break free (as Slippery Mind). The targets of this ability must be able to hear and see you in order to benefit from your commands. This is a mind-effecting ability. You can use this ability a number of times per day equal to your class level plus your charisma bonus (if positive). The benefits last one minute.}

\ability{Bonus Feat (Ex):}{At 4th level, select a bonus feat. You must meet the requirements normally. Bonus feats must be selected from the following list: Any Feat from Tome of Necromancy, Extra Turning, Lichloved, Sacrificial Mastery (BV), Arcane Disciple, Bonus Domain, Empower Turning, Profane Boost, Quicken Turning, Undead Mastery, Zone of Animation (CD), Any Leader feat, Veteran Knowledge (HoB). Note that Undead Leadership will substitute as a pre-requisite for feats requiring leadership.}

\ability{Elite Followers (Ex):}{All of your undead followers may have one more level than would ordinarily be allowed by your leadership score once you reach 5th level. For example, For example, if your leadership score is 21, you would ordinarily be allowed 60 1st level followers, you are allowed 60 2nd level followers instead. You must attract (or train, at GM discretion) these elite followers normally. At 10th level, this bonus increases to 2 levels. In addition, you automatically qualify as having Epic Leadership if your leadership score is 25 or more.}

\ability{Rallying Cry (Ex):}{At 6th level, you can rally your allies with a powerful shout as a free action. Doing so costs two uses of your Exceptional Leadership ability. Firstly, this enables you to perform a free rally check (Heroes of Battle, pg. 73), which is useful if you lead living troops. Secondly, your Commander Aura (Heroes of Battle, pg. 75) radius increases to 60 ft. and the benefits of your Commander Aura are doubled for a number of rounds equal to your class level + your charisma bonus. The increased radius applies to the energy resistance granted by your Uttercold Assault! class feature.}

\ability{Fearsome Charge (Ex):}{At 8th level, when you direct your forces into battle, your enemies quaver in terror. Calling for a fearsome charge is a swift action that requires four uses of your Exceptional Leadership ability. In addition to the benefits of a Rallying Cry (above), your unit retains the benefits of your commander aura when charging enemies outside of your commander aura. Any enemies charged by members of your unit when they began begin the charge move within your commander aura must make an immediate Morale check (a will save, see Heroes of Battle pg. 72), but the DC (instead of 20) is 10 + your class level + your charisma bonus. The modifiers on Heroes of Battle table 4-3 apply as normal. Any given unit of enemies cannot be forced to take more than one Morale Check from Fearsome Charge during any given battle, but further morale checks (from casualties, for example) may be called for.}

\ability{Crush Them (Ex):}{When an Uttercold Assault Necromancer of 9th level exerts Exceptional Leadership, he can expend three additional uses to give the nominated subordinates additional bonuses. In all cases, these benefits last only one turn. They may count any Shaken (or worse) opponent as flat-footed, and inflict +2d6 points of damage against them (treated as Sudden Strike damage, and stacks with Sudden Strike, Sneak Attack, etc. if any of those apply.)

They may count any Frightened or Panicked opponent as Helpless. The Necromancer's followers may coup de grace or grapple against such an opponent without provoking an attack of opportunity from enemies who are themselves at least Shaken. Note that under her Code of Conduct they are generally required to use this ability to order a grapple (capture) of any opponent who communicates a desire to surrender. Enemies who simply flee can be killed or captured, as desired.}
