\classname{Disciple of the Spirit Wave} \label{comm:prestige:disciplespiritwave}
\vspace*{-8pt}
\quot{``I won't hold back! I'll put everything into this one shot!"}

There are some who take up exercising and focusing their spirit in order to gain power, and the reasons power seek power are myriad. Whatever the reason, Spirit energy grows when exercised, just like muscles do--and Spirit energy isn't restrained by the strength of flesh and bone. 

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+5}
\itemability{Skills:}{Concentration 4 ranks}
\itemability{Feats:}{Iron Will or Great Fortitude, Ghost Hunter}
\itemability{Special:}{Fatal Strike or Improved Unarmed Strike}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Disciple of the Spirit Wave's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Diplomacy (Cha), Heal (Wis), Intimidate (Cha), Jump (Str), Knowledge (All) (Int), Listen (Wis), Move Silently (Dex), Sense Motive (Wis), Spot (Wis), Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+2&Spirit Energy, Spirit Boost, Spirit Ray\\
2&+2&+3&+3&+3&Strength Against Adversity\\
3&+3&+3&+3&+3&Spirit Multi-Ray, Improved Spirit Boost\\
4&+4&+4&+4&+4&Spirit Donation\\
5&+5&+4&+4&+4&Greater Spirit Boost\\
6&+6&+5&+5&+5&Spirit Wave, Spirit Mastery\\
7&+7&+5&+5&+5&Superior Spirit Boost\\
8&+8&+6&+6&+6&Improved Spirit Donation\\
9&+9&+6&+6&+6&Indomitable Spirit\\
10&+10&+7&+7&+7&Spirit Sun\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Disciple of the Spirit Wave class:

\ability{Weapon and Armor Proficiency:}{A Disciple of the Spirit Wave gains proficiency with no new weapons or armor.}

\ability{Spirit Energy (Su):}{The Disciple of the Spirit Wave gets a number of uses of Spirit Energy each day, equal to Class Level + (Higher of Con or Wisdom bonus). Uses of Spirit energy recover over time (one every hour Spirit Energy is not used). If he expends all his uses, he's drained until he gets 8 hours (or racial equivalent) of sleep.}

\ability{Spirit Boost (Su):}{The Disciple of the Spirit Wave immediately learns to use spirit energy to toughen up his body. He may spend a use of Spirit Energy as a free action to either reduce the damage he takes from any source, or to increase the damage he inflicts with unarmed strikes or natural weapons. This boost lasts for one round

He may reduce damage taken by 1 point for every rank in Concentration, or increase it by the same amount.

At 3rd level, his spirit is Improved, and he now can absorb or inflict 2 points per rank in Concentration. At 5th level, his spirit is Greater and absorbs or inflicts 3 points per rank in Concentration. At 7th level, his spirit is Superior, and absorbs or inflicts 4 ranks per rank in Concentration, and at level 9, his spirit is indomitable and each use of the spirit boost absorbs or inflict 5 points of damage per rank of Concentration.}

\ability{Spirit Ray (Su):}{The Disciple learns a simple, but effective, technique. By spending a full-round action, he may gather spirit energy into the tip of his index finger and release it as a focused ray. The Spirit Ray’s properties depend on a number of factors:}

\begin{itemize}
    \item{For every 4 ranks in concentration, the damage die increases (starting at d4 with 4 ranks of concentration)}
    \item{Range is Long.}
    \item{The number of damage die is equal to ranks in Concentration.}
    \item{It takes one use of his Spirit energy}
\end{itemize}

\ability{Strength Against Adversity (Su):}{The Spirit Wave responds to desperation and need by growing stronger. For every 5 HP of damage the Disciple takes, he gains back one use of Spirit Energy.}

\ability{Spirit Multi-Ray (Su):}{The Spirit Wave technique is very fluid, with sufficient practice. A Spirit Monk may fire a whole spray of Spirit Rays at once as a full-round action, affecting a 60-foot cone. Those within the cone take damage as if affected by a Spirit Ray with a step lower die (Reflex DC 10 + \half Character Level + Wis for half). This likewise takes one use of Spirit energy.}

\ability{Spirit Donation (Su):}{At 4th level, the Disciple learns to donate some of his spirit energy into others with a touch. If the recipient of the spirit energy is not a Disciple of the Spirit Wave, their bodies do not how to consciously focus the Spirit Energy, but respond it nonetheless by healing an amount equal to the Disciple's ranks in Concentration. If they are a Disciple, they get a use of Spirit Energy.

At 8th level, the Disciple has learned to turn his Spirit energy towards purifying others--a use of his Spirit Energy to cleanse another removes all afflictions, including curses, enchantments, level loss, ability score damage/drain, blindness/deafness, and disease; it's pretty much a cure-all. Also, his Spirit energy intensifies and when used to heal, it instead heals 4 points per rank in Concentration.}

\ability{Spirit Wave (Su):}{At 6th level, the Disciple has achieved the namesake technique of his path of power---the Spirit Wave. Rather than just a concentrated beam of Spirit energy from one point, the Disciple of the Spirit Wave emits flows and streams from all over his body. It can be used to make ranged touch attacks within short range which do damage a die size smaller than Spirit Ray (and as many attacks as the Disciple has attacks), but its real strength comes from adding its force to melee attacks.

When used with a successful melee attack, it does the same number and die size of damage as a Spirit Multi-Ray in addition to the damage from the attack. This also takes one use of his Spirit Energy. }

\ability{Spirit Mastery (Su):}{At 6th level, the Disciple of the Spirit Wave has learned to manage his energy more effectively. By using his abilities at substantially less than full power, their drain on his spirit energy is practically non-existent. He may use any of his abilities as if they were 4 levels lower, without expending a use of Spirit power.}

\ability{Spirit Sun (Su):}{The Disciple's Spirit energy is now akin to the blaze of the sun, and if he so chooses, he may pour some or all of his power into what he does. By using more than one use of Spirit Energy, the effects of his spirit techniques are multiplied by the number of uses expended. So, by expending two uses on a Spirit Ray, he does 36d10 damage rather than the usual 18d6. When used in conjunction with Spirit Boost or Spirit Donation, this multiplies the ranks in Concentration.}

\ability{Spirit Sun (Su):}{The Disciple's Spirit energy is now akin to the blaze of the sun, and if he so chooses, he may pour some or all of his power into what he does.
By using more than one use of Spirit Energy, he increases the power of what he's doing.}

\begin{itemize}
    \item{For each additional use expended on the Ray, Multi-Ray, or Spirit Wave, he does an extra three dice of damage.}
    \item{For Spirit Boost each additional use spent adds one point to the amount that can be blocked or inflicted per point of Concentration.}
    \item{For Spirit Donation, the amount healed by each point of Concentration likewise goes up by 1 for each additional use, and a use can be expended to purify someone (as per Improved Spirit Donation).}
\end{itemize}