%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How Combat Works}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Combat is cyclical; everybody acts in turn in a regular cycle of rounds. Combat 
follows this sequence:

\begin{enumerate}
\item Each combatant starts out flat-footed. Once a combatant acts, he or she is no 
longer flat-footed.
\item Determine which characters are aware of their opponents at the start of the 
battle. If some but not all of the combatants are aware of their opponents, a surprise 
round happens before regular rounds of combat begin. The combatants who are aware 
of the opponents can act in the surprise round, so they roll for initiative. In 
initiative order (highest to lowest), combatants who started the battle aware of 
their opponents each take one action (either a standard action or a move action) 
during the surprise round. Combatants who were unaware do not get to act in the 
surprise round. If no one or everyone starts the battle aware, there is no surprise 
round.
\item Combatants who have not yet rolled initiative do so. All combatants are now 
ready to begin their first regular round of combat.
\item Combatants act in initiative order (highest to lowest).
\item When everyone has had a turn, the combatant with the highest initiative acts 
again, and steps 4 and 5 repeat until combat ends.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combat Statisics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This section summarizes the statistics that determine success in combat, and then 
details how to use

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Attack Roll}
%%%%%%%%%%%%%%%%%%%%%%%%%

An attack roll represents your attempt to strike your opponent on your turn in 
a round. When you make an attack roll, you roll a d20 and add your attack bonus. 
(Other modifiers may also apply to this roll.) If your result equals or beats the 
target's Armor Class, you hit and deal damage.

\textbf{Automatic Misses and Hits:} A natural 1 (the d20 comes up 1) on an attack 
roll is always a miss. A natural 20 (the d20 comes up 20) is always a hit. A natural 
20 is also a threat -- a possible critical hit.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Attack Bonus}\index{Attack Bonus}
%%%%%%%%%%%%%%%%%%%%%%%%%

Your attack bonus with a melee weapon is:

Base attack bonus + Strength modifier + size modifier

With a ranged weapon, your attack bonus is:

Base attack bonus + Dexterity modifier + size modifier + range penalty

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Size Modifiers}
\centering
\begin{tabular}{l c l c}
\textbf{Size} & \textbf{Modifier} & \textbf{Size} & \textbf{Modifier} \\
Colossal & -8 & Small & +1\\
Gargantuan & -4 & Tiny & +2\\
Huge & -2 & Diminutive & +4\\
Large & -1 & Fine & +8\\
Medium & +0 & &\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Damage}
%%%%%%%%%%%%%%%%%%%%%%%%%

When your attack succeeds, you deal damage. The type of weapon used determines 
the amount of damage you deal. Effects that modify weapon damage apply to unarmed 
strikes and the natural physical attack forms of creatures.

Damage reduces a target's current hit points.

\textbf{\gameterm{Minimum Damage}:} If penalties reduce the damage result to less than 1, 
a hit still deals 1 point of damage.

Strength Bonus: When you hit with a melee or thrown weapon, including a sling, 
add your Strength modifier to the damage result. A Strength penalty, but not a 
bonus, applies on attacks made with a bow that is not a composite bow.

\textit{\gameterm{Off-Hand Weapon}:} When you deal damage with a weapon in your off hand, 
you add only 1/2 your Strength bonus.

\textit{Wielding a Weapon Two-Handed:} When you deal damage with a weapon that 
you are wielding two-handed, you add 1-1/2 times your Strength bonus. However, 
you don't get this higher Strength bonus when using a light weapon with two hands.

\textbf{Multiplying Damage:} Sometimes you multiply damage by some factor, such 
as on a critical hit. Roll the damage (with all modifiers) multiple times and total 
the results. \textit{Note:} When you multiply damage more than once, each multiplier 
works off the original, unmultiplied damage.

\textit{Exception:} Extra damage dice over and above a weapon's normal damage are 
never multiplied.

\textbf{Ability Damage:} Certain creatures and magical effects can cause temporary 
ability damage (a reduction to an ability score).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Armor Class}\index{Armor Class}
%%%%%%%%%%%%%%%%%%%%%%%%%

Your Armor Class (AC) represents how hard it is for opponents to land a solid, 
damaging blow on you. It's the attack roll result that an opponent needs to achieve 
to hit you. Your AC is equal to the following: 10 + armor bonus + shield bonus 
+ Dexterity modifier + size modifier

Note that armor limits your Dexterity bonus, so if you're wearing armor, you might 
not be able to apply your whole Dexterity bonus to your AC.

Sometimes you can't use your Dexterity bonus (if you have one). If you can't react 
to a blow, you can't use your Dexterity bonus to AC. (If you don't have a Dexterity 
bonus, nothing happens.)

Other Modifiers: Many other factors modify your AC.

\textit{\gameterm{Enhancement Bonuses}:} Enhancement effects make your armor better.

\textit{\gameterm{Deflection Bonus}:} Magical deflection effects ward off attacks and improve your AC.

\textit{\gameterm{Natural Armor}:} Natural armor improves your AC.

\textit{\gameterm{Dodge Bonuses}:} Some other AC bonuses represent actively avoiding blows. 
These bonuses are called dodge bonuses. Any situation that denies you your Dexterity 
bonus also denies you dodge bonuses. (Wearing armor, however, does not limit these 
bonuses the way it limits a Dexterity bonus to AC.) Unlike most sorts of bonuses, 
dodge bonuses stack with each other.

\textbf{\gameterm{Touch Attacks}:} Some attacks disregard armor, including shields and natural 
armor. In these cases, the attacker makes a touch attack roll (either ranged or 
melee). When you are the target of a touch attack, your AC doesn't include any 
armor bonus, shield bonus, or natural armor bonus. All other modifiers, such as 
your size modifier, Dexterity modifier, and deflection bonus (if any) apply normally.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hit Points}\index{Hit Points}
%%%%%%%%%%%%%%%%%%%%%%%%%

When your hit point total reaches 0, you're disabled. When it reaches -1, you're 
dying. When it gets to -10, you're dead.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Speed}\index{Speed}
%%%%%%%%%%%%%%%%%%%%%%%%%

Your speed tells you how far you can move in a round and still do something, such 
as attack or cast a spell. Your speed depends mostly on your race and what armor 
you're wearing.

Dwarves, gnomes, and halflings have a speed of 20 feet (4 squares), or 15 feet 
(3 squares) when wearing medium or heavy armor (except for dwarves, who move 20 
feet in any armor).

Humans, elves, half-elves, and half-orcs have a speed of 30 feet (6 squares), or 
20 feet (4 squares) in medium or heavy armor.

If you use two move actions in a round (sometimes called a "double move" action), 
you can move up to double your speed. If you spend the entire round to run all 
out, you can move up to quadruple your speed (or triple if you are in heavy armor).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Saving Throws}\index{Saving Throws}
%%%%%%%%%%%%%%%%%%%%%%%%%

Generally, when you are subject to an unusual or magical attack, you get a saving 
throw to avoid or reduce the effect. Like an attack roll, a saving throw is a d20 
roll plus a bonus based on your class, level, and an ability score. Your saving 
throw modifier is: Base save bonus + ability modifier 

\textbf{Saving Throw Types:} The three different kinds of saving throws are Fortitude, 
Reflex, and Will:

\textit{Fortitude:} These saves measure your ability to stand up to physical punishment 
or attacks against your vitality and health. Apply your Constitution modifier to 
your Fortitude saving throws. 

\textit{Reflex:} These saves test your ability to dodge area attacks. Apply your 
Dexterity modifier to your Reflex saving throws. 

\textit{Will:} These saves reflect your resistance to mental influence as well 
as many magical effects. Apply your Wisdom modifier to your Will saving throws.

\textbf{Saving Throw Difficulty Class:} The DC for a save is determined by the 
attack itself.

\textbf{Automatic Failures and Successes:} A natural 1 (the d20 comes up 1) on 
a saving throw is always a failure (and may cause damage to exposed items; see 
\linksec{Saving Throw Type}{Items Surviving after a Saving Throw}). A natural 20 (the d20 comes up 20) is always 
a success.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Initiative}\index{Initiative}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Initiative Checks:} At the start of a battle, each combatant makes an initiative 
check. An initiative check is a Dexterity check. Each character applies his or 
her Dexterity modifier to the roll. Characters act in order, counting down from 
highest result to lowest. In every round that follows, the characters act in the 
same order (unless a character takes an action that results in his or her initiative 
changing; see Special Initiative Actions).

If two or more combatants have the same initiative check result, the combatants 
who are tied act in order of total initiative modifier (highest first). If there 
is still a tie, the tied characters should roll again to determine which one of 
them goes before the other.

\textbf{\gameterm{Flat-Footed}:} At the start of a battle, before you have had a chance to 
act (specifically, before your first regular turn in the initiative order), you 
are flat-footed. You can't use your Dexterity bonus to AC (if any) while flat-footed. 
Barbarians and rogues have the uncanny dodge extraordinary ability, which allows 
them to avoid losing their Dexterity bonus to AC due to being flat-footed.

A flat-footed character can't make attacks of opportunity.

\textbf{Inaction:} Even if you can't take actions, you retain your initiative score 
for the duration of the encounter.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Surprise}\index{Surprise}
%%%%%%%%%%%%%%%%%%%%%%%%%

When a combat starts, if you are not aware of your opponents and they are aware 
of you, you're surprised.

%%%
\subsubsection{Determining Awareness}
%%%

Sometimes all the combatants on a side are aware of their opponents, sometimes 
none are, and sometimes only some of them are. Sometimes a few combatants on each 
side are aware and the other combatants on each side are unaware.

Determining awareness may call for \linkskill{Listen} checks, \linkskill{Spot} checks, or other checks.

\textbf{The Surprise Round:} If some but not all of the combatants are aware of 
their opponents, a surprise round happens before regular rounds begin. Any combatants 
aware of the opponents can act in the surprise round, so they roll for initiative. 
In initiative order (highest to lowest), combatants who started the battle aware 
of their opponents each take a standard action during the surprise round. You can 
also take free actions during the surprise round. If no one or everyone is surprised, 
no surprise round occurs.

\textbf{Unaware Combatants:} Combatants who are unaware at the start of battle 
don't get to act in the surprise round. Unaware combatants are flat-footed because 
they have not acted yet, so they lose any Dexterity bonus to AC.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Attacks of Opportunity}\index{Attacks of Opportunity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sometimes a combatant in a melee lets her guard down. In this case, combatants 
near her can take advantage of her lapse in defense to attack her for free. These 
free attacks are called attacks of opportunity.

\textbf{Threatened Squares:} You threaten all squares into which you can make a 
melee attack, even when it is not your action. Generally, that means everything 
in all squares adjacent to your space (including diagonally). An enemy that takes 
certain actions while in a threatened square provokes an attack of opportunity 
from you. If you're unarmed, you don't normally threaten any squares and thus can't 
make attacks of opportunity.

\textit{\gameterm{Reach Weapons}:} Most creatures of Medium or smaller size have a reach of 
only 5 feet. This means that they can make melee attacks only against creatures 
up to 5 feet (1 square) away. However, Small and Medium creatures wielding reach 
weapons threaten more squares than a typical creature. In addition, most creatures 
larger than Medium have a natural reach of 10 feet or more.

\textbf{Provoking an Attack of Opportunity:} Two kinds of actions can provoke attacks 
of opportunity: moving out of a threatened square and performing an action within 
a threatened square.

\textit{Moving:} Moving out of a threatened square usually provokes an attack of 
opportunity from the threatening opponent. There are two common methods of avoiding 
such an attack -- the 5-foot-step and the withdraw action (see below).

\textit{Performing a Distracting Act:} Some actions, when performed in a threatened 
square, provoke attacks of opportunity as you divert your attention from the battle. 
Table: Actions in Combat notes many of the actions that provoke attacks of opportunity.

Remember that even actions that normally provoke attacks of opportunity may have 
exceptions to this rule.

\textbf{Making an Attack of Opportunity:} An attack of opportunity is a single 
melee attack, and you can only make one per round. You don't have to make an attack 
of opportunity if you don't want to.

An experienced character gets additional regular melee attacks (by using the full 
attack action), but at a lower attack bonus. You make your attack of opportunity, 
however, at your normal attack bonus -- even if you've already attacked in the round.

An attack of opportunity "interrupts" the normal flow of actions in the round. 
If an attack of opportunity is provoked, immediately resolve the attack of opportunity, 
then continue with the next character's turn (or complete the current turn, if 
the attack of opportunity was provoked in the midst of a character's turn).

\textit{Combat Reflexes and Additional Attacks of Opportunity:} If you have the 
Combat Reflexes feat you can add your Dexterity modifier to the number of attacks 
of opportunity you can make in a round. This feat does not let you make more than 
one attack for a given opportunity, but if the same opponent provokes two attacks 
of opportunity from you, you could make two separate attacks of opportunity (since 
each one represents a different opportunity). Moving out of more than one square 
threatened by the same opponent in the same round doesn't count as more than one 
opportunity for that opponent. All these attacks are at your full normal attack 
bonus.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Actions in Combat}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Combat Round}
%%%%%%%%%%%%%%%%%%%%%%%%%

Each round represents 6 seconds in the game world. A round presents an opportunity 
for each character involved in a combat situation to take an action. 

Each round's activity begins with the character with the highest initiative result 
and then proceeds, in order, from there. Each round of a combat uses the same initiative 
order. When a character's turn comes up in the initiative sequence, that character 
performs his entire round's worth of actions. (For exceptions, see Attacks of Opportunity 
and Special Initiative Actions.)

For almost all purposes, there is no relevance to the end of a round or the beginning 
of a round. A round can be a segment of game time starting with the first character 
to act and ending with the last, but it usually means a span of time from one round 
to the same initiative count in the next round. Effects that last a certain number 
of rounds end just before the same initiative count that they began on.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Action Types}
%%%%%%%%%%%%%%%%%%%%%%%%%

An action's type essentially tells you how long the action takes to perform (within 
the framework of the 6-second combat round) and how movement is treated. There 
are four types of actions: standard actions, move actions, full-round actions, 
and free actions.

In a normal round, you can perform a standard action and a move action, or you 
can perform a full-round action. You can also perform one or more free actions. 
You can always take a move action in place of a standard action.

In some situations (such as in a surprise round), you may be limited to taking 
only a single move action or standard action.

\textbf{\gameterm{Standard Action}:} A standard action allows you to do something, most commonly 
make an attack or cast a spell. See Table: Actions in Combat for other standard 
actions.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Standard Actions In Combat}
\centering
\begin{tabular}{l c l c}
\textbf{Standard Action} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Attack (melee) & No\\
Attack (ranged) & Yes\\
Attack (unarmed) & Yes\\
Activate a magic item other than a potion or oil & No\\
Aid another & Maybe\textsuperscript{2}\\
Bull rush & Yes\\
Cast a spell (1 standard action casting time) & Yes\\
Concentrate to maintain an active spell & No\\
Dismiss a spell & No\\
Draw a hidden weapon (see Sleight of Hand skill) & No\\
Drink a potion or apply an oil & Yes\\
Escape a grapple & No\\
Feint & No\\
Light a torch with a tindertwig & Yes\\
Lower spell resistance & No\\
Make a dying friend stable (see Heal skill) & Yes\\
Overrun & No\\
Read a scroll & Yes\\
Ready (triggers a standard action) & No\\
Sunder a weapon (attack) & Yes\\
Sunder an object (attack) & Maybe\textsuperscript{3}\\
Total defense & No\\
Turn or rebuke undead & No\\
Use extraordinary ability & No\\
Use skill that takes 1 action & Usually\\
Use spell-like ability & Yes\\
Use supernatural ability & No\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{1} Regardless of the action, if you move out of a threatened square, you usually provoke an attack of opportunity. This column indicates whether the action itself, not moving, provokes an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{2} If you aid someone performing an action that would normally provoke an attack of opportunity, then the act of aiding another provokes an attack of opportunity as well.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{3} If the object is being held, carried, or worn by a creature, yes. If not, no.}\\
\end{tabular}
\end{table}

\textbf{\gameterm{Move Action}:} A move action allows you to move your speed or perform an 
action that takes a similar amount of time. See Table: Actions in Combat.

You can take a move action in place of a standard action. If you move no actual 
distance in a round (commonly because you have swapped your move for one or more 
equivalent actions), you can take one 5-foot step either before, during, or after 
the action.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Move Actions In Combat}
\centering
\begin{tabular}{l c l c}
\textbf{Move Action} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Move & Yes\\
Control a frightened mount & Yes\\
Direct or redirect an active spell & No\\
Draw a weapon\textsuperscript{4} & No\\
Load a hand crossbow or light crossbow & Yes\\
Open or close a door & No\\
Mount a horse or dismount & No\\
Move a heavy object & Yes\\
Pick up an item & Yes\\
Sheathe a weapon & Yes\\
Stand up from prone & Yes\\
Ready or loose a shield\textsuperscript{4} & No\\
Retrieve a stored item & Yes\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{1} Regardless of the action, if you move out of a threatened square, you usually provoke an attack of opportunity. This column indicates whether the action itself, not moving, provokes an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{4} If you have a base attack bonus of +1 or higher, you can combine one of these actions with a regular move. If you have the \linkfeat{Two-Weapon Fighting} feat, you can draw two light or one-handed weapons in the time it would normally take you to draw one.}\\
\end{tabular}
\end{table}

\textbf{\gameterm{Full-Round Action}:} A full-round action consumes all your effort during 
a round. The only movement you can take during a full-round action is a 5-foot 
step before, during, or after the action. You can also perform free actions (see 
below).

Some full-round actions do not allow you to take a 5-foot step.

Some full-round actions can be taken as standard actions, but only in situations 
when you are limited to performing only a standard action during your round. The 
descriptions of specific actions, below, detail which actions allow this option.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Full-Round Actions In Combat}
\centering
\begin{tabular}{l c l c}
\textbf{Full-Round Action} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Full attack & No\\
Charge\textsuperscript{5} & No\\
Deliver coup de grace & Yes\\
Escape from a net & Yes\\
Extinguish flames & No\\
Light a torch & Yes\\
Load a heavy or repeating crossbow & Yes\\
Lock or unlock weapon in locked gauntlet & Yes\\
Prepare to throw splash weapon & Yes\\
Run & Yes\\
Use skill that takes 1 round & Usually\\
Use touch spell on up to six friends & Yes\\
Withdraw\textsuperscript{5} & No\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{1} Regardless of the action, if you move out of a threatened square, you usually provoke an attack of opportunity. This column indicates whether the action itself, not moving, provokes an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{5} May be taken as a standard action if you are limited to taking only a single action in a round.}\\
\end{tabular}
\end{table}

\textbf{\gameterm{Swift Action}:} A swift action consumes a very small amount of time, but 
represents a larger expenditure of effort and energy than a free action. You can 
perform one swift action per turn without affecting your ability to perform other 
actions. In that regard, a swift action is like a free action. However, you can 
perform only a single swift action per turn, regardless of what other actions you 
take. You can take a swift action any time you would normally be allowed to take 
a free action.

Casting a \linkfeat{Quicken Spell}{Quickened} spell is a swift action. In addition, casting any spell 
with a casting time of 1 swift action is a swift action.

Casting a spell with a casting time of 1 swift action does not provoke 
attacks of opportunity. 

\textbf{\gameterm{Immediate Action}:} Much like a swift action, an immediate action consumes 
a very small amount of time, but represents a larger expenditure of effort and 
energy than a free action. However, unlike a swift action, an immediate action 
can be performed at any time -- even if it's not your turn. Using an immediate action 
on your turn is the same as using a swift action, and counts as your swift action 
for that turn. You cannot use another immediate action or a swift action until 
after your next turn if you have used an immediate action when it is not currently 
your turn (effectively, using an immediate action before your turn is equivalent 
to using your swift action for the coming turn). You also cannot use an immediate 
action if you are currently flat-footed.

\textbf{\gameterm{Free Action}:} Free actions consume a very small amount of time and effort. 
You can perform one or more free actions while taking another action normally. 
However, there are reasonable limits on what you can really do for free.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Free Actions In Combat}
\centering
\begin{tabular}{l c l c}
\textbf{Free Action} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Cease concentration on a spell & No\\
Drop an item & No\\
Drop to the floor & No\\
Prepare spell components to cast a spell\textsuperscript{6} & No\\
Speak & No\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{1} Regardless of the action, if you move out of a threatened square, you usually provoke an attack of opportunity. This column indicates whether the action itself, not moving, provokes an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{6} Unless the component is an extremely large or awkward item.}\\
\end{tabular}
\end{table}

\textbf{Not an Action:} Some activities are so minor that they are not even considered 
free actions. They literally don't take any time at all to do and are considered 
an inherent part of doing something else.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{Other Actions In Combat}
\centering
\begin{tabular}{l c l c}
\textbf{Non-Action} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Delay & No\\
5-foot step & No\\
\textbf{Action Type Varies} & \textbf{Attack of Opportunity\textsuperscript{1}}\\
Disarm\textsuperscript{7} & Yes\\
Grapple\textsuperscript{7} & Yes\\
Trip an opponent\textsuperscript{7} & Yes\\
Use feat\textsuperscript{8} & Varies\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{1} Regardless of the action, if you move out of a threatened square, you usually provoke an attack of opportunity. This column indicates whether the action itself, not moving, provokes an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{7} These attack forms substitute for a melee attack, not an action. As melee attacks, they can be used once in an attack or charge action, one or more times in a full attack action, or even as an attack of opportunity.}\\
\multicolumn{2}{p{12.5cm}}{\textsuperscript{8} The description of a feat defines its effect.}\\
\end{tabular}
\end{table}

\textbf{Restricted Activity:} In some situations, you may be unable to take a full 
round's worth of actions. In such cases, you are restricted to taking only a single 
standard action or a single move action (plus free actions as normal). You can't 
take a full-round action (though you can start or complete a full-round action 
by using a standard action; see below).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Standard Actions}\index{Standard Action}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{Attack}\index{Attacking}
%%%

Making an attack is a standard action.

\textbf{Melee Attacks:} With a normal melee weapon, you can strike any opponent 
within 5 feet. (Opponents within 5 feet are considered adjacent to you.) Some melee 
weapons have reach, as indicated in their descriptions. With a typical reach weapon, 
you can strike opponents 10 feet away, but you can't strike adjacent foes (those 
within 5 feet).

\textbf{Unarmed Attacks:} Striking for damage with punches, kicks, and head butts 
is much like attacking with a melee weapon, except for the following:

\textit{Attacks of Opportunity:} Attacking unarmed provokes an attack of opportunity 
from the character you attack, provided she is armed. The attack of opportunity 
comes before your attack. An unarmed attack does not provoke attacks of opportunity 
from other foes nor does it provoke an attack of opportunity from an unarmed foe.

An unarmed character can't take attacks of opportunity (but see "Armed" Unarmed 
Attacks, below).

\textit{"Armed" Unarmed Attacks:} Sometimes a character's or creature's unarmed 
attack counts as an armed attack. A monk, a character with the Improved Unarmed 
Strike feat, a spellcaster delivering a touch attack spell, and a creature with 
natural physical weapons all count as being armed.

Note that being armed counts for both offense and defense (the character can make 
attacks of opportunity)

\textit{Unarmed Strike Damage:}\index{Unarmed Strike} An unarmed strike from a Medium character deals 
1d3 points of damage (plus your Strength modifier, as normal). A Small character's 
unarmed strike deals 1d2 points of damage, while a Large character's unarmed strike 
deals 1d4 points of damage. All damage from unarmed strikes is nonlethal damage. 
Unarmed strikes count as light weapons (for purposes of two-weapon attack penalties 
and so on).

\textit{Dealing Lethal Damage:} You can specify that your unarmed strike will deal 
lethal damage before you make your attack roll, but you take a -4 penalty on your 
attack roll. If you have the Improved Unarmed Strike feat, you can deal lethal 
damage with an unarmed strike without taking a penalty on the attack roll.

\textbf{Ranged Attacks:} With a ranged weapon, you can shoot or throw at any target 
that is within the weapon's maximum range and in line of sight. The maximum range 
for a thrown weapon is five range increments. For projectile weapons, it is ten 
range increments. Some ranged weapons have shorter maximum ranges, as specified 
in their descriptions.

\textbf{Attack Rolls:} An attack roll represents your attempts to strike your opponent. 

Your attack roll is 1d20 + your attack bonus with the weapon you're using. If the 
result is at least as high as the target's AC, you hit and deal damage.

\textbf{Automatic Misses and Hits:} A natural 1 (the d20 comes up 1) on the attack 
roll is always a miss. A natural 20 (the d20 comes up 20) is always a hit. A natural 
20 is also a threat -- a possible critical hit.

\textbf{Damage Rolls:} If the attack roll result equals or exceeds the target's 
AC, the attack hits and you deal damage. Roll the appropriate damage for your weapon. 
Damage is deducted from the target's current hit points.

\textbf{Multiple Attacks:} A character who can make more than one attack per round 
must use the full attack action (see Full-Round Actions, below) in order to get 
more than one attack.

\textbf{Shooting or Throwing into a Melee:}\index{Firing Into Melee} If you shoot or throw a ranged weapon 
at a target engaged in melee with a friendly character, you take a -4 penalty on 
your attack roll. Two characters are engaged in melee if they are enemies of each 
other and either threatens the other. (An unconscious or otherwise immobilized 
character is not considered engaged unless he is actually being attacked.)

If your target (or the part of your target you're aiming at, if it's a big target) 
is at least 10 feet away from the nearest friendly character, you can avoid the 
-4 penalty, even if the creature you're aiming at is engaged in melee with a friendly 
character.

\textit{Precise Shot:} If you have the \linkfeat{Precise Shot} feat you don't take this penalty.

\textbf{\gameterm{Fighting Defensively} as a Standard Action:} You can choose to fight defensively 
when attacking. If you do so, you take a -4 penalty on all attacks in a round to 
gain a +2 dodge bonus to AC for the same round.

\textbf{\gameterm{Critical Hits}:} When you make an attack roll and get a natural 20 (the 
d20 shows 20), you hit regardless of your target's Armor Class, and you have scored 
a threat. The hit might be a critical hit (or "crit"). To find out if it's a 
critical hit, you immediately make a critical roll -- another attack roll with all 
the same modifiers as the attack roll you just made. If the critical roll also 
results in a hit against the target's AC, your original hit is a critical hit. 
(The critical roll just needs to hit to give you a crit. It doesn't need to come 
up 20 again.) If the critical roll is a miss, then your hit is just a regular hit.

A critical hit means that you roll your damage more than once, with all your usual 
bonuses, and add the rolls together. Unless otherwise specified, the threat range 
for a critical hit on an attack roll is 20, and the multiplier is x2.

\textit{Exception:} Extra damage over and above a weapon's normal damage 
is not multiplied when you score a critical hit.

\textit{Increased Threat Range:}\index{Threat Range} Sometimes your threat range is greater 
than 20. That is, you can score a threat on a lower number. In such cases, a roll 
of lower than 20 is not an automatic hit. Any attack roll that doesn't result in 
a hit is not a threat.

\textit{Increased Critical Multiplier:}\index{Critical Multiplier} Some weapons deal better than 
double damage on a critical hit.

\textit{Spells and Critical Hits:} A spell that requires an attack roll
can score a critical hit. A spell attack that requires no attack roll
cannot score a critical hit.

%%%
\subsubsection{Cast a Standard Action Spell}\index{Spellcasting}
%%%

Most spells require 1 standard action to cast. You can cast such a spell either 
before or after you take a move action. 

\textit{Note:} You retain your Dexterity bonus to AC while casting.

\textbf{\gameterm{Spell Components}:} To cast a spell with a verbal (V) component, your character 
must speak in a firm voice. If you're gagged or in the area of a \linkspell{Silence}
spell, you can't cast such a spell. A spellcaster who has been deafened has a 
20\% chance to spoil any spell he tries to cast if that spell has a verbal component.

To cast a spell with a somatic (S) component, you must gesture freely with at least 
one hand. You can't cast a spell of this type while bound, grappling, or with both 
your hands full or occupied.

To cast a spell with a material (M), focus (F), or divine focus (DF) component, 
you have to have the proper materials, as described by the spell. Unless these 
materials are elaborate preparing these materials is a free action. For 
material components and focuses whose costs are not listed, you can assume that 
you have them if you have your spell component pouch.

Some spells have an experience point (XP) component and entail an experience point 
cost to you. No spell can restore the lost XP. You cannot spend so much XP that 
you lose a level, so you cannot cast the spell unless you have enough XP to spare. 
However, you may, on gaining enough XP to achieve a new level, immediately spend 
the XP on casting the spell rather than keeping it to advance a level. The XP are 
expended when you cast the spell, whether or not the casting succeeds.

\textbf{Concentration:} You must concentrate to cast a spell. If you can't concentrate 
you can't cast a spell. If you start casting a spell but something interferes with 
your concentration you must make a Concentration check or lose the spell. The check's 
DC depends on what is threatening your concentration (see the Concentration skill). 
If you fail, the spell fizzles with no effect. If you prepare spells, it is lost 
from preparation. If you cast at will, it counts against your daily limit of spells 
even though you did not cast it successfully.

\textbf{Concentrating to Maintain a Spell:} Some spells require continued concentration 
to keep them going. Concentrating to maintain a spell is a standard action that 
doesn't provoke an attack of opportunity. Anything that could break your concentration 
when casting a spell can keep you from concentrating to maintain a spell. If your 
concentration breaks, the spell ends.

\textbf{Casting Time:} Most spells have a casting time of 1 standard action. A 
spell cast in this manner immediately takes effect.

\textbf{Attacks of Opportunity:} Generally, if you cast a spell, you provoke attacks 
of opportunity from threatening enemies. If you take damage from an attack of opportunity, 
you must make a Concentration check (DC 10 + points of damage taken + spell level) 
or lose the spell. Spells that require only a free action to cast don't provoke 
attacks of opportunity.

\textbf{Casting on the Defensive:}\index{Casting Defensively} Casting a spell while on the defensive does 
not provoke an attack of opportunity. It does, however, require a Concentration 
check (DC 15 + spell level) to pull off. Failure means that you lose the spell.

\textbf{Touch Spells in Combat:} Many spells have a range of touch. To use these 
spells, you cast the spell and then touch the subject, either in the same round 
or any time later. In the same round that you cast the spell, you may also touch 
(or attempt to touch) the target. You may take your move before casting the spell, 
after touching the target, or between casting the spell and touching the target. 
You can automatically touch one friend or use the spell on yourself, but to touch 
an opponent, you must succeed on an attack roll.

\textit{Touch Attacks:} Touching an opponent with a touch spell is considered to 
be an armed attack and therefore does not provoke attacks of opportunity. However, 
the act of casting a spell does provoke an attack of opportunity. Touch attacks 
come in two types: melee touch attacks and ranged touch attacks. You can score 
critical hits with either type of attack. Your opponent's AC against a touch attack 
does not include any armor bonus, shield bonus, or natural armor bonus. His size 
modifier, Dexterity modifier, and deflection bonus (if any) all apply normally.

\textit{Holding the Charge:} If you don't discharge the spell in the round when 
you cast the spell, you can hold the discharge of the spell (hold the charge) indefinitely. 
You can continue to make touch attacks round after round. You can touch one friend 
as a standard action or up to six friends as a full-round action. If you touch 
anything or anyone while holding a charge, even unintentionally, the spell discharges. 
If you cast another spell, the touch spell dissipates. Alternatively, you may make 
a normal unarmed attack (or an attack with a natural weapon) while holding a charge. 
In this case, you aren't considered armed and you provoke attacks of opportunity 
as normal for the attack. (If your unarmed attack or natural weapon attack doesn't 
provoke attacks of opportunity, neither does this attack.) If the attack hits, 
you deal normal damage for your unarmed attack or natural weapon and the spell 
discharges. If the attack misses, you are still holding the charge.

\textbf{Dismiss a Spell:} Dismissing an active spell is a standard action that 
doesn't provoke attacks of opportunity.

%%%
\subsubsection{Activate Magic Item}
%%%

Many magic items don't need to be activated. However, certain magic items need 
to be activated, especially potions, scrolls, wands, rods, and staffs. Activating 
a magic item is a standard action (unless the item description indicates otherwise).

\textbf{\gameterm{Spell Completion Items}:} Activating a spell completion item is the equivalent 
of casting a spell. It requires concentration and provokes attacks of opportunity. 
You lose the spell if your concentration is broken, and you can attempt to activate 
the item while on the defensive, as with casting a spell.

\textbf{Spell Trigger\index{Spell Trigger Items}, Command Word\index{Command Word Items},
or \gameterm{Use-Activated Items}:} Activating any of 
these kinds of items does not require concentration and does not provoke attacks 
of opportunity.

%%%
\subsubsection{Use Standard Action Special Ability}
%%%

Using a special ability is usually a standard action, but whether it is a standard 
action, a full-round action, or not an action at all is defined by the ability.

\textbf{Spell-Like Abilities:}\index{Spell-Like Ability} Using a spell-like ability works like casting a 
spell in that it requires concentration and provokes attacks of opportunity. Spell-like 
abilities can be disrupted. If your concentration is broken, the attempt to use 
the ability fails, but the attempt counts as if you had used the ability. The casting 
time of a spell-like ability is 1 standard action, unless the ability description 
notes otherwise.

\textit{Using a Spell-Like Ability on the Defensive:} You may attempt to use a 
spell-like ability on the defensive, just as with casting a spell. If the Concentration 
check (DC 15 + spell level) fails, you can't use the ability, but the attempt counts 
as if you had used the ability.

\textbf{Supernatural Abilities:}\index{Supernatural Ability} Using a supernatural ability is usually a standard 
action (unless defined otherwise by the ability's description). Its use cannot 
be disrupted, does not require concentration, and does not provoke attacks of opportunity.

\textbf{Extraordinary Abilities:}\index{Extraordinary Ability} Using an extraordinary ability is usually not 
an action because most extraordinary abilities automatically happen in a reactive 
fashion. Those extraordinary abilities that are actions are usually standard actions 
that cannot be disrupted, do not require concentration, and do not provoke attacks 
of opportunity.

%%%
\subsubsection{Total Defense}\index{Total Defense}
%%%

You can defend yourself as a standard action. You get a +4 dodge bonus to your 
AC for 1 round. Your AC improves at the start of this action. You can't combine 
total defense with fighting defensively or with the benefit of the Combat Expertise 
feat (since both of those require you to declare an attack or full attack). You 
can't make attacks of opportunity while using total defense.

%%%
\subsubsection{Start/Complete Full-Round Action}
%%%

The "start full-round action" standard action lets you start undertaking a full-round 
action, which you can complete in the following round by using another standard 
action. You can't use this action to start or complete a full attack, charge, run, 
or withdraw.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Move Actions}\index{Move Action}
%%%%%%%%%%%%%%%%%%%%%%%%%

With the exception of specific movement-related skills, most move actions don't 
require a check.

%%%
\subsubsection{Move}\index{Movement}
%%%

The simplest move action is moving your speed. If you take this kind of move action 
during your turn, you can't also take a 5-foot step.

Many nonstandard modes of movement are covered under this category, including climbing 
(up to one-quarter of your speed) and swimming (up to one-quarter of your speed).

\textbf{Accelerated Climbing:} You can climb one-half your speed as a move action 
by accepting a -5 penalty on your Climb check.

\textbf{Crawling:}\index{Crawling} You can crawl 5 feet as a move action. Crawling incurs attacks 
of opportunity from any attackers who threaten you at any point of your crawl.

%%%
\subsubsection{Draw or Sheathe a Weapon}
%%%

Drawing a weapon so that you can use it in combat, or putting it away so that you 
have a free hand, requires a move action. This action also applies to weapon-like 
objects carried in easy reach, such as wands. If your weapon or weapon-like object 
is stored in a pack or otherwise out of easy reach, treat this action as retrieving 
a stored item.

If you have a base attack bonus of +1 or higher, you may draw a weapon as a free 
action combined with a regular move. If you have the Two-Weapon Fighting feat, 
you can draw two light or one-handed weapons in the time it would normally take 
you to draw one.

Drawing ammunition for use with a ranged weapon (such as arrows, bolts, sling bullets, 
or shuriken) is a free action.

%%%
\subsubsection{Ready or Loose a Shield}
%%%

Strapping a shield to your arm to gain its shield bonus to your AC, or unstrapping 
and dropping a shield so you can use your shield hand for another purpose, requires 
a move action. If you have a base attack bonus of +1 or higher, you can ready or 
loose a shield as a free action combined with a regular move.

Dropping a carried (but not worn) shield is a free action.

%%%
\subsubsection{Manipulate an Item}
%%%

In most cases, moving or manipulating an item is a move action.

This includes retrieving or putting away a stored item, picking up an item, moving 
a heavy object, and opening a door. Examples of this kind of action, along with 
whether they incur an attack of opportunity, are given in Table: Actions in Combat.

%%%
\subsubsection{Direct or Redirect a Spell}
%%%

Some spells allow you to redirect the effect to new targets or areas after 
you cast the spell. Redirecting a spell requires a move action and does not provoke 
attacks of opportunity or require concentration.

%%%
\subsubsection{Stand Up}\index{Stand Up}
%%%

Standing up from a prone position requires a move action and provokes attacks of 
opportunity.

%%%
\subsubsection{Mount/Dismount a Steed}
%%%

Mounting or dismounting from a steed requires a move action.

\textbf{Fast Mount or Dismount:} You can mount or dismount as a free action with 
a DC 20 Ride check (your armor check penalty, if any, applies to this check). If 
you fail the check, mounting or dismounting is a move action instead. (You can't 
attempt a fast mount or fast dismount unless you can perform the mount or dismount 
as a move action in the current round.)

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Full-Round Actions}\index{Full-Round Action}
%%%%%%%%%%%%%%%%%%%%%%%%%

A full-round action requires an entire round to complete. Thus, it can't be coupled 
with a standard or a move action, though if it does not involve moving any distance, 
you can take a 5-foot step.

%%%
\subsubsection{Full Attack}\index{Full Attack}
%%%

If you get more than one attack per round because your base attack bonus is high 
enough, because you fight with two weapons or a double weapon, or for some special 
reason, you must use a full-round action to get your additional attacks. You do 
not need to specify the targets of your attacks ahead of time. You can see how 
the earlier attacks turn out before assigning the later ones.

The only movement you can take during a full attack is a 5-foot step. You may take 
the step before, after, or between your attacks.

If you get multiple attacks because your base attack bonus is high enough, you 
must make the attacks in order from highest bonus to lowest. If you are using two 
weapons, you can strike with either weapon first. If you are using a double weapon, 
you can strike with either part of the weapon first.

\textbf{Deciding between an Attack or a Full Attack:} After your first attack, 
you can decide to take a move action instead of making your remaining attacks, 
depending on how the first attack turns out. If you've already taken a 5-foot step, 
you can't use your move action to move any distance, but you could still use a 
different kind of move action.

\textbf{\gameterm{Fighting Defensively} as a Full-Round Action:} You can choose to fight defensively 
when taking a full attack action. If you do so, you take a -4 penalty on all attacks 
in a round to gain a +2 dodge bonus to AC for the same round.

\textbf{Cleave:} The extra attack granted by the \linkfeat{Cleave} feat or \linkfeat{Great Cleave} feat 
can be taken whenever they apply. This is an exception to the normal limit to the 
number of attacks you can take when not using a full attack action.

%%%
\subsubsection{Cast a 1 Round Spell}
%%%

A spell that takes 1 round to cast is a full-round action. It comes into effect 
just before the beginning of your turn in the round after you began casting the 
spell. You then act normally after the spell is completed.

A spell that takes 1 minute to cast comes into effect just before your turn 1 minute 
later (and for each of those 10 rounds, you are casting a spell as a full-round 
action). These actions must be consecutive and uninterrupted, or the spell automatically 
fails.

When you begin a spell that takes 1 round or longer to cast, you must continue 
the invocations, gestures, and concentration from one round to just before your 
turn in the next round (at least). If you lose concentration after starting the 
spell and before it is complete, you lose the spell.

You only provoke attacks of opportunity when you begin casting a spell, even though 
you might continue casting for at least one full round. While casting a spell, 
you don't threaten any squares around you.

This action is otherwise identical to the cast a spell action described under Standard 
Actions.

\textbf{Casting a Metamagic Spell:} Sorcerers and bards must take more time to 
cast a metamagic spell (one enhanced by a metamagic feat) than a regular spell. 
If a spell's normal casting time is 1 standard action, casting a metamagic version 
of the spell is a full-round action for a sorcerer or bard. Note that this isn't 
the same as a spell with a 1-round casting time -- the spell takes effect in the 
same round that you begin casting, and you aren't required to continue the invocations, 
gestures, and concentration until your next turn. For spells with a longer casting 
time, it takes an extra full-round action to cast the metamagic spell.

Clerics must take more time to spontaneously cast a metamagic version of a \textit{cure}
or \textit{inflict} spell. Spontaneously casting a metamagic version 
of a spell with a casting time of 1 standard action is a full-round action, and 
spells with longer casting times take an extra full-round action to cast.

%%%
\subsubsection{Use Full-Round Special Ability}
%%%

Using a special ability is usually a standard action, but some may be full-round 
actions, as defined by the ability.

%%%
\subsubsection{Withdraw}\index{Withdraw}
%%%

Withdrawing from melee combat is a full-round action. When you withdraw, you can 
move up to double your speed. The square you start out in is not considered threatened 
by any opponent you can see, and therefore visible enemies do not get attacks of 
opportunity against you when you move from that square. (Invisible enemies still 
get attacks of opportunity against you, and you can't withdraw from combat if you're 
blinded.) You can't take a 5-foot step during the same round in which you withdraw.

If, during the process of withdrawing, you move out of a threatened square (other 
than the one you started in), enemies get attacks of opportunity as normal.

You may not withdraw using a form of movement for which you don't have a listed 
speed. 

Note that despite the name of this action, you don't actually have to leave combat 
entirely.

\textbf{Restricted Withdraw:} If you are limited to taking only a standard action 
each round you can withdraw as a standard action. In this case, you may move up 
to your speed (rather than up to double your speed).

%%%
\subsubsection{Run}\index{Running}
%%%

You can run as a full-round action. (If you do, you do not also get a 5-foot step.) 
When you run, you can move up to four times your speed in a straight line (or three 
times your speed if you're in heavy armor). You lose any Dexterity bonus to AC 
unless you have the Run feat 

You can run for a number of rounds equal to your Constitution score, but after 
that you must make a DC 10 Constitution check to continue running. You must check 
again each round in which you continue to run, and the DC of this check increases 
by 1 for each check you have made. When you fail this check, you must stop running. 
A character who has run to his limit must rest for 1 minute (10 rounds) before 
running again. During a rest period, a character can move no faster than a normal 
move action.

You can't run across difficult terrain or if you can't see where you're going.

A run represents a speed of about 12 miles per hour for an unencumbered human.

%%%
\subsubsection{Move 5 Feet through Difficult Terrain}
%%%

In some situations, your movement may be so hampered that you don't have sufficient 
speed even to move 5 feet (a single square). In such a case, you may spend a full-round 
action to move 5 feet (1 square) in any direction, even diagonally. Even though 
this looks like a 5-foot step, it's not, and thus it provokes attacks of opportunity 
normally.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Free Actions}\index{Free Action}
%%%%%%%%%%%%%%%%%%%%%%%%%

Free actions don't take any time at all, though there may be limits to the number 
of free actions you can perform in a turn. Free actions rarely incur attacks of 
opportunity. Some common free actions are described below.

%%%
\subsubsection{Drop an Item}
%%%

Dropping an item in your space or into an adjacent square is a free action.

%%%
\subsubsection{Drop Prone}
%%%

Dropping to a prone position in your space is a free action.

%%%
\subsubsection{Speak}
%%%

In general, speaking is a free action that you can perform even when it isn't your 
turn. Speaking more than few sentences is generally beyond the limit of a free 
action.

%%%
\subsubsection{Cease Concentration on Spell}
%%%

You can stop concentrating on an active spell as a free action.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Swift Actions}\index{Swift Action}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{Cast a Quickened Spell}
%%%

You can cast a quickened spell (see the \linkfeat{Quicken Spell} feat) or any spell whose 
casting time is designated as a free action as a free action. Only one such spell 
can be cast in any round, and such spells don't count toward your normal limit 
of one spell per round. Casting a spell with a casting time of a free action doesn't 
incur an attack of opportunity.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Miscellaneous Actions}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
\subsubsection{Take 5-Foot Step}\index{5ft Step}
%%%

You can move 5 feet in any round when you don't perform any other kind of movement. 
Taking this 5-foot step never provokes an attack of opportunity. You can't take 
more than one 5-foot step in a round, and you can't take a 5-foot step in the same 
round when you move any distance.

You can take a 5-foot step before, during, or after your other actions in the round. 

You can only take a 5-foot-step if your movement isn't hampered by difficult terrain 
or darkness. Any creature with a speed of 5 feet or less can't take a 5-foot step, 
since moving even 5 feet requires a move action for such a slow creature.

You may not take a 5-foot step using a form of movement for which you do not have 
a listed speed. 

%%%
\subsubsection{Use Feat}
%%%

Certain feats let you take special actions in combat. Other feats do not require 
actions themselves, but they give you a bonus when attempting something you can 
already do. Some feats are not meant to be used within the framework of combat. 
The individual feat descriptions tell you what you need to know about them.

%%%
\subsubsection{Use Skill}
%%%

Most skill uses are standard actions, but some might be move actions, full-round 
actions, free actions, swift actions, or non-actions.

The individual skill descriptions tell you what sorts of actions are required to 
perform skills.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Injury and Death}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Your hit points measure how hard you are to kill. No matter how many hit points 
you lose, your character isn't hindered in any way until your hit points drop to 
0 or lower.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Loss of Hit Points}
%%%%%%%%%%%%%%%%%%%%%%%%%

The most common way that your character gets hurt is to take lethal damage and 
lose hit points

\textbf{What Hit Points Represent:} Hit points mean two things in the game world: 
the ability to take physical punishment and keep going, and the ability to turn 
a serious blow into a less serious one.

\textbf{Effects of Hit Point Damage:} Damage doesn't slow you down until your current 
hit points reach 0 or lower. At 0 hit points, you're disabled.

At from -1 to -9 hit points, you're dying.

At -10 or lower, you're dead.

\textbf{\gameterm{Massive Damage}:} If you ever sustain a single attack deals 50 points of 
damage or more and it doesn't kill you outright, you must make a DC 15 Fortitude 
save. If this saving throw fails, you die regardless of your current hit points. 
If you take 50 points of damage or more from multiple attacks, no one of which 
dealt 50 or more points of damage itself, the massive damage rule does not apply.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Disabled (0 Hit Points)}\index{Disabled}
%%%%%%%%%%%%%%%%%%%%%%%%%

When your current hit points drop to exactly 0, you're disabled.

You can only take a single move or standard action each turn (but not both, nor 
can you take full-round actions). You can take move actions without further injuring 
yourself, but if you perform any standard action (or any other strenuous action) 
you take 1 point of damage after the completing the act. Unless your activity increased 
your hit points, you are now at -1 hit points, and you're dying.

Healing that raises your hit points above 0 makes you fully functional again, just 
as if you'd never been reduced to 0 or fewer hit points.

You can also become disabled when recovering from dying. In this case, it's a step 
toward recovery, and you can have fewer than 0 hit points (see
\linksec{Stable Characters and Recovery},below).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dying (-1 to -9 Hit Points)}\index{Dying}
%%%%%%%%%%%%%%%%%%%%%%%%%

When your character's current hit points drop to between -1 and -9 inclusive, he's 
dying.

A dying character immediately falls unconscious and can take no actions.

A dying character loses 1 hit point every round. This continues until the character 
dies or becomes stable (see below).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Dead (-10 Hit Points or lower)}\index{Dead}
%%%%%%%%%%%%%%%%%%%%%%%%%

When your character's current hit points drop to -10 or lower, or if he takes massive 
damage (see \linksec{Loss of Hit Points}{above}), he's dead. A character can also die from taking ability damage 
or suffering an ability drain that reduces his Constitution to 0.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stable Characters and Recovery}\index{Stabilization}
%%%%%%%%%%%%%%%%%%%%%%%%%

On the next turn after a character is reduced to between -1 and -9 hit points and 
on all subsequent turns, roll d\% to see whether the dying character becomes stable. 
He has a 10\% chance of becoming stable. If he doesn't, he loses 1 hit point. (A 
character who's unconscious or dying can't use any special action that changes 
the initiative count on which his action occurs.)

If the character's hit points drop to -10 or lower, he's dead.

You can keep a dying character from losing any more hit points and make him stable 
with a DC 15 \linkskill{Heal} check.

If any sort of healing cures the dying character of even 1 point of damage, he 
stops losing hit points and becomes stable.

Healing that raises the dying character's hit points to 0 makes him conscious and 
disabled. Healing that raises his hit points to 1 or more makes him fully functional 
again, just as if he'd never been reduced to 0 or lower. A spellcaster retains 
the spellcasting capability she had before dropping below 0 hit points.

A stable character who has been tended by a healer or who has been magically healed 
eventually regains consciousness and recovers hit points naturally. If the character 
has no one to tend him, however, his life is still in danger, and he may yet slip 
away.

\textbf{Recovering with Help:} One hour after a tended, dying character becomes 
stable, roll d\%. He has a 10\% chance of becoming conscious, at which point he 
is disabled (as if he had 0 hit points). If he remains unconscious, he has the 
same chance to revive and become disabled every hour. Even if unconscious, he recovers 
hit points naturally. He is back to normal when his hit points rise to 1 or higher.

\textbf{Recovering without Help:} A severely wounded character left alone usually 
dies. He has a small chance, however, of recovering on his own. 

A character who becomes stable on his own (by making the 10\% roll while dying) 
and who has no one to tend to him still loses hit points, just at a slower rate. 
He has a 10\% chance each hour of becoming conscious. Each time he misses his hourly 
roll to become conscious, he loses 1 hit point. He also does not recover hit points 
through natural healing.

Even once he becomes conscious and is disabled, an unaided character still does 
not recover hit points naturally. Instead, each day he has a 10\% chance to start 
recovering hit points naturally (starting with that day); otherwise, he loses 1 
hit point.

Once an unaided character starts recovering hit points naturally, he is no longer 
in danger of naturally losing hit points (even if his current hit point total is 
negative).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Healing}\index{Healing Damage}
%%%%%%%%%%%%%%%%%%%%%%%%%

After taking damage, you can recover hit points through natural healing or through 
magical healing. In any case, you can't regain hit points past your full normal 
hit point total.

\textbf{Natural Healing:} With a full night's rest (8 hours of sleep or more), 
you recover 1 hit point per character level. Any significant interruption during 
your rest prevents you from healing that night.

If you undergo complete bed rest for an entire day and night, you recover twice 
your character level in hit points. 

\textbf{Magical Healing:} Various abilities and spells can restore hit points.

\textbf{Healing Limits:} You can never recover more hit points than you lost. Magical 
healing won't raise your current hit points higher than your full normal hit point 
total.

\textbf{Healing Ability Damage:} Ability damage is temporary, just as hit point 
damage is. Ability damage returns at the rate of 1 point per night of rest (8 hours) 
for each affected ability score. Complete bed rest restores 2 points per day (24 
hours) for each affected ability score.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Temporary Hit Points}\index{Temporary Hit Points}
%%%%%%%%%%%%%%%%%%%%%%%%%

Certain effects give a character temporary hit points. When a character gains temporary 
hit points, note his current hit point total. When the temporary hit points go 
away the character's hit points drop to his current hit point total. If the character's 
hit points are below his current hit point total at that time, all the temporary 
hit points have already been lost and the character's hit point total does not 
drop further.

When temporary hit points are lost, they cannot be restored as real hit points 
can be, even by magic.

\textbf{Increases in Constitution Score and Current Hit Points:} An increase in 
a character's Constitution score, even a temporary one, can give her more hit points 
(an effective hit point increase), but these are not temporary hit points. They 
can be restored and they are not lost first as temporary hit points are.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nonlethal Damage}\index{Nonlethal Damage}
%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Dealing Nonlethal Damage:} Certain attacks deal nonlethal damage. Other 
effects, such as heat or being exhausted, also deal nonlethal damage. When you 
take nonlethal damage, keep a running total of how much you've accumulated. \textit{Do 
not deduct the nonlethal damage number from your current hit points.} It is not 
"real" damage. Instead, when your nonlethal damage equals your current hit points, 
you're staggered, and when it exceeds your current hit points, you fall unconscious. 
It doesn't matter whether the nonlethal damage equals or exceeds your current hit 
points because the nonlethal damage has gone up or because your current hit points 
have gone down.

\textit{Nonlethal Damage with a Weapon that Deals Lethal Damage:} You can use a 
melee weapon that deals lethal damage to deal nonlethal damage instead, but you 
take a -4 penalty on your attack roll.

\textit{Lethal Damage with a Weapon that Deals Nonlethal Damage:} You can use a 
weapon that deals nonlethal damage, including an unarmed strike, to deal lethal 
damage instead, but you take a -4 penalty on your attack roll.

\textbf{\gameterm{Staggered} and Unconscious:} When your nonlethal damage equals your current 
hit points, you're staggered. You can only take a standard action or a move action 
in each round. You cease being staggered when your current hit points once again 
exceed your nonlethal damage.

When your nonlethal damage exceeds your current hit points, you fall unconscious. 
While unconscious, you are helpless.

Spellcasters who fall unconscious retain any spellcasting ability they had before 
going unconscious.

\textbf{Healing Nonlethal Damage:} You heal nonlethal damage at the rate of 1 hit 
point per hour per character level.

When a spell or a magical power cures hit point damage, it also removes an equal 
amount of nonlethal damage.
