%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conditions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If more than one condition affects a character, apply them all. If certain effects 
can't combine, apply the most severe effect.

%%%
\subsubsection{Ability Damaged}\index{Ability Damage}
%%%

The character has temporarily lost 1 or more ability 
score points. Lost points return at a rate of 1 per day unless noted otherwise 
by the condition dealing the damage. A character with Strength 0 falls to the ground 
and is helpless. A character with Dexterity 0 is paralyzed. A character with Constitution 
0 is dead. A character with Intelligence, Wisdom, or Charisma 0 is unconscious. 
Ability damage is different from penalties to ability scores, which go away when 
the conditions causing them go away.

%%%
\subsubsection{Ability Drained}\index{Ability Drain}
%%%

The character has permanently lost 1 or more ability 
score points. The character can regain these points only through magical means. 
A character with Strength 0 falls to the ground and is helpless. A character with 
Dexterity 0 is paralyzed. A character with Constitution 0 is dead. A character 
with Intelligence, Wisdom, or Charisma 0 is unconscious. 

%%%
\subsubsection{Blinded}\index{Blind}
%%%

The character cannot see. He takes a -2 penalty to Armor Class, 
loses his Dexterity bonus to AC (if any), moves at half speed, and takes a -4 penalty 
on \linkskill{Search} checks and on most Strength- and Dexterity-based skill checks. All checks 
and activities that rely on vision (such as reading and \linkskill{Spot} checks) automatically 
fail. All opponents are considered to have total concealment (50\% miss chance) 
to the blinded character. Characters who remain blinded for a long time grow accustomed 
to these drawbacks and can overcome some of them.

%%%
\subsubsection{Blown Away}\index{Blown Away}
%%%

Depending on its size, a creature can be blown away by winds 
of high velocity. A creature on the ground that is blown away is knocked down and 
rolls 1d4 x 10 feet, taking 1d4 points of nonlethal damage per 10 feet. A flying 
creature that is blown away is blown back 2d6 x 10 feet and takes 2d6 points of 
nonlethal damage due to battering and buffering. 

%%%
\subsubsection{Checked}\index{Checked}
%%%

Prevented from achieving forward motion by an applied force, 
such as wind. Checked creatures on the ground merely stop. Checked flying creatures 
move back a distance specified in the description of the effect.

%%%
\subsubsection{Confused}\index{Confused}
%%%

A confused character's actions are 
determined by rolling d\% at the beginning of his turn: 01-10, attack caster with 
melee or ranged weapons (or close with caster if attacking is not possible); 11-20, 
act normally; 21-50, do nothing but babble incoherently; 51-70, flee away from 
caster at top possible speed; 71-100, attack nearest creature (for this purpose, 
a familiar counts as part of the subject's self). A confused character 
who can't carry out the indicated action does nothing but babble incoherently. 
Attackers are not at any special advantage when attacking a confused character. 
Any confused character who is attacked automatically attacks its attackers 
on its next turn, as long as it is still confused when its turn comes. 
A confused character does not make attacks of opportunity against any 
creature that it is not already devoted to attacking (either because of its most 
recent action or because it has just been attacked).

%%%
\subsubsection{Cowering}\index{Cowering}
%%%

The character is frozen in fear and can take no actions. A cowering 
character takes a -2 penalty to Armor Class and loses her Dexterity bonus (if any).

%%%
\subsubsection{Dazed}\index{Dazed}
%%%

The creature is unable to act normally. A dazed creature can take 
no actions, but has no penalty to AC.

A dazed condition typically lasts 1 round.

%%%
\subsubsection{Dazzled}\index{Dazzled}
%%%

The creature is unable to see well because of overstimulation 
of the eyes. A dazzled creature takes a -1 penalty on attack rolls, \linkskill{Search} checks, 
and \linkskill{Spot} checks.

%%%
\subsubsection{Dead}\index{Dead}
%%%

The character's hit points are reduced to -10, his Constitution 
drops to 0, or he is killed outright by a spell or effect. The character's soul 
leaves his body. Dead characters cannot benefit from normal or magical healing, 
but they can be restored to life via magic. A dead body decays normally unless 
magically preserved, but magic that restores a dead character to life also restores 
the body either to full health or to its condition at the time of death (depending 
on the spell or device). Either way, resurrected characters need not worry about 
rigor mortis, decomposition, and other conditions that affect dead bodies.

%%%
\subsubsection{Deafened}\index{Deafened}
%%%

A deafened character cannot hear. She takes a -4 penalty on 
initiative checks, automatically fails \linkskill{Listen} checks, and has a 20\% chance of 
spell failure when casting spells with verbal components. Characters who remain 
deafened for a long time grow accustomed to these drawbacks and can overcome some 
of them.

%%%
\subsubsection{Disabled}\index{Disabled}
%%%

A character with 0 hit points, or one who has negative hit points 
but has become stable and conscious, is disabled. A disabled character may take 
a single move action or standard action each round (but not both, nor can she take 
full-round actions). She moves at half speed. Taking move actions doesn't risk 
further injury, but performing any standard action (or any other action the DM 
deems strenuous, including some free actions such as casting a quickened spell) 
deals 1 point of damage after the completion of the act. Unless the action increased 
the disabled character's hit points, she is now in negative hit points and dying.

A disabled character with negative hit points recovers hit points naturally if 
she is being helped. Otherwise, each day she has a 10\% chance to start recovering 
hit points naturally (starting with that day); otherwise, she loses 1 hit point. 
Once an unaided character starts recovering hit points naturally, she is no longer 
in danger of losing hit points (even if her current hit points are negative).

%%%
\subsubsection{Dying}\index{Dying}
%%%

A dying character is unconscious and near death. She has -1 to 
-9 current hit points. A dying character can take no actions and is unconscious. 
At the end of each round (starting with the round in which the character dropped 
below 0 hit points), the character rolls d\% to see whether she becomes stable. 
She has a 10\% chance to become stable. If she does not, she loses 1 hit point. 
If a dying character reaches -10 hit points, she is dead.

%%%
\subsubsection{Energy Drained}\index{Energy Drain}
%%%

The character gains one or more negative levels, which 
might permanently drain the character's levels. If the subject has at least as 
many negative levels as Hit Dice, he dies. Each negative level gives a creature 
the following penalties: -1 penalty on attack rolls, saving throws, skill checks, 
ability checks; loss of 5 hit points; and -1 to effective level (for determining 
the power, duration, DC, and other details of spells or special abilities). In 
addition, a spellcaster loses one spell or spell slot from the highest spell level 
castable.

%%%
\subsubsection{Entangled}\index{Entangled}
%%%

The character is ensnared. Being entangled impedes movement, 
but does not entirely prevent it unless the bonds are anchored to an immobile object 
or tethered by an opposing force. An entangled creature moves at half speed, cannot 
run or charge, and takes a -2 penalty on all attack rolls and a -4 penalty to Dexterity. 
An entangled character who attempts to cast a spell must make a Concentration check 
(DC 15 + the spell's level) or lose the spell. 

%%%
\subsubsection{Exhausted}\index{Exhausted}
%%%

An exhausted character moves at half speed and takes a -6 penalty 
to Strength and Dexterity. After 1 hour of complete rest, an exhausted character 
becomes fatigued. A fatigued character becomes exhausted by doing something else 
that would normally cause fatigue.

%%%
\subsubsection{Fascinated}\index{Fascinated}
%%%

A fascinated creature is entranced by a supernatural or spell 
effect. The creature stands or sits quietly, taking no actions other than to pay 
attention to the fascinating effect, for as long as the effect lasts. It takes 
a -4 penalty on skill checks made as reactions, such as \linkskill{Listen} and \linkskill{Spot} checks. 
Any potential threat, such as a hostile creature approaching, allows the fascinated 
creature a new saving throw against the fascinating effect. Any obvious threat, 
such as someone drawing a weapon, casting a spell, or aiming a ranged weapon at 
the fascinated creature, automatically breaks the effect. A fascinated creature's 
ally may shake it free of the spell as a standard action. 

%%%
\subsubsection{Fatigued}\index{Fatigued}
%%%

A fatigued character can neither run nor charge and takes a 
-2 penalty to Strength and Dexterity. Doing anything that would normally cause 
fatigue causes the fatigued character to become exhausted. After 8 hours of complete 
rest, fatigued characters are no longer fatigued. 

%%%
\subsubsection{Flat-Footed}\index{Flat-Footed}
%%%

A character who has not yet acted during a combat is flat-footed, 
not yet reacting normally to the situation. A flat-footed character loses his Dexterity 
bonus to AC (if any) and cannot make attacks of opportunity. 

%%%
\subsubsection{Frightened}\index{Frightened}
%%%

A frightened creature flees from the source of its fear as 
best it can. If unable to flee, it may fight. A frightened creature takes a -2 
penalty on all attack rolls, saving throws, skill checks, and ability checks. A 
frightened creature can use special abilities, including spells, to flee; indeed, 
the creature must use such means if they are the only way to escape. 

Frightened is like shaken, except that the creature must flee if possible.
\linksec{Panicked} is a more extreme state of fear.

%%%
\subsubsection{Grappling}\index{Grappling}
%%%

Engaged in wrestling or some other form of hand-to-hand struggle 
with one or more attackers. A grappling character can undertake only a limited 
number of actions. He does not threaten any squares, and loses his Dexterity bonus 
to AC (if any) against opponents he isn't grappling.

%%%
\subsubsection{Helpless}\index{Helpless}
%%%

A helpless character is paralyzed, \textit{held}, bound, sleeping, 
unconscious, or otherwise completely at an opponent's mercy. A helpless target 
is treated as having a Dexterity of 0 (-5 modifier). Melee attacks against a helpless 
target get a +4 bonus (equivalent to attacking a prone target). Ranged attacks 
gets no special bonus against helpless targets. Rogues can sneak attack helpless 
targets. 

As a full-round action, an enemy can use a melee weapon to deliver a coup de grace 
to a helpless foe. An enemy can also use a bow or crossbow, provided he is adjacent 
to the target. The attacker automatically hits and scores a critical hit. (A rogue 
also gets her sneak attack damage bonus against a helpless foe when delivering 
a coup de grace.) If the defender survives, he must make a Fortitude save (DC 10 
+ damage dealt) or die. 

Delivering a \gameterm{Coup de Grace} provokes attacks of opportunity. 

Creatures that are immune to critical hits do not take critical damage, nor do 
they need to make Fortitude saves to avoid being killed by a coup de grace.

%%%
\subsubsection{Incorporeal}\index{Incorporeal}
%%%

Having no physical body. Incorporeal creatures are immune 
to all nonmagical attack forms. They can be harmed only by other incorporeal creatures, 
+1 or better magic weapons, spells, spell-like effects, or supernatural effects. 

%%%
\subsubsection{Invisible}\index{Invisible}
%%%

Visually undetectable. An invisible creature gains a +2 bonus 
on attack rolls against sighted opponents, and ignores its opponents' Dexterity 
bonuses to AC (if any). (See \linksec{Invisibility}, under Special Abilities.)

%%%
\subsubsection{Knocked Down}\index{Knocked Down}
%%%

Depending on their size, creatures can be knocked down by 
winds of high velocity. Creatures on the ground are knocked prone by the force 
of the wind. Flying creatures are instead blown back 1d6 x 10 feet.

%%%
\subsubsection{Nauseated}\index{Nauseated}
%%%

Experiencing stomach distress. Nauseated creatures are unable 
to attack, cast spells, concentrate on spells, or do anything else requiring attention. 
The only action such a character can take is a single move action per turn.

%%%
\subsubsection{Panicked}\index{Panicked}
%%%

A panicked creature must drop anything it holds and flee at 
top speed from the source of its fear, as well as any other dangers it encounters, 
along a random path. It can't take any other actions. In addition, the creature 
takes a -2 penalty on all saving throws, skill checks, and ability checks. If cornered, 
a panicked creature cowers and does not attack, typically using the total defense 
action in combat. A panicked creature can use special abilities, including spells, 
to flee; indeed, the creature must use such means if they are the only way to escape.

Panicked is a more extreme state of fear than \linksec{Shaken} or \linksec{Frightened}.

%%%
\subsubsection{Paralyzed}\index{Paralyzed}
%%%

A paralyzed character is frozen in place and unable to move 
or act. A paralyzed character has effective Dexterity and Strength scores of 0 
and is helpless, but can take purely mental actions. A winged creature flying in 
the air at the time that it becomes paralyzed cannot flap its wings and falls. 
A paralyzed swimmer can't swim and may drown. A creature can move through a space 
occupied by a paralyzed creature -- ally or not. Each square occupied by a paralyzed 
creature, however, counts as 2 squares.

%%%
\subsubsection{Petrified}\index{Petrified}
%%%

A petrified character has been turned to stone and is considered 
unconscious. If a petrified character cracks or breaks, but the broken pieces are 
joined with the body as he returns to flesh, he is unharmed. If the character's 
petrified body is incomplete when it returns to flesh, the body is likewise incomplete 
and there is some amount of permanent hit point loss and/or debilitation.

%%%
\subsubsection{Pinned}\index{Pinned}
%%%

Held immobile (but not helpless) in a grapple.

%%%
\subsubsection{Prone}\index{Prone}
%%%

The character is on the ground. An attacker who is prone has a 
-4 penalty on melee attack rolls and cannot use a ranged weapon (except for a crossbow). 
A defender who is prone gains a +4 bonus to Armor Class against ranged attacks, 
but takes a -4 penalty to AC against melee attacks.

Standing up is a move-equivalent action that provokes an attack of opportunity.

%%%
\subsubsection{Shaken}\index{Shaken}
%%%

A shaken character takes a -2 penalty on attack rolls, saving 
throws, skill checks, and ability checks.

Shaken is a less severe state of fear than \linksec{Frightened} or \linksec{Panicked}.

%%%
\subsubsection{Sickened}\index{Sickened}
%%%

The character takes a -2 penalty on all attack rolls, weapon 
damage rolls, saving throws, skill checks, and ability checks.

%%%
\subsubsection{Stable}\index{Stable}
%%%

A character who was dying but who has stopped losing hit points 
and still has negative hit points is stable. The character is no longer dying, 
but is still unconscious. If the character has become stable because of aid from 
another character (such as a \linkskill{Heal} check or magical healing), then the character 
no longer loses hit points. He has a 10\% chance each hour of becoming conscious 
and disabled (even though his hit points are still negative). 

If the character became stable on his own and hasn't had help, he is still at risk 
of losing hit points. Each hour, he has a 10\% chance of becoming conscious and 
disabled. Otherwise he loses 1 hit point.

%%%
\subsubsection{Staggered}\index{Staggered}
%%%

A character whose nonlethal damage exactly equals his current 
hit points is staggered. A staggered character may take a single move action or 
standard action each round (but not both, nor can she take full-round actions).

A character whose current hit points exceed his nonlethal damage is no longer staggered; 
a character whose nonlethal damage exceeds his hit points becomes unconscious.

%%%
\subsubsection{Stunned}\index{Stunned}
%%%

A stunned creature drops everything held, can't take actions, 
takes a -2 penalty to AC, and loses his Dexterity bonus to AC (if any).

%%%
\subsubsection{Turned}\index{Turned}
%%%

Affected by a turn undead attempt. Turned undead flee for 10 rounds 
(1 minute) by the best and fastest means available to them. If they cannot flee, 
they cower.

%%%
\subsubsection{Unconscious}\index{Unconscious}
%%%

Knocked out and helpless. Unconsciousness can result from 
having current hit points between -1 and -9, or from nonlethal damage in excess 
of current hit points.
