%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Special Ability Descriptions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A special ability is either extraordinary, spell-like, or supernatural in nature.

\textbf{Extraordinary Abilities (Ex):}\index{Extraordinary Ability} Extraordinary abilities are nonmagical. 
They are, however, not something that just anyone can do or even learn to do without 
extensive training. Effects or areas that negate or disrupt magic have no effect 
on extraordinary abilities.

\textbf{Spell-Like Abilities (Sp):}\index{Spell-Like Ability} Spell-like abilities, as the name implies, 
are spells and magical abilities that are very much like spells. Spell-like abilities 
are subject to spell resistance and \linkspell{Dispel Magic}. They do not function 
in areas where magic is suppressed or negated (such as an \linkspell{Antimagic Field}).

\textbf{Supernatural Abilities (Su):}\index{Supernatural Ability} Supernatural abilities are magical but not 
spell-like. Supernatural abilities are not subject to spell resistance and do not 
function in areas where magic is suppressed or negated (such as an \textit{Antimagic Field}).
A supernatural ability's effect cannot be dispelled and is not subject 
to counterspells. See the table below for a summary of the types of special abilities.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Special Ability Types}
\centering
\begin{tabular}{l c c c}
 & \textbf{Extraordinary} & \textbf{Spell-Like} & \textbf{Supernatural}\\
Dispel & No & Yes & No\\
Spell Resistance & No & Yes & No\\
Antimagic Field & No & Yes & Yes\\
Attack of Opportunity & No & Yes & No\\
\end{tabular}
\end{table}

\textit{Dispel:} Can \linkspell{Dispel Magic} and similar spells dispel the effects of abilities of this type?

\textit{Spell Resistance:} Does spell resistance protect a creature from these abilities?

\textit{Antimagic Field:} Does an \linkspell{Antimagic Field} or similar magic suppress the ability?

\textit{Attack of Opportunity:} Does using the ability provoke attacks of opportunity the way casting a spell does?

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ability Score Loss}\index{Ability Score Loss}
%%%%%%%%%%%%%%%%%%%%%%%%%

Various attacks cause ability score loss, either ability damage or ability drain. 
Points lost to ability damage return at the rate of 1 point per day (or double 
that if the character gets complete bed rest) to each damaged ability, and the 
spells \linkspell{Lesser Restoration} and \linkspell{Restoration} offset ability damage 
as well. Ability drain, however, is permanent, though \textit{Restoration} can 
restore even those lost ability score points.

While any loss is debilitating, losing all points in an ability score can be devastating.

\begin{itemize*}
\item Strength 0 means that the character cannot move at all. He lies helpless on the ground.
\item Dexterity 0 means that the character cannot move at all. He stands motionless, rigid, and helpless.
\item Constitution 0 means that the character is dead.
\item Intelligence 0 means that the character cannot think and is unconscious in a coma-like stupor, helpless.
\item Wisdom 0 means that the character is withdrawn into a deep sleep filled with nightmares, helpless.
\item Charisma 0 means that the character is withdrawn into a catatonic, coma-like stupor, helpless.
\end{itemize*}

Keeping track of negative ability score points is never necessary. A character's 
ability score can't drop below 0.

Having a score of 0 in an ability is different from having no ability score whatsoever.

Some spells or abilities impose an effective ability score reduction, which is 
different from ability score loss. Any such reduction disappears at the end of 
the spell's or ability's duration, and the ability score immediately returns to 
its former value.

If a character's Constitution score drops, then he loses 1 hit point per Hit Die 
for every point by which his Constitution modifier drops. A hit point score can't 
be reduced by Constitution damage or drain to less than 1 hit point per Hit Die.

The ability that some creatures have to drain ability scores is a supernatural 
one, requiring some sort of attack. Such creatures do not drain abilities from 
enemies when the enemies strike them, even with unarmed attacks or natural weapons.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Antimagic}\index{Antimagic}
%%%%%%%%%%%%%%%%%%%%%%%%%

An \linkspell{Antimagic Field} spell or effect cancels magic altogether. An antimagic 
effect has the following powers and characteristics.

\begin{itemize*}
\item No supernatural ability, spell-like ability, or spell works in an area of antimagic (but extraordinary abilities still work).
\item Antimagic does not dispel magic; it suppresses it. Once a magical effect is no longer affected by the antimagic (the antimagic fades, the center of the effect moves away, and so on), the magic returns. Spells that still have part of their duration left begin functioning again, magic items are once again useful, and so forth.
\item Spell areas that include both an antimagic area and a normal area, but are not centered in the antimagic area, still function in the normal area. If the spell's center is in the antimagic area, then the spell is suppressed.
\item Golems and other constructs, elementals, outsiders, and corporeal undead, still function in an antimagic area (though the antimagic area suppresses their spellcasting and their supernatural and spell-like abilities normally). If such creatures are summoned or conjured, however, see below. 
\item Summoned or conjured creatures of any type, as well as incorporeal undead, wink out if they enter the area of an antimagic effect. They reappear in the same spot once the field goes away.
\item Magic items with continuous effects do not function in the area of an antimagic effect, but their effects are not canceled (so the contents of a \textit{Bag of Holding} are unavailable, but neither spill out nor disappear forever).
\item Two antimagic areas in the same place do not cancel each other out, nor do they stack.
\item \linkspell{Wall of Force}, \linkspell{Prismatic Wall}, and \linkspell{Prismatic Sphere} are not affected by antimagic. \linkspell{Break Enchantment}, \linkspell{Dispel Magic}, and \linkspell{Greater Dispel Magic} spells do not dispel antimagic. \linkspell{Mage's Disjunction} has a 1\% chance per caster level of destroying an \textit{Antimagic Field}. If the \textit{Antimagic Field} survives the \textit{Disjunction}, no items within it are disjoined.
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Blindsight and Blindsense}\index{Blindsight}\index{Blindsense}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some creatures have blindsight, the extraordinary ability to use a nonvisual sense 
(or a combination of such senses) to operate effectively without vision. Such sense 
may include sensitivity to vibrations, acute scent, keen hearing, or echolocation. 
This ability makes invisibility and concealment (even magical darkness) irrelevant 
to the creature (though it still can't see ethereal creatures). This ability operates 
out to a range specified in the creature description.

\begin{itemize*}
\item Blindsight never allows a creature to distinguish color or visual contrast. A creature cannot read with blindsight.
\item Blindsight does not subject a creature to gaze attacks (even though darkvision does).
\item Blinding attacks do not penalize creatures using blindsight. 
\item Deafening attacks thwart blindsight if it relies on hearing.
\item Blindsight works underwater but not in a vacuum.
\item Blindsight negates displacement and blur effects.
\end{itemize*}

\textbf{Blindsense:} Other creatures have blindsense, a lesser ability that lets 
the creature notice things it cannot see, but without the precision of blindsight. 
The creature with blindsense usually does not need to make Spot or Listen checks 
to notice and locate creatures within range of its blindsense ability, provided 
that it has line of effect to that creature. Any opponent the creature cannot see 
has total concealment (50\% miss chance) against the creature with blindsense, 
and the blindsensing creature still has the normal miss chance when attacking foes 
that have concealment. Visibility still affects the movement of a creature with 
blindsense. A creature with blindsense is still denied its Dexterity bonus to Armor 
Class against attacks from creatures it cannot see.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Breath Weapon}\index{Breath Weapon}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature attacking with a breath weapon is actually expelling something from 
its mouth (rather than conjuring it by means of a spell or some other magical effect). 
Most creatures with breath weapons are limited to a number of uses per day or by 
a minimum length of time that must pass between uses. Such creatures are usually 
smart enough to save their breath weapon until they really need it.

\begin{itemize*}
\item Using a breath weapon is typically a standard action.
\item No attack roll is necessary. The breath simply fills its stated area.
\item Any character caught in the area must make the appropriate saving throw or suffer the breath weapon's full effect. In many cases, a character who succeeds on his saving throw still takes half damage or some other reduced effect.
\item Breath weapons are supernatural abilities except where noted.
\item Creatures are immune to their own breath weapons.
\item Creatures unable to breathe can still use breath weapons. (The term is something of a misnomer.)
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Charm and Compulsion}\index{Charm}\index{Compulsion}
%%%%%%%%%%%%%%%%%%%%%%%%%

Many abilities and spells can cloud the minds of characters and monsters, leaving 
them unable to tell friend from foe -- or worse yet, deceiving them into thinking 
that their former friends are now their worst enemies. Two general types of enchantments 
affect characters and creatures: charms and compulsions.

Charming another creature gives the charming character the ability to befriend 
and suggest courses of actions to his minion, but the servitude is not absolute 
or mindless. Charms of this type include the various \textit{charm} spells. Essentially, 
a \textit{charmed} character retains free will but makes choices according to a 
skewed view of the world.

\begin{itemize*}
\item A \textit{charmed} creature doesn't gain any magical ability to understand his new friend's language.
\item A \textit{charmed} character retains his original alignment and allegiances, generally with the exception that he now regards the \textit{charming} creature as a dear friend and will give great weight to his suggestions and directions.
\item A \textit{charmed} character fights his former allies only if they threaten his new friend, and even then he uses the least lethal means at his disposal as long as these tactics show any possibility of success (just as he would in a fight between two actual friends).
\item A \textit{charmed} character is entitled to an opposed Charisma check against his master in order to resist instructions or commands that would make him do something he wouldn't normally do even for a close friend. If he succeeds, he decides not to go along with that order but remains \textit{charmed}.
\item A \textit{charmed} character never obeys a command that is obviously suicidal or grievously harmful to her.
\item If the charming creature commands his minion to do something that the influenced character would be violently opposed to, the subject may attempt a new saving throw to break free of the influence altogether.
\item A \textit{charmed} character who is openly attacked by the creature who \textit{charmed} him or by that creature's apparent allies is automatically freed of the spell or effect.
\end{itemize*}

Compulsion is a different matter altogether. A compulsion overrides the subject's 
free will in some way or simply changes the way the subject's mind works. A charm 
makes the subject a friend of the caster; a compulsion makes the subject obey the 
caster.

Regardless of whether a character is charmed or compelled, he won't volunteer information 
or tactics that his master doesn't ask for.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cold Immunity}\index{Cold Immunity}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature with cold immunity never takes cold damage. It has vulnerability to 
fire, which means it takes half again as much (+50\%) damage as normal from fire, 
regardless of whether a saving throw is allowed, or if the save is a success or 
failure.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Damage Reduction}\index{Damage Reduction}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some magic creatures have the supernatural ability to instantly heal damage from 
weapons or to ignore blows altogether as though they were invulnerable.

The numerical part of a creature's damage reduction is the amount of hit points 
the creature ignores from normal attacks. Usually, a certain type of weapon can 
overcome this reduction. This information is separated from the damage reduction 
number by a slash. Damage reduction may be overcome by special materials, by magic 
weapons (any weapon with a +1 or higher enhancement bonus, not counting the enhancement 
from masterwork quality), certain types of weapons (such as slashing or bludgeoning), 
and weapons imbued with an alignment. If a dash follows the slash then the damage 
reduction is effective against any attack that does not ignore damage reduction.

Ammunition fired from a projectile weapon with an enhancement bonus of +1 or higher 
is treated as a magic weapon for the purpose of overcoming damage reduction. Similarly, 
ammunition fired from a projectile weapon with an alignment gains the alignment 
of that projectile weapon (in addition to any alignment it may already have).

Whenever damage reduction completely negates the damage from an attack, it also 
negates most special effects that accompany the attack, such as injury type poison, 
a monk's stunning, and injury type disease. Damage reduction does not negate touch 
attacks, energy damage dealt along with an attack, or energy drains. Nor does it 
affect poisons or diseases delivered by inhalation, ingestion, or contact. 

Attacks that deal no damage because of the target's damage reduction do not disrupt 
spells.

Spells, spell-like abilities, and energy attacks (even nonmagical fire) ignore 
damage reduction.

Sometimes damage reduction is instant healing. Sometimes damage reduction represents 
the creature's tough hide or body,. In either case, characters can see that conventional 
attacks don't work.

If a creature has damage reduction from more than one source, the two forms of 
damage reduction do not stack. Instead, the creature gets the benefit of the best 
damage reduction in a given situation. 

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Darkvision}\index{Darkvision}
%%%%%%%%%%%%%%%%%%%%%%%%%

Darkvision is the extraordinary ability to see with no light source at all, out 
to a range specified for the creature. Darkvision is black and white only (colors 
cannot be discerned). It does not allow characters to see anything that they could 
not see otherwise -- invisible objects are still invisible, and illusions are still 
visible as what they seem to be. Likewise, darkvision subjects a creature to gaze 
attacks normally. The presence of light does not spoil darkvision.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Death Attacks}\index{Death Attacks}
%%%%%%%%%%%%%%%%%%%%%%%%%

In most cases, a death attack allows the victim a Fortitude save to avoid the affect, 
but if the save fails, the character dies instantly.

\begin{itemize*}
\item \linkspell{Raise Dead} doesn't work on someone killed by a death attack. 
\item Death attacks slay instantly. A victim cannot be made stable and thereby kept alive.
\item In case it matters, a dead character, no matter how she died, has -10 hit points.
\item The spell \linkspell{Death Ward} protects a character against these attacks.
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Disease}\index{Disease}
%%%%%%%%%%%%%%%%%%%%%%%%%

When a character is injured by a contaminated attack touches an item smeared with 
diseased matter, or consumes disease-tainted food or drink, he must make an immediate 
Fortitude saving throw. If he succeeds, the disease has no effect -- his immune 
system fought off the infection. If he fails, he takes damage after an incubation 
period. Once per day afterward, he must make a successful Fortitude saving throw 
to avoid repeated damage. Two successful saving throws in a row indicate that he 
has fought off the disease and recovers, taking no more damage.

These Fortitude saving throws can be rolled secretly so that the player doesn't 
know whether the disease has taken hold.

%%%
\subsubsection{Disease Descriptions}
%%%

Diseases have various symptoms and are spread through a number of vectors. The 
characteristics of several typical diseases are summarized on Table: Diseases and 
defined below.

\textit{Disease:} Diseases whose names are printed in \textit{italic} in the table 
are supernatural in nature. The others are extraordinary.

\textit{Infection:} The disease's method of delivery -- ingested, inhaled, via injury, 
or contact. Keep in mind that some injury diseases may be transmitted by as small 
an injury as a flea bite and that most inhaled diseases can also be ingested (and 
vice versa).

\textit{DC:} The Difficulty Class for the Fortitude saving throws to prevent infection 
(if the character has been infected), to prevent each instance of repeated damage, 
and to recover from the disease.

\textit{Incubation Period:} The time before damage begins.

\textit{Damage:} The ability damage the character takes after incubation and each 
day afterward.

\textbf{Types of Diseases:} Typical diseases include the following:

\textit{Blinding Sickness:} Spread in tainted water.

\textit{Cackle Fever:} Symptoms include high fever, disorientation, and frequent 
bouts of hideous laughter. Also known as "the shrieks".

\textit{Demon Fever:} Night hags spread it. Can cause permanent ability drain.

\textit{Devil Chills:} Barbazu and pit fiends spread it. It takes three, not two, 
successful saves in a row to recover from devil chills.

\textit{Filth Fever:} Dire rats and otyughs spread it. Those injured while in filthy 
surroundings might also catch it.

\textit{Mindfire:} Feels like your brain is burning. Causes stupor.

\textit{Mummy Rot:} Spread by mummies. Successful saving throws do not allow the 
character to recover (though they do prevent damage normally).

\textit{Red Ache:} Skin turns red, bloated, and warm to the touch.

\textit{The Shakes:} Causes involuntary twitches, tremors, and fits.

\textit{Slimy Doom:} Victim turns into infectious goo from the inside out. Can 
cause permanent ability drain.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Diseases}
\centering
\begin{tabular}{llll}
\textbf{Disease} & \textbf{Infection DC} & \textbf{Incubation} & \textbf{Damage}\\
Blinding Sickness & Ingested 16 & 1d3 days & 1d4 Str\textsuperscript{1}\\
Cackle Fever & Inhaled 16 & 1 day & 1d6 Wis\\
Demon Fever & Injury 18 & 1 day & 1d6 Con\textsuperscript{2}\\
Devil Chills\textsuperscript{3} & Injury 14 & 1d4 days & 1d4 Str\\
Filth Fever & Injury 12 & 1d3 days & 1d3 Dex, 1d3 Con\\
Mindfire & Inhaled 12 & 1 day & 1d4 Int\\
Mummy Rot\textsuperscript{4} & Contact 20 & 1 day & 1d6 Con\\
Red Ache & Injury 15 & 1d3 days & 1d6 Str\\
Shakes & Contact 13 & 1 day & 1d8 Dex\\
Slimy Doom & Contact 14 & 1 day & 1d4 Con\textsuperscript{2}\\
\multicolumn{4}{p{10cm}}{\textsuperscript{1} Each time the victim takes 2 or more damage from the disease, he must make another Fortitude save or be permanently blinded.}\\
\multicolumn{4}{p{10cm}}{\textsuperscript{2} When damaged, character must succeed on another saving throw or 1 point of damage is permanent drain instead.}\\
\multicolumn{4}{p{10cm}}{\textsuperscript{3} The victim must make three successful Fortitude saving throws in a row to recover from devil chills.}\\
\multicolumn{4}{p{10cm}}{\textsuperscript{4} Successful saves do not allow the character to recover. Only magical healing can save the character.}\\
\end{tabular}
\end{table}

%%%
\subsubsection{Healing a Disease}
%%%

Use of the Heal skill can help a diseased character. Every time a diseased character 
makes a saving throw against disease effects, the healer makes a check. The diseased 
character can use the healer's result in place of his saving throw if the Heal 
check result is higher. The diseased character must be in the healer's care and 
must have spent the previous 8 hours resting.

Characters recover points lost to ability score damage at a rate of 1 per day per 
ability damaged, and this rule applies even while a disease is in progress. That 
means that a character with a minor disease might be able to withstand it without 
accumulating any damage.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Energy Drain And Negative Levels}\index{Energy Drain}\index{Negative Levels}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some horrible creatures, especially undead monsters, possess a fearsome supernatural 
ability to drain levels from those they strike in combat. The creature making an 
energy drain attack draws a portion of its victim's life force from her. Most energy 
drain attacks require a successful melee attack roll -- mere physical contact is 
not enough. Each successful energy drain attack bestows one or more negative levels 
on the opponent. A creature takes the following penalties for each negative level 
it has gained.

\begin{itemize*}
\item -1 on all skill checks and ability checks.
\item -1 on attack rolls and saving throws.
\item -5 hit points.
\item -1 effective level (whenever the creature's level is used in a die roll or calculation, reduce it by one for each negative level).
\end{itemize*}

If the victim casts spells, she loses access to one spell as if she had cast her 
highest-level, currently available spell. (If she has more than one spell at her 
highest level, she chooses which she loses.) In addition, when she next prepares 
spells or regains spell slots, she gets one less spell slot at her highest spell 
level. 

Negative levels remain for 24 hours or until removed with a spell, such as \linkspell{Restoration}.
After 24 hours, the afflicted creature must attempt a Fortitude save (DC 10 + 
1/2 attacker's HD + attacker's Cha modifier). (The DC is provided in the attacker's 
description.) If the saving throw succeeds, the negative level goes away with no 
harm to the creature. The afflicted creature makes a separate saving throw for 
each negative level it has gained. If the save fails, the negative level goes away, 
but the creature's level is also reduced by one.

A character with negative levels at least equal to her current level, or drained 
below 1st level, is instantly slain. Depending on the creature that killed her, 
she may rise the next night as a monster of that kind. If not, she rises as a wight. 
A creature gains 5 temporary hit points for each negative level it bestows (though 
not if the negative level is caused by a spell or similar effect).

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Etherealness}\index{Etherealness}
%%%%%%%%%%%%%%%%%%%%%%%%%

Phase spiders and certain other creatures can exist on the Ethereal Plane. While 
on the Ethereal Plane, a creature is called ethereal. Unlike incorporeal creatures, 
ethereal creatures are not present on the Material Plane.

Ethereal creatures are invisible, inaudible, insubstantial, and scentless to creatures 
on the Material Plane. Even most magical attacks have no effect on them. \linkspell{See Invisibility}
and \linkspell{True Seeing} reveal ethereal creatures.

An ethereal creature can see and hear into the Material Plane in a 60-foot radius, 
though material objects still block sight and sound. (An ethereal creature can't 
see through a material wall, for instance.) An ethereal creature inside an object 
on the Material Plane cannot see. Things on the Material Plane, however, look gray, 
indistinct, and ghostly. An ethereal creature can't affect the Material Plane, 
not even magically. An ethereal creature, however, interacts with other ethereal 
creatures and objects the way material creatures interact with material creatures 
and objects.

Even if a creature on the Material Plane can see an ethereal creature the ethereal 
creature is on another plane. Only force effects can affect the ethereal creatures. 
If, on the other hand, both creatures are ethereal, they can affect each other 
normally.

A force effect originating on the Material Plane extends onto the Ethereal Plane, 
so that a \linkspell{Wall of Force} blocks an ethereal creature, and a \linkspell{Magic Missile}
can strike one (provided the spellcaster can see the ethereal target). 
Gaze effects and abjurations also extend from the Material Plane to the Ethereal 
Plane. None of these effects extend from the Ethereal Plane to the Material Plane.

Ethereal creatures move in any direction (including up or down) at will. They do 
not need to walk on the ground, and material objects don't block them (though they 
can't see while their eyes are within solid material).

Ghosts have a power called manifestation that allows them to appear on the Material 
Plane as incorporeal creatures. Still, they are on the Ethereal Plane, and another 
ethereal creature can interact normally with a manifesting ghost. Ethereal creatures 
pass through and operate in water as easily as air. Ethereal creatures do not fall 
or take falling damage. 

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evasion and Improved Evasion}\index{Evasion}\index{Improved Evasion}
%%%%%%%%%%%%%%%%%%%%%%%%%

These extraordinary abilities allow the target of an area attack to leap or twist 
out of the way. Rogues and monks have evasion and improved evasion as class features, 
but certain other creatures have these abilities, too.

If subjected to an attack that allows a Reflex save for half damage, a character 
with evasion takes no damage on a successful save. 

As with a Reflex save for any creature, a character must have room to move in order 
to evade. A bound character or one squeezing through an area cannot use evasion.

As with a Reflex save for any creature, evasion is a reflexive ability. The character 
need not know that the attack is coming to use evasion.

Rogues and monks cannot use evasion in medium or heavy armor. Some creatures with 
the evasion ability as an innate quality do not have this limitation.

Improved evasion is like evasion, except that even on a failed saving throw the 
character takes only half damage.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Healing}\index{Fast Healing}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature with fast healing has the extraordinary ability to regain hit points 
at an exceptional rate. Except for what is noted here, fast healing is like natural 
healing. 

At the beginning of each of the creature's turns, it heals a certain number of 
hit points (defined in its description).

Unlike regeneration, fast healing does not allow a creature to regrow or reattach 
lost body parts.

A creature that has taken both nonlethal and lethal damage heals the nonlethal 
damage first.

Fast healing does not restore hit points lost from starvation, thirst, or suffocation.

Fast healing does not increase the number of hit points regained when a creature 
polymorphs.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fear}\index{Fear Effects}
%%%%%%%%%%%%%%%%%%%%%%%%%

Spells, magic items, and certain monsters can affect characters with fear. In most 
cases, the character makes a Will saving throw to resist this effect, and a failed 
roll means that the character is shaken, frightened, or panicked.

\textbf{\gameterm{Shaken}:} Characters who are shaken take a -2 penalty on attack rolls, saving 
throws, skill checks, and ability checks.

\textbf{\gameterm{Frightened}:} Characters who are frightened are shaken, and in addition 
they flee from the source of their fear as quickly as they can. They can choose 
the path of their flight. Other than that stipulation, once they are out of sight 
(or hearing) of the source of their fear, they can act as they want. However, if 
the duration of their fear continues, characters can be forced to flee once more 
if the source of their fear presents itself again. Characters unable to flee can 
fight (though they are still shaken).

\textbf{\gameterm{Panicked}:} Characters who are panicked are shaken, and they run away from 
the source of their fear as quickly as they can. Other than running away from the 
source, their path is random. They flee from all other dangers that confront them 
rather than facing those dangers. Panicked characters cower if they are prevented 
from fleeing.

\textbf{Becoming Even More Fearful:} Fear effects are cumulative. A shaken character 
who is made shaken again becomes frightened, and a shaken character who is made 
frightened becomes panicked instead. A frightened character who is made shaken 
or frightened becomes panicked instead.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fire Immunity}\index{Fire Immunity}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature with fire immunity never takes fire damage. It has vulnerability to 
cold, which means it takes half again as much (+50\%) damage as normal from cold, 
regardless of whether a saving throw is allowed, or if the save is a success or 
failure.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Gaseous Form}\index{Gaseous Form}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some creatures have the supernatural or spell-like ability to take the form of 
a cloud of vapor or gas.

Creatures in gaseous form can't run but can fly. A gaseous creature can move about 
and do the things that a cloud of gas can conceivably do, such as flow through 
the crack under a door. It can't, however, pass through solid matter. Gaseous creatures 
can't attack physically or cast spells with verbal, somatic, material, or focus 
components. They lose their supernatural abilities (except for the supernatural 
ability to assume gaseous form, of course).

Creatures in gaseous form have damage reduction 10/magic. Spells, spell-like abilities, 
and supernatural abilities affect them normally. Creatures in gaseous form lose 
all benefit of material armor (including natural armor), though size, Dexterity, 
deflection bonuses, and armor bonuses from force armor still apply.

Gaseous creatures do not need to breathe and are immune to attacks involving breathing 
(troglodyte stench, poison gas, and the like).

Gaseous creatures can't enter water or other liquid. They are not ethereal or incorporeal. 
They are affected by winds or other forms of moving air to the extent that the 
wind pushes them in the direction the wind is moving. However, even the strongest 
wind can't disperse or damage a creature in gaseous form.

Discerning a creature in gaseous form from natural mist requires a DC 15 Spot check. 
Creatures in gaseous form attempting to hide in an area with mist, smoke, or other 
gas gain a +20 bonus.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Gaze Attacks}\index{Gaze Attacks}
%%%%%%%%%%%%%%%%%%%%%%%%%

While the medusa's gaze is well known, gaze attacks can also charm, curse, or even 
kill. Gaze attacks not produced by a spell are supernatural.

Each character within range of a gaze attack must attempt a saving throw (which 
can be a Fortitude or Will save) each round at the beginning of his turn.

An opponent can avert his eyes from the creature's face, looking at the creature's 
body, watching its shadow, or tracking the creature in a reflective surface. Each 
round, the opponent has a 50\% chance of not having to make a saving throw. The 
creature with the gaze attack gains concealment relative to the opponent. An opponent 
can shut his eyes, turn his back on the creature, or wear a blindfold. In these 
cases, the opponent does not need to make a saving throw. The creature with the 
gaze attack gains total concealment relative to the opponent.

A creature with a gaze attack can actively attempt to use its gaze as an attack 
action. The creature simply chooses a target within range, and that opponent must 
attempt a saving throw. If the target has chosen to defend against the gaze as 
discussed above, the opponent gets a chance to avoid the saving throw (either 50\% 
chance for averting eyes or 100\% chance for shutting eyes). It is possible for 
an opponent to save against a creature's gaze twice during the same round, once 
before its own action and once during the creature's action.

Looking at the creature's image (such as in a mirror or as part of an illusion) 
does not subject the viewer to a gaze attack.

A creature is immune to its own gaze attack.

If visibility is limited (by dim lighting, a fog, or the like) so that it results 
in concealment, there is a percentage chance equal to the normal miss chance for 
that degree of concealment that a character won't need to make a saving throw in 
a given round. This chance is not cumulative with the chance for averting your 
eyes, but is rolled separately.

Invisible creatures cannot use gaze attacks.

Characters using darkvision in complete darkness are affected by a gaze attack 
normally.

Unless specified otherwise, a creature with a gaze attack can control its gaze 
attack and "turn it off " when so desired.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Incorporeality}\index{Incorporeal}
%%%%%%%%%%%%%%%%%%%%%%%%%

Spectres, wraiths, and a few other creatures lack physical bodies. Such creatures 
are insubstantial and can't be touched by nonmagical matter or energy. Likewise, 
they cannot manipulate objects or exert physical force on objects. However, incorporeal 
beings have a tangible presence that sometimes seems like a physical attack against 
a corporeal creature. 

Incorporeal creatures are present on the same plane as the characters, and characters 
have some chance to affect them. 

Incorporeal creatures can be harmed only by other incorporeal creatures, by magic 
weapons, or by spells, spell-like effects, or supernatural effects. They are immune 
to all nonmagical attack forms. They are not burned by normal fires, affected by 
natural cold, or harmed by mundane acids.

Even when struck by magic or magic weapons, an incorporeal creature has a 50\% 
chance to ignore any damage from a corporeal source -- except for a force effect
or damage dealt by a ghost touch weapon.

Incorporeal creatures are immune to critical hits, extra damage from being favored 
enemies, and from sneak attacks. They move in any direction (including up or down) 
at will. They do not need to walk on the ground. They can pass through solid objects 
at will, although they cannot see when their eyes are within solid matter. 

Incorporeal creatures hiding inside solid objects get a +2 circumstance bonus on 
Listen checks, because solid objects carry sound well. Pinpointing an opponent 
from inside a solid object uses the same rules as pinpointing invisible opponents 
(see Invisibility, below). 

Incorporeal creatures are inaudible unless they decide to make noise.

The physical attacks of incorporeal creatures ignore material armor, even magic 
armor, unless it is made of force (such as mage armor or bracers of armor) or has 
the ghost touch ability. 

Incorporeal creatures pass through and operate in water as easily as they do in 
air.

Incorporeal creatures cannot fall or take falling damage.

Corporeal creatures cannot trip or grapple incorporeal creatures. 

Incorporeal creatures have no weight and do not set off traps that are triggered 
by weight.

Incorporeal creatures do not leave footprints, have no scent, and make no noise 
unless they manifest, and even then they only make noise intentionally.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Invisibility}\index{Invisibility}
%%%%%%%%%%%%%%%%%%%%%%%%%

The ability to move about unseen is not foolproof. While they can't be seen, invisible 
creatures can be heard, smelled, or felt. 

Invisibility makes a creature undetectable by vision, including darkvision.

Invisibility does not, by itself, make a creature immune to critical hits, but 
it does make the creature immune to extra damage from being a ranger's favored 
enemy and from sneak attacks.

A creature can generally notice the presence of an active invisible creature within 
30 feet with a DC 20 \linkskill{Spot} check. The observer gains a hunch that "something's 
there" but can't see it or target it accurately with an attack. A creature who 
is holding still is very hard to notice (DC 30). An inanimate object, an unliving 
creature holding still, or a completely immobile creature is even harder to spot 
(DC 40). It's practically impossible (+20 DC) to pinpoint an invisible creature's 
location with a Spot check, and even if a character succeeds on such a check, the 
invisible creature still benefits from total concealment (50\% miss chance).

A creature can use hearing to find an invisible creature. A character can make 
a \linkskill{Listen} check for this purpose as a free action each round. A Listen check result 
at least equal to the invisible creature's Move Silently check result reveals its 
presence. (A creature with no ranks in Move Silently makes a Move Silently check 
as a Dexterity check to which an armor check penalty applies.) A successful check 
lets a character hear an invisible creature "over there somewhere". It's practically 
impossible to pinpoint the location of an invisible creature. A Listen check that 
beats the DC by 20 pinpoints the invisible creature's location.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Listen Check DCs to Detect Invisible Creatures}
\centering
\begin{tabular}{ll}
\textbf{Invisible Creature Is\ldots{}} & \textbf{DC}\\
In combat or speaking & 0\\
Moving at half speed & Move Silently check result\\
Moving at full speed & Move Silently check result -4\\
Running or Charging & Move Silently result -20\\
Some distance away & +1 per 10ft\\
Behind an obstacle (door) & +5\\
Behind an obstacle (stone wall) & +15\\
\end{tabular}
\end{table}

A creature can grope about to find an invisible creature. A character can make 
a touch attack with his hands or a weapon into two adjacent 5-foot squares using 
a standard action. If an invisible target is in the designated area, there is a 
50\% miss chance on the touch attack. If successful, the groping character deals 
no damage but has successfully pinpointed the invisible creature's current location. 
(If the invisible creature moves, its location, obviously, is once again unknown.)

If an invisible creature strikes a character, the character struck still knows 
the location of the creature that struck him (until, of course, the invisible creature 
moves). The only exception is if the invisible creature has a reach greater than 
5 feet. In this case, the struck character knows the general location of the creature 
but has not pinpointed the exact location.

If a character tries to attack an invisible creature whose location he has pinpointed, 
he attacks normally, but the invisible creature still benefits from full concealment 
(and thus a 50\% miss chance). A particularly large and slow creature might get 
a smaller miss chance.

If a character tries to attack an invisible creature whose location he has not 
pinpointed, have the player choose the space where the character will direct the 
attack. If the invisible creature is there, conduct the attack normally. If the 
enemy's not there, roll the miss chance as if it were there, don't let the player 
see the result, and tell him that the character has missed. That way the player 
doesn't know whether the attack missed because the enemy's not there or because 
you successfully rolled the miss chance.

If an invisible character picks up a visible object, the object remains visible. 
One could coat an invisible object with flour to at least keep track of its position 
(until the flour fell off or blew away). An invisible creature can pick up a small 
visible item and hide it on his person (tucked in a pocket or behind a cloak) and 
render it effectively invisible. 

Invisible creatures leave tracks. They can be tracked normally. Footprints in sand, 
mud, or other soft surfaces can give enemies clues to an invisible creature's location.

An invisible creature in the water displaces water, revealing its location. The 
invisible creature, however, is still hard to see and benefits from concealment.

A creature with the scent ability can detect an invisible creature as it would 
a visible one.

A creature with the Blind-Fight feat has a better chance to hit an invisible creature. 
Roll the miss chance twice, and he misses only if both rolls indicate a miss. (Alternatively, 
make one 25\% miss chance roll rather than two 50\% miss chance rolls.)

A creature with blindsight can attack (and otherwise interact with) creatures regardless 
of invisibility.

An invisible burning torch still gives off light, as does an invisible object with 
a light spell (or similar spell) cast upon it.

Ethereal creatures are invisible. Since ethereal creatures are not materially present, 
Spot checks, Listen checks, Scent, Blind-Fight, and blindsight don't help locate 
them. Incorporeal creatures are often invisible. Scent, Blind-Fight, and blindsight 
don't help creatures find or attack invisible, incorporeal creatures, but Spot 
checks and possibly Listen checks can help.

Invisible creatures cannot use gaze attacks.

Invisibility does not thwart \textit{detect} spells.

Since some creatures can detect or even see invisible creatures, it is helpful 
to be able to hide even when invisible.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Level Loss}\index{Level Loss}
%%%%%%%%%%%%%%%%%%%%%%%%%

A character who loses a level instantly loses one Hit Die. The character's base 
attack bonus, base saving throw bonuses, and special class abilities are now reduced 
to the new, lower level. Likewise, the character loses any ability score gain, 
skill ranks, and any feat associated with the level (if applicable). If the exact 
ability score or skill ranks increased from a level now lost is unknown (or the 
player has forgotten), lose 1 point from the highest ability score or ranks from 
the highest-ranked skills. If a familiar or companion creature has abilities tied 
to a character who has lost a level, the creature's abilities are adjusted to fit 
the character's new level.

The victim's experience point total is immediately set to the midpoint of the previous 
level.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Low-Light Vision}\index{Low-Light Vision}
%%%%%%%%%%%%%%%%%%%%%%%%%

Characters with low-light vision have eyes that are so sensitive to light that 
they can see twice as far as normal in dim light. Low-light vision is color vision. 
A spellcaster with low-light vision can read a scroll as long as even the tiniest 
candle flame is next to her as a source of light.

Characters with low-light vision can see outdoors on a moonlit night as well as 
they can during the day.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Paralysis}\index{Paralysis}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some monsters and spells have the supernatural or spell-like ability to paralyze 
their victims, immobilizing them through magical means. (Paralysis from toxins 
is discussed in the Poison section below.)

A paralyzed character cannot move, speak, or take any physical action. He is rooted 
to the spot, frozen and helpless. Not even friends can move his limbs. He may take 
purely mental actions, such as casting a spell with no components.

A winged creature flying in the air at the time that it becomes paralyzed cannot 
flap its wings and falls. A swimmer can't swim and may drown.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poison}\index{Poison}
%%%%%%%%%%%%%%%%%%%%%%%%%

When a character takes damage from an attack with a poisoned weapon, touches an 
item smeared with contact poison, consumes poisoned food or drink, or is otherwise 
poisoned, he must make a Fortitude saving throw. If he fails, he takes the poison's 
initial damage (usually ability damage). Even if he succeeds, he typically faces 
more damage 1 minute later, which he can also avoid with a successful Fortitude 
saving throw.

One dose of poison smeared on a weapon or some other object affects just a single 
target. A poisoned weapon or object retains its venom until the weapon scores a 
hit or the object is touched (unless the poison is wiped off before a target comes 
in contact with it). Any poison smeared on an object or exposed to the elements 
in any way remains potent until it is touched or used.

Although supernatural and spell-like poisons are possible, poisonous effects are 
almost always extraordinary.

Poisons can be divided into four basic types according to the method by which their 
effect is delivered, as follows.

\textbf{Contact:} Merely touching this type of poison necessitates a saving throw. 
It can be actively delivered via a weapon or a touch attack. Even if a creature 
has sufficient damage reduction to avoid taking any damage from the attack, the 
poison can still affect it. A chest or other object can be smeared with contact 
poison as part of a trap.

\textbf{Ingested:} Ingested poisons are virtually impossible to utilize in a combat 
situation. A poisoner could administer a potion to an unconscious creature or attempt 
to dupe someone into drinking or eating something poisoned. Assassins and other 
characters tend to use ingested poisons outside of combat.

\textbf{Inhaled:} Inhaled poisons are usually contained in fragile vials or eggshells. 
They can be thrown as a ranged attack with a range increment of 10 feet. When it 
strikes a hard surface (or is struck hard), the container releases its poison. 
One dose spreads to fill the volume of a 10-foot cube. Each creature within the 
area must make a saving throw. (Holding one's breath is ineffective against inhaled 
poisons; they affect the nasal membranes, tear ducts, and other parts of the body.)

\textbf{Injury:} This poison must be delivered through a wound. If a creature has 
sufficient damage reduction to avoid taking any damage from the attack, the poison 
does not affect it. Traps that cause damage from weapons, needles, and the like 
sometimes contain injury poisons.

The characteristics of poisons are summarized on Table: Poisons. Terms on the table 
are defined below.

\textit{Type:} The poison's method of delivery (contact, ingested, inhaled, or 
via an injury) and the Fortitude save DC to avoid the poison's damage.

\textit{Initial Damage:} The damage the character takes immediately upon failing 
his saving throw against this poison. Ability damage is temporary unless marked 
with an asterisk (*), in which case the loss is a permanent drain. Paralysis lasts 
for 2d6 minutes.

\textit{Secondary Damage:} The amount of damage the character takes 1 minute after 
exposure as a result of the poisoning, if he fails a second saving throw. Unconsciousness 
lasts for 1d3 hours. Ability damage marked with an asterisk is permanent drain 
instead of temporary damage.

\textit{Price:} The cost of one dose (one vial) of the poison. It is not possible 
to use or apply poison in any quantity smaller than one dose. The purchase and 
possession of poison is always illegal, and even in big cities it can be obtained 
only from specialized, less than reputable sources.

%%%
\subsubsection{Perils of Using Poison}
%%%

A character has a 5\% chance of exposing himself to a poison whenever he applies 
it to a weapon or otherwise readies it for use. Additionally, a character who rolls 
a natural 1 on an attack roll with a poisoned weapon must make a DC 15 Reflex save 
or accidentally poison himself with the weapon.

%%%
\subsubsection{Poison Immunities}
%%%

Creatures with natural poison attacks are immune to their own poison. Nonliving 
creatures (constructs and undead) and creatures without metabolisms (such as elementals) 
are always immune to poison. Oozes, plants, and certain kinds of outsiders are 
also immune to poison, although conceivably special poisons could be concocted 
specifically to harm them.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}\mcinherit
\caption{Poisons}
\centering
\begin{tabular}{l l l l r}
\textbf{Poison} & \textbf{Type} & \textbf{Initial Damage} & \textbf{Secondary Damage} & \textbf{Price}\\
Nitharit & Contact DC 13 & 0 & 3d6 Con & 650 gp\\
Sassone Leaf Residue & Contact DC 16 & 2d12 hp & 1d6 Con & 300 gp\\
Malyss Root Paste & Contact DC 16 & 1 Dex & 2d4 Dex & 500 gp\\
Terinav Root & Contact DC 16 & 1d6 Dex & 2d6 Dex & 750 gp\\
Black Lotus Extract & Contact DC 20 & 3d6 Con & 3d6 Con & 4,500 gp\\
Dragon Bile & Contact DC 26 & 3d6 Str & 0 & 1,500 gp\\
Striped Toadstool & Ingested DC 11 & 1 Wis & 2d6 Wis + 1d4 Int & 180 gp\\
Arsenic & Ingested DC 13 & 1 Con & 1d8 Con & 120 gp\\
Id Moss & Ingested DC 14 & 1d4 Int & 2d6 Int & 125 gp\\
Oil of Taggit & Ingested DC 15 & 0 & Unconsciousness & 90 gp\\
Lich Dust & Ingested DC 17 & 2d6 Str & 1d6 Str & 250 gp\\
Dark Reaver Powder & Ingested DC 18 & 2d6 Con & 1d6 Con + 1d6 Str & 300 gp\\
Ungol Dust & Inhaled DC 15 & 1 Cha & 1d6 Cha + 1 Cha\textsuperscript{D} & 1,000 gp\\
Insanity Mist & Inhaled DC 15 & 1d4 Wis & 2d6 Wis & 1,500 gp\\
Burnt Othur Fumes & Inhaled DC 18 & 1 Con\textsuperscript{D} & 3d6 Con & 2,100 gp\\
Black Adder Venom & Injury DC 11 & 1d6 Con & 1d6 Con & 120 gp\\
Small Centipede Poison & Injury DC 11 & 1d2 Dex & 1d2 Dex & 90 gp\\
Bloodroot & Injury DC 12 & 0 & 1d4 Con + 1d3 Wis & 100 gp\\
Drow Poison & Injury DC 13 & Unconsciousness & Unconsciousness for 2d4 hours & 75gp\\
Greenblood Oil & Injury DC 13 & 1 Con & 1d2 Con & 100 gp\\
Blue Whinnis & Injury DC 14 & 1 Con & Unconsciousness & 120 gp\\
Medium Spider Venom & Injury DC 14 & 1d4 Str & 1d4 Str & 150 gp\\
Shadow Essence & Injury DC 17 & 1 Str\textsuperscript{D} & 2d6 Str & 250 gp\\
Wyvern Poison & Injury DC 17 & 2d6 Con & 2d6 Con & 3,000 gp\\
Large Scorpion Venom & Injury DC 18 & 1d6 Str & 1d6 Str & 200 gp\\
Giant Wasp Poison & Injury DC 18 & 1d6 Dex & 1d6 Dex & 210 gp\\
Deathblade & Injury DC 20 & 1d6 Con & 2d6 Con & 1,800 gp\\
Purple Worm Poison & Injury DC 24 & 1d6 Str & 2d6 Str & 700 gp\\
\multicolumn{5}{l}{\textsuperscript{D}Permanent drain, not temporary damage.}\\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Polymorph}\index{Polymorph}
%%%%%%%%%%%%%%%%%%%%%%%%%

Magic can cause creatures and characters to change their shapes -- sometimes against 
their will, but usually to gain an advantage. Polymorphed creatures retain their 
own minds but have new physical forms.

The \linkspell{Polymorph} spell defines the general polymorph effect.

Since creatures do not change types, a slaying or bane weapon designed to kill 
or harm creatures of a specific type affects those creatures even if they are polymorphed. 
Likewise, a creature polymorphed into the form of a creature of a different type 
is not subject to slaying and bane effects directed at that type of creature. 

A ranger's favored enemy bonus is based on knowing what the foe is, so if a creature 
that is a ranger's favored enemy polymorphs into another form, the ranger is denied 
his bonus.

A dwarf 's bonus for fighting giants is based on shape and size, so he does not 
gain a bonus against a giant polymorphed into something else, but does gain the 
bonus against any creature polymorphed into a giant.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Psionics}\index{Psionics}
%%%%%%%%%%%%%%%%%%%%%%%%%

Telepathy, mental combat and psychic powers -- psionics is a catchall word that 
describes special mental abilities possessed by various creatures. These are spell-like 
abilities that a creature generates from the power of its mind alone -- no other 
outside magical force or ritual is needed. Each psionic creature's description 
contains details on its psionic abilities.

Psionic attacks almost always allow Will saving throws to resist them. However, 
not all psionic attacks are mental attacks. Some psionic abilities allow the psionic 
creature to reshape its own body, heal its wounds, or teleport great distances. 
Some psionic creatures can see into the future, the past, and the present (in far-off 
locales) as well as read the minds of others. 

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rays}\index{Ray}
%%%%%%%%%%%%%%%%%%%%%%%%%

All ray attacks require the attacker to make a successful ranged touch attack against 
the target. Rays have varying ranges, which are simple maximums. A ray's attack 
roll never takes a range penalty. Even if a ray hits, it usually allows the target 
to make a saving throw (Fortitude or Will). Rays never allow a Reflex saving throw, 
but if a character's Dexterity bonus to AC is high, it might be hard to hit her 
with the ray in the first place.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regeneration}\index{Regeneration}
%%%%%%%%%%%%%%%%%%%%%%%%%

Creatures with this extraordinary ability recover from wounds quickly and can even 
regrow or reattach severed body parts. Damage dealt to the creature is treated 
as nonlethal damage, and the creature automatically cures itself of nonlethal damage 
at a fixed rate.

Certain attack forms, typically fire and acid, deal damage to the creature normally; 
that sort of damage doesn't convert to nonlethal damage and so doesn't go away. 
The creature's description includes the details.

Creatures with regeneration can regrow lost portions of their bodies and can reattach 
severed limbs or body parts. Severed parts die if they are not reattached.

Regeneration does not restore hit points lost from starvation, thirst, or suffocation.

Attack forms that don't deal hit point damage ignore regeneration.

An attack that can cause instant death only threatens the creature with death if 
it is delivered by weapons that deal it lethal damage.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Resistance to Energy}\index{Energy Resistance}\index{Resistance to Energy}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature with resistance to energy has the ability (usually extraordinary) to 
ignore some damage of a certain type each round, but it does not have total immunity. 

Each resistance ability is defined by what energy type it resists and how many 
points of damage are resisted. It doesn't matter whether the damage has a mundane 
or magical source.

When resistance completely negates the damage from an energy attack, the attack 
does not disrupt a spell. This resistance does not stack with the resistance that 
a spell might provide.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scent}\index{Scent}
%%%%%%%%%%%%%%%%%%%%%%%%%

This extraordinary ability lets a creature detect approaching enemies, sniff out 
hidden foes, and track by sense of smell.

A creature with the scent ability can detect opponents by sense of smell, generally 
within 30 feet. If the opponent is upwind, the range is 60 feet. If it is downwind, 
the range is 15 feet. Strong scents, such as smoke or rotting garbage, can be detected 
at twice the ranges noted above. Overpowering scents, such as skunk musk or troglodyte 
stench, can be detected at three times these ranges.

The creature detects another creature's presence but not its specific location. 
Noting the direction of the scent is a move action. If it moves within 5 feet of 
the scent's source, the creature can pinpoint that source.

A creature with the Track feat and the scent ability can follow tracks by smell, 
making a Wisdom check to find or follow a track. The typical DC for a fresh trail 
is 10. The DC increases or decreases depending on how strong the quarry's odor 
is, the number of creatures, and the age of the trail. For each hour that the trail 
is cold, the DC increases by 2. The ability otherwise follows the rules for the 
Track feat. Creatures tracking by scent ignore the effects of surface conditions 
and poor visibility.

Creatures with the scent ability can identify familiar odors just as humans do 
familiar sights.

Water, particularly running water, ruins a trail for air-breathing creatures. Water-breathing 
creatures that have the scent ability, however, can use it in the water easily.

False, powerful odors can easily mask other scents. The presence of such an odor 
completely spoils the ability to properly detect or identify creatures, and the 
base Survival DC to track becomes 20 rather than 10.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spell Resistance}\index{Spell Resistance}
%%%%%%%%%%%%%%%%%%%%%%%%%

Spell resistance is the extraordinary ability to avoid being affected by spells. 
(Some spells also grant spell resistance.)

To affect a creature that has spell resistance, a spellcaster must make a caster 
level check (1d20 + caster level) at least equal to the creature's spell resistance. 
(The defender's spell resistance is like an Armor Class against magical attacks.) 
If the caster fails the check, the spell doesn't affect the creature. The possessor 
does not have to do anything special to use spell resistance. The creature need 
not even be aware of the threat for its spell resistance to operate.

Only spells and spell-like abilities are subject to spell resistance. Extraordinary 
and supernatural abilities (including enhancement bonuses on magic weapons) are 
not. A creature can have some abilities that are subject to spell resistance and 
some that are not. Even some spells ignore spell resistance; see When Spell Resistance 
Applies, below. 

A creature can voluntarily lower its spell resistance. Doing so is a standard action 
that does not provoke an attack of opportunity. Once a creature lowers its resistance, 
it remains down until the creature's next turn. At the beginning of the creature's 
next turn, the creature's spell resistance automatically returns unless the creature 
intentionally keeps it down (also a standard action that does not provoke an attack 
of opportunity).

A creature's spell resistance never interferes with its own spells, items, or abilities.

A creature with spell resistance cannot impart this power to others by touching 
them or standing in their midst. Only the rarest of creatures and a few magic items 
have the ability to bestow spell resistance upon another.

Spell resistance does not stack. It overlaps. 

%%%
\subsubsection{When Spell Resistance Applies}
%%%

Each spell includes an entry that indicates whether spell resistance applies to 
the spell. In general, whether spell resistance applies depends on what the spell 
does:

\textbf{Targeted Spells:} Spell resistance applies if the spell is targeted at 
the creature. Some individually targeted spells can be directed at several creatures 
simultaneously. In such cases, a creature's spell resistance applies only to the 
portion of the spell actually targeted at that creature. If several different resistant 
creatures are subjected to such a spell, each checks its spell resistance separately.

\textbf{Area Spells:} Spell resistance applies if the resistant creature is within 
the spell's area. It protects the resistant creature without affecting the spell 
itself.

\textbf{Effect Spells:} Most effect spells summon or create something and are not 
subject to spell resistance. Sometimes, however, spell resistance applies to effect 
spells, usually to those that act upon a creature more or less directly, such as 
\linkspell{Web}.

Spell resistance can protect a creature from a spell that's already been cast. 
Check spell resistance when the creature is first affected by the spell.

Check spell resistance only once for any particular casting of a spell or use of 
a spell-like ability. If spell resistance fails the first time, it fails each time 
the creature encounters that same casting of the spell. Likewise, if the spell 
resistance succeeds the first time, it always succeeds. If the creature has voluntarily 
lowered its spell resistance and is then subjected to a spell, the creature still 
has a single chance to resist that spell later, when its spell resistance is up.

Spell resistance has no effect unless the energy created or released by the spell 
actually goes to work on the resistant creature's mind or body. If the spell acts 
on anything else and the creature is affected as a consequence, no roll is required. 
Creatures can be harmed by a spell without being directly affected. 

Spell resistance does not apply if an effect fools the creature's senses or reveals 
something about the creature.

Magic actually has to be working for spell resistance to apply. Spells that have 
instantaneous durations but lasting results aren't subject to spell resistance 
unless the resistant creature is exposed to the spell the instant it is cast. 

When in doubt about whether a spell's effect is direct or indirect, consider the 
spell's school:

\textbf{\gameterm{Abjuration}:} The target creature must be harmed, changed, or restricted 
in some manner for spell resistance to apply. Perception changes aren't subject 
to spell resistance.

Abjurations that block or negate attacks are not subject to an attacker's spell 
resistance -- it is the protected creature that is affected by the spell (becoming 
immune or resistant to the attack).

\textbf{\gameterm{Conjuration}:} These spells are usually not subject to spell resistance 
unless the spell conjures some form of energy. Spells that summon creatures 
or produce effects that function like creatures are not subject to spell resistance.

\textbf{\gameterm{Divination}:} These spells do not affect creatures directly and are not 
subject to spell resistance, even though what they reveal about a creature might 
be very damaging.

\textbf{\gameterm{Enchantment}:} Since enchantment spells affect creatures' minds, they are 
typically subject to spell resistance.

\textbf{\gameterm{Evocation}:} If an evocation spell deals damage to the creature, it has 
a direct effect. If the spell damages something else, it has an indirect effect.

\textbf{\gameterm{Illusion}:} These spells are almost never subject to spell resistance. Illusions 
that entail a direct attack are exceptions.

\textbf{\gameterm{Necromancy}:} Most of these spells alter the target creature's life force 
and are subject to spell resistance. Unusual necromancy spells that don't affect 
other creatures directly are not subject to spell resistance.

\textbf{\gameterm{Transmutation}:} These spells are subject to spell resistance if they transform 
the target creature. Transmutation spells are not subject to spell resistance if 
they are targeted on a point in space instead of on a creature. Some transmutations 
make objects harmful (or more harmful), such as \linkspell{Magic Stone}. Even these 
spells are not generally subject to spell resistance because they affect the objects, 
not the creatures against which the objects are used. Spell resistance works against 
\textit{Magic Stone} only if the creature with spell resistance is holding the 
stones when the cleric casts \textit{Magic Stone} on them. 

%%%
\subsubsection{Successful Spell Resistance}
%%%

Spell resistance prevents a spell or a spell-like ability from affecting or harming 
the resistant creature, but it never removes a magical effect from another creature 
or negates a spell's effect on another creature. Spell resistance prevents a spell 
from disrupting another spell.

Against an ongoing spell that has already been cast, a failed check against spell 
resistance allows the resistant creature to ignore any effect the spell might have. 
The magic continues to affect others normally.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tremorsense}\index{Tremorsense}
%%%%%%%%%%%%%%%%%%%%%%%%%

A creature with tremorsense automatically senses the location of anything that 
is in contact with the ground and within range.

If no straight path exists through the ground from the creature to those that it's 
sensing, then the range defines the maximum distance of the shortest indirect path. 
It must itself be in contact with the ground, and the creatures must be moving. 

As long as the other creatures are taking physical actions, including casting spells 
with somatic components, they're considered moving; they don't have to move from 
place to place for a creature with tremorsense to detect them.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Turn Resistance}\index{Turn Resistance}
%%%%%%%%%%%%%%%%%%%%%%%%%

Some creatures (usually undead) are less easily affected by the turning ability 
of clerics or paladins.

Turn resistance is an extraordinary ability.

When resolving a turn, rebuke, command, or bolster attempt, added the appropriate 
bonus to the creature's Hit Dice total. 
