%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\classentry{Adept}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Hit Die:} d6.

\textbf{Class Skills}

The adept's class skills (and the key ability for each skill) are \linkskill{Concentration} 
(Con), \linkskill{Craft} (Int), \linkskill{Handle Animal} (Cha), \linkskill{Heal} (Wis), \linkskill{Knowledge} (all skills taken 
individually) (Int), \linkskill{Profession} (Wis), \linkskill{Spellcraft} (Int), and \linkskill{Survival} (Wis). 

\textbf{Skill Points at 1st Level:} (2 + Int modifier) x4.

\textbf{Skill Points at Each Additional Level:} 2 + Int modifier.

\begin{table}[htb]
\rowcolors{1}{white}{offyellow}
\caption{The Adept}
\centering
\begin{tabular}{*{6}{l}*{6}{c}}
\textbf{Level} & \textbf{BAB} & \textbf{Fort} & \textbf{Reflex} & \textbf{Will} & \textbf{Special} & \textbf{0th} & \textbf{1st} & \textbf{2nd} & \textbf{3rd} & \textbf{4th} & \textbf{5th}\\
1st & +0 & +0 & +0 & +2 & -- & 3 & 1 & -- & -- & -- & -- \\
2nd & +1 & +0 & +0 & +3 & Summon Familiar & 3 & 1 & -- & -- & -- & -- \\
3rd & +1 & +1 & +1 & +3 & -- & 3 & 2 & -- & -- & -- & -- \\
4th & +2 & +1 & +1 & +4 & -- & 3 & 2 & 0 & -- & -- & -- \\
5th & +2 & +1 & +1 & +4 & -- & 3 & 2 & 1 & -- & -- & -- \\
6th & +3 & +2 & +2 & +5 & -- & 3 & 2 & 1 & -- & -- & -- \\
7th & +3 & +2 & +2 & +5 & -- & 3 & 3 & 2 & -- & -- & -- \\
8th & +4 & +2 & +2 & +6 & -- & 3 & 3 & 2 & 0 & -- & -- \\
9th & +4 & +3 & +3 & +6 & -- & 3 & 3 & 2 & 1 & -- & -- \\
10th & +5 & +3 & +3 & +7 & -- & 3 & 3 & 2 & 1 & -- & -- \\
11th & +5 & +3 & +3 & +7 & -- & 3 & 3 & 3 & 2 & -- & -- \\
12th & +6 & +4 & +4 & +8 & -- & 3 & 3 & 3 & 2 & 0 & -- \\
13th & +6 & +4 & +4 & +8 & -- & 3 & 3 & 3 & 2 & 1 & -- \\
14th & +7 & +4 & +4 & +9 & -- & 3 & 3 & 3 & 3 & 1 & -- \\
15th & +7 & +5 & +5 & +9 & -- & 3 & 3 & 3 & 3 & 2 & -- \\
16th & +8 & +5 & +5 & +10 & -- & 3 & 3 & 3 & 3 & 2 & 0 \\
17th & +8 & +5 & +5 & +10 & -- & 3 & 3 & 3 & 3 & 2 & 1 \\
18th & +9 & +6 & +6 & +11 & -- & 3 & 3 & 3 & 3 & 3 & 1 \\
19th & +9 & +6 & +6 & +11 & -- & 3 & 3 & 3 & 3 & 3 & 2 \\
20th & +10 & +6 & +6 & +12 & -- & 3 & 3 & 3 & 3 & 3 & 2 \\
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%
\ClassFeatures
%%%%%%%%%%%%%%%%%%%%%%%%%

All of the following are class features of the adept NPC class.

\textbf{Weapon and Armor Proficiency:} Adepts are skilled with all simple weapons. 
Adepts are not proficient with any type of armor nor with shields.

\textbf{Spells:} An adept casts divine spells which are drawn from the adept spell 
list (see below). Like a cleric, an adept must choose and prepare her spells in 
advance. Unlike a cleric, an adept cannot spontaneously cast \textit{cure} or \textit{inflict} spells.

To prepare or cast a spell, an adept must have a Wisdom score equal to at least 
10 + the spell level. The Difficulty Class for a saving throw against an adept's 
spell is 10 + the spell level + the adept's Wisdom modifier.

Adepts, unlike wizards, do not acquire their spells from books or scrolls, nor 
do they prepare them through study. Instead, they meditate or pray for their spells, 
receiving them as divine inspiration or through their own strength of faith. Each 
adept must choose a time each day at which she must spend an hour in quiet contemplation 
or supplication to regain her daily allotment of spells. Time spent resting has 
no effect on whether an adept can prepare spells.

Like other spellcasters, an adept can cast only a certain number of spells of each 
spell level per day. Her base daily spell allotment is given on Table: The Adept. 
In addition, she receives bonus spells per day if she has a high Wisdom score.

When Table: The Adept indicates that the adept gets 0 spells per day of a given 
spell level, she gains only the bonus spells she would be entitled to based on 
her Wisdom score for that spell level.

Each adept has a particular holy symbol (as a divine focus) depending on the adept's 
magical tradition.

\textbf{Summon Familiar:} At 2nd level, an adept can call a familiar, just as a 
sorcerer or wizard can.

%%%
\subsubsection{Adept Spell List}
%%%

Adepts choose their spells from the following list.

\textbf{0th Level:} \linkspell{Create Water}, \linkspell{Cure Minor Wounds}, \linkspell{Detect Magic}, \linkspell{Ghost Sound}, \linkspell{Guidance}, \linkspell{Light}, \linkspell{Mending}, \linkspell{Purify Food and Drink}, \linkspell{Read Magic}, \linkspell{Touch of Fatigue}.

\textbf{1st Level:} \linkspell{Bless}, \linkspell{Burning Hands}, \linkspell{Cause Fear}, \linkspell{Command}, \linkspell{Comprehend Languages}, \linkspell{Cure Light Wounds}, \linkspell{Detect Chaos}, \linkspell{Detect Evil}, \linkspell{Detect Good}, \linkspell{Detect Law}, \linkspell{Endure Elements}, \linkspell{Obscuring Mist}, \linkspell{Protection From Chaos}, \linkspell{Protection From Evil}, \linkspell{Protection From Good}, \linkspell{Protection From Law}, \linkspell{Sleep}.

\textbf{2nd Level:} \linkspell{Aid}, \linkspell{Animal Trance}, \linkspell{Bear's Endurance}, \linkspell{Bull's Strength}, \linkspell{Cat's Grace}, \linkspell{Cure Moderate Wounds}, \linkspell{Darkness}, \linkspell{Delay Poison}, \linkspell{Invisibility}, \linkspell{Mirror Image}, \linkspell{Resist Energy}, \linkspell{Scorching Ray}, \linkspell{See Invisibility}, \linkspell{Web}.

\textbf{3rd Level:} \linkspell{Animate Dead}, \linkspell{Bestow Curse}, \linkspell{Contagion}, \linkspell{Continual Flame}, \linkspell{Cure Serious Wounds}, \linkspell{Daylight}, \linkspell{Deeper Darkness}, \linkspell{Lightning Bolt}, \linkspell{Neutralize Poison}, \linkspell{Remove Curse}, \linkspell{Remove Disease}, \linkspell{Tongues}.

\textbf{4th Level:} \linkspell{Cure Critical Wounds}, \linkspell{Minor Creation}, \linkspell{Polymorph}, \linkspell{Restoration}, \linkspell{Stoneskin}, \linkspell{Wall of Fire}.

\textbf{5th Level:} \linkspell{Baleful Polymorph}, \linkspell{Break Enchantment}, \linkspell{Commune}, \linkspell{Heal}, \linkspell{Major Creation}, \linkspell{Raise Dead}, \linkspell{True Seeing}, \linkspell{Wall of Stone}.

