\classname{Boneblade Reaper}
\vspace*{-8pt}
\quot{``I have bested Death itself and cannot die. Your powers do not impress me.''}

Necromancy is the magic of death, and the study of this art can reveal martial secrets for dealing of death. To be a Boneblade Reaper is not just to study death as a means of bringing it to your enemies, but it is a path of dark enlightenment. To reach a pinnacle of this art, one must embrace death as a lover, and to erase his name from the book of life and enter it into the book of death. This is not the embrace of corrupted state of undeath, but the rewriting of the self as an avatar of an implacable and unknowable force of existence - death itself.

To begin this path, one masters the boneblade, a symbol of the art of dealing death. Then he etches the necromantic runes into his own flesh that mark him as one of Deathís Own. From there, he begins learning the death art of the boneblade, mastering martial techniques culled from the study of necromancy.

%While the original Boneblade Reaper was intended to address the fact that Monk levels from the PHB don't make a spellcaster any good in combat (although admittedly they do allow you to come in \textit{second} in any 1 on 1 combat), the Boneblade Reaper for the Dungeonomicon Monk should be there to address the problem that taking Wizard levels doesn't really help your Monk combatting.

\ability{Prerequisites:}{}
\listprereq
	\itemability{Skills:}{Move Silently 9 ranks, Concentration 4 ranks}
	\itemability{Feats:}{Boneblade Master, Weapon Finesse}
	\itemability{Spellcasting:}{Must be able to cast second level spells.}
	\itemability{Special:}{Cannot be undead.}
	\itemability{Special:}{Must have two Fighting Styles \emph{or} must have the Evasion ability.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Boneblade Reaper's class skills (and the key ability for each skill) are Bluff (Cha), Concentration (Con), Craft (Int), Disable Device (Int), Hide(Dex), Intimidate (Cha), Knowledge (all skills, taken individually) (Int), Listen (Wis), Move Silently(Dex), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot(Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Spellcasting\\
1&+1&+2&+2&+2&Deathscribed Flesh, Death Art Strike&+1 spellcasting level\\
2&+2&+3&+3&+3&Secrets of the Boneblade Art&+1 spellcasting level\\
3&+3&+3&+3&+3&Dark Life&+1 spellcasting level\\
4&+4&+4&+4&+4&Fighting Style, Speed of Death +20 feet&+1 spellcasting level\\
5&+5&+4&+4&+4&Runes of Lifetrapping&+1 spellcasting level\\
6&+6&+5&+5&+5&Speed of Death +40 feet&+1 spellcasting level\\
7&+7&+5&+5&+5&Ghost Strike&+1 spellcasting level\\
8&+8&+6&+6&+6&Master Fighting Style, Speed of Death +60 feet&+1 spellcasting level\\
9&+9&+6&+6&+6&Dance with the Reaper&+1 spellcasting level\\
10&+10&+7&+7&+7&Runes of the Dark Reaper, Speed of Death +80 feet&+1 spellcasting level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Boneblade Reaper prestige class.

\ability{Weapon and Armor Proficiency:}{The Boneblade Reaper gains no proficiency with armor or weapons, although if he has any ability that applies to a Slam attack he may use it with any Boneblade weapon.}

\ability{Spellcasting:}{Every level, the Boneblade Reaper casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Deathscribed Flesh (Ex):}{The Boneblade Reaper has scribed necromantic runes into the own flesh of his arms and chest, never healing and faintly shimmering with dark energy. As long as these runes are not covered by clothing or armor, these runes provide protection from the blades and claws of the Boneblade Reaper's enemies. In game terms, this counts a +8 armor bonus that counts against touch attacks and incorporeal touch attacks. For each additional level of this class, this bonus increases by +1.

These runes also make the Boneblade Reaper immune to any effect that would turn him into an undead creature, even if he is currently dead.}

\ability{Death Art Strike (Su):}{Each time the Boneblade Reaper kills an enemy with a boneblade weapon melee attack, he may make an additional touch attack with a free hand at the same attack bonus. If this attack hits, he may cast one targeted spell against the target of his attack as a free action.}

\ability{Secrets of the Boneblade Art (Su):}{From 2nd level on, the Boneblade Reaper may cast his targeted Necromancy spells through his boneblades. Once per turn, with a successful melee attack on an enemy with a boneblade weapon, the Boneblade Reaper may cast a targeted Necromancy spell as a free action that does not provoke an attack of opportunity. This spell affects the enemy as if the boneblade had been enchanted with the Spellstoring attribute and the spell had been inside it when it struck (and been activated during the attack).}

\ability{Dark Life (Su):}{At 3rd level, the Boneblade Reaper has learned to draw power from negative energy. Any damage he would receive from negative energy is instead converted to healing on a point for point basis. He is still healed by Positive Energy as well.}

\ability{Fighting Style:}{At 4th level, the Boneblade Reaper gains a \hyperref[class:monk]{Monk's} Fighting Style. Appropriate names are generally of a dark tone such as ``Wasting Serpent Style" or ``Hopeless Basilisk Stance".}

\ability{Speed of Death (Ex):}{Even light is not faster than the dark, and nothing living is faster than death. When the Boneblade Reaper achieves 4th level, his speed increases by 20 feet. His speed increases 20 more feet at 6th, 8th, and 10th level.}

\ability{Runes of Life Trapping (Ex):}{At 5th level, the Boneblade Reaper is immune to any effect that moves his soul from his body, even if he is currently dead. This includes effects like \spell{magic jar}, \spell{soul bind}, \spell{trap the soul}, and the class features of PrCs like Soul Merchant and Heartless Mage (even if he has levels in these PrCs).

Also, the Boneblade Reaper gains Heavy Fortification in addition to the armor bonus he gains from his Deathscribed Flesh ability.}

\ability{Ghost Strike (Su):}{At 7th level, the Boneblade Reaper can lose any prepared spell in order to cast \spell{wraithstrike}, even if this spell is not on his spell list. This casting does not provoke Attacks of Opportunity.}

\ability{Master Fighting Style:}{A Boneblade Reaper of 8th level gains access to a Master Fighting Style as a Monk.}

\ability{Dance with the Dark Reaper (Ex):}{Due to a bargain with Death, a 9th level Boneblade Reaper must battle the Dark Reaper to win freedom from Death's grasp. Should the Boneblade Reaper die, his body is pulled into a featureless pocket demiplane that cannot be accessed or exited by dimensional traveling magic. Once there, the Boneblade Reaper is stripped of his equipment and he receives the effects of a \spell{true resurrection} spell and a \spell{disjunction}, and he is fully healed. A boneblade weapon is created for him while he is in this demiplane.

He is then immediately forced into a battle with the Dark Reaper (treat as an Entropic Reaper without the Entropic Blade ability). Should he win this battle, he is returned with all his equipment to a safe location 1d4 miles from the place where he died and he does not age for 10 years.

If he loses, he dies again and can only be returned to life with resurrection magic that does not require his body; casting this kind of spell calls a Dark Reaper to the location of the spellcaster and he must kill the Dark Reaper without aid for the spell to take effect. Once returned to life, the Boneblade Reaper's equipment is transported to the location of his new body. The Boneblade Reaper cannot refuse to return to life if resurrection magic is used on his behalf.

If the Boneblade Reaper dies due to reaching his maximum age, his life is extended long enough for him to finish his battle with the Reaper. Should he defeat the Reaper, his maximum age is instead increased by 10 years (during which he does not age any further). If he fails, he cannot be returned to life by any means.}

\ability{Runes of the Dark Reaper (Ex):}{At 10th level, the Boneblade Reaper ascends to the honored position of Dark Reaper, and so he cuts the representative runes into his flesh. Any creature he kills with a boneblade is affected by a soul bind effect that binds the soul to the body of the Boneblade Reaper. The only way to release a soul affected by this power is to convince the Boneblade Reaper to release the soul (he can do so as a standard action).

At this level, the Boneblade Reaper also becomes immune to mind-affecting magic or effects.}
