\classname{Heartless Mage}
\vspace*{-8pt}
\quot{``Now that I live forever, it seems that I no longer need you. Our relationship is most likely over."}

Some necromancers seek to emulate the immortality of the lich without losing the pleasures of the flesh, and they master techniques to remove their own heart and place it within a box of polished obsidian. The price is terrible emotional stasis, but in return the Heartless Mage is free from death. Having sacrificed their own hearts in pursuit of power, they are emotionally sterile, driven by pure ambition.

\ability{Prerequisites:}{}
\listprereq
\itemability{Spells:}{Must be able to cast 5th level arcane spells including \spell{magic jar}.}
\itemability{Skills:}{Knowledge(arcana) 10 ranks, Knowledge (religion) 10 ranks}
\end{list} \vspace*{8pt}

\ability{Hit Die:}{1d6}

\ability{Class Skills:}{The Heartless Mage's class skills (and the key ability for each skill) are Concentration (Con), Craft (alchemy) (Int), Knowledge (all skills taken individually) (Int), Profession (Wis), Search (Int), and Spellcraft (Int).}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+2 &+0 &+2 &Box the Mortal Heart &+1 spellcaster level\\
2nd &+1 &+3 &+0 &+3 &Lessons of the True Heart &+1 spellcaster level\\
3rd &+1 &+3 &+1 &+3 &True Ownership &+1 spellcaster level\\
4th &+2 &+4 &+1 &+4 &Heartless Resurrection &+1 spellcaster level\\
5th &+2 &+4 &+1 &+4 &Heartless Immortal &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Heartless Mage class.

\ability{Weapon and Armor Proficiency:}{The Heartless Mage gains no proficiency with armor or weapons.}

\ability{Spellcasting:}{Every level, the Heartless Mage casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level.}

\ability{Box the Mortal Heart(Ex):}{At 1st level, the Heartless Mage removes his own heart and places it within an obsidian box worth at least 1,000 gp. The effect of this transformation is that whenever the Heartless Mage is killed, the obsidian box holding his heart may be used as a focus component to a \spell{raise dead} or \spell{resurrection} spell. Using his heart in this way means that he is returned to life without level or XP loss. Should the Heartless Mage's heart be destroyed or removed from the box, he is instantly killed wherever he stands.

In addition, each level of Heartless Mage grants a cumulative -1 penalty on all Charisma-based checks. Also, from this point onward the Heartless Mage does not age further or advance in age categories.}

\ability{Lessons of the True Heart:}{At 2nd level, a Heartless Mage may use any of the following spells as spell-like abilities: \spell{heart of stone}, \spell{hoard life}, and \spell{false life}, each usable once per day. When he uses these abilities he must use the obsidian box holding his heart as a focus component, and the box counts as the final resting place of his heart for the effects of \spell{heart of stone} spell.}

\ability{True Ownership (Sp):}{At 3nd level, the Heartless Mage improves the mystical connection to his heart. He may cast \spell{scrying} and \spell{discern location} as a spell-like abilities at will, but only if he is seeking the obsidian box holding his heart.}

\ability{Heartless Resurrection:}{At 4th level, the Heartless Mage does not die when his body is killed. Instead, his soul is transferred to the obsidian box containing his heart (treat as a tiny construct with a hardness of 20 and no movement abilities). While in this form, he may cast \spell{magic jar} at will as a spell-like ability(caster level equal to his character level, and his obsidian box is the focus). For the purposes of this effect, soulless bodies in perfect physical condition (such as clones preserved by \spell{gentle repose} or soulless bodies produced by \spell{magic jar} effects) can be targeted by this effect as if they were living. If the body possessed is a duplicate of the Heartless Mage's own body (via \spell{clone} or a \spell{simulacrum} spell, for example), successful use of this ability counts as a \spell{true resurrection} on the Heartless Mage with a material component being the body he is possessing (it is consumed).}

\ability{Heartless Immortal:}{When a Heartless Mage is possessing a body with his Heartless Resurrection ability, he may perform a 12-hour ritual costing 1,000 gp in material components that recreates his current body into duplicate of his original body. This counts as a casting of \spell{true resurrection} with a material component of the body he is using.}
