\classname{Tiger Monk} \label{comm:prestige:tigermonk}
\vspace*{-8pt}
\quot{``Waeow!"}

The Tiger Monks are a quiet, contemplative order who spend years meditating on the strength and possibilities of the spirit and honing the perfection of the body, achieving enlightenment and then using it to kick people's kidneys out through their ears. 

\ability{Prerequisites:}{}
\listprereq
\itemability{BAB:}{+6}
\itemability{Skills:}{Concentration 9 ranks}
\itemability{Feats:}{Two Weapon Fighting, Improved Natural Attack}
\itemability{Special:}{Must have a slam attack.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Tiger Monk's class skills, and the key ability for each skill are: Balance (Dex), Climb (Str), Craft (Int), Concentration (Con), Diplomacy (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (All) (Int), Listen (Wis), Move Silently (Dex), Sense Motive (Wis), Spot (Wis), Tumble (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}


\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{9.5cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+1&+2&+2&+2&Wind Kick, Endokuken, Astounding Leap, Even Muscle Tone\\
2&+2&+3&+3&+3&Swift Wind, Devastating Kick\\
3&+3&+3&+3&+3&Swift Strikes\\
4&+4&+4&+4&+4&Punishing Fist, Magic Endokuken\\
5&+5&+4&+4&+4&Tiger Fury\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Tiger Monk class:

\ability{Weapon and Armor Proficiency:}{The Tiger Monk gains proficiency in the Really Thin, Really Sharp Sword. He gains no new armor proficiencies.}

\ability{Wind Kick (Ex):}{The spirit of the Tiger carries its devotees swiftly, delivering their foot to its target. As a special move action, the Tiger Monk may perform a flying charge that terminates in a powerful kick. The Tiger Monk really does fly, but he stays at the same level as his starting elevation (meaning this will not get you far going uphill, and using it facing down an incline will earn you a bit of a drop) and can only travel his normal charge distance (but see Swift Wind, below). He must also have a line of effect to his target}

\ability{Endokuken (Su):}{The Tiger Spirit is strong, and may fill the hands with power to be released. As a standard action, the Tiger Monk may perform a medium-range touch attack which does 1d8 energy damage/2 character levels + \half ranks in concentration. An Endokuken may be performed in an Antimagic Field if the Tiger Monk can succeed on a Concentrate Check equal to DC 15 + Antimagic Field's Caster Level. An Endokuken has a recharge of 1d4 - 1 (minimum 1) rounds.}

\ability{Astounding Leap (Ex):}{The Tiger Monk jumps good. He may take 10 on jump checks at any time, and his High Jump DCs are two times the height to be cleared, rather than four times.}

\ability{Even Muscle Tone (Ex):}{The Tiger Monk conscientiously develops all the limbs in his body. He does not take off-hand penalties, and always deals at least full Str damage on his attacks.}

\ability{Swift Wind (Ex):}{A Wind Kick now carries you further. For each class level after 1st, a Tiger Monk's charge distance increases by one move increment. If his Wind Kick connects, the opponent must make a Reflex Save equal DC 10 + \half character level + Dex bonus, or be subject to an AoO. If they succeed, the Tiger Monk must make an equivalent save or the opponent gets an AoO.}

\ability{Devastating Kick (Ex):}{The Tiger Monk has lower body strength. At 2nd level, when his slam attack is described as being a kick, his Slam attack is treated as being one size larger. This includes his Wind Kick.}

\ability{Swift Strikes (Ex):}{The Tiger Monk is one quick sonofabitch. When he uses a standard action or AoO to attack, he gets an additional attack at full bonus. This is not doubled by Two-Weapon Fighting. Also, the Tiger Monk may draw or sheath a one-handed or smaller weapon as a free action, as many times a round as he has attacks.}

\ability{Punishing Fist (Ex):}{The Tiger Spirit punishes those who allow themselves to be hit. If he hits someone in the course of a normal attack or a full attack (but no AoOÕs), the target must make a Fort Save (DC 10 + \half character level + Str) or be dazed. The Tiger Monk gets AoO on people who are dazed.}

\ability{Magic Endokuken (Su):}{As a full-round action, the Tiger Monk may do an even more powerful Endokuken. It does 1d8 per character level, plus ranks in Concentration, in Even More Bullshit damage. It ignores all DR and Hardness, and only blanket energy resistance may reduce the damage it does. The Magic Endokuken has a recharge time of 1d4 + 1 rounds.}

\ability{Tiger Fury (Ex):}{The Tiger Monk now masters one of his ultimate techniques. As a full-round action, he may do a leaping uppercut as an upwards charge attack. This involves a jump check, and the Tiger Monk rises 5 feet in the air for every 5 points on his Jump check. He may attack an adjacent target, or one overhead - in either case, the opponent is carried with the punch and then launched into the air (an additional 5 feet for every 5 points of damage). It deals double Slam damage if it hits. The target is also knocked prone and takes falling damage as appropriate.}


\ability{New Equipment!}{The Really Thin, Really Sharp Sword is a Small blade weighing only two pounds. But it is *dreadfully* sharp. It does 1d8 (piercing or slashing), and has critical properties of 18-20/x3. It is a Special Monk Weapon, and an exotic weapon.}