
\classname{Green Mage} \label{class:greenmage}
\vspace{-8pt}
\quot{"Got a bag on my head and the wind at my back."}

\desc{Green Mages use the power of Wind. Many people think this element is "weak" or "childish" compared to the more visible powers of Fire and Ice. But Wind users suggest that all magic is equally powerful, but that since theirs is the only one you can't see coming, that perhaps you should fear it most of all.}

\ability{Playing a Green Mage:}{The Green Mage is a user of magic, and that magic is based on Charisma. But they are also a heavy user of ranged attacks, and those manipulations are Dexterity based. Green Mages have a strong tendency to use staves.}

\ability{Alignment:}{Green Mages favor secrecy and conniving. But since the game rants extensively on how conniving can be Lawful or Chaotic, so can they.}

\ability{Starting Equipment:}{5d4x10 gp (125 gold)}

\ability{Starting Age:}{As Sorcerer.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Green Mage's class skills (and the key ability for each skill) are Balance (Dex), Bluff (Cha), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Hide (Dex), Jump (Str), Knowledge (Any) (Int), Heal (Wis), Listen (Wis), Move Silently (Dex), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Survival (Wis), and Use Magic Device (Cha).}

\ability{Skills/Level:}{4 + Intelligence Bonus}



\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{1cm}p{1cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+2 &+2 &Wind Blast, Wind Resistance, Message, Ghost Sound, Air Magic\\
2nd &+1 &+0 &+3 &+3 &Gust of Wind, Shocking Grasp\\
3rd &+2 &+1 &+3 &+3 &Wind Wall, Whispering Winds\\
4th &+3 &+1 &+4 &+4 &More Resistance, Clairaudience\\
5th &+3 &+1 &+4 &+4 &Air Walk\\
6th &+4 &+2 &+5 &+5 &Thunder Clap, Silence\\
7th &+5 &+2 &+5 &+5 &Scary Noises, Pin Drops\\
8th &+6/+1 &+2 &+6 &+6 &Slow, Secrets on the Wind\\
9th &+6/+1 &+3 &+6 &+6 &Chain Lightning, Wind Tunnel\\
10th &+7/+2 &+3 &+7 &+7 &Gaseous Form, Sending\\
11th &+8/+3 &+3 &+7 &+7 &Speed of the Wind, Weather Control\\
12th &+9/+4 &+4 &+8 &+8 &Animate Air, Wind Walk\\
13th &+9/+4 &+4 &+8 &+8 &Control Winds\\
14th &+10/+5 &+4 &+9 &+9 &Breath of Life, Calming Voice\\
15th &+11/+6/+6 &+5 &+9 &+9 &Storm of Vengeance, Whirlwind\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Green Mage class.

\ability{Weapon and Armor Proficiency:}{Green Mages are proficient with Simple Weapons. A Green Mage's Spell-like abilities suffer from Arcane Spell Failure if they are wearing armor with which they are not proficient. A Green Mage may add the masterwork or enhancement bonus (if any) of any staff they are wielding to any attack or damage rolls they make with their Supernatural and Spell-Like abilities.}

\ability{Wind Blast (Sp):}{A Green Mage can throw blasts of wind as an attack action. A Wind Blast travels out to short range, and inflicts 1d4 of Sonic damage per level. A Wind Blast strikes its target with a ranged touch attack.}

\ability{Wind Resistance (Ex):}{A Green Mage has resistance to Sonic and Electricity equal to her level. In addition, she treats wind as being one step less intense.}

\ability{Message (Sp):}{A Green Mage can cast \spell{message} at will.}

\ability{Ghost Sound (Sp):}{A Green Mage can use \spell{ghost sound} at will.}

\ability{Air Magic (Ex):}{A Green Mage is considered to have all spells with the [Air] or [Electricity] key word on her spell list for purposes of activating magic items. A Green Mage's caster level is always equal to her character level. The Save DC of any of her effects is DC 10 + \half\ Level + Charisma Modifier.}

\ability{Gust of Wind (Sp):}{A 2nd level Green Mage can cast \spell{Gust of Wind} as a standard action, at will.}

\ability{Shocking Grasp (Su):}{A 2nd level Green Mage can shock people with a touch. As a melee attack action, the Green Mage can make a touch attack that inflicts 1d6 of Electricity damage per level. The Green Mage can use her Dexterity modifier instead of her Strength modifier on her attack roll. A Shocking Grasp attack can be made with a staff.}

\ability{Wind Wall (Sp):}{A 3rd level Green Mage can create a \spell{wind wall} at will, as a standard action. The Green Mage can only have 1 such wall in existence at a time for every three whole levels she has. If she creates a new wall while she is already at her maximum, one wall of her choice dissipates.}

\ability{Whispering Winds (Sp):}{A 3rd level Green Mage can use \spell{whispering winds} at will.}

\ability{More Resistance (Ex):}{At 4th level a Green Mage may personally ignore Wind Effects. Also her Sonic Resistance improves to twice her level.}

\ability{Clairaudience (Sp):}{At 4th level, a Green Mage can hear things at great distances. She can use \spell{clairvoyance/clairaudience} at will as a free action, but only the audio version.}

\ability{Air Walk (Su):}{From 5th level on, a Green Mage constantly benefits from \spell{air walk}.}

\ability{Thunder Clap (Sp):}{At 6th level, a Green Mage can create a tremendous clap of thunder that damages and deafens. The Thunder Clap can be created within Medium range. It is a 20 foot radius burst, and it inflicts 1d8 + 1d8/2 levels in Sonic Damage (Fortitude save partial for half damage). Those creatures that fail their save are knocked prone and deafened for 1 round/level. At 11th level, the Wind Mage may make her Thunder Clap larger, doing an extra d8 of damage and having a radius of 30 feet.}

\ability{Silence (Sp):}{A 6th level Green Mage can create a zone of silence, as per \spell{silence}. The Green Mage can only have one such zone active for every three full levels she has attained, and if she creates a new one when she already has her maximum she chooses one to be dispelled.}

\ability{Scary Noises (Sp):}{A 7th level Green Mage can use \spell{fear} as a spell-like ability. Once she has used it, she may not use it again for 10 rounds. Scary Noises is a [Sonic] ability.}

\ability{Pin Drop (Ex):}{A 7th level Green Mage gains a bonus to her Listen checks equal to her ranks in Listen.}

\ability{Slow (Sp):}{A Green Mage of 8th level can cast \spell{slow} as a Swift Action at will.}

\ability{Secrets on the Wind (Sp):}{An 8th level Green Mage can \spell{scry} at will with a minute's concentration. Unlike a normal scrying, the Green Mage cannot see through to the target, but instead can hear from that area as if she was there herself. There is no literal sensor in this case, the scrying is entirely passive.}

\ability{Chain Lightning (Sp):}{A 9th level Green Mage can use \spell{chain lightning} as a standard action, at will.}

\ability{Wind Tunnel (Sp):}{At 9th level, a Green Mage may invoke \spell{wind tunnel} once per day as a Swift Action.}

\ability{Gaseous Form (Sp):}{A 10th level Green Mage can use \spell{gaseous form} at will. Gaseous Form used by a Green Mage is permanent until dismissed, and Green Mages often use it to bottle captured enemies.}

\ability{Sending (Sp):}{A 10th level Green Mage can use \spell{sending} at will simply by speaking into the wind.}

\ability{Speed of the Wind (Sp):}{An 11th level Green Mage can use \spell{haste} as a Swift Action once per hour.}

\ability{Weather Control (Sp):}{An 11th level Green Mage can \spell{control weather} every day.}

\ability{Animate Air (Sp):}{At 12th level, a Green Mage can animate the very air. By spending a Standard Action, she essentially creates a Huge Air Elemental that follows her orders. She can only have one at a time, and if she creates a new one, the old one dissipates. She can only create one an hour in any case. At 16th level, her Elemental can be made as a Greater Elemental instead. At 20th level, it can be an Elder Elemental.}

\ability{Wind Walk (Sp):}{A 12th level Green Mage can invoke or terminate \spell{wind walk} at will as a Swift Action.}

\ability{Control Winds (Sp):}{A 13th level Green Mage can cast \spell{control winds} as a Druid of her level. This ability can only be invoked once per hour.}

\ability{Breath of Life (Sp):}{A 14th level Green Mage can \spell{raise dead} a number of times per day equal to her Charisma modifier.}

\ability{Calming Voice (Sp):}{Once per hour, a 14th level Green Mage can cast \spell{charm monster}.}

\ability{Storm of Vengeance (Sp):}{Once per hour, a 15th level Green Mage can invoke a \spell{Storm of Vengeance}.}

\ability{Whirlwind (Sp):}{A 15th level Green Mage can use \spell{whirlwind} or \spell{greater whirlwind} at will.}
