\classname{Master of Wrath} \label{comm:class:masterofwrath}
\vspace{-8pt}
\quot{"Some Quote Here"}

Class Description Goes Here.

\ability{Alignment:}{Whatever you like.}

\ability{Races:}{Any. Usually the smarter ones.}

\ability{Starting Gold:}{4d4x10 gp (100 gold)}

\ability{Starting Age:}{As Wizard.}

\ability{Hit Die:}{d8.}

\ability{Class Skills:}{The Master of Wrath’s skills (and the key ability for each skill) are Appraise (Int), Climb (Str), Concentration (Con), Craft (Int), Jump (Str), Intimidate (Cha), Knowledge (all) (Int), Listen (Wis), Move Silently (Dex), Profession (-), Search (Int), Sense Motive (Wis), Spellcraft (Int), Spot (Wis), Swim (Str).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special\\
1&+0&+2&+0&+2&Initiate of the Breaking Point, Sudden Gale, Elemental Casting\\
2&+1&+3&+0&+3&Ruinous Blow\\
3&+2&+3&+1&+3&Shatter the Air\\
4&+3&+4&+1&+4&Render the Earth\\
5&+3&+4&+1&+4&Master of the Breaking Point\\
6&+4&+5&+2&+5&Eye of the Storm\\
7&+5&+5&+2&+5&Speak with Earth and Air\\
8&+6/+1&+6&+2&+6&Mind of the Maelstrom\\
9&+6/+1&+6&+3&+6&Riot of Stone\\
10&+7/+2&+7&+3&+7&Call the Storm\\
11&+8/+3&+7&+3&+7&Master the Storm\\
12&+9/+4&+8&+4&+8&One with the Storm\\
\end{tabular}
\end{small}
\end{table}

\smallskip \noindent All of the following are Class Features of the Master of Wrath class:

\ability{Weapon and Armor Proficiency:}{Masters of Wrath are proficient with all simple weapons and all axes. Masters of Wrath are proficient with light armor but not with shields of any kind.}

\ability{Initiate of the Breaking Point (Sp):}{At 1st level, you learn to find the point of instability in all objects. By striking the ground as an attack action, you may cause a minor explosion that hurls shrapnel into the air, striking all creatures within 10' except for yourself. Affected creatures must succeed on a Reflex save (DC 10 + 1/2 Level + Intelligence Modifier) or suffer 1d6 points of Sonic and Piercing damage and fall prone.}

\ability{Sudden Gale (Sp):}{With violent slash of her arm, a 1st level Master of Wrath may create a powerful blast of air in a 60' line as a standard action. You make bullrush attempts against every creatures affected, except that you may use your Intelligence modifier in place of your Strength modifier. You are treated as large for the purposes of these bullrush checks.

In addition, this can do anything else that a 50 mph gale would be expected to do, such as extinguishing torches, knocking over lightweight objects, and blowing gases to the edge of its range.}

\ability{Elemental Casting (Ex):}{A Master of Wrath is considered to have every spell with the Earth, Sonic, and Electricity Descriptors on his spell list for the purpose of activating magic items.}

\ability{Ruinous Blow (Sp):}{A 2nd level Master of Wrath gains the power to shatter objects into mere dust with a touch. As a melee touch attack, you may destroy any object weighing up to 10 pounds per character level. Unattended mundane objects get no save, but an attended or magical object is entitled to a Fortitude save (DC 10 + 1/2 Level + Intelligence Modifier) to resist the effect.}

\ability{Shatter the Air (Sp):}{At 3rd level, the Master of Wrath learns to find the weak points in the air itself. As an attack action, you may create a violent burst, 10' in radius, at any point in the air within Close range. Every creature in the area takes 1d8 points of Sonic damage and must succeed on a Fortitude save (DC 10 + 1/2 Level + Intelligence Modifier) to avoid being stunned for 1 round.}

\ability{Render the Earth (Sp):}{At 4th level, the Master of Wrath learns to make terrain treacherous. As a standard action, you may transform one 10' square per character level of ground into grasping, trapping terrain: wooden floors crumble into jagged gaps, stone becomes oozing clay, and so on. Any creature standing in this area must succeed on a Reflex save or be caught for 1d2 rounds, unable to move, attack, or cast spells. A creature that succeeds on its save can move through the area at half speed, and it can’t run or charge.

Creatures that can burrow or otherwise move through the ground normally are unaffected.

The depth of this area depends on the terrain and material, but is never more than one foot.}

\ability{Master of the Breaking Point (Sp):}{A 5th level Master of Wrath can trigger the breaking point of any solid, unattended, inanimate object within Long Range as a Full Round Action. This object explodes into a 20' radius burst and inflicts 1d4 points of Sonic and Piercing damage per level, including to the object itself. All creatures within the area are entitled to a Reflex save to halve this damage (DC 10 + 1/2 Level + Intelligence Modifier).

In addition, the affected area is filled with hazardous debris. A creature can walk within or through the blast area at half normal speed with a DC 10 Balance check. Failure means it can’t move that round (and must then make a Reflex save or fall), while failure by 5 or more means it falls (see the Balance skill for details, including the possibility of being flat-footed).}

\ability{Eye of the Storm (Sp):}{A 6th level Master of Wrath gains some protection from the elemental forces. She may cast resist energy as spell-like ability with a caster level equal to her character level.}

\ability{Speak with Earth and Air (Sp):}{A 7th level Master of Wrath can contact other plane to communicate with the denizens of the Elemental Plane of Earth or the Elemental Plane of Air. A Master of Wrath is in no danger of becoming insane or damaged by this experience. Invoking this ability requires a 10 minute ritual and has a caster level equal to your character level.}

\ability{Mind of the Maelstrom (Sp):}{At 8th level, the Master of Wrath's own mind becomes a reflection of the destructive and chaotic forces she studies. She is immune to all mind-affecting effects, as well as mental ability damage and ability drain.}

\ability{Riot of Stone (Sp):}{At 9th level, the Master of Wrath may stir the stone to violence. As a standard action, you may cause jagged spikes of stone to rise from the ground, filling one 20-ft. square per character level within Medium range. Any creature moving on foot into or through this area moves at half speed and suffers 1d8 points of piercing damage for each 5 feet of movement.

Alternately, you make create a single spike 1' wide at its base that rises to a height of 10', though it stops if it reaches a ceiling. Any creature in the way of this spike's violent eruption suffers 1d6 Piercing damage per character level. Affected creatures are entitled to a Reflex save to halve this damage (DC 10 + 1/2 Level + Intelligence Modifier), but any creature that fails this save is impaled on the spike and trapped in its current location. Flying creatures have a +4 bonus on this save.

The creature may free itself with an Escape Artist check (DC 15), a Strength check (DC 25), or by getting rid of the spike somehow (hardness 8, 90 HP).}

\ability{Call the Storm:}{At 10th level, the Master of Wrath may cast control weather, though the range and radius are halved. Invoking this ability requires a 10 minute ritual and has a caster level equal to your character level.

In addition, you may call down a 5' wide, 30' long bolt of lightning within Medium range that deals 2d6 points of Electricity damage. Doing so is a swift action.}

\ability{Master the Storm:}{At 11th level, the Master of Wrath gains control over a Huge Storm Elemental (MM3). It is completely loyal to the Master of Wrath and the two may communicate regardless of ambient noise or poor weather.

The elemental is called in a 10-minute ritual that requires a storm of some kind, such that those created by Call the Storm. If the elemental is lost or destroyed, another may be called, but the Master of Wrath may only control one at any given time.}

\ability{One with the Storm (Sp):}{At 12th level, the Master of Wrath gains some of the physical traits of the power she harnesses. She gains a flight speed equal to her land speed (perfect maneuverability) and is healed by electricity and sonic damage. She is unaffected by extreme weather conditions of all kinds, including wind, rain, and natural extremes of heat and cold. She is constantly surrounded by gusts of wind and debris, unless she chooses to suppress this effect (a free action).}
