
\classname{Star Mage} \label{class:starmage}
\vspace{-8pt}
\quot{"I will open a gate to the farthest reaches of the deepest netherworld, and you will gaze upon the face of the first and last being. And it will not go well for you."}

\desc{Star Mages use the inexplicable elemental magic of "Star." It is the harsh light of space and also that which existed before matter. The great sages of the Star Mages say that it will persist long after matter itself is a distant memory.}

\desc{Star Mages are distant and anti-social compared with other mages.}

\ability{Playing a Star Mage:}{The Star Mage is a user of magic, and that magic is based on Intelligence. Star Mages also have access to a number of secondary abilities that revolve around Wisdom. These abilities help them become creepier and more into crazy space stuff. Star Mages have a strong tendency to use staves.}

\ability{Alignment:}{Star Mages are totally inscrutable and come from every alignment.}

\ability{Starting Equipment:}{5d4x10 gp (125 gold)}

\ability{Starting Age:}{As Wizard.}

\ability{Hit Die:}{d6}

\ability{Class Skills:}{The Star Mage's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Jump (Str), Knowledge (Any) (Int), Heal (Wis), Search (Int), Sense Motive (Wis), Spot (Wis), Survival (Wis), and Use Magic Device (Cha).}

\ability{Skills/Level:}{2 + Intelligence Bonus}



\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{1cm}p{1cm}p{0.7cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+0 &+2 &Baleful Glare, Light, Star Magic, Ray of Light\\
2nd &+1 &+0 &+0 &+3 &Attune Form, Armor Break, Day Break\\
3rd &+1 &+1 &+1 &+3 &Searing Light, Dimension Hop\\
4th &+2 &+1 &+1 &+4 &Silent Image, Wrath of the Heavens\\
5th &+2 &+1 &+1 &+4 &Cryptic Demands, End of Sight\\
6th &+3 &+2 &+2 &+5 &Contact Other Plane, Tenuous Sanity, Draining Light\\
7th &+3 &+2 &+2 &+5 &Dimension Door\\
8th &+4 &+2 &+2 &+6 &Flashburst, Delaying Light\\
9th &+4 &+3 &+3 &+6 &End of Life\\
10th &+5 &+3 &+3 &+7 &Aid From Beyond, Resist Break\\
11th &+5 &+3 &+3 &+7 &True Seeing\\
12th &+6/+1 &+4 &+4 &+8 &Gateway\\
13th &+6/+1 &+4 &+4 &+8 &End of Hope\\
14th &+7/+2 &+4 &+4 &+9 &Prismatic Spray\\
15th &+7/+2 &+5 &+5 &+9 &End of Time\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Star Mage class.

\ability{Weapon and Armor Proficiency:}{Star Mages are proficient with Simple Weapons. A Star Mage's Spell-like abilities suffer from Arcane Spell Failure if they are wearing armor with which they are not proficient. A Star Mage may add the masterwork or enhancement bonus (if any) of any staff they are wielding to any attack or damage rolls they make with their Supernatural and Spell-Like abilities.}

\ability{Baleful Glare (Sp):}{The Star Mage can as a standard action blast a target with inerrant light that sears them to their core. The Baleful Glare always hits and has a Medium range. It inflicts d8 + Wisdom Modifier damage, +1 damage/level. The target can make a Fortitude Save to halve the damage.}

\ability{Light (Sp):}{The Star Mage can use \spell{Dancing Lights} and \spell{Glowing Orb} at will. The Star Mage can have a number of total light sources sustained equal to her Wisdom Modifier. If she creates another one when she has the maximum number, one light source of her choice winks out. Each light source is otherwise permanent. The Glowing Orbs do not require glass spheres to be provided for them.}

\ability{Star Magic (Ex):}{The Star Mage's Save DC on any of their Spell-Like and Supernatural abilities is 10 + \half\ Level + Intelligence Modifier. A Green Mage's caster level is always equal to her character level. For purposes of activating magic items, the Star Mage is a Wizard.}

\ability{Ray of Light (Sp):}{A Star Mage can use \spell{ray of light} as a standard action at will.}

\ability{Attune Form (Sp):}{A 2nd level Star Mage can cast \spell{attune form} at will.}

\ability{Armor Break (Sp):}{A 2nd level Star Mage can phase a target's armor away. As a standard action, the Star Mage can make one target creature within Short Range glow as per \spell{faerie fire} for one round. During that period, all attacks against them are resolved as touch attacks.}

\ability{Day Break (Sp):}{A 2nd level Star Mage can awaken any sleeping creature within Short range as a move action. From 6th level on, this can be done as a Swift action.}

\ability{Searing Light (Sp):}{From 3rd level on, a Star Mage can cast \spell{searing light} as an attack action.}

\ability{Dimension Hop (Sp):}{A 3rd level Star Mage can teleport themselves as per a \spell{greater dimension door} effect that was always on (with themselves as the only target).}

\ability{Silent Image (Sp):}{Beginning at 4th level, a Star Mage can use \spell{silent image} at will.}

\ability{Wrath of the Heavens (Sp):}{When a 4th level Star Mage uses Baleful Glare, they may target a number of enemies with it equal to their level.}

\ability{Cryptic Demands (Ex):}{A 5th level Star Mage can use Knowledge (Planes) in lieu of Diplomacy when dealing with Elementals and Outsiders. Also, they can use their Intelligence modifier in place of their Charisma for purposes of Leadership.}

\ability{End of Sight (Sp):}{A 5th level Star Mage can create a 20' radius burst of light anywhere out to Medium range. Any creatures within the burst must make a Fortitude save or be blinded for 2d8 rounds.}

\ability{Contact Other Plane (Sp):}{A 6th level Star Mage can use \spell{contact other plane} once per day for each point of Wisdom modifier they have. Their Caster level must be no worse than 1 less than the Sanity DC of the plane to be contacted.}

\ability{Tenuous Sanity (Ex):}{A 6th level Star Mage does not lose mental stats, whether from damage, drain, or other effects. Also they are immune to the confused and dazed conditions.}

\ability{Draining Light:}{From 6th level on, any target who fails their save against the Star Mage's Baleful Glare also suffers 4 points of Strength Damage.}

\ability{Dimension Door (Sp):}{A 7th level Star Mage can cast \spell{dimension door} at will.}

\ability{Flashburst (Sp):}{An 8th level Star Mage can use \spell{flashburst} at will.}

\ability{Delaying Light:}{From 8th level on, any target who fails their save against the Star Mage's Baleful Glare is also slowed for 1 round.}

\ability{End of Life (Sp):}{As a standard action, a 9th level Star Mage can target an enemy within Medium range and cause them to die. The target makes a Fortitude save, and if they fail they are dead. This is a [Death] effect. Even if they survive, they still suffer 1d8/2 levels in damage.}

\ability{Aid from Beyond (Sp):}{Once per day, a 10th level Star Mage can summon a rampaging monster from the Far Realm. It fights her enemies and breaks stuff for an hour and then vanishes. The far realm beast has a CR lower than the star mage's level.}

\ability{Resist Break (Ex):}{From 10th level onwards, creatures who have Spell Resistance or Energy Resistance have those abilities negated for 10 rounds if they fail a save against Baleful Glare.}

\ability{True Seeing (Sp):}{An 11th level Star Mage benefits from \spell{true seeing} at all times.}

\ability{Gateway (Sp):}{At 12th level, a Star Mage can open up the portal version of \spell{gate} a number of times per day equal to her Wisdom modifier.}

\ability{End of Hope (Sp):}{A 13th level Star Mage can open up a vortex within Long Range that transports all creatures within a 30' burst from its center to the far reaches of the multiverse. Creatures are entitled to a Will Save to avoid being banished to a plane of the Star Mage's choice. At the Star Mage's option, any creature so transported can be returned to the point they were before the vortex opened with a Swift Action.}

\ability{Prismatic Spray (Sp):}{At 14th level, a Star Mage can use \spell{prismatic spray} at will.}

\ability{End of Time (Sp):}{A 15th level Star Mage can open up a rift to the very end of everything, causing the very ultimate of termini to be unleashed upon those underneath its dread regard. The Star Mage chooses a spot within Long range and a column 40' in radius and 120' high erupts in doom. All creatures (even undead and constructs) within that area must make a Fortitude Save or Die. Those who pass their save merely suffer 1d6/level in damage.}
