
\classname{Thaumaturge} 
\vspace{-8pt}

\ability{Alignment:}{A Thaumaturge may be of any alignment.}

\ability{Races:}{Any}

\ability{Starting Gold:}{4d4x10 (100 gold)}

\ability{Starting Age:}{As Wizard}

\ability{Hit Die:}{d4}

\ability{Class Skills:}{Concentration (Con), Craft (Int), Knowledge (all) (Int), Profession (Wis), Spellcraft (Int), Use Magic Device (Cha), any two others.}

\ability{Skills/Level:}{2 + Intelligence Bonus}
 
\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.2cm}p{0.7cm}p{0.7cm}p{0.7cm}p{4.7cm}llllllllll}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special & \multicolumn{10}{c}{Spells Per Day}\\
       &       &   &   &    &                         &0 &1 &2 &3 &4 &5 &6 &7 &8 &9 \\
1st    &+0     &+0 &+0 &+2  & Familiar, Spellcasting  &2 &0 &- &- &- &- &- &- &- &- \\
2nd    &+1     &+0 &+0 &+3  & Bonus Metamagic         &2 &1 &- &- &- &- &- &- &- &- \\
3rd    &+1     &+1 &+1 &+3  & Sudden Metamagic (1/day)&2 &1 &0 &- &- &- &- &- &- &- \\
4th    &+2     &+1 &+1 &+4  & Free Metamagic (-1)     &2 &1 &1 &- &- &- &- &- &- &- \\
5th    &+2     &+1 &+1 &+4  &                         &2 &1 &1 &0 &- &- &- &- &- &- \\
6th    &+3     &+2 &+2 &+5  & Bonus Metamagic         &2 &1 &1 &1 &- &- &- &- &- &- \\
7th    &+3     &+2 &+2 &+5  & Sudden Metamagic (2/day)&2 &2 &1 &1 &0 &- &- &- &- &- \\
8th    &+4     &+2 &+2 &+6  & Free Metamagic (-2)     &2 &2 &1 &1 &1 &- &- &- &- &- \\
9th    &+4     &+3 &+3 &+6  &                         &2 &2 &2 &1 &1 &0 &- &- &- &- \\
10th   &+5     &+3 &+3 &+7  & Bonus Metamagic         &2 &2 &2 &1 &1 &1 &- &- &- &- \\
11th   &+5     &+3 &+3 &+7  & Sudden Metamagic (3/day)&2 &2 &2 &2 &1 &1 &0 &- &- &- \\
12th   &+6/+1  &+4 &+4 &+8  & Free Metamagic (-3)     &2 &2 &2 &2 &1 &1 &1 &- &- &- \\
13th   &+6/+1  &+4 &+4 &+8  &                         &2 &2 &2 &2 &2 &1 &1 &0 &- &- \\
14th   &+7/+2  &+4 &+4 &+9  & Bonus Metamagic         &2 &2 &2 &2 &2 &1 &1 &1 &- &- \\
15th   &+7/+2  &+5 &+5 &+9  & Sudden Metamagic (4/day &2 &2 &2 &2 &2 &2 &1 &1 &0 &- \\
16th   &+8/+3  &+5 &+5 &+10 & Free Metamagic (-4)     &2 &2 &2 &2 &2 &2 &1 &1 &1 &- \\
17th   &+8/+3  &+5 &+5 &+10 &                         &2 &2 &2 &2 &2 &2 &2 &1 &1 &0 \\
18th   &+9/+4  &+6 &+6 &+11 & Bonus Metamagic         &2 &2 &2 &2 &2 &2 &2 &1 &1 &1 \\
19th   &+9/+4  &+6 &+6 &+11 & Sudden Metamagic (5/day &2 &2 &2 &2 &2 &2 &2 &2 &1 &1 \\
20th   &+10/+5 &+6 &+6 &+12 & Free Metamagic (-5)     &2 &2 &2 &2 &2 &2 &2 &2 &2 &2 \\
\end{tabular}
\end{small}
\end{table}
  
\ability{Weapon and Armor Proficiency:}{Thaumaturges are proficient with all simple weapons, but not with any armors.}

\ability{Spellcasting:}{A thaumaturge casts arcane spells which are drawn from the core cleric, druid, and sorcerer/wizard spell lists; if a spell appears at different levels on these lists, the thaumaturge may cast it at the lowest level it appears on any of them. He can cast any spell he knows without preparing it ahead of time, the way a wizard or a cleric must (see below).

To learn or cast a spell, a thaumaturge must have an Intelligence, Wisdom, or Charisma score equal to at least 10 + the spell level. The Difficulty Class for a saving throw against a thaumaturge's spell is 10 + the spell level + the thaumaturge's highest mental ability modifier. 
Unlike a wizard or a cleric, a thaumaturge need not prepare his spells in advance. He can cast any spell he knows at any time, assuming he has not yet used up his spells per day for that spell level. He does not have to decide ahead of time which spells he'll cast. 
Like other spellcasters, a thaumaturge can cast only a certain number of spells of each spell level per day. His base daily spell allotment is given on Table: The Thaumaturge. In addition, he receives bonus spells per day if he has a high mental ability score (use the highest one). Nevertheless the thaumaturge has the fewest spells per day of any spellcasting class. He makes up for this with his spell selection: thanks to his intuitive connection to magic, a thaumaturge can choose spontaneously from any spell on the core cleric, druid, or sorcerer/wizard lists, so long as he has a spell slot of that level (or any higher level, if he wishes to use a higher slot) available to cast it. However, thaumaturges take longer to cast their highest-level spells than usual: if a spell's casting time is less than one full-round action and is of the highest level a thaumaturge can cast, its casting time increases to one full-round action. 

A thaumaturge can add non-core cleric, druid, or sorcerer/wizard spells to his spontaneous casting list by spell research, just as a wizard can, but using his highest mental ability to modify the Spellcraft check instead of intelligence.}

\ability{Familiar:}{A thaumaturge can obtain a familiar. Doing so takes 24 hours and uses up magical materials that cost 100 gp. A familiar is a magical beast that resembles a small animal and is unusually tough and intelligent. The creature serves as a companion and servant. 
The thaumaturge chooses the kind of familiar he gets. As the thaumaturge advances in level, his familiar also increases in power, as per the familiar class ability boxed text. 

A slain or dismissed familiar cannot be replaced for a month. A slain familiar can be raised from the dead just as a character can be, and it does not lose a level or a Constitution point when this happy event occurs. 

A character with more than one class that grants a familiar may have only one familiar at a time, but the levels in such classes stack for the familiar benefits.}

\ability{Bonus Metamagic:}{At 2nd level and every four levels thereafter, the thaumaturge gains a bonus non-sudden metamagic feat for which he meets the prerequisites.}

\ability{Sudden Metamagic:}{At 3rd level and every four levels thereafter, the thaumaturge gains a bonus sudden metamagic feat for which he meets the prerequisites.}

\ability{Free Metamagic:}{From 4th level on, a thaumaturge can reduce the metamagic adjustment of his spells by 1 level, as long as he would be capable to cast each spell without this reduction. The reduction is applied once, after all metamagic has been applied to the spell. At 8th level, and every 4 levels thereafter, the maximum reduction increases by 1 level; it doesn't have to be applied fully.}
