%\newcommand{\babfeat}[7]{\noindent\textbf{#1} \\ \emph{#2} \\ \textbf{Benefit:}#3 \\ \textbf{+1:}#4  \\ \textbf{+6:}#5 \\ \textbf{+11:}#6 \\ \textbf{+16:}#7 \bigskip }
%\newcommand{\skillfeat}[7]{\noindent\textbf{#1} \\ \emph{#2} \\ \textbf{Benefit:} #3 \\ \textbf{4:} #4  \\ \textbf{9:} #5 \\ \textbf{14:} #6 \\ \textbf{19:} #7 \bigskip }



%\minitabular{cheese & spice!}

\section{The Failure of Feats}
\vspace*{-10pt}
\quot{``How about instead of being able to travel anywhere in the multiverse, transform yourself into anything you can think of, stop time, and slay everyone you can see, we just give a nice +1 to hit with your secondary weapon? Deal?"}

Feats were an interesting idea when they were ported to 3rd edition D\&D. But let's face it; they don't go nearly far enough. Feats were made extremely conservative in their effects on the game because the authors didn't want to offend people with too radical a change. Well, now we've had third edition for 6 years, and we're offended. Feats are an interesting and tangible way to get unique abilities onto a character, but they have fallen prey to two key fallacies that has ended up turning the entire concept to ashes in our mouths. The first is the idea that if you think of something kind of cool for a character to do, you should make it a feat. That sounds compelling, but you only get 7 feats in your whole life. If you have to spend a feat for every cool thing you ever do, you're not going to do very many cool things in the approximately 260 encounters you'll have on your way from 1st to 20th level. The second is the idea that a feat should be equivalent to a cantrip or two. This one is even less excusable, and just makes us cry. A +1 bonus is something that you seriously might forget that you even have. Having one more +1 bonus doesn't make your character unique, it makes you a sucker for spending one of the half dozen feats you'll ever see on a bonus the other players won't even mention when discussing your character.

We all understand this problem, what do we do about it? Well, for starters, Feats have to do more things. Many characters are 5th level or so and they only have 2 feats. Those feats should describe their character in a much more salient way than ``I'm no worse shooting into melee than I am shooting at people with cover that isn't my friends." This was begun with the tactical feats, but it didn't go far enough. It's not enough to add additional feats that do something halfway interesting for high level characters to have -- we actually have to replace the stupid one dimensional feats in the PHB with feats that rational people would care about in any way. Spending a single feat should be enough to make you a ``sniper character" because for a substantial portion of your life you only get one feat. Secondly, we have to clear away feats that don't provide numeric bonuses large enough to care about. The minimum bonus you'll ever notice is +3, because that's actually larger than the difference between having rolled well and having rolled poorly on your starting stats. Numeric bonuses smaller than that are actually insulting and need to be removed from the feats altogether. 3.5 Skill Focus was a nice start, but that's all it was -- a start.

Furthermore, the fundamental structure of feats has been a disaster. The system of prerequisites often ensures that characters won't get an ability before it would be level appropriate for them to do so, but actually does nothing to ensure that such characters are in fact getting level appropriate abilities. Indeed, if a 12th level character decides that they want to pursue a career in shooting people in the face, they have to start all over gaining an ability that is supposed to be level appropriate for a 1st level character. Meanwhile, when a wizard of 12th level decides to pursue some new direction in spellcasting -- he learns a new 6th level spell right off -- and gets an ability that's level appropriate for a 12th level character.

\subsection{Exploits}
Getting proficiency with a weapon isn't worth a feat. They hand that crap out with your character class for free. Seriously, even exotic weapon proficiencies aren't a big deal. Therefore, we're instituting Exploits as something that can be acquired in-game. These are for any of the binary abilities that simply don't have a massive impact on your character's performance at any level.

If you have Martial Weapon Proficiency, it's really unreasonable for it to be that hard to learn how to use a new weapon, whether it's exotic or not. If you spend a week training with a weapon, you can make an Int check (DC 10) to simply gain the Exploit of Exotic Weapon Proficiency. And no, you can't take 10 on that.

If you don't have Martial Weapon Proficiency and you want to use a new weapon, that's touchier. But if you have a weapon for an entire level, you should just gain proficiency in it when you gain your next level whatever level you happen to select.

\subsection{The New Feat System}

So where are we going with this? First of all, feat chains are gone. That seemed like a good idea, but it wasn't. Secondly, the vast majority of feats don't have prerequisites at all, they scale. A [Combat] feat scales to your Base Attack Bonus, a [Skill] feat scales to your ranks in a skill, and a [Metamagic] feat scales to the highest level spell you can cast. And that's because those are the only things in the game that actually have anything to do with the level your character is in any way that we feel good about.

\section{[Combat] Feats} \label{feats:combat}

\begin{multicols}{2}
\hypertarget{feat:blindfighting}{}\babfeat{Blind Fighting [Combat]}{
You don't have to see to kill.}{
You may reroll your miss chances caused by concealment.}{
While in darkness, you may move your normal speed without difficulty.}{
You have Blindsense out to 60', this allows you to know the location of all creatures within 60'.}{
You have Tremorsense out to 120', this allows you to ``see" anything within 120' that is touching the earth.}{
You cannot be caught flat footed.}

\hypertarget{feat:blitz}{}\babfeat{Blitz [Combat]}{
You go all out and try to achieve goals in a proactive manner.}{
While charging, you may opt to lose your Dexterity Bonus to AC for one round, but inflicting an extra d6 of damage if you hit.}{
You may go all out when attacking, adding your Base Attack Bonus to your damage, but provoking an Attack of Opportunity.}{
Bonus attacks made in a Full Attack for having a high BAB are made with a -2 penalty instead of a -5 penalty.}{
Every time you inflict damage upon an opponent with your melee attacks, you may immediately use an Intimidate attempt against that opponent as a bonus action.}{
You may make a Full Attack action as a Standard Action.}

\hypertarget{feat:combatlooting}{}\babfeat{Combat Looting [Combat]}{
You can put things into your pants in the middle of combat.}{
You may sheathe or store an object as a free action.}{
You get a +3 bonus to  \hyperlink{combat:disarm}{Disarm} attempts. Picking up objects off the ground does not provoke an attack of opportunity.}{
As a Swift action, you may take a ring, amulet/necklace, headband, bracer, or belt from an opponent you have successfully \hyperlink{combat:grapple}{grappled}. You may pick up an item off the ground in the middle of a move action.}{
If you are grappling with an opponent, you may activate or deactivate their magic items with a successful Use Magic Device check. You may make Appraise checks as a free action.}{
You can take 10 on Use Magic Device and Sleight of Hand checks.}


\hypertarget{feat:combatschool}{}\babfeat{Combat School [Combat]}{
You are a member of a completely arbitrary fighting school that has a number of recognizable signature fighting moves.}{
First, name your fighting style (such as ``Hammer and Anvil Technique'' or ``Crescent Moon Style'', or ``Way of the Lightning Mace''). This fighting style only works with a small list of melee weapons that you have to describe the connectedness to the DM in a half-way believable way. Now, whenever you are using that technique in melee combat, you gain a +2 bonus on attack rolls.}{
Your immersion in your technique gives you great martial prowess, you gain a +2 to damage rolls in melee combat.}{
When you strike your opponent with the signature moves of your fighting school in melee, they must make a Fortitude Save (DC 10 + 1/2 your level + your Strength bonus) or become dazed for one round.}{
You may take 10 on attack rolls while using your special techniques. The DC to disarm you of a school-appropriate weapon is increased by 4.}{
You may add +5 to-hit on any one attack you make after the first each turn. If you hit an opponent twice in one round, all further attacks this round against that opponent are made with The Edge.}

\hypertarget{feat:command}{}\babfeat{Command [Combat] [Leadership]}{
You lead tiny men.}{
You have a Command Rating equal to your Base Attack Bonus divided by five (round up).}{
You can muster a group of followers. Your leadership score is your Base Attack Bonus plus your Charisma Modifier.}{
You are able to delegate command to a loyal cohort. A cohort is an intelligent and loyal creature with a CR at least 2 less than your character level. Cohorts gain levels when you do.}{
With a Swift Action you may rally troops, allowing all allies within medium range of yourself to reroll their saves vs. Fear and gain a +2 Morale Bonus to attack and damage rolls for 1 minute. This is a language-dependent ability that may be used an unlimited number of times.}{
Your allies gain a +2 morale bonus to all saving throws if they can see you and you are within medium range.}


\hypertarget{feat:dangersense}{}\babfeat{Danger Sense [Combat]}{
Maybe Spiders tell you what's up. You certainly react to danger with uncanny effectiveness.}{
You get a +3 bonus on Initiative checks.}{
For the purpose of Search, Spot, and Listen, you are always considered to be ``actively searching". You also get Uncanny Dodge.}{
You may take 10 on Listen, Spot, and Search checks.}{
You may make a Sense Motive check (opposed by your opponent's Bluff check) immediately whenever any creature approaches within 60' of you with harmful intent. If you succeed, you know the location of the creature even if you cannot see it.}{
You are never surprised and always act on the first round of any combat.}


\hypertarget{feat:elusivetarget}{}\babfeat{Elusive Target [Combat]}{
You are very hard to hit when you want to be.}{
You gain a +2 Dodge bonus to AC.}{
Your opponents do not gain flanking or higher ground bonuses against you.}{
Your opponents do not inflict extra damage from the \hyperlink{combat:powerattack}{Power Attack} option.}{
Diverting Defense -- As an immediate action, you may redirect an attack against you to any creature in your threatened range, friend or foe. You may not redirect an attack to the creature making the attack.}{
As an immediate action, you may make an attack that would normally hit you miss instead.}


\hypertarget{feat:experttactician}{}\babfeat{Expert Tactician [Combat]}{
You benefit your allies so good they remember you long time.}{
You gain a +4 bonus when flanking instead of the normal +2 bonus. Your allies who flank with you gain the same advantage.}{
You may \hyperlink{combat:feint}{Feint} as an Immediate action.}{
As a move action, you may make any 5' square adjacent to yourself into difficult ground.}{
For determining flanking with your allies, you may count your location as being 5' in any direction from your real location.}{
You ignore Cover bonuses less than full cover.}


\hypertarget{feat:ghosthunter}{}\babfeat{Ghost Hunter [Combat]}{
You smack around those folks in the spirit world.}{
Your attacks have a 50\% chance of striking incorporeal opponents even if they are not magical.}{
You can hear incorporeal and ethereal creatures as if they lacked those traits (note that shadows and the like rarely bother to actively move silently).}{
You can see invisible and ethereal creatures as if they lacked those traits.}{
Your attacks count as if you had the Ghost Touch property on your weapons.}{
Any Armor or shield you use benefits from the Ghost Touch quality.}


\hypertarget{feat:giantslayer}{}\babfeat{Giant Slayer [Combat]}{
Everyone has a specialty. Yours is miraculously finding ways to stab creatures in the face when it seems improbable that you would be able to reach that high.}{
When you perform a \hyperlink{combat:grabon}{grab on} Grapple maneuver, you do not provoke an attack of opportunity.}{
You gain a +4 Dodge bonus to your AC and Reflex Saves against attacks from any creature with a longer natural reach than your own.}{
You have The Edge against any creature you attack that is larger than you. Also, an opponent using the Improved Grab ability on you provokes an attack of opportunity from you. You may take this attack even if you do not threaten a square occupied by your opponent.}{
When you attempt to trip an opponent, you may choose whether your opponent resists with Strength or Dexterity.}{
When involved in an opposed bull rush, grapple, or trip check as the attacker or defender, you may negate the size modifier of both participants. You may not choose to negate the size modifier of only one character.}


\hypertarget{feat:greatfortitude}{}\babfeat{Great Fortitude [Combat]}{
You are so tough. Your belly is like a prism.}{
You gain a +3 bonus to your Fortitude Saves.}{
You die at -20 instead of -10.}{
You gain 1 hit point per level.}{
You gain DR of 5/-.}{
You are immune to the fatigued and exhausted conditions. If you are already immune to these conditions, you gain 1 hit point per level for each condition you were already immune to.}


\hypertarget{feat:hordebreaker}{}\babfeat{Horde Breaker[Combat]}{
You kill really large numbers of people.}{
You gain a number of extra attacks of opportunity each round equal to your Dexterity Bonus (if positive).}{
Whenever you drop an opponent with a melee attack, you are entitled to a bonus ``cleave" attack against another opponent you threaten. You may not take a 5' step or otherwise move before taking this bonus attack. This Cleave attack is considered an attack of opportunity.}{
You may take a bonus 5' step every time you are entitled to a Cleave attack, which you may take either before or after the attack.}{
You may generate an aura of fear on any opponents within 10' of yourself whenever you drop an opponent in melee. The save DC is 10 + the Hit Dice of the dropped creature.}{
Opponents you have the Edge against provoke an attack of opportunity from you by moving into your threatened area or attacking you.}


\hypertarget{feat:hunter}{}\babfeat{Hunter [Combat]}{
You can move around and shoot things with surprising effectiveness.}{
The penalties for using a ranged weapon from an unstable platform (such as a ship or a moving horse) are halved.}{
Shot on the Run -- you may take a standard action to attack with a ranged weapon in the middle of a move action, taking some of your movement before and some of your movement after your attack. That still counts as your standard and move action for the round.}{
You suffer no penalties for firing from unstable ground, a running steed, or any of that.}{
You may take a full round action to take a double move and make a single ranged attack from any point during your movement.}{
You may take a full round action to run a full four times your speed and make a single ranged attack from any point during your movement. You retain your Dexterity modifier to AC while running.}


\hypertarget{feat:insightfulstrike}{}\babfeat{Insightful Strike [Combat]}{
You Hack people down with inherent awesomeness.}{
You may use your Wisdom Modifier in place of your Strength Modifier for your melee attack rolls.}{
Your attacks have The Edge against an opponent who has a lower Wisdom and Dexterity than your own Wisdom, regardless of relative BAB.}{
Your melee attacks have a doubled critical threat range.}{
You make horribly telling blows. The extra critical multiplier of your melee attacks is doubled (x2 becomes x3, x3 becomes x5, and x4 becomes x7).}{
Any Melee attack you make is considered to be made with a magic weapon that has an enhancement bonus equal to your Wisdom Modifier (if positive).}


\hypertarget{feat:ironwill}{}\babfeat{Iron Will [Combat]}{
You are able to grit your teeth and shake off mental influences.}{
You gain a +3 bonus to your Willpower saves.}{
You gain the slippery mind ability of a Rogue.}{
If you are stunned, you are dazed instead.}{
You do not suffer penalties from pain and fear.}{
You are immune to compulsion effects.}


\hypertarget{feat:juggernaut}{}\babfeat{Juggernaut [Combat]}{
You are an unstoppable Juggernaut.}{
You may be considered one size category larger for the purposes of any size dependant roll you make (such as a Bull Rush, Overrun, or Lift action).}{
You do not provoke an attack of opportunity for entering an opponent's square.}{
You gain a +4 bonus to attack and damage rolls to destroy objects. You may shatter a Force Effect by inflicting 30 damage on it.}{
When you successfully \hyperlink{combat:bullrush}{bullrush} or overrun an opponent, you automatically Trample them, inflicting damage equal to a natural slam attack for a creature of your size.}{
You gain the Rock Throwing ability of any standard Giant with a strength equal to or less than yourself.}


\hypertarget{feat:lightningreflexes}{}\babfeat{Lightning Reflexes [Combat]}{
You are fasty McFastFast. It helps keep you alive.}{
You gain a +3 bonus to your Reflex saves.}{
You gain Evasion, if you already have Evasion, that stacks to Improved Evasion.}{
You may make a Balance Check in place of your Reflex save.}{
You gain a +3 bonus to your Initiative.}{
When you take the Full Defense Action, add your level to your AC.}


\hypertarget{feat:mageslayer}{}\babfeat{Mage Slayer [Combat]}{
You have trained long and hard to kill magic users. Maybe you hate them, maybe you just noticed that most of the really dangerous creatures in the world use magic.}{
You gain Spell Resistance of 5 + Character Level.}{
Damage you inflict is considered ``ongoing damage" for the purposes of concentration checks made before the beginning of your next round. All your attacks in a round are considered the same source of continuing damage.}{
Creatures cannot cast defensively within your threat range.}{
Your attacks ignore Deflection bonuses to AC.}{
When a creature uses a [Teleportation] effect within medium range of yourself, you may choose to be transported as well. This is not an action.}


\hypertarget{feat:murderousintent}{}\babfeat{Murderous Intent [Combat]}{
You stab people in the face.}{
You may make a \hyperlink{combat:coupdegrace}{Coup de Grace} as a standard action.}{
When you kill an opponent, you gain a +2 Morale Bonus to your attack and damage rolls for 1 minute.}{
Once per round, you may take an attack of opportunity against an opponent who is denied their Dexterity bonus to AC.}{
You may take a \hyperlink{combat:coupdegrace}{Coup de Grace} action against opponents who are stunned.}{
You may take a \hyperlink{combat:coupdegrace}{Coup de Grace} action against opponents who are dazed.}


\hypertarget{feat:phalanxfighter}{}\babfeat{Phalanx Fighter[Combat]}{
You fight well in a group.}{
You may take attacks of opportunity even while flat footed.}{
Any Dodge bonus to AC you gain is also granted to any adjacent allies for as long as you benefit from the bonus and your ally remains adjacent.}{
Charging is an action that provokes an attack of opportunity from you. This attack is considered to be a ``readied attack" if it matters for purposes like setting against a charge.}{
You may attack with a reach weapon as if it was not a reach weapon. Thus, a medium creature would normally threaten at 5' and 10' with a reach weapon.}{
You may take an Aid Another action once per round as a free action. You provide double normal bonuses from this effect.}


\hypertarget{feat:pointblankshot}{}\hypertarget{feat:pbshot}{}\babfeat{Point Blank Shot [Combat]}{
You are crazy good using a ranged weapon in close quarters.}{
When you are within 30' of your target, your attacks with a ranged weapon gain a +3 bonus to-hit.}{
You add your base attack bonus to damage with any ranged attack within the first range increment.}{
You do not provoke an attack of opportunity when you make a ranged attack.}{
When armed with a Ranged Weapon, you may make attacks of opportunity against opponents who provoke them within 30' of you. Movement within this area does not provoke an attack of opportunity.}{
With a Full Attack action, you may fire a ranged weapon once at every single opponent within the first range increment of your weapon. You gain no additional attacks for having a high BAB. Make a single attack roll for the entire round, and compare to the armor class of each opponent within range.}

\hypertarget{feat:sniper}{}\babfeat{Sniper [Combat]}{
Your shooting is precise and dangerous.}{
Your range increments are 50\% longer than they would ordinarily be. Any benefit of being within 30' of an opponent is retained out to 60'.}{
Precise Shot -- You do not suffer a -4 penalty when firing a ranged weapon into melee and never hit an unintended target in close combats or grapples.}{
Sharp Shooting -- Your ranged attacks ignore Cover Bonuses (total cover still bones you).}{
Opponents struck by your ranged attacks do not automatically know what square your attack came from, and must attempt to find you normally.}{
Any time you hit an opponent with a ranged weapon, it is counted as a critical threat. If your weapon already had a 19-20 threat range, increase its critical multiplier by 1.}


\hypertarget{feat:subtlecut}{}\babfeat{Subtle Cut [Combat]}{
You cut people so bad they have to ask you about it later.}{
Any time you damage an opponent, that damage is increased by 1.}{
As a standard action, you can make a weapon attack that also reduces a creature's movement rate. For every 5 points of damage this attack does, reduce the creature's movement by 5'. This penalties lasts until the damage is healed.}{
As a standard action, you may make a weapon attack that also does 2d4 points of Dexterity damage.}{
Any weapon attack that you make at this level acts as if the weapon had the wounding property.}{
As a standard action, you may make an attack that dazes your opponent. This effect lasts one round, and has a DC of 10 + half your level + your Intelligence bonus.}


\hypertarget{feat:twoweaponfighting}{}\babfeat{Two Weapon Fighting [Combat]}{
When armed with two weapons, you fight with two weapons rather than picking and choosing and fighting with only one. Kind of obvious in retrospect.}{
You suffer no penalty for doing things with your off-hand. When you make an attack or full-attack action, you may make a number of attacks with your off-hand weapon equal to the number of attacks you are afforded with your primary weapon.}{
While armed with two weapons, you gain an extra Attack of Opportunity each round for each attack you would be allowed for your BAB, these extra attacks of opportunity must be made with your off-hand.}{
You gain a +2 Shield Bonus to your armor class when fighting with two weapons and not flat footed.}{
You may Feint as a Swift action.}{
While fighting with two weapons and not flat footed you may add the enhancement bonus of either your primary or your off-hand weapon to your Shield Bonus to AC.}


\hypertarget{feat:weaponfinesse}{}\babfeat{Weapon Finesse [Combat]}{
You are incredibly deft with a sword.}{
You may use your Dexterity Modifier instead of your Strength modifier for calculating your melee attack bonus.}{
Your special attacks are considered to have the Edge when you attack an opponent with a Dexterity modifier smaller than yours, even if your Base Attack Bonus is not larger.}{
You may use your Dexterity modifier in place of your Strength modifier when attempting to trip an opponent.}{
You may use your Dexterity modifier in place of your Strength modifier for calculating your melee damage.}{
Opportunist -- Once per turn, when an opponent is struck, you may take an attack of opportunity on that opponent.}

\hypertarget{feat:whirlwind}{}\hypertarget{feat:whirlwindattack}{}\babfeat{Whirlwind [Combat]}{
You are just as dangerous to everyone around you as to anyone around you.}{
As a full round action, you may make a single attack against each opponent you can reach. Roll one attack roll and compare to each available opponent's AC individually.}{
You gain a +3 bonus to Balance checks.}{
As a full round action, you may take a regular move action and make a single attack against each opponent you can reach at any point during your movement. Roll one attack roll and compare to each available opponent's AC individually.}{
Until your next round after making a whirlwind attack, you may take an attack of opportunity against any opponent that enters your threatened area.}{
As a full round action, you take a charge action, overrunning any creature in your path, and may make a single attack against each opponent you can reach at any point during your movement. Roll one attack roll and compare to each available opponent's AC individually.}


\hypertarget{feat:zenarchery}{}\babfeat{Zen Archery [Combat]}{
You are very calm about shooting people in the face. That's a good place to be.}{
You may use your Wisdom Modifier in place of your Dexterity Modifier on ranged attack rolls.}{
Any opponent you can hear is considered an opponent you can see for purposes of targeting them with ranged attacks.}{
If you cast a Touch Spell, you can deliver it with a ranged weapon (though you must hit with a normal attack to deliver the spell).}{
As a Full Round Action, you may make one ranged attack with a +20 Insight bonus to hit.}{
As a Full Round Action, you may make one ranged attack with a +20 Insight bonus to hit. If this attack hits, your attack is automatically upgraded to a critical threat. If the threat range of your weapon is 19-20, your critical multiplier is increased by one.}

\end{multicols}

\section{[Skill] Feats}

\begin{multicols}{2}
\hypertarget{feat:mountedcombat}{}\skillfeat{Mounted Combat [Skill]}{
You are at your best when fighting with an ally that you are sitting on.}{
Ride Ranks:}{
Once per turn, you may attempt to negate an attack that hits your mount by making a Ride skill check with a DC equal to the AC that the attack hit. Attacks that do not require an attack roll cannot be negated in this way.}{
While Mounted, you may take a charge attack at any point along your mount's movement, so long as your mount is moving in a straight line up to the point of your attack.}{
You suffer no penalty to your ride or handle animal skill checks when training or riding unusual mounts such as magical beasts or dragons.}{
You may use your Ride Check in place of your mount's Balance, Jump, Climb, or Reflex Saving Throws.}{
Any time a spell effect would target your mount, you may elect to have it target you instead. Any time a spell effect would target you, you may elect to have it affect your Mount instead.}
\end{multicols}
