%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

{\LARGE POWER LIST}

\vspace{12pt}
An \textsuperscript{\textbf{A}}{\scriptsize  }appearing at the end of a power's 
name in the power lists denotes an augmentable power. An \textsuperscript{\textbf{X}}{\scriptsize  
}denotes a power with an XP component paid by the manifester.

\textbf{Power Chains:} Some powers reference other powers that they are based upon. 
Only information in a power later in the power chain that is different from the 
base power is covered in the power being described. Header entries and other information 
that are the same as the base power are not repeated. The same holds true for powers 
that are the equivalents of spells, only the way the power varies from the spell 
is noted, such as power point cost.

\textbf{Order of Presentation:} In the power lists and the power descriptions that 
follow them, the powers are presented in alphabetical order by name---except for 
those belonging to certain power chains and those that are psionic equivalents 
of spells\textit{. }When a power's name begins with ``lesser,'' ``greater,'' ``mass,'' 
or a similar kind of qualifier, the power description is alphabetized under the 
second word of the power description instead. When the effect of a power is essentially 
the same as that of a spell, the power's name is simply ``Psionic'' followed by 
the name of the spell, and it is alphabetized according to the spell name.

\textbf{Manifester Level:} A power's effect often depends on the manifester level, 
which is the manifester's psionic class level. A creature with no classes has a 
manifester level equal to its Hit Dice unless otherwise specified. The word ``level'' 
in the power lists always refers to manifester level.

\textbf{Creatures and Characters:} ``Creatures'' and ``characters'' are used synonymously 
in the power descriptions.

\textbf{Augment:} Many powers vary in strength depending on how many power points 
you put into them. The more power points you spend, the more powerful the manifestation. 
However, you can spend only a total number of points on a power equal to your manifester 
level, unless you have an ability that increases your effective manifester level.

Many powers can be augmented in more than one way. When the Augment section contains 
numbered paragraphs, you need to spend power points separately for each of the 
numbered options. When a paragraph in the Augment section begins with ``In addition,'' 
you gain the indicated benefit according to how many power points you have already 
decided to spend on manifesting the power.

\vspace{12pt}
{\LARGE PSION/WILDER POWERS}

1ST-LEVEL PSION/WILDER POWERS

\textbf{Astral Traveler: }Enable yourself or another to join an \textit{astral 
caravan}-enabled trip.

\textbf{Attraction}\textsuperscript{\textbf{A}}\textbf{: }Subject has an attraction 
you specify.

\textbf{Bolt}\textsuperscript{\textbf{A}}\textbf{: }You create a few enhanced short-lived 
bolts, arrows, or bullets.

\textbf{Call to Mind: }Gain additional Knowledge check with +4 competence bonus.

\textbf{Catfall}\textsuperscript{\textbf{A}}\textbf{: }Instantly save yourself 
from a fall.

\textbf{Conceal Thoughts: }You conceal your motives.

\textbf{Control Flames}\textsuperscript{\textbf{A}}\textbf{: }Take control of nearby 
open flame.

\textbf{Control Light: }Adjust ambient light levels.

\textbf{Create Sound: }Create the sound you desire.

\textbf{Crystal Shard}\textsuperscript{\textbf{A}}\textbf{: }Ranged touch attack 
for 1d6 points of piercing damage.

\textbf{Daze, Psionic}\textsuperscript{\textbf{A}}\textbf{: }Humanoid creature 
of 4 HD or less loses next action.

\textbf{Deceleration}\textsuperscript{\textbf{A}}\textbf{: }Target's speed is halved.

\textbf{Déjà Vu}\textsuperscript{\textbf{A}}\textbf{: }Your target repeats his 
last action.

\textbf{Demoralize}\textsuperscript{\textbf{A}}\textbf{: }Enemies become shaken.

\textbf{Detect Psionics: }You detect the presence of psionics.

\textbf{Disable}\textsuperscript{\textbf{A}}\textbf{: }Subjects incorrectly believe 
they are disabled.

\textbf{Dissipating Touch}\textsuperscript{\textbf{A}}\textbf{: }Touch deals 1d6 
damage.

\textbf{Distract: }Target gets -4 bonus on Listen, Search, Sense Motive, and Spot 
checks.

\textbf{Ecto Protection}\textsuperscript{\textbf{A}}\textbf{: }An astral construct 
gains bonus against \textit{dismiss ectoplasm}.

\textbf{Empathy}\textsuperscript{\textbf{A}}\textbf{: }You know the subject's surface 
emotions.

\textbf{Empty Mind}\textsuperscript{\textbf{A}}\textbf{: }You gain +2 on Will saves 
until your next action.

\textbf{Energy Ray}\textsuperscript{\textbf{A}}\textbf{: }Deal 1d6 energy (cold, 
electricity, fire, or sonic) damage.

\textbf{Entangling Ectoplasm: }You entangle a foe in sticky goo. 

\textbf{Far Hand}\textsuperscript{\textbf{A}}\textbf{: }Move small objects at a 
limited distance. 

\textbf{Float}\textsuperscript{\textbf{A}}\textbf{: }You buoy yourself in water 
or other liquid.

\textbf{Force Screen}\textsuperscript{\textbf{A}}\textbf{: }Invisible disc provides 
+4 shield bonus to AC.

\textbf{Grease, Psionic: }Makes 10-ft. square or one object slippery.

\textbf{Hammer}\textsuperscript{\textbf{A}}\textbf{: }Melee touch attack deals 
1d8/round.

\textbf{Inertial Armor}\textsuperscript{\textbf{A}}\textbf{: }Tangible field of 
force provides you with +4 armor bonus to AC.

\textbf{Know Direction and Location: }You discover where you are and what direction 
you face.

\textbf{Matter Agitation: }You heat a creature or object.

\textbf{Mind Thrust}\textsuperscript{\textbf{A}}\textbf{: }Deal 1d10 damage.

\textbf{Missive}\textsuperscript{\textbf{A}}\textbf{: }Send a one-way telepathic 
message to subject.

\textbf{My Light}\textsuperscript{\textbf{A}}\textbf{: }Your eyes emit 20-ft. cone 
of light.

\textbf{Precognition, Defensive}\textsuperscript{\textbf{A}}\textbf{: }Gain +1 
insight bonus to AC and saving throws.

\textbf{Precognitionion, Offensive}\textsuperscript{\textbf{A}}\textbf{: }Gain 
+1 insight bonus on your attack rolls.

\textbf{Prescience, Offensive}\textsuperscript{\textbf{A}}\textbf{: }Gain +2 insight 
bonus on your damage rolls.

\textbf{Sense Link}\textsuperscript{\textbf{A}}\textbf{: }You sense what the subject 
senses (single sense).

\textbf{Skate: }Subject slides skillfully along the ground.

\textbf{Synesthete: }You receive one kind of sense when another sense is stimulated.

\textbf{Telempathic Projection: }Alter the subject's mood.

\textbf{Vigor}\textsuperscript{\textbf{A}}\textbf{: }Gain 5 temporary hit points.

2ND-LEVEL PSION/WILDER POWERS

\textbf{Bestow Power}\textsuperscript{\textbf{A}}\textbf{: }Subject receives 2 
power points.

\textbf{Biofeedback}\textsuperscript{\textbf{A}}\textbf{: }Gain damage reduction 
2/-.

\textbf{Body Equilibrium: }You can walk on nonsolid surfaces.

\textbf{Cloud Mind: }You erase knowledge of your presence from target's mind.

\textbf{Concealing Amorpha: }Quasi-real membrane grants you concealment.

\textbf{Concussion Blast}\textsuperscript{\textbf{A}}\textbf{: }Deal 1d6 force 
damage to target.

\textbf{Control Sound: }Create very specific sounds.

\textbf{Detect Hostile Intent: }You can detect hostile creatures within 30 ft. 
of you.

\textbf{Ego Whip}\textsuperscript{\textbf{A}}\textbf{: }Deal 1d4 Cha damage and 
daze for 1 round.

\textbf{Elfsight: }Gain low-light vision, +2 bonus on Search and Spot checks, and 
notice secret doors.

\textbf{Energy Adaptation, Specified}\textsuperscript{\textbf{A}}\textbf{: }Gain 
resistance 10 against one energy type.

\textbf{Energy Push}\textsuperscript{\textbf{A}}\textbf{: }Deal 2d6 damage and 
knock subject back.

\textbf{Energy Stun}\textsuperscript{\textbf{A}}\textbf{: }Deal 1d6 damage and 
stun target if it fails both saves.

\textbf{Feat Leech}\textsuperscript{\textbf{A}}\textbf{: }Borrow another's psionic 
or metapsionic feats.

\textbf{Id Insinuation}\textsuperscript{\textbf{A}}\textbf{: }Swift tendrils of 
thought disrupt and confuse your target.

\textbf{Identify, Psionic: }Learn the properties of a psionic item.

\textbf{Inflict Pain}\textsuperscript{\textbf{A}}\textbf{: }Telepathic stab gives 
your foe -4 on attack rolls, or -2 if he makes the save.

\textbf{Knock, Psionic: }Opens locked or psionically sealed door.

\textbf{Levitate, Psionic: }You move up and down, forward and back via mental support.

\textbf{Mental Disruption}\textsuperscript{\textbf{A}}\textbf{: }Daze creatures 
within 10 feet for 1 round.

\textbf{Missive, Mass}\textsuperscript{\textbf{A}}\textbf{: }You send a one-way 
telepathic message to an area.

\textbf{Psionic Lock: }Secure a door, chest, or portal.

\textbf{Recall Agony}\textsuperscript{\textbf{A}}\textbf{: }Foe takes 2d6 damage.

\textbf{Sense Link, Forced: }Sense what subject senses.

\textbf{Share Pain: }Willing subject takes some of your damage.

\textbf{Sustenance: }Go without food and water for one day.

\textbf{Swarm of Crystals}\textsuperscript{\textbf{A}}\textbf{: }Crystal shards 
are sprayed forth doing 3d4 slashing damage.

\textbf{Thought Shield}\textsuperscript{\textbf{A}}\textbf{: }Gain PR 13 against 
mind-affecting powers.

\textbf{Tongues, Psionic: }You can communicate with intelligent creatures.

3RD-LEVEL PSION/WILDER POWERS

\textbf{Body Adjustment}\textsuperscript{\textbf{A}}\textbf{: }You heal 1d12 damage.

\textbf{Body Purification}\textsuperscript{\textbf{A}}\textbf{: }You restore 2 
points of ability damage.

\textbf{Danger Sense}\textsuperscript{\textbf{A}}\textbf{: }You gain +4 bonus against 
traps.

\textbf{Darkvision, Psionic: }See 60 ft. in total darkness.

\textbf{Dismiss Ectoplasm: }Dissipates ectoplasmic targets and effects.

\textbf{Dispel Psionics}\textsuperscript{\textbf{A}}\textbf{: }Cancels psionic 
powers and effects.

\textbf{Energy Bolt}\textsuperscript{\textbf{A}}\textbf{: }Deal 5d6 energy damage 
in 120-ft. line.

\textbf{Energy Burst}\textsuperscript{\textbf{A}}\textbf{: }Deal 5d6 energy damage 
in 40-ft. burst.

\textbf{Energy Retort}\textsuperscript{\textbf{A}}\textbf{: }Ectoburst of energy 
automatically targets your attacker for 4d6 damage once each round. 

\textbf{Energy Wall: }Create wall of your chosen energy type.

\textbf{Eradicate Invisibility}\textsuperscript{\textbf{A}}\textbf{: }Negate invisibility 
in 50-ft. burst.

\textbf{Keen Edge, Psionic: }Doubles normal weapon's threat range.

\textbf{Mental Barrier}\textsuperscript{\textbf{A}}\textbf{: }Gain +4 deflection 
bonus to AC until your next action.

\textbf{Mind Trap}\textsuperscript{\textbf{A}}\textbf{: }Drain 1d6 power points 
from anyone who attacks you with a telepathy power.

\textbf{Psionic Blast: }Stun creatures in 30-ft. cone for 1 round.

\textbf{Share Pain, Forced}\textsuperscript{\textbf{A}}\textbf{: }Unwilling subject 
takes some of your damage.

\textbf{Solicit Psicrystal}\textsuperscript{\textbf{A}}\textbf{: }Your psicrystal 
takes over your concentration power.

\textbf{Telekinetic Force}\textsuperscript{\textbf{A}}\textbf{: }Move an object 
with the sustained force of your mind.

\textbf{Telekinetic Thrust}\textsuperscript{\textbf{A}}\textbf{: }Hurl objects 
with the force of your mind.

\textbf{Time Hop}\textsuperscript{\textbf{A}}\textbf{: }Subject hops forward in 
time 1 round/level.

\textbf{Touchsight}\textsuperscript{\textbf{A}}\textbf{: }Your telekinetic field 
tells you where everything is.

\textbf{Ubiquitous Vision: }You have all-around vision.

4TH-LEVEL PSION/WILDER POWERS

\textbf{Aura Sight}\textsuperscript{\textbf{A}}\textbf{: }Reveals creatures, objects, 
powers, or spells of selected alignment axis.

\textbf{Correspond: }Hold mental conversation with another creature at any distance.

\textbf{Death Urge}\textsuperscript{\textbf{A}}\textbf{: }Implant a self-destructive 
compulsion.

\textbf{Detect Remote Viewing: }You know when others spy on you remotely.

\textbf{Dimension Door, Psionic: }Teleports you short distance.

\textbf{Divination, Psionic: }Provides useful advice for specific proposed action.

\textbf{Empathic Feedback}\textsuperscript{\textbf{A}}\textbf{: }When you are hit 
in melee, your attacker takes damage.

\textbf{Energy Adaptation}\textsuperscript{\textbf{A}}\textbf{: }Your body converts 
energy to harmless light.

\textbf{Freedom of Movement, Psionic: }You cannot be held or otherwise rendered 
immobile.

\textbf{Intellect Fortress}\textsuperscript{\textbf{A}}\textbf{: }Those inside 
fortress take only half damage from all powers and psi-like abilities until your 
next action.

\textbf{Mindwipe}\textsuperscript{\textbf{A}}\textbf{: }Subject's recent experiences 
wiped away, bestowing negative levels.

\textbf{Personality Parasite: }Subject's mind calves self-antagonistic splinter 
personality for 1 round/level.

\textbf{Power Leech: }Drain 1d6 power points/round while you maintain concentration; 
you gain 1/round.

\textbf{Psychic Reformation}\textsuperscript{\textbf{X}}\textbf{: }Subject can 
choose skills, feats, and powers anew for previous levels.

\textbf{Telekinetic Maneuver}\textsuperscript{\textbf{A}}\textbf{: }Telekinetically 
bull rush, disarm, grapple, or trip your target.

\textbf{Trace Teleport}\textsuperscript{\textbf{A}}\textbf{: }Learn destination 
of subject's \textit{teleport}.

\textbf{Wall of Ectoplasm: }You create a protective barrier.

5TH-LEVEL PSION/WILDER POWERS

\textbf{Adapt Body: }Your body automatically adapts to hostile environments.

\textbf{Catapsi}\textsuperscript{\textbf{A}}\textbf{: }Psychic static inhibits 
power manifestation.

\textbf{Ectoplasmic Shambler: }Foglike predator deals 1 point of damage/two levels 
each round to an area.

\textbf{Incarnate}\textsuperscript{\textbf{X}}\textbf{: }Make some powers permanent.

\textbf{Leech Field}\textsuperscript{\textbf{A}}\textbf{: }Leech power points each 
time you make a saving throw.

\textbf{Major Creation, Psionic: }As \textit{psionic minor creation}, plus stone 
and metal.

\textbf{Plane Shift, Psionic: }Travel to other planes.

\textbf{Power Resistance: }Grant PR equal to 12 + level.

\textbf{Psychic Crush}\textsuperscript{\textbf{A}}\textbf{: }Brutally crush subject's 
mental essence, reducing subject to -1 hit points.

\textbf{Shatter Mind Blank: }Cancels target's \textit{mind blank }effect.

\textbf{Tower of Iron Will}\textsuperscript{\textbf{A}}\textbf{: }Grant PR 19 against 
mind-affecting powers to all creatures within 10 ft. until your next turn.

\textbf{True Seeing, Psionic}\textsuperscript{\textbf{A}}\textbf{: }See all things 
as they really are.

6TH-LEVEL PSION/WILDER POWERS

\textbf{Aura Alteration}\textsuperscript{\textbf{A}}\textbf{: }Repairs psyche or 
makes subject seem to be something it is not.

\textbf{Breath of the Black Dragon}\textsuperscript{\textbf{A}}\textbf{: }Breathe 
acid for 11d6 damage.

\textbf{Cloud Mind, Mass: }Erase knowledge of your presence from the minds of one 
creature/level.

\textbf{Contingency, Psionic}\textsuperscript{\textbf{X}}\textbf{: }Sets trigger 
condition for another power.

\textbf{Co-opt Concentration: }Take control of foe's concentration power.

\textbf{Disintegrate, Psionic}\textsuperscript{\textbf{A}}\textbf{: }Turn one creature 
or object to dust.

\textbf{Fuse Flesh}\textsuperscript{\textbf{A}}\textbf{: }Fuse subject's flesh, 
creating a helpless mass.

\textbf{Overland Flight, Psionic: }You fly at a speed of 40 ft. and can hustle 
over long distances.

\textbf{Remote View Trap: }Deal 8d6 points electricity damage to those who seek 
to view you at a distance.

\textbf{Retrieve}\textsuperscript{\textbf{A}}\textbf{: }Teleport to your hand an 
item you can see.

\textbf{Suspend Life: }Put yourself in a state akin to suspended animation.

\textbf{Temporal Acceleration}\textsuperscript{\textbf{A}}\textbf{: }Your time 
frame accelerates for 1 round.

7TH-LEVEL PSION/WILDER POWERS

\textbf{Decerebrate: }Remove portion of subject's brain stem.

\textbf{Divert Teleport: }Choose destination for another's \textit{teleport}.

\textbf{Energy Conversion: }Offensively channel energy you've absorbed.

\textbf{Energy Wave}\textsuperscript{\textbf{A}}\textbf{: }Deal 13d4 damage of 
your chosen energy type in 120-ft. cone.

\textbf{Evade Burst}\textsuperscript{\textbf{A}}\textbf{: }You take no damage from 
a burst on a successful Reflex save.

\textbf{Insanity}\textsuperscript{\textbf{A}}\textbf{: }Subject is permanently 
\textit{confused.}

\textbf{Mind Blank, Personal: }You are immune to scrying and mental effects.

\textbf{Moment of Prescience, Psionic: }You gain insight bonus on single attack 
roll, check, or save.

\textbf{Oak Body}\textsuperscript{\textbf{A}}\textbf{: }Your body becomes as hard 
as oak.

\textbf{Phase Door, Psionic: }Invisible passage through wood or stone.

\textbf{Sequester, Psionic}\textsuperscript{\textbf{X}}\textbf{: }Subject invisible 
to sight and remote viewing; renders subject comatose.

\textbf{Ultrablast}\textsuperscript{\textbf{A}}\textbf{: }Deal 13d6 damage in 15-ft. 
radius.

8TH-LEVEL PSION/WILDER POWERS

\textbf{Bend Reality}\textsuperscript{\textbf{X}}\textbf{: }Alters reality within 
power limits.

\textbf{Iron Body, Psionic: }Your body becomes living iron.

\textbf{Matter Manipulation}\textsuperscript{\textbf{X}}\textbf{: }Increase or 
decrease an object's base hardness by 5.

\textbf{Mind Blank, Psionic: }Subject immune to mental/emotional effects, scrying, 
and remote viewing.

\textbf{Recall Death: }Subject dies or takes 5d6 damage.

\textbf{Shadow Body: }You become a living shadow (not the creature).

\textbf{Teleport, Psionic Greater: }As \textit{psionic teleport}, but no range 
limit and no off-target arrival.

\textbf{True Metabolism: }You regenerate 10 hit points/round.

9TH-LEVEL PSION/WILDER POWERS

\textbf{Affinity Field:} Effects that affect you also affect others.

\textbf{Apopsi}\textsuperscript{\textbf{X}}\textbf{:} You delete target's psionic 
powers.

\textbf{Assimilate:} Incorporate creature into your own body.

\textbf{Etherealness,} Psionic: Become ethereal for 1 min./level.

\textbf{Microcosm}\textsuperscript{\textbf{A}}\textbf{:} Creature or creature lives 
forevermore in world of his own imagination.

\textbf{Reality Revision}\textsuperscript{\textbf{X}}\textbf{:} As \textit{bend 
reality}, but fewer limits.

\textbf{Timeless Body:} Ignore all harmful, and helpful, effects for 1 round.

\vspace{12pt}
{\LARGE PSION DISCIPLINE POWERS}

EGOIST (PSYCHOMETABOLISM) DISCIPLINE POWERS

\textbf{1\tab Thicken Skin}\textsuperscript{\textbf{A}}\textbf{: }Gain +1 enhancement 
bonus to your AC for 10 min./level.

\textbf{2\tab Animal Affinity}\textsuperscript{\textbf{A}}\textbf{: }Gain +4 enhancement 
to one ability.

\textbf{Chameleon: }Gain +10 enhancement bonus on Hide checks.

\textbf{Empathic Transfer}\textsuperscript{\textbf{A}}\textbf{: }Transfer another's 
wounds to yourself.

\textbf{3\tab Ectoplasmic Form: }You gain benefits of being insubstantial and can 
fly slowly.

\textbf{Hustle: }Instantly gain a move action. 

\textbf{4\tab Metamorphosis: }Assume shape of creature or object.

\textbf{Psychic Vampire: }Touch attack drains 2 power points/level from foe.

\textbf{5\tab Psionic Revivify}\textsuperscript{\textbf{A}}{\scriptsize \textbf{ 
}}\textsuperscript{\textbf{X}}. Return the dead to life before the psyche leaves 
the corpse.\textbf{ }

\textbf{Psychofeedback: }Boost Strength, Dexterity, or Constitution at the expense 
of one or more other scores.

\textbf{Restore Extremity: }Return a lost digit, limb, or other appendage to subject.

\textbf{6\tab Restoration, Psionic: }Restores level and ability score drains.

\textbf{7\tab Fission: }You briefly duplicate yourself.

\textbf{8\tab Fusion}\textsuperscript{\textbf{X}}\textbf{: }You combine your abilities 
and form with another.

\textbf{9\tab Metamorphosis, Greater}\textsuperscript{\textbf{X}}\textbf{: }Assume 
shape of any nonunique creature or object each round.

\vspace{12pt}
KINETICIST (PSYCHOKINESIS) DISCIPLINE POWERS

\textbf{1\tab Control Object:} Telekinetically animate a small object.

\textbf{2\tab Control Air}\textsuperscript{\textbf{A}}\textbf{:} You have control 
over wind speed and direction.

\textbf{Energy Missile}\textsuperscript{\textbf{A}}\textbf{:} Deal 3d6 energy damage 
to up to five subjects.

\textbf{3\tab Energy Cone}\textsuperscript{\textbf{A}}\textbf{:} Deal 5d6 energy 
damage in 60-ft. cone.

\textbf{4\tab Control Body}\textsuperscript{\textbf{A}}\textbf{:} Take rudimentary 
control of your foe's limbs.

\textbf{Energy Ball}\textsuperscript{\textbf{A}}\textbf{:} Deal 7d6 energy damage 
in 20-ft. radius.

\textbf{Inertial Barrier:} Gain DR 5/-.

\textbf{5\tab Energy Current}\textsuperscript{\textbf{A}}\textbf{: }Deal 9d6 damage 
to one foe and half to another foe as long as you concentrate.

\textbf{Fiery Discorporation}\textsuperscript{\textbf{A}}\textbf{:} Cheat death 
by discorporating into nearby fire for one day.

\textbf{6\tab Dispelling Buffer:} Subject is buffered from one \textit{dispel psionics 
}effect.

\textbf{Null Psionics Field:} Create a field where psionic power does not function.

\textbf{7\tab Reddopsi:} Powers targeting you rebound on manifester.

\textbf{8\tab Telekinetic Sphere, Psionic:} Mobile force globe encapsulates creature 
and moves it.

\textbf{9\tab Tornado Blast}\textsuperscript{\textbf{A}}\textbf{:} Vortex of air 
subjects your foes to 17d6 damage and moves them.

\vspace{12pt}
NOMAD (PSYCHOPORTATION) DISCIPLINE POWERS

\textbf{1\tab Burst:} Gain +10 ft. to speed this round.

\textbf{Detect Teleportation}\textsuperscript{\textbf{A}}\textbf{:} Know when teleportation 
powers are used in close range.

\textbf{2\tab Dimension Swap}\textsuperscript{\textbf{A}}\textbf{:} You and ally 
or two allies switch positions.

\textbf{Levitate, Psionic:} Subject moves up and down, forward and back, at your 
direction.

\textbf{3\tab Astral Caravan}\textsuperscript{\textbf{A}}\textbf{:} You lead \textit{astral 
traveler}-enabled group to a planar destination.

\textbf{4\tab Dimensional Anchor, Psionic:} Bars extra dimensional movement.

\textbf{Dismissal, Psionic:} Forces a creature to return to its native plane.

\textbf{Fly, Psionic:} You fly at a speed of 60 ft.

\textbf{5\tab Baleful Teleport}\textsuperscript{\textbf{A}}\textbf{:} Destructive 
teleport deals 9d6 damage.

\textbf{Teleport, Psionic:} Instantly transports you as far as 100 miles/level.

\textbf{Teleport Trigger:} Predetermined event triggers \textit{teleport.}

\textbf{6\tab Banishment, Psionic}\textsuperscript{\textbf{A}}\textbf{:} Banishes 
extraplanar creatures.

\textbf{7\tab Dream Travel}\textsuperscript{\textbf{A}}\textbf{:} Travel to other 
places through dreams.

\textbf{Ethereal Jaunt, Psionic:} Become ethereal for 1 round/level.

\textbf{8\tab Time Hop, Mass}\textsuperscript{\textbf{A}}\textbf{:} Willing subjects 
hop forward in time.

\textbf{9\tab Teleportation Circle, Psionic:} Circle teleports any creatures inside 
to designated spot.

Time Regression\textsuperscript{\textbf{X}}: Relive the last round.

\vspace{12pt}
SEER (CLAIRSENTIENCE) DISCIPLINE POWERS

\textbf{1\tab Destiny Dissonance:} Your dissonant touch sickens a foe.

\textbf{Precognition:} Gain +2 insight bonus to one roll.

\textbf{2\tab Clairvoyant Sense:} See and hear a distant location.

\textbf{Object Reading}\textsuperscript{\textbf{A}}\textbf{:} Learn details about 
an object's previous owner.

\textbf{Sensitivity to Psychic Impressions:} You can find out about an area's past.

\textbf{3\tab Escape Detection:} You become difficult to detect with clairsentience 
powers.

\textbf{Fate Link}\textsuperscript{\textbf{A}}\textbf{:} You link the fates of 
two targets. 

\textbf{4\tab Anchored Navigation}\textsuperscript{\textbf{A}}\textbf{:} Establish 
a mishap-free \textit{teleport }beacon.

\textbf{Remote Viewing}\textsuperscript{\textbf{X}}\textbf{:} See, hear, and potentially 
interact with subjects at a distance.

\textbf{5\tab Clairtangent Hand}\textsuperscript{\textbf{A}}\textbf{:} Emulate 
\textit{far hand }at a distance.

\textbf{Second Chance}\textsuperscript{\textbf{X}}\textbf{:} Gain a reroll.

\textbf{6\tab Precognition, Greater:} Gain +4 insight bonus to one roll.

\textbf{7\tab Fate of One:} Reroll any roll you just failed.

\textbf{8\tab Hypercognition:} You can deduce almost anything.

\textbf{9\tab Metafaculty}\textsuperscript{\textbf{X}}\textbf{:} You learn details 
about any one creature.

\textbf{Reality Revision}\textsuperscript{\textbf{X}}\textbf{:} Break the laws 
of reality.

\vspace{12pt}
SHAPER (METACREATIVITY) DISCIPLINE POWERS

\textbf{1 \tab Astral Construct}\textsuperscript{\textbf{A}}\textbf{:} Creates 
astral construct to fight for you.

\textbf{Minor Creation, Psionic:} Creates one cloth or wood object.

\textbf{2 \tab Psionic Repair Damage:} Repairs construct of 3d8 hit points +1 hp/level.

\textbf{3 \tab Concealing Amorpha, Greater:} Quasi-real membrane grants you total 
concealment.

\textbf{Ectoplasmic Cocoon}\textsuperscript{\textbf{A}}\textbf{:} You encapsulate 
a foe so it can't move.

\textbf{4 \tab Fabricate, Psionic:} Transforms raw goods to finished items.

\textbf{Quintessence:} You collapse a bit of time into a physical substance.

\textbf{5 \tab Hail of Crystals}\textsuperscript{\textbf{A}}: A crystal explodes 
in an area, dealing 9d4 slashing damage.

\textbf{6 \tab Crystallize:} Turn subject permanently to crystal.

\textbf{Fabricate, Greater Psionic:} Transforms a lot of raw goods to finished 
items.

\textbf{7 \tab Ectoplasmic Cocoon, Mass:} You encapsulate all foes in a 20-ft. 
radius.

\textbf{8 \tab Astral Seed:} You plant the seed of your rebirth from the Astral 
Plane.

\textbf{9 \tab Genesis}\textsuperscript{\textbf{X}}\textbf{:} You instigate a new 
demiplane on the Astral Plane.

\textbf{True Creation}\textsuperscript{\textbf{X}}\textbf{:} As \textit{psionic 
major creation}, except items are completely real.

\vspace{12pt}
TELEPATH (TELEPATHY) DISCIPLINE POWERS

\textbf{1 \tab Charm, Psionic}\textsuperscript{\textbf{A}}\textbf{:} Makes one 
person your friend.

\textbf{Mindlink}\textsuperscript{\textbf{A}}\textbf{:} You forge a limited mental 
bond with another creature.

\textbf{2 \tab Aversion}\textsuperscript{\textbf{A}}\textbf{:} Subject has aversion 
you specify.

\textbf{Brain Lock}\textsuperscript{\textbf{A}}\textbf{:} Subject cannot move or 
take any mental actions.

\textbf{Read Thoughts:} Detect surface thoughts of creatures in range.

\textbf{Suggestion, Psionic:} Compels subject to follow stated course of action.

\textbf{3 \tab Crisis of Breath}\textsuperscript{\textbf{A}}: Disrupt subject's 
breathing.

\textbf{Empathic Transfer, Hostile}\textsuperscript{\textbf{A}}\textbf{:} Your 
touch transfers your hurt to another.

\textbf{False Sensory Input}\textsuperscript{\textbf{A}}\textbf{:} Subject sees 
what isn't there.

\textbf{4 \tab Dominate, Psionic}\textsuperscript{\textbf{A}}\textbf{:} Control 
target telepathically.

\textbf{Mindlink, Thieving}\textsuperscript{\textbf{A}}\textbf{:} Borrow knowledge 
of a subject's power.

\textbf{Modify Memory, Psionic:} Changes 5 minutes of subject's memories.

\textbf{Schism:} Your partitioned mind can manifest lower level powers.

\textbf{5\tab Metaconcert}\textsuperscript{\textbf{A}}\textbf{:} Mental concert 
of two or more increases the total power of the participants.

\textbf{Mind Probe:} You discover the subject's secret thoughts.

\textbf{6 \tab Mind Switch}\textsuperscript{\textbf{A}}{\scriptsize \textbf{, }}\textsuperscript{\textbf{X}}\textbf{:} 
You switch minds with another.

\textbf{7 \tab Crisis of Life}\textsuperscript{\textbf{A}}: Stop subject's heart.

\textbf{8 \tab Mind Seed}\textsuperscript{\textbf{X}}\textbf{:} Subject slowly 
becomes you.

\textbf{9 \tab Mind Switch, True}\textsuperscript{\textbf{X}}\textbf{:} A permanent 
brain swap.

\textbf{Psychic Chirurgery}\textsuperscript{\textbf{X}}\textbf{:} You repair psychic 
damage or impart knowledge of new powers.

\vspace{12pt}
{\LARGE PSYCHIC WARRIOR POWERS}

1ST-LEVEL PSYCHIC WARRIOR POWERS 

\textbf{Astral Traveler: }Enable yourself or another to join an \textit{astral 
caravan}-enabled trip.

\textbf{Biofeedback}\textsuperscript{\textbf{A}}\textbf{: }Gain DR 2/-.

\textbf{Bite of the Wolf: }Gain bite attack for 1d8 damage.

\textbf{Burst: }Gain +10ft. to speed this round.

\textbf{Call Weaponry}\textsuperscript{\textbf{A}}\textbf{: }Create temporary weapon.

\textbf{Catfall}\textsuperscript{\textbf{A}}\textbf{: }Instantly save yourself 
from a fall. 

\textbf{Chameleon: }Gain +10 enhancement bonus on Hide checks.

\textbf{Claws of the Beast}\textsuperscript{\textbf{A}}\textbf{: }Your hands become 
deadly claws.

\textbf{Compression}\textsuperscript{\textbf{A}}\textbf{: }You grow smaller.

\textbf{Conceal Thoughts: }You conceal your motives.

\textbf{Detect Psionics: }You detect the presence of psionics.

\textbf{Dissipating Touch}\textsuperscript{\textbf{A}}\textbf{: }Touch deals 1d6 
damage.

\textbf{Distract: }Subject gets -4 on Listen, Search, Sense Motive, and Spot checks.

\textbf{Elfsight: }Gain low-light vision, +2 bonus on Search and Spot checks, and 
notice secret doors.

\textbf{Empty Mind: }Gain +2 on Will saves until your next action.

\textbf{Expansion}\textsuperscript{\textbf{A}}\textbf{: }Become one size category 
larger.

\textbf{Float}\textsuperscript{\textbf{A}}\textbf{: }Buoy yourself in water or 
other liquid.

\textbf{Force Screen}\textsuperscript{\textbf{A}}\textbf{: }Invisible disc provides 
+4 shield bonus to AC.

\textbf{Grip of Iron}\textsuperscript{\textbf{A}}\textbf{: }Your iron grip gives 
+4 bonus on grapple checks.

\textbf{Hammer}\textsuperscript{\textbf{A}}\textbf{: }Melee touch attack deals 
1d8/round.

\textbf{Inertial Armor}\textsuperscript{\textbf{A}}\textbf{: }Tangible field of 
force provides you with +4 armor bonus to AC.

\textbf{Metaphysical Claw}\textsuperscript{\textbf{A}}\textbf{: }Your natural weapon 
gains +1 bonus.

\textbf{Metaphysical Weapon}\textsuperscript{\textbf{A}}\textbf{: }Weapon gains 
+1 bonus.

\textbf{My Light}\textsuperscript{\textbf{A}}\textbf{: }Your eyes emit 20-ft. cone 
of light.

\textbf{Precognition, Defensive}\textsuperscript{\textbf{A}}\textbf{: }Gain +1 
insight bonus to AC and saving throws.

\textbf{Precognition, Offensive}\textsuperscript{\textbf{A}}\textbf{: }Gain +1 
insight bonus on your attack rolls.

\textbf{Prescience, Offensive}\textsuperscript{\textbf{A}}\textbf{: }Gain +2 insight 
bonus on your damage rolls.

\textbf{Prevenom}\textsuperscript{\textbf{A}}\textbf{: }Your claws gain a poison 
coating.

\textbf{Prevenom Weapon}\textsuperscript{\textbf{A}}\textbf{: }Your weapon is mildly 
venomous.

\textbf{Skate: }Subject slides skillfully along the ground.

\textbf{Stomp}\textsuperscript{\textbf{A}}\textbf{: }Subjects fall prone and take 
1d4 nonlethal damage.

\textbf{Synesthete: }You receive one kind of sense when another sense is stimulated.

\textbf{Thicken Skin}\textsuperscript{\textbf{A}}\textbf{: }Gain +1 enhancement 
bonus to your AC for 10 min./level.

\textbf{Vigor}\textsuperscript{\textbf{A}}\textbf{: }Gain 5 temporary hit points.

2ND-LEVEL PSYCHIC WARRIOR POWERS 

\textbf{Animal Affinity}\textsuperscript{\textbf{A}}\textbf{: }Gain +4 enhancement 
to one ability.

\textbf{Body Adjustment}\textsuperscript{\textbf{A}}\textbf{: }Heal 1d12 damage.

\textbf{Body Equilibrium: }You can walk on nonsolid surfaces.

\textbf{Body Purification}\textsuperscript{\textbf{A}}\textbf{: }Restore 2 points 
of ability damage.

\textbf{Concealing Amorpha: }Quasi-real membrane grants you concealment.

\textbf{Darkvision, Psionic: }See 60 ft. in total darkness.

\textbf{Detect Hostile Intent: }You can detect hostile creatures within 30 ft. 
of you.

\textbf{Dimension Swap}\textsuperscript{\textbf{A}}\textbf{: }You and an ally switch 
positions.

\textbf{Dissolving Touch}\textsuperscript{\textbf{A}}\textbf{: }Your touch deals 
4d6 acid damage.

\textbf{Dissolving Weapon}\textsuperscript{\textbf{A}}\textbf{: }Your weapon deals 
4d6 acid damage.

\textbf{Empathic Transfer}\textsuperscript{\textbf{A}}\textbf{: }Transfer another's 
wounds to yourself.

\textbf{Energy Adaptation, Specified}\textsuperscript{\textbf{A}}\textbf{: }Gain 
resistance 10 to one energy type.

\textbf{Feat Leech}\textsuperscript{\textbf{A}}\textbf{: }Borrow another's psionic 
or metapsionic feats.

\textbf{Hustle: }Instantly gain a move action.

\textbf{Levitate, Psionic: }You move up and down, forward and back, via mental 
support.

\textbf{Painful Strike}\textsuperscript{\textbf{A}}\textbf{: }Your natural weapons 
deal an extra 1d6 nonlethal damage.

\textbf{Prowess: }Instantly gain another attack of opportunity.

\textbf{Psionic Scent: }Gain the scent ability.

\textbf{Psionic Lion's Charge}\textsuperscript{\textbf{A}}\textbf{: }You can make 
full attack in same round you charge.

\textbf{Strength of My Enemy}\textsuperscript{\textbf{A}}\textbf{: }Siphon away 
your enemy's strength and grow stronger.

\textbf{Sustenance: }You can go without food and water for one day.

\textbf{Thought Shield}\textsuperscript{\textbf{A}}\textbf{: }Gain PR 13 against 
mind-affecting powers.

\textbf{Wall Walker: }Grants ability to walk on walls and ceilings.

3RD-LEVEL PSYCHIC WARRIOR POWERS 

\textbf{Claws of the Vampire: }Heal half of your claw's base damage. 

\textbf{Concealing Amorpha, Greater: }Quasi-real membrane grants you total concealment.

\textbf{Danger Sense: }Gain +4 bonus against traps.

\textbf{Dimension Slide}\textsuperscript{\textbf{A}}\textbf{: }Teleports you very 
short distance.

\textbf{Duodimensional Claw: }Increases your natural weapon's threat range.

\textbf{Ectoplasmic Form: }You gain benefits of being insubstantial and can fly 
slowly.

\textbf{Empathic Feedback}\textsuperscript{\textbf{A}}\textbf{: }When you are hit 
in melee, your attacker takes damage.

\textbf{Empathic Transfer, Hostile}\textsuperscript{\textbf{A}}\textbf{: }Your 
touch transfers your hurt to another.

\textbf{Escape Detection: }You become difficult to detect with clairsentience powers.

\textbf{Evade Burst}\textsuperscript{\textbf{A}}\textbf{: }You take no damage from 
a burst on a successful Reflex save.

\textbf{Exhalation of the Black Dragon}\textsuperscript{\textbf{A}}\textbf{: }Your 
acid breath deals 3d6 damage to a close target.

\textbf{Graft Weapon: }Your hand is replaced seamlessly by your weapon.

\textbf{Keen Edge, Psionic: }Doubles normal weapon's threat range.

\textbf{Mental Barrier}\textsuperscript{\textbf{A}}\textbf{: }Gain +4 deflection 
bonus to AC until your next action.

\textbf{Ubiquitous Vision: }You have all-around vision. 

\textbf{Vampiric Blade: }You heal half of your base weapon damage.

4TH-LEVEL PSYCHIC WARRIOR POWERS 

\textbf{Claw of Energy: }Your claws deal additional energy damage.

\textbf{Dimension Door, Psionic: }Teleports you short distance. 

\textbf{Energy Adaptation}\textsuperscript{\textbf{A}}\textbf{: }Your body converts 
energy to harmless light.

\textbf{Freedom of Movement, Psionic: }You cannot be held or otherwise rendered 
immobile.

\textbf{Immovability: }You are almost impossible to move and gain DR 15/-.

\textbf{Inertial Barrier: }Gain DR 5/-.

\textbf{Psychic Vampire. Touch attack drains 2 power points/level from foe. }

\textbf{Steadfast Perception: }Gain immunity to illusory effects, +6 bonus on Spot 
and Search checks.

\textbf{Truevenom: }Your natural weapons are covered in horrible poison.

\textbf{Truevenom Weapon: }Your weapon is horribly poisonous. 

\textbf{Weapon of Energy: }Weapon deals additional energy damage.

5TH-LEVEL PSYCHIC WARRIOR POWERS 

\textbf{Adapt Body: }Your body automatically adapts to hostile environments.

\textbf{Catapsi}\textsuperscript{\textbf{A}}\textbf{: }Psychic static inhibits 
power manifestation.

\textbf{Metaconcert}\textsuperscript{\textbf{A}}\textbf{: }Mental concert of two 
or more increases the total power of the participants.

\textbf{Oak Body}\textsuperscript{\textbf{A}}\textbf{: }Your body becomes as hard 
as oak.

\textbf{Psychofeedback: }Boost Str, Dex, or Con at the expense of one or more other 
scores.

6TH-LEVEL PSYCHIC WARRIOR POWERS

\textbf{Breath of the Black Dragon}\textsuperscript{\textbf{A}}\textbf{:} Breathe 
acid for 11d6 damage.

\textbf{Dispelling Buffer:} You are buffered from one \textit{dispel psionics }effect.

\textbf{Form of Doom}\textsuperscript{\textbf{A}}\textbf{:} You transform into 
a frightening tentacled beast.

\textbf{Mind Blank, Personal:} You are immune to scrying and mental effects.

\textbf{Suspend Life:} Put yourself into a state akin to suspended animation.

\end{document}
