%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsection*{{\LARGE PSIONIC POWERS (Q-W)}}

\vspace{12pt}
\section*{Quintessence}

Metacreativity (Creation)

\textbf{Level:} Shaper 4

\textbf{Display:} Material; see text

\textbf{Manifesting Time:} 1 round

\textbf{Range:} 0 ft.

\textbf{Effect:} 1-inch-diameter dollop of quintessence; see text

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 7

You collapse a bit of time from the continuum, forming a 1-ounce dollop of thick, 
gooey material called quintessence. This substance shimmers like a silver mirror 
when viewed from some angles but is transparent from other viewpoints. You can 
smooth a dollop of quintessence around any extremely small object.

Objects sealed within quintessence are protected from the effects of time; in practical 
terms, they enter a state of stasis. Living flesh with only partial contact with 
quintessence is also partially pulled out of the time stream (the manifester is 
immune to this effect). This disruption deals 1 point of damage per round beginning 
10 rounds after partial contact occurs.

Quintessence can be manually scraped away from a protected object, freeing it to 
rejoin the time stream. When you do this, there is a 75\% chance that the quintessence 
evaporates back into the continuum. Otherwise, it coalesces again into a 1-inch-diameter 
bead, available for later use.

Large quantities of quintessence could theoretically be gathered to preserve large 
items or structures (or even a complete living creature; if completely immersed, 
a living creature would not take the damage associated with partial contact). However, 
psionic characters and creatures are generally loath to do so because accumulations 
of quintessence weighing 1 pound or more hinder psionic activity within a 5-foot 
radius of the accumulation: Powers require twice as many power points to manifest, 
unless the manifester makes a successful Will save each time he or she attempts 
to manifest a power. Also in these circumstances, manifesting a psi-like ability 
that is usable at will is a full-round action rather than a standard action.

\vspace{12pt}
\section*{Read Thoughts}

Telepathy [Mind-Affecting]

\textbf{Level:} Telepath 2

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Area:} Cone-shaped emanation centered on you

\textbf{Duration:} Concentration, up to 1 min./level (D)

\textbf{Saving Throw:} Will negates; see text

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You know the surface thoughts of the mind of any creature in the area that fails 
a Will save. A target that succeeds on its save is not affected by this manifestation 
of the power, even if it leaves the area and then reenters the area before the 
duration expires.

Creatures of animal intelligence have simple, instinctual thoughts that you can 
pick up. If you read the thoughts of a creature with an Intelligence of 26 or higher 
(and at least 10 points higher than your own Intelligence score), you are stunned 
for 1 round and the power ends. This power does not let you pinpoint the location 
of an affected mind if you don't have line of sight to the subject.

Each round, you can turn to use this power in a new area. The power can penetrate 
barriers, but 1 foot of stone, 1 inch of common metal, a thin sheet of lead, or 
3 feet of wood or dirt blocks it.

\vspace{12pt}
\section*{Reality Revision}

Clairsentience

\textbf{Level:} Psion/wilder 9

\textbf{Saving Throw:} See text

\textbf{Power Resistance:} See text

\textbf{Power Points:} 17, XP

As \textit{bend reality}, but with more farreaching effects. A \textit{reality 
revision }can produce any one of the following effects.•

Duplicate any psion power of 8th level or lower, provided the power is not prohibited 
to you.•

Duplicate any other power (but not a spell) of 6th level or lower, such as a psychic 
warrior power.•

Duplicate any psion power of 7th level or lower even if it's a power prohibited 
to you.•

Undo the harmful effects of many other powers, such as \textit{microcosm, geas/quest, 
}or \textit{insanity}.•

Create a nonpsionic item of up to 25,000 gp in value.•

Create a psionic item, or add to the powers of an existing psionic item (see XP 
cost below).•

Grant a creature a +1 inherent bonus to an ability score. Two to five \textit{reality 
revisions }manifested in immediate succession can grant a creature a +2 to +5 inherent 
bonus to an ability score. Inherent bonuses are instantaneous, so they cannot be 
negated or dispelled. An inherent bonus cannot exceed +5 for a single ability score. 
Inherent bonuses to a particular ability score do not stack; only the best one 
applies.•

Remove injuries and afflictions. A single \textit{reality revision }can aid one 
creature per manifester level, and all subjects are cured of the same kind of affliction. 

\textit{Reality revision }can not restore the experience point loss from manifesting 
a power or casting a spell, or the level or  Constitution loss from being returned 
to life by those effects that reduce level or Constitution.•

Revive the dead. \textit{Reality revision }can bring a dead creature back to life 
by duplicating a \textit{resurrection }spell. This power can revive a dead creature 
whose body has been destroyed, but the task takes two manifestations of \textit{reality 
revision}, one to recreate the body and another to infuse the body with life again. 
\textit{Reality revision }cannot prevent a character who is brought back to life 
from losing a level.•

Transport travelers. This power can lift one creature per manifester level from 
anywhere on any plane and place those creatures anywhere else on any plane regardless 
of local conditions. An unwilling target gets a Will save to negate the effect, 
and power resistance (if any) applies.•

Undo misfortune. \textit{Reality revision }can undo a single recent event. Manifesting 
the power forces a reroll of any roll made within the last round (including your 
last turn). Reality reshapes itself to accommodate the new result. The reroll, 
however, may be as bad as or worse than the original roll. An unwilling target 
gets a Will save to negate the effect, and power resistance (if any) applies.

You can try to use \textit{reality revision }to produce more powerful effects than 
these, but doing so is dangerous. The manifestation may pervert your intent into 
a literal but undesirable fulfillment or only a partial fulfillment.

Duplicated powers allow saves and power resistance as normal (but save DCs are 
calculated as though the power is 9th level).

\textit{XP Cost: }The minimum XP cost for manifesting \textit{reality revision 
}is 5,000

XP. When a manifestation duplicates a power that has an XP cost, you must pay 5,000 
XP or that cost, whichever is more. When a manifestation creates or improves a 
psionic item, you must pay twice the normal XP cost for crafting or improving the 
item, plus an additional 5,000 XP.

\vspace{12pt}
\section*{Recall Agony}

Clairsentience [Mind-Affecting]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will half

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

The fabric of time parts to your will, revealing wounds your foe has received in 
the past (or has yet to receive). That foe takes 2d6 points of damage as the past 
(or future) impinges briefly on the present.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d6 points. For each extra 2d6 points of damage, this power's save 
DC increases by 1.

\vspace{12pt}
\section*{Recall Death}

Clairsentience [Death, Mind-Affecting]

\textbf{Level:} Psion/wilder 8

\textbf{Saving Throw:} Will partial; see text

\textbf{Power Points:} 15

As \textit{recall agony}, except the wounds revealed by folding the fourth dimension 
are potentially fatal. If the target fails its Will save. it dies. If the save 
succeeds, the target instead takes 5d6 points of damage.

\vspace{12pt}
\section*{Reddopsi}

Psychokinesis

\textbf{Level:} Kineticist 7

\textbf{Display:} Auditory, mental, and olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Until discharged or 10 min./level

\textbf{Power Points:} 13

When you manifest \textit{reddopsi, }powers targeted against you rebound to affect 
the original manifester. This effect reverses powers that have only you as a target 
(except \textit{dispel psionics }and similar powers or effects). Powers that affect 
an area and those that produce effects can't be reversed. \textit{Reddopsi }also 
can't reverse any power with a range of touch.

Should you rebound a power back against a manifester who also is protected by \textit{reddopsi}, 
the power rebounds once more upon you.

\vspace{12pt}
\section*{Remote View Trap}

Clairsentience [Electricity]

\textbf{Level:} Psion/wilder 6

\textbf{Display:} Mental and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 24 hours + 1 hour/level

\textbf{Saving Throw:} Will half; see text

\textbf{Power Resistance:} No

\textbf{Power Points:} 11

When others use \textit{clairvoyant sense}, \textit{remote viewing}, or other means 
of scrying you from afar, your prepared trap gives them a nasty surprise. If the 
scryer fails its saving throw, you are undetected. Moreover, the would-be observer 
takes 8d6 points of electricity damage. If the scryer makes its saving throw, it 
takes only 4d6 points of electricity damage and is able to observe you normally. 
Either way, you are aware of the attempt to view you, but not of the viewer or 
the viewer's location. It is possible that you might recognize the quasireal viewpoint 
of someone using the \textit{remote viewing }power if you could pierce its \textit{invisibility 
}(which is true for \textit{remote viewing }whether or not you use this power).

\vspace{12pt}
\section*{Remote Viewing}

Clairsentience (Scrying; see text)

\textbf{Level:} Seer 4

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 hour

\textbf{Range:} See text

\textbf{Effect:} Quasi-real viewpoint

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 7, XP

You send your mind across space and dimensions, forming it into a quasireal viewpoint 
from which you can see and hear some creature located at any distance from you, 
even if planar boundaries separate you. If the subject succeeds on a Will save, 
the \textit{remote viewing }attempt fails, and you can't attempt to view that creature 
again for at least 24 hours. The difficulty of the save depends on how well you 
know the subject and what sort of physical connection (if any) you have to that 
creature. Furthermore, if the subject is on another plane, it gets a +5 bonus on 
its Will save.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{2.657in}|}{\begin{minipage}[t]{2.657in}\raggedright
\textbf{Knowledge}\end{minipage}} & \multicolumn{1}{p{0.885in}|}{\begin{minipage}[t]{0.885in}\centering
\textbf{Will Save Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
None*\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+10\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{2.657in}|}{\begin{minipage}[t]{2.657in}\centering
Secondhand (you have heard of the subject)\end{minipage}} & \multicolumn{1}{p{0.885in}|}{\begin{minipage}[t]{0.885in}\centering
+5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Firsthand (you have met the subject)\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{2.657in}|}{\begin{minipage}[t]{2.657in}\centering
Familiar (you know the subject well)\end{minipage}} & \multicolumn{3}{p{1.024in}|}{\begin{minipage}[t]{1.024in}\centering
-5\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
*You must have some sort of connection to a creature you have no knowledge of.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{2.287in}|}{\begin{minipage}[t]{2.287in}\raggedright
\textbf{Connection}\end{minipage}} & \multicolumn{1}{p{0.822in}|}{\begin{minipage}[t]{0.822in}\centering
\textbf{Will Save Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Likeness or picture\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
-2\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{2.287in}|}{\begin{minipage}[t]{2.287in}\centering
Possession or garment\end{minipage}} & \multicolumn{1}{p{0.822in}|}{\begin{minipage}[t]{0.822in}\centering
-4\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Body part, lock of hair, bit of nail, etc.\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
-10\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{2.287in}|}{\begin{minipage}[t]{2.287in}\centering
Subject on another plane\end{minipage}} & \multicolumn{3}{p{0.960in}|}{\begin{minipage}[t]{0.960in}\centering
+5\end{minipage}}\\
\hline
\end{longtable}

If the subject fails its Will save, your mind coalesces a quasi-real viewpoint 
near enough to the subject to see and hear the subject and its immediate surroundings 
(up 30 feet in all directions away from the subject).

While the \textit{remote viewing }lasts, your real body remains unmoving and unaware 
of your actual surroundings. On the other hand, your quasi-real viewpoint is treated 
in some ways as if it were an invisible \textit{ectoplasmic form }of yourself, 
except as follows. This power is of the Scrying subdiscipline, but use the following 
information in place of the standard scrying sensor. As a quasi-real viewpoint, 
you can speak (though your voice is whispery).

You may potentially be sensed by the subject of your viewing (subjects who can 
see or sense invisible or hidden creatures automatically sense you; otherwise you 
make a Hide check with a +40 bonus to escape detection if immobile, or a +20 bonus 
if moving). You could be attacked (although if you become subject to \textit{dispel 
psionics}, the \textit{remote viewing }simply ends). If the subject moves, you 
can attempt to follow it at a speed of 20 feet, though if it gets farther than 
30 feet from you (or you move farther than 30 feet from it), the power ends.

You can attempt to manifest one power through your quasi-real viewpoint, but you 
must make a Concentration check (DC 20 + level of the power you wish to manifest) 
to succeed. Manifesting (or attempting and failing to manifest) a power immediately 
ends the \textit{remote viewing.}

Furthermore, all powers from your quasi-real viewpoint cost twice the usual number 
of power points (you can't exceed the power point limit set by your manifester 
level, so you are restricted to manifesting lower-level powers than you otherwise 
could). Power points you spend as a quasireal viewpoint are drained from your real 
body.

\textit{XP Cost: }20 XP.

\vspace{12pt}
\section*{Restoration, Psionic}

Psychometabolism (Healing)

\textbf{Level:} Egoist 6

\textbf{Display:} Material

\textbf{Manifesting Time:} 3 rounds

\textbf{Range:} Touch

\textbf{Target:} Creature touched

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates (harmless)

\textbf{Power Resistance:} Yes (harmless)

\textbf{Power Points:} 11

This power cures all ability damage, and it restores all points drained from a 
single ability score (your choice if more than one score is drained). It also eliminates 
any fatigue or exhaustion suffered by the target. \textit{Restoration }does not 
restore levels or Constitution points lost due to death.

\textit{Restoration }can remove negative levels. It can also restore one level 
to a creature who has had a level drained, if the number of days since the creature 
lost the level is equal to or less than your manifester level. In such a case, 
\textit{restoration }brings the creature up to the minimum number of experience 
points necessary to advance it to the next higher level, gaining it an additional 
Hit Die and level benefits accordingly.

\vspace{12pt}
\section*{Restore Extremity}

Psychometabolism (Healing)

\textbf{Level:} Egoist 5

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} Creature touched

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will half (harmless)

\textbf{Power Resistance:} Yes (harmless)

\textbf{Power Points:} 9

You restore a severed extremity to a creature that has lost a digit, hand, arm, 
leg, or even its head. This power does not restore life, but it returns a lost 
extremity to a living or dead creature if the creature is otherwise mostly intact. 
The original extremity need not be present when this power is manifested; a new 
extremity is created by the power. If a head is restored to a body, the original 
head (if not already destroyed) loses all spark of identity, and can be considered 
so much dead tissue.

\vspace{12pt}
\section*{Retrieve}

Psychoportation (Teleportation)

\textbf{Level:} Psion/wilder 6

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One object you can hold or carry in one hand, weighing up to 10 
lb./level

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates; see text

\textbf{Power Resistance:} No

\textbf{Power Points:} 11

You automatically teleport an item you can see within range directly to your hand. 
If the object is in the possession of an opponent, it comes to your hand if your 
opponent fails a Will save.

\textbf{Augment:} For every additional power point you spend, the weight limit 
of the target increases by 10 pounds.

\vspace{12pt}
\section*{Schism}

Telepathy [Mind-Affecting]

\textbf{Level:} Telepath 4

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level (D)

\textbf{Power Points:} 7

Your mind splits into two independent parts. Each part functions in complete autonomy, 
like two characters in one body. Your new ``second mind'' does not control your 
body physically but is free to take one standard action in each round if the action 
is purely mental (such as manifesting a power) in the same round you take your 
normal actions.

Your second mind can manifest powers using your power point reserve, but only as 
if your manifester level were six lower than it is. Your second mind doesn't provoke 
attacks of opportunity when manifesting a power, because doing so doesn't distract 
your primary mind.

Your second mind takes its first action on your turn in the round after \textit{schism 
}is manifested.

Both your minds communicate with each other telepathically. If you are subject 
to a compulsion or charm effect while you are of two minds, make a second saving 
throw if you fail the first. If you fail both, then the \textit{schism }ends and 
you are affected normally by the power. If you fail just one, the \textit{schism 
}ends immediately, but you are not subject to the compulsion or charm.

Your second mind does not gain any advantages if you are subject to a \textit{haste 
}effect, although you gain the overall standard benefits.

\vspace{12pt}
\section*{Second Chance}

Clairsentience

\textbf{Level:} Seer 5

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level or until discharged

\textbf{Power Points:} 9

You take a hand in influencing the probable outcomes of your immediate environment. 
You see the many alternative branches that reality could take in the next few seconds, 
and with this foreknowledge you gain the ability to reroll one attack roll, one 
saving throw, one ability check, or one skill check each round. You must take the 
result of the reroll, even if it's worse than the original roll. You do not have 
to make another roll if satisfied with your original roll.

\vspace{12pt}
\section*{Sense Link}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Target:} One willing creature

\textbf{Duration:} Concentration, up to 1min./level

\textbf{Power Points:} 1

You perceive what the subject creature perceives using its sight, hearing, taste, 
or smell. Only one sense is linked, and you cannot switch between senses with the 
same manifestation.

You make any skill checks involving senses, such as Spot or Listen, as the subject, 
and only within the subject's field of view. You lose your Dexterity bonus to AC 
while directly sensing what the subject senses.

Once \textit{sense link }is manifested, the link persists even if the subject moves 
out of the range of the original manifestation (but the link does not work across 
planes). You do not control the subject, nor can you communicate with it by means 
of this power.

The strength of the subject's linked sense could be enhanced by other powers or 
items, allowing you the same enhanced sense. You are subject to any gaze attack 
affecting the subject creature (if you linked vision). If you are blinded or deafened, 
or suffer some other sensory deprivation, the linked creature functions as an independent 
sensory organ, and provides you the benefit of the linked sense from its perspective 
while this power's duration lasts.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. If you spend 2 additional power points, you can have the subject perceive one 
of your senses instead of the other way around.

2. If you spend 4 additional power points, you can link to a second sense of the 
same subject.

\vspace{12pt}
\section*{Sense Link, Forced}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 2

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

As \textit{sense link, }except you can use this power on any creature (willing 
or unwilling), and this power can't be augmented.

\vspace{12pt}
\section*{Sensitivity to Psychic Impressions}

Clairsentience

\textbf{Level:} Seer 2

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 hour

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} Spread with a radius of 25 ft. + 5 ft./2 levels, centered on you

\textbf{Duration:} Concentration, up to 10 min./level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You gain historical vision in a given location. Rooms, streets, tunnels, and other 
discrete locations accumulate psychic impressions left by powerful emotions experienced 
in a given area. These impressions offer you a picture of the location's past.

The types of events most likely to leave psychic impressions are those that elicited 
strong emotions: battles and betrayals, marriages and murders, births and great 
pain, or any other event where one emotion dominates. Everyday occurrences leave 
no residue for a manifester to detect.

The vision of the event is dreamlike and shadowy. You do not gain special knowledge 
of those involved in the vision, though you might be able to read large banners 
or other writing if they are in your language.

Beginning with the most recent significant event at a location and working backward 
in time, you can sense one distinct event for every 10 minutes you maintain concentration, 
if any such events exist to be sensed. Your sensitivity extends into the past a 
maximum number of years equal to 100 x your manifester level.

\vspace{12pt}
\section*{Sequester, Psionic}

Clairsentience

\textbf{Level:} Psion/wilder 7

\textbf{Display:} None

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} One willing creature or one object (up to a 2-ft. cube/level) 
touched

\textbf{Duration:} One day/level (D)

\textbf{Saving Throw:} None or Will negates (object)

\textbf{Power Resistance:} No or Yes (object)

\textbf{Power Points:} 13, XP

As the \textit{sequester }spell, except as noted here. 

\textit{XP Cost: }75 XP.

\vspace{12pt}
\section*{Shadow Body}

Psychometabolism

\textbf{Level:} Psion/wilder 8

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level (D)

\textbf{Power Points:} 15

Your body and all your equipment are subsumed by your shadow. As a living shadow, 
you blend perfectly into any other shadow and vanish in darkness. You appear as 
an unattached shadow in areas of full light.

You can move at your normal speed, on any surface, including walls and ceilings, 
as well as across the surfaces of liquids---even up the face of a waterfall.

Your space does not change, so you cannot move into locations you would not normally 
be able to move into.

While in your \textit{shadow body, }you gain damage reduction 10/magic and darkvision 
out to 60 feet. You are immune to extra damage from critical hits, ability damage, 
disease, drowning, and poison. You take only half damage from acid, electricity, 
and fire of all kinds.

While affected by this power, you can be detected by powers that read thoughts, 
life, or presences (including \textit{true seeing}), or if you make suspicious 
movements in lighted areas.

You cannot harm anyone physically or manipulate any objects, but you can use your 
powers normally. Doing so may attract notice, but if you remain in a shadowed area, 
you get a +15 bonus on your Hide check to remain unnoticed.

\vspace{12pt}
\section*{Share Pain}

Psychometabolism

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Material and mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Targets:} You and one willing creature, or two willing creatures; see text

\textbf{Duration:} 1 hour/level (D)

\textbf{Power Points:} 3

This power creates a psychometabolic connection between you and a willing subject 
so that some of your wounds are transferred to the subject. You take half damage 
from all attacks that deal hit point damage to you, and the subject takes the remainder. 
The amount of damage not taken by you is taken by the subject. If your hit points 
are reduced by a lowered Constitution score, that reduction is not shared with 
the subject because it is not a form of hit point damage. When this power ends, 
subsequent damage is no longer divided between the subject and you, but damage 
already shared is not reassigned.

If you and the subject move farther away from each other than close range, the 
power ends.

You can manifest this power on two willing subjects, one of which you designate 
to share its damage with the other.

\vspace{12pt}
\section*{Share Pain, Forced}

Psychometabolism

\textbf{Level:} Psion/wilder 3

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} Fortitude negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 5

As \textit{share pain}, except as noted here.

You attempt to force the sharing of your wounds with an unwilling creature, and 
for less time. If you are immune to the type of damage dealt, or if you convert 
lethal damage into nonlethal damage, the target takes no damage.

\textbf{Augment:} For every 2 additional power points you spend, this power's save 
DC increases by 1.

\vspace{12pt}
\section*{Shatter Mind Blank}

Telepathy

\textbf{Level:} Psion/wilder 5

\textbf{Display:} Olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 30 ft.

\textbf{Area:} 30-ft.-radius burst centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 9

This power can negate a \textit{psionic mind blank }or a \textit{personal mind 
blank }affecting the target. If the target fails its save and does not overcome 
your attempt with its power resistance, you can shatter the mind blank by making 
a successful check (1d20 + your manifester level, maximum +20) against a DC equal 
to 11 + the manifester level of the creator of the \textit{mind blank }effect. 
If you succeed, the \textit{psionic mind blank }or \textit{personal mind blank 
}ends, allowing you to affect the target thereafter with mind-affecting powers.

\vspace{12pt}
\section*{Skate}

Psychoportation

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal or touch; see text

\textbf{Target:} You or one willing creature or one unattended object (total weight 
up to 100 lb./level); see text

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} Yes (harmless, object)

\textbf{Power Points:} 1

You, another willing creature, or an unattended object can slide along solid ground 
as if on smooth ice. If you manifest \textit{skate }on yourself or another creature, 
the subject of the power retains equilibrium by mental desire alone, allowing her 
to gracefully skate along the ground, turn, or stop suddenly as desired. The skater's 
land speed increases by 15 feet. (This adjustment is treated as an enhancement 
bonus.) As with any effect that increases speed, this power affects the subject's 
maximum jumping distance.

The subject can skate up or down any incline or decline she could normally walk 
upon without mishap, though skating up an incline reduces the subject's speed to 
normal, while skating down a decline increases her speed by an additional 15 feet. 
(This adjustment is treated as a circumstance bonus.)

If you manifest \textit{skate }on an object, treat the object as having only one-tenth 
of its normal weight for the purpose of dragging it along the ground.

\vspace{12pt}
\section*{Solicit Psicrystal}

Telepathy

\textbf{Level:} Psion/wilder 3

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 swift action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} Your psicrystal

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} No

\textbf{Power Resistance:} No

\textbf{Power Points:} 5

Your psicrystal takes over the responsibility of maintaining concentration on any 
single power you

have manifested and are concentrating on. While maintaining this concentration, 
the psicrystal is limited to move actions in each round, as normal. When the duration 
of \textit{solicit psicrystal }expires, the power you transferred to the psicrystal 
ends (even if this would mean that the power ends earlier than normal). If necessary, 
the psicrystal makes Concentration checks using your Concentration modifier.

You can manifest this power (and transfer the responsibility) with an instant thought, 
quickly enough to gain the benefit of the power before you take any other actions 
in a round. Manifesting the power is a swift action, like manifesting a quickened 
power, and it counts toward the normal limit of one quickened power per round. 
You cannot manifest this power when it isn't your turn.

\textbf{Augment:} For every additional power point you spend, this power's maximum 
duration increases by 1 round.

\vspace{12pt}
\section*{Steadfast Perception}

Clairsentience

\textbf{Level:} Psychic warrior 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level (D)

\textbf{Power Points:} 7

Your vision cannot be distracted or misled, granting you immunity to all figments 
and glamers (such as \textit{invisibility}). Moreover, your Spot and Search checks 
receive a +6 enhancement bonus for the duration of this power. This power also 
grants you another saving throw against someone using \textit{false sensory input 
}on you, but you must realize that that power has been used in order to know enough 
to manifest \textit{steadfast perception}.

\vspace{12pt}
\section*{Stomp}

Psychokinesis

\textbf{Level:} Psychic warrior 1

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 20 ft.

\textbf{Area:} Cone-shaped spread

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Reflex negates

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

Your foot stomp precipitates a psychokinetic shock wave that travels along the 
ground, toppling creatures and loose objects. The shock wave affects only creatures 
standing on the ground within the power's area. Creatures that fail their saves 
are thrown to the ground, become prone, and take 1d4 points of nonlethal damage.

\textbf{Augment:} For every additional power point you spend, this power's nonlethal 
damage increases by 1d4 points.

\vspace{12pt}
\section*{Strength of My Enemy}

Psychometabolism

\textbf{Level:} Psychic warrior 2

\textbf{Display:} Visual; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level (D)

\textbf{Power Points:} 3

You gain the ability to siphon away your enemy's strength for your own use. One 
of your natural or manufactured weapons becomes the instrument of your desire, 
and deals 1 point of Strength damage on each successful hit. You gain that point 
of Strength as an enhancement bonus to your Strength score. Strength you siphon 
from different foes is tracked separately---the total siphoned from each individual 
foe is considered a separate enhancement bonus to your Strength (maximum +8), and 
you gain only the highest total.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every 3 additional power points you spend, the maximum enhancement bonus 
you can add to your Strength increases by 2.

2. If you spend 6 additional power points, you can manifest this power as a swift 
action.

\vspace{12pt}
\section*{Suggestion, Psionic}

Telepathy (Compulsion) [Mind-Affecting, Language-Dependent]

\textbf{Level:} Telepath 2

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} 1 hour/level or until completed

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

As the \textit{suggestion }spell, except as noted here.

\textbf{Augment:} For every 2 additional power points you spend, this power can 
affect an additional target. Any additional target cannot be more than 15 feet 
from another target of the power.

\vspace{12pt}
\section*{Suspend Life}

Psychometabolism

\textbf{Level:} Psion/wilder 6, psychic warrior 6

\textbf{Display:} Olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Permanent unless ended or dismissed; see text

\textbf{Power Points:} 11

You can place yourself into a trance so deep that you are almost in suspended animation. 
Even powers that detect life or thought are incapable of determining that you are 
alive.

While you are suspended, you are aware of your surroundings. You feel the passage 
of one day for every year that actually passes. Though on a slower schedule, you 
grow hungry after a ``day'' without food (though a year passes in actuality) and 
begin to suffer the effects of thirst and starvation as appropriate.

If you take any damage, you come out of your trance 4 rounds later. The trance 
can also be ended by a successful use of \textit{dispel psionics. }If you choose 
to dismiss the power, your trance ends 10 rounds later.

\vspace{12pt}
\section*{Sustenance}

Psychometabolism

\textbf{Level:} Psion/wilder 2, psychic warrior 2

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

\textbf{Power Points:} 3

You can go without food and water for one day. Each time you manifest this power, 
your body manufactures suffi- cient solid and liquid nourishment to satisfy your 
needs for that time.

\vspace{12pt}
\section*{Swarm of Crystals}

Metacreativity (Creation)

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 15 ft.

\textbf{Area:} Cone-shaped spread

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

Thousands of tiny crystal shards spray forth in an arc from your hand. These razorlike 
crystals slice everything in their path. Anyone caught in the cone takes 3d4 points 
of slashing damage.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d4 points.

\vspace{12pt}
\section*{Synesthete}

Psychometabolism

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display: }Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level (D)

\textbf{Power Points:} 1

You receive one kind of sensory input when a different sense is stimulated. In 
particular, you can either feel light or feel sound. You can shift your stimulated 
sense between these two options once per round as a swift action. Your senses continue 
to work normally as well, unless they are impaired for some reason.

Your face must be uncovered to use this power, because it is the skin of your face 
that acts as the sensory receiver.

If you are feeling light by absorbing ambient light onto your skin, you have your 
normal visual abilities (except for darkvision), even if your eyes are closed or 
you are blinded. If your eyes are working normally, you gain a +4 circumstance 
bonus on all Spot and Search checks. While feeling light, you are immune to gaze 
attacks.

If you are feeling sound by absorbing sound onto your skin and your ears are working 
normally, the expanded audio input provides you with a +4 circumstance bonus on 
Listen checks.

Psionic or magical displacement effects, invisibility effects, illusions, and other 
similar effects confuse your \textit{synesthete }senses just as they would your 
normal senses.

You can also use this power to see sound if you are deafened, or hear light if 
you are blinded, thus removing all penalties associated with either condition (though 
you gain no bonuses for using the power in this way if you are not deafened or 
blinded).

\vspace{12pt}
\section*{Telekinetic Force}

Psychokinesis [Force]

\textbf{Level:} Psion/wilder 3

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One object at a time

\textbf{Duration:} Concentration, up to 1 round/level

\textbf{Saving Throw:} Will negates (object); see text

\textbf{Power Resistance:} Yes (object)

\textbf{Power Points:} 5

You move an object by concentrating your mind upon its current location and then 
the location you desire, creating a sustained force. You can move an object weighing 
no more than 250 pounds up to 20 feet per round. A creature can negate the effect 
on an object it possesses with a successful Will save or with power resistance. 
The weight can be moved across the ground or through the air. This power ends if 
the object is forced out of range. If you cease concentration, the object falls 
or stops.

You can drop a weight and pick up another during the power's duration, as long 
as you don't stop concentrating on maintaining the power. An object can be telekinetically 
manipulated as if you were moving it with one hand.

If you spend at least 5 rounds concentrating on an unattended object, you can attempt 
to break or burst it as if making a Strength check, except that you apply your 
key ability modifier to the check instead of your Strength modifier.

\textbf{Augment:} For every additional power point you spend, the weight limit 
of the target increases by 25 pounds.

\vspace{12pt}
\section*{Telekinetic Maneuver}

Psychokinesis [Force]

\textbf{Level:} Psion/wilder 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature

\textbf{Duration:} Concentration, up to 1 round/level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 7

You can affect a foe by concentrating your mind upon its current status and the 
status you desire, once per round. You can perform a bull rush, a disarm, a grapple 
(including a pin), or a trip. Resolve these attempts as normal, except that they 
don't provoke attacks of opportunity, you use your manifester level in place of 
your base attack bonus (for disarm and grapple attempts), you use your Intelligence 
modifier in place of your Strength modifier or Dexterity modifier, and a failed 
attempt doesn't allow a reactive attempt by the target (such as normally allowed 
on disarm or trip attempts). No save is allowed against these attempts, but power 
resistance applies normally.

\textbf{Augment:} For every 2 additional power points you spend, this power grants 
a +1 bonus on your checks involving bull rush, disarm, grapple, or trip attempts.

\vspace{12pt}
\section*{Telekinetic Sphere, Psionic}

Psychokinesis [Force]

\textbf{Level:} Kineticist 8

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} 1-ft.-diameter/level sphere, centered around creatures or objects

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} Reflex negates (object)

\textbf{Power Resistance:} Yes (object)

\textbf{Power Points:} 15

As the \textit{telekinetic sphere }spell, except as noted here.

\vspace{12pt}
\section*{Telekinetic Thrust}

Psychokinesis

\textbf{Level:} Psion/wilder 3

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target or Targets:} One or more objects or creatures with a total weight 
of 250 lb. or less

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates or Will negates (object); see text

\textbf{Power Resistance:} Yes or Yes (object); see text

\textbf{Power Points:} 5

You can affect one or more objects or creatures by concentrating your mind upon, 
sending them in a deadly hail at your foes---or simply by hurling your foe! You 
can hurl one object or creature per manifester level (maximum fifteen separate 
targets), as long as all are within the power's range and each is no more than 
10 feet away from another one. Each object or creature can be hurled a maximum 
distance of 10 feet per level.

You must succeed on ranged attack rolls (one per creature or object thrown) to 
hit the target of the hurled items with the items, applying your Intelligence modifier 
to the attack roll instead of your Dexterity modifier. Hurled weapons deal their 
standard damage (your Strength bonus does not apply; arrows or bolts deal damage 
as daggers of their size when used in this manner). Other objects deal damage ranging 
from 1 point per 25 pounds of weight (for less dangerous objects such as an empty 
barrel) to 1d6 points per 25 pounds of weight (for hard, dense objects such as 
a boulder).

Creatures are allowed Will saves (and power resistance) to negate the effect, as 
are those whose held possessions are targeted by this power.

If you use this power to hurl a creature against a solid surface, it takes damage 
as if it had fallen 10 feet (1d6 points).

\textbf{Augment:} For every additional power point you spend, the weight limit 
of the target or targets increases by 25 pounds.

\vspace{12pt}
\section*{Telempathic Projection}

Telepathy (Charm) [Mind-Affecting]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 1

You alter the subject's mood, adjusting its attitude toward you by one step in 
a positive direction. For instance, an unfriendly creature can be made indifferent, 
or a hostile creature unfriendly. You can grant a +4 bonus on your own (or others') 
Bluff, Diplomacy, Intimidate, Perform, or Sense Motive checks involving the affected 
creature.

\vspace{12pt}
\section*{Teleport, Psionic}

Psychoportation (Teleportation)

\textbf{Level:} Nomad 5

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal and touch

\textbf{Target or Targets:} You and touched objects or other touched willing creatures

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None or Will negates (object)

\textbf{Power Resistance:} No or Yes (object)

\textbf{Power Points:} 9

As the \textit{teleport }spell, except as noted here.

\vspace{12pt}
\section*{Teleport, Psionic Greater}

Psychoportation (Teleportation)

\textbf{Level:} Psion/wilder 8

\textbf{Power Points:} 15

As the \textit{greater teleport }spell, except as noted here.

\vspace{12pt}
\section*{Teleportation Circle, Psionic}

Psychoportation (Teleportation)

\textbf{Level:} Nomad 9

\textbf{Display:} Mental

\textbf{Manifesting Time:} 10 minutes

\textbf{Range:} 0 ft.

\textbf{Effect:} 5-ft.-radius circle that teleports those who activate it

\textbf{Duration:} 10 min./level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 17

As the \textit{teleportation circle }spell, except as noted here.

\vspace{12pt}
\section*{Teleport Trigger}

Psychoportation (Teleportation)

\textbf{Level:} Nomad 5

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 hour/level (D)

\textbf{Power Points:} 9

You specify a situation that triggers your automatic manifestation of a \textit{psionic 
teleport, }taking you to a predetermined location. You must know the \textit{psionic 
teleport }power and have sufficient power points to manifest it when the specified 
situation occurs.

The \textit{teleport trigger }goes off on the initiative count immediately after 
the specified situation occurs, even if you are flat-footed or you have already 
taken your turn in the current round. The specified situation can be described 
in general terms or specific terms.

\vspace{12pt}
\section*{Temporal Acceleration}

Psychoportation

\textbf{Level:} Psion/wilder 6

\textbf{Display:} None

\textbf{Manifesting Time:} 1 swift action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round (in apparent time); see text

\textbf{Power Points:} 11

You enter another time frame, speeding up so greatly that all other creatures seem 
frozen, though they are actually still moving at normal speed. You are free to 
act for 1 round of apparent time. You can manifest powers, cast spells, move, or 
perform other types of actions, subject to the restrictions outlined below.

While your \textit{temporal acceleration }is in effect, other creatures are invulnerable 
to your attacks and powers. This means you cannot target a creature with any attack 
or power. However, a power you manifest that affects an area and has a duration 
longer than the remaining duration of your \textit{temporal acceleration }has its 
normal effect on creatures in the area once this power ends.

You can affect an unattended object but not an object held, carried, or worn by 
another creature. You are undetectable by any means while your \textit{temporal 
acceleration }lasts.

While under the effect of this power, you cannot enter an area protected by a \textit{null 
psionics field }or by a power or spell that neutralizes high-level powers or spells. 
Normal and magical fire, cold, acid, and the like can still harm you.

When your \textit{temporal acceleration }expires, you resume acting during your 
current turn in the standard time frame. You are shaken for 1 round upon your return 
to the standard time frame.

Splintered or partitioned minds within your own mind, such as might be in effect 
through the use of powers such as \textit{schism}, are not temporally speeded up, 
even if your second mind manifested this power (your primary mind gains the benefit, 
while your second mind remains stuck in the standard time frame).

Manifesting this power is a swift action, like manifesting a quickened power, and 
it counts toward the normal limit of one quickened power per round. You cannot 
manifest this power when it isn't your turn.

\textbf{Augment:} For every 4 additional power points you spend, this power's duration 
(in apparent time) increases by 1 round.

\vspace{12pt}
\section*{Thicken Skin}

Psychometabolism

\textbf{Level:} Egoist 1, psychic warrior 1

\textbf{Display:} Material and olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level

\textbf{Power Points:} 1

Your skin or natural armor thickens and spreads across your body, providing a +1 
enhancement bonus to your Armor Class.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every 3 additional power points you spend, the enhancement bonus increases 
by 1.

2. If you spend 6 additional power points, you can manifest this power as a swift 
action.

\vspace{12pt}
\section*{Thought Shield}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 2, psychic warrior 2

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 immediate action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round

\textbf{Power Points:} 3

You fortify your mind against intrusions, gaining power resistance 13 against all 
mind-affecting powers.

You can manifest this power instantly, quickly enough to gain its benefits in an 
emergency. Manifesting the power is an immediate action, like manifesting a quickened 
power, and it counts toward the normal limit of one quickened power per round. 
You can use this power even when it's not your turn.

\textbf{Augment:} For every additional power point you spend, this power's duration 
increases by 1 round, and the power resistance it provides increases by 1 point.

\vspace{12pt}
\section*{Time Hop}

Psychoportation

\textbf{Level:} Psion/wilder 3

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} One Medium or smaller creature, or one object weighing 300 lb. 
or less

\textbf{Duration:} 1 round/level; see text

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 5

The subject of the power hops forward in time 1 round for every manifester level 
you have. In effect, the subject seems to disappear in a shimmer of silver energy, 
then reappear after the duration of this power expires. The subject reappears in 
exactly the same orientation and condition as before. From the subject's point 
of view, no time has passed at all.

In each round of the power's duration, on what would have been the subject's turn, 
it can attempt a DC 15 Wisdom check. Success allows the subject to return. The 
subject can act normally on its next turn after this power ends.

If the space from which the subject departed is occupied upon his return to the 
time stream, he appears in the closest unoccupied space, still in his original 
orientation. Determine the closest space randomly if necessary.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every 2 additional power points you spend, you can affect a creature of 
one size category larger, or double the weight of an object to be affected.

2. For every 2 additional power points you spend, this power can affect an additional 
target. Any additional target cannot be more than 15 feet from another target of 
the power.

\vspace{12pt}
\section*{Time Hop, Mass}

Psychoportation

\textbf{Level:} Nomad 8

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} All willing creatures in range

\textbf{Duration:} Up to 1 hour/level; see text

\textbf{Power Points:} 15

As \textit{time hop}, except you can affect any number of willing subjects in range, 
including yourself. You can choose which creatures are affected by the power. The 
subjects hop forward in time a number of hours equal to your manifester level, 
or some shorter number of hours; you decide how many hours the \textit{mass time 
hop }lasts when you manifest the power.

\textbf{Augment:} If you spend 6 additional power points, you can manifest this 
power as an immediate action.

\vspace{12pt}
\section*{Time Regression}

Psychoportation

\textbf{Level:} Nomad 9

\textbf{Display:} None

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

\textbf{Power Points:} 17, XP

You can regress apparent time 1 round into the past. In effect, you ``replay'' 
the previous round of activity. The power regresses time to the point along the 
time stream just prior to your previous turn, undoing the effects of everyone else's 
actions in the meantime. Once you have used \textit{time regression, }only you 
retain knowledge of what happened during the round that is being replayed; however, 
you can communicate that knowledge verbally to your companions, if desired. During 
the round that you live through a second time, you can act on knowledge you previously 
gained by already living through the immediate future. In all likelihood, you'll 
probably not choose to manifest \textit{time regression }during your second pass 
through the time stream, instead taking completely new actions, but you pay the 
XP cost all the same.

\textit{XP Cost: }1,000 XP.

\vspace{12pt}
Timeless Body

Psychoportation

\textbf{Level:} Psion/wilder 9

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round

\textbf{Power Points:} 17

Your body ignores all harmful (and helpful) effects, beginning when you finish 
manifesting this power and ending at the end of your next turn. While \textit{timeless 
body }is in effect, you are invulnerable to all attacks and powers.

This power cannot be quickened.

\vspace{12pt}
\section*{Tongues, Psionic}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} None

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level

\textbf{Power Points:} 3

As the \textit{tongues }spell, except as noted here. This power does not enable 
you to speak with creatures immune to mind-affecting powers.

\vspace{12pt}
\section*{Tornado Blast}

Psychokinesis

\textbf{Level:} Kineticist 9

\textbf{Display:} Auditory and visual; see text

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Area:} 40-ft.-radius spread

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Reflex half; see text

\textbf{Power Resistance:} No

\textbf{Power Points:} 17

You induce the formation of a slender vortex of fiercely swirling air. When you 
manifest it, a vortex of air visibly and audibly snakes out from your outstretched 
hand.

If you want to aim the vortex at a specific creature, you can make a ranged touch 
attack to strike the creature. If you succeed, direct contact with the vortex deals 
8d6 points of damage to the creature (no save).

Regardless of whether your ranged touch attack hits (and even if you forgo the 
attack), all creatures in the area (including the one possibly damaged by direct 
contact) are picked up and violently dashed about, dealing 17d6 points of damage 
to each one. Creatures that make a successful Reflex save take half damage.

After being dashed about, each creature that was affected finds itself situated 
in a new space 1d4 x 10 feet away from its original space in a random direction. 
Walls and other barriers can restrict this relocation; in such a case, the creature 
ends up adjacent to the barrier.

\textbf{Augment:} For every additional power point you spend, this power's area 
damage (not the damage from direct contact dealt to a specific creature) increases 
by 1d6 points (to a maximum of 24d6 points). For each extra 2d6 points of damage, 
this power's save DC increases by 1.

\vspace{12pt}
\section*{Touchsight}

Psychometabolism

\textbf{Level:} Psion/wilder 3

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal; see text

\textbf{Target:} You

\textbf{Duration:} 1 min./level (D)

\textbf{Power Points:} 5

You generate a subtle telekinetic field of mental contact, allowing you to ``feel'' 
your surroundings even in total darkness or when your sight would otherwise be 
obscured by your physical environment. Your \textit{touchsight }field emanates 
from you out to 60 feet. You ignore invisibility, darkness, and concealment, though 
you must have line of effect to a creature or an object to discern it. You do not 
need to make Spot or Listen checks to notice creatures; you can detect and pinpoint 
all creatures within 60 feet. In many circumstances, comparing your regular senses 
to what you learn with \textit{touchsight }is enough to tell you the difference 
between visible, invisible, hiding, and concealed creatures.

\textbf{Augment:} For every 2 additional power points you spend, the radius of 
your \textit{touchsight }field increases by 10 feet.

\vspace{12pt}
\section*{Tower of Iron Will}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 5

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 immediate action

\textbf{Range:} 10 ft.

\textbf{Area:} 10-ft.-radius emanation centered on you

\textbf{Duration:} 1 round

\textbf{Saving Throw:} None (harmless)

\textbf{Power Resistance:} Yes (harmless)

\textbf{Power Points:} 9

You generate a bastion of thought so strong that it offers protection to you and 
everyone around you, improving the self-control of all. You and all creatures in 
the power's area gain power resistance 19 against all mindaffecting powers.

You can manifest this power instantly, quickly enough to gain its benefits in an 
emergency. Manifesting the power is an immediate action, like manifesting a quickened 
power, and it counts toward the normal limit of one quickened power per round.

You can use this power even when it is not your turn.

\textbf{Augment:} For every additional power point you spend, this power's duration 
increases by 1 round and the power resistance it provides increases by 1 point.

\vspace{12pt}
\section*{Trace Teleport}

Clairsentience

\textbf{Level:} Psion/wilder 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} Spread with a radius of 25 ft. + 5 ft./2 levels, centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 7

As \textit{detect teleportation}, except you can trace the destination of any psionic 
or magical teleportation made by others within this power's area within the last 
minute.

You know the direction and distance the individuals traveled and could teleport 
to the location yourself if you so desired (and if you know the \textit{psionic 
teleport }power), as if you had ``seen casually'' the location. This power does 
not grant you any information on the conditions at the other end of the trace beyond 
the mental coordinates of the location.

\textbf{Augment:} If you spend 2 additional power points, this power's range increases 
to Medium (100 ft. + 10 ft./level).

\vspace{12pt}
\section*{True Creation}

Metacreativity (Creation)

\textbf{Level:} Shaper 9

\textbf{Duration:} Instantaneous

\textbf{Power Points:} 17, XP

As \textit{psionic major creation}, except items created are enduring and cannot 
be negated by dispelling magic or negating powers. For all intents and purposes, 
these items are completely real.

\textit{XP Cost: }1/5 of the item's gold piece value, or a minimum of 1 XP.

\vspace{12pt}
\section*{True Metabolism}

Psychometabolism

\textbf{Level:} Psion/wilder 8

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 15

You are difficult to kill while this power persists. You automatically heal damage 
at the rate of 10 hit points per round.

This power is not effective against damage from starvation, thirst, or suffocation. 
Also, attack forms that don't deal hit point damage (for example, most poisons) 
ignore \textit{true metabolism}. You can also use this power to regrow lost portions 
of your body and to reattach severed limbs or body parts, if you do nothing but 
concentrate on regrowing the lost body part or reattaching the severed limb for 
the duration of the power. You do not gain the benefits described earlier when 
you manifest \textit{true metabolism }for this purpose. You must have a Constitution 
score to gain any of this power's benefits.

\vspace{12pt}
\section*{True Seeing, Psionic}

Clairsentience

\textbf{Level:} Psion/wilder 5

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 9

As the \textit{true seeing }power, except as noted here. 

\vspace{12pt}
\section*{Truevenom}

Psychometabolism

\textbf{Level:} Psychic warrior 4

\textbf{Display:} Material; see text

\textbf{Manifesting Time:} 1 swift action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level or until discharged

\textbf{Saving Throw:} None and Fortitude negates; see text

\textbf{Power Points:} 7

If you have a claw attack (either from an actual natural weapon or from an effect 
such as \textit{claws of the beast}), you can use this power to produce a horrible 
poison that coats one of your claws. On your next successful melee attack with 
the claw during the power's duration, the poison deals 1d8 points of Constitution 
damage immediately and another 1d8 points of Constitution damage 1 minute later. 
The target of your attack can negate each instance of damage with a Fortitude save.

\vspace{12pt}
\section*{Truevenom Weapon}

Psychometabolism (Creation)

\textbf{Level:} Psychic warrior 4

\textbf{Range:} Touch

\textbf{Target:} Weapon touched

\textbf{Power Points:} 7

As \textit{truevenom}, except your weapon gains the poison coating as long as it 
remains in your grip, until the effect is discharged, or until the duration expires, 
whichever occurs first.

\vspace{12pt}
\section*{Ubiquitous Vision}

Clairsentience

\textbf{Level:} Psion/wilder 3, psychic warrior 3

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level (D)

\textbf{Power Points:} 5

You have metaphoric ``eyes in the back of your head,'' and on the sides and top 
as well, granting you benefits in specific situations. In effect, you have a 360-degree 
sphere of sight, allowing you a perfect view of creatures that might otherwise 
flank you. Thus, flanking opponents gain no bonus on their attack rolls, and rogues 
are denied their sneak attack ability because you do not lose your Dexterity bonus 
(but they may still sneak attack you if you are caught flat-footed). Your Spot 
and Search checks gain a +4 enhancement bonus. Concurrently, you take a -4 penalty 
on saves against all gaze attacks during the power's duration.

\vspace{12pt}
\section*{Ultrablast}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 7

\textbf{Display:} Auditory; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 15 ft.

\textbf{Area:} 15-ft.-radius spread centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will half

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 13

You ``grumble'' psychically (which both psionic and nonpsionic creatures can detect), 
then release a horrid shriek from your subconscious that disrupts the brains of 
all enemies in the power's area, dealing 13d6 points of damage to each enemy.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d6 points. 

\vspace{12pt}
\section*{Vampiric Blade}

Psychometabolism

\textbf{Level:} Psychic warrior 3

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 0 ft.

\textbf{Target:} One weapon you hold

\textbf{Duration:} 1 round/level

\textbf{Power Points:} 5

As \textit{claws of the vampire}, except your weapon is affected as long as it 
remains in your grip or until this power's duration expires.

\vspace{12pt}
\section*{Vigor}

Psychometabolism

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display:} Material and olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 1

You suffuse yourself with power, gaining 5 temporary hit points. Using this power 
again when an earlier manifestation has not expired merely replaces the older temporary 
hit points (if any remain) with the newer ones.

\textbf{Augment:} For every additional power point you spend, the number of temporary 
hit points you gain increases by 5.

\vspace{12pt}
\section*{Wall of Ectoplasm}

Metacreativity (Creation)

\textbf{Level:} Psion/wilder 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} Wall whose area is up to one 10-ft. square/level or a sphere or 
hemisphere with a radius of up to 1 ft./level

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 7

You fashion a roiling wall of ectoplasm, imbuing it with solidity. The wall cannot 
move once it is formed. It is 1 inch thick per four manifester levels and occupies 
up to one 5-foot square per level. Each 5-foot square of the wall has 10 hit points 
per inch of thickness and hardness 5. A section of the wall whose hit points drop 
to 0 is breached. If a creature tries to break through the wall, the DC for the 
Strength check is 15 + 2 per inch of thickness.

The \textit{wall of ectoplasm }is susceptible to \textit{dispel psionics}, but 
it gains a +4 bonus on any check to determine whether the wall is negated. Spells, 
powers, and breath weapons cannot pass through the wall in either direction (though 
they could damage it). It blocks ethereal creatures as well as material creatures 
(though ethereal creatures can usually get around the wall by floating under or 
over it through material floors and ceilings). The wall is opaque, so neither vision 
nor gaze attacks operate through it. The wall does not block psychoportive travel, 
such as that provided by the \textit{psionic teleport }power.

You can form the wall into a flat, vertical plane whose area is up to one 10-foot 
square per level or into a sphere or hemisphere with a radius of up to 1 foot per 
level.

The \textit{wall of ectoplasm }must be continuous and unbroken when manifested. 
If its surface is interrupted by any object or creature, the power fails.

\vspace{12pt}
\section*{Wall Walker}

Psychoportation

\textbf{Level:} Psychic warrior 2

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 3

You can walk on vertical surfaces or even traverse ceilings (you need not make 
Climb checks to traverse these surfaces). Because of the need to keep at least 
one foot in contact with the wall or ceiling at all times, you cannot jump or use 
the run action, and you can move at only half speed.

You retain your Dexterity bonus to Armor Class, if any, and opponents gain no special 
bonuses against you. 

\vspace{12pt}
\section*{Weapon of Energy}

Psychokinesis [see text]

\textbf{Level:} Psychic warrior 4

\textbf{Display:} Visual

\textbf{Range:} Touch

\textbf{Target:} Weapon touched

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} Fortitude negates (object, harmless)

\textbf{Power Resistance:} None

\textbf{Power Points:} 7

As \textit{claw of energy, }except this power can be manifested on a touched weapon. 
This power's subtype is the same as the type of energy infused in the touched weapon.

\end{document}
