%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\section*{{\LARGE PSIONIC RACES}}

\vspace{12pt}
{\LARGE DROMITES•}

+2 Charisma, -2 Strength, -2 Wisdom•

Monstrous Humanoid: Dromites are not subject to spells or effects that affect humanoids 
only, such as \textit{charm person }or \textit{dominate person}.•

Small: As a Small creature, a dromite gains a +1 size bonus to Armor Class, a +1 
size bonus on attack rolls, and a +4 size bonus on Hide checks, but it uses smaller 
weapons than humans use, and its lifting and carrying limits are three-quarters 
of those of a Medium character.•

Dromite base land speed is 20 feet.•

Chitin: A dromite's skin is hardened, almost like an exoskeleton, and grants the 
character a +3 natural armor bonus to AC and one of the following kinds of resistance 
to energy: cold 5, electricity 5, fire 5, or sonic 5. The player chooses what type 
of energy resistance is gained when the character is created. (This choice also 
dictates which caste the dromite belongs to.) This natural energy resistance stacks 
with any future energy resistance gained through other effects.•

Naturally Psionic: Dromites gain 1 bonus power point at 1st level. This benefit 
does not grant them the ability to manifest powers unless they gain that ability 
through another source, such as levels in a psionic class.•

Psi-Like Ability: 1/day---\textit{energy ray. }A dromite always deals the kind 
of energy damage that its chitin has resistance to (for example, a dromite who 
has resistance to cold 5 deals cold damage with its \textit{energy ray}). Manifester 
level is equal to 1/2 Hit Dice (minimum 1st). The save DC is Charisma-based.•

Scent: Its antennae give a dromite the scent ability. A dromite can detect opponents 
by scent within 30 feet. If the opponent is upwind, the range increases to 60 feet; 
if downwind, it drops to 15 feet. Strong scents, such as smoke or rotting garbage, 
can be detected at twice the ranges noted above. Overpowering scents, such as skunk 
musk or troglodyte stench, can be detected at triple normal range. When a dromite 
detects a scent, the exact location of the source is not re vealed---only its presence 
somewhere within range. The dromite can take a move action to note the direction 
of the scent. Whenever the dromite comes within 5 feet of the source, the dromite 
pinpoints the source's location.•

Blind-Fight: Its antennae also give a dromite Blind-Fight as a bonus feat.•

Compound Eyes: This feature of its anatomy gives a dromite a +2 racial bonus on 
Spot checks.•

Automatic Languages: Common. Bonus Languages: Dwarven, Gnome, Goblin, Terran.•

Favored Class: Wilder.•

Level Adjustment: +1.

\vspace{12pt}
{\LARGE DUERGAR•}

+2 Constitution, -4 Charisma•

Medium: As Medium creatures, duergar have no special bonuses or penalties due to 
their size.•

Duergar base land speed is 20 feet. However, gray dwarves can move at this speed 
even when wearing medium or heavy armor or when carrying a medium or heavy load 
(unlike other creatures, whose speed is reduced in such situations).•

Darkvision out to 120 feet.•

Immunity to paralysis, phantasms, and poison.•

+2 racial bonus on saves against spells and spell-like effects.•

Stability: Duergar are exceptionally stable on their feet. A duergar receives a 
+4 bonus on ability checks made to resist being bull rushed or tripped when standing 
on the ground (but not when climbing, flying, riding or otherwise not standing 
firmly on the ground).•

Stonecunning: This ability grants a duergar a +2 racial bonus on Search checks 
to notice unusual stonework, such as sliding walls, stonework, traps, new construction 
(even when built to match the old), unsafe stone surfaces, shaky stone ceilings, 
and the like. Something that isn't stone but that is disguised as stone also counts 
as unusual stonework.

A gray dwarf who merely comes within 10 feet of unusual stonework can make a Search 
check as if he were actively searching, and a duergar can use the Search skill 
to find stonework traps as a rogue can. A duergar can also intuit depth, sensing 
his approximate depth underground as naturally as a human can sense which way is 
up. Duergar have a sixth sense about stonework, an innate ability that they get 
plenty of opportunity to practice and hone in their underground homes.•

Psi-Like Abilities: 1/day---\textit{expansion}, \textit{invisibility}. These abilities 
affect only the duergar and whatever he carries. Manifester level is equal to Hit 
Dice (minimum 3rd).•

Naturally Psionic: Duergar gain 3 bonus power points at 1st level. This benefit 
does not grant them the ability to manifest powers unless they gain that ability 
through another source, such as levels in a psionic class.•

+1 racial bonus on attack rolls against orcs (including half-orcs) and goblinoids 
(including goblins, hobgoblins, and bugbears).•

+4 dodge bonus to Armor Class against creatures of the giant type (such as ogres, 
trolls, and hill giants).•

Light Sensitivity (Ex): Duergar are dazzled in sunlight or within the radius of 
a \textit{daylight }spell.•

Duergar have a +4 racial bonus on Move Silently checks and a +1 racial bonus on 
Listen and Spot checks. They have a +2 racial bonus on Appraise and Craft checks 
that are related to stone or metal.•

Automatic Languages: Common, Dwarven, Undercommon. Bonus Languages: Draconic, Giant, 
Goblin, Orc, Terran.•

Favored Class: Fighter.•

Level Adjustment: +1.

\vspace{12pt}
{\LARGE ELANS•-}

2 Charisma•

Aberration: Elans are not subject to spells or effects that affect humanoids only, 
such as \textit{charm person }or \textit{dominate person}.•

Medium: As Medium creatures, elans have no special bonuses or penalties due to 
their size.•

Elan base land speed is 30 feet.•

Elans (unlike most aberrations) do not have darkvision.•

Naturally Psionic: Elans gain 2 bonus power points at 1st level. This benefit does 
not grant them the ability to manifest powers unless they gain that ability through 
another source, such as levels in a psionic class.•

Resistance (Su): Elans can use psionic energy to increase their resistance to various 
forms of attack. As an immediate action, an elan can spend 1 power point to gain 
a +4 racial bonus on saving throws until the beginning of her next action.•

Resilience (Su): When an elan takes damage, she can spend power points to reduce 
its severity. As an immediate action, she can reduce the damage she is about to 
take by 2 hit points for every 1 power point she spends.•

Repletion (Su): An elan can sustain her body without need of food or water. If 
she spends 1 power point, an elan does not need to eat or drink for 24 hours.•

Automatic Language: Common. Bonus Languages: Any (other than secret languages, 
such as Druidic). Elans' past lives expose them to wide ranges of language.•

Favored Class: Psion.•

Level Adjustment: +0.

\vspace{12pt}
{\LARGE HALF-GIANTS•}

+2 Strength, +2 Constitution, -2 Dexterity: Half-giants are tough and strong, but 
not too nimble.•

Giant: Half-giants are not subject to spells or effects that affect humanoids only, 
such as \textit{charm person }or \textit{dominate person}.•

Medium: As Medium creatures, half-giants have no special bonuses or penalties due 
to their size.•

Half-giant base land speed is 30 feet.•

Low-Light Vision: A half-giant can see twice as far as a human in starlight, moonlight, 
torchlight, and similar conditions of poor illumination. He retains the ability 
to distinguish color and detail under these conditions.•

Fire Acclimated: Half-giants have a +2 racial bonus on saving throws against all 
fire spells and effects. Half-giants are accustomed to enduring high temperatures.•

Powerful Build: The physical stature of half-giants lets them function in many 
ways as if they were one size category larger.

Whenever a half-giant is subject to a size modifier or special size modifier for 
an opposed check (such as during grapple checks, bull rush attempts, and trip attempts), 
the half-giant is treated as one size larger if doing so is advantageous to him.

A half-giant is also considered to be one size larger when determining whether 
a creature's special attacks based on size (such as improved grab or swallow whole) 
can affect him. A half-giant can use weapons designed for a creature one size larger 
without penalty. However, his space and reach remain those of a creature of his 
actual size. The benefits of this racial trait stack with the effects of powers, 
abilities, and spells that change the subject's size category.•

Naturally Psionic: Half-giants gain 2 bonus power points at 1st level. This benefit 
does not grant them the ability to manifest powers unless they gain that ability 
through another source, such as levels in a psionic class.•

Psi-Like Ability: 1/day---\textit{stomp}. Manifester level is equal to 1/2 Hit 
Dice (minimum 1st). The save DC is Charisma-based.•

Automatic Language: Common. Bonus Languages: Draconic, Giant, Gnoll, Ignan.•

Favored Class: Psychic warrior.•

Level Adjustment: +1.

\vspace{12pt}
{\LARGE MAENADS•}

Medium: As Medium creatures, maenads have no special bonuses or penalties due to 
their size.•

Maenad base land speed is 30 feet.•

Naturally Psionic: Maenads gain 2 bonus power points at 1st level. This benefit 
does not grant them the ability to manifest powers unless they gain that ability 
through another source, such as levels in a psionic class.•

Psi-Like Ability: 1/day---\textit{energy ray}. A maenad can deal only sonic damage 
with this ability. It is accompanied by a tremendous scream of rage. Manifester 
level is equal to 1/2 Hit Dice (minimum 1st). The save DC is Charisma-based.•

Outburst (Ex): Once per day, for up to 4 rounds, a maenad can subjugate her mentality 
to gain a boost of raw physical power. When she does so, she takes a -2 penalty 
to Intelligence and Wisdom but gains a +2 bonus to Strength.•

Automatic Languages: Common, Maenad. Bonus Languages: Aquan, Draconic, Dwarven, 
Elven, Goblin. Maenads commonly know the languages of their enemies and of their 
friends, as well as Draconic, the language commonly found in ancient tomes of secret 
knowledge.•

Favored Class: Wilder.•

Level Adjustment: +0

\vspace{12pt}
{\LARGE XEPHS•}

+2 Dexterity, -2 Strength•

Medium: As Medium creatures, xephs have no special bonuses or penalties due to 
their size.•

Xeph base land speed is 30 feet.•

Darkvision out to 60 feet.•

+1 racial bonus on saving throws against powers, spells, and spell-like effects. 
Xephs have an innate resistance to psionics and magic.•

Naturally Psionic: Xephs gain 1 bonus power point at 1st level. This benefit does 
not grant them the ability to manifest powers unless they gain that ability through 
another source, such as levels in a psionic class.•

Burst (Su): Three times per day, a xeph can put on a burst of speed to increase 
her speed by 10 feet, plus 10 feet per four character levels beyond 1st, to a maximum 
increase of 30 feet at 9th character level and higher. These bursts of speed are 
considered a competence bonus to the xeph's base speed. A burst of speed lasts 
3 rounds.•

Automatic Languages: Common, Xeph. Bonus Languages: Draconic, Elven, Gnoll, Goblin, 
Halfling, Sylvan.•

Favored Class: Soulknife.

\vspace{12pt}
{\LARGE AGE, HEIGHT, AND WEIGHT}

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{3.867in}|}{\begin{minipage}[t]{3.867in}\raggedright
\linebreak
\textbf{Table: Random Starting Ages}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\raggedright
\textbf{Race}\end{minipage}} & \multicolumn{1}{|p{0.833in}|}{\begin{minipage}[t]{0.833in}\centering
\textbf{Adulthood}\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
\textbf{Barbarian Rogue Sorcerer Soulknife Wilder}\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
\textbf{Bard Fighter Paladin Ranger Psychic Warrior}\end{minipage}} & \multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\raggedright
\textbf{Cleric Druid Monk Psion Wizard}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\centering
Dromite\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
13 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+1d4\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+1d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+2d6\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Duergar\end{minipage}} & \multicolumn{1}{|p{0.833in}|}{\begin{minipage}[t]{0.833in}\centering
40 years\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+3d6\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+5d6\end{minipage}} & \multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\raggedright
+7d6\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\centering
Elan\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
20 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+2d4\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+2d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+3d6\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Half-giant\end{minipage}} & \multicolumn{1}{|p{0.833in}|}{\begin{minipage}[t]{0.833in}\centering
30 years\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+3d6\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+2d6\end{minipage}} & \multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\raggedright
+4d6\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.051in}|}{\begin{minipage}[t]{1.051in}\centering
Maenad\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
40 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+1d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+4d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+6d6\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Xeph\end{minipage}} & \multicolumn{1}{|p{0.833in}|}{\begin{minipage}[t]{0.833in}\centering
18 years\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+1d4\end{minipage}} & \multicolumn{1}{p{0.812in}|}{\begin{minipage}[t]{0.812in}\raggedright
+2d4\end{minipage}} & \multicolumn{1}{p{0.704in}|}{\begin{minipage}[t]{0.704in}\raggedright
+2d6\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.131in}|}{\begin{minipage}[t]{4.131in}\raggedright
\textbf{Table: Aging Effects}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\raggedright
\textbf{Race}\end{minipage}} & \multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
\textbf{Middle Age}\textsuperscript{\textbf{1}}\end{minipage}} & \multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\centering
\textbf{Old}\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{0.686in}|}{\begin{minipage}[t]{0.686in}\centering
\textbf{Venerable}\textsuperscript{\textbf{3}}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\centering
\textbf{Maximum Age}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.033in}|}{\begin{minipage}[t]{1.033in}\centering
Dromite\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
30 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
55 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
75 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+2d20 years\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Duergar\end{minipage}} & \multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
125 years\end{minipage}} & \multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\raggedright
188 years\end{minipage}} & \multicolumn{1}{p{0.686in}|}{\begin{minipage}[t]{0.686in}\raggedright
250 years\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
+2d\% years\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.381in}|}{\begin{minipage}[t]{1.381in}\centering
Elan\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
200 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
400 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1,000 years\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+10d\% years\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Half-giant\end{minipage}} & \multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
60 years\end{minipage}} & \multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\raggedright
80 years\end{minipage}} & \multicolumn{1}{p{0.686in}|}{\begin{minipage}[t]{0.686in}\raggedright
120 years\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
+4d\% years\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.381in}|}{\begin{minipage}[t]{1.381in}\centering
Maenad\end{minipage}} & \multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
90 years\end{minipage}} & \multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\raggedright
150 years\end{minipage}} & \multicolumn{1}{p{0.686in}|}{\begin{minipage}[t]{0.686in}\raggedright
220 years\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
+2d\% years\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.381in}|}{\begin{minipage}[t]{1.381in}\centering
Xeph\end{minipage}} & \multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
45 years\end{minipage}} & \multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\raggedright
85 years\end{minipage}} & \multicolumn{1}{p{0.686in}|}{\begin{minipage}[t]{0.686in}\raggedright
120 years\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
+2d20 years\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.381in}|}{\begin{minipage}[t]{1.381in}\centering
1 -1 to Str, Dex, and Con; +1 to Int, Wis, and Cha.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.721in}|}{\begin{minipage}[t]{0.721in}\centering
2 -2 to Str, Dex, and Con; +1 to Int, Wis, and Cha.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{p{0.886in}|}{\begin{minipage}[t]{0.886in}\centering
3 -3 to Str, Dex, and Con; +1 to Int, Wis, and Cha.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.231in}|}{\begin{minipage}[t]{4.231in}\raggedright
\textbf{Table: Random Height and Weight}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.269in}|}{\begin{minipage}[t]{0.269in}\raggedright
\textbf{Race}\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
\textbf{Base Height}\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
\textbf{Height Modifier}\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
\textbf{Base Weight}\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
\textbf{Weight Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.939in}|}{\begin{minipage}[t]{0.939in}\centering
Dromite\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
2′8″\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
2d4\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
30 lb.\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
x1 lb.\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Duergar, male\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
3′9″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d4\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
110 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.939in}|}{\begin{minipage}[t]{0.939in}\centering
Duergar, female\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
3′7″\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
2d4\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
80 lb.\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Elan, male\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
4′10″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
120 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Elan, female\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
4′5″\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
85 lb.\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Half-giant, male\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
6′4″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d12\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
220 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d6) lb.\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Half-giant, female\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
6′1″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d12\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
180 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d6) lb.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Maenad, male\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
5′4″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
150 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Maenad, female\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
5′3″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
120 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Xeph, male\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
4′8″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
100 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{6}{p{1.208in}|}{\begin{minipage}[t]{1.208in}\centering
Xeph, female\end{minipage}} & \multicolumn{1}{|p{0.905in}|}{\begin{minipage}[t]{0.905in}\centering
4′4″\end{minipage}} & \multicolumn{1}{p{0.724in}|}{\begin{minipage}[t]{0.724in}\raggedright
2d10\end{minipage}} & \multicolumn{1}{p{0.915in}|}{\begin{minipage}[t]{0.915in}\raggedright
75 lb.\end{minipage}} & \multicolumn{1}{p{0.748in}|}{\begin{minipage}[t]{0.748in}\raggedright
x(2d4) lb.\end{minipage}}\\
\hline
\end{longtable}
}

\end{document}
