%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\newcommand{\tab}{\hspace{5mm}}

pen Game Content, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsubsection*{{\LARGE PSIONIC FEATS}}

\vspace{12pt}
Psionic feats are available only to characters and creatures with the ability to 
manifest powers. (In other words, they either have a power point reserve or have 
psi-like abilities.)

Because psionic feats are supernatural abilities---a departure from the general 
rule that feats do not grant supernatural abilities---they cannot be disrupted 
in combat (as powers can be) and generally do not provoke attacks of opportunity 
(except as noted in their descriptions). Supernatural abilities are not subject 
to power resistance and cannot be dispelled; however, they do not function in areas 
where psionics is suppressed, such as a \textit{null psionics field. }Leaving such 
an area immediately allows psionic feats to be used.

Many psionic feats can be used only when you are psionically focused; others require 
you to expend your psionic focus to gain their benefit. Expending your psionic 
focus does not require an action; it is part of another action (such as using a 
feat). When you expend your psionic focus, it applies only to the action for which 
you expended it.

\vspace{12pt}
PSIONIC ITEM CREATION FEATS

Manifesters can use their personal power to create lasting psionic items. Doing 
so, however, is draining. A manifester must put a little of himself or herself 
into every psionic item he or she creates.

A psionic item creation feat lets a manifester create a psionic item of a certain 
type. Regardless of the type of items they involve, the various item creation feats 
all have certain features in common.

\textbf{XP Cost:} Power and energy that the manifester would normally keep is expended 
when making a psionic item. The experience point cost of using a psionic item creation 
feat equals 1/25 the cost of the item in gold pieces. A character cannot spend 
so much XP on an item that he or she loses a level. However, upon gaining enough 
XP to attain a new level, he or she can immediately expend XP on creating an item 
rather than keeping the XP to advance a level.

\textbf{Raw Materials Cost:} Creating a psionic item requires costly components, 
most of which are consumed in the process. The cost of these materials equals 1/2 
the cost of the item.

Using a psionic item creation feat also requires access to a laboratory or psionic 
workshop, special tools, and other equipment. A character generally has access 
to what he or she needs unless unusual circumstances apply (such as if he's traveling 
far from home).

\textbf{Time:} The time to create a psionic item depends on the feat and the cost 
of the item. The minimum time is one day.

\textbf{Item Cost:} Craft Dorje, Imprint Stone, and Scribe Tattoo create items 
that directly reproduce the effects of powers, and the strength of these items 
depends on their manifester level---that is, a power from such an item has the 
strength it would have if manifested by a manifester of that level. Often, that 
is the minimum manifester level necessary to manifest the power. (Randomly discovered 
items usually follow this rule.) However, when making such an item, the item's 
strength can be set higher than the minimum. Any time a character creates an item 
using a power augmented by spending additional power points, the character's effective 
manifester level for the purpose of calculating the item's cost increases by 1 
for each 1 additional power point spent. (Augmentation is a feature of many powers 
that allows the power to be amplified in various ways if additional power points 
are spent.) All other level-dependent parameters of the power forged into the item 
are set according to the effective manifester level.

The price of psionic items (and thus the XP cost and the cost of the raw materials) 
depends on the level of the power and a character's manifester level. The character's 
manifester level must be high enough that the item creator can manifest the power 
at the chosen level. To find the final price in each case, multiply the character's 
manifester level by the power level, then multiply the result by a constant, as 
shown below.

\textit{Power Stones: }Base price = power level x manifester level x 25 gp

\textit{Psionic Tattoos: }Base price = power level x manifester level x 50 gp

\textit{Dorjes: }Base price = power level x manifester level x 750 gp

\textbf{Extra Costs:} Any dorje, power stone, or psionic tattoo that stores a power 
with an XP cost also carries a commensurate cost. 

For psionic tattoos and power stones, the creator must pay the XP cost when creating 
the item. For a dorje, the creator must pay fifty times the XP cost. 

Some psionic items similarly incur extra costs in XP, as noted in their descriptions.

\vspace{12pt}
METAPSIONIC FEATS

As a manifester's knowledge of psionics grows, he can learn to manifest powers 
in ways slightly different from how the powers were originally designed or learned. 
Of course, manifesting a power while using a metapsionic feat is more expensive 
than manifesting the power normally.

\textbf{Manifesting Time:} Powers manifested using metapsionic feats take the same 
time as manifesting the powers normally unless the feat description specifically 
says otherwise.

\textbf{Manifestation Cost:} To use a metapsionic feat, a psionic character must 
both expend his psionic focus (see the Concentration skill description) and pay 
an increased power point cost as given in the feat description.

\textbf{Limits on Use:} As with all powers, you cannot spend more power points 
on a power than your manifester level. Metapsionic feats merely let you manifest 
powers in different ways; they do not let you violate this rule. 

\textbf{Effects of Metapsionic Feats on a Power:} In all ways, a metapsionic power 
operates at its original power level, even though it costs additional power points. 
The modifications to a power made by a metapsionic feat have only their noted effect 
on the power. A manifester can't use a metapsionic feat to alter a power being 
cast from a power stone, dorje, or other device.

Manifesting a power modified by the Quicken Power feat does not provoke attacks 
of opportunity.

Some metapsionic feats apply only to certain powers, as described in each specific 
feat entry.

\textbf{Psionic Items and Metapsionic Powers:} With the right psionic item creation 
feat, you can store a metapsionic power in a power stone, psionic tattoo, or dorje. 
Level limits for psionic tattoos apply to the power's higher metapsionic level. 

A character doesn't need the appropriate metapsionic feat to activate an item in 
which a metapsionic power is stored, but does need the metapsionic feat to create 
such an item.

\vspace{12pt}
{\LARGE FEAT DESCRIPTIONS}

These feat descriptions follow the standard format.

\vspace{12pt}
ALIGNED ATTACK [PSIONIC]

Your melee or ranged attack overcomes your opponent's alignment-based damage reduction 
and deals additional damage.

\textbf{Prerequisite:} Base attack bonus +6.

\textbf{Benefit:} When you take this feat, choose either chaos, good, evil or law. 
(Your choice must match one of your alignment components. Once you've made this 
alignment choice, it cannot be changed.

To use this feat, you must expend your psionic focus. When you make a successful 
melee or ranged attack, you deal an extra 1d6 points of damage, and your attack 
is treated as either a good, evil, chaotic, or lawful attack (depending on your 
original choice) for the purpose of overcoming damage reduction.

You must decide whether or not to use this feat prior to making an attack. If your 
attack misses, you still expend your psionic focus.

\vspace{12pt}
ANTIPSIONIC MAGIC [GENERAL]

Your spells are more potent when used against psionic characters and creatures.

\textbf{Prerequisite:} Spellcraft 5 ranks.

\textbf{Benefit:} You get a get a +2 bonus on caster level checks made to overcome 
a psionic creature's power resistance.

This bonus stacks with the bonus conferred by Spell Penetration and Greater Spell 
Penetration. Moreover, whenever a psionic creature attempts to dispel a spell you 
cast, it makes its manifester level check against a DC of 13 + its manifester level.

The benefits of this feat apply only to power resistance. 

The bonus does not apply to spell resistance. This is an exception to the psionics-magic 
transparency rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
AUTONOMOUS [GENERAL]

You have a knack for psionic self-sufficiency.

\textbf{Benefit:} You get a +2 bonus on all Autohypnosis checks and Knowledge (psionics) 
checks.

\vspace{12pt}
BODY FUEL [PSIONIC]

You can expand your power point total at the expense of your health.

\textbf{Benefit:} You can recover 2 power points by taking 1 point of ability burn 
damage to each of your three ability scores: Strength, Dexterity, and Constitution.

You can recover additional power points for a proportional cost to Strength, Dexterity, 
and Constitution. These recovered points are added to your power point reserve 
as if you had gained them by resting overnight.

\textbf{Special:} Only living creatures can use this feat. You can take advantage 
of this feat only while in your own body.

\vspace{12pt}
BOOST CONSTRUCT [PSIONIC]

Your astral constructs have more abilities.

\textbf{Benefit:} When you create an astral construct, you can give it one additional 
special ability from any menu that the construct currently has an ability from.

\vspace{12pt}
BURROWING POWER [METAPSIONIC]

Your powers sometimes bypass barriers.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
attempt to manifest your powers against targets that are sheltered behind a wall 
or force effect. Your power briefly skips through the Astral Plane to bypass the 
barrier.

The strength and thickness of the barrier determine your chance of success. To 
successfully bypass the barrier with your power, you make a Psicraft check against 
a DC equal to 10 + the hardness of the barrier + 1 per foot of thickness (minimum 
1). Assign a hardness of 20 to barriers without a hardness rating, such as force 
effects (or a \textit{wall of ectoplasm}). Force walls or \textit{walls of ectoplasm 
}are assumed to have less than 1 foot of thickness unless noted otherwise.

If a power requires line of sight (which includes most powers that affect a target 
or targets instead of an area), you cannot manifest it as a burrowing power unless 
you can somehow see the target, such as with \textit{clairvoyant sense}. Using 
this feat increases the power point cost of the power by 2. The power's total cost 
cannot exceed your manifester level.

\vspace{12pt}
CHAIN POWER [METAPSIONIC]

You can manifest powers that arc to hit other targets in addition to the primary 
target. 

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
chain any power that affects a single target and that deals either acid, cold, 
electricity, fire, or sonic damage. After the primary target is struck, the power 
can arc to a number of secondary targets equal to your manifester level (maximum 
twenty). The secondary arcs each strike one target and deal half as much damage 
as the primary one did (round down).

Each target gets to make a saving throw, if one is allowed by the power. You choose 
secondary targets as you like, but they must all be within 30 feet of the primary 
target, and no target can be struck more than once. You can choose to affect fewer 
secondary targets than the maximum (to avoid allies in the area, for example).

Using this feat increases the power point cost of the power by 6. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
CHAOTIC MIND [GENERAL]

The turbulence of your thoughts prevents others from gaining insight into your 
actions.

\textbf{Prerequisite:} Chaotic alignment, Cha 15.

\textbf{Benefit:} Creatures and characters who have an insight bonus on their attack 
rolls, an insight bonus to their Armor Class, or an insight bonus on skill checks 
or ability checks do not gain those bonuses against you.

The benefit of this feat applies only to insight bonuses gained from psionic powers 
and psi-like abilities. This is an exception to the psionics-magic transparency 
rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).



\vspace{12pt}
CLOSED MIND [GENERAL]

Your mind is better able to resist psionics than normal.

\textbf{Benefit:} You get a +2 bonus on all saving throws to resist powers.

The benefit of this feat applies only to psionic powers and psi-like abilities. 
This is an exception to the psionics-magic transparency rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
COMBAT MANIFESTATION [PSIONIC]

You are adept at manifesting powers in combat.

\textbf{Benefit:} You get a +4 bonus on Concentration checks made to manifest a 
power or use a psi-like ability while on the defensive or while you are grappling 
or pinned.

\vspace{12pt}
CRAFT COGNIZANCE CRYSTAL [ITEM CREATION]

You can create psionic \textit{cognizance crystals }that store power points.

\textbf{Prerequisite: }Manifester level 3rd.

\textbf{Benefit:} You can create a \textit{cognizance crystal}. Doing so takes 
one day for each 1,000 gp in its base price. The base price of a \textit{cognizance 
crystal }is equal to the highest-level power it could manifest using all its stored 
power points, squared, multiplied by 1,000 gp. To create a \textit{cognizance crystal}, 
you must spend 1/25 of its base price in XP and use up raw materials costing one-half 
its base price.

\vspace{12pt}
CRAFT DORJE [ITEM CREATION]

You can create slender crystal wands called dorjes than manifest powers when charges 
are expended.

\textbf{Prerequisite:} Manifester level 5th.

\textbf{Benefit:} You can create a dorje of any psionic power you know (barring 
exceptions, such as \textit{bestow power}, as noted in a power's description). 
Crafting a dorje takes one day for each 1,000 gp in its base price. The base price 
of a dorje is its manifester level x the power level x 750 gp. To craft a dorje, 
you must spend 1/25 of this base price in XP and use up raw materials costing one-half 
of this base price.

A newly created dorje has 50 charges.

Any dorje that stores a power with an XP cost also carries a commensurate cost. 
In addition to the XP cost derived from the base price, you must pay fifty times 
the XP cost.

\vspace{12pt}
CRAFT PSICROWN [ITEM CREATION]

You can create psicrowns, which have multiple psionic effects.

\textbf{Prerequisite:} Manifester level 12th.

\textbf{Benefit:} You can create any psicrown whose prerequisites you meet. Crafting 
a psicrown takes one day for each 1,000 gp in its base price. To craft a psicrown, 
you must spend 1/25 of its base price in XP and use up raw materials costing one-half 
of its base price. Some psicrowns incur extra costs in XP as noted in their descriptions. 
These costs are in addition to those derived from the psicrown's base price.

\vspace{12pt}
CRAFT PSIONIC ARMS AND ARMOR [ITEM CREATION]

You can create psionic weapons, armor, and shields.

\textbf{Prerequisite:} Manifester level 5th.

\textbf{Benefit:} You can create any psionic weapon, armor, or shield whose prerequisites 
you meet. Enhancing a weapon, suit of armor, or shield takes one day for each 1,000 
gp in the price of its psionic features. To enhance a weapon, you must spend 1/25 
of its features' total price in XP and use up raw materials costing one-half of 
this total price.

The weapon, armor, or shield to be enhanced must be a masterwork item that you 
provide. Its cost is not included in the above cost.

You can also mend a broken psionic weapon, suit of armor, or shield if it is one 
that you could make. Doing so costs half the XP, half the raw materials, and half 
the time it would take to enhance that item in the first place.

\vspace{12pt}
CRAFT PSIONIC CONSTRUCT [ITEM CREATION]

You can create golems and other psionic automatons that obey your orders.

\textbf{Prerequisites:} Craft Psionic Arms and Armor, Craft Universal Item.

\textbf{Benefit:} You can create any psionic construct whose prerequisites you 
meet. Creating a construct takes one day for each 1,000 gp in its base price. To 
create a construct, you must spend 1/25 of the construct's base price in XP and 
use up raw materials costing one-half of this price. A newly created construct 
has average hit points for its Hit Dice.

\vspace{12pt}
CRAFT UNIVERSAL ITEM [ITEM CREATION]

You can create universal psionic items.

\textbf{Prerequisite:} Manifester level 3rd.

\textbf{Benefit:} You can create any universal psionic item whose prerequisites 
you meet. Crafting a universal psionic item takes one day for each 1,000 gp in 
its base price. To craft a universal psionic item, you must spend 1/25 of the item's 
base price in XP and use up raw materials costing one-half of this price.

You can also mend a broken universal item if it is one that you could make. Doing 
so costs half the XP, half the raw materials, and half the time it would take to 
craft that item in the first place.

Some universal items incur extra costs in XP, as noted in their descriptions. These 
costs are in addition to those derived from the item's base price. You must pay 
such a cost to create an item or to mend a broken one.



\vspace{12pt}
DEEP IMPACT [PSIONIC]

You can strike your foe with a melee weapon as if making a touch attack.

\textbf{Prerequisite:} Str 13, Psionic Weapon, base attack bonus +5.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
resolve your attack with a melee weapon as a touch attack. You must decide whether 
or not to use this feat prior to making an attack. If your attack misses, you still 
expend your psionic focus.

\vspace{12pt}
DELAY POWER [METAPSIONIC]

You can manifest powers that go off up to 5 rounds later.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
manifest a power as a delayed power. A delayed power doesn't activate immediately. 
When you manifest the power, you choose one of three trigger mechanisms: (1) The 
power activates when you take a standard action to activate it; (2) It activates 
when a creature enters the area that the power will affect (only powers that affect 
areas can use this trigger condition); or (3) It activates on your turn after 5 
rounds pass. If you choose one of the first two triggers and the conditions are 
not met within 5 rounds, the power activates automatically on the fifth round.

Only area and personal powers can be delayed.

Any decisions you would make about the delayed power, including attack rolls, designating 
targets, or determining or shaping an area, are decided when the power is manifested. 
Any effects resolved by those affected by the power, including saving throws, are 
decided when the delay period ends.

A delayed power can be dispelled normally during the delay, and can be detected 
normally in the area or on the target by the use of powers that can detect psionic 
effects. 

Using this feat increases the power point cost of the power by 2. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
EMPOWER POWER [METAPSIONIC]

You can manifest powers to greater effect.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

You can empower a power. All variable, numeric effects of an empowered power are 
increased by one-half. An empowered power deals half again as much damage as normal, 
cures half again as many hit points, affects half again as many targets, and so 
forth, as appropriate. Augmented powers can also be empowered (multiply 1-1/2 times 
the damage total of the augmented power). Saving throws and opposed checks (such 
as the one you make when you manifest \textit{dispel psionics}) are not affected, 
nor are powers without random variables.

Using this feat increases the power point cost of the power by 2. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
ENLARGE POWER [METAPSIONIC]

You can manifest powers farther than normal.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
alter a power with a range of close, medium, or long to increase its range by 100\%. 
An enlarged power with a range of close has a range of 50 feet + 5 feet per level, 
a medium-range power has a range of 200 feet + 20 feet per level, and a long-range 
power has a range of 800 feet + 80 feet per level.

Powers whose ranges are not defined by distance, as well as powers whose ranges 
are not close, medium, or long, are

not affected.

Using this feat does not increase the power point cost of the power.

\vspace{12pt}
EXPANDED KNOWLEDGE [PSIONIC]

You learn another power.

\textbf{Prerequisites:} Manifester level 3rd.

\textbf{Benefit:} Add to your powers known one additional power of any level up 
to one level lower than the highest-level power you can manifest. You can choose 
any power, including powers from another discipline's list or even from another 
class's list.

\textbf{Special:} You can gain this feat multiple times. Each time, you learn one 
new power at any level up to one less than the highest-level power you can manifest.

\vspace{12pt}
EXTEND POWER [METAPSIONIC]

You can manifest powers that last longer than normal.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

You can manifest an extended power. An extended power lasts twice as long as normal. 
A power with a duration of concentration, instantaneous, or permanent is not affected 
by this feat.

Using this feat increases the power point cost of the power by 2. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
FELL SHOT [PSIONIC]

You can strike your foe with a ranged weapon as if making a touch attack.

\textbf{Prerequisite:} Dex 13, Point Blank Shot, Psionic Shot, base attack bonus 
+5.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
resolve your ranged attack as a ranged touch attack.

You must decide whether or not to use this feat prior to making an attack. If your 
attack misses, you still expend your psionic focus.

\vspace{12pt}
FOCUSED SUNDER [PSIONIC]

You can sense the stress points on others' weapons.

\textbf{Prerequisite:} Str 13, Power Attack, Improved Sunder.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

When you strike at an opponent's weapon, you ignore half of the weapon's total 
hardness (round down). Total hardness includes any magical or psionic enhancements 
possessed by the weapon that increase its hardness.

\textbf{Special:} You can also sense the stress points in any hard construction, 
such as wooden doors or stone walls, and can ignore half of the object's total 
hardness (round down) when attacking that object.

\vspace{12pt}
FORCE OF WILL [GENERAL]

You are able to resist psionic attacks with extreme force of will.

\textbf{Prerequisite:} Iron Will.

\textbf{Benefit:} Once per round, when targeted by a psionic effect that allows 
a Reflex save or a Fortitude save, you can instead make a Will saving throw to 
avoid the effect.

The benefit of this feat applies only to psionic powers and psi-like abilities. 
This is an exception to the psionics-magic transparency rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
GHOST ATTACK [PSIONIC]

Your deadly strikes against incorporeal foes always find their mark.

\textbf{Prerequisite:} Base attack bonus +3.

\textbf{Benefit:} You must be psionically focused to use this feat. When you make 
a melee attack or a ranged attack against an incorporeal creature, you can make 
two rolls to check for the miss chance. If either is successful, the attack is 
treated as if it were made with a ghost touch weapon for the purpose of affecting 
the creature. Your weapon or natural weapon actually appears to become briefly 
incorporeal as the attack is made.



\vspace{12pt}
GREATER POWER PENETRATION [PSIONIC]

Your powers are especially potent at breaking through power resistance.

\textbf{Prerequisite:} Power Penetration.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You get 
a +4 bonus on manifester level checks to overcome a creature's power resistance. 
This bonus stacks with the bonus from Power Penetration.

\vspace{12pt}
GREATER POWER SPECIALIZATION [PSIONIC]

You deal more damage with your powers.

\textbf{Prerequisites:} Power Specialization, Weapon Focus (ray), manifester level 
12th.

\textbf{Benefit:} Your powers that deal damage deal an extra 2 points of damage. 
This damage stacks with other bonuses on damage rolls to powers, including the 
one from Power Specialization. The damage bonus applies only if the target or targets 
are within 30 feet.

\vspace{12pt}
GREATER PSIONIC ENDOWMENT [PSIONIC]

You can use meditation to focus your powers.

\textbf{Prerequisite:} Psionic Endowment.

\textbf{Benefit:} When you use the Psionic Endowment feat, you add +2 to the save 
DC of a power you manifest instead of +1.

\vspace{12pt}
GREATER PSIONIC FIST [PSIONIC]

You can charge your unarmed strike or natural weapon with additional damage potential.

\textbf{Prerequisite:} Str 13, Psionic Fist, base attack bonus +5.

\textbf{Benefit:} When you use the Psionic Fist feat, your unarmed attack or attack 
with a natural weapon deals an extra 4d6 points of damage instead of an extra 2d6 
points.

\vspace{12pt}
GREATER PSIONIC SHOT [PSIONIC]

You can charge your ranged attacks with additional damage potential.

\textbf{Prerequisite:} Point Blank Shot, Psionic Shot, base attack bonus +5.

\textbf{Benefit:} When you use the Psionic Shot feat, your ranged attack deals 
an extra 4d6 points of damage instead of an extra 2d6 points.

\vspace{12pt}
GREATER PSIONIC WEAPON [PSIONIC]

You can charge your melee weapon with additional damage potential.

\textbf{Prerequisite:} Str 13, Psionic Weapon, base attack bonus +5.

\textbf{Benefit:} When you use the Psionic Weapon feat, your attack with a melee 
weapon deals an extra 4d6 points of damage instead of an extra 2d6 points.

\vspace{12pt}
HOSTILE MIND [GENERAL]

Your mind recoils violently against those who use psionics against you.

\textbf{Prerequisite:} Cha 15.

\textbf{Benefit:} Whenever you are subject to a power from the telepathy discipline 
(regardless of whether the power is harmful or beneficial to you), the manifester 
must make a Will saving throw against a DC of 10 + 1/2 your character level + your 
Charisma bonus or take 2d6 points of damage.

The benefit of this feat applies only to psionic powers and psi-like abilities. 
This is an exception to the psionics-magic transparency rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
IMPRINT STONE [ITEM CREATION]

You can create power stones to store psionic powers.

\textbf{Prerequisite:} Manifester level 1st.

\textbf{Benefit:} You can create a power stone of any power that you know. Encoding 
a power stone takes one day for each 1,000 gp in its base price. The base price 
of a power stone is the level of the stored power x its manifester level x 25 gp. 
To imprint a power stone, you must spend 1/25 of this base price in XP and use 
up raw materials costing one-half of this base price.

Any power stone that stores a power with an XP cost also carries a commensurate 
cost. In addition to the costs derived from the base price, you must pay the XP 
when encoding the stone.

\vspace{12pt}
IMPROVED PSICRYSTAL [PSIONIC]

You can upgrade your psicrystal.

\textbf{Prerequisites:} Psicrystal Affinity.

\textbf{Benefit:} You can implant another personality fragment in your psicrystal. 
You gain the benefits of both psicrystal personalities. Your psicrystal's personality 
adjusts and becomes a blend between all implanted personality fragments. From now 
on, when determining the abilities of your psicrystal, treat your manifester level 
as one higher than your normal manifester level.

\textbf{Special:} You can gain this feat multiple times. Each time, you implant 
a new personality fragment in your psicrystal, from which you derive the noted 
benefits, and you treat your level as one higher for the purpose of determining 
your psicrystal's abilities.

\vspace{12pt}
INQUISITOR [PSIONIC] 

You know when others lie.

\textbf{Prerequisite:} Wis 13.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

You gain a +10 bonus on a Sense Motive check to oppose a Bluff check.

You must decide whether or not to use this feat prior to making a Sense Motive 
check. If your check fails, or if the opponent isn't lying, you still expend your 
psionic focus. 

\vspace{12pt}
MAXIMIZE POWER [METAPSIONIC]

You can manifest powers to maximum effect.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

You can maximize a power. All variable, numeric effects of a power modified by 
this feat are maximized. A maximized power deals maximum damage, cures the maximum 
number of hit points, affects the maximum number of targets, and so on, as appropriate. 
Saving throws and opposed checks are not affected, nor are powers without random 
variables.

Augmented powers can be maximized; a maximized augmented power deals the maximum 
damage (or cures the maximum hit points, and so on) of the augmented power.

An empowered and maximized power gains the separate benefits of each feat: the 
maximum result plus one-half the normally rolled result.

Using this feat increases the power point cost of the power by 4. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
MENTAL LEAP [PSIONIC]

You can make amazing jumps.

\textbf{Prerequisite:} Str 13, Jump 5 ranks.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You gain 
a +10 bonus on a Jump check. 

\vspace{12pt}
MENTAL RESISTANCE [GENERAL]

Your mind is armored against mental intrusion.

\textbf{Prerequisite:} Base Will save bonus +2.

\textbf{Benefit:} Against psionic attacks that do not employ an energy type to 
deal damage you gain damage reduction 3/-. In addition, when you are hit with ability 
damage (but not ability drain or ability burn damage) from a psionic attack, you 
take 3 points less than you would normally take.

The benefit of this feat applies only to psionic powers and psi-like abilities. 
This is an exception to the psionics-magic transparency rule.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
METAMORPHIC TRANSFER [PSIONIC]

You can gain a supernatural ability of a metamorphed form.

\textbf{Prerequisite:} Wis 13, manifester level 5th.

\textbf{Benefit:} Each time you change your form, such as through the \textit{metamorphosis 
}power, you gain one of the new form's supernatural abilities, if it has any.

You gain only three uses of the metamorphic ability per day, even if the creature 
into which you metamorph has a higher limit on uses (You are still subject to other 
restrictions on the use of the ability.) The save DC to resist a supernatural ability 
gained through Metamorphic Transfer (if it is an attack) is 10 + your Cha modifier 
+ 1/2 your Hit Dice.

\textbf{Normal:} You cannot use the supernatural abilities of creatures whose form 
you assume.

\textbf{Special:} You can gain this feat multiple times. Each time, you can gain 
one additional supernatural ability.

\vspace{12pt}
MIND OVER BODY [GENERAL]

Your ability damage heals more rapidly.

\textbf{Prerequisite:} Con 13.

\textbf{Benefit:} You heal ability damage and ability burn damage more quickly 
than normal. You heal a number of ability points per day equal to 1 + your Constitution 
bonus. 

\textbf{Normal:} You heal ability damage and ability burn damage at a rate of 1 
point per day.

\vspace{12pt}
NARROW MIND [PSIONIC]

Your ability to concentrate is as keen as an arrowhead, allowing you to gain your 
psionic focus even in the most turbulent situations.

\textbf{Prerequisite:} Wis 13.

\textbf{Benefit:} You gain a +4 bonus on Concentration checks you make to become 
psionically focused.



\vspace{12pt}
OPPORTUNITY POWER [METAPSIONIC]

You can make power-enhanced attacks of opportunity.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. When you 
make an attack of opportunity, you can use any power you know with a range of touch, 
if you have at least one hand free.

Manifesting this power is an immediate action.

You cannot use this feat with a touch power whose manifesting time is longer than 
1 full-round action.

Using this feat increases the power point cost of the power by 6. The power's total 
cost cannot exceed your manifester level.

\textbf{Normal:} Attacks of opportunity can be made only with melee weapons.

\vspace{12pt}
OVERCHANNEL [PSIONIC]

You burn your life force to strengthen your powers.

\textbf{Benefit:} While manifesting a power, you can increase your effective manifester 
level by one, but in so doing you take 1d8 points of damage. At 8th level, you 
can choose to increase your effective manifester level by two, but you take 3d8 
points of damage. At 15th level, you can increase your effective manifester level 
by three, but you take 5d8 points of damage.

The effective increase in manifester level increases the number of power points 
you can expend on a single power manifestation, as well as increasing all manifester 
level-dependent effects, such as range, duration, and overcoming power resistance.

\textbf{Normal:} Your manifester level is equal to your total levels in classes 
that manifest powers.

\vspace{12pt}
POWER PENETRATION [PSIONIC]

Your powers are especially potent, breaking through power resistance more readily 
than normal.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You get 
a +4 bonus on manifester level checks made to overcome a creature's power resistance.

\vspace{12pt}
POWER SPECIALIZATION [PSIONIC]

You deal more damage with your powers.

\textbf{Prerequisites:} Weapon Focus (ray), manifester level 4th.

\textbf{Benefit:} With rays and ranged touch attack powers that deal damage, you 
deal an extra 2 points of damage. If you expend your psionic focus when you manifest 
a ray or a ranged touch attack power that deals damage, you add your key ability 
bonus to the damage (instead of adding 2).

\vspace{12pt}
PSICRYSTAL AFFINITY [PSIONIC]

You have created a psicrystal.

\textbf{Prerequisites:} Manifester level 1st.

\textbf{Benefit:} This feat allows you to gain a psicrystal.

\vspace{12pt}
PSICRYSTAL CONTAINMENT [PSIONIC]

Your psicrystal has advanced enough that it can hold a psionic focus that you store 
within it.

\textbf{Prerequisites:} Psicrystal Affinity, manifester level 3rd.

\textbf{Benefit:} You can spend a full-round action attempting to psionically focus 
your psicrystal. At any time when you need to expend your psionic focus, you can 
expend your psicrystal's psionic focus instead, as long as the crystal is within 
5 feet of you. Psionically focusing your psicrystal works just like focusing yourself. 
The psicrystal cannot focus itself---only the owner can spend the time to focus 
the crystal.

\vspace{12pt}
PSIONIC AFFINITY [GENERAL]

You have a knack for psionic endeavors.

\textbf{Benefit:} You get a +2 bonus on all Psicraft checks and Use Psionic Device 
checks.

\vspace{12pt}
PSIONIC BODY [PSIONIC]

Your mind reinforces your body.

\textbf{Benefit:} When you take this feat, you gain 2 hit points for each psionic 
feat you have (including this one). Whenever you take a new psionic feat, you gain 
2 more hit points. 

\vspace{12pt}
PSIONIC CHARGE [PSIONIC]

You can charge in a crooked line.

\textbf{Prerequisite:} Dex 13, Speed of Thought.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. When you 
charge, you can make one turn of up to 90 degrees during your movement. All other 
restrictions on charges still apply; for instance, you cannot pass through a square 
that blocks or slows movement, or that contains a creature. You must have line 
of sight to the opponent at the start of your turn.

\vspace{12pt}
PSIONIC DODGE [PSIONIC]

You are proficient at dodging blows.

\textbf{Prerequisite:} Dex 13, Dodge.

\textbf{Benefit:} You must be psionically focused to use this feat. You receive 
a +1 dodge bonus to your Armor Class. This bonus stacks with the bonus from the 
Dodge feat (but only applies on attacks made by the opponent you have designated).

\vspace{12pt}
PSIONIC ENDOWMENT [PSIONIC]

You can endow your manifestations with more concentrated focus.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You add 
1 to the save DC of a power you manifest.

\vspace{12pt}
PSIONIC FIST [PSIONIC]

You can charge your unarmed strike or natural weapon with additional damage potential.

\textbf{Prerequisite:} Str 13.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. Your unarmed 
strike or attack with a natural weapon deals an extra 2d6 points of damage.

You must decide whether or not to use this feat prior to making an attack. If your 
attack misses, you still expend your psionic focus.

\vspace{12pt}
PSIONIC HOLE [GENERAL]

You are anathema to psionic creatures and characters.

\textbf{Prerequisite:} Con 15.

\textbf{Benefit:} When a foe strikes you in melee combat, the foe immediately loses 
its psionic focus, if any. Also, if you are the target of a power, the manifester 
of the power must spend an additional number of power points equal to your Wisdom 
bonus, or the power fails (all the power points spent on the power are still lost). 
This extra cost does not count toward the maximum power points a manifester can 
spend on a single power.

\textbf{Special:} You cannot take or use this feat if you have the ability to use 
powers (if you have a power point reserve or psi-like abilities).

\vspace{12pt}
PSIONIC MEDITATION [PSIONIC]

You can focus your mind faster than normal, even under duress.

\textbf{Prerequisite:} Wis 13, Concentration 7 ranks.

\textbf{Benefit:} You can take a move action to become psionically focused.

\textbf{Normal:} A character without this feat must take a full-round action to 
become psionically focused.

\vspace{12pt}
PSIONIC SHOT [PSIONIC]

You can charge your ranged attacks with additional damage potential.

\textbf{Prerequisite:} Point Blank Shot.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. Your ranged 
attack deals +2d6 points of damage. You must decide whether or not to use this 
feat prior to making an attack. If your attack misses, you still expend your psionic 
focus.

\vspace{12pt}
PSIONIC TALENT [PSIONIC]

You gain additional power points to supplement those you already had.

\textbf{Prerequisite:} Having a power point reserve.

\textbf{Benefit:} When you take this feat for the first time, you gain 2 power 
points.

\textbf{Special:} You can take this feat multiple times. Each time you take the 
feat after the first time, the number of power points you gain increases by 1.

\vspace{12pt}
PSIONIC WEAPON [PSIONIC]

You can charge your melee weapon with additional damage potential.

\textbf{Prerequisite:} Str 13.

\textbf{Benefit:} To use this feat, you must expend your psionic focus.

Your attack with a melee weapon deals an extra 2d6 points of damage. You must decide 
whether or not to use this feat prior to making an attack. If your attack misses, 
you still expend your psionic focus.

\vspace{12pt}
QUICKEN POWER [METAPSIONIC]

You can manifest a power with a moment's thought.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
quicken a power. You can perform another action, even manifest another power, in 
the same round that you manifest a quickened power. You can manifest only one quickened 
power per round. A power whose manifesting time is longer than 1 round cannot be 
quickened.

Using this feat increases the power point cost of the power by 6. The power's total 
cost cannot exceed your manifester level.

Manifesting a quickened power does not provoke attacks of opportunity.



\vspace{12pt}
RECKLESS OFFENSE [GENERAL]

You can shift your focus from defense to offense.

\textbf{Prerequisite:} Base attack bonus +1.

\textbf{Benefit:} When you use the attack action or full attack action in melee, 
you can take a penalty of -4 to your Armor Class and add a +2 bonus on your melee 
attack roll. The bonus on attack rolls and penalty to Armor Class last until the 
beginning of your next turn.

\vspace{12pt}
RETURN SHOT [PSIONIC]

You can return incoming arrows, as well as crossbow bolts, spears, and other projectile 
or thrown weapons.

\textbf{Prerequisite:} Point Blank Shot, Psionic Shot, Fell Shot, base attack bonus 
+3.

\textbf{Benefit:} To use this feat, you must expend your psionic focus and have 
at least one hand free. Once per round when you would normally be hit by a projectile 
or a thrown weapon no more than one size category larger than your size, you can 
deflect the attack so that you take no damage from it. The attack is deflected 
back at your attacker, using the attack bonus of the original attack on you. You 
must be aware of the attack and not flat-footed. Attempting to return a shot is 
a free action.

\textbf{Special:} If you also have the Deflect Arrows feat, the deflected attack 
is made with the original attack bonus plus your Dexterity bonus.

\vspace{12pt}
SCRIBE TATTOO [ITEM CREATION]

You can create psionic tattoos, which store powers within their designs.

\textbf{Prerequisite:} Manifester level 3rd.

\textbf{Benefit:} You can create a psionic tattoo of any power of 3rd level or 
lower that you know and that targets one or more creatures. Scribing a psionic 
tattoo takes one day. When you create a psionic tattoo, you set the manifester 
level. The manifester level must be sufficient to manifest the power in question 
and no higher than your own level. The base price of a psionic tattoo is its power 
level x its manifester level x 50 gp. To scribe a tattoo, you must spend 1/25 of 
this base price in XP and use up raw materials (special inks, masterwork needles, 
and so on) costing one-half of this base price.

When you create a psionic tattoo, you make any choices that you would normally 
make when manifesting the power.

When its wearer physically activates the tattoo, the wearer is the target of the 
power.

Any psionic tattoo that stores a power with an XP cost also carries a commensurate 
cost. In addition to the costs derived from the base price, you must pay the XP 
when creating the tattoo.

\vspace{12pt}
SIDESTEP CHARGE [PSIONIC]

You are skilled at dodging past charging opponents and taking advantage when they 
miss.

\textbf{Prerequisite:} Dex 13, Dodge.

\textbf{Benefit:} You get a +4 dodge bonus to Armor Class against charge attacks. 
If a charging opponent fails to make a successful attack against you, you gain 
an immediate attack of opportunity. This feat does not grant you more attacks of 
opportunity than you are normally allowed in a round. If you are flat-footed or 
otherwise denied your Dexterity bonus to Armor Class, you do not gain the benefit 
of this feat.

\vspace{12pt}
SPEED OF THOUGHT [PSIONIC]

The energy of your mind energizes the alacrity of your body.

\textbf{Prerequisite:} Wis 13.

\textbf{Benefit:} As long as you are psionically focused and not wearing heavy 
armor, you gain an insight bonus to your speed of 10 feet.

\vspace{12pt}
SPLIT PSIONIC RAY [METAPSIONIC]

You can affect two targets with a single ray.

\textbf{Prerequisite:} Any other metapsionic feat.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
split psionic rays you manifest. The split ray affects any two targets that are 
both within the power's range and within 30 feet of each other. If the ray deals 
damage, each target takes as much damage as a single target would take.

Using this feat increases the power point cost of the power by 2.



\vspace{12pt}
TALENTED [PSIONIC]

You can overchannel powers with less cost to yourself.

\textbf{Prerequisite:} Overchannel.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. When manifesting 
a power of 3rd level or lower, you do not take damage from overchanneling.

\vspace{12pt}
TWIN POWER [METAPSIONIC]

You can manifest a power simultaneously with another power just like it.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
twin a power. Manifesting a power altered by this feat causes the power to take 
effect twice on the area or target, as if you were simultaneously manifesting the 
same power two times on the same location or target. Any variables in the power 
(such as duration, number of targets, and so on) are the same for both of the resulting 
powers. The target experiences all the effects of both powers individually and 
receives a saving throw (if applicable) for each. In some cases, such as a twinned 
\textit{psionic charm}, failing both saving throws results in redundant effects 
(although, in this example, any ally of the target would have to succeed on two 
dispel attempts to free the target from the charm effect).

Using this feat increases the power point cost of the power by 6. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
UNAVOIDABLE STRIKE [PSIONIC]

You can make an unarmed strike or use a natural weapon against your foe as if delivering 
a touch attack.

\textbf{Prerequisite:} Str 13, Psionic Fist, base attack bonus +5.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
resolve your unarmed strike or attack with a natural weapon as a touch attack.

You must decide whether or not to use this feat prior to making an attack. If your 
attack misses, you still expend your psionic focus.

\vspace{12pt}
UNCONDITIONAL POWER [METAPSIONIC]

Disabling conditions do not hold you back.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. Your mental 
strength is enough to overcome some otherwise disabling conditions. You can manifest 
an unconditional power when you are dazed, \textit{confused, }nauseated, shaken, 
or stunned.

Only personal powers and powers that affect your person can be manifested as unconditional 
powers.

Using this feat increases the power point cost of the power by 8. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
UP THE WALLS [PSIONIC]

You can run on walls for brief distances.

\textbf{Prerequisite:} Wis 13.

\textbf{Benefit:} While you are psionically focused, you can take part of one of 
your move actions to traverse a wall or other relatively smooth vertical surface 
if you begin and end your move on a horizontal surface. The height you can achieve 
on the wall is limited only by this movement restriction. If you do not end your 
move on a horizontal surface, you fall prone, taking falling damage as appropriate 
for your distance above the ground. Treat the wall as a normal floor for the purpose 
of measuring your movement. Passing from floor to wall or wall to floor costs no 
movement; you can change surfaces freely. Opponents on the ground can make attacks 
of opportunity as you move up the wall.

\textbf{Special:} You can take other move actions in conjunction with moving along 
a wall. For instance, the Spring Attack feat allows you to make an attack from 
the wall against a foe standing on the ground who is within the area you threaten; 
however, if you are somehow prevented from completing your move, you fall. Likewise, 
you could tumble along the wall to avoid attacks of opportunity.

\vspace{12pt}
WIDEN POWER [METAPSIONIC]

You can increase the area of your powers.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
alter a burst, emanation, line, or spread-shaped power to increase its area. (Powers 
that do not have an area of one of these four sorts are not affected by this feat.) 
Any numeric measurements of the power's area increase by 100\%.

Using this feat increases the power point cost of the power by 4. The power's total 
cost cannot exceed your manifester level.

\vspace{12pt}
WILD TALENT [GENERAL]

Your mind wakes to a previously unrealized talent for psionics.

\textbf{Benefit:} Your latent power of psionics flares to life, conferring upon 
you the designation of a psionic character. As a psionic character, you gain a 
reserve of 2 power points and can take psionic feats, metapsionic feats, and psionic 
item creation feats. You do not, however, gain the ability to manifest powers simply 
by virtue of having this feat.

\vspace{12pt}
WOUNDING ATTACK [PSIONIC]

Your vicious attacks wound your foe.

\textbf{Prerequisite:} Base attack bonus +8.

\textbf{Benefit:} To use this feat, you must expend your psionic focus. You can 
make an attack with such vicious force that you wound your opponent. A wound deals 
1 point of Constitution damage to your foe in addition to the usual damage dealt.

You must decide whether or not to use this feat prior to making an attack. If your 
attack misses, you still expend your psionic focus.

\end{document}
