%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

pen Game Content, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsubsection*{{\LARGE PSIONIC MONSTERS}}

\vspace{12pt}
\subsubsection*{PSIONIC CREATURES}

Any creature with psionic powers has the psionic subtype. A psionic creature can 
be born with the subtype or can gain the subtype during its life.

A creature meeting any one of the following criteria has the psionic subtype:•

Creatures with a power point reserve, including characters who have levels in a 
character class that grants them a power point reserve or creatures who have the 
Wild Talent feat.•

Creatures with psi-like abilities, including characters who have racial psi-like 
abilities.•

Creatures that have spell-like abilities described as ``psionics.''

\textit{Traits: }Other than the fact that all psionic creatures have psionic powers, 
power points, or psi-like abilities, psionic creatures have no specific traits. 
The psionic subtype serves to identify creatures that may be vulnerable to powers, 
spells, and effects targeting psionic creatures.

\vspace{12pt}
\subsubsection*{THE PSIONIC SUBTYPE}

The psionic subtype applies to creatures that can use psionic powers or abilities 
or that have the ability to manifest powers. (In other words, a creature with the 
psionic subtype either has a power point reserve or has psi-like abilities.) It 
also applies to creatures from other sources that have spell-like abilities labeled 
as ``psionics.''

Characters who have levels in any class that grants the use of psionics, or who 
have psi-like abilities as racial traits, gain the psionic subtype.

\textbf{Traits:} Other than the fact that all psionic creatures have psionic powers 
or psi-like abilities, psionic creatures have no specific traits. The psionic subtype 
simply identifies creatures that may be vulnerable to powers, spells, and effects 
targeting psionic creatures.

\section*{\textbf{Undead Psionic Creatures}}

A psionic undead creature, although rare, is a force to be reckoned with.

Because undead are immune to mind-affecting effects (including charms and compulsions), 
they are particularly threatening to other psionic creatures and characters (especially 
telepaths). Psionic undead creatures can use mind-affecting powers on the living, 
even though they themselves are immune to such attacks. However, an undead creature 
may have the psionic subtype if it meets the criteria described above, and thus 
be vulnerable to non-mindaffecting powers or effects that specifically affect psionic 
creatures.

Intelligent constructs and plants with psionic powers or psi-like abilities also 
share this advantage.

\vspace{12pt}
\subsubsection*{PSIONIC POWERS}

Creatures with psionic powers are similar to creatures with racial spellcasting 
ability. They have the ability to manifest powers just as a member of a psionic 
character class can (and can activate psionic items accordingly).

Creatures with the ability to use powers are subject to the same rules for manifesting 
powers that characters are, but they are not actually members of a class and do 
not gain any class abilities unless otherwise specified.

Creatures with psionic powers generally emulate the manifesting ability of a particular 
psionic class. When such a creature takes levels in that same class, it can stack 
its innate psionic powers and its class power progression together. 

Creatures with psionic powers that take levels in a class other than the one they 
emulate combine their two power point reserves into a single reserve, but they 
manifest powers from each psionic class separately.

\vspace{12pt}
\subsubsection*{PSI-LIKE ABILITIES}

Most psionic monsters have some number of psi-like abilities. These are very similar 
to spell-like abilities. Naturally, they are psionic and work just like powers 
or spells. A creature with psi-like abilities does not pay for these abilities 
with power points and does not pay any XP cost associated with manifesting the 
power the ability duplicates.

Psi-like abilities do not work in a \textit{null psionics field }and are subject 
to power resistance if the power or spell the ability duplicates would be subject 
to power resistance. A psi-like ability usually has a limit on how often it can 
be used. A psi-like ability that can be used at will has no use limit. Using a 
psi-like ability is a standard action unless noted otherwise, and doing so while 
threatened provokes attacks of opportunity. It is possible to make a Concentration 
check to use a psi-like ability defensively and avoid provoking attacks of opportunity, 
just as when using a power or casting a spell. A psi-like ability can be interrupted 
just as a spell can be. Psi-like abilities cannot be used to counterspell, nor 
can they be counterspelled.

All creatures with psi-like abilities are assigned a manifester level, which indicates 
how difficult it is to dispel their psi-like effects and determines all level-dependent 
variables (such as range or duration) the abilities might have. When a creature 
uses a psi-like ability, the power is manifested as if the creature had spent a 
number of power points equal to its manifester level, which may augment the power 
to improve its damage or save DC. However, the creature does not actually spend 
power points for its psi-like abilities, even if it has a power point reserve due 
to racial abilities, class levels, or some other psionic ability.

The DC of a saving throw (if applicable) against a creature's psi-like ability 
is 10 + the level of the power or spell the ability duplicates + the creature's 
Cha modifier. Remember to check the power's Augment entry to see if the creature's 
manifester level (and thus the effective power point expenditure) increases the 
DC of the saving throw. Changes to the effect's save DC, damage, and so on are 
noted in the psi-like ability entry.

\vspace{12pt}
\section*{\textbf{Psionic Focus}}

Some creatures have feats that can be used only when the creature is psionically 
focused, or that require the creature to expend its psionic focus. Assume that 
such a creature is psionically focused before entering combat.

\vspace{12pt}
\section*{\textbf{Psi-Like Abilities and Feats}}

Creatures with access to psi-like abilities can use the feats Empower Spell-Like 
Ability and Quicken Spell-Like Ability.

These feats can be used only on psi-like abilities that do not have increased effects 
due to augmentation. Furthermore, the creature can empower only a psi-like ability 
with a level less than or equal to half its manifester level (round down) minus 
2, and can quicken only a psi-like ability with a level less than or equal to half 
its manifester level (round down) minus 4.

\vspace{12pt}
\section*{\textbf{Creatures with ``Psionics'' Entries}}

Psionic monsters often possess spell-like abilities that are identified as ``psionics,'' 
instead of ``spell-like abilities.'' For all intents and purposes, creatures with 
spell-like abilities described as psionics are considered to possess psi-like abilities, 
and they manifest their powers as described above.

\vspace{12pt}
\section*{\textbf{Psionic Spells}}

In some cases, a creature's psi-like abilities (or abilities listed under a creature's 
psionics entry) may include an effect that does not duplicate any listed power. 
For such abilities, simply use the existing spell description\textit{. }Treat the 
creature's

manifester level as the caster level for the spell. The ability is still psionic 
in origin, so spells and powers that specifically affect psionic powers can negate 
or reduce its effects as they would any other psionic power.

\vspace{12pt}
\section*{\textbf{Psionic Versions Of Creatures}}

Below are presented psionic versions of the following creatures\textit{: }aboleth, 
couatl, and duergar,. These alternate versions are psionic equivalents of their 
standard counterparts.

Only the portions of the monster entry that are specifically changed by the addition 
of psionics rules have been listed.  All other elements of the creature remain 
the same.

\vspace{12pt}
\subsubsection*{READING PSIONIC CREATURE ENTRIES}

\section*{\textbf{Creatures with Psi-Like Abilities}}

Each of a creature's psi-like abilities has a manifester level. Each ability that 
allows a saving throw also gives a save DC in parentheses following the power name.

Powers that have increased effects due to augmentation include information about 
the effect. An asterisk indicates that the power has already been augmented by 
the creature's innate ability.

Powers that can't be augmented, or that are manifested at their normal minimum 
level, do not contain any special notations. Resolve the effect of manifesting 
the power without augmentation at the creature's given manifester level.

Some creatures may have particular powers that are manifested at a higher or lower 
level than their normal manifester level. In such cases, the manifester level is 
given in the parenthetical information following the power name.

\vspace{12pt}
{\LARGE ABOLETH, PSIONIC}

Huge Aberration (Aquatic, Psionic)

\textbf{Special Attacks:} Psi-like abilities, slime

\textbf{Feats:} Alertness, Combat Manifestation, Iron Will

\subsubsection*{COMBAT}

A psionic aboleth does not possess spell-like abilities or the enslave ability 
of the standard aboleth. Instead, it has psi-like abilities, including \textit{psionic 
dominate.}

\textbf{Psi-Like Abilities:} At will---\textit{disable }(30-ft. cone, 12 HD, DC 
20*), \textit{false sensory input }(five targets, DC 16*), \textit{mental disruption 
}(20-ft. radius\textit{, }DC 18*), \textit{mindlink }(unwilling, nine targets, 
DC 14*); 3/day---\textit{ego whip }(ML 7th, 2d4, DC 17*)\textit{, id insinuation 
}(ML 7th, three targets, DC 17*)\textit{, psionic dominate }(any target, 24 hours, 
DC 20*), \textit{thought shield }(power resistance 21, 3 rounds*); 1/day---\textit{psionic 
modify memory }(DC 17)\textit{, remote viewing }(DC 17)\textit{, wall of ectoplasm 
}(DC 17)\textit{. }

Manifester level 13th. The save DCs are Charisma-based.

*Includes augmentation for the aboleth's manifester level.

\vspace{12pt}
{\LARGE ASTRAL CONSTRUCT}

Astral constructs are brought into being by the metacreativity power \textit{astral 
construct}. They are formed from raw ectoplasm (a portion of the astral medium 
drawn into the Material Plane). The power points spent by the construct's creator 
during the manifestation of the power determine the level of the astral construct 
created. However, even astral constructs of the same level vary somewhat from each 
other, depending on the whims of their creators.

\subsubsection*{COMBAT}

Astral constructs act as directed by their creators. As a free action, a construct's 
manifester can direct the construct to attack particular enemies, use specific 
tactics or powers, perform other actions, or do nothing at all. The construct does 
exactly what its creator directs it to do. 

An astral construct generally appears as an animate clump of ectoplasm with a vaguely 
humanoid shape, but the manifester can mold or sculpt one according to his or her 
whim within the limits imposed by the creature's size. The quality of such ``construct 
sculpture'' is determined by a Craft (sculpting) check. A result of 10 to 19 creates 
a creature that is recognizably similar to the desired creature shape; a result 
of 20 to 29 creates a construct that looks like an accurate portrayal of that creature 
type; a result of 30 or higher creates a construct that looks like a specific individual. 
No matter how high the Craft (sculpting) check result, though, an astral construct's 
appearance can't hide the otherworldly material from which it is formed.

\textbf{Construct Traits:} An astral construct has immunity to poison, \textit{sleep, 
}paralysis, stunning, disease, death effects, necromancy effects, mind-affecting 
effects (charms, compulsions, phantasms, patterns, and morale effects), and any 
effect that requires a Fortitude save unless it also works on objects or is harmless. 
It is not subject to critical hits, nonlethal damage, ability damage, ability drain, 
fatigue, exhaustion, or energy drain. It cannot heal damage, but it can be repaired.

\textbf{Special Abilities:} Every time an astral construct is created, the manifester 
can choose to apply one special ability to the construct. When the manifester begins 
to manifest the \textit{astral construct }power, he chooses one or more special 
abilities from a menu of abilities appropriate to that level of astral construct.

\subsubsection*{CREATING AN ASTRAL CONSTRUCT}

When manifesting the \textit{astral construct }power, the manifester assembles 
the desired creature from a menu of choices, as specified in the construct's statistics 
block. A manifester can always substitute two choices from a lesser menu for one 
of its given abilities. Multiple selections of the same menu choice do not stack 
unless the ability specifically notes that stacking is allowed.

Some menu choices grant an astral construct the ability to manifest specific powers 
as psi-like abilities. Unless using the ability is a free action, an astral construct 
manifesting such a power does so as a standard action that provokes attacks of 
opportunity. All such powers have a manifester level equal to the astral construct's 
Hit Dice or the creator's manifester level, whichever is lower.

An astral construct does not need to meet the prerequisites for a feat granted 
by a menu choice. 

\vspace{12pt}
\section*{Astral Construct Menu A}

A manifester creating a 1st-level, 2nd-level, or 3rd-level astral construct can 
choose one special ability from this menu.

\textbf{Buff (Ex): }The astral construct gains an extra 5 hit points.

\textbf{Celerity (Ex):} The astral construct's land speed is increased by 10 feet.

\textbf{Cleave (Ex):} The astral construct gains the Cleave feat. 

\textbf{Deflection (Ex):} The astral construct gains a +1 deflection bonus to Armor 
Class.

\textbf{Fly (Ex):} The astral construct has physical wings and a fly speed of 20 
feet (average).

\textbf{Improved Bull Rush (Ex):} The astral construct gains the Improved Bull 
Rush feat.

\textbf{Improved Slam Attack (Ex):} The astral construct gains the Improved Natural 
Attack feat.

\textbf{Mobility (Ex):} The astral construct gains the Mobility feat.

\textbf{Power Attack (Ex):} The astral construct gains the Power Attack feat.

\textbf{Resistance (Ex): }Choose one of the following energy types: fire, cold, 
acid, electricity, or sonic. The astral construct gains resistance 5 against that 
energy type.

\textbf{Swim (Ex):} The astral construct is streamlined and shark like, and gains 
a swim speed of 30 feet.

\textbf{Trip (Ex):} If the astral construct hits with a slam attack, it can attempt 
to trip the opponent as a free action without making a touch attack or provoking 
attacks of opportunity. If the attempt fails, the opponent cannot react to trip 
the astral construct.

\vspace{12pt}
\section*{Astral Construct Menu B}

A manifester creating a 4th-level, 5th-level, or 6th-level astral construct can 
choose one special ability from this menu. Alternatively, the construct can have 
two special abilities from Menu A.

\textbf{Energy Touch (Ex):} If you are a kineticist, the astral construct's physical 
attacks are wreathed in your energy type, dealing an extra 1d6 points of energy 
damage. If you are not a kineticist, the astral construct deals an extra 1d4 points 
of damage of an energy type you choose (fire, cold, acid, or electricity) when 
you manifest the construct.

\textbf{Extra Attack: }If the astral construct is Medium or smaller, it gains two 
slam attacks instead of one when it makes a full attack. Its bonus on damage rolls 
for each attack is equal to its Strength modifier, not its Strength modifier x 
1-1/2. If the astral construct is Large or larger, it gains three slams instead 
of two when it makes a full attack. Its attacks are otherwise unchanged. 

\textbf{Fast Healing (Ex):} The astral construct heals 2 hit points each round. 
It is still immediately destroyed when it reaches 0 hit points.

\textbf{Heavy Deflection (Ex):} The astral construct gains a +4 deflection bonus 
to Armor Class.

\textbf{Improved Buff (Ex):} The astral construct gains an extra 15 hit points.

\textbf{Improved Critical (Ex):} The astral construct gains the Improved Critical 
feat with its slam attacks.

\textbf{Improved Damage Reduction (Ex):} The astral construct's surface forms a 
hard carapace and provides an additional 3 points of damage reduction (or damage 
reduction 3/magic if it does not already have damage reduction).

\textbf{Improved Fly (Ex):} The astral construct has physical wings and a fly speed 
of 40 feet (average).

\textbf{Improved Grab (Ex): }To use this ability, the construct must hit with its 
slam attack. A construct can use this ability only on a target that is at least 
one size smaller than itself. 

Improved Swim: The astral construct is streamlined and sharklike, and gains a swim 
speed of 60 feet.

\textbf{Muscle (Ex):} The astral construct gains a +4 bonus to its Strength score.

\textbf{Poison Touch (Ex):} If the astral construct hits with a melee attack, the 
target must make an initial Fortitude save (DC 10 + 1/2 astral construct's HD + 
astral construct's Cha modifier) or take 1 point of Constitution damage. One minute 
later, the target must save again or take 1d2 points of Constitution damage.

\textbf{Pounce (Ex):} If the astral construct charges a foe, it can make a full 
attack. 

\textbf{Smite (Su):} Once per day the astral construct can make one attack that 
deals extra damage equal to its Hit Dice.

\textbf{Trample (Ex):} As a standard action during its turn each round, a Large 
or larger astral construct can literally run over an opponent at least one size 
smaller than itself. It merely has to move over the opponent to deal bludgeoning 
damage equal to 1d8 + its Str modifier. The target can attempt a Reflex save (DC 
10 + 1/2 astral construct's Hit Dice + astral construct's Str modifier) to negate 
the damage, or it can instead choose to make an attack of opportunity at a -4 penalty.

\vspace{12pt}
\section*{Astral Construct Menu C}

A manifester creating a 7th-level, 8th-level, or 9th-level astral construct can 
choose one special ability from this menu. Alternatively, the astral construct 
can have two special abilities from Menu B. (One or both of the Menu B choices 
can be swapped for two choices from Menu A.)

\textbf{Blindsight (Ex): }The astral construct has blindsight out to 60 feet.

\textbf{Concussion (Sp):} The astral construct can manifest \textit{concussion 
blast }(manifester level 7th) as a free action once per round.

\textbf{Constrict (Ex):} The astral construct has the improved grab ability with 
its slam attack. In addition, on a successful grapple check, the astral construct 
deals damage equal to its slam damage.

\textbf{Dimension Slide (Sp):} The astral construct can manifest \textit{dimension 
slide }(manifester level equal to Hit Dice) as a move action once per round.

\textbf{Energy Bolt (Sp):} The astral construct can manifest \textit{energy bolt 
}(manifester level 8th) as a standard action once per round. The creator sets the 
energy type that the astral construct can manifest when he creates it. 

\textbf{Extra Buff (Ex):} The astral construct gains an extra 30 hit points.

\textbf{Extreme Damage Reduction (Ex):} The astral construct's surface forms hard, 
armor-like plates and provides an additional 6 points of damage reduction.

\textbf{Extreme Deflection (Ex):} The astral construct gains a +8 deflection bonus 
to Armor Class.

\textbf{Natural Invisibility (Su):} The astral construct is constantly invisible, 
even when attacking. This ability is inherent and not subject to the \textit{invisibility 
purge }spell.

\textbf{Power Resistance (Ex):} The astral construct gains power resistance equal 
to 10 + its Hit Dice.

\textbf{Rend (Ex):} The astral construct makes claw attacks instead of slam attacks 
(it deals the same amount of damage as it would with its slam damage, but does 
slashing damage instead of bludgeoning damage). An astral construct that hits the 
same opponent with two claw attacks in the same round rends its foe, which deals 
extra damage equal to 2d6 + 1-1/2 times its Str modifier.

\textbf{Spring Attack (Ex):} The astral construct gains the Spring Attack feat.

\textbf{Whirlwind Attack (Ex):} The astral construct gains the Whirlwind Attack 
feat.

\vspace{12pt}
{\LARGE 1ST-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.310in}|}{\begin{minipage}[t]{3.310in}\raggedright
Small Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
1d10+10 (15 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.310in}|}{\begin{minipage}[t]{3.310in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
18 (+2 Dex, +5 natural, +1 size), touch 13, flatfooted 16\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+2/-1\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Slam +3 melee (1d4+3)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Slam +3 melee (1d4+3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
One ability from Menu A, construct traits, darkvision 60 ft., low-light vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Fort +0, Ref +2, Will +0\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Str 15, Dex 15, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{{\LARGE 2ND-LEVEL ASTRAL CONSTRUCT}}

\subsection*{\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.849in}|}{\begin{minipage}[t]{2.849in}\raggedright
Medium Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
2d10+20 (31 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.849in}|}{\begin{minipage}[t]{2.849in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
18 (+2 Dex, +6 natural), touch 12, flat-footed 16\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+3/+4\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Slam +4 melee (1d6+4)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Slam +4 melee (1d6+4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
traits, darkvision 60 ft., low-light vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Fort +0, Ref +2, Will +0\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Str 17, Dex 15, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
1\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{2.987in}|}{\begin{minipage}[t]{2.987in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}
}

\vspace{12pt}
{\LARGE 3RD-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.286in}|}{\begin{minipage}[t]{3.286in}\raggedright
Medium Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
3d10+20 (36 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.286in}|}{\begin{minipage}[t]{3.286in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
20 (+2 Dex, +8 natural), touch 12, flatfooted 18\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
+4/+7\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Slam +7 melee (1d6+7)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Slam +7 melee (1d6+7)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
One ability from Menu A, construct traits, darkvision 60 ft., low-light vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Fort +1, Ref +3, Will +1\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Str 21, Dex 15, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.112in}|}{\begin{minipage}[t]{1.112in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.388in}|}{\begin{minipage}[t]{3.388in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 4TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.308in}|}{\begin{minipage}[t]{3.308in}\raggedright
Medium Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
5d10+20 (47 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.308in}|}{\begin{minipage}[t]{3.308in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
22 (+2 Dex, +10 natural), touch 12, flatfooted 20\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+5/+10\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Slam +10 melee (1d6+10)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Slam +10 melee (1d6+10)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
One ability from Menu B, construct traits, darkvision 60 ft., low-light vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Fort +1, Ref +3, Will +1\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Str 25, Dex 15, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.087in}|}{\begin{minipage}[t]{1.087in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.413in}|}{\begin{minipage}[t]{3.413in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 5TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.264in}|}{\begin{minipage}[t]{3.264in}\raggedright
Large Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
7d10+30 (68 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.264in}|}{\begin{minipage}[t]{3.264in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
23 (+1 Dex, +13 natural, -1 size), touch 10, flat-footed 22\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+7/+18\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Slam +13 melee (1d8+9)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
2 slams +13 melee (1d8+9)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
One ability from Menu B, construct traits, damage reduction 5/magic, darkvision 
60 ft., lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Fort +2, Ref +3, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Str 29, Dex 13, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
5\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.132in}|}{\begin{minipage}[t]{1.132in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.368in}|}{\begin{minipage}[t]{3.368in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 6TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.120in}|}{\begin{minipage}[t]{3.120in}\raggedright
Large Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
10d10+30 (85 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.120in}|}{\begin{minipage}[t]{3.120in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
25 (+1 Dex, +15 natural, -1 size), touch 10, flat-footed 24\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
+9/+22\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Slam +17 melee (1d8+11)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
2 slams +17 melee (1d8+11)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
One ability from Menu B, construct traits, damage reduction 10/magic, darkvision 
60 ft., lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Fort +3, Ref +4, Will +3\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Str 33, Dex 13, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
7\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 7TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.202in}|}{\begin{minipage}[t]{3.202in}\raggedright
Large Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
13d10+30 (101 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.202in}|}{\begin{minipage}[t]{3.202in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
27 (+1 Dex, +17 natural, -1 size), touch 10, flat-footed 26\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
+11/+25\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Slam +20 melee (1d8+12)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
2 slams +20 melee (1d8+12)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
One ability from Menu C, construct traits, damage reduction 10/magic, darkvision 
60 ft., lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Fort +4, Ref +5, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Str 35, Dex 13, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
8\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.316in}|}{\begin{minipage}[t]{3.316in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 8TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.106in}|}{\begin{minipage}[t]{3.106in}\raggedright
Large Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
16d10+30 (118 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.106in}|}{\begin{minipage}[t]{3.106in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
29 (+1 Dex, +19 natural, -1 size), touch 10, flat-footed 28\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
+14/+30\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Slam +25 melee (1d8+14)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
2 slams +25 melee (1d8+14)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
One ability from Menu C, construct traits, damage reduction 15/magic, darkvision 
60 ft., lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Fort +5, Ref +6, Will +5\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Str 39, Dex 13, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
9\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.272in}|}{\begin{minipage}[t]{1.272in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.228in}|}{\begin{minipage}[t]{3.228in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE 9TH-LEVEL ASTRAL CONSTRUCT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.203in}|}{\begin{minipage}[t]{3.203in}\raggedright
Huge Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
19d10+40 (144 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.203in}|}{\begin{minipage}[t]{3.203in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
50 ft. (10 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
33 (+25 natural, -2 size), touch 8, flatfooted 33\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
+16/+38\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Slam +28 melee (2d6+16)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
2 slams +28 melee (2d6+16)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
15 ft./15 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Two abilities from Menu C, construct traits, damage reduction 15/magic, darkvision 
60 ft., lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Fort +6, Ref +6, Will +6\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Str 43, Dex 11, Con ---, Int ---, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
10\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.183in}|}{\begin{minipage}[t]{1.183in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
{\LARGE BLUE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.257in}|}{\begin{minipage}[t]{3.257in}\raggedright
Blue, 1st-Level Psion (Telepath)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
Small Humanoid (Goblinoid, Psionic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.257in}|}{\begin{minipage}[t]{3.257in}\raggedright
1d4+1 (3 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
15 (+1 size, +4 \textit{inertial armor}), touch 11, flatfooted 15\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
+0/-6\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Quarterstaff -2 melee (1d4-2) or light crossbow +0 ranged (1d6/19-20)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Quarterstaff -2 melee (1d4-2) or light crossbow +0 ranged (1d6/19-20)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Psionic powers\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Darkvision 60 ft.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Fort +1, Ref +0, Will +2\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Str 6, Dex 11, Con 12, Int 15, Wis 10, Cha 7\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Concentration +5, Hide +6, Move Silently +4,\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Psicraft +6, Ride +4, Spot +2}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Psionic Body, Wild Talent\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Temperate plains\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Solitary, gang (1 plus 4-9 goblin warriors), band (2d10 plus 10-100 goblin warriors 
plus 100\% noncombatants plus 1 3rd-level sergeant per 20 adults and 1 leader of 
4th-6th level), warband (2d4 plus 10-24 goblin warriors with worg mounts), or tribe 
(4d10 plus 40-400 goblin warriors plus 100\% noncombatants plus 1 3rd-level sergeant 
per 20 adults, 1 or 2 lieutenants of 4th or 5th level, 1 leader of 6th-8th level, 
10-24 worgs, and 2-4 dire wolves)\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
1\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
Usually neutral evil\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
By character class (usually psion)\end{minipage}}\\
\hline
% ROW 24
\multicolumn{1}{|p{1.135in}|}{\begin{minipage}[t]{1.135in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.365in}|}{\begin{minipage}[t]{3.365in}\raggedright
+0\end{minipage}}\\
\hline
\end{longtable}

Blues are a subrace of goblins with an innate knack for psionics. A blue is often 
smaller than an average goblin, standing just about 3 feet tall and weighing about 
40 pounds. Blues have noticeably blue-tinged skin, and their eyes are less dull 
than those of a common goblin. Otherwise, they resemble their kin. They generally 
dress in short leather robes, dyed black.

Blues speak Goblin and Common.

Most blues encountered outside their homes are psions; the information in the statistics 
block is for a psion of 1st level.

\subsubsection*{COMBAT}

Blues support goblin warriors in combat and are often called upon to lead a gang 
of goblins (from the rear) into battle.

\textbf{Psionic Powers:} The blue described here is a 1st-level psion.

\textit{Typical Psion Powers Known }(power points 3*; save DC 12 + power level): 
1st---\textit{inertial armor, mind thrust }(DC 13), \textit{psionic charm }(DC 
13). 

Manifester level 1st. The save DCs are Intelligence-based.

*The blue shown here has already manifested \textit{inertial armor; }its reserve 
is normally 4 power points.

\textbf{Skills:} Blues have a +4 racial bonus on Move Silently checks and Ride 
checks.

The blue psion presented here had the following ability scores before racial adjustments: 
Str 8, Dex 11, Con 12, Int 13, Wis 10, Cha 9.

\subsubsection*{BLUES AS CHARACTERS}

Blues tend to be psions, although blues raised in communities where their kind 
are rare may choose the path of the wilder.

Blue characters possess the following racial traits.----

2 Strength, +2 Intelligence, -2 Charisma.---

Small size: +1 bonus to Armor Class, +1 bonus on attack rolls, +4 bonus on Hide 
checks, -4 penalty on grapple checks, lifting and carrying limits 3/4 of those 
of Medium characters.---

Blue base land speed is 30 feet.---

Darkvision out to 60 feet.---

Naturally Psionic: Blues gain 1 bonus power point at 1st level.---

Racial Skills: A blue character has a +4 racial bonus on Move Silently checks and 
Ride checks.---

Automatic Languages: Common, Goblin. Bonus Languages: Draconic, Elven, Giant, Gnoll, 
Orc.---

Favored Class: Psion.---

Level Adjustment: +1.

\vspace{12pt}
{\LARGE BRAIN MOLE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.821in}|}{\begin{minipage}[t]{2.821in}\raggedright
Tiny Magical Beast (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d10-2 (3 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.821in}|}{\begin{minipage}[t]{2.821in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
15 ft. (3 squares), burrow 15 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
14 (+2 size, +2 Dex), touch 14, flat-footed 12\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+1/-11\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Bite +5 melee (1d3-4)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Bite +5 melee (1d3-4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
2-1/2 ft./0 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Cascade flu, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Low-light vision, power conversion, scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Fort +0, Ref +4, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Str 2, Dex 14, Con 7, Int 2, Wis 14, Cha 11\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Hide +15, Move Silently +7, Listen +6, Spot +2\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Alertness, Weapon Finesse\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Temperate forest\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Nest (3-8)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{2.960in}|}{\begin{minipage}[t]{2.960in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Brain moles are burrowing animals that use psionic powers to overcome large psionic 
prey. Small, furry, and nearly blind, brain moles are almost indistinguishable 
from their common animal cousins.

Brain moles eat small insects when they can't get psionic energy.

\subsubsection*{COMBAT}

Brain moles hunger for psionic energy. They hide in loose dirt and detritus on 
forest floors, watching for the approach of psionic creatures with their \textit{detect 
psionics }power. When a suitable target comes in range, the brain moles then attack 
with their \textit{power leech }ability. The moles remain hidden as long as possible. 
If threatened, they use \textit{aversion }and \textit{mind thrust }to discourage 
attackers, using their bite only as a last resort.

\textbf{Cascade Flu (Ex):} Disease---bite; Fortitude DC 9, incubation period one 
day, damage psionic cascade (every time an afflicted character manifests a power, 
she must make a DC 16 Concentration check; on a failed check, a psionic cascade 
is triggered [see Psionic Maladies]). The save DC is Constitution-based. 

\textbf{Psi-Like Abilities:} At will---\textit{detect psionics, power leech }(ML 
5th, DC 14)\textit{; }3/day---\textit{aversion }(DC 12)\textit{, mind thrust }(DC 
11)\textit{. }Manifester level 1st. The save DCs are Charisma-based. 

\textbf{Hide Mind (Su): }A brain mole cannot be identified as psionic by divination 
spells or clairsentience powers. 

\textbf{Power Conversion (Su):} When a brain mole drains a power point by means 
of its \textit{power leech }power, it immediately heals 1 hit point. If it is already 
at full normal hit points, it instead gains psionic sustenance sufficient to supply 
its need for nourishment for 24 hours. 

\textbf{Skills: }Brain moles have a +4 racial bonus on Hide and Move Silently checks 
and a -2 racial penalty on Spot checks.

\vspace{12pt}
{\LARGE CALLER IN DARKNESS}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.272in}|}{\begin{minipage}[t]{3.272in}\raggedright
Large Undead (Incorporeal, Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
11d12 (71 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.272in}|}{\begin{minipage}[t]{3.272in}\raggedright
+7\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
30 ft. (6 squares), fly 60 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
14 (-1 size, +3 Dex, +2 deflection), touch 14, flat-footed 11\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
+5/---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Incorporeal touch +7 melee (2d6)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
4 incorporeal touches +7 melee (2d6)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Psi-like abilities, steal essence\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Incorporeal traits, undead traits, unnatural aura, vulnerability to sunlight\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Fort +3, Ref +6, Will +9\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Str ---, Dex 16, Con ---, Int 14, Wis 14, Cha 15\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Hide +9, Intimidate +12, Knowledge (psionics) +12, Listen +14, Psicraft +12, Search 
+12, Sense Motive +12, Spot +14\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Blind-Fight, Combat Reflexes, Improved Initiative, Weapon Finesse \end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
9\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
Always chaotic evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
12-22 HD (Large); 23-33 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.380in}|}{\begin{minipage}[t]{3.380in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A caller in darkness is an incorporeal creature composed of the minds of dozens 
of victims who died together in terror. It seeks to draw others into its fearwracked, 
hellish existence.

Callers in darkness rarely speak, but when they do, they speak Common.

\subsection*{COMBAT}

\textbf{Psi-Like Abilities: }At will---\textit{clairvoyant sense, concussion blast 
}(two targets, 3d6*)\textit{, detect psionics, ego whip }(2d4, DC 16*), \textit{mind 
thrust }(7d10, DC 16*); 3/day---\textit{death urge }(DC 16), \textit{psychic crush 
}(DC 13**), \textit{psionic suggestion }(three targets, DC 14*); 1/ day---\textit{co-opt 
concentration }(DC 18). Manifester level 7th. The save DCs are Charisma-based.

*Includes augmentation for the caller's manifester level.

**Includes the inherent +4 save adjustment described in the power.

\textbf{Steal Essence (Su):} Any living, intelligent creature slain by a caller 
in darkness's touch attack is mentally absorbed into the monster's consciousness. 
(The physical body of the victim remains intact). Stealing a victim's essence is 
a free action; it grants the caller 12 temporary hit points, and a permanent new 
screaming face appears within its cloud.

A caller in darkness can also steal the essence of living, intelligent creatures 
within 30 feet that are paralyzed or sleeping, or that are helpless due to having 
a mental ability score reduced to 0 (often by the caller's \textit{ego whip }attack). 
Doing so is a standard action that provokes attacks of opportunity. The victim 
dies, and the caller gains 12 temporary hit points.

\textbf{Incorporeal Traits:} A caller in darkness is harmed only by other incorporeal 
creatures, magic weapons, spells, spell-like abilities, and supernatural abilities. 
It has a 50\% chance to ignore any damage from a corporeal source, except for force 
effects or attacks made with ghost touch weapons. It can pass through solid objects, 
but not force effects, at will. Its attacks ignore natural armor, armor, and shields, 
but deflection bonuses and force effects work normally against them. The creature 
always moves silently and cannot be heard with Listen checks if it doesn't wish 
to be. 

\textbf{Undead Traits:} A caller in darkness is immune to mind-affecting effects, 
poison, \textit{sleep, }paralysis, stunning, disease, death effects, and any effect 
that requires a Fortitude save unless it also works on objects or is harmless. 
It is not subject to critical hits, nonlethal damage, ability damage to its physical 
ability scores, ability drain, energy drain, fatigue, exhaustion, or death from 
massive damage. It cannot be raised, and \textit{resurrection }works only if it 
is willing. It has darkvision out to 60 feet.

\textbf{Unnatural Aura (Su): }Animals can sense the unnatural presence of a caller 
in darkness. Any animal within 30 feet must make a DC 17 Will save or become panicked 
until it is no longer within 30 feet of the caller in darkness. A panicked creature 
that is cornered begins cowering. The save DC is Charisma-based.

\textbf{Vulnerability to Sunlight (Ex): }Callers in darkness are utterly powerless 
in natural sunlight (not merely a \textit{daylight }spell) and flee from it. A 
caller caught in sunlight cannot attack and can take only a single move action 
or standard action each turn, but  not both (nor can it take full-round actions).

\vspace{12pt}
{\LARGE CEREBRILITH}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.628in}|}{\begin{minipage}[t]{3.628in}\raggedright
Large Outsider (Chaotic, Evil, Extraplanar, Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
9d8+63 (103 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.628in}|}{\begin{minipage}[t]{3.628in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
25 (-1 size, +1 Dex, +15 natural), touch 10, flat-footed 24\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
+9/+19\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Bite +14 melee (1d8+6)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Bite +14 melee (1d8+6) and 2 claws +9 melee (1d6+3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Psi-like abilities, spell-like abilities, \textit{summon demon}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Damage reduction 10/good, darkvision 60 ft., immunity to electricity and poison, 
outsider traits, psionic traits, resistance to acid 10, cold 10, and fire 10, power 
resistance 20, telepathy 100 ft.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Fort +13, Ref +7, Will +10\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Str 22, Dex 13, Con 25, Int 15, Wis 18, Cha 21\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Concentration +17, Hide +7, Jump +16, Knowledge (arcana) +12, Knowledge (psionics) 
+12, Knowledge (planes) +12, Listen +22, Move Silently +11, Psicraft +12, Search 
+12, Sense Motive +14, Spot +22\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Power Attack, Psionic Meditation, Psionic Fist, Unavoidable Strike, Wild Talent\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Chaotic evil planes\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Solitary or gang (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
10\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
Always chaotic evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
10-18 HD (Large); 19-27 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.786in}|}{\begin{minipage}[t]{0.786in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.714in}|}{\begin{minipage}[t]{3.714in}\raggedright
+9\end{minipage}}\\
\hline
\end{longtable}

COMBAT

Cerebriliths favor telepathic attacks, usually beginning a battle by launching 
a furious barrage of \textit{ego whip }and \textit{id insinuation }attacks. In 
melee, cerebriliths often use their Concentration skill to gain psionic focus, 
so that they can use Psionic Fist or Unavoidable Strike (the latter in conjunction 
with Power Attack).

A cerebrilith's natural weapons, as well as any weapons it wields, are treated 
as chaotic-aligned and evil-aligned for the purpose of overcoming damage reduction.

\textbf{Psi-Like Abilities:} At will---\textit{brain lock }(any nonmindless, DC 
17*), \textit{detect psionics, ego whip }(2d4, DC 19*)\textit{, id insinuation 
}(four targets, DC 20*)\textit{, mind trap }(5 rounds*)\textit{; }3/day---\textit{psionic 
dominate }(24 hours, DC 20*), \textit{ectoplasmic form}, \textit{mind probe }(DC 
20); 1/day---\textit{mind thrust }(9d10, DC 20*). Manifester level 9th. The save 
DCs are Charisma-based.

*Includes augmentation for the cerebrilith's manifester level.

\textbf{Spell-Like Abilities:} At will---\textit{deeper darkness, desecrate, detect 
good, dispel good }(DC 20)\textit{, greater teleport }(self plus 50 pounds of objects 
only), \textit{magic circle against good }(DC 18)\textit{, unholy blight }(DC 19). 
Caster level 9th. The save DCs are Charisma-based.

\textbf{Summon Demon (Sp):} Once per day a cerebrilith can attempt to summon 4d6 
dretches or another cerebrilith with a 35\% chance of success. This ability is 
equivalent to a 4th-level spell.

\textbf{Outsider Traits: }A cerebrilith cannot be \textit{raised, reincarnated 
}or \textit{resurrected }(though a \textit{limited wish, wish}, \textit{miracle}, 
or \textit{true resurrection }spell can restore life). It has darkvision out to 
60 feet. 

\textbf{Skills:} Cerebriliths have a +8 racial bonus on Listen and Spot checks.

\vspace{12pt}
{\LARGE COUATL, PSIONIC}

Large Outsider (Native, Psionic) 

\textbf{Special Attacks:} Constrict 2d8+6, improved grab, poison, psi-like abilities, 
spells

\subsubsection*{COMBAT}

The psionic couatl does not possess the psionic spell-like abilities of the standard 
couatl. Instead, it has psi-like abilities\textit{.}

\textbf{Psi-Like Abilities: }At will---\textit{aura sight, cloud mind }(DC 15), 
\textit{detect psionics, read thoughts }(DC 15); 3/day---\textit{mental barrier 
}(2 rounds*)\textit{, metamorphosis, psionic plane shift, thought shield }(power 
resistance 19*)\textit{. }Manifester level 9th. The save DCs are Charisma-based.

*Includes augmentation for the psionic couatl's manifester level.

\vspace{12pt}
{\LARGE CRYSMAL}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Small Elemental (Earth, Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
6d8+6 (33 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
30 ft. (6 squares), burrow 20 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
21 (+1 size, +2 Dex, +8 natural), touch 13, flat-footed 19\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
+4/+2\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Sting +7 melee (1d3+3)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Sting +7 melee (1d3+3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Damage reduction 5/ bludgeoning, elemental traits, immunity to fire and cold, resistance 
to electricity 15 \end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Fort +8, Ref +6, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Str 15, Dex 14, Con 12, Int 6, Wis 10, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Appraise +9, Climb +5, Jump +5, Listen +2, Spot +10\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Alertness, Great Fortitude, Lightning Reflexes\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Solitary or facet (2-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Double goods (gems only)\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
Any lawful\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
7-12 HD (Medium); 13-18 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.881in}|}{\begin{minipage}[t]{0.881in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.619in}|}{\begin{minipage}[t]{3.619in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A conglomerate of stone and crystal, a crysmal above all else seeks to perpetuate 
its kind.

Crysmals transform mundane minerals into juvenile crysmals. Gems are the perfect 
substance for this reproductive cycle: To make a single juvenile, a crysmal generally 
needs eight to ten gems, each of 25 gp value or more. 

Crysmals understand Terran but do not speak.

\subsubsection*{COMBAT}

\textbf{Psi-Like Abilities:} At will---\textit{control object, control sound, detect 
psionics, empty mind, mind thrust }(2d10, DC 13*); 3/day---\textit{psionic dimension 
door. }Manifester level 2nd. The save DCs are Charisma-based.

*Includes augmentation for the crysmal's manifester level.

\textbf{Skills: }Crysmals have a +8 racial bonus on Appraise checks and Spot checks.

\vspace{12pt}
{\LARGE DROMITE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.313in}|}{\begin{minipage}[t]{3.313in}\raggedright
Dromite, 1st-Level Warrior\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
Small Monstrous Humanoid (Psionic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.313in}|}{\begin{minipage}[t]{3.313in}\raggedright
1d8+1 (5 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
20 ft. (4 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
18 (+1 size, +3 natural armor, +3 studded leather, +1 light shield), touch 11, 
flat-footed 18\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
+1/-3\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Longsword +3 melee (1d6/19-20) or light crossbow +2 ranged (1d6/19-20)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Longsword +3 melee (1d6/19-20) or light crossbow +2 ranged (1d6/19-20)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Psi-like abilities\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Darkvision 60 ft., resistance to fire 5, scent\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Fort +3, Ref +0, Will -2\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Str 11, Dex 11, Con 12, Int 10, Wis 7, Cha 10\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Climb +2, Spot +4\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Weapon Focus (longsword), Blind-Fight\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Squad (2-4), company (11-20 plus 2 3rd-level sergeants and 1 leader of 3rd-6th 
level), or band (30-100 plus 100\% noncombatants plus 1 3rdlevel sergeant per 20 
adults, 5 5th-level lieutenants, 3 7th-level captains, 6-10 giant beetles, and 
2-5 riding giant beetles)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
+1\end{minipage}}\\
\hline
\end{longtable}

Dromites stand about 3 feet tall and usually weigh slightly more than 30 pounds. 
They have iridescent compound eyes. Dromites wear heavy boots and light clothing, 
and are sometimes content with just a sturdy harness. 

Dromites speak Common.

Most dromites encountered outside their homes are warriors; the information in 
the statistics block is for a warrior of 1st level.

COMBAT

\textbf{Psi-Like Abilities:} 1/day: \textit{energy ray }(fire, 1d6+1)\textit{. 
}Manifester level 1st. The save DC is Charisma-based. (Other dromites may manifest 
electricity, cold, or sonic \textit{energy rays }instead; the \textit{energy ray 
}always matches the type of energy the dromite is resistant to.)

The dromite warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8.

DROMITES AS CHARACTERS

Dromite characters possess the following racial traits.---

+2 Charisma, -2 Strength, -2 Wisdom.---

Small size: +1 bonus to Armor Class, +1 bonus on attack rolls, +4 bonus on Hide 
checks, -4 penalty on grapple checks, lifting and carrying limits 3/4 of those 
of Medium characters.---

Dromite base land speed is 20 feet.---

+3 natural armor bonus.---

Naturally Psionic: Dromites gain 1 bonus power point at 1st level.---

Special Attacks (see above): Psi-like abilities.---

Special Qualities (see above): Resistance to fire 5 (other dromites may have resistance 
to cold, electricity, or sonics instead of fire), scent.---

Racial Skills: Dromites have a +2 racial bonus on Spot checks due to their compound 
eyes.---

Racial Feats: Dromites gain Blind-fight as a bonus feat.---

Automatic Languages: Common. Bonus Languages: Dwarven, Gnome, Goblin, Terran.---

Favored Class: Wilder.---

Level Adjustment: +1.

\vspace{12pt}
{\LARGE DUERGAR, PSIONIC}

Duergar, 1st-Level Warrior

Medium Humanoid (Dwarf, Psionic) 

\textbf{Special Attacks:} Duergar traits, psi-like abilities

\subsubsection*{COMBAT}

A psionic duergar does not possess the spell-like abilities of standard duergars. 
Instead, it has psi-like abilities\textit{.}

\textbf{Psi-Like Abilities:} 1/day---\textit{expansion, invisibility. }These abilities 
are as the power (or spell) manifested by a psion (or sorcerer) of the duergar's 
Hit Dice (minimum 3rd level) and affect only the duergar and whatever he carries.

\subsubsection*{DUERGAR AS CHARACTERS}

Duergar characters possess the following racial traits.---

+2 Constitution, -4 Charisma.---

Medium size.---

Duergar base land speed is 20 feet. However, gray dwarves can move at this speed 
even when wearing medium or heavy armor or when carrying a medium or heavy load 
(unlike other creatures, whose speed is reduced in such situations).---

Darkvision out to 120 feet.---

Immunity to paralysis, phantasms, and poison.---

+2 racial bonus on saves against spells and spell-like effects.---

Stability: Duergar are exceptionally stable on their feet. A duergar receives a 
+4 bonus on ability checks made to resist being bull rushed or tripped when standing 
on the ground (but not when climbing, flying, riding or otherwise not standing 
firmly on the ground).---

Stonecunning: This ability grants a duergar a +2 racial bonus on Search checks 
to notice unusual stonework, such as sliding walls, stonework, traps, new construction 
(even when built to match the old), unsafe stone surfaces, shaky stone ceilings, 
and the like. Something that isn't stone but that is disguised as stone also counts 
as unusual stonework. A gray dwarf who merely comes within 10 feet of unusual stonework 
can make a Search check as if he were actively searching, and a duergar can use 
the Search skill to find stonework traps as a rogue can. A duergar can also intuit 
depth, sensing his approximate depth underground as naturally as a human can sense 
which way is up.

Duergar have a sixth sense about stonework, an innate ability that they get plenty 
of opportunity to practice and hone in their underground homes.---

Psi-Like Abilities: 1/day---expansion, invisibility. These abilities affect only 
the duergar and whatever he carries. Manifester level is equal to Hit Dice (minimum 
3rd).---

Naturally Psionic: Duergar gain 3 bonus power points at 1st level. This benefit 
does not grant them the ability to manifest powers unless they gain that ability 
through another source, such as levels in a psionic class.---

+1 racial bonus on attack rolls against orcs (including half-orcs) and goblinoids 
(including goblins, hobgoblins, and bugbears). ---

+4 dodge bonus to Armor Class against creatures of the giant type (such as ogres, 
trolls, and hill giants).---

Light Sensitivity (Ex): Duergar are dazzled in sunlight or within the radius of 
a daylight spell.---

Duergar have a +4 racial bonus on Move Silently checks and a +1 racial bonus on 
Listen and Spot checks. They have a +2 racial bonus on Appraise and Craft checks 
that are related to stone or metal.---

Automatic Languages: Common, Dwarven, Undercommon. Bonus Languages: Draconic, Giant, 
Goblin, Orc, Terran. ---

Favored Class: Fighter.---

Level Adjustment: +1.

\vspace{12pt}
{\LARGE ELAN}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.227in}|}{\begin{minipage}[t]{3.227in}\raggedright
Elan, 1st-Level Warrior\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
Medium Aberration (Psionic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.227in}|}{\begin{minipage}[t]{3.227in}\raggedright
1d8+1 (5 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
14 (+3 studded leather, +1 light shield), touch 10, flat-footed 14\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
+1/+2\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Warhammer +3 melee (1d8+1/x3) or longbow +1 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Warhammer +3 melee (1d8+1/x3) or longbow +1 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
---\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Repletion, resilience, resistance\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Fort +3, Ref +0, Will -1\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Climb +3, Jump +3\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Weapon Focus (warhammer)\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Congregate (2-4), squad (11-20 plus 2 3rdlevel sergeants and 1 leader of 3rd-6th 
level), or band (30-100 plus 150\% noncombatants plus 1 3rd-level sergeant per 
10 adults, 5 5thlevel lieutenants, and 3 7thlevel captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.161in}|}{\begin{minipage}[t]{1.161in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.339in}|}{\begin{minipage}[t]{3.339in}\raggedright
+0\end{minipage}}\\
\hline
\end{longtable}

Elans typically stand just under 6 feet tall and weigh in the neighborhood of 180 
pounds, with men sometimes taller and heavier than women, but not always.

Elans speak Common.

Most elans are psions or psychic warriors.

\subsubsection*{COMBAT}

\textbf{Repletion (Su):} By expending 1 power point, an elan does not need to eat 
or drink for 24 hours. 

\textbf{Resilience (Su): }As an immediate action, an elan can reduce the damage 
he is about to take by 2 points for every 1 power point spent.

\textbf{Resistance (Su):} As an immediate action, an élan can spent 1 power point 
to gain a +4 racial bonus on saving throws until the beginning of his next turn.

The elan warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8.

\subsubsection*{ELANS AS CHARACTERS}

Elan characters possess the following racial traits.----

2 Charisma.---

Medium size.---

Elan base land speed is 30 feet.---

No darkvision.---

Naturally Psionic: Elans gain 1 bonus power point at 1st level.---

Special Qualities (see above): Repletion, resilience, resistance.---

Automatic Languages: Common. ---

Favored Class: Psion.---

Level Adjustment: +0.

\vspace{12pt}
{\LARGE FOLUGUB}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.167in}|}{\begin{minipage}[t]{3.167in}\raggedright
Medium-Size Aberration\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
4d8+12 (30 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.167in}|}{\begin{minipage}[t]{3.167in}\raggedright
+3\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
18 (+3 Dex, +5 natural), touch 13, flatfooted 15\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
+3/+3\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Tongue +6 melee touch (liquefy crystal)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Tongue +6 melee touch (liquefy crystal) and bite +1 melee (2d4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Liquefy crystal\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Darkvision 60 ft., scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Fort +4, Ref +4, Will +5\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Str 10, Dex 17, Con 17, Int 2, Wis 13, Cha 11\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Listen +6, Move Silently +4, Spot +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Alertness, Weapon Finesse\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Solitary or pair\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
5-6 HD (Medium); 7-14 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.216in}|}{\begin{minipage}[t]{1.216in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.284in}|}{\begin{minipage}[t]{3.284in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

COMBAT

A folugub can scent a crystal object up to 90 feet away, and once it has the scent, 
little deters it from its goal. It usually ceases attacking to devour a freshly 
liquefied crystal. The creature targets the largest crystal object available.

\textbf{Liquefy Crystal (Ex):} A folugub that makes a successful touch attack with 
its tongue causes the target crystal to change phase, turning immediately from 
solid to liquid and becoming worthless. The touch can destroy up to a 5-foot cube 
of crystal instantly. Magic or psionic items made of crystal (including crystalline 
armor and weapons) must succeed on a DC 19 Reflex save or be liquefied. The save 
DC is Constitution-based and includes a +4 racial modifier.

A crystalline weapon that deals damage to a folugub becomes liquefied immediately.

\vspace{12pt}
{\LARGE GRAY GLUTTON}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.120in}|}{\begin{minipage}[t]{3.120in}\raggedright
Huge Magical Beast\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
9d10+36 (85 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.120in}|}{\begin{minipage}[t]{3.120in}\raggedright
-1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
20 (-2 size, -1 Dex, +13 natural), touch 7, flatfooted 20\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
+9/+25\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Bite +15 melee (2d8+8)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Bite +15 melee (2d8+8) and 2 claws +10 melee (2d6+4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
15 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Null psionic exhalation\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Darkvision 60 ft., low-light vision, power resistance 20, scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Fort +10, Ref +5, Will +7\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Str 27, Dex 9, Con 19, Int 2, Wis 15, Cha 20\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Jump +14, Listen +7, Spot +3\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Closed Mind, Hostile Mind, Iron Will, Psionic Hole, Track\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Solitary, pair, or cluster (3-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
7\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
10-20 HD (Huge); 21-27 HD (Gargantuan)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.259in}|}{\begin{minipage}[t]{1.259in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\subsubsection*{COMBAT }

A gray glutton attacks anything psionic, or anything that stands in its way of 
tracking down new psionic prey. Of course, a gray glutton has to eat---and eat 
a lot to feed its bulk---so when not on the scent it will attack any living creature. 
It always breaks off attacks against nonpsionic foes if psionic prey is an option. 
The only creatures it refuses to eat are elves (and it dislikes the taste of dwarves). 
No challenge seems too extreme to it, even if that means bulling into the center 
of a powerful party of manifesters.

\textbf{Null Psionic Exhalation (Su): }As a free action, a gray glutton can breathe 
forth a cloud of pale blue translucent gas into an adjacent 10-foot cube. The gas 
is psionically poisonous; the initial damage is 1d4 power points, and the secondary 
damage is 3d4 power points (Fortitude DC 18 negates). Affected psionic characters 
and creatures subtract the lost power points from their reserves.

The save DC is Constitution-based.

Once a gray glutton has used its exhalation, it must wait 4 rounds before it can 
exhale again.

\vspace{12pt}
{\LARGE HALF-GIANT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Half-Giant, 1st-Level Warrior\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
Medium Giant (Psionic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
1d8+2 (6 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
-1\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.050in}|}{\begin{minipage}[t]{0.050in}\raggedright
13 (-1 Dex, +4 scale mail), touch 9, flat-footed 13\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
+1/+7\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Large greatsword +4 melee (3d6+3/19-20) or Large javelin +0 ranged (1d8+2)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Large greatsword +4 melee (3d6+3/19-20) or Large javelin +0 ranged (1d8+2)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Psi-like abilities\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Fire acclimated, giant's stature, low-light vision\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Fort +4, Ref -1, Will -1\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Str 15, Dex 9, Con 14, Int 10, Wis 9, Cha 8\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Listen +1, Spot +1\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Weapon Focus (greatsword)\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Warm desert\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Team (2-4), squad (11-20 plus 2 3rd-level sergeants and 1 leader of 3rd-6th level), 
or band (30-100 plus 150\% noncombatants plus 1 3rd-level sergeant per 10 adults, 
5 5th-level lieutenants, and 3 7th-level captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
1\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
Usually neutral good\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.083in}|}{\begin{minipage}[t]{1.083in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.417in}|}{\begin{minipage}[t]{3.417in}\raggedright
+1\end{minipage}}\\
\hline
\end{longtable}

Half-giants typically stand from 7 feet to nearly 8 feet tall and weigh from 250 
to 400 pounds, with men noticeably taller and heavier than women.

Half-giants speak Common. Many also learn Giant.

\subsubsection*{COMBAT}

Because of their giant ancestry, half-giants are able to use weapons sized for 
creatures larger than normal humans. They gain considerable satisfaction in using 
these large weapons in combat against their foes.

\textbf{Psi-Like Abilities:} 1/day: \textit{stomp }(DC 10)\textit{. }Manifester 
level equal to 1/2 HD (minimum 1st). The save DC is Charisma-based.

\textbf{Fire Acclimated (Ex): }Half-giants have a +2 racial bonus on saving throws 
against all fire spells and effects. 

\textbf{Powerful Build (Ex):} The physical stature of half-giants lets them function 
in many ways as if they were one size category larger. Whenever a half-giant is 
subject to a size modifier or special size modifier for an opposed check (such 
as during grapple checks, bull rush attempts, and trip attempts), the half-giant 
is treated as one size larger if doing so is advantageous to him. A half-giant 
is also considered to be one size larger when determining whether a creature's 
special attacks based on size (such as improved grab or swallow whole) can affect 
him. A half-giant can use weapons designed for a creature one size larger without 
penalty. However, his space and reach remain those of a creature of his actual 
size. The benefits of this racial trait stack with the effects of powers, abilities, 
and spells that change the subject's size category.

The half-giant warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8.

\subsubsection*{HALF-GIANTS AS CHARACTERS}

Half-giant characters possess the following racial traits.---

+2 Constitution, +2 Strength, -2 Dexterity.---

Medium size.---

Half-giant base land speed is 30 feet.---

Low-light vision.---

Naturally Psionic: Half-giants gain 2 bonus power points at 1st level, regardless 
of whether they choose a psionic class.---

Fire Acclimated: Half-giants have a +2 racial bonus on saving throws against all 
fire spells and effects. ---

Powerful build (see above).---

Special Attacks (see above): Psi-like abilities.---

Automatic Language: Common. Bonus Language: Draconic, Giant, Gnoll, Ignan.---

Favored Class: Psychic warrior.---

Level adjustment: +1.

\vspace{12pt}
{\LARGE INTELLECT DEVOURER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.201in}|}{\begin{minipage}[t]{3.201in}\raggedright
Small Aberration (Evil, Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
6d8+15 (42 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.201in}|}{\begin{minipage}[t]{3.201in}\raggedright
+5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
21 (+1 size, +5 Dex, +5 natural), touch 16, flat-footed 16\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.057in}|}{\begin{minipage}[t]{0.057in}\raggedright
+4/+1\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Claw +6 melee (1d3+1)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
4 claws +6 melee (1d3+1)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Body thief, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Blindsight 60 ft., damage reduction 10/adamantine, immunity to fire, power resistance 
23, resistance to electricity 15, vulnerability to \textit{protection from evil}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Fort +4, Ref +7, Will +6\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Str 13, Dex 21, Con 15, Int 12, Wis 12, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Bluff + 15, Concentration +11 (+15 when manifesting defensively), Hide +14, Listen 
+14, Move Silently +16\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Combat Manifestation, Toughness, Up the Walls, Wild Talent\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Solitary or pod (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
7\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
1/2 coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
Always chaotic evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
7-8 HD (Small); 9-15 HD (Medium); 16-18 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.185in}|}{\begin{minipage}[t]{1.185in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.315in}|}{\begin{minipage}[t]{3.315in}\raggedright
+6\end{minipage}}\\
\hline
\end{longtable}

Intellect devourers understand Common but must be in possession of a body to speak. 
An intellect devourer in possession of a body also knows the languages known by 
that victim.

\subsubsection*{COMBAT}

\textbf{Body Thief (Su):} When an intellect devourer overcomes a lone victim, it 
consumes the victim's brain and enters the skull. As a full-round action that provokes 
attacks of opportunity, the devourer can merge its form with that of a helpless 
or dead creature of Small size or larger. The devourer cannot merge its body with 
that of a creature immune to extra damage from critical hits.

When an intellect devourer completes its merging, it psionically consumes the brain 
of the victim (which kills it if it is not already dead). The devourer can exit 
the body at any time as a standard action, bursting the victim's skull and resuming 
its normal form.

After consuming its victim's brain, an intellect devourer can instead choose to 
animate the body for up to seven days as if it were the victim's original brain. 
The devourer retains its hit points, saving throws, and mental ability scores, 
as well as its psi-like abilities. It assumes the physical qualities and ability 
scores of the victim, as if it had used \textit{polymorph }to assume the victim's 
form. As long as the intellect devourer occupies the body, it knows the languages 
spoken by the victim and very basic information about the victim's identity and 
personality, but none of the victim's specific memories or knowledge.

\textbf{Psi-Like Abilities:} At will---\textit{cloud mind, compression, detect 
psionics, ego whip }(2d4, DC 16*), \textit{empty mind }(+5 on Will saves*), \textit{id 
insinuation }(three targets, DC 16*); 3/day---\textit{body adjustment }(2d12*), 
\textit{intellect fortress, painful strike. }Manifester level 7th.

The save DCs are Charisma-based.

*Includes augmentation for the intellect devourer's manifester level.

\textbf{Blindsight (Ex): }An intellect devourer can use nonvisual means to ascertain 
all foes within 60 feet as a sighted creature would.

\textbf{Vulnerability to Protection from Evil (Ex):} An intellect devourer is treated 
as a summoned creature for the purpose of determining how it is affected by a \textit{protection 
from evil }spell. 

\textbf{Skills: }Intellect devourers have a +8 racial bonus on Bluff checks, useful 
for passing off the possessed body as the original. They also have a +8 racial 
bonus on Move Silently checks and Listen checks.

\vspace{12pt}
{\LARGE MAENAD}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.193in}|}{\begin{minipage}[t]{3.193in}\raggedright
Maenad, 1st-Level Warrior\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
Medium Humanoid (Maenad, Psionic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.193in}|}{\begin{minipage}[t]{3.193in}\raggedright
1d8+1 (5 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.055in}|}{\begin{minipage}[t]{0.055in}\raggedright
14 (+3 studded leather, +1 light shield), touch 10, flat-footed 14\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
+1/+2\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Longsword +3 melee (1d8+1/19-20) or longbow +1 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Longsword +3 melee (1d8+1/19-20) or longbow +1 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Psi-like abilities\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Outburst\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Fort +3, Ref +0, Will -1 \end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Climb +3, Jump +3\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Weapon Focus (longsword)\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Warm hills\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Party (2-4), squad (11-20 plus 2 3rd-level sergeants and 1 leader of 3rd-6th level), 
or band (30-100 plus 150\% noncombatants plus 1 3rd-level sergeant per 10 adults, 
5 5th-level lieutenants, and 3 7th-level captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.197in}|}{\begin{minipage}[t]{1.197in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.303in}|}{\begin{minipage}[t]{3.303in}\raggedright
+0\end{minipage}}\\
\hline
\end{longtable}

Maenads typically stand more than 6 feet tall and weigh about 200 pounds; males 
are the same height as and only marginally heavier than maenad females. Maenads 
have no facial or body hair, and they prefer heavier clothing and armor if possible.

Maenads speak their own language and Common.

\subsubsection*{COMBAT}

\textbf{Psi-Like Abilities:} 1/day---\textit{energy ray}. A maenad can deal only 
sonic damage with this ability. Manifester level equal to 1/2 Hit Dice (minimum 
1st). The save DC is Charisma-based.

\textbf{Outburst (Ex): }Once per day for up to 4 rounds a maenad can subjugate 
his mentality. He takes a -2 penalty to Intelligence and Wisdom but gains a +2 
bonus to Strength.

\subsubsection*{MAENADS AS CHARACTERS}

Maenad characters possess the following racial traits.---

Medium size.---

Maenad base land speed is 30 feet.---

Naturally Psionic: Maenads gain 2 bonus power points at 1st level.---

Special Attacks (see above): Psi-like abilities.---

Special Qualities (see above): Outburst.---

Automatic Languages: Common, Maenad. Bonus Languages: Aquan, Draconic, Dwarven, 
Elven, Goblin.---

Favored Class: Wilder.---

Level Adjustment: +0.

\vspace{12pt}
{\LARGE NEOTHELID}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.309in}|}{\begin{minipage}[t]{3.309in}\raggedright
Gargantuan Aberration (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
25d8+200 (312 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.309in}|}{\begin{minipage}[t]{3.309in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
20 ft. (4 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
28 (-4 size, -2 Dex, +24 natural), touch 4, flatfooted 28\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+18/+40\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Tentacle rake +24 melee (2d6+10/19-20)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
4 tentacle rakes +24 melee (2d6+10/19-20)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
30 ft./30 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Breath weapon, improved grab, psi-like abilities, swallow whole\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Blindsight 100 ft., damage reduction 5/-, power resistance 25\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Fort +16, Ref +6, Will +16\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Str 30, Dex 7, Con 27, Int 16, Wis 15, Cha 20\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Climb +38, Knowledge (psionics) +31, Listen +30, Psicraft +31, Spot +30\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Cleave, Improved Critical (tentacle rake), Improved Initiative, Power Attack, Psionic 
Endowment, Psionic Fist, Psionic Meditation, Speed of Thought, Wild Talent\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
15\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
Always lawful evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
26-45 HD (Colossal)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.086in}|}{\begin{minipage}[t]{1.086in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.414in}|}{\begin{minipage}[t]{3.414in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A mature neothelid is a gigantic worm scores of feet long and weighing tens of 
thousands of pounds. Although they understand Undercommon, they rarely communicate 
in a meaningful way.

\subsubsection*{COMBAT}

\textbf{Breath Weapon (Su): }Cone of acid 50 feet long, once every 1d4 rounds; 
damage 14d10 acid, Reflex half DC 30. 

\textbf{Improved Grab (Ex): }To use this ability, a neothelid must hit a creature 
with two tentacles during the same attack. If it gets a hold, it automatically 
deals tentacle damage and can attempt to swallow the foe. 

\textbf{Psi-Like Abilities: }At will---\textit{body equilibrium, psionic charm 
}(all targets, duration 15 days, DC 21*), \textit{clairvoyant sense, psionic levitate, 
read thoughts }(DC 17*), \textit{psionic suggestion }(seven targets, DC 17*), \textit{telekinetic 
force }(500 lb., DC 18*), \textit{telekinetic maneuver }(+4 bonus, DC 19*), \textit{telekinetic 
thrust }(500 lb., DC 18*), \textit{psionic teleport, trace teleport, truevenom 
}(DC 19); 3/day---\textit{mind thrust }(15d10, DC 23*), \textit{psychic thrust 
}(6d6, DC 16**). Manifester level 15th. The save DCs are Charisma-based.

*Includes augmentation for the neothelid's manifester level. 

**Includes the inherent +4 save adjustment described in the power.

\textbf{Swallow Whole (Ex):} A neothelid can try to swallow a grabbed opponent 
of a smaller size than itself by making a successful grapple check. Once inside, 
the opponent takes 2d8+15 points of crushing damage plus 2d6 points of acid damage 
per round from stomach secretions. A swallowed creature can cut its way out by 
using a light slashing or piercing weapon to deal 25 points of damage to the stomach 
(AC 22). Once the creature exits, muscular action closes the hole; another swallowed 
opponent must cut its own way out. A neothelid's interior can hold 1 Huge, 2 Large, 
8 Medium, 32 Small, 128 Tiny, or 512 Diminutive or smaller opponents.

\textbf{Blindsight (Ex):} A neothelid can use nonvisual means to ascertain all 
foes within 100 feet as a sighted creature would.

\vspace{12pt}
{\LARGE PHRENIC CREATURE}

Seemingly no different from standard examples of their kind, phrenic creatures 
harbor mental might.

Monsters who naturally possess psionic ability are not found as phrenic creatures. 
Phrenic creatures are freaks among their kind, otherwise normal creatures whose 
minds are more powerful than those of their fellows. Similarly, creatures who advance 
by character class are usually not phrenic creatures---they simply take levels 
in a psionic class to hone their mental powers.

{\large CREATING A PHRENIC CREATURE}

``Phrenic'' is an inherited template that can be added to any nonmindless creature 
that does not already have the psionic subtype (referred to hereafter as the ``base 
creature''). A phrenic creature uses all the base creature's statistics and special 
abilities except as noted here.

\textbf{Size and Type: }The creature's type does not change, unless it is an animal 
(in which case it becomes a magical beast [augmented animal]). It gains the psionic 
subtype.

\textbf{Psi-Like Abilities (Sp): }A phrenic creature possesses the psi-like abilities 
indicated below, depending on its Hit Dice. The abilities are cumulative. Unless 
otherwise noted, an ability is usable once per day. Manifester level is equal to 
the creature's HD. The save DCs for a phrenic creature's psi-like abilities are 
Charisma-based.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
\textbf{HD}\end{minipage}} & \multicolumn{1}{p{3.070in}|}{\begin{minipage}[t]{3.070in}\centering
\textbf{Abilities}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1-2\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
3/day---\textit{defensive precognition; }1/day---\textit{force screen}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
3-4\end{minipage}} & \multicolumn{1}{p{3.070in}|}{\begin{minipage}[t]{3.070in}\centering
3/day---\textit{empty mind, mind thrust}\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
5-6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1/day---\textit{body adjustment, brain lock}\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
7-8\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
1/day---\textit{aversion, blast}\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
9-10\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
3/day---\textit{intellect fortress; }1/day---\textit{psychic crush}\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
11-12\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
1/day---\textit{psionic dominate}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
13-14\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
1/day---\textit{energy current, tower of iron will}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
15-16\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
3/day---\textit{psionic teleport}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
17-18\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
1/day---\textit{fission}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.497in}|}{\begin{minipage}[t]{0.497in}\centering
19-20\end{minipage}} & \multicolumn{3}{p{3.209in}|}{\begin{minipage}[t]{3.209in}\centering
1/day---\textit{ultrablast}\end{minipage}}\\
\hline
\end{longtable}

\textbf{Special Qualities:} A phrenic creature has all the special qualities of 
the base creature, plus the following special qualities.

\textit{Naturally Psionic: }A phrenic creature gains 1 bonus power point.

\textit{Power Resistance (Ex): }A phrenic creature has power resistance equal to 
its Hit Dice +10. 

\textbf{Abilities:} Increase from the base creature as follows: Int +2 (if Int 
is 3 or greater), Wis +2, Cha +4.

\textbf{Feats:} A phrenic creature can take psionic feats, if it meets the prerequisites 
for such feats.

\textbf{Challenge Rating: }Up to 5 HD, same as base creature +1; 6-10 HD, same 
as base creature +2; 11+ HD, same as base creature +3.

\textbf{Level Adjustment:} Same as base creature +2.

\vspace{12pt}
{\LARGE PHTHISIC}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.441in}|}{\begin{minipage}[t]{3.441in}\raggedright
Large Monstrous Humanoid (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
6d8+30 (57 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.441in}|}{\begin{minipage}[t]{3.441in}\raggedright
+5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
18 (-1 size, +1 Dex, +8 natural), touch 10, flat-footed 17\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.047in}|}{\begin{minipage}[t]{0.047in}\raggedright
+6/+16\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Claw +11 melee (1d6+6)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
2 claws +11 melee (1d6+6) and bite +6 melee (1d6+3 plus mind feed)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Mind feed, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Damage reduction 10/magic, darkvision 60 ft., regeneration 5, resistance to cold 
10, scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Fort +9, Ref +6, Will +8\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Str 23, Dex 12, Con 21, Int 10, Wis 16, Cha 16\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Listen +11, Move Silently +7, Spot +11\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Alertness, Great Fortitude, Improved Initiative\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Solitary or gang (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
6\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
Always chaotic evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
7-12 HD (Large); 13-18 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.966in}|}{\begin{minipage}[t]{0.966in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.534in}|}{\begin{minipage}[t]{3.534in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A phthisic stands 10 feet tall and weighs 600 pounds. It vaguely resembles the 
person whose mind the phthisic escaped from, but is severely distorted (someone 
who knows the individual from whom the phthisic sprung can make a DC 25 Spot check 
to note the resemblance).

A phthisic speaks the primary language of the mind that birthed it, usually Common.

\subsubsection*{COMBAT}

\textbf{Mind Feed (Ex): }A phthisic that hits with its bite attack deals 1d4 points 
of Intelligence damage. If this effect reduces the opponent's Intelligence score 
to 0, the ability damage becomes ability drain.

\textbf{Psi-Like Abilities:} 3/day---\textit{brain lock }(affects animals, fey, 
giants, humanoids, magical beasts, and monstrous humanoids, DC 15*), \textit{dimension 
slide}, \textit{ego whip }(1d4, DC 15*)\textit{, mental barrier, mind thrust }(ML 
4th, 4d10\textit{, }DC 15*), \textit{skate; }1/day---\textit{body adjustment }(heal 
1d12*), \textit{catapsi }(DC 18). Manifester level 6th. The save DCs are Charisma-based.

*Includes augmentation for the phthisic's manifester level.

\textbf{Regeneration (Ex): }Fire and acid deal normal damage to a phthisic.

\vspace{12pt}
{\LARGE PSICRYSTAL}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.337in}|}{\begin{minipage}[t]{3.337in}\raggedright
Diminutive Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
As master's HD (hp 1/2 master's)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.337in}|}{\begin{minipage}[t]{3.337in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
30 ft. (6 squares), climb 20 ft.*\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
16 (+4 size, +2 Dex*), touch 16, flatfooted 14\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.051in}|}{\begin{minipage}[t]{0.051in}\raggedright
+0/-17\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
---\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
---\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
1 ft./0 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Construct traits, hardness 8, psicrystal granted abilities (improved evasion, personality, 
self-propulsion, share powers, sighted, telepathic link)\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
As master's saves\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Str 1*, Dex 15*, Con ---, Int 6, Wis 10, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Climb +14*, Listen +6, Move Silently +6, Search +2, Spot +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Alertness\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
Included with master\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
As master\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.439in}|}{\begin{minipage}[t]{3.439in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.061in}|}{\begin{minipage}[t]{1.061in}\raggedright
*With self-propulsion ability activated.\end{minipage}}\\
\hline
\end{longtable}

The psicrystal described here is that of a 1st-level manifester.

\subsubsection*{COMBAT}

A psicrystal's characteristics depend on its master. Its Hit Dice are equal to 
its master's Hit Dice (counting only levels in psion or wilder), its hit points 
are equal to half its master's, and its saving throw bonuses are the same as its 
master's.

\textbf{Construct Traits:} A psicrystal has immunity to poison, \textit{sleep, 
}paralysis, stunning, disease, death effects, necromancy effects, mind-affecting 
effects (charms, compulsions, phantasms, patterns, and morale effects), and any 
effect that requires a Fortitude save unless it also works on objects or is harmless. 
It is not subject to critical hits, nonlethal damage, ability damage, ability drain, 
fatigue, exhaustion, or energy drain. It cannot heal damage, but it can be repaired. 
Psicrystals do not have the usual construct traits of darkvision and low-light 
vision.

\textbf{Psicrystal Granted Abilities:} The psicrystal described here has the special 
abilities of self-propulsion, alertness, improved evasion, share powers, telepathic 
link, sighted, and personality (If its master chooses not to activate the self-propulsion 
ability, the psicrystal reverts to a speed of 0 feet and has no Strength score 
and no Dexterity score.)

\textbf{Skills: }A psicrystal (with its self-propulsion ability activated) uses 
its Dexterity modifier instead of its Strength modifier on Climb checks. It has 
a +8 racial bonus on Climb checks and can always choose to take 10, even if rushed 
or threatened.

\vspace{12pt}
{\LARGE PSION-KILLER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.056in}|}{\begin{minipage}[t]{3.056in}\raggedright
Large Construct\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
15d10+30 (112 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.056in}|}{\begin{minipage}[t]{3.056in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
20 ft. (4 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
28 (-1 size, +19 natural), touch 9, flat-footed 28\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+11/+25\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Slam +20 melee (2d10+10)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
2 slams +20 melee (2d10+10)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Dispel psionics\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Construct traits, damage reduction 10/adamantine, darkvision 60 ft., immunity to 
psionics, lowlight vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Fort +5, Ref +5, Will +5\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Str 31, Dex 10, Con ---, Int ---, Wis 11, Cha 1\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Solitary or gang (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
12\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
16-21 HD (Large); 22-45 (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.318in}|}{\begin{minipage}[t]{1.318in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.182in}|}{\begin{minipage}[t]{3.182in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A psion-killer (also called a crystal golem) is 9-1/2 feet tall and weighs around 
2,500 pounds. Its body is composed of sharply faceted crystal.

\subsubsection*{COMBAT}

A psion-killer does nothing without explicit orders from its creator. It follows 
instructions literally and is incapable of any strategy or tactics. Psion-killers 
don't use weapons, even if ordered to, but always strike with their fists. 

A psion-killer's creator can command it if the psion-killer is within 60 feet and 
can see and hear its creator. If uncommanded, a psion-killer usually follows its 
last instruction to the best of its ability, though if attacked it returns the 
attack. Its creator can give a psion-killer a simple command to govern its actions 
in his or her absence.

\textbf{Dispel Psionics (Su):} A psion-killer can use \textit{dispel psionics }as 
a free action once per round. The effect is as an area dispel in a 30-foot-radius 
burst. The dispel check is 1d20+10.

\textbf{Construct Traits:} A psion-killer has immunity to poison, \textit{sleep 
}effects, paralysis, stunning, disease, death effects, necromancy effects, mind-affecting 
effects (charms, compulsions, phantasms, patterns, and morale effects), and any 
effect that requires a Fortitude save unless it also works on objects or is harmless. 
It is not subject to critical hits, nonlethal damage, ability damage, ability drain, 
fatigue, exhaustion, or energy drain. It cannot heal damage, but it can be repaired.

\textbf{Immunity to Psionics (Ex): }Psion-killers completely resist psionic effects 
that are subject to power resistance.

\subsubsection*{CONSTRUCTION}

A psion-killer's body is constructed from massive blocks of quartz crystal with 
a total weight of at least 5,000 pounds and costing at least 8,000 gp. Assembling 
the body requires a DC 20 Craft (sculpting) check or a DC 20 Craft (stonemasonry) 
check.

ML 16th; Craft Construct, \textit{bend reality}, \textit{dispel psionics}, \textit{fabricate}, 
\textit{mind seed}, manifester must be at least 16th level; Price 150,000 gp; Cost 
79,000 gp + 5,680 XP.

\vspace{12pt}
{\LARGE PUPPETEER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.862in}|}{\begin{minipage}[t]{2.862in}\raggedright
Fine Magical Beast (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1/4 d10 (1 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.862in}|}{\begin{minipage}[t]{2.862in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
5 ft. (1 square)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
20 (+8 size, +2 Dex), touch 20, flat-footed 18\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+1/-20\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Bite +4 melee (1d2-5)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Bite +4 melee (1d2-5)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
1/2 ft./0 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Enthrall, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Blindsight 60 ft., host protection, telepathy 20 ft. \end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Fort +2, Ref +4, Will +5\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Str 1, Dex 15, Con 11, Int 14, Wis 16, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Hide +22, Listen +7, Sense Motive +7, Spot +7\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Iron Will\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Solitary or pack (2-8)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
1\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
Usually lawful evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.001in}|}{\begin{minipage}[t]{3.001in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Puppeteers do not speak, though they can speak indirectly using a host body's vocal 
cords, in whatever language the host knows (usually Common).

\subsubsection*{COMBAT }

Puppeteers use their psionic powers in conjunction with their enthrall ability 
to gain control over potential hosts. Once it is in control, a puppeteer almost 
exclusively relies on the host's mental and physical abilities, although it can 
use its own powers to enhance their effectiveness in a particularly dangerous situation.

\textbf{Enthrall (Ex):} If a puppeteer is in physical contact with a person it 
has charmed (the puppeteer establishes a physical hold by means of slender infiltrating 
tendrils), the subject acts as if dominated. (Puppeteers often seek to charm victims 
first and then ``ask'' to be picked up.) So long as the puppeteer remains in contact 
with the victim, the domination remains in effect, even if a check would normally 
indicate that the effect is broken.

\textbf{Psi-Like Abilities:} 3/day--- \textit{detect psionics, mental barrier, 
psionic charm }(DC 13)\textit{. }Manifester level 1st. The save DCs are Charisma-based.

\textbf{Blindsight (Ex):} A puppeteer can ascertain creatures by nonvisual means 
within 60 feet.

\textbf{Hide Mind (Su):} A puppeteer cannot be identified as psionic by divination 
spells or clairsentience powers.

\textbf{Host Protection (Ex):} A puppeteer in control of a host is treated as an 
attended magic item for the purpose of making saving throws, even if the puppeteer 
is specifically targeted. A puppeteer that is attached to its host is treated as 
a creature in a grapple for the purpose of striking at the puppeteer instead of 
the host (but the host is not considered grappled in turn).

\textbf{Telepathy (Su):} A puppeteer can communicate telepathically with any creature 
within 20 feet that has a language.

\vspace{12pt}
{\LARGE PUPPETEER, FLESH HARROWER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.068in}|}{\begin{minipage}[t]{3.068in}\raggedright
Small Magical Beast (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
3d10+15 (31 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.068in}|}{\begin{minipage}[t]{3.068in}\raggedright
+3\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
20 ft. (4 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
16 (+3 Dex, +3 natural), touch 13, flat-footed 13\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+3/+1\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Bite +6 melee (1d6+2)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Bite +6 melee (1d6+2) and 2 tail blades +1 melee (1d4+1)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Blindsight 60 ft., telepathy 20 ft.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Fort +8, Ref +6, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Str 14, Dex 17, Con 21, Int 11, Wis 12, Cha 12\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Hide +10, Move Silently +6, Listen +6, Spot +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Alertness, Iron Will\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Solitary or cluster (2-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
4-6 HD (Small); 7-9 HD (Medium)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.306in}|}{\begin{minipage}[t]{1.306in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.194in}|}{\begin{minipage}[t]{3.194in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

COMBAT

\textbf{Psi-Like Abilities:} 3/day---\textit{concealing amorpha}, \textit{hustle}, 
\textit{mental barrier; }1/day---\textit{vigor }(+15 hp*). Manifester level 3rd. 

*Includes augmentation for the flesh harrower's manifester level.

\vspace{12pt}
{\LARGE TEMPORAL FILCHER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.305in}|}{\begin{minipage}[t]{3.305in}\raggedright
Large Aberration (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
8d8+16 (52 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.305in}|}{\begin{minipage}[t]{3.305in}\raggedright
+7\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
15 (-1 size, +3 Dex, +3 natural), touch 12, flat-footed 12\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.052in}|}{\begin{minipage}[t]{0.052in}\raggedright
+6/+11\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Claw +6 melee (1d6+1)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
4 claws +6 melee (1d6+1) and bite +1 melee (1d8) and horn +1 melee (1d4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Improved grab, psi-like abilities, time filch\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Darkvision 60 ft.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Fort +4, Ref +5, Will +7\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Str 13, Dex 17, Con 14, Int 7, Wis 12, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Listen +7, Spot +7, Tumble +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Alertness, Dodge, Improved Initiative\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
Usually evil (any)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
9-15 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.090in}|}{\begin{minipage}[t]{1.090in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Temporal filchers do not speak.

\subsubsection*{COMBAT}

\textbf{Improved Grab (Ex):} To use this ability, a temporal filcher must hit a 
creature of Large size or smaller with two claw attacks. It can then attempt to 
start a grapple as a free action without provoking attacks of opportunity. If it 
wins the grapple check, it establishes a hold and uses its time filch ability.

\textbf{Psi-Like Abilities:} At will---\textit{chameleon}, \textit{distract }(DC 
13), \textit{psionic dimension door}, \textit{psionic levitate}, \textit{wall walker; 
}3/ day---\textit{mental barrier}. Manifester level 8th. The save DC is Charisma-based.

\textbf{Time Filch (Su):} If a temporal filcher successfully grapples a Large or 
smaller creature, it latches onto the opponent's body and shifts 7 minutes forward 
in time as a free action. Observers (if any) see the temporal filcher and its prey 
disappear in a shimmer, then reappear 7 minutes later in exactly the orientation 
and condition they left. For the filcher and its prey, no time passes at all. The 
victim must succeed on a Will save (DC 16) or be dazed for 1 round from temporal 
disorientation. The ability is otherwise identical to \textit{time hop }manifested 
by an 8th-level manifester.

\vspace{12pt}
{\LARGE THOUGHT EATER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.033in}|}{\begin{minipage}[t]{3.033in}\raggedright
Small Aberration (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
3d8 (13 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.033in}|}{\begin{minipage}[t]{3.033in}\raggedright
+8\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
40 ft. (8 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
17 (+1 size, +4 Dex, +2 natural), touch 15, flatfooted 13\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
+2/-1\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
+4 melee touch (eat thoughts)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
+4 melee touch (eat thoughts)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Eat thoughts, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Darkvision 60 ft., ethereal jaunt\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Fort +1, Ref +5, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Str 12, Dex 18, Con 11, Int 7, Wis 12, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Hide +10, Listen +5, Spot +5\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Alertness, Improved Initiative\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Ethereal Plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Solitary or group (1-3)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
4-6 HD (Small)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.338in}|}{\begin{minipage}[t]{1.338in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.162in}|}{\begin{minipage}[t]{3.162in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Thought eaters do not speak.

\subsubsection*{COMBAT}

A thought eater can spend a maximum of 10 continuous rounds on the Material Plane 
before its wispy flesh finally dissipates and it falls dead. If badly wounded, 
it escapes to the Ethereal Plane rather than continuing the fight.

\textbf{Eat Thoughts (Su):} A thought eater can drain psionic power points with 
a successful melee touch attack. Each touch drains 6 power points from the opponent 
(or fewer, if the opponent has fewer than 6 points remaining). Against a nonpsionic 
creature or a psionic creature that currently has no power points, this touch attack 
instead deals 1 point of Intelligence damage, which provides nourishment equivalent 
to 6 power points.

A thought eater requires 12 power points per day to survive but will gorge itself 
on weak prey.

\textbf{Psi-Like Abilities:} At will---\textit{detect psionics}, \textit{distract 
}(DC 13), \textit{precognition, psionic daze }(DC 13*)\textit{; }3/day---\textit{thought 
shield. }

Manifester level 3rd. The save DCs are Charisma-based.

*Includes augmentation for the thought eater's manifester level.

\textbf{Ethereal Jaunt (Su): }A thought eater can shift from the Ethereal Plane 
to the Material Plane as part of any move action, and then shift back again as 
a free action. The ability is otherwise identical to the \textit{psionic ethereal 
jaunt }power.

\vspace{12pt}
{\LARGE THOUGHT SLAYER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Huge Aberration (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
14d8+70 (133 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
50 ft. (10 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
23 (-2 size, +1 Dex, +14 natural), touch 9, flatfooted 22\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
+10/+26\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Bite +17 melee (3d6+12)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Bite +17 melee (3d6+12)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
15 ft./15 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Mind-consuming gaze, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Darkvision 60 ft., ethereal jaunt, power resistance 21\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Fort +11, Ref +5, Will +10\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Str 26, Dex 13, Con 21, Int 7, Wis 12, Cha 15\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Climb +12, Jump +20, Listen +7, Spot +8\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Alertness, Cleave, Great Fortitude, Power Attack,\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Weapon Focus (bite)}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Ethereal Plane\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Solitary or pack (2-4)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
13\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
Often chaotic neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
15-28 HD (Huge)\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.340in}|}{\begin{minipage}[t]{1.340in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.160in}|}{\begin{minipage}[t]{3.160in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Thought slayers do not speak.

\subsubsection*{COMBAT}

A thought slayer can spend a maximum of 10 continuous minutes on the Material Plane 
before its wispy flesh finally dissipates and it falls dead. If badly wounded, 
it escapes to the Ethereal Plane rather than continuing the fight.

\textbf{Mind-Consuming Gaze (Su):} Instantly kill (by draining the mind away), 
range 30 feet, Fortitude DC 19 negates. The save DC is Charisma-based. This is 
considered a mind-affecting death effect. If a thought slayer's gaze is met indirectly 
(such as through a mirror or a reflection in water), the opponent does not die 
on a failed save but instead is dazed for 14 rounds. This otherwise is a gaze effect\textit{.}

The gaze cannot affect creatures on the Material Plane while the thought slayer 
remains ethereal, but it can affect ethereal creatures while the thought slayer 
is on the Material Plane.

\textbf{Psi-Like Abilities:} At will---\textit{brain lock }(any nonmindless, DC 
14*), \textit{chameleon}, \textit{detect psionics}, \textit{distract }(DC 13); 
3/day---\textit{body adjustment }(5d12*), \textit{mental barrier }(+6 AC, 2 rounds*)\textit{, 
mind trap }(10 rounds*), \textit{precognition}, \textit{wall walker; }1/day---\textit{escape 
detection. }Manifester level 14th. The save DCs are Charisma-based.

*Includes augmentation for the thought slayer's manifester level.

\textbf{Ethereal Jaunt (Su):} A thought slayer can shift from the Ethereal Plane 
to the Material Plane as part of any move action, and then shift back again as 
a free action. The ability is otherwise identical to the \textit{psionic ethereal 
jaunt }power.

\vspace{12pt}
{\LARGE UDOROOT}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.071in}|}{\begin{minipage}[t]{3.071in}\raggedright
Huge Plant (Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
6d8+18 (45 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.071in}|}{\begin{minipage}[t]{3.071in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
0 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
11 (-2 size, -5 Dex, +8 natural), touch 3, flatfooted 11\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+4/---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
---\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
---\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
15 ft./0 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Double manifest, psi-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Blindsight 60 ft., immunity to electricity, plant traits, resistance to cold 10 
and fire 10\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Fort +8, Ref +4, Will +5\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Str ---, Dex ---, Con 16, Int 4, Wis 13, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Listen +10\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Iron Will, Lightning Reflexes\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Temperate forest\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Solitary or patch (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
5\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
1/5 coins; 50\% goods; 50\% items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
7-16 HD (Huge); 17-18 HD (Gargantuan)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.303in}|}{\begin{minipage}[t]{1.303in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.197in}|}{\begin{minipage}[t]{3.197in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

COMBAT

An udoroot can be killed only if its root is dug up or exposed, then burned, hacked 
apart, or otherwise destroyed. Severing or destroying all six crowns puts the plant 
out of commission, allowing excavation of the helpless root. The crowns are Medium 
objects with a hardness of 5 and 7 hit points. To sever a crown, an opponent must 
use the sunder action. The crowns can also be affected by spells or effects that 
affect an area or targeted by spells that affect an individual target.

An udoroot takes no damage from having a crown severed or destroyed. A severed 
crown dies and can no longer be used to attack, but the udoroot takes no other 
penalties.  As long as the root system remains intact, the crown regrows in about 
a month.

\textbf{Double Manifest (Ex):} An udoroot senses its surroundings and manifests 
its psi-like abilities through its crowns. It can manifest two psi-like abilities 
per round, as long as it has at least two crowns remaining.

\textbf{Psi-Like Abilities:} At will---\textit{energy stun }(electricity, 2d6, 
DC 15*), \textit{false sensory input }(DC 15), \textit{id insinuation }(two targets, 
DC 15*), \textit{mind thrust }(ML 4th, 4d10, DC 14*), \textit{telekinetic force 
}(275 lb., DC 15*), \textit{thought shield }(power resistance 16*); 3/day---\textit{astral 
construct }(3rd level*), \textit{body adjustment, mental barrier. }

Manifester level 6th. The save DCs are Charisma-based. 

An udoroot can use its \textit{body adjustment }power to repair damage to one of 
its crowns, as long as the crown has not been severed or destroyed.

*Includes augmentation for the udoroot's manifester level.

\textbf{Blindsight (Ex): }An udoroot can ascertain all foes by nonvisual means 
within 60 feet. If its crowns are destroyed, it can no longer perceive its surroundings.

\textbf{Plant Traits:} An udoroot is immune to poison, \textit{sleep}, paralysis, 
stunning, polymorphing, and mind-affecting effects (charms, compulsions, phantasms, 
patterns, and morale effects). It is not subject to critical hits.

\vspace{12pt}
{\LARGE UNBODIED}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.006in}|}{\begin{minipage}[t]{3.006in}\raggedright
Medium Monstrous Humanoid (Incorporeal, Psionic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
4d8+4 (22 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.006in}|}{\begin{minipage}[t]{3.006in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
Fly 30 ft. (good) (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
13 (+1 Dex, +2 deflection), touch 13, flatfooted 12\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
+4/---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Incorporeal touch +5 melee (1d6)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Incorporeal touch +5 melee (1d6)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Psionic powers, telekinetic force\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Assume likeness, incorporeal traits, telepathy 100 ft.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Fort +2, Ref +5, Will +6\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Str ---, Dex 13, Con 12, Int 15, Wis 14, Cha 15\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Bluff +10*, Diplomacy +6, Disguise +10*, Intimidate +6, Listen +6, Sense Motive 
+6, Spot +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Overchannel, Wild Talent\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Solitary or illumination (3-6)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
5\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Half standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.362in}|}{\begin{minipage}[t]{1.362in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.138in}|}{\begin{minipage}[t]{3.138in}\raggedright
+4\end{minipage}}\\
\hline
\end{longtable}

An unbodied uses telepathy to communicate with others.

\subsubsection*{COMBAT}

\textbf{Psionic Powers: }An unbodied manifests powers as a 4th-level psion (telepath). 
The save DCs are Intelligence-based. 

\textit{Typical Psion Powers Known }(power points 21, base save DC 12 + power level): 
1st--- \textit{detect psionics, empty mind, mind thrust }(DC 13*), \textit{psionic 
charm }(DC 13*); 2nd---\textit{brain lock }(DC 14), \textit{cloud mind }(DC 14), 
\textit{energy push }(DC 14), \textit{read thoughts }(DC 14).

*Power can be augmented. 

\textbf{Telekinetic Force (Su):} An unbodied can use \textit{telekinetic force 
}(DC 15) as a standard action that does not provoke attacks of opportunity. Manifester 
level 4th. The save DC is Charisma-based.

\textbf{Assume Likeness (Su):} An unbodied can assume the likeness of any Small, 
Medium, or Large creature as a standard action that does not provoke attacks of 
opportunity. Its abilities do not change, but it appears to be that creature, relying 
on its Bluff and Disguise skills to deflect suspicion.

\textbf{Hide Mind (Su): }An unbodied cannot be identified as psionic by divination 
spells or clairsentience powers. 

\textbf{Incorporeal Traits:} An unbodied is harmed only by other incorporeal creatures, 
magic weapons, powers, spells, spell-like abilities, and supernatural abilities. 
It has a 50\% chance to ignore any damage from a corporeal source, except for force 
effects or attacks made with ghost touch weapons. It can pass through solid objects, 
but not force effects, at will. Its attacks ignore natural armor, armor, and shields, 
but deflection bonuses and force effects work normally against them. An incorporeal 
creature always moves silently and cannot be heard with Listen checks if it doesn't 
wish to be.

\textbf{Skills:} An unbodied has a +4 racial bonus on Bluff and Disguise checks. 
*When using its assume likeness ability, an unbodied gets an additional +10 circumstance 
bonus on Disguise checks. If it can read an opponent's mind, it gets a further 
+4 circumstance bonus on Bluff and Disguise checks.

\subsubsection*{UNBODIED AS CHARACTERS}

Unbodied characters possess the following racial traits.---

+2 Dexterity, +2 Constitution, +4 Intelligence, +4 Wisdom, +4 Charisma. As an incorporeal 
creature, an unbodied has no Strength score.---

Medium size.---

An unbodied has a fly speed of 30 feet (good maneuverability).---

Darkvision out to 60 feet.---

Deflection bonus to Armor Class equal to character's Charisma modifier (minimum 
+1).---

Natural Attack: An unbodied can make a melee touch attack to deal 1d6 points of 
damage.---

Special Attacks (see above): Psionic powers, telekinetic force. An unbodied who 
takes levels in psion (telepath) adds its racial manifesting ability and psion 
levels together to determine its power point reserve, manifester level, and powers 
known.---

Special Qualities (see above): Assume likeness, incorporeal traits.---

Racial Hit Dice: An unbodied begins with four levels of monstrous humanoid, which 
provide 4d8 Hit Dice, a base attack bonus of +4, and base saving throw bonuses 
of Fort +1, Ref +4, and Will +4.---

Racial Skills: An unbodied's monstrous humanoid levels give it skill points equal 
to 7 x (2 + Int modifier). Its class skills are Bluff, Diplomacy, Disguise, Intimidate, 
Listen, Sense Motive, and Spot. Unbodied have a +4 racial bonus on Bluff checks 
and Disguise checks. When using its assume likeness ability, an unbodied gets an 
additional +10 circumstance bonus on Disguise checks. If it can read an opponent's 
mind, it gets a further +4 circumstance bonus on Bluff and Disguise checks.---

Racial Feats: An unbodied's monstrous humanoid levels give it two feats.---

Favored Class: Psion (telepath).---

Level Adjustment: +4.

\vspace{12pt}
{\LARGE XEPH}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
Xeph, 1st-Level Warrior\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
Medium Humanoid (Psionic, Xeph)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.241in}|}{\begin{minipage}[t]{3.241in}\raggedright
1d8+1 (5 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
15 (+1 Dex, +3 studded leather, +1 light shield), touch 11, flat-footed 14\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
+1/+1\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Rapier +2 melee (1d6/18-20) or longbow +2 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Rapier +2 melee (1d6/18-20) or longbow +2 ranged (1d8/x3) \end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
---\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Burst, darkvision 60 ft.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Fort +3, Ref +1, Will -1\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Str 11, Dex 13, Con 12, Int 10, Wis 9, Cha 8\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Climb +2, Jump +2\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Weapon Finesse\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Warm forest\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Team (2-4), squad (11-20 plus 2 3rd-level sergeants and 1 leader of 3rd-6th level), 
or band (30-100 plus 150\% noncombatants plus 1 3rd-level sergeant per 10 adults, 
5 5th-level lieutenants, and 3 7th-level captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
1/2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.153in}|}{\begin{minipage}[t]{1.153in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.347in}|}{\begin{minipage}[t]{3.347in}\raggedright
+0\end{minipage}}\\
\hline
\end{longtable}

Xephs speak their own language and Common.

\subsubsection*{COMBAT}

\textbf{Burst (Su):} Three times per day, a xeph can increase his or her speed 
by 10 feet, plus 10 feet per four character levels beyond 1st, to a maximum increase 
of 30 feet at 9th character level and higher. These bursts of speed are considered 
a competence bonus to the xeph's base speed. A burst of speed lasts 3 rounds.

The xeph warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int

10, Wis 9, Cha 8.

\subsubsection*{XEPHS AS CHARACTERS}

Xeph characters possess the following racial traits.----

2 Strength, +2 Dexterity.---

Medium size.---

Xeph base land speed is 30 feet.---

Darkvision out to 60 feet.---

Naturally Psionic: Xephs gain 1 bonus power point at 1st level. ---

+1 racial bonus on saving throws against powers, spells, and spell-like effects.---

Special Qualities (see above): Burst.---

Racial Feats: A xeph character gains feats according to his or her character class.---

Automatic Languages: Xeph, Common.---

Favored Class: Soulknife.---

Level Adjustment: +0.

\end{document}
