%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}
\usepackage{multirow}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsection*{{\LARGE PSIONIC POWERS (A-C)}}

\vspace{12pt}
\section*{Adapt Body}

Psychometabolism

\textbf{Level:} Psion/wilder 5, psychic warrior 5

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 hour/level (D)

\textbf{Power Points:} 9

Your body automatically adapts to hostile environments. You can adapt to underwater, 
extremely hot, extremely cold, or airless environments, allowing you to survive 
as if you were a creature native to that environment. You can breathe and move 
(though penalties to movement and attacks, if any for a particular environment, 
remain), and you take no damage simply from being in that environment. You need 
not specify what environment you are adapting to when you manifest this power; 
simply activate it, and your body will instantly adapt to any hostile environment 
as needed throughout the duration.

You can somewhat adapt to extreme environmental features such as acid, lava, fire, 
and electricity. Any environmental feature that normally directly deals 1 or more 
dice of damage per round deals you only half the usual amount of damage.

\vspace{12pt}
\section*{Affinity Field}

Psychometabolism

\textbf{Level:} Psion/wilder 9

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 20 ft.

\textbf{Area:} 20-ft.-radius emanation, centered on you

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} Fortitude negates (potentially harmless)

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 17

You create an affinity feedback loop with all creatures within the area. While 
the duration lasts, affected creatures take all damage (including ability damage) 
as you do and heal all wounds as you do. Hit points gained or lost persist after 
this power ends.

Creatures in range are also subject to magical and psionic effects of 3rd level 
or lower. Creatures that have an affinity to you gain a saving throw against each 
new power transferred through the \textit{affinity field }as if the power were 
manifested upon them normally. All magical and psionic effects transferred to subjects 
fade at the end of this power's duration, although instantaneous effects remain. 
If you suddenly become immune to a particular effect or power, the effect or power 
to which you are immune cannot be transferred to creatures that have affinity to 
you.

\vspace{12pt}
\section*{Anchored Navigation}

Clairsentience

\textbf{Level:} Seer 4

\textbf{Display:} Material and olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 hour/level

\textbf{Power Points:} 7

You know where you are in relation to a fixed starting point, which is essential 
for setting up a mishap-free \textit{teleport }beacon. While the duration lasts, 
you are aware of your exact distance and route (physical or psychoportive) back 
to a fixed starting point. The ``anchored'' starting point is your exact location 
when you manifest the power. To designate other anchored starting points, you must 
manifest this power multiple times and be present at the desired locations when 
you do so.

You can also retrace your steps through a maze automatically while the power lasts, 
without resorting to a map.

\textit{Anchored navigation }grants you a \textit{mindlink }with one designated 
creature who remains within a 60-foot radius of the starting point, regardless 
of the distance between you and the creature. The use of \textit{anchored navigation 
}is confined to the plane of existence where you manifest it.

\textbf{Augment:} If you spend 6 additional power points, the effect of this power 
extends across all planar boundaries.

\vspace{12pt}
\section*{Animal Affinity}

Psychometabolism

\textbf{Level:} Egoist 2, psychic warrior 2

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 3

You forge a psychometabolic affinity with an idealized animal form, thereby boosting 
one of your ability scores (choose either Strength, Dexterity, Constitution, Intelligence, 
Wisdom, or Charisma). The power grants a +4 enhancement bonus to the ability score 
you choose, adding the usual benefits provided by a high ability bonus. Because 
you are emulating the idealized form of an animal, you also take on minor aspects 
of the animal you choose. If you choose to increase the ability you use to manifest 
powers, you do not gain the benefit of an increased ability score long enough to 
gain any bonus power points for a high ability score, but the save DCs of your 
powers increase for the duration of this power.

\textbf{Augment:} For every 5 additional power points you spend, this power grants 
a +4 enhancement bonus to another ability.

\vspace{12pt}
\section*{Apopsi}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 9

\textbf{Display:} Auditory, material, and visual

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One living psionic creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Fortitude negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 17, XP

By using this power, you delete 1d4 powers permanently from the subject's mind. 
You specify the level of each power, and the DM randomly determines which of the 
subject's powers is actually deleted. \textit{Psychic chirurgery }or \textit{reality 
revision }can be used to restore the lost powers, but it must be performed within 
1 week of losing the powers.

\textit{XP Cost: }50 XP per level of the deleted powers.

\vspace{12pt}
\section*{Assimilate}

Psychometabolism

\textbf{Level:} Psion/wilder 9

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Touch

\textbf{Target:} One living creature touched

\textbf{Duration:} Instantaneous and 1 hour; see text

\textbf{Saving Throw:} Fortitude half

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 17

Your pointing finger turns black as obsidian. A creature touched by you is partially 
assimilated into your form and takes 20d6 points of damage. Any creature reduced 
to 0 or fewer hit points by this power is killed, entirely assimilated into your 
form, leaving behind only a trace of fine dust. An assimilated creature's equipment 
is unaffected.

A creature that is partially assimilated into your form (that is, a creature that 
has at least 1 hit point following your use of this power) grants you a number 
of temporary hit points equal to half the damage you dealt for 1 hour.

A creature that is completely assimilated grants you a number of temporary hit 
points equal to the damage you dealt and a +4 bonus to each of your ability scores 
for 1 hour. If the assimilated creature knows psionic powers, you gain knowledge 
of one of its powers for 1 hour. You gain some semblance of a creature you completely 
assimilate for 1 hour, granting you a +10 bonus on Disguise checks made to appear 
as that creature during that time.

\vspace{12pt}
\section*{Astral Caravan}

Psychoportation

\textbf{Level:} Nomad 3

\textbf{Display:} None

\textbf{Manifesting Time:} 1 hour

\textbf{Range:} Personal

\textbf{Targets:} You and touched willing creatures

\textbf{Duration:} See text

\textbf{Power Points:} 5

You lead a caravan into the Astral Plane, leaving the Material Plane behind. Since 
the Astral Plane touches upon other planes, you can travel astrally to any of these 
other planes as you wish, but only if you know your way (see below).

You can bring other willing creatures with you, provided that these subjects have 
each manifested \textit{astral traveler }and are linked hand to hand with you at 
the time of the \textit{astral caravan'}s manifestation. These fellow travelers 
are dependent upon you and must accompany you at all times. If something happens 
to you during the journey that causes you to break hand-to-hand contact, your companions 
are stranded wherever you leave them. Because the planes are a dangerous place, 
those who lead \textit{astral caravans }usually choose to manifest this power only 
if they have a large party of travelers assembled. Sometimes groups of lower-level 
adventurers may hire you to lead forays beyond the Material Plane.

The \textit{astral caravan }power lasts while you and your fellow travelers maintain 
your original formation, until (1) you reach your intended destination plane, (2) 
you desire to end the power while still traversing the Astral Plane, (3) you or 
anyone traveling with you breaks the hand-to-hand chain connecting the travelers 
for 2 consecutive rounds, or (4) the power is terminated by some outside means, 
such as \textit{dispel psionics}. When the power ends, you and your fellow travelers 
halt in whatever portion of the Astral Plane you happen to be traversing (the Astral 
Plane is in many ways subjective in location; in any event, one place on the Astral 
looks much like any other).

While you are traveling through the Astral Plane, those natives who happen to glimpse 
you and your fellow travelers perceive you to be moving at a speed of 30 feet (you 
can't run), with you flying in the lead and your fellow travelers strung out behind 
you, each linked to the next by one hand.

Depending on your knowledge of the planes, your journey through the subjective 
space that is the Astral Plane may take a longer or shorter period of time. For 
each 24 hours you travel, make a Knowledge (the planes) check. Unless a location 
is particularly hard to find and well guarded, or conversely easy to find and well 
advertised, the average DC for an \textit{astral caravan }journey should be set 
at 20. You cannot take 20 on this check, though you can take 10. Each check may 
be modified by your degree of familiarity with the destination or by some connection 
you have with the place; see the tables below.

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{4.192in}|}{\begin{minipage}[t]{4.192in}\raggedright
\textbf{Destination Knowledge (the planes)}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.139in}|}{\begin{minipage}[t]{0.139in}\raggedright
\textbf{Knowledge}\end{minipage}} & \multicolumn{1}{|p{2.873in}|}{\begin{minipage}[t]{2.873in}\centering
\textbf{Check Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.319in}|}{\begin{minipage}[t]{1.319in}\centering
None*\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
n/a\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Secondhand (you have heard of the destination)\end{minipage}} & \multicolumn{1}{|p{2.873in}|}{\begin{minipage}[t]{2.873in}\centering
-10\end{minipage}}\\
\hline
% ROW 5
\multicolumn{3}{p{1.458in}|}{\begin{minipage}[t]{1.458in}\centering
Firsthand (you have visited before)\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+0\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Familiar (you have visited three or more times)\end{minipage}} & \multicolumn{1}{|p{2.873in}|}{\begin{minipage}[t]{2.873in}\centering
+5\end{minipage}}\\
\hline
% ROW 7
\multicolumn{3}{p{1.458in}|}{\begin{minipage}[t]{1.458in}\centering
*If you have no direct knowledge of your destination, you must have some connection 
to it in order to travel there; see below.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{3.529in}|}{\begin{minipage}[t]{3.529in}\raggedright
\textbf{Knowledge (the planes)}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.139in}|}{\begin{minipage}[t]{0.139in}\raggedright
\textbf{Connection}\end{minipage}} & \multicolumn{1}{|p{2.442in}|}{\begin{minipage}[t]{2.442in}\centering
\textbf{Check Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.087in}|}{\begin{minipage}[t]{1.087in}\centering
Likeness or picture of destination\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Object from destination \end{minipage}} & \multicolumn{1}{|p{2.442in}|}{\begin{minipage}[t]{2.442in}\centering
+4\end{minipage}}\\
\hline
% ROW 5
\multicolumn{3}{p{1.226in}|}{\begin{minipage}[t]{1.226in}\centering
Planar Cartographer's map of destination\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+10\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
Each successful check indicates that you are one step closer to your goal. To finally 
arrive at your location, you must succeed on six checks within a span of 12 days. 
(If you fail to make six successful checks within the first 12 days, you can continue 
to make one check per day until you get the requisite six successes within a span 
of 12 consecutive days). When you successfully make the requisite number of checks, 
the journey ends, and you appear on your chosen plane within 10-1,000 (1d\% x 10) 
miles of your intended destination on that plane.

\textbf{Augment:} If you spend 2 additional power points, this power weaves a quasi-real 
filmy membrane around yourself and all those adjacent to each other in the caravan 
(being linked by hand is not required if this membrane is used). You remain visible 
within the translucent, amorphous enclosure. You can pick up or drop willing passengers, 
easily reaching through the film. Anything you hold is enveloped by the film. Any 
attacks made through the enclosure in either direction have a 25\% miss chance 
due to the rippling membrane.

When you manifest this power in its augmented form, your apparent speed to those 
observing on the Astral Plane is 40 feet, and you can make a Knowledge (the planes) 
check once every 12 hours to attempt to make it to your destination (six successful 
checks within 12 consecutive days still sees you to your desired goal).

\vspace{12pt}
\section*{Astral Construct}

Metacreativity (Creation)

\textbf{Level:} Shaper 1

\textbf{Display:} Visual; see text

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} One created astral construct

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

This power creates one 1st-level astral construct of solidified ectoplasm that 
attacks your enemies. It appears where you designate and acts immediately, on your 
turn. It attacks your opponents to the best of its ability. As a free action, you 
can mentally direct it not to attack, to attack particular enemies, or to perform 
other actions. The astral construct acts normally on the last round of the power's 
duration and dissipates at the end of its turn.

Astral constructs are not summoned; they are created on the plane you inhabit (using 
ectoplasm drawn from the Astral Plane). Thus, they are not subject to effects that 
hedge out or otherwise affect outsiders; they are constructs, not outsiders.

\textbf{Augment:} For every 2 additional power points you spend, the level of the 
astral construct increases by one.

\vspace{12pt}
\section*{Astral Seed}

Metacreativity

\textbf{Level:} Shaper 8

\textbf{Display:} Material; see text

\textbf{Manifesting Time:} 10 minutes

\textbf{Range:} 0 ft.

\textbf{Effect:} One storage crystal

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 15

This power weaves strands of astral ectoplasm into a crystal containing the seed 
of your living mind (hardness 1 and 1 hit point). You can have only one \textit{astral 
seed }in existence at any one time. Until such time as you perish, the \textit{astral 
seed }(also called the storage crystal) is utterly inert. If you are slain at some 
later date, your soul transfers into the storage crystal, which begins to dimly 
glow.

Upon transference, your physical remains (should they still exist) become inert 
matter and cannot thereafter be restored to life. The transfer from the slain body 
to the \textit{astral seed }works over any distance, physical or extradimensional.

Once your body's physical demise activates the storage crystal, you have the abilities 
of a psicrystal of the appropriate level, plus all the powers you knew and the 
maximum power points you possessed when \textit{astral seed }was manifested---but 
you also have a negative level that cannot be healed and that does not convert 
to real level loss in your current crystalline form. You have thirty days to grow 
an organic body, after which time your sentience fades and your soul passes on 
if it hasn't entered a new body.

To grow a body, you (in the storage crystal) must spend ten days in uninterrupted 
solitude. The body's constituent parts are pulled as ectoplasm from the Astral 
Plane, then slowly molded and transformed into a living, breathing body that is 
an exact duplicate of your body at the time you manifested \textit{astral seed 
}(the crystal itself breaks down and becomes a part of the new organic body). When 
the tenth day ends, you completely and totally inhabit the new body. You possess 
all the abilities you possessed when \textit{astral seed }was manifested, at one 
level lower, but you have none of your equipment.

If the body is struck for any amount of damage during the ten-day period when it 
is growing, it is destroyed and your soul passes on.

Conceivably, you could manifest \textit{mind switch }to utilize a temporary body, 
but only an evil creature would smash his own temporarily empty storage crystal 
to permanently usurp a subject's organic body (unless the subject is itself irredeemably 
evil).

\vspace{12pt}
\section*{Astral Traveler}

Psychoportation

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display:} None

\textbf{Manifesting Time:} 1 hour

\textbf{Range:} Touch

\textbf{Target:} Creature touched

\textbf{Duration:} See text

\textbf{Saving Throw:} Will negates (harmless)

\textbf{Power Resistance:} Yes (harmless)

\textbf{Power Points:} 1

This power allows you or a creature you touch to participate in an astral caravan 
created through use of the \textit{astral caravan }power. While participating in 
a journey allowed by the \textit{astral caravan }power, you must hold the hand 
of both your fellow passenger ahead of you (or the caravan leader) and your fellow 
passenger behind you (unless you happen to be the last in the hand-linked line). 
If you or any one of your fellow passengers breaks the hand-to-hand link for 2 
consecutive rounds, the impetus through the Astral Plane provided by \textit{astral 
caravan }fails. See the \textit{astral caravan }power for more information.

All those who are part of the caravan who are capable of performing purely mental 
actions, such as manifesting a power, may do so while maintaining hand-to-hand 
contact with their fellow travelers. When astral travelers begin their journey, 
each one is connected to the Material Plane by an insubstantial silvery cord. Very 
few weapons exist that can damage a silvery cord.

The last creature in the line of those making up the caravan is sometimes referred 
to as the rear guard, because he or she has one hand free and can use it to wield 
a weapon without relinquishing his or her grip on the next traveler in line. The 
weightless, subjective environment of the Astral Plane allows the caravan to flex 
and bend as necessary to bring the rear guard's weapon to bear.

\vspace{12pt}
\section*{Attraction}

Telepathy (Charm) [Mind-Affecting]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} 1 hour/level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 1

You plant a compelling attraction in the mind of the subject. The attraction can 
be toward a particular person or an object. The subject will take reasonable steps 
to meet, get close to, attend, or find the object of its implanted attraction. 
For the purpose of this power, ``reasonable'' means that, while attracted, the 
subject doesn't suffer from blind obsession. He will act on this attraction only 
when not engaged in combat. The subject won't perform obviously suicidal actions. 
He can still recognize danger but will not flee unless the threat is immediate. 
If you make the subject feel an attraction to yourself, you can't command him indiscriminately, 
although he will be willing to listen to you (even if he disagrees). This power 
grants you a +4 bonus on any interaction checks you make involving the subject 
(such as Bluff, Diplomacy, Intimidate, and Sense Motive).

\textbf{Augment:} For every 2 additional power points you spend, this power's save 
DC increases by 1 and the bonus on interaction checks increases by 1.

\vspace{12pt}
\section*{Aura Alteration}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 6

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One willing creature

\textbf{Duration:} 10 min./level or instantaneous; see text

\textbf{Power Points:} 11

You can use this power in one of two ways: to disguise the subject's aura (alignment) 
and level, or to remove a compulsion or charm effect from the subject.

\textit{Disguise: }If you use this power to disguise the subject's alignment and 
level, the power has a duration of 10 minutes per level. You can change the subject's 
alignment by only one step. You can adjust the subject's apparent level up or down 
by a number equal to one-half your own level (rounded down) or less.

\textit{Remove Compulsion: }If you use this power to attempt to cleanse the subject's 
aura of a baleful or controlling effect, the duration is instantaneous. This power 
can remove the compulsion of a curse or a \textit{geas/quest }effect. It can also 
negate any charm and compulsion powers of 6th level or lower, such as \textit{crisis 
of breath }or \textit{death urge. }When \textit{aura alteration }is manifested 
for this purpose, the subject gains another saving throw to remove the compulsion 
afflicting it against the original save DC, but with a +2 bonus.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every additional power point you spend, the duration of the disguise aura 
increases by 10 minutes.

2. If you spend 2 additional power points, the subject's alignment shifts an additional 
step; if you spend 4 additional power points, the subject's alignment changes to 
its opposite.

\vspace{12pt}
\section*{Aura Sight}

Clairsentience

\textbf{Level:} Psion/wilder 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 60 ft.

\textbf{Area:} Cone-shaped emanation centered on you

\textbf{Duration:} Concentration, up to 10 min./level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 7

You discern auras. Auras are invisible to the naked eye, but to a psionic viewer 
manifesting this power they appear as glowing halos or envelopes of colored light 
that surround all objects. The color of each aura reveals information to the psionic 
character. The amount of information revealed depends on how long you study a

particular area.

\textit{1st Round: }Presence of good and evil auras in the area. You can't pin 
an aura to a particular object or individual at this stage; instead, you see a 
colored haze suffusing the area. (This power can detect lawful and chaotic auras 
as well, but doing so requires a separate manifestation that focuses only on that 
alignment axis.)

\textit{2nd Round: }Number of auras (creatures, objects, powers, or spells) in 
the area. You know how many auras are in the area, even though each aura doesn't 
resolve to its actual location quite yet.

\textit{3rd Round: }The owner of each aura is revealed, unless the individual is 
outside your line of sight. If a creature whose aura you detect has 5 or more Hit 
Dice than you do, you are overwhelmed by its presence and dazed for 1 round, and 
the power ends.

\textbf{Augment:} For every 2 additional power points you spend, this power's range 
increases by 5 feet.

\vspace{12pt}
\section*{Aversion}

Telepathy (Compulsion) [Mind-Affecting]

\textbf{Level:} Telepath 2

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} 1 hour/level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

You plant a powerful aversion in the mind of the subject. If the object of the 
implanted aversion is an individual or a physical object, she will prefer not to 
approach within 30 feet of it. If it is a word, she will try not to utter it; if 
it is an action, she will not willingly attempt to perform it; and if it is an 
event, she will not willingly attend it. The subject will take reasonable steps 
to avoid the object of its aversion, but will not put herself in jeopardy by doing 
so.

If the subject is forced into taking an action she has an aversion to, she takes 
a -2 penalty on any attack rolls, ability checks, or skill checks involved.

\textbf{Augment:} For every 2 additional power points you spend, this power's save 
DC increases by 1 and the duration increases by 1 hour.

\vspace{12pt}
\section*{Baleful Teleport}

Psychoportation (Teleportation)

\textbf{Level:} Nomad 5

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One corporeal creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Fortitude half

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 9

You psychoportively disperse minuscule portions of the subject, dealing 9d6 points 
of damage. Targets can be protected from the effects of \textit{baleful teleport 
}by \textit{dimensional anchor}.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d6 points. For each extra 2d6 points of damage, this power's save 
DC increases by 1 and your manifester level increases by 1 for the purpose of overcoming 
power resistance.

\vspace{12pt}
\section*{Banishment, Psionic}

Psychoportation

\textbf{Level:} Nomad 6

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Targets:} One or more extraplanar creatures, no two of which can be more 
than 30 ft. apart

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 11

As the \textit{banishment }spell, except as noted here. 

Psions gain no benefit from presenting objects or substances that the target hates, 
fears, or otherwise opposes.

\textbf{Augment:} For every 2 additional power points you spend, this power's save 
DC increases by 1 and your manifester level increases by 1 for the purpose of overcoming 
power resistance.

\vspace{12pt}
\section*{Bend Reality}

Clairsentience

\textbf{Level:} Psion/wilder 8

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Target, Effect, or Area:} See text

\textbf{Duration:} See text

\textbf{Saving Throw:} None; see text

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 15, XP

\textit{Bend reality }lets you create nearly any type of effect. For example, \textit{bend 
reality }can do any of the following:•

Duplicate any psion power of 6th level or lower, provided the power is not of a 
discipline prohibited to you.•

Duplicate any other power (but not a spell) of 5th level or lower, provided the 
power is not of a discipline prohibited to you.•

Duplicate any psion power of 5th level or lower, even if it's of a prohibited discipline.•

Duplicate any other power (but not a spell) of 4th level or lower, even if it's 
of a prohibited discipline.•

Undo the harmful effects of many powers, such as \textit{psionic dominate, geas/quest, 
}or \textit{insanity}.•

Produce any other effect whose power level is in line with the above effects, such 
as a single creature automatically hitting on its next attack or taking a -8 penalty 
on its next saving throw. 

A duplicated power allows saving throws and power resistance as normal (but the 
save DC is for a 8th-level power).

When \textit{bend reality }duplicates a power that has an XP cost, you must pay 
that cost or 300 XP, whichever is more. When \textit{bend reality }duplicates a 
spell with a material component, you must pay additional XP equal to the value 
of the material component divided by 5.

\textit{XP Cost: }300 XP or more (see above).

\vspace{12pt}
\section*{Bestow Power}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 20 ft.

\textbf{Target:} One psionic creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You link your mind with another psionic creature's mind, creating a brief conduit 
through which mental energy can be shared. When you manifest this power, the subject 
gains up to 2 power points. You can transfer only as many power points to a subject 
as it has manifester levels.

Because of the intimate nature of this power, it cannot be fabricated into a psionic 
item---only power points generated by a psionic creature in the moment can be shared 
using \textit{bestow power}.

\textbf{Augment:} For every 3 additional power points you spend, the subject gains 
2 additional power points.

\vspace{12pt}
\section*{Biofeedback}

Psychometabolism

\textbf{Level:} Psion/wilder 2, psychic warrior 1

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level (D)

\textbf{Power Points:} Psion/wilder 3, psychic warrior 1

You can toughen your body against wounds, lessening their impact. During the duration 
of this power, you gain damage reduction 2/-.

\textbf{Augment:} For every 3 additional power points you spend, your damage reduction 
increases by 1.

\vspace{12pt}
\section*{Bite of the Wolf}

Psychometabolism

\textbf{Level:} Psychic warrior 1

\textbf{Display:} Visual; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 min./level

\textbf{Power Points:} 1

Your posture becomes stooped forward, and you grow a muzzle complete with fangs. 
You gain one bite attack each round, instead of or in addition to any other attacks 
you have, that deals 1d8 points of damage (assuming you are a Medium creature) 
when it hits.

Your bite attack is a natural weapon, so you are considered armed when attacking 
with it, and it can be affected by powers, spells, and effects that enhance or 
improve natural weapons. You can choose to deal nonlethal damage with your bite, 
taking the standard -4 penalty on your attack roll. If you bite as your only attack, 
you use your highest base attack bonus on the attack roll, and you can apply your 
full Strength bonus to damage. If you bite in addition to making other attacks, 
the bite is a secondary attack.

If you are not a Medium creature, your bite attack's base damage varies as follows: 
Fine 1d2, Diminutive 1d3, Tiny 1d4, Small 1d6, Large 2d6, Huge 2d8, Gargantuan 
4d6, Colossal 6d6.

Based on your psychic warrior level, your bite increases in ferocity as noted here: 
at 5th level your bite deals an extra 1d8 points of damage, at 10th level an extra 
2d8, at 15th level an extra 3d8, and at 20th level an extra 4d8 points.

\vspace{12pt}
\section*{Body Adjustment}

Psychometabolism (Healing)

\textbf{Level:} Psion/wilder 3, psychic warrior 2

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

\textbf{Power Points:} Psion/wilder 5, psychic warrior 3

You take control of your body's healing process, curing yourself of 1d12 points 
of damage. As usual, when regular damage is healed, an equal amount of nonlethal 
damage is also healed.

\textbf{Augment:} For every 2 additional power points you spend, this power heals 
an additional 1d12 points of damage.

\vspace{12pt}
\section*{Body Equilibrium}

Psychometabolism

\textbf{Level:} Psion/wilder 2, psychic warrior 2

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level (D)

\textbf{Power Points:} 3

You can adjust your body's equilibrium to correspond with any solid or liquid that 
you stand on. Thus, you can walk on water, quicksand, or even a spider's web without 
sinking or breaking through (this effect does not confer any resistance to particularly 
sticky webs). You can move at your normal speed, but you cannot run (x4 speed) 
on an unfirm surface without sinking or breaking through.

If you fall from any height while using this power, damage from the impact is halved.

\vspace{12pt}
\section*{Body Purification}

Psychometabolism (Healing)

\textbf{Level:} Psion/wilder 3, psychic warrior 2

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 round

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

\textbf{Power Points:} Psion/wilder 5, psychic warrior 3

You restore up to 2 points of damage to a single ability score. You cannot use 
\textit{body purification }to heal ability drain.

\textbf{Augment:} For every additional power point you spend, this power heals 
1 additional point of damage to the same ability score.

\vspace{12pt}
\section*{Bolt}

Metacreativity (Creation)

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 0 ft.

\textbf{Effect:} A normal bolt, arrow, or sling bullet

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

You create 2d4 ectoplasmic crossbow bolts, arrows, or sling bullets, appropriate 
to your size, which dissipate into their constituent ectoplasmic particles when 
the duration ends or after being fired. Ammunition you create has a +1 enhancement 
bonus on attack rolls and damage rolls.

\textbf{Augment:} For every 3 additional power points you spend, this power improves 
the ammunition's enhancement bonus on attack rolls and damage rolls by 1.

\vspace{12pt}
\section*{Brain Lock}

Telepathy (Compulsion) [Mind-Affecting]

\textbf{Level:} Telepath 2

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One humanoid

\textbf{Duration:} Concentration + 1 round

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

The subject's higher mind is locked away. He stands dazed, unable to take any psionic 
actions (including manifesting powers or using psionic feats that require a decision 
to be used) nor any mental actions at all.

A \textit{brain locked }subject is not stunned, so attackers get no special advantage 
against him.

A \textit{brain locked }flyer must descend to the closest safe level area below 
it. An air-breathing swimmer must make for the surface.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. If you spend 2 additional power points, this power can also affect an animal, 
fey, giant, magical beast, or monstrous humanoid.

2. If you spend 4 additional power points, this power can also affect an aberration, 
dragon, elemental, or outsider in addition to the creature types mentioned above.

\vspace{12pt}
\section*{Breath of the Black Dragon}

Psychometabolism [Acid]

\textbf{Level:} Psion/wilder 6, psychic warrior 6

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Area:} Cone-shaped burst centered on you

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Reflex half

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 11

Your mouth spews forth vitriolic acid that deals 11d6 points of acid damage to 
any targets in the area.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d6 points.

\vspace{12pt}
\section*{Burst}

Psychoportation

\textbf{Level:} Nomad 1, psychic warrior 1

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 swift action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round

\textbf{Power Points:} 1

This power increases your land speed by 10 feet. (This adjustment counts as an 
enhancement bonus to speed.)

You can manifest this power with an instant thought, quickly enough to gain the 
benefit of the power on your turn before you move. Manifesting this power is a 
swift action, like manifesting a quickened power, and it counts toward the normal 
limit of one quickened power per round. You cannot manifest this power when it 
isn't your turn.

\vspace{12pt}
\section*{Call to Mind}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 minute

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Instantaneous

\textbf{Power Points:} 1

By meditating on a subject, you can recall natural memories and knowledge otherwise 
inaccessible to you.

On a failed Knowledge check, you can manifest this power to gain a new check with 
a +4 competence bonus. If successful, you instantly recall what was previously 
buried in your subconscious.

\vspace{12pt}
\section*{Call Weaponry}

Psychoportation (Teleportation)

\textbf{Level:} Psychic warrior 1

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 round

\textbf{Range:} 0 ft.

\textbf{Effect:} One weapon; see text

\textbf{Duration:} 1 min./level; see text (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

You call a weapon ``from thin air'' into your waiting hand (actually, it is a real 
weapon hailing from another location in space and time). You don't have to see 
or know of a weapon to call it---in fact, you can't call a specific weapon; you 
just specify the kind. If you call a projectile weapon, it comes with 3d6 nonmagical 
bolts, arrows, or sling bullets, as appropriate. The weapon is made of ordinary 
materials as appropriate for its kind. If you relinquish your grip on the weapon 
you called for 2 or more consecutive rounds, it automatically returns to wherever 
it originated.

Weapons gained by \textit{call weaponry }are distinctive due to their astral glimmer. 
They are considered magic weapons and thus are effective against damage reduction 
that requires a magic weapon to overcome.

\textbf{Augment:} For every 4 additional power points you spend, this power improves 
the weapon's enhancement bonus on attack rolls and damage rolls by 1.

\vspace{12pt}
\section*{Catapsi}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 5, psychic warrior 5

\textbf{Display:} Mental and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 30 ft.

\textbf{Area:} 30-ft.-radius emanation centered on you

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} Will negates; see text

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 9

By manifesting this power, you generate psychic static, interfering with the ability 
of other psionic characters to manifest their powers or use psi-like abilities 
(you are not affected by your own \textit{catapsi }manifestation). All psionic 
activity within the area requires 4 more power points to manifest than normal, 
unless a character makes a Will save each time he attempts to manifest a power. 
Using a psi-like ability becomes a full-round action, instead of a standard action, 
in a \textit{catapsi }field. If two or more fields of \textit{catapsi }overlap, 
the effects are not cumulative.

The limit on the number of power points a subject can spend on a power remains 
in effect; thus, a subject may not be able to manifest its highest-level powers. 
If manifesting a power would cause the manifester to exceed his available power 
points or his spending limits, the manifestation fails automatically, but no power 
points are expended.

\textbf{Augment:} For every 4 additional power points you spend, this power's range 
and the radius of its area both increase by 5 feet.

\vspace{12pt}
\section*{Catfall}

Psychoportation

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 immediate action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} Until landing or 1 round/ level

\textbf{Power Points:} 1

You recover instantly from a fall and can absorb some damage from falling. You 
land on your feet no matter how far you fall, and you take damage as if the fall 
were 10 feet shorter than it actually is. This power affects you and anything you 
carry or hold (up to your maximum load). You can manifest this power with an instant 
thought, quickly enough to gain the benefit of the power while you fall. Manifesting 
the power is an immediate action, like manifesting a quickened power, and it counts 
toward the normal limit of one quickened power per round. You can manifest this 
power even when it isn't your turn.

\textbf{Augment:} For every additional power point you spend, this power reduces 
your damage as if the fall were an additional 10 feet shorter.

\vspace{12pt}
\section*{Chameleon}

Psychometabolism

\textbf{Level:} Egoist 2, psychic warrior 1

\textbf{Display:} Olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 10 min./level (D)

\textbf{Power Points:} 1

Your skin and equipment take on the color and texture of nearby objects, including 
floors and walls. You receive a +10 enhancement bonus on Hide checks.

\vspace{12pt}
\section*{Charm, Psionic}

Telepathy (Charm) [Mind-Affecting]

\textbf{Level:} Telepath 1

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One humanoid

\textbf{Duration:} 1 hour/level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 1

As the \textit{charm person }spell, except as noted here.

\textbf{Augment:} You can augment this power in one or more of the following ways.

1. If you spend 2 additional power points, this power can also affect an animal, 
fey, giant, magical beast, or monstrous humanoid.

2. If you spend 4 additional power points, this power can also affect an aberration, 
dragon, elemental, or outsider in addition to the creature types mentioned above.

3. If you spend 4 additional power points, this power's duration increases to one 
day per level.

In addition, for every 2 additional power points you spend to achieve any of these 
effects, this power's save DC increases by 1.

\vspace{12pt}
\section*{Clairtangent Hand}

Clairsentience (Scrying)

\textbf{Level:} Seer 5

\textbf{Display:} Auditory, mental, and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Area:} See text

\textbf{Duration:} Up to 1 min./level; see text (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 9

You can emulate a \textit{far hand }effect at any distance while simultaneously 
emulating \textit{clairvoyant sense }to target your \textit{far hand; }see the 
appropriate power descriptions. \textit{Clairtangent hand'}s duration is up to 
1 minute per level when used with a \textit{far hand }effect.

\textbf{Augment:} If you spend 8 additional power points, you can emulate \textit{clairvoyant 
sense }in conjunction with either \textit{telekinetic force, telekinetic maneuver, 
}or \textit{telekinetic thrust, }but this power's duration expires as soon as any 
of the noted telekinetic powers deals damage.

\vspace{12pt}
\section*{Clairvoyant Sense}

Clairsentience (Scrying)

\textbf{Level:} Seer 2

\textbf{Display:} Auditory and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} See text

\textbf{Effect:} Psionic sensor

\textbf{Duration:} 1 min./level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You can see and hear a distant location almost as if you were there. You don't 
need line of sight or line of effect, but the locale must be known---a place familiar 
to you or an obvious one, such as behind a door, around a corner, or in a grove 
of trees. Once you have selected the locale, the focus of your \textit{clairvoyant 
sense }doesn't move, but you can rotate it in all directions to view the area as 
desired. Unlike other scrying powers, this power does not allow psionically or 
supernaturally enhanced senses to work through it.

If the chosen locale is magically or psionically dark, you see nothing. If it is 
naturally pitch black, you can see in a 10- foot radius around the center of the 
power's effect or out to the extent of your natural darkvision. The power does 
not work across planes.

\vspace{12pt}
\section*{Claw of Energy}

Psychokinesis [see text]

\textbf{Level:} Psychic warrior 4

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level

\textbf{Power Points:} 7

If you have a claw attack (either from an actual natural weapon or from an effect 
such as \textit{claws of the beast}), you can use this power to energize that weapon. 
The claw attack deals an extra 1d6 points of cold, electricity, or fire damage 
(as chosen by you at the time of manifestation) on a successful hit. On a critical 
hit, it deals an extra 1d10 points of energy damage. If the claw's critical multiplier 
is x3, add 2d10 points of energy damage instead; if the multiplier is x4, add 3d10 
points of energy damage.

This power can be manifested on a claw attack that already deals energy damage, 
but if the claw already deals the same type of damage as the power, the effects 
stack. If this power is manifested on a claw attack already benefiting from the 
effect of the power, the newer manifestation supersedes the older manifestation, 
even if both manifestations are of different energy types.

This power's subtype is the same as the type of energy infused in the natural weapon.

\vspace{12pt}
\section*{Claws of the Beast}

Psychometabolism

\textbf{Level:} Psychic warrior 1

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 swift action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 hour/level

\textbf{Power Points:} see text

You call forth the aggressive nature of the beast inherent in yourself, psionically 
transforming your hands into deadly claws. You gain two natural attacks with your 
claws, each dealing 1d4 points of damage (1d6 if you are Large, or 1d3 if you are 
Small) plus your Strength bonus.

Your claws are natural weapons, so you are considered armed when attacking with 
them, and they can be affected by powers, spells, and effects that enhance or improve 
natural. You can choose to deal nonlethal damage with your claws, taking the standard 
-4 penalty on your attack roll.

Your claws work just like the natural weapons of many monsters. You can make an 
attack with one claw or a full attack with two claws at your normal attack bonus, 
replacing your normal attack routine. You take no penalties for two-weapon fighting, 
and neither attack is a secondary attack. If your base attack bonus is +6 or higher, 
you do not gain any additional attacks---you simply have two claw attacks at your 
normal attack bonus.

You can manifest this power with an instant thought, quickly enough to gain the 
benefit of the power on your turn before you attack. Manifesting this power is 
a swift action, like manifesting a quickened power, and it counts toward the normal 
limit of one quickened power per round. You cannot manifest this power when it 
isn't your turn.

You can call or dismiss the claws as a swift action during the duration of the 
power. If you attack with a manufactured weapon or another natural attack, you 
can't make any claw attacks in that round. You can still hold and manipulate items 
with your claws or cast spells just as well as you could with your hands.

\textbf{Augment:} If you spend additional power points, you can create larger, 
sharper, and more deadly claws, as shown on the table below.

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\multirow{2}{0.617in}{\centering \textbf{Power 
Points}}\end{minipage}} & \multicolumn{3}{p{1.785in}|}{\begin{minipage}[t]{1.785in}\centering
\textbf{Claw Damage}\end{minipage}}\\
\cline{2-4}\cline{6-8}
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\multirow{2}{0.069in}{\centering }\end{minipage}} & \multicolumn{3}{p{0.208in}|}{\begin{minipage}[t]{0.208in}\raggedright
\textbf{Small}\end{minipage}} & \multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.559in}|}{\begin{minipage}[t]{0.559in}\raggedright
\textbf{Large}\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}
% ROW 3
\multicolumn{1}{p{0.722in}|}{\begin{minipage}[t]{0.722in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.505in}|}{\begin{minipage}[t]{0.505in}\raggedright
1d3\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d4\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d6\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d4\end{minipage}} & \multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\raggedright
1d6\end{minipage}} & \multicolumn{1}{p{0.559in}|}{\begin{minipage}[t]{0.559in}\raggedright
1d8\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-8}
% ROW 5
\multicolumn{1}{p{0.722in}|}{\begin{minipage}[t]{0.722in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.505in}|}{\begin{minipage}[t]{0.505in}\raggedright
1d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d8\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
2d6\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-8}
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
7\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1d8\end{minipage}} & \multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\raggedright
2d6\end{minipage}} & \multicolumn{1}{p{0.559in}|}{\begin{minipage}[t]{0.559in}\raggedright
3d6\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-8}
% ROW 7
\multicolumn{1}{p{0.722in}|}{\begin{minipage}[t]{0.722in}\centering
11\end{minipage}} & \multicolumn{5}{p{0.783in}|}{\begin{minipage}[t]{0.783in}\raggedright
2d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
3d6\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
4d6\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-8}
% ROW 8
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
15\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
3d6\end{minipage}} & \multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\raggedright
4d6\end{minipage}} & \multicolumn{1}{p{0.559in}|}{\begin{minipage}[t]{0.559in}\raggedright
5d6\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-8}
% ROW 9
\multicolumn{1}{p{0.722in}|}{\begin{minipage}[t]{0.722in}\centering
19\end{minipage}} & \multicolumn{5}{p{0.783in}|}{\begin{minipage}[t]{0.783in}\raggedright
4d6\end{minipage}} & \multicolumn{1}{|p{0.617in}|}{\begin{minipage}[t]{0.617in}\raggedright
5d6\end{minipage}} & \multicolumn{1}{p{0.559in}|}{\begin{minipage}[t]{0.559in}\raggedright
6d6\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\section*{Claws of the Vampire}

Psychometabolism

\textbf{Level:} Psychic warrior 3

\textbf{Display:} Material and visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level

\textbf{Power Points:} 5

If you have a claw attack (either from an actual natural weapon or from an effect 
such as \textit{claws of the beast}), you can use this power to change the nature 
of that weapon. When this power is manifested, your claws take on an ominous glimmer. 
Each time you make a successful claw attack against a living creature of Small 
or larger size, you are healed of some amount of damage.

You heal a number of hit points equal to half the base damage dealt by your \textit{claws 
of the vampire, }rounded down (additional damage dealt because of a high Strength 
score or other enhancements does not count toward the amount you heal). You heal 
as many hit points as can be gained while the creature remains at 1 hit point or 
higher. Any damage that would reduce the creature to 0 or fewer hit points does 
not benefit you.

You do not heal damage if your attack deals nonlethal damage, such as when you 
attack a creature that has the regeneration ability. Moreover, you gain no healing 
from attacking any creature that is under the effect of \textit{biofeedback}. Using 
\textit{fission }on yourself and then attacking your duplicate also fails to grant 
any healing.

\vspace{12pt}
\section*{Cloud Mind}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} None

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. +5 ft./2 levels)

\textbf{Target:} One creature

\textbf{Duration:} 1 min./level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

You make yourself completely undetectable to the subject by erasing all awareness 
of your presence from its mind. This power has the following effects.

First, you are invisible and inaudible to the creature. It cannot even detect your 
presence by means of blindsense, blindsight, scent, or tremorsense. It cannot pinpoint 
your location by any means.

Second, the subject remains unaware of your actions, provided you do not make any 
attacks or cause any obvious or directly threatening changes in the subject's environment. 
If you attack the subject creature, the effect ends.

If you take an action that creates a sustained and obvious change in the subject's 
environment---for example, attacking a creature aside from the subject or moving 
a large or attended object the subject can see---the subject immediately gains 
a new saving throw against the power. An ally of the subject creature that is able 
to see or perceive you can use a move action to warn the subject and thereby grant 
it a new saving throw.

\vspace{12pt}
\section*{Cloud Mind, Mass}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 6

\textbf{Target:} One creature/level

\textbf{Power Points:} 11

As \textit{cloud mind, }except as noted above. Each creature is affected individually.

\vspace{12pt}
\section*{Compression}

Psychometabolism

\textbf{Level:} Psychic warrior 1

\textbf{Display:} Olfactory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} 1 round/level (D)

\textbf{Power Points:} 1

This power causes instant diminution, halving your height, length, and width and 
dividing your weight by 8. This decrease changes your size category to the next 
smaller one. You gain a +2 size bonus to Dexterity, a -2 size penalty to Strength 
(to a minimum effective Strength score of 1), a +1 size bonus on attack rolls, 
and a +1 size bonus to Armor Class due to your reduced size. If your new size is 
Tiny, you have a space of 2 1/2 feet and a natural reach of 0 feet (meaning that 
you must enter an opponent's square to attack). If your new size is Diminutive, 
you have a space of 1 foot and a natural reach of 0 feet. This power doesn't change 
your speed. 

All your equipment, worn or carried, is similarly reduced by the power. Melee and 
projectile weapons deal less damage. Other psionic or magical properties are not 
affected by this power. Any affected item that leaves your possession (including 
a projectile or thrown weapon) instantly returns to its normal size. This means 
that thrown weapons deal their normal damage (projectiles deal damage based on 
the size of the weapon that fired them). Multiple effects that reduce size do not 
stack, which means (among other things) that you can't use a second manifestation 
of this power to further reduce yourself.

\textbf{Augment:} You can augment this power in one or more of the following ways.

1. If you spend 6 additional power points, this power decreases your size by two 
size categories. You gain a +4 size bonus to Dexterity, a -4 size penalty to Strength 
(to a minimum effective Strength score of 1), a +2 size bonus on attack rolls, 
and a +2 size bonus to Armor Class due to your reduced size.

2. If you spend 6 additional power points, you can manifest this power as a swift 
action instead of a standard action.

3. If you spend 2 additional power points, this power's duration is 1 minute per 
level rather than 1 round per level.

\vspace{12pt}
\section*{Conceal Thoughts}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 1, psychic warrior 1

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Target:} One willing creature

\textbf{Duration:} 1 hour/level

\textbf{Saving Throw:} Will negates (harmless)

\textbf{Power Resistance:} Yes (harmless)

\textbf{Power Points:} 1

You protect the subject's thoughts from analysis. While the duration lasts, the 
subject gains a +10 circumstance bonus on Bluff checks against those attempting 
to discern its true intentions with Sense Motive. It also gains a +4 bonus on its 
saving throw against any power or spell used to read its mind (such as \textit{read 
thoughts }or \textit{mind probe}).

\vspace{12pt}
\section*{Concealing Amorpha}

Metacreativity (Creation)

\textbf{Level:} Psion/wilder 2, psychic warrior 2

\textbf{Display:} Material; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} 0 ft.

\textbf{Effect:} Quasi-real amorphous film centered on you

\textbf{Duration:} 1 min./level (D)

\textbf{Power Points:} 3

Using \textit{concealing amorpha, }you weave a quasi-real membrane around yourself. 
You remain visible within the translucent, amorphous enclosure. This distortion 
grants you concealment (opponents have a 20\% miss chance), thanks to the rippling 
membrane encasing your form. You can pick up or drop objects, easily reaching through 
the film. Anything you hold is enveloped by the amorpha. Likewise, you can engage 
in melee, make ranged attacks, and manifest powers without hindrance.

\vspace{12pt}
\section*{Concealing Amorpha, Greater}

Metacreativity (Creation)

\textbf{Level:} Shaper 3, psychic warrior 3

\textbf{Duration:} 1 round/level (D)

\textbf{Power Points:} 5

As \textit{concealing amorpha}, except the quasi-real membrane so distorts your 
image and actual position that you gain total concealment (opponents have a 50\% 
miss chance), but for a shorter period of time.

\vspace{12pt}
\section*{Concussion Blast}

Psychokinesis [Force]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature or object

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 3

A subject you select is pummeled with telekinetic force for 1d6 points of force 
damage. You can choose to have the power deal an equal amount of nonlethal damage 
instead. \textit{Concussion blast }always affects a subject within range that you 
can see, even if the subject is in melee or has cover or concealment (you cannot 
use this power against creatures with total cover or total concealment).

Nonmagical, unattended objects (including doors, walls, locks, and so on) may also 
be damaged by this power.

\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every 2 additional power points you spend, this power's damage increases 
by 1d6 points.

2. For every 2 additional power points you spend, this power can affect an additional 
target. Any additional target cannot be more than 15 feet from another target of 
the power.

\vspace{12pt}
\section*{Contingency, Psionic}

Clairsentience

\textbf{Level:} Psion/wilder 6

\textbf{Display:} Olfactory

\textbf{Manifesting Time:} 10 minutes or longer; see text

\textbf{Range:} Personal

\textbf{Target:} You

\textbf{Duration:} One day/level (D) or until discharged

\textbf{Power Points:} 11, XP

You can place another power upon your person so that it comes into effect under 
some condition you dictate when manifesting \textit{psionic contingency}. The \textit{psionic 
contingency }power and the companion power are manifest at the same time. The 10-minute 
manifesting time is the minimum total for both manifestations; if the companion 
power has a manifesting time longer than 10 minutes, use that instead. The power 
to be brought into effect by the \textit{psionic contingency }must be one that 
affects your person and be of a power level no higher than one-third your manifester 
level (rounded down, maximum 6th level).

The conditions needed to bring the power into effect must be clear, although they 
can be general. In all cases, the \textit{psionic contingency }immediately brings 
into effect the companion power, the latter being ``manifested'' instantaneously 
only when the prescribed circumstances occur. If complicated or convoluted conditions 
are prescribed, the power combination (\textit{psionic contingency }and the companion 
power) may fail when called on.

You can use only one \textit{psionic contingency }companion power at a time; if 
a second is manifested, the first one (if still active) is dismissed.

\textit{XP Cost: }15 XP.

\vspace{12pt}
\section*{Control Air}

Psychokinesis

\textbf{Level:} Kineticist 2

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Long (400 ft. + 40 ft./level)

\textbf{Area:} 50-ft.-radius spread

\textbf{Duration:} Concentration, up to 1 min./level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You have some control over wind speed and direction. The speed of the wind within 
the area of this power can be increased or decreased by up to 10 miles per hour.

You can spend as many as 5 additional power points to augment this power, with 
each point allowing you to modify the wind speed by an additional 10 miles per 
hour, to a maximum change in wind speed of 60 miles per hour.

This power also gives you the ability to alter the direction of the wind by as 
much as 90 degrees.

Powerful enough winds can cause creatures to be blown away, knocked down, or checked.

\textbf{Augment:} See above.

\vspace{12pt}
\section*{Control Body}

Psychokinesis

\textbf{Level:} Kineticist 4

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Target:} One Medium or smaller creature with humanoid physiology

\textbf{Duration:} Concentration, up to 1 min./level

\textbf{Saving Throw:} Fortitude negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 7

You psychokinetically control the actions of any humanoid (including undead or 
outsiders with a humanoid physiology) that is within range and to which you have 
line of sight. \textit{Control body }doesn't require mental contact with the subject, 
since you are actually forcing limb movements independent of the target's mind. 
You can force the subject to stand up, sit down, walk, turn around, and so on, 
but operating the vocal cords is too difficult. You can also hold the subject immobile, 
rendering it helpless. You cannot force the subject to manifest powers, cast spells, 
or use any special ability that is not a function of just its body movements. If 
you lose line of sight to the subject, the effect of this power ends.

If you force the subject to engage in combat, its attack bonus is equal to your 
base attack bonus + your Intelligence bonus, and its bonus on damage rolls is equal 
to your Intelligence bonus. A subject of this power cannot make attacks of opportunity. 
The subject gains no benefit to Armor Class from its Dexterity, but it does gain 
a bonus to its AC equal to your Intelligence bonus.

Although the subject's body is under your control, the subject's mind is not. Creatures 
capable of taking purely mental actions (such as manifesting powers) can do so.

\textbf{Augment:} For every 2 additional power points you spend, this power can 
affect a target one size category larger.

\vspace{12pt}
\section*{Control Flames}

Psychokinesis [Fire]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Area:} One nonmagical fire source; see text

\textbf{Duration:} Concentration, up to 1 min./level

\textbf{Saving Throw:} See text

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

You pyrokinetically control the intensity or movements of one fire source. A nonmagical 
fire source can be controlled if it is equal to or smaller than the maximum size 
of fire you can control according to your manifester level, as noted on the accompanying 
table. You can freely switch control between fire sources, or change the nature 
of your control, while you maintain concentration, but only one specified change 
(keeping a fire burning, animating it, or altering its size) can be made to one 
fire source in a round. When your control over a fire source lapses, that fire 
immediately returns to its original state (or goes out if it has no fuel or has 
been moved away from its original location). With this power, you can artificially 
keep a fire burning that would normally expire for lack of fuel; even dousing a 
controlled flame with water does not put it out (though completely submerging the 
flame would). Normally, a creature at risk of catching on fire can avoid this fate 
by making a DC 15 Reflex saving throw, with success indicating that the fire has 
gone out. If the fire is one that has been kept burning by the use of \textit{control 
flames, }then the DC of the Reflex save needed to put out the flames increases 
to 25.

This power also enables you to make a fire move as if it were a living creature. 
You can animate only a naturally burning fire; if you attempt to animate one that 
has been increased or decreased in size by your augmentation of this power, the 
fire immediately returns to its original size. An animated fire moves at a speed 
of 30 feet. A fire that moves away from its fuel or its original location dies 
as soon as your control over it lapses. 

An animated fire can enter any square, even if a creature already occupies it. 
If an animated fire enters a square occupied by a creature, that creature can make 
a Reflex save to get out of the way (DC 11 + the number of dice of damage the fire 
does + your Int modifier if you are a psion or your Cha modifier if you are a wilder). 
A successful Reflex save moves the creature to the nearest unoccupied square. The 
flames deal the indicated damage to any creature that is either on fire or surrounded 
by the flames (in the fire's space); see the accompanying table).

At the start of your turn, the animated fire deals damage to any creature in its 
space, and the creature catches on fire unless it makes a Reflex save (DC as noted 
above). A victim on fire takes 1d6 points of damage each round. Additional rounds 
in the same space as the animated fire occupies mean additional chances of ignition. 
The damage from multiple normal fires stacks, but the victim gets a saving throw 
each round to negate each fire. It is possible to switch control from the animated 
fire (causing it to disappear) to intensify f lames that are already burning (thus 
denying the foe Ref lex saves after the first).

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.258in}|}{\begin{minipage}[t]{4.258in}\raggedright
\textbf{Control Flames}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.242in}|}{\begin{minipage}[t]{0.242in}\raggedright
\textbf{Manifester Level }\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
\textbf{Fire Size }\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
\textbf{Example }\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
\textbf{Maximum Damage per Round}\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
\textbf{Space}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.259in}|}{\begin{minipage}[t]{1.259in}\centering
1st-2nd\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Fine\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Tindertwig\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
1 foot square\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
3rd-4th\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Diminutive\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Torch\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
1d3\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
1 foot square\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{1.259in}|}{\begin{minipage}[t]{1.259in}\centering
5th-6th\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Tiny\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Small campfire\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
1d6\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
1 foot square\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
7th-8th\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Small\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Large campfire\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
2d6\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
1 foot square\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.501in}|}{\begin{minipage}[t]{1.501in}\centering
9th-10th\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Medium\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\raggedright
Forge\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
3d6\end{minipage}} & \multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
1 foot square\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.048in}|}{\begin{minipage}[t]{0.048in}\centering
11th-12th\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Large\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Bonfire\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
4d6\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
2-by-2-foot square\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.501in}|}{\begin{minipage}[t]{1.501in}\centering
13th-14th\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Huge\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Burning shack\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
5d6\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
3-by-3-foot square\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.501in}|}{\begin{minipage}[t]{1.501in}\centering
15th-16th\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Gargantuan\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Burning tavern\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
6d6\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
4-by-4-foot square\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.501in}|}{\begin{minipage}[t]{1.501in}\centering
17th or higher\end{minipage}} & \multicolumn{1}{|p{0.807in}|}{\begin{minipage}[t]{0.807in}\raggedright
Colossal\end{minipage}} & \multicolumn{1}{p{0.557in}|}{\begin{minipage}[t]{0.557in}\raggedright
Burning inn\end{minipage}} & \multicolumn{1}{p{0.699in}|}{\begin{minipage}[t]{0.699in}\centering
7d6\end{minipage}} & \multicolumn{1}{p{0.936in}|}{\begin{minipage}[t]{0.936in}\centering
5-by-5-foot square\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\textbf{Augment:} You can augment this power in one or both of the following ways.

1. For every 2 additional power points you spend, you can increase the size of 
a fire you want to control by one step, up to the maximum size of fire you can 
control according to your manifester level.

2. For every 2 additional power points you spend, you can decrease the size of 
a fire you want to control by one step. You can reduce a Tiny or smaller fire to 
nothing, extinguishing it.

\vspace{12pt}
\section*{Control Light}

Psychokinesis [Light]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Visual

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./level)

\textbf{Area:} Nine 10-ft. cubes + three 10-ft. cubes/level

\textbf{Duration:} Concentration, up to 1 min./level, or 1 round; see text

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

By manipulating the ambient light level, you can decrease or increase the illumination 
of an area. The change in illumination can be gradual (taking as long as 1 minute) 
or sudden (occurring immediately when you manifest this power). You can alter the 
level of illumination from its original level at any time during the power's duration.

\textit{Decrease: }You can decrease the illumination of an area by as little as 
5\% (barely perceptible) or as much as 100\% (total darkness). If you decrease 
the light by 50\% or more, the visual ability of creatures that depend on light 
to see declines accordingly.If you decrease the ambient light in an area by 100\%, 
even those with lowlight vision are unable to see within the affected area. For 
each 25\% decrease in ambient light, characters in the area gain a cumulative +1 
circumstance bonus on Hide checks (to a maximum of +4 when all the light is gone).

\textit{Increase: }You can increase the illumination of an area by as little as 
5\% (barely perceptible) or as much as 100\%. If you increase the light by 50\% 
or more, the visual ability of creatures that depend on light to see improves accordingly.

You can use this power to increase the illumination of an area by 200\%  (improving 
visual abilities accordingly), but in such a case the power's duration is only 
1 round.

\vspace{12pt}
\section*{Control Object}

Psychokinesis

\textbf{Level:} Kineticist 1

\textbf{Display:} Material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One unattended object weighing up to 100 lb.

\textbf{Duration:} Concentration, up to 1 round/level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

You telekinetically ``bring to life'' an inanimate object. Though it is not actually 
alive, the object moves under your control. Live vegetation cannot be controlled 
in this fashion, nor can already animated objects or undead. The controlled object 
moves like a puppet, with jerky and clumsy movements, at a speed of up to 20 feet. 
If its form is rigid, it makes creaking, groaning, or grating sounds as you control 
it.

A controlled object can attack an opponent if you direct it to do so. It has one 
slam attack, at a base attack bonus equal to your base attack bonus plus your Intelligence 
modifier. If the attack hits, it deals points of damage equal to 1d6 plus your 
Intelligence modifier. A controlled object has its usual hardness and hit points.

You can use this power on a nonmagical lock, making it move in such a way as to 
attempt to unlock itself. If another character makes an Open Lock check involving 
a lock that you are concentrating on controlling, the character gains a +4 bonus 
on the check.

\vspace{12pt}
\section*{Control Sound}

Psychokinesis [Sonic]

\textbf{Level:} Psion/wilder 2

\textbf{Display:} Auditory; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One sound or mixture of related sounds

\textbf{Duration:} Concentration, up to 1 min./level; see text

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 3

You shape and alter existing sounds. You can target one sound, such as a person 
speaking or singing, or a group of related sounds, such as the patter of many raindrops 
or the tramp of soldiers passing by. A sound as quiet as a snapping finger can 
be controlled. You can substitute any sound you have heard for the target sound. 
If you attempt to exactly duplicate the voice of a specific individual, or an inherently 
terrifying sound (such as a dragon's roar), you must succeed on a Bluff check with 
a +5 circumstance bonus opposed by the intended listener's Sense Motive check to 
avoid arousing suspicion.

You can entirely muffle a noise or magnify a sound to such loudness that it drowns 
out all other conversation in the immediate area. In this way, you can provide 
yourself or any with a +4 circumstance bonus on Move Silently and Listen checks.

Alternatively, you can use up the power in an instant. You do this by modulating 
a sound into a one-time destructive impetus that shatters nonmagical/nonpsionic, 
unattended objects of crystal, glass, ceramics, or porcelain (vials, bottles, flasks, 
jugs, mirrors, and so forth) in the area.

\vspace{12pt}
\section*{Co-Opt Concentration}

Telepathy (Compulsion) [Mind-Affecting]

\textbf{Level:} Psion/wilder 6

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature

\textbf{Duration:} Concentration, up to 1 round/level

\textbf{Saving Throw:} Will negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 11

You take over control of a power that was manifested by the subject and that must 
be maintained through concentration. Once you wrest control of the power from the 
subject, you have

several options.•

Allow the power to function as normal.•

Keep the power targeted on the subject (if a personal power) but decide how the 
power fulfills its function each round.•

Retarget the power on yourself (if a personal power).•

Choose not to concentrate on the co-opted power in the next round, ending the power 
at that point.

When the duration of \textit{co-opt concentration }expires, the power you took 
control of ends (even if this would mean that the power ends earlier than normal).

\vspace{12pt}
\section*{Correspond}

Telepathy [Mind-Affecting]

\textbf{Level:} Psion/wilder 4

\textbf{Display:} Mental

\textbf{Manifesting Time:} 10 minutes

\textbf{Range:} See text

\textbf{Target:} One creature with an Intelligence score of 3 or higher

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 7

You forge a passive mental link with a creature with which you have previously 
had physical or mental contact. The subject need not be within sight or even on 
the same plane as you are. The subject recognizes you, and you can mentally communicate 
with it for the duration (though nothing forces the subject to respond to you), 
exchanging messages of twenty-five words or less once per round. Receiving a message 
is not an action and does not provoke attacks of opportunity; however, sending 
a message is equivalent to a standard action that can provoke attacks of opportunity.

\vspace{12pt}
\section*{Create Sound}

Metacreativity (Creation) [Sonic]

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Auditory; see text

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} Sounds; see text

\textbf{Duration:} 1 round/level (D)

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

You create a volume of sound that rises, recedes, approaches, or remains at a fixed 
place. You choose what type of sound the power creates when manifesting it and 
cannot thereafter change its basic character. The volume of sound created, however, 
depends on your level. You can produce as much noise as four normal humans per 
manifester level (maximum twenty humans). Thus, talking, singing, shouting, walking, 
marching, or running sounds can be created. The noise produced can be virtually 
any type of sound within the volume limit. A horde of rats running and squeaking 
is about the same volume as eight humans running and shouting. A roaring lion is 
equal to the noise from sixteen humans, while a roaring dire lion is equal to the 
noise from twenty humans.

If you wish to create a specific message, up to twenty-five words can be created, 
and those words repeat over and over until the duration expires or the power is 
dismissed. If you attempt to exactly duplicate the voice of a specific individual 
or an inherently terrifying sound (such as a dragon's roar), you must succeed on 
a Bluff check with a +2 circumstance bonus opposed by the listener's Sense Motive 
check to avoid arousing suspicion.

\textit{Create sound }can be used to bring sounds into existence that you later 
manipulate by manifesting \textit{control sound.}

\vspace{12pt}
\section*{Crisis of Breath}

Telepathy (Compulsion) [Mind-Affecting]

\textbf{Level:} Telepath 3

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One breathing humanoid

\textbf{Duration:} 1 round/level

\textbf{Saving Throw:} Will negates, Fortitude partial; see text

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 5

You compel the subject to purge its entire store of air in one explosive exhalation, 
and thereby disrupt the subject's autonomic breathing cycle. The subject's lungs 
do not automatically function again while the power's duration lasts.

If the target succeeds on a Will save when \textit{crisis of breath }is manifested, 
it is unaffected by this power. If it fails its Will save, it can still continue 
to breathe by taking a standard action in each round to gasp for breath.

An affected creature can attempt to take actions normally (instead of consciously 
controlling its breathing), but each round it does so, beginning in the round when 
it failed its Will save, the subject risks blacking out from lack of oxygen. It 
must succeed on a Fortitude save at the end of any of its turns in which it did 
not consciously take a breath. The DC of this save increases by 1 in every consecutive 
round after the first one that goes by without a breath; the DC drops back to its 
original value if the subject spends an action to take a breath.

If a subject fails a Fortitude save, it is disabled (0 hp). In the following round, 
it drops to -1 hit points and is dying. Curing powers or spells can revive a dying 
subject normally, so long as this power's duration has expired; if the power is 
still in effect, a revived creature is still subject to Fortitude saves in each 
round when it does not consciously breathe.

\textbf{Augment:} You can augment this power in one or more of the following ways.

1. If you spend 2 additional power points, this power can also affect an animal, 
fey, giant, magical beast, or monstrous humanoid.

2. If you spend 4 additional power points, this power can also affect an aberration, 
dragon, elemental, or outsider in addition to the creature types mentioned above.

3. If you spend 6 additional power points, this power can affect up to four creatures 
all within a 20-ft.-radius burst.

In addition, for every 2 additional power points you spend to achieve any of these 
effects, this power's save DC increases by 1.

\vspace{12pt}
\section*{Crisis of Life}

Telepathy [Mind-Affecting, Death]

\textbf{Level:} Telepath 7

\textbf{Display:} Mental

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One creature

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} Fortitude partial; see text

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 13

You interrupt the subject's autonomic heart rhythm, killing it instantly on a failed 
saving throw if it has 11 Hit Dice or less. If the target makes its saving throw 
or has more than 11 Hit Dice, it takes 7d6 points of damage.

\textbf{Augment:} For every additional power point you spend, this power can kill 
a subject that has Hit Dice equal to 11 + the number of additional points.

\vspace{12pt}
\section*{Crystal Shard}

Metacreativity (Creation)

\textbf{Level:} Psion/wilder 1

\textbf{Display:} Auditory and material

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Close (25 ft. + 5 ft./2 levels)

\textbf{Effect:} Ray

\textbf{Duration:} Instantaneous

\textbf{Saving Throw:} None

\textbf{Power Resistance:} No

\textbf{Power Points:} 1

Upon manifesting this power, you propel a razor-sharp crystal shard at your target. 
You must succeed on a ranged touch attack with the ray to deal damage to a target. 
The ray deals 1d6 points of piercing damage.

\textbf{Augment:} For every additional power point you spend, this power's damage 
increases by 1d6 points.

\vspace{12pt}
\section*{Crystallize}

Metacreativity

\textbf{Level:} Shaper 6

\textbf{Display:} Auditory

\textbf{Manifesting Time:} 1 standard action

\textbf{Range:} Medium (100 ft. + 10 ft./ level)

\textbf{Target:} One living creature

\textbf{Duration:} Permanent

\textbf{Saving Throw:} Fortitude negates

\textbf{Power Resistance:} Yes

\textbf{Power Points:} 11

You seed the subject's flesh with supersaturated crystal. In an eyeblink, the subject's 
form seems to freeze over, as its flesh and fluids are instantly crystallized. 
Following the application of this power, the subject appears lifeless. In fact, 
it is not dead (though no life can be detected with powers or spells that detect 
such).

This power has a chance of being dispelled only by a manifester of a higher level 
than you when you manifested this power. When the power is dispelled, crystal melts 
back into flesh, and the subject is in exactly the state he was prior being affected 
by \textit{crystallize.}

\end{document}
