%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsubsection*{{\LARGE PSIONIC ITEMS}}

\vspace{12pt}
USING ITEMS

To use a psionic item, it must be activated, although sometimes activation is accomplished 
simply by picking up an item or putting it on. Some items, once they are carried 
or worn, function constantly. In most cases, using an item requires a standard 
action that does not provoke attacks of opportunity. By contrast, power completion 
items (see below) are treated just like powers in combat and do provoke attacks 
of opportunity.

Activating a psionic item is a standard action unless the item description indicates 
otherwise. The manifesting time of a power is the time required to activate the 
same power in an item, whether it's a power stone, a dorje, or a psionic tattoo, 
unless the item description specifically states otherwise.

The four ways to activate psionic items are described below.

\textbf{Power Completion:} This is the activation method for power stones. A power 
stone holds a power that is mostly finished. All that's left to do is perform the 
short, simple, finishing parts of the manifestation (the final mental coda, as 
it were). To use a power completion item safely, a character must be of high enough 
level in the appropriate class to manifest the power already. If he can't already 
manifest the power, there's a chance he'll make a mistake (see Brainburn in the 
power stone description). Activating a power completion item is a standard action 
and provokes attacks of opportunity exactly as manifesting a power does.

Powers stored in power completion items are usually not augmented, because the 
manifester level of such an item is assumed to be the minimum necessary to manifest 
the stored power. However, an item's description may specify otherwise (some power 
stones have manifester levels higher than the minimum required to manifest the 
stored power, and are then assumed to be augmented as well).

\textbf{Power Trigger:} This is the activation method for dorjes and psicrowns. 
It requires the special knowledge of power manifestation that a character of the 
appropriate class would know, and the formation of the appropriate command thought. 
If a power is on a character's power list, the character knows how to use a power 
trigger item that stores that power. The user must still determine what power is 
stored in the item before she can activate it. Activating a power trigger item 
is a standard action that does not provoke attacks of opportunity.

Powers stored in power trigger items are not augmented. Such powers are assumed 
to be stored in the item at the minimum manifester level necessary to manifest 
the power. However, certain items may specify a higher manifester level than necessary. 
If such an item holds a power that deals hit point damage, the power is assumed 
to be augmented to the maximum allowed by the power and the manifester level.

\textbf{Command Thought:} If no activation method is suggested either in the psionic 
item description or by the nature of the item, assume that a command thought is 
needed to activate it. Command thought activation means that a character mentally 
projects a thought, and the item activates. No other special knowledge is needed. 
Activating a command thought psionic item is a standard action that does not provoke 
attacks of opportunity. 

Sometimes the command thought to activate an item is mentally imprinted within 
it and is whispered into the mind of a creature who picks it up. Other items are 
silent, but a Knowledge (psionics) or Knowledge (history) check might be useful 
in helping to identify command thoughts. A successful DC 30 check is needed to 
come up with the command thought in this case. The power \textit{psionic identify 
}reveals command thoughts.

Powers stored in command thought items are usually not augmented, because the manifester 
level of such an item is assumed to be the minimum possible to manifest the stored 
power.

\textbf{Use-Activated: }This type of psionic item simply has to be used to activate. 
Use activation is generally straightforward and self-explanatory.

Many use-activated items are objects that a character wears. Some items made for 
wearing must still be activated. Although this activation sometimes requires a 
command thought (see above), usually it means mentally willing the activation to 
happen  (a free action). The description of an item states whether a command thought 
is needed in such a case.

Unless stated otherwise, activating a use-activated psionic item is either a standard 
action or not an action at all and does not provoke attacks of opportunity, unless 
the use involves performing an action that provokes attacks of opportunity in itself. 
If the use of the item takes time before a psionic effect occurs, then use activation 
is a standard action. If the item's activation is subsumed in its use and takes 
no extra time, use activation is not an action at all.

Use activation doesn't mean that if you use an item, you automatically know what 
it can do. You must know (or at least guess) what the item can do and then use 
the item to activate it, unless the benefit of the item comes automatically.

Powers stored in use-activated items are usually not augmented, because the manifester 
level of such an item is assumed to be the minimum possible to manifest the stored 
power.

\vspace{12pt}
SAVING THROWS AGAINST PSIONIC ITEM POWERS

Psionic items produce psionic powers. The DC of a saving throw against a power 
from a psionic item is always 10 + the level of the power or effect + the ability 
modifier of the minimum ability score needed to manifest that level of power.

Another way to figure the same number is to multiply the power's level by 1-1/2 
and add 10 to the result.

Psicrowns are an exception to the rule. Treat the saving throw as if the wielder 
manifested the power, including caster level and all modifiers to save DC.

Some psionic items take advantage of the fact that powers can be augmented to increase 
their saving throw DCs. These items are special and have their cost to create and 
market price calculated using the manifester's level instead of the power's level.

Most item descriptions give saving throw DCs for various effects, particularly 
when the effect has no exact power equivalent (making its level otherwise difficult 
to quickly determine).

\vspace{12pt}
DAMAGING PSIONIC ITEMS

A psionic item doesn't need to make a saving throw unless it is unattended, it 
is specifically targeted by the effect, or its wielder rolls a natural 1 on his 
saving throw. Psionic items should always get a save against powers or spells that 
might deal damage to them---even against attacks from which a mundane item would 
normally get no chance to save. All types of psionic item saves---Fortitude, Reflex, 
and Will---are calculated the same way: The item's saving throw bonus equals 2 
+ 1/2 its manifester level (round down). The only exceptions to this rule are intelligent 
psionic items, which make Will saves based on their own Wisdom scores.

A psionic item, unless otherwise noted, takes damage as a normal item of the same 
type. A damaged psionic item continues to function, but if it is destroyed, all 
its psionic power is lost.

\vspace{12pt}
REPAIRING ITEMS

Some psionic items (especially psionic weapons and shields) may take damage over 
the course of an adventure. It costs no more to repair a psionic item with the 
Craft skill than it does to repair its nonpsionic counterpart. The \textit{make 
whole }spell can repair a damaged---but not completely broken--- psionic item.

\vspace{12pt}
INTELLIGENT ITEMS

Some psionic items, particularly weapons, have an intelligence all their own. Only 
permanent psionic items (as opposed to those that are single-use items, those that 
have charges, or those that store power points) can be intelligent. (This means 
that psionic tattoos, power stones, and dorjes, among other items, are never intelligent.) 
In general, less than 1\% of psionic items have intelligence. 

\vspace{12pt}
CURSED ITEMS

Some psionic items are cursed---incorrectly made, or corrupted by outside forces. 
Cursed items might be particularly dangerous to the user, or they might be normal 
items with a minor f law, an inconvenient requirement, or an unpredictable nature. 
Randomly generated items are cursed 5\% of the time.

\vspace{12pt}
CHARGES AND MULTIPLE USES

Some items are limited in power by the number of charges they hold or the number 
of power points they contain. Normally, charged items (such as dorjes) have 50 
charges at most. If such an item is found as a random part of a treasure, roll 
d\% and divide by 2 to determine the number of charges left (round down, minimum 
1).

Similarly, items that contain power points (such as psicrowns) have a number of 
points equal to 50 x the manifester level of the creator. If such an item is found 
as a random part of a treasure, roll d\% and divide by 2 to determine the number 
by which the manifester level is multiplied (round down, minimum 1).

Market prices given on the tables are always for fully charged or fully powered 
items. (When an item is created, it is fully charged or fully powered.) For an 
item that's worthless when its charges or power points run out (which is the case 
for almost all charged or powered items), the value of the partially used item 
is proportional to the number of charges left. For an item that has usefulness 
in addition to its charges, only part of the item's value is based on the number 
of charges left.

Some items are single-use and expendable. Such items can often be found in sets 
or groups.

\vspace{12pt}
MAGIC ITEMS FOR PSIONIC CHARACTERS

Many magic items can aid psionic characters. The table below provides some possibilities.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{4.414in}|}{\begin{minipage}[t]{4.414in}\raggedright
\textbf{Table: Magic-Psionics Equivalencies}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.086in}|}{\begin{minipage}[t]{0.086in}\raggedright
\textbf{Magic Item}\end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
\textbf{Psionic Effect}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{3.657in}|}{\begin{minipage}[t]{3.657in}\raggedright
\textit{Helm of telepathy}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Substitute power for spell\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textit{Pearl of power}\end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
Treat in all ways as a \textit{cognizance crystal }with power point capacity appropriate 
to the equivalent power level\end{minipage}}\\
\hline
% ROW 5
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
\textit{Crystal ball }\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Substitute power for spell \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textit{Ioun stones}\end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
\end{minipage}}\\
\hline
% ROW 7
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
Vibrant purple \end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
Stores three levels of psionic powers\end{minipage}}\\
\hline
% ROW 8
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
Pale lavender \end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
Absorbs powers up to 4th level (burns out as normal)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
Rainbow\textsuperscript{\textbf{1}} \end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
Provides 5 power points per day (regenerates)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
Dull gray\textsuperscript{\textbf{2}} \end{minipage}} & \multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
Provides 1 power point to a psionic character, then disintegrates\end{minipage}}\\
\hline
% ROW 11
\multicolumn{3}{p{3.742in}|}{\begin{minipage}[t]{3.742in}\raggedright
1 New item: Treat as a \textit{cognizance crystal }in \textit{ioun stone }form, 
except that it regenerates its stored power points each day; Price 16,000 gp.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.758in}|}{\begin{minipage}[t]{0.758in}\raggedright
2 Dull gray stones are useless for magic but still harbor just enough resonance 
that a psionic character can eke out 1 power point before the stone is gone forever.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsubsection*{{\LARGE PSIONIC ITEM DESCRIPTIONS}}

In the following sections, each type of psionic item, such as armor or psionic 
tattoos, has a general description, followed by descriptions of specific items.

General descriptions include notes on activation, random generation, and other 
information. The Armor Class, hardness, hit points, and break DC are given for 
typical examples of some types of psionic items. The Armor Class assumes that the 
item is unattended and includes a -5 penalty for the item's effective Dexterity 
of 0. If a creature holds the item, use the creature's Dexterity modifier as an 
adjustment to Armor Class in place of the -5 penalty.

Some individual items, notably those that simply store psionic powers, don't get 
full-blown descriptions. Simply reference the power's description. Assume that 
the power is manifested at the minimum level required to manifest it, unless otherwise 
noted. Increasing the manifester level so increases the cost of the item; see Table: 
Estimating Magic Item Gold Piece Value,\textit{ }substituting ``spell'' for ``power'' 
and ``caster level'' for ``manifester level'' as appropriate. The main reason to 
make the manifester level higher, or course, would be to increase the potency of 
the power. Raising the manifester level is common for powers such as \textit{astral 
construct}, the duration of which increases with the level of the manifester.

Items with full descriptions have their abilities detailed, and each of the following 
aspects of these items is summarized at the end of the description.

\textbf{Aura:} Most of the time, a \textit{detect psionics }power will reveal the 
discipline associated with a psionic item and the strength of the aura an item 
emits. This information (when applicable) is given at the beginning of the item's 
notational entry in the form of a phrase. See the \textit{detect psionics }power 
description for more information.

\textbf{Manifester Level:} The next entry in the summary indicates the level of 
the creator (or the manifester level of the powers placed within the item, if this 
level is lower than the actual level of the creator). The manifester level provides 
the item's saving throw bonus, as well as range and other level-dependent aspects 
of the powers of the item (if variable).

It also determines the level that must be contended with should the item come under 
the effect of a \textit{dispel psionics }power or a similar situation. This information 
is given in the form ``ML x,'' where ``ML'' is an abbreviation for manifester

level and ``x'' is an ordinal number representing the manifester level itself.

For psionic tattoos, power stones, and dorjes, the creator can set the manifester 
level of an item at any number high enough to manifest the stored power and not 
higher than her own manifester level. For other psionic items, the item itself 
determines the manifester level. In this case, the creator's manifester level must 
be as high as the item's manifester level (and prerequisites may effectively put 
a higher minimum on the creator's level).

\textbf{Prerequisites:} Certain requirements must be met in order for a character 
to create a psionic item. These include feats, powers, and miscellaneous requirements 
such as level, alignment, and race or kind. The prerequisites for creation of an 
item are given in the summary immediately following the item's manifester level.

A power prerequisite can be provided by a character who knows the power, or through 
the use of a power completion or power trigger psionic item or a psi-like ability 
that produces the desired power effect. For each day that passes during the creation 
process, the creator must expend one power completion item (such as a power stone) 
or 1 charge from a power trigger item (such as a dorje), if either of those objects 
is used to supply a prerequisite.

It is possible for more than one character to cooperate in the creation of an item, 
with each participant providing one or more of the prerequisites. In some cases, 
cooperation may even be necessary, such as if one character knows some of the powers 
necessary to create an item and another character knows the rest.

If two or more characters cooperate to create an item, they must agree among themselves 
who will be considered the creator for the purpose of determinations where the 
creator's level must be known. (It's sensible, although not mandatory, for the 
highest-level character involved to be considered the creator.) The character designated 
as the creator pays the experience points required to make the item.

Typically, a list of prerequisites includes one feat and one or more powers (or 
some other requirement in addition to the feat). When two powers at the end of 
a list are separated by ``or,'' one of those powers is required in addition to 
every other power mentioned prior to the last two.

\textbf{Market Price:} This gold piece value, given in the summary following the 
word ``Price,'' represents the price someone should expect to pay to buy the item. 
Market prices are also included on the random generation tables for easy reference. 
The market price of an item that can be constructed with a psionic item creation 
feat is usually equal to the base price + the price for any components (special 
materials or experience point expenditure).

\textbf{Cost to Create:} The cost in gold pieces and experience points to create 
the item is given in the summary following the word ``Cost.'' This information 
appears only for items with components (material or experience points) that make 
their market prices higher than their base prices. The cost to create includes 
the costs derived from the base cost plus the cost of the components. Items without 
components do not have a ``Cost'' entry. For them, the market price and base price 
are the same. The cost in gold pieces is 1/2 the market price, and the cost in 
experience points is 1/25 the market price. 

\textbf{Weight: }The notational entry for many items ends with a value for the 
item's weight. When a weight figure is not given, the item has no weight worth 
noting (for the purpose of determining how much of a load a character can carry).

\vspace{12pt}
RANDOM PSIONIC ITEMS

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{4}{|p{4.236in}|}{\begin{minipage}[t]{4.236in}\raggedright
\textbf{Table: Random Psionic Item Generation}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{4}{p{0.264in}|}{\begin{minipage}[t]{0.264in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
\textbf{Item}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{2.536in}|}{\begin{minipage}[t]{2.536in}\centering
01-02\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\centering
Armor, possibly with special ability\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\centering
03-04\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
06-10\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
06-10\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Shield, possibly with special ability\end{minipage}}\\
\hline
% ROW 5
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
05-06\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
11-15\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
11-15\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\centering
Melee weapon, possibly with special ability\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\centering
08-09\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
16-20\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
16-20\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Ranged weapon, possibly with special ability\end{minipage}}\\
\hline
% ROW 7
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
10-40\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
21-40\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
21-35\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
\textit{Cognizance crystal}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
41-46\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
41-50\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
36-45\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Dorje\end{minipage}}\\
\hline
% ROW 9
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
47-81\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
51-68\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
46-67\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Power stone\end{minipage}}\\
\hline
% ROW 10
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
82-87\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
69-82\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
68-75\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Psicrown\end{minipage}}\\
\hline
% ROW 11
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
88-93\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
83-89\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
76-87\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Psionic tattoo\end{minipage}}\\
\hline
% ROW 12
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
94-100\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Minor universal item\end{minipage}}\\
\hline
% ROW 13
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
90-100\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Medium universal item\end{minipage}}\\
\hline
% ROW 14
\multicolumn{5}{p{2.801in}|}{\begin{minipage}[t]{2.801in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.539in}|}{\begin{minipage}[t]{0.539in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.621in}|}{\begin{minipage}[t]{0.621in}\raggedright
88-100\end{minipage}} & \multicolumn{1}{p{0.539in}|}{\begin{minipage}[t]{0.539in}\centering
Major universal item\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
ARMOR AND SHIELDS

In general, psionic armor and shields follow the rules for the equivalent magic 
items, as far as enhancement bonuses, stacking, and other base abilities are concerned. 
An enhancement bonus is treated the same way regardless of whether magic or psionics 
created it.

Psionic armor and shields differ from standard and magical equivalents in that 
psionic armor and shields incorporate one or more crystals into their construction. 
Particularly powerful armor and shields may be entirely composed of brightly hued 
or transparent crystals.

\textbf{Special Qualities:} Roll d\%. An 01 result indicates the item is intelligent, 
an 02-31 result indicates that the command thought (if any) is psionically imprinted 
and whispers itself into the user's mind on acquisition, and 32-100 indicates no 
special qualities.

Intelligent items have extra abilities and sometimes also extraordinary powers 
and special purposes. Substitute manifesting for spellcasting as required.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.189in}|}{\begin{minipage}[t]{4.189in}\raggedright
\textbf{Table: Psionic Armor Special Abilities}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.311in}|}{\begin{minipage}[t]{0.311in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
\textbf{Special Ability}\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
\textbf{Base Price Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.248in}|}{\begin{minipage}[t]{1.248in}\centering
01-30\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
01-07\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
01-03\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\centering
Quickness\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\centering
31-74\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
08-30\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
04-05\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Landing\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+4,000 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
75-80\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
31-46\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
06-10\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\centering
Floating\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedleft
+4,000 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\centering
81-96\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
47-55\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
11-20\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Linked\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+6,000 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
97\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
56-66\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
21-30\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Seeing\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+6,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
98\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
67-75\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
31-40\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Power resistance (13)\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
99\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
76-83\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
41-50\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Ectoplasmic\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+10,800 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
84-89\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
51-60\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Gleaming\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
90-94\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
61-70\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Power resistance (15)\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
95-98\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
71-77\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Vanishing\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
99\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
78-83\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Mindarmor\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+24,000 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
84-89\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Power resistance (17)\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+4 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
90-94\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Radiant\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+4 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
95-96\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Aporter\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+40,320 gp\end{minipage}}\\
\hline
% ROW 17
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
97-98\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Power resistance (19)\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+5 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 18
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
99\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Phasing\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
+65,520 gp\end{minipage}}\\
\hline
% ROW 19
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\centering
100\end{minipage}} & \multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedright
100\end{minipage}} & \multicolumn{1}{p{0.612in}|}{\begin{minipage}[t]{0.612in}\raggedright
100\end{minipage}} & \multicolumn{1}{p{0.496in}|}{\begin{minipage}[t]{0.496in}\centering
Roll twice again\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{1.336in}|}{\begin{minipage}[t]{1.336in}\raggedleft
---\end{minipage}}\\
\hline
% ROW 20
\multicolumn{6}{p{1.559in}|}{\begin{minipage}[t]{1.559in}\raggedleft
1 Add to enhancement bonus\textit{ }to determine total market price.\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.496in}|}{\begin{minipage}[t]{0.496in}\raggedleft
2 If you roll a special ability twice, only one counts. If you roll two versions 
of the same special ability, use the better.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.182in}|}{\begin{minipage}[t]{4.182in}\raggedright
\textbf{Table: Psionic Shield Special Abilities}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
\textbf{Special Ability}\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
\textbf{Base Price Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.222in}|}{\begin{minipage}[t]{1.222in}\centering
01-35\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
01-03\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\centering
Heartening\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
+720 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\centering
35-60\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
06-10\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
04-05\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Ranged\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
61-89\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
11-15\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
06-10\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\centering
Linked\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedleft
+6,000 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\centering
90-97\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
16-35\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
11-24\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Power resistance (13)\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
98\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
36-58\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
25-34\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Manifester\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+10,800 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
99\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
69-88\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
35-44\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Averter\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+12,960 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
89-92\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
45-54\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Vanishing\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
93-96\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
55-64\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Power resistance (15)\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
97-98\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
65-74\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Wall\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+20,160 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
99\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
75-81\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Mindarmor\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+24,000 gp\end{minipage}}\\
\hline
% ROW 13
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
82-88\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Power resistance (17)\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+4 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
89-93\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Aporter\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+40,320 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
94-96\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Time buttress\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+5 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
97-99\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Power resistance (19)\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
+5 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 17
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\centering
100\end{minipage}} & \multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedright
100\end{minipage}} & \multicolumn{1}{p{0.600in}|}{\begin{minipage}[t]{0.600in}\raggedright
100\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Roll twice again\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{1.386in}|}{\begin{minipage}[t]{1.386in}\raggedleft
---\end{minipage}}\\
\hline
% ROW 18
\multicolumn{6}{p{1.540in}|}{\begin{minipage}[t]{1.540in}\raggedleft
1 Add to enhancement bonus to determine total market price.\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.487in}|}{\begin{minipage}[t]{0.487in}\raggedleft
2 If you roll a special ability twice, only one counts. If you roll two versions 
of the same special ability, use the better.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\section*{\textbf{Psionic Armor and Shield Special Ability Descriptions}}

Most psionic armor and shields have only enhancement bonuses. Such items can also 
have one or more of the special abilities detailed below. Armor or a shield with 
a special ability must have at least a +1 enhancement bonus. 

\textbf{Aporter:} As a standard action, a suit of aporter armor or an aporter shield 
transports the wearer and her equipment to any spot within 800 feet that she can 
visualize or specify, as the \textit{psionic dimension door }power. The armor or 
shield can transport the wearer in this fashion twice per day.

Moderate psychoportation; ML 10th; Craft Psionic Arms and Armor, \textit{psionic 
dimension door; }Price +40,320 gp.

\textbf{Averter:} On command, up to three times per day, any creature to whom the 
wearer presents an averter shield must succeed on a DC 14 Will save or be overcome 
by a powerful aversion to the wielder (actually the shield), and will not approach 
within 30 feet. This is a mind-affecting compulsion effect, as the \textit{aversion 
}power.

Faint telepathy; ML 5th; Craft Psionic Arms and Armor, \textit{aversion; }Price 
+12,960 gp.

\textbf{Ectoplasmic:} As a standard action, ectoplasmic armor converts itself, 
its wearer, and all the wearer's equipment into \textit{ectoplasmic form }for up 
to 5 minutes once per day, as the power of the same name. In this semisolid state, 
the wearer gains damage reduction 10/psionics.

Faint psychometabolism; ML 5th; Craft Psionic Arms and Armor, \textit{ectoplasmic 
form; }Price +10,800 gp.

\textbf{Floating:} This kind of armor is psionically buoyant in water or a similar 
liquid, negating the normal penalty for wearing armor when making Swim checks. 
Additionally, it grants a +4 circumstance bonus on Swim checks.

Faint psychoportation; ML 4th; Craft Psionic Arms and Armor, \textit{float; }Price 
+4,000 gp.

\textbf{Gleaming:} This kind of armor is usually made of crystal, though it doesn't 
have to be. Gleams and flashes from the armor give the wearer and his armor a ``fuzzy'' 
appearance, granting the wearer concealment.

Faint metacreativity; ML 5th; Craft Psionic Arms and Armor, \textit{concealing 
amorpha; }Price +3 bonus.

\textbf{Heartening: }This kind of shield grants the wearer up to 5 temporary hit 
points per day on command. These temporary hit points fade after 4 minutes. The 
wearer can activate this power as an immediate action at any time.

Faint psychometabolism; ML 4th; Craft Psionic Arms and Armor, \textit{vigor; }Price 
+720 gp.

\textbf{Landing:} A suit of armor with this capability allows the wearer to ignore 
any damage dealt by the first 60 feet of a fall. Regardless of the height of a 
fall, the wearer always lands on her feet.

Faint psychoportation; ML 4th; Craft Psionic Arms and Armor, \textit{catfall; }Price 
+4,000 gp.

\textbf{Linked:} This kind of armor or shield allows the wearer to form a telepathic 
bond with other wearers of linked armor or shields within 10 miles. This ability 
is otherwise similar to the \textit{mindlink }power.

Moderate telepathy; ML 6th; Craft Psionic Arms and Armor, \textit{mindlink; }Price 
+6,000 gp.

\textbf{Manifester:} This kind of shield generates 3 power points once per day 
that the wearer can use when manifesting a power he knows. These power points must 
all be used on the same power. As usual, a psionic character cannot pay a power's 
cost with power points from more than one source, so the power points in the shield 
must be used for discrete manifestations.

Moderate clairsentience; ML 6th; Craft Psionic Arms and Armor, knowledge of any 
2nd-level power; Price +10,800 gp.

\textbf{Mindarmor:} This kind of armor or shield grants the wearer a +3 insight 
bonus on Will saving throws to resist all mind-affecting and/or compulsion powers.

Faint psychokinesis; ML 5th; Craft Psionic Arms and Armor, \textit{empty mind; 
}Price +24,000 gp.

\textbf{Phasing:} The wearer of this kind of armor can move through wooden, plaster, 
or stone walls, but not other materials. The wearer can call on this special ability 
as a standard action. When the phasing ability is active, the wearer can pass through 
a wall or some other kind of appropriate object for a total distance of 60 feet 
per day (see below), breaking this distance up into several smaller passages or 
one long one, as desired. A wearer who exceeds this daily distance limit while 
inside solid material is ejected from the material at the point of entry, ending 
up prone in front of the now impassable barrier.

Phasing through a wall that separates two adjacent squares on the grid counts as 
5 feet of distance. Phasing through a wall or barrier of any greater thickness 
counts as a distance equal to the barrier's thickness plus 5 feet.

feet of distance.

Strong psychoportation; ML 13th; Craft Psionic Arms and Armor, \textit{psionic 
phase door; }Price +65,520 gp.

\textbf{Power Resistance:} This kind of armor or shield grants the wearer power 
resistance while it is worn. The power resistance can be 13, 15, 17, or 19, depending 
on the amount that was built into the armor or shield.

Moderate clairsentience; ML 9th; Craft Psionic Arms and Armor, \textit{power resistance; 
}Price +2 bonus (PR 13); +3 bonus (PR 15); +4 bonus (PR 17); or +5 bonus (PR 19).

\textbf{Quickness: }This kind of armor increases the wearer's speed by 5 feet. 
Thus, a character whose normal speed in armor is 20 feet moves 25 feet in \textit{armor 
of quickness. }

Faint psychoportation; ML 4th; Craft Psionic Arms and Armor, \textit{burst; }Price 
+1 bonus.

\textbf{Radiant:} The wearer of this kind of armor gains resistance 10 against 
energy attacks (acid, cold, electricity, fire, or sonic). The armor absorbs the 
first 10 points of damage dealt by any such attack, and this absorption causes 
it to radiate light for a number of rounds equal to the points of damage absorbed. 
This light is sufficient to illuminate a 60-foot-radius area.

If the armor absorbs more damage while it is radiating light, the newer radiant 
effect overlaps (does not stack with) the effect that was already in place. 

Moderate psychokinesis; ML 9th; Craft Psionic Arms and Armor; \textit{energy adaptation; 
}Price +4 bonus.

\textbf{Ranged:} The wielder of a ranged shield can throw it in combat, with a 
range increment of 30 feet. While in the air, the shield is treated in all ways 
as a ranged weapon and cannot be blocked or grabbed except by those with appropriate 
feats. No matter the size of the wielder, a buckler or light shield deals 1d6 points 
of damage and a heavy one 1d8 points. (A tower shield cannot be created with this 
special ability.) The wielder's Strength modifier and the shield's enhancement 
bonus add to the base damage.

A ranged shield flies through the air back to the creature that threw it. It returns 
to the wielder just before the creature's next turn (and is therefore ready to 
use again in that turn).

Catching a ranged shield when it comes back is a free action. If the wielder can't 
catch it, or if the wielder has moved since throwing it, the shield drops to the 
ground in the square from which it was thrown.

Faint psychokinesis; ML 5th; Craft Psionic Arms and Armor\textit{, far hand; }Price 
+1 bonus.

\textbf{Seeing:} This kind of armor grants a wider than normal field of vision, 
so that opponents flanking the wearer gain only a +1 bonus on their attack rolls 
instead of +2 (rogues still get their full sneak attack damage because the wearer 
is still flanked). The wearer gains a +1 enhancement bonus on Spot checks but takes 
a -2 penalty on saves against gaze attacks.

Faint clairsentience; ML 5th; Craft Psionic Arms and Armor, \textit{ubiquitous 
vision; }Price +6,000 gp.

\textbf{Time Buttress:} This kind of shield gives the wielder a chance to avoid 
telling blows by using time itself as a shield. Once per day, the wielder can use 
\textit{timeless body }as though manifesting the power.

Strong psychoportation; ML 17th; Craft Psionic Arms and Armor, \textit{timeless 
body; }Price +5 bonus.

\textbf{Vanishing: }On command, this suit of armor or shield renders its wearer 
and all the wearer's equipment invisible to the minds of others, as if he had manifested 
the power \textit{cloud mind}. The wearer can use this ability twice per day.

Faint psychokinesis; ML 5th; Craft Psionic Arms and Armor, \textit{cloud mind; 
}Price +3 bonus.

\textbf{Wall:} As a standard action once per day, the wielder can drop this kind 
of shield at his feet and command a \textit{wall of ectoplasm }(as the power) to 
come into being, with the shield as the point of origin for the effect. This effect 
forms a wall whose area is up to twelve 10-foot squares or a sphere or hemisphere 
with a radius of up to 12 feet. The wall dissipates after 7 minutes, or sooner 
if the wielder of the shield reclaims it (thus dismissing the effect).

Strong metacreativity; ML 12th; Craft Psionic Arms and Armor, \textit{wall of ectoplasm}; 
Price +20,160 gp.

\vspace{12pt}
WEAPONS

Although they generally follow the rules for magic weapons, psionic weapons differ 
from mundane and magic weapons in their design. Most possess some crystal components, 
and some are composed entirely of crystal. Many also sport intricate traceries 
along the blade or haft, which flicker now and then as if channeling flows of psychic 
energy.

Psionic weapons have enhancement bonuses ranging from +1 to +5. They apply these 
bonuses on both attack and damage rolls when used in combat. This enhancement bonus 
is effective for the purpose of overcoming creatures with damage resistance that 
is penetrated by magic. All psionic weapons are also masterwork weapons, but their 
masterwork bonus on attack rolls does not stack with their enhancement bonus on 
attack rolls.

Weapons come in two basic categories: melee and ranged. Some of the weapons listed 
as melee weapons can also be used as ranged weapons. In this case, their enhancement 
bonus applies to either type of attack. 

In addition to enhancement bonuses, psionic weapons can also have the special abilities 
detailed here. A weapon with a special ability must have at least a +1 enhancement 
bonus.

The rules for manifester level for weapons (called caster level), additional damage 
dice, ranged weapons and ammunition, ammunition and breakage, hardness and hit 
points, critical hits, and weapons for unusually sized creatures for psionic weapons 
are the same as for magic weapons\textit{. }Psionic weapons do not have the chance 
to generate light (though some may be mentally audible; see below).

\textbf{Mentally Audible:} Fully 30\% of psionic weapons telepathically mutter, 
croon, recite battle poems, scream, or produce other mental ``noises'' when first 
drawn, at first blood, or when they slay a significant enemy. Such a weapon cannot 
be concealed from creatures within 15 feet when it is drawn, nor can its mental 
``soundtrack'' be curbed.

\textbf{Activation:} Usually a character benefits from a psionic weapon in the 
same way a character benefits from a mundane weapon---by attacking with it. If 
a weapon has a special ability that the user needs to activate, then the user usually 
needs to project a command thought (a standard action).

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.219in}|}{\begin{minipage}[t]{4.219in}\raggedright
\textbf{Table: Psionic Melee Weapon Special Abilities}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.281in}|}{\begin{minipage}[t]{0.281in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
\textbf{Special Ability}\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
\textbf{Base Price Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.144in}|}{\begin{minipage}[t]{1.144in}\centering
01-15\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
01-10\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\centering
Psychokinetic\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\centering
16-45\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
11-25\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
01-09\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Dissipater\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
46-55\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
26-30\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedright
10-12\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\centering
Lucky\end{minipage}} & \multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.056in}|}{\begin{minipage}[t]{0.056in}\centering
56-70\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
31-40\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
13-17\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Sundering\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
71-80\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
41-46\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
18-21\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Power storing\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
81-99\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
51-56\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
22-30\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Collision\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
57-65\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
31-37\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Mindcrusher\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
66-71\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
38-41\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Psychokinetic burst\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
72-75\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
42-49\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Suppression\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
76-78\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
50-58\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Psibane\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
79-81\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
59-61\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Parrying\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+8,000 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
82-85\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
62-65\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Manifester\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+16,000 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
86-88\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
66-71\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Bodyfeeder\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 16
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
89-91\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
72-77\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Mindfeeder\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 17
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
92-93\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
78-83\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Soulbreaker\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 18
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
94\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
84-86\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Psychic\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+35,000 gp\end{minipage}}\\
\hline
% ROW 19
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
95\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
87-90\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Coup de grace\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
+5 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 20
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\centering
100\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
96-100\end{minipage}} & \multicolumn{1}{p{0.721in}|}{\begin{minipage}[t]{0.721in}\raggedright
91-100\end{minipage}} & \multicolumn{1}{p{0.487in}|}{\begin{minipage}[t]{0.487in}\centering
Roll again twice\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedleft
---\end{minipage}}\\
\hline
% ROW 21
\multicolumn{6}{p{1.425in}|}{\begin{minipage}[t]{1.425in}\raggedleft
1 Add to enhancement bonus to determine total market price.\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedleft
2 Reroll if you get a duplicate special ability, an ability incompatible with an 
ability that you've already rolled, or if the extra ability puts you over the +10 
limit. A weapon's enhancement bonus and special ability bonus equivalents can't 
total more than +10.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.237in}|}{\begin{minipage}[t]{4.237in}\raggedright
\textbf{Table: Psionic Ranged Weapon Special Abilities}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.263in}|}{\begin{minipage}[t]{0.263in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
\textbf{Special Ability}\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
\textbf{Base Price Modifier}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.061in}|}{\begin{minipage}[t]{1.061in}\centering
01-20\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
01-15\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\centering
Teleporting\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\centering
21-40\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
16-30\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Psychokinetic\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+1 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
41-100\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
31-45\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedright
01-30\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\centering
Collision\end{minipage}} & \multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.053in}|}{\begin{minipage}[t]{0.053in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
46-50\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
31-40\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Suppression\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
51-66\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
41-65\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Psychokinetic burst\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
67-74\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
66-69\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Psibane\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+2 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
75-78\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
70-73\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Manifester\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+16,000 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
79-82\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
74-79\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Dislocator\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+3 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
83-98\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
80-90\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Great dislocator\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+4 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
91-97\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Coup de grace\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
+5 bonus\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
99-100\end{minipage}} & \multicolumn{1}{p{0.863in}|}{\begin{minipage}[t]{0.863in}\raggedright
98-100\end{minipage}} & \multicolumn{1}{p{0.815in}|}{\begin{minipage}[t]{0.815in}\centering
Roll again twice\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedleft
---\end{minipage}}\\
\hline
% ROW 14
\multicolumn{6}{p{1.324in}|}{\begin{minipage}[t]{1.324in}\raggedleft
1 Add to enhancement bonus to determine total market price.\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedleft
2 Reroll if you get a duplicate special ability, an ability incompatible with an 
ability that you've already rolled, or if the extra ability puts you over the +10 
limit. A weapon's enhancement bonus and special ability bonus equivalents can't 
total more than +10.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\section*{\textbf{Psionic Weapon Special Ability Descriptions}}

Most psionic weapons have only enhancement bonuses. They can also have the special 
abilities detailed here. A weapon with a special ability must have at least a +1 
enhancement bonus.

\textbf{Bodyfeeder:} All feeder weapons have a special ability that functions only 
upon scoring a successful critical hit. A bodyfeeder weapon grants its wielder 
temporary hit points equal to the total damage dealt by a successful critical hit. 
These temporary hit points last for 10 minutes. Thus, if the wielder of a bodyfeeder 
weapon successfully scores a critical hit while the wielder still enjoys temporary 
hit points from a previous critical hit, the wielder gains only the better of the 
two values: either his current number of temporary hit points, or the new influx 
of temporary hit points, whichever is higher.

Strong psychometabolism; ML 12th; Craft Psionic Arms and Armor, \textit{claws of 
the vampire; }Price +3 bonus.

\textbf{Collision: }Collision weapons psionically increase their own mass at the 
end point of each swing or shot. Such weapons deal an extra 5 points of damage 
on each successful strike, in addition to the weapon's enhancement bonus. Bows, 
crossbows, and slings bestow the extra damage upon their ammunition.

Moderate metacreativity; ML 10th; Craft Psionic Arms and Armor, \textit{matter 
manipulation; }Price +2 bonus.

\textbf{Coup de Grace: }Coup de grace weapons are exceptionally dangerous. On a 
successful critical hit, the foe must succeed on a DC 27 Will save or be paralyzed 
for 1 round. While this ability does work on creatures that are immune to extra 
damage from critical hits, it does not work on creatures without an Intelligence 
score. Bows, crossbows, and slings bestow this ability on their ammunition.

Strong telepathy; ML 19th; Craft Psionic Arms and Armor, \textit{psionic dominate; 
}Price +5 bonus.

\textbf{Dislocator:} The wielder of this kind of weapon can attempt to dislocate 
a designated foe up to three times per day. On a successful hit, the foe must succeed 
on a DC 17 Will save or be teleported 1-100 miles in a random direction. If the 
weapon misses, the use is wasted. Bows, crossbows, and slings bestow this ability 
on their ammunition.

Strong psychoportation; ML 12th; Craft Psionic Arms and Armor, \textit{psionic 
teleport; }Price +3 bonus.

\textbf{Dissipater: }This kind of weapon is devastating to creatures and objects 
composed of or originally formed from ectoplasm (such as astral constructs, walls 
of ectoplasm, creatures in ectoplasmic form, and items created using the metacreativity 
discipline). Against qualifying targets, a dissipater weapon ignores damage reduction 
and hardness, and treats all successful hits as critical hits. 

Strong metacreativity; ML 12th; Craft Psionic Arms and Armor, \textit{dismiss ectoplasm; 
}Price +1 bonus.

\textbf{Great Dislocator:} The wielder of this kind of weapon can attempt to greatly 
dislocate a designated foe up to three times per day. On a successful hit, the 
foe must succeed on a DC 20 Will save or be cast into a random alternate plane 
of existence. If the weapon misses, the use is wasted. Bows, crossbows, and slings 
bestow this ability upon their ammunition.

Strong psychoportation; ML 12th; Craft Psionic Arms and Armor, \textit{psionic 
plane shift}; Price +4 bonus.

\textbf{Lucky:} A lucky weapon offers a second chance at success. Once per day, 
the wielder can reroll a failed attack roll (whether a single attack or one in 
a series of multiple attacks) as a free action. The rerolled attack uses the same 
bonuses or penalties as the missed roll.

Moderate clairsentience; ML 8th; Craft Psionic Arms and Armor\textit{, fate of 
one; }Price +1 bonus.

\textbf{Manifester:} This kind of weapon generates 5 power points once per day 
that the wearer can use when manifesting a power he knows. These power points must 
all be used on the same power. As usual, a psionic character cannot pay a power's 
cost with power points from more than one source, so the power points in the shield 
must be used for discrete manifestations.

Moderate clairsentience; ML 8th; Craft Psionic Arms and Armor, knowledge of any 
3rd-level power; Price +16,000 gp.

\textbf{Mindcrusher:} Any psionic creature struck in combat by a mindcrusher weapon 
loses a number of power points equal to half the amount of hit point damage the 
weapon deals (only the base damage of the weapon contributes to the power point 
loss; additional damage from high Strength or other sources does not cause additional 
power point loss). A psionic creature that is out of power points (or has none) 
must succeed on a DC 17 Will save or take 1d2 points of Wisdom damage.

Strong psychometabolism; ML 12th; Craft Psionic Arms and Armor, \textit{psychic 
vampire; }Price +2 bonus.

\textbf{Mindfeeder: }All feeder weapons have a special ability that functions only 
upon scoring a successful critical hit. A mindfeeder weapon grants its wielder 
temporary power points equal to the total damage dealt by a successful critical 
hit. These temporary power points last for 10 minutes. The wielder gains power 
points even if the target has none (effectively, its hit point damage is converted 
to power points). Constructs and undead are not subject to mindfeeder weapons. 
As with temporary hit points, temporary power points do not stack with each other; 
they overlap. Thus, if a mindfeeder weapon successfully scores a critical hit while 
the wielder still enjoys temporary power points from a previous critical hit, the 
wielder gains only the better of the two values: either her current number of temporary 
power points, or the new influx of temporary power points, whichever is higher.

Strong psychometabolism; ML 15th; Craft Psionic Arms and Armor, \textit{psychic 
vampire; }Price +3 bonus.

\textbf{Parrying: }A parrying weapon perceives an instant into the future, and 
of its own accord resists melee and ranged attacks aimed at the wielder, granting 
a +1 insight bonus to the wielder's Armor Class. The weapon is so adept at parrying 
that it even affects incoming powers, granting the wielder a +1 insight bonus on 
saving throws. The bonuses are granted whenever the wielder holds the weapon, even 
if flat-footed.

Faint clairsentience; ML 5th; Craft Psionic Arms and Armor, \textit{defensive precognition; 
}Price +8,000 gp.

\textbf{Power Storing:} A power storing weapon allows a manifester to store a single 
targeted power of up to 5 power points in the weapon. (The power must have a manifesting 
time of 1 standard action.) Any time the weapon strikes a creature and the creature 
takes damage from it, the weapon can immediately manifest the power on that creature 
as a swift action if the wielder desires. (This ability is an exception to the 
rule that manifesting a power from an item takes at least as long as manifesting 
that power normally.) Once the power is manifested, the weapon is empty, and a 
manifester can imbed any other targeted power of up to 5 power points into it. 
The weapon telepathically whispers to the wearer the name of the power currently 
stored within it. A randomly generated power storing weapon has a 50\% chance to 
have a power stored in it already.

Strong psychokinesis; ML 12th; Craft Psionic Arms and Armor, creator must be a 
manifester of at least 12th level; Price +1 bonus.

\textbf{Psibane:} A psibane weapon is crafted to oppose psionic beings. When used 
against such creatures, its effective enhancement bonus is 2 higher than its actual 
enhancement bonus. It deals an extra 2d6 points of damage against psionic opponents. 
It bestows one negative level on any psionic creature attempting to wield it. This 
negative level remains as long as the weapon is in hand and disappears when the 
weapon is no longer wielded. This negative level never results in actual level 
loss, but it cannot be overcome in any way while the weapon is wielded. Psibane 
bows, crossbows, and slings bestow this ability upon their ammunition.

Strong clairsentience; ML 15th; Craft Psionic Arms and Armor, \textit{bend reality; 
}Price +2 bonus.

\textbf{Psychic:} A psychic weapon's power depends on its wielder. In the hands 
of a nonpsionic creature, the weapon possesses the qualities of a nonmagical, nonpsionic 
masterwork weapon. When wielded by a psionic creature, this weapon has an enhancement 
bonus based on the wielder's current power point reserve, as shown on the following 
table. The weapon's enhancement bonus decreases as the wielder spends power points, 
and it increases whenever the wielder gains enough power points (by any means) 
to put his power point reserve into the next higher category.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.385in}|}{\begin{minipage}[t]{1.385in}\raggedright
\textbf{Power Point Reserve}\end{minipage}} & \multicolumn{1}{p{1.374in}|}{\begin{minipage}[t]{1.374in}\centering
\textbf{Enhancement Bonus}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1-4 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+1\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.385in}|}{\begin{minipage}[t]{1.385in}\centering
5-29 \end{minipage}} & \multicolumn{1}{p{1.374in}|}{\begin{minipage}[t]{1.374in}\centering
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
30-79 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+3\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.385in}|}{\begin{minipage}[t]{1.385in}\centering
80-129 \end{minipage}} & \multicolumn{3}{p{1.512in}|}{\begin{minipage}[t]{1.512in}\centering
+4\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
130 or higher \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+5\end{minipage}}\\
\hline
\end{longtable}

Strong clairsentience; ML 17th; Craft Psionic Arms and Armor, \textit{reality revision; 
}Price +35,000.

\textbf{Psychokinetic:} Upon command, a psychokinetic weapon glows from the inside 
with lethal psionic energy. The energy does not harm the hands that hold the weapon. 
Such a weapon deals an extra 1d4 points of damage on a successful hit. This extra 
damage is ectoplasmic in nature and is not affected by damage reduction. Bows, 
crossbows, and slings bestow this ability upon their ammunition.

Moderate psychokinesis\textit{; }ML 10th; Craft Psionic Arms and Armor, \textit{concussion 
blast; }Price +1 bonus.

\textbf{Psychokinetic Burst:} This weapon functions as a psychokinetic weapon that 
also releases a blast of destructive psionic energy upon scoring a successful critical 
hit. In addition to the extra damage of the psychokinetic ability (see above), 
a psychokinetic burst weapon deals an extra 1d6 points of damage on a successful 
critical hit. If the weapon's critical multiplier is x3, add 2d6 points of extra 
damage instead, and if the multiplier is x4, add 3d6 points of extra damage. This 
extra damage is ectoplasmic in nature and is not affected by damage reduction. 
Bows, crossbows, and slings bestow this ability upon their ammunition.

Strong psychokinesis; ML 12th; Craft Psionic Arms and Armor, \textit{concussion 
blast; }Price +2 bonus.

\textbf{Soulbreaker:} This weapon has a special ability that functions only upon 
scoring a successful critical hit. On a successful critical hit, a soulbreaker 
weapon bestows one negative level on the foe. One day after being struck, if the 
negative levels have not been purged, the subject must succeed on a DC 18 Fortitude 
save for each negative level or lose a character level.

Strong telepathy; ML 12th; Craft Psionic Arms and Armor, \textit{mindwipe; }Price 
+3 bonus.

\textbf{Sundering: }This kind of weapon allows a wielder to attack opponents' weapons 
as if he had the Improved Sunder feat.

Faint metacreativity; ML 5th; Craft Psionic Arms and Armor, Great Sunder, \textit{metaphysical 
weapon; }Price +1 bonus.

\textbf{Suppression:} An opponent or object struck by this kind of weapon is subject 
to a targeted \textit{dispel psionics }power. The wielder makes a power check (1d20 
+ 5 + manifester level, maximum +15) against a DC of 11 + the manifester level 
of the power to be dispelled. Bows, crossbows, and slings bestow this ability upon 
their ammunition, but can do so only three times per day.

Moderate psychokinesis ML 10th; Craft Psionic Arms and Armor, \textit{dispel psionics; 
}Price +2 bonus.

\textbf{Teleporting:} This ability can be imbedded only in weapons that can be 
thrown. A teleporting weapon returns through the Astral Plane to the creature that 
threw it. It teleports into the throwing creature's empty hand in the round following 
the round when it was thrown, just before that creature's turn. It is therefore 
ready to use again on that turn.

Faint psychoportation; ML 5th; Craft Psionic Arms and Armor\textit{, psionic dimension 
door; }Price +1 bonus.

\vspace{12pt}
COGNIZANCE CRYSTALS

\textit{Cognizance crystals }store power points that psionic characters can use 
to pay for manifesting their powers.

\textbf{Physical Description: }A \textit{cognizance crystal }consists of a core 
crystal and two or three smaller crystals arranged in specific positions around 
it on strands of silver wire. The crystals give off a faint glow. A typical \textit{cognizance 
crystal }weighs approximately 1 pound, has AC 7, 10 hit points, a hardness of 8, 
and a break DC of 16.

\textbf{Activation:} The user must merely hold or have a crystal on her person 
for a period of at least 10 minutes (which is long enough to attune oneself to 
the crystal). Thereafter, the owner can use power points stored in the crystal 
to manifest powers she knows.

The maximum number of points a \textit{cognizance crystal }can store is always 
an odd number and is never more than 17. It can store only as many power points 
as its original maximum, set at the time of its creation. When a \textit{cognizance 
crystal's }power points are used up, the glow of the crystal dims. However, the 
user can recharge it by paying power points on a 1-for-1 basis. While doing this 
depletes the user's own power point reserve for the day, those power points remain 
available in the \textit{cognizance crystal }until used.

A user cannot directly replenish her personal power points from those stored in 
a \textit{cognizance crystal, }nor can she draw power points from more than one 
source to manifest a power. See Using Stored Power Points for more information.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.065in}|}{\begin{minipage}[t]{4.065in}\raggedright
\textbf{Table: Cognizance Crystals}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
\textbf{Maximum Power Point Storage}\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.010in}|}{\begin{minipage}[t]{1.010in}\centering
01-90\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
01-40\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
1,000 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
91-100\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
41-74\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
4,000 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{1.010in}|}{\begin{minipage}[t]{1.010in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
75-89\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
01-39\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
9,000 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
90-98\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
40-59\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
7\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
16,000 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
99-100\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60-69\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
9\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
25,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
70-70\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
11\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
36,000 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
80-89\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
13\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
49,000 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
90-95\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
15\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
64,000 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.636in}|}{\begin{minipage}[t]{0.636in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
96-100\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
17\end{minipage}} & \multicolumn{1}{p{1.199in}|}{\begin{minipage}[t]{1.199in}\raggedleft
81,000 gp\end{minipage}}\\
\hline
\end{longtable}

Faint to strong psychokinesis; ML equal to maximum power point storage; Craft Cognizance 
Crystal; Weight 1 lb.

\vspace{12pt}
DORJES

A dorje is a slender crystal that contains a single power. Each dorje has 50 charges 
when created, and each charge expended allows one use of that power. A dorje that 
runs out of charges is just a simple crystal.

\textbf{Physical Description:} A typical dorje is an elongated crystal of one color 
(or colorless), between 8 inches and 10 inches long and about 1/2 inch thick, which 
can weigh up to 1/4 pound. Occasionally, a dorje is decorated with carvings or 
inscribed runes along a face of the crystal. A typical dorje has AC 7, 7 hit points, 
a hardness of 8, and a break DC of 18.

\textbf{Activation:} Dorjes use the power trigger activation method, so manifesting 
a power from a dorje is usually a standard action that does not provoke attacks 
of opportunity. (If the power being manifested has a manifesting time longer than 
1 standard action, however, it takes that long to manifest the power from a dorje.) 
The user must have the power on his class list, even if he knows the command thought. 
Additionally, to activate a dorje, a character must hold it in hand and point it 
in the general direction of the target or area to be affected.

Dorjes are normally created at the minimum manifester level required to manifest 
the power, and powers that can be augmented are not augmented when stored in a 
dorje. A dorje's wielder cannot augment the power contained within the dorje. However, 
dorjes can be created at a higher manifester level than required to manifest the 
power. In this case, the dorje that holds an augmentable power is augmented, to 
the limit of the manifester level and the power's augmentation maximums, if any. 
The manifester level of a dorje cannot be more than five higher than the minimum 
manifester level to use the power it contains.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.161in}|}{\begin{minipage}[t]{4.161in}\raggedright
\textbf{Table: Dorjes}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
\textbf{Power Level}\textsuperscript{\textbf{1}}\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
\textbf{Market Price}\textsuperscript{\textbf{2}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.038in}|}{\begin{minipage}[t]{1.038in}\centering
01-50\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
1st\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedleft
750 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
51-95\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
2nd\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
4,500 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
96-100\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
06-65\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
3rd\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedleft
11,250 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
66-95\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
4th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
21,000 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
96-100\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
06-50\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
5th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
33,750 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
51-70\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
6th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
49,500 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
71-85\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
7th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
68,250 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
86-95\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
8th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
90,000 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.767in}|}{\begin{minipage}[t]{0.767in}\raggedright
95-100\end{minipage}} & \multicolumn{1}{p{0.638in}|}{\begin{minipage}[t]{0.638in}\raggedright
9th\end{minipage}} & \multicolumn{1}{p{0.977in}|}{\begin{minipage}[t]{0.977in}\raggedleft
114,750 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedleft
1 Some dorjes have higher manifester levels than the minimum power level, which 
give them commensurately higher costs.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.740in}|}{\begin{minipage}[t]{0.740in}\raggedleft
2 Any dorje that stores a power with an experience point cost also has an XP cost 
in addition to that noted here.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
POWER STONES

A power stone stores a power (or collection of powers). A stored power can be used 
only once, ``flushing'' the stone. Using a power stone is basically like manifesting 
a power.

\textbf{Physical Description:} A power stone is a thumb-sized chunk of crystal 
that possesses a barely detectable interior glow if it holds a low-level power. 
A stone imprinted with more than one power or a higher-level power glows more brightly, 
but never enough to provide illumination in its own right. A typical power stone 
has AC 7, 5 hit points, a hardness of 8, and a break DC of 20.

\textbf{Activation:} To activate a power stone, a manifester must mentally address 
it, as described below. Once the power is known, the power stone is treated as 
a power completion item, except as noted below.

\textit{Addressing the Stone: }A power stone must be ``addressed'' before a character 
can use it or know exactly what power it contains. Doing this requires a successful 
Psicraft check (DC 15 + power level). Once a particular power stone has been addressed, 
it is not necessary to do so again. Addressing a power stone in advance lets a 
character proceed directly to the next step when the time comes to use it.

Using a stone's stored power after addressing the stone requires holding the stone 
and willing the power's manifestation, as if manifesting a power normally (a standard 
action). Activating a power stone is subject to disruption just as manifesting 
a power normally would be.

Additionally, the user must meet the following requirements.

The user must have the power on his or her class list.

The user must have the requisite key ability score.

If the user meets these requirements and has a manifester level at least equal 
to the power's manifester level, she can automatically manifest the stored power 
without a check. If she meets both requirements but her own level is lower than 
the power stone's manifester level, she has to make a manifester level check (1d20 
+ user's level), against a DC equal to the power stone's manifester level +1, to 
manifest the power successfully. On a failure, the user must succeed on a DC 5 
Wisdom check to avoid brainburn (see below). A natural roll of 1 on this check 
is always a failure.

\textit{Determine Effect: }A power successfully manifested from a power stone works 
exactly as if manifested normally. Assume the power stone's manifester level is 
always the minimum level required to manifest the power for the character who imprinted 
the stone, unless the creator specifically desires otherwise.

A power stone's glow fades when its stored power is flushed.

\textit{Brainburn: }When something goes awry, the user of a power stone improperly 
manifests the stored power. The resultant psionic surge persists for 1d4 rounds, 
unless the power stone is flung farther than 100 feet away or is destroyed. This 
surge deals 1d6 points of damage per power stored per round and arcs across multiple 
targets, similar to \textit{energy current}, except the damage type isn't specified. 
The user is the primary target, and one nearby ally is the secondary target (chosen 
at random).

The manifester level for a standard power stone is the minimum manifester level 
needed to manifest the power (unless otherwise specified).

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{1.705in}|}{\begin{minipage}[t]{1.705in}\raggedright
\textbf{Table: Power Stone Types}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.139in}|}{\begin{minipage}[t]{0.139in}\centering
\textbf{d\%}\end{minipage}} & \multicolumn{1}{|p{0.607in}|}{\begin{minipage}[t]{0.607in}\raggedright
\textbf{Type}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\centering
01-70\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Psion/wilder\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
71-100\end{minipage}} & \multicolumn{1}{|p{0.607in}|}{\begin{minipage}[t]{0.607in}\raggedright
Psychic warrior\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{2.681in}|}{\begin{minipage}[t]{2.681in}\raggedright
\textbf{Table: Powers Imprinted in a Power Stone}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.139in}|}{\begin{minipage}[t]{0.139in}\raggedright
\textbf{Power Stone Type}\end{minipage}} & \multicolumn{1}{|p{1.324in}|}{\begin{minipage}[t]{1.324in}\raggedleft
\textbf{Number of Powers}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.357in}|}{\begin{minipage}[t]{1.357in}\raggedleft
Minor\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
1d3 powers\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Medium\end{minipage}} & \multicolumn{1}{|p{1.324in}|}{\begin{minipage}[t]{1.324in}\raggedleft
1d4 powers\end{minipage}}\\
\hline
% ROW 5
\multicolumn{3}{p{1.496in}|}{\begin{minipage}[t]{1.496in}\raggedleft
Major\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
1d6 powers\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{4.193in}|}{\begin{minipage}[t]{4.193in}\raggedright
\textbf{Table: Power Stone Levels}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.307in}|}{\begin{minipage}[t]{0.307in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
\textbf{Power Level}\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
\textbf{Market Price}\textsuperscript{\textbf{1}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.036in}|}{\begin{minipage}[t]{1.036in}\centering
01-50\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
1st\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedleft
25 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
51-95\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
2nd\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
150 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
96-100\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
06-65\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
3rd\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedleft
375 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
66-95\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
01-05\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
4th\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
700 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
96-100\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
06-50\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
5th\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
1,125 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
51-70\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
6th\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
1,650 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
71-85\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
7th\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
2,275 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
86-95\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
8th\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
3,000 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.757in}|}{\begin{minipage}[t]{0.757in}\raggedright
95-100\end{minipage}} & \multicolumn{1}{p{0.595in}|}{\begin{minipage}[t]{0.595in}\raggedright
9th\textsuperscript{\textbf{2}}\end{minipage}} & \multicolumn{1}{p{0.931in}|}{\begin{minipage}[t]{0.931in}\raggedleft
3,825 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{6}{p{1.342in}|}{\begin{minipage}[t]{1.342in}\raggedleft
1 Any power stone that has an imprinted power with an experience point cost also 
has an XP cost in addition to that noted here.\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.874in}|}{\begin{minipage}[t]{0.874in}\raggedleft
2 Reroll if a level of 7th or higher is indicated for a psychic warrior power stone. 
The maximum level for a psychic warrior power stone is 6th.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
PSICROWNS

A psicrown is a special headband that stores several powers. Unlike dorjes, which 
can contain a wide variety of powers, each psicrown is of a certain kind and holds 
specific powers. Unless otherwise stated, a psicrown has power points equal to 
50 x its manifester level when created. These power points can be spent only on 
the powers that are contained in the psicrown.

\textbf{Physical Description:} A typical psicrown is large enough to fit on the 
head of a Medium creature. Some psicrowns are actually crownlike and heavily adorned, 
while others are simple headbands with crystal centerpieces. All psicrowns weigh 
less than 1 pound. Most psicrowns are metallic, but one could potentially be composed 
of any material. Metallic psicrowns have AC 10, 10 hit points, hardness 8, and 
a break DC of 28. Psicrowns made of psionically reinforced silk have AC 7, 10 hit 
points, hardness 2, and a break DC of 24. Psicrowns can be made from other, more 
exotic materials, but all have at least the strength and durability of psicrowns 
made of psionically reinforced silk.

\textbf{Activation:} Psicrowns use the power trigger activation method, so manifesting 
a power from a psicrown is usually a standard action that does not provoke attacks 
of opportunity. (If the power being manifested, however, has a longer manifesting 
time than 1 standard action, it takes that long to manifest the power from a psicrown.) 
When activating a psicrown, the user spends power points contained in the psicrown 
on any one of the psicrown's powers. Powers activated from a psicrown can be augmented 
with additional power points from the psicrown itself, so long as the total number 
of power points spent does not exceed the user's manifester level. The user can't 
manifest a power from a psicrown using his own power points.

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{4}{|p{3.410in}|}{\begin{minipage}[t]{3.410in}\raggedright
\textbf{Table: Psicrowns}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{4}{p{0.278in}|}{\begin{minipage}[t]{0.278in}\centering
\textbf{Medium}\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textbf{Psicrown}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\centering
01-20\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
01-09\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Dominator}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
20,250 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
21-51\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
10-20\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Evader}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
28,500 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
52-64\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
21-31\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Cautious warrior}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
32,063 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
65-79\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
32-41\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Beast}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
33,750 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
80-89\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
42-58\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Great dominator}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
45,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
90-97\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
59-68\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Astral legion}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
47,250 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
98-100\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
69-78\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Discerning watcher}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
51,469 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
79-89\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Fiery ruin}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
67,500 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
90-97\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Traveler}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
80,156 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{5}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
98-100\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Temporal juggler}\end{minipage}} & \multicolumn{1}{p{1.250in}|}{\begin{minipage}[t]{1.250in}\raggedleft
95,625 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\section*{\textbf{Psicrown Descriptions}}

Psicrowns have immense utility because they pack so many capabilities into one 
item and because they use the wearer's ability score and relevant feats to set 
the DC for saves against their powers.

Unlike with other sorts of psionic items, the wearer can use his manifester level 
when activating the power of a psicrown if it's higher than the manifester level 
of the psicrown. 

The minimum manifester level of a psicrown is 8th. The manifester level of a psicrown 
cannot be more than five levels higher than the minimum manifester level for the 
highest-level power in the psicrown. Standard psicrowns are described below.

\textbf{Astral Legion:} This psicrown has 900 power points. It is made from white 
silk interwoven with crystalline strands of thread. It allows use of the following 
power.

\textit{Astral construct }

Strong metacreativity; ML 18th; Craft Psicrown, \textit{astral construct; }Price 
47,250 gp.

\textbf{Beast:} This psicrown has 450 power points. It is made from a prickly collection 
of bear claws and snake fangs. It allows use of the following powers.

\textit{Claw of energy}

\textit{Duodimensional claw}

\textit{Prevenom}

\textit{Psionic lion's charge}

\textit{Truevenom}

Moderate psychometabolism; ML 9th; Craft Psicrown, \textit{claw of energy, duodimensional 
claw, prevenom, psionic lion's charge, truevenom; }Price 33,750 gp.

\textbf{Cautious Warrior:} This psicrown has 450 power points. It is made from 
a shining iron alloy, similar to the material of a metallic shield. It allows use 
of the following powers.

\textit{Adapt body}

\textit{Body adjustment}

\textit{Precognition, defensive}

\textit{Inertial barrier}

Moderate psychometabolism; ML 9th; Craft Psicrown, \textit{adapt body, body adjustment, 
defensive precognition, inertial barrier; }Price 32,063 gp.

\textbf{Discerning Watcher:} This psicrown has 450 power points. It is made from 
pure transparent crystal. It allows use of the following powers.

\textit{Aura sight}

C\textit{lairtangent hand}

\textit{Clairvoyant sense}

\textit{Darkvision, psionic}

\textit{Remote viewing}

\textit{True seeing, psionic}

Moderate clairsentience; ML 9th; Craft Psicrown, \textit{aura sight, clairtangent 
hand, clairvoyant sense, psionic darkvision, psionic true seeing, remote viewing; 
}Price 51,469 gp.

\textbf{Dominator: }This psicrown has 450 power points. It is made from gray iron 
and is shaped into an intricately fluted crown. It allows use of the following 
powers.

\textit{Charm, psionic}

\textit{Dominate, psionic}

\textit{Suggestion, psionic}

Moderate telepathy; ML 9th; Craft Psicrown, \textit{psionic charm, psionic dominate, 
psionic suggestion; }Price 20,250 gp.

\textbf{Evader:} This psicrown has 400 power points. It is made from silk, usually 
dyed emerald green, with an emerald crystal affixed to the material. It allows 
use of the following powers.

\textit{Catfall}

\textit{Hustle}

\textit{Fly, psionic}

\textit{Freedom of movement, psionic}

\textit{Wall walker}

Moderate psychoportation; ML 8th; Craft Psicrown, \textit{catfall, hustle, psionic 
fly, psionic freedom of movement, wall walker; }Price 28,500 gp.

\textbf{Fiery Ruin:} This psicrown has 750 power points. It is made from reddish 
iron and is shaped into a twisted circlet studded with reddish crystals. It allows 
use of the following powers.

\textit{Energy ball}

\textit{Energy cone}

\textit{Energy missile}

\textit{Energy stun}

\textit{Fiery discorporation}

Strong psychokinesis; ML 15th; Craft Psicrown, \textit{energy ball, energy cone, 
energy missile, energy stun, fiery discorporation;  }Price 67,500 gp.

\textbf{Great Dominator:} This psicrown has 750 power points. It is made from black 
iron without further ornamentation. It allows use of the following powers.

\textit{Charm, psionic}

\textit{Suggestion, psionic}

\textit{Dominate, psionic}

Strong telepathy; ML 15th; Craft Psicrown, \textit{psionic charm, psionic dominate, 
psionic suggestion; }Price 45,000 gp.

\textbf{Temporal Juggler:} This psicrown has 850 power points. It is made from 
silk, usually dyed in several colors, with a clear crystal affixed to the material. 
It allows use of the following powers.

\textit{Temporal acceleration}

\textit{Time hop}

\textit{Timeless body}

Strong psychoportation; ML 17th; Craft Psicrown, \textit{temporal acceleration, 
time hop, timeless body; }Price 95,625 gp. 

\textbf{Traveler: }This psicrown has 750 power points. It is made from silk, usually 
dyed emerald green, with an emerald crystal affixed to the material. It allows 
use of the following powers.

\textit{Astral traveler}

\textit{Dimension door, psionic}

\textit{Teleport, greater psionic}

\textit{Teleport, psionic}

Strong psychoportation; ML 15th; Craft Psicrown, \textit{astral traveler, psionic 
dimension door, psionic greater teleport, psionic teleport; }Price 80,156 gp.

\vspace{12pt}
PSIONIC TATTOOS

Psionic tattoos are designs scribed on the skin that manifest powers on their wearers. 
The wearer doesn't get to make any decisions about the tattoo's effect---the manifester 
who scribed it has already done so.

Psionic tattoos can vary in size, but a creature can wear only a total of twenty 
tattoos at one time---attempting to add one more than this maximum causes all previously 
scribed tattoos to simultaneously activate. A psionic tattoo fades away after use.

\textbf{Physical Description:} A typical psionic tattoo is a colorful pattern of 
tiny, interlacing lines within a larger design. This design can be as simple as 
a circle or a star, or as complex as an artist wishes to make it. Once it is scribed, 
a tattoo's design does not change. A psionic tattoo usually covers an area of skin 
no more than 5 inches in diameter (larger ones could be designed, but would have 
no added effect).

\textbf{Scribing and Transferring Tattoos:} The manifester level of a psionic tattoo 
is the minimum level required to manifest the scribed power. A psionic tattoo can 
contain only powers of 3rd level or lower.

A psionic tattoo inscribed on a wearer is potentially more mobile than a mundane 
tattoo. As a standard action, the wearer can will the tattoo to move to a different 
part of his body or onto the skin of any willing (or unconscious) living creature 
he touches. If the wearer of a psionic tattoo is rendered unconscious or is slain, 
another sentient creature can touch the tattoo while willing it to leave the previous 
wearer and apply itself to the new creature as a standard action. Psionic tattoos 
cannot overlay one another.

\textbf{Identifying Psionic Tattoos: }In addition to the standard methods of identification, 
the wearer of a tattoo can concentrate on it and attempt to gain some sense of 
how it would feel if activated. A successful DC 13 Intelligence check provides 
a hint to the tattoo's effect. 

\textbf{Activation: }A psionic tattoo produces its effect when touched by its wearer 
and willed to do so. This activity, called ``tapping'' the tattoo, is a standard 
action that provokes attacks of opportunity. A psionic tattoo fades away after 
use.

The following rules govern the use of psionic tattoos.

A creature must have an appropriate physical surface on which to scribe the pattern 
(thus, incorporeal creatures or creatures with impermanent flesh, such as fire 
elementals, cannot use psionic tattoos).

Tapping a psionic tattoo provokes attacks of opportunity. A successful attack (including 
grappling attacks) against the wearer forces a Concentration check. A wearer who 
fails this check cannot concentrate effectively on the tattoo to use it. The tattoo 
remains untapped, and the wearer can make another attempt.

A character can trigger the effects of another's psionic tattoo if the other wearer 
is unconscious. It is a full-round action to find, touch, and concentrate on an 
unconscious creature's tattoo in order to tap it. 

The manifester level for a standard psionic tattoo is the minimum manifester level 
needed to manifest the power (unless otherwise specified).

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{3.613in}|}{\begin{minipage}[t]{3.613in}\raggedright
\textbf{Table: Psionic Tattoos}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\centering
\textbf{Minor}\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
\textbf{Medium}\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
\textbf{Major}\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
\textbf{Power Level}\end{minipage}} & \multicolumn{1}{p{0.887in}|}{\begin{minipage}[t]{0.887in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\centering
01-47\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
01-08\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1st\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
50 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
47-100\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
09-75\end{minipage}} & \multicolumn{1}{p{0.652in}|}{\begin{minipage}[t]{0.652in}\raggedright
01-50\end{minipage}} & \multicolumn{1}{p{0.567in}|}{\begin{minipage}[t]{0.567in}\raggedright
2nd\end{minipage}} & \multicolumn{1}{p{0.887in}|}{\begin{minipage}[t]{0.887in}\raggedleft
300 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{6}{p{1.288in}|}{\begin{minipage}[t]{1.288in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
76-100\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
51-100\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
3rd\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
750 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
UNIVERSAL ITEMS

This is a catchall category for any psionic item that doesn't fall into the other 
groups. Anyone can use a universal item (unless specified otherwise in the description).

\textbf{Physical Description:} Varies.

\textbf{Activation: }Usually command thought, but details vary from item to item.

\vspace{12pt}
\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{3}{|p{3.401in}|}{\begin{minipage}[t]{3.401in}\raggedright
\textbf{Table: Minor Universal Items}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{3}{p{0.208in}|}{\begin{minipage}[t]{0.208in}\centering
\textbf{d\%}\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textbf{Item}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\centering
01-04\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Shard }(+1, any one skill)\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
10 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
05-07\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+2, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
40 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
08-10\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Crawling tattoo (any 1st level)\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
50 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
11-14\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crawling tattoo of concussion}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
50 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
15-18\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+3, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
90 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
19-21\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+4, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
160 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
22-24\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+5, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
250 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
25-28\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
Crawling tattoo (any 2nd level)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
300 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
29-31\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Pearl, brain lock}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
300 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
32-35\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+6, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
360 gp\end{minipage}}\\
\hline
% ROW 13
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
36-38\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+7, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
490 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
39-41\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Boots of stomping}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
600 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
42-44\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+8, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
640 gp\end{minipage}}\\
\hline
% ROW 16
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
45-47\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
Crawling tattoo (any 3rd level)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
750 gp\end{minipage}}\\
\hline
% ROW 17
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
48-50\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crawling tattoo of energy bolt}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
750 gp\end{minipage}}\\
\hline
% ROW 18
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
51-53\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Pearl, breath crisis}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
750 gp\end{minipage}}\\
\hline
% ROW 19
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
54-56\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+9, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
810 gp\end{minipage}}\\
\hline
% ROW 20
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
57-59\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Boots of landing }\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
1,000 gp\end{minipage}}\\
\hline
% ROW 21
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
60-63\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionic restraints, lesser}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
1,000 gp\end{minipage}}\\
\hline
% ROW 22
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
64-67\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Shard }(+10, any one skill)\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
1,000 gp\end{minipage}}\\
\hline
% ROW 23
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
68-71\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Pearl, personality parasite}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
1,400 gp\end{minipage}}\\
\hline
% ROW 24
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
72-75\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of knowledge}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
2,500 gp\end{minipage}}\\
\hline
% ROW 25
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
76-79\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of languages}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
2,500 gp\end{minipage}}\\
\hline
% ROW 26
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
80-85\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Eyes of expanded vision}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
3,000 gp\end{minipage}}\\
\hline
% ROW 27
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
86-89\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Gloves of object reading}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
3,000 gp\end{minipage}}\\
\hline
% ROW 28
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
90-92\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Mirror of suggestion}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
3,600 gp\end{minipage}}\\
\hline
% ROW 29
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
93-94\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionic restraints, average}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
6,000 gp\end{minipage}}\\
\hline
% ROW 30
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
95-97\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Torc of free will}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
6,000 gp\end{minipage}}\\
\hline
% ROW 31
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
98-100\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Boots of skating}\end{minipage}} & \multicolumn{1}{p{1.894in}|}{\begin{minipage}[t]{1.894in}\raggedleft
7,000 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{3}{|p{3.633in}|}{\begin{minipage}[t]{3.633in}\raggedright
\textbf{Table: Medium Universal Items}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{3}{p{0.208in}|}{\begin{minipage}[t]{0.208in}\centering
\textbf{d\%}\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textbf{Item}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\centering
01-04\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Psionatrix of clairsentience}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
05-08\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionatrix of metacreativity}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
09-12\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Psionatrix of psychokinesis}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
13-16\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionatrix of psychometabolism}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
17-20\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionatrix of psychoportation}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
21-25\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionatrix of telepathy}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
26-27\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye penetrate}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
8,000 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
28-29\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Mirror of time hop}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
9,000 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
30-31\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of detection}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
32-33\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of discernment}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 13
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
34-35\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of dread}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
36-38\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of psionic craft}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
39-41\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Ring of self-sufficiency}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 16
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
42-43\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of nimbleness}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 17
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
44-45\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye aware}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 18
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
46-47\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye concentrate}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 19
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
48-49\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye gather}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,000 gp\end{minipage}}\\
\hline
% ROW 20
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
50-52\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Eyes of power leech}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,080 gp\end{minipage}}\\
\hline
% ROW 21
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
53-55\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye powerthieve}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,080 gp\end{minipage}}\\
\hline
% ROW 22
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
56-58\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye view}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,180 gp\end{minipage}}\\
\hline
% ROW 23
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
59-61\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of mindarmor}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
10,667 gp\end{minipage}}\\
\hline
% ROW 24
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
62-63\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionic restraints, greater}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
12,000 gp\end{minipage}}\\
\hline
% ROW 25
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
64-65\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Torc of leech freedom}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
12,000 gp\end{minipage}}\\
\hline
% ROW 26
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
66-68\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Gloves of titan's grip}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
14,000 gp\end{minipage}}\\
\hline
% ROW 27
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
69-70\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the claw}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
16,000 gp\end{minipage}}\\
\hline
% ROW 28
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
71-72\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Amulet of catapsi}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
16,200 gp\end{minipage}}\\
\hline
% ROW 29
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
73-74\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the chameleon}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
18,000 gp\end{minipage}}\\
\hline
% ROW 30
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
75-76\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Pearl, mind seed}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
18,500 gp\end{minipage}}\\
\hline
% ROW 31
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
77-78\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Mirror of mind switch}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
19,800 gp\end{minipage}}\\
\hline
% ROW 32
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
79-80\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Eyes of power leech, vampiric}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
20,160 gp\end{minipage}}\\
\hline
% ROW 33
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
81-82\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal mask of insightful detection}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
20,250 gp\end{minipage}}\\
\hline
% ROW 34
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
83-84\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, body}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 35
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
85-86\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, comprehension}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 36
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
87-88\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, creation}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 37
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
89-90\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, energy}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 38
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
91\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, ghost}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 39
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
92-93\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, mind}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 40
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
94-95\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Crystal anchor, travel}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 41
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
96-97\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Psionic restraints, damping}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
% ROW 42
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
98-100\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye sense}\end{minipage}} & \multicolumn{1}{p{2.126in}|}{\begin{minipage}[t]{2.126in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{3}{|p{3.382in}|}{\begin{minipage}[t]{3.382in}\raggedright
\textbf{Table: Major Universal Items}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{3}{p{0.208in}|}{\begin{minipage}[t]{0.208in}\centering
\textbf{d\%}\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textbf{Item}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\centering
01-08\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Skin of the defender}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
32,000 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
09-16\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Torc of power preservation}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
36,000 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
17-24\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textit{Boots of temporal acceleration}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
43,200 gp\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
25-32\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye repudiate}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
43,200 gp\end{minipage}}\\
\hline
% ROW 7
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
33-40\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of fiery response}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
60,000 gp\end{minipage}}\\
\hline
% ROW 8
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
41-49\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the troll}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
61,200 gp\end{minipage}}\\
\hline
% ROW 9
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
50-57\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the hero}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
77,500 gp\end{minipage}}\\
\hline
% ROW 10
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
58-63\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the spider}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
79,080 gp\end{minipage}}\\
\hline
% ROW 11
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
64-72\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of proteus}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
84,000 gp\end{minipage}}\\
\hline
% ROW 12
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
73-80\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye expose}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
112,000 gp\end{minipage}}\\
\hline
% ROW 13
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
81-87\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye conceal}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
120,000 gp\end{minipage}}\\
\hline
% ROW 14
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
88-92\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Third eye dominate}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
120,000 gp\end{minipage}}\\
\hline
% ROW 15
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
93-97\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of iron}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
129,600 gp\end{minipage}}\\
\hline
% ROW 16
\multicolumn{4}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
98-100\end{minipage}} & \multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textit{Skin of the psion}\end{minipage}} & \multicolumn{1}{p{1.874in}|}{\begin{minipage}[t]{1.874in}\raggedleft
151,000 gp\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\section*{\textbf{Universal Item Descriptions}}

Universal items can be configured to do just about anything. 

Standard universal items are described below.

\textbf{Amulet of Catapsi:} This copper amulet aids the wearer against other psionic 
characters. Once per day, the wearer can mentally command the \textit{catapsi }power, 
which blankets a 30- foot-radius area surrounding the wearer in telepathic noise 
for 9 rounds. Each time other psionic characters within this range attempt to manifest 
a power, they must succeed on a DC 17 Will save or pay 4 more points than they 
otherwise would for each power manifestation. The limit on the number of power 
points a subject can spend on a power remains in effect, so the subject may not 
be able to manifest his or her highest-level powers.

Moderate telepathy; ML 9th; Craft Universal Item, \textit{catapsi; }Price 16,200 
gp.

\textbf{Boots of Landing:} These boots allow the wearer to recover instantly from 
a fall and can absorb some damage from falling once per day. The wearer lands on 
her feet no matter how far she falls, and takes 2 fewer dice of damage from the 
fall than normal.

Faint psychoportation; ML 2nd; Craft Universal Item, \textit{catfall; }Price 1,000 
gp; Weight 1 lb.

\textbf{Boots of Skating:} These boots allow the wearer to slide along the ground 
at will as if using the \textit{skate }power.

Faint psychoportation; ML 1st; Craft Universal Item, \textit{skate; }Price 7,000 
gp; Weight 1 lb.

\textbf{Boots of Stomping: }These boots allow the wearer to use \textit{stomp }as 
the power three times per day (Reflex save DC 13) when the wearer stomps her feet. 

Faint psychokinesis; ML 3rd; Craft Universal Item, \textit{stomp; }Price 600 gp; 
Weight 1 lb.

\textbf{Boots of Temporal Acceleration:} These boots allow the wearer to speed 
up his own time frame for 2 rounds as if using the power \textit{temporal acceleration}. 
The wearer can use this power once per day.

Strong psychoportation; ML 15th; Craft Universal Item, \textit{temporal acceleration; 
}Price 43,200 gp; Weight 1 lb.

\textbf{Crawling Tattoos:} Crawling tattoos resemble standard psionic tattoos, 
but their effects are often harmful rather than beneficial. Like a psionic tattoo, 
a crawling tattoo can be scribed only with a power of no higher than 3rd level 
that targets one or more creatures. Exceptions are the \textit{body adjustment 
}power, which can be scribed even though it affects only the manifester, and telepathy 
(compulsion) powers, which cannot be scribed at all. Powers that normally have 
an area affect only one target if scribed in a crawling tattoo. Powers with an 
experience point requirement cannot be scribed into a crawling tattoo. Otherwise, 
crawling tattoos are treated as psionic tattoos until they are activated by the 
wearer.

The wearer of a crawling tattoo can tap the tattoo as a standard action that provokes 
attacks of opportunity, mentally specifying a target (to which the wearer must 
have line of sight). Instead of manifesting its stored power, the tattoo animates, 
drops to the ground, and scuttles toward the target. The original wearer need no 
longer concentrate on the tattoo once animated.

The animated tattoo moves toward its designated target in the same round when it 
is activated. Treat it as a Fine construct that has AC 18, 10 hit points, a hardness 
of 5, speed 30 feet, and a bonus on attack rolls equal to the wearer's manifester 
level + his key ability modifier. Crawling tattoos, unlike true constructs, are 
subject to illusions, darkness, fog, and similar effects. Should the target be 
killed, teleport away, or otherwise absent itself before the animated tattoo reaches 
it, the wearer can reclaim the tattoo. If it is destroyed, a crawling tattoo shatters 
and evaporates.

A crawling tattoo must enter the target's square to attack and thus provokes attacks 
of opportunity as it passes through the target's threatened area. The tattoo makes 
one touch attack  per round thereafter until it strikes its target or is destroyed. 
On a successful attack, the power scribed in the crawling tattoo affects the target 
if the target fails the appropriate saving throw; however, powers that normally 
allow a Reflex saving throw automatically affect the touched target. Crawling tattoos 
can ferry beneficial powers as well as harmful ones, and a target can allow the 
tattoo's touch attack to succeed if he or she desires.

Two examples of crawling tattoos are described below; many more types are possible.

\textit{Market Price: }The cost of a crawling tattoo depends on the level of the 
power scribed in it.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.887in}|}{\begin{minipage}[t]{0.887in}\centering
\textbf{Power Level}\end{minipage}} & \multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1st\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
50 gp\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.887in}|}{\begin{minipage}[t]{0.887in}\centering
2nd\end{minipage}} & \multicolumn{1}{p{0.941in}|}{\begin{minipage}[t]{0.941in}\raggedleft
300 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
3rd\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
750 gp\end{minipage}}\\
\hline
\end{longtable}

\textit{Crawling Tattoo of Concussion}: This crawling tattoo delivers a concussion 
effect, dealing 1d6 points of damage to a creature hit by its touch attack.

Faint psychokinesis; ML 1st; Craft Universal Item, \textit{concussion blast; }Price 
50 gp.

\textit{Crawling Tattoo of Energy Bolt}: Each of these tattoos is keyed to one 
energy type: cold, electricity, fire, or sonic. This crawling tattoo delivers the 
\textit{energy bolt }power, dealing 5d6 points of damage of its energy type.

Faint psychokinesis; ML 5th; Craft Universal Item, \textit{energy bolt; }Price 
750 gp.

\textbf{Crystal Anchor: }A \textit{crystal anchor }is a shaft of transparent crystal 
4 to 5 feet in length, with a sharpened, spearlike head on one end. It ensnares 
the minds of those within range who manifest powers of a specified psionic discipline. 
The triggering discipline is specified at the time of creation.

A \textit{crystal anchor }is activated by plunging the sharp head into the ground, 
leaving the shaft freestanding. It projects an invisible, 30-foot-radius field. 
If a power from the speci- fied discipline is manifested within this range, the 
manifester must succeed on a Will save (DC 15 + power level) or become subject 
to an effect similar to \textit{brain lock}, except that the effect is permanent 
until dispelled or dismissed by the individual who initially drove the \textit{crystal 
anchor }into the earth. Any anchor can be pulled out of the ground and reused at 
a later time.

When a \textit{crystal anchor }successfully ensnares a target, a slender filament 
of insubstantial ectoplasm connects the victim to the shaft, even one outside the 
original area of the field.

A \textit{crystal anchor }can attempt to ensnare a victim only five times per day. 
Previously caught targets can remain caught day after day and do not count against 
this daily limit on attempts.

An anchor's owner can designate certain creatures to be unaffected by the anchor; 
such creatures need not make a saving throw and do not count against the daily 
limit on attempts. One \textit{crystal anchor }can ensnare multiple targets simultaneously, 
and multiple \textit{crystal anchors }can share overlapping fields.

Anchors that activate when a specific power is manifested in range are also possible, 
but are rarer.

A \textit{crystal anchor }has AC 7, 15 hit points, a hardness of 8, and a break 
DC of 20.

\textit{Body Crystal Anchor: }Those who manifest psychometabolism powers are affected 
as described above.

Faint psychometabolism; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, any psychometabolism power; Price 24,000 gp; Weight 3 lb.

\textit{Comprehension Crystal Anchor: }Those who manifest clairsentience powers 
are affected as described above.

Faint clairsentience; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, any clairsentience power; Price 24,000 gp; Weight 3 lb.

\textit{Creation Crystal Anchor: }Those who manifest metacreativity powers are 
affected as described above.

Faint metacreativity; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, any metacreativity power; Price 24,000 gp; Weight 3 lb.

\textit{Energy Crystal Anchor: }Those who manifest psychokinesis powers are affected 
as described above.

Faint psychokinesis; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, any psychokinesis power; Price 24,000 gp; Weight 3 lb.

\textit{Ghost Crystal Anchor: }Those who manifest \textit{remote viewing }are affected 
as described above.

Faint clairsentience; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, \textit{remote viewing; }Price 24,000 gp; Weight 3 lb.

\textit{Mind Crystal Anchor: }Those who manifest telepathy powers are affected 
as described above.

Faint telepathy; ML 5th; Craft Universal Item, \textit{brain lock, psionic contingency}, 
any telepathy power; Price 24,000 gp; Weight 3 lb.

\textit{Travel Crystal Anchor: }Those who manifest psychoportation powers are affected 
as described above.

Faint psychoportation; ML 5th; Craft Universal Item, \textit{brain lock, psionic 
contingency}, any psychoportation power; Price 24,000 gp; Weight 3 lb.

\textbf{Crystal Masks:} Each of the various types of crystal masks fits over the 
face of any Medium or Small humanoid, with slits for eyes and nostrils. The mask 
is transparent, although it distorts the wearer's features. Leather straps attached 
to small holes on the sides of a mask enable the owner to affix the mask to his 
face.

Crystal masks confer special abilities or improved skills on their wearers.

A crystal mask is treated as eyewear or goggles for the purpose of determining 
which items can be worn on the body.

\textit{Crystal Mask of Detection: }The wearer of a \textit{crystal mask of detection 
}can make Search checks with a +10 competence bonus.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Search; Price 10,000 gp; Weight 1/2 lb.

\textit{Crystal Mask of Discernment: }The wearer of a \textit{crystal mask of discernment 
}can make Sense Motive checks with a +10 insight bonus.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Sense Motive; Price 10,000 gp; Weight 1/2 lb.

\textit{Crystal Mask of Dread: }The wearer of a \textit{crystal mask of dread }can 
attempt to frighten other beings to her will. The wearer makes all Intimidate checks 
with a +10 competence bonus. 

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Intimidate; Price 10,000 gp; Weight 1/2 lb.

\textit{Crystal Mask of Insightful Detection: }The wearer of a \textit{crystal 
mask of insightful detection }can make Search checks and Spot checks checks with 
a +9 insight bonus.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 9 ranks 
in both Search and Spot; Price 20,250 gp; Weight 1/2 lb.

\textit{Crystal Mask of Knowledge: }Each of the various \textit{crystal masks of 
knowledge }grants the wearer a +5 competence bonus on a specific type of Knowledge 
check. 

Faint clairsentience; ML 3rd; Craft Universal Item, creator must have 5 ranks in 
the Knowledge skill of the appropriate type; Price 2,500 gp; Weight 1/2 lb.

\textit{Crystal Mask of Languages: }Each of the various \textit{crystal masks of 
language }grants the wearer the ability to speak and write five different languages. 

Faint clairsentience; ML 3rd; Craft Universal Item, creator must have the Speak 
Language skill for each of five languages; Price 2,500 gp; Weight 1/2 lb.

\textit{Crystal Mask of Mindarmor: }A \textit{crystal mask of mindarmor }grants 
the wearer a +4 insight bonus on all Will saving throws.

Faint telepathy; ML 5th; Craft Universal Item, \textit{conceal thoughts; }Price 
10,667 gp; Weight 1/2 lb.

\textit{Crystal Mask of Psionic Craft: }The wearer of a \textit{crystal mask of 
psionic craft }makes all Psicraft checks with a +10 competence bonus.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Psicraft; Price 10,000 gp; Weight 1/2 lb.

\textbf{Eyes of Expanded Vision:} These crystal lenses fit over the user's eyes 
to expand his field of vision. Flanking opponents gain only a +1 bonus when attacking 
the user instead of +2 (rogues still get their full sneak attack damage because 
the wearer is still flanked). The wearer gains a +1 enhancement bonus on Spot checks 
but takes a -2 penalty on saves against gaze attacks.

Faint clairsentience; ML 1st; Craft Universal Item, \textit{ubiquitous vision; 
}Price 3,000 gp.

\textbf{Eyes of Power Leech:} These crystal lenses fit over the user's eyes. Once 
per day, the wearer is able to drain power points from another psionic creature 
or character by meeting its gaze as if using \textit{power leech}. A selected target 
within 40 feet must succeed on a DC 16 Will save, or a connection of crackling 
energy is formed between the wearer and the victim. The connection drains 1d6 power 
points from the target for every round in which the wearer maintains concentration 
(to a maximum of 7 rounds). The wearer gains 1 power point from those drained from 
the target each round (subject to his normal maximum; points he cannot gain immediately 
are lost).

If the wearer has only one lens, the DC of the Will save is 14 instead of 16.

\textit{Eyes of power leech }have no effect on nonpsionic targets or psionic creatures 
with a current power point reserve of 0.

Moderate telepathy; ML 7th; Craft Universal Item, \textit{power leech; }Price 10,080 
gp.

\textbf{Eyes of Power Leech, Vampiric:} As \textit{eyes of power leech, }except 
the wearer gains drained power points from the subject even if doing so would bring 
him over his normal maximum. The wearer of \textit{vampiric eyes of power leech 
}can maintain concentration for up to 13 rounds. Power points the wearer gains 
in excess of his maximum fade after 8 hours if they are not spent before that time.

Strong telepathy; ML 15th; Craft Universal Item, \textit{bend reality, power leech; 
}Price 20,160 gp.

\textbf{Gloves of Object Reading: }While wearing these gloves, the user can learn 
the details of an inanimate object's previous owner if he handles the object, as 
if manifesting the \textit{object reading }power.

Faint clairsentience; ML 1st; Craft Universal Item, \textit{object reading; }Price 
3,000 gp.

\textbf{Gloves of Titan's Grip:} While wearing these oversize gloves, the user 
gains a +8 enhancement bonus on grapple checks. The power is activated when the 
user enters a grapple. The enhancement bonus lasts for a maximum of 7 rounds per 
use, up to three uses per day.

Moderate psychometabolism; ML 9th; Craft Universal Item, \textit{grip of iron; 
}Price 14,000 gp.

\textbf{Mirror of Mind Switch: }This small hand mirror manifests its power once 
per day against a creature that sees its reflection within it, as a gaze attack 
with a range of 30 feet. Potential victims can attempt to avert their eyes or look 
away as they would from a normal gaze attack. A creature meeting its own gaze in 
the mirror must succeed on a DC 19 Will save, or its mind and the mind of the mirror's 
wielder switch, as if by the \textit{mind switch }power. Because the mirror is 
small, only a single creature can meet its own gaze. The wielder of the mirror 
is not affected by seeing himself.

Moderate telepathy; ML 11th; Craft Universal Item, \textit{mind switch; }Price 
19,800 gp; Weight 1/2 lb.

\textbf{Mirror of Suggestion:} This small hand mirror manifests its power up to 
twice per day against creatures that see their reflections within it, as a gaze 
attack with a range of 30 feet. Potential victims can attempt to avert their eyes 
or look away as they would from a normal gaze attack. A creature meeting its own 
gaze in the mirror must succeed on a DC 13 Will save or be affected by a \textit{suggestion 
}chosen by the mirror's wielder. Because the mirror is small, only a single creature 
can meet its own gaze each round. The wielder of the mirror is not affected by 
seeing herself.

Faint telepathy; ML 3rd; Craft Universal Item, \textit{psionic suggestion; }Price 
3,600 gp; Weight 1/2 lb.

\textbf{Mirror of Time Hop: }This small hand mirror manifests its power up to twice 
per day against creatures that see their reflections within it, as a gaze attack 
with a range of 30 feet. Potential victims can attempt to avert their eyes or look 
away as they would from a normal gaze attack. A creature meeting its own gaze in 
the mirror must succeed on a DC 14 Will save or be pushed forward in time by 5 
rounds, as if subject to the \textit{time hop }power. Because the mirror is small, 
only a single creature can meet its own gaze each round. The wielder of the mirror 
is not affected by seeing herself.

Faint psychoportation; ML 5th; Craft Universal Item, \textit{time hop; }Price 9,000 
gp; Weight 1/2 lb.

\textbf{Pearl, Brain Lock:} This tiny pearly sphere speeds toward its target when 
hurled by its owner. He can hurl the pearl at any target within 130 feet that he 
can see and to which he has line of effect. If the target fails a DC 13 Will saving 
throw, the pearl seems to impact and then enter the flesh of the target. The target 
stands mentally paralyzed, as if by \textit{brain lock, }for 3 rounds. The use 
destroys the item. 

Faint telepathy: ML 3rd; Craft Universal Item, \textit{brain lock; }Price 300 gp.

\textbf{Pearl, Breath Crisis:} This tiny pearly sphere speeds toward its target 
when hurled by its owner. He can hurl the pearl at any target within 150 feet that 
he can see and to which he has line of effect. If the target fails a DC 14 Will 
saving throw, the pearl seems to impact and then enter the flesh of the target. 
The target is affected as if by \textit{crisis of breath }for 5 minutes. The use 
destroys the item. 

Faint telepathy; ML 5th; Craft Universal Item, \textit{crisis of breath; }Price 
750 gp.

\textbf{Pearl, Mind Seed: }This tiny pearly sphere instantly takes on the skin 
tone and texture of whatever creature handles it. It speeds toward its target when 
hurled by its owner. He can hurl the pearl at any target within 150 feet that he 
can see and to which he has line of effect. If the target fails a DC 22 Will saving 
throw, the pearl seems to impact and then enter the flesh of the target. The target 
is affected as if by a \textit{mind seed }power, with the pearl's wielder acting 
as the manifester. The use destroys the item.

Strong telepathy; ML 15th; Craft Universal Item, \textit{mind seed; }Cost 6,000 
gp + 2,500 XP; Price 18,500 gp.

\textbf{Pearl, Personality Parasite:} This tiny pearly sphere speeds toward its 
target when hurled by its owner. He can hurl the pearl at any target within 130 
feet that he can see and to which he has line of effect. If the target fails a 
DC 16 Will saving throw, the pearl seems to impact and then enter the flesh of 
the target. The target is affected as if by \textit{personality parasite }for 5 
rounds. The use destroys the item. 

Faint telepathy; ML 7th; Craft Universal Item, \textit{personality parasite; }Price 
1,400 gp.

\textbf{Psionatrix: }Each of these multifaceted crystals is worn as an amulet. 
Unless noted otherwise, a psionatrix adds a +1 enhancement bonus to the save DC 
when the wearer uses powers of the discipline to which the psionatrix is keyed.

\textit{Psionatrix of clairsentience: }Blue light glimmers in this crystal's heart. 

Moderate clairsentience; ML 8th; Craft Universal Item, creator must be a seer; 
Price 8,000 gp.

\textit{Psionatrix of metacreativity: }Green light glimmers in this crystal's heart.

Moderate metacreativity; ML 8th; Craft Universal Item, creator must be a shaper; 
Price 8,000 gp.

\textit{Psionatrix of psychokinesis: }Red light glimmers in this crystal's heart.

Moderate psychokinesis; ML 8th; Craft Universal Item, creator must be a kineticist; 
Price 8,000 gp.

\textit{Psionatrix of psychometabolism: }Violet light glimmers in this crystal's 
heart.

Moderate psychometabolism; ML 8th; Craft Universal Item, creator must be an egoist; 
Price 8,000 gp.

\textit{Psionatrix of psychoportation: }Yellow-red light glimmers in this crystal's 
heart.

Moderate psychoportation; ML 8th; Craft Universal Item, creator must be a nomad; 
Price 8,000 gp.

\textit{Psionatrix of telepathy: }Piercing yellow light shines from this crystal's 
heart.

Moderate telepathy; ML 8th; Craft Universal Item, creator must be a telepath; Price 
8,000 gp.

\textbf{Psionic Restraints:} Each of the various psionic restraints is an iron 
cuff that cunningly locks around the wrist (DC 27 Open Lock check). The cuff limits 
the total number of power points a psionic creature wearing it can use in 1 round 
(regardless of the creature's total power point reserve), or completely damps the 
ability to use psionics. All types of psionic restraints prevent the free manifesting 
of powers.

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
\textbf{Restraint Type}\end{minipage}} & \multicolumn{1}{p{1.146in}|}{\begin{minipage}[t]{1.146in}\centering
\textbf{Allowed Power Points/Round}\end{minipage}} & \multicolumn{1}{p{1.010in}|}{\begin{minipage}[t]{1.010in}\raggedleft
\textbf{Market Price}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Lesser\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
1,000 gp\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedleft
Average\end{minipage}} & \multicolumn{1}{p{1.146in}|}{\begin{minipage}[t]{1.146in}\centering
3\end{minipage}} & \multicolumn{1}{p{1.010in}|}{\begin{minipage}[t]{1.010in}\raggedleft
6,000 gp\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
Greater\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedleft
12,000 gp\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedleft
Damping\end{minipage}} & \multicolumn{1}{p{1.146in}|}{\begin{minipage}[t]{1.146in}\centering
0\end{minipage}} & \multicolumn{4}{p{1.219in}|}{\begin{minipage}[t]{1.219in}\raggedleft
24,000 gp\end{minipage}}\\
\hline
\end{longtable}

Strong psychokinesis; ML 16th; Craft Universal Item, \textit{bend reality, dispel 
psionics; }Weight 1 lb.

\textbf{Psychoactive Skins:} Psychoactive skins (also sometimes called ectoshells) 
are fistsized globs of psionically charged ectoplasm. As a standard action, a psychoactive 
skin spreads over and covers a Medium or smaller creature that projects the proper 
command thought; the same command thought causes the skin to shrink back down to 
its former size. Each of the various psychoactive skins is charged with one of 
a wide array of powers that constantly affect the wearer.

A deployed skin completely covers the wearer and all his equipment like a second 
skin, allowing the wearer to see, hear, and breathe normally. It rolls away from 
various parts of the body as needed, such as when the wearer needs to eat or access 
a backpack. Held items or items specifically excluded are not covered by a psychoactive 
skin.

Up to three skins can be worn simultaneously, although only the outermost is active 
in any given round (the powers of hidden skins cannot be manifested). Skin layers 
can be changed with a command thought as a standard action, which causes a lower-layer 
skin to come to the surface.

\textit{Skin of the Chameleon: }This psychoactive skin adjusts to surrounding textures 
and colors, continually granting the wearer a +10 enhancement bonus on Hide checks.

Faint psychometabolism; ML 3rd; Craft Universal Item, \textit{chameleon; }Price 
18,000 gp; Weight 2 lb.

\textit{Skin of the Claw: }This psychoactive skin benefits only a wearer who has 
levels in psychic warrior. If such a character wears this skin, he can activate 
the \textit{claws of the beast }power at will, as a free action that does not provoke 
attacks of opportunity. He can also dismiss the claws equally quickly.

Faint psychometabolism; ML 4th; Craft Universal Item, \textit{claws of the beast; 
}Price 16,000 gp; Weight 2 lb.

\textit{Skin of the Defender: }This psychoactive skin continually grants the wearer 
a +4 bonus to natural armor.

Faint psychometabolism; ML 5th; Craft Universal Item, \textit{thicken skin; }Price 
32,000 gp; Weight 2 lb.

\textit{Skin of Fiery Response: }This psychoactive skin answers the first attack 
made against the wearer in each round with an automatically manifested and targeted 
``ectoburst'' against the attacker. The burst ejects from the skin on the wearer's 
turn, making a ranged touch attack as described in the \textit{energy retort }power, 
but the energy type chosen is always fire. If the attack hits, the target takes 
2d6 points of fire damage as the ectoburst flames up and is consumed. This attack 
does not in any way hinder the wearer, count against her total actions for the 
round, or provoke attacks of opportunity.

Faint psychokinesis; ML 5th; Craft Universal Item, \textit{energy retort; }Price 
60,000 gp; Weight 2 lb.

\textit{Skin of the Hero: }This psychoactive skin continually grants the wearer 
a +3 deflection bonus to Armor Class, a +3 resistance bonus on all saving throws, 
and a +3 enhancement bonus on attack rolls.

Strong psychometabolism; ML 18th; Craft Universal Item, \textit{bend reality; }Price 
77,500 gp; Weight 2 lb.

\textit{Skin of Iron: }This psychoactive skin affects the wearer as the \textit{psionic 
iron body }power up to three times per day for 15 minutes with each use. When the 
skin's power is not active, it has no protective qualities. Activating the \textit{psionic 
iron body }effect is a standard action that provokes attacks of opportunity.

Strong metacreativity; ML 15th; Craft Universal Item, \textit{psionic iron body; 
}Price 129,600 gp; Weight 2 lb.

\textit{Skin of Nimbleness: }This psychoactive skin continually grants the wearer 
a +10 competence bonus on Tumble checks.

Moderate psychometabolism; ML 8th; Craft Universal Item, creator must have 10 ranks 
in Tumble; Price 10,000 gp; Weight 2 lb.

\textit{Skin of Proteus: }This psychoactive skin continually affects the wearer 
as the \textit{metamorphosis }power. While in a form other than his natural form, 
the wearer does not appear to be wearing the skin.

Moderate psychometabolism; ML 7th; Craft Universal Item, \textit{metamorphosis; 
}Price 84,000 gp; Weight 2 lb.

\textit{Skin of the Psion: }This psychoactive skin grants the wearer 7 bonus power 
points per day and power resistance 21. 

Strong clairsentience; ML 17th; Craft Universal Item, \textit{power resistance; 
}Price 151,000 gp; Weight 2 lb.

\textit{Skin of the Spider: }This psychoactive skin continually grants the wearer 
a +20 competence bonus on Climb checks and continually affects the wearer as the 
\textit{body equilibrium }power. Three times per day, the wearer can manifest \textit{entangling 
ectoplasm }against a target within 30 feet.

Faint psychometabolism; ML 3rd; Craft Universal Item, creator must have 10 ranks 
in Climb, \textit{body equilibrium, entangling ectoplasm; }Price 79,080 gp; Weight 
2 lb.

\textit{Skin of the Troll: }This psychoactive skin continually allows a living 
wearer to heal more quickly. The wearer heals 5 points of damage per minute. Except 
for the slower rate of healing, this skin affects its wearer as if the wearer were 
under the effect of a continual \textit{true metabolism }power. 

Strong psychometabolism; ML 17th; Craft Universal Item, \textit{true metabolism; 
}Price 61,200 gp; Weight 2 lb.

Ring of Self-Sufficiency: This crystalline ring continually grants the wearer a 
+10 competence bonus on Autohypnosis checks.

Moderate psychometabolism; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Autohypnosis; Price 10,000 gp.

\textbf{Shards:} These universal items are tiny fragments of cast-off crystal imprinted 
with minuscule bits of psionic power. Using a \textit{shard }requires grasping 
it and projecting a command thought as a standard action (most \textit{shards }telepathically 
whisper their command word into the minds of living creatures who handle them). 
A \textit{shard }grants a temporary competence bonus on one specific skill, ranging 
from +1 to +10. The granted bonus lasts until the skill is used or 10 rounds pass, 
whichever comes first. Once its effect is activated, a \textit{shard }disintegrates 
immediately, whether or not the bonus granted by the \textit{shard }is eventually 
used.

Moderate psychometabolism; ML 7th; Craft Universal Item, creator must have ranks 
in the specified skill at least equal to the imprinted bonus; Price 10 gp (+1), 
40 gp (+2), 90 gp (+3), 160 gp (+4), 250 gp (+5), 360 gp (+6), 490 gp (+7), 640 
gp (+8), 810 gp (+9), or 1,000 gp (+10). 

\textbf{Third Eyes: }These objects appear as small crystals, always with at least 
one wide, flat facet, and contain a variety of powers. When the owner uses the 
proper command thought, the crystal adheres to the center of his forehead (the 
same command thought causes the \textit{third eye }to disengage). Only one \textit{third 
eye }can be worn at a time.

A \textit{third eye }is treated as eyewear or goggles for the purpose of determining 
which items can be worn on the body.

\textit{Aware: }This kind of \textit{third eye }continually grants the wearer a 
+10 competence bonus on Spot checks.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Spot; Price 10,000 gp.

\textit{Conceal: }While worn, a \textit{third eye conceal }protects the wearer 
from view by all devices, powers, and spells that detect, inf luence, or read emotions 
or thoughts. This power protects against all mind-affecting powers and effects 
as well as information-gathering by clairsentience powers or effects (except for 
\textit{metafaculty}); this item affects the wearer as if he enjoyed the benefit 
of the \textit{psionic mind blank }power.

Strong telepathy; ML 15th; Craft Universal Item, \textit{psionic mind blank; }Price 
120,000 gp.

\textit{Concentrate: }This kind of \textit{third eye }continually grants the wearer 
a +10 competence bonus on Concentration checks. 

Moderate telepathy; ML 7th; Craft Universal Item, creator must have 10 ranks in 
Concentration; Price 10,000 gp.

\textit{Dominate: }The wearer of a \textit{third eye dominate }can attempt to dominate 
a subject as with the power \textit{psionic dominate, }augmented to target any 
creature type it can affect, once per day (save DC 18).

Strong telepathy; ML 15th; Craft Universal Item, \textit{psionic dominate; }Price 
120,000 gp.

\textit{Expose: }The wearer of this kind of \textit{third eye }always knows when 
someone lies directly to him.

Strong telepathy; ML 15th; Craft Universal Item, \textit{bend reality; }Price 112,000 
gp.

\textit{Gather: }This kind of \textit{third eye }continually grants the wearer 
a +10 competence bonus on Gather Information checks.

Moderate clairsentience; ML 7th; Craft Universal Item, creator must have 10 ranks 
in Gather Information; Price 10,000 gp.

\textit{Penetrate: }While worn, a \textit{third eye penetrate }grants the wearer 
a +2 bonus on manifester level checks to overcome a creature's power resistance.

Strong clairsentience; ML 15th; Craft Universal Item, \textit{bend reality; }Price 
8,000 gp.

\textit{Powerthieve: }While worn, a \textit{third eye powerthieve }allows the wearer 
to borrow one power from a psionic target within 40 feet once per day. If the target 
fails a DC 16 Will save, it instantly loses one power of the wearer's choice, and 
the wearer instantly gains temporary knowledge of this power.

The wearer can manifest the borrowed power normally if she has sufficient power 
points to pay for its cost. The wearer retains knowledge of the power for up to 
70 minutes, at which time she loses knowledge of the power and the former owner 
regains it, regardless of the distance between them. If the former owner is dead, 
the wearer still loses the borrowed power.

Moderate telepathy; ML 7th; Craft Universal Item, \textit{thieving mindlink; }Price 
10,080 gp.

\textit{Repudiate: }While worn, this powerful item allows the wearer to manifest 
\textit{dispel psionics }once per day with a +20 modifier on the dispel check (the 
wearer uses the +20 modifier in place of his manifester level).

Strong psychokinesis; ML 20th; Craft Universal Item, \textit{dispel psionics; }Price 
43,200 gp.

\textit{Sense}: The wearer of this kind of \textit{third eye }can manifest \textit{clairvoyant 
sense }at will.

Faint clairsentience; ML 3rd; Craft Universal Item, \textit{clairvoyant sense; 
}Price 24,000 gp.

\textit{View: }The wearer of this kind of \textit{third eye }can spin a quasireal 
version of himself and send it over virtually any distance or into other planes 
of existence, as if manifesting the \textit{remote viewing }power, once per day.

Moderate clairsentience; ML 7th; Craft Universal Item, \textit{remote viewing; 
}Price 10,180 gp.

\textbf{Torc of Free Will:} This item is a band inlaid with precious metal, worn 
around the neck or upper arm. The wearer of a \textit{torc of free will }is not 
affected by the \textit{brain lock }power or items that produce \textit{brain lock 
}effects (such as \textit{crystal anchors}).

A torc is treated as an amulet for the purpose of determining which items can be 
worn on the body.

Faint telepathy; ML 3rd; Craft Universal Item, \textit{brain lock; }Price 6,000 
gp; Weight 2 lb.

\textbf{Torc of Leech Freedom:} This item is a band inlaid with precious metal, 
worn around the neck or upper arm. The wearer of a \textit{torc of leech freedom 
}automatically resists up to two uses of \textit{power leech }against him per day.

A torc is treated as an amulet for the purpose of determining which items can be 
worn on the body.

Faint telepathy; ML 5th; Craft Universal Item, \textit{power leech; }Price 12,000 
gp; Weight 2 lb.

\textbf{Torc of Power Preservation:} This item is a band inlaid with precious metal, 
worn around the neck or upper arm. The wearer of a \textit{torc of power preservation 
}manifests all powers by paying power points equal to the standard cost minus 1 
(minimum of 1).

A torc is treated as an amulet for the purpose of determining which items can be 
worn on the body.

Strong clairsentience; ML 15th; Craft Universal Item, \textit{bend reality; }Price 
36,000 gp; Weight 2 lb.

\vspace{12pt}
CURSED ITEMS

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
\textbf{d\%}\end{minipage}} & \multicolumn{1}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
\textbf{Curse}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
01-33\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Backfire\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.567in}|}{\begin{minipage}[t]{0.567in}\centering
34-66\end{minipage}} & \multicolumn{1}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
Exhausting\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
67-100\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Subversive\end{minipage}}\\
\hline
\end{longtable}

\textbf{Backfire:} The imbedded psionic effect of the cursed item targets the user 
instead of its intended target.

\textbf{Exhausting:} A cursed item of this sort resembles a normal psionic item 
with a power that can be freely activated, but it instead drains the user of power 
points whenever he activates its power. 

\textbf{Subversive: }A cursed item of this sort appears identical to a standard 
psionic item. However, it holds an inner malice for the wearer, whose saving throws 
take a constant -2 penalty. The owner isn't instantly aware of this penalty but 
may become aware after a while, when it becomes clear that he fails saves that 
others make with the same result on the saving throw.

\vspace{12pt}
\section*{\textbf{Specific Cursed Item}}

\textbf{Reverse Capacitor:} A \textit{reverse capacitor }doesn't store power points---it 
drains them, to the surprise and chagrin of a psionic character taken in by its 
resemblance to a \textit{cognizance crystal. }Powers that identify psionic items 
incorrectly identify a \textit{reverse capacitor }as a \textit{cognizance crystal 
}50\% of the time.

A psionic character attempting to use the power points supposedly stored in a \textit{reverse 
capacitor }instead loses 1d6 power points per round for 7 rounds. A crackling arc 
connects the brow of the character with the stone. If the character can put more 
than 40 feet between himself and the \textit{reverse capacitor, }the effect ends. 
If the \textit{reverse capacitor }drains more power points than the psionic character 
possesses, the draining effect ends.

The drained power points are simply lost. Each new attempt to use the power points 
supposedly stored in the \textit{reverse capacitor }initiates the draining effect 
anew.

Strong telepathy; ML 15th; Craft Universal Item, \textit{bend reality, power leech; 
}Price 112,000 gp; Weight 1 lb.

\vspace{12pt}
PSIONIC ARTIFACTS

\section*{\textbf{Minor Artifacts}}

Minor artifacts are not necessarily unique items, Instead, they are psionic items 
that no longer can be made, at least by common mortal means.

\textbf{Sutra of Tranquil Thought:} This monastic tome describes ancient techniques 
of mental focus and is highly prized by psionic practitioners. If a psionic character 
who is not evil studies the work during one week of solitary contemplation, he 
gains 17 bonus power points and experience points sufficient to place him halfway 
into the next level of experience. Those who use their powers for evil are punished 
for their impertinence, losing 5d6 x 1,000 XP for defiling the book. In addition, 
an evil reader must make an immediate DC 15 Will save or become permanently \textit{confused 
}as if affected by the \textit{insanity }power. Only \textit{psychic chirurgery 
}or similarly extreme measures can restore sanity.

The minds of nonpsionic beings are too clouded to benefit from the secrets of this 
book. To anyone without psionic aptitude, the book's pages appear to contain nothing 
but elaborate patterns and drawings of mysterious beings. Once it is read, the 
book vanishes into the Astral Plane to an unknown destination. Even if it is found 
again, the same character cannot benefit twice from perusing its contents.

Strong telepathy; ML 20th; Weight 3 lb. 

\vspace{12pt}
\section*{\textbf{Major Artifacts}}

Major artifacts are unique items---only one of each such item exists. They are 
difficult to find and dangerous to handle, but once found, are often even more 
difficult to destroy. A major psionic artifact has only a single, specific means 
of destruction.

\textbf{Annulus: }This artifact is the ultimate psionic nullifier. Forged to keep 
enemies of vast psionic power at bay, the \textit{Annulus }is an artifact that 
any psionic being should fear. It has been forgotten in the modern age, and merely 
finding it would precipitate a great upheaval across the planes.

The \textit{Annulus }is a 1-foot-diameter ring of silvery material. Tiny slots, 
antennae, spheres, and other intricate projections decorate the exterior of the 
hoop; however, two smoothed lengths of the ring provide an adequate surface for 
grasping the item.

The \textit{Annulus }has several powers, all of which require a wielder to tightly 
grasp the ring with at least one hand. When it is first grasped, knowledge of the 
artifact's powers immediately flood the wielder's mind. The wielder can access 
all powers of the \textit{Annulus }at manifester level 20th.

The \textit{Annulus }generates a continuous \textit{catapsi }effect within a 100-foot-radius 
of the wielder (who is unaffected).

The wielder gains a +4 enhancement bonus on any attempt to resist an effect that 
deals ability damage.

Once per day, the wielder can trigger \textit{ultrablast }as a standard action.

Three times per day, as a standard action, the wielder can trigger an effect similar 
to \textit{psionic dimensional anchor }that affects all creatures in a 50-foot 
radius.

The primary power of the \textit{Annulus, }however, is psionic nullification. Once 
per year, the wielder can trigger this effect as a special action requiring 10 
rounds of continuous concentration to complete. The wielder specifies a target 
or targets within a 100-foot radius, ranging from a specific psionic individual 
or item to a group of psionic beings that share the same philosophy. The nullification 
effect is accompanied by blasts of light, heat, and sound from the \textit{Annulus. 
}Nonpsionic creatures and items are unaffected, as are nontargeted beings, but 
any psionic target---regardless of any protection it may possess---disintegrates 
in a terrific explosion. Nothing is left but floating dust.

It is relatively easy to nullify a single target or a small group of targets, but 
nullifying a more powerful being (such as a demigod or greater entity) or another 
major artifact taxes the \textit{Annulus }to its limits. If it is used to nullify 
such a target, the artifact succeeds but is destroyed in the process and cannot 
be retrieved by any means.

\textbf{Psicrown of the Crystal Mind:} An elaborate crystalline psicrown etched 
with strange designs, this exceptional psicrown is so invested with power that 
it is considered an artifact. 

The power points in the \textit{Psicrown of the Crystal Mind }can be used to manifest 
any of the following powers at manifester level 20th (or at the wearer's manifester 
level if it is higher than 20th).

\textit{Burst}

\textit{Catfall}

C\textit{oncealing amorpha, greater}

\textit{Concussion blast}

\textit{Daze, psionic}

\textit{Detect psionics}

\textit{Dominate, psionic}

\textit{Far hand}

\textit{Float}

\textit{Mindlink}

\textit{Inertial barrier}

\textit{Telekinetic force}

\textit{Telekinetic maneuver}

\textit{Telekinetic thrust}

\textit{Teleport, psionic}

\textit{Thicken skin}

\textit{True metabolism}

The wearer of the \textit{Psicrown of the Crystal Mind }also gains power resistance 
equal to 10 + his manifester level.

The \textit{Psicrown of the Crystal Mind }has 1,000 power points when discovered. 
Anyone who dons the crown instantly knows the number of power points it has at 
the current time. The crown recharges itself, gaining back 1 power point per day 
if it currently has fewer than 1,000 points.

As a special one-time use of the psicrown, the wearer can channel all the remaining 
charges in the psicrown into an uncontrolled burst of energy. The wearer triggers 
this use as a standard action. All within 20 feet of the wearer take hit points 
of damage equal to half the power points left in the staff (Reflex DC 18 half). 
The wearer inhabits a tiny eye of calm at the center of the destruction and is 
unharmed, but the psicrown is reduced to a burned-out cinder.

\vspace{12pt}
{\LARGE CREATING PSIONIC ITEMS}

To calculate the costs involved in creating a psionic item, refer to Creating Magic 
Items. Although that information deals with magic items, the price formulas presented 
there are identical to those for psionic items.

Creating psionic armor and psionic weapons is almost identical to the requirements 
for creating magic armor and magic weapons\textit{.}

\section*{\textbf{Creating Dorjes}}

To create a dorje, a character needs a small supply of materials, the most obvious 
being a chunk of crystal or the crystal shards of the dorje to be carved from or 
assembled. The cost of the materials is subsumed in the cost of creating the dorje---375 
gp x the level of the power x the level of the manifester. Dorjes are always fully 
charged (50 charges) when created.

If an augmentable power is incorporated into a dorje at a higher manifester level 
than the minimum level required to manifest the power, each discharge of the power 
from the dorje is augmented to the limit of that higher manifester level. Alternatively, 
if you want to have a higher manifester level in the dorje, you must pay for the 
dorje as if the power was one level higher for each additional two manifester levels 
you want. 

The creator must know the power or powers to be imprinted in the dorje (or must 
have the power available in some other form). If manifesting the power would reduce 
the manifester's experience point total, she pays the cost (multiplied by 50) upon 
beginning the dorje in addition to the experience point cost for making the dorje 
itself. The act of working on the dorje costs a number of power points per day 
equal to the power point cost of the power that is being embedded in the crystal 
of the dorje.

Crafting a dorje requires one day for each 1,000 gp of the base price.

Item Creation Feat Required: Craft Dorje.

\section*{\textbf{Creating Power Stones}}

To create a power stone, a character needs a supply of incense and fine etching 
tools, the cost of which is subsumed in the cost of encoding the power stone---12.5 
gp x the level of the power x the level of the manifester. All materials used to 
imprint a power stone must be fresh and unused. A character must pay the full cost 
for encoding each power stone no matter how many times she previously has imprinted 
the same power.

The creator must know the power or powers to be imprinted in the power stone (or 
must have the power available in some other form). If manifesting the power would 
reduce the manifester's experience point total, she pays the cost upon beginning 
the power stone in addition to the experience point cost for making the power stone 
itself. The act of encoding triggers the power as if it had been manifested, costing 
the character an appropriate number of power points.

Encoding a power stone requires one day for each 1,000 gp of the base price.

Item Creation Feat Required: Imprint Stone. 

\section*{\textbf{Creating Psicrowns}}

To create a psicrown, a character needs a supply of materials, the most obvious 
being a circlet, crown, or the pieces of the crown to be assembled. The cost of 
the materials is subsumed in the cost of creating the psicrown---375 gp x the level 
of the highest-level power x the level of the manifester, + 75\% of the value of 
the next highest-level power (281.25 gp x the level of the power x the level of 
the manifester), + one-half of the value of any other powers (187.5 gp x the level 
of the power x the level of the manifester). Psicrowns are always created with 
full power points.

Alternatively, if you want to have a higher manifester level in the psicrown, you 
must pay for the psicrown as if the highest-level power is one level higher for 
each additional two manifester levels you want.

The creator must know the power or powers to be imprinted in the psicrown (or must 
have the power available in some other form). If any of the powers has an XP cost, 
the creator must provide XP equal to 50 x that cost. This expense is in addition 
to the experience point cost for making the psicrown itself. The act of working 
on a psicrown costs a number of power points per day equal to the cost of manifesting 
each of the powers associated with the psicrown once per day.

Crafting a psicrown requires one day for each 1,000 gp of the base price.

Item Creation Feat Required: Craft Psicrown.

\section*{\textbf{Creating Psionic Tattoos}}

The creator of a psionic tattoo must have a patch of uncovered skin free of hair 
and fur, and at least a few containers in which to mix dyes. In addition, he needs 
special materials, usually to create dyes. The costs for materials and dyes are 
subsumed in the cost for scribing the psionic tattoo--- 25 gp x the level of the 
power x the level of the manifester. All ingredients and materials used to scribe 
a psionic tattoo must be fresh and unused. The character must pay the full cost 
for scribing each psionic tattoo. (Economies of scale do not apply.)

The user of the psionic tattoo is both the manifester and the target; therefore, 
powers that target another creature\textit{ }cannot be stored in psionic tattoo 
form. Powers with a range of personal can be made into psionic tattoos, but they 
cost double the price of standard psionic tattoos.

The creator must know the power to be placed in the psionic tattoo (or must have 
the power available in some other form). If manifesting the power would reduce 
the manifester's XP total, he pays the XP cost upon beginning the scribing in addition 
to the experience point cost for making the psionic tattoo itself. The act of scribing 
triggers the power as if it had been manifested, costing the character an appropriate 
number of power points.

Scribing a psionic tattoo requires one day.

Item Creation Feat Required: Scribe Tattoo.

\section*{\textbf{Creating Universal Items}}

To create a universal item, a character usually needs some sort of equipment or 
tools to work on the item. He also needs a supply of materials, the most obvious 
being the item itself or the pieces of the item to be assembled. The cost for the 
materials is subsumed in the cost for creating the item. Universal item costs are 
difficult to formularize. Refer to Table: Estimating Magic Item Gold Piece Values\textit{ 
}and use the given item prices as a guideline. Creating an item costs half the 
market value listed.

If powers are involved in the prerequisites for making the item, the creator must 
know the power to be placed in the item (or must have the power available in some 
other form). Any experience point cost for a prerequisite power is not incurred 
by the creator of the item. The act of working on the item requires a payment of 
power points appropriate to the power or powers associated with the item during 
each day of the item's creation.

Crafting a universal item requires one day for each 1,000 gp of the base price.

Item Creation Feat Required: Craft Universal Item.

\vspace{12pt}
{\LARGE SPECIAL MATERIALS}

In addition to psionic items with imbedded powers, some substances have innate 
special properties.

\textbf{Crystal, Deep: }Deep crystal is crystal of above-average quality found 
at the hearts of large veins or deposits of mundane crystal (see below). Deep crystal 
is renowned for its strength and its psionically resonant nature. Mundane crystal 
is used for many items of psionic manufacture, such as dorjes, power stones, and 
psicrystals. Deep crystal is a better grade.

While a weapon made of deep crystal is no different from a mundane crystal weapon 
for a nonpsionic character, a psionic wielder of a deep crystal weapon can focus 
psionic power through it, increasing the damage that weapon deals. As a free action 
that does not provoke attacks of opportunity, the wielder can channel psionic power 
into a melee weapon or ranged weapon made of deep crystal. For 2 power points, 
the deep crystal weapon deals an extra 2d6 points of damage. The weapon will stay 
charged for 1 minute or until it scores its next hit. Bows, crossbows, and slings 
bestow this power on their ammunition. All missile weapons lose this effect if 
they miss. However, they may be recovered and charged again.

Any weapon made of deep crystal costs 1,000 gp more than its noncrystal counterpart. 
Any item could potentially be made out of deep crystal. Because deep crystal armor 
is considered to be made out of metal, druids cannot wear it.

Deep crystal has 30 hit points per inch of thickness and a hardness of 10.

\textbf{Crystal, Mundane:} Mundane crystal can be used in place of metal in weapons 
or armor, using a special forging process. The fortified crystal possesses the 
properties of a similar masterwork steel weapon or armor, except for visual appearance.

Weapons and armor made of mundane crystal cost the same amount to make as their 
masterwork counterparts. Any item could potentially be made with mundane crystal. 
Because mundane crystal armor is considered to be made out of metal, druids cannot 
wear it.

Mundane crystal properly forged has 25 hit points per inch of thickness and a hardness 
of 8.

\end{document}
