%What it does: The Gadgeteer builds things, then activates those things so as to use them to solve problems. Often using them in combat, in fact. It has quite a few recipes, and can have a bundle of things active at any one time, so is sort of a problem solver, but is likely to stick with a few main shticks for many encounters.

%What it doesn't do: this isn't an Alchemist, so making expendable items isn't actually part of the deal. It also isn't any old mad scientist -- the Doctor Frankenstein routine is better handled with a necromancer of some kind or a Puppeteer. Likewise it doesn't do genetics and breed super-soldiers -- I don't think that is even something we really want in the game. Also, while it builds many things, most of which are based of specific methods of power and thus similar components, it doesn't actually make hundreds of components and then make things based on those recipes. That's fun in PC games, not in D&D. That all said...

\newcommand{\gadgetdesc}[3]{\noindent\underline{#1} [#2]

\noindent\desc{#3}}


\classname{The Gadgeteer}

\quot{``When my Armageddon Clock is complete, no-one will ever again laugh at me!''}

\desc{\ability{Alignment:}{Any.}

\ability{Starting Age:}{As Rogue}

\ability{Starting Wealth:}{I don't actually care}}

\desc{\ability{Hit Die:}{d8}

\ability{Skill Points:}{6+Int}

\ability{BAB:}{3/4}

\ability{Good saves:}{Fort and Ref}}

\ability{Class Skills:}{Appraise, Bluff, Concentration, Craft, Decipher Script, Disable Device, Jump, Knowledge (Any), Search, Sense Motive, Spot, Use Magic Device.}

\begin{tabular}[h]{|l|l|l|l|}
\hline
\textbf{Level} &\textbf{Special} &\textbf{Daily Blueprints Known} &\textbf{Charged Blueprints Known}\\
\hline
1 &Gadgetry, Coax Device &1 &2\\
\hline
2 &Invention &2 &2\\
\hline
3 &Evasion &2 &3\\
\hline
4 &Good Gadgets &3 &4\\
\hline
5 &Invention, Duct Tape &4 &4\\
\hline
6 &Confuse Magic Device &4 &5\\
\hline
7 &Specialty Field &5 &5\\
\hline
8 &Greater Gadgets &6 &6\\
\hline
9 &Invention &6 &7\\
\hline
10 &Crafted Companion &7 &7\\
\hline
11 &Rapid Rebuild &8 &7\\
\hline
12 &Giga Gadgets &9 &8\\
\hline
13 &Invention, Percussive Maintenance &9 &9\\
\hline
14 &Specialty Field &9 &10\\
\hline
15 &Command Magic Device &10 &10\\
\hline
16 &Galactic Gadgets &11 &11\\
\hline
17 &Invention, Throw a Spanner at it &11 &12\\
\hline
18 &Stronger, Faster, More Expensive &12 &12\\
\hline
19 &Cybernetic Soldier &13 &12\\
\hline
20 &The Grand Contraption &13 &13\\
\hline
\end{tabular}

\noindent{The following are class abilities of the Gadgeteer:}

\ability{Weapon and Armor Proficiencies:}{Gadgeteers are proficient with simple weapons and any weapons built as a Gadget. They are proficient with light and medium armor, as well as any armor built as a Gadget.}

\ability{Gadgetry (Ex):}{\desc{The Gadgeteer is able to create Gadgets. As he gains levels, he learns more blueprints (according to the table). Some are ``Daily'' -- the preparation involved means they are set up at the beginning of the day (requiring an hour in total) and then once used, are unavailable for the rest of the day. Others are simpler, and can be used essentially at will, as long as they are charged (covered in the item description). Making multiples of the same thing does not allow more uses, for reasons unknown.}}

\noindent\desc{Any save DC is 10 + half level + Int modifier. Anything that scales with level uses the character level.}

\noindent{Pick from this list:}

\begin{list}{$\bullet$}{\itemspace}
\item Flamethrower [Daily] -- area fire damage and smoke cloud
\item Shotgun [Daily] -- area damage and deafening, 2 shots
\item Mining Drill [Daily] -- tunnel out a large area/damage
\item Hover Pack [Daily] -- decent duration of hovering/levitating
\item Dynamite [Daily] -- large area of damage, more to structures
\item Shock Staff [Charged] -- zap enemies like a taser
\item Glider [Charged] -- glide instead of falling
\item Launch Boots [Charged] -- big jumps
\item Harpoon [Charged] -- ranged stab + grappling hook effect
\item Steam Spray [Charged] -- small area fire damage
\item Wind-up Flare Lantern [Charged] -- blind foes/light area
\item Proximity Detector [Charged] -- trapsense and blindsense
\end{list}

\ability{Coax Device (Su):}{The Gadgeteer can always take 10 on Use Magic Device and Disable Device checks, even if threatened, rushed or on fire.}

\ability{Inventions (Ex):}{Any time the Gadgeteer becomes able to make an Invention, he may base it on anything he currently holds a blueprint to -- at the time of gaining the ability (so they cannot be stored up for later levels to cash them all in for Galactic Gadgets). An Invention takes twice as long to build, but grants one of the following benefits when equipped, not counting as a magic item for the limit:}

\begin{list}{$\bullet$}{\itemspace}
\item +1/3 levels Enhancement bonus to Int (round up)
\item +1/4 levels Deflection bonus to AC (round up)
\item +1/3 levels Resistance bonus to saving throws (round up)
\item +1/4 levels Enhancement bonus to all attack rolls (round up)
\item Damage Reduction 1/2 levels, overcome by Adamantine (round up)
\end{list}

\noindent{Additionally it may be used twice per day if a Daily, or truly at will without charging if Charged.}

\ability{Evasion (Ex):}{At third level the Gadgeteer gets Evasion.}

\ability{Good Gadgets:}{At level 4, the Gadgeteer starts to learn blueprints for Good Gadgets:}

\begin{list}{$\bullet$}{\itemspace}
\item Pressure Jetpack [Daily] -- fly for a bit
\item Gatling Gun [Daily] -- lots of shootan
\item Cannon [Daily] -- one big blast
\item Defibrillator [Daily] -- bring someone back from the verge of death
\item Cog Powered Fist [Charged] -- it's a power fist
\item Frost Blaster [Charged] -- cold damage/slow enemies
\item Lightning Rod [Charged] -- lightning bolt
\item Jetskates [Charged] -- move really fast
\item Spy Balloon [Charged] -- sort of a scrying deal
\item Flashbang Generator [Charged] -- blinds and deafens enemies
\end{list}

\ability{Duct Tape (Sp):}{At level 5, the Gadgeteer gains the ability to perform quick repairs on things. He may cast \spell{mending}, \spell{make whole} and \spell{repair light damage} at will, with a caster level equal to his character level.}

\ability{Confuse Magic Device (Su):}{At level 6, the Gadgeteer gains the ability to confuse magic items with an Use Magic Device check. If it possesses charges, adding +10 to the DC can activate the item without using a charge (this does not apply to single-use items). If it casts a spell that deals a type of damage, or grants protection against a type of damage, this can be changed for that use by adding +5 to the DC. It can be Widened or Extended by adding +5 to the DC as well. Finally, traps that use a magic form of detection are not triggered by the Gadgeteer.}

\ability{Specialty Field (Ex):}{At levels 7 and 14, the Gadgeteer gains a specialty field. This is an area of expertise with the type of Gadget in question. The benefits depend on the field chosen:}

\begin{list}{$\bullet$}{\itemspace}
\item Energy: all Fire/Electricity/Light damage dealt by Gadgets is Empowered (multiplied by 1.5)
\item Locomotion: any movement speeds or teleport ranges are doubled
\item Durability: any Gadget has twice as many HP and +10 to Hardness, which means fuck-all for ray guns but is awesome for steam tanks.
\item Efficiency: any non-instantaneous duration is multiplied by 1.5 (round up)
\item Destruction: all damage except for Fire/Electricity/Light dealt by Gadgets is Empowered.
\item Overcharge: any areas of effect are doubled in size.
\item Homing: Gadgets ignore soft cover and any Concealment less than total, and may re-roll failed Miss Chances.
\end{list}

\ability{Greater Gadgets:}{At level 8, the Gadgeteer starts to learn the blueprints for Greater Gadgets:}

\begin{list}{$\bullet$}{\itemspace}
\item Cog Staff [Daily] -- generate an ``I can't believe it's not magic'' effect
\item Teleport-Pump [Daily] -- teleport
\item Toxic Incense Burner [Daily] -- create a poison cloud
\item Boiler-Powered Armour [Daily] -- have an hour of awesomeness
\item Wand-Gatler [Charged] -- fire many wands, pewpewpew
\item Aero-Amplifier [Charged] -- sonic damage and knockdown/knockback
\item Turbo Boost [Charged] -- go really fast for a bit
\item Clockwork Chainsaw [Charged] -- chainsaw, duh
\item Buggy [Charged] -- handy transport/shielding
\item Turbine Laser [Charged] -- charges up, then zots things
\end{list}

\ability{Crafted Companion (Ex):}{At level 10, the Gadgeteer may build a cohort, mount or familiar -- a Construct with a CR at least 3 less than his level. As he levels, he may add to it, to keep the creature's CR up -- or outright disassemble and rebuild into a new form. It takes 8 hours to construct. If it is destroyed, all he needs to do is repair it or build a new one.}

\ability{Rapid Rebuild (Ex):}{At level 11, the Gadgeteer becomes faster at making things he is familiar with. As long as he has built something once in the past, he may rebuild it in half the time it would take to build normally (including his cohort), and can use a full round action to restore 150 HP to any Gadget or Invention.}

\ability{Giga Gadgets:}{At level 12, the Gadgeteer begins to learn blueprints for Giga Gadgets:}

\begin{list}{$\bullet$}{\itemspace}
\item Hurricane Device [Daily] -- create a proper hurricane
\item Disintegration Torch [Daily] -- disintegrate things
\item Mechanical Suit [Daily] -- better than the power armour
\item Mind Control Helmet [Daily] -- mind control
\item Aero-Barrier [Charged] -- shield of air/sound
\item Scalding Mist Generator [Charged] -- a large area of damage
\item Anti-Magic Pressure Generator [Charged] -- AMF
\item Prism Flash Bulb [Charged] -- prismatic spray
\item Shadowcrank [Charged] -- various shadow effects
\item Steam Tank [Charged] -- rumble around in a tank
\end{list}

\ability{Percussive Maintenance (Su):}{At level 13, the Gadgeteer learns how to fix (and damage) objects with a solid kick. With a melee attack that must hit the AC of the target, he may duplicate a \spell{heal} or \spell{harm} effect that only works on Constructs (ignoring any usual immunities to \spell{heal}/\spell{harm} or supernatural effects in general).}

\ability{Command Magic Device (Su):}{\desc{At level 15. the Gadgeteer knows how to command magic devices that don't even belong to him: no Construct will ever attack him, even sentient ones, unless he attacks them first. Furthermore, with a DC (15 + CR of Construct) Use Magic Device check, he may control it (as per Dominate Monster, except it affects the Construct despite immunities, and allows no save) for one minute, after which it cannot be controlled by him again that day.}}

\noindent{Additionally, as a standard action he may activate a magic item somebody else is using or holding, from up to 50 feet away, as long as he is aware of it and targets it. This adds +10 to the activation DC. He may also make an Use Magic Device check as an immediate action (DC = base DC to activate) to prevent it from being used, wasting the attempt.}

\ability{Galactic Gadgets:}{At level 16, the Gadgeteer begins learning blueprints for Galactic Gadgets:}

\begin{list}{$\bullet$}{\itemspace}
\item Doomsday Cannon [Daily] -- stupid high damage
\item Gate-Gun [Daily] -- now you're thinking with portals
\item Timestop Clock [Daily] -- stop time
\item Clockwork Defence Tower [Daily] -- it blasts things
\item Dragonmech [Daily] -- it flies and fries
\item Storm Treadmill [Charged] -- keep running to blast stuff
\item Gravity Pump [Charged] -- it reverses gravity. SCIENCE!
\item Boiler of Untouchability [Charged] -- keeps effects away for a while
\item Binding Box [Charged] -- imprison a creature and keep it in a quantum state of dead/alive
\item Turbine of Death [Charged] -- charges up, then kills everything
\end{list}

\ability{Throw a Spanner at it(Ex):}{At level 17, the Gadgeteer learns how to affect Constructs at a distance. The Percussive Maintenance ability can work with any ranged attack, though actually throwing a construction tool gains a +5 Circumstance bonus to the attack roll.}

\ability{Stronger, Faster, More Expensive (Ex):}{At level 18, the Gadgeteer learns how to make impressive golem bodies for people. With 24 hours and some amount of planar currency, he may transfer someone (even himself) into a body of iron, granting them the following benefits:}

\begin{list}{$\bullet$}{\itemspace}
\item Type: Construct (Augmented (former type) as Subtype)
\item Leave BAB, HP, ability scores (even Con) etc. all the same
\item +6 Enhancement bonus to Strength
\item Double one movement speed
\item Damage Reduction 15/Adamantine
\item Natural weapons overcome DR and Hardness as though made of Adamantine (they are)
\item Not immune to Mind-Affecting Effects
\item Always counts as Exhausted (ignore the immunity to such). A full round action spent winding them up (they can do this to themselves) negates this for one minute.
\end{list}

\ability{Cybernetic Soldier (Ex):}{At level 19, the Gadgeteer adds pieces of gadgetry to himself to become a sort of cyborg. Don't think sleek Shadowrun stuff, he probably has a key in the back of his head. He gains the following benefits:}

\begin{list}{$\bullet$}{\itemspace}
\item Immune to Mind-Affecting Effects
\item Medium Fortification
\item -3 Circumstance Penalty to all Int-based skills unless a standard action is spent winding up or whatever, which turns it into a +3 Enhancement Bonus for one minute.
\item Low-Light Vision and Darkvision 120'
\item Always-on Detect Magic effect
\end{list}

\ability{The Grand Contraption (Ex):}{At level 20, the Gadgeteer wins the game.}


\subsubsection{Gadgets}

\gadgetdesc{Flamethrower}{Daily}
{This device must be wielded in both hands to be used, and requires a Standard action to activate. This creates a 30' cone or 60' line of fire, dealing 1d10 Fire damage per level (Ref half). Those who fail the save catch fire. Additionally, the area is filled with thick smoke that causes Concealment and forces a Fort save to all in the area, against being Nauseated for one round due to choking. It dissipates after 1d4 rounds.\medskip

\noindent This also ignites any unattended flammable objects in the area.}

\gadgetdesc{Shotgun}{Daily}
{This device must be wielded in both hands to be used, and requires an attack action to activate. It can be activated twice before being used up for the day. Each activation deals 1d4 bludgeoning damage per level to a 20' cone (Ref half). Additionally, everyone within 30' must make a Fort save or be Deafened for 1 minute.}

\gadgetdesc{Mining Drill}{Daily}
{This device must be wielded in both hands to be used, and requires a Standard action to activate. It then lasts for one minute, though requires a Standard action to utilise each round. With a Standard action it can destroy an adjacent 5' cube of anything softer than stone, or deal 1d6 piercing damage per 2 levels (round up), ignoring material DR or DR/magic, to a target.\medskip

\noindent As a steam-powered device, this is quite noisy and grants a -10 penalty to Move Silently checks when activated.}

\gadgetdesc{Hover Pack}{Daily}
{This must be worn on the back, and requires a Swift or Immediate action to activate. it then lasts for one hour, causing the wearer to fall slowly (as Featherfall), and hover up to 20' above the ground (though only able to move up to 15' per round in a given direction).}

\gadgetdesc{Dynamite}{Daily}
{This device is small enough to be carried or stored in a pocket, and requires a Swift action to activate. Three rounds later, hopefully with the user nowhere near it, it explodes in a 50' radius spread. This deals 1d10 Fire/Sonic damage per level to all in the area, Ref half, and anyone who fails the save is knocked prone. Additionally, it specifically affects all objects and structures in the area (including individual 5' cubes of terrain), dealing double damage and ignoring Hardness less than that of Steel.}

\gadgetdesc{Shock Staff}{Charged}
{This device can be wielded in one hand, and has reach. It requires a Move Equivalent action to charge up by winding, then holds the charge for up to a minute or until used. A melee touch attack activates it, dealing 1d6 Electricity damage per 2 levels (round up) and requiring the target to make a Fortitude save. If they fail the save, they are Dazed for 1 round.}

\gadgetdesc{Glider}{Charged}
{This device can be folded up to take little space, but must be worn in the Cloak slot to be used. It is effectively charged by any rush of air, so any time you would want to use it, it is going to be charged anyway. This causes the wearer to slowly fall instead of plummeting to their death, at the rate of 10' per round, but they may also move up to 20' per round in any other direction except for up.}

\gadgetdesc{Launch Boots}{Charged}
{These bulky boots must be worn on the feet (duh), and require the user to move 30' or more in order to charge, at which point they remain charged until used, which requires a Move action. Doing so launches them up to 50' in the air (this can be adjusted on use in 10' increments so as to only go, say, 20' up). The jumper may move as far forward as upward. The fall afterwards is treated as though 10' less for the purpose of working out falling damage.}

\gadgetdesc{Harpoon}{Charged}
{This weapon must be wielded in both hands to activate. it requires a Full Round action to fully wind up, and can then be activated at any time with a Swift action, firing out to 60' away. It deals 1d6 piercing damage per level, and if it deals any damage (after DR/Hardness), sticks in firmly, requiring a DC 20 Strength check to remove. A cable attached can be wound up as a Move-equivalent action, allowing the user to either pull himself towards the landing point, or drag a target towards him with an opposed Strength check.}

\gadgetdesc{Steam Spray}{Charged}
{This weapon must be wielded in both hands to activate. It requires one minute to charge up, but will then boil away happily for up to 8 hours or until used up. Charging it provides 3 activations, each one requiring a Standard action. Doing so creates a 20' cone of steam, dealing 1d4 Fire damage per level (Ref half) but also really cleaning the targets, though they may not appreciate it. Failing the save causes a -2 morale penalty to attacks and a -4 morale penalty to AC for 3 rounds.}

\gadgetdesc{Wind-up Flare Lantern}{Charged}
{This device may be freely worn on the shoulder or even on top of a helmet, but takes a free hand to activate or adjust the settings. Winding it up for one minute provides a charge to keep it providing light (as per a Light) spell for one hour or a Daylight effect that even reveals Ethereal/Incorporeal creatures for 10 minutes. At any time a Standard action may be used to end this effect, suddenly using up all the remaining power in one flash. This forces all in 50' to attempt a Fortitude save or be rendered Blind for 1 round per level. Those warned may cover their eyes with a Reflex save.}

\gadgetdesc{Proximity Detector}{Charged}
{This device takes up no slot, whirling around the wearer. If it is moderately windy (enough to potentially knock a lightweight travelling hat off a head or lift a summer dress), this requires no charging at all, otherwise it requires the use of a Swift action every turn to turn a crank that helps the wheels spin.\medskip

\noindent Using sonar echoes, it grants Blindsense out to 15' and Trapsense to the wearer.}

\subsubsection{Good Gadgets}

\gadgetdesc{Pressure Jetpack}{Daily}
{This device must be worn on the back, and requires a Standard action to activate. It then fires a blast of steam, lifting the wearer into the sky and allowing them to Fly with a speed of 40' (Average). This lasts for 1 hour before it runs out of water and overheats, used up for the day. It will sputter and slowly lower to the ground when this happens.}

\gadgetdesc{Oil Spray}{Daily}
{This device can be carried and fired with just one hand, and firing it takes a Standard action. A 40' cone is filled with a fine mist of oil -- the ground is affected as though by Incendiary Slime, as are all people in the area, and all in the area must additionally make a Fortitude save or be Nauseated for 1d4 rounds.}

\gadgetdesc{Gatling Gun}{Daily}
{This device must be carried in both hands when activated, requiring a Full Round action to do so. It then fires for that entire round, and the next two rounds (Standard actions are required to keep control of it for this duration) before finally running out of ammunition. Each round of use, one target of choice within 60' takes 1 hit per 3 levels that each deal 4d6 Piercing damage (Ref negates). For every save passed, the next target behind them (providing they are also in range) is hit and must save, and so on until you run out of targets/range/hits.}

\gadgetdesc{Cannon}{Daily}
{This device can be assembled or taken apart with a Full Round action, but must otherwise be rolled or carried about. To activate, it must be set on the ground, braced and lit, requiring a Full Round action. On the following round it fires, Bullrushing the user with a bonus of +10, and deafening all in 30' on a failed Fort save. However even more damage happens at the other end, where the shot lands: one 40' radius blast is designated up to 250' away, dealing 2d6 Fire/Bludgeoning damage per level to all in the area (Ref half). Those who fail the save are knocked prone, and Stunned for 1 round.}

\gadgetdesc{Defibrillator}{Daily}
{This device can fit inside a regular backpack (barely), but to activate, one component must be held in each hand (assuming two hands), and a Standard action used on an adjacent ally. This causes an incredible bolt of electricity, burning out the mechanisms. This duplicates a Raise Dead spell, but with no level loss, or can stabilise anyone who is Dying.}

\gadgetdesc{Spy Balloon}{Daily}
{This device can easily be stored in a pouch when not in use, then takes only one Full Round action to activate. A small balloon fills with air and starts to drift at the speed of 50' per round, assisted by small nozzles controlled via wire attached to the control box. It has a glass ball connected to a long fibre leading back to a ``screen'' on the control box, as well as a basic speaker system: two horns connected by string. Effectively, it can be controlled out to 1000' and requires a Spot check of DC 10 + class level + Int mod in order to spot. It allows the user to see and hear through it, and pass messages on as well. After two hours of use, however, it runs out of air and must be rewound and stored away, to be refilled and the wires repaired the next day.}

\gadgetdesc{Cog Powered Fist}{Charged}
{This device must be worn on one hand, like a bulky gauntlet, and provides a -3 penalty to skill checks involving that hand. It must be wound up to be activated, requiring a Standard action to provide enough power for five rounds. When powered, it can be used to make Slam attacks that deal 2d6+Str for a Medium creature, with a critical value of 20/x3. It also adds a +6 Enhancement bonus to the wearer's Strength, and grants a Constrict attack of automatic Slam damage.}

\gadgetdesc{Pump-Action}{Charged}
{This device must be wielded in both hands to be used, and requires an attack action to activate. It can be activated eight times before being used up, needed 10 minutes to make another 8 shells, and one Full Round action to load them all in. Each activation deals 1d4 bludgeoning damage per level to a 20' cone (Ref half). Additionally, everyone within 30' must make a Fort save or be Deafened for 1 minute.}

\gadgetdesc{Frost Blaster}{Charged}
{This device is worn as a back-pack, but to be used it also has an attachment that must be wielded in one hand. It has three uses per charge, with a minute required to re-fill it. With a Standard action, it unleashes a very cold spray in a 20' cone. This deals 1d4 Cold damage per level (Fort half), and all who fail the Fortitude save become Entangled for one minute or until exposed to a strong source of heat. Anyone already Entangled instead becomes Slowed for one minute or until exposed to a strong source of heat, and anyone already Slowed becomes Paralysed for one minute or until exposed to a strong source of heat.}

\gadgetdesc{Lightning Rod}{Charged}
{This device can be carried in one hand quite easily. It can be charged either by winding it up to generate power (requiring one Standard action per charge) or by being hit by a source of electricity that would do at least 5d6 Electricity damage (providing one charge). it can hold one charge at a time, and can be discharged with a Standard action. Doing so unleashes a Lightning Bolt (as per the spell), except the damage is uncapped. Additionally, if it is not charged, it will automatically absorb any electricity-based attacks aimed at the wielder (until it is charged).}

\gadgetdesc{Jetskates}{Charged}
{These are worn on the feet like bulky boots. To create a fuel charge requires a minute of work, and they can hold up to three charges at a time. Activating them requires only a Swift action, and allows the user to move at 100' per Move action and skim over water, but they cannot fly. Turning is possible but difficult and stopping is out of the question, as though flying [Clumsy]. Each charge lasts for one round.}

\gadgetdesc{Fuel-Efficient Flamethrower}{Charged}
{This device must be wielded in both hands to be used, and requires a Standard action to activate. This creates a 30' cone or 60' line of fire, dealing 1d10 Fire damage per level (Ref half). Those who fail the save catch fire. Additionally, the area is filled with thick smoke that causes Concealment and forces a Fort save to all in the area, against being Nauseated for one round due to choking. It dissipates after 1d4 rounds.\medskip

\noindent This also ignites any unattended flammable objects in the area. Refilling the device with fuel takes three full rounds.}

\gadgetdesc{Flashbang Generator}{Charged}
{This device is carried as a staff, and holds one charge at a time. It takes three rounds to mix up another charge to load in, but only a Move equivalent action to activate. Activating it creates a bright flash of light (as the Flare Lantern, double the duration) and a loud ``bang'', causing those who pass the save to be Deafened for 2d6 rounds, and those who fail to be Stunned for 1 round and Deafened for 2d6 minutes.}

\subsubsection{Greater Gadgets}

\gadgetdesc{Cog Staff}{Daily}
{This staff must be held in two hands to use properly. It requires a Standard action to activate by twisting, the cogs turning and grinding to produce a charge of energy similar to magic. This burns the cogs out, but creates an Extraordinary effect from the following list:

\listone
\item Shadow Evocation
\item Eyebite (2 or more HD more than inventor: Sickened, within 1 HD of inventor: Panicked and Sickened, 2 or more HD less than inventor: Comatose, Panicked and Sickened)
\item One 10' radius burst in 60' takes 2d6 Fire damage per level (Fort half), with those who fail the save becoming Nauseated for one round
\item Maximised Lightning Leap
\end{list}}

\gadgetdesc{Teleport-Pump}{Daily}
{This fold-out device can be carried in one hand or stored in a pack until unfolded (a Swift action). It then takes a Full Round action to pump up until it sparks, frying the fuse and teleporting the user as per Teleport Without Error.}

\gadgetdesc{Fume Engine}{Daily}
{This device is bulky, but fits in a backpack. It also comes with a gas mask that can be worn on the face to provide immunity to inhaled Poisons and Diseases, as well as gases and smell-based effects. The main device, however, can only be used once per day, with a Swift action to activate. One round later, the engine starts, running for one minute before being empty. For the duration, it creates a 20' radius spread of Poison gas. It obscures vision, granting Concealment to all, but also poisons all who breathe it in (Fort negates). Primary and Secondary damage are both 2d6 Con.}

\gadgetdesc{Boiler-Powered Armour}{Daily}
{This armour must be worn all over the body, except the hands, feet and head. It is treated as Adamantine Full Plate normally, but when activated (a Standard action to start the boiling process, then a one minute wait), it provides 4 hours of uninterrupted power. When powered, the user gains a +6 Enhancement bonus to Constitution, and replaces the Armour bonus with a Deflection bonus to AC. Additionally, they gain a +10 bonus to Break checks and their melee attacks ignore Hardness. As long as at least one full hour remains the remainder may be used up in one burst, granting a +10 Enhancement bonus to Strength and treating the wearer as two size categories larger, both for only one round. It is a Swift action to do this.}

\gadgetdesc{Turbine Laser}{Daily}
{This weapon must be held in two hands, with an additional mount on a shoulder or on the head, consisting of a turbine. It requires some form of breeze to charge, providing one charge per two rounds unless in strong winds where it provides a charge every round, or hurricane force winds, where it provides three charges in one round. It may store up to three charges at a time, and requires an Attack action to fire -- however it can only be fired once per day, the power destroying the laser components.\medskip

\noindent Once activated, it makes a Ranged Touch Attack with a maximum range of 200'. This deals 1d6 untyped energy damage per level and has a regular critical hit (20/x2). If two charges are stored when it is fired, it deals 2d6 damage per level. If three charges are stored when it is fired, it deals 3d6 damage per level.}

\gadgetdesc{Wand-Gatler}{Daily}
{This device can be wielded in one hand, though a second hand is needed to actually turn the handle. One to five wands must be slotted in before use. Turning the handle is a Standard action, and activates all wands at the same time, with the same target/targets/area of effect (or closest match). The magical overload burns the engine out.}

\gadgetdesc{Aero-Amplifier}{Charged}
{This device can be held in both hands or worn around the shoulders. It resembles a giant brass instrument, with one handle. As long as there is even a light breeze or source of sound, a Standard action can be used to squeeze the handle, opening the valves and amplifying the noise and airflow. This creates a 30' cone that deals 1d6 Sonic damage per level (Fort half). All who fail the save are knocked prone and hurled 50' backward, +/- 10' for every size category smaller/larger than Medium. Those who pass the save are merely shoved back 10'.}

\gadgetdesc{Simple-Ammo Gat}{Charged}
{This device must be carried in both hands when activated, requiring a Full Round action to do so. It then fires for that entire round, and the next two rounds (Standard actions are required to keep control of it for this duration) before finally running out of ammunition. Each round of use, one target of choice within 60' takes 1 hit per 3 levels that each deal 4d6 Piercing damage (Ref negates). For every save passed, the next target behind them (providing they are also in range) is hit and must save, and so on until you run out of targets/range/hits.\medskip

\noindent Once it runs out of ammunition, it takes only 10 minutes to make a new chain of ammunition, and a Standard action to load in.}

\gadgetdesc{Turbo Boost}{Charged}
{This device is worn like a vest, clamped onto the torso. It has a key which must be wound to power it up. One Full Round action of winding supplies one minute of power, treating the wearer as though under a Haste effect.}

\gadgetdesc{Clockwork Chainsaw}{Charged}
{This bulky melee weapon must be wielded with two hands, and requires one Full Round action to provide power for three rounds. Up to 9 rounds of power can be charged up at a time. Using it is as simple as making a melee attack, where it has the following profile (treated as a magic weapon):

\listone
\item +1 Adamantine Chainsaw, 3d6+1 (+ Str*1.5) Magical Slashing, 18-20/x3
\item Flesh Tearing: anyone hit by the Chainsaw takes 1 point of Ability Damage to each of Strength, Dexterity and Constitution. This is tripled on a critical hit.
\item Romero Effect: this weapon can score critical hits against corporeal Undead.
\end{list}}

\gadgetdesc{Buggy}{Charged}
{This device cannot be carried (save by a very strong character) but can instead carry four Medium creatures (or any mix that equals the same amount of space). It requires one minute to power up via turning the handle and pouring more basic fuel in, in order to keep it moving for one straight hour. This device has 200 HP and Hardness 15, and provides Full Cover to everyone inside. It trundles along at 100' per round (and cannot run, make double-move actions etc.).\medskip

\noindent Spells such as Heat Metal have an especially intense effect on those inside, causing double damage. Being rammed (requiring a ``ranged'' attack by the driver that does not benefit from Rapid Shot or whatever) deals 2d8+10 bludgeoning damage and a Bullrush at +13 (+8 size, +5 Strength).}

\gadgetdesc{Perpetual Pressure Jetpack}{Charged}
{This device must be worn on the back, and requires a Standard action to activate. It then fires a blast of steam, lifting the wearer into the sky and allowing them to Fly with a speed of 40' (Average). This device somehow recharges itself, using steam power at first, which also turns turbines to store up power, letting it be used at will.}

\subsubsection{Giga Gadgets}

\gadgetdesc{Hurricane Device}{Daily}
{This device requires ten minutes of assembly (if the user doesn't wish to carry around a 20' long pole with a rotor on top), and must be placed on the ground before use. Activating it simply requires turning the handle for one minute, at which point the storm begins. It creates a hurricane with a 2 mile radius, lasting for 6 hours, with a safety zone in the eye of the storm -- a 50' radius spread originating from the device itself. If the device moves, the storm moves, and if the device is disassembled or destroyed, the storm will simply remain in place for the duration.}

\gadgetdesc{Disintegration Torch}{Daily}
{This device can be carried in one hand, and requires only a Standard action to activate. The fuel ignites, sending out a blast of plasma that is hot enough to effectively annihilate whatever it torches. One creature, object or 15' cube of material must be hit with a melee touch attack and, if hit, must succeed on a Fortitude save that affects objects. If they fail the save, they are reduced to a carbon shadow (this is not a [Death] effect). If they succeed, they still take 2d6 Fire damage per level. Should this be enough to kill them, they are also completely destroyed. The heat is even sufficient to destroy [Force] effects.}

\gadgetdesc{Mechanical Suit}{Daily}
{This suit is very similar to the Steam-Powered Armour (above), but is powered by a fuel engine and cogs, and more powerful. It is treated as +3 Adamantine Full Plate normally, but when activated (a Standard action to start the engine), it provides 4 hours of uninterrupted power. When powered, the user gains a +10 Enhancement bonus to Strength and Constitution, and replaces the Armour bonus with a Deflection bonus to AC. Additionally, they gain a +10 bonus to Break checks and their melee attacks ignore Hardness.\medskip

\noindent The wearer is also treated as two size categories larger, gains a 4d8+2*Str Trample, and pumps out smoke. All creatures adjacent to the wearer must pass a Fort save each round or be rendered Nauseated for the round. Additionally, the furnace can blast excess fire out from large shoulder-mounted pipes, dealing 1d10 Fire damage per level in a 30' cone (Ref half, those who fail the save catch fire) as a Standard action.\medskip

\noindent The suit of armour has 300 Hit Points, and only stops functioning when reduced to zero.}

\gadgetdesc{Mind Control Helmet}{Daily}
{Although it isn't subtle, the device is still effective: it consists of a bulky remote that must be held in two hands, and a bulky helmet with an antenna and a key. The helmet, if placed on the head of a creature not immune to [Mind Affecting] effects, must then be activated with a Standard action by turning the key. The wearer is then under the control of whoever has the remote, for up to 4 hours or until the helmet is removed or destroyed, whichever happens first.\medskip

\noindent There is no saving throw against this effect initially, but any time the controller attempts to make them do anything particularly against their personal beliefs/ethics/morality/code, they are entitled to a Will save to resist that command. It requires a Standard action to input a command, and commands cannot be received from further than 100' away.}

\gadgetdesc{Shadowcrank}{Daily}
{This device could fit into a small backpack, and has a large crank attached to a pipe, in turn attached to the device by a cable. Turning the crank for three rounds activates it, sucking darkness in through the plane of shadow and squeezing it out to replicate any of the following effects as an Extraordinary ability:

\listone
\item Mass Invisibility
\item Shadow Conjuration, Greater
\item Shadow Evocation, Greater
\end{list}}

\gadgetdesc{Aero-Barrier}{Charged}
{This device can be worn as a backpack, and has a mouth-piece for activation. Activating it requires a Move-Equivalent action each round, and prevents speaking. Each round that it is activated, it provides a bubble of protection for one full round (thus allowing it to be maintained indefinitely). This bubble extends out to 5' in each direction past the space occupied by the user, and prevents anything from getting in, like a [Force] effect. An opposed check (Strength of intruder against Int of user) can break past this to force entry, though this requires a Standard action. If attacked from outside the Bubble, anything not requiring an Attack roll automatically fails, and against things that do require an attack roll, it is treated as a +10 Deflection bonus to AC.}

\gadgetdesc{Scalding Mist Generator}{Charged}
{This bulky device must be carried in both hands to be activated, and as such, comes with protective clothing in the form of a thick, water-resistant sheet and goggles. Those who forego the goggles, feeling they do nothing, are not protected from the effects.\medskip

\noindent To activate, a mere Swift action is needed to switch it on, however it will take two full rounds for steam to start pouring out. Once this happens, it keeps going for a full minute, creating a 75' radius spread of mist that obscures vision. Additionally, all in the area who are not protected take an automatic 5d4 Fire damage every round (though no ignition occurs). Anyone not wearing protective goggles must also pass a Fort save or be rendered permanently blind as well as suffering a -2 Morale penalty to attacks and -4 Morale penalty to AC for 10 minutes. Those wearing goggles need only save against the penalties. The penalties are a [Pain] effect.}

\gadgetdesc{Anti-Magic Pressure Generator}{Charged}
{This large pump can be carried in one hand, but needs two hands to use. It can be activated with a Standard action, using incredible pressure to force magic out of the area. This creates a 30' radius Anti-Magic Field, however it will reduce by 15' radius per round until ended. Every round that the device is activated, the radius extends by 25', allowing it to slowly grow in size if kept up.}

\gadgetdesc{Prism Flash Bulb}{Charged}
{This device can be mounted on a shoulder or on the head and looks quite pretty, though looking pretty is not the main use. Powder must be loaded into it (a Move-Equivalent action) before it can be activated (a Swift action), and creating the powder only requires a minute of work.\medskip

\noindent When activated, it duplicates an (Ex) Prismatic Spray effect. I know it can banish people to other planes, that sounds pretty extraordinary to me.}

\gadgetdesc{Airship}{Charged}
{This device cannot feasibly be carried, and actually requires 6 full hours to build. Once built, however, it is built to last, with 300 HP and Hardness 10 for the main section of it. It has an engine that must be stoked and filled every 10 minutes to retain power, and generally requires somebody to pilot it, spending a Standard action every round. When active, this device flies with a Fly speed of 150' (Average), and provides Full Cover for those inside, although it does have arrow slits. People may elect to climb up onto the roof so as to leap off, throw things etc. however this requires a Balance check to avoid falling off (10 if sailing smoothly, 15 for some turbulence, 20 for clouds and heavy turbulence, 25 for hurricanes or snowstorms, +10 for being in active combat).\medskip

\noindent It can carry six Medium creatures inside, or any other combination equating to the same.}

\gadgetdesc{Steam Tank}{Charged}
{This device requires 4 hours to build, and only carries up to two Medium creatures. It provides Full Cover to those inside, though it has arrow slits that can be closed, and rumbles along at up to 40' per round. it has 300 HP and Hardness 20, and a +8 Stability bonus to avoid being knocked over. Every ten minutes, the boiler must be attended to (a Standard action) or it will run out of steam and stall. Best of all, a large cannon sits on the top, and can be rotated and fired at any angle, treated as the Good Gadget: Cannon. Crafting more shot and powder takes a full minute, and loading it from inside takes another full minute, so it is a slow process but a safe one.}

\subsubsection{Galactic Gadgets}

\gadgetdesc{Doomsday Cannon}{Daily}
{This device is similar to the Cannon, except three times as large in each dimension, and thus involves more effort to trundle it around. Firing it requires one round to simply get it aimed in the right general vicinity, then a Standard action to fire it afterwards. It can be fired anywhere out to 1 mile away, however cannot be fired at a point within 200 feet of itself. Everything within 500' of the point of impact has an extremely bad day. Everything -- including objects and the ground itself -- must make a Fort save or be obliterated. Even those who pass still take 2d6 Fire/Bludgeoning damage per level and are Stunned for 1 round and permanently Deafened. The terrain is also obliterated, effectively becoming a giant, cracked, smoking crater.}

\gadgetdesc{Gate-Gun}{Daily}
{This device involves a one-handed gun attached to a belt. When fired (a Standard action), the point designated opens up into a Gate, as per the Gate spell. This can be the travel kind [i]or[/i] the broken kind.}

\gadgetdesc{Timestop Clock}{Daily}
{This looks like a simple watch, however a Standard action to halt it shows otherwise. Time is stopped for all but the one who activated it, as per the Timestop spell. If the watch then breaks or is destroyed, the effect ends. Otherwise, in 10 pseudo-rounds, time will resume as the tightly wound springs snap, smashing the watch to pieces.}

\gadgetdesc{20MT Bomb}{Daily}
{This bomb is as large as a Medium creature, and weighs about 500lbs, so may be difficult to carry, but using it is worth the effort. To activate, one merely needs to strike the end of it (a Standard action, or dropping it from a height). At this point, everything within 500' takes 2d6 Fire damage per level (Ref half) and 2d4 Negative levels (Fort half), and everything out to 1 mile takes 1d6 Fire damage per level (Ref half) and 1 Negative level (Fort negates). The 0-500' radius area is then obscured completely by thick smoke for one minute.}

\gadgetdesc{Dragonmech}{Daily}
{This Colossal device can carry only one Large or smaller pilot inside, sadly, and requires a minute to activate. Once activated, it can be controlled for a full hour, with a Fly speed of 100' (Poor). It has Hardness 20, an Armour Class of 35 (+0 Dex, -8 Size, +28 Armour, +5 Deflection), and 300 Hit Points. If used to attack, use the BAB of the pilot, plus the Strength (50) of the Dragon. It has one Primary Bite (4d6+Str*1.5), two Secondary Claws (2d6+Str*.5) and one Primary Tail (3d6+Str*1.5), as well as a breath weapon once per 3 rounds: a 100' cone of fire that deals 2d6 Fire damage per level (Ref half). Additionally, the eyes may fire one Lightning Bolt per 3 rounds, and once per minute it may create an Acid Fog effect beneath it with a Standard action.\medskip

\noindent It also has a payload of six bombs, any number of which can be dropped as one Standard action. They explode like Dynamite upon hitting the ground. The bombs may instead be replaced with a pair of Gatling Guns, though they may not be used if the dragon is unpowered.\medskip

\noindent When unpowered, it still lumbers along with a Fly speed of 50 (Clumsy) and provides the basic protection, but lacks the Deflection bonus, lightning, acid fog and fiery breath, and only has a Strength of 30.}

\gadgetdesc{Storm Treadmill}{Charged}
{This device is fairly large and bulky, taking up most of a 5' square, but being only 1 foot tall. The user may activate it by setting it down and running in place atop it (a Full Round action). Doing so causes a Whirlwind or Storm of Vengeance effect, though the effect ends on the round the user stops running.}

\gadgetdesc{Gravity Pump}{Charged}
{This device can be carried in one hand, but requires both hands and a Standard action to activate. Doing so creates a Reverse Gravity and Vertigo Field effect in a 100' spread, though the user can elect to not include his own occupied space (at time of use) in this area. This lasts until undone by a second activation, or for 10 minutes, whichever comes first.}

\gadgetdesc{Boiler of Untouchability}{Charged}
{This boiler is big and heavy, but can still be carried in both arms. It must be set down to be used, and requires a Swift action to activate, though there is a three round wait as the boiler gets going. It then remains active for one minute, though towards the end of this, a Full Round action can be spent adding more water and fuel to extend it for another minute.\medskip

\noindent While active, a force field is created, creating a safety bubble of 30' radius. Nothing is able to pass through it, and it blocks line of effect.}

\gadgetdesc{Binding Box}{Charged}
{This box is about 1' cubed, and can be carried with little difficulty. Activating it is a Full Round action, twisting the cogs to make them spin. The box opens and whirls, and one designated target within 100' is sucked inside despite the size, and trapped there as though by an Imprisonment effect.\medskip

\noindent Only one creature at a time can be stored there, and when released (a Standard action or the destruction of the device), there is a 50\% chance that they will be dead and a 50\% chance that they will be alive. This is only revealed when actually released -- until that moment they are in a quantum state and cannot be affected by any effect that targets only the dead/undead (such as Resurrection) or only the living.}

\gadgetdesc{Turbine of Death}{Charged}
{This device can barely be carried in both arms, and is quite heavy. To activate, it must be set down and a Swift action spent pulling a lever. It then charges up for three rounds if there is a breeze (two rounds if in strong winds, one round in a hurricane, impossible if there is no breeze). After it has charged, it unleashes on the following round: everyone within 100' except for those actually touching it must pass a Fort save or die instantly.}

\gadgetdesc{Fusion Torch}{Charged}
{This device works exactly like the Disintegration torch, aside from being Charged, except where noted below:

\listone
\item It is effectively unlimited in use, always charged.
\item It can be used with an Attack action.
\item Passing the save still bestows a Negative level on top of the damage.
\end{list}}