\classname{Monk} \label{class:monk}
\vspace{-8pt}
\quot{``I am a Grand Master of Flowers. You are not.''}

\desc{Fantasy literature's view of the ``martial artist'' has about as much to do with a real martial artist as its view of salamanders has to do with real salamanders. But let's face the facts: Monks are totally sweet. They flip out and kill people with their hands. A Monk does not practice any ``real" martial art, we call those people ``Fighters" -- a Monk practices an entirely magical martial art that only works in areas where badgers can talk and winged horses can fly.}

\desc{Every Monk follows a different martial path that involves jumping super high and having glowing things coming off of their hands when they perform their super moves. Some monks use weapons, but most just use their hands and feet to devastating effect. Some Monks shout the names of their techniques in battle to demoralize their opponents, others stay aloof and silent during even the toughest of challenges.}

\ability{Alignment:}{Monks may be of any alignment. Really. If a bar brawl breaks out, some Monks will try to break it up, other Monks will join in. Whatever.}

\ability{Races:}{Because the martial paths of a Monk embrace all manners of comportment, from Stoic Lawfulness to Boisterous Chaos, almost every sapient race has those who take up the monk's path. With its lack of emphasis on ranged weaponry, few of the slower races turn towards these magical combat styles, and halflings and dwarves rarely become monks. The discipline emphasizes physical strength as much as it emphasizes perceptiveness and inner strength, so orcs are as likely to become monks as Kuo-Toa are.}

\ability{Starting Gold:}{2d4x10 gp (50 gold)}

\ability{Starting Age:}{As Monk.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Monk's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Craft (Int), Diplomacy (Cha), Escape Artist (Dex), Hide (Dex), Jump (Str), Knowledge (all skills individually) (Int), Listen (Wis), Move Silently (Dex), Perform (Cha), Profession (Wis), Sense Motive (Wis), Spot (Wis), Swim (Str), and Tumble (Dex).}

\ability{Skills/Level:}{4 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6.5cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &AC Bonus\\
1st &+1 &+2 &+2 &+2 &Armored in Life, Fatal Strike, Willow Step, Fighting Style &+4\\
2nd &+2 &+3 &+3 &+3 &Rain of Flowers, Abundant Leap &+5\\
3rd &+3 &+3 &+3 &+3 &Fighting Style &+5\\
4th &+4 &+4 &+4 &+4 &Diamond Soul &+6\\
5th &+5 &+4 &+4 &+4 &Fighting Style &+6\\
6th &+6/+1 &+5 &+5 &+5 &Walk of a Thousand Steps &+7\\
7th &+7/+2 &+5 &+5 &+5 &Fighting Style &+7\\
8th &+8/+3 &+6 &+6 &+6 &Immaculate Diamond Soul &+8\\
9th &+9/+4 &+6 &+6 &+6 &Master Fighting Style &+8\\
10th &+10/+5 &+7 &+7 &+7 &Leap of the Clouds &+9\\
11th &+11/+6/+6 &+7 &+7 &+7 &Master Fighting Style &+9\\
12th &+12/+7/+7 &+8 &+8 &+8 &Master of the Four Winds &+10\\
13th &+13/+8/+8 &+8 &+8 &+8 &Master Fighting Style &+10\\
14th &+14/+9/+9 &+9 &+9 &+9 &Master of the Four Seasons &+11\\
15th &+15/+10/+10 &+9 &+9 &+9 &Grand Master Fighting Style &+11\\
16th &+16/+11/+11/+11 &+10 &+10 &+10 &Master of Diamond Soul &+12\\
17th &+17/+12/+12/+12 &+10 &+10 &+10 &Grand Master Fighting Style &+12\\
18th &+18/+13/+13/+13 &+11 &+11 &+11 &Perfect Mastery &+13\\
19th &+19/+14/+14/+14 &+11 &+11 &+11 &Grand Master Fighting Style &+13\\
20th &+20/+15/+15/+15 &+12 &+12 &+12 &Grand Master of Flowers &+14\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Monk class.

\ability{Weapon and Armor Proficiency:}{Monks are proficient with all simple weapons, as well any weapon defined as a special monk weapon, such as the sai, the nunchuka, the kama, the shuriken, and the triple staff. Monks are not proficient with any armor or shields of any kind.}

\ability{Armored in Life (Su):}{A Monk has a special Armor bonus whenever they are not using armor or shields that he is not proficient in. This Armor Bonus applies against Touch Attacks and Incorporeal Touch Attacks, and has a value of +4. Every even numbered class level, the Armored in Life bonus increases by 1. If the Monk wears armor which he is proficient in (for example: normal clothing) that has an enhancement bonus, that enhancement bonus applies to his Armored in Life Armor Bonus.}

\ability{Wilow Step (Su):}{A true monk does not seek to outrun the fist, but to anticipate it. If a Monk would be allowed to add his Dexterity modifier to a Reflex Save or Armor Class, he may add his Wisdom bonus (if positive) instead.}

\ability{Fatal Strike (Su):}{A Monk has a natural weapon Slam in addition to whatever else he is capable of doing. As a natural slam attack, if he uses no other natural or manufactured weapons he adds his Strength and a half to damage and may make iterative attacks if he has sufficient BAB. If the slam is used with other weaponry, it becomes a secondary natural attack, suffers a -5 penalty to-hit, and adds only half his Strength modifier to damage. A monk's slam attack does a base of 1d8 damage for a medium sized monk and does more or less damage as appropriate if the Monk is larger or smaller than medium size.}

\ability{Fighting Style (Su):}{At levels 1, 3, 5, and 7, the Monk learns a Fighting Style. Each Fighting style requires a Swift Action to activate, lasts one round, and is usable at will. Each Fighting Style must have a name (see Naming Your Fighting Style below), and provides two bonuses from the Fighting Style Abilities:}

\begin{itemize}\itemspace\begin{small}
    \item{While Active, your Fighting Style provides a +4 Dodge Bonus to AC.}
    \item{While Active, your Fighting Style provides a +4 Dodge Bonus to Saving Throws.}
    \item{While Active, your Fighting Style forces any opponent struck by your slam attack to make a Fortitude Save (DC 10 + \half\  your character level + your Wisdom Modifier) or become stunned for one round.}
    \item{While Active, your Fighting Style allows you to make an attack of opportunity against any opponent who attacks you. This attack of opportunity must be a trip or disarm attempt.}
    \item{While Active, your Fighting Style provides you with concealment.}
    \item{While Active, your Fighting Style provides a +30' Insight Bonus to your movement rate.}
    \item{While Active, your Fighting Style allows your slam attacks to ignore hardness and DR.}
    \item{While Active, your Fighting Style provides any bonuses it gives to your slam attack to any attack you make with any weapon.}
    \item{While Active, your Fighting Style causes your slam attack to inflict piercing damage and to inflict 2 points of Constitution damage.}
    \item{While Active, your Fighting Style causes your slam attack to inflict slashing damage and to reduce your opponent's movement rate by 10' every time they suffer damage from it. This movement rate reduction can be healed like ability damage (treating 5' of movement as 1 point of ability damage).}
    \item{While Active, your Fighting Style allows you to move through occupied spaces as if they were unoccupied and you provoke no attacks of opportunity for your movement.}
\end{small}\end{itemize}

\ability{Rain of Flowers (Su):}{Any time a 2nd level Monk inflicts lethal damage, he may elect to inflict non-lethal damage instead. Any time a Monk inflicts non-lethal damage, he may elect to inflict lethal damage instead.}

\ability{Abundant Leap (Su):}{At 2nd level, a Monk's ability to jump is unbounded by his height. In addition, the DC for any jump check is divided by two.}

\ability{Diamond Soul (Su):}{At 4th level, the Monk gains Spell Resistance equal to 5 + his character level. At 8th level, his soul becomes immaculate and his Spell Resistance improves to 10 + character level, and at 16th level he masters his diamond soul and his spell resistance improves to 15 + character level.}

\ability{Walk of a Thousand Steps:}{Once per day, a Monk of sixth level or higher may activate a Fighting Style and extend its duration to 1 round/level rather than 1 round. Activating this Fighting Style is still a Swift Action. Other Fighting Styles may be activated during this period, though their duration is normally going to be only 1 round.}

\ability{Master Fighting Style (Su):}{At levels 9, 11, and 13, the Monk learns a Master Fighting Style. Each Master Fighting style requires a Swift Action to activate, lasts one round, and is usable at will. Each Master Fighting Style must have a name (see Naming Your Fighting Style below), and provides two bonuses from the Master Fighting Style Abilities. When a Monk gains a new Master Fighting Style, he may replace one of his Fighting Styles with a different Fighting Style.}



\begin{itemize}\itemspace\begin{small}
    \item{While Active, your Master Fighting Style allows you to \spell{teleport} yourself and everything you are physically carrying 60 feet in any direction as a free action usable once per round.}
    \item{While Active, your Master Fighting Style provides total concealment.}
    \item{While Active, your Master Fighting Style transforms your slam attacks into Force effects that inflict Force damage.}
    \item{While Active, your Master Fighting Style affects any creature struck with your slam attack with a \spell{banishment} effect that transports it back to its home plane unless it succeeds at a Will save (DC 10 + \half\  character level + Wisdom Modifier). Outsiders suffer a -4 penalty to their saving throw. A creature so banished, may not return to the plane it was banished from for a year.}
    \item{While Active, your Master Fighting Style forces any creature struck by your slam attack to make a Reflex Save (DC 10 + \half\  character level + Wisdom Modifier) or be helpless for one round.}
    \item{While Active, your Master Fighting Style provides you the effect of an \spell{air walk} spell, and gives you a +20' Competence bonus to your speed.}
    \item{While Active, your Master Fighting Style affects any opponent you successfully trip or bulrush with the violent thrust version of \spell{telekinesis}, with a caster level equal to your character level. There is no saving throw against this effect.}
    \item{While Active, your Master Fighting Style allows you to shoot fire out of your hands or mouth as a standard action. The fire can be shot out to medium range, requires a ranged touch attack, and inflicts 1d6 of fire damage per character level if it hits.}
    \item{While Active, your Master Fighting Style causes your slam attack to inflict vile damage.}
    \item{While Active, your Master Fighting Style forces every creature within 10 feet of you to make a Will save (DC 10 + \half\  character level + Wisdom Modifier) or become panicked for one minute.}
    \item{While Active, your Master Fighting Style affects any target you strike with your slam attack with a targeted version \spell{greater dispelling} with a caster level equal to your character level.}
    \item{While Active, your Master Fighting Style causes 5d6 of Sonic damage to everything within 30 feet of you when you inflict damage with your slam attack against any target. You are immune to Sonic damage while your Master Fighting Style is active.}
    \item{Instead of gaining a Master Fighting Style Ability, you may choose two regular Fighting Style Abilties.}
\end{small}\end{itemize}




\ability{Leap of the Clouds (Su):}{At 10th level, the DC for any jump check is divided by 5.}

\ability{Master of the Four Winds (Su):}{The Monk's breath of life is carried on the winds of fate. At 12th level, if the monk is restored to life, he doesn't lose a level for doing so.}

\ability{Master of the Four Seasons:}{Time passes relentlessly in the world, but for a monk of 14th level, the change of seasons is as no change at all. He no longer appears to age, never accumulates any additional penalties for growing older and will never die of old age.}

\ability{Grand Master Fighting Style (Su):}{At levels 15, 17, and 19, the Monk learns a Grand Master Fighting Style. Each Grand Master Fighting style requires a Swift Action to activate, lasts one round, and is usable at will. Each Grand Master Fighting Style must have a name (see Naming Your Fighting Style below), and provides two bonuses from the Grand Master Fighting Style Abilities. When a Monk gains a new Grand Master Fighting Style, he may replace one of his Fighting Styles or Master Fighting Style with a different Style of the same type. Grand Master Fighting Style Abilities:}

\begin{itemize}\itemspace \begin{small}
    \item{While Active, your Grand Master Fighting Style makes you and everything you are carrying incorporeal, your slam attacks are incorporeal touch attacks.}
    \item{While Active, your Grand Master Fighting Style slows down time to the point where you can act twice each round, you do not gain an extra Swift Action during your extra actions.}
    \item{While Active, your Grand Master Fighting Style allows you to punch a hole through space and time, allowing you to open a travel version of \spell{gate} with a slam attack.}
    \item{While Active, your Grand Master Fighting Style prevents all [Teleport] effects from entering or exiting within 1 mile of your location.}
    \item{While Active, your Grand Master Fighting Style causes your slam attacks to reduce the spell resistance of enemies by an equal amount to the damage the slam attack inflicts.}
    \item{While Active, your Grand Master Fighting Style forces every creature struck with your slam attack to make a Fortitude save (DC 10 + \half\  character level + Wisdom Modifier) or die.}
    \item{While Active, your Grand Master Fighting Style affects any target you strike with your slam attack with a \spell{disintegrate} effect, with a caster level equal to your character level (DC 10 + \half\  character level + Wisdom Modifier).}
    \item{While Active, your Grand Master Fighting Style causes you to regenerate. You recover a number of points of nonlethal damage each round equal to your character level. Unarmed or Slam attacks inflict regular damage.}
    \item{While Active, your Grand Master Fighting Style forces any opponent you strike with your slam attack to make a Willpower save (DC 10 + \half\  character level + Wisdom Modifier) or become \spell{feebleminded}.}
    \item{While Active, your Grand Master Fighting Style affects every target you strike with a slam attack with the violent thrust version of \spell{telekinesis}, with a caster level equal to your character level. There is no saving throw against this effect.}
    \item{Instead of gaining a Grand Master Fighting Style Ability, you may choose two Master Fighting Style Abilties.}
\end{small}\end{itemize}

\begin{table}[tbh]
\begin{small}
\begin{center}
\noindent \begin{tabular}{|ll||ll||ll|}
\multicolumn{6}{l}{Naming your Soulmelds: Roll a d20, or choose}\\
\multicolumn{6}{l}{an adjective, an animal, and a noun:} \\
\hline 1&Running&1&Ox&1&Fist\\
2&Hungry&2&Tiger&2&Stance\\
3&Angry&3&Dragon&3&Spinning Kick\\
4&Naked&4&Crane&4&Attack\\
5&Drunken&5&Monkey&5&Technique\\
6&Fortunate&6&Turtle&6&Style\\
7&Lazy&7&Manticore&7&Dance\\
8&Swift&8&Serpent&8&Movement\\
9&Powerful&9&Hummingbird&9&Touch\\
10&Enlightened&10&Demon&10&Fu\\ \hline
\multicolumn{6}{l}{Note from the authors: Feel free to add any adjectives, animals,}\\
\multicolumn{6}{l}{or nouns that you want.  There's no reason that your character's}\\
\multicolumn{6}{l}{fighting style has to be called ``Naked Tiger Stance" rather than}\\
\multicolumn{6}{l}{``Astonished Centaur Defense''.}\\
\end{tabular}
\end{center}
\end{small}
\end{table}


\ability{Perfect Mastery:}{Once per day, a Monk of 18th level or higher may activate a Fighting Style, Master Fighting Style, or Grand Master Fighting Style and extend its duration to 1 round/level rather than 1 round. Activating this style is still a Swift Action. Other styles may be activated during this period, though their duration is normally going to be only 1 round.}

\ability{Grand Master of Flowers:}{At 20th level, the Monk becomes an Outsider, and immortal of legend. He gains the augmented subtype of his previous type, and has Damage Reduction of 20/Epic.}
