
\classname{True Fiend [Fiend]} \label{class:truefiend}
\vspace*{-8pt}


\quot{``I am a lord of the realms infernal, if I wanted your opinion I would beat it out of you.''}

\desc{Tanar'ri, Baatezu, Yugoloth, Demodand\ldots\  these are the
names that inspire terror throughout the planes, and with good
reason. These True Fiends are far more powerful than the other
denizens of the Dark Realms. These fiends stand above others and are
destined to a life of greatness, to be legendary in the annals of
Evil.}

\desc{These true fiends are good at everything they do, but this doesn't make them more powerful at any particular level than any other fiend. Indeed, level is a measure of power. The most powerful fiends are True Fiends and higher level than Fiendish Brutes. The True Fiend advances in everything all at once, and thus gains new abilities relatively slowly compared to what other, more focused Fiendish progressions are capable of.}

\ability{Alignment:}{Nothing \textit{requires} a True Fiend to be Evil, but
it's\ldots\  highly recommended that they be Evil.}

\ability{Races:}{The True Fiend is \emph{only} available to
Outsiders with a plane of origin in the Lower Planes. Creatures from
the prime material plane whose ancestors were from a Lower Plane may
take this class, but they must have the Outsider type.}

\ability{Starting Gold:}{6d6x10 gp (210 gold)}

\ability{Starting Age:}{Since a True Fiend is immortal and never
ages, a character may claim any starting age she wishes.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The True Fiend's class skills (and the key
ability for each skill) are Bluff (Cha), Climb (Str), Concentration
(Con), Diplomacy (Cha), Disguise (Cha), Escape Artist (Dex), Hide
(Dex), Intimidate (Cha), Knowledge (all skills taken individually)
(Int), Listen (Wis), Move Silently (Dex), Search (Int), Sense Motive
(Wis), Sleight of Hand (Dex), Spellcraft (Int), Spot (Wis), Survival
(Wis), Use Magic Device (Cha), and Use Rope (Dex).}

\ability{Skills/Level:}{8 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{3.5cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Immortality, Fiendish Traits\\
2nd &+2 &+3 &+3 &+3 &Telepathy\\
3rd &+3 &+3 &+3 &+3 &Fiendish Damage Reduction\\
4th &+4 &+4 &+4 &+4 &Sphere\\
5th &+5 &+4 &+4 &+4 &Greater Fiendish Traits\\
6th &+6/+1 &+5 &+5 &+5 &\\
7th &+7/+2 &+5 &+5 &+5 &Greater Fiendish Damage Reduction\\
8th &+8/+3 &+6 &+6 &+6 &Sphere\\
9th &+9/+4 &+6 &+6 &+6 &Summon\\
10th &+10/+5 &+7 &+7 &+7 &\\
11th &+11/+6/+6 &+7 &+7 &+7 &Bonus Feat\\
12th &+12/+7/+7 &+8 &+8 &+8 &Sphere\\
13th &+13/+8/+8 &+8 &+8 &+8 &Greater Fiendish Damage Reduction\\
14th &+14/+9/+9 &+9 &+9 &+9 &\\
15th &+15/+10/+10 &+9 &+9 &+9 &Greater Summoning\\
16th &+16/+11/+11/+11 &+10 &+10 &+10 &Sphere\\
17th &+17/+12/+12/+12 &+10 &+10 &+10 &Dark Power\\
18th &+18/+13/+13/+13 &+11 &+11 &+11 &\\
19th &+19/+14/+14/+14 &+11 &+11 &+11 &Epic Damage Reduction\\
20th &+20/+15/+15/+15 &+12 &+12 &+12 &Sphere\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the True Fiend class.

\ability{Weapon and Armor Proficiency:}{True Fiends are proficient with all simple and martial weapons, as well as the whip, the scourge, and the dire flail. True Fiends are proficient with light armor but not with shields of any kind.}

\ability{Immortality (Ex):}{Like a pizza on the counter, the True
Fiend only gets worse with age.}

\ability{Fiendish Traits:}{A True Fiend is a member of one of the
iconic aristocracies evil. Starting at first level she has gains
access to the distinctive abilities of her race, as befits her plane
of origin:}

\listone
    \itemability{Baator:}{Baatezu Traits:}
    \listtwo
      \itemability{See in Darkness (Ex):}{A Baatezu can see in normal or magical darkness as if it was fully illuminated.}
      \itemability{Immunity to Fire:}{A Baatezu takes no damage from fire of any kind.}
    \end{list}
    \itemability{Gehenna:}{Yugoloth Traits:}
    \listtwo
      \itemability{Magic Resistance (Ex):}{Yugoloths are inherently resistant to magic, and have a Spell Resistance of \mbox{10 + their character level}. If a Yugoloth has SR from any other source, this ability increases that SR by +2 (if that would be more beneficial than simply replacing the other SR).}
      \itemability{Immunity to Acid:}{A Yugoloth takes no damage from Acid of any kind.}
    \end{list}
    \itemability{The Abyss:}{Tanar'ri Traits:}
    \listtwo
      \itemability{Bonus Feat:}{Forged with unbridled Chaos, every Tanar'ri is unique. Upon gaining access to its Fiendish Traits, a Tanar'ri gains one bonus feat of any [Fiend] feat that it qualifies for.}
      \itemability{Immunity to Electricity:}{A Tanar'ri takes no damage from electricity of any kind.}
    \end{list}
    \itemability{Carceri:}{Demodand Traits:}
    \listtwo
    \itemability{Freedom of Movement (Ex):}{A Demodand benefits from the effects of a freedom of movement spell at all times.}
      \itemability{Immunity to Poison (Ex):}{A Demodand suffers no harmful effect from poisons of any kind.}
    \end{list}
\end{list}


\ability{Telepathy (Su):}{At 2nd level, a True Fiend gains the
ability to communicate telepathically with any creature that speaks
a language within 100 feet.}

\ability{Fiendish Damage Reduction (Su):}{At 3rd level, the True
Fiend gains damage reduction that stops their class level in damage
and that can be penetrated by Good weapons or weapons made out of a
material that is baneful to the Fiend's race (Silver for Baatezu,
Wood for Yugoloths, Iron for Tanar'ri, and Stone for Demodands). At
7th level, the Damage Reduction can be penetrated only by Good
weapons. At 13th level the Damage Reduction is only penetrated by
weapons which are both Good and made of a baneful substance. At 19th
level, the True Fiend's Damage Reduction can only be penetrated by
Epic weapons.}

\ability{Sphere:}{The True Fiend gains basic access to a sphere at
4th level, and gains a new sphere at every fourth level afterwards.
If the True Fiend selects a sphere that she already has basic access
to, she upgrades it to advanced access. If she already had advanced
access, she gains expert access.}

\ability{Greater Fiendish Traits:}{A True Fiend of 5th level or more
gains access to more of the distinctive abilities of her race, as
befits her plane of origin:}

\listone
    \itemability{Baator:}{Baatezu Traits:}
    \listtwo
      \itemability{Mundane Poison Immunity (Ex):}{A Baatezu is immune to all non-magical poisons.}
      \itemability{Resistances:}{A Baatezu has Cold and Acid Resistance 10.}
    \end{list}
    \itemability{Gehenna:}{}{Yugoloth Traits:}
    \listtwo
      \itemability{Mundane Poison Immunity (Ex):}{A Yugoloth is immune to all non-magical poisons.}
      \itemability{Resistances:}{A Yugoloth has Cold, Fire, and Electricity Resistance 10.}
    \end{list}
    \itemability{The Abyss:}{}{Tanar'ri Traits:}
    \listtwo
      \itemability{Mundane Poison Immunity (Ex):}{A Tanar'ri is immune to all non-magical poisons.}
      \itemability{Resistances:}{A Tanar'ri has Cold, Fire, and Acid Resistance 10.}
    \end{list}
    \itemability{Carceri:}{Demodand Traits:}
    \listtwo
      \itemability{Immunities:}{The worlds of Carceri are varied beyond belief and each is filled with a new torture that defies comprehension. Upon reaching 5th level, a Demodand gains immunity to 2 Energy Types. Once chosen, the energy types cannot be changed.}
    \end{list}
\end{list}

\ability{Summon (Sp):}{At 9th level, a True Fiend can attempt to
summon others of its kind \example{(for example: a Yugoloth could
summon other Yugoloths)}. Summoning another Fiend of the same
character level has a 40\% chance of success, and summoning a Fiend
of a lower level increases the chances of success by 10\% for every
level the summoner's level exceeds the CR of the target.}

\ability{Bonus Feat:}{At 11th level, a True Fiend gains a bonus
feat. This feat may be any [Fiend] feat for which she meets the
prerequisites.}

\ability{Greater Summoning:}{A True Fiend of 15th level may attempt
to use her summon power to summon a fiend of a level higher than her
own, though doing so carries only a 30\% chance of success.}

\ability{Dark Power:}{The powers of the lower planes are awesome to
behold. At 17th level, the True Fiend gains a +10 bonus to defeating
Spell Resistance with the spell-like abilities granted by her
spheres.}
