\classname{Gadgeteer}
\vspace{-8pt}
\quot{When my Armageddon Clock is complete, no-one will ever again laugh at me!}

\ability{Alignment:}{Gadgeteers can be of any alignment.}

\ability{Starting Age:}{As the Rogue} 

\ability{Starting Wealth:}{PLACEHOLDER} 

\ability{Hit Die:}{d8} 

\ability{Class Skills:}{Appraise (Int), Bluff (Cha), Concentration (Con), Craft (Wis), Decipher Script (Int), Disable Device (Int), Jump (Str), Knowledge [Any] (Int), Search (Int), Sense Motive (Wis), Spot (Wis), (Ab)Use Magic Device (Cha)}

\ability{Skills/Level:}{6 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}[h]{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{7cm}ll}
Level&Base Attack Bonus&Fort Save&Ref Save&Will Save&Special&Daily&Charged\\
1st&  +0  & +2&  +2&  +0&Gadgetry, Coax Device  & 1& 2 \\
2nd&  +1  & +3&  +3&  +0&Invention  & 2& 2 \\
3rd&  +2  & +3&  +3&  +1&Evasion  & 2& 3 \\
4th&  +3  & +4&  +4&  +1&Good Gadgets  & 3& 4 \\
5th&  +3  & +4&  +4&  +1&Invention, Duct Tape  & 4& 4 \\
6th&  +4  & +5&  +5&  +2&Confuse Magic Device  & 4& 5 \\
7th&  +5  & +5&  +5&  +2&Specialty Field  & 5& 5 \\
8th&  +6  & +6&  +6&  +2&Greater Gadgets  & 6& 6 \\
9th&  +6  & +6&  +6&  +3&Invention  & 6& 7 \\
10th& +7  & +7&  +7&  +3&Crafted Companion  & 7& 7 \\
11th& +8  & +7&  +7&  +3&Rapid Rebuild  & 8& 7 \\
12th& +9  & +8&  +8&  +4&Giga Gadgets  & 9& 8 \\
13th& +9  & +8&  +8&  +4&Invention, Percussive Maintenance  & 9& 9 \\
14th& +10 & +9&  +9&  +4&Specialty Field  & 9& 10\\
15th& +11 & +9&  +9&  +5&Command Magic Device  & 10&10\\
16th& +12 & +10& +10& +5&Galactic Gadgets  & 11&11\\
17th& +12 & +10& +10& +5&Invention, Throw a Spanner at it  & 11&12\\
18th& +13 & +11& +11& +6&'Stronger, Faster, More Expensive'  & 12&12\\
19th& +14 & +11& +11& +6&Cybernetic Soldier  & 13&12\\
20th& +15 & +12& +12& +6&The Grand Contraption  & 13&13\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are class features of the gadgeteer.

\ability{Weapon and Armor Proficiency:}{Clerics are proficient with all simple weapons, light armor, medium armour, and any gadget they create.}

\ability{Gadgetry (Ex):}{The Gadgeteer is able to create Gadgets. As he gains levels, he learns more blueprints (according to the table). Some are ``Daily'' - the preparation involved means they are set up at the beginning of the day (requiring an hour total) and then once used, are unavailable for the rest of the day. Others are simpler, and can be used essentially at will, as long as they are charged (covered in the item description). Making multiples of the same thing does not allow more uses, for reasons unknown. 

\smallskip\noindent Devices can be handed to other people to use, however they are not automatically considered proficient (anyone with "All Martial Weapons" proficiency should be considered proficient with weaponlike Gadgets), and the Gadgeteer must continue to maintain the items (as part of his "pool" of Gadgets) for them to continue functioning. 

\smallskip\noindent Any save DC is 10 + half level + Int modifier. Anything that scales with level uses the character level.}

\ability{Coax Device (Su:)}{The Gadgeteer can always take 10 on Abuse Magic Device and Disable Device checks, even if threatened, rushed or on fire.}

\ability{Inventions (Ex):}{Any time the Gadgeteer becomes able to make an Invention, he may base it on anything he currently holds a blueprint to - at the time of gaining the ability (so they cannot be stored up for later levels to cash them all in for Galactic Gadgets). An Invention takes twice as long to build, but grants one of the following benefits when equipped, not counting as a magic item for the limit:

\smallskip

\begin{list}{$\bullet$}{\itemspace}
\item +1/3 levels Enhancement bonus to Int (round up) 
\item +1/4 levels Deflection bonus to AC (round up) 
\item +1/3 levels Resistance bonus to saving throws (round up) 
\item +1/4 levels Enhancement bonus to all attack rolls (round up) 
\item Damage Reduction 1/2 levels, overcome by Adamantine (round up)
\end{list}

\smallskip

\smallskip\noindent Additionally it may be used twice per day if a Daily, or truly at will without charging if Charged.}

\ability{Evasion (Ex):}{At third level the Gadgeteer gets Evasion.}

\ability{Good Gadgets:}{At level 4, the Gadgeteer starts to learn blueprints for Good Gadgets.}

\ability{Duct Tape (Sp):}{At level 5, the Gadgeteer gains the ability to perform quick repairs on things. He may cast Mending, Make Whole and Repair Light Damage at will, with a caster level equal to his character level.}

\ability{Confuse Magic Device (Su):}{At level 6, the Gadgeteer gains the ability to confuse magic items with an Abuse Magic Device check. If it possesses charges, adding +10 to the DC can activate the item without using a charge (this does not apply to single-use items). If it casts a spell that deals a type of damage, or grants protection against a type of damage, this can be changed for that use by adding +5 to the DC. It can be Widened or Extended by adding +5 to the DC as well. Finally, traps that use a magic form of detection are not triggered by the Gadgeteer.}

\ability{Specialty Field (Ex):}{At levels 7 and 14, the Gadgeteer gains a specialty field. This is an area of expertise with the type of Gadget in question. The benefits depend on the field chosen.}

\smallskip

\begin{itemize}\itemspace\begin{small}
\item \ability{Energy:} All Fire/Electricity/Light damage dealt by Gadgets is Empowered (multiplied by 1.5)
\item \ability{Locomotion:} Any movement speeds or teleport ranges are doubled 
\item \ability{Durability:} Any Gadget has twice as many HP and +10 to Hardness, which means fuck-all for ray guns but is awesome for steam tanks. 
\item \ability{Efficiency:} Any non-instantaneous duration is multiplied by 1.5 (round up) 
\item \ability{Destruction:} All damage (except for Fire/Electricity/Light) dealt by Gadgets is Empowered. 
\item \ability{Overcharge:} Any areas of effect are doubled in size. 
\item \ability{Homing:} Gadgets ignore soft cover and any Concealment less than total, and may re-roll failed Miss Chances.
\end{small}\end{itemize}

\smallskip

\ability{Greater Gadgets:}{At level 8, the Gadgeteer starts to learn the blueprints for Greater Gadgets.}

\ability{Crafted Companion (Ex):}{At level 10, the Gadgeteer may build a cohort, mount or familiar - a Construct with a CR at least 3 less than his level. As he levels, he may add to it, to keep the creature's CR up - or outright disassemble and rebuild into a new form. It takes 8 hours to construct. If it is destroyed, all he needs to do is repair it or build a new one.}

\ability{Rapid Rebuild (Ex):}{At level 11, the Gadgeteer becomes faster at making things he is familiar with. As long as he has built something once in the past, he may rebuild it in half the time it would take to build normally (including his cohort), and can use a full round action to restore 150 HP to any Gadget or Invention.}

\ability{Giga Gadgets:}{At level 12, the Gadgeteer begins to learn blueprints for Giga Gadgets.}

\ability{Percussive Maintenance (Su):}{At level 13, the Gadgeteer learns how to fix (and damage) objects with a solid kick. With a melee attack that must hit the AC of the target, he may duplicate a Heal or Harm effect that only works on Constructs (ignoring any usual immunities to Heal/Harm or supernatural effects in general).}

\ability{Command Magic Device (Su):}{At level 15. the Gadgeteer knows how to command magic devices that don't even belong to him: no Construct will ever attack him, even sentient ones, unless he attacks them first. Furthermore, with a DC (15 + CR of Construct) Abuse magic Device check, he may control it (as per Dominate Monster, except it affects the Construct despite immunities, and allows no save) for one minute, after which it cannot be controlled by him again that day.

\smallskip\noindent Additionally, as a standard action he may activate a magic item somebody else is using or holding, from up to 50 feet away, as long as he is aware of it and targets it. This adds +10 to the activation DC. He may also make an Abuse Magic Device check as an immediate action (DC = base DC to activate) to prevent it from being used, wasting the attempt. }

\ability{Galactic Gadgets:}{At level 16, the Gadgeteer begins learning blueprints for Galactic Gadgets.}

\ability{Throw a Spanner at it (Ex):}{At level 17, the Gadgeteer learns how to affect Constructs at a distance. The Percussive Maintenance ability can work with any ranged attack, though actually throwing a construction tool gains a +5 Circumstance bonus to the attack roll.}

\ability{Stronger, Faster, More Expensive (Ex):}{At level 18, the Gadgeteer learns how to make impressive golem bodies for people. With 24 hours and some amount of planar currency, he may transfer someone (even himself) into a body of iron, granting them the following benefits:

\smallskip

\begin{list}{$\bullet$}{\itemspace}
\item Type: Construct (Augmented (former type) as Subtype) 
\item Leave BAB, HP, ability scores (even Con) etc. all the same 
\item +6 Enhancement bonus to Strength 
\item Double one movement speed 
\item Damage Reduction 15/Adamantine 
\item Natural weapons overcome DR and Hardness as though made of Adamantine (they are) 
\item Not immune to Mind-Affecting Effects 
\item Always counts as Exhausted (ignore the immunity to such). A full round action spent winding them up (they can do this to themselves) negates this for one minute.
\end{list}}

\smallskip

\ability{Cybernetic Soldier (Ex):}{At level 19, the Gadgeteer adds pieces of gadgetry to himself to become a sort of cyborg. Don't think sleek Shadowrun stuff, he probably has a key in the back of his head. He gains the following benefits:

\smallskip

\begin{list}{$\bullet$}{\itemspace}
\item Immune to Mind-Affecting Effects 
\item Medium Fortification 
\item -3 Circumstance Penalty to all Int-based skills unless a standard action is spent winding up or whatever, which turns it into a +3 Enhancement Bonus for one minute. 
\item Low-Light Vision and Darkvision 120' 
\item Always-on Detect Magic effect
\end{list}}

\smallskip

\ability{The Grand Contraption (Ex):}{At level 20, the Gadgeteer wins the game.}