%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

{\LARGE MONSTERS (Dr-Dw)}

\vspace{12pt}
{\LARGE DRAGON, TRUE}

The known varieties of true dragons (as opposed to other creatures that have the 
dragon type) fall into two broad categories: chromatic and metallic. The chromatic 
dragons are black, blue, green, red, and white; they are all evil and extremely 
fierce. The metallic dragons are brass, bronze, copper, gold, and silver; they 
are all good, usually noble, and highly respected by the wise.

All true dragons gain more abilities and greater power as they age. (Other creatures 
that have the dragon type do not.) They range in length from several feet upon 
hatching to more than 100 feet after attaining the status of great wyrm. The size 
of a particular dragon varies according to age and variety.

A dragon's metabolism operates like a highly efficient furnace and can metabolize 
even inorganic material. Some dragons have developed a taste for such fare.

Although goals and ideals vary among varieties, all dragons are covetous. They 
like to hoard wealth, collecting mounds of coins and gathering as many gems, jewels, 
and magic items as possible. Those with large hoards are loath to leave them for 
long, venturing out of their lairs only to patrol the immediate area or to get 
food. For dragons, there is no such thing as enough treasure. It's pleasing to 
look at, and they bask in its radiance. Dragons like to make beds of their hoards, 
shaping nooks and mounds to fit their bodies. By the time a dragon matures to the 
age of great wyrm, hundreds of gems and coins may be imbedded in its hide.

All dragons speak Draconic.

COMBAT

A dragon attacks with its powerful claws and bite, and can also use a breath weapon 
and special physical attacks, depending on its size. It prefers to fight on the 
wing, staying out of reach until it has worn down the enemy with ranged attacks. 
Older, more intelligent dragons are adept at sizing up the opposition and eliminating 
the most dangerous foes first (or avoiding them while picking off weaker enemies).

The table below provides space and reach statistics for dragons of various sizes, 
plus the natural weapons a dragon of a certain size can employ and the damage those 
attacks deal.

\textbf{Bite:} Bite attacks deal the indicated damage plus the dragon's Strength 
bonus. A dragon also can use its bite to snatch opponents if it has the Snatch 
feat.

\textbf{Claw:} Claw attacks deal the indicated damage plus 1/2 the dragon's Strength 
bonus (round down). The dragon also can use its claws to snatch opponents if it 
has the Snatch feat. Claw attacks are secondary attacks, requiring a -5 penalty 
on the attack roll. (Many dragons choose the Multiattack feat to lessen this penalty 
to -2).

\textbf{Wing:} The dragon can slam opponents with its wings, even when flying. 
Wing attacks deal the indicated damage plus 1/2 the dragon's Strength bonus (round 
down) and are treated as secondary attacks.

\textbf{Tail Slap:} The dragon can slap one opponent each round with its tail. 
A tail slap deals the indicated damage plus 1-1/2 times the dragon's Strength bonus 
(round down) and is treated as a secondary attack.

\textbf{Crush (Ex):} This special attack allows a flying or jumping dragon of at 
least Huge size to land on opponents as a standard action, using its whole body 
to crush them. Crush attacks are effective only against opponents three or more 
size categories smaller than the dragon (though it can attempt normal overrun or 
grapple attacks against larger opponents).

A crush attack affects as many creatures as can fit under the dragon's body. Creatures 
in the affected area must succeed on a Reflex save (DC equal to that of the dragon's 
breath weapon) or be pinned, automatically taking bludgeoning damage during the 
next round unless the dragon moves off them. If the dragon chooses to maintain 
the pin, treat it as a normal grapple attack. Pinned opponents take damage from 
the crush each round if they don't escape.

A crush attack deals the indicated damage plus 1-1/2 times the dragon's Strength 
bonus (round down).

\textbf{Tail Sweep (Ex):} This special attack allows a dragon of at least Gargantuan 
size to sweep with its tail as a standard action. The {\small sweep affects a half-circle 
with a radius of 30 feet (or 40 feet for a Colossal dragon), extending from an 
}intersection on the edge of the dragon's space in any direction. Creatures within 
the swept area are affected if they are four or more size categories smaller than 
the dragon. A tail sweep automatically deals the indicated damage plus 1-1/2 times 
the dragon's Strength bonus (round down). Affected creatures can attempt Reflex 
saves to take half damage (DC equal to that of the dragon's breath weapon).

\textbf{Grappling: }Dragons do not favor grapple attacks, though their crush attack 
(and Snatch feat, if they know it) use normal grapple rules. A dragon can always 
use its breath weapon while grappling, as well as its spells and spell-like or 
supernatural abilities, provided it succeeds on Concentration checks.

\textbf{Breath Weapon (Su):} Using a breath weapon is a standard action. Once a 
dragon breathes, it can't breathe again until 1d4 rounds later. If a dragon has 
more than one type of breath weapon, it still can breathe only once every 1d4 rounds. 
A blast from a breath weapon always starts at any intersection adjacent to the 
dragon and extends in a direction of the dragon's choice, with an area as noted 
on the table below. If the breath weapon deals damage, creatures caught in the 
area can attempt Reflex saves to take half damage; the DC depends on the dragon's 
age and variety, and is given in each individual entry. Saves against nondamaging 
breath weapons use the same DC; the kind of saving throw is noted in the variety 
descriptions. The save DC against a breath weapon is 10 + 1/2 dragon's HD + dragon's 
Con modifier.

Breath weapons come in two basic shapes, line and cone, whose areas vary with the 
dragon's size.

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{3}{|p{3.062in}|}{\begin{minipage}[t]{3.062in}\raggedright
\textbf{Dragon Breath Weapons}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{3}{p{0.208in}|}{\begin{minipage}[t]{0.208in}\raggedright
\textbf{Dragon Size}\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
\textbf{Line* (Length)}\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
\textbf{Cone** (Length)}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{1.149in}|}{\begin{minipage}[t]{1.149in}\centering
Tiny\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
30 ft.\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
15 ft.\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Small\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
40 ft.\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
20 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{4}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
Medium\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
60 ft.\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
30 ft.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Large\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
80 ft.\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
40 ft.\end{minipage}}\\
\hline
% ROW 7
\multicolumn{4}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
Huge\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
100 ft.\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
50 ft.\end{minipage}}\\
\hline
% ROW 8
\multicolumn{4}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
Gargantuan\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
120 ft.\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
60 ft.\end{minipage}}\\
\hline
% ROW 9
\multicolumn{4}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
Colossal\end{minipage}} & \multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
140 ft.\end{minipage}} & \multicolumn{1}{p{1.042in}|}{\begin{minipage}[t]{1.042in}\raggedright
70 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{4}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\centering
*A line is always 5 feet high and 5 feet wide.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.872in}|}{\begin{minipage}[t]{0.872in}\centering
**A cone is as high and wide as its length.\end{minipage}}\\
\hline
\end{longtable}

\textbf{Frightful Presence (Ex):} A young adult or older dragon can unsettle foes 
with its mere presence. The ability takes effect automatically whenever the dragon 
attacks, charges, or flies overhead. Creatures within a radius of 30 feet x the 
dragon's age category are subject to the effect if they have fewer HD than the 
dragon. A potentially affected creature that succeeds on a Will save (DC 10 + 1/2 
dragon's HD + dragon's Cha modifier) remains immune to that dragon's frightful 
presence for 24 hours. On a failure, creatures with 4 or less HD become panicked 
for 4d6 rounds and those with 5 or more HD become shaken for 4d6 rounds. Dragons 
ignore the frightful presence of other dragons.

\textbf{Spells:} A dragon knows and casts arcane spells as a sorcerer of the level 
indicated in its variety description, gaining bonus spells for a high Charisma 
score. Some dragons can also cast spells from the cleric list or cleric domain 
lists as arcane spells.

\textbf{Spell-Like Abilities:} A dragon's spell-like abilities depend on its age 
and variety. It gains the abilities indicated for its age plus all previous ones. 
Its age category or its sorcerer caster level, whichever is higher, is the caster 
level for these abilities. The save DC is 10 + dragon's Cha modifier + spell level. 
All spell-like abilities are usable once per day unless otherwise noted.

\textbf{Damage Reduction:} Young adult and older dragons have damage reduction. 
Their natural weapons are treated as magic weapons for the purpose of overcoming 
damage reduction.

\textbf{Immunities (Ex):} All dragons have immunity to \textit{sleep }and paralysis 
effects. Each variety of dragon has immunity to one or two additional forms of 
attack no matter what its age, as given in its description.

\textbf{Spell Resistance (Ex):} As dragons age, they become more resistant to spells 
and spell-like abilities, as indicated in the variety descriptions.

\textbf{Blindsense (Ex):} Dragons can pinpoint creatures within a distance of 60 
feet. Opponents the dragon can't actually see still have total concealment against 
the dragon.

\textbf{Keen Senses (Ex):} A dragon sees four times as well a human in shadowy 
illumination and twice as well in normal light. It also has darkvision out to 120 
feet.

\textbf{Skills:} All dragons have skill points equal to (6 + Int modifier, minimum 
1) x (Hit Dice + 3). Most dragons purchase the following skills at the maximum 
ranks possible: Listen, Search, and Spot. The remaining skill points are generally 
spent on Concentration, Diplomacy, Escape Artist, Intimidate, Knowledge (any), 
Sense Motive, and Use Magic Device at a cost of 1 skill point per rank. All these 
skills are considered class skills for dragons. (Each dragon has other class skills 
as well, as noted in the variety descriptions.)

\textbf{Feats:} All dragons have one feat, plus additional feats based on Hit Dice 
just like any other creature. Dragons favor Alertness, Blind-Fight, Cleave, Flyby 
Attack, Hover, Improved Initiative, Improved Sunder, Power Attack, Snatch, Weapon 
Focus (claw or bite), Wingover, and any metamagic feat that is available and useful 
to sorcerers.

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{2}{|p{1.924in}|}{\begin{minipage}[t]{1.924in}\raggedright
\textbf{Dragon Age Categories}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{2}{p{0.139in}|}{\begin{minipage}[t]{0.139in}\raggedright
\textbf{Category}\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
\textbf{Age (Years)}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.933in}|}{\begin{minipage}[t]{0.933in}\raggedright
1 Wyrmling\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
0-5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
2 Very young\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
6-15\end{minipage}}\\
\hline
% ROW 5
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
3 Young\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
16-25\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
4 Juvenile\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
26-50\end{minipage}}\\
\hline
% ROW 7
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
5 Young adult\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
51-100\end{minipage}}\\
\hline
% ROW 8
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
6 Adult\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
101-200\end{minipage}}\\
\hline
% ROW 9
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
7 Mature adult\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
201-400\end{minipage}}\\
\hline
% ROW 10
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
8 Old\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
401-600\end{minipage}}\\
\hline
% ROW 11
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
9 Very old\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
601-800\end{minipage}}\\
\hline
% ROW 12
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
10 Ancient\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
801-1,000\end{minipage}}\\
\hline
% ROW 13
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
11 Wyrm\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
1,001-1,200\end{minipage}}\\
\hline
% ROW 14
\multicolumn{3}{p{1.072in}|}{\begin{minipage}[t]{1.072in}\raggedright
12 Great wyrm\end{minipage}} & \multicolumn{1}{|p{0.991in}|}{\begin{minipage}[t]{0.991in}\raggedright
1,201 or more\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllllll}
\hline
% ROW 1
\multicolumn{8}{|p{4.176in}|}{\begin{minipage}[t]{4.176in}\raggedright
\textbf{Dragon Space/Reach, Attacks, and Damage}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{8}{p{0.324in}|}{\begin{minipage}[t]{0.324in}\raggedright
\textbf{Size}\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
\textbf{Space/Reach*}\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
\textbf{1 Bite}\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
\textbf{2 Claws}\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
\textbf{2 Wings}\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
\textbf{1 Tail Slap}\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
\textbf{1Crush}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
\textbf{1 Tail Sweep}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.587in}|}{\begin{minipage}[t]{0.587in}\centering
Tiny\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
2-1/2 ft./0 ft. (5 ft. with bite)\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
1d4\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
1d3\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
Small\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
1d6\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
1d4\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{9}{p{0.912in}|}{\begin{minipage}[t]{0.912in}\centering
Medium\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
1d8\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
1d6\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
1d4\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
Large\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
10 ft./5 ft. (10 ft. with bite)\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
2d6\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
1d8\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
1d6\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
1d8\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{9}{p{0.912in}|}{\begin{minipage}[t]{0.912in}\centering
Huge\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
15 ft./10 ft. (15 ft. with bite)\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
2d8\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
2d6\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
1d8\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
2d6\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
2d8\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
---\end{minipage}}\\
\hline
% ROW 8
\multicolumn{9}{p{0.912in}|}{\begin{minipage}[t]{0.912in}\centering
Gargantuan\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
20 ft./15 ft. (20 ft. with bite)\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
4d6\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
2d8\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
2d6\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
2d8\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
4d6\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
2d6\end{minipage}}\\
\hline
% ROW 9
\multicolumn{9}{p{0.912in}|}{\begin{minipage}[t]{0.912in}\centering
Colossal\end{minipage}} & \multicolumn{1}{|p{0.507in}|}{\begin{minipage}[t]{0.507in}\raggedright
30 ft./20 ft. (30 ft. with bite)\end{minipage}} & \multicolumn{1}{p{1.054in}|}{\begin{minipage}[t]{1.054in}\centering
4d8\end{minipage}} & \multicolumn{1}{p{0.329in}|}{\begin{minipage}[t]{0.329in}\raggedright
4d6\end{minipage}} & \multicolumn{1}{p{0.401in}|}{\begin{minipage}[t]{0.401in}\raggedright
2d8\end{minipage}} & \multicolumn{1}{p{0.410in}|}{\begin{minipage}[t]{0.410in}\raggedright
4d6\end{minipage}} & \multicolumn{1}{p{0.502in}|}{\begin{minipage}[t]{0.502in}\raggedright
4d8\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
2d8\end{minipage}}\\
\hline
% ROW 10
\multicolumn{9}{p{0.912in}|}{\begin{minipage}[t]{0.912in}\centering
*A dragon's bite attack has reach as if the creature were one size category larger. 
All other attacks are made with the standard reach for the dragon's size.\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
Dragon Overland Movement

Chromatic and metallic dragons are exceedingly strong flyers and can cover vast 
distances quickly. A dragon's overland flying speed is a function of its tactical 
fly speed, as shown on the table below.

\begin{longtable}{llllllllll}
\hline
% ROW 1
\multicolumn{5}{|p{3.874in}|}{\begin{minipage}[t]{3.874in}\raggedright
\textbf{Dragon Overland Flying Speeds}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{5}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\raggedright
\end{minipage}} & \multicolumn{1}{|p{0.818in}|}{\begin{minipage}[t]{0.818in}\centering
---------------\textbf{ Dragon's Fly Speed ---------------}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{4}{p{3.056in}|}{\begin{minipage}[t]{3.056in}\centering
\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textbf{100 feet}\end{minipage}} & \multicolumn{4}{p{0.278in}|}{\begin{minipage}[t]{0.278in}\raggedright
\textbf{150 feet}\end{minipage}} & \multicolumn{1}{|p{0.818in}|}{\begin{minipage}[t]{0.818in}\raggedright
\textbf{200 feet}\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{250 feet}\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
\textbf{One Hour}\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Normal\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
15 miles\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
20 miles\end{minipage}} & \multicolumn{1}{|p{0.818in}|}{\begin{minipage}[t]{0.818in}\raggedright
30 miles\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
40 miles\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
Hustle\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
24 miles\end{minipage}} & \multicolumn{6}{p{1.111in}|}{\begin{minipage}[t]{1.111in}\raggedright
40 miles\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 miles\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
80 miles\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\textbf{One Day}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\end{minipage}} & \multicolumn{1}{|p{0.818in}|}{\begin{minipage}[t]{0.818in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
Normal\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\centering
120 miles\end{minipage}} & \multicolumn{6}{p{1.111in}|}{\begin{minipage}[t]{1.111in}\raggedright
160 miles\end{minipage}} & \multicolumn{1}{|p{0.818in}|}{\begin{minipage}[t]{0.818in}\raggedright
240 miles\end{minipage}} & \multicolumn{1}{p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
320 miles\end{minipage}}\\
\hline
\end{longtable}

Dragons do not tire as quickly as other creatures when moving overland on the ground. 
If a dragon attempts a hustle or a forced march, check for nonlethal damage once 
every 2 hours instead of every hour.

DRAGONHIDE

Armorsmiths can work with the hides of dragons to produce armor or shields of masterwork 
quality.

\vspace{12pt}
{\LARGE CHROMATIC DRAGONS}

Chromatic dragons form the evil branch of dragonkind. They are aggressive, greedy, 
vain, and nasty.

\vspace{12pt}
BLACK DRAGON

\textbf{Dragon (Water)}

\textbf{Environment:} Warm marshes

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Rating:} Wyrmling 3; very young 4; young 5; juvenile 7; young 
adult 9; adult 11; mature adult 14; old 16; very old 18; ancient 19; wyrm 20; great 
wyrm 22

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always chaotic evil

\textbf{Advancement:} Wyrmling 5-6 HD; very young 8-9 HD; young 11-12 HD; juvenile 
14-15 HD; young adult 17-18 HD; adult 20-21 HD; mature adult 23-24 HD; old 26-27 
HD; very old 29-30 HD; ancient 32-33 HD; wyrm 35-36 HD; great wyrm 38+ HD

\textbf{Level Adjustment:} Wyrmling +3; very young +3; young +3; juvenile +4; others 
---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.884in}|}{\begin{minipage}[t]{3.884in}\raggedright
\textbf{Black Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.616in}|}{\begin{minipage}[t]{0.616in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\centering
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small T}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 4d12+4 (30)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4/-4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 2d4 (13)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 7d12+7 (52)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +7/+4}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 4d4 (14)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.347in}|}{\begin{minipage}[t]{0.347in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10d12+20 (85)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +10/+12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 6d4 (17)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 13d12+26 (110)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +13/+16}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 8d4 (18)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 16d12+48 (152)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +16/+24}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10d4 (21)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 19}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 19d12+76 (199)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +19/+29}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 12d4 (23)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 22d12+110 (253)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +22/+38}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 14d4 (26)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 25d12+125 (287)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +25/+42}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 16d4 (27)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 28d12+168 (350)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +28/+46}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +36}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 18d4 (30)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 31d12+186 (387)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +31/+50}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +40}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 20d4 (31)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 34d12+238 (459)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +34/+58}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +42}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 22d4 (34)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.963in}|}{\begin{minipage}[t]{0.963in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.337in}|}{\begin{minipage}[t]{0.337in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 37d12+296 (536)}\end{minipage}} & \multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.193in}|}{\begin{minipage}[t]{0.193in}\raggedright
{\small +37/+62}\end{minipage}} & \multicolumn{1}{p{0.302in}|}{\begin{minipage}[t]{0.302in}\raggedright
{\small +46}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 24d4 (36)}\end{minipage}} & \multicolumn{1}{p{0.376in}|}{\begin{minipage}[t]{0.376in}\raggedright
{\small 33}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Black Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., fly 100 ft. (average), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small 15 (+2 size,+3 natural), touch 12, flat-footed 15}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to acid, water breathing}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 100 ft. (average), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 17 (+1 size,+6 natural), touch 11, flat-footed 17}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small 19 (+9 natural), touch 10, flat-footed 19 }\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 22 (+12 natural), touch 10, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\centering
{\small \textit{Darkness}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 24 (-1 size,+15 natural), touch 9, flat-footed 24}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 17}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 27 (-1 size,+18 natural), touch 9, flat-footed 27}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\centering
{\small \textit{Corrupt water}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\centering
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 18}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 29 (-2 size,+21 natural), touch 8, flat-footed 29}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 32 (-2 size,+24 natural), touch 8, flat-footed 32}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\centering
{\small \textit{Plant growth}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\centering
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 35 (-2 size,+27 natural), touch 8, flat-footed 35}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 38 (-2 size,+30 natural), touch 8, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\centering
{\small \textit{Insect plague}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\centering
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 200 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 39 (-4 size,+33 natural), touch 6, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 60 ft., fly 200 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.919in}|}{\begin{minipage}[t]{0.919in}\centering
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\centering
{\small 42 (-4 size,+36 natural), touch 6, flat-footed 42}\end{minipage}} & \multicolumn{1}{p{1.058in}|}{\begin{minipage}[t]{1.058in}\centering
{\small \textit{Charm reptiles}}\end{minipage}} & \multicolumn{1}{p{0.825in}|}{\begin{minipage}[t]{0.825in}\centering
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.416in}|}{\begin{minipage}[t]{0.416in}\raggedright
{\small 28}\end{minipage}}\\
\hline
\end{longtable}

Black dragon are sometimes known as skull dragons because of their skeletal faces. 
Adding to the skeletal impression is the gradual deterioration of the hide around 
the base of the horn and the cheekbones. This deterioration increases with age 
and does not harm the dragon. On hatching, a black dragon's scales are thin, small, 
and glossy. As the dragon ages, they become larger, thicker, and duller, helping 
it camouflage itself in swamps and marshes.

Black dragons are especially fond of coins. Older dragons sometimes capture and 
question humanoids about stockpiles of gold, silver, and platinum coins before 
killing them.

Combat

Black dragons prefer to ambush their targets, using their surroundings as cover. 
When fighting in heavily forested swamps and marshes, they try to stay in the water 
or on the ground; trees and leafy canopies limit their aerial maneuverability. 
When outmatched, a black dragon attempts to fly out of sight, so as not to leave 
tracks, and hide in a deep pond or bog.

\textbf{Breath Weapon (Su):} A black dragon has one type of breath weapon, a line 
of acid.

\textbf{Water Breathing (Ex):} A black dragon can breathe underwater indefinitely 
and can freely use its breath weapon, spells, and other abilities while submerged.

\textit{\textbf{Corrupt Water }}\textbf{(Sp):} Once per day an adult or older black 
dragon can stagnate 10 cubic feet of water, making it become still, foul, and unable 
to support animal life. The ability spoils liquids containing water. Magic items 
(such as potions) and items in a creature's possession must succeed on a Will save 
(DC equal to that of the dragon's frightful presence) or become fouled. This ability 
is the equivalent of a 1st-level spell. Its range is equal to that of the dragon's 
frightful presence.

\textit{\textbf{Charm Reptiles }}\textbf{(Sp):} A great wyrm black dragon can use 
this ability three times per day. It works as a \textit{mass charm }spell that 
affects only reptilian animals. The dragon can communicate with any charmed reptiles 
as though casting a \textit{speak with animals }spell. This ability is the equivalent 
of a 1st-level spell.

\textbf{Other Spell-Like Abilities:} 3/day---\textit{darkness }(juvenile or older; 
radius 10 feet per age category), \textit{insect plague }(ancient or older); 1/day---\textit{plant 
growth }(old or older).

\textbf{Skills:} Hide, Move Silently, and Swim are considered class skills for 
black dragons.

\vspace{12pt}
BLUE DRAGON

\textbf{Dragon (Earth)}

\textbf{Environment:} Temperate deserts

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 3; very young 4; young 6; juvenile 8; young 
adult 11; adult 14; mature adult 16; old 18; very old 19; ancient 21; wyrm 23; 
great wyrm 25

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always lawful evil

\textbf{Advancement:} Wyrmling 7-8 HD; very young 10-11 HD; young 13-14 HD; juvenile 
16-17 HD; young adult 19-20 HD; adult 22-23 HD; mature adult 25-26 HD; old 28-29 
HD; very old 31-32 HD; ancient 34-35 HD; wyrm 37-38 HD; great wyrm 40+ HD

\textbf{Level Adjustment:} Wyrmling +4; very young +4; young +5; others ---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Blue Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d12+6 (45)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6/+3}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d8 (14)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 9d12+18 (76)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +9/+11}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d8 (16)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12d12+24 (102)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12/+15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d8 (18)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 15d12+45 (142)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +15/+23}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d8 (20)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18d12+72 (189)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +18/+28}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d8 (23)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 21d12+105 (241)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +21/+37}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d8 (25)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 24d12+120 (276)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +24/+41}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d8 (27)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 27d12+162 (337)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +27/+45}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +35}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d8 (29)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 30d12+180 (375)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +30/+49}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +39}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d8 (31)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 33d12+231 (445)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +33/+57}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +41}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d8 (33)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 36d12+288 (522)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +36/+61}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +45}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d8 (36)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 33}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 39d12+312 (565)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +39/+65}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +49}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d8 (37)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 35}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Blue Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., burrow 20 ft., fly 100 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 16 (+1 size, +5 natural), touch 11, flat-footed 16}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to electricity, }{\small \textit{create/destroy water}}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 18 (+8 natural), touch 10, flat-footed 18}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 21 (+11 natural), touch 10, flat-footed 21}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 23 (-1 size, +14 natural), touch 9, flat-footed 23}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small Sound imitation}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 26 (-1 size, +17 natural), touch 9, flat-footed 26}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 19}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 28 (-2 size, +20 natural), touch 8, flat-footed 28}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small \textit{Ventriloquism}}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 31 (-2 size, +23 natural), touch 8, flat-footed 31}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 34 (-2 size, +26 natural), touch 8, flat-footed 34}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small \textit{Hallucinatory terrain}}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 37 (-2 size, +29 natural), touch 8, flat-footed 37}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 38 (-4 size, +32 natural), touch 6, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small \textit{Veil}}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 41 (-4 size, +35 natural), touch 6, flat-footed 41}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.432in}|}{\begin{minipage}[t]{0.432in}\raggedright
{\small 40 ft., burrow 20 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.864in}|}{\begin{minipage}[t]{0.864in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 44 (-4 size, +38 natural), touch 6, flat-footed 44}\end{minipage}} & \multicolumn{1}{p{0.967in}|}{\begin{minipage}[t]{0.967in}\raggedright
{\small \textit{Mirage arcana}}\end{minipage}} & \multicolumn{1}{p{0.994in}|}{\begin{minipage}[t]{0.994in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.399in}|}{\begin{minipage}[t]{0.399in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Air, Evil, and Law domains 
as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

A blue dragon's scales vary in color from an iridescent azure to a deep indigo, 
polished to a glossy finish by blowing desert sands. The size of its scales increases 
little as the dragon ages, although they do become thicker and harder. Its hide 
tends to hum and crackle faintly with built-up static electricity. These effects 
intensify when the dragon is angry or about to attack, giving off an odor of ozone 
and sand. Their vibrant color makes blue dragons easy to spot in barren desert 
surroundings. However, they often burrow into the sand so only part of their heads 
are exposed.

Blue dragons love to soar in the hot desert air, usually flying in the daytime 
when temperatures are highest. Some nearly match the color of the desert sky and 
use this coloration to their advantage.

Blue dragons lair in vast underground caverns, where they also store their treasure. 
Although they collect anything that looks valuable, they are most fond of gems---especially 
sapphires.

Combat

Typically, blue dragons attack from above or burrow beneath the sands until opponents 
come within 100 feet. Older dragons use their special abilities, such as \textit{hallucinatory 
terrain}, in concert with these tactics to mask the land and improve their chances 
to surprise the target. Blue dragons run from a fight only if they are severely 
damaged, since they view retreat as cowardly.

\textbf{Breath Weapon (Su):} A blue dragon has one type of breath weapon, a line 
of lightning.

\textit{\textbf{Create/Destroy Water }}\textbf{(Sp):} A blue dragon of any age 
can use this ability three times per day. It works like the \textit{create water 
}spell, except that the dragon can decide to destroy water instead of creating 
it, which automatically spoils unattended liquids containing water. Magic items 
(such as potions) and items in a creature's possession must succeed on a Will save 
(DC equal to that of the dragon's frightful presence) or be ruined. This ability 
is the equivalent of a 1st-level spell.

\textbf{Sound Imitation (Ex):} A juvenile or older blue dragon can mimic any voice 
or sound it has heard, anytime it likes. Listeners must succeed on a Will save 
(DC equal to that of the dragon's frightful presence) to detect the ruse.

\textbf{Other Spell-Like Abilities:} 3/day---\textit{ventriloquism }(adult or older); 
1/day---\textit{hallucinatory terrain }(old or older), \textit{veil }(ancient or 
older), \textit{mirage arcana }(great wyrm).

\textbf{Skills:} Bluff, Hide, and Spellcraft are considered class skills for blue 
dragons.

\vspace{12pt}
GREEN DRAGON

\textbf{Dragon (Air)}

\textbf{Environment: }Temperate forests

\textbf{Organization: }Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings: }Wyrmling 3; very young 4; young 5; juvenile 8; young 
adult 11; adult 13; mature adult 16; old 18; very old 19; ancient 21; wyrm 22; 
great wyrm 24

\textbf{Treasure: }Triple standard

\textbf{Alignment:} Always lawful evil

\textbf{Advancement:} Wyrmling 6-7 HD; very young 9-10 HD; young 12-13 HD; juvenile 
15-16 HD; young adult 18-19 HD; adult 21-22 HD; mature adult 24-25 HD; old 27-28 
HD; very old 30-31 HD; ancient 33-34 HD; wyrm 36-37 HD; great wyrm 39+ HD

\textbf{Level Adjustment: }Wyrmling +5; very young +5; young +5; juvenile +6; others 
---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Green Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 5d12+5 (37)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5/+2}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d6 (13)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 8d12+16 (68)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +8/+10}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d6 (16)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11d12+22 (93)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11/+14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d6 (17)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 14d12+42 (133)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +14/+22}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d6 (20)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17d12+68 (178)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +17/+27}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d6 (22)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 20d12+100 (230)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +20/+36}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d6 (25)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 23d12+115 (264)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +23/+40}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +30}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d6 (26)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 26d12+156 (325)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +26/+44}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +34}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d6 (29)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 29d12+174 (362)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +29/+48}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +38}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d6 (30)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 32d12+224 (432)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +32/+56}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +40}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d6 (33)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 35d12+280 (507)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +35/+60}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +44}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d6 (35)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 32}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 38d12+304 (551)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +38/+64}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +48}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d6 (37)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 35}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Green Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 100 ft. (average), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 15 (+1 size, +4 natural), touch 11, flat-footed 15}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to acid, water breathing}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 17 (+7 natural), touch 10, flat-footed 17}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 20 (+10 natural), touch 10, flat-footed 20}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 22 (-1 size, +13 natural), touch 9, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 25 (-1 size, +16 natural), touch 9, flat-footed 25}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 19}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 27 (-2 size, +19 natural), touch 8, flat-footed 27}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small \textit{Suggestion}}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 30 (-2 size, +22 natural), touch 8, flat-footed 30}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 33 (-2 size, +25 natural), touch 8, flat-footed 33}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small \textit{Plant growth}}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 36 (-2 size, +28 natural), touch 8, flat-footed 36}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 37 (-4 size, +31 natural), touch 6, flat-footed 37}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small \textit{Dominate person}}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 40 (-4 size, +34 natural), touch 6, flat-footed 40}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.438in}|}{\begin{minipage}[t]{0.438in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 40 ft}\end{minipage}} & \multicolumn{1}{p{0.904in}|}{\begin{minipage}[t]{0.904in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 43 (-4 size, +37 natural), touch 6, flat-footed 43}\end{minipage}} & \multicolumn{1}{p{1.065in}|}{\begin{minipage}[t]{1.065in}\raggedright
{\small \textit{Command plants}}\end{minipage}} & \multicolumn{1}{p{0.834in}|}{\begin{minipage}[t]{0.834in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.415in}|}{\begin{minipage}[t]{0.415in}\raggedright
{\small 30}\end{minipage}}\\
\hline
\end{longtable}

A wyrmling green dragon's scales are thin, very small, and a deep shade of green 
that appears nearly black. As the dragon ages, the scales grow larger and lighter, 
turning shades of forest, emerald, and olive green, which helps it blend in with 
its wooded surroundings.

Combat

Green dragons initiate fights with little or no provocation, picking on creatures 
of any size. If the target is intriguing or seems formidable, the dragon stalks 
the creature to determine the best time to strike and the most appropriate tactics 
to use. If the target appears weak, the dragon makes its presence known quickly---it 
enjoys

evoking terror. Sometimes the dragon elects to control a humanoid creature through 
intimidation and \textit{suggestion. }Green dragons especially like to question 
adventurers to learn more about their society and abilities, what is going on in 
the countryside, and if there is treasure nearby.

\textbf{Breath Weapon (Su):} A green dragon has one type of breath weapon, a cone 
of corrosive (acid) gas.

\textbf{Water Breathing (Ex):} A green dragon can breathe underwater indefinitely 
and can freely use its breath weapon, spells, and other abilities while submerged.

\textbf{Spell-Like Abilities:} 3/day---\textit{suggestion }(adult or older), \textit{dominate 
person }(ancient or older); 1/day--- \textit{plant growth }(old or older), \textit{command 
plants }(great wyrm).

\textbf{Skills:} Bluff, Hide, and Move Silently are considered class skills for 
green dragons.

\vspace{12pt}
RED DRAGON

\textbf{Dragon (Fire)}

\textbf{Environment: }Warm mountains

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 4; very young 5; young 7; juvenile 10; young 
adult 13; adult 15; mature adult 18; old 20; very old 21; ancient 23; wyrm 24; 
great wyrm 26

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always chaotic evil

\textbf{Advancement: }Wyrmling 8-9 HD; very young 11-12 HD; young 14-15 HD; juvenile 
17-18 HD; young adult 20-21 HD; adult 23-24 HD; mature adult 26-27 HD; old 29-30 
HD; very old 32-33 HD; ancient 35-36 HD; wyrm 38-39 HD; great wyrm 41+ HD

\textbf{Level Adjustment:} Wyrmling +4; very young +5; young +6; others ---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Red Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 7d12+14 (59)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7/+10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d10 (15)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 10d12+30 (95)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +10/+19}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d10 (18)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13d12+39 (123)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13/+24}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d10 (19)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 16d12+64 (168)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +16/+29}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d10 (22)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19d12+95 (218)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +19/+37}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d10 (24)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 22d12+110 (253)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +22/+41}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d10 (26)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 25d12+150 (312)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +25/+44}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +34}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d10 (28)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 28d12+196 (378)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +28/+52}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +36}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d10 (31)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 31d12+248 (449)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +31/+56}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +40}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d10 (33)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 34d12+306 (527)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +34/+60}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +44}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d10 (36)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 34}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 37d12+370 (610)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 41}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +37/+64}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +48}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +30}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d10 (38)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 35}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small C}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 40d12+400 (660)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 45}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +40/+73}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +49}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +30}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d10 (40)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 38}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Red Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 16 (+6 natural), touch 10, flat-footed 16}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to fire, vulnerability to cold}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 18 (-1 size, +9 natural), touch 9, flat-footed 18}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 21 (-1 size, +12 natural), touch 9, flat-footed 21}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 24 (-1 size, +15 natural), touch 9, flat-footed 24}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small \textit{Locate object}}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 26 (-2 size, +18 natural), touch 8, flat-footed 26}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 19}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 29 (-2 size, +21 natural), touch 8, flat-footed 29}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 32 (-2 size, +24 natural), touch 8, flat-footed 32}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 33 (-4 size, +27 natural), touch 6, flat-footed 33}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small \textit{Suggestion}}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 36 (-4 size, +30 natural), touch 6, flat-footed 36}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 39 (-4 size, +33 natural), touch 6, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small \textit{Find the path}}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 42 (-4 size, +36 natural), touch 6, flat-footed 42}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 30}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.442in}|}{\begin{minipage}[t]{0.442in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 41 (-8 size, +39 natural), touch 2, flat-footed 41}\end{minipage}} & \multicolumn{1}{p{1.128in}|}{\begin{minipage}[t]{1.128in}\raggedright
{\small \textit{Discern location}}\end{minipage}} & \multicolumn{1}{p{0.969in}|}{\begin{minipage}[t]{0.969in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 32}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Chaos, Evil, and Fire domains 
as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

The small scales of a wyrmling red dragon are a bright glossy scarlet, making the 
dragon easily spotted by predators and hunters, so it stays underground and does 
not venture outside until it is more able to take care of itself. Toward the end 
of young age, the scales turn a deeper red, and the glossy texture is replaced 
by a smooth, dull finish. As the dragon grows older, the scales become large, thick, 
and as strong as metal. The neck frill and wings are an ash blue or purple-gray 
toward the edges, becoming darker with age. The pupils of a red dragon fade as 
it ages; the oldest red dragons have eyes that resemble molten lava orbs.

Combat

Because red dragons are so confident, they seldom pause to appraise an adversary. 
On spotting a target, they make a snap decision whether to attack, using one of 
many strategies worked out ahead of time. A red dragon lands to attack small, weak 
creatures with its claws and bite rather than obliterating them with its breath 
weapon, so as not to destroy any treasure they might be carrying.

\textbf{Breath Weapon (Su):} A red dragon has one type of breath weapon, a cone 
of fire.

\textit{\textbf{Locate Object }}\textbf{(Sp): }A juvenile or older red dragon can 
use this ability as the spell of the same name, once per day per age category.

\textbf{Other Spell-Like Abilities:} 3/day---\textit{suggestion }(old or older); 
1/day---\textit{find the path }(ancient or older), \textit{discern location }(great 
wyrm).

\textbf{Skills:} Appraise, Bluff, and Jump are considered class skills for red 
dragons.

\vspace{12pt}
WHITE DRAGON

\textbf{Dragon (Cold)}

\textbf{Environment:} Cold mountains

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 2; very young 3; young 4; juvenile 6; young 
adult 8; adult 10; mature adult 12; old 15; very old 17; ancient 18; wyrm 19; great 
wyrm 21

\textbf{Treasure: }Triple standard

\textbf{Alignment:} Always chaotic evil

\textbf{Advancement:} Wyrmling 4-5 HD; very young 7-8 HD; young 10-11 HD; juvenile 
13-14 HD; young adult 16-17 HD; adult 19-20 HD; mature adult 22-23 HD; old 25-26 
HD; very old 28-29 HD; ancient 31-32 HD; wyrm 34-35 HD; great wyrm 37+ HD 

\textbf{Level Adjustment:} Wyrmling +2; very young +3; young +3; juvenile +5; others 
---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.895in}|}{\begin{minipage}[t]{3.895in}\raggedright
\textbf{White Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.605in}|}{\begin{minipage}[t]{0.605in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.362in}|}{\begin{minipage}[t]{0.362in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small T}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 3d12+3 (22)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +3/-5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +3}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +3}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 1d6 (12)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 6d12+6 (45)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +6/+3}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 2d6 (14)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.362in}|}{\begin{minipage}[t]{0.362in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 9d12+18 (76)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9/+11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 3d6 (16)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 12d12+24 (102)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +12/+15}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 4d6 (18)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15d12+45 (142)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15/+23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 5d6 (20)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 18d12+72 (189)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +18/+28}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 6d6 (23)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 21d12+105 (241)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +21/+37}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 7d6 (25)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 24d12+120 (276)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +24/+41}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 8d6 (27)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 27d12+162 (337)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +27/+45}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +35}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 9d6 (29)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 30d12+180 (375)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +30/+49}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +39}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 10d6 (31)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 33d12+231 (445)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +33/+57}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +41}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 11d6 (33)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.339in}|}{\begin{minipage}[t]{0.339in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 36d12+288 (522)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small +36/+61}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +45}\end{minipage}} & \multicolumn{1}{p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.216in}|}{\begin{minipage}[t]{0.216in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.219in}|}{\begin{minipage}[t]{0.219in}\raggedright
{\small 12d6 (36)}\end{minipage}} & \multicolumn{1}{p{0.340in}|}{\begin{minipage}[t]{0.340in}\raggedright
{\small 32}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{White Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., burrow 30 ft., fly 150 ft. (average), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 14 (+2 size, +2 natural), touch 12, flat-footed 14}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Icewalking, immunity to cold, vulnerability to fire}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 150 ft. (average), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 16 (+1 size, +5 natural), touch 11, flat-footed 16}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small  }\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 18 (+8 natural), touch 10, flat-footed 18}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small  }\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 21 (+11 natural), touch 10, flat-footed 21}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textit{Fog cloud}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 23 (-1 size, +14 natural), touch 9, flat-footed 23}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 16}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 26 (-1 size, +17 natural), touch 9, flat-footed 26}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textit{Gust of wind}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 18}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 28 (-2 size, +20 natural), touch 8, flat-footed 28}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 31 (-2 size, +23 natural), touch 8, flat-footed 31}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textit{Freezing fog}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 34 (-2 size, +26 natural), touch 8, flat-footed 34}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 37 (-2 size, +29 natural), touch 8, flat-footed 37}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textit{Wall of ice}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 38 (-4 size, +32 natural), touch 6, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 60 ft., burrow 30 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 41 (-4 size, +35 natural), touch 6, flat-footed 41}\end{minipage}} & \multicolumn{1}{p{0.884in}|}{\begin{minipage}[t]{0.884in}\raggedright
{\small \textit{Control weather}}\end{minipage}} & \multicolumn{1}{p{0.979in}|}{\begin{minipage}[t]{0.979in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 27}\end{minipage}}\\
\hline
\end{longtable}

The scales of a wyrmling white dragon glisten like mirrors. As the dragon ages, 
the sheen disappears, and by very old age, scales of pale blue and light gray are 
mixed in with the white.

Combat

White dragons prefer sudden assaults, swooping down from aloft or bursting from 
beneath water, snow, or ice. They loose their breath weapon, then try to knock 
out a single opponent with a follow-up attack.

\textbf{Breath Weapon (Su): }A white dragon has one type of breath weapon, a cone 
of cold.

\textbf{Icewalking (Ex):} This ability works like the \textit{spider climb }spell, 
but the surfaces the dragon climbs must be icy. It is always in effect.

\textit{\textbf{Freezing Fog }}\textbf{(Sp): }An old or older white dragon can 
use this ability three times per day. It is similar to a \textit{solid fog }spell 
but also causes a rime of slippery ice to form on any surface the fog touches, 
creating the effect of a \textit{grease }spell. The dragon is immune to the \textit{grease 
}effect because of its icewalking ability. This ability is the equivalent of a 
5th-level spell.

\textbf{Other Spell-Like Abilities:} 3/day---\textit{fog cloud }(juvenile or older), 
\textit{gust of wind }(adult or older), \textit{wall of ice }(ancient or older); 
1/day---\textit{control weather }(great wyrm).

\textbf{Skills: }Hide, Move Silently, and Swim are considered class skills for 
white dragons.

\vspace{12pt}
{\LARGE METALLIC DRAGONS}

Metallic dragons make up the good branch of dragonkind, but they are every bit 
as aggressive as their evil cousins when threatened or challenged. They also tend 
to be covetous and proud.

\vspace{12pt}
BRASS DRAGON

\textbf{Dragon (Fire)}

\textbf{Environment:} Warm deserts

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 3; very young 4; young 6; juvenile 8; young 
adult 10; adult 12; mature adult 15; old 17; very old 19; ancient 20; wyrm 21; 
great wyrm 23

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always chaotic good

\textbf{Advancement:} Wyrmling 5-6 HD; very young 8-9 HD; young 11-12 HD; juvenile 
14-15 HD; young adult 17-18 HD; adult 20-21 HD; mature adult 23-24 HD; old 26-27 
HD; very old 29-30 HD; ancient 32-33 HD; wyrm 35-36 HD; great wyrm 38+ HD

\textbf{Level Adjustment:} Wyrmling +2; very young +3; young +4; juvenile +4; others 
---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.882in}|}{\begin{minipage}[t]{3.882in}\raggedright
\textbf{Brass Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.618in}|}{\begin{minipage}[t]{0.618in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.363in}|}{\begin{minipage}[t]{0.363in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small T}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 4d12+4 (30)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4/-4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 1d6 (13)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 7d12+7 (52)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +7/+4}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 2d6 (14)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.363in}|}{\begin{minipage}[t]{0.363in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10d12+20 (85)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +10/+12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 3d6 (17)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 13d12+26 (110)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +13/+16}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 4d6 (18)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 16d12+48 (152)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +16/+24}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 5d6 (21)}\end{minipage}} & \multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.039in}|}{\begin{minipage}[t]{0.039in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 19d12+76 (199)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +19/+29}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 6d6 (23)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 22d12+110 (253)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +22/+38}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 7d6 (26)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 25d12+125 (287)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +25/+42}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 8d6 (27)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 28d12+168 (350)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +28/+46}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +36}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 9d6 (30)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 31d12+186 (387)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +31/+50}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +40}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 10d6 (31)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 34d12+238 (459)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +34/+58}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +42}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 11d6 (34)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 32}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.981in}|}{\begin{minipage}[t]{0.981in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.190in}|}{\begin{minipage}[t]{0.190in}\raggedright
{\small 37d12+296 (536)}\end{minipage}} & \multicolumn{1}{p{0.366in}|}{\begin{minipage}[t]{0.366in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.166in}|}{\begin{minipage}[t]{0.166in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.163in}|}{\begin{minipage}[t]{0.163in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.187in}|}{\begin{minipage}[t]{0.187in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
{\small +37/+62}\end{minipage}} & \multicolumn{1}{p{0.303in}|}{\begin{minipage}[t]{0.303in}\raggedright
{\small +46}\end{minipage}} & \multicolumn{1}{p{0.262in}|}{\begin{minipage}[t]{0.262in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.207in}|}{\begin{minipage}[t]{0.207in}\raggedright
{\small 12d6 (36)}\end{minipage}} & \multicolumn{1}{p{0.349in}|}{\begin{minipage}[t]{0.349in}\raggedright
{\small 33}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Brass Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., burrow 30 ft., fly 150 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 15 (+2 size, +3 natural), touch 12, flat-footed 15}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to fire, }{\small \textit{speak with animals, }}{\small vulnerability 
to cold}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 150 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 17 (+1 size, +6 natural), touch 11, flat-footed 17}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small  }\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 19 (+9 natural), touch 10, flat-footed 19}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 22 (+12 natural), touch 10, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textit{Endure elements}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 24 (-1 size, +15 natural), touch 9, flat-footed 24}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 18}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 27 (-1 size, +18 natural), touch 9, flat-footed 27}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textit{Suggestion}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 29 (-2 size, +21 natural), touch 8, flat-footed 29}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 32 (-2 size, +24 natural), touch 8, flat-footed 32}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textit{Control winds}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 35 (-2 size, +27 natural), touch 8, flat-footed 35 DR}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small 15/magic}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 200 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 38 (-2 size, +30 natural), touch 8, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textit{Control weather}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 250 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 39 (-4 size, +33 natural), touch 6, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.427in}|}{\begin{minipage}[t]{0.427in}\raggedright
{\small 60 ft., burrow 30 ft., fly 250 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.802in}|}{\begin{minipage}[t]{0.802in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 42 (-4 size, +36 natural), touch 6, flat-footed 42}\end{minipage}} & \multicolumn{1}{p{0.943in}|}{\begin{minipage}[t]{0.943in}\raggedright
{\small \textit{Summon djinni}}\end{minipage}} & \multicolumn{1}{p{1.098in}|}{\begin{minipage}[t]{1.098in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.386in}|}{\begin{minipage}[t]{0.386in}\raggedright
{\small 30}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Chaos and Knowledge domains 
as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
At birth, a brass dragon's scales are a dull, mottled brown. As the dragon gets 
older, the scales become more brassy until they reach a warm, burnished appearance. 
The grand head-plates of a brass dragon are smooth and metallic, and it sports 
bladed chin horns that grow sharper with age. Wings and frills are mottled green 
toward the edges, darkening with age. As the dragon grows older, its pupils fade 
until the eyes resemble molten metal orbs.

Combat

Brass dragons would rather talk than fight. If an intelligent creature tries to 
leave without engaging in conversation, the dragon might force compliance in a 
fit of pique, using \textit{suggestion }or a dose of \textit{sleep }gas. A creature 
put to sleep may wake to find itself pinned or buried to the neck in the sand until 
the dragon's thirst for small talk is slaked. When faced with real danger, younger 
brass dragons fly out of sight, then hide by burrowing into the sand. Older dragons 
spurn this ploy but still prefer to have the advantage in combat.

\textbf{Breath Weapon (Su):} A brass dragon has two types of breath weapon, a line 
of fire and a cone of \textit{sleep}. Creatures within the cone must succeed on 
a Will save or fall asleep, regardless of HD, for 1d6 rounds plus 1 round per age 
category of the dragon.

\textbf{Spell-Like Abilities: }At will---\textit{speak with animals; }3/day---\textit{endure 
elements }(juvenile or older; radius 10 ft. x $ $dragon's age category); 1/day---\textit{suggestion 
}(adult or older), \textit{control winds }(old or older), \textit{control weather 
}(ancient or older).

\textit{\textbf{Summon Djinni }}\textbf{(Sp):} This ability, usable by a great 
wyrm brass dragon, works like a \textit{summon monster }spell, except that it summons 
one djinni. This ability is the equivalent of a 7th-level spell. 

Skills: Bluff, Gather Information, and Survival are considered class skills for 
brass dragons.

\vspace{12pt}
BRONZE DRAGON

\textbf{Dragon (Water)}

\textbf{Environment:} Temperate hills

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 3; very young 5; young 7; juvenile 9; young 
adult 12; adult 15; mature adult 17; old 19; very old 20; ancient 22; wyrm 23; 
great wyrm 25

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always lawful good

\textbf{Advancement:} Wyrmling 7-8 HD; very young 10-11 HD; young 13-14 HD; juvenile 
16-17 HD; young adult 19-20 HD; adult 22-23 HD; mature adult 25-26 HD; old 28-29 
HD; very old 31-32 HD; ancient 34-35 HD; wyrm 37-38 HD; great wyrm 40+ HD

\textbf{Level Adjustment:} Wyrmling +4; very young +4; young +6; others ---

\vspace{12pt}
\section*{\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Bronze Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d12+6 (45)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6/+3}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d6 (14)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 9d12+18 (76)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +9/+11}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d6 (16)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12d12+24 (102)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12/+15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d6 (18)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 15d12+45 (142)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +15/+23}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d6 (20)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18d12+72 (189)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +18/+28}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d6 (23)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 21d12+105 (241)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +21/+37}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d6 (25)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 24d12+120 (276)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +24/+41}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d6 (27)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 27d12+162 (337)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +27/+45}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +35}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d6 (29)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 30d12+180 (375)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +30/+49}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +39}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d6 (31)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 33d12+231 (445)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +33/+57}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +41}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d6 (33)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 33}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 36d12+288 (522)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +36/+61}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +45}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d6 (36)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 36}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 39d12+312 (565)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +39/+65}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +49}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d6 (37)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 37}\end{minipage}}\\
\hline
\end{longtable}
}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Bronze Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 100 ft. (average), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 16 (+1 size, +5 natural), touch 11, flat-footed 16}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to electricity, water breathing, }{\small \textit{speak with animals}}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 18 (+8 natural), touch 10, flat-footed 18}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 21 (+11 natural), touch 10, flat-footed 21}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Alternate form}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 23 (-1 size, +14 natural), touch 9, flat-footed 23}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 26 (-1 size, +17 natural), touch 9, flat-footed 26}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 28 (-2 size, +20 natural), touch 8, flat-footed 28}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small \textit{Create food and water, fog cloud}}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 31 (-2 size, +23 natural), touch 8, flat-footed 31}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 34 (-2 size, +26 natural), touch 8, flat-footed 34}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small \textit{Detect thoughts}}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 150 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 37 (-2 size, +29 natural), touch 8, flat-footed 37}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 38 (-4 size, +32 natural), touch 6, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small \textit{Control water}}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 41 (-4 size, +35 natural), touch 6, flat-footed 41}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.428in}|}{\begin{minipage}[t]{0.428in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.805in}|}{\begin{minipage}[t]{0.805in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 44 (-4 size, +38 natural), touch 6, flat-footed 44}\end{minipage}} & \multicolumn{1}{p{0.913in}|}{\begin{minipage}[t]{0.913in}\raggedright
{\small \textit{Control weather}}\end{minipage}} & \multicolumn{1}{p{1.120in}|}{\begin{minipage}[t]{1.120in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.390in}|}{\begin{minipage}[t]{0.390in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Animal, Law, and Water 
domains as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

A bronze wyrmling's scales are yellow tinged with green, showing only a hint of 
bronze. As the dragon approaches adulthood, its color deepens slowly to a darker, 
rich bronze tone. Very old dragons develop a blue-black tint to the edges of their 
scales. Powerful swimmers, they have webbed feet and smooth, flat scales. The pupils 
of its eyes fade as a dragon ages, until in the oldest the eyes resemble glowing 
green orbs.

Combat

Bronze dragons dislike killing animals and would rather bribe them (perhaps with 
food) or force them away magically. They use \textit{detect thoughts }to learn 
intelligent creatures' intentions.

When attacking they blind their opponents with \textit{fog cloud }and then charge 
or, if flying, snatch them up. Against seafaring opponents they conjure up a storm 
or use their tails to smash the vessels' hulls. If a dragon is inclined to be lenient, 
ships might be merely becalmed, fogbound, or broken-masted.

\textbf{Breath Weapon (Su): }Bronze dragons have two types of breath weapon, a 
line of lightning and a cone of \textit{repulsion }gas. Creatures within the cone 
must succeed on a Will save or be compelled to do nothing but move away from the 
dragon for 1d6 rounds plus 1 round per age category of the dragon. This is a mind-affecting 
compulsion enchantment effect.

\textbf{Water Breathing (Ex): }A bronze dragon can breathe underwater indefinitely 
and can freely use its breath weapon, spells, and other abilities while submerged.

\textbf{Alternate Form (Su): }A young or older bronze dragon can assume any animal 
or humanoid form of Medium size or smaller as a standard action three times per 
day. This ability functions as a \textit{polymorph }spell cast on itself at its 
caster level, except that the dragon does not regain hit points for changing form 
and can only assume the form of an animal or humanoid. The dragon can remain in 
its animal or humanoid form until it chooses to assume a new one or return to its 
natural form.

\textbf{Spell-Like Abilities:} At will---\textit{speak with animals; }3/day---\textit{create 
food and water }(adult or older), \textit{fog cloud }(adult or older), \textit{detect 
thoughts }(old or older), \textit{control water }(ancient or older); 1/day---\textit{control 
weather }(great wyrm).

\textbf{Skills:} Disguise, Swim, and Survival are considered class skills for bronze 
dragons.

\vspace{12pt}
COPPER DRAGON

\textbf{Dragon (Earth)}

\textbf{Environment: }Warm hills

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings: }Wyrmling 3; very young 5; young 7; juvenile 9; young 
adult 11; adult 14; mature adult 16; old 19; very old 20; ancient 22; wyrm 23; 
great wyrm 25

\textbf{Treasure: }Triple standard

\textbf{Alignment:} Always chaotic good

\textbf{Advancement:} Wyrmling 6-7 HD; very young 9-10 HD; young 12-13 HD; juvenile 
15-16 HD; young adult 18-19 HD; adult 21-22 HD; mature adult 24-25 HD; old 27-28 
HD; very old 30-31 HD; ancient 33-34 HD; wyrm 36-37 HD; great wyrm 39+ HD

\textbf{Level Adjustment:} Wyrmling +2; very young +3; young +4; juvenile +4; others 
---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Copper Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small T}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 5d12+5 (37)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5/-3}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +4}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d4 (13)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 8d12+8 (60)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 12}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +8/+5}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d4 (15)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 11d12+22 (93)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11/+13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d4 (17)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 14d12+28 (119)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +14/+17}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d4 (19)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17d12+51 (161)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +17/+25}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d4 (21)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 20d12+80 (210)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +20/+30}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d4 (24)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 23d12+115 (264)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +23/+39}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d4 (26)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 26d12+130 (299)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +26/+43}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +33}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d4 (28)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 29d12+174 (362)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +29/+47}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +37}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d4 (30)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 32d12+192 (400)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +32/+51}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +41}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d4 (32)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 35d12+245 (472)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +35/+59}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +43}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d4 (34)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 33}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 38d12+304 (551)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 37}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +38/+63}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +47}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d4 (37)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 35}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Copper Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 100 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 16 (+2 size, +4 natural), touch 12, flat-footed 16}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Immunity to acid, spider climb}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 100 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 18 (+1 size, +7 natural), touch 11, flat-footed 18}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 20 (+10 natural), touch 10, flat-footed 20}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 23 (+13 natural), touch 10, flat-footed 23}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 25 (-1 size, +16 natural), touch 9, flat-footed 25}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 19}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 28 (-1 size, +19 natural), touch 9, flat-footed 28}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small \textit{Stone shape}}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 30 (-2 size, +22 natural), touch 8, flat-footed 30}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 33 (-2 size, +25 natural), touch 8, flat-footed 33}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small \textit{Transmute rock to mud/mud to rock}}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 36 (-2 size, +28 natural), touch 8, flat-footed 36}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 39 (-2 size, +31 natural), touch 8, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small \textit{Wall of stone}}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 40 (-4 size, +34 natural), touch 6, flat-footed 40}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.444in}|}{\begin{minipage}[t]{0.444in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.715in}|}{\begin{minipage}[t]{0.715in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 43 (-4 size, +37 natural), touch 6, flat-footed 43}\end{minipage}} & \multicolumn{1}{p{1.150in}|}{\begin{minipage}[t]{1.150in}\raggedright
{\small \textit{Move earth}}\end{minipage}} & \multicolumn{1}{p{0.918in}|}{\begin{minipage}[t]{0.918in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.429in}|}{\begin{minipage}[t]{0.429in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Chaos, Earth, and Trickery 
domains as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

At birth, a copper dragon's scales have a ruddy brown color with a metallic tint. 
As the dragon gets older, the scales become finer and more coppery, assuming a 
soft, warm gloss by young adult age. Very old dragons' scales pick up a green tint. 
A copper dragon's pupils fade with age, and the eyes of great wyrms resemble glowing 
turquoise orbs.

Combat

A copper dragon appreciates wit and usually doesn't harm creatures that can relate 
a joke, humorous story, or riddle the dragon has not heard before. It quickly gets 
annoyed with anyone who doesn't laugh at its jokes or accept its tricks with good 
humor. It likes to taunt and annoy opponents into giving up or acting foolishly.

An angry copper dragon prefers to mire foes using \textit{transmute rock to mud}. 
The dragon pushes trapped opponents into the mud or snatches and carries them aloft. 
A copper dragon tries to draw airborne enemies into narrow, stony gorges where 
it can use its spider climb ability and maneuver them into colliding with the walls.

\textbf{Breath Weapon (Su):} A copper dragon has two types of breath weapon, a 
line of acid and a cone of \textit{slow }gas. Creatures within the cone must succeed 
on a Fortitude save or be slowed for 1d6 rounds plus 1 round per age category of 
the dragon.

\textbf{Spider Climb (Ex):} A copper dragon can climb on stone surfaces as though 
using the \textit{spider climb }spell.

\textbf{Spell-Like Abilities:} 2/day---\textit{stone shape }(adult or older); 1/day---\textit{transmute 
rock to mud }or \textit{mud to rock }(old or older), \textit{wall of stone }(ancient 
or older), \textit{move earth }(great wyrm).

\textbf{Skills:} Bluff, Hide, and Jump are considered class skills for copper dragons.

\vspace{12pt}
GOLD DRAGON

\textbf{Dragon (Fire)}

\textbf{Environment: }Warm plains

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 5; very young 7; young 9; juvenile 11; young 
adult 14; adult 16; mature adult 19; old 21; very old 22; ancient 24; wyrm 25; 
great wyrm 27

\textbf{Treasure:} Triple standard

\textbf{Alignment: }Always lawful good

\textbf{Advancement: }Wyrmling 9-10 HD; very young 12-13 HD; young 15-16 HD; juvenile 
18-19 HD; young adult 21-22 HD; adult 24-25 HD; mature adult 27-28 HD; old 30-31 
HD; very old 33-34 HD; ancient 36-37 HD; wyrm 39-40 HD; great wyrm 42+ HD

\textbf{Level Adjustment:} Wyrmling +4; very young +5; young +6; others ---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Gold Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 8d12+16 (68)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8/+11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d10 (16)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 11d12+33 (104)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +11/+20}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d10 (18)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14d12+42 (133)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +14/+25}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d10 (20)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 17d12+68 (178)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +17/+30}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +25}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d10 (22)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 20d12+100 (230)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +20/+38}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d10 (25)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 23d12+115 (264)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +23/+42}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d10 (26)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 26d12+156 (325)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +26/+46}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +36}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d10 (29)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 29d12+203 (391)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +29/+55}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +39}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d10 (31)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 32d12+256 (464)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 41}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +32/+59}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +43}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d10 (34)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 34}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 35d12+315 (542)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 43}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 28}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 28}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +35/+63}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +47}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d10 (36)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 36}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small C}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 38d12+380 (627)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 45}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 30}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 30}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +38/+71}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +47}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +21}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +31}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d10 (39)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 39}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small C}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 41d12+451 (717)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 47}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 32}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 32}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +41/+75}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +51}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +33}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +33}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d10 (41)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 41}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Gold Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 17 (+7 natural), touch 10, flat-footed 17}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Alternate form, immunity to fire, vulnerability to cold, water breathing}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 19 (-1 size, +10 natural), touch 9, flat-footed 19}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 22 (-1 size, +13 natural), touch 9, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 25 (-1 size, +16 natural), touch 9, flat-footed 25}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textit{Bless}}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 27 (-2 size, +19 natural), touch 8, flat-footed 27}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 21}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 30 (-2 size, +22 natural), touch 8, flat-footed 30}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textit{Luck bonus}}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 200 ft. (poor), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 33 (-2 size, +25 natural), touch 8, flat-footed 33}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 25}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 34 (-4 size, +28 natural), touch 6, flat-footed 34}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textit{Geas/quest, detect gems}}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 37 (-4 size, +31 natural), touch 6, flat-footed 37}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 28}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 40 (-4 size, +34 natural), touch 6, flat-footed 40}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textit{Sunburst }}{\small 15th}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 30}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 39 (-8 size, +37 natural), touch 2, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 31}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.425in}|}{\begin{minipage}[t]{0.425in}\raggedright
{\small 60 ft., fly 250 ft. (clumsy), swim 60 ft.}\end{minipage}} & \multicolumn{1}{p{0.753in}|}{\begin{minipage}[t]{0.753in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 42 (-8 size, +40 natural), touch 2, flat-footed 42}\end{minipage}} & \multicolumn{1}{p{0.862in}|}{\begin{minipage}[t]{0.862in}\raggedright
{\small \textit{Foresight}}\end{minipage}} & \multicolumn{1}{p{1.233in}|}{\begin{minipage}[t]{1.233in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.383in}|}{\begin{minipage}[t]{0.383in}\raggedright
{\small 33}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Law, Luck, and Good domains 
as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

On hatching, a gold dragon's scales are dark yellow with golden metallic flecks.

The flecks get larger as the dragon matures until, at the adult stage, the scales 
are completely golden. Gold dragons' faces are bewhiskered and sagacious; as they 
age, their pupils fade until the eyes resemble pools of molten gold.

Combat

Gold dragons usually parley before fighting. When conversing with intelligent creatures, 
they use Intimidate and Sense Motive to gain the upper hand. In combat, they employ 
\textit{bless }and their \textit{luck bonus; }older dragons use their \textit{luck 
bonus }at the start of each day. They make heavy use of spells in combat. Among 
their favorites are \textit{cloudkill, delayed blast fireball, fire shield, globe 
of invulnerability, maze, sleep, slow, }and \textit{stinking cloud.}

\textbf{Breath Weapon (Su): }A gold dragon has two types of breath weapon, a cone 
of fire and a cone of weakening gas. Creatures within a cone of weakening gas must 
succeed on a Fortitude save or take 1 point of Strength damage per age category 
of the dragon.

\textbf{Alternate Form (Su):} A gold dragon can assume any animal or humanoid form 
of Medium size or smaller as a standard action three times per day. This ability 
functions as a \textit{polymorph }spell cast on itself at its caster level, except 
that the dragon does not regain hit points for changing form and can only assume 
the form of an animal or humanoid. The dragon can remain in its animal or humanoid 
form until it chooses to assume a new one or return to its natural form.

\textbf{Water Breathing (Ex):} A gold dragon can breathe underwater indefinitely 
and can freely use its breath weapon, spells, and other abilities while submerged 
(the cone of fire becomes a cone of superheated steam underwater).

\textit{\textbf{Luck Bonus }}\textbf{(Sp):} Once per day an adult or older gold 
dragon can touch a gem, usually one embedded in the dragon's hide, and enspell 
it to bring good luck. As long as the dragon carries the gem, it and every good 
creature in a 10-foot radius per age category of the dragon receives a +1 luck 
bonus on all saving throws and similar rolls, as for a \textit{stone of good luck}. 
If the dragon gives an enspelled gem to another creature, only that bearer gets 
the bonus. The effect lasts 1d3 hours plus 3 hours per age category of the dragon 
but ends if the gem is destroyed. This ability is the equivalent of a 2nd-level 
spell.

\textit{\textbf{Detect Gems }}\textbf{(Sp):} An old or older gold dragon can use 
this ability three times per day. This is a divination effect similar to a \textit{detect 
magic }spell, except that it finds only gems. The dragon can scan a 60-degree arc 
each round: By concentrating for 1 round it knows if there are any gems within 
the arc; 2 rounds of concentration reveal the exact number of gems; and 3 rounds 
reveal their exact location, type, and value. This ability is the equivalent of 
a 2ndlevel spell.

\textbf{Other Spell-Like Abilities:} 3/day---\textit{bless }(juvenile or older); 
1/day---\textit{geas/quest }(old or older), \textit{sunburst }(ancient or older), 
\textit{foresight }(great wyrm).

\textbf{Skills: }Disguise, Heal, and Swim are considered class skills for gold 
dragons.

\vspace{12pt}
SILVER DRAGON

\textbf{Dragon (Cold)}

\textbf{Environment:} Temperate mountains

\textbf{Organization:} Wyrmling, very young, young, juvenile, and young adult: 
solitary or clutch (2-5); adult, mature adult, old, very old, ancient, wyrm, or 
great wyrm: solitary, pair, or family (1-2 and 2-5 offspring)

\textbf{Challenge Ratings:} Wyrmling 4; very young 5; young 7; juvenile 10; young 
adult 13; adult 15; mature adult 18; old 20; very old 21; ancient 23; wyrm 24; 
great wyrm 26

\textbf{Treasure:} Triple standard

\textbf{Alignment:} Always lawful good

\textbf{Advancement:} Wyrmling 8-9 HD; very young 11-12 HD; young 14-15 HD; juvenile 
17-18 HD; young adult 20-21 HD; adult 23-24 HD; mature adult 26-27 HD; old 29-30 
HD; very old 32-33 HD; ancient 35-36 HD; wyrm 38-39 HD; great wyrm 41+ HD

\textbf{Level Adjustment:} Wyrmling +4; very young +4; young +5; others ---

\vspace{12pt}
\begin{longtable}{llllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{16}{|p{3.897in}|}{\begin{minipage}[t]{3.897in}\raggedright
\textbf{Silver Dragons by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{16}{p{0.603in}|}{\begin{minipage}[t]{0.603in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small \textbf{Size}}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small \textbf{Hit Dice (hp)}}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small \textbf{Str}}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small \textbf{Dex}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Con}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Int}}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small \textbf{Wis}}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small \textbf{Cha}}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small \textbf{Base Attack/}}\linebreak
{\small \textbf{Grapple}}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small \textbf{Attack}}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small \textbf{Fort Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Ref Save}}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small \textbf{Will Save}}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small \textbf{Breath Weapon (DC)}}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small \textbf{Frightful Presence DC}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small S}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 7d12+7 (52)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7/+4}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +6}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +5}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 2d8 (14)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 10d12+20 (85)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 14}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +10/+12}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +12}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +7}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +9}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 4d8 (17)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.365in}|}{\begin{minipage}[t]{0.365in}\centering
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small M}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 13d12+26 (110)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +13/+16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +8}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 6d8 (18)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 16d12+48 (152)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 17}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +16/+24}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +10}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 8d8 (21)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Young adult}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small L}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19d12+76 (199)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 19}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 18}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +19/+29}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +11}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small +15}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 10d8 (23)}\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\raggedright
{\small 23}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 22d12+110 (253)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +22/+38}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +28}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +13}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +18}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 12d8 (26)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 25d12+125 (287)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 21}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 20}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +25/+42}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +14}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 14d8 (27)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 28d12+168 (350)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 22}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +28/+46}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +36}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +16}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 16d8 (30)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 30}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small H}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 31d12+186 (387)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 33}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 23}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 24}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +31/+50}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +40}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +23}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +17}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +24}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 18d8 (31)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 32}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 34d12+238 (459)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 35}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 25}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 27}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 26}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +34/+58}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +42}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +26}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +19}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +27}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 20d8 (34)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 35}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small G}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 37d12+333 (573)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 39}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 28}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 29}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 28}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +37/+63}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +47}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +20}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +29}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 22d8 (37)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 37}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{17}{p{0.968in}|}{\begin{minipage}[t]{0.968in}\centering
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.338in}|}{\begin{minipage}[t]{0.338in}\centering
{\small C}\end{minipage}} & \multicolumn{1}{p{0.186in}|}{\begin{minipage}[t]{0.186in}\raggedright
{\small 40d12+400 (660)}\end{minipage}} & \multicolumn{1}{p{0.377in}|}{\begin{minipage}[t]{0.377in}\raggedright
{\small 43}\end{minipage}} & \multicolumn{1}{p{0.162in}|}{\begin{minipage}[t]{0.162in}\raggedright
{\small 10}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small 30}\end{minipage}} & \multicolumn{1}{p{0.159in}|}{\begin{minipage}[t]{0.159in}\raggedright
{\small 31}\end{minipage}} & \multicolumn{1}{p{0.182in}|}{\begin{minipage}[t]{0.182in}\raggedright
{\small 30}\end{minipage}} & \multicolumn{1}{p{0.189in}|}{\begin{minipage}[t]{0.189in}\raggedright
{\small +40/+72}\end{minipage}} & \multicolumn{1}{p{0.312in}|}{\begin{minipage}[t]{0.312in}\raggedright
{\small +48}\end{minipage}} & \multicolumn{1}{p{0.256in}|}{\begin{minipage}[t]{0.256in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small +22}\end{minipage}} & \multicolumn{1}{p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
{\small +32}\end{minipage}} & \multicolumn{1}{p{0.220in}|}{\begin{minipage}[t]{0.220in}\raggedright
{\small 24d8 (40)}\end{minipage}} & \multicolumn{1}{p{0.343in}|}{\begin{minipage}[t]{0.343in}\raggedright
{\small 40}\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{7}{|p{4.214in}|}{\begin{minipage}[t]{4.214in}\raggedright
\textbf{Silver Dragon Abilities by Age}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{7}{p{0.286in}|}{\begin{minipage}[t]{0.286in}\raggedright
{\small \textbf{Age}}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small \textbf{Speed}}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small \textbf{Initiative}}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small \textbf{AC}}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textbf{Special Abilities}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small \textbf{Caster Level}}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small \textbf{SR}}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.183in}|}{\begin{minipage}[t]{0.183in}\raggedright
{\small Wyrmling}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 100 ft. (average)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 17 (+1 size, +6 natural), touch 11, flat-footed 17}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Alternate form, immunity to acid and cold, cloudwalking, vulnerability 
to fire}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Very young}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 19 (+9 natural), touch 10, flat-footed 19}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 22 (+12 natural), touch 10, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small 1st}\end{minipage}} & \multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.041in}|}{\begin{minipage}[t]{0.041in}\raggedright
{\small Juvenile}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 24 (-1 size, +15 natural), touch 9, flat-footed 24}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textit{Feather fall}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 3rd}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Young adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 27 (-1 size, +18 natural), touch 9, flat-footed 27}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small DR 5/magic}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 5th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 20}\end{minipage}}\\
\hline
% ROW 8
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 29 (-2 size, +21 natural), touch 8, flat-footed 29}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textit{Fog cloud}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 7th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 22}\end{minipage}}\\
\hline
% ROW 9
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Mature adult}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 32 (-2 size, +24 natural), touch 8, flat-footed 32}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small DR 10/magic}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 9th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 24}\end{minipage}}\\
\hline
% ROW 10
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Old}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 35 (-2 size, +27 natural), touch 8, flat-footed 35}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textit{Control winds}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 11th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 26}\end{minipage}}\\
\hline
% ROW 11
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Very old}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 150 ft. (poor)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 38 (-2 size, +30 natural), touch 8, flat-footed 38}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small DR 15/magic}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 13th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 27}\end{minipage}}\\
\hline
% ROW 12
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Ancient}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 39 (-4 size, +33 natural), touch 6, flat-footed 39}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textit{Control weather}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 15th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 29}\end{minipage}}\\
\hline
% ROW 13
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Wyrm}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 42 (-4 size, +36 natural), touch 6, flat-footed 42}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small DR 20/magic}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 17th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 30}\end{minipage}}\\
\hline
% ROW 14
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small Great wyrm}\end{minipage}} & \multicolumn{1}{|p{0.426in}|}{\begin{minipage}[t]{0.426in}\raggedright
{\small 40 ft., fly 200 ft. (clumsy)}\end{minipage}} & \multicolumn{1}{p{0.598in}|}{\begin{minipage}[t]{0.598in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{1}{p{0.375in}|}{\begin{minipage}[t]{0.375in}\raggedright
{\small 41 (-8 size, +39 natural), touch 2, flat-footed 41}\end{minipage}} & \multicolumn{1}{p{0.877in}|}{\begin{minipage}[t]{0.877in}\raggedright
{\small \textit{Reverse gravity}}\end{minipage}} & \multicolumn{1}{p{1.370in}|}{\begin{minipage}[t]{1.370in}\raggedright
{\small 19th}\end{minipage}} & \multicolumn{1}{p{0.385in}|}{\begin{minipage}[t]{0.385in}\raggedright
{\small 32}\end{minipage}}\\
\hline
% ROW 15
\multicolumn{8}{p{0.469in}|}{\begin{minipage}[t]{0.469in}\raggedright
{\small *Can also cast cleric spells and those from the Air, Good, Law, and Sun 
domains as arcane spells.}\end{minipage}}\\
\hline
\end{longtable}

A silver wyrmling's scales are blue-gray with silver highlights. As the dragon 
approaches adulthood, its color gradually brightens until the individual scales 
are scarcely visible.

Combat

Silver dragons are not violent and avoid combat except when faced with highly evil 
or aggressive foes. If necessary, they use \textit{fog cloud }or \textit{control 
weather }to blind or confuse opponents before attacking. When angry, they use \textit{reverse 
gravity }to fling enemies helplessly into the air, where they can be snatched. 
Against flying opponents, a silver dragon hides in clouds (creating some with \textit{control 
weather }on clear days), then jumps to the attack when it has the advantage.

\textbf{Breath Weapon (Su): }A silver dragon has two types of breath weapon, a 
cone of cold and a cone of paralyzing gas. Creatures within a cone of paralyzing 
gas must succeed on a Fortitude save or be paralyzed for 1d6 rounds plus 1 round 
per age category of the dragon.

\textbf{Alternate Form (Su):} A silver dragon can assume any animal or humanoid 
form of Medium size or smaller as a standard action three times per day. This ability 
functions as a \textit{polymorph }spell cast on itself at its caster level, except 
that the dragon does not regain hit points for changing form and can only assume 
the form of an anirmal or humanoid. The dragon can remain in its animal or humanoid 
form until it chooses to assume a new one or return to its natural form.

\textbf{Cloudwalking (Su):} A silver dragon can tread on clouds or fog as though 
on solid ground. The ability functions continuously but can be negated or resumed 
at will.

\textbf{Spell-Like Abilities: }3/day---\textit{fog cloud }(adult or older), \textit{control 
winds }(old or older); 2/day---\textit{feather fall }(juvenile or older); 1/day--- 
\textit{control weather }(ancient or older), \textit{reverse gravity }(great wyrm).

\textbf{Skills: }Bluff, Disguise, and Jump are considered class skills for silver 
dragons.

\vspace{12pt}
{\LARGE DRAGON TURTLE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.941in}|}{\begin{minipage}[t]{2.941in}\raggedright
Huge Dragon (Aquatic)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
12d12+60 (138 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.941in}|}{\begin{minipage}[t]{2.941in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
20 ft. (4 squares), swim 30 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
25 (-2 size, +17 natural), touch 8, flat-footed 25\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
+12/+28\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Bite +18 melee (4d6+8)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Bite +18 melee (4d6+8) and 2 claws +13 melee (2d8+4)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
15 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Breath weapon, snatch, capsize\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Darkvision 60 ft., immunity to fire, \textit{sleep, }and paralysis, low-light vision, 
scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Fort +13, Ref +8, Will +9\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Str 27, Dex 10, Con 21, Int 12, Wis 13, Cha 12\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Diplomacy +3, Hide +7*, Intimidate +16, Listen +16, Search +16, Sense Motive +16, 
Spot +16, Survival +16 (+18 following tracks), Swim +21\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Blind-Fight, Cleave, Improved Bull Rush, Power Attack, Snatch\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Temperate aquatic\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
9\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Triple standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
13-24 HD (Huge); 25-36 HD (Gargantuan)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.422in}|}{\begin{minipage}[t]{1.422in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.078in}|}{\begin{minipage}[t]{3.078in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Its rough, deep green shell is much the same color as the deep water the monster 
favors, and the silver highlights that line the shell resemble light dancing on 
open water. The turtle's legs, tail, and head are a lighter green, flecked with 
golden highlights. An adult dragon turtle can measure from 20 to 30 feet from snout 
to tail, with a shell from 15 to 25 feet in diameter, and can weigh 8,000 to 32,000 
pounds.

Dragon turtles speak Aquan, Draconic, and Common.

COMBAT

Dragon turtles are fierce fighters and generally attack any creature that threatens 
their territory or looks like a potential meal.

\textbf{Breath Weapon (Su):} Cloud of superheated steam 20 feet high, 25 feet wide, 
and 50 feet long, once every 1d4 rounds, damage 12d6 fire, Reflex DC 21 half; effective 
both on the surface and underwater. The save DC is Constitution-based.

\textbf{Capsize (Ex): }A submerged dragon turtle that surfaces under a boat or 
ship less than 20 feet long capsizes the vessel 95\% of the time. It has a 50\% 
chance to capsize a vessel from 20 to 60 feet long and a 20\% chance to capsize 
one over 60 feet long. 

\textbf{Skills:} A dragon turtle has a +8 racial bonus on any Swim check to perform 
some special action or avoid a hazard. It can always choose to take 10 on a Swim 
check, even if distracted or endangered.

It can use the run action while swimming, provided it swims in a straight line.

*Dragon turtles have a +8 racial bonus on Hide checks when submerged.

\vspace{12pt}
{\LARGE DRAGONNE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.062in}|}{\begin{minipage}[t]{3.062in}\raggedright
Large Magical Beast\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
9d10+27 (76 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.062in}|}{\begin{minipage}[t]{3.062in}\raggedright
+6\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
40 ft. (8 squares), fly 30 ft. (poor)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
18 (-1 size, +2 Dex, +7 natural), touch 11, flat-footed 16\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+9/+17\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Bite +12 melee (2d6+4)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Bite +12 melee (2d6+4) and 2 claws +7 melee (2d4+2)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
10 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Pounce, roar\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Darkvision 60 ft., low-light vision, scent\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Fort +9, Ref +8, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Str 19, Dex 15, Con 17, Int 6, Wis 12, Cha 12\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Listen +11, Spot +11\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Blind-Fight, Combat Reflexes, Improved Initiative, Track\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Temperate deserts\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Solitary, pair, or pride (5-10)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
7\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Double standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
10-12 HD (Large); 13-27 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.312in}|}{\begin{minipage}[t]{1.312in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.188in}|}{\begin{minipage}[t]{3.188in}\raggedright
+4 (cohort)\end{minipage}}\\
\hline
\end{longtable}

A dragonne possesses huge claws and fangs, and large eyes, usually the color of 
its scales. A dragonne is about 12 feet long and weighs about 700 pounds.

Dragonnes speak Draconic.

COMBAT

A dragonne's wings are useful only for short flights, carrying the creature for 
10 to 30 minutes at a time. Nevertheless, it uses its wings effectively in battle. 
If opponents attempt to charge or encircle it, the dragonne simply takes to the 
air and finds a more defensible position.

\textbf{Pounce (Ex): }If a dragonne charges, it can make a full attack in the same 
round.

\textbf{Roar (Su):} A dragonne can loose a devastating roar every 1d4 rounds. All 
creatures except dragonnes within 120 feet must succeed on a DC 15 Will save or 
become fatigued. Those within 30 feet who fail their saves become exhausted. The 
save DC is Charisma-based.

\textbf{Skills: }Dragonnes have a +4 racial bonus on Listen and Spot checks. 

\textbf{Carrying Capacity:} A light load for a dragonne is up to 348 pounds; a 
medium load, 349-699 pounds, and a heavy load, 700-1,050 pounds.

\vspace{12pt}
\subsection*{{\LARGE DRIDER}}

\subsection*{\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.048in}|}{\begin{minipage}[t]{3.048in}\raggedright
Large Aberration\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
6d8+18 (45 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.048in}|}{\begin{minipage}[t]{3.048in}\raggedright
+2\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
30 ft. (6 squares), climb 15 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
17 (-1 size, +2 Dex, +6 natural), touch 11, flat-footed 15\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.064in}|}{\begin{minipage}[t]{0.064in}\raggedright
+4/+10\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Dagger +5 melee (1d6+2/19-20) or bite +6 melee (1d4+1 plus poison) or shortbow 
+5 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
2 daggers +3 melee (1d6+2/19-20, 1d6+1/19-20) and bite +1 melee (1d4+1 plus poison); 
or shortbow +5 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
10 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Spells, spell-like abilities, poison\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Darkvision 60 ft., spell resistance 17\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Fort +5, Ref +4, Will +8\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Str 15, Dex 15, Con 16, Int 15, Wis 16, Cha 16\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Climb +14, Concentration +9, Hide +10, Listen +9, Move Silently +12, Spot +9\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Combat Casting, Two-Weapon Fighting, Weapon Focus (bite)\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Solitary, pair, or troupe (1-2 plus 7-12 Medium monstrous spiders)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
7\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Double standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
Always chaotic evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.325in}|}{\begin{minipage}[t]{1.325in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.175in}|}{\begin{minipage}[t]{3.175in}\raggedright
+4\end{minipage}}\\
\hline
\end{longtable}
}

Driders speak Elven, Common, and Undercommon.

COMBAT

Driders seldom pass up an opportunity to attack other creatures, especially from 
ambush. They usually begin with a spell assault and often levitate out of the enemy's 
reach.

\textbf{Poison (Ex):} Injury, Fortitude DC 16, initial and secondary damage 1d6 
Str. The save DC is Constitution based.

\textbf{Spell-Like Abilities: }1/day---\textit{dancing lights }(DC 13), \textit{clairaudience/clairvoyance, 
darkness, detect good, detect law, detect magic, dispel magic, faerie fire, levitate, 
suggestion }(DC 16). Caster level 6th. The save DCs are Charisma-based.

\textbf{Spells:} Driders cast spells as 6th-level clerics, wizards, or sorcerers. 
Drider clerics can choose from the following domains: Chaos, Destruction, Evil, 
and Trickery. The typical spells prepared shown here are for a drider sorcerer.

\textit{Typical Sorcerer Spells Known }(6/7/6/4, base save DC 13 + spell level): 
0---\textit{daze, detect magic, ghost sound, mage hand, ray of frost, read magic, 
resistance; }1st---\textit{mage armor, magic missile, ray of enfeeblement, silent 
image; }2nd--- \textit{invisibility, web; }3rd---\textit{lightning bolt}.

\textbf{Skills: }A drider has a +4 racial bonus on Hide and Move Silently checks. 
It has a +8 racial bonus on Climb checks and can always choose to take 10 on a 
Climb check, even if rushed or threatened.

\vspace{12pt}
{\LARGE DRYAD}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.892in}|}{\begin{minipage}[t]{2.892in}\raggedright
Medium Fey\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
4d6 (14 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.892in}|}{\begin{minipage}[t]{2.892in}\raggedright
+4\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
30 ft. (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
17 (+4 Dex, +3 natural), touch 14, flat-footed 13\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+2/+2\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Dagger +6 melee (1d4/19-20) or masterwork longbow +7 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Dagger +6 melee (1d4/19-20) or masterwork longbow +7 ranged (1d8/x3)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Spell-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Damage reduction 5/cold iron, tree dependent, wild empathy\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Fort +3, Ref +8, Will +6\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Str 10, Dex 19, Con 11, Int 14, Wis 15, Cha 18\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Escape Artist +11, Handle Animal +11, Hide +11, Knowledge (nature) +11, Listen 
+9, Move Silently +11, Ride +6, Spot +9, Survival +9, Use Rope +4 (+6 with bindings)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Great Fortitude, Weapon Finesse\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Temperate forests\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Solitary or grove (4-7)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
Usually chaotic good\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.031in}|}{\begin{minipage}[t]{3.031in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A dryad's delicate features are much like a female elf 's, though her flesh is 
like bark or fine wood, and her hair is like a canopy of leaves that changes color 
with the seasons. 

Although they are generally solitary, up to seven dryads have been encountered 
in one place on rare occasions.

Dryads speak Common, Elven, and Sylvan.

COMBAT

Shy, intelligent, and resolute, dryads are as elusive as they are alluring---they 
avoid physical combat and are rarely seen unless they wish to be. If threatened, 
or in need of an ally, a dryad uses \textit{charm person }or \textit{suggestion, 
}attempting to gain control of the attacker(s) who could help the most against 
the rest. Any attack on her tree, however, provokes the dryad into a frenzied defense.

\textbf{Spell-Like Abilities:} At will---\textit{entangle }(DC 13), \textit{speak 
with plants, tree shape; }3/day--- \textit{charm person }(DC 13), \textit{deep 
slumber }(DC 15), \textit{tree stride; }1/day---\textit{suggestion }(DC 15)\textit{. 
}Caster level 6th. The save DCs are Wisdom-based.

\textbf{Tree Dependent (Su): }Each dryad is mystically bound to a single, enormous 
oak tree and must never stray more than 300 yards from it. Any who do become ill 
and die within 4d6 hours. A dryad's oak does not radiate magic. 

\textbf{Wild Empathy (Ex):} This power works like the druid's wild empathy class 
feature, except that the dryad has a +6 racial bonus on the check.

\vspace{12pt}
{\LARGE DWARF}

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
\textbf{Dwarf, 1st-Level Warrior}\end{minipage}} & \multicolumn{1}{p{1.826in}|}{\begin{minipage}[t]{1.826in}\raggedright
\textbf{Duergar, 1st-Level Warrior}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Humanoid (Dwarf)\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Humanoid (Dwarf)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
1d8+2 (6 hp)\end{minipage}} & \multicolumn{1}{p{1.826in}|}{\begin{minipage}[t]{1.826in}\raggedright
1d8+5 (9 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+0\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
20 ft. in scale mail (4 squares); base speed 20 ft.\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
20 ft. in chainmail (4 squares); base speed 20 ft.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
16 (+4 scale mail, +2 heavy shield), touch 10, flat-footed 16\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
17 (+5 chainmail, +2 heavy shield), touch 10, flat-footed 17\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
+1/+2\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
+1/+2\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Dwarven waraxe +3 melee (1d10+1/x3) or shortbow +1 ranged (1d6/x3)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Warhammer +2 melee (1d8+1/x3) or light crossbow +1 ranged (1d8/19-20)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Dwarven waraxe +3 melee (1d10+1/x3) or shortbow +1 ranged (1d6/x3)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Warhammer +2 melee (1d8+1/x3) or light crossbow +1 ranged (1d8/19-20)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Dwarf traits\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Duergar traits, spell-like abilities\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Darkvision 60 ft., dwarf traits\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Darkvision 60 ft., duergar traits\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Fort +4*, Ref +0*, Will -1*\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Fort +4*, Ref +0*, Will -1*\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Str 13, Dex 11, Con 14, Int 10, Wis 9, Cha 6\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Str 13, Dex 11, Con 14, Int 10, Wis 9, Cha 4\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Appraise +2, Craft (blacksmithing) +2, Craft (stonemasonry) +2, Listen +2, Spot 
+2\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Appraise +2, Craft (blacksmithing) +2, Craft (stonemasonry) +2, Listen +3, Move 
Silently -4, Spot +2\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Weapon Focus (dwarven waraxe)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Toughness\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Temperate mountains \linebreak
(Deep: Underground)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Team (2-4), squad (11-20 plus 2 3rd-level sergeants and 1 leader of 3rd-6th level), 
or clan (30-100 plus 30\% noncombatants plus 1 3rd-level sergeant per 10 adults, 
5 5th-level lieutenants, and 3 7th-level captains)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Team (2-4), squad (9-16 plus 3 3rd-level sergeants and 1 leader of 3rd-8th level) 
or clan (20-80 plus 25\% noncombatants plus 1 3rd-level sergeant per 5 adults, 
3-6 6th-level lieutenants, and 1-4 9th-level captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
{\small \textbf{Challenge Rating:}}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
{\small }\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
{\small 1}\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Standard coins; double goods; standard items\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Standard coins, double goods, standard items\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
Often lawful good \linebreak
(Deep: Usually lawful neutral or neutral)\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
Often lawful evil\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
By character class\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{0.725in}|}{\begin{minipage}[t]{0.725in}\raggedright
{\small \textbf{Level Adjustment:}}\end{minipage}} & \multicolumn{1}{p{1.822in}|}{\begin{minipage}[t]{1.822in}\raggedright
{\small +0}\end{minipage}} & \multicolumn{4}{p{1.953in}|}{\begin{minipage}[t]{1.953in}\raggedright
{\small +1}\end{minipage}}\\
\hline
\end{longtable}

Dwarves favor earth tones in their clothing and prefer simple and functional garb. 
The skin can be very dark, but it is always some shade of tan or brown. Hair color 
can be black, gray, or brown. Dwarves average 4 feet tall and weigh as much as 
adult humans.

Dwarves speak Dwarven. Most who travel outside dwarven lands (as traders, mercenaries, 
or adventurers) know the Common tongue, while warriors in the dwarven cities usually 
learn Goblin to better interrogate and spy on those evil denizens of the deep caves.

Most dwarves encountered outside their home are warriors.

COMBAT

Dwarves are experts in combat, effectively using their environment and executing 
well-planned group attacks. They rarely use magic in fights, since they have few 
wizards or sorcerers (but dwarven clerics throw themselves into battle as heartily 
as their fellow warriors). If they have time to prepare, they may build deadfalls 
or other traps involving stone. In addition to the dwarven waraxe and thrown hammer, 
dwarves also use warhammers, picks, shortbows, heavy crossbows, and maces.

\textbf{Dwarf Traits (Ex):} Dwarves possess the following racial traits.---

+2 Constitution, -2 Charisma.---

Medium size.---

A dwarf 's base land speed is 20 feet. However, dwarves can move at this speed 
even when wearing medium or heavy armor or when carrying a medium or heavy load.---

Darkvision out to to 60 feet.---

Stonecunning: This ability grants a dwarf a +2 racial bonus on Search checks to 
notice unusual stonework, such as sliding walls, stonework traps, new construction 
(even when built to match the old), unsafe stone surfaces, shaky stone ceilings, 
and the like. Something that isn't stone but that is disguised as stone also counts 
as unusual stonework. A dwarf who merely comes within 10 feet of unusual stonework 
can make a Search check as if he were actively searching, and a dwarf can use the 
Search skill to find stonework traps as a rogue can. A dwarf can also intuit depth, 
sensing his approximate depth underground as naturally as a human can sense which 
way is up. Dwarves have a sixth sense about stonework, an innate ability that they 
get plenty of opportunity to practice and hone in their underground homes.---

Weapon Familiarity: Dwarves treat dwarven waraxes and dwarven urgroshes as martial 
weapons, rather than exotic weapons.---

Stability: Dwarves are exceptionally stable on their feet. A dwarf has a +4 bonus 
on ability checks made to resist being bull rushed or tripped when standing on 
the ground (but not when climbing, flying, riding, or otherwise not standing firmly 
on the ground).---

+2 racial bonus on saving throws against poison. *Not reflected in the saving throw 
numbers given here.---

+2 racial bonus on saving throws against spells and spell-like effects. *Not reflected 
in the saving throw numbers given here.---

+1 racial bonus on attack rolls against orcs (including halforcs) and goblinoids 
(including goblins, hobgoblins, and bugbears).---

+4 dodge bonus to Armor Class against creatures of the giant type (such as ogres, 
trolls, and hill giants).---

+2 racial bonus on Appraise checks that are related to stone or metal items.---

+2 racial bonus on Craft checks that are related to stone or metal.---

Automatic Languages: Common, Dwarven. Bonus Languages: Giant, Gnome, Goblin, Orc, 
Terran, Undercommon.---

Favored Class: Fighter.

The dwarf warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8.

SUBRACES

The information above is for hill dwarves, the most common variety.

There are three other major dwarven subraces, which differ from hill dwarves as 
follows.

\textbf{Deep Dwarf}

These dwarves live far underground and tend to be more standoffish with non-dwarves.

Deep dwarves are the same height as other dwarves, but leaner.  Their skin sometimes 
has a reddish tinge, and their large eyes lack the brightness of those of their 
kindred, being a washed-out blue. Their hair color ranges from bright red to straw 
blond. They have little contact with surface dwellers, relying on hill dwarves 
or mountain dwarves to trade goods for them.

Deep dwarves speak Dwarven and Goblin, and occasionally Draconic or Undercommon.

\textbf{Deep Dwarf Traits (Ex):} These traits are in addition to the hill dwarf 
traits, except where noted.---

Racial bonus on saves against spells and spell-like abilities increases to +3.---

Racial bonus on Fortitude saves against poisons increases to +3.---

Darkvision out to 90 feet.---

Light Sensitivity: Deep dwarves are dazzled in bright sunlight or within the radius 
of a \textit{daylight }spell.

\textbf{Duergar}

Sometimes called gray dwarves, these evil beings dwell in the underground.

Most duergar are bald (even the females), and they dress in drab clothing that 
is designed to blend into stone. In their lairs they may wear jewelry, but it is 
always kept dull. They war with other dwarves, even allying with other underground 
creatures from time to time.

Duergar speak Dwarven and Undercommon.

\textbf{Duergar Traits (Ex):} These traits are in addition to the hill dwarf traits, 
except where noted.----

4 Charisma instead of -2.---

Darkvision out to 120 feet.---

Immunity to paralysis, phantasms, and poison. This trait replaces the hill dwarf 
's +2 racial bonus on saving throws against poison.---

+2 racial bonus on saves against spells and spell-like abilities.---

Spell-Like Abilities: 1/day---\textit{enlarge person }and \textit{invisibility 
}as a wizard of twice the duergar's class level (minimum caster level 3rd); these 
abilities affect only the duergar and whatever it carries.---

Light Sensitivity: Duergar are dazzled in bright sunlight or within the radius 
of a \textit{daylight }spell.---

+4 racial bonus on Move Silently checks.---

+1 racial bonus on Listen and Spot checks.---

Automatic Languages: Common, Dwarven, Undercommon.

Bonus Languages: Draconic, Giant, Goblin, Orc, Terran. This trait replaces the 
hill dwarf 's automatic and bonus languages.---

Favored Class: Fighter.---

Level adjustment +1---

Unlike other dwarves, duergar do not have weapon familiarity with the dwarven waraxe 
and dwarven urgrosh.

The duergar warrior presented here had the following ability scores before racial 
adjustments: Str 13, Dex 11, Con 12, Int 10, Wis 9, Cha 8.

\textbf{Challenge Rating:} Duergar with levels in NPC classes have a CR equal to 
their character level. Duergar with levels in PC classes have a CR equal to their 
character level +1.

\textbf{Mountain Dwarf}

Mountain dwarves live deeper under the mountains than hill dwarves but generally 
not as far underground as deep dwarves. They average about 4-1/2 feet tall and 
have lighter skin and hair than hill dwarves, but the same general appearance.

\end{document}
