%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\subsection*{{\LARGE MONSTERS (INTRO-A)}}

\vspace{12pt}
\subsection*{{\LARGE READING THE ENTRIES}}

Each monster description is organized in the same general format, as outlined below. 

\vspace{12pt}
STATISTICS BLOCK

This portion of a monster description contains basic game information on the creature.

\section*{\textbf{Name}}

This is the name by which the creature is generally known. The descriptive text 
may provide other names.

\section*{\textbf{Size and Type}}

This line describes the creature's size. A size modifier applies to the creature's 
Armor Class (AC) and attack bonus, as well as to certain skills. A creature's size 
also determines how far it can reach to make a melee attack and how much space 
it occupies in a fight (see Space/Reach, below). 

The size and type line continues with the creature's type. Type determines how 
magic affects a creature. Type determines certain features, such as Hit Dice size, 
base attack bonus, base saving throw bonuses, and skill points. 

\section*{\textbf{Hit Dice}}

This line gives the creature's number and type of Hit Dice, and lists any bonus 
hit points. A parenthetical note gives the average hit points for a creature of 
the indicated number of Hit Dice. A creature's Hit Dice total is also treated as 
its level for determining how spells affect the creature, its rate of natural healing, 
and its maximum ranks in a skill.

\section*{\textbf{Initiative}}

This line gives the creature's modifier on initiative checks.

\section*{\textbf{Speed}}

This line gives the creature's tactical speed on land (the amount of distance it 
can cover in one move action). If the creature wears armor that reduces its speed, 
the creature's base land speed follows.

If the creature has other modes of movement, these are given after (or in place 
of) the land speed. Unless noted otherwise, modes of movement are natural (not 
magical).

\section*{\textbf{Armor Class}}

The Armor Class line gives the creature's AC for normal combat and includes a parenthetical 
mention of the modifiers contributing to it (usually size, Dexterity, and natural 
armor). The creature's touch and flat-footed ACs follow the combat-ready AC.

A creature's armor proficiencies (if it has any) depend on its type, but in general 
a creature is automatically proficient with any kind of armor it is described as 
wearing (light, medium, or heavy), and with all lighter kinds of armor.

\section*{\textbf{Base Attack/Grapple}}

The number before the slash on this line is the creature's base attack bonus (before 
any modifiers are applied). This number won't often be used, but it can be handy 
sometimes, especially if the creature has the Power Attack or Combat Expertise 
feats.

The number after the slash is the creature's grapple bonus, which is used when 
the creature makes a grapple attack or when someone tries to grapple the creature. 
The grapple bonus includes all modifiers that apply to the creature's grapple checks 
(base attack bonus, Strength modifier, special size modifier, and any other applicable 
modifier, such as a racial bonus on grapple checks).

\section*{\textbf{Attack}}

This line shows the single attack the creature makes with an attack action. In 
most cases, this is also the attack the creature uses when making an attack of 
opportunity as well. The attack line provides the weapon used (natural or manufactured), 
attack bonus, and form of attack (melee or ranged). The attack bonus given includes 
modifications for size and Strength (for melee attacks) or Dexterity (for ranged 
attacks). A creature with the Weapon Finesse feat can use its Dexterity modifier 
on melee attacks. If the creature uses natural attacks, the natural weapon given 
here is the creature's primary natural weapon. If the creature has several different 
weapons at its disposal, the alternatives are shown, with each different attack 
separated by the word ``or.'' A creature can use one of its secondary natural weapons 
when making an attack action, but if it does it takes an attack penalty, as noted 
in the Full Attack section below. The damage that each attack deals is noted parenthetically. 
Damage from an attack is always at least 1 point, even if a subtraction from a 
die roll reduces the result to 0 or lower.

\section*{\textbf{Full Attack}}

This line shows all the physical attacks the creature makes when it uses a full-round 
action to make a full attack. It gives the number of attacks along with the weapon, 
attack bonus, and form of attack (melee or ranged). The first entry is for the 
creature's primary weapon, with an attack bonus including modifications for size 
and Strength (for melee attacks) or Dexterity (for ranged attacks). A creature 
with the Weapon Finesse feat can use its Dexterity modifier on melee attacks. The 
remaining weapons are secondary, and attacks with them are made with a -5 penalty 
to the attack roll, no matter how many there are. Creatures with the Multiattack 
feat take only a -2 penalty on secondary attacks. The damage that each attack deals 
is noted parenthetically. Damage from an attack is always at least 1 point, even 
if a subtraction from a die roll reduces the result to 0 or lower.

A creature's primary attack damage includes its full Strength modifier (1-1/2 times 
its Strength bonus if the attack is with the creature's sole natural weapon) and 
is given first. Secondary attacks add only 1/2 the creature's Strength bonus and 
are given second in the parentheses. 

If any attacks also have some special effect other than damage, that information 
is given here.

Unless noted otherwise, creatures using natural weapons deal double damage on critical 
hits.

\textbf{Manufactured Weapons:} Creatures that use swords, bows, spears, and the 
like follow the same rules as characters do. The bonus for attacks with two-handed 
weapons is 1-1/2 times the creature's Strength modifier (if it is a bonus), and 
is given first. Offhand weapons add only 1/2 the Strength bonus and are given second 
in the parentheses.

\section*{\textbf{Space/Reach}}

This line describes how much space the creature takes up on the battle grid and 
thereby needs to fight effectively, as well as how close it has to be to threaten 
an opponent. The number before the slash is the creature's space, or how many feet 
one side of the creature occupies. The number after the slash is the creature's 
natural reach. If the creature has exceptional reach due to a weapon, tentacle, 
or the like, the extended reach and its source are noted in parentheses at the 
end of the line.

\section*{\textbf{Special Attacks and Special Qualities}}

Many creatures have unusual abilities. A monster entry breaks these abilities into 
special attacks and special qualities. The latter category includes defenses, vulnerabilities, 
and other special abilities that are not modes of attack. A special ability is 
either extraordinary (Ex), spell-like (Sp), or supernatural (Su). Additional information 
(when needed) is provided in the creature's descriptive text.

When a special ability allows a saving throw, the kind of save and the save DC 
is noted in the descriptive text. Most saving throws against special abilities 
have DCs calculated as follows: 10 + 1/2 the attacker's racial Hit Dice + the relevant 
ability modifier.

The save DC is given in the creature's description along with the ability on which 
the DC is based.

\section*{\textbf{Saves}}

This line gives the creature's Fortitude, Reflex, and Will save modifiers.

\section*{\textbf{Abilities}}

This line lists the creature's ability scores, in the customary order: Str, Dex, 
Con, Int, Wis, Cha. Except where noted otherwise, each creature is assumed to have 
the standard array of ability scores before racial adjustments (all 11s and 10s). 
To determine any creature's racial ability adjustments, subtract 10 from any even-numbered 
ability score and subtract 11 from any odd-numbered score. (Exceptions are noted 
in the Combat section of a creature's descriptive text.) 

\textbf{Strength:} Quadrupeds can carry heavier loads than bipeds can. Any creature 
with four or more motive limbs can carry a load as a quadruped, even if it does 
not necessarily use all the limbs at once.

\textbf{Intelligence:} A creature can speak all the languages mentioned in its 
description, plus one additional language per point of Intelligence bonus. Any 
creature with an Intelligence score of 3 or higher understands at least one language 
(Common, unless noted otherwise).

\textbf{Nonabilities:} Some creatures lack certain ability scores. These creatures 
do not have an ability score of 0---they lack the ability altogether. The modifier 
for a nonability is +0. 

\section*{\textbf{Skills}}

This line gives the creature's skills, along with each skill's modifier (including 
adjustments for ability scores, armor check penalties, and any bonuses from feats 
or racial traits). All listed skills are class skills, unless the creature has 
a character class (noted in the entry). A creature's type and Intelligence score 
determine the number of skill points it has.

The Skills section of the creature's description recaps racial bonuses and other 
adjustments to skill modifiers for the sake of clarity; these bonuses should not 
be added to the listed skill modifiers.

An asterisk (*) beside the relevant score and in the Skills section of the descriptive 
text indicates a conditional adjustment, one that applies only in certain situations.

\textbf{Natural Tendencies:} Some creatures simply aren't made for certain types 
of physical activity. If it seems clear that a particular creature simply is not 
made for a particular physical activity, that creature takes a -8 penalty on skill 
checks that defy its natural tendencies.

In extreme circumstances the creature fails the check automatically.

\section*{\textbf{Feats}}

The line gives the creature's feats. A monster gains feats just as a character 
does. Sometimes a creature has one or more bonus feats, marked with a superscript 
B (\textsuperscript{B}). Creatures often do not have the prerequisites for a bonus 
feat. If this is so, the creature can still use the feat. If you wish to customize 
the creature with new feats, you can reassign its other feats, but not its bonus 
feats. A creature cannot have a feat that is not a bonus feat unless it has the 
feat's prerequisites.

\section*{\textbf{Environment}}

This line gives a type of climate and terrain where the creature is typically found. 
This describes a tendency, but is not exclusionary.

\section*{\textbf{Organization}}

This line describes the kinds of groups the creature might form. A range of numbers 
in parentheses indicates how many combat-ready adults are in each type of group. 
Many groups also have a number of noncombatants, expressed as a percentage of the 
fighting population. Noncombatants can include young, the infirm, slaves, or other 
individuals who are not inclined to fight. If the organization line contains the 
term ``domesticated,'' the creature is generally found only in the company of other 
creatures, whom it serves in some capacity.

\section*{\textbf{Challenge Rating}}

This shows the average level of a party of adventurers for which one creature would 
make an encounter of moderate difficulty.

\section*{\textbf{Treasure}}

This line reflects how much wealth the creature owns\textit{. }In most cases, a 
creature keeps valuables in its home or lair and has no treasure with it when it 
travels. Intelligent creatures that own useful, portable treasure (such as magic 
items) tend to carry and use these, leaving bulky items at home.

\section*{\textbf{Alignment}}

This line gives the alignment that the creature is most likely to have. Every entry 
includes a qualifier that indicates how broadly that alignment applies to the species 
as a whole.

\section*{\textbf{Advancement}}

The monster entry usually describes only the most commonly encountered version 
of a creature. The advancement line shows how tough a creature can get, in terms 
of extra Hit Dice. (This is not an absolute limit, but exceptions are extremely 
rare.) Often, intelligent creatures advance by gaining a level in a character class 
instead of just gaining a new Hit Die.

\section*{\textbf{Level Adjustment}}

This line is included in the entries of creatures suitable for use as player characters 
or as cohorts (usually creatures with Intelligence scores of at least 3 and possessing 
opposable thumbs). Add this number to the creature's total Hit Dice, including 
class levels, to get the creature's effective character level (ECL). A character's 
ECL affects the experience the character earns, the amount of experience the character 
must have before gaining a new level, and the character's starting equipment.

\vspace{12pt}
{\LARGE ABOLETH}

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
\textbf{Aboleth}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
\textbf{Aboleth Mage, 10th-Level Wizard}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Huge Aberration (Aquatic)\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Huge Aberration (Aquatic)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
8d8+40 (76 hp)\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
8d8+56 plus 10d4+70 (177 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
+1\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
+7\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
10 ft. (2 squares), swim 60 ft.\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
10 ft. (2 squares), swim 60 ft.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
16 (-2 size, +1 Dex, +7 natural), touch 9, flat-footed 15\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
18 (-2 size, +3 Dex, +7 natural), touch 11, flat-footed 15\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
+6/+22\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
+11/+28\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Tentacle +12 melee (1d6+8 plus slime)\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Tentacle +18 melee (1d6+9 plus slime)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
4 tentacles +12 melee (1d6+8 plus slime)\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
4 tentacles +18 melee (1d6+9 plus slime)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
15 ft./10 ft.\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
15 ft./10 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Enslave, psionics, slime\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Enslave, psionics, slime, spells \end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Aquatic subtype, darkvision 60 ft., mucus cloud\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Aquatic subtype, darkvision 60 ft., mucus cloud, summon familiar\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Fort +7, Ref +3, Will +11\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Fort +15, Ref +10, Will +15\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
 Str 26, Dex 12, Con 20, Int 15, Wis 17, Cha 17\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Str 28, Dex 16, Con 24, Int 20, Wis 16, Cha 14\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Concentration +16, Knowledge (any one) +13, Listen +16, Spot +16, Swim +8\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Bluff +13, Concentration +25, Decipher Script +15, Diplomacy +6, Disguise +2 (+4 
acting), Intimidate +4, Knowledge (arcana) +15, Knowledge (dungeoneering) +25, 
Knowledge (history) +15, Knowledge (the planes) +15, Listen +15, Search +10, Sense 
Motive +15, Spellcraft +20, Spot +17, Survival +3 (+5 following tracks, on other 
planes, and underground), Swim +8\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Feats: }\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Alertness, Combat Casting, Iron Will\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Combat Casting, Empower Spell, Eschew Materials, Great Fortitude, Improved Initiative, 
Lightning Reflexes, Scribe Scroll, Spell Focus (illusion), Spell Focus (enchantment), 
Spell Penetration\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Environment}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Underground\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Underground\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Solitary, brood (2-4),or slaver brood (1d3+1 plus 7-12 skum)\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
7\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
17\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Double standard\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Double standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
Usually lawful evil\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
Usually lawful evil\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
9-16 HD (Huge); 17-24 HD (Gargantuan)\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{0.707in}|}{\begin{minipage}[t]{0.707in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{1}{p{1.831in}|}{\begin{minipage}[t]{1.831in}\raggedright
---\end{minipage}} & \multicolumn{4}{p{1.962in}|}{\begin{minipage}[t]{1.962in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

The aboleth is a revolting fishlike amphibian found primarily in subterranean lakes 
and rivers. An aboleth has a pink belly. Four pulsating blueblack orifices line 
the bottom of its body and secrete gray slime that smells like rancid grease. It 
uses its tail for propulsion in the water and drags itself along with its tentacles 
on land. An aboleth weighs about 6,500 pounds.

Aboleths speak their own language, as well as Undercommon and Aquan.

COMBAT

An aboleth attacks by flailing with its long, slimy tentacles, though it prefers 
to fight from a distance using its illusion powers.

\textbf{Enslave (Su):} Three times per day, an aboleth can attempt to enslave any 
one living creature within 30 feet. The target must succeed on a DC 17 Will save 
or be affected as though by a \textit{dominate person }spell (caster level 16th). 
An enslaved creature obeys the aboleth's telepathic commands until freed by \textit{remove 
curse, }and can attempt a new Will save every 24 hours to break free. The control 
is also broken if the aboleth dies or travels more than 1 mile from its slave. 
The save DC is Charisma-based.

\textbf{Psionics (Sp):} At will---\textit{hypnotic pattern }(DC 15), \textit{illusory 
wall }(DC 17), \textit{mirage arcana }(DC 18), \textit{persistent image }(DC 18), 
\textit{programmed image }(DC 19), \textit{project image }(DC 20), \textit{veil 
}(DC 19). Effective caster level 16th. The save DCs are Charisma-based.

\textbf{Slime (Ex):} A blow from an aboleth's tentacle can cause a terrible affliction. 
A creature hit by a tentacle must succeed on a DC 19 Fortitude save or begin to 
transform over the next 1d4+1 minutes, the skin gradually becoming a clear, slimy 
membrane. An afflicted creature must remain moistened with cool, fresh water or 
take 1d12 points of damage every 10 minutes. The slime reduces the creature's natural 
armor bonus by 1 (but never to less than 0). The save DC is Constitution-based.

A \textit{remove disease }spell cast before the transformation is complete will 
restore an afflicted creature to normal. Afterward, however, only a \textit{heal 
}or \textit{mass heal }spell can reverse the affliction.

\textbf{Mucus Cloud (Ex):} An aboleth underwater surrounds itself with a viscous 
cloud of mucus roughly 1 foot thick. Any creature coming into contact with and 
inhaling this substance must succeed on a DC 19 Fortitude save or lose the ability 
to breathe air for the next 3 hours. An affected creature suffocates in 2d6 minutes 
if removed from the water. Renewed contact with the mucus cloud and failing another 
Fortitude save continues the effect for another 3 hours. The save DC is Constitution-based.

\textbf{Skills:} An aboleth has a +8 racial bonus on any Swim check to perform 
some special action or avoid a hazard. It can always choose to take 10 on a Swim 
check, even if distracted or endangered. It can use the run action while swimming, 
provided it swims in a straight line.

\vspace{12pt}
ABOLETH MAGE

COMBAT

The save DC for the aboleth mage's transformation tentacle attack (DC 21) and its 
mucus cloud (DC 21) are adjusted for its higher Constitution score. The save DC 
for its enslave ability (DC 16) is adjusted for its lower Charisma score, as are 
the save DCs for its psionic abilities: \textit{Hypnotic pattern }(DC 14), \textit{illusory 
wall }(DC 16), \textit{mirage arcana }(DC 17), \textit{persistent image }(DC 17), 
\textit{programmed image }(DC 18), \textit{project image }(DC 19), \textit{veil 
}(DC 18). Effective caster level 16th.

The aboleth mage uses a number of spells, such as \textit{displacement}, \textit{greater 
invisibility}, and \textit{wall of force, }to protect itself while seizing control 
of its foes with spells and innate abilities.

\textit{Typical Wizard Spells Prepared }(4/6/5/4/4/3; save DC 15 + spell level): 
0---\textit{daze, detect magic }(2), \textit{resistance}; 1st---\textit{alarm, 
charm person, color spray, mage armor, magic missile }(2)\textit{; }2nd---\textit{blur, 
bull's strength, darkness, fox's cunning, see invisibilty; }3rd---\textit{dispel 
magic, displacement,} \textit{fly, lightning bolt; }4th---\textit{greater invisibility}, 
\textit{phantasmal killer, scrying, stoneskin; }5th---\textit{hold monster, }empowered 
\textit{lightning bolt, wall of force.}

\vspace{12pt}
{\LARGE ACHAIERAI}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
Large Outsider (Evil, Extraplanar, Lawful)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
6d8+12 (39 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
50 ft. (10 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
20 (-1 size, +1 Dex, +10 natural), touch 10, flat-footed 19\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+6/+14\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Claw +9 melee (2d6+4)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
2 claws +9 melee (2d6+4) and bite +4 melee (4d6+2)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Black cloud\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Darkvision 60 ft., spell resistance 19\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Fort +7, Ref +6, Will +7\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Str 19, Dex 13, Con 14, Int 11, Wis 14, Cha 16\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Balance +10, Climb +13, Diplomacy +5, Hide +6, Jump +21, Listen +11, Move Silently 
+10, Sense Motive +11, Spot +11\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Dodge, Mobility, Spring Attack\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
A lawful-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Solitary or flock (5-8)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
5\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Double standard\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Always lawful evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
7-12 HD (Large); 13-18 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Achaierais are massive, 15-foot-tall flightless birds that inhabit lawful planes 
of battle and are only occasionally encountered elsewhere. 

Achaierais speak Infernal. They weigh about 750 pounds.

COMBAT

In close combat, an achaierai lashes out with two of its four legs and snaps with 
its powerful beak. It makes frequent use of its Spring Attack feat to strike quickly 
and then retreat out of range before an enemy can counterattack.

An achaierai's natural weapons, as well as any weapons it wields, are treated as 
evil-aligned and lawfulaligned for the purpose of overcoming damage reduction.

\textbf{Black Cloud (Ex):} Up to three times per day an achaierai can release a 
choking, toxic black cloud.

Those other than achaierai within 10 feet instantly take 2d6 points of damage. 
They must also succeed on a DC 15 Fortitude save or be affected for 3 hours as 
though by an \textit{insanity }spell (caster level 16th). The save DC is Constitution-based.

\vspace{12pt}
\subsection*{{\LARGE ALLIP}}

\subsection*{\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.990in}|}{\begin{minipage}[t]{2.990in}\raggedright
Medium Undead (Incorporeal)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
4d12 (26 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.990in}|}{\begin{minipage}[t]{2.990in}\raggedright
+5\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
Fly 30 ft. (perfect) (6 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
15 (+1 Dex, +4 deflection), touch 15, flat-footed 14\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
+2/---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Incorporeal touch +3 melee (1d4 Wisdom drain)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Incorporeal touch +3 melee (1d4 Wisdom drain)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Babble, madness, Wisdom drain\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Darkvision 60 ft., incorporeal traits, +2 turn resistance, undead traits\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Fort +1, Ref +4, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Str ---, Dex 12, Con ---, Int 11, Wis 11, Cha 18\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Hide +8, Intimidate +7, Listen +7, Search +4, Spot +7, Survival +0 (+2 following 
tracks)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Improved Initiative, Lightning Reflexes\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Always neutral evil\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
5-12 HD (Medium)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}
}

An allip is the spectral remains of someone driven to suicide by a madness that 
afflicted it in life. It craves only revenge and unrelentingly pursues those who 
tormented it in life and pushed it over the brink. 

An allip cannot speak intelligibly.

COMBAT

An allip is unable to cause physical harm, although it doesn't appear to know that. 
It keeps flailing away at enemies, yet it inflicts no wounds.

\textbf{Babble (Su):} An allip constantly mutters and whines to itself, creating 
a hypnotic effect. All sane creatures within 60 feet of the allip must succeed 
on a DC 16 Will save or be affected as though by a \textit{hypnotism }spell for 
2d4 rounds. This is a sonic mind-affecting compulsion effect.

Creatures that successfully save cannot be affected by the same allip's babble 
for 24 hours. The save DC is Charisma-based.

\textbf{Madness (Su):} Anyone targeting an allip with a thought detection, mind 
control, or telepathic ability makes direct contact with its tortured mind and 
takes 1d4 points of Wisdom damage.

\textbf{Wisdom Drain (Su): }An allip causes 1d4 points of Wisdom drain each time 
it hits with its incorporeal touch attack. On each such successful attack, it gains 
5 temporary hit points.

\vspace{12pt}
{\LARGE ANGEL}

Angels are a race of celestials, beings who live on the good-aligned Outer Planes.

Angels can be of any good alignment. Regardless of their alignment, angels never 
lie, cheat, or steal. They are impeccably honorable in all their dealings and often 
prove the most trustworthy and diplomatic of all the celestials.

All angels are blessed with comely looks, though their actual appearances vary 
widely.

Angels speak Celestial, Infernal, and Draconic, though they can speak with almost 
any creature because of their tongues ability.

COMBAT

In combat, most angels make full use of their mobility and their ability to attack 
at a distance.

\textbf{Angel Traits:} An angel possesses the following traits (unless otherwise 
noted in a creature's entry).---

Darkvision out to 60 feet and low-light vision.---

Immunity to acid, cold, and petrification.---

Resistance to electricity 10 and fire 10.---

+4 racial bonus on saves against poison.---

\textit{Protective Aura (Su): }Against attacks made or effects created by evil 
creatures, this ability provides a +4 deflection bonus to AC and a +4 resistance 
bonus on saving throws to anyone within 20 feet of the angel. Otherwise, it functions 
as a \textit{magic circle against evil }effect and a \textit{lesser globe of invulnerability, 
}both with a radius of 20 feet (caster level equals angel's HD). This aura can 
be dispelled, but the angel can create it again as a free action on its next turn. 
(The defensive benefits from the circle are not included in an angel's statistics 
block.)---

\textit{Tongues (Su): }All angels can speak with any creature that has a language, 
as though using a \textit{tongues }spell (caster level equal to angel's Hit Dice). 
This ability is always active.

\vspace{12pt}
ANGEL, ASTRAL DEVA

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.990in}|}{\begin{minipage}[t]{2.990in}\raggedright
Medium Outsider (Angel, Extraplanar, Good)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
12d8+48 (102 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.990in}|}{\begin{minipage}[t]{2.990in}\raggedright
+8\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
50 ft. (10 squares), fly 100 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
29 (+4 Dex, +15 natural), touch 14, flat-footed 25\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.066in}|}{\begin{minipage}[t]{0.066in}\raggedright
+12/+18\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
\textit{+3 heavy mace of disruption }+21 melee (1d8+12 plus stun) or slam +18 melee 
(1d8+9)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
\textit{+3 heavy mace of disruption }+21/+16/+11 melee (1d8+12 plus stun) or slam 
+18 melee (1d8+9)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Spell-like abilities, stun\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Damage reduction 10/evil, darkvision 60 ft., low-light vision, immunity to acid, 
cold, and petrification, protective aura, resistance to electricity 10 and fire 
10, spell resistance 30, tongues, uncanny dodge\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Fort +14 (+18 against poison), Ref +12, Will +12\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Str 22, Dex 18, Con 18, Int 18, Wis 18, Cha 20\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Concentration +19, Craft or Knowledge (any three) +19, Diplomacy +22, Escape Artist 
+19, Hide +19, Intimidate +20, Listen +23, Move Silently +19, Sense Motive +19, 
Spot +23, Use Rope +4 (+6 with bindings)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Alertness, Cleave, Great Fortitude, Improved Initiative, Power Attack\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Any good-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Solitary, pair, or squad (3-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
14\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
No coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
Always good (any)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
13-18 HD (Medium); 19-36 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.377in}|}{\begin{minipage}[t]{1.377in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.123in}|}{\begin{minipage}[t]{3.123in}\raggedright
+8\end{minipage}}\\
\hline
\end{longtable}

An astral deva is about 7-1/2 feet tall and weighs about 250 pounds.

\section*{COMBAT}

An astral deva is not afraid to enter melee combat. It takes a fierce joy in bashing 
evil foes with its powerful \textit{+3 heavy mace of disruption.}

An astral deva's natural weapons, as well as any weapons it wields, are treated 
as good-aligned for the purpose of overcoming damage reduction.

\textbf{Spell-Like Abilities:} At will---\textit{aid, continual flame, detect evil, 
discern lies }(DC 19), \textit{dispel evil }(DC 20), \textit{dispel magic, holy 
aura }(DC 23), \textit{holy smite }(DC 19), \textit{holy word }(DC 22), \textit{invisibility 
}(self only), \textit{plane shift }(DC 22), \textit{polymorph }(self only), \textit{remove 
curse }(DC 18), \textit{remove disease }(DC 18), \textit{remove fear }(DC 16); 
7/day---\textit{cure light wounds }(DC 16), \textit{see invisibility; }1/day---\textit{blade 
barrier }(DC 21), \textit{heal }(DC 21). Caster level 12th. The save DCs are Charisma-based.

\textbf{Stun (Su):} If an astral deva strikes an opponent twice in one round with 
its mace, that creature must succeed on a DC 22 Fortitude save or be stunned for 
1d6 rounds. The save DC is Strength-based.

\textbf{Uncanny Dodge (Ex):} An astral deva retains its Dexterity bonus to AC when 
flat-footed, and it cannot be flanked except by a rogue of at least 16th level. 
It can flank characters with the uncanny dodge ability as if it were a 12th-level 
rogue.

\vspace{12pt}
ANGEL, PLANETAR

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
Large Outsider (Angel, Extraplanar, Good)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
14d8+70 (133 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
+8\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
30 ft. (6 squares), fly 90 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
32 (-1 size, +4 Dex, +19 natural), touch 13, flat-footed 28\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+14/+25\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
\textit{+3 greatsword }+23 melee (3d6+13/19-20) or slam +20 melee (2d8+10)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
\textit{+3 greatsword }+23/+18/+13 melee (3d6+13/19-20) or slam +20 melee (2d8+10)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Spell-like abilities, spells\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Damage reduction 10/evil, darkvision 60 ft., low-light vision, immunity to acid, 
cold, and petrification, protective aura, regeneration 10, resistance to electricity 
10 and fire 10, spell resistance 30, tongues\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Fort +14 (+18 against poison), Ref +13, Will +15\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Str 25, Dex 19, Con 20, Int 22, Wis 23, Cha 22\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Concentration +22, Craft or Knowledge (any four) +23, Diplomacy +25, Escape Artist 
+21, Hide +17, Intimidate +23, Listen +23, Move Silently +21, Sense Motive +23, 
Search +23, Spot +23, Use Rope +4 (+6 with bindings)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Blind-Fight, Cleave, Improved Initiative, Improved Sunder, Power Attack\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Any good-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Solitary or pair\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
16\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
No coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Always good (any)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
15-21 HD (Large); 22-42 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A planetar is nearly 9 feet tall and weighs about 500 pounds.

\section*{COMBAT}

Despite their vast array of magical powers, planetars are likely to wade into melee 
with their \textit{+3 greatswords. }They particularly enjoy fighting fiends.

A planetar's natural weapons, as well as any weapons it wields, are treated as 
good-aligned for the purpose of overcoming damage reduction.

\textbf{Regeneration:} A planetar takes damage from evil-aligned weapons and from 
spells and effects with the evil descriptor.

\textbf{Spell-Like Abilities:} At will---\textit{continual flame, dispel magic, 
holy smite }(DC 20), \textit{invisibility }(self only), \textit{lesser restoration 
}(DC 18), \textit{remove curse }(DC 19), \textit{remove disease }(DC 19), \textit{remove 
fear }(DC 17), \textit{speak with dead }(DC 19); 3/day---\textit{blade barrier 
}(DC 22), \textit{flame strike }(DC 21), \textit{polymorph }(self only), \textit{power 
word stun, raise dead}, \textit{waves of fatigue}; 1/day---\textit{earthquake }(DC 
24), \textit{greater restoration }(DC 23), \textit{mass charm monster }(DC 24)\textit{, 
waves of exhaustion}. Caster level 17th. The save DCs are Charisma-based.

The following abilities are always active on the planetar's person, as the spells 
(caster level 17th): \textit{detect evil, detect snares and pits, discern lies 
}(DC 20), \textit{see invisibility}, and \textit{true seeing}. They can be dispelled, 
but the planetar can reactivate them as a free action.

\textbf{Spells:} Planetars can cast divine spells as 17th-level clerics. A planetar 
has access to two of the following domains: Air, Destruction, Good, Law, or War 
(plus any others from its deity). The save DCs are Wisdom-based.

\textit{Typical Cleric Spells Prepared }(6/8/8/7/7/6/6/4/3/2; save DC 16 + spell 
level): 0---\textit{create water, detect magic, guidance}, \textit{resistance }(2), 
\textit{virtue; }1st---\textit{bless }(2), \textit{cause fear, divine favor }(2), 
\textit{entropic shield, inflict light wounds*}, \textit{shield of faith; }2nd---\textit{aid*, 
align weapon, bear 's endurance}, \textit{bull's strength }(2), \textit{consecrate, 
eagle's splendor, hold person; }3rd---\textit{contagion*, daylight, invisibility 
purge}, \textit{prayer }(2), \textit{summon monster III, wind wall; }4th--- \textit{death 
ward}, \textit{dismissal}, \textit{inflict critical wounds*}, \textit{neutralize 
poison }(2), \textit{summon monster IV; }5th--- \textit{break enchantment, circle 
of doom}*, \textit{dispel evil, mark of justice, plane shift, righteous might; 
}6th---\textit{banishment, greater dispel magic, harm*, heal, heroes' feast, mass 
cure moderate wounds; }7th--- \textit{dictum, disintegrate*, holy word}, \textit{regenerate; 
}8th---\textit{holy aura*, mass cure critical wounds, shield of law}; 9th---\textit{implosion, 
summon monster IX (good)*.}

*Domain spell. Domains: Destruction and Good.

\vspace{12pt}
ANGEL, SOLAR

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.102in}|}{\begin{minipage}[t]{3.102in}\raggedright
Large Outsider (Angel, Extraplanar, Good)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
22d8+110 (209 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.102in}|}{\begin{minipage}[t]{3.102in}\raggedright
+9\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
50 ft. (10 squares), fly 150 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
35 (-1 size, +5 Dex, +21 natural), touch 14, flat-footed 30\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.061in}|}{\begin{minipage}[t]{0.061in}\raggedright
+22/+35\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
\textit{+5 dancing greatsword }+35 melee (3d6+18/19-20) or \textit{+2 composite 
longbow }(+5 Str bonus) +28 ranged (2d6+7/x3 plus slaying) or slam +30 melee (2d8+13)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
\textit{+5 dancing greatsword }+35/+30/+25/+20 melee (3d6+18/19-20) or \textit{+2 
composite longbow }(+5 Str bonus) +28/+23/+18/+13 ranged (2d6+7/x3 plus slaying) 
or slam +30 melee (2d8+13)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
10 ft./10 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Spell-like abilities, spells\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Damage reduction 15/epic and evil, darkvision 60 ft., low-light vision, immunity 
to acid, cold, and petrification, protective aura, regeneration 15, resistance 
to electricity 10 and fire 10, spell resistance 32, tongues\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Fort +18 (+22 against poison), Ref +18, Will +20\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Str 28, Dex 20, Con 20, Int 23, Wis 25, Cha 25\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Concentration +30, Craft or Knowledge (any five) +33, Diplomacy +34, Escape Artist 
+30, Hide +26, Listen +32, Move Silently +30, Search +31, Sense Motive +32, Spellcraft 
+31, Spot +32, Survival +7 (+9 following tracks), Use Rope +5 (+7 with bindings)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Cleave, Dodge, Great Cleave, Improved Initiative, Improved Sunder, Mobility, Power 
Attack, Track\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Any good-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Solitary or pair\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
23\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
No coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
Always good (any)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
23-33 HD (Large); 34-66 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.275in}|}{\begin{minipage}[t]{1.275in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.225in}|}{\begin{minipage}[t]{3.225in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

A solar has a deep and commanding voice, and stands about 9 feet tall. It weighs 
about 500 pounds.

\section*{\textbf{Combat}}

Solars are puissant champions of good. Only the most powerful fiends approach their 
power.

Even more fearsome than their \textit{+5 dancing greatswords }are their \textit{+2 
composite longbows }that create any sort of \textit{slaying arrow }when drawn.

A solar's natural weapons, as well as any weapons it wields, are treated as good-aligned 
and epic for the purpose of overcoming damage reduction.

\textbf{Regeneration (Ex):} A solar takes normal damage from epic evil-aligned 
weapons, and from spells or effects with the evil descriptor.

\textbf{Spell-Like Abilities:} At will---\textit{aid, animate objects, commune, 
continual flame, dimensional anchor, greater dispel magic, holy smite }(DC 21), 
i\textit{mprisonment }(DC 26), \textit{invisibility }(self only), \textit{lesser 
restoration }(DC 19), \textit{polymorph }(self only) \textit{power word stun, remove 
curse }(DC 20), \textit{remove disease }(DC 20), \textit{remove fear }(DC 18), 
\textit{resist energy, summon monster VII, speak with dead }(DC 20)\textit{, waves 
of fatigue}; 3/day---\textit{blade barrier }(DC 23), \textit{earthquake }(DC 25), 
\textit{heal }(DC 23), \textit{mass charm monster }(DC 25), \textit{permanency, 
resurrection, waves of exhaustion}; 1/day---\textit{greater restoration }(DC 24), 
\textit{power word blind}, \textit{power word kill}, \textit{power word stun, prismatic 
spray }(DC 24), \textit{wish}. Caster level 20th. The save DCs are Charisma-based.

The following abilities are always active on a solar's person, as the spells (caster 
level 20th): \textit{detect evil, detect snares and pits, discern lies }(DC 21), 
\textit{see invisibility, true seeing}. They can be dispelled, but the solar can 
reactivate them as a free action.

\textbf{Spells:} Solars can cast divine spells as 20th-level clerics. A solar has 
access to two of the following domains: Air, Destruction, Good, Law, or War (plus 
any others from its deity). The save DCs are Wisdom-based.

\textit{Typical Cleric Spells Prepared }(6/8/8/8/7/7/6/6/5/5; save DC 17 + spell 
level): 0---\textit{create water, detect magic, guidance }(2), \textit{resistance 
} (2); 1st---\textit{bless }(2), \textit{cause fear, divine favor }(2), \textit{entropic 
shield, obscuring mist}*, \textit{shield of faith; }2nd---\textit{align weapon, 
bear's endurance }(2), \textit{bull's strength }(2), \textit{consecrate, eagle's 
splendor, spiritual weapon}*; 3rd---\textit{daylight, invisibility purge, magic 
circle against evil, magic vestment}*, \textit{prayer }(2), \textit{protection 
from energy, wind wall; }4th---\textit{death ward }(2), \textit{dismissal }(2), 
\textit{divine power}*, \textit{neutralize poison }(2); 5th---\textit{break enchantment, 
control winds}*, \textit{dispel evil, plane shift, righteous might }(2), \textit{symbol 
of pain; }6th---\textit{banishment, chain lightning}*, \textit{heroes' feast, mass 
cure moderate wounds, undeath to death, word of recall; }7th---\textit{control 
weather}*, \textit{destruction, dictum, ethereal jaunt, holy word, regenerate; 
}8th---\textit{fire storm, holy aura, mass cure critical wounds }(2), \textit{whirlwind}*; 
9th--- \textit{etherealness, elemental swarm (air)}*\textit{, mass heal, miracle, 
storm of vengeance}.

*Domain spell. Domains: Air and War.

\vspace{12pt}
{\LARGE ANIMATED OBJECT}

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
\textbf{Animated Object, Tiny}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
\textbf{Animated Object, Small}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
\textbf{Animated Object, Medium}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Tiny Construct\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Small Construct\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Construct\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
1/2 d10 (2 hp)\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
1d10+10 (15 hp)\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
2d10+20 (31 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+2\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+1\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
40 ft. (8 squares); 50 ft. legs, 60 ft. multiple legs; 80 ft. wheels\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
30 ft. (6 squares); 40 ft. legs, 50 ft. multiple legs, 70 ft. wheels\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
30 ft. (6 squares); 40 ft. legs, 50 ft. multiple legs, 70 ft. wheels\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
14 (+2 size, +2 Dex), touch 14, flat-footed 12\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
14 (+1 size, +1 Dex, +2 natural), touch 12, flat-footed 13\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
14 (+4 natural), touch 10, flat-footed 14\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
+0/-9\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
+0/-4\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
+1/+2\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Slam +1 melee (1d3-1)\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Slam +1 melee (1d4)\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Slam +2 melee (1d6+1)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Slam +1 melee (1d3-1)\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Slam +1 melee (1d4)\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Slam +2 melee (1d6+1)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
2-1/2 ft./0 ft.\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
See text\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
See text\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
See text\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Fort +0, Ref +2, Will -5\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Fort +0, Ref +1, Will -5\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Fort +0, Ref +0, Will -5\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Str 8, Dex 14, Con ---, Int ---, Wis 1, Cha 1\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Str 10, Dex 12, Con ---, Int ---, Wis 1, Cha 1\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Str 12, Dex 10, Con ---, Int ---, Wis 1, Cha 1\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
---\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Any\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Any\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Group (4)\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Pair\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
1/2\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
1\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
None\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
None\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
None\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Always neutral\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
Always neutral\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{0.764in}|}{\begin{minipage}[t]{0.764in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.189in}|}{\begin{minipage}[t]{1.189in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.358in}|}{\begin{minipage}[t]{1.358in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
\textbf{Animated Object, Large}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
\textbf{Animated Object, Huge}\end{minipage}} & \multicolumn{1}{p{1.223in}|}{\begin{minipage}[t]{1.223in}\raggedright
\textbf{Animated Object, Gargantuan}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Large Construct\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Huge Construct\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Gargantuan Construct\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
4d10+30 (52 hp)\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
8d10+40 (84 hp)\end{minipage}} & \multicolumn{1}{p{1.223in}|}{\begin{minipage}[t]{1.223in}\raggedright
16d10+60 (148 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+0\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
-1\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
-2\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
20 ft. (4 squares); 30 ft. legs, 40 ft. multiple legs, 60 ft. wheels\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
20 ft. (4 squares); 30 ft. legs, 40 ft. multiple legs, 60 ft. wheels\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
10 ft. (2 squares); 20 ft. legs, 30 ft. multiple legs, 50 ft. wheels\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
14 (-1 size, +5 natural), touch 9, flat-footed 14\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
13 (-2 size, -1 Dex, +6 natural), touch 7, flat-footed 13\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
12 (-4 size, -2 Dex, +8 natural), touch 4, flat-footed 12\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
+3/+10\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
+6/+19\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
+12/+31\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Slam +5 melee (1d8+4)\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Slam +9 melee (2d6+7)\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Slam +15 melee (2d8+10)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Slam +5 melee (1d8+4)\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Slam +9 melee (2d6+7)\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Slam +15 melee (2d8+10)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Space/Reach: }\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
10 ft./5 ft. (long)\linebreak
10 ft./10 ft. (tall)\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
15 ft./10 ft. (long)\linebreak
15 ft./15 ft. (tall)\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
20 ft./15 ft. (long)\linebreak
20 ft./20 ft. (tall)\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
See text\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
See text\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
See text\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Saves:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Fort +1, Ref +1, Will -4\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Fort +2, Ref +1, Will -3\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Fort +5, Ref +3, Will +0\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Abilities: \end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Str 16, Dex 10, Con ---, Int ---, Wis 1, Cha 1\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Str 20, Dex 8, Con ---, Int ---, Wis 1, Cha 1\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Str 24, Dex 6, Con ---, Int ---, Wis 1, Cha 1\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Skills:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Feats:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
---\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Environment:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Any\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Any\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Organization:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Solitary\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
Solitary\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Challenge Rating:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
5\end{minipage}} & \multicolumn{5}{p{1.392in}|}{\begin{minipage}[t]{1.392in}\raggedright
7\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Treasure:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
None\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
None\end{minipage}} & \multicolumn{1}{p{1.223in}|}{\begin{minipage}[t]{1.223in}\raggedright
None\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Alignment:\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Always neutral\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Always neutral\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.761in}|}{\begin{minipage}[t]{0.761in}\raggedright
Advancement:\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.173in}|}{\begin{minipage}[t]{1.173in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.223in}|}{\begin{minipage}[t]{1.223in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Level Adjustment:\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.151in}|}{\begin{minipage}[t]{3.151in}\raggedright
\textbf{Animated Object, Colossal}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
Colossal Construct\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{3.151in}|}{\begin{minipage}[t]{3.151in}\raggedright
32d10+80 (256 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
-3\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
10 ft. (2 squares); 20 ft. legs, 30 ft. multiple legs, 50 ft. wheels\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.059in}|}{\begin{minipage}[t]{0.059in}\raggedright
11 (-8 size, -3 Dex, +12 natural), touch -1, flat-footed 11\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
+24/+49\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Slam +25 melee (4d6+13)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Slam +25 melee (4d6+13)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
30 ft./20 ft. (long) 30 ft./30 ft. (tall)\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
See text\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Construct traits, darkvision 60 ft., low-light vision; also see text\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Fort +10, Ref +7, Will +5\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Str 28, Dex 4, Con ---, Int ---, Wis 1, Cha 1\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
---\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Any\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Solitary\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
10\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
None\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.231in}|}{\begin{minipage}[t]{1.231in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.269in}|}{\begin{minipage}[t]{3.269in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Animated objects come in all sizes, shapes, and colors. They owe their existence 
as creatures to spells such as \textit{animate objects }or similar supernatural 
abilities.

COMBAT

Animated objects fight only as directed by the animator. They follow orders without 
question and to the best of their abilities. Since they do not need to breathe 
and never tire, they can be extremely capable minions. 

An animated object can have one or more of the following special abilities, depending 
on its form.

\textbf{Blind (Ex):} A sheetlike animated object such as a carpet or tapestry can 
grapple an opponent up to three sizes larger than itself. The object makes a normal 
grapple check. If it wins, it wraps itself around the opponent's head, causing 
that creature to be blinded until removed.

\textbf{Constrict (Ex): }A flexible animated object such as a rope, vine, or rug 
deals damage equal to its slam damage value plus 1- 1/2 times its Strength bonus 
with a successful grapple check against a creature up to one size larger than itself.

An object of at least Large size can make constriction attacks against multiple 
creatures at once, if they all are at least two sizes smaller than the object and 
can fit under it.

\textbf{Hardness (Ex): }An animated object has the same hardness it had before 
it was animated.

\textbf{Improved Speed (Ex):} The base land speed given in the statistics block 
assume that an animated object lurches, rocks, or slithers along.

Objects with two legs (statues, ladders) or a similar shape that allows faster 
movement have a +10 foot bonus to speed. Objects with multiple legs (tables, chairs) 
have a +20 foot bonus to speed. Wheeled objects have a +40 foot bonus to speed.

Objects might have additional modes of movement. A wooden object can float and 
has a swim speed equal to half its land speed. A rope or similar sinuous object 
has a climb speed equal to half its land speed. A sheetlike object can fly (clumsy 
maneuverability) at half its normal speed.

\textbf{Trample (Ex): }An animated object of at least Large size and with a hardness 
of at least 10 can trample creatures two or more sizes smaller than itself, dealing 
damage equal to the object's slam damage + 1-1/2 times its Strength bonus. Opponents 
who do not make attacks of opportunity against the object can attempt Reflex saves 
(DC 10 + 1/2 object's HD + object's Str modifier) to halve the damage.

\vspace{12pt}
{\LARGE ANKHEG}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\end{minipage}} & \multicolumn{1}{p{2.985in}|}{\begin{minipage}[t]{2.985in}\raggedright
Large Magical Beast\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
3d10+12 (28 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.985in}|}{\begin{minipage}[t]{2.985in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
30 ft. (6 squares), burrow 20 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
18 (-1 size, +9 natural), touch 9, flat-footed 18\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.067in}|}{\begin{minipage}[t]{0.067in}\raggedright
+3/+12\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Bite +7 melee (2d6+7 plus 1d4 acid)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Bite +7 melee (2d6+7 plus 1d4 acid)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
10 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Improved grab, spit acid\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Darkvision 60 ft., low-light vision, tremorsense 60 ft.\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Fort +6, Ref +3, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Str 21, Dex 10, Con 17, Int 1, Wis 13, Cha 6\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Climb +8, Listen +6, Spot +3\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Alertness, Toughness\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Warm plains\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Solitary or cluster (2-4)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
3\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
4 HD (Large); 5-9 HD (Huge)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.382in}|}{\begin{minipage}[t]{1.382in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.118in}|}{\begin{minipage}[t]{3.118in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

The ankheg is a burrowing monster with a taste for fresh meat. An ankheg has six 
legs, and some specimens are yellow rather than brown. It is about 10 feet long 
and weighs about 800 pounds.

An ankheg burrows with legs and mandibles. A burrowing ankheg usually does not 
make a usable tunnel, but can construct a tunnel; it burrows at half speed when 
it does so. It often digs a winding tunnel up to 40 feet below the surface in the 
rich soil of forests or farmlands. The tunnel is 5 feet tall and wide, and from 
60 to 150 feet long ([1d10 + 5] x$ $10). 

COMBAT

An ankheg usually lies 5 to 10 feet below the surface until its antennae detect 
the approach of prey. It then burrows up to attack. (Treat this as a charge, even 
though the ankheg does not need to move 10 feet before attacking.)

Clusters of ankhegs share the same territory but do not cooperate.

\textbf{Improved Grab (Ex): }To use this ability, an ankheg must hit with its bite 
attack. It can then attempt to start a grapple as a free action without provoking 
an attack of opportunity. If the ankheg is damaged after grabbing its prey, it 
retreats backward down its tunnel at its land speed (not its burrow speed), dragging 
the victim with it.

\textbf{Spit Acid (Ex):} 30-ft. line, once every 6 hours; damage 4d4 acid, Reflex 
DC 14 half. One such attack depletes the ankheg's acid supply for 6 hours. It cannot 
spit acid or deal acid damage during this time. The save DC is Constitution-based.

An ankheg does not use this ability unless it is desperate or frustrated. It most 
often spits acid when reduced to fewer than half its full normal hit points or 
when it has not successfully grabbed an opponent.

\vspace{12pt}
{\LARGE ARANEA}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.949in}|}{\begin{minipage}[t]{2.949in}\raggedright
Medium Magical Beast (Shapechanger)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
3d10+6 (22 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.949in}|}{\begin{minipage}[t]{2.949in}\raggedright
+6\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
50 ft. (10 squares), climb 25 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
13 (+2 Dex, +1 natural), touch 12, flat-footed 11\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
+3/+3\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Bite +5 melee (1d6 plus poison) or web +5 ranged\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Bite +5 melee (1d6 plus poison) or web +5 ranged\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Poison, spells, web\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Change shape, darkvision 60 ft., low-light vision\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Fort +5, Ref +5, Will +4\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Str 11, Dex 15, Con 14, Int 14, Wis 13, Cha 14\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Climb +14, Concentration +8, Escape Artist +5, Jump +13, Listen +6, Spot +6\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Improved Initiative, Iron Will\textsuperscript{B}, Weapon Finesse\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Temperate forests\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Solitary or colony (3-6)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
4\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Standard coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Usually neutral\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
+4\end{minipage}}\\
\hline
\end{longtable}

An aranea is an intelligent, shapechanging spider with sorcerous powers. In its 
natural form, an aranea resembles a big spider, with a humpbacked body a little 
bigger than a human torso. It has fanged mandibles like a normal spider. Two small 
arms, each about 2 feet long, lie below the mandibles. Each arm has a hand with 
four many-jointed fingers and a double-jointed thumb.

An aranea weighs about 150 pounds. The hump on its back houses its brain.

Araneas speak Common and Sylvan.

COMBAT

An aranea avoids physical combat and uses its webs and spells when it can. In a 
battle, it tries to immobilize or distract the most aggressive opponents first. 
Araneas often subdue opponents for ransom.

\textbf{Poison (Ex):} Injury, Fortitude DC 13, initial damage 1d6 Str, secondary 
damage 2d6 Str. The save DC is Constitution-based.

\textbf{Spells:} An aranea casts spells as a 3rd-level sorcerer. It prefers illusions 
and enchantments and avoids fire spells.

\textit{Typical Sorcerer Spells Known }(6/6; save DC 12 + spell level): 0--- \textit{daze, 
detect magic, ghost sound, light, resistance; }1st---\textit{mage armor, silent 
image, sleep.}

\textbf{Web (Ex):} In spider or hybrid form (see below), an aranea can throw a 
web up to six times per day. This is similar to an attack with a net but has a 
maximum range of 50 feet, with a range increment of 10 feet, and is effective against 
targets of up to Large size. The web anchors the target in place, allowing no movement.

An entangled creature can escape with a DC 13 Escape Artist check or burst the 
web with a DC 17 Strength check. The check DCs are Constitution-based, and the 
Strength check DC includes a +4 racial bonus. The web has 6 hit points, hardness 
0, and takes double damage from fire.

\textbf{Change Shape (Su):} An aranea's natural form is that of a Medium monstrous 
spider. It can assume two other forms. The first is a unique Small or Medium humanoid; 
an aranea in its humanoid form always assumes the same appearance and traits, much 
as a lycanthrope would. In humanoid form, an aranea cannot use its bite attack, 
webs, or poison.

The second form is a Medium spider-humanoid hybrid. In hybrid form, an aranea looks 
like a Medium humanoid at first glance, but a DC 18 Spot check reveals the creature's 
fangs and spinnerets. The aranea retains its bite attack, webs, and poison in this 
form, and can also wield weapons or wear armor. When in hybrid form, an aranea's 
speed is 30 feet (6 squares).

An aranea remains in one form until it chooses to assume a new one. A change in 
form cannot be dispelled, nor does an aranea revert to its natural form when killed. 
A \textit{true seeing }spell, however, reveals its natural form if it is in humanoid 
or hybrid form.

\textbf{Skills:} Araneas have a +2 racial bonus on Jump, Listen, and Spot checks. 
They have a +8 racial bonus on Climb checks and can always choose to take 10 on 
Climb checks even if rushed or threatened.

\vspace{12pt}
\subsection*{{\LARGE ARCHON}}

Archons are celestials from a lawful good-aligned plane.

Archons speak Celestial, Infernal, and Draconic, but can speak with almost any 
creature because of their tongues ability.

COMBAT

Archons generally prefer to meet a foe head-on if it is prudent to do so, but if 
outmatched, they do what they can to even the odds (usually by employing hit-and 
run tactics or standing off and engaging a foe with magic before moving into melee).

\textbf{Archon Traits:} An archon possesses the following traits (unless otherwise 
noted in a creature's entry).---

Darkvision out to 60 feet and low-light vision.---

\textit{Aura of Menace (Su): }A righteous aura surrounds archons that fight or 
get angry. Any hostile creature within a 20-foot radius of an archon must succeed 
on a Will save to resist its effects. The save DC varies with the type of archon, 
is Charisma-based, and includes a +2 racial bonus. Those who fail take a -2 penalty 
on attacks, AC, and saves for 24 hours or until they successfully hit the archon 
that generated the aura. A creature that has resisted or broken the effect cannot 
be affected again by the same archon's aura for 24 hours.---

Immunity to electricity and petrification.---

+4 racial bonus on saves against poison.---

\textit{Magic Circle against Evil (Su): }A magic circle against evil effect always 
surrounds an archon (caster level equals the archon's Hit Dice). (The defensive 
benefits from the circle are not included in an archon's statistics block.)---

\textit{Teleport (Su): }Archons can use greater teleport at will, as the spell 
(caster level 14th), except that the creature can transport only itself and up 
to 50 pounds of objects.---

\textit{Tongues (Su): }All archons can speak with any creature that has a language, 
as though using a \textit{tongues }spell (caster level 14th). This ability is always 
active.

\vspace{12pt}
LANTERN ARCHON

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.997in}|}{\begin{minipage}[t]{2.997in}\raggedright
Small Outsider (Archon, Extraplanar, Good, Lawful)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Hit Dice :}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
1d8 (4 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Initiative :}\end{minipage}} & \multicolumn{1}{p{2.997in}|}{\begin{minipage}[t]{2.997in}\raggedright
+4\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Speed :}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
Fly 60 ft. (perfect) (12 squares)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Armor Class :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
15 (+1 size, +4 natural), touch 11, flat-footed 15\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
\textbf{Base Attack/Grapple :}\end{minipage}} & \multicolumn{1}{p{0.065in}|}{\begin{minipage}[t]{0.065in}\raggedright
+1/-8\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Attack :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Light ray +2 ranged touch (1d6)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Full Attack :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
2 light rays +2 ranged touch (1d6)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Space/Reach :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Special Attacks :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Spell-like abilities\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Special Qualities :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Aura of menace, damage reduction 10/evil and magic, darkvision 60 ft., immunity 
to electricity and petrification, magic circle against evil, teleport, tongues\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Saves :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Fort +2 (+6 against poison), Ref +2, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Abilities :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Str 1, Dex 11, Con 10, Int 6, Wis 11, Cha 10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Skills :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Concentration +4, Diplomacy +4, Knowledge (the planes) +2, Listen +4, Sense Motive 
+4, Spot +4\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Feats :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Improved Initiative\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Environment :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
A lawful good-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Organization :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Solitary, pair, or squad (3-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Challenge Rating :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
2\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Treasure :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
None\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Alignment :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
Always lawful good\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Advancement :}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
2-4 HD (Small)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.374in}|}{\begin{minipage}[t]{1.374in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.126in}|}{\begin{minipage}[t]{3.126in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

Lantern archons appear as floating balls of light that glow about as brightly as 
a torch. Only their destruction can extinguish the glow, though they can try to 
hide it.

\section*{COMBAT}

A lantern archon has little reason to get within melee range. It usually hovers 
just close enough to bring the enemy within its aura of menace, then blasts away 
with its light rays. Lantern archons prefer to concentrate on a single opponent, 
seeking to reduce enemy numbers quickly.

\textbf{Aura of Menace (Su):} Will DC 12 negates.

\textbf{Light Ray (Ex):} A lantern archon's light rays have a range of 30 feet. 
This attack overcomes damage reduction of any type.

\textbf{Spell-Like Abilities:} At will---\textit{aid, detect evil, continual flame. 
}Caster level 3rd.

\vspace{12pt}
HOUND ARCHON

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
\textbf{Hound Archon}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
\textbf{Hound Archon Hero, 11th-Level Paladin}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Outsider (Archon, Extraplanar, Good, Lawful)\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Outsider (Archon, Extraplanar, Good, Lawful)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
6d8+6 (33 hp)\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
6d8+18 plus 11d10+33 (143 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+4\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+4\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
40 ft. (8 squares)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
30 ft. in full plate armor (6 squares); base speed 40 ft.\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
19 (+9 natural), touch 10, flat-footed 19\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
30 (+9 natural, +11 \textit{+3 full plate armor}), touch 10, flat-footed 30\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
+6/+8\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
+17/+22\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Bite +8 melee (1d8+2) or greatsword +8 melee (2d6+3/19-20)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
\textit{+2 cold iron greatsword }+25 melee (2d6+9/19-20) or bite +22 melee (1d8+5)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Bite +8 melee (1d8+2) and slam +3 melee (1d4+1); or greatsword +8/+3 melee (2d6+3/19-20) 
and bite +3 melee (1d8+1)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
\textit{+2 cold iron greatsword }+25/+20/+15/+10 melee (2d6+9/19-20) and bite +17 
melee (1d8+2); or bite +22 melee (1d8+5) and slam +17 melee (1d4+2)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Spell-like abilities\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Smite evil, spells, spell-like abilities, turn undead 6/day\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Aura of menace, change shape, damage reduction 10/evil, darkvision 60 ft., immunity 
to electricity and petrification, magic circle against evil, scent, spell resistance 
16, teleport, tongues\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Aura of menace, change shape, damage reduction 10/evil, darkvision 60 ft., immunity 
to electricity and petrification, magic circle against evil, paladin abilities, 
scent, spell resistance 27, teleport, tongues\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Fort +6 (+10 against poison), Ref +5, Will +6\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Fort +18 (+22 against poison), Ref +11, Will +13\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Str 15, Dex 10, Con 13, Int 10, Wis 13, Cha 12\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Str 21, Dex 10, Con 16, Int 8, Wis 14, Cha 16\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Concentration +10, Diplomacy +3, Hide +9*, Jump +15, Listen +10, Move Silently 
+9, Sense Motive +10, Spot +10, Survival +10* (+12 following tracks)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Concentration +20, Diplomacy +19, Hide +2*, Jump +0, Listen +10, Ride +14, Sense 
Motive +19, Spot +10, Survival +2*\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Improved Initiative, Power Attack, Track\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Improved Initiative, Leadership, Mounted Combat, Ride-By Attack, Track, Weapon 
Focus (greatsword) \end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Environment}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
A lawful good-aligned plane\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
A lawful good-aligned plane\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Solitary, pair, or squad (3-5)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Solitary or with juvenile bronze dragon\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
4\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
16\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
No coins; double goods; standard items\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Standard\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
Always lawful good\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
Always lawful good\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
7-9 HD (Medium); 10-18 HD (Large)\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{0.691in}|}{\begin{minipage}[t]{0.691in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{1}{p{1.841in}|}{\begin{minipage}[t]{1.841in}\raggedright
+5\end{minipage}} & \multicolumn{4}{p{1.968in}|}{\begin{minipage}[t]{1.968in}\raggedright
+5\end{minipage}}\\
\hline
\end{longtable}

Hound archons look like well-muscled humans with canine heads.

\section*{COMBAT}

Hound archons prefer to attack with their natural weapons but occasionally use 
greatswords.

A hound archon's natural weapons, as well as any weapons it wields, are treated 
as good-aligned and lawful-aligned for the purpose of overcoming damage reduction.

\textbf{Spell-Like Abilities:} At will---\textit{aid, continual flame, detect evil, 
message. }Caster level 6th.

\textbf{Aura of Menace (Su): }Will DC 16 negates.

\textbf{Change Shape (Su):} A hound archon can assume any canine form of Small 
to Large size. While in canine form, the hound archon loses its bite, slam, and 
greatsword attacks, but gains the bite attack of the form it chooses. For the purposes 
of this ability, canines include any doglike or wolflike animal of the animal type.

\textbf{Skills: }*While in canine form, a hound archon gains a +4 circumstance 
bonus on Hide and Survival checks.

\vspace{12pt}
HOUND ARCHON HERO

The hound archon hero is a mighty champion of justice, devoted to the pursuit and 
destruction of evil in all its forms. 

COMBAT

Hound archon heroes have over time developed a love for their weapons. They prefer 
to use their \textit{holy greatswords }over their bite and slam attacks.

\textbf{Spell-Like Abilities:} At will---\textit{aid, continual flame, detect evil, 
message. }Caster level 6th.

\textbf{Aura of Menace (Su):} The save DC for the hound archon hero's aura of menace 
(DC 18) is adjusted for its higher Charisma score.

\textbf{Smite Evil (Su):} Three times per day a hound archon hero can make a normal 
melee attack with a +3 bonus that deals an extra 11 points of damage against an 
evil foe.

\textbf{Change Shape (Su):} A hound archon hero can assume any canine form of Small 
to Large size. While in canine form, the hound archon loses its bite, slam, and 
greatsword attacks, but gains the bite attack of the form it chooses. For the purposes 
of this ability, canines include any doglike or wolflike animal of the animal type.

\textbf{Skills:} *While in canine form, a hound archon hero gains a +4 circumstance 
bonus on Hide and Survival checks.

\textbf{Paladin Abilities: }Aura of courage, aura of good, \textit{detect evil}, 
divine grace, divine health, lay on hands (33 points/day), \textit{remove disease 
}2/week, special mount (juvenile bronze dragon). 

\textit{Typical Paladin Spells Prepared }(2/2; save DC 12 + spell level): 1st--- 
\textit{divine favor}, \textit{protection from evil; }2nd---\textit{bull's strength, 
eagle's splendor.}

\textit{Possessions: +3 full plate armor, +2 cold iron greatsword.}

\vspace{12pt}
HOUND ARCHON HERO MOUNTS

In the course of their adventures, many hound archon heroes befriend bronze dragons, 
which may come to serve as their mounts. The relationship between these mounts 
and their celestial riders goes beyond even the special bond between paladin and 
mount. The dragon and the archon are naturally allies and friends, as can be expected 
of two powerful servants of cosmic justice. The juvenile bronze dragon mount gains 
2 additional HD, 4 points of Strength, an additional 4 points of natural armor, 
improved evasion, and +10 feet to speed in all its movement forms. The dragon cannot, 
however, command other creatures of its type as other kinds of paladin mounts can.

\vspace{12pt}
HOUND ARCHONS AS CHARACTERS

Hound archon characters possess the following racial traits.---

+4 Strength, +2 Constitution, +2 Wisdom, +2 Charisma.---

Medium size.---

A hound archon's base land speed is 40 feet.---

Racial Hit Dice: A hound archon begins with six levels of outsider, which provide 
6d8 Hit Dice, a base attack bonus of +6, and base saving throw bonuses of Fort 
+5, Ref +5, and Will +5.---

Racial Skills: A hound archon's outsider levels give it skill points equal to 9 
\ensuremath{\times} (8 + Int modifier). Its class skills are Concentration, Hide, 
Jump, Listen, Move Silently, Sense Motive, Spot, and Survival.---

Racial Feats: A hound archon's outsider levels give it three feats.---

+9 natural armor bonus.---

Natural Weapons: Bite (1d8) and slam (1d4).---

Archon Traits (see page 16): Darkvision 60 ft., low-light vision, aura of menace 
(Will DC 15 + character's Cha modifier), immunity to electricity and petrification, 
+4 racial bonus on saves against poison, magic circle against evil, teleport, tongues.---

Special Attacks: Spell-like abilities.---

Special Qualities: Change shape, damage reduction 10/evil, scent, spell resistance 
equal to 16 + class levels.---

Automatic Languages: Celestial. Bonus Languages: Common, Draconic, Infernal.---

Favored class: Ranger.---

Level adjustment +5.

\vspace{12pt}
TRUMPET ARCHON

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
Medium Outsider (Archon, Extraplanar, Good, Lawful)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
12d8+72 (126 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.067in}|}{\begin{minipage}[t]{3.067in}\raggedright
+7\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
40 ft. (8 squares), fly 90 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
27 (+3 Dex, +14 natural), touch 13, flat-footed 24\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.063in}|}{\begin{minipage}[t]{0.063in}\raggedright
+12/+17\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
\textit{+4 greatsword }+21 melee (2d6+11/19-20)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
\textit{+4 greatsword }+21/+16/+11 melee (2d6+11/19-20)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Spell-like abilities, spells, trumpet\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Aura of menace, damage reduction 10/evil, darkvision 60 ft., immunity to electricity 
and petrification, magic circle against evil, spell resistance 29, teleport, tongues\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Fort +14 (+18 against poison), Ref +11, Will +11\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Str 20, Dex 17, Con 23, Int 16, Wis 16, Cha 16\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Concentration +21, Diplomacy +20, Escape Artist +18, Handle Animal +18, Knowledge 
(any one) +18, Listen +18, Move Silently +18, Perform (wind instruments) +18, Ride 
+20, Sense Motive +18, Spot +18, Use Rope +3 (+5 with bindings)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Blind-Fight, Cleave, Combat Reflexes, Improved Initiative, Power Attack\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
A lawful good-aligned plane\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Solitary, pair, or squad (3-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
14\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
No coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
Always lawful good\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
13-18 HD (Medium); 19-36 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.308in}|}{\begin{minipage}[t]{1.308in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.192in}|}{\begin{minipage}[t]{3.192in}\raggedright
+8\end{minipage}}\\
\hline
\end{longtable}

Each Trumpet Archon carries a gleaming silver trumpet about 6 feet long.

COMBAT

A trumpet archon usually disdains physical combat, preferring to obliterate foes 
with spells quickly and return to its duties. If forced into an extended battle, 
it sounds its trumpet and attacks with a vengeance.

A trumpet archon's natural weapons, as well as any weapons it wields, are treated 
as good-aligned and lawful-aligned for the purpose of overcoming damage reduction.

\textbf{Spell-Like Abilities: }At will---\textit{detect evil, continual flame, 
message. }Caster level 12th.

\textbf{Aura of Menace (Su):} Will DC 21 negates.

\textbf{Spells: }Trumpet archons can cast divine spells as 14th-level clerics. 
A trumpet archon has access to two of the following domains: Air, Destruction, 
Good, Law, or War (plus any others from its deity). The save DCs are Wisdom-based.

\textit{Typical Cleric Spells Prepared }(6/7/7/6/5/4/4/3; DC 13 + spell level): 
0---\textit{detect magic, light, purify food and drink, read magic, resistance 
}(2); 1st---\textit{bless }(2), \textit{divine favor }(2), \textit{protection from 
chaos*, sanctuary, shield of faith; }2nd---\textit{aid*, bull's strength }(2), 
\textit{consecrate, lesser restoration, owl's wisdom }(2); 3rd---\textit{daylight, 
invisibility purge, magic circle against chaos*, magic vestment, protection from 
energy }(2); 4th--- \textit{dismissal, divine power, holy smite*, neutralize poison, 
spell immunity; }5th---\textit{dispel evil*, mass cure light wounds, plane shift, 
raise dead; }6th--- \textit{blade barrier*, banishment, heal, undeath to death; 
}7th---\textit{dictum*, holy word, mass cure serious wounds.}

*Domain spell. Domains: Good and Law.

\textbf{Trumpet (Su): }An archon's trumpet produces music of utter clarity, piercing 
beauty, and, if the trumpet archon wills it, paralyzing awe. All creatures except 
archons within 100 feet of the blast must succeed on a DC 19 Fortitude save or 
be paralyzed for 1d4 rounds. The save DC is Charisma-based. The archon can also 
command its trumpet to become a \textit{+4 greatsword }as a free action.

If a trumpet is ever stolen, it becomes a chunk of useless metal until the owner 
can recover it. Woe betide any thief caught with one.

\vspace{12pt}
{\LARGE ARROWHAWK}

\begin{longtable}{llllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
\textbf{Juvenile Arrowhawk}\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
\textbf{Adult Arrowhawk}\end{minipage}} & \multicolumn{1}{p{1.240in}|}{\begin{minipage}[t]{1.240in}\raggedright
\textbf{Elder Arrowhawk}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Small Outsider (Air, Extraplanar)\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Medium Outsider (Air, Extraplanar)\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
Large Outsider (Air, Extraplanar)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
3d8+3 (16 hp)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
7d8+7 (38 hp)\end{minipage}} & \multicolumn{1}{p{1.240in}|}{\begin{minipage}[t]{1.240in}\raggedright
15d8+45 (112 hp)\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+5\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+5\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
+5\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Fly 60 ft. (perfect) (12 squares)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Fly 60 ft. (perfect) (12 squares)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Fly 60 ft. (perfect) (12 squares)\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
20 (+1 size, +5 Dex, +4 natural), touch 16, flat-footed 15\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
21 (+5 Dex, +6 natural), touch 15, flat-footed 16\end{minipage}} & \multicolumn{1}{p{0.042in}|}{\begin{minipage}[t]{0.042in}\raggedright
22 (-1 size, +5 Dex, +8 natural), touch 14, flat-footed 17\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
+3/+0\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
+7/+9\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
+15/+25\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Electricity ray +9 ranged touch (2d6) or bite +9 melee (1d6+1)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Electricity ray +12 ranged touch (2d8) or bite +12 melee (1d8+3)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Electricity ray +19 ranged touch (2d8) or bite +21 melee (2d6+9)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Electricity ray +9 ranged touch (2d6) or bite +9 melee (1d6+1)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Electricity ray +12 ranged touch (2d8) or bite +12 melee (1d8+3)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Electricity ray +19 ranged touch (2d8) or bite +20 melee (2d6+9)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
5 ft./5 ft.\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
10 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Electricity ray\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Electricity ray\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Electricity ray\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Darkvision 60 ft., immunity to acid, electricity, and poison, resistance to cold 
10 and fire 10\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Darkvision 60 ft., immunity to acid, electricity, and poison, resistance to cold 
10 and fire 10\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Darkvision 60 ft., immunity to acid, electricity, and poison, resistance to cold 
10 and fire 10\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Fort +4, Ref +8, Will +4\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Fort +6, Ref +10, Will +6\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Fort +12, Ref +14, Will +10\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Str 12, Dex 21, Con 12, Int 10, Wis 13, Cha 13\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Str 14, Dex 21, Con 12, Int 10, Wis 13, Cha 13\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Str 22, Dex 21, Con 16, Int 10, Wis 13, Cha 13\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Diplomacy +3, Escape Artist +11, Knowledge (the planes) +6, Listen +7, Move Silently 
+11, Search +6, Sense Motive +7, Spot +7, Survival +7 (+9 following tracks, +9 
Plane of Air), Use Rope +5 (+7 with bindings)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Diplomacy +3, Escape Artist +15, Knowledge (the planes) +10, Listen +11, Move Silently 
+15, Search +10, Sense Motive +11, Spot +11, Survival +11 (+13 following tracks, 
+13 Plane of Air), Use Rope +5 (+7 with bindings)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Diplomacy +3, Escape Artist +23, Knowledge (the planes) +18, Listen +21, Move Silently 
+23, Search +18, Sense Motive +19, Spot +21, Survival +19 (+21 following tracks, 
+21 Plane of Air), Use Rope +5 (+7 involving bindings)\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Dodge, Weapon Finesse\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Dodge, Flyby Attack, Weapon Finesse\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Alertness, Blind-Fight, Combat Reflexes, Dodge, Flyby Attack, Weapon Finesse, Weapon 
Focus (bite)\textsuperscript{B}\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Environment}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Elemental Plane of Air\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Elemental Plane of Air\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Elemental Plane of Air\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Solitary or clutch (2-4)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Solitary or clutch (2-4)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Solitary or clutch (2-4)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
5\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
8\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
None\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
None\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
None\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
Always neutral\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
Always neutral\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
4-6 HD (Small)\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
8-14 HD (Medium)\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
16-24 HD (Large); 25-32 HD (Gargantuan)\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{0.702in}|}{\begin{minipage}[t]{0.702in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{1}{p{1.179in}|}{\begin{minipage}[t]{1.179in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{1.211in}|}{\begin{minipage}[t]{1.211in}\raggedright
---\end{minipage}} & \multicolumn{5}{p{1.408in}|}{\begin{minipage}[t]{1.408in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

An arrowhawk is a predator and scavenger from the Elemental Plane of Air.  By twisting 
its body and varying the cadence of its wingbeats, an arrowhawk can fly at top 
speed in any direction. A juvenile arrowhawk (1 to 10 years old) is about 5 feet 
long from beak to tail, with the body accounting for about one-third of that length. 
Its wingspan is about 7 feet, and it weighs about 20 pounds. An adult (11 to 40 
years old) is about 10 feet long from beak to tail, with a wingspan of about 15 
feet and a weight of about 100 pounds. An elder arrowhawk (41 to 75 years old) 
is about 20 feet long with a wingspan of 30 feet and a weight of about 800 pounds.

Arrowhawks speak Auran, but they are not usually talkative creatures.

COMBAT

Arrowhawks are extremely territorial and always hungry. They attack almost any 
other creature they meet, seeking a meal or trying to drive away a rival. The primary 
mode of attack is an electricity ray, fired from the tail. The creature also bites, 
but it prefers to stay out of reach.

\textbf{Electricity Ray (Su):} An arrowhawk can fire this ray once per round, with 
a range of 50 feet.

\vspace{12pt}
{\LARGE ASSASSIN VINE}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.775in}|}{\begin{minipage}[t]{2.775in}\raggedright
Large Plant\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
4d8+12 (30 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.775in}|}{\begin{minipage}[t]{2.775in}\raggedright
+0\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
5 ft. (1 square)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
15 (-1 size, +6 natural), touch 9, flat-footed 15\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+3/+12\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Slam +7 melee (1d6+7)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Slam +7 melee (1d6+7)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
10 ft./10 ft. (20 ft. with vine)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Constrict 1d6+7, entangle, improved grab\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Blindsight 30 ft., camouflage, immunity to electricity, low-light vision, plant 
traits, resistance to cold 10 and fire 10\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Fort +7, Ref +1, Will +2\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Str 20, Dex 10, Con 16, Int ---, Wis 13, Cha 9\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Temperate forests\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Solitary or patch (2-4)\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
3\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
1/10th coins; 50\% goods; 50\% items\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
Always neutral\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
5-16 HD (Huge); 17-32 HD (Gargantuan); 33+ HD (Colossal)\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.442in}|}{\begin{minipage}[t]{1.442in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{2.914in}|}{\begin{minipage}[t]{2.914in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

The assassin vine is a semi-mobile plant that collects its own grisly fertilizer 
by grabbing and crushing animals and depositing the carcasses near its roots.

A mature plant consists of a main vine, about 20 feet long. Smaller vines up to 
5 feet long branch off from the main vine about every 6 inches. These small vines 
bear clusters of leaves, and in late summer they produce bunches of small fruits 
that resemble wild grapes. The fruit is tough and has a hearty but bitter flavor. 
Assassin vine berries make a heady wine.

An assassin vine can move about, albeit very slowly, but usually stays put unless 
it needs to seek prey in a new vicinity.

A subterranean version of the assassin vine grows near hot springs, volcanic vents, 
and other sources of thermal energy. These plants have thin, wiry stems and gray 
leaves shot through with silver, brown, and white veins so that they resemble mineral 
deposits. An assassin vine growing underground usually generates enough offal to 
support a thriving colony of mushrooms and other fungi, which spring up around 
the plant and help conceal it.

COMBAT

An assassin vine uses simple tactics:

It lies still until prey comes within reach, then attacks. It uses its entangle 
ability both to catch prey and to deter counterattacks.

\textbf{Constrict (Ex):} An assassin vine deals 1d6+7 points of damage with a successful 
grapple check.

\textbf{Entangle (Su): }An assassin vine can animate plants within 30 feet of itself 
as a free action (Ref DC 13 partial).

The effect lasts until the vine dies or decides to end it (also a free action). 
The save DC is Wisdom-based. The ability is otherwise similar to \textit{entangle 
}(caster level 4th).

\textbf{Improved Grab (Ex):} To use this ability, an assassin vine must hit with 
its slam attack.

It can then attempt to start a grapple as a free action without provoking an attack 
of opportunity.

If it wins the grapple check, it establishes a hold and can constrict.

\textbf{Blindsight (Ex): }Assassin vines have no visual organs but can ascertain 
all foes within 30 feet using sound, scent, and vibration.

\textbf{Camouflage (Ex):} Since an assassin vine looks like a normal plant when 
at rest, it takes a DC 20 Spot check to notice it before it attacks.

Anyone with ranks in Survival or Knowledge (nature) can use one of those skills 
instead of Spot to notice the plant. Dwarves can use stonecunning to notice the 
subterranean version.

\vspace{12pt}
{\LARGE ATHACH}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.949in}|}{\begin{minipage}[t]{2.949in}\raggedright
Huge Aberration\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
14d8+70 (133 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.949in}|}{\begin{minipage}[t]{2.949in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
35 ft. in hide armor (7 squares); base speed 50 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
20 (-2 size, +1 Dex, +3 hide armor, +8 natural), touch 9, flat-footed 19\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
+10/+26 Attack:Morningstar +16 melee (3d6+8) or rock +9 ranged (2d6+8)\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Morningstar +12/+7 melee (3d6+8), and 2 morningstars +12 melee (3d6+4), and bite 
+12 melee (2d8+4 plus poison); or rock +5 ranged (2d6+8), and 2 rocks +5 ranged 
(2d6+4)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
15 ft./15 ft.\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Poison\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Darkvision 60 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Fort +9, Ref +5, Will +10\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Str 26, Dex 13, Con 21, Int 7, Wis 12, Cha 6\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Climb +9, Jump +18, Listen +7, Spot +7\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Alertness, Cleave, Multiweapon Fighting, Power Attack, Weapon Focus (bite)\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Temperate hills\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Solitary, gang (2-4), or tribe (7-12)\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
8\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
1/2 coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
Often chaotic evil\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
15-28 HD (Huge)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.414in}|}{\begin{minipage}[t]{1.414in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.086in}|}{\begin{minipage}[t]{3.086in}\raggedright
+5\end{minipage}}\\
\hline
\end{longtable}

The athach is a hulking, misshapen biped. An adult stands some 18 feet tall and 
weighs about 4,500 pounds. Athachs speak a crude dialect of Giant.

COMBAT

Athachs charge into melee combat unless their opponents are out of reach, in which 
case they throw rocks. They sometimes try to overrun armored opponents to reach 
unarmored opponents in back ranks. With its first few melee attacks, an athach 
tends to flail about indiscriminately. After a few rounds, it concentrates on foes 
that have been hitting it most often and uses its bite on whoever has dealt it 
the most damage.

\textbf{Poison (Ex): }Injury, Fortitude DC 22, initial damage 1d6 Str, secondary 
damage 2d6 Str. The save DC is Constitution-based.

\vspace{12pt}
{\LARGE AVORAL}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{3.083in}|}{\begin{minipage}[t]{3.083in}\raggedright
Medium Outsider (Extraplanar, Good)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
7d8+35 (66 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{3.083in}|}{\begin{minipage}[t]{3.083in}\raggedright
+6\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
40 ft. (8 squares), fly 90 ft. (good)\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
24 (+6 Dex, +8 natural), touch 16, flat-footed 18\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{1}{p{0.062in}|}{\begin{minipage}[t]{0.062in}\raggedright
+7/+9\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Claw +13 melee (2d6+2) or wing +13 melee (2d8+2)\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
2 claws +13 melee (2d6+2) or 2 wings +13 melee (2d8+2)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Spell-like abilities, fear aura\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Damage reduction 10/evil or silver, darkvision 60 ft., immunity to electricity 
and petrification, lay on hands, low-light vision, resistance to cold 10 and sonic 
10, speak with animals, spell resistance 25, true seeing\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Fort +10 (+14 against poison), Ref +11, Will +8\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Str 15, Dex 23, Con 20, Int 15, Wis 16, Cha 16\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Bluff +13, Concentration +15, Diplomacy +7, Disguise +3 (+5 acting), Handle Animal 
+13, Hide +16, Intimidate +5, Knowledge (any one) +12, Listen +13, Move Silently 
+16, Ride +8, Sense Motive +13, Spellcraft +12, Spot +21\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Empower Spell-Like Ability (\textit{magic missile}), Flyby Attack, Weapon Finesse\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
A good-aligned plane.\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Solitary, pair, or squad (3-5)\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
9\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
No coins; double goods; standard items\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
Always neutral good\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
8-14 HD (Medium); 15-21 HD (Large)\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.292in}|}{\begin{minipage}[t]{1.292in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{3.208in}|}{\begin{minipage}[t]{3.208in}\raggedright
---\end{minipage}}\\
\hline
\end{longtable}

An avoral's bones are strong but hollow, so even the largest specimens weigh no 
more than 120 pounds. An avoral is about 7 feet tall. Each of an avoral's wings 
has a small hand at the midpoint. When the wings are folded, these appendages are 
about where human hands would be and can do nearly anything hands can do.

An avoral's visual acuity is virtually unmatched: It can see detail on objects 
up to 10 miles away and is said to be able to discern the color of a creature's 
eyes at 200 paces.

Avorals speak Celestial, Infernal, and Draconic, but can speak with almost any 
creature, thanks to their \textit{tongues }ability.

COMBAT

On the ground, an avoral can lash out with its wings to deliver punishing blows. 
However, it prefers to meet its foes in the air, where it can employ its talons 
and make full use of its aerial speed and agility. It can't make wing attacks while 
flying, however.

An avoral's natural weapons, as well as any weapons it wields, are treated as good-aligned 
for the purpose of overcoming damage reduction.

\textbf{Spell-Like Abilities:} At will---\textit{aid, blur }(self only), \textit{command 
}(DC 14), \textit{detect magic, dimension door, dispel magic, gust of wind }(DC 
15), \textit{hold person }(DC 16), \textit{light, magic circle against evil }(self 
only), \textit{magic missile, see invisibility; }3/day---\textit{lightning bolt 
}(DC 16). Caster level 8th. The save DCs are Charisma-based.

\textbf{Fear Aura (Su):} Once per day an avoral can create an aura of fear in a 
20-foot radius. It is otherwise identical with \textit{fear }from an 8th-level 
caster (save DC 17). The save DC is Charisma-based.

\textbf{Lay on Hands (Su):} As the paladin class feature, except that each day, 
an avoral can heal an amount of damage equal to its full normal hit points.

\textbf{Speak with Animals (Su):} This ability works like \textit{speak with animals 
}(caster level 8th) but is a free action and does not require sound.

\textbf{True Seeing (Su):} This ability is identical with \textit{true seeing }(caster 
level 14th), except that it has personal range and the avoral must concentrate 
for 1 full round before it takes effect. Thereafter the ability remains in effect 
as long as the avoral concentrates on it.  

\textbf{Skills:} An avoral's sharp eyes give it a +8 racial bonus on Spot checks.

\vspace{12pt}
{\LARGE AZER}

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{1}{p{2.672in}|}{\begin{minipage}[t]{2.672in}\raggedright
Medium Outsider (Extraplanar, Fire)\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
\textbf{Hit Dice:}\end{minipage}} & \multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
2d8+2 (11 hp)\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Initiative:}\end{minipage}} & \multicolumn{1}{p{2.672in}|}{\begin{minipage}[t]{2.672in}\raggedright
+1\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
\textbf{Speed:}\end{minipage}} & \multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
20 ft. in scale mail (4 squares); base speed 30 ft.\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Armor Class:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
23 (+1 Dex, +6 natural, +4 scale mail, +2 heavy\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
\textbf{shield), touch 11, flat-footed 22}\end{minipage}} & \multicolumn{1}{p{0.060in}|}{\begin{minipage}[t]{0.060in}\raggedright
\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Base Attack/Grapple:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
+2/+3\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Attack:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Warhammer +3 melee (1d8+1/x3 plus 1 fire) or shortspear +3 ranged (1d6+1 plus 1 
fire)\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Full Attack:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Warhammer +3 melee (1d8+1/x3 plus 1 fire) or shortspear +3 ranged (1d6+1 plus 1 
fire)\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Space/Reach:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
5 ft./5 ft.\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Special Attacks:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Heat\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Special Qualities:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Darkvision 60 ft., immunity to fire, spell resistance 13, vulnerability to cold\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Saves:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Fort +4, Ref +4, Will +4\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Abilities:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Str 13, Dex 13, Con 13, Int 12, Wis 12, Cha 9\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Skills:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Appraise +6, Climb +0, Craft (any two) +6, Hide +0, Jump -6, Listen +6, Search 
+6, Spot +6\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Feats:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Power Attack\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Environment:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Elemental Plane of Fire\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Organization:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Solitary, pair, team (3-4), squad (11-20 plus 2 3rd-level sergeants and 1 leader 
of 3rd-6th level), or clan (30-100 plus 50\% noncombatants plus 1 3rd-level sergeant 
per 20 adults, 5 5th-level lieutenants, and 3 7th-level captains)\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Challenge Rating:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
2\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Treasure:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Standard coins; double goods (nonflammables only); standard items (nonflammables 
only)\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Alignment:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
Always lawful neutral\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Advancement:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
By character class\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{|p{1.708in}|}{\begin{minipage}[t]{1.708in}\raggedright
\textbf{Level Adjustment:}\end{minipage}} & \multicolumn{3}{p{2.792in}|}{\begin{minipage}[t]{2.792in}\raggedright
+4\end{minipage}}\\
\hline
\end{longtable}

Azers are dwarflike beings native to the Elemental Plane of Fire. They wear kilts 
of brass, bronze, or copper, and speak Ignan and Common.

COMBAT

Azers use broad-headed spears or well-crafted hammers in combat. When unarmed, 
they attempt to grapple foes.

Although unfriendly and taciturn, azers rarely provoke a fight except to relieve 
a foe of gems, which they love. If threatened, they fight to the death, but they 
see the value of taking prisoners themselves.

\textbf{Heat (Ex):} An azer's body is intensely hot, so its unarmed attacks deal 
extra fire damage. Its metallic weapons also conduct this heat.

\vspace{12pt}
AZERS AS CHARACTERS

Azer characters possess the following racial traits.---

+2 Strength, +2 Dexterity, +2 Constitution, +2 Intelligence, +2 Wisdom, -2 Charisma.---

Medium size.---

An azer's base land speed is 30 feet.---

Darkvision: Azers can see in the dark up to 60 feet.---

Racial Hit Dice: An azer begins with two levels of outsider, which provide 2d8 
Hit Dice, a base attack bonus of +2, and base saving throw bonuses of Fort +3, 
Ref +3, and Will +3.---

Racial Skills: An azer's outsider levels give it skill points equal to 5 x (8 + 
Int modifier). Its class skills are Appraise, Climb, Craft, Hide, Jump, Listen, 
Search, and Spot.---

Racial Feats: An azer's outsider levels give it one feat.---

+6 natural armor bonus.---

Special Attacks (see above): Heat.---

Special Qualities (see above): Immunity to fire, spell resistance equal to 13 + 
class levels, vulnerability to cold.---

Automatic Languages: Common, Ignan. Bonus Languages: Abyssal, Aquan, Auran, Celestial, 
Infernal, Terran.---

Favored Class: Fighter.---

Level adjustment +4.

\end{document}
