\descfeat{Child Necromancer}
{An obsession with death and experimentation with necromancy early in your childhood perverted your body and blossoming magical talent. As a result, your body never aged past childhood, and you are an adult in a child's body, magically powerful but physically weak.}
\shortability{Prerequisite:}{Caster level 1, must know at least one necromancy spell of each spell level you can cast.}
\shortability{Benefit:}{All Necromancy spells you cast are at +4 caster level, and you gain the effects of \hyperlink{feat:weaponfinesse}{Weapon Finesse} for all Necromancy touch attack spells you use (if you desire). You have -4 Strength, and appear to be a child despite your actual age category (this does not prevent penalties or bonuses from advancing in age categories, or stop the aging process). You are one size category smaller than normal for your race (do not further adjust ability modifiers). If you are a spontaneous caster, you may permanently exchange any spell known for any Necromancy spell you possess in written or scroll form. If you are a preparation caster, you may learn any Necromancy spell you possess in written or scroll form from any list, and you may not select Necromancy as a restricted school. These Necromancy spells may be from any list, can be exchanged at any time, and once gained are cast as spells of your spellcasting class. These spells remain as spells known even if you later lose this feat.}
\shortability{Special:}{This feat can only be taken at 1st level. If circumstances ever cause a character to no longer meet the prerequisites of this feat, they may choose any metamagic feat they qualify for to permanently replace this feat.}

