\subsection{Combat Feats} \label{comm:combatfeats}

\begin{multicols}{2}

\label{comm:feat:aerialassault}{}\babfeat{Aerial Assault [Combat]}{
You are adept at fighting in the sky. Oh yeah, and you have to be able to fly to take this feat.}{
Your maneuverability improves by one category, and you gain a +3 bonus to damage when charging in the air.}{
You deal double damage when flying at least 10 feet and attacking. Also, your flight speed increases by 10 feet.}{
You can now hover in mid-air, and when making a move action while flying, can make a single standard action at any point inside the move action.}{
You can snatch foes from the ground while flying, by making a normal Grapple check against any foe at least one size category smaller than you. Dropping them is a free action, although they may make a Grapple check to hang on. Your flight speed increases by another 10 feet.}{When charging in midair, you may make a full attack action at the end of your charge.}

\label{comm:feat:bloodsoaked}{}\babfeat{Blood-Soaked Charger [Combat]}{
You like to impale people upon your sharp spikes.
}{ You gain proficiency with spiked gauntlets, armour spikes, shield spikes and any natural spike attacks. You also gain a +1 to hit and damage with such weapons.
}{ The bonus to attack and damage rolls increases to +4.
}{ When you attack someone with the spiky weapons mentioned above, you may additionally bullrush them, and can attack with all such weapons in the one action.
}{ When you successfully charge or Bullrush a foe with such weapons, each successful hit deals extra damage equal to 2d6+one and a half times your Strength modifier.
}{ The additional charge damage deals 4d6 plus double your Strength modifier damage, as well as 2 points of Con damage. They now all gain an effective Enhancement Bonus equal to one quarter of your level (round down). This means they get the bonus to hit and damage, bypass magical DR as well as all material DR, and additionally can hit incorporeal foes.}


\label{comm:feat:brutalgrappler}{}\babfeat{Brutal Grappler [Combat]}{ 
You like to hold onto people. And rip them into pieces. Basically, you're a sadistic bastard.}{ 
You gain a +3 bonus to Grapple checks. }{ 
You may perform a Coup De Grace against a pinned opponent against whom you have the Edge. }{
When you perform a Coup De Grace either unarmed or with a natural weapon in a grapple, you may opt to break an opponent's limb. The damage done with the Coup De Grace is not lethal damage; rather, it is used for the DC for the Fort save (DC 10+ half weapon damage + Str mod, large creatures gain a +3 bonus for each size larger and small creatures -3 for each size smaller than Medium.) used to resist the bone-breaking. If victim fails the save, he takes a number of d6's equal to one quarter of his HD in non-lethal damage and the limb is rendered useless (a broken arm may not use a weapon nor grant a shield bonus; a broken leg reduces speed by half for bipeds, a quarter for quadrupeds, takes a full-round action to move). A broken bone may be healed by 16 points of healing for a Medium creature, halving for each size category smaller and doubling for each size category larger. }{
After Holding On to an opponent, you may spend a standard action and a grapple check each round 'optimizing' your grapple. Optimizing can be adjusting your grip on the opponent, or climbing up a larger opponent to reach a better spot to attack. After spending a round optimizing, you may perform a Coup De Grace. You may also use a one-handed weapon to attack any time you are allowed to attack in a Grapple. }{
When you take a Coup De Grace, you may elect to take a Coup De Grace that instead maims the opponent. Maiming usually involves the loss of a body part. Examples of maiming include pulling or cutting an appendage of off the victim, pulling an eye (or eyes) out, or inflicting a horrible wound (punching hard enough to break the skin and the bones underneath and other), and so on. 
Maiming requires a Fort save. The DC is (10 + Half-damage dealt + Str mod. Opponents at 50\% HP take a -3 penalty to their saves, and opponents at 25\% hit points take a -8.) A failed save means a successful maiming, the infliction of a wound (which could be the loss of an arm or leg) and lethal damage equal to a maximized critical hit. 
Maiming must be half-way believable (for example, you can't cut off a limb with a weapon that is too short to cut all the way through.) At the DM's option, fatal maiming options are available, and then the sky's the limit.}

\label{comm:feat:deadlyaura}{}\babfeat{Deadly Aura [Combat]}{
You belong in a series that has a GT on the end of it. }{
As a swift action, you may call upon an aura of destructive energy for a round. All your natural attacks deal an extra 1d6 damage per four levels (Minimum 1d6), and enemies hitting you with their natural attacks take the same value.}{
Your aura is considered a Force effect, as are your empowered natural attacks.}{
You may now shoot bolts of energy when your aura is activated as an attack action. They have a 10 ft range, and deal damage equal to your aura's.}{
Your aura now lasts one round per level.}{
Your aura may be activated as a free action.}

\label{comm:feat:duelist}{}\babfeat{Duelist [Combat]}
{You wade into heavy melee with nothing but a rapier and some shiny pants; it seems to work pretty well for you.
}{Whenever you use the combat expertise option you gain a +2 Dodge Bonus to AC for every -1 you take on your attack rolls.(Any and all benefits of this feat only apply when wearing only Light or lighter armor, carrying no more than light load, wielding only one weapon, and keeping one hand free.)
}{You gain extra attacks due to BaB at multiples of 3 instead of 5, you gain your first extra attack at +4 BaB, your second at +7 Bab, etc, ect. You never take more than a -3 penalty to your attacks due to being secondary (ie. at level 10 your full attack would normally look like this: +10/+7/+7+7.)
}{You gain a +4 bonus to disarm checks. If you are disarmed or you disarm your opponent with your weapon you can spend an attack of opportunity to grab the disarmed item out of the air with your free hand. As an attack action you can immediately throw a newly disarmed and caught weapon. If the weapon normally has a range increment this can be a normal ranged attack, if it doesn't have a range increment then you can only target a square within 50ft. of you and not a creature. This thrown attack doesn't count against your one weapon only, one free-hand status.
}{You may attempt to Feint, as a free action, once per attack granted by virtue of a high BaB by spending one attack of opportunity per Feint. You may use Sleight of Hand or an attack roll in place of Bluff for the purpose of Feinting if you wish.
}{You can choose to make a single melee attack as a Standard Action to gain a +4 bonus on your attack roll and multiply your damage by 10. This attack may only be used against an opponent that is denied their dexterity bonus to AC or that you are Flanking.}

\label{comm:feat:foewielder}{}\babfeat{Foe Wielder (Combat)}
{You like to club people. With other people.
}{You are considered proficient with living creatures (including constructs and undead), and gain a +2 bonus on attack and damage rolls when using them as weapons. Damage is 2d6 for a Medium creature, and you add their natural armour bonus (or armour bonus if worn, whichever is greater) to the damage.
}{Your reach extends by five feet per size category beyond Medium that the wielded creature is. Additionally, you may elect for the wielded creature to take damage equal to that dealt to the target.
}{Any foe struck by a creature you wield must succeed at a Balance check opposed by your attack roll, or fall prone. You may also throw living creatures, with a ten foot range increment. They land prone and both them and the target take an additional 1d6 damage.
}{Whether the wielded creature wishes to or not, you may force them to make a full attack against one target you strike with them, once per round. They use Expertise and Power Attack the same amount that you do. When thrown, they automatically make a bullrush attempt, attacking everyone in the path, but still fall prone nonetheless.
}{You may throw the creature to hit an area in a splash attack - designate a number of squares equal to their space, all foes in the area must make a Reflex save with a DC equal to your attack roll, or be hit. Additionally, when you hit someone in melee with another creature who has at least two hands (or other grappling limbs) free, you may force them to grab their target, adding even more to your reach. You may continue this indefinitely, up to your normal weight limit, and may disarm all except the first by making a line attack (equal to their combined height). This line attack deals their combined hit dice in d6 of damage, and is negated by a Ref save (DC equals your attack roll).}

\label{comm:feat:kibomb}{}\babfeat{Ki Bomb (Combat)}
{There really should be a TV show which does this kind of thing. Or at least a character class.
}{As a full-round action, you may build up and then expel some of your body's energy in an explosive ki bomb. It inflicts 1d10 fire [(or maybe Light?)]damage, hits on a ranged touch attack, and has a range increment of 50 feet. 
}{ Your ki bomb is now a burst with a 5ft radius. 
}{Your ki bomb now does 1d8 damage per two character levels. 
}{Charge it up!--for every round you spend a standard action 'charging up' your ki bomb, the ki bomb's radius increases by 10 feet and your damage die increases by one step. You may spend a number of rounds charging up equal to your character level divided by 4. If you are hit before you can fire off a charged ki bomb, you must make a concentration check 
}{Your ki bomb now inflicts 1d6 damage per character level. It now is a Force effect and inflicts Force damage. Obi-Wan taught you well.}

\label{comm:feat:knockdown}{}\babfeat{Knock Down [Combat]}
{You like to make people fall on their asses. 
}{You may be considered one size category larger for the purposes of any size dependant roll you make (such as a Bull Rush, Overrun, or Lift action). This stacks with all similar abilities such as powerful build.
}{ Any time you hit and deal at least 10 points of damage you may make a free trip attempt. If you succeed you do not gain the standard extra attack on them.
}{If you score a hit while you are using the Power Attack feat, you can make a free bull rush attempt against the foe you hit, applying the number by which you reduced your attack roll as a bonus on the opposed Strength check (as well as on the damage you deal). If you hit with a two-handed weapon, you can apply double that number on the opposed Strength check. Unlike standard bull rush attempts, knockback attempts don't provoke attacks of opportunity, and you don't move with the enemy you knock backward. Bull Rush rules can be found on page 154 of the Player's Handbook.
If you choose to use this option in conjunction with a trip attempt the target falls prone at the end of the movement.
}{Every time you hit an enemy in melee they must make a fort save (DC 10+Str mod+ PA bonus damage) or take a cumulative -2 penalty to attack rolls, AC, and checks. This penalty lasts until the start of your next turn. In addition, by spending a swift action you gain a bonus equal to half your BAB on advanced combat technique checks (Trip, Bull Rush, etc) for a number of rounds equal to your BAB.
}{Flying creatures are now subject to your combat maneuvers. If you make a successful trip check against a flying creature (flying creatures get a +4 bonus to resist trips) then you may hurtle them to the ground (use the rules for the +6 bab ability for the check, but regardless of positioning they head straight down). If you hurtle them far enough to strike the ground they take a number of d6 equal to the number of squares they were prevented from moving plus three times your strength modifier.
If you do not hurtle them into the ground they end their movement still flying, but must make a move equivalent action to stop themselves from falling further.}

\label{comm:feat:legendarywrestler}{}\babfeat{Legendary Wrestler}
{You're not just good at grabbing people and throwing them to the ground, no. You're That. Damn. Good.
}{You gain a +4 bonus to any Grapple-type checks. You can also grapple foes one size larger than normal, and can still grapple even if damaged by an AoO made.
}{ When damaging someone in a grapple, you can choose to also make them prone, or to end the grapple, throwing them 5' forever 2 points you beat them by in the grapple.
}{You don't provoke for starting a grapple, and you also aren't flat-footed when grappling someone. If you grapple someone to deal damage and are near a solid wall or on stone (or harder material), you may add the hardness of the wall/ground to the damage. If pinning and next to a wall, you gain +4 to the grapple check due to the leverage.
}{You can even grapple foes who are incorporeal, ethereal, insubstantial, benefiting from \spell{freedom of movement} or any other immunity to grappling. They gain a +5 bonus to escape, but at this point you probably don't even care. When dealing damage as a grapple attack, you can also force the target to make a Fort save (Strength-based DC) or become Dazed for 1d4 rounds.
}{You gain a finishing move. If a foe is denied their dexterity modifier (being grappled alone cannot be enough for this - something else must cause this) or are prone, dazed, exhausted, nauseated, cowering or stunned (because some people have Uncanny Dodge), you may make a grapple attack to deal damage, hitting them with your finisher.

The finishing move does +1d6 damage per level and forces them to make a Fortitude save (Strength-based DC) or be knocked out for three rounds. Performing this makes you fatigued for two rounds, and you cannot perform it while fatigued.}

\label{comm:feat:natureswarrior}{}\babfeat{Nature's Warrior (Combat)}
{You stab people in the face with foliage.
}{You are considered proficient with sticks, rocks, stones, boulders, menhirs, logs, branches, trees, cacti, vines, thornbushes, moss and other naturally occuring things that could loosely be considered weapons. As an added bonus, you gain a +2 bonus to hit and damage with them.
}{ If you club someone with a piece of rock, they take two points of Dexterity damage on a failed Fortitude save (DC 10 + 1/2 your level + STR). If you hit someone with a thorny or otherwise sharp piece of nature, they take two points of Strength damage on a failed Fortitude save (same DC). If neither of the above apply, but it contains a lot of leaves, dirt, moss or loose bark, then they must make a Reflex save (same DC) or be dazed and blinded for a round as they cough and choke. You may use vines and long, flexible plants to grapple at a range. This allows you to choke them while grappling, forcing a Fort save (same DC) every round. Every round they fail, they are Dazed and take 2d6 damage.
}{Any foe you hit with a rock must succeed on a Balance check opposed by your attack roll or fall prone. If they fail their Fortitude save against Dexterity damage, they are Stunned for one round. If hit with sharp pieces of nature, they must save against poison (usual DC, damage is 1d4 Constitution). If hit with logs, trees, bushes or other things which may contain insects, they must make a Reflex save (usual DC) or be attacked by a swarm of insects with a CR at least 4 lower than your level. This swarm lasts for four rounds, then automatically returns to the source.
}{Any piece of nature you wield, including thrown weapons and swarms that emerge from such weapons, have an enhancement bonus equal to one quarter of your character level (round down), but only when wielded by you. You may also apply one +1 special property to all such weapons, and can change it using a Swift action.
}{Rocks now deal an extra 1d6 damage per four levels (round down), when wielded by you. Sharp or spiky plants now gain an extra rend attack on any round that they successfully hit, dealing double their usual damage, plus double your strength modifier (triple if wielded 2-handed), plus 4d6 damage. Weapons with loose things that can be choked on now Nauseate targets for 1d4 rounds if they fail a Fortitude save (usual DC). If they succeed, they are Sickened instead.}

\label{comm:feat:sunderer}{}\babfeat{Sunderer (Combat)}
{You break things. Other peoples things.
}{Your sundering attempts do not provoke an AoOs.
}{You gain a +4 bonus on opposed Sunder rolls.
}{You gain the Sundering Cleave ability (you make make a Cleave attack as an AoO following a successful sunder).
}{Your weapons are considered to have the Sharpness property from Book of Gears.
}{You may attempt a Sunder or Ranged Sunder as part of an attack once per round.}

\label{comm:feat:toughasnails}{}\babfeat{Tough as Nails [Combat]}
{Also entitled: The Dwarf Feat
}{You think nothing of pushing your body to limits that would leave anyone else sprained and sore. You add your Con bonus to Grapple, Climb, Swim checks, as well as Str checks. Your also add your Con bonus to your Str for determining lifting/carrying capacity.
}{You may use your Con bonus instead of your Dex for determining Dodge bonus to AC.
}{Take yer best shot: As a swift action you may opt to lose your Dex bonus for a round, and any damage you take from enemies during that round is added to your melee damage the round afterwards.
}{Counterpuncher: Activating this is a swift or immediate action. When you're next hit in melee, you get an AoO at the enemy, getting half the damage he inflicted to your own attack and damage.
}{When reduced to negative HP, you automatically stabilize and can act and move normally, although you still die when you're reduced to your limit. Also, when you lose half your HP, you become pissed and you gain your Con bonus to attack and damage, and gain DR X/-, where X is equal to 10 + your Con score, and blanket energy resistance equal to your DR (If you manage to get Energy Resistance 25, you get Immunity). Being pissed lasts for one minute.}

\label{comm:feat:turnabout}{}\babfeat{Turnabout [Combat]}
{Turnabout is fair play.
}{Enemies do not gain the standard flanking bonus to attack rolls. You can still be flanked for the purposes of SA and similar.
}{If an enemy scores a critical hit against you, deals sneak attack damage, or uses a similar crit-tastic ability against you and you live, then on the next turn on your first attack against them if you successfully hit them it is an automatic critical hit.
}{Every time you hit an enemy in melee you heal 4 hp.
}{Any time you are attacked in melee you may make an AoO against the enemy that attacks you. This AoO is resolved before the attack and may prevent the attack from happening if it causes the enemy to be unable to attack you in melee.
}{Any time you make an AoO you may also headbutt the enemy as a free action. This is not considered an attack and simply adds damage equal to a gore attack of a creature of your size +2 times your strength modifier.}

\label{comm:feat:unorthodoxfighter}{}\babfeat{Unorthodox Fighter (Combat)}
{You fight in an unexpected manner that confounds your foes.
}{You take no penalty for using improvised weapons. Additionally, while climbing, you retain your Dex bonus to AC.
}{When charging, you do not provoke attacks of opportunity. You can also move through any square occupied by a foe.
}{You gain a Climb and Swim speed of 20 feet, with all associated bonuses. You also gain a +3 bonus to hit and +1 Dodge bonus to AC when fighting while climbing or swimming against a foe who lacks the relevant movement form.
}{You gain a +2 to hit and damage with improvised weapons. Additionally, any foe struck by a hard improvised weapon you wield must make a Fortitude save against being Dazed for one round. If the weapon is flexible, they must make a Reflex save against being Entangled for two rounds. The DC is 10 + 1/2 your level + your Strength modifier.
}{Your Climb and Swim speeds increase by 30 feet, and you deal bonus damage equal to +2d6 plus your Dexterity modifier when using these movement forms against someone who lacks them. Your Dodge bonus to AC increases to +3, and you can make an additional 5' step each turn in such environments.}

\end{multicols}