\begin{multicols}{2}

\hypertarget{feat:weaponrighteousdestruction}{}\babfeat{Weapon of Righteous Destruction [Combat]}{

Your hands make whatever is being held by them holy and on fire. For some reason this doesn't make them melt or burn up.}{

Whatever weapon you are wielding is considered Magical (+1/3 bonus/level) in addition to any other properties that it has. Your unarmed attacks, even if not proficient, count for this effect.}{

The above, Flaming weapon.}{

The above, Holy instead of Flaming.}{

The above, Sun weapon, Fort save. (BoG)}{

The above, Vorpal weapon (BoG).}

The following feats from the Tome of Fiends are now also [Celestial] feats, and you don't pick up fiendish traits for taking them as a [Celestial] feat:

Breath Weapon 

Elemental Aura 

Extra Arms 

Extra Summons 

Greater Teleport 

Harmless form 

Large Size 

Huge Size 

Heighten Spell Like Ability 

\descfeat{Product of Celestial Dalliance[Celestial]}{One of your recent ancestors was an celestial Outsider or from a good-aligned plane. Maybe your parents play it off as a virgin birth, maybe your dad became a Saint.}
You may take any [Celestial] feat, Resistance 5 to Acid, Cold, Electricity, the Angel, Archon, Eladrin, or Guardinal subtype, and a Smite Evil attack usable at will that does bonus damage equal to 1/2 of your strength modifier.

\featname{Wings of Good [Celestial]}{}
You gain wings and a fly speed equal to double your base land speed with good maneuverability that requires special armor to stay aloft. These must be feathery or energy-based.

\end{multicols}