\classname{Hellwalker}
\vspace*{-8pt}
\quot{``What terrors do you think I have not already seen?"}

Life in the Lower Planes is generally nasty, brutish, and short, and it is only the strongest survive long enough to learn the mysteries and unique properties of these locales. The Hellwalker is one such individual. Trained in the Lower Planes and weaned on the taint of evil, these solitary hunters roam the Lower Planes, traveling along planar byways and through networks of portals too dangerous or erratic for regular use.

\ability{Requirements}{}
\listprereq
%To qualify to become a Hellwalker, a character must fulfill all the following criteria.
\itemability{Skills:}{Knowledge (Planes) 4 ranks, Survival 8 ranks.}
\itemability{Feats:}{Track}
\itemability{Special:}{Must have visited every Lower Plane, and lived at least one year in the Lower Planes.}
\end{list}\vspace*{8pt}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Hellwalker's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Concentration (Con), Diplomacy (Cha), Handle Animal (Cha), Hide (Dex), Knowledge (geography) (Int), Knowledge (planes) (Int), Listen (Wis), Move Silently (Dex), Profession (Wis), Ride (Dex), Speak Language, Spellcraft(Int), Spot (Wis), and Survival (Wis).}

\ability{Skill Points at Each Level:}{4 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}p{6cm}l}
Level  &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special &Spellcasting\\
1st &+0 &+2 &+2 &+0 &Members Only &+1 spellcaster level\\
2nd &+1 &+3 &+3 &+0 &Craft of the Lower Planes & --\\
3rd &+2 &+3 &+3 &+1 &Free Traveller's Checks &+1 spellcaster level\\
4th &+3 &+4 &+4 &+1 &Craft of the Lower Planes & --\\
5th &+3 &+4 &+4 &+1 &Membership has Privileges, Skill of War &+1 spellcaster level\\
\end{tabular}
\end{small}
\end{table}


\smallskip\noindent All of the following are Class Features of the Hellwaker prestige class.

\ability{Weapon and Armor Proficiency:}{Hellwalkers gain no proficiency with any weapon or armor.}

\ability{Spellcasting:}{At levels 1, 3, and 5, the Hellwalker casts spells (including gaining any new spell slots and spell knowledge) as if he had also gained a level in a spellcasting class he had previous to gaining that level. If the character does not have any levels in any spellcasting classes when he takes his first level of Hellwalker, this class feature gives him levels in Sorcerer spellcasting.}

\ability{Members Only(Ex):}{At 1st level, a Hellwalker attunes himself to energies of the Lower Planes. While on the Lower Planes, he counts as if under the effect of a \spell{Attune Form} spell. If not currently on a Lower Plane, he may cast \spell{plane shift} at will, with his target destination being a location on a Lower Plane.}

\ability{Craft of the Lower Planes:}{At 2nd and 4th level, the Hellwalker learns the martial or mystical arts of the Lower Planes. He can choose to gain a +1 to spellcasting level, or a +1d6 to sneak attack dice (but only if he has sneak attack dice from another class), or a [Combat] feat (which he qualifies for). Once chosen, this ability cannot be changed.}

\ability{Free Traveller's Checks(Sp):}{At 3rd level, the Hellwalker has so attuned himself to the energies of the Lower Planes that he can call this energy to himself, ferrying himself with it when the energy is strong and drawing it to him when it does not exist. While on a Lower Plane, the Hellwalker can cast \spell{greater teleport} at will as a spell-like ability, with a limit of 50 pounds over his own weight. While not on a Lower Plane, a Hellwalker can cast \spell{planar bubble} on himself, at will, and he can choose to be a native of any one Lower Plane (chosen each time this effect is used) for the purposes of this spell.}

\ability{Membership has Privileges(Sp):}{A Hellwalker of 5th level has tapped into a rarely used and poorly maintained network of portals dotting the Lower Planes, and he can manipulate those portals for his own purposes. The Hellwalker may cast \spell{gate} (travel version only) as a spell-like ability once per day. Unlike a normal \spell{gate}, only living creatures and attended objects may pass through this gate. This ability can only be used if at least one side of the gate is on a Lower Plane.}

\ability{Skill of War:}{At 5th level, the Hellwalker's Base Attack Bonus increases by 1 permanently.}
