\section{Character Backgrounds}
\vspace*{-10pt}
\quot{"I... I'm a fighter. I stab people. In the face."}

D\&D is a cooperative storytelling game, and we would hope that the stories it generates will be worth retelling again and again. In the interest of that actually happening, it is imperative that each and every point of view character in the story (that is, the Player Characters) be interesting. To be interesting, a fictional character really only has to have three things: An interesting motivation, an interesting schtick, and an interesting set of adventures. The schtick of the character is generally going to be handled by a character's class levels and equipment and is really up to the game mechanics themselves to generate -- ideally the classes contained in this writing will cover that. Interesting adventures are the game itself and hopefully involve challenges only barely overcome and dastardly deeds thwarted in the nick of time -- and this falls largely upon the DM to properly gauge the talents of the PCs and provide challenges that can be bested by the skin of the teeth. But the character's motivation, their backstory, really comes from the player's own mind. That's something that the player really needs to bring to the table on his own lookout.

A character with an interesting backstory is fundamentally better for the story than one without. And while it is true that the DM's world is going to highly flavor it (sorry, there are no elven maidens in those mountains!) the fact remains that the player is pretty much going to get what he puts into this. And yet, while the story is frankly going to be somewhat uninteresting if the players don't put some effort into their backstories, putting effort into anything is... well... effort. If people don't get some tangible effect from putting in that effort, they are quite likely to just not do it at all.

So here's what we're going to do: we're going to make some minor character advantages accessible only by writing yourself a character background. Then, when your character has a simple set-piece introduction, you get a tangible bonus that isn't especially game breaking. Note that we don't expect, or even want your character's background to be 7 pages of narrow font before the beginning of the first game. In fact, we probably want it to never get that long. This is a cooperative storytelling game, in D\&D you tell the story with the input of the other players and the DM. If you just want to write the story of an awesome character without the input of other players -- don't play D\&D at all. You really can just type up a story and either submit it for publication or hide it in your diary all emo style as your relative shyness dictates. So no, we want your character's background to be short, but we need it to be there. The kind of thing that a character might actually be able to relate in a one-paragraph info-dump in a book without causing the reader to skim. Normally, a character gets one background. This is as much to keep character background from filling up the world as anything else.

\medskip\descfeat{Amnesia}
{Sometimes a player is really lazy or cannot think of a backstory.}
\textbf{Effect:}{ None. If you're too lazy to think of a damned backstory, you get nothing at all. If the DM is feeling generous or vindictive, she can have things gradually get surreal on you like a David Lynch extravaganza. In doing so, you'll gradually find out that you actually have a backstory, and all the perks and flaws of whatever it is.}

\medskip\descfeat{Apprenticed}
{You learned from the best. Or maybe not the best. But you learned from a successful adventurer, and that's pretty good. Maybe they were your parents, maybe your parents saw fit to hire you on to a master wizard.}
\textbf{Effect:}{ Hide, Spot, and Spellcraft are class skills for you. That's how people stay alive in the adventuring business, after all. You probably know some adventurers, and that means that they'll show you all the tricks like how to identify objects or scribe spells for free, how to turn artifacts into artifacts you want, and how to spend planar currency.}

\medskip\descfeat{Experimental Stock}
{You, or your parents, were experimented upon by one of the many mad arcanists that dot the D\&D landscape. Maybe they were members of the dreaded Mad Wizards Guild that claims responsibility for Gulguthhydras and Perytons. Maybe it was another group. You might not even know.}
\textbf{Effect:}{ You have a positive, if really messed up looking trait grafted into you. You either have a natural weapon, or your natural armor bonus is increased by 1, or you have low light vision. But you also have some bad trait, like a 5' reduction in speed, or a flipper hand, or a -2 to initiative checks. Also, in polite company you might want to cover up your eyestalk. The ladies do not find it your most attractive feature.}

\medskip\descfeat{Hero of the Peasants}
{You're the third son of a poor woodcutter or something. Maybe your father remarried and your new mother hates you. Whatever. The point is that you come from an exceedingly poor background, and your plucky spirit and do-gooder nature propels you forward to make a difference in the world.}
\textbf{Effect:}{ It's not that you're too lazy to pick starting equipment it's that... OK, you're too lazy to pick out starting equipment. Believe me, I understand. A Hero of the Peasants character begins play practically naked. Leather armor or functional clothing, a sling, a quarterstaff, 10 copper pieces, and some bread. Have fun with that. But you're just generally kind of awesome. You get a +2 bonus on Survival, Handle Animal, and Sense Motive checks for no reason. And don't forget that you probably have a destiny of some sort, which means that periodically the DM will go off on a tirade about your destiny (this is worth nothing, all D\&D characters have a destiny).}

\medskip\descfeat{Moil Wrought}
{Every setting has some horribly tainted land filled with necromantic power. People who live there become tainted with necromantic power and grow up twisted and evil more often than not. You grew up there too, which means that either you grew up all evil, or you grew up tragically misunderstood, which makes you Good and totally awesome.}
\textbf{Effect:}{ You are damaged by Positive Energy as if you were undead. You are also healed by negative energy as if you were undead. Also, some people find you really creepy and you have a tendency to talk in flat affect like the girl in Aliens.}

\medskip\descfeat{Raised by Owlbears}
{Tarzan was raised by an ape, Mowgli was raised by a bear, Romulus was raised by a wolf, and in the D\&D world your character can be raised by creatures much more exotic. The sky is really the limit here: simply pick some improbable beast and your character was protected and fed as a small child by that beast after she was orphaned or abandoned in the wilderness. While I'd like to think that we've all read enough Burroughs that this story pretty much tells itself, the truth is even more astonishing. This character background has become clich\'ed and we're totally fine with that. You can really have an interesting and memorable character with a clich\'ed backstory and a three sentence intro that ends with "And then I came to this village to reclaim my birthright as a gnome."}
\textbf{Effect:}{ Characters who were raised by Girallon (or whatever) are arbitrarily able to talk to magical beasts and animals as if they shared a language. No one knows how they do it, but they do. Unfortunately, such characters didn't grow up surrounded by humanoid languages, and your only starting language is Common no matter what your Intelligence is.}

\medskip\descfeat{Refugee from The War}
{When the big war came, not everyone was old enough or brave enough to fight in it, and your character was in one of those categories and fled to a new land. The people already living in the new land treated your people poorly and made them live in ghettos with little food and poor access to magical healing. You spent several years living as a pawn in someone else's lands and all you got was a disease. Now you're adventuring, to find a new place where you fit in and possibly get a little vengeance on all those peoples who took time out of their day to screw your people.}
\textbf{Effects:}{ Refugees are exposed to a wide variety of places, dangers, diseases, and people that those who live relatively comfortable lives will never know. In essence, they can be thought of as adventurers already, though they rarely get any rewards out of the deal. A refugee begins play knowing one additional language, and this language need not be an available bonus language for her race. In addition, a refugee may consider Knowledge (Geography) and Sense Motive as class skills for the rest of their lives. A refugee character is missing teeth or has the distinctive circular scars of having survived The Pox.}

\medskip\descfeat{The Resistance}
{Your nation got overrun by someone you didn't like. And those Halfling oppressors (or whatever) went way too far. You were in a cell of revolutionaries dedicated to removing the foreign devils from the lands of your people.}
\textbf{Effect:}{ Those who spent time in The Resistance have a number of contacts and can easily make contacts in new areas. Essentially this means that they get a +2 bonus on Gather Information checks. Members of The Resistance can make disguises out of substandard materials and suffer no penalties while doing so. Of course, The Resistance is a downright cannibalistic organization what with all the time all of the members spend betraying people. Every even modestly successful member is certain to have a wide variety of enemies, and not just from the oppressors they are fighting! Of course, it would be folly to claim that having large numbers of enemies is much of a disadvantage for a D\&D character. I'm more concerned about the fact that you can never really be sure about the loyalty of another person. Not enough to risk sleeping with them anyway.}

\medskip\descfeat{Royalty of a Fallen Nation}
{Welcome to the harsh realities of the Iron Age. If the last hard core member of a noble house dies, there is nothing keeping people from arbitrarily taking all their lands and gold away. Such was apparently the case with your family. When you were young, the last powerful Fighter (or Wizard, or whatever) in your family was slain, and now the only people left in your family with more than a level or two have aristocrat levels. Needless to say, more powerful characters came and took all your stuff. Now you wander the land attempting to gain power and secure your revenge.}
\textbf{Effect:}{ People believe in you for no good reason. Some ancestor of yours was awesome, and people just assume that you'll get the band back together. You get free drinks when people know who you are, and your Leadership value is increased by +2. People will also offer you assistance and otherwise try to get on your good side. Of course, your family's enemies will send ninja and assassins to finish off your line (note: this may seem like a disadvantage, but it's really not -- you're a D\&D character so you are going to get into fights all the time, the fact that it's ninja attempting to erase your family name is just flavor). And of course, not everyone liked the way your family did things, so sometimes people are going to spit on your horse or in your burritos.}

\medskip\descfeat{Slave of the Hobgoblin Clans}
{The Hobgoblin Clans take slaves every generation, and the children of those slaves are also slaves, but also members of the clans, and they can potentially be promoted within the clan to the point where they aren't even a slave anymore. You may have done that. Or you may have simply run away and escaped Hobgoblin society to become an adventurer.}
\textbf{Effect:}{ You speak Goblin. You also speak any other language you know with a Goblin Accent that makes Dwarves distrust you. If you ran away from the Hobgoblins, there may be a group of them out looking for you who will start adventures for you. If not, then you are still part of the Hobgoblin clans and there will be Hobgoblin plothooks that will draw you into adventures. Of more importance, perhaps, is the fact that you've grown up your whole life among Hobgoblins, and have a +2 racial bonus to Move Silently (yes, that's a racial bonus, so it doesn't stack with the racial bonus you get from actually being a Hobgoblin). Also, Listen is a class skill for you no matter what you do.}

\medskip\descfeat{Street Rat}
{You grew up on the hard end of the streets. The part where kids are total jerks and sometimes the wererats just make one of your friends disappear, and no one else seems to care. You had to lie and steal just to survive, man.}
\textbf{Effect:}{ You have Bluff and Sleight of Hand as class skills no matter what you do. You don't catch normal diseases because you've already had them all. You get a +2 bonus on handle animal checks with street animals like dogs, rats, and pigeons. Also, you have a small shell that a girl gave you when you were twelve. You think she's dead, but really she's been turned into a wererat, so when eventually you meet again it'll be traumatic and you might have to kill her. Or maybe you'll be able to convince her to turn away from Team Monster and live happily ever after.}

\medskip\descfeat{Veteran of The War}
{There was a great and terrible war that wracked the lands, and you fought on one or more sides of it.}
\textbf{Effect:}{ Veterans have proficiency with 3 Martial weapons and one armor type. Veterans who belong to a class that already has martial weapon proficiency begin play with proficiency in 3 Exotic weapons appropriate to the lands upon which the battles raged. Veterans also have nightmares sometimes and talk about The War more than is perhaps strictly required.}

\medskip\descfeat{War Profiteer}
{The War came... and that spells P-R-O-F-I-T. Hoo boy! Maybe you just came from a Goblin family and you really like this sort of thing, maybe you consider yourself a visionary who can see through to a new economic theory based less on gold and more on value. Whatever, you've sold people daggers to cut themselves out of snare traps, and you're proud of it.}
\textbf{Effect:}{ Appraise and Search are class skills for you no matter what you do. Also, you're a jerk. Your personal weapons and armor start masterwork at no cost.}
