\classname{Adept [NPC]}
\vspace{-8pt}
\quot{``The acolytes of the college of sorceries will not allow an outsider to see the Necromancer.''}

\desc{The worlds of D\&D have a multitude of world altering magicians who slay dragons with their mighty magics and transform the very fabric of history and reality with their minds. But while these characters are often the primary focus of the D\&D game, the fact remains that magic is an extremely palpable and utilitarian force in the D\&D world, and the vast majority of those who use it are not actually capable of performing such awesome displays of magical prowess. These are the Adepts -- the people who wield sorceries in a manner that is entirely unlikely to get their names told in lasting song and story.}

\desc{Adepts in the Game:  Adepts aren't playable as PCs. They lack the depth and tactical versatility to be an interesting character and they are not powerful enough to pull their weight in any real adventuring setup. They have a CR equal to half their Adept level and don't get multiclassed with real classes at all. In order to keep this from being potentially unbalanced, we strongly suggest that Adepts show up in groups. So while a 4th level Adept is nominally a CR 2 opponent, he's not really a good challenge for a 2nd level party. But 2 of them are an appropriate challenge for a 4th level party. And that's really what the Adept is for -- showing up in groups and getting smacked around anyway.}

\ability{Hit Die:}{d8}

\ability{Class Skills:}{The Adept's class skills (and the key ability for each skill) are Balance (Dex), Climb (Str), Craft (Int), Handle Animal (Cha), Intimidate (Cha), Knowledge (Any, Int), Profession.}

\ability{Skills/Level:}{2 + Intelligence Bonus}

\begin{table}[htb]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level &Base Attack Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+0 &+2 &Replaceable, Elemental Attack\\
2nd &+1 &+0 &+0 &+3 &Dangerous Magic\\
3rd &+1 &+1 &+1 &+3 &Versatile Magic\\
4th &+2 &+1 &+1 &+4 &Defensive Magic\\
5th &+2 &+1 &+1 &+4 &Specific Magic\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Adept class.

\ability{Weapon and Armor Proficiency:}{An Adept is proficient with all simple weapons, as well as Light Armor.}

\ability{Replaceable:}{Adepts represent the faceless hordes of assistant spellcasters, acolytes, and cultists. They are intended to be easy to use, and relatively easy to replace. Instead of worrying about the feats that an Adept has, simply give Adepts +1 to the damage of their magic powers for each feat they would be eligible for.}

\ability{Elemental Attack (Sp):}{Depending upon what school of magic or cult they belong to, the Adept may use one of a number of different energy types. Necromancers and Death cultists use Negative Energy, Fire Adepts and Pyromancers use Fire, and so on. Each Adept has an elemental attack which does one kind of energy damage chosen when the Adept is created. It does a d8 of damage to a single target within Medium range and allows a Saving Throw of the \textit{target's} choice to halve the damage. The Save DC is either Intelligence, Wisdom, or Charisma based depending upon what the precepts of the group happen to be. This is a spell-like ability, but it has Somatic and Verbal Components anyway (no Arcane Spell Failure though). Energy types are chosen from the following list (though nothing prevents unique cults from having Adepts which use more obscure energy types):}

\listone
	\item Negative Energy
	\item Fire
	\item Electricity
	\item Acid
	\item Cold
	\item Force
\end{list}

\ability{Dangerous Magic:}{2nd level Adepts have magic that causes a dangerous side effects on those who fail their save against the effect and take at least one point of damage. The effects are based on what kind of magic is being used:}

\listone
	\item \ability{Negative Energy:}{Targets who fail their save are \condition{frightened} for one round.}
	\item \ability{Fire:}{Targets who fail their save are \condition{on fire} until they are put out.}
	\item \ability{Electricity:}{Targets who fail their save are \condition{stunned} for one round.}
	\item \ability{Acid:}{Targets who fail their save will take damage again next turn (save for half), and will continue to take damage every round until they make a save or they are washed off with alcohol.}
	\item \ability{Cold:}{Targets who fail their save are \condition{slowed} for 10 rounds.}
	\item \ability{Force:}{Targets who fail their save are pushed back a number of 5' squares equal to the bonus damage the Adept has from lost feats, minus one square for every size category the target is larger than Medium.}
\end{list}

\ability{Versatile Magic:}{3rd level Adepts can use their choice of two different energy types, which are still both selected when the Adept is created (the original and the extra energy type).}

\ability{Defensive Magic:}{4th level Adepts use magic defensively somehow. All allies within 10' of a 4th level Adept have a +2 Resistance Bonus to Saving Throws and a +2 Deflection bonus to AC.}

\ability{Specific Magic:}{5th level Adepts no longer allow their target to select the Saving Throw type they make against their Magic. The Adept selects one save type (Fort, Reflex, or Will), and all targets must make that saving throw type against their Elemental Attacks regardless of whether that's a good thing for them or not.}

\ability{Trading Out Adept Levels:}{Adept levels aren't capable of doing anything good. If for some reason an Adept became a named character, he becomes a member of a real character class. That is, simply trade levels of Adept for levels in a real class that has a casting or spell-like abililty progression.}
