\subsection{25 Video Game Magic Items} \label{comm:25videogame}

Note: if I list something as 15,001 GP, that really just means "You can't buy it. You might find one however, or go for a crazy quest or something." 

\begin{multicols}{2}

1. Geo Pyramids - Disgaea

These strange objects are a true mystery. Some believe they are made by druids wishing to alter the very world they walk upon, whereas others believe they just grow. It looks like no-one will ever be able to figure it out.

Price: 15,001 GP
Appearance: A coloured, crystal-like d4, basically. About 1' tall.

Effect: Each pyramid grants a different effect, however it always extends to all creatures in a 30' radius of the pyramid (including itself). Multiple pyramids with a shared area grant all effects.

Red: Every round, all living creatures in the area take damage equal to their HD as blood seems to burst from their body towards the pyramid.

Blue: Dimensions and reality flicker around the pyramid, allowing everyone in the area to Dimension Door to anywhere else in the area as a free action once per round.

Green: Pulses of magical energy emanate forth, causing people to blink in and out of reality. All attacks, spells and effects have a 50 percent miss chance.

Yellow: Energy crackles, randomly enhancing the power of attacks. Any critical threat is automatically confirmed, for maximum damage. 


2. Rocket Punch - FF7

Presumably crafted at the request of an insane monk, this gigantic boxing glove has a rather special property: whenever it is worn, the wearer may fire their fist at opponents, taking no damage as the arm always returns, resealing itself to the joint.

This allows all unarmed/monk attacks to be made as ranged attacks, with 20' range increments.

Price: 10,000 GP


3. Cauldron - FF7

It is apparent that these cauldrons were not merely crafted, but are instead traditional cooking/brewing pots that were corrupted, tainted in poisonous swamps and affected by wild magic. Though small enough to fit in one's hand - shrunk through magical means - they can cause a world of trouble for foes.

Price: 15,001 GP

Effect: If it is filled with water, and then heated for ten minutes, the contents are transformed into a thick, inky gunk. This may be hurled at an enemy within 20' as a ranged touch attack. If it hits, they must make a Fortitude save, with effects based on how well they roll:

40+ No Effect
37-39 Deafened for 1 minute
35-36 Unable to speak for 3 rounds
32-34 Blinded for 3 rounds
30-31 Fatigued until rested
27-29 Confused for 1 minute
25-26 Stunned for 3 rounds
22-24 Nauseated for 1 minute
20-21 Affected by Black Lotus Poison
<20 Afflicted with Devil Chills


4. "Magic Wand" - Makai Kingdom

Plenty of people wield wands. Those wands, however, look like sticks. In essence they ARE sticks, merely sticks that are filled with magic. Perhaps as a sick joke, someone created a new, special type of wand. With any luck it was made by a young girl, and not a grown man.

Price: 15,000 GP exactly

Appearance: A 2' long, 1" diameter stick, pink in colour, with a winged red heart at the end. Small ribbons flow from the heart, and it radiates magic.

Effect:
There are several uses of this wand.
1. It can cast the Shadowspray spell at will, except spraying brightly coloured ribbons.

2. As a standard action at will, it can fire a stream of exploding pink hearts, functioning as a Scorching Ray (CL 11) spell. The target(s) must also, if hit, make a Will save (DC 10 + half the user's level + her Charisma modifier) or be Charmed for 1 minute.

3. It may cast Hypnotic Pattern once per hour.


5. Variable Blade - Shadow Hearts 3

This magical item is merely a sword handle. However, the true magic lies within what can be attached to it: a saw, a cactus, a swordfish or a street sign. Any will do, though they always transform slightly to properly fit, gaining magical properties.

Price: 15,000 GP

Saw: This counts as a +1 Wounding Fleshgrinding Falchion. Nothing particularly fancy. It also ignores the hardness of wooden items.

Cactus: This counts as a +1 Greatsword that deals bludgeoning and piercing damage. Additionally, any target struck takes 2d6 desiccation damage and must make a Fortitude save (DC = total damage taken) or be sickened for one minute (this doesn't stack up to nausea or anything). It can also be used to drain up to ten 5' cubes of water at a time, storing them indefinitely.

Swordfish: This counts as a +1 Dancing Rapier, and additionally, allows one free feint to be made per round as the swordfish squirms about. It adds 2d6 Sneak Attack damage.

Sign: Amusingly, this sign is changed to say "Warning: this sign has sharp edges that can cause painful lacerations." It counts as a +1 Wounding Scimitar, and can also be used to deal non-lethal bludgeoning damage without penalty. If the sign is clean, anyone struck must, on the following turn, make a Fortitude save (DC = damage taken) or take another 10 points of damage through blood loss. If it is not clean, then they must instead save against contracting Filth Fever.


6. Bio-Force Gauntlet (the BFG) - Doom

This is an enormous gauntlet that has to be strapped to the arm, weighing it down somewhat. It provides a -1 Armour Check Penalty and 5 percent ASF all on its own. This gauntlet has an enormous emerald at the end, above the hand, that pulses with power.

Price: 15,000 GP

As a standard action it may be activated, and a location within 100' designated. It crackles with energy, but nothing happens until the following round, at which point an immense burst of green energy is released. This energy explodes at any designated point within 100' into a 30' burst. All in the area take 10d6 Force damage (Ref half, DC = 10 + 1/2 the wielder's Hit Dice + wielder's Dex modifier). Additionally, for reasons unknown, anyone in the original designated area takes 5d6 automatic Force damage. The two locations can be one and the same, and the damage stacks.


7. Judgement Ring - Shadow Hearts

This ring, when worn, seems to be fairly ordinary. It really comes into play when the wearer starts performing actions in combat, however.

Price: 3,000 GP, +3,000 GP for each +1 bonus applied

The Judgement ring provides no actual benefit in and of itself. Instead, it has a number of floating +1 bonuses that can be reassigned as a Swift action. These can be added to:
*BAB (the actual BAB, not just an attack bonus)
*Damage (all attacks, 1d6+1 damage per +1)
*Caster Level (all effects)
*Save DCs (all effects)
*Critical Threat Range (all attacks)

A DC 30 Abuse Magic Device check can fool the device into thinking it has 1 extra bonus point above what it actually has. Failure results in being caught out and punished by the ring, resulting in no bonuses for the round.


8. Technique Manuscript - Pokemon

These are a collection of secret writings containing ancient techniques... well, some aren't that ancient, actually. But they're still useful, and that's what's important. Due to the magical way these are written, it takes about a day of proper reading and practice to master the teachings, at which point magic causes the technique to bind to you. Thus, these are single-use items that grant a permanent ability.

Even if multiple abilities could be taught, any one person can only benefit from a given TM number once.

Price: varies

TM 1: Combat Knowledge
-Gain a bonus [Combat] feat.
-Price: 15,001 GP

TM 2: Skilful Reserves
-Gain a bonus [Skill] feat.
-Price: 15,001 GP

TM 3: Arcane Manipulation
-Gain a bonus [Meta-magic] feat.
-Price: 15,001 GP

TM 4: Odour Sleuth
-Gain the Track ability
-Price: 7,500 GP

TM 5: Body Slam
-All of your unarmed/natural attacks deal +1d6 damage
-Targets must also make a Fort save at the end of your turn if struck
-The DC is 10 + 1/2 your level + your Str
-Failure results in paralysis for 2 turns
-Price: 15,001 GP

TM 6: Grass Knot
-You may cast Entangle as a Spell-like ability at will
-You may also cast Wall of Thorns as a Spell-like ability once per minute
-Price: 6,000 GP

TM 7: Draco Meteor
-Special: Only available to Dragons (the type) or Dragon-blooded (the subtype)
-Once per hour you may charge up a Draconic meteor storm.
-You must spend one full round building up power, becoming flat-footed.
-If you do not use the ability on your next turn, you lose the charge.
-When used, it casts a Twin Meteor Storm, Twin Comet and Iceburg.
-Afterwards, you become Exhausted
-Price: 15,001 GP

TM 8: Flame Thrower
-You gain a 1d4+1 rounds breath weapon. It is a 30' cone of Fire.
-The DC is Con-based, and it deals 1d6 Fire damage per level (Ref half)
-Failure causes the target to catch fire, suffering 2d6 damage per round
-Price: 12,000 GP

TM 9: Sucker Punch
-You gain +3d6 Sneak Attack.
-This stacks if you already possess any.
-Price: 15,001 GP

TM 10: Sing
-You can use the Bardsong ability 1/day as a level 1 Bard
-If you have bard levels, you gain 2 extra uses of your Bardsong
-Price: 15,001 GP

TM 11: Rage
-You can Rage as a level 2 Barbarian, but lose any fast healing when Raging
-If you have Barbarian levels, merely add +2d6 Rage dice
-Price: 15,001 GP

TM 12: Mega Punch
-You gain 1 Fighting Style, like a Monk
-If you are a Monk, it upgrades to a Master Fighting Style
-Price: 15,001 GP

TM 13: Return
-This ability requires you to have a morale bonus of some kind
-Pick the highest one you have (attacks, saves vs Fear, whatever)
-1/hour, you can apply this ability to one attack or damaging effect.
-You apply the morale bonus to the attack roll/saving throw DC
-It also deals extra damage equal to 2d6 per point of bonus
-Price: 10,000 GP



9. Psypher Weapons - Odin Sphere

Weapons get made out of all kinds of crazy shit. Some people make them out of steel, whereas others think that isn't enough and use adamantine, or mithral, or Baatorian green steel. Some like killing werewolves and devils enough to make them out of a soft metal like silver. Yet more decide the only good material is diamond, "the second-hardest metal" or Dragonforce, "the hardest metal".

But if you get someone clever and good at making things, as well as good at stealing from the lands of the dead, you get soul-crystals that get forged into Psypher blades. Maybe they're not that sharp, but they will steal your soul.

Price: 15,001 GP or making your way into an underworld, fighting swarms of monsters, slapping the piss out of Hel (or another random evil deity) and stealing a chunk of crystal.

Game effect:
A Psypher weapon (must be bladed or piercing) is always at least a +3 weapon, straight out of the forge. You can cast GMW to increase this, you can improve it even, but they're never less. Every time it delivers a killing blow to a creature with a soul inhabiting its body (enjoy arguing with your DM), the soul is absorbed by the blade. This causes it to glow slightly. It can hold up to 20 souls at once, the glow becoming brighter each time.

While a soul is held inside it, they cannot be raised or resurrected. If the soul is consumed for an ability, it would take a Miracle to ever find the soul again.

For every 5 souls contained within, the bonus improves by +1 and it deals an additional d6 damage on a successful hit.

5 souls may be consumed by the blade, depleting its reserves, to do one of the following:
*Grant Fast Healing equal to your Hit Dice for 1 hour
*Cast Ethereal Jaunt with a caster level equal to your hit dice
*Planeshift the wielder to any plane they choose
*Grant a Haste effect for one hour
*Create a burst of light, dealing 2d6 bullshit damage per level of the wielder to all (except the wielder and individuals chosen by them) within 15' feet. A Reflex save (the DC is Charisma-based) halves this.


10. Chaos Emeralds - Sonic the Hedgehog

Chaos Emeralds are, first and foremost, emeralds. They are never smaller than the fist of a halfling, and never larger than the rest of a halfling. They sparkle with incredible green light that shows the power contained within.

Another noteworthy feature is that they are, as the name suggests, Chaotic. They are created in Limbo or similar planes, and made from Raw Chaos. These actually utilise powers, however.

Price: 15,001 GP or Raw Chaos and the assistance of a Green Slaad.

There are a number of different effects to be gained by carrying these emeralds around. Each one does something different. Note that all powers immediately end if the holder loses possession of the emerald - they needn't actually hold it, it just needs to vaguely belong to them, and they must be the last to have touched it.

*Immortality: the holder never ages, and does not need to eat, sleep, drink or breathe to survive. They also gain Damage Reduction 10/- and Fast Healing 10.

*Invisibility: the holder is naturally invisible from this point on, and can see invisible creatures as well. Just to be tricky, they can activate a Mirror Image effect once per hour, with a caster level equal to their hit dice. The images are not invisible, so actually draw attention towards you, but if someone can see naturally invisible things, it means they might not hit you.

*The Power of Life: The emerald works as a phylactery, allowing the owner to be restored to life as close to it as possible 2d12 hours after being killed, unless it is stolen. They may also cast True Resurrection, Awaken Animal, Awaken Plant and Awaken Construct each once per day. These effects are permanent.

*Time: the holder has a permanent Haste effect, and can cast Slow as a supernatural ability at will. They are immune to ageing effects and any other time-based powers (such as Slow, Timestop or Phane powers, even the "blasts of raw time").

If one person gathers all four emeralds and sacrifices at least 50,000 GP worth of magical rings (of any individual value - they can totally use 25 free wishes for 25 rings of Protection +1), they become "all-powerful".

The ritual takes one hour to perform, and for the next 24 hours (during which time it cannot be performed again) they are immune to all forms of damage, including nonlethal damage, instant death, ability damage/drain or level drain. This cannot in any way be extended past the 24 hour duration. Furthermore, they gain a 250' fly speed (Clumsy) and their land speed is tripled. Their very touch deals 10d6 Fire damage, and they glow with golden light as their footsteps leave glowing magma and a whirl of chaotic energies. If even a single Chaos Emerald is stolen from them during this time, the effect ends and they are instantly slain, imploding as their soul transforms into a new lower level of Limbo (how low can you go?) or random-encounter-filled corridor in Pandemonium. 



11. True Runes (spellcasting items) - Suikoden

There are various "True Runes" floating around - legendary glass orbs containing magical sigils of power. Usually they are very well-guarded. There are three in particular that we will cover, because I haven't played much of Suikoden V and haven't played I, III or IV.

Price: 15,001 GP

Bright Shield Rune: This glows a brilliant green, and grants a +5 Deflection bonus to AC when held. Additionally, there are several spells it can cast:
At Will - Cure Serious Wounds, Mass Cure Light Wounds, Daylight
1/hour - Telekinetic Sphere, Mass Rage, Mass Cure Moderate Wounds
1/day - Heal, Forcecage, Sunbeam

Dark Sword Rune: This pulses with dark light, stinging the flesh of the wielder but granting a permanent Sadism effect. Additionally, there are several spells it can cast:
At Will - Inflict Serious Wounds, Mass Inflict Light Wounds, Bull's Strength
1/hour - Finger of Death, Harm, Masochism
1/day - Wail of the Banshee, Chained Disintegrate, Black Blade of Disaster

Blue Moon Rune: This rune has a faint blue glow, but there is nothing tranquil or faint about its effect. It binds to the owner if touched, and after that only removing the body part or a Wish can separate them. If it binds to someone, they immediately become a vampire, with all the benefits and drawbacks. If it is removed, they must make a DC 30 Fortitude save (using their old Constitution score, hit dice etc.) or die. If they survive, they return to normal.


12. Painkillers - Odin Sphere

Painkillers are good. These ones are excellent. Little magical pills filled with secret ingredients (rumour has it carrots and wolfbane are involved) and treated with magic, they can help dull the pain - and damage - of future injuries.

Price: 5,000 GP

Effect: once consumed, a painkiller lasts for five rounds. During this time, all damage is halved and you are immune to non-lethal damage and actual "Pain" type effects.


13. UFO-Yoink - Makai Kingdom

This most strange of devices was made to assist thieves. Presumably. It is shaped like a saucer, except tall, and with little glowing windows on it. It appears that occasionally, very small faces appear, similar to bodaks.

Price: 10,000 GP
The UFO-Yoink has to be wielded in one hand. As an attack action, it can be hurled within 30 feet. A ranged touch attack must be made. If it succeeds, one option may be selected:

*A little mechanical arm-claw extends and steals one non-worn item from the target. A worn item may be stolen with a Sleight of Hand check (DC 20 + BAB of the target).

*It grows, and captures the target within itself. The target is then damaged, taking 1d6 points of damage, plus sneak attack damage (if the wielder has any). They then emerge prone and shaken (for one minute, in the case of being shake), with no memory of what happened. If a player says "Roll for anal circumference", everyone else may punch them. Hard.

*One spell slot is stolen by the claw-grabber. For a spontaneous caster, it is simply an un-used slot (of the highest level available), and one spell they know of that level (thief's choice). It cannot be cast for one minute, or until cast by the thief, whichever happens first. For a prepared caster, one of their highest-level prepared spells is stolen. At any given time, they may have a number of stolen spells equal to their Charisma modifier. 


14. The Upgraded Shotgun - Resident Evil

This resembles a crossbow. Indeed, in some capacity it IS a crossbow, although a large, magical one with multiple bolts fired at once. It seems to have been designed for the slaying of undead.

Price: 15,000 GP, Special Ammunition: 600 GP each

This +1 crossbow is rather special. Firstly, any bolt fired from it does double damage (just the bolt itself, not extra damage dice from added effects). This becomes triple damage on a critical hit. Also, any bolt fired may threaten a critical hit against undead, although it can only ever threaten against them on a natural twenty. Critical hits with it are maximised against the undead.

It can hold up to 18 bolts, and it takes a standard action to load three in (or a move action if you have Rapid Reload). It fires three at a time as an attack action, and to re-cock it, ready for firing, only takes a Swift action (or a free action once per turn if you have Rapid Reload) to pump the slide (like a shotgun).

The special bolts that can be purchased for it are specially made, and as such take a -2 penalty to hit if fired from any other crossbow. They are +1 Undead Bane bolts with built-in acid flasks in the tips. Therefore, striking an enemy also affects them as though they were hit by the flask, and missing their AC but hitting their touch AC causes them to still be hit by the flask.

Additionally, a CL 10 Fire Trap is cast upon the hollow, acid-filled bolt heads, causing any hit by them (even if only the acid hits them) to take 1d4+10 Fire damage.


15. Ashbringer - WoW

This sword is a legendary weapon, made from the shard of a godlike creature from a far-off plane, and designed with the purpose of destroying undead, reducing them to a pile of ash.

Price: 15,001 GP or a piece of a god

Firstly, this is a +5 Undead Slaughtering Falchion.
The Slaughtering property is a unique one: it effectively is a super-powered Bane property, counting as though it were +5 better and dealing an additional 5d6 damage.
So against undead, it is a +10 Falchion that deals 5d6 extra damage to undead.

Additionally, once per day, it may be infused with brilliant energy, hitting an undead creature with a Heal effect (CL 15, Cha-based DC).

Note: A sufficiently bad-ass evil spell-caster can corrupt this. If you're Evil (and really hardcore about being evil), and preferably undead, you can perform a ritual of defilement, turning it into a corrupted Ashbringer.

It works exactly the same, except instead of being Undead Slaughtering, it is Humanoid (all) Bane, and the "Heal (target: Undead)" ability is changed to "Harm (target: living creature)". 


16. Blade of the Kingdom Heart - Kingdom Hearts

Some people like to make weapons with really stupid designs. This is a classic example, as someone figured a key would make a good blade. At any rate, this sword... axe... key... thing is a decent weapon, especially when additional devices are added to it like a keyring.

Price: 12,000 GP

The Keyblade itself is only a +2 Scimitar, nothing more. However, it has a special clasp on the handle for amulets to be attached to. This effectively lets the wielder wear a second amulet. Alternatively, a ring could be attached, allowing a third ring to be worn. There are also specific keyrings just for the Keyblade:

Keyring of Sharpness: This makes the blade Keen, and costs 10,000 GP

Keyring of Ghost Hunting: The Ghost Touch property is added, at the cost of 10,000 GP

Fire Materia Keyring: This adds 1d6+BAB Fire Damage to all hits, and allows the wielder to cast Scorching Ray and Fireball each once per day (CL = level, Cha-based DC). Creating one requires the soul of an Efreeti, so costs 15,001 GP.

Ice Materia Keyring: This adds 1d6+BAB Cold Damage to all hits, and allows the wielder to cast Chill Metal and Shivering Touch each once per day (CL = level, Cha-based DC). Creating one requires the soul of a White Dragon, so costs 15,001 GP. 


17. Bunny Girl Outfit - Dragon Quest

It... is a bunny girl outfit, as one might find in certain establishments that cater to gentlemen. If you know what I mean. They boost certain types of magic, as well as helping the wearer to look Va-Va... VOOM!

Price: Thankfully over 15,000

This takes up the armour item slot, as well as the head item slot. It increases the DCs of any Charm, Dominate or Fascinate effects by +2 when cast by the user, and the targets, if they save, must still save again on the very next round, or else they suffer one Suggestion of the caster's choice.

Once per hour, the wearer may fire a "Sexy Beam", named only because of the outfit. It is in fact a ranged touch attack as a Supernatural ability, to the range of 60 feet, dealing 2d6 Fire damage per level.

If the wearer spends three consecutive rounds dancing, then at the end they may make a Perform (Dance) check. All designated targets within 30 feet must make a Will save (DC = Perform check) or be subject to Otto's Irresistible Dance until the wearer stops dancing.


18. Fossilised Amber - Pokemon

Sometimes, things die out and are never seen again. Granted, in D&D-land it's rare, but still, it happens. Luckily, they sometimes become fossilised, DNA remaining in Amber. This can totally be Resurrected into your very own loyal steed that won't just get killed every time something attacks you.

Price: 15,001 and the cost of a Resurrection on top of that.

It's a lump of amber, with something remaining. Not much, mind you. So it's a real surprise when it transforms into a loyal critter! This becomes a flying stone dragon of sorts, the legendary Aerodactyl. There are probably others out there with other creatures, too.

Aerodactyl (Huge Dragon (Earth))

Str 30 Dex 10 Con 30 Int 06 Wis 08* Cha 10
*Wis increases by 1 every week for 6 weeks.

Speed: 30'
Fly: 100' (clumsy)
Burrow: 60'

Init: +0
HP: 10d12+100 (165)
AC: 23 (-2 size +15 natural)
flat 23, touch 8

Fort +17
Ref +7
Will +6

BAB/Grapple: +10/+28

Attack: Bite +18 (4d6+10)
Full Attack:
Bite +18 (2d6+10)
2 Claws +18 (1d8+5)
2 Wings +18 (1d8+5)
Tail +18 (2d6+15)

Reach: 10' (15' for tail and bite)

Feats:
Multi-attack, Improved Multi-attack
Improved Natural Attack: Bite, Heighten Breath (up to +10)

Special:
Natural Weapons count as stone for overcoming DR
Fast Healing 5
DR 10/Adamantine
Immune to Disease, Poison, Electricity, Magical Sleep & Magical Paralysis
Blindsense 120'

Breath Weapon 1/d4+1 rounds:
60' cone of Fire, 10d8 Fire damage, Ref half (DC 25)
Failed Save: Keep burning until put out, 2d6 per round + panicked

Ancient Power (Su):
1/minute, can telekinetically launch up to 3 chunks of rock/stone within 100 feet. These are launched as ranged attacks, and, if at least as large as a Medium character, deal 10d6 damage each.
Furthermore, upon activation, there is a 10 percent chance that Aerodactyl will become stronger for 3 rounds, gaining +4 Strength, +6 Natural Armour and Immunity to all negative conditions (harmed only by actual damage).

Hatred (Ex):
Aerodactyls hate all dinosaurs and primeval creatures. They gain a +2 to hit and damage them in combat, as well as doubling their critical threat ranges, however if such a creature is in sight it must make a Will save (DC 15 + half the dinosaur's HD) or focus on attacking it, ignoring any commands. It can save again every 3 rounds, or when the opponent dies/flees.


19. Tome of Eternal Darkness - Eternal Darkness

This book contains the writings of a madman, a lunatic who was revealed secrets of the creatures that lie beyond the far realm - and that's the nicest possibility of its origins. Some say it was dictated by the outer gods themselves, some believe aboleths or mind flayers wrote it (but they are always blamed for these things), and yet more put it down to reality creating it as a container for all that should not exist.

Price: 15,001 GP and your very sanity.

Just possessing the book is problematic enough. Although the whispered secrets do confer complete alertness, granting 120' blindsense and the inability to be surprised, monsters do seem drawn towards it. This might seem like a disadvantage, but really, it gives the DM an excuse to have your 4 level-appropriate encounters per day actually seek you out.

Opening it requires a Will save, DC 25. On a failure, you take 1d4 points of Wisdom damage and are shaken for the rest of the day. If successful, you can read up to ten of the fifty pages. Only one attempt at reading may happen each day.

Benefits are gained based on how many pages are read (you accumulate them as you go).
10: Your type changes to Aberration simply by reading the texts. You gain a Mental Taint effect as though gaining a Sphere. On the plus side, you become immune to Confusion and can cast Greater Dispel Magic as a supernatural ability once per 3 rounds.

20: You are permanently displaced in space, like a Displacer Beast. Additionally, any time you take more than a quarter of your maximum HP in damage, your skin bursts open to unleash a Hellwasp swarm controlled by you. This swarm dissolves into goo after one minute if not killed beforehand.

30: You gain Fast Healing 5, and both Positive and Negative energy heal you. You gain a Physical Taint effect as though taking a Fiendish feat.

40: Once per day you may summon a Pseudonatural or Half Farspawn creature with a CR less than your level. It lasts for 1 hour or until dead. You develop a Mental Taint effect as though gaining a Sphere.

50: You are no longer what you used to be. You gain immunity to fear and critical hits, and suffer no effect from venturing into the Far Realm. You also permanently lose 2 points of Wisdom; however, you become immune to any further Wisdom damage, drain or loss.


20. Sacred Tome - Makai Kingdom

After the last book, this one is fairly tame. It has many benefits, as it can not only tell you information about the past and future, it can also change both of these things. Also, to own a Sacred Tome is to be an Overlord of a Netherworld.

Price: 15,001 GP

Firstly, by dint of owning it you are now an Overlord. You get your very own demiplane, one mile in each direction from the centre point, to rule over. You can create a Gate to it by concentrating for one full round. Returning requires opening a Gate on the other side, and it leads back to the last place you entered from.

If you abuse this for 1-encounter work days, monsters will likely break in to fight you just because it's what they do. But that's okay, their deaths will help it to grow - 100 feet in radius per soul it absorbs in this manner. It starts off fairly bleak and desolate, but slowly develops trees, vending machines and the like.

Additionally, the Tome can cast the following Spells:
Wish: making a Wish reduces all of your ability scores by 2 for 24 hours. At the end of this time, they pop back to normal.
Augury: Caster Level 20
Speak With Dead: Caster Level 20
Commune: Caster Level 20

Finally, if you die in possession of it, you can permanently possess the Tome, using it as a receptacle to cast Magic Jar once per day, CL 20.


21. Drill Emperor - Disgaea 2

This is one of the mightiest of all spears. as it does not just stab people. Oh no. The head of this spear is larger than many, and a very smooth, finely pointed cone. It is made of Baatorian green steel, with a diamond tip, and whirls around at a rapid pace.

Price: 15,001 GP

First of all, it's a +1 Greatspear. That is actually all, at the beginning. However, being an item from the Disgaea universe, it possesses a portal to the Item World, allowing you to leap in and fight floors filled with level-appropriate monsters. There tend to be 2-3 encounters per floor, with 20 floors total, and each floor cleared grants bonuses.

Also, you can find more nice loot inside the Item World. Better still, at the 20th level there is a single boss, as well as some annoying Geo-Pyramids, and another Drill Emperor so you can do it all again.

Level 1: +1d6 damage
Level 2: Wounding
Level 3: Returning
Level 4: +2 enhancement bonus to Strength
Level 5: +2 Weapon
Level 6: +2d6 damage
Level 7: Can be thrown as a 30' line, making an attack against all in area
Level 8: Fleshgrinding
Level 9: When fleshgrinding, nails the target to the spot (cannot move)
Level 10: +3 Weapon
Level 11: +3d6 damage
Level 12: Targets struck must make a Fort save (Str-based DC) or be nauseated for 1 round
Level 13: +2 enhancement bonus to Dexterity
Level 14: +4 enhancement bonus to Strength
Level 15: +4 Weapon
Level 16: +4d6 damage
Level 17: Cast Lightning Bolt 1/minute, add 2d6 electricity to weapon damage
Level 18: Ghost touch, Wounding improves to 2 Con damage
Level 19: User gains a 30' (average) fly speed
Level 20: +5 Weapon, anyone hit falls prone (no save)

I might do more of these items later, because the concept is cool. But you know that if I do, I'll be covering the "Love Spanking" (glove), "Sexy Panties" (armour) and "Supremacy" (weakest sword ever). 


22. Prinny - Disgaea

No-one seems entirely sure whether they should be called items or not. At the end of the day though, you can have them made, they're objects that hold souls, and... they're not exactly living creatures. Not quite, anyway.

At any rate, they look like stuffed toys that are vaguely penguin-like. With peg-legs, pouches and little bat wings. They have a tendency to shout "Dood!" a lot, and aren't too bright. Also, they explode when thrown.

Price: 15,001 GP (or 1,000 GP and the soul of an unsuccessful Evil creature)

A prinny is essentially a construct that follows you around. It is a Small creature with a move speed of 20 feet, and possesses the following attributes:

14 10 -- 04 04 04

AC: 20 (+1 size, +9 natural armour)
HP: 5d10+10 (37)
Init: +0
BAB/Grapple: +3/+1
Fort +4
Ref +1
Will -2

Immune to mind-affecting effects

Knife Attack +6 (1d4+2, 19-20 x2)
*Slashing Frenzy (Full attack) +4/+4/+4 (1d6+2, 19-20 x2)

Explodes when thrown: 30' radius, 10d6 Hellfire damage, Ref half (DC 20)

Healed not by positive energy, but by Repair spells. Fabricate will work as a True Resurrection.

---

If you place your own soul into one, for whatever reason, then you gain the physical ability scores (and nonability score), size, Slashing Frenzy ability (all attacks are at -2, make two bonus attacks, weapon size improves by 1), type, immunity and speed. Your hit dice all change to d10s but you receive 10 bonus HP. You still explode when thrown. The body can be used as a receptacle if you can cast Magic Jar. Should the prinny be thrown while someone is jarred inside it, then you then gain their body permanently, and they are forced to be the (dead) prinny.

Life sucks like that. 


23. Wand of Sheep Strike - Worms Armageddon

To many people, this would seem like a large stick, smoothly shaved and polished. A regular wand or staff. However to those with magical capacity, it has a sheep-like aura surrounding it.

Price: 15,000 GP
Once per day, the mighty powers of the Sheep Strike may be invoked. Four 30' bursts within 100 feet are struck, exploding for 20d6 Fire damage, Ref half (Int-based). The areas continue to burn for 3 rounds afterwards, dealing 10d6 Fire damage to anyone dumb enough to wander into the area (no save). Furthermore, extremely bad-tempered sheep are released - one in each exploding burst. They rampage, attacking anything except the wielder of the wand, however they disappear after 3 rounds.

The sheep count as Reikar (MM3), except gain immunity to Fire.


24. Companion Cube - Portal

The companion cube is a large box, about as big as a halfling. It is made of a sturdy metal, and is extremely useful as a step-ladder. It will not speak to or threaten to kill you. It is a comfort in a harsh, cold world.

Price: 500 GP

The companion cube mostly works as a handy indestructible object to stand on or push places. However, it also provides comfort, in the form of a +2 bonus on saving throws against Fear effects, and if held for three consecutive rounds, removes any active Fear effects or morale penalties.


25. Amulet of the Elements - Story of Thor

This golden amulet was crafted by Efreeti thousands of years ago as an experiment. They had based much of their research on the Gems of Elemental Control, but perfected this new creation. Unfortunately, they are hard to make, and require rare components such as the souls of elementals.

Price: 15,001 GP

This can be, as a standard action, aimed at a source of elemental power within 30 feet to summon an obedient elemental. This can only be performed once per hour, and the elemental lasts for ten minutes.

A fire: Large Fire Elemental (Huge if the wearer is 15th level or more)
Water: Large Water Elemental (Huge if the wearer is 15th level or more)
A plant: Assassin Vine (with 2 hit dice per level of the wielder)
Any reflective surface except water: Invisible Stalker
\end{multicols}{2}
