\renewcommand{\minitabular}[1]{\begin{tabular}{p{0.25in}p{2.9in}} #1\\ \end{tabular}\\}
\newcommand{\skillarmor}[7]{\noindent \minitabular{\multicolumn{2}{l}{\textbf{#1}}}  \minitabular{\multicolumn{2}{l}{\parbox{3.3in}{\small #2}}} \minitabular{\multicolumn{2}{l}{\small \textbf{#3}}} \minitabular{\raggedleft\textbf{\small 4:} & {\small #4}} \minitabular{\raggedleft\textbf{\small 8:} & {\small #5}} \minitabular{\raggedleft\textbf{\small 13:} & {\small #6}} \minitabular{\raggedleft\textbf{\small 18:} &{\small #7}}\vspace*{-6pt}}
\newcommand{\attackarmor}[7]{\noindent\minitabular{\multicolumn{2}{l}{\textbf{#1}}} \minitabular{\multicolumn{2}{l}{\parbox{3.3in}{\small #2}}} \minitabular{\multicolumn{2}{l}{\small \textbf{#3}}} \minitabular{\raggedleft\textbf{\small +1:} & {\small #4}} \minitabular{\raggedleft\textbf{\small +5:} & {\small #5}} \minitabular{\raggedleft\textbf{\small +10:} & {\small #6}} \minitabular{\raggedleft\textbf{\small +15:} &{\small #7}}\vspace*{-6pt}}

\section{Armor}

The sad fact of the matter is that in the D\&D rules, there are really only 3 kinds of armor most people ever care about: Chain Shirt, Breast Plate, Full Plate. That's not only dumb, it's also a shame, because the D\&D world is potentially full of all kinds of crazy armor that is both awesome to look at and totally flavorful for all kinds of characters.

\subsection{Fantastic Armors}
\vspace*{-8pt}
\quot{``I know it's stupid looking, but I get the best possible protection from having this duck sit on my head, so I'm going to let it do that."}
/
People in Fantasy settings wear all kinds of crazy crap and call it protective gear. That's fine; we even encourage that sort of thing. What we don't encourage is people mixing and matching their metaphors. And yet, by having people keep track of separate materials and armor types -- that's exactly what happens. We've all seen Lord of the Rings, we know what Mithril Armor is supposed to be like, and what it is not supposed to be like. And making your plate mail out of Mithril isn't what things are supposed to look like -- you're supposed to get Mithril Chain. When was the last time anyone used Mithril Chain?

The fact is that materials naturally lend themselves to certain kinds of armor. Just as braided twigs are always going to make Wicker Armor and cured cow skin is always going to make Leather Armor, there's just a certain way that armoring yourself with Dragon Scales or Cloyster Shells is going to work. For the vast majority of materials, there is a known ``right way" to wear it for protection and the only real choice is wearing more of it or less.

\subsection{Armor Non-Proficiency}

Every armor, shield, or clothing has an Armor Check Penalty, though that penalty is sometimes -0. A Masterwork version has the magnitude of its Armor Check Penalty reduced by 1 (to a minimum of zero). If you are wearing armor or using a shield which you are not proficient in, the armor check penalty of that armor or shield is counted as 4 higher. If you are using an outfit with a total armor check penalty that is greater than your Base Attack Bonus, you can only move at 2/3 speed. If your outfit has an armor check penalty that is more than 4 more than your BAB, you can't run. If your outfit provides a total armor check penalty that is 10 or more than your BAB, you can only stagger around.

Just because you're proficient in heavy armor doesn't mean that you're familiar with every piece of heavy armor you encounter. Mechanus Armor is very protective, but chances are slim that a character has actually encountered this equipment before. In general, when a character runs into some new armor (as they will from time to time), they will continue to be non-proficient with it for about a day as they ``break it in". So to make full use of your new Chitin Carapace, you'll need two things: Medium Armor Proficiency, and a day to practice with your new bug exoskeleton.

\subsection{Armor Penalties}

Armor you wear has an Armor Check Penalty, and armor you aren't proficient with has an Armor Check Penalty that is 4 points higher. Your Armor Check Penalty is applied to any Balance, Climb, Escape Artist, Jump, Sleight of Hand, or Tumble checks you make. Your Swim Checks are penalized by double your Armor Check Penalty. If you cast arcane spells in armor which has an armor check penalty, your spells with somatic components have a 5\% chance of failing for every point of armor check penalty.

Armor you wear also has an Armor Stealth Penalty. This number is reduced by 1 for every two points your BAB exceeds the Armor Check Penalty of the Armor. The Modified Armor Stealth Penalty is applied as a penalty to any Hide and Move Silently checks you make.

Finally, Armor has a maximum Dexterity Bonus that you can take advantage of while wearing that armor. That is, if your armor has a max dex bonus of +4 and you have a +5 dexterity bonus, then you may only apply a +4 bonus towards your armor class while wearing that armor. Just like stealthiness, however, a more experienced warrior has an easier time defending himself in heavier armor. The Max Dex Bonus of an armor is increased by 1 for every two points your BAB exceeds the Armor Check Penalty of the armor.

\newpage

\begin{center}
\begin{footnotesize}
\noindent \begin{tabular}{|lrrrrr|}\hline
\parbox[c][12pt]{1pt}{}\textbf{Nonarmors}&AC&Max Dex&ACP&ASP&Price\\\hline
\parbox[c][12pt]{1pt}{}Camouflaged Clothing&+0&+8&+0&+0&1 gp\\
Fancy Clothing&+0&+6&$-1$&$-2$&30 gp\\
Functional Clothing&+0&+8&+0&+0&1 gp\\
Magic Clothes& +2&+9&+0&+0&8,000 gp\\\hline
\parbox[c][12pt]{1pt}{}\textbf{Light Armors}&AC&Max Dex&ACP&ASP&Price\\\hline
\parbox[c][12pt]{1pt}{}Brigandine&+5&+3&$-4$&$-3$&125 gp\\
Chain Shirt&+4&+5&$-2$&$-4$&100 gp\\
Cord Armor&+2&+4&$-1$&+0&20 gp\\
Darkleaf Armor&+4&+6&$-1$&+0&600 gp\\
Gray Armor&+3&+8&+0&+0&1,000 gp\\
Leather Armor&+2&+7&$-1$&+0&15 gp\\
Mithril Shirt&+5&+6&+0&+0&1,000 gp\\
Padded Armor&+1&+8&+0&+0&10 gp\\
Spiderweb Clothing&+4&+6&$-1$&$-1$&300 gp\\
Still Suit&+2&+5&$-3$&$-2$&350 gp\\
Studded Leather Armor&+3&+6&$-1$&$-1$&25 gp\\
Wicker Armor&+3&+7&$-1$&$-6$&15 gp\\
Winter Clothes&+2&+4&$-4$&$-4$&30 gp\\\hline
\parbox[c][12pt]{1pt}{}\textbf{Medium Armors}&AC&Max Dex&ACP&ASP&Price\\\hline
\parbox[c][12pt]{1pt}{}Adamantine Breastplate&+7&+3&$-6$&$-2$&5,000 gp\\
Animal Spirit Armor&+4&+3&$-3$&$-3$&750 gp\\
Bone Armor&+3&+4&$-3$&$-5$&450 gp\\
Breastplate&+5&+4&$-4$&$-2$&200 gp\\
Chainmail&+5&+3&$-3$&$-5$&150 gp\\
Chitin Carapace&+5&+4&$-3$&$-1$&500 gp\\
Dragonscale Shirt&+6&+5&$-4$&$-2$&1,400 gp\\
Elaborate Gown&+1&+3&$-5$&$-8$&300 gp\\
Gith Armor&+5&+4&$-1$&$-5$&900 gp\\
Hide Armor&+3&+4&$-4$&$-4$&15 gp\\
Lamellar Armor&+4&+4&$-4$&$-4$&190 gp\\
Lobster Mail&+5&+2&$-5$&$-3$&350 gp\\
Mithril Suit&+6&+5&$-2$&$-1$&5,000 gp\\
Rime Hauberk&+5&+3&$-5$&$-3$&150 gp\\
Ringmail&+4&+4&$-2$&$-3$&100 gp\\
Scale Mail&+4&+3&$-5$&$-2$&50 gp\\\hline
\parbox[c][12pt]{1pt}{}\textbf{Heavy Armors}&AC&Max Dex&ACP&ASP&Price\\\hline
\parbox[c][12pt]{1pt}{}Adamantine Carapace&+11&+2&$-9$&$-4$&9,000 gp\\
Coral Armor&+5&+2&$-3$&$-6$&1,300 gp\\
Demon Armor&+9&+5&$-10$&$-3$&10,000 gp\\
Elukian Clay Armor&+6&+3&$-4$&$-5$&4,000 gp\\
Dragonscale Suit&+9&+4&$-5$&$-2$&3,000 gp\\
Full Plate&+8&+1&$-6$&$-6$&1,500 gp\\
Great Armor&+7&+2&$-7$&$-5$&1,400 gp\\
Half Plate&+7&+2&$-5$&$-7$&800 gp\\
Hoplite Armor&+6&+1&$-9$&$-5$&500 gp\\
Mechanus Armor&+12&+0&$-8$&$-8$&10,000 gp\\
Silk Steel Armor&+7&+3&$-4$&$-1$&4,500 gp\\
Stone Plate&+10&+0&$-9$&$-11$&1,750 gp\\
Sun Plate&+9&+6&$-10$&$-8$&6,000 gp\\\hline
\parbox[c][12pt]{1pt}{}\textbf{Shields}&AC&Max Dex& ACP&ASP&Price\\\hline
\parbox[c][12pt]{1pt}{}Adamantine&+3&--&+0&+0&2,000 gp\\
Buckler&+1&--&$-1$&+0&15 gp\\
Dragonscale Shield&+3&--&$-1$&$-6$&350 gp\\
Force Shield&+3&--&+0&+0&1,800 gp\\
Mithril Shield&+2&--&$-1$&--&1,020 gp\\
Steel Shield&+2&--&$-1$&--&20 gp\\
Vine Shield&+1&--&$-1$&--&45 gp\\
Wooden Shield&+1&--&$-1$&--&15 gp\\\hline
\parbox[c][12pt]{1pt}{}\textbf{Great Shields}&AC&Max Dex&ACP&ASP&Price\\ \hline
\parbox[c][12pt]{1pt}{}Bone Wall&+3&--&$-10$&$-2$&150 gp\\
Crystal Shield&+3&--&$-3$&$-1$&2,000 gp\\
Ice Aegis&+5&--&$-5$&$-3$&1,600 gp\\
Kappa Shell&+3&--&$-12$&$-5$&500 gp\\
Kite Shield&+4&--&$-5$&$-2$&120 gp\\
Tower Shield&+4&--&$-10$&$-2$&100 gp\\\hline
\end{tabular}
\end{footnotesize}
\end{center}

\newpage

\columnsections
\subsection{Not Armors}
\begin{multicols}{2}
Anything you wear is a form of armor, but anything sufficiently light as to not count even as Light Armor can be worn by characters who lack armor proficiency without suffering penalties.\\




\skillarmor{Camouflaged Clothing:}{Clothes specifically made to blend into the surroundings, whether by making your outline blotchy and incomprehensible, or simply matching the drapes.}
{Hide Ranks Benefit
}{Opponents do not get a +4 bonus for spotting you for knowing what to look for.
}{You may hide while being observed without taking a special action.
}{You gain a +2 circumstance bonus on Hide checks.
}{You gain concealment.
}


\skillarmor{Fancy Clothing:}{It's expensive and it looks it.}
{Bluff Ranks Benefit}
{You receive a +2 circumstance bonus to Diplomacy and Bluff in civilized settings.}
{You may make a Bluff check as a free action to convince a character that you belong wherever you happen to be.}
{You may demand shelter from peasants at any time. No Bluff check required.}
{Once per turn, you may Feint as a free action.}



\skillarmor{Functional Clothing:}{Your outfit is covered in pockets and has many supporting straps designed to distribute weight.}
{Sleight of Hand Ranks Benefit}
{You receive a +2 circumstance bonus to Escape Artist and Sleight of Hand checks.}
{You may Force March for one day without being Fatigued.}
{You may retrieve stored items about your person as a free action.}
{You can carry 50\% more stuff relative to your strength.}



\skillarmor{Magic Clothing:}{Your pants, your shirt, and your socks exude magic. Truth be told, it's mostly your pants.}
{Diplomacy Ranks Benefit}
{You gain a +1 bonus on all Charisma-related checks.}
{You gain a +2 Deflection bonus to AC.}
{You gain a +3 bonus on all Charisma-related checks.}
{You gain a +5 Deflection bonus to AC.}



\subsection{Light Armors}

\attackarmor{Brigandine:}{A chain shirt on top of which has been layered some studded leather. It's like having chocolate and strawberry at the same time.
}{BAB Benefit
}{You are encased in leather and steel and negate the first 5 points of nonlethal damage inflicted on you by any source.
}{You gain DR 5/Piercing
}{You can effectively disguise your armor as functional clothing. You gain a +5 bonus to Disguise checks to conceal your armor.
}{Your Armor check Penalty is halved.
}


\attackarmor{Chain Shirt:}{Interwoven links of the finest steel cover your torso.
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of nonlethal damage inflicted on you by any source.
}{You gain DR 5/Piercing
}{You receive a +2 bonus on any checks to resist grapple maneuvers.
}{Slashing damage from any source is reduced by half.
}


\skillarmor{Cord Armor:}{A series of knots wrapped about your person protect you from incoming attacks.
}{Tumble Ranks Benefit
}{You are encased in cords and negate the first 5 points of bludgeoning damage you take.
}{As an immediate action, you can replace the AC for one attack made against you with the result of a tumble check.  You may use this ability after an attack has hit you, but not before damage has been rolled.
}{You gain a swim speed equal to your base land speed.
}{You may move up to your move speed with a swift action.
}


\skillarmor{Darkleaf Armor:}{This armour, grown rather than made, consists of hundreds of leaves that are as hard as iron.
}{Knowledge (Nature) Ranks Benefit
}{Your armour grows small roots into you, granting you fast healing 1. 
}{You gain DR 5/piercing.
}{You gain hide in plain sight, but only in natural surroundings. 
}{You and your armor are one with nature, letting you move through any natural vegetation (such as a tree trunk
or brambles) as if they were level ground, as long as you end your turn in an unoccupied square. If you end your
turn inside a plant, you are ejected from the nearest open space.
}


\attackarmor{Gray Armor:}{Made from slaadskin, grey armour shifts to anticipate attacks with the power of Limbo.
}{BAB Benefit
}{You are encased in shifting skin and negate the first 5 points of damage from any critical hit or sneak attack.
}{You gain DR 5/lawful.
}{Your armour is so shifty that you negate an amount of damage from any critical hit or sneak attack equal to
your BAB.
}{You are surrounded by a 10ft radius area of Raw Limbo. You automatically succeed on unopposed control checks
over this area, and gain a +4 bonus to opposed control checks. The controlled area reverts to normal once it
leaves the affected radius.
}


\skillarmor{Leather Armor:}{Made from cured cowhide, it's cheap, but does its job.
}{Tumble Ranks Benefit
}{You are encased in leather and negate the first 2 points of bludgeoning damage you take. 
}{You gain fire resistance 5. 
}{As an immediate action, you can replace your AC for one attack with the result of a Tumble check.You may use
this ability after an attack has hit you, but before damage has been determined. 
}{You may move up to your speed as a swift action.
}


\attackarmor{Mithril Shirt:}{The links that make up this chain shirt are woven much tighter and made of mithril.
}{BAB Benefit
}{You are encased in Mithril and negate the first 5 points of extra damage inflicted on you by a critical hit or sneak attack.
}{Your armor moves so easily that you can use the Tumble skill during a charge. 
}{You gain DR 5/bludgeoning and piercing. 
}{You convert an amount of lethal physical damage that you take equal to your BAB into nonlethal damage.
}


\skillarmor{Padded Armor:}{You wear thick cloth padding as protection.
}{Tumble Ranks Benefit
}{You may reroll a failed tumble check when you attempt to move your full speed or through an occupied space.
}{You can gain the benefits of 8 hours of sleep with 7 hours of sleep.
}{As an immediate action, you can replace your AC for one attack with the result of a Tumble check.
}{You may move up to your speed as a swift action. 
}


\skillarmor{Spiderweb Clothing:}{Made of magical spiderwebs by Drow weavers, this magical clothing bursts into flames when struck with direct sunlight.
}{Move Silently Ranks Benefit
}{You gain a +2 bonus on climb and grapple checks.
}{You may pass through web and similar effects without impediment.
}{You are immune to natural poisons.
}{You gain concealment when in natural darkness even when observed with darkvision.
}


\skillarmor{Still Suit:}{A watertight suit envelops your whole body, recycling all of your excretions and protecting you from the heat.
}{Survival Ranks Benefit
}{You do not have to make checks to avoid Heat Exhaustion and Heat Stroke.
}{You have Fire Resistance 5.
}{You do not have to drink.
}{You are immune to Fire.
}


\skillarmor{Studded Leather Armor:}{Leather armor that has been adorned with metal studs to help protect your vitals.
}{Tumble Ranks Benefit
}{Your important bits are protected by metal chunks, allowing you to negate the first 3 points of extra damage inflicted on you by a critical hit or sneak attack.
}{You gain DR 5/piercing.
}{When you deal damage in a grapple, you deal additional damage equal to this armour's AC bonus.
}{You may move up to your speed as a swift action. 
}


\skillarmor{Wicker Armor:}{This armor is made of woven willow branches, and makes you look a bit like furniture with wings.
}{Jump Ranks Benefit
}{You are encased in wood, and gain DR 2/-. 
}{All your jumps are considered to have a running start. 
}{You no longer take falling damage. 
}{Your wooden wings give you a fly speed equal to your base land speed, at perfect manoeuvreability.
}


\skillarmor{Winter Clothing:}{Thick clothing that keeps you warm.
}{Survival Ranks Benefit
}{You do not have to make checks to avoid hypothermia or frostbite while in cold areas.
}{You have Cold Resistance 5.
}{You have Cold Resistance 10.
}{You are immune to Cold.
}


\subsection{Medium Armors}


\attackarmor{Adamantine Breastplate:}{
}{BAB Benefit
}{You gain Damage Reduction equal to your Base Attack Bonus, which is negated by Adamantine Weapons.
}{You gain a +2 bonus on Bullrush checks.
}{You do not provoke attacks of opportunity when charging.
}{You gain 5 points of Energy Resistance to Electricity, Acid, and Sonic.
}


\skillarmor{Animal Spirit Armor:}{Fashioned of the skin of an angry beast, this armor still carries its spirit and will lend you its strength.
}{Survival Ranks Benefit
}{You inflict +2d6 damage while charging.
}{You gain scent.
}{You gain a natural weapon. This is used as a secondary natural weapon, even if you are otherwise unarmed.
}{You may Wildshape into an appropriate mighty beast.
}


\skillarmor{Bone Armor:}{Made from the bones of magical beasts, this armor makes you look the part of a necromancer.
}{Knowledge (Religion) Ranks Benefit
}{You gain Energy Resistance to Positive or Negative Energy equal to the Armor Bonus of the armor.
}{You are ignored by unintelligent undead as if you were undead.
}{Any undead creature you rebuke is controlled.
}{When you kill a living creature, you heal 10 hit points.
}


\attackarmor{Breastplate:}{A solid steel armor underlayed with chainmail, it protects all of your vital bits.
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/critical hits. 
}{You reduce the critical multiplier of any weapons used against you by 1 point, and reduce the bonus damage
dice from sneak attacks and death attacks against you by 2 dice. 
}{You gain DR 10/critical hits. 
}


\skillarmor{Chitin Carapace:}{Made out an Ankheg or something, it's amazingly light and makes you look like a crazy mantis man when you wear it.
}{Climb Ranks Benefit
}{You are ignored by Vermin until you attack them and you cannot be detected by the scent ability of creatures with the [Bug] subtype.
}{You gain a Climb Speed equal to your land speed.
}{You are immune to non-magical poison.
}{You gain a Flight Speed equal to your land speed (perfect).
}


\attackarmor{Dragonscale shirt:}{
}{BAB Benefit
}{Each shirt provides Energy Resistance to a specific Energy type as appropriate to the dragon whose scales formed the shirt. The ER is equal to the Armor Bonus the shirt provides.
}{The Armor Check Penalty of this armor does not apply to Jump checks.
}{You gain a +4 intimidate bonus against Dragons. And a similar bonus to your saving throws against Fear from Dragons.
}{You gain Immunity to the appropriate energy type.
}


\skillarmor{Elaborate Gowns:}{It's a big frilly dress, or a bulky robe, or something else that's expensive and hard to move in.
}{Diplomacy Ranks Benefit
}{You gain a +2 bonus to Intimidate and Perform checks.
}{You can hide weapons of a size up to your own inside your outfit with a normal Sleight of hand check.
}{You gain a +2 bonus to Escape Artist and Sleight of Hand checks.
}{You can cast \spell{sanctuary}, at will, as a sorcerer of your level.
}


\skillarmor{Gith Armor:}{The Gith have mastered the techniques of manipulating Astral Driftmetal and the chaotic stuff of Limbo to make a reasonably lightweight, yet oddly protective garment.
}{Concentration Ranks Benefit
}{You gain a +2 bonus on Concentration checks.
}{You do not suffer any Arcane Spell Failure in this armor if you are proficient with it.
}{You are protected from the harmful effects of Limbo and the Astral Plane.
}{You may \spell{planeshift} to the Astral Plane or Limbo as a standard action.
}


\skillarmor{Hide Armor:}{You wear some other creature as a hat.
}{Survival Ranks Benefit
}{You reek in those animal pants. But you reek like another creature, making you unlocatable by Scent.
}{The DC to Track you is increased by 4.
}{You gain DR 5/Piercing
}{You do not suffer a penalty to your Disguise to emulate other creatures.
}


\attackarmor{Lamellar Armor:}{Small metal or leather plates that are linked together to protect you.
}{BAB Benefit
}{You are encased in laquered wood and steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Slashing
}{You do not take falling damage.
}{Once per round, you can convert an amount of lethal physical damage that you take equal to your BAB into nonlethal damage.
}


\skillarmor{Lobster Mail:}{A living carapace of a deep aquatic design. The engineering style is reminiscent of that of Kwalish, but much sleeker and individualized.
}{Swim Ranks Benefit
}{You can breathe under water.
}{The Armor Check Penalty of this Armor is reduced to zero under water.
}{Each empty hand may be used as a Natural Weapon (Pincher). At Medium size, it does 1d6 damage.
}{You may walk on water, beginning or ending the effect as a free action (or immediate action). You can also \spell{control water} as a standard action. Your ability to use \spell{control water} refreshes when the last \spell{control water} effect ends for whatever reason.
}


\skillarmor{Mithril Suit:}{A full body covering of light metal. Very shiny, and nearly skin tight, the mithril suit is surprisingly protective.
}{Tumble Ranks Benefit
}{Mithril is very light, and its Armor Check Penalty is not applied against your skill checks.
}{You allow no miss chance when averting your eyes from an opponent.
}{Your Commander Rating is increases by 1.
}{When you have concealment, you have total concealment instead.
}


\attackarmor{Rime Hauberk:}{Crystalized water covers most of your body.
}{BAB Benefit
}{You gain Energy Resistance to Cold equal to the Armor Bonus of the Armor.
}{You may produce a pall of frost as a Swift Action that inflicts 1d6 of Cold Damage per round on all creatures within 10 feet of where you were standing, and which lasts 3 rounds.
}{You gain Immunity to Cold.
}{Your pall of frost causes 1d6 of damage for every 2 points of Base Attack Bonus you have.
}


\attackarmor{Ringmail:}{Steel rings are woven flat onto a leather armor backing.
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Piercing
}{You gain a +2 bonus on Disarm checks.
}{You gain a +4 AC bonus against bludgeoning ranged weapons.
}


\skillarmor{Scale Mail:}{
}{Intimidate Ranks Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Piercing
}{You reduce the damage from Falling and Constriction damage by 10 points.
}{You can make an Intimidate check as a Swift action.
}



\subsection{Heavy Armors}

\attackarmor{Adamantine Carapace:}{Made of one of the hardest and most durable known metals, this armor completely encases you.
}{BAB Benefit
}{You gain Damage Reduction equal to your Base Attack Bonus, which is negated by Adamantine Weapons.
}{You gain a +2 bonus on Bullrush checks.
}{You do not provoke attacks of opportunity when charging.
}{You gain 5 points of Energy Resistance to Electricity, Acid, and Sonic.
}


\attackarmor{Coral Armor:}{Made of living Coral, this armor is as dangerous to your opponents as it is protective. All Coral Armor counts as having been made with Armor Spikes (a weapon three sizes smaller than the Armor).
}{BAB Benefit
}{The Armor Check Penalty of Coral Armor does not get applied against your Swimming checks. You gain a Swim Speed equal to your land speed.
}{Enemies you damage with the Coral spikes are poisoned (DC 10 + \half your Level + Con Bonus), initial and secondary damage of 1d3 Dex.
}{You gain a +5 bonus to Hide checks under water.
}{You gain DR 5/Bludgeoning
}


\skillarmor{Demon Armor:}{Crafted from a live Demon, the Demon Armor must be constantly put in its place or it will think itself the master of the Warrior who wears it.
}{Intimidate Ranks Benefit
}{All of your attacks are Evil-aligned.
}{You can see souls, allowing you to see all living and undead creatures within 120' of you, regardless of current illumination or intervening objects.
}{Every time you kill a living creature, you heal 10 hit points.
}{Outsiders with a CR more than 8 less than your level cannot approach within 30 feet of you unless you allow it.
}

\skillarmor{Elukian Clay Armor:}{Made of a strange clay from the Elemental Plane of Water, this heavy suit takes to water like a puppy to a well.
}{Swim Ranks Benefit
}{The Armor Check Penalty of Elukian Clay does not get applied against your Swimming checks. You gain a Swim Speed equal to your land speed.
}{The Armor Check Penalty of Elukian Clay is reduced to zero while you are completely submerged in water.
}{You breathe water as easily as air.
}{As a standard action, you may \spell{planeshift} to the Elemental Plane of Water.
}


\attackarmor{Dragonscale Suit:}{This armor is forged from the hide of a dragon.
}{BAB Benefit
}{Each suit provides Energy Resistance to a specific Energy type as appropriate to the dragon whose scales formed the suit. The ER is equal to the Armor Bonus the suit provides.
}{The Armor Check Penalty of this armor does not apply to Jump checks.
}{You gain a +4 intimidate bonus against Dragons. And a similar bonus to your saving throws against Fear from Dragons.
}{You gain Immunity to the appropriate energy type.
}


\attackarmor{Full Plate:}{Plates of steel, flexible chain armor, and leather straps encase your entire body.
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Critical Hits
}{You negate the first three points of energy damage from any source.
}{Your DR improves to DR 10/Critical Hits
}


\attackarmor{Great Armor:}{
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Slashing
}{You gain a +3 bonus on Intimidate checks.
}{You are immune to fear.
}


\attackarmor{Half Plate:}{A mixture of rigid plates and flexible chain, Half Plate combines protection with flexibility. It is very noisy, however.
}{BAB Benefit
}{You are encased in steel and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/Critical Hits
}{You gain a +2 bonus on Grapple checks.
}{You may make an Escape Artist check as a Swift Action.
}


\attackarmor{Hoplite Armor:}{Oldschool armor made of bronze and layered on in thick sheets all over the vitals.
}{BAB Benefit
}{You are encased in bronze and negate the first 5 points of non-lethal damage from any physical attack.
}{You gain DR 5/critical hits. 
}{Your armour check penalty is halved. 
}{You gain DR 10/critical hits. 
}


\skillarmor{Mechanus Armor:}{A powerful collection of gears and chains that offers the finest protection that the Clockwork Nirvana can devise. Sometimes, a small jet of steam or oil will be ejected for no particular reason.
}{Knowledge (Engineering) Ranks Benefit
}{You gain a +2 bonus to Strength.
}{You are not staggered or unconscious when reduced to zero or less hit points. You still die at -10 hit points, though it is not unknown for the armor to continue fighting for some time after that.
}{You gain DR equal to the Armor Bonus of the armor, which is negated by adamantine weaponry.
}{Your size increases one level, and receive all relevant bonuses and penalties.
}


\skillarmor{Silk Steel Armor:}{Made of an ancient bugbear technique, overlapping plates of steel are held apart by layers of silk and the entire carapace slides virtually without sound. While bulky, this black armor is remarkably stealthy.
}{Move Silently Ranks Benefit
}{You gain a +2 Synergy bonus to Hide checks.
}{You negate 10 points of penalty to Move Silently for moving quickly (so running or fighting suffers only a -10 penalty, moving at normal speed is at no penalty).
}{You negate the first 10 points of Falling damage any time you fall (this does not negate damage caused by something you fall on, such as poison spikes or lava).
}{Once per round, you may attempt to hide while being observed.
}


\attackarmor{Stone Plate:}{Grown or carved from solid stone, this Dwarven armor is amazingly hard to move in, but the protection is amazing.
}{BAB Benefit
}{You are encased in stone and negate the first 5 points of non-lethal damage from any physical attack.
}{You are regarded as a great hero of the Dwarves. Unless you do something hostile, Dwarves will treat you
as Friendly. You also have the Earth subtype as long as you wear this armor. 
}{You are regarded as a great hero of the Dwarves. Unless you do something hostile, Dwarves will treat you as Friendly. You also have the [Earth] subtype.
}{You move through earth and stone as easily as walking upon. You earthglide as an earth elemental creature.
}

\skillarmor{Sun Plate:}{Glorious golden armor forged from Hope and filled with Goodness.
}{Sense Motive Ranks Benefit
}{You radiate light like a \spell{daylight} effect. Undead creatures and Evil Outsiders within this area suffer 1d6 of Light damage each round.
}{Successful Turn checks destroy enemy Undead and Outsiders.
}{You may sprout wings, granting you a Flight Speed of 90' (Good).
}{Once per day, the armor will cast a \spell{heal} spell on you with a Caster level of 11. This is a contingent effect and goes off when you need it to.
}




\subsection{Shields}


\attackarmor{Adamantine Shield:}{A target shield constructed of pure Adamantine, it is nearly indestructible and can be placed between your important bits and deadly weapons.
}{BAB Benefit
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}

\skillarmor{Buckler:}{A small shield strapped to the wrist or forearm used for parrying. It provides no bonuses while you are denied your Dexterity bonus to AC.
}{Balance Ranks Benefit
}{You may use a weapon with the hand using the Buckler, but doing so causes you to suffer a -1 penalty to attack rolls using this hand (including two handed weapons).
}{You gain a +2 bonus to Sleight of Hand or Bluff checks to draw a weapon or feint in combat.
}{You no longer suffer a penalty to attack rolls when using a weapon in your buckler hand.
}{Your shield bonus works against touch attacks.
}


\attackarmor{Dragonscale Shield:}{
}{BAB Benefit
}{Each shield provides Energy Resistance to a specific Energy type as appropriate to the dragon whose scales formed the shield. The ER is equal to the Shield Bonus the shield provides.
}{The Shield bonus of the shield adds to your Reflex saves against Supernatural Abilities.
}{You gain a +4 intimidate bonus against Dragons. And a similar bonus to your saving throws against Fear from Dragons.
}{You gain Evasion.
}


\skillarmor{Force Shield:}{A clear shield made out of pure Force. It cannot be sundered by anything less than a completely arbitrary effect like a Sphere of Annihilation.
}{Spot Ranks Benefit
}{A Force Shield's shield bonus applies against Incorporeal attacks.
}{You gain a +2 Cover bonus to Armor Class from your shield at any time that you are not denied your Dexterity bonus to AC.
}{You gain Energy Resistance against Force Damage equal to the Shield Bonus the shield provides.
}{You can claim \half Cover from your shield at any time that you are not denied your Dexterity bonus to AC. We assume that you'll do that most of the time.
}


\attackarmor{Mithril Shield:}{It's as strong as titanium and as light as titanium. Who are we fooling? This is a great shield.
}{Sleight of Hand Ranks Benefit
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}


\attackarmor{Steel Shield:}{It can be round or square or shaped like something in particular. It's not important, the key is that it's between you and sharp objects and it's made out of steel.
}{BAB Benefit
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}


\skillarmor{Vine Shield:}{A writhing mass of vines extends from your arm and at your direction -- protects you.
}{Knowledge (Nature) Ranks Benefit
}{Your shield is a tripping weapon.
}{Opponents missing you in melee provoke an attack of opportunity from you, but you may only take this attack as a Trip or Grapple attempt.
}{You gain a +2 bonus on Trip and Grapple attempts.
}{You have the Edge on any opponent you attack who has a Dexterity less than your Ranks in Knowledge (Nature).
}


\attackarmor{Wooden Shield:}{Made of wood and held together with bands of steel or strips of leather, a wooden shield makes up in shock absorbance what it loses in resilience.
}{BAB Benefit
}{You can use your shield as a point of leverage, gaining a +2 bonus on Bullrush attempts.
}{Your shield may act as a wedge, providing a +2 bonus on Disarm attempts.
}{You can add your Shield bonus to the DC to grapple you.
}{You can throw your shield, performing any special combat maneuver with a range increment twice your natural reach.
}






\subsection{Great Shields}


\skillarmor{Bone Wall:}{A seemingly random assortment of bones collected into a large shield.
}{Knowledge (Religion) Ranks Benefit
}{You gain a bonus to your Saving throws against death effects equal to the Shield Bonus of this shield.
}{You may cast Necromancy spells without somatic components.
}{You gain Positive Energy Resistance equal to the shield bonus of this shield.
}{This shield provides bonuses to your AC against Incorporeal Touch Attacks.
}


\skillarmor{Crystal Shield:}{A shield crafted out of a single solid crystal. It's transparent, but the refraction of the crystal can make things appear differently on the face of the shield than they are.
}{Spot Ranks Benefit
}{You gain a +2 bonus to any saving throw vs. a spell-like ability.
}{The DC of any spell-like ability you use while using this shield is increased by 1.
}{You may Feint once per round as a free action.
}{You gain Immunity to Gaze Attacks.
}


\attackarmor{Ice Aegis:}{A magically inscribed block of ice shaped into a massive shield.
}{BAB Benefit
}{You gain Fire and Cold Resistance equal to the Shield bonus of this Shield.
}{If the ambient temperature is cold, the shield bonus of this shield is increased by 1.
}{You gain Immunity to Cold.
}{You gain Immunity to Fire.
}


\attackarmor{Kappa Shell:}{Fitting on the back of a character like the Kappa's Shell it is named after, the Kappa Shell provides decent protection for units moving across a dangerous battlefield.
}{BAB Benefit
}{You may use both your hands while using this shield, but your attacks suffer a -2 penalty.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{You cannot be Flanked, except by a Rogue with 4 more levels than you have BAB.
}{You do not suffer a penalty to attack rolls when using both hands.
}


\skillarmor{Kite Shield:}{Shaped metal shields fit easily over a rider and his steed, allowing good protection for mounted troops.
}{Ride Ranks Benefit
}{Your Mount gains the same shield bonus to AC that you gain from this shield.
}{Your Mount gains Evasion.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{Your Mount gains Improved Evasion.
}


\attackarmor{Tower Shield:}{Giant pieces of wood or metal, tower shields offer tremendous protection, but cannot be effectively used while mounted.
}{BAB Benefit
}{You may claim \half Cover at any time, but your own attacks suffer a -2 penalty.
}{You may catch one ranged attack per turn on your shield automatically (the attack misses, whether it was an arrow or a magical ray).
}{You may negate one bite attack per turn from a creature that is at least 2 sizes larger than yourself.
}{If you claim cover from your shield, you suffer no penalties to your attack rolls. So you're pretty much going to have cover all the time.
}
\end{multicols}


\subsection{Necromantic Armors}
\listone
\itemability{Blood steel} Blood steel is steel that has been mixed with the blood of certain powerful creatures, making it redder than normal steel and with unusual properties.

Any armor made of blood steel has an armor bonus two higher. These effects only manifest if the blood steel is allowed to hungrily latch onto its user's flesh, at which point it reduces the bearer’s Constitution by two points. Treat blood steel as normal steel for creatures with no Constitution or creatures protected from this effect.\\

Cost: 1,000 gp for armor or shield.\\

\end{list} 

\normalsections
