\section{[Celestial] and [Fiend] Feats} \label{feats:outsider}

A feat with the [Celestial] or [Fiend] tag can only be taken by a creature who is an Outsider. For this purpose, any creature from any upper plane is a Celestial regardless of its alignment, while any creature from any lower plane is a Fiend regardless of its alignment. Further, any elemental or outsider with a Good alignment is a Celestial regardless of its plane of origin., while any elemental or outsider with an Evil alignment is a Fiend regardless of its plane of origin. The abilities granted by feats with the [Celestial] or [Fiend] tag are Extraordinary abilities unless otherwise stated. A Celestial does not gain a Fiendish trait from taking a [Celestial] feat that also has the [Fiend] tag.

\begin{multicols}{2}

\descfeat{Apprenticeship}
{New Mentor Types for the Lower Planes:}
While the race of a mentor is usually irrelevant, some mentors draw their knowledge and experience solely from their racial heritage and the magical radiations of their home plane. To choose one of these extraplanar mentors, the character must have at least 2 ranks in Knowledge (planes).\vspace*{\baselineskip}

\shortability{Devil:}{A devil mentor is a powerful baatezu from the Nine Hells of Baator that has decided to share its knowledge with a worthy apprentice. An apprentice of this mentor gains an innate understanding of infernal contracts, and may use Knowledge(planes) to influence the attitude of any native of a plane that is aligned to law and evil, or any subject of a calling spell.}
 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Knowledge (any one)\end{list} \vspace*{\baselineskip}

\shortability{Demon:}{A demon mentor is a powerful tanar'ri from the Abyss, and it has forced his apprentices to hide a portion of his power. Once per month, you may use one of its spell-like abilities of a 2nd level effect or less.}
 \vspace*{-\baselineskip}\listone \item Bluff \item Knowledge (Planes)\end{list} \vspace*{\baselineskip}

\shortability{Yugoloth:}{While utterly evil, Yugoloth mentors are honorable in their own way and have been known to train apprentices in the dark arts. Apprentices of these fiends learn the true nature of evil, and may choose to count as evil for the prerequisites of feats or prestige classes, and for magical effects like spells or magic items.}
 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Diplomacy\end{list} \vspace*{\baselineskip}

\shortability{Demondand:}{A demondand mentor is a powerful fiend from Carceri. An apprentice of this mentor learns the arts of punishment at the hands of these extraplanar jailors, and may use Intimidate to influence a creature's attitude to Helpful by accepting a +10 to the DC of the check.}
 \vspace*{-\baselineskip}\listone \item Knowledge (Planes) \item Intimidate\end{list} \vspace*{\baselineskip}

\descfeat{Attune Domain}{You incorporate the workings of a divine domain into your magic.}
\shortability{Prerequisite:}{Caster level 1+, Must follow a god or philosophy consistent with the chosen domain.}
\shortability{Benefit:}{Choose a domain when this feat is selected. Every spell from that domain is considered to be on your spell-list for any spellcasting classes you happen to have. These spells are considered to be spells known at the level they appear in the chosen domain. These spells are cast (and prepared, if appropriate) as normal for your class.}
\shortability{Special:}{You may select this feat multiple times, its effects do not stack. Each time you may select a new domain, so long as your chosen god or philosophy can incorporate all of them. As usual, your DM must approve any god or philosophy. You may not have more than three attuned domains or spheres together.}


\descfeat{Attune Sphere}{You incorporate the workings of a sphere into your magic.}
\shortability{Prerequisite:}{Caster level 1+, Must have bled from a wound inflicted by an outsider with access to the chosen sphere.}
\shortability{Benefit:}{Choose a sphere when this feat is selected. Every spell from that sphere is considered to be on your spell-list for any spellcasting classes you happen to have. You are considered to know each of those spells at the level they appear in the chosen sphere. These spells are cast (and prepared, if appropriate) as normal for your class.}
\shortability{Special:}{You may select this feat multiple times, its effects do not stack. Each time you may select a new sphere. You may not have more than three attuned domains or spheres together.}

\descfeat{Blood War Sorcerer}
{As a battle magician in the Blood War, you've learned killing arts that would amaze common spellcasters.}
\shortability{Prerequisite:}{Blood War Squaddie, Caster level 5, must have fought in the Blood war for one year.}
\shortability{Benefit:}{Each time one of your spells successfully damages a creature with Spell Resistance, they take a cumulative -1 penalty to SR. This penalty is reduced by 5 for every day of rest, and can be otherwise healed as ability damage. In addition, you may cast any spell that requires you to be of a fiendish race.}

\descfeat{Blood War Squaddie}
{Due to your time during the Blood War, you've been tainted, honed, and hardened by the horrors you've seen.}
\shortability{Prerequisite:}{Knowledge(planes) 2, must have fought in the Blood War for one year.}
\shortability{Benefit:}{You are immune to fear, and actually gain a +2 Morale bonus to hit, damage, and saves when exposed to an enemy's fear effect (this bonus lasts one minute). In addition, you may treat any fiendish Exotic weapons as martial weapons.}
\shortability{Special:}{This can only be taken at 1st level.}

\begin{small}
\begin{tabular}{ll}
Spell   &CR\\
Summon Monster I    &2\\
Summon Monster II   &4\\
Summon Monster III  &6\\
Summon Monster IV   &8\\
Summon Monster V    &10\\
Summon Monster VI   &12\\
Summon Monster VII  &14\\
Summon Monster VIII &16\\
Summon Monster IX   &18\\
\end{tabular}
\end{small}

\featname{Breath Weapon [Celestial], [Fiend]}
\shortability{Prerequisites:}{Character level 6.}
\shortability{Benefits:}{Choose a spell-like ability you possess with a duration of Instantaneous: this ability can be used as a Supernatural Breath Weapon with an area equal to a 10' per spell level of the spell-like ability used. Each use of this ability expends one use of the spell-like ability. Each time this breath weapon is used, it cannot be used again for 1d4 rounds.}

\descfeat{Broker of the Infernal}{Dues to the study of the Infernal laws, you have learned to harness the powers of True Names in your summoning magic.}
\shortability{Prerequisites:}{Knowledge (Planes) 10, must be able to cast a spell of the [calling] subtype}
\shortability{Benefits:}{When you possess the True Name of a creature, you may summon it with a Summon Monster spell. The version of the summon monster spell used must equal half their CR, as shown below. For all effects, this spell is a summoning spell, and functions as if the creature were a summoned monster, but if killed the creature is dead as normal and cannot be summoned again until it is returned from the dead.}



\descfeat{Carrier [Fiend]}
{You are a carrier of a dangerous disease, though you are immune to its effects}
\shortability{Prerequisite:}{Must have one level of a Fiend class.}
\shortability{Benefit:}{When you gain this ability choose a disease with a DC equal to the DC your disease would have(Half HD + Con mod). You disease does ability damage or special effects equal to the disease chosen. Once chosen, your disease type does not change, but your disease DC will increase when your HD or Con modifier increase. Unlike a normal disease, this is a supernatural disease, and its initial effects occur immediately.}



\descfeat{Constricting Fiend [Fiend]}
{Your legs merge into a long tail, and you gain the ability to squeeze the life from your foes.}
\shortability{Prerequisites:}{Character level 6.}
\shortability{Benefits:}{On a successful Grapple check, you can choose to do a 4d6 Constricting attack as a normal attack. Due to you change in form and body type, you can only use nonstandard-sized armor.}



\descfeat{Craft of the Soulstealer}
{By studying stolen souls, you have learned to fully tap their power for your magical creations.}
\shortability{Prerequisites:}{Three or more item creation feats, caster level 6.}
\shortability{Benefits:}{When creating magic items, you can bind a soul into the item by adding the actual receptacle of the soul into the item. In many cases, this is a gemstone that is added as decoration. A single soul is worth GP equal to its CR square, times 100 for magic item creation purposes, and is worth 1/5th of that value in XP. Only one soul may be added to an item, and any extra gold or XP provided by the soul above the cost of the item is wasted. Also, if the creature whose soul was taken had spell-like abilities, these spells may be used as prerequisites for the item's creation. Any item created by this art radiates the alignment of the soul inside the item, and it also radiates strong evil. If the receptacle containing the soul is removed from the item, the item is destroyed and the soul is released.}



\descfeat{Devour the Soul [Fiend]}
{As a fiend, you gain nourishment from devouring souls.}
\shortability{Prerequisite:}{Must have one level of a Fiend class.}
\shortability{Benefit:}{Each time a soul is consumed (either a receptacle or petitioner), you regain HPs equal to 10 times its CR, and heal ability damage or drain equal to its CR. Souls eaten in this fashion cannot be restored from the dead until you are killed.}

\descfeat{Dominions of the Infernal}
{When you call, armies of those you have defeated are forced to answer in service.}
\shortability{Prerequisite:}{Must have the signature \spell{summon} ability of the great Fiendish Houses; must have a Leadership score.}
\shortability{Benefit:}{If you successfully \spell{summon} a fiend with a CR less than your level, more than one creature may appear. The weaker the creatures are, the more are summoned.}

\begin{small}
\begin{tabular}{ll}%
CR  &Number Appearing\\
Level-2   &d2\\
Level-3   &d3\\
Level-4   &d4\\
Level-5   &d6\\
Level-6   &d8\\
Level-7   &2d6\\
Level-8   &2d10\\
Level-9   &3d10\\
Level-10  &7d6\\
Level-11  &3d20\\
Level-12  &7d12\\
Level-13  &d100\\
Level-14  &6d20\\
Level-15  &25d6\\
Level-16  &10d20\\
Level-17  &40d6\\
Level-18  &60d6\\
Level-19  &80d6\\
\end{tabular}
\end{small}

\descfeat{Elemental Aura [Celestial], [Fiend]}
{Your close relationship with primal elemental forces has manifested in a damaging aura.}
\shortability{Prerequisites:}{Character level 7, must have a subtype granting immunity to a form of elemental damage.}
\shortability{Benefits:}{Choose one of your elemental subtypes granting immunity to a form of elemental damage. You radiate a damaging aura that does 4d6 of elemental damage of that type to any creature within 10' of you at the beginning of your turn.}

\descfeat{Extra Arms [Celestial], [Fiend]}
{You have more arms than normal.}
\shortability{Prerequisite:}{Character level 6 (per extra pair).}
\shortability{Benefit:}{You have two extra humanoid arms. Each arm has your full strength and dexterity.}
\shortability{Special:}{You may take this feat more than once, its effects stack. You must have a minimum of 6 levels for each iteration of this feat (so a 12th level character may have 2 sets of extra arms).}

\descfeat{Essence Gourmand [Fiend]}
{Even among soul-eating fiends, you are a accomplished eater.}
\shortability{Prerequisite:}{Must have one level of a Fiend class, Devour the Soul.}
\shortability{Benefit:}{Whenever you devour a soul, you gain knowledge of your victim's personal history and important memories (not skills, levels, feats, etc), in addition to the normal effects. You also may cure any one status effect.}

\descfeat{Extra Summons [Celestial], [Fiend]}
{You may use your Summoning ability two extra times each day}
\shortability{Prerequisite:}{Must have the signature \spell{summon} ability of the great Angelic or Fiendish Houses.}
\shortability{Benefit:}{Your \spell{summon} ability may be used two extra times each day (the ability is normally usable once each day, so it could be used for 3 separate chances to conjure an ally.)}

\descfeat{Fiend Cabalist}
{You were trained in the mystic arts by a powerful fiend, and your magical power stems from a dark source.}
\shortability{Prerequisite:}{Caster level 1}
\shortability{Benefit:}{You gain Knowledge(planes) as a class skill, and all of your spells gain the [evil] subtype, and spells you cast and magic items you create radiate an evil aura equal to the strength of their normal magical aura. Any spells you cast that already have the Evil subtype gain a +4 caster level.}
\shortability{Special:}{This can only be taken at 1st level.}

\descfeat{Fiendish Invisibility [Fiend]}
{You cannot be seen.}
\shortability{Prerequisite:}{Character level 6}
\shortability{Benefit:}{You are naturally invisible, as with the spell improved invisibility.}
\shortability{Special:}{Fiendish Invisibility always has a flaw, something that will allow your character to be seen. Examples include:} \vspace*{-\baselineskip}
\listone
    \item\ability{Invisible in Light:}{If you are ever in shadowy illumination, you are visible.}
    \item\ability{Visible by Breath:}{You are only invisible if you hold your breath for 3 rounds first. When you next exhale, you become visible again.}
    \item\ability{Invisible on Stone:}{Your character is invisible when touching the ground. While standing on worked floors or flying, you can be seen.}
\end{list}\vspace{\baselineskip}


\descfeat{Greater Teleport [Celestial], [Monstrous]}
{The extraplanar blood running through your veins allows you to use the signature travel methods of the outer planes.}
\shortability{Prerequisite:}{Outsider, character level 5+}
\shortability{Benefit:}{You may use \spell{greater teleport} at will as a spell-like ability. You may only transport yourself and 50 pounds of carried items.}

\descfeat{Harmless Form [Celestial], [Fiend]}
{You can assume the likeness of a mortal.}
\shortability{Prerequisites:}{Character level 4}
\shortability{Benefits:}{You can Change Shape into a medium-sized Humanoid appearance. You can use this ability to Disguise yourself as other people, and it gives a +10 to Disguise checks as normal. When using this ability, your reflection in mirrors is of your true form.}

\descfeat{Heighten Spell-like Ability [Celestial], [Fiend]}
{You can treat your spell-like abilities as more powerful spell effects.}
\shortability{Benefit:}{When you use a spell-like ability, you may use it as if it were of a higher than normal spell level. You may not raise a spell-like ability to in this fashion to an effective spell-level higher than half your character level.}

\descfeat{Hellscarred}
{Having had your mind or body twisted by the essence of a fiend, you have gained some sensitivity and immunity to their power.}
\shortability{Prerequisites:}{Must have failed a saving throw to a spell or effect associated with a fiend, and cannot be a fiend or have any feats with the [Fiend] subtype.}
\shortability{Benefits:}{If you ever fail a save to a Special attack, Special Quality, or spell of a fiend, you may a reroll that save (once per save). This ability may be used a number of times per day equal to your Charisma modifier (minimum 1).
In addition, you may cast detect fiends as a spell like ability at will. This spell functions as enlarged detect magic (120 foot range), but it only detects the presence of fiends and their magical effects. This effect also cannot determine school of magic, but instead will indicate the race of the fiend (baazetu, tanar'ri, yugoloth, or demondand subtype if appropriate).}

\descfeat{Huge Size [Celestial], [Fiend]}
{Your size increases to Huge.}
\shortability{Prerequisites:}{Character level 10}
\shortability{Benefits:}{If your size would normally be Large without this feat, it increases to Huge (with all the usual changes).}

\descfeat{Large Size [Celestial], [Fiend]}
{Your size increases to Large.}
\shortability{Prerequisites:}{Character level 5.}
\shortability{Benefits:}{If your size would normally be Medium without this feat, it increases to Large (with all the usual changes).}

\descfeat{Memories of Death}
{You retain your memories perfectly after you are slain and brought back from the dead.}
\shortability{Prerequisite:}{Must be a native to the Prime Material Plane}
\shortability{Benefit:}{When you die and are returned back from the dead by any means, you do not lose a level, any XP, or Constitution. Any other penalties associated with returning to life (such as being exhausted or waking up in a new body) are unchanged. Note that this means that you have flawless intelligence as to the alignment of whoever brought you back from the dead.}

\descfeat{Pincers [Fiend]}
{Two of your hands are converted into pincers.}
\shortability{Benefit:}{Each Pincer is a natural weapon, and attacks made with the Pincer are considered to have the Improved Grab ability.}

\descfeat{Poison Sacs [Fiend]}
{One of your natural weapons is envenomed.}
\shortability{Prerequisite:}{Must have one level of a Fiend class.}
\shortability{Benefit:}{When you gain this ability choose any poison in Dungeons and Dragons with a DC equal or less to the DC your poison would have(Half HD + Con mod). You poison does ability damage or special effects equal to the poison chosen. Once chosen, your poison type does not change, but your poison DC will increase when your HD or Con modifier increase.}

\descfeat{Product of Celestial Dalliance}
{One of your recent ancestors was a Celestial Outsider or from a good-aligned plane. Maybe your parents play it off as a virgin birth, maybe your dad became a Saint.}
\shortability{Benefits:}{You may take any [Celestial] feat. Additionally, you gain Resistance 5 to Acid, Cold, and  Electricity; the [Angel], [Archon], [Eladrin], or [Guardinal] subtype; and a Smite Evil attack usable at will that does bonus damage equal to \half of your strength modifier.}
\shortability{Special:}{Can only be taken at 1st level.}

\descfeat{Product of Infernal Dalliance}
{One of your recent ancestors mated with an infernal creature, and now the tainted blood of a Lower Planar creature flows in your veins. Though you can resist the call of your evil heritage, it manifests itself in an inheritance of fiendish power.}
\shortability{Benefits:}{You may take any feat with the [Fiend] subtype. In addition, you radiate faint evil, have either two claws or one bite natural weapon, and have Cold Resistance 5 or Fire Resistance 5. When this feat is gained, you also gain the [Baazetu], [Tanar'ri], [Yugoloth], or [Demondand] subtype.}
\shortability{Special:}{Can only be taken at 1st level.}

\descfeat{Slime Trail [Fiend]}
{Your body secretes a slick mucus that dries quickly in contact with air, but you've learned to use this to your advantage.}
\shortability{Prerequisites:}{Character level 2.}
\shortability{Benefits:}{Your square counts as if the spell grease has been cast in it, and this effect ends when you leave a square and renews itself at the end of your turn. You are immune to this grease effect. You also gain a +4 bonus any checks to escape a Grapple.}

\descfeat{Sphere Focus [Monstrous]}{You can draw on the power of a specific Sphere more easily.}
\shortability{Prerequisite:}{Access to at least one Sphere}
\shortability{Benefit:}{Select a Sphere that you know.  The DC of any saving throw against spell-like abilities from that Sphere increases by 1.}
\shortability{Special:}{You may select this feat multiple times.  Its effects do not stack.  Each time you take this feat, it applies to a different Sphere.}

\descfeat{Spines of Fury [Fiend]}
{Spines cover your body, and you may fire these spine at your enemies.}
\shortability{Prerequisites:}{Character level 3.}
\shortability{Benefits:}{You may fire up to two of your body's protruding spines per round as a standard action. You are proficient in these spines, and they have the same game effects as daggers. You may also remove them and use them as daggers, and they count as your natural weapons for purposes of damage reduction and spell effects. You body has a number of spines equal to twice your character level, and regenerate these amounts after one day of rest.}

\descfeat{Sting of the Scorpion [Fiend]}
{You have a viciously barbed tail that carries a lethal poison.}
\shortability{Benefit:}{You have a stinger as a natural weapon that carries a poison that inflicts initial and secondary damage of 1d6 Con. The save DC is Constitution based. You may only inject a number of doses of poison per day equal to your Con bonus.}

\featname{Stolen Breath [Fiend]}
\shortability{Prerequisites:}{Character level 3.}
\shortability{Benefits:}{On a successful grapple check, your opponent may not speak or breathe for one round in addition to any normal effects of a successful Grapple check.}

\descfeat{Stoning Gaze [Fiend]}
{Your gaze petrifies the living and leaves them as statue to decorate your domain as a warning to others.}
\shortability{Prerequisite:}{Character level 9}
\shortability{Benefit:}{Once per round as a Free Action, you must designate one living creature within 60 feet of you. If that creature meets your gaze before your next turn, it must make a Fortitude save or be permanently transformed into Stone as by a stone to flesh spell. The save DC is Charisma based. The effects of this feat are a Supernatural Ability.}

\descfeat{Supernatural Virulence [Fiend]}
{Your poison is as much magical as it is biological.}
\shortability{Prerequisite:}{Must have a poisonous natural weapon.}
\shortability{Benefit:}{Choose one of your spell-like abilities of 3rd level or lower. Any time you successfully poison a victim, they are also targeted by this spell-like ability as if this effect was cast (this expends one use of the ability). While poisoned with your venom, the victim cannot be affected by your spell-like ability again.}

\descfeat{Wings of Evil [Fiend]}
{You have sinister bat-like wings growing from your back.}
\shortability{Prerequisite:}{Character level 5.}
\shortability{Benefit:}{You have a fly speed double that of your normal ground speed. You have good maneuverability, and you must be able to flap your wings to stay aloft (meaning that it requires very specialized armor or cloaks to permit flight).}
\shortability{Special:}{If you would prefer to have insectile wings or feathered wings instead, you can do that. The maneuverability and speed are unchanged. Once the look and feel of the wings is selected it cannot be changed.}

\featname{Wings of Good [Celestial]}
\shortability{Benefits:}{You gain wings and a fly speed equal to double your base land speed with good maneuverability. You must be able to flap your wings to stay aloft (meaning that it requires very specialized armor or cloaks to permit flight). These must be feathery or energy-based.}

\end{multicols}
