\section{[Elemental] Feats} \label{feats:elemental}

A feat with the [Elemental] tag can only be taken by a creature who is from an inner plane or any Elemental or Outsider with an elemental subtype. If the feat has another similar tag (such as [Celestial], [Fey], or [Fiend]), a creature who fulfills the criteria for the other tag may waive this requirement. The abilities granted by feats with the [Elemental] tag are Extraordinary abilities unless otherwise stated.

\begin{multicols}{2}

\descfeat{Abode of Earth [Elemental]}{You are at home within the earth.}
\shortability{Prerequisites:}{(Earth) subtype, Burrow speed, Character level 3+}
\shortability{Benefits:}{Your Burrow speed improves by 10' or to a minimum of 30', and you may burrow through rock.  You may leave a tunnel or leave the earth behind you undisturbed, as you choose.  If you leave the earth undisturbed, there is no sign of your passage unless you are in a square adjacent to a surface, except to creatures with Tremorsense or who make the Perception check to hear you.  The Perception check is not made more difficult by the earth you are in, just by distance through it.  Other rocks and earthen walls do interfere as normal.}


\descfeat{Adept Flyer [Elemental]}{You are a natural flyer.}
\shortability{Prerequisites:}{(Air) subtype, Fly speed, Character level 5+}
\shortability{Benefits:}{Your Fly speed improves to twice your base land speed (minimum 60'), or +10', whichever is more, and your maneuverability improves to Perfect.  Your Fly speed improves by 20' for every five character levels you gain beyond 5th.}


\descfeat{Binding Growth [Elemental]}{You grow on people.}
\shortability{Prerequisite:}{Wood Elemental Creature (e.g., Psuedoelemental Being (Wood) feat)}
\shortability{Benefit:}{After pinning or lifting a creature for a round, you may attempt to grow a Binding Growth on them with another grapple check against a DC of 10 + their Grapple modifier.  Once you do so, they are bound, losing their Dexterity bonus to AC and their ability to take physical actions other than try to escape, until they break the bonds.  The bonds can be broken by others with a slashing melee weapon capable of doing 5 + your hit dice points of damage against AC 5+your Constitution modifier, but a miss hurts the bound creature, or by a Strength check (DC 15 + your Constitution modifier) or Escape Artist check (DC 10 + your hit dice + your Constitution modifier).  Even once broken, they remain on for 1d4 rounds, entangling the bound creature.}


\descfeat{Ice Trail [Elemental]}{You leave a trail of ice wherever you go.}
\shortability{Prerequisite:}{Character Level 3+, (Cold) Subtype}
\shortability{Benefit:}{Your square counts as if it had the \emph{Grease} spell cast on it, except that the slick is made of ice and has the (Cold) descriptor.  Any square you leave has this effect on it, lasting until the end of your next turn.  You never slip on ice, making you immune to this effect.}


\descfeat{Infusion of Elemental Essence}{You have been infused with the power of one of the elemental planes, granting you an affinity for that element and a small degree of magical power.}
\shortability{Benefit:}{You may take any feat with the [Elemental] subtype that you qualify for; additionally, choose an elemental subtype (Air, Earth, Fire, or Water), and you may take [Elemental] feats as though you had that subtype. You also gain Resistance 10 to an energy type dependent on your element:

\begin{list}{}{\itemspace}
    \item Air or Earth: Acid or Electricity
    \item Fire: Fire
    \item Water: Acid or Cold
\end{list}
You may select this feat only once.}


\featname{Large Size [Elemental]}
As the Outsider feat of the same name, except that, optionally, two points of the Strength boost and one point of the Natural Armor increase for the size increase may be traded to remove the reduction to Dexterity. You may do this trade twice, for a final total of STR +4, Dex +2, Natural Armor +0.


\descfeat{Primal Armor [Elemental]}{Your body deflects blows off of itself.}
\shortability{Benefit:}{You gain impenetrable Damage Reduction equal to half your character level, rounded up (1/- at first level, 2/- at 3rd, 5/- at 9th, 10/- at 19th).}


\descfeat{Primal Fortification [Elemental], [Racial]}{Your body has become even more impenetrable.}
\shortability{Prerequisite:}{Elemental-Bodied, Hardiness of the Elements}
\shortability{Benefit:}{You gain immunity to Critical Hits.  You also cannot be flanked, as your undiffentiated body has no clear front or back.}


\descfeat{Psuedoelemental Being [Racial]}{You are a psuedoelemental being, with rare and unique powers.}
\shortability{Prerequisite:}{Elemental-Bodied.}
\shortability{Benefits:}{Instead of picking a normal elemental type as an elemental-bodied, select one of the following other planes: Ice, Magma, Shadow, or Wood.  You gain benefits as follows for the type you've picked:
\begin{list}{}{\itemspace}
    \item Ice: You gain the (Cold) subtype, a 30' base land speed, a 30' swim speed, and +2 to Str.  Your melee attacks do 1d6 bonus Cold damage.  You speak Aquan and Auran.
    \item Magma: You gain both the (Earth) and (Fire) subtypes. Your base land speed is 20', and you gain +2 Str. Otherwise you gain the full benefits of both elements.
    \item Shadow: You have a 30' base land speed and a Fly speed of 10', with good maneuverability, and gain +2 Dex. You are \emph{invisible} in any lighting less than bright light. You speak Common. Despite your affiliation to the Plane of Shadow instead of to the Inner Planes, you still qualify for [Elemental] feats.
    \item Wood: You have no elemental subtype, and gain +2 Con and a 10' Climb speed. You gain Regeneration 0, penetrable by Fire and Slashing weapons, which improves to Regeneration equal to your level in areas of natural daylight or equivalent brightness (such as a \emph{daylight} spell). You only gain natural healing if you spend at least 8 hours/day in such brightness. You count as a Plant, in addition to an Elemental, for all effects relating to type. You speak your choice of Sylvan or Treant, and any Elemental language.
\end{list}
Other Dual-element types than Magma, such as Ooze (Water and Earth), Smoke (Air and Fire), Vapor (Water and Air), and so on are possible.}
\shortability{Special:}{This feat can only be taken at 1st level.}


\featname{Stolen Breath [Elemental]}
As the [Fiend] feat of the same name, except where noted below.
\shortability{Prerequisites:}{(Air) Subtype or Drowning Grasp, Character level 3+}


\descfeat{Tremorsense [Elemental]}{Your close connection to your home element gives you Tremorsense.}
\shortability{Prerequisites:}{(Earth) or (Water) Subtype, Character level 6+}
\shortability{Benefits:}{You gain Tremorsense out to 120'.  You gain Blindsight out to 30' against any creature you can Tremorsense.  If you have the (Water) subtype and not the (Earth) subtype, your Tremorsense works at its full range in liquids, but only to half range and you do not gain Blindsight through solids.}


\descfeat{Touch of Shadow [Elemental]}{Your shadowy touch can bypass armor.}
\shortability{Prerequisite:}{Shadow Elemental Creature (Psuedoelemental Being (Shadow), Shadow Genasi, or similar), Natural weapon, Character Level 3+}
\shortability{Benefit:}{You may choose to make natural weapon attacks as touch attacks.  Such attacks use your Dexterity bonus to hit, instead of Strength, and do not gain Strength to damage.}


\descfeat{Uncanny Flexibility [Elemental], [Racial]}{Your body, being made of a material other than flesh, bends in directions and places that flesh neither can  nor should.}
\shortability{Prerequisite:}{Airbodied, Firebodied, or Waterbodied; or Psuedoelemental Being (Magma or Shadow).}
\shortability{Benefit:}{You gain a +4 bonus to Escape Artist checks, and Escape Artist is always a class skill for you.  You can compress your head to about half area for purposes of slipping through tight spaces, and may attempt to slip manacles, ropes, webs, nets, grapplers, and similar bonds as a free action.}


\descfeat{Unstoppable Force [Elemental], [Racial]}{You cannot be stopped.}
\shortability{Prerequisites:}{Elemental-Bodied, Hardiness of the Elements}
\shortability{Benefit:}{You become immune to paralysis and stunning.}

\end{multicols}