%\section{Fiends With Style}

\section{Fiendish Taint}

Fiendish power is a taint upon the realms, and so its power corrupts those who are strong in its power. As a fiend allows more of the energies of the Lower Planes to enter his body, transformations beyond his control alter his true form, forcing him to become an image of evil. The forms of the fiendish subraces are well known; balors and lemures are easily recognizable in order to better signify their roles in fiendish society, but those who embrace the quintessential nature of fiendish existence can exhibit a wild and wide variety of forms. Some are merely permutations on a theme, such as succubus who has embraced the Sphere of Violation might merely be an emotionally distant ice princess, while a bone devil who has wallowed in his Brutish nature may exhibit the addition of anorexic wings to accompany an acquired ability to fly and colorful markings along his claws that denote their mutation into poisonous implements. Other fiends offer no such frame of reference, such the totally unique Demon Princes, symbols of fiendish power and might.

Some mortals gain fiendish power by bloodline or transformation, and these beings find that they pay the same price as a True Fiend. Having dabbled in fiendish power, most believed that they could embrace true evil without consequences; the truth is that fiendish power marks its bearers, displaying their nature and allegiance for all to see.

\subsection{Game Effects} Game mechanically, there is no reason for any demonic creature to look like anything. A gelugon could look like a planetar and aside from a little player confusion at the beginning, then any combat or non-combat situation would play out the same. This is a purely flavor model, and it reinforces the choice a player has made to become a Fiend. In this way, he's getting the feeling of becoming a more powerful fiend, and the class and feat options aren't just another power option. Once he's leaving a trail of ooze or he's hiding his scales in the local pub, he's certain to feel like a fiend.

The system for these changes is simple: for every feat with the Fiend subtype you acquire, you choose one physical trait over and beyond any transformations these feats might grant or inflict, and for every Sphere you acquire you choose one mental trait. Feel free to create any new traits with your DM's permission, but make sure that they are both obvious and disturbing. Feel free to disallow the choice of a trait if it overlaps another trait (like fur covering a change in color on a set of limbs).

Physical traits can be hidden with the Disguise skill or shape-changing magic or effects, and mental traits can be played off by using Bluff. Once someone has noticed a trait, they may make a Knowledge (planes) check to identify that a person is a Fiend. How they react at that point is up to them.

\begin{table}[tbh]
\begin{small}
\begin{multicols}{2}
\featnamelist{Physical Traits}
\listone
\item Drips slime or excessive dust wherever he goes
\item A pair of appendages are of different color from the rest of body.
\item Scales, fur, or loose/cracking skin cover arms, legs, chest, back, or face (no game effect)
\item Has a stylized wound that never heals
\item Gains non-functional horns, spurs, or bone ridges
\item Small hump on back
\item Body is feverishly hot or cold
\item Drools incessantly
\item Breathe steams in any ambient temperature
\item Extra joint in fingers and toes.
\item Sharpened teeth (enlarged canines, shark teeth, or some other style)
\item Alien eyes(change in color, shape, or composition)
\item Extra non-functional eye or eyes on face.
\item Altered body proportions(longer or shorts arms, legs torso, etc) or size(large head, fist, etc).
\item Apparently dying of a disease(choose a disease, but it has no game effect)
\item Limb is rotted and skeletal (no game effect).
\item Limbs have extra tendons.
\item Gain non-functional wings.
\item Hands resembles spiders.
\item Smells of ash or brimstone.
\item Hole all the way through body in the center of torso.
\item Stand unnaturally still when not paying attention.
\item Cloven feet.
\item Tentacles for fingers
\item Appears as if worms or bugs are crawling under skin.
\item Plants droop when held.
\item Extra ribs extend to pelvis
\item Skin wrinkles when struck, and must be smoothed down.
\item When sleeping, runes and glyphs press up from under skin.
\item Holy symbols and holy water cause very mild burns(no game effect)
\end{list}

\featnamelist{Mental Traits}
\listone
\item Gaze lingers hungrily at acts associated with one’s Spheres.
\item Cruel smile or laugh.
\item Distaste for the company of good-aligned people
\item Fondness for disturbing imagery.
\item Seems pained or ill in good-aligned temples.
\item Must taste the blood on his weapons after every kill.
\item Displays no emotion at atrocity or other’s pain.
\item Obviously enjoys the taste of bloody meat.
\item Eat bugs when you think no one is watching.
\item Only laughs when seeing others in pain.
\item Must keep an unholy symbol in your possession, if possible.
\item Appears extremely avaricious in the presence of exposed wealth.
\item Becomes visibly excited when pain is inflicted on others.
\item Seems in awe of more powerful demons.
\item Must lie about one’s past, but only about unimportant details.
\item Seems fearful and guilty in the presence of celestials.
\item Bathes as little as possible.
\item Must keep lair and possessions as clean as possible.
\item Seems angry and resentful with given a command.
\item Seems gloating and sarcastic when giving orders.
\item Always asks to keep evil magic items or spellbooks with Corrupt or [evil] spells (can change mind as soon as one round later).
\item Seems bored when morality is discussed.
\item Seems happy during funerals and executions.
\item Leers at any woman of child-bearing age or older.
\item When confront by authority figures, always seems bitter.
\item Seems angry when charity or help is offered.
\item Seems to not understand respect for the dead.
\item Is rude when asked for help or charity.
\item Unable to show love.
\item Unable to express appreciation.
\end{list}
\end{multicols}
\end{small}
\end{table}
