\section{Fiendish Spheres} \label{spheres}

Fiends (and some of their minions and associates) cast magic primarily through spell-like abilities. While many signature fiends have arbitrary lists of spell-like abilities, the Tome of Fiends offers a method to advance Fiends into thematically appropriate spell-like abilities when they advance. When a fiend has access to a sphere, she is able to use all of the abilities within that sphere up to her character level. If she gains more levels, more powers of the sphere become available. In this way the spell-like abilities of fiends created with the rules in this tome should always be \ae sthetically and level appropriate.

\ability{Basic Sphere Access:}{When a creature has basic access to a sphere, she can use any of the spells listed in the sphere may be used once per day (each) as spell-like abilities, provided that their listed level is equal or lower to the creature's character level.}

\ability{Advanced Sphere Access:}{When a creature has advanced access to a sphere, she can use any of the spells listed in the sphere may be used 3 times per day (each) as spell-like abilities, provided that their listed level is equal or lower to the creature's character level.}

\ability{Expert Sphere Access:}{When a creature has expert access to a sphere, any spells listed in the sphere may be used at will as spell-like abilities, provided that their listed level is equal or lower to the creature's character level.}

\ability{Creating new spheres:}{The following list of spheres isn't intended to be comprehensive, and we fully expect that some players and DMs will want many more spheres than we have scribed. All new spheres must be approved of by the DM, and should represent some actual (indifferent or evil) trait like ``intoxication" or ``badgers" rather than a game mechanical notion like ``kicking ass and being totally sweet" or something praiseworthy like ``generosity". A good place to start is actually Domains, as these are already a source by which a character gain a spell at every odd-numbered level.}

\ability{Spheres and Spell Levels:}{Spell-like abilities used out of spheres are considered to be cast as a spell level equal to half the minimum needed character level to use the ability (rounded up). The save DC of a spell-like ability granted through Sphere access is Charisma-based. Thus, the save DC for a spell-like ability which becomes available at character level 5 is 13 + Charisma bonus.}



\newcommand{\sphere}[9]{\begin{list}{}{\itemspace}\item \textbf{1:} \spell{#1} \item \textbf{3:} \spell{#2} \item \textbf{5:} \spell{#3} \item \textbf{7:} \spell{#4} \item \textbf{9:} \spell{#5} \item \textbf{11:} \spell{#6} \item \textbf{13:} \spell{#7} \item \textbf{15:} \spell{#8} \item \textbf{17:} \spell{#9}}
\newcommand{\spherecont}[1]{\item\textbf{19:} \spell{#1} \end{list}\medskip}

\begin{multicols}{2}

\featname{\hypertarget{sphere:bone}{Bone}}
\textbf{Special: }{Any creature of 10 HD or less killed by one of your spell-like abilities rises as a zombie under your control, with no control limits.}
\sphere
{Command Undead}
{Descecrate}
{Animate Dead}
{Black Sand}
{Summon Undead V}
{Awaken Dread Warrior}
{Revive Undead}
{Awaken Undead}
{General of Undeath}
\spherecont{Plague of Undead}

\featname{\hypertarget{sphere:bubbles}{Bubbles}}
\textbf{Special: }{Three times per day, you may use the Sculpt Spell metamagic on any spell-like ability you can use, but only if you do not use the cone option of this metamagic feat.}
\sphere
{Flaming Sphere}
{Water Breathing}
{Magic Circle against Good}
{Resilient Sphere}
{Binding}
{Telekinetic Sphere}
{Forcecage}
{Prismatic sphere}
{Temporal Stasis}
\spherecont{Time Stop}

\featname{\hypertarget{sphere:carnage}{Carnage}}
\textbf{Special: }{All of your damaging spell-like abilities do vile damage.}
\sphere
{Seething Eyebane}
{Blade of Fear and Pain}
{Lahm's Finger Darts}
{Blade Barrier}
{Fleshshiver}
{Disintigrate}
{Flensing}
{Horrid Wilting}
{Mass Harm}
\spherecont{Implosion}

\featname{\hypertarget{sphere:cold}{Cold}}
\textbf{Special: }{You gain the [Cold] Subtype.}
\sphere
{Cone of Cold}
{Creeping Cold}
{Ice Storm}
{Wall of Ice}
{Freezing Sphere}
{Control Weather}
{Heat Drain}
{Freezing Fog}
{Fimbul Winter}
\spherecont{Frostfell}

\featname{\hypertarget{sphere:death}{Death}}
\textbf{Special: }{You are immune to any magical death effect You are also healed by negative energy like an undead creature (this does not interfere with any existing ability to be healed by positive energy).}
\sphere
{Death Knell}
{Ghoul Gauntlet}
{Vampire Touch}
{Enervation}
{Raise Dead}
{Symbol of Death}
{Finger of Death}
{Death Pact}
{Wail of the Banshee}
\spherecont{Implosion}

\featname{\hypertarget{sphere:dominion}{Dominion}}
\textbf{Special: }{Once per month, you may make one of these effects permanent.}
\sphere
{Obscuring Mist}
{Web}
{Wall of Fire}
{Solid Fog}
{Black Tentacles}
{Programmed Illusion}
{Wall of Force}
{Teleport Circle}
{Gate (travel version only)}
\spherecont{Storm of Vengeance}

\featname{\hypertarget{sphere:fire}{Fire}}
\textbf{Special: }{You gain the [Fire] subtype.}
\sphere
{Fireball}
{Scorching Ray}
{Firetrap}
{Wall of Fire}
{Fireshield}
{Incendiary Cloud}
{Blackfire}
{Fire Seeds}
{Meteor Swarm}
\spherecont{Flame Strike (this ability can be used as an Immediate action).}

\featname{\hypertarget{sphere:frostbite}{Frostbite}}
\textbf{Special: }{Any creature taking cold damage from your spell-like abilities is frostbitten (treat as fatigued, which is removed when the damage is healed). If you have Frostburn, you may use those frostbite rules if you want.}
\sphere
{Shivering Touch}
{Freezing Ray (as Scorching Ray, but Cold subtyped and doing Cold damage).}
{Shivering Touch, Greater}
{Cone of Cold}
{Flesh to Ice}
{Entomb}
{Flesh to Ice, Chained}
{Frostfell}
{Iceburg}
\spherecont{Soul Bind (uses a piece of ice to hold the soul)}

\featname{\hypertarget{sphere:heresy}{Heresy}}
\textbf{Special: }{Gain immunity to the Destroyed result of Turning and the Commanded result of Rebuking.}
\sphere
{Align Weapon (evil only)}
{Desecrate}
{Magic Circle Against Good}
{Unholy Sword}
{Planar Ally, Lesser}
{Dispel Good}
{Unhallow}
{Blasphemy}
{Gate}
\spherecont{Miracle}

\featname{\hypertarget{sphere:pyre}{Pyre}}
\textbf{Special: }{Fire damage from your spell-like abilities bypasses Fire Resistance, but not Immunity to Fire.}
\sphere
{Burning Hands}
{Flame Blade}
{Fireball}
{Charnal Fire}
{Parboil}
{Ashen Union}
{Fireball, Quickened}
{Incendary Cloud}
{Gate (calling version only, fire subtype creatures only)}
\spherecont{Storm of Vengence (all elemental damage is fire damage)}

\featname{\hypertarget{sphere:seduction}{Seduction}}
\textbf{Special: }{You gain a +2 bonus to Bluff, Diplomacy, and Sense Motive.}
\sphere
{Entice Gift}
{Suggestion}
{Glibness}
{Charm Monster}
{Sympathy}
{Mass Suggestion}
{Mass Charm}
{Simulacrum}
{Programmed Amnesia}
\spherecont{Mind Rape}

\featname{\hypertarget{sphere:sleep}{Sleep}}
\textbf{Special: }{You can coup de grace a sleeping foe as an attack action.}
\sphere
{Deep Slumber}
{Waves of Fatigue}
{Waves of Exhaustion}
{Dream}
{Nightmare}
{Symbol of Sleep}
{Demand}
{Weird}
{Programmed Amnesia}
\spherecont{Astral Projection}

\featname{\hypertarget{sphere:stone}{Stone}}
\textbf{Special: }{You gain the Tremorsense ability, allowing you to detect and target anything touching the ground within 60 feet of yourself.}
\sphere
{Earth Glide}
{Spike Stones}
{Stone Shape}
{Stone Tell}
{Wall of Stone}
{Move Earth}
{Transmute Rock to Mud (special bonus: Transmute Mud to Rock)}
{Earthquake}
{Meteor Swarm}
\spherecont{Genesis}

\featname{\hypertarget{sphere:terror}{Terror}}
\textbf{Special: }{Gain Intimidate as a class skill, and may make an Intimidate check to Demoralize Opponent as a free action once a round.}
\sphere
{Cause Fear}
{Scare}
{Halt Undead}
{Fear}
{Phantasmal Killer}
{Symbol of Fear}
{Eyebite}
{Fear, Quickened}
{Weird}
\spherecont{Wail of the Banshee}

\featname{\hypertarget{sphere:venom}{Venom}}
\textbf{Special: }{Gain immunity to poison.}
\sphere
{Desecrate}
{Poison}
{Bestow Curse}
{Mind Poison}
{Cloudkill}
{Major Creation (poison or venom only)}
{Circle of Death}
{Finger of Death}
{Shapechange (venomous creatures only)}
\spherecont{Symbol of Death}

\featname{\hypertarget{sphere:violation}{Violation}}
\textbf{Special: }{Gain the telepathy special quality. If you already have this special quality, or later gain it from another source, then you gain \spell{Detect Thoughts} as an at-will spell like ability.}
\sphere
{Hypnotism}
{Suggestion}
{Modify Memory}
{Dominate Person}
{Lesser Planar Binding}
{Geas}
{Greater Planar Binding}
{Dominate Monster}
{Gate (Calling verson only)}
\spherecont{Mind Rape}

\featname{\hypertarget{sphere:voracity}{Voracity}}
\textbf{Special: }{Any time one of your spell-like abilities grants negative levels or ability damage/drain to a target, you heal 5 HPs of damage per level or point.}
\sphere
{Death Knell}
{Shadow Spray}
{Vampiric Touch}
{Enervation}
{Magic Jar}
{Power Leech}
{Steal Life}
{Energy Drain}
{Reaving Dispel}
\spherecont{Absorption}

\end{multicols}
