\section{High Adventure in the Lower Planes}

The Lower Planes are infinite in size, and this is often taken as meaning that they are somehow filled with infinite power. This is essentially completely false. Remember that the Primes are essentially infinite in scope as well, and while there are ancient dragons and even Xixicals\ldots \textit{somewhere}, the fact is that you could adventure your whole life and never ever meet one. The world is mostly filled with forests, and mountains, and little river valleys, and most of the time the villains you encounter are going to be rabid dire weasels and bugbear junkies who will try to resell your shoes for a hit of mordayn vapor. Gehena is actually just like that, except that instead of you never seeing powerful dragons in your day to day life, you never see Arcanoloths. The bad guys you encounter may well be a \textit{fiendish} dire weasel and a bugbear junkie \textit{petitioner}, but the essential threat level is pretty much the same.

Low level adventuring, thus, is extremely plausible in the lower planes. It's not advisable for low level characters to go running around Tiamat's lair or anything, but the fact that the Elder Brain Pool is somewhere in the Underdark hasn't stopped \textit{any} low level campaigns from tunnel crawling as far as I can recall. What follows is some wilderness adventure seeds from the lower planes for low (1-5), medium (6-10), and high (11-15) level. Players who want to adventure at near epic levels (16+) don't even need adventure seeds of this sort because they actually can just take on The Dark Eight or whatever. For whatever reason, lots of ink has been spilled on near epic adventuring in the lower planes, and I have every confidence in a decent DM's ability to throw a Balor at a party and make a rollicking and dangerous encounter.


\subsection{High Adventure in\ldots Acheron!}

The first thing to realize about Acheron is that it really isn't a bad place to be. It's not even Evilly Aligned, so even campaigns using The Face of Horror have no reason to play up the terror of being here -- the sand of Acheron is not Evil. But it \textbf{is} made out of steel. Characters who are going to go adventuring will do so in Avalas, because that's the part of the plane that doesn't \textit{turn you to stone}.

\subsubsection{Campaign Seed: The Tunnel to Pandemonium}

Here's a little piece of D\&D history for you -- In AD\&D, Orcs were \textit{Lawful Evil}, so the Orcish pantheon lives in Acheron to war eternally with the Goblin pantheon \textit{even though Orcs are Chaotic now}. That means that the cube of Nishrek, where Gruumsh calls his most favored and despised for Gruumshian Justice when they have passed on -- is itself a bubble of Pandemonium found far from its place in the Wheel. There are, therefore, numerous portals to Pandemonium all over Clangor and Nishrek, so characters who wish to fight Orcs and Goblins in the lower planes can do so to an unlimited degree by portal hopping through the Pandemonium and Acheron layers. As an agent of Gruumsh or Maglubiet, characters can fight their way through savage humanoids, savage humanoid armies, savage humanoids with fiendish allies, savage humanoid war machines, and even powerful outsiders aligned with savage humanoids \textit{well into epic}. You can also use this rivalry as the backdrop for any of a number of ``find the artifact before it falls into seriously the wrong hands'' type adventures, with the characters switching sides repeatedly based on who seems to have the artifact now.

\subsubsection{Campaign Seed: You're in the Army Now}

Cities and castles populate the lands of Acheron without number, and all of them are on a war footing at all times. Characters can travel generally without molestation throughout this area and conduct a fairly profitable bit of trading and scavenging if they do things right. But if they do things wrong, they may end up drafted into some local militia or imperial army. Characters can have substantial numbers of adventures as part of a military force, or they can attempt to resist being drafted by any of a number of means. Unfortunately, the laws of Acheron being what they are, once the characters impress their will by force of personality or arms enough to avoid the draft, they'll find themselves as a \textit{side} -- which means that they'll be treated as a hostile army all themselves by other forces. At that point they can try to stick it out alone, or try to get some help, of course almost every empire in Acheron started the same way. So the players can progress smoothly from the ``chased by bad guys'' scenarios to the ``forge an empire in blood'' scenarios to the ``marry the princess, design your castle'' scenarios.

\subsubsection{Ten Low Level Adventures in Acheron}

You pull into the hamlet's bar, and see what they have to offer a stranger. It isn't good. After a brief set of questions to make sure you aren't going to burn the place down, the bartender tells you\ldots

\listone
	\item The town is infested with fiendish rats. Beer just isn't safe until their gone, sorry.
	\item A rival faction as poisoned the well, and someone needs to find a new source of water.
	\item Brigands are holding the pass. I hear one of them is an Ogre.
	\item The man you are looking for\ldots he was taken away by the Scarthian Army.
	\item That signet ring is part of King Imag's royal accoutrements. If someone could get all of them together\ldots it could spell big changes for the County of Yevekh.
	\item Orcs have come through the tunnel, their leader has a silver sword and noone dares to stand against him.
	\item After the Citadel of Zor fell, bodies were piled as high as your arm pit. I hear someone is making them all into zombies now, it's a shame really.
	\item I'd love to give you change, but after Sir Garreth set the taxes to 100\%, I'm afraid I have no coins to give you.
	\item In this town, either you're for Sheriff Braxton, or you're dead. This town, we like to have choices.
	\item It's free drinks here if you can get Clarrissa the hobgoblin matron to allow her daughters to marry.
\end{list}

\subsubsection{Ten Mid Level Adventures in Acheron}

An emissary of hoary Surog, the ice count, contacts you. He has (the ring, the antidote, the code) you need, and he'll give it you, but first\ldots

\listone
	\item One of his lieutenants has betrayed him; since you are random strangers, he can trust you to find out which one.
	\item His daughter has run off with the blue falcon, that accursed do-gooder. Bring her home, do with him as you wish.
	\item His daughter is the blue falcon. Stop her, but don't kill her.
	\item His daughter is the blue falcon, and Surog's rival, Cardinal Valgos, has put-her-in-a-death-trap. Rescue her, without letting on that Surog knows her identity.
	\item Cardinal Valgos has found some route to smuggle forces into Yevekh. Find how they're getting in.
	\item Cardinal Valgos is planning an attack, and Surog is not prepared. Infiltrate his mercenary forces and cause as much delay as possible.
	\item Cardinal Valgos has placed Surog in some kind of suspended animation! You have to lift the curse before one of Surog's underlings makes a play for power.
	\item A blue crossbow bolt with a head shaped like a stylized raptor strikes the emissary from nowhere, killing him before he can deliver your mission! Who is trying to stop you, and why?
	\item Cardinal Valgos has Imag's heir, or so he claims. Prove the heir is false, or steal him away.
	\item Cardinal Valgos has tricked the fox of the mountains, Dagipert, into allying with him. Break up this alliance one way or another.
\end{list}

\subsubsection{Ten High Level Adventures in Acheron}

You stand at the front of your army, triumphant over every foe the Lichking has sent against you, over the next hill you see\ldots

\listone
	\item The Lichking's vampire sister, all alone with a white flag.
	\item A pile of bodies impaled to the top of a 200 foot metal rod.
	\item A stampede of zombie elephants.
	\item A chasms cleaved into the side of the cube burbling with lava.
	\item A portal opening up upon an army of orcs in Pandemonium, easily the equal of your own.
	\item A huge pile of what appears to be gold.
	\item A huge pile of what appears to be skulls on fire.
	\item A wyvern bearing a message in its claws.
	\item The daughter of King Zormmund, tied to an elder earth elemental.
	\item Your grand vizier, who has apparently betrayed you again.
\end{list}


\subsection{High Adventure in\ldots Pandemonium!}

Pandemonium is a victim of the terrible confusion that permeates Law and Chaos in D\&D literature, and its inhabitants are portrayed in a number of improbable lights. Pandemonium is not an Evil plane, but it's fairly wicked and it's inherently Chaotic. How it and the people who live there appear in your game is entirely dependent upon how your game ends up handling Chaos in general. Pandemonium might be extremely disorganized, or inherently deceitful, or starkly unhelpful, or simply a lawless wilderness. But what it almost certainly \textit{isn't} is a source of low comedy where people do ``whacky stuff'' because they are so ``crazy''. That's the kind of thing that makes us cry.

Pandemonium can be a source of classic D\&D adventure at its finest -- the towns of Pandemonium are located right next to twisting tunnels through the stone and loud noises sound continuously through the warrens. So characters can go right from the town to the dungeon crawl without any explanation or overland travel, and those dungeon encounters are inherently episodic because nothing can hear your combats.

Pandemonium is dark and loud, and filled with confused people. At its best, Pandemonium is basically a huge rave. At its worst, Pandemonium is a huge rave. Like every part of the D\&D afterlife, Pandemonium can be a punishment or a reward. And like Acheron, this place isn't inherently Evil. So even if you are using The Face of Horror, the Eternal Rave isn't that bad of a place.

\subsubsection{Campaign Seed: Life in the Big City}

Welcome to The Madhouse. It's one of the largest planar metropolises in D\&D, and unlike places like the City of Brass or Sigil, it really \textit{doesn't} have some group of powerful outsiders ruling it with an iron fist. In fact, The Madhouse has no rulership of any kind. The place is dark, and loud, and the only light comes from naked women with glow sticks. Essentially, you can get away with pretty much anything without interference from opponents significantly outside your level range. You can keep having urban adventures continuously from 1st to 20th without ever getting seriously derailed by concerns of DM self-insertion characters coming over to knock over your house of cards. At the same time, there really \textit{are} Balors in this complex, so if you actually want to \textit{seek out} higher-powered enemies, that's doable.

\subsubsection{Campaign Seed: The Largest Dungeon}

Tunnels crisscross Pandemonium all over the place, and they are completely stable because the way gravity works there actually can't be a cave-in. But the place is dark and windy, and filed with tunnels that move around for no reason. The caverns are filled with monsters, traps, and treasure. It's all there, from shambling zombies to ninja temples, the low level areas cross seamlessly into the higher level ones. Oddly, this is the only place in the entire multiverse of D\&D where the old Gygaxian standby of having deeper and deeper levels of the dungeon filled with nastier and nastier monsters and traps actually makes sense. There's a town nearby, and the map doesn't have to make any sense at all. If you're looking for Nethack style adventuring, Pandemonium delivers.

\subsubsection{Ten Low Level Adventures in Pandemonium}

You lean over the counter to the waitress, not because she's so beautiful, but because you can barely hear her over the din. Honest. You're pretty sure she said\ldots

\listone
	\item WE DON'T SERVE YOUR KIND HERE. THE MILLER ONLY SENDS US BASALT FLOUR NOW.
	\item WE GOT AN ORDER OF APRICOTS IN THIS WEEK, THE CRAZ NAKED MAN CLAIMS TO MAKE IT HIMSELF.
	\item THE TUNNELS ON THE WEST SIDE, NO ONE COMES BACK FROM THOSE. NOT EVEN THOSE NICE MEN FROM LAST MONTH WITH ALL THE WEAPONS.
	\item IF KELLIGAN SEES YOU LEANING ON ME LIKE THIS, HE'LL KILL US BOTH.
	\item THERE WAS A MAN LOOKING FOR YOU. HE SAID HE OWED YOU MONEY.
	\item DO I KNOW YOU? AFTER THE WATER TURNED BLACK, I'VE HAD TO ASK EVERYONE THAT.
	\item I HAVE THE CURSE. YOU SHOULDN'T STAND SO CLOSE.
	\item I CAN'T FEEL MY MIND. STOP TAUNTING ME!
	\item THE BEER IS FREE TODAY. IT'S A LONG STORY.
	\item DON'T UNCOVER THOSE LIGHTS! THERE'S A WIGHT IN THE BUILDING.
\end{list}

\subsubsection{Ten Mid Level Adventures in Pandemonium}

You've found the sage you were looking for, but it looks like he's dead. His corpse is torn apart and lying on a heap against the part of the floor that's the ceiling to you. Droplets of congealing blood rotate slowly in the la grange points between ceiling and floor. He's got a piece of parchment in his cold hands, and it says\ldots

\listone
	\item wights have found me kill me kill me kill me
	\item I think this corpse will fool the howlers. At least for a while. If you wanted some water it's become more dangerous.
	\item NWNENWWS
	\item This man is an example. If Hruggek's Ninja Temple requests taxes, pay them.
	\item It's written in an old Orcish tongue. You'll have to find an Orc slain on the Prime at least a thousand years ago.
	\item The man's name is Gregor.
	\item Orcs! How I hate them! Their scimitars open the way!
	\item This is a ruse. The sage has escaped.
	\item Go back. Erythnul is not to be mocked.
	\item Itchy. Tasty.
\end{list}

\subsubsection{Ten High Level Adventures in Pandemonium}

The gates of the building have been torn asunder, as the characters run in, it seems that they're too late because\ldots

\listone
	\item Wights swarm over the insides, covering every piece of furniture with writhing limbs and moaning incessantly.
	\item Neogi great old masters hang from the ceiling, affixed by strands of hardened mucous.
	\item The pews stand empty as dust sweeps through the ancient church propelled by powerful winds.
	\item Hruggekian throwing stars are imbedded in virtually every wooden surface.
	\item A gaping planar rift hovers in the middle of the room, the winds of Pandemonium hurtling small objects into the void.
	\item The red dragon is already here, the hobgoblin princess is in his grasp.
	\item Black fires lick the insides of the room, the tomes are most likely destroyed!
	\item A tremendous serpent creeps over the tattered carpet.
	\item The winds howl even louder in here. Or maybe\ldots there are air elementals!
	\item A friendly and purring kitten is tossed back and forth by the terrible winds.
\end{list}


\subsection{High Adventure in\ldots Carceri!}

Point of fact: being in Carceri sucks. It's hard to leave, and it's an unpleasant place to be. That's the whole point. But believe it or not, those who please Nerull sufficiently are \textit{rewarded} with an eternity in Carceri. Now some of these people are just sadists -- creatures who enjoy the suffering of others so much that being able to assist in the degradation of others is payment and more for having to live in a hell dimension in the Prison Plane. But for others, life in Carceri is just genuinely pretty good. Some of these prison dimensions are minimum security white people jail -- there's a golf course and your ``guards'' are attractive women. It's still a prison of course, but if someone doesn't \textit{want} to leave, are they really a prisoner?

Anywhere you go in Carceri, it's all Evil, and people normally only go here if they are themselves Evil. That means that the people who are being punished here are being punished for \textit{failure}, not wickedness. The most successfully wicked individuals actually are rewarded here. Carceri can be a great place to introduce horrific elements into your story because by its nature anything that happens in Carceri, \textit{stays} in Carceri. Horrifying and depraved elements you introduce in a Carceri adventures don't have to apply to any subsequent adventures if you don't want them to.

\subsubsection{Campaign Seed: A Ring of Keys}

Carceri is a never ending parade of pocket dimensions filled with punishments and rewards that are both cruel and ironic. Travel between these cells is almost impossible, but there are ways. Most notably, there are maps that can tell you a secret path to get from one prison to the next; and there are adjustable rings that can transport a character directly from one prison to another depending upon how it is adjusted. Either can make for unlimited hours of enjoyment as players hop from one piece of episodic turmoil to the next. The maps work just like the map from \underline{Time Bandits}, and the rings work just like the devices from \underline{Sliders}. Really. Furthermore, those objects are authorized personnel \textit{only}, so if the players have one they are going to be hunted by Demodands with a new wacky scheme to catch them every adventure.

\subsubsection{Campaign Seed: Escape from Tartarus}

Just because you have been placed in a prison plane doesn't mean you deserved this punishment, or even that you committed a crime. The plane itself will punish impersonally, hiding its portals behind elaborate stages designed to elicit suffering.

Fight your way our of Tartarus, and no prison in any plane will every hold you\ldots

\subsubsection{Ten Low Level Adventures in Carceri}

You pass through the portal and find yourself in a new prison dimension. This one is\ldots

\listone
	\item Filled with thick, thorny foliage. Also it smells like boar and the thorns splinter and get into your armor.
	\item A town where the streets are filled with fighting.
	\item An expansive desert. Vultures fly overhead, but the scorpions seem unwilling to wait for you to die.
	\item A foul sewer. The water is waste deep. At least, you hope it's water.
	\item A scrubland with rusted iron spikes jutting out of the ground. Cages filled with starving madmen top some of the spikes, while other cages have long since fallen to the ground.
	\item A banquet hall stacked with delicious looking food. Haggard goblins look at the food with longing, but nothing seems to stand between them\ldots
	\item A windswept glacier. Far beneath you, there is a shadow in the ice. Far in the distance, a wolf howls.
	\item A stark stone room, where light filters oddly through a great number of spider webs and a dusty stained glass window.
	\item An earthy sinkhole. Worms poke through the topsoil everywhere around you, their eyeless heads wriggling like mad.
	\item A garden maze under an overcast sky. Fantastic shapes are cut into the hedges, and some ever seem to watch you.
\end{list}

\subsubsection{Ten Mid Level Adventures in Carceri}

If you could figure out the secret of this prison, you could escape\ldots

\listone
	\item The labyrinth seems to have four spatial dimensions\ldots
	\item The land shakes with earthquakes, but they still try to build houses.
	\item That eagle keeps eating that guy's entrails\ldots hey wait, I have entrails\ldots
	\item Why does that sanitarium seem to be inside-out?
	\item Why does everyone here wear a mask?
	\item Criminals in this put themselves into prison cells?
	\item The ghosts don't die when we kill them, and if we can't kill them we can't leave this building.
	\item It looks like a brothel, but who are the petitioners? The clients or the girls?
	\item The portal has a gold lock on it, and I was sure I saw a glint of gold in one of those oozes.
	\item An endless desert of white sand\ldots Or is it bone dust? 
\end{list}

\subsubsection{Ten High Level Adventures in Carceri}

If you just had it, then you'd be free\ldots

\listone
	\item A ship of chaos passes this way every day at the same time. If I could only make it notice me\ldots
	\item I almost have enough money to bribe the demodands into releasing me.
	\item That demon is a master of planar magic, and its said that his enemies get tossed to other planes.
	\item The fiends involved in the Blood War come from other planes. If I had an army large enough to impress them, they might show me a way out.
	\item If I could remember my home, I could just cast a spell and go home.
	\item The sage knows a way out, but he's so crazy that he'll only tell the secret to someone he considers a peer. What do I have to learn to do that?
	\item I can't believe that she's here. Do you think she'll forgive me?
	\item That war machine that looks like a bug the size of a mountain\ldots I hear its powered by a portal to the Astral Plane.
	\item I could open this portal, but I need the Blessing of Nerull.
	\item A wizard has been traveling Carceri for rare components, and it's said that he has access to plane-hopping effects.
\end{list}


\subsection{High Adventure in\ldots Hell!}

The Infernal Realm of Baator is essentially 9 infinitely large regions that happen to have a big pit that acts as a portal to the other 8 somewhere in them. So while the gods (and official publications) spend a lot of time worrying about that big pit in the middle, the fact is that the vast majority \textit{of Baatorian residents} don't even know it exists. Near epic play will spend an inordinate amount of time worrying about the goings-on around The Pit, and send the heroes off to go siege the fortresses around the ledge and such, but for the rest of your character's life the Nine Hells of Baator are just some inhospitable terrain filled with level-appropriate monsters.

\subsubsection{Campaign Seed: A Kafkaesque Nightmare}

Baator is home to one of the multiverse's most pervasive, efficient, and \textit{evil} bureaucracies. They don't lose your documents, they don't forget to mail things to you when they said they were going to, they simply have a set of rules that is at once awe-inspiringly complex and actually \textit{designed} to cause suffering to those who need to use its services. A campaign set around the backdrop of filling out forms sounds about as entertaining as doing your taxes in Hell, but there's ample opportunity for comedy, horror, and adventure in such a scenario, as well as ample prospect for character growth. The action starts when the characters need to change their registered employment, or want to protest their home getting knocked over to build a throughway, or perform some other completely mundane bureaucratic task. Unfortunately, the form they need to begin this process is clearly on display downstairs in the room marked ``Beware of Leopard''.

Surfing bureaucracy in Baator is about the only place where that makes for exciting D\&D adventures. The challenges to be overcome are social, mental, physical, and magical and efficient bureaucrats will tell you \textit{exactly what you need to do} to get things accomplished. This isn't like a Kafkaesque Nightmare on Earth, where you'll get stonewalled or your papers will just get lost, this is completely efficient and functional -- but designed by super geniuses to make your character uncomfortable. At lower levels there's a fiendish leopard in the room with the papers you need. At higher levels there's a golem that's supposed to stop people from entering the office where you need to convince a Gelugon to stamp your form. As the characters push their way to the top, they will find themselves in the position of being able to create their own red tape\ldots

On a side note: I just want to point out that my spell-checker recognizes ``Kafkaesque'' as a word. Sweet.

\subsubsection{Campaign Seed: Law of the West}

The great cities of Baator are infinitely far away from some of the nether regions of the plane. But the Law (and the Evil) still needs to be maintained. If you get far enough out into the boonies, Pit Fiends and the like just can't be bothered to show up and solve problems. So when Chaos (or Good) comes in to assault a frontier town, it falls to hard boiled individuals like the Player Characters to set things right. There's a new sheriff in town, and he's got levels in a PC class. This is your chance to use all your Western clichéin a fantasy setting, when you can turn Cowboy Movies into Kurosawa flicks.

Once the players beat back the gnolls who have come in at the behest of hyena ranchers trying to drive the gloom farmers off the land, the place is going to be a nicer place and attract Ogre Duelists or dishonest bankers. When it becomes known that the portal nexus is coming through, suddenly all that property is going to shoot up in value. And suddenly the pit fiends \textit{do} care what goes on in your sleepy neck of the woods.

\subsubsection{Ten Low Level Adventures in Hell}

It's a dusty little town, like an infinite number of others just like it both functionally and aesthetically. You don't know what makes this town special, and with the number of horrors you've seen on the plains -- you're not sure you want to. Still, this is a place it doesn't pay to break the rules when it isn't important, so the first thing you to is walk in through the curtain they hung up on the door to the Town Hall. Inside you see\ldots

\listone
	\item A dried out sahuagin sits behind the desk. He's mumbling about how the water is all gone.
	\item An officious imp attempts to shoo you right back out the door.
	\item Five corpses in fancy clothes lay strewn about the entrance hall.
	\item Putrid husks of humans in cages hang from the ceiling while a ghoul repeatedly jumps up trying to get at the rotting morsels.
	\item A mountain of papers covers the desk. From somewhere behind them a voice tells you that it is busy.
	\item A hobgoblin sits with his feet on the desk. As you enter, he stands up smartly and asks your business.
	\item Long lines of petitioners block off any hope of registering an time soon.
	\item Zombies shamble around the insides of the building and an imp is attempting to complete its paperwork while flying around the ceiling.
	\item The floor has collapsed entirely
	\item The front counter has been smashed and the interior smells like hyena urine.
\end{list}

\subsubsection{Ten Mid Level Adventures in Hell}

At last! You stand before the magistrate, it seems like you've been waiting for an eternity. You state your case, and he tells you\ldots

\listone
	\item ``You have the choice of death by platricorn or death by fire. Choose!''
	\item ``I grant you writ of ownership of Gelzugh's Tavern. You have the full backing of Hell in taking control of it from Gelzugh. Way back.''
	\item ``Your circlet is not \textit{jade}, it's \textit{malachite}, which is totally different. You're going to have to go back into the mines and find a \textit{jade} circlet.''
	\item ``Every one of you are sentenced to clean the sewers of Leng of the crawlers or die in the attempt.''
	\item ``It is Tuesday, so you're going to have to travel to Chitterport to have this taken care of.''
	\item ``Actually, this contract looks legitimate to me; Baelphor is legally the child's father.''
	\item ``I find nothing in this documentation to lead me to believe that these passports have been stamped correctly. Deport everyone.''
	\item ``You can't be serious. These swords aren't even magical.''
	\item ``Foolhardy mortals! You have wasted my valuable time and now I shall waste yours!''
	\item ``Raelzella's marriage is now void, the ownership of the larvae will be decided by combat.''
\end{list}

\subsubsection{Ten High Level Adventures in Hell}

Sorting through the ancient paperwork in the forgotten tower, you've found\ldots

\listone
	\item Documentation that proves that you personally are descended from an Erinyes.
	\item A small plush doll of a petrified Pit Fiend. It appears to be a \spell{shrunk item}.
	\item Spellbooks belonging to an evil lich.
	\item A map of a mighty fortress that appears to have stood where the shard spires stand now.
	\item Proof that a powerful Gelugon is not entitled to his position.
	\item A recipe for a dish now famous throughout the plane.
	\item Tongues of an ancient beast in a box. When the box is opened, the tongues speak of a fortress filled with giants.
	\item A portal to a deeper Hell in between the pages of a book.
	\item Poetry thought lost for a thousand years.
	\item Prophecies that mention you by name.
\end{list}


\subsection{High Adventure in\ldots The Abyss!}

The Abyss is well known for being infinitely big and infinitely bad in all directions, and it is. If there is some hellscape in your nightmares, its probably somewhere in the Abyss and there is someone there waiting to hurt you. The only thing it has going for it is that its very unorganized, meaning that the endless evil is only rarely directed enough the threaten other planes and planar oasis tend to places of great turmoil, meaning that small groups can easily blend in and ingratiated themselves amid the variety of beings that call these planes home.

Unlike other planes, there is no ``standard'' Abyssal Plane, aside from the top level called the Plane of Infinite Portals. These planes may be set up like a deck of cards, but they only share the chaos and evil traits, any particular plane can have any elemental or magic traits in the book and have geography ranging from the mundane mountains, forests, and plains to fantastic locations harmful to all but the most exotic forms of life. The only thing one can depend on is that pits and holes in the Abyss are often planar portals, and they only lead to deeper and wilder layers of the Abyss. Climbing back out of the Abyss is a much more difficult task, one that requires knowledge of planar pathways like the River Styx or powerful magic.

\subsubsection{Campaign Seed: We're the Exotic Products Trading Company (Abyssal Branch!)}

``We are here to serve your needs, and we offer a range of services ranging from capture of exotic lifeforms to collection of unique minerals and lore! We even have an on-call Search and Recovery Team available to recover lost individuals, `bargain' with demon governments, or protect important trade shipments! Contact one of our offices in Sigil or our home office on the Plane of Infinite Portals!''

\subsubsection{Campaign Seed: Pirates of the River Styx!}

``Yo ho, me hearties! The River Styx be vast and mysterious and its waters kiss the Abyssal planes like a cheating lover! Why set sail in the other Lower Planes when the Abyss is infinite and lawlessness is a virtue of its people? The good boat The Groping Marilith has room for any brave soul whose handy with steel or spell and has an eye for exotic and demonic beauties in every port and magic and jewels hidden in the nether regions of every fiend. Come ply the Abyss with us, and forget your troubles on the River Styx!''

\subsubsection{Ten Low Level Adventures in The Abyss}

\listone
	\item Food Run! Demon weevils have infected an Abyssal Town on the river Styx, and the first group to bring untainted food for them will earn a valuable ally.
	\item Race! A Nalfeshness ruler of miles-long city straddling the River Styx on the 33th level of the Abyys has decided to host a riverboat race to please his unruly people. There's big money to be made in this no holds barred sailing race through an Abyssal city!
	\item The good ship Lollyjaws is plying the River Styx with its zombie crew, and they've decided that you've hit a big score and you need help ``investing'' it.
	\item Message in a bottle. A map written in Celestial has been found in a blottle on the River Styx. Its this a map to a treasure, some poor soul's hope for rescue, or a clever trap to capture well equipped adventure seekers?
	\item Run aground! A chaos ship containing mysterious spices and drugs and run aground near a port town, and its bedlam as psychotropic clouds spew forth to wreak chaos in the town. Loot the vessel before the helplessness of the townsfolk attracts powerful fiends who'll sweep up the any booty.
	\item A dark, beautiful, and mysterious stranger decides that only your organization can retrieve a packet of information from the 411th plane.
	\item Mapquest! Map a planar route to an exotic locale in the Abyss, and return to collect your reward.
	\item ``There's an emergency! Deliver this call for help to the 911th plane!''
	\item Worm farmer! Travel to Noisesome Vale on the 489th layer of the Abyss and collect samples of the worms that eat sulfer gas and exhale breathable air for a Fiendish Gnome client with ideas for a Styxian submarine.
	\item An erratic portal between the 1st and 239th planar has started functioning properly again, and the Lost of City of Azzabanazanazan has been found (much to the inhabitants surprise). A little clever negotiating between this city and a few of the more popular demon cities could mean big profit.
\end{list}

\subsubsection{Ten Mid Level Adventures in The Abyss}

\listone
	\item Naval vessels of the Nine Hells have made serious incursions along the river Styx, and a clever ``privateer'' can make a little coin by signing up with a demon lord to resist these salty devils.
	\item Smiley Tom, the infamous Incubus captain of the legendary Slippery Cat has been imprisoned in Graz'zt realm for unknown crimes. Rescue him to gain his legendary gratitude, or use this opportunity to steal the Slippery Cat, the greatest ship to ever sail the River Styx.
	\item The Forgetful Fog Technique. Some clever pirate has figured out a way to create fog on the waters of the River Styx, then push these vapors onto towns and cities, looting them silly while the inhabitants are blissfully unaware. Catch these clever thieves to stop their amnesiac attacks, or perhaps gain a monopoly on this tactic yourself.
	\item One of your mates have finally bedded one lass too many\ldots she's been granted a wish by a glabrezu, and ill-luck follows your mate and his friends(which is unfortunately you). Win her affections back or find her a new romance in the Abyss, or else the curse will be the end of you.
	\item Ever hear of the sea elves living in a city hidden under the River Styx on the 356th plane? Their touch steal memories and they sell them on the demonic market and\ldots what was I saying? Hey, who are you? Who am I?
	\item A lazy balor chief running the glorious demon city of Belzasharazar on the 45th layer wants a new pleasure palace constructed, but his succubus consort has other ideas. Burn the construction often enough and he'll lose interest, and you'll earn a powerful patron in the demon city.
	\item The latest fad in Sigil is the practice of keeping glowing dragonflies as party lighting, but these exotic insects are found only on the 232nd layer of the Abyss, a plane suddenly caught in a vicious conflict between two barely-known demon lords. Deliver a shipment of these blinky bugs to Sigil and you'll be invited to all the best parties, opening up other pecuniary possibilities.
	\item You've been approached by a cabal of wizard from the Prime, and they want information on the Black Tower. Infiltrate the Black Tower to steal their secrets, or turn sides and lead a strike force to the Prime to nip these nosy wizards in the bud.
	\item A cargo box shows up on your door with a valuable, but difficult-to-sell and dangerous product (like a shipment of souls), and several parties seem to think that you are the owner. Find a way to sell the cargo to a more powerful individual or else these parties will take it from you with extreme prejudice.
	\item An old associate has deeded you a confectionary in the City of Brass that specializes in demon chocolates and sweets. The Sultan has decreed that if you don't pay back taxes in city of Brass currency that he'll foreclose on the property (and your soul). Go on a whirlwind tour of the Abyss to collect enough stock to make enough quick cash to save the shop (and your hide).
\end{list}

\subsubsection{Ten High Level Adventures in The Abyss}

\listone
	\item Over a dozen pirate ships working the River Styx have been declaring that they are part of an Armada in order to pass along blame, and they are saying that you are the Admiral! Find and smash these lying upstarts or ``gently convince'' them to actually accept your command.
	\item A general in the Blood War has found a way to divert the River Styx and he is using these pathways to strike key demon and devil armies, killing both his enemies and competitors. Both sides are willing to handsomely reward the party capable of ending this maritime terrorism.
	\item Rumors and hints point to a powerful artifact being transported along the River Styx in a vessel of unusual design, and factions vie to be one to seize this powerful item.
	\item An island has appeared in a notoriously wide section of the River Styx, and dragons have been leaving the island to raid vessels. By your estimation, they should have amassed a horde that is fantastically large, even by the standards of dragons.
	\item The Mask of the Captain has resurfaced, a powerful artifact that creates and closes permanent gateways between the River Styx and the Prime Material Plane, and a powerful Prime nation has decided that they will increase the wealth of their people by plundering the cities of the Abyss.
	\item A trading vessel of unusual design flies into the Abyss, avoiding known planar pathways. It is crewed by a race that planar sages have never seen, and they offer trade goods of exotic and powerful design. Is this a simple trade mission, or an incursion from another plane by a new planar power?
	\item Orcus's agents have begun purchasing magic items related to planar travel, hinting at an invasion of enormous proportions.
	\item A demon lord of waning power has declared that his power and command over his layer of the Abyss will pass onto the individual to defeat him in single combat, and contestants have gathered at his fortress. Is this a ruse to gather the equipment and souls of powerful individuals, or is he truly offering a chance at the title of demon lord?
	\item An old friend brings news of the discovery of an empty city found in perfect condition in the Abyss full of trade goods and magic, but without a single living or undead soul. To take control of this city is to learn its secrets, and possibly gain its enemies\ldots enemies unconcerned with wealth or magical power.
	\item Yeenoghu has decided that you are a demon lord in disguise who is pretending at weakness as a ruse, and he is sparing no cost to send agents to test this theory. Convince him that you are a mortal, or strike him so hard that he ceases his attacks.
\end{list}


\subsection{High Adventure in\ldots Gehenna!}

First, it's the home of the Yugoloths. These outsiders are the dealmakers and compromisers of the fiendish world, so they might be involved in any plot or any scheme that makes its way across the planes. The land itself is series of volcanic mountains where sentients have forced their own existence into, jammed between the Hades and Hell and connect to the River Styx, so it is well situated between several of the Lower Planes. The works of mortals and immortals alike are eventually destroyed by tremors in this architect's nightmare of a plane and only the works of the gods last here. That being said, the entire plane has an angle that ranges from inconvenient (45 degrees) to unlivable (straight up), meaning life in Gehenna is far more socially dependant than other Lower Planes due to the fact that the only place to live is in the cubbies, caves, boltholes and settlements that litter this plane. It's not that you can't live in on the slopes and are forced to cooperate and co-oexist and you are forced to compete for space like in Hades, its just that life in Gehenna without a clique \textit{sucks}.

What do all of these things mean? It means that Gehenna is a realm for movers and shakers, a place where ``the deal'' and ``the juice'' matters more than any ideals or hopes. Even the petitioners of this plane are only concerned with power, and only the cruel nature of this plane keeps them chained here. Brinksmanship and counting coup and favors are the symbols of power here, and mere physical might or magical power take a backseat to one's ability to \textit{manipulate people with physical power and magical might}.

\subsubsection{Campaign Seed: The Yugoloths Want You!}

While Tanar'ri generals are known the power and might of their hordes and Baatezu armies are know for their frightening disciple and efficiency, it is the Yugoloth forces that are know for their subtlety and tactical elegance. They don't fight for reputation or honor; they fight to fulfill a contract and make a profit, making them among the deadliest generals in the Lower Planes.

You've joined that organization now, and the Yugoloths have need for elite squads of problem-solvers with a propensity for violence and a capability for discretion.

\subsubsection{Campaign Seed: The Grand Game in the Crawling City}

In the Crawling City, you've got to be useful or you're dead. You attached yourself to a minor Yugoloth noble, and he's begun using you as behind the scenes agents in the Lower Planar courts. With skill and nerve, one day you might earn the fear and respect of the fiends and become a player in your own right.

\subsubsection{Ten Low Level Adventures in Gehenna}

\listone
	\item A famous Yugoloth tactician is taking new students, and he's set a distinctly fiendish entry requirement: interested students publicly apply, and one week later the first to present themselves is accepted. The last time he took new students, no applicant ended the week alive enough to show up\ldots
	\item Small bands of petitioners have been gathering under the banner of a charismatic profit and raiding minor settlements in the night. Eliminate the threat by assassination or counterattack.
	\item Tremors! Minor rumblings and a trusted fiendish seer predict a major lava spout in a small settlement, destroying it, and several interestied parties want to loot it or the refugees in the final hour. Intercept these rogues, or plunder the settlement for yourselves.
	\item A minor Baatezu noble has been spotted in the Crawling City, and it's suspected that he's trying to hire away an elite group of Baatezu mercenaries when their current contract expires. Find and interrogate him, and the Yugoloths will repay this little favor. Whether he returns to his home plane with his life and valuables is your own business.
	\item The Double ``H'' Run. Despite the Blood War, some trade does exist between the Baatezu and the certain Tanar'ri, and the Yugoloths have their hand in it. Escort a package between the Nine Hells and Hades, avoiding agents from both fiendish factions who would use it to discredit their countrymen.
	\item The Masked Ball is next week, and a clever soul capable of learning the identities of several indiscrete parties can earn a few coins with the information brokers of Gehenna.
	\item A tiefling fop of a swordsman has defeated several prominent Yugoloth blademasters in mostly fair duels, despite his obvious lack of skill. Several persons of note would like to know his secret, and would pay even more to have that secret removed at an opportune moment.
	\item A mortal Sorceress of rare skill and infamous carnal desires has come to Crawling City, and entities of power are jostling to be known as one of her clients. Secure her cooperation for a client and win wealth; secure it for yourselves and win power and danger.
	\item A Tanar'ri of an unusually Lawful bent has entered the service of a Yugoloth of middling power. Discover the secret of his service, and that service can be passed on to a more worthy fiend, or kept as secret weapon for yourself.
	\item A Yugoloth of some influence has secured the services of an unusual household staff of famous, though powerless, Prime mortals. Spoil his coup by tempting, tricking, or intimidating these mortals into committing terrible blunders during the next power meeting, and you can harvest some amount of his influence.
\end{list}

\subsubsection{Ten Mid Level Adventures in Gehenna}

\listone
	\item A powerful Tanar'ri fortress has been bidded for destruction, and the Yugoloths will pay well for the group that finds an exploitable weakness.
	\item Several subcommanders have been bickering over the right to extract a powerful dragon of a military bent from Carceri, and rewards will fall upon anyone capable of securing this beast's services for the Yugoloth.
	\item A key planar touchstone in Hades will prove the key to an isolated fraction of the Blood War, insuring victory for one side or the other. Destroy this site, or profits for the Yugoloth in this conflict will fall dramatically. Secure it for yourself and turn it against both armies to secure a stalemate, and some fraction of the increased profits will fall your way.
	\item A powerful Yugoloth well- known for patronizing up-and-coming allies has declared that you are his protege, making you a target for his enemies Punish these enemies, and you might secure his patronage for real.
	\item A small army in the Blood War has wandered into Gehenna and is a threat to the Yugoloths. Destroy its leadership and loot its paymaster, and the Yugoloths will see that you are amply rewarded.
	\item A band of thieves have turned the Crawling City upside-down. Recover and return the valuable objects and win influence. Hold the objects hostage for future favors, and gain power that money can't buy.
	\item An unknown magical effect has stopped the feet of the Crawling City, and the first to discover the cause will win no small amount of gratitude from the ultraloth ruler of the city
	\item A series of businesses across Gehenna have been vandalized, an obvious turf war between two competing interests, and the first group to discover the identity of either player can earn a contract to accelerate or reverse the destruction.
	\item A spellbook of unique magics useful to a courtly mage has been found, and the owner of such magics would pay handsomely to not have his secrets revealed.
	\item A Baatezu diplomat has come to Crawling City, and he has decided that you will become his agent. Avoid a diplomatic incident without betraying the Yugoloths, and the powers that be may reward your ability to resolve such a conflict.
\end{list}

\subsubsection{Ten High Level Adventures in Gehenna}

\listone
	\item A cabal of liches have a sudden need for several rare components, and they are willing to trade battlefield magic for the first party to collect their list.
	\item It has come to your attention that several key subcommanders are plotting a coup over the control of the Crawling City. Shatte this conspiracy, or risj all and become its ringleader.
	\item The Yugoloths are looking to subcontract a dangerous mission on the prime against a noble house of demon-hunters. Get the contract and eliminate the hunters, or accept a greater bribe from the them to hold the contract long enough for them to counterattack.
	\item Key contracts for the Blood War have been stolen, and the first person to recover them will control a Yugoloth army of immense proportions.
	\item A war machine of great size and terrible power has been spotted in Mechanus, and such a device would fetch a king's ransom in the war markets of the Crawling City.
	\item A clique of fiendish spellcasters has set a challenge: the first entity to scour the planes for a specific but almost unique spell will earn a tome of their greatest spells. They expect one of their members to win and then resolve a dispute about claims of leadership of the clique, but an indiscrete servant blabbed the rules of the contract and now several interests seek to win the contest.
	\item A mortal noble of rare talents has entered the Crawling City and is recruiting agents for one goal: recover the contract that dooms his soul to property after death. To help him is to defy Yugoloth tradition, but the rewards might just be right.
	\item For some unknown reason, Inevitables stalk the Crawling City, and a clever stagemen might just be able to divert them towards one's enemies.
	\item The ruler of the Crawling city is missing, and chaos rules as several factions make a bid for power.
	\item Negative energy has begun to permeate the Crawling City and undead powerful enough to challenge of Yugoloth leadership have begun to rise. Is this an attack by a god whose portfolio is death, or some ruse to put the Yugoloth against an enemy they cannot defeat.
\end{list}


\subsection{High Adventure in\ldots Hades!}

One would think that Hades is among the worst Lower Planes to adventure in\ldots and they'd be right. The plane itself has the two nasty qualities: it poisons you with the Grays until you become a depressed Goth, and the Entrapping trait takes your memories and makes you want to never leave like a bad house guest. That being said, adventure is still possible, even for the least powerful adventurer.

It works like this: think of Hades as an unforgiving desert. Travel in this ``desert'' is only done by moving from oasis to oasis. These oases are towns and settlements that are built in such a way to resist the Grays and the Entrapping trait (see the Handbook of the Planes for an example of such a place). The only things that permanently live in the desert are creatures who are both immune to the Entrapping trait (like outsiders) or who have already succumbed to it (which has no other game effect other than ``become an NPC who doesn't want to leave''); these creatures also have some way of dealing with the Grays, and so they are creatures with SR 10 or better or are immune to Wis damage (like undead). This generally means that the ``desert'' that is Hades is filled with wild-eyed hermits and bandits and other forlorn spirits (which might be actual undead) living in the blasted and ruined geography of Hades, or creatures of some special power who skirt the edges of civilizations. Some NPCs you meet might just be Entrapped, but enter an oasis once in a while to recover from the Grays; other such characters might have ways to cure the Wis damage that the Grays cause, thus they are entrapped by Hades, but have no reason to enter an oasis, and some powerful creatures can resist The Grays almost indefinitely due to their high Saves.

Hades also has a few other features of note: It's the ultimate source of Evil of all types, and all of the evil outsiders are equally (un)welcome there. You could easily see a Yugoloth, a Devil, or a Demon without that being part of a plot device. Since Hades is the creation place for larva, the serving-sized petitioner souls of very evil people, the big evils of the multiverse have taken to fighting and brokering for this natural resource full time, and it all starts here. Night Hags and Liches are other players in this economy, but they are the freelancers in the publication of evil.

\subsubsection{Campaign Seed: The End of Oasis}

You've lived in the town all your life, and you know that only madmen and the 'loths live beyond the walls, but now you must travel the wasted plains to find your destiny.

\subsubsection{Campaign Seed: A World At War}

The Blood War wages endlessly and pointlessly across the Gray Wastes, with most territory never held or even claimed. The only things that have value in this whole plane are the occasional portal, oasis, or larva vein. Every other patch of land is a liability and \textit{no one} wants it.

\subsubsection{Ten Low Level Adventures in Hades}

\listone
	\item A Yugoloth has died while on a trading mission to your town, leaving behind a shipment of larva. To prevent your town from falling under the 'Loths gaze, you must take them to the nearest Yugoloth city for sale.
	\item A battle in the Blood War was fought near your town, and the undead fodder from that battle now terrorize the countryside.
	\item The leader of your town wants it to become a waypoint for message delivery, and he hires you to delivery the first messages.
	\item Something has been coming in from the wilderness to stalk the townsfolk. Will you track it back to its lair outside of town?
	\item The well has been poisoned, and you must find a new source of water for the town deep underground, far from the protective influence of your home.
	\item A terrible new disease has been ravaging all the nearby towns, and the Oinoloth has decreed that the town with the best gift will be spared.
	\item Devil agents want to construct a supply depot far from their own infernal realm, and will pay well for the location of new oasis(minus any current inhabitants).
	\item The nearest town has its eye on the riches of your town, and now has agents and a small force scouting for weak points and key personality to kidnap.
	\item Two caravans have entered your town at the same time, and now they have begun attacking and sabotaging each other at night in an effort to be the only one to leave.
	\item It's Election Day! Factions in town work against each other in an effort to become the new Mayor, and everyone knows that the loser will end up exiled to the wastes.
\end{list}

\subsubsection{Ten Mid Level Adventures in Hades}

\listone
	\item For some, mere death is not a real revenge. A powerful leader hires the party to defend a prison built in order to entrap entities in Hades in a spot unprotected from the effects of the plane.
	\item A legion of elemental soldiers have been led through a Gate, and they have succumbed to the effects of the plane. The first town leader to convince them to join him will gain a powerful fighting force.
	\item The Yugoloths have decided to annex your township, and only a show of overwhelming force or a high bribe will convince them to leave your town alone.
	\item Something is destroying oasis after oasis, isolating your town from the trade paths.
	\item A Gate has been opened to Celestia, and celestials have offered asylum to your township. Is this an opportunity to evacuate your town, or is this a fiendish trick to destroy your town?
	\item during a battle in an unfamiliar oasis, your party is trasnported to an unknown location in Hades, far from any oasis. Can you find your way home, or even to a safe location before you succumb to the planes traits.
	\item A series of Gates have opened up to a distant region in Hades, and townships now vie to control the altered landscape.
	\item The river Styx is flooding, and threatens to wipe out several cities built on its waters, including your town's primary trade partner.
	\item A caravan of bioloths has entered your town, beginning a carnival that threatens to enslave everyone.
	\item A powerful Yugoloth has been working against the Oinoloth, and your town is caught in the cross-fire. Will you work against it, or for it?
\end{list}

\subsubsection{Ten High Level Adventures in Hades}

\listone
	\item Rumors hint that your town holds a mystical font that can make anyone bathing in its waters immune to Entrapping and the Grays, and several powerful forces vie to control this wonder.
	\item The Blood War has boiled up in your region, and a clever party could benefit from working with one side or the other, or even both.
	\item A powerful devil decides that he needs more exotic troops, and he is willing to extend his protection to your town if you can capture powerful creatures from several legendary parts of Hades.
	\item Angels have gained a foothold into Hades, and have decided that your town is the first to be ``purified.''
	\item During a particularly brutal battle in the Blood War, a powerful artifact has been lost. The first to regain such an artifact might be a threat to even the Yugoloths.
	\item A cabal of Night Hag Sorcerers have decided to harvest your town, and the only way to catch them is to breach the barrier between your plane and theirs.
	\item A powerful outsider offers his services to your town, saying that he can create planar gates. Such a resource would transform your town into a planar metropolis, but can it survive the attention it will attract?
	\item A powerful Warlord has taken over rulership of several towns, attempting to build an empire in Hades, and your town must either gather the forces of the surrounding towns to fight this menace, or usurp rulership for yourselves.
	\item A dangerous wizard has found a way to concentrate the evil of the plane, and he is using this evil as weapon that can corrupt even the Yugoloths to his person brand of evil.
	\item Strange and terrible diseases are taking their roll on all the inhabitants of Hades, and the only way to stop these plagues is to assume the mantle of the Oinoloth.
\end{list}

\section{High Adventure in the Elemental Planes}

\subsection{High Adventure in\ldots The Plane of Fire!}

More than any other Inner Plane, adventures in the Plane of Fire tend to take place in planar bubbles. If you can breathe water, the majority of the Plane of Water is basically just a lukewarm benthic zone, and it's the kind of place that Sahuagin might live without even realizing that they weren't on the Prime. But the archetypical expanse of the Plane of Fire is just, well, fire. It's like the churning surface of a sun that extends in all directions for eternity. And while it is colder and less destructively melty than the all-consuming plasma of an actual star, it's still basically just an endless expanse of fluid, dangerous, useless fire. Did I say useless? You bet, because heat engines actually work by heat difference, so from the standpoint of residents of the Plane of Fire it is actually cold that you use to run a power plant. The fire in between everything is just like the worthless emptiness of deep space except that it will also catch you on fire. Forget Carceri or the Gray Wastes - the Elemental Plane of Fire is the worst place in the D\&D multiverse.

But just because it's a horrible place, even the worst place, doesn't mean that there isn't stuff you want there. And just because it is the most inhospitable place imaginable, doesn't mean that low level characters can't adventure there. The key is the planar bubbles exist. That is basically the only reason that anyone gives the Plane of Fire the time of day. The most important bubbles are Prime Bubbles. These are areas of land and sea with atmospheres, that happen to be shaped like a Ptolemic world - a circle of land and sea with a hemisphere of atmosphere above. And of course, outside that is endless roiling fire. So the ground gets kind of rocky and parched, what with the sky being a never-ending holocaust without reason or respite - essentially it's like living in a Dragonforce video.

Those Bubbles aren't just the only place your characters can survive, they are the only places that any of the residents give a damn about. Remember that even if you happen to be a fire elemental, you still eat ``flammable" materials if you want to grow any larger, and those only come from the ``cold" spots. So not only is the practically usable terrain in the Plane of Fire very small compared to the plane's total volume, but the space between is inhospitable void. And not just inhospitable void - it's opaque inhospitable void. Standing on one of the floating islands, you can't even see the other islands. When you look into the inferno you have no way of knowing whether the next place of value or substance is a few centimeters or a few parsecs of burning emptiness in any particular direction.

So what does that mean for the low level adventurer? It means that practically speaking, no one expects your character to want to go anywhere that would cause them to actually catch fire. No one else does, not even the planar residents who are actually made out of fire. So it's totally workable as an adventure locale at any level. The Plane of Fire is run by the Efreet Sultans, and that gives the entire place a very fantasy-Arabic feel. Ignan, the approved lingua franca of the universe, is explicitly based on Arabic. That thing where Arabic calligraphy kind of looks like living flame? Yeah, they went there. While the Djinn have a presence in the Plane of Air and the Dao have their own Caliphate in the Plane of Earth, the Sultan of Fire owns the Plane of Fire. Because there is hardly any real estate, and finding or getting to it is in most cases a Wish Economy proposition.

The Plane of Fire is your chance not only to throw out every Arabian Nights cliché you know, it's also a place to throw in 1950s sci-fi left and right. Basically everywhere that anyone lives is one of those bubble colonies or asteroid mining facilities from the Heinlein juveniles. To get from on planetoid to another requires getting into a heat protected shell and then throwing yourself from one to the other. Once you leave a Planar Bubble, there's no gravity or wind, so it's basically exactly like one of those personal space ships that were talked about in the old Republic Serials. Some of them are even saucer shaped.

Campaign Seed: Conquest of the New World: Even beings of pure fire cannot see far into the firmament, and so it is that new places of interest are ``discovered" all the time in the most surprising of places. The iron ships that travel between bubbles need exacting angles of departure, because once they are off course, there's really no measurement you could take to figure that out (and often nothing you could do about it if you did). So a new island might well be just 1 degree off an established trade route. And once a new land is discovered, it's Columbian Conquest all over again. This new world may well have occupants that object to being ``discovered" let alone colonized, but on the other hand they could seriously have fountains of youth or cities of gold.

Exploring a new Planar Bubble in The Plane of Fire is a good way to bring out any kind of D\&D adventure you want. The PCs have literally no idea what they might find there, and there's a very great incentive to keep exploring since even wood and water are hugely valuable resources once you get off this gravity well and back to a more civilized one. You don't just get to loot the temples of stone using pyramids, you also get to confront their heathen demon gods, find relics of fallen ancient civilizations or the secrets of long forgotten wizards. A Planar Bubble that ``no one" knew about on The Plane of Fire is about the safest place in the entire damn multiverse, so anyone who did know about it could have stored or imprisoned, well, anything there.

\subsubsection{Campaign Seed: Janissaries of the Fire Sultan:} The Efreeti sultan is cruel, but he is not stupid. And he is well aware of the limitations of being a guy who is on fire all the time when the only things in the entire universe that have any value are things that are not on fire. And so it is that the Fire Sultan has children of non-flaming races raised in his employ. These children grow up to be Janissaries: creatures who act as agents for the Efreeti and build their empire without incidentally burning it down. There is a lot of room for advancement in the Janissaries, the Sultan genuinely values your skills more than he values the skills of the other Efreeti. First of all, there is basically no chance of you ever actually becoming Sultan (you just don't have the right fire in your blood), and secondly, unlike a real Efreet, you can do stuff that the Sultan cannot. There are a lot of politics that go in court, and the rest of the Efreeti have a tendency to rather resent Janissaries; while at the same time doing their damnedest (literally) to avoid any direct confrontation with something the Sultan considers to be ``his." Do the Sultan proud, and you can have your every wish granted (as long as that wish doesn't include becoming Sultan or leaving the Sultan's employ). Fail him sufficiently, and he may allow the more jealous members of the court to take their frustrations out on you.

\subsubsection{Ten Low Level Adentures in The Plane of Fire:}

You're getting the report from the overseer of the pipeline workers. The Kobold tells you that they aren't getting as much water as expected because\ldots

\listone
	\item A group of Firenewts has claimed that the pipeline runs through their tribal lands and have begun monkey wrenching.
    \item The water reserves aren't as extensive as hoped near the surface, and the pipeline will have to be extended into the caverns.
    \item Superstitious fears have broken out among the workers, they speak of burning snakes.
    \item Drilling has broken through to inferno before expected, this rock isn't as stable as we'd hoped.
    \item The water has some kind of creatures living in it. Creatures that live in water.
    \item Some creatures have been bringing clouds of smoke with them when they crawl over the pipeline.
    \item A rival mining group is siphoning water from our reserves.
    \item Some guy who looked like a Yak has paid more than enough money for the land to get the crew to drill elsewhere.
    \item Everyone who touches the water seems to forget what they were doing.
    \item The water has been draining up to the mountain.
\end{list}


\subsubsection{Ten Mid Level Adentures in The Plane of Fire:}

Laughing, the Efreet relays the news. It's never a good thing when an Efreet is happy to tell you something, and this is no exception because\ldots

\listone
    \item Some group of xorn came in with a load of opals just two days ago. You're going to have to go farther afield if you want to liquidate those gems.
    \item It seems that while you were out, they've made a new appointment of Sheriff.
    \item The land title has been revoked and given to Hakim
    \item Surtyr wants his money back. Now.
    \item Yak Men have taken over the entire city.
    \item A Red Dragon has claimed the water reserves.
    \item The Bubble has begun wobbling, the only way home is by wish.
    \item The princess is in another palace.
    \item The gnomes have themselves a Frost Salamander that they are keeping alive somehow, and mere flammables are virtually worthless here.
    \item The great astrolabe has been shattered.
\end{list}


\subsubsection{Ten High Level Adentures in The Plane of Fire:}

The Iron Flask isn't completely inscrutable, and your research indicates that it contains\ldots

\listone
    \item One of the Sultan's uncles.
    \item A potion of Immortality
    \item A gate to a deep layer of Baator
    \item The heart's blood of Baphomet
    \item The phylactery of a powerful Lich
    \item A decree from the previous Sultan
    \item A heretical Genie who was imprisoned for predictions that appear to have come true.
    \item The crown of Pyriria
    \item The condensed gaseous form of a Chaos Roc. One of several, if the accompanying letter is to be believed.
    \item The laughter of Queen Chandra.
\end{list}


\subsection{High Adventure in\ldots The Plane of Water!}

The Elemental Plane of Water is an endless expanse of relatively static water permeated by a soft ambient light. There is only gravity if you want there to be, and the incompressible medium makes gravitational movement slower than walking. But nonetheless, you can move pretty much anything at the rate of about three and a half miles per hour just by ``falling" or ``rising" with it. Outside of an occasional ``pressure zone" the entire plane is pretty much one giant coastal shallows, with a water pressure at any point about that of being under just a meter of water. The Elemental Plane of Water is also the largest place in all of the D\&D multiverse in real terms.

Sure, it is ``infinite in all spacial dimensions and time" just like all the other Inner Planes, but it is markedly different in that every point in the Plane of Water is also a place. None of it is empty or impassable, it's all just made of water. So you can go and be anywhere, and you won't be ``between" things because the place you will be will be an actually stable location in and of itself that you can put stuff down in or give directions to. Every point. And that means that there are more places to be, and by extension more stuff than in any of the other planes. Indeed, like how on Earth about 70\% of your body is water, and about 70\% of the world's surface is water, about 70\% of the creatures and structures in the Inner Planes are on the Elemental Plane of Water. And like the oceans of every Prime World - the Plane of Water still gets less press than the other planes because it is full of water. In general, things on the Elemental Plane of Water stay where they are put, with little in the way of mobility. This means that when there is an air bubble, people can pretty much run around in it without fear that the air will bubble up away from them. Because there is no up. This also means that disposal of bodily waste is ``gross." There is nowhere to ``bury" anything, so stuff that comes out of you just sits there accusingly. Fortunately, there are a lot of plants and little animals that will come clean that up, but this process is no nicer to watch on the Plane of Water than it is anywhere else. There are areas where, for whatever reason, the ambient water is flowing with some kind of current. Some of these currents are incredibly fast, but as a rule they are not that ``large" and full mixing doesn't happen. The fresh parts of the endless sea stay fresh and the salty parts stay salty. The hot parts stay hot and the frozen parts stay frozen.

The Marids are, individually speaking, the most hard core of the Genies. However, the Great Padisha of the Citadel of Ten Thousand Pearls is basically just the mayor of a town of one thousand occupants. One thousand occupants where one in five of them can grant frickin wishes, but just a thousand all the same. You could seriously move around the plane your whole life and never come within the demesnes of a Marid. Each Marid considers themselves to be royalty and to rule all they survey - which is basically true but functionally meaningless because you normally can only see about 60 feet on the Plane of Water because there's microbes and sand and stuff in the water pretty much everywhere. This contrasts sharply with the Sahuagin empires, some of which are ten thousand miles across (note: this is bigger than the entire Earth, and we're talking volume rather than surface area, so some of these empires have populations that measure in the tens of billions), but which due entirely to the sheer vastness of the plane and the smallness of any visitor's personal experience of the place (60 feet or so around them and movement as fast as they can sink or swim), it is still entirely likely that you've never heard of any of them.

While the visibility on the plane of water is total crap, the audibility is intense. Water is nearly incompressible and it's nothing but water forever and ever. Sound pretty much follows the rule that any noise is four times as quiet when at twice the distance, with no additional dampening from the atmosphere. Any noise ever propagates with such totality and speed that to the human visitor it is nothing but a constant deafening roar. Indeed, since sound travels so much faster in water than in air, any non-aquatic visitor needs 10 ranks of listen to even have a hope of locating any sound. Even sounds that are loud or close enough to be distinctly made out sound like they are from “everywhere.” This is not a problem that natives have, and indeed a Sahuagin can locate you by the sound of the water against your skin.

Secession is constant in the Plane of Water. Anyone can just pick up their house and leave at a bit over 3 miles an hour. Between this tax day and the next, you could have moved your house about 29,000 miles – which is noticeably more than the circumference of the Earth. And when you factor in the fact that there is no guaranty that anyone will find your house if you move it 100 meters, one can see that you can vanish from a government's radar very easily if you are not actively imprisoned. The standard therefore is to be required to pay taxes to the local authorities at the beginning of the year and subsequently be allowed to provide proof of citizenship to receive services for the following year. Surprisingly, much of the civilization in the Plane of Water is actually more recognizable by connoisseurs of modern nationalism than are the kingdoms of other planes of existence. If you want to live in a “country”, you have a citizenship card and rights and social services and stuff. Anyone who doesn't want those things (or doesn't want to pay for them), just leaves and lives elsewhere in the roaring darkness.

\subsubsection{Campaign Seed: Heralds of the Empire:} Sound travels fast under water, but news does not. When a new nation takes hold of a region, it can take a long time to even find everyone who lives there. And so it is that any nation state or empire needs to send out groups to patrol their territory. Not just to keep an eye on the citizens and provide whatever services the empire provides to the hinterlands – but also to keep the maps updated. After all, any part of the empire that hasn't been patrolled in the last month could seriously have had someone move a castle from 4000 kilometers away to there in the meantime. As representatives of the state being sent into areas of water that the state either has not been to yet or has not been to recently, the PCs could encounter pretty much anything at all. And they have a built-in plot hook that encourages them to interact with anything they fine. Whether they face level appropriate wandering monsters, social encounters with dubious locathah, or hostile empires coming the other way, the PCs can plausibly encounter level appropriate opposition at any level.

\subsubsection{Campaign Seed: Tidal Merchants:} The great tidal streams are currents that move with surpassing speed. Those who ride them can get places that are very far away in very short periods of time. And that's saying something in a world where seriously anyone can tie themselves to their cargo and “sink” 80 miles a day just by deciding to. The currents don't just provide fast transport, they also provide a path, a place to go. And so it is no surprise that as one drifts along the tidal stream, one can hear the drums of civilization from all sides just as you can see the glowing lights of fast food joints while driving on a freeway on Earth. Traveling along the tidal streams brings one from one urban development to another with all the vast spaces between literally washed away.

\subsubsection{Ten Low Level Adventures in the Plane of Water:}

The old Locathah is certainly interested in your proposal. But he says he has other problems\ldots

\listone
    \item Sahuagin raiding has hit several nearby kelp farms.
    \item Shark attacks are on the rise.
    \item No one seems to want to buy the sponges he has been growing.
    \item His daughter has the ick.
    \item Food supplies are running low.
    \item The fish are migrating out.
    \item A local hot spot is attributed to Fire leakage.
    \item Those who die seem to come back as zombies.
    \item A siren has been throwing her weight around.
    \item Pirates have seized the oyster bed. 
\end{list}

\subsubsection{Ten Mid Level Adventures in the Plane of Water:}

The sound of drums has called you to the activities like moths to a flame. When it comes into view, it appears to be\ldots

\listone
    \item A brass sphere, with no immediately obvious entrances.
    \item An army of skeletons.
    \item The coral towers of a merfolk city; they look sick.
    \item An ice factory.
    \item Angry tritons.
    \item A giant eel that had been mimicking civilization sounds by slapping rocks together.
    \item A Sahuagin kelp outpost.
    \item A family of scrag wreckers.
    \item A Marid Sattrapi.
    \item Some sort of mechanical vessel shaped like a lobster. 
\end{list}

\subsubsection{Ten High Level Adventures in the Plane of Water:}

You've broken into the massive mechanical manta ship. Inside you find\ldots

\listone
	\item Spongy, organic passageways... this ship is alive.
    \item The crew are long dead and dust.
    \item The captain's log mentions you by name.
    \item Kuo-Toan pirates and their Yugoloth servants.
    \item Sack after sack of dream dust.
    \item These look like dragon eggs.
    \item The spectral pirates who run this thing.
    \item A cargo hold full of wild eyed prisoners.
    \item A cargo hold full of non aquatic and fearful prisoners.
    \item The ship's wizard captain and his crew of blood-indifferent golem pirates.
\end{list}


\subsection{High Adventure in\ldots The Negative Energy Plane!}

If you're even considering running a game in the Negative Energy Plane, it is very probable that you are using Playing With Fire morality for your necromancy. This is in large part because every writeup of the NEP ever made has assumed Playing With Fire, and that indeed it is precisely these descriptions that give people the best scriptural ammunition against Crawling Darkness. But also because if Negative Energy is inherently evil, the plane becomes incredibly boring. We already have the Gray Wastes of Gehenna, so there's no real point in having another gray desert made out of ultimate evil.

The game provides two supposedly different Negative Energy Planes for you to consider. One is made out of Major Negative Energy Dominant with patches that are Minor Negative Energy Dominant, and the other is made out of Minor Negative Energy Dominant with patches of Major Energy Dominant. Well, anyone who has ever looked at a splotchy cow knows that whether you have a black cow with white spots or a white cow with black spots is entirely a matter of perspective. Since the NEP is infinite, both Major and Minor patches are infinite in size and in scope, so it really makes no difference at all which one you are nominally using. From a practical standpoint, either way you're going to be in either a Major or Minor Negative Energy area, the adventure location you are going to next will either be in the same area or a different one, and if you go far enough in any direction you will go from one to the other. And anyway, both Minor and Major Negative Dominant ares are totally fatal to living creatures, and completely harmless to undead and constructs, and the baleful effects are completely negated by negative energy protection or attune plane. So seriously: who cares? Since the only actual difference is the unprotected living creatures crumble to ash in Minor Dominant and are transformed into wraiths in Major Dominant, our suggestion would be to go with Major Dominant most of the time. It's largely academic, because outside the planar bubbles there is no air (so without some sort of magical attunement, every living creature is just going to die of asphyxiation, negative energy or no).

The Negative Energy Plane hates life. It hates the good, and it hates the wicked both the same. It does not condone or aid harm or murder, it simply greedily and expeditiously extinguishes any life exposed to it. But if you're alive that's basically no worse than the vacuum of space, and if you're not alive it's a whole lot better. For those who are undead, non-living, or have the right kind of protections, the Negative Energy Plane is a lot like any other void plane of the D\&D cosmology save that there is no ambient light source. Comparisons can be made to Limbo, the Astral Plane, and of course: the Elemental Plane of Air. The difference is just the fact that it is unlit, and therefore looks like the night sky rather than extending out to a gray fog where the soft glow of the ambient light eventually wipes out anything you could see.

Once you factor in the Planar Bubbles (which as an ironic statement, are called ``doldrums" by Negative Energy inhabitants), the Negative Energy Plane is basically exactly the same as our universe. If you were on a prime bubble, you pretty much would only with difficulty be able to know that you weren't on a Prime. There's a dark hostile, airless void outside your planet, and there's absolutely nothing stopping any light source of any distance from eventually sending its ray to you. So the sky above you is black and full of tiny lights. Well, it wouldn't really be that difficult to figure it out, because absolutely everyone can fly just by thinking about it. And the lights in the sky are just like what ancient people thought about them: some of them are very large and far away (like Elemental Fire bubbles that function as stars), and others are more modest light sources that are more reasonable distances. The intrinsic flight includes not only hovering, but also acceleration that is only relativistically limited. You can accelerate at 1G or more by sheer willpower as long as you want without energy expenditure. So a trip from the Earth to Mars would take less than 5 days even at its most distant point (assuming that they were both on the Negative Material Plane). So titanic, even solar distances are quite reachable. Also of note is that the directions to Neverland (Third star on the left, and straight on 'til morning) are completely reasonable directions, and represent another planar bubble that is about 2 million kilometers away. Like all regions of subjective gravity, going ``towards" a point will automatically have you accelerate continuously to the halfway mark and then have acceleration away from it for the rest of the journey, so you never ram into anything at relativistic speed.

The distances between things in the Negative Elemental Plane are truly vast, but travel is so easy that from a practical standpoint, things in the Negative Energy Plane are actually kind of ``happening." The exception of course, is unlit structures. These are called ``Castles Perilous" by the locals, and making one is pretty much a declaration that you under no circumstances want visitors. After all, without giving off any light, you're basically about as findable as any rock out in deep space is in the real world. The only ways to find one are to happen to see them passing in front of a light source or to shoot one's self off into the void looking for the automatic deceleration that accompanies moving towards a real object - and even knowing that second one is an option requires the kind of math you'd need a Knowledge (Planes or Engineering) DC 25 test to do.

An important thing to consider is the presence of Voidstone. It's a special material that will destroy and absorb any creature (even undead creatures) if they come into contact with it for a few seconds. Truly badass creatures like dragons and gods might be able to hold it for a minute or two before being eradicated from existence, but as you might imagine, that stuff is still in huge demand for making into weaponry. Since it doesn't do anything to other inert elemental material like, say metal tools, it ends up being quite workable and incredibly valuable. Voidstone is planar currency for obvious reasons - but finding it is very difficult because it's not very large, pure black, and forms in the middle of large sections of empty void.

But perhaps the most important point about the Negative Energy Plane is that the parity with the Positive Energy Plane is not complete. Living creatures are natural, so they have no protection from being exposed to ``too much" positive energy - and they can totally explode. Undead creatures are unnatural and only exist at all because they are supported by magic to siphon off a specific and measured quantity of negative energy. So they don't ever ``explode" in Negative Dominant areas, whether they have ``protection" or not. As such, groups of intelligent undead often make homes out of Castles Perilous in the middle of strong Negative Energy Vortices. Because seriously: why not?

\subsubsection{Campaign Seed: Death World:} A Doldrum region in the Negative Energy Plane is a lot like Neverland if it was made by American McGee. Everyone can fly like Peter Pan, and each region fills up with weird crap from all over the planes like tribes of Indians, mermaids, and pirates. However, these places are also constantly under assault by a low level rain of zombies from space. That's not a joke, undead beasts literally float around in the void and choose to fall towards points of light. So if you're running around Pixie Hollow, there is a not insignificant chance that some undead monster is going to fall out of the sky and go on a rampage. This setup allows for very reasonably scaling D\&D adventuring. After all, if the PCs become masters of their surroundings and conquer the Maze of Regrets, you have a totally reasonable excuse to have a level appropriate undead army fall from space and tart causing havoc. In the meantime, even though the levels of Negative Energy aren't high enough to snuff the life out of anything, they are leaking into Doldrums enough to make things subtly creepy and unpleasant. Feel free to use any Ravenloft clichés you want. Or just American McGee it up - people live on a fricking Death World, so have just messed up stuff happen all the time. Have cats croak out ``help\ldots me\ldots" for no reason. Have thorns drip unexplained blood. Have trees inexplicably drain of color. Inhabitants go crazy and start eating pieces of themselves. Go nuts.

\subsubsection{Campaign Seed: Welcome to the Void Heart:} There is a city built into the inside of a one-mile diameter iron Dyson Sphere which is called ``Heart of the Void" or ``Deathheart" depending on who you ask. Some sages built a city there a long time ago and eventually an army of the undead broke in and murdered everyone. Tonight it's a minor necropolis that is broken up into factions that fight each other for domination. And I know what you're thinking: so what? I mean, that's only 3.14 square miles of city, and even though it has the population density of New York, it still only has 70,000 inhabitants, and a lot of them are ghouls. But the really important thing is what the sages used to do, which was to track all the objects in the Negative Energy Plane. All the rocks of Voidstone, all the Castles Perilous, everything. No one knows how they did it, because some vampiric minotaur killed the last of them a few hundred years back and feasted on her heart - but they did leave notes. All over the city, there are books filled with page after page of descriptions of the size, shape, and location of various objects in the void. There are a lot of adventures there: some books are useless without other books in the same series; some books are the possessions of hostile undead gangs that either do or do not know how valuable they are; and many books detail the locations of items and structures that are themselves interesting and valuable adventuring locales.

\subsubsection{Ten Low-Level Adventures in The Negative Energy Plane}

The ghoul chitters and licks his parched lips. Seemingly reluctant to proceed, he whispers\ldots

\listone
	\item ``You may have defeated me, but there are a dozen more on their way\ldots"
    \item ``Fellnax wants his coins. He wants them bad\ldots"
    \item ``You can kill me, I'll never tell you were the diadem is."
    \item ``I knew someone would find me. I didn't know who, but after the Hellmire job, I knew it was only a matter of time\ldots"
    \item ``These bones\ldots these bones are mine\ldots"
    \item ``You traitors! I'll feast on you!"
    \item ``Do you have the scrolls? My master said you would have the scrolls\ldots"
    \item ``You don't look like Fellnax's men."
    \item ``Fellnax sent me to tell you, to tell you that he is going to kill all of you\ldots"
    \item ``We still have the girl, please don't do anything we'd both regret."
\end{list}


\subsubsection{Ten Mid-Level Adventures in The Negative Energy Plane}

It's good to meet another outworlder. But there's something weird about this guy\ldots

\listone
    \item There are faint sobs coming from his backpack.
    \item He casts no reflection.
    \item Everytime he mentions the Castle Perilous he came from, he looks over his shoulder.
    \item There are the scars of bite marks all over his arm.
    \item When he talks about his family getting eaten, it's like he doesn't even care.
    \item When he mentions the golden statues of Kath, it's like he doesn't even care.
    \item He seems genuinely relieved to be here.
    \item He steps right over the ghoul corpses as if that was a normal thing.
    \item He has one of Fellnax's amulets. Or something that looks just like one\ldots
    \item There is a wraith following behind him, one that looks just like he does\ldots
\end{list}


\subsubsection{Ten High-Level Adventures in The Negative Energy Plane}

You've got a fix on the Voidstone you were looking for. Unfortunately it's\ldots

\listone
    \item Suspended inside the chest cavity of a dracolich.
    \item Worshiped by a death cult of Kuo Toa.
    \item Inside a Castle Perilous named ``Doom Watch"
    \item Been made into a sword by a mad Duergar.
    \item Guarded by a Void Shadow.
    \item Guarded by a Shadow Dragon
    \item The Tomb of a fallen god.
    \item Locked in Lethe Ice.
    \item On the far side of an Allip Belt
    \item In the workshop of a Master Skincrafter.
\end{list}