\section{Other Spheres}

Not all spheres are necessarily evil or fiendish; spheres themselves are a good mechanic for all outsiders, and spell-like abilities gained over time in general. These spheres are used by non-fiendish sphere users such as celestials, elementals, and the Curator class. Elemental spheres have the element tag that they belong to ([Earth], [Fire], [Wood], etc), and may also have the [Fiend] tag. An [Elemental] tag indicates that the sphere can be taken by any type of elemental. These spheres follow all of the same rules as Fiendish spheres, but unless they specifically have the [Fiend] tag and are taken as a Fiend, no Fiendish traits are gained for possessing access to a given sphere.

\begin{multicols}{2}

\featname{\hypertarget{sphere:aegis}{Aegis}}
\textbf{Special: }{You radiate an aura of protection out to 10 feet. All allies in this aura receive a resistance bonus to saves OR a deflection bonus to AC equal to character level / 3, rounding up.}
\newline\textbf{Special Bonus: }{If you upgrade this Sphere to Advanced access, your aura of protection grants a resistance bonus to saves AND a deflection bonus to AC.}
\newline\textbf{Special Bonus: }{If you upgrade this Sphere to Expert access, your aura of protection goes out to Short range instead of 10 feet.}
\sphere
{Mage Armor}
{Resist Energy}
{Protection From Energy}
{Stoneskin}
{Extended Globe of Invulnerability, Lesser}
{Energy Immunity (As Resist Energy, but grants Immunity instead of resistance)}
{Spell Turning}
{Protection from Spells}
{Foresight}
\spherecont{19 Double Extended (lasts for 3 times as long as normal) Mind Blank}

\featname{\hypertarget{sphere:air}{Air} [Air], [Fiend]}
\textbf{Special: }{Elemental - Your Fly speed improves by one maneuverability class and 10'. If already perfect, it improves by 20'. Fiend - You gain the (Air) Subtype and the above ability. If you have no Fly speed, you instead gain a Fly speed of 15' (Good).}
\sphere
{Expeditious Retreat (Also applies to Fly speed)}
{Gaseous Form}
{Wind Wall}
{Control Winds}
{Overland Flight}
{Summon Nature's Ally VI (Cast as [Air] spell only)}
{Control Weather}
{Whirlwind}
{Telekinesis, Quickened (Violent thrust only)}
\spherecont{Summon Elemental Monolith ([Air] only, no need to concentrate)}

\featname{\hypertarget{sphere:arctic}{Arctic} [Ice], [Fiend]}
\textbf{Special: }{Your spell-like abilities with the [Cold] descriptor leave a frozen slick over all surfaces in their areas or touched by their Effects. This slick functions as a Grease spell, and lasts for two rounds.}
\sphere
{Chill Metal}
{Icy Sphere (as Flaming Sphere, but Cold)}
{Sleet Storm}
{Polar Ray}
{Fire Shield (Chill shield only)}
{Transmute Mud to Rock (new rock is frozen and gets ice slick)}
{Prismatic Spray (has [Cold] descriptor)}
{Flesh to Ice, Quickened}
{Comet Swarm (as Meteor Swarm, but Cold)}
\spherecont{Earthquake with added Ice Storm (covers entire area of Earthquake for full duration)}

\featname{\hypertarget{sphere:courage}{Courage}}
\textbf{Special: }{You are immune to fear.}
\sphere
{Bless (can be used as a swift action)}
{Heroism}
{Remove Fear}
{Heroes' Feast}
{Righteous Might}
{Greater Heroism}
{Break Enchantment (can be used as a swift action)}
{Freedom}
{Mass Righteous Might*}
\spherecont{Greater Heroism (can be used as an immediate action)}

\featname{\hypertarget{sphere:creation}{Creation} [Elemental], [Fiend]}
\textbf{Special: }{You gain a bonus [Item Creation] feat.}
\sphere
{Unseen Servant}
{Make Whole}
{Minor Creation}
{Stone Shape}
{Major Creation}
{Fabricate}
{Wall of Iron}
{Magnificent Mansion}
{Wish (Wealth and Magic Item only for free, spend for Raise the Dead and Increase power of item only)}
\spherecont{Genesis (SpC)}

\featname{\hypertarget{sphere:dust}{Dust} [Air], [Earth], [Shadow], [Fiend]}
\textbf{Special: }{Your area spell-like abilities may, at your option, stir up a stinging dust cloud, inflicting a -2 penalty to Perception checks and a -1 penalty to attack rolls for one minute to any creature that does not successfully save against the spell. The cloud lasts one round, and its effects last one minute after the affected creature takes its last increase.}
\sphere
{Gust of Wind}
{Glitterdust}
{Sleet Storm ([Air], not [Cold], descriptor. Fine dust has same effect as ice)}
{Disintegrate}
{Cloudkill}
{Mass Blindness (as Blindness/Deafness, but Blindness only, 1 creature/level)}
{Creeping Doom}
{Horrid Wilting}
{Summon Golem (Clay Only)}
\spherecont{Disintegrate (usable as an immediate action)}

\featname{\hypertarget{sphere:electricity}{Electricity} [Air], [Earth], [Shadow], [Fiend]}
\textbf{Special: }{You gain Immunity to Electricity.}
\sphere
{Lightning Bolt}
{Shocking Ray (as Scorching Ray, but electric)}
{Orb of Electricity}
{Chain Lightning}
{Electric Shield (Sonic Shield, but Electricity)}
{Thunder Field}
{Power Word: Stun}
{Greater Shout, Electric-Substituted}
{Lightning Bolt, Maximized and Uncapped}
\spherecont{Chain Lightning, Quickened}

\featname{\hypertarget{sphere:ether}{Ether} [Elemental] (except Shadow)}
\textbf{Special: }{Your equipment all gains the Ghost Touch property.}
\sphere
{Alarm}
{See Invisibility}
{Blink}
{Baleful Blink}
{Mage's Faithful Hound}
{Ethereal Jaunt}
{Greater Arcane Sight}
{Maze}
{Etherealness}
\spherecont{Gate (Travel version only)}

\featname{\hypertarget{sphere:exorcism}{Exorcism}}
\textbf{Special: }{You gain the ability to turn undead three times per day as a good-aligned cleric of the same level as the class that granted you this sphere. You cannot use these turning attempts to power divine feats.}
\sphere
{Protection from Evil}
{Consecrate}
{Magic Circle against Evil}
{Dispel Evil}
{Disrupting Weapon}
{Banishment}
{Holy Word}
{Sunburst}
{Undeath's Eternal Foe (SpC)}
\spherecont{Freedom}

\featname{\hypertarget{sphere:healing}{Healing}}
\textbf{Special: }{Any spells of the Healing subschool that you cast (including SLAs) have a range of 30ft, unless it would normally be longer.}
\sphere
{Cure Moderate Wounds}
{Lesser Restoration}
{Cure Critical Wounds}
{Mass Cure Critical Wounds}
{Heal}
{Restoration}
{Ressurection}
{Mass Heal}
{Heal (can be used as an immediate action)}
\spherecont{Greater Restoration (can be used as an immediate action)}

\featname{\hypertarget{sphere:judgement}{Judgement}}
\textbf{Special: }{You gain Intimidate as a class skill, and may demoralise an opponent as a swift action.}
\sphere
{Doom}
{Mark of the Outcast [SC]}
{Awaken Sin [SC]}
{Castigate [SC]}
{Sicken Evil [BoED]}
{Wages of Sin [BoED]}
{Tomb of Light [BoED]}
{Last Judgement [BoED]}
{Rain of Black Tulips [BoED]}
\spherecont{Sanctify the Wicked [BoED]}

\featname{\hypertarget{sphere:light}{Light}}
\textbf{Special: }{You shed light like a torch, and can suppress or resume this ability at-will. This ability is considered extraordinary.}
\sphere
{Faerie Fire}
{Searing Light}
{Daylight}
{Sunbeam}
{Sunburst}
{True Seeing}
{Power Word Blind}
{Prismatic Wall}
{Prismatic Sphere}
\spherecont{Sunburst (can be used as an immediate action)}

\featname{\hypertarget{sphere:magic}{Magic}}
\textbf{Special: }{You gain the Scribe Scroll feat. You can treat scrolls as spellbooks.}
\sphere
{Magic Missile}
{Arcane Sight}
{Anyspell}
{Mnemonic Enhancer}
{Lesser Spell Matrix}
{Greater Anyspell}
{Limited Wish}
{Spell Engine}
{Antimagic Field}
\spherecont{Wish}

\featname{\hypertarget{sphere:majesty}{Majesty}}
\textbf{Special: }{You gain Diplomacy as a class skill. Additionally, you may use your Charisma modifier on any skills dependant on Wisdom or Intelligence instead.}
\sphere
{Lantern Light [BoED]}
{Glorious Raiment [BoED]}
{Crown of Flame [BoED]}
{Luminous Armor [BoED]}
{Sicken Evil [BoED]}
{Crown of Brilliance [BoED] }
{Heaven's Trumpet [BoED]}
{Crown of Glory [SC]}
{Blinding Glory [BoED]}
\spherecont{Greater Aspect of the Deity [BoED]}

\featname{\hypertarget{sphere:martyrdom}{Martyrdom}}
\textbf{Special: }{You never lose experience, levels, or attribute points from death or ressurection.}
\sphere
{Divine Sacrifice [SC]}
{Shield Other}
{Consecrated Masochism [BoVD, Consecrate Spell from BoED]}
{Blood of the Martyr (immediate action) [BoED]}
{Renewal Pact [SC]}
{Karmic Retribution [CM]}
{Tomb of Light [BoED]}
{Phoenix Fire [BoED]}
{Transcend Mortality [CM]}
\spherecont{Exalted Fury [BoED]}

\featname{\hypertarget{sphere:metal}{Metal} [Earth], [Fire], [Fiend]}
\textbf{Special: }{You may burrow through metal using any existing Burrow speed.}
\sphere
{Magic Vestment}
{Chill Metal (special bonus: Heat Metal, uses same slots)}
{Keen Edge}
{Rusting Grasp}
{Major Creation (metals only)}
{Wall of Iron}
{Blade Barrier}
{Iron Body}
{Binding}
\spherecont{Summon Golem (Iron Only)}

\featname{\hypertarget{sphere:mystery}{Mystery}}
\textbf{Special: }{You benefit from a constant undetectable alignment effect.}
\sphere
{Disguise Self}
{Silence}
{Blacklight}
{Greater Invisibility}
{Mirage Arcana}
{Forbiddance}
{Screen}
{Mind Blank}
{Etherealness}
\spherecont{Time Stop}

\featname{\hypertarget{sphere:oracle}{Oracle} [Elemental]}
\textbf{Special: }{Roll all chances for a divination you cast to work or backfire twice, and take the more advantageous result.}
\sphere
{Identify}
{Augury}
{Tongues}
{Divination}
{Commune}
{True Seeing}
{Vision}
{Discern Location}
{Metafaculty (Psionic power)}
\spherecont{Wish (Undo Misfortune and Turn Back Time only, no EXP cost for Undo Misfortune if you don't undo the same round more than once)}

\featname{\hypertarget{sphere:plant}{Plant} [Wood]}
\textbf{Special: }{You gain the Druid's Wilderness Stride ability.}
\sphere
{Entangle}
{Wood Shape (bonus: Warp Wood)}
{Plant Growth}
{Command Plants}
{Wall of Thorns}
{Liveoak}
{Animate Plants}
{Control Plants}
{Shambler}
\spherecont{Mass Awaken (Trees only)}

\featname{\hypertarget{sphere:prayer}{Prayer}}
\textbf{Special: }{You gain Perform (oratory) as a class skill. Additionally, any spell or SLA with the [Sonic] descriptor that you use has its area of effect doubled.}
\sphere
{Prayer}
{Shout}
{Dismissal}
{Greater Shout}
{Commune}
{Word of Recall}
{Power Word Stun}
{Blasphemy/Holy Word/Dictum/Word of Chaos (choose one when you gain this level, and you cannot choose one of opposite alignment to your own)}
{Wail of the Banshee}
\spherecont{19: Power Word Kill (can be used as a swift action)}

\featname{\hypertarget{sphere:piety}{Piety}}
\textbf{Special: }{If you succeed on a Sense Motive check (opposed by Bluff), you know the target's alignment. If you fail, you cannot make another attempt until you gain another rank of Sense Motive.}
\sphere
{Bless}
{Aid}
{Prayer}
{Lesser Globe of Invulnerability}
{Hallow}
{Heroes' Feast}
{Refuge}
{Holy Aura}
{Gate (Calling version only)}
\spherecont{Miracle}

\featname{\hypertarget{sphere:quicksand}{Quicksand} [Earth], [Water], [Fiend]}
\textbf{Special: }{You can walk and stand on soft or sticky ground, even quicksand, as if it was firm.}
\sphere
{Soften Earth and Stone}
{Earthen Grasp (CArc)}
{Water Walk}
{Stony Grasp (CArc)}
{Transmute Rock to Mud}
{Acid Fog}
{Flesh to Stone}
{Sympathy}
{Gate (Travel only)}
\spherecont{Imprisonment}

\featname{\hypertarget{sphere:restraint}{Restraint}}
\textbf{Special: }{You gain a +3 bonus on saves against mind-affecting effects.}
\sphere
{Entangle}
{Web}
{Stinking Cloud}
{Black Tentacles}
{Wall of Stone}
{Repulsion}
{Forcecage}
{Prismatic Wall}
{Temporal Stasis}
\spherecont{Imprisonment}

\featname{\hypertarget{sphere:revelation}{Revelation}}
\textbf{Special: }{You receive a +2 bonus on all Knowledge checks, and never count as untrained in any Knowledge skill.}
\sphere
{Detect Evil}
{Detect Thoughts}
{Clairaudience/Clairvoyance}
{Divination}
{True Seeing}
{Find the Path}
{Legend Lore}
{Discern Location}
{Foresight}
\spherecont{Astral Projection}

\featname{\hypertarget{sphere:roots}{Roots} [Earth]}
\textbf{Special: }{You can heal yourself by one hit point per spell-like ability this Sphere has granted you as a standard action as long as you are in either light as bright as natural sunlight or standing on earth (stone if you can burrow into it).}
\sphere
{Pass without Trace}
{Barkskin}
{Poison}
{Antiplant Shell}
{Transport via Plants}
{Ironwood}
{Transmute Metal to Wood}
{Regenerate}
{Clone (Self only, must grow in earth)}
\spherecont{Soul Bind (Uses a seed to hold the soul)}

\featname{\hypertarget{sphere:shadow}{Shadow} [Shadow], [Fiend]}
\textbf{Special: }{You can see in any kind of darkness, even magical darkness, out to 60', or 30' more than you normally could, whichever is more.}
\sphere
{Darkness}
{Mirror Image}
{Displacement}
{Shadow Conjuration}
{Shadow Evocation}
{Shadow Walk}
{Project Image}
{Greater Shadow Conjuration (specical bonus: Greater Shadow Evocation)}
{Simulacrum}
\spherecont{Shades}

\featname{\hypertarget{sphere:smoke}{Smoke} [Air], [Fire], [Shadow], [Fiend]}
\textbf{Special: }{Any [Fire] spell-like ability you cast that affects an area may, at your option, produce a smoke cloud that provides concealment to any creature more than 5' away through it, and total concealment to any creature more than 10' away through it. This smoke cloud lasts for one round per caster level.}
\sphere
{Heat Metal}
{Pyrotechnics}
{Stinking Cloud}
{Flame Blade, Quickened}
{Cloudkill}
{Mirage Arcana}
{Delayed Blast Fireball}
{Horrid Wilting}
{Implosion}
\spherecont{Summon Efreeti (as Summon Monster IX, but summons and Efreeti)}

\featname{\hypertarget{sphere:splendor}{Splendor}}
\textbf{Special: }{You gain a +2 bonus to Diplomacy, Intimidate, and Sense Motive}
\sphere
{Charm Person}
{Eagle's Splendor}
{Flame Strike}
{Glorious Form (as Monstrous Form in the Dungeonomicon, except the new form appears glorious instead of monstrous)}
{Sympathy}
{Greater Heroism}
{Planar Ally}
{Sunburst}
{Weird}
\spherecont{Implosion}

\featname{\hypertarget{sphere:vigor}{Vigor}}
\textbf{Special: }{Whenever you heal someone with a spell-like ability, they recover additional HP equal to your ranks in the Heal skill.}
\sphere
{Cure Light Wounds}
{Shield Other}
{Cure Serious Wounds}
{Death Ward}
{Raise Dead}
{Heal}
{Greater Restoration}
{Greater Spell Immunity}
{Mass Heal}
\spherecont{True Resurrection}

\featname{\hypertarget{sphere:water}{Water} [Water], [Fiend]}
\textbf{Special: }{You gain the (Water) subtype and a Swim speed equal to your base land speed. If you already have those, your Swim speed improves by 10'}
\sphere
{Grease ([Water] descriptor)}
{Quench}
{Control Water}
{Freedom of Movement}
{Transmute Rock to Mud}
{Acid Fog}
{Telekinetic Sphere (the Sphere is filled with water, water weighs nothing for your telekinesis)}
{Arctic Cloud (as Incendiary Cloud, but Cold damage)}
{Summon Elemental Monolith ([Water] only)}
\spherecont{Crushing Hand}

\featname{\hypertarget{sphere:weather}{Weather} [Air], [Water], [Fiend]}
\textbf{Special: }{You suffer no penalties due to weather conditions}
\sphere
{Obscuring Mist}
{Sleet Storm}
{Call Lightning Storm}
{Solid Fog}
{Control Winds}
{Control Weather}
{Acid Fog}
{Horrid Wilting}
{Meteor Swarm}
\spherecont{Storm of Vengeance}

\featname{\hypertarget{sphere:cold}{Cold} [Air], [Ice], [Water]}

\featname{Dominion [Elemental]}

\featname{Fire [Fire]}

\featname{Frostbite [Ice], [Water], [Shadow]}

\featname{Pyre [Fire]}

\featname{Stone [Earth]}

\featname{\hypertarget{sphere:trickery}{Trickery} [Shadow]}

\end{multicols}