
\textbf{Physical Traits}
\begin{small}
\listone
\item Drips slime or excessive dust wherever he goes
\item A pair of appendages are of different color from the rest of body.
\item Scales, fur, or loose/cracking skin cover arms, legs, chest, back, or face (no game effect)
\item Has a stylized wound that never heals
\item Gains non-functional horns, spurs, or bone ridges
\item Small hump on back
\item Body is feverishly hot or cold
\item Drools incessantly
\item Breathe steams in any ambient temperature
\item Extra joint in fingers and toes.
\item Sharpened teeth (enlarged canines, shark teeth, or some other style)
\item Alien eyes(change in color, shape, or composition)
\item Extra non-functional eye or eyes on face.
\item Altered body proportions(longer or shorts arms, legs torso, etc) or size(large head, fist, etc).
\item Apparently dying of a disease(choose a disease, but it has no game effect)
\item Limb is rotted and skeletal (no game effect).
\item Limbs have extra tendons.
\item Gain non-functional wings.
\item Hands resembles spiders.
\item Smells of ash or brimstone.
\item Hole all the way through body in the center of torso.
\item Stand unnaturally still when not paying attention.
\item Cloven feet.
\item Tentacles for fingers
\item Appears as if worms or bugs are crawling under skin.
\item Plants droop when held.
\item Extra ribs extend to pelvis
\item Skin wrinkles when struck, and must be smoothed down.
\item When sleeping, runes and glyphs press up from under skin.
\item Holy symbols and holy water cause very mild burns(no game effect)
\end{list}\end{small}

\textbf{Mental Traits}
\begin{small}
\listone
\item Gaze lingers hungrily at acts associated with one's Spheres.
\item Cruel smile or laugh.
\item Distaste for the company of good-aligned people
\item Fondness for disturbing imagery.
\item Seems pained or ill in good-aligned temples.
\item Must taste the blood on his weapons after every kill.
\item Displays no emotion at atrocity or other's pain.
\item Obviously enjoys the taste of bloody meat.
\item Eat bugs when you think no one is watching.
\item Only laughs when seeing others in pain.
\item Must keep an unholy symbol in your possession, if possible.
\item Appears extremely avaricious in the presence of exposed wealth.
\item Becomes visibly excited when pain is inflicted on others.
\item Seems in awe of more powerful demons.
\item Must lie about one's past, but only about unimportant details.
\item Seems fearful and guilty in the presence of celestials.
\item Bathes as little as possible.
\item Must keep lair and possessions as clean as possible.
\item Seems angry and resentful with given a command.
\item Seems gloating and sarcastic when giving orders.
\item Always asks to keep evil magic items or spellbooks with Corrupt or [evil] spells (can change mind as soon as one round later)
\item Seems bored when morality is discussed.
\item Seems happy during funerals and executions.
\item Leers at any woman of child-bearing age or older.
\item When confront by authority figures, always seems bitter.
\item Seems angry when charity or help is offered.
\item Seems to not understand respect for the dead.
\item Is rude when asked for help or charity.
\item Unable to show love.
\item Unable to express appreciation.
\end{list}\end{small}
