
\documentclass[10pt]{article}

\usepackage{multicol}
\usepackage{floatflt}
\pagestyle{empty}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep
\textheight 8.9in
\oddsidemargin 1in
\evensidemargin \oddsidemargin
%\marginparwidth 0.5in
\textwidth 7in
\setlength {\parindent} {0pt}
\oddsidemargin -0.25in

%\setlength{\itemsep}{1in}

\newcommand{\ability}[2]{\smallskip \textbf{#1} #2}
\newcommand{\classname}[1]{{\huge \textbf{#1}}}
\newcommand{\quot}[1]{\emph{#1}\bigskip}
\newcommand{\desc}[1]{#1 \medskip}
\newcommand{\example}[1]{\emph{#1}}



\newcommand{\half}[0]{\ensuremath{\frac{1}{2}}}

\begin{document}




\classname{Conduit of the Lower Planes}

\quot{``My powers are more than enough to deal with the likes of you!''}

\desc{A fiend is more than an individual; he is a representative of a particular brand of evil, and that role carries power with it. To become a Conduit of the Lower Planes is to embrace that role and become a living pathway by which the energies of the Lower Planes can be made manifest. Raw magical power is the result of this process, and a fiend that walks this route refines his mastery of his innate mystical arts to a terrible degree.}

\ability{Alignment:}{ A character must be non-good to take any levels in Conduit of the Lower Planes. Nothing happens to a Conduit of the Lower Planes if he becomes Good, save that he must look elsewhere for class advancing.}

\ability{Races:}{ The Conduit of the Lower Planes is only available to creatures with a plane of origin in the Lower Planes. Creatures from the prime material plane whose ancestors were from a Lower Plane may take this class.}

\ability{Starting Gold:}{ 4d4x10 gp (100 gold)}

\ability{Starting Age:}{ As Wizard.}

\ability{Hit Die:}{ d6}

\ability{Class Skills:}{ The Conduit of the Lower Planes 's class skills (and the key ability for each skill) are Concentration (Con), Craft (Int), Diplomacy (Cha), Handle Animal(Cha), Knowledge (arcana) (Int), Knowledge (history) (Int), Knowledge (religion) (Int), Knowledge (the planes) (Int), Profession (Wis), and Spellcraft (Int).}

\ability{Skills/Level:}{ 2 + Intelligence Bonus}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{2cm}p{1cm}p{1cm}p{1cm}l}
Level  &Base Attack Bonus &Fort  Save &Ref Save &Will Save &Special\\
1st &+0 &+0 &+0 &+2 &Sphere, Petitioner Immunities\\
2nd &+1 &+0 &+0 &+3 &Enhanced Sphere Access\\
3rd &+2 &+1 &+1 &+3 &Sphere\\
4th &+3 &+1 &+1 &+4 &Bonus Feat\\
5th &+3 &+1 &+1 &+4 &Sphere\\
6th &+4 &+2 &+2 &+5 &Petitioner Skills\\
7th &+5 &+2 &+2 &+5 &Sphere\\
8th &+6/+1 &+2 &+2 &+6 &Bonus Feat\\
9th &+6/+1 &+3 &+3 &+6 &Sphere\\
10th &+7/+2 &+3 &+3 &+7 &Magical Training\\
\end{tabular}
\end{small}
\end{table}

All of the following are Class Features of the Conduit of the Lower Planes class.

\ability{Weapon and Armor Proficiency:}{ Conduits of the Lower Planes are proficient with all simple and martial weapons, as well as the whip, the scourge, and the dire flail. Conduits of the Lower Planes are proficient with light armor but not with shields of any kind.}

\ability{Sphere:}{ The Conduit of the Lower Planes gains basic access to a sphere at every odd numbered level. If the Conduit of the Lower Planes selects a sphere that he already has basic access to, he upgrades it to advanced access. If he already had advanced access, he gains expert access.}

\ability{Petitioner Immunities:}{ A Conduit of the Lower Planes gains his power from a specific lower plane, and is protected by the nature of that plane:}

%\addtolength{\itemsep}{-0.5\baselineskip}

\begin{itemize} \setlength{\itemsep}{-2mm}
    \item \ability{Pandemonium:}{ Sonic Immunity}
    \item \ability{The Abyss:}{ Immunity to Electricity}
    \item \ability{Carceri:}{ Immunity to Cold}
    \item \ability{Hades:}{ Immunity to Fear and Morale Effects}
    \item \ability{Gehenna:}{ Immunity to Acid}
    \item \ability{Baator:}{ Immunity to Fire}
    \item \ability{Acheron:}{ Immunity to [Compulsion] effects}
\end{itemize}

\ability{Enhanced Sphere Access:}{ At 2nd level, the Conduit of the Lower Planes gains extra uses of the spell-like abilities that he gains from his Spheres. The Conduit of the Lower Planes gains a number of extra uses of any spell-like ability equal to half the number his character level exceeds the minimum character level to use the spell-like ability (rounded up). So if the Conduit of the Lower Planes has a character level of 4, he would gain 1 extra use of a spell-like ability that is granted by one of his spheres at character level 3 and 2 extra uses of any spell-like from one of his spheres with a minimum level of 1. Upon gaining this ability, the Conduit of the Lower Planes immediately gains a number of extra feats that must all have the [Fiend] tag equal to the number of spheres he has expert access to. If he ever gains expert access to another sphere, he also gains an extra [Fiend] feat.}

\ability{Bonus Feat:}{ At 4th level, the Conduit of the Lower Planes gains a bonus feat. This feat may be any [Fiend], [Monstrous], or [Item Creation] feat, and the Conduit of the Lower Planes must meet the prerequisites. He gains another such feat at level 8.}

\ability{Petitioner Skills:}{ A Conduit of the Lower Planes gains his power from a specific lower plane, and at 6th level gains abilities from the nature of that plane (this must be the same plane as was chosen at 1st level):}
\begin{itemize}
    \item \ability{Pandemonium:}{ +10 to Listen checks.}
    \item \ability{The Abyss:}{ +10 bonus to Survival checks.}
    \item \ability{Carceri:}{ +10 bonus to Bluff checks.}
    \item \ability{Hades:}{ +10 bonus to Hide checks.}
    \item \ability{Gehenna:}{ +10 bonus to Climb checks, if he doesn't already have a climb speed, he gains one equal to half his normal ground speed (bonuses to Climb from having a Climb speed gained in this way would be included in the +10 bonus)}
    \item \ability{Baator:}{ +10 bonus to Disguise checks.}
    \item \ability{Acheron:}{ +10 bonus to Intimidate checks.}
\end{itemize}
\ability{Magical Training:}{ At 10th level, the Conduit of the Lower Planes is able to cast magic in a more traditional fashion. He has the spells known and spells per day of a 6th level Sorcerer. The Conduit of the Lower Planes has a caster level of 10, and can take classes that improve spellcasting in order to gain additional spellcasting ability.}







\end{document}
