\subsubsection{Elemental-Bodied}

Elemental-Bodied are humanoid figures born from the essense of one of the elemental planes, solidified into something fleshlike.  While not entirely bright, Elemental-Bodied are more than capable of becoming both powerful creatures and adventurers.

Elemental-Bodied is a general term; an Elemental-Bodied character with the (Earth) subtype, for instance, is called an Earthbodied.

Elemental-Bodied have the following racial traits:
\listone
    \item [b]Medium Size[/b] Elemental-bodied average about 6' tall.  They have no sex or gender.
    \item 20' movement, plus additional movement depending on type.
    \item Outsider Type, appropriate subtype (Air, Earth, Fire, or Water).  Elemental-Bodied are native to the appropriate elemental plane, and are (Extraplanar) on the Material Plane.
    \item Elemental Flesh: Elemental-Bodied are counted as Elementals, not Outsiders, for effects that target specific creature types.
    \item +2 Str (Earth, Water), +2 Dex (Air, Fire), -2 Int
    \item Darkvision 60'
    \item Elemental-Bodied do not sleep, and are immune to magic sleep effects.
    \item +4 to saves against Poison, Disease, and Paralysis.  Elemental-Bodied have an unusual physiology that is not subject to the same constraints as mortals.
    \item Light Fortification
\end{list}

Elemental-Bodied gain more abilities, dependent on their specific type:
\listone
    \item Airbodied gain a 15' Fly speed with Perfect maneuverability, a 30' base land speed, and a +2 bonus on Athletics checks.
    \item Earthbodied gain a 20' Burrow speed, and a +2 bonus on Survival checks.
    \item Firebodied have a 20 Climb speed.  They also shed light, brightly illuminating between up 40', and shedding shadowy illumination  over twice that distance, or a minimum of 5'.  They may change brightness or douse thesmelves to smoulder (5' shadow illumination) as a swift action.  They also gain a +2 bonus on Acrobatics checks (Balance and Tumble, under PHB skills).
    \item Waterbodied gain a 60' Swim Speed and breathe both water and air.  They also gain a +2 bonus on Escape Artist checks.
    \item Favored Class: Elemental Brute and Elemental Weird
    \item Automatic Languages: Appropriate elemental language
    \item Bonus Languages: Abyssal, Aquan, Auran, Celestial, Common, Draconic, Formian, Ignan, Infernal, Slaad, Terran.
\end{list}