%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}
\usepackage{multirow}

\newcommand{\tab}{\hspace{5mm}}

pen Game Content, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\section*{{\LARGE EPIC FEATS }}

\vspace{12pt}
\subsection*{{\LARGE ACQUIRING EPIC FEATS}}

Characters gain epic feats in the following ways: 

At 21st level, and every three levels thereafter, the character may select an epic 
feat in place of a nonepic feat.

Each character class gains bonus epic feats according to the class description. 
These feats must be selected from the list of bonus epic feats for that class. 

\vspace{12pt}
\subsection*{{\LARGE PREREQUISITES}}

Most epic feats have prerequisites. A character must have the listed ability score, 
feat, skill, class feature, or base attack modifier in order to select or use that 
feat. A character can gain an epic feat at the same level at which he or she gains 
the prerequisite, just as with regular feats. A prerequisite expressed as a numerical 
value is a minimum; any value higher than the one given also meets the prerequisite. 
A character can't use an epic feat if he or she has lost a prerequisite. 

\vspace{12pt}
\subsection*{{\LARGE TYPES OF EPIC FEATS }}

Most epic feats are general, meaning that no special rules govern them as a group. 
Others may be item creation feats or metamagic feats, which follow all the normal 
rules for such feats, except as specified in the feat's description. In addition, 
some feats are defined as divine feats or as wild feats. Such feats are described 
below. 

\vspace{12pt}
\subsection*{DIVINE FEATS }

The feats in this category share a few characteristics. First, they all have as 
a prerequisite the ability to turn (or, in most cases, rebuke) undead. Thus, they 
are open to clerics, paladins of 4th level or higher, and any prestige class that 
has that ability. (An ability to turn other creatures does not qualify a character 
to select one of these feats.) Second, the force that powers a divine feat is the 
ability to channel positive or negative energy to turn or rebuke undead. Each use 
of a divine feat costs the character one turn/rebuke attempt from his or her number 
of attempts each day. If a character doesn't have any turn/rebuke attempts left, 
he or she can't use the feat. Since turning or rebuking is a standard action, activating 
any of these feats is also a standard action. 

\vspace{12pt}
\subsection*{WILD FEATS }

The feats in this category share the characteristic of relating to the ability 
to use \textit{wild shape }as a druid. These feats require the character to have 
the ability to use \textit{wild shape }before acquiring the feat. 

\vspace{12pt}
\subsection*{EPIC PSIONIC FEATS }

Psionic characters can acquire epic ``psionically flavored'' feats.  Some feats 
require so much translation that converted feats are provided. Whenever a feat 
concerns conferring or altering a spell in some fashion, some translation must 
be done to use it with psionics. Sometimes this translation is as straightforward 
as changing a few names. Translating epic metamagic feats to epic metapsionic feats 
requires that Spellcraft prerequisites be replaced with Psicraft. It also requires 
a little math---instead of casting a spell at a higher level, a psionic character 
pays more power points. For every spell slot one level higher than the spell's 
actual level the metamagic feat requires, the metapsionic feat requires a character 
to pay a power point cost equal to its standard cost +2. Likewise, when a feat 
allows a spellcaster to ``pay'' one less level to use a metamagic feat, the psionic 
version allows a character to pay 2 power points less for a given metapsionic feat. 

\vspace{12pt}
{\LARGE FEATS}

\vspace{12pt}
ADDITIONAL MAGIC ITEM SPACE [EPIC] 

\textbf{Benefit:} Choose one type of magic item that has a limit on the number 
a character can simultaneously wear and gain its benefit. The character can now 
wear one more magic item of this type and also gain its benefit. 

\textbf{Normal:} Without this feat, a character is limited to one headband, hat, 
or helmet; one pair of eye lenses or goggles; one cloak, cape, or mantle; one amulet, 
brooch, medallion, necklace, periapt, or scarab; one suit of armor; one robe; one 
vest, vestment, or shirt; one pair of bracers or bracelets; one pair of gloves 
or gauntlets; two rings; one belt; and one pair of boots. 

\textbf{Special:} A character can gain this feat multiple times. Each time the 
character takes the feat, it applies to a new type of wearable magic item. 

\vspace{12pt}
ARMOR SKIN [EPIC] 

\textbf{Benefit:} The character gains a +1 natural armor bonus to Armor Class, 
or his or her existing natural armor bonus increases by 1. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
AUGMENTED ALCHEMY [EPIC] 

\textbf{Prerequisites:} Int 21, Craft(alchemy) 24 ranks. 

\textbf{Benefit:} Whenever creating an alchemical item or substance, the character 
can choose to make it more powerful than normal by adding +20 to the DC required 
to create it and multiplying its price by 5. If the item or substance deals damage, 
double the damage dealt. If the item or substance doesn't deal damage, double the 
duration of its effect. If the item or substance doesn't deal damage and doesn't 
have a specific listed duration (or has an instantaneous duration), double all 
dimensions of its area. If the item or substance doesn't fit any of these categories, 
then it cannot be affected by this feat. See the Craft (alchemy) skill description. 

\vspace{12pt}
AUTOMATIC QUICKEN SPELL [EPIC] 

\textbf{Prerequisites:} Quicken Spell, Spellcraft 30 ranks, ability to cast 9th-level 
arcane or divine spells. 

\textbf{Benefit:} The character may cast all 0-, 1st-, 2nd-, and 3rd-level spells 
as quickened spells without using higher-level spell slots. The normal limit to 
the number of quickened spells a character may cast per round applies. Spells with 
a casting time of more than 1 full round can't be quickened. 

\textbf{Special:} A character can gain this feat multiple times. Each time a character 
takes the feat, the spells of his or her next three lowest spell levels can now 
be quickened with no adjustment to their spell slots. This feat doesn't increase 
the casting time for those spells that normally become full-round actions when 
cast in metamagic form. 

\vspace{12pt}
AUTOMATIC SILENT SPELL [EPIC] 

\textbf{Prerequisites:} Silent Spell, Spellcraft 24 ranks, ability to cast 9th-level 
arcane or divine spells. 

\textbf{Benefit:} The character may cast all 0-, 1st-, 2nd-, and 3rd-level spells 
as silent spells without using higher-level spell slots. 

\textbf{Special:} A character can gain this feat multiple times. Each time a character 
takes the feat, the spells of his or her next three lowest spell levels can now 
be silenced with no adjustment to their spell slots. This feat doesn't increase 
the casting time for those spells that normally become full-round actions when 
cast in metamagic form. However, since bard spells can't be enhanced with the Silent 
Spell feat, they can't be affected by this feat either. 

\vspace{12pt}
AUTOMATIC STILL SPELL [EPIC] 

\textbf{Prerequisites:} Still Spell, Spellcraft 27 ranks, ability to cast 9th-level 
arcane or divine spells. 

\textbf{Benefit:} The character may cast all 0-, 1st-, 2nd-, and 3rd-level spells 
as stilled spells without using higher-level spell slots. 

\textbf{Special:} A character can gain this feat multiple times. Each time a character 
takes the feat, the spells of his or her next three lowest spell levels can now 
be stilled with no adjustment to their spell slots. This feat doesn't increase 
the casting time for those spells that normally become full-round actions when 
cast in metamagic form. 

\vspace{12pt}
BANE OF ENEMIES [EPIC] 

\textbf{Prerequisites:} Survival 24 ranks, five or more favored enemies. 

\textbf{Benefit:} Any weapon the character wields against one of his or her favored 
enemies is treated as a bane weapon for that creature type (thus, its enhancement 
bonus is increased by +2 and it deals +2d6 points of damage). This ability doesn't 
stack with similar abilities. 

\vspace{12pt}
BLINDING SPEED [EPIC] 

\textbf{Prerequisite:} Dex 25. 

\textbf{Benefit:} The character can act as if \textit{hasted }for 5 rounds each 
day. The duration of the effect need not be consecutive rounds. Activating this 
power is a free action. 

\textbf{Special:} A character can gain this feat multiple times. Each time he or 
she takes the feat, it grants an additional 5 rounds of \textit{haste }per day. 

\vspace{12pt}
BONUS DOMAIN [EPIC] 

\textbf{Prerequisites:} Wis 21, ability to cast 9th-level divine spells. 

\textbf{Benefit:} Choose an additional domain from the character's deity's domain 
list. The character now has access to that domain's spells as normal for his or 
her domain spells and the domain's granted powers. 

\textbf{Special:} A character can gain this feat multiple times. Each time he or 
she takes the feat, it applies to a different domain. 

\vspace{12pt}
BULWARK OF DEFENSE [EPIC] 

\textbf{Prerequisites:} Con 25, defensive stance 3/day. 

\textbf{Benefit:} The character's defensive stance bonuses increase to +4 Strength, 
+6 Constitution, +4 resistance bonus on all saves, and +6 dodge bonus to AC. 

\vspace{12pt}
CHAOTIC RAGE [EPIC] 

\textbf{Prerequisites:} Rage 5/day, chaotic alignment. 

\textbf{Benefit:} Any weapon the character wields while in a rage is treated as 
an anarchic weapon (it is chaos-aligned and deals an extra 2d6 points of damage 
against creatures of lawful alignment). This ability does not stack with similar 
abilities. 

\vspace{12pt}
COLOSSAL WILD SHAPE [WILD][EPIC] 

\textbf{Prerequisite:} The ability to \textit{wild shape }into a Gargantuan creatur\textit{e.}

\textbf{Benefit:} The character can use his or her \textit{wild shape }to take 
the shape of a Colossal animal. 

\textbf{Normal:} Without this feat, a character cannot \textit{wild shape }into 
an animal of greater than Huge size. 

\vspace{12pt}
COMBAT ARCHERY [EPIC] 

\textbf{Prerequisites:} Dodge, Mobility, Point Blank Shot. 

\textbf{Benefit:} The character does not incur any attacks of opportunity for firing 
a bow when threatened. 

\textbf{Normal:} Without this feat, a character incurs an attack of opportunity 
from all opponents who threaten him or her whenever he or she uses a bow. 

\vspace{12pt}
CRAFT EPIC MAGIC ARMS AND ARMOR [ITEM CREATION] [EPIC] 

\textbf{Prerequisites:} Craft Magic Arms and Armor, Knowledge (arcana) 28 ranks, 
Spellcraft 28 ranks. 

\textbf{Benefit:} The character can craft magic arms and armor which exceed the 
normal limits for such items

\vspace{12pt}
CRAFT EPIC ROD [ITEM CREATION][EPIC] 

\textbf{Prerequisites:} Craft Rod, Knowledge (arcana) 32 ranks, Spellcraft 32 ranks. 

\textbf{Benefit:} The character can craft rods that exceed the normal limits for 
such items. 

\vspace{12pt}
CRAFT EPIC STAFF [ITEM CREATION][EPIC] 

\textbf{Prerequisites:} Craft Staff, Knowledge (arcana) 35 ranks, Spellcraft 35 
ranks. 

\textbf{Benefit:} The character can craft staffs that exceed the normal limits 
for such items. 

\vspace{12pt}
CRAFT EPIC WONDROUS ITEM [ITEM CREATION][EPIC] 

\textbf{Prerequisites:} Craft Wondrous Item, Knowledge (arcana) 26 ranks, Spellcraft 
26 ranks. 

\textbf{Benefit:} The character can craft wondrous items that exceed the normal 
limits for such items. 

\vspace{12pt}
DAMAGE REDUCTION [EPIC] 

\textbf{Prerequisite:} Con 21. 

\textbf{Benefit:} The character gains damage reduction 3/-. This does not stack 
with damage reduction granted by magic items or nonpermanent magical effects, but 
it does stack with any damage reduction granted by permanent magical effects, class 
features, or this feat itself. 

\textbf{Special:} A character can gain this feat multiple times. Each time he or 
she gains the feat, his or her damage reduction increases by 3. 

\vspace{12pt}
DEAFENING SONG [EPIC] 

\textbf{Prerequisites:} Perform 24 ranks, bardic music class feature. 

\textbf{Benefit:} The character can use song or poetics to temporarily deafen all 
enemies within a 30-foot spread from him or her. A successful Fortitude save (DC 
10 + 1/2 the character's class level + the character's Charisma modifier) negates 
the effect. The deafening effect lasts for as long as the character continues the 
deafening song. The character can choose to exclude any characters from this effect. 
The character may sing, play, or recite a deafening song while taking other mundane 
actions, but not magical ones (see the bard's inspire courage ability for more 
details). The character may keep up the deafening song for a maximum of 10 rounds. 
Using the deafening song counts as one of the character's uses of song or poetics 
for the day. 

\vspace{12pt}
DEATH OF ENEMIES [EPIC] 

\textbf{Prerequisites:} Bane of Enemies, Survival 30 ranks, five or more favored 
enemies. 

\textbf{Benefit:} Any time the character scores a critical hit against one of his 
or her favored enemies, it must make a Fortitude save (DC 10 + 1/2 character's 
ranger class level + character's Wisdom modifier) or die instantly.

\textbf{Special:} Creatures immune to critical hits can't be affected by this feat. 

\vspace{12pt}
DEVASTATING CRITICAL [EPIC] 

\textbf{Prerequisites:} Str 25, Cleave, Great Cleave, Improved Critical (chosen 
weapon), Overwhelming Critical (chosen weapon), Power Attack, Weapon Focus (chosen 
weapon). 

\textbf{Benefit:} Whenever the character scores a critical hit with the chosen 
weapon, the target must make a Fortitude save (DC 10 + 1/2 character level + character's 
Strength modifier) or die instantly. (Creatures immune to critical hits can't be 
affected by this feat.) 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different type 
of weapon. 

\vspace{12pt}
DEXTEROUS FORTITUDE [EPIC] 

\textbf{Prerequisites:} Dex 25, slippery mind class feature. 

\textbf{Benefit:} Once per round, when targeted by an effect that requires a Fortitude 
saving throw, the character may make a Reflex save instead to avoid the effect 
(evasion is not applicable). 

\vspace{12pt}
DEXTEROUS WILL [EPIC] 

\textbf{Prerequisites:} Dex 25, slippery mind class feature. 

\textbf{Benefit:} Once per round, when targeted by an effect that requires a Will 
saving throw, the character may make a Reflex save instead to avoid the effect 
(evasion is not applicable). 

\vspace{12pt}
DIMINUTIVE WILD SHAPE [WILD][EPIC] 

\textbf{Prerequisite:} Ability to \textit{wild shape }into a Huge animal. 

\textbf{Benefit:} The character can use \textit{wild shape }to take the shape of 
a Diminutive animal. 

\textbf{Normal:} Without this feat, a character cannot \textit{wild shape }into 
an animal of smaller than Tiny size. 

\vspace{12pt}
DIRE CHARGE [EPIC] 

\textbf{Prerequisite:} Improved Initiative. 

\textbf{Benefit:} If the character charges a foe during the first round of combat 
(or the surprise round, if the character is allowed to act in it), he or she can 
make a full attack against the opponent charged. 

\textbf{Normal:} Without this feat, a character may only make a single attack as 
part of a charge. 

\vspace{12pt}
DISTANT SHOT [EPIC]

\textbf{Prerequisites:} Dex 25, Far Shot, Point Blank Shot, Spot 20 ranks. 

\textbf{Benefit:} The character may throw or fire a ranged weapon at any target 
within line of sight, with no penalty for range. 

\vspace{12pt}
DRAGON WILD SHAPE [WILD][EPIC]

\textbf{Prerequisites:} Wis 30, Knowledge (nature) 30 ranks, \textit{wild shape 
}6/day. 

\textbf{Benefit:} The character may use \textit{wild shape }to change into a dragon 
(black, blue, green, red, white, brass, bronze, copper, gold, or silver). The size 
limitation is the same as the character's limitation on animal size. The character 
gains all extraordinary and supernatural abilities of the dragon whose form he 
or she takes. 

\vspace{12pt}
EFFICIENT ITEM CREATION [EPIC] 

\textbf{Prerequisites:} Item creation feat to be selected, Knowledge (arcana) 24 
ranks, Spellcraft 24 ranks. 

\textbf{Benefit:} Select an item creation feat. Creating a magic item using that 
feat requires one day per 10,000 gp of the item's market price, with a minimum 
of one day. 

\textbf{Normal:} Without this feat, creating a magic item requires one day for 
each 1,000 gp of the item's market price.

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different item 
creation feat. 

\vspace{12pt}
ENERGY RESISTANCE [EPIC] 

\textbf{Benefit:} Choose a type of energy (acid, cold, electricity, fire, or sonic). 
The character gains resistance 10 to that type of energy, or the character's existing 
resistance to that type of energy increases by 10. This feat does not stack with 
energy resistance granted by magic items or nonpermanent magical effects. 

\textbf{Special:} A character can gain this feat multiple times. If the same type 
of energy is chosen, the effects stack. 

\vspace{12pt}
ENHANCE SPELL [METAMAGIC][EPIC] 

\textbf{Prerequisite:} Maximize Spell. 

\textbf{Benefit:} The damage cap for the character's spells increases by 10 dice 
(for spells that deal a number of dice of damage equal to caster level) or by 5 
dice (for spells that deal a number of dice of damage equal to half caster level). 
An enhanced spell uses up a spell slot four levels higher than the spell's actual 
level. This feat has no effect on spells that don't specifically deal a number 
of dice of damage equal to the caster's level or half level, even if the spell's 
effect is largely dictated by the caster's level. 

\textbf{Normal:} Without this feat, use the damage dice caps indicated in the spell's 
description. 

\textbf{Special:} A character may gain this feat multiple times. Each time he or 
she selects this feat, the damage cap increases by 10 dice or 5 dice, as appropriate 
to the spell, and the enhanced spell takes up a spell slot an additional four levels 
higher. 

\vspace{12pt}
EPIC DODGE [EPIC] 

\textbf{Prerequisites:} Dex 25, Dodge, Tumble 30 ranks, improved evasion, defensive 
roll class feature. 

\textbf{Benefit:} Once per round, when struck by an attack from an opponent the 
character has designated as the object of his or her dodge, the character may automatically 
avoid all damage from the attack. 

\vspace{12pt}
EPIC ENDURANCE [EPIC] 

\textbf{Prerequisites:} Con 25, Endurance. 

\textbf{Benefit:} Whenever the character makes a check for performing a physical 
action that extends over a period of time, he or she gets a +10 bonus on the check. 

\vspace{12pt}
EPIC EXPANDED KNOWLEDGE [EPIC, PSIONIC]

You learn another power.

\textbf{Prerequisites:} Character level 21st, ability to manifest powers of the 
normal maximum power level in at least one psionic class.

\textbf{Benefit:} You learn one additional power at any level up to the highest 
level of power you can manifest. You can choose any power, even one that is part 
of another discipline's list or another class's list.

\textbf{Special:} You can gain this feat multiple times. Each time, you learn one 
new power at any level up to the highest level of power you can manifest.

\vspace{12pt}
EPIC FORTITUDE\textit{\textbf{ }}[EPIC]\textit{ }

\textbf{Benefit:} The character gains a +4 bonus on all Fortitude saving throws. 

\vspace{12pt}
EPIC INSPIRATION [EPIC] 

\textbf{Prerequisites:} Cha 25, Perform 30 ranks, bardic music class feature. 

\textbf{Benefit:} All competence bonuses, dodge bonuses, and morale bonuses granted 
by the character's bardic music ability increase by +1.  If you have the inspire 
greatness bardic music ability, it grants one additional bonus HD. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
EPIC LEADERSHIP [EPIC] 

\textbf{Prerequisites:} Cha 25, Leadership, Leadership score 25. 

\textbf{Benefit:} The character attracts a cohort and followers as shown below 
on Table: Epic Leadership.  In all other ways Epic Leadership functions as the 
Leadership feat.

\textbf{Normal:} The Leadership feat provides no benefit for leadership scores 
beyond 25.

\vspace{12pt}
\subsubsection*{\textbf{Table: Epic Leadership}}

\subsubsection*{\begin{longtable}{llllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\multirow{2}{0.516in}{\raggedright \textbf{Leadership 
Score}}\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\multirow{2}{0.342in}{\raggedright \textbf{Cohort 
Level}}\end{minipage}} & \multicolumn{10}{p{3.186in}|}{\begin{minipage}[t]{3.186in}\centering
------------------------------\textbf{Number of Followers by Level ---------------------------}\end{minipage}}\\
\cline{3-12}\cline{15-24}
% ROW 2
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\multirow{2}{0.038in}{\centering }\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\multirow{2}{0.038in}{\raggedright }\end{minipage}} & \multicolumn{10}{p{0.380in}|}{\begin{minipage}[t]{0.380in}\centering
\textbf{1st}\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
\textbf{2nd}\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
\textbf{3rd}\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
\textbf{4th}\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
\textbf{5th}\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
\textbf{6th}\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
\textbf{7th}\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
\textbf{8th}\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
\textbf{9th}\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
\textbf{10th}\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-12}\cline{13-13}\cline{14-14}\cline{15-15}\cline{16-16}\cline{17-17}\cline{18-18}\cline{19-19}\cline{20-20}\cline{21-21}\cline{22-22}\cline{23-23}\cline{24-24}
% ROW 3
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
25\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
17th\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
135\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
13\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
7\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-12}\cline{13-13}\cline{14-14}\cline{15-15}\cline{16-16}\cline{17-17}\cline{18-18}\cline{19-19}\cline{20-20}\cline{21-21}\cline{22-22}\cline{23-23}\cline{24-24}
% ROW 4
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
26\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
18th\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
160\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
16\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
8\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 5
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
27\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
18th\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
190\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
19\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
10\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 6
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
28\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
19th\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
220\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
22\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
11\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 7
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
29\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
19th\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
260\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
26\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
13\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
7\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 8
\multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
30\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
20th\end{minipage}} & \multicolumn{1}{p{0.038in}|}{\begin{minipage}[t]{0.038in}\centering
300\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
30\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
15\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
8\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 9
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
31\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
20th\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
350\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
35\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
18\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
9\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 10
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
32\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
21st\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
400\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
40\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
20\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
10\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 11
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
33\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
21st\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
460\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
46\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
23\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
12\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 12
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
34\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
22nd\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
520\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
52\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
26\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
13\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 13
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
35\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
22nd\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
590\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
59\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
30\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
15\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
8\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 14
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
36\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
23rd\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
660\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
66\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
33\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
17\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
9\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 15
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
37\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
23rd\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
740\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
74\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
37\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
19\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
10\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
5\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 16
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
38\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
24th\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
820\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
82\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
41\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
21\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
11\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 17
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
39\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
24th\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
910\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
91\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
46\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
23\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
12\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
6\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
3\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 18
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
40\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
25th\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
1000\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
100\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
50\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
25\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
13\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
7\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
4\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
2\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
---\end{minipage}}\\
\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}\cline{6-6}\cline{7-7}\cline{8-8}\cline{9-9}\cline{10-10}\cline{11-11}\cline{12-24}
% ROW 19
\multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
per +1\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
+1/2*\end{minipage}} & \multicolumn{13}{p{0.775in}|}{\begin{minipage}[t]{0.775in}\centering
+100**\end{minipage}} & \multicolumn{1}{|p{0.516in}|}{\begin{minipage}[t]{0.516in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.342in}|}{\begin{minipage}[t]{0.342in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.318in}|}{\begin{minipage}[t]{0.318in}\centering
†\end{minipage}} & \multicolumn{1}{p{0.319in}|}{\begin{minipage}[t]{0.319in}\centering
†\end{minipage}}\\
\hline
\end{longtable}
}

\vspace{12pt}
\textbf{Leadership Score:} A character's Leadership score equals his or her level 
plus any Charisma modifier. Outside factors can affect a character's Leadership 
score, as detailed in the Leadership feat. 

\textbf{Cohort Level: }The character can attract a cohort of up to this level. 
Regardless of the character's Leadership score, he or she can't recruit a cohort 
of his or her level or higher. 

\textbf{Number of Followers by Level: }The character can lead up to the indicated 
number of characters of each level. 

*The maximum cohort level increases by 1 for every 2 points of Leadership above 
40. **The number of 1st-level followers increases by 100 for every point of Leadership 
above 40. 

†A character can command one-tenth as many 2nd-level followers as 1st-level followers. 
A character can command one-half as many 3rd-level followers as 2nd-level followers, 
one-half as many 4th-level followers as 3rd-level followers, and so on (round fractions 
up, except any fraction less than 1 rounds to 0). A character can't have a follower 
of higher than 20th level.

Table: Example Special Epic Cohorts presents some creatures that make good cohorts 
for epic characters. 

\vspace{12pt}
\textbf{Table: Example Special Epic Cohorts}

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
\textbf{Creature}\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
\textbf{Alignment}\end{minipage}} & \multicolumn{1}{p{1.436in}|}{\begin{minipage}[t]{1.436in}\raggedright
\textbf{Level Equivalent}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Angel, astral deva\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Any good\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
20nd\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Dragon, ancient silver\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Lawful good\end{minipage}} & \multicolumn{1}{p{1.436in}|}{\begin{minipage}[t]{1.436in}\raggedright
42nd\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Couatl\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Lawful good\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
16th\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Giant, cloud\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Neutral good\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
24th\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Ghaele \end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Chaotic good\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
20st\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Giant, storm\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Chaotic good\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
28th\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Dragon, wyrm brass\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Chaotic good\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
42th\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Dragon turtle\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Neutral\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
21st\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Hydra, 12-headed\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Neutral\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
19th\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Roc\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Neutral\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
23rd\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Dragon, ancient green\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Lawful evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
40th\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Devil, ice (gelugon)\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Lawful evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
21st\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Giant, cloud\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Neutral evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
24th\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Demon, glabrezu\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Chaotic evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
23rd\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Demon, succubus\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Chaotic evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
12th\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{|p{1.807in}|}{\begin{minipage}[t]{1.807in}\raggedright
Dragon, wyrm white\end{minipage}} & \multicolumn{1}{p{1.127in}|}{\begin{minipage}[t]{1.127in}\raggedright
Chaotic evil\end{minipage}} & \multicolumn{4}{p{1.566in}|}{\begin{minipage}[t]{1.566in}\raggedright
41th\end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
EPIC PROWESS [EPIC] 

\textbf{Benefit:} Gain a +1 bonus on all attacks. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
EPIC PSIONIC FOCUS [EPIC, PSIONIC]

You can expend your psionic focus to greater effect.

\textbf{Prerequisites:} Character level 21st, ability to manifest powers of the 
normal maximum power level in at least one psionic class.

\textbf{Benefit:} When you expend your psionic focus, you can simultaneously use 
two feats that require a psionic focus to be expended, instead of just one. The 
feats must be stackable. You must still spend the requisite power points required 
to use each metapsionic feat, and you cannot exceed the power point limit set by 
your manifester level.

\textbf{Special:} You can take this feat multiple times. Each time you do so, you 
can simultaneously use one additional feat that requires a psionic focus to be 
expended.

\vspace{12pt}
EPIC REFLEXES [EPIC] 

\textbf{Benefit:} The character gains a +4 bonus on all Reflex saving throws. 

\vspace{12pt}
EPIC REPUTATION [EPIC] 

\textbf{Benefit:} The character gains a +4 bonus on Bluff, Diplomacy, Gather Information, 
Intimidate, and Perform checks. 

\vspace{12pt}
EPIC SKILL FOCUS [EPIC] 

\textbf{Prerequisite:} 20 ranks in the skill selected. 

\textbf{Benefit:} The character gains a +10 bonus on all skill checks with that 
skill. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different skill. 

\vspace{12pt}
EPIC SPEED [EPIC] 

\textbf{Prerequisites:} Dex 21, Run. 

\textbf{Benefit:} The character's speed increases by 30 feet. This benefit does 
not stack with increased speed granted by magic items or nonpermanent magical effects. 

\textbf{Special:} This feat only functions when the character is wearing medium 
armor, light armor, or no armor. 

\vspace{12pt}
EPIC SPELL FOCUS [EPIC] 

\textbf{Prerequisites:} Greater Spell Focus and Spell Focus in the school selected, 
ability to cast at least one 9th-level spell of the school to be chosen. 

\textbf{Benefit:} Add +1 to the Difficulty Class for all saving throws against 
spells from the school of magic the character selects to focus on. This stacks 
with the bonuses from Spell Focus and Greater Spell Focus. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time the character takes the feat, it applies to a different school 
of magic. 

\vspace{12pt}
EPIC SPELL PENETRATION [EPIC] 

\textbf{Prerequisites:} Greater Spell Penetration, Spell Penetration. 

\textbf{Benefit:} The character gets a +2 bonus on caster level checks to beat 
a creature's spell resistance. This stacks with the bonuses from Spell Penetration 
and Greater Spell Penetration. 

\vspace{12pt}
EPIC SPELLCASTING [EPIC] 

\textbf{Prerequisite:} Spellcraft 24 ranks, Knowledge (arcana) 24 ranks, ability 
to cast 9th-level arcane spells. OR Spellcraft 24 ranks, Knowledge (religion) 24 
ranks, ability to cast 9th-level divine spells. OR Spellcraft 24 ranks, Knowledge 
(nature) 24 ranks, ability to cast 9th-level divine spells. 

\textbf{Benefit:} The character may develop and cast epic spells.  If the character 
is an arcane spellcaster, he or she may cast a number of epic spells per day equal 
to his or her ranks in Knowledge (arcana) divided by 10. If the character is a 
divine spellcaster, he or she may cast a number of epic spells per day equal to 
his or her ranks in Knowledge (religion) or Knowledge (nature) divided by 10. 

\textbf{Special:} If the character meets more than one set of prerequisites, the 
limit on the number of spells he or she may cast per day is cumulative. 

\vspace{12pt}
EPIC TOUGHNESS [EPIC] 

\textbf{Benefit:} The character gains +30 hit points. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
EPIC WEAPON FOCUS [EPIC] 

\textbf{Prerequisite:} Weapon Focus in the chosen weapon. 

\textbf{Benefit:} Add a +2 bonus to all attack rolls the character makes using 
the selected weapon. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time the character takes the feat it applies to a different type 
of weapon. 

\vspace{12pt}
EPIC WEAPON SPECIALIZATION [EPIC] 

\textbf{Prerequisites:} Epic Weapon Focus, Weapon Focus, Weapon Specialization 
(all in the chosen weapon). 

\textbf{Benefit:} Add +4 to all damage the character deals using the selected weapon. 
If the weapon is a ranged weapon, the damage bonus only applies if the target is 
within 30 feet. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time the character takes the feat, it applies to a different type 
of weapon. 

\vspace{12pt}
EPIC WILL [EPIC] 

\textbf{Benefit:} The character gains a +4 bonus on all Will saving throws. 

\vspace{12pt}
EXCEPTIONAL DEFLECTION [EPIC] 

\textbf{Prerequisites:} Dex 21, Wis 19, Deflect Arrows, Improved Unarmed Strike. 

\textbf{Benefit:} The character can deflect any ranged attacks (including spells 
that require ranged touch attacks) as if they were arrows. 

\vspace{12pt}
EXTENDED LIFE SPAN [EPIC] 

\textbf{Benefit:} Add one-half the maximum result of the character's race's maximum 
age modifier to the character's normal middle age, old, and venerable age categories. 
Calculate the character's maximum age using the new venerable number. This feat 
can't lower the character's current age category. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
FAMILIAR SPELL [EPIC] 

\textbf{Prerequisite:} Int 25 (if the character's spellcasting is controlled by 
Intelligence) or Cha 25 (if the character's spellcasting is controlled by Charisma). 

\textbf{Benefit:} Choose one arcane spell the character knows of 8th level or lower. 
The character's familiar can now use this spell once per day as a spell-like ability, 
at a caster level equal to the character's caster level. A character cannot bestow 
a spell to his or her familiar if the spell normally has a material component cost 
of more than 1 gp or an XP cost. 

\textbf{Special:} A character can gain this feat multiple times. Each time the 
character takes the feat, he or she can give his or her familiar a different spell-like 
ability or another daily use of the same spell-like ability. 

\vspace{12pt}
FAST HEALING [EPIC] 

\textbf{Prerequisite:} Con 25. 

\textbf{Benefit:} The character gains fast healing 3, or the character's existing 
fast healing increases by 3. This feat does not stack with fast healing granted 
by magic items or nonpermanent magical effects. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. 

\vspace{12pt}
FINE WILD SHAPE [WILD][EPIC]

\textbf{Prerequisite:} Ability to \textit{wild shape }into a Diminutive creatur\textit{e. 
}

\textbf{Benefit:} The character can use his or her \textit{wild shape }to take 
the shape of a Fine animal. 

\textbf{Normal:} Without this feat, a character cannot \textit{wild shape }into 
an animal smaller than Tiny size. 

\vspace{12pt}
FORGE EPIC RING [ITEM CREATION][EPIC] 

\textbf{Prerequisites:} Forge Ring, Knowledge (arcana) 35 ranks, Spellcraft 35 
ranks. 

\textbf{Benefit:} The character can forge magic rings that exceed the normal limits 
for such items.

\vspace{12pt}
GARGANTUAN WILD SHAPE [WILD][EPIC]

\textbf{Prerequisite:} Ability to \textit{wild shape }into a Huge animal. 

\textbf{Benefit:} The character can use your \textit{wild shape }to take the shape 
of a Gargantuan animal. 

\textbf{Normal:} Without this feat, a character cannot \textit{wild shape }into 
an animal greater than Huge size. 

\vspace{12pt}
GREAT CHARISMA [EPIC] 

\textbf{Benefit:} The character's Charisma increases by 1 point. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GREAT CONSTITUTION [EPIC] 

\textbf{Benefit:} The character's Constitution increases by 1 point.

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GREAT DEXTERITY [EPIC] 

\textbf{Benefit:} The character's Dexterity increases by 1 point. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GREAT INTELLIGENCE [EPIC] 

\textbf{Benefit:} The character's Intelligence increases by 1 point. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GREAT SMITING [EPIC] 

\textbf{Prerequisites:} Cha 25, smite ability (from class feature or domain granted 
power). 

\textbf{Benefit:} Whenever the character makes a successful smite attack, add twice 
the appropriate level to damage (rather than just the character's level). 

\textbf{Special:} A character may select this feat multiple times. Its effects 
stack. Remember that two doublings equals a tripling, and so forth.

\vspace{12pt}
GREAT STRENGTH [EPIC] 

\textbf{Benefit:} The character's Strength increases by 1 point. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GREAT WISDOM [EPIC] 

\textbf{Benefit:} The character's Wisdom increases by 1 point. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
GROUP INSPIRATION [EPIC] 

\textbf{Prerequisite:} Perform 30 ranks, bardic music class feature. 

\textbf{Benefit:} The number of allies the character can affect with his or her 
inspire competence or inspire greatness bardic music ability doubles. When inspiring 
competence in multiple allies, the character can choose different skills to inspire 
for different allies. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 
Remember that two doublings equals a tripling, and so forth. 

\vspace{12pt}
HINDERING SONG [EPIC] 

\textbf{Prerequisite:} Deafening Song, Perform 27 ranks, bardic music class feature. 

\textbf{Benefit:} The character can use song or poetics to hinder enemy spellcasters 
within a 30-foot spread from the character. To successfully cast a spell within 
this area, a spellcaster must make a Concentration check as if he or she were casting 
defensively, and all such checks have a penalty equal to half the character's level. 
The character can choose to exclude any characters from this effect. The character 
may sing, play, or recite a hindering song while taking other mundane actions, 
but not magical ones (see the bard's inspire courage ability for more details). 
The character may keep up the hindering song for a maximum of 10 rounds. Using 
the hindering song counts as one of the character's uses of song or poetics for 
the day. 

\vspace{12pt}
HOLY STRIKE [EPIC] 

\textbf{Prerequisites:} Smite evil class feature, any good alignment. 

\textbf{Benefit:} Any weapon the character wields is treated as a holy weapon (is 
good-aligned and deals an extra 2d6 points of damage against creatures of evil 
alignment).If the weapon already has an alignment, this feat has no effect on the 
weapon. 

\vspace{12pt}
IGNORE MATERIAL COMPONENTS [EPIC] 

\textbf{Prerequisites:} Eschew Materials, Spellcraft 25 ranks, ability to cast 
9th-level arcane or divine spells. 

\textbf{Benefit:} The character may cast spells without any material components. 
This feat does not affect the need for a focus or divine focus. 

\vspace{12pt}
IMPROVED ALIGNMENT-BASED CASTING [EPIC] 

\textbf{Prerequisites:} Access to domain of Chaos, Evil, Good, or Law, alignment 
must match domain chosen, ability to cast 9th-level divine spells. 

\textbf{Benefit:} Select an alignment-based domain (Chaos, Evil, Good, or Law) 
to which the character has access. The character casts spells with that alignment 
descriptor at +3 caster level. 

\textbf{Special:} This benefit overrides (does not stack with) the granted powers 
of the Chaos, Evil, Good, and Law domains. A character may select this feat multiple 
times. Its effects do not stack. Each time a character takes the feat, it applies 
to a different alignment-based domain to which the character has access. 

\vspace{12pt}
IMPROVED ARROW OF DEATH [EPIC] 

\textbf{Prerequisites:} Dex 19, Wis 19, Point Blank Shot, Precise Shot, arrow of 
death class feature. 

\textbf{Benefit:} Add +2 to the DC of the character's arrows of death. This feat 
may be taken multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED AURA OF COURAGE [EPIC] 

\textbf{Prerequisite:} Cha 25, aura of courage class ability. 

\textbf{Benefit:} The character's aura of courage grants a +8 morale bonus on saving 
throws against fear effects. 

\vspace{12pt}
IMPROVED AURA OF DESPAIR [EPIC] 

\textbf{Prerequisite:} Cha 25, aura of despair class ability. 

\textbf{Benefit:} The character's aura of despair causes a -4 morale penalty on 
all saving throws. 

\vspace{12pt}
IMPROVED COMBAT CASTING [EPIC] 

\textbf{Prerequisites:} Combat Casting, Concentration 25 ranks. 

\textbf{Benefit:} The character doesn't incur attacks of opportunity for casting 
spells when threatened. 

\vspace{12pt}
IMPROVED COMBAT REFLEXES [EPIC] 

\textbf{Prerequisites:} Dex 21, Combat Reflexes. 

\textbf{Benefit:} There is no limit to the number of attacks of opportunity the 
character can make in one round. (the character still can't make more than one 
attack of opportunity for a given oppertunity.) 

\vspace{12pt}
IMPROVED DARKVISION [EPIC]

\textbf{Prerequisite:} Darkvision. 

\textbf{Benefit:} The range of the character's darkvision doubles. This feat does 
not stack with darkvision granted by magic items or nonpermanent magical effects. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. Remember 
that two doublings equals a tripling, and so on. 

\vspace{12pt}
IMPROVED DEATH ATTACK [EPIC] 

\textbf{Prerequisites:} Death attack class feature, sneak attack +5d6. 

\textbf{Benefit:} Add +2 to the DC of the character's death attack. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED ELEMENTAL WILD SHAPE [WILD][EPIC] 

\textbf{Prerequisites:} Wis 25, ability to \textit{wild shape }into an elemental. 

\textbf{Benefit:} The character's ability to \textit{wild shape }into an elemental 
is expanded to include all elemental creatures (not just air, earth, fire, and 
water elementals) of any size that the character can take when using \textit{wild 
shape }to become an animal. The character gains all extraordinary and supernatural 
abilities of the elemental whose form he or she takes. 

\textbf{Normal:} Without this feat, a character may only \textit{wild shape }into 
a Small, Medium-size, or Large air, earth, fire, or water elemental. 

\vspace{12pt}
IMPROVED FAVORED ENEMY [EPIC] 

\textbf{Prerequisite:} Five or more favored enemies. 

\textbf{Benefit:} Add +1 to the bonus on Bluff, Listen, Sense Motive, Spot, and 
Survival checks and damage rolls against all the character's favored enemies. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED HEIGHTEN SPELL [EPIC] 

\textbf{Prerequisites:} Heighten Spell, Spellcraft 20 ranks. 

\textbf{Benefit:} As Heighten Spell, but there is no limit to the level to which 
the character can heighten the spell. 

\textbf{Normal:} Without this feat, a spell can only be heightened to a maximum 
of 9th level. 

\vspace{12pt}
IMPROVED KI STRIKE [EPIC] 

\textbf{Prerequisites:} Wis 21, \textit{Ki }strike (adamantine). 

\textbf{Benefit:} The character's unarmed strikes are treated as epic magic weapons 
for the purposes of damage reduction. 

\vspace{12pt}
IMPROVED LOW-LIGHT VISION [EPIC] 

\textbf{Prerequisite:} Low-light vision. 

\textbf{Benefit:} The range of the character's low-light vision doubles. This feat 
does not stack with low-light vision granted by magic items or nonpermanent magical 
effects. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. Remember 
that two doublings equals a tripling, and so on. 

\vspace{12pt}
IMPROVED MANIFESTATION [EPIC, PSIONIC]

You increase your power point reserve.

\textbf{Prerequisites:} Character level 21st, ability to manifest powers of the 
normal maximum power level in at least one psionic class.

\textbf{Benefit:} When you select this feat, you gain 19 power points.

\textbf{Special:} You can gain this feat multiple times. Each time you do so, you 
gain an additional number of power points

equal to your previous benefit +2.

\vspace{12pt}
IMPROVED MANYSHOT [EPIC] 

\textbf{Prerequisites:} Dex 19, base attack bonus +21, Many-shot, Point Blank Shot, 
Rapid Shot 

Benefits: As Manyshot, but the number of arrows the character can fire is limited 
only by his or her base attack bonus (two arrows, plus one arrow for every 5 points 
of base attack bonus above +6). 

\textbf{Special:} Regardless of the number of arrows the character fires, he or 
she only applies precision-based damage (such as sneak attack damage or the ranger's 
favored enemy bonus) once. If the character scores a critical hit, only one of 
the arrows deals critical damage (character's choice); all others deal normal damage. 

\textbf{Normal:} With the Manyshot feat, the character is limited to a maximum 
of four arrows fired (when the character's base attack bonus is +16 or higher).

\vspace{12pt}
IMPROVED METAMAGIC [EPIC] 

\textbf{Prerequisites:} Four metamagic feats, Spellcraft 30 ranks. 

\textbf{Benefit:} The spell slot modifier of all the character's metamagic feats 
is reduced by one level, to a minimum of +1. This feat has no effect on metamagic 
feats whose spell slot modifier is +1 or less. 

\textbf{Special:} A character can gain this feat multiple times. The effects stack, 
though a character can't reduce any metamagic feat's spell slot modifier to less 
than +1. 

\vspace{12pt}
IMPROVED METAPSIONICS [EPIC, PSIONIC]

You can manifest powers using metapsionic feats more easily than normal.

\textbf{Prerequisites:} Character level 21st, four metapsionic feats, Psicraft 
30 ranks.

\textbf{Benefit: }Metapsionic powers you manifest cost 2 power points less than 
normal (to a minimum of 1 power point).

This feat has no effect on metapsionic powers that inflate the cost by only 2 power 
points.

\textbf{Special:} You can gain this feat multiple times. The effects stack, though 
you can't lower the cost of any metapsionic

power to less than 1 power point.

\vspace{12pt}
IMPROVED SNEAK ATTACK [EPIC] 

\textbf{Prerequisite:} Sneak attack +8d6. 

\textbf{Benefit:} Add +1d6 to the character's sneak attack damage. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED SPELL CAPACITY [EPIC] 

\textbf{Prerequisite:} Ability to cast spells of the normal maximum spell level 
in at least one spellcasting class. 

\textbf{Benefit:} When the character selects this feat, he or she gains one spell 
slot per day of any level up to one level higher than the highest-level spell the 
character can already cast in a particular class. The character must still have 
the requisite ability score (10 + spell level) in order to cast any spell stored 
in this slot. If the character has a high enough ability modifier to gain one or 
more bonus spells for this spell level, he or she also gains the bonus spells for 
this spell level. The character must use the spell slot as a member of the class 
in which he or she can already cast spells of the normal maximum spell level.

\textbf{Special:} A character can gain this feat multiple times.

\vspace{12pt}
\subsection*{\textbf{Spell Slots Above 9th Level }}

The Improved Spell Capacity feat allows characters to gain spell slots above 9th 
level (which can be used to hold lower-level spells or spells whose level has been 
increased beyond 9th by the use of metamagic feats).

A character with a very high score in the ability associated with his or her spellcasting 
(Intelligence for wizards; Wisdom for clerics, druids, paladins, and rangers; or 
Charisma for bards and sorcerers) may receive bonus spells of those levels, as 
shown on Table: Expanded Ability Modifiers and Bonus Spells, but only if they already 
have at least one spell slot of that level (such as from the Improved Spell Capacity 
feat). A character without any spell slots of a level can't receive any bonus spells 
of that level, even if the appropriate ability score is high enough to award them.

Even though the table only includes ability scores up to 61 and spell slots up 
to 25th level, the progression continues infinitely in both directions. For ability 
scores beyond 61, or for spell slots above 25th level, expand the table to follow 
the same patterns as shown. 

\vspace{12pt}
\subsection*{\textbf{Table: Expanded Ability Modifiers and Bonus Spells}}

\subsection*{\begin{longtable}{lllllllllllllllllllllllllllllllllllll}
\hline
% ROW 1
\multicolumn{3}{|p{0.577in}|}{\begin{minipage}[t]{0.577in}\centering
\end{minipage}} & \multicolumn{16}{p{3.301in}|}{\begin{minipage}[t]{3.301in}\centering
---------------------------------------------\textbf{ Spells per Day -----------------------------------------------------}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
\textbf{Score}\end{minipage}} & \multicolumn{17}{p{0.588in}|}{\begin{minipage}[t]{0.588in}\raggedright
\textbf{Modifier}\end{minipage}} & \multicolumn{1}{|p{0.240in}|}{\begin{minipage}[t]{0.240in}\raggedright
\textbf{10th}\end{minipage}} & \multicolumn{2}{p{0.336in}|}{\begin{minipage}[t]{0.336in}\raggedright
\textbf{11th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{12th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{13th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{14th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{15th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{16th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{17th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{18th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{19th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{20th}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{21st}\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\textbf{22nd}\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
\textbf{23rd}\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
\textbf{24th}\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
\textbf{25th}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
10-11\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
+0\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
12-13\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+1\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
14-15\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
+2\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
16-17\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+3\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
18-19\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+4\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
---\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\centering
20-21\end{minipage}} & \multicolumn{1}{p{0.035in}|}{\begin{minipage}[t]{0.035in}\raggedright
+5\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 9
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
22-23\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+6\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 10
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
24-25\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+7\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 11
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
26-27\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+8\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 12
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
28-29\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+9\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 13
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
30-31\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+10\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 14
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
32-33\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+11\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 15
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
34-35\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+12\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 16
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
36-37\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+13\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 17
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
38-39\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+14\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 18
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
40-41\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+15\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 19
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
42-43\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+16\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 20
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
44-45\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+17\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 21
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
46-47\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+18\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 22
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
48-49\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+19\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 23
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
50-51\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+20\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 24
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
52-53\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+21\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 25
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
54-55\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+22\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 26
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
56-57\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+23\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 27
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
58-59\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+24\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
---\end{minipage}}\\
\hline
% ROW 28
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
60-61\end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
+25\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
4\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
3\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
2\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
1\end{minipage}}\\
\hline
% ROW 29
\multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\centering
etc. . . \end{minipage}} & \multicolumn{19}{p{0.828in}|}{\begin{minipage}[t]{0.828in}\raggedright
\end{minipage}} & \multicolumn{2}{|p{0.257in}|}{\begin{minipage}[t]{0.257in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.320in}|}{\begin{minipage}[t]{0.320in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.206in}|}{\begin{minipage}[t]{0.206in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.194in}|}{\begin{minipage}[t]{0.194in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.221in}|}{\begin{minipage}[t]{0.221in}\raggedright
\end{minipage}} & \multicolumn{1}{p{0.213in}|}{\begin{minipage}[t]{0.213in}\raggedright
\end{minipage}}\\
\hline
\end{longtable}
}

\vspace{12pt}
IMPROVED SPELL RESISTANCE [EPIC] 

\textbf{Prerequisite:} Must have spell resistance from a feat, class feature, or 
other permanent effect. 

\textbf{Benefit:} The character's spell resistance increases by +2. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED STUNNING FIST [EPIC] 

\textbf{Prerequisite:} Dex 19, Wis 19, Improved Unarmed Strike, Stunning Fist. 

\textbf{Benefit:} Add +2 to the DC of the character's stunning attack. 

\textbf{Special:} This feat may be taken multiple times. Its effects stack. 

\vspace{12pt}
IMPROVED WHIRLWIND ATTACK [EPIC] 

\textbf{Prerequisites:} Int 13, Dex 23, Combat Expertise, Dodge, Mobility, Spring 
Attack, Whirlwind Attack. 

\textbf{Benefit:} As a standard action, the character can make one melee attack 
for every five points of his or her base attack bonus (including epic attack bonus, 
round fractions down).

The character cannot attack any one opponent more than once as part of this action. 
 These attacks (as well as all other attacks made until the start of the character's 
next turn) suffer a -4 penalty.

When using the Improved Whirlwind feat, the character also forfeits any bonus or 
extra attacks granted by other spells or abilities (such as Cleave or the haste 
spell).

Since these attacks are made as part of a standard action the character can't make 
a 5-foot step between any two of the attacks.

\textbf{Normal:} Without this feat, using the Whirlwind Attack feat requires a 
full attack action, and the character can take a 5-foot step between any two of 
the attacks. 

\vspace{12pt}
INCITE RAGE [EPIC] 

\textbf{Prerequisites:} Cha 25, greater rage class feature. 

\textbf{Benefit:} When the character enters a rage, he or she can incite a barbarian 
rage in any or all allies within 60 feet. (Any ally who doesn't wish to become 
enraged is unaffected.) The ally gains +4 to Strength, +4 to Constitution, and 
a +2 morale bonus on Will saves, but takes a -2 penalty to AC, for as long as the 
character remains raging. The rage of affected allies lasts a number of rounds 
equal to 3 + their Constitution modifier, regardless of whether they remain within 
60 feet of the character. This is otherwise identical with normal barbarian rage 
(including the fatigue at its end). 

\textbf{Special:} This is a mind-affecting effect. 

\vspace{12pt}
INFINITE DEFLECTION [EPIC]

\textbf{Prerequisites:} Dex 25, Combat Reflexes, Deflect Arrows, Improved Unarmed 
Strike. 

\textbf{Benefit:} The character may perform any number of deflections each round, 
as the Deflect Arrows feat.

\vspace{12pt}
INSPIRE EXCELLENCE [EPIC] 

\textbf{Prerequisite:} Perform 30 ranks, bardic music class feature. 

\textbf{Benefit:} The character can use song or poetics to grant a bonus to one 
ability score to his or her allies. To be affected, an ally must hear the bard 
sing for 1 full round. The effect lasts as long as the bard sings and for 5 rounds 
after the bard stops singing (or 5 rounds after the ally can no longer hear the 
bard). While singing, the bard can fight but cannot cast spells, activate magic 
items by spell completion (such as scrolls), or activate magic items by command 
word (such as wands). Each ally to be inspired gains a +4 competence bonus to the 
same ability score, which the character must choose before he or she begins inspiring. 
Inspire excellence is a supernatural, mind-affecting ability. Use of this feat 
counts as one of the character's bardic music uses for the day.

\textbf{Special:} This feat is treated as a bardic music inspiration ability for 
purposes of feats that affect such abilities. 

\vspace{12pt}
INSTANT RELOAD [EPIC]

\textbf{Prerequisite:} Quick Draw, Rapid Reload, Weapon Focus (crossbow type to 
be selected). 

\textbf{Benefit:} The character may fire the selected type of crossbow at his or 
her full normal attack rate. Reloading the crossbow does not provoke attacks of 
opportunity. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different type 
of crossbow. 

\vspace{12pt}
INTENSIFY SPELL [METAMAGIC][EPIC] 

\textbf{Prerequisites:} Empower Spell, Maximize Spell, Spellcraft 30 ranks, ability 
to cast 9th-level arcane or divine spells. 

\textbf{Benefit:} All variable, numeric effects of an intensified spell are maximized, 
then doubled. An intensified spell deals twice maximum damage, cures twice the 
maximum number of hit points, affects twice the maximum number of targets, and 
so forth, as appropriate. Saving throws and opposed rolls are not affected. An 
intensified spell uses up a spell slot seven levels higher than the spell's actual 
level. A character can't combine the effects of this feat with any other feat that 
affects the variable, numeric effects of a spell. 

\vspace{12pt}
KEEN STRIKE [EPIC] 

\textbf{Prerequisites:} Str 23, Wis 23, Improved Critical (unarmed strike), Improved 
Unarmed Strike, Stunning fist, \textit{ki }strike (adamantine). 

\textbf{Benefit:} The character's unarmed strike has a critical threat range of 
18-20 and deals slashing damage (at the character's option any attack can deal 
bludgeoning damage, but cannot then take advantage of the enhanced threat range). 
This ability doesn't stack with other abilities that expand that character's unarmed 
strike's threat range. 

\vspace{12pt}
LASTING INSPIRATION [EPIC] 

\textbf{Prerequisite:} Perform 25 ranks, bardic music class feature. 

\textbf{Benefit:} The effects of the character's bardic music inspiration abilities 
last for ten times as long as normal after he or she stops singing. This feat has 
no effect on inspiration abilities that have no duration after the character stops 
singing. 

\vspace{12pt}
LEGENDARY CLIMBER [EPIC]

\textbf{Prerequisites:} Dex 21, Balance 12 ranks, Climb 24 ranks. 

\textbf{Benefit:} The character can ignore any check penalties applied for accelerated 
climbing or rapid climbing. 

\textbf{Normal:} Without this feat, a character takes a -5 penalty on Climb checks 
when attempting to cover his or her full speed in climbing distance in a round, 
or a -20 penalty when attempting to cover twice his or her speed in climbing distance 
in a round.

\vspace{12pt}
LEGENDARY COMMANDER [EPIC]

\textbf{Prerequisites:} Cha 25, Epic Leadership, Leadership, Diplomacy 30 ranks, 
must rule own kingdom and have a stronghold. 

\textbf{Benefit:} Multiply the number of followers of each level that the character 
can lead by 10. This has no effect on cohorts. 

\vspace{12pt}
LEGENDARY LEAPER [EPIC] 

\textbf{Prerequisite:} Jump 24 ranks. 

\textbf{Benefit:} The character need only move 5 feet in a straight line to make 
a running jump.

\textbf{Normal:} Without this feat, a character must move at least 20 feet in a 
straight line before attempting a running jump. 

\vspace{12pt}
LEGENDARY RIDER [EPIC]

\textbf{Prerequisite:} Ride 24 ranks. 

\textbf{Benefit:} The character doesn't take a penalty on Ride checks when riding 
a mount without a saddle (bareback).  The character never needs to make a Ride 
check to control a mount in combat (and even controlling a mount not trained for 
combat doesn't require an action). 

\textbf{Normal:} Without this feat, a character takes a -5 penalty on Ride checks 
without a saddle, and must make a Ride check to control a mount in combat (and 
controlling a mount not trained for combat requires a move action). 

\vspace{12pt}
LEGENDARY TRACKER [EPIC] 

\textbf{Prerequisites:} Wis 25, Track, Knowledge (nature) 30 ranks, Survival 30 
ranks. 

\textbf{Benefit:} The character can track creatures across water, under-water, 
or through the air. This adds the surfaces of water, underwater, and air to the 
list of surfaces found under the Track feat: 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.806in}|}{\begin{minipage}[t]{0.806in}\raggedright
\textbf{Surface}\end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Water\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.806in}|}{\begin{minipage}[t]{0.806in}\raggedright
Underwater\end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
80 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Air\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
120 \end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
LEGENDARY WRESTLER [EPIC] 

\textbf{Prerequisite:} Str 21, Dex 21, Improved Unarmed Strike, Escape Artist 15 
ranks. 

\textbf{Benefit:} The character gains a +10 bonus on all grapple checks. 

\vspace{12pt}
LINGERING DAMAGE [EPIC] 

\textbf{Prerequisite:} Sneak attack +8d6, crippling strike class feature. 

\textbf{Benefit:} Any time the character deals damage with a sneak attack, that 
target takes damage equal to the character's sneak attack bonus damage on the character's 
next turn as well. 

\vspace{12pt}
MAGICAL BEAST COMPANION [WILD][EPIC] 

\textbf{Prerequisites:} Knowledge (nature) 24 ranks, \textit{wild shape }6/day. 

\textbf{Benefit:} The following magical beasts are added to the lists of animal 
companions from which you can select.

\textbf{1st Level (no adjustment)} 

Stirge

Darkmantle

\vspace{12pt}
\textbf{4th Level (-3)}

Hippogriff

Shocker lizard

\vspace{12pt}
\textbf{7th Level (-6)}

Cockatrice

Ankheg

Griffon

Owlbear

Sea cat*

\vspace{12pt}
\textbf{10th Level (-9)}

Basilisk

Digerster

Girallon

Spider eater

\vspace{12pt}
\textbf{13th Level (-12)}

Bulette

Chimera

Remorhaz

\vspace{12pt}
\textbf{16th Level (-15)}

Gorgon

Gray render

\vspace{12pt}
\textbf{Special:} Creatures marked with an asterisk are available only in an aquatic 
environment.

\vspace{12pt}
MAGICAL BEAST WILD SHAPE [WILD][EPIC]

\textbf{Prerequisites:} Wis 25, Knowledge (nature) 27 ranks, \textit{wild shape 
}6/day. 

\textbf{Benefit:} The character can use his or her normal \textit{wild shape }ability 
to take the form of a magical beast. The size limitation is the same as the character's 
limitation on animal size. The character gains all supernatural abilities of the 
magical beast whose form he or she takes. 

\vspace{12pt}
MASTER STAFF [EPIC] 

\textbf{Prerequisite:} Craft Staff, Spellcraft 15 ranks. 

\textbf{Benefit:} When the character activates a staff, he or she can substitute 
a spell slot instead of using a charge. The spell slot must be one the character 
ahs not used for the day, though the character may lose a prepared spell to emulate 
a wand charge (the character may not lose prepared spells from his or her school 
of specialty, if any). The spell slot lost must be equal to or higher in level 
than the specific spell stored in the staff, including any level-increasing metamagic 
enhancements. A character cannot emulate a charge for a staff function that does 
not match a specific spell.

\vspace{12pt}
MASTER WAND [EPIC] 

\textbf{Prerequisite:} Craft Wand, Spellcraft 15 ranks. 

\textbf{Benefit:} When the character activates a wand, he or she can substitute 
a spell slot instead of using a charge. The spell slot must be one the character 
has not used for the day, though he or she may lose a prepared spell to emulate 
a wand charge (the character may not lose prepared spells from his or her school 
of specialty, if any). The spell slot lost must be equal to or higher in level 
than the spell stored in the wand, including any level-increasing metamagic enhancements. 

\vspace{12pt}
MIGHTY RAGE [EPIC] 

\textbf{Prerequisites:} Str 21, Con 21, greater rage class feature, rage 5/day. 

\textbf{Benefit:} When the character rages, he or she gains a +8 bonus to Strength 
and Constitution and a +4 morale bonus on Will saves. (These bonuses replace the 
normal rage bonuses.) 

\vspace{12pt}
MOBILE DEFENSE [EPIC]

\textbf{Prerequisites:} Dex 15, Dodge, Mobility, Spring Attack, defensive stance 
3/day class feature. 

\textbf{Benefit:} While in a defensive stance, the character may take one 5-foot 
adjustment each round without losing the benefits of the stance. 

\textbf{Normal:} Without this feat, a character can't move while in a defensive 
stance. 

\vspace{12pt}
MULTISPELL [EPIC] 

\textbf{Prerequisites:} Quicken Spell, ability to cast 9th-level arcane or divine 
spells. 

\textbf{Benefit:} The character may cast one additional quickened spell in a round. 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 

\vspace{12pt}
MULTIWEAPON REND [EPIC] 

\textbf{Prerequisites:} Dex 15, base attack bonus +9, three or more hands, Multiweapon 
Fighting. 

\textbf{Benefit:} If the character hits an opponent with two or more weapons (wielded 
in different hands) in the same round, he or she may automatically rend the opponent. 
This rending deals additional damage equal to the base damage of the smallest weapon 
that hit plus 1 1/2 times the character's Strength modifier. The character can 
only rend once per round, regardless of how many successful attacks he or she makes. 

\textbf{Special:} This feat replaces the Two-Weapon Rend feat for creatures with 
more than two arms. 

\vspace{12pt}
MUSIC OF THE GODS [EPIC] 

\textbf{Prerequisites:} Cha 25, Perform 30 ranks, bardic music class feature. 

\textbf{Benefit:} The character's bardic music can affect even those normally immune 
to mind-affecting effects. However, such creatures gain a +10 bonus on their Will 
saves to resist such effects. 

\vspace{12pt}
NEGATIVE ENERGY BURST [DIVINE][EPIC] 

\textbf{Prerequisites:} Cha 25, ability to rebuke or command undead, ability to 
cast \textit{inflict critical wound}s, any evil alignment. 

\textbf{Benefit:} The character can use one rebuke or command undead attempt to 
unleash a wave of negative energy in a 60-foot-burst. Roll a normal rebuke (or 
command) check, except that the negative energy burst affects living creatures 
rather than undead. Any creature that would be rebuked by this result gains one 
negative level. Any creature that would be commanded by this check gains two negative 
levels. The Fortitude save DC to remove these levels one day later is equal to 
10 + 1/2 the character's effective turning level + the character's Charisma modifier. 

\vspace{12pt}
OVERWHELMING CRITICAL [EPIC] 

\textbf{Prerequisites:} Str 23, Cleave, Great Cleave, Improved Critical (chosen 
weapon), Power Attack, Weapon Focus (chosen weapon). 

\textbf{Benefit:} When using the weapon the character has selected, he or she deals 
an extra 1d6 points of bonus damage on a successful critical hit. If the weapon's 
critical multiplier is x3, add +2d6 points of bonus damage instead, and if the 
multiplier is x4, add +3d6 points of bonus damage instead. Creatures immune to 
critical hits can't be affected by this feat.

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different type 
of weapon. 

\vspace{12pt}
PENETRATE DAMAGE REDUCTION [EPIC] 

Select a special material, such as adamantine. 

\textbf{Benefit: }The character melee weapons (including natural weapons) are treated 
as being crafted from the chosen special material for the purposes of bypassing 
the damage reduction of any creature the character strikes. None of the other special 
properties of special materials are gained by the character's melee weapons.

\textbf{Special:} A character can gain this feat multiple times.  Each time the 
feat is selected the character selects a different special material.  The character's 
melee attacks are treated as being crafted of all chosen materials for the purposes 
of bypassing damage reduction.

\vspace{12pt}
PERFECT HEALTH [EPIC] 

\textbf{Prerequisite:} Con 25, Great Fortitude. 

\textbf{Benefit:} The character is immune to all nonmagical diseases, as well as 
to all poisons whose Fortitude save DC is 25 or less. 

\vspace{12pt}
PERFECT MULTIWEAPON FIGHTING [EPIC] 

\textbf{Prerequisite:} Dex 25, three or more hands, Greater Multiweapon Fighting, 
Multiweapon Fighting. 

\textbf{Benefit:} The character can make as many attacks with each extra weapon 
as with his or her primary weapon, using the same base attack bonus. The character 
still takes the normal penalties for fighting with two weapons. 

\textbf{Normal:} A creature without this feat can make only one attack per round 
with each extra weapon (or two attacks per round with each weapon if it has Multiweapon 
Fighting, or three attacks per round with each extra weapon if it has Greater Multiweapon 
Fighting). Each attack after the first extra attack has a cumulative -5 penalty. 

\textbf{Special:} This feat replaces the Perfect Two-Weapon Fighting feat for creatures 
with more than two arms.

\vspace{12pt}
PERFECT TWO-WEAPON FIGHTING [EPIC] 

\textbf{Prerequisites:} Dex 25, Greater Two-Weapon Fighting, Improved Two-Weapon 
Fighting, Two-Weapon Fighting. 

\textbf{Benefit:} The character can make as many attacks with his or her off-hand 
weapon as with his or her primary weapon, using the same base attack bonus. The 
character still takes the normal penalties for fighting with two weapons. 

\textbf{Normal:} Without this feat, a character can only get a single attack with 
an off-hand weapon (or two attacks with an off-hand weapon if he or she has Improved 
Two-Weapon Fighting, or three attacks with an off-hand weapon if he or she has 
Greater Two-Weapon Fighting). 

\vspace{12pt}
PERMANENT EMANATION [EPIC] 

\textbf{Prerequisites:} Spellcraft 25 ranks, ability to cast the spell to be made 
permanent. 

\textbf{Benefit:} Designate any one of the character's spells whose area is an 
emanation from the character. This spell's effect is permanent (though the character 
can dismiss or restart it as a free action). Effects that would normally dispel 
this spell instead suppress it for 2d4 rounds. 

\textbf{Special:} This feat may be taken multiple times. Each time, select a different 
spell to become permanent. 

\vspace{12pt}
PLANAR TURNING [EPIC] 

\textbf{Prerequisites:} Wis 25, Cha 25, ability to turn or rebuke undead. 

\textbf{Benefit:} The character can turn or rebuke outsiders as if they were undead. 
An outsider has effective turn resistance equal to half its spell resistance (round 
down). If the character can turn undead, he or she turns (or destroys) all evil 
outsiders and rebukes (or commands) all nonevil outsiders. If the character can 
rebuke undead, he or she rebukes (or commands) all evil outsiders and turns (or 
destroys) all nonevil outsiders. 

\vspace{12pt}
PLANT WILD SHAPE [WILD][EPIC]

\textbf{Prerequisites:} Knowledge (nature) 24 ranks, \textit{wild shape }4/day. 

\textbf{Benefit:} The character can use his or her normal \textit{wild shape }ability 
to take the form of a plant. The size limitation is the same as the character's 
limitation on animal size. 

\vspace{12pt}
POLYGLOT [EPIC] 

\textbf{Prerequisites:} Int 25, Speak Language (five languages). 

\textbf{Benefit:} The character can speak all languages. If the character is literate, 
he or she can also read and write all languages (not including magical script). 

\vspace{12pt}
POSITIVE ENERGY AURA [EPIC] 

\textbf{Prerequisites:} Cha 25, ability to turn undead, ability to cast \textit{dispel 
evil. }

\textbf{Benefit:} Every undead creature that comes within 15 feet of the character 
is automatically affected as if the character had turned it. This doesn't cost 
a turning attempt, and the character doesn't have to roll turning damage (it automatically 
affects all undead in a 15-foot burst), but it only turns undead with Hit Dice 
equal to or less than the character's effective cleric level minus 10 (and automatically 
destroys undead with Hit Dice equal to or less than the character's effective cleric 
level minus 20). Just as with normal turning, the character can't affect undead 
that have total cover relative to him or her. 

\vspace{12pt}
POWER KNOWLEDGE [EPIC, PSIONIC]

You add two additional powers to your list of powers known.

\textbf{Prerequisites: }Character level 21st, ability to manifest powers of the 
normal maximum power level in at least one psionic class.

\textbf{Benefit:} You learn two new powers of any level up to the highest level 
of power you can manifest. The powers you select must be on your class list or 
the list for your discipline.

\textbf{Special:} You can gain this feat multiple times. Each time, you learn two 
new powers at any level up to the highest level of power you can manifest.

\vspace{12pt}
PSICRYSTAL POWER [EPIC, PSIONIC]

Your psicrystal can manifest a power.

\textbf{Prerequisites:} Character level 21st, Intelligence 25 or Charisma 25 (depending 
on which is your key ability score for manifesting).

\textbf{Benefit:} Choose one power you know of 8th level or lower. Your psicrystal 
can now manifest this power once per day at your manifester level (the psicrystal 
gains sufficient power points to manifest the power once). You cannot bestow a 
power upon your psicrystal if the power normally has any experience point cost.

\textbf{Special: }You can gain this feat multiple times. Each time you take the 
feat, you can give your psicrystal knowledge of a new power (and it gains sufficient 
power points to manifest that power once).

All power points gained by a psicrystal from multiple applications of this feat 
go into its reserve and can be used to manifest the powers it knows as you desire.

\vspace{12pt}
RANGED INSPIRATION [EPIC] 

\textbf{Prerequisite:} Bardic music class feature, Perform 25 ranks 

\textbf{Benefit:} Double the range of any bardic music ability that has a range. 
(If the creature must hear the bard to be affected by the ability, that requirement 
doesn't change regardless of any extended range the bard's ability may have.) 

\textbf{Special:} A character can gain this feat multiple times. Its effects stack. 
Remember that two doublings equals a tripling, and so forth.

\vspace{12pt}
RAPID INSPIRATION [EPIC]

\textbf{Prerequisite:} Perform 25 ranks, bardic music class feature. 

\textbf{Benefit:} The character can use any of his or her bardic music inspiration 
abilities as a standard action. The inspiration takes effect immediately after 
the character concludes the action. 

\vspace{12pt}
REACTIVE COUNTERSONG [EPIC] 

\textbf{Prerequisite:} Combat Reflexes, Perform 30 ranks, bardic music class feature. 

\textbf{Benefit:} The character can begin a countersong at any time, even when 
it isn't his or her turn (much like a wizard who has readied a counterspell action), 
though the character doesn't have to ready an action to do so. The character can't 
use Reactive Countersong at the same time he or she isusing another bardic music 
ability (though the character could stop the other bardic music ability to begin 
Reactive Countersong if so desired). 

\textbf{Normal:} Without this feat, a character can only use counter-song on his 
or her turn. 

\vspace{12pt}
REFLECT ARROWS [EPIC] 

\textbf{Prerequisites:} Dex 25, Deflect Arrows, Improved Unarmed Strike. 

\textbf{Benefit:} When the character deflects an arrow or other ranged attack, 
the attack is reflected back upon the attacker at the character's base ranged attack 
bonus. 

\vspace{12pt}
RIGHTEOUS STRIKE [EPIC] 

\textbf{Prerequisites:} Wis 19, Improved Unarmed Strike, Stunning Fist, any lawful 
alignment. 

\textbf{Benefit:} The character's unarmed strike is treated as an axiomatic weapon 
(it is lawfully aligned and deals an extra 2d6 points of damage against creatures 
of chaotic alignment). This ability doesn't stack with similar abilities. 

\vspace{12pt}
RUINOUS RAGE [EPIC] 

\textbf{Prerequisites:} Str 25, Improved Sunder, Power Attack, rage 5/day. 

\textbf{Benefit:} While in a rage, the character ignores the hardness of any object 
he or she strikes. Also, double the character's Strength bonus for the purposes 
of any Strength check made to break an object with sudden force rather than by 
dealing normal damage (including bursting bindings, such as ropes or manacles). 

\vspace{12pt}
SCRIBE EPIC SCROLL [ITEM CREATION][EPIC] 

\textbf{Prerequisites:} Scribe Scroll, Knowledge (arcana) 24 ranks, Spellcraft 
24 ranks. 

\textbf{Benefit:} The character can scribe scrolls that exceed the normal limits 
for such items. Even this feat does not allow the character to scribe a scroll 
with an epic spell.

\vspace{12pt}
SELF-CONCEALMENT [EPIC] 

\textbf{Prerequisites:} Dex 30, Hide 30 ranks, Tumble 30 ranks, improved evasion. 

\textbf{Benefit:} Attacks against the character have a 10\% miss chance, similar 
to the effect of concealment. The character loses this benefit whenever he or she 
would lose his or her Dexterity bonus to AC. 

\textbf{Special:} This feat may be taken multiple times. Each time it is taken, 
the miss chance increases by 10\% to a maximum of 50\% after it has been taken 
five times. 

\vspace{12pt}
SHATTERING STRIKE [EPIC] 

\textbf{Prerequisites:} Epic Weapon Focus (unarmed strike), Weapon Focus (unarmed 
strike), Concentration 25 ranks, \textit{ki }strike (adamantine). 

\textbf{Benefit:} When using an unarmed strike to attempt to break an object with 
sudden force (rather than by dealing normal damage), make a Concentration check 
rather than a Strength check. The break DC remains the same. Using Shattering Strike 
is a full-round action that incurs attacks of opportunity. The character can't 
use Shattering Strike to escape bonds (unless he or she is so bound as to allow 
the character to make an unarmed strike against his or her bindings). 

\vspace{12pt}
SNEAK ATTACK OF OPPORTUNITY [EPIC] 

\textbf{Prerequisites:} Sneak attack +8d6, opportunist class feature. 

\textbf{Benefit:} Any attack of opportunity the character makes is considered a 
sneak attack. 

\vspace{12pt}
SPECTRAL STRIKE [EPIC] 

\textbf{Prerequisites:} Wis 19, ability to turn or rebuke undead. 

\textbf{Benefit:} The character's attacks deal damage normally against incorporeal 
creatures. 

\textbf{Normal:} Without this feat, even attacks that can damage an incorporeal 
creature have a 50\% chance to deal no damage.

\vspace{12pt}
SPELL KNOWLEDGE [EPIC] 

\textbf{Prerequisite:} Ability to cast spells of the maximum normal spell level 
of an arcane spellcasting class. 

\textbf{Benefit:} The character learns two new arcane spells of any level up to 
the maximum level he or she can cast. This feat does not grant any additional spell 
slots. 

\textbf{Special:} A character can gain this feat multiple times. 

\vspace{12pt}
SPELL OPPORTUNITY [EPIC] 

\textbf{Prerequisites:} Combat Casting, Combat Reflexes, Quicken Spell, Spellcraft 
25 ranks. 

\textbf{Benefit:} Whenever the character is allowed an attack of opportunity, he 
or she may cast (and attack with) a touch spell as the character's attack of opportunity. 
This incurs attacks of opportunity just as if the character had cast the spell 
normally. 

\textbf{Normal:} Without this feat, a character can only make a melee attack as 
an attack of opportunity. 

\vspace{12pt}
SPELL STOWAWAY [EPIC] 

\textbf{Prerequisites:} Spellcraft 24 ranks, caster level 12th. 

\textbf{Benefit:} Choose a spell-like ability the character knows, or a spell the 
character cam cast.  The character is attuned to the magic he or she chooses. If 
another spellcaster within 300 feet of the character uses this magic, the character 
also immediately gains the magic's effect as if it had been used on the character 
by the same caster. The character must have direct line of effect to the spellcaster 
in order to gain the benefit of the attuned magic (though the character does not 
have to know the spellcaster is present, and he or she can be flat-footed). The 
magic's duration, effect, and other specifics are determined by its original caster's 
level. 

\textbf{Special:} A character can gain this feat multiple times. Its effects do 
not stack. Each time a character takes the feat, it applies to a different spell 
or spell-like ability. 

\vspace{12pt}
SPELLCASTING HARRIER [EPIC] 

\textbf{Prerequisite:} Combat Reflexes. 

\textbf{Benefit:} Any spellcaster the character threatens in melee provokes an 
attack of opportunity if he or she tries to cast defensively.  The character gets 
a +4 bonus on this attack roll.

\vspace{12pt}
SPONTANEOUS DOMAIN ACCESS [EPIC]

\textbf{Prerequisites:} Wis 25, Spellcraft 30 ranks, ability to cast 9th-level 
divine spells. 

\textbf{Benefit:} Select a domain the character has access to. The character may 
spontaneously convert any prepared cleric spell (except a domain spell) into a 
domain spell of the same level in the selected domain, just as a cleric channels 
energy to convert spells into \textit{cure }spells. 

\textbf{Special:} A character can gain this feat multiple times. Each time a character 
takes the feat, it applies to a different domain. 

\vspace{12pt}
SPONTANEOUS SPELL [EPIC]

\textbf{Prerequisite:} Spellcraft 25 ranks, ability to cast the maximum normal 
spell level of at least one spell-casting class. 

\textbf{Benefit:} Select a spell the character can cast. The character may spontaneously 
convert any prepared spell of the selected spell's level into the selected spell, 
just as a cleric channels energy to convert spells into \textit{cure }spells. 

\textbf{Special:} A character can gain this feat multiple times. Each time he or 
she takes the feat, it applies to a different spell. 

\vspace{12pt}
STORM OF THROWS [EPIC] 

\textbf{Prerequisite:} Dex 23, Point Blank Shot, Quick Draw, Rapid Shot. 

\textbf{Benefit:} As a full-round action, the character may throw a light weapon 
at his or her full base attack bonus at each opponent within 30 feet. All light 
weapons thrown need not be the same type. 

\vspace{12pt}
SUPERIOR INITIATIVE [EPIC] 

\textbf{Prerequisite:} Improved Initiative. 

\textbf{Benefit:} The character gets a +8 bonus on initiative checks. This bonus 
overlaps (does not stack with) the bonus from Improved Initiative. 

\vspace{12pt}
SWARM OF ARROWS [EPIC]

\textbf{Prerequisites:} Dex 23, Point Blank Shot, Rapid Shot, Weapon Focus (type 
of bow used). 

\textbf{Benefit:} As a full-round action, the character may fire an arrow at his 
or her full base attack bonus at each opponent within 30 feet. 

\vspace{12pt}
TERRIFYING RAGE [EPIC]

\textbf{Prerequisites:} Intimidate 25 ranks, rage 5/day

\textbf{Benefit:} While you are raging, any enemy that views you must make a Will 
save opposed by your Intimidate check of become panicked (if it have HD less than 
your character level) or shaken (if it has HD equal to or up to twice your character 
level) for 4d6 rounds.  An enemy with Hit Dice greater than twice your character 
level is not affected by this feat.

\vspace{12pt}
TENACIOUS MAGIC [EPIC] 

\textbf{Prerequisites:} Spellcraft 15 ranks. 

\textbf{Benefit:} Choose one spell the character knows or spell-like ability the 
character possesses. Whenever the chosen form of magic would otherwise end due 
to a \textit{dispel }effect, the magic is instead only suppressed for 1d4 rounds. 
The magic still ends when its duration expires, but the suppressed rounds do not 
count against its duration. The character can dismiss his or her own spell or spell-like 
ability (if dismissible) or dispel his or her own tenacious magic normally. 

\textbf{Special:} A character can gain this feat multiple times. Each time he or 
she takes the feat, it applies to a different spell or spell-like ability. 

\vspace{12pt}
THUNDERING RAGE [EPIC] 

\textbf{Prerequisites:} Str 25, rage 5/day. 

\textbf{Benefit:} Any weapon the character wields while in a rage is treated as 
a thundering weapon. The DC of the Fortitude save to resist deafness is equal to 
10 + 1/2 the character's level. This ability does not stack with similar abilities. 

\vspace{12pt}
TRAP SENSE [EPIC] 

\textbf{Prerequisites:} Search 25 ranks, Spot 25 ranks, trapfinding class ability. 

\textbf{Benefit:} If the character passes within 5 feet of a trap, he or she is 
entitled to a Search check to notice it as if the character was actively looking 
for it. 

\vspace{12pt}
TWO-WEAPON REND [EPIC] 

\textbf{Prerequisites:} Dex 15, base attack bonus +9, Improved Two-Weapon Fighting, 
Two-Weapon Fighting. 

\textbf{Benefit:} If the character hits an opponent with a weapon in each hand 
in the same round, he or she may automatically rend the opponent. This deals additional 
damage equal to the base damage of the smaller weapon plus 1 1/2 times the character's 
Strength modifier. Base weapon damage includes an enhancement bonus on damage, 
if any. The character can only rend once per round, regardless of how many successful 
attacks he or she makes. 

\vspace{12pt}
UNCANNY ACCURACY [EPIC]

\textbf{Prerequisites:} Dex 21, base attack bonus +11, Point Blank Shot, Precise 
Shot, Improved Precise Shot, Spot 20 ranks. 

\textbf{Benefit:} The character's ranged attacks ignore the miss chance granted 
to targets by total concealment.  The character must aim his or her attacks at 
the correct square to gain advantage of this feat. 

\textbf{Normal:} Without this feat, characters suffer a 50\% miss chance when making 
a ranged attack against a target with total concealment.

\textbf{Special:} A character with at least 11 levels of ranger can qualify for 
this feat even if he or she does not have the prerequisites for it, but can only 
use it when wearing light or no armor.

\vspace{12pt}
UNDEAD MASTERY [DIVINE][EPIC] 

\textbf{Prerequisites:} Cha 21, ability to rebuke or command undead. 

\textbf{Benefit:} The character may command up to ten times his or her level in 
HD of undead. 

\vspace{12pt}
UNHOLY STRIKE [EPIC] 

\textbf{Prerequisites:} Smite good class feature, any evil alignment. 

\textbf{Benefit:} Any weapon the character wields is treated as an unholy weapon 
(it is evil-aligned and deals an extra 2d6 points of damage against creatures of 
good alignment). This ability doesn't stack with similar abilities. If the weapon 
already has an alignment, this feat has no effect on the weapon.

\vspace{12pt}
VERMIN WILD SHAPE [WILD][EPIC] 

\textbf{Prerequisites:} Knowledge (nature) 24 ranks, \textit{wild shape }6/day. 

\textbf{Benefit:} The character can use his or her normal \textit{wild shape }ability 
to take the form of a vermin. The size limitation is the same as the character's 
limitation on animal size. 

\vspace{12pt}
VORPAL STRIKE [EPIC] 

\textbf{Prerequisites:} Str 25, Wis 25, Improved Critical (unarmed strike), Improved 
Unarmed Strike, Keen Strike, Stunning Fist, \textit{ki }strike (adamantine). 

\textbf{Benefit:} The character's unarmed strike is considered to be a slashing 
vorpal weapon. (At the character's option, any unarmed strike can do bludgeoning 
damage instead, but it loses the vorpal quality.) This ability doesn't stack with 
similar abilities

\vspace{12pt}
WIDEN AURA OF COURAGE [EPIC]

\textbf{Prerequisite:} Cha 25, aura of courage class ability. 

\textbf{Benefit:} The character's aura of courage extends to all allies within 
100 feet of the character. 

\vspace{12pt}
WIDEN AURA OF DESPAIR [EPIC] 

\textbf{Prerequisite:} Cha 25, aura of despair class ability. 

\textbf{Benefit:} The character's aura of despair extends to all allies within 
100 feet of the character. 

\vspace{12pt}
ZONE OF ANIMATION [DIVINE][EPIC]

\textbf{Prerequisite:} Cha 25, Undead Mastery, ability to rebuke or command undead. 

\textbf{Benefit:} The character can use a rebuke or command undead attempt to animate 
corpses within range of his or her rebuke or command attempt. The character animates 
a total number of HD of undead equal to the number of undead that would be commanded 
by the character's result (though the character can't animate more undead than 
there are available corpses within range). The character can't animate more undead 
with any single attempt than the maximum number he or she can command (including 
any undead already under his or her command). These undead are automatically under 
the character's command, though his or her normal limit of commanded undead still 
applies. If the corpses are relatively fresh, the animated undead are zombies. 
Otherwise, they are skeletons.

\end{document}
