%&LaTeX
% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\usepackage{longtable}

\newcommand{\tab}{\hspace{5mm}}

nt, and is licensed for public use under the terms 
of the Open Game License v1.0a.

\section*{{\LARGE EPIC SKILLS }}

\vspace{12pt}
Despite the near-magical nature of some epic level skill uses, all uses of skills 
are considered exceptional abilities (except if noted otherwise), and thus function 
normally even within areas of antimagic. 

\vspace{12pt}
\subsection*{\textbf{Skill Synergy }}

Many skills are noted as granting a synergy bonus to the use of another skill when 
a character has 5 or more ranks in the first skill. This synergy bonus increases 
by +2 for every additional 20 ranks the character has in the skill. 

\vspace{12pt}
SKILL DESCRIPTIONS 

This section describes new DCs and new modifiers for skills. 

\vspace{12pt}
\subsection*{Appraise }

The character can sense magical auras in objects. 

\begin{longtable}{|p{0.887in}|p{0.351in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.887in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{0.351in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Detect magic\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright 50 
\end{minipage}\\
\hline
\end{longtable}

\textbf{Detect Magic:}\textit{ }The character can sense if an item has a magical 
aura. He or she can then use Spellcraft to learn more about the item as if he or 
she had already cast \textit{detect magic }on the item. This requires a full-round 
action. 

\vspace{12pt}
\subsection*{Balance }

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.146in}|}{\begin{minipage}[t]{1.146in}\raggedright
\textbf{Surface}\end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1-2 inches wide\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
20 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.146in}|}{\begin{minipage}[t]{1.146in}\raggedright
Up to 1 inch wide\end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
40 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Hair-thin\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.146in}|}{\begin{minipage}[t]{1.146in}\raggedright
Liquid*\end{minipage}} & \multicolumn{3}{p{0.497in}|}{\begin{minipage}[t]{0.497in}\raggedright
90 \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Cloud\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
120 \end{minipage}}\\
\hline
\end{longtable}


*Includes any other surface that couldn't support the character's weight, such 
as a fragile branch. 

\vspace{12pt}
\subsection*{Bluff }

The character can implant a nonmagical suggestion in a target, display a false 
alignment, or disguise his or her surface thoughts. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.597in}|}{\begin{minipage}[t]{1.597in}\raggedright
\textbf{Example Circumstance}\end{minipage}} & \multicolumn{1}{p{1.492in}|}{\begin{minipage}[t]{1.492in}\centering
\textbf{Sense Motive Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Instill suggestion in target\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+50\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.597in}|}{\begin{minipage}[t]{1.597in}\centering
\textbf{Task}\end{minipage}} & \multicolumn{1}{p{1.492in}|}{\begin{minipage}[t]{1.492in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
Display false alignment\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
70 \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.597in}|}{\begin{minipage}[t]{1.597in}\centering
Disguise surface thoughts\end{minipage}} & \multicolumn{1}{p{1.492in}|}{\begin{minipage}[t]{1.492in}\raggedright
100 \end{minipage}}\\
\hline
\end{longtable}

\textbf{Instill Suggestion in Target:}\textit{ }This is identical to the effect 
of the \textit{suggestion }spell, except that it is nonmagical and lasts for only 
10 minutes. It can be sensed as if it were an enchantment effect (Sense Motive 
DC 25). 

\textbf{Display False Alignment:}\textit{ }The character can fool alignment-sensing 
effects by displaying a false alignment of his or her choice. Once set, a false 
alignment remains as long as the character remains conscious and awake. Setting 
or changing a false alignment requires a full-round action. 

\textbf{Disguise Surface Thoughts:}\textit{ }The character can fool spells such 
as \textit{detect thoughts }(or similar effects) by displaying false surface thoughts. 
While the character can't completely mask the presence of his or her thoughts, 
he or she can change his or her apparent Intelligence score (and thus the character's 
apparent mental strength) by as much as 10 points and can place any thought in 
his or her ``surface thoughts'' to be read by such spells or effects. If a character 
attempts to use Sense Motive to detect his or her surface thoughts (see the Sense 
Motive skill description), this becomes an opposed check (though any result lower 
than 100 automatically fails). 

\vspace{12pt}
\subsection*{Climb }

The character can climb otherwise unclimbable surfaces. 

\begin{longtable}{|p{0.358in}|p{2.626in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.358in}\raggedright \textbf{DC}\end{minipage} & \begin{minipage}[t]{2.626in}\raggedright \textbf{Surface 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright 70\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright A 
perfectly smooth, flat, vertical surface \end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{0.358in}\raggedright 100\end{minipage} & \begin{minipage}[t]{2.626in}\raggedright A 
perfectly smooth, flat, overhang or ceiling \end{minipage}\\
\hline
\end{longtable}

\textbf{Rapid Climbing:}\textit{ }A character can climb his or her speed as a move-equivalent 
action, or double his or her speed as a full-round action (requiring two Climb 
checks), but the character takes a -20 penalty on his or her check. 

Special: The Legendary Climber feat allows a character to ignore any penalties 
for accelerated or rapid climbing. 

\vspace{12pt}
\subsection*{Concentration }

The character can cast spells with somatic components even while grappled. 

\begin{longtable}{|p{3.028in}|p{1.250in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{3.028in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{1.250in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Cast spell with somatic component while 
grappled\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright 50 + spell level 
\end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Craft }

The character can craft items more quickly than normal. 

\begin{longtable}{|p{0.972in}|p{1.208in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.972in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{1.208in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Quick creation\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright +10 
or more to DC \end{minipage}\\
\hline
\end{longtable}

\textbf{Quick Creation: }A character can voluntarily increase the DC of crafting 
an item by any multiple of 10. This allows the character to create an item more 
quickly (since he or she will be multiplying this higher DC by his or her skill 
check result to determine progress). The character must decide the increase to 
the DC before making the check. 

\vspace{12pt}
\subsection*{Craft (Alchemy)}

\subsection*{\begin{longtable}{|p{1.731in}|p{1.403in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.731in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{1.403in}\raggedright \textbf{DC 
(or DC Modifier) }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Create augmented substance\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright +20 
or more to DC \end{minipage}\\
\hline
\end{longtable}
}

\textbf{Create Augmented Alchemical Item or Substance:}\textit{ }This requires 
the Augmented Alchemy feat, and allows a character to create alchemical items and 
substances of greater power than normal. To augment an alchemical substance, add 
+20 to the DC required to create the item and multiply the cost by 5. If the item 
or substance deals damage, double the damage dealt. If the item or substance doesn't 
deal damage, double the duration of its effect. If the item or substance doesn't 
deal damage and doesn't have a specific listed duration (or has an instantaneous 
duration), double all dimensions of its area. If the item or substance doesn't 
fit any of these categories, then it cannot be improved in this manner. A character 
can create an item with multiple degrees of augmentation. For every additional 
multiplier applied to damage, duration, or area, add an additional +20 to the DC 
and add an additional 5 to the cost multiplier. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.049in}|}{\begin{minipage}[t]{1.049in}\raggedright
\textbf{Item}\end{minipage}} & \multicolumn{1}{p{2.665in}|}{\begin{minipage}[t]{2.665in}\raggedright
\textbf{Effect of Augmenting }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Acid\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Direct hit 2d6, splash 2 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.049in}|}{\begin{minipage}[t]{1.049in}\raggedright
Alchemist's fire\end{minipage}} & \multicolumn{1}{p{2.665in}|}{\begin{minipage}[t]{2.665in}\raggedright
Direct hit 2d6, splash 2 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Antitoxin\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Duration 2 hours \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.049in}|}{\begin{minipage}[t]{1.049in}\raggedright
Smokestick\end{minipage}} & \multicolumn{3}{p{2.803in}|}{\begin{minipage}[t]{2.803in}\raggedright
Smoke fills a 20-foot cube \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Sunrod\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Glows for 12 hours \end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.049in}|}{\begin{minipage}[t]{1.049in}\raggedright
Tanglefoot bag \end{minipage}} & \multicolumn{3}{p{2.803in}|}{\begin{minipage}[t]{2.803in}\raggedright
Becomes brittle and fragile after 20 minutes\end{minipage}}\\
\hline
% ROW 8
\multicolumn{1}{|p{1.049in}|}{\begin{minipage}[t]{1.049in}\raggedright
Tindertwig\end{minipage}} & \multicolumn{3}{p{2.803in}|}{\begin{minipage}[t]{2.803in}\raggedright
No effect \end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Decipher Script }

The character can decipher magic scrolls. 

\begin{longtable}{|p{2.200in}|p{1.750in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{2.200in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{1.750in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Decipher a written spell (such as a scroll) 
without using \textit{read magi}c. One try per day.\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright 50 
+ 5 times spell level \end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Diplomacy }

The character can turn a person into a fanatic follower. Refer to the accompanying 
table.

\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
\end{minipage}} & \multicolumn{6}{p{3.307in}|}{\begin{minipage}[t]{3.307in}\centering
------------------\textbf{New Attitude ------------------}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
\textbf{Initial Attitude}\end{minipage}} & \multicolumn{6}{p{0.325in}|}{\begin{minipage}[t]{0.325in}\centering
\textbf{Hos}\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
\textbf{Unf}\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
\textbf{Indif}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
\textbf{Friend}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
\textbf{Help}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
\textbf{Fanatic}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Hostile\end{minipage}} & \multicolumn{1}{p{0.467in}|}{\begin{minipage}[t]{0.467in}\centering
Less than 20\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
20\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
25\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
35\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
50\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
150\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Unfriendly\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Less than 5\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
15\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
25\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
40\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
120\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Indifferent\end{minipage}} & \multicolumn{8}{p{0.847in}|}{\begin{minipage}[t]{0.847in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
15\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
30\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
90\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Friendly\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
20\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
60\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Helpful\end{minipage}} & \multicolumn{8}{p{0.847in}|}{\begin{minipage}[t]{0.847in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
50\end{minipage}}\\
\hline
\end{longtable}

\textbf{Hos:}\textit{ }hostile. \textbf{Unf:}\textit{ }unfriendly. \textbf{Indif:}\textit{ 
}indifferent. \textbf{Friend:}\textit{ }friendly. \textbf{Help: }helpful. 

\textbf{Fanatic: }The attitude of fanatic is added here. In addition to the obvious 
effects, any NPC whose attitude is fanatic gains a +2 morale bonus to Strength 
and Constitution scores, a +1 morale bonus on Will saves, and a -1 penalty to AC 
whenever fighting for the character or his or her cause. This attitude will remain 
for one day plus one day per point of the character's Charisma bonus, at which 
point the NPC's attitude will revert to its original attitude (or indifferent, 
if no attitude is specified). 

Treat the fanatic attitude as a mind-affecting enchantment effect for purposes 
of immunity, save bonuses, or being detected by the Sense Motive skill. Since it 
is nonmagical, it can't be dispelled; however, any effect that suppresses or counters 
mind-affecting effects will affect it normally. A fanatic NPC's attitude can't 
be further adjusted by the use of skills. 

\begin{longtable}{|p{0.394in}|p{1.023in}|p{2.955in}|p{0.042in}|p{0.042in}|p{0.042in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.394in}\raggedright \textbf{Attitude }\end{minipage} & \begin{minipage}[t]{1.023in}\raggedright \textbf{Means}\end{minipage} & \begin{minipage}[t]{2.955in}\raggedright \textbf{Possible 
Actions }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.042in}\raggedright Fanatic \end{minipage} & \begin{minipage}[t]{0.042in}\raggedright Will 
give life to serve you\end{minipage} & \begin{minipage}[t]{0.042in}\raggedright Fight 
to the death against overwhelming odds, throw self in front of onrushing dragon 
\end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Disable Device }

The character can rush his or her Disable Device attempt, reducing the amount of 
time it takes to perform the attempt.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.473in}|}{\begin{minipage}[t]{1.473in}\raggedright
\textbf{Reduce to}\end{minipage}} & \multicolumn{1}{p{0.910in}|}{\begin{minipage}[t]{0.910in}\raggedright
\textbf{DC Modifier }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1 round\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+20 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.473in}|}{\begin{minipage}[t]{1.473in}\raggedright
Move-equivalent action\end{minipage}} & \multicolumn{1}{p{0.910in}|}{\begin{minipage}[t]{0.910in}\raggedright
+50 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Free action\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
+100 \end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Disguise }

The character can change his or her apparent height and weight much more than normal. 

\begin{longtable}{|p{2.480in}|p{0.675in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{2.480in}\raggedright \textbf{Disguise}\end{minipage} & \begin{minipage}[t]{0.675in}\centering \textbf{Modifier}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\centering Change height and/or weight 11\% to 25\%\end{minipage} & \begin{minipage}[t]{0.069in}\centering -25*\end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{2.480in}\centering Change height and/or weight 26\% to 50\%\end{minipage} & \begin{minipage}[t]{0.675in}\centering -50*\end{minipage}\\
\hline
\end{longtable}

*Can be negated by any effect that can duplicate a height and/or weight change 
of this degree. 

\vspace{12pt}
\subsection*{Escape Artist }

The character can pass through spaces smaller than his or her head, or even through 
a \textit{wall of forc}e.

\begin{longtable}{|p{0.358in}|p{1.601in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.358in}\raggedright \textbf{DC}\end{minipage} & \begin{minipage}[t]{1.601in}\raggedright \textbf{Task 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright 80\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright Extremely 
tight space \end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{0.358in}\raggedright 120\end{minipage} & \begin{minipage}[t]{1.601in}\raggedright Pass 
through \textit{wall of force }\end{minipage}\\
\hline
\end{longtable}

\textbf{Extremely Tight Space:}\textit{ }This is the DC for getting through a space 
when one's head shouldn't even be able to fit; this can be as small as 2 inches 
square for Medium-size creatures. Halve this limit for each size category less 
than Medium-size; double it for each size category greater than Medium-size. If 
the space is long, such as in a chimney, multiple checks may be called for. 

\textbf{Pass through }\textit{\textbf{Wall of Force}}\textit{: }This allows a character 
to find a gap of weakness in a \textit{wall of force }(or similar force effect) 
and squeeze through it. 

\vspace{12pt}
\subsection*{Forgery }

The character can forge handwriting he or she haven't even seen.

\begin{longtable}{|p{1.944in}|p{1.655in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.944in}\raggedright \textbf{Condition}\end{minipage} & \begin{minipage}[t]{1.655in}\centering \textbf{Reader's 
Check Modifier}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\centering Forge document without sample\end{minipage} & \begin{minipage}[t]{0.069in}\centering +50\end{minipage}\\
\hline
\end{longtable}

\textbf{Forge Document without Sample: }\textit{ }The character can forge a document 
without having seen a similar document or having a sample of the handwriting to 
be copied.

\vspace{12pt}
\subsection*{Gather Information }

The character can gather information without eliciting suspicion. 

\begin{longtable}{|p{1.057in}|p{1.087in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.057in}\raggedright \textbf{Task }\end{minipage} & \begin{minipage}[t]{1.087in}\raggedright \textbf{Check 
Modifier }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Avoid suspicion\end{minipage} & \begin{minipage}[t]{0.069in}\centering -20\end{minipage}\\
\hline
\end{longtable}

\textbf{Avoid Suspicion:}\textit{ }By accepting a -20 penalty on his or her Gather 
Information check, a character can avoid any suspicions that might otherwise be 
aroused by someone pursuing sensitive information. 

\vspace{12pt}
\subsection*{Handle Animal }

The character can handle creatures other than animals, and can teach or train in 
much less time than normally required. 

\begin{longtable}{llllll}
\hline
% ROW 1
\multicolumn{1}{|p{1.253in}|}{\begin{minipage}[t]{1.253in}\raggedright
\textbf{Task}\end{minipage}} & \multicolumn{1}{p{0.663in}|}{\begin{minipage}[t]{0.663in}\raggedright
\textbf{Time}\end{minipage}} & \multicolumn{1}{p{1.583in}|}{\begin{minipage}[t]{1.583in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Rear magical beast \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
1 year\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
30 + HD of magical beast \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.253in}|}{\begin{minipage}[t]{1.253in}\raggedright
Train magical beast \end{minipage}} & \multicolumn{1}{p{0.663in}|}{\begin{minipage}[t]{0.663in}\raggedright
2 months\end{minipage}} & \multicolumn{1}{p{1.583in}|}{\begin{minipage}[t]{1.583in}\raggedright
40 + HD of magical beast \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Rear vermin \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
6 months\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
35 + HD of vermin \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{1.253in}|}{\begin{minipage}[t]{1.253in}\raggedright
Train vermin \end{minipage}} & \multicolumn{1}{p{0.663in}|}{\begin{minipage}[t]{0.663in}\raggedright
2 months\end{minipage}} & \multicolumn{4}{p{1.791in}|}{\begin{minipage}[t]{1.791in}\raggedright
50 + HD of vermin \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Rear other creature \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Varies\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
40 + HD of creature \end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{1.253in}|}{\begin{minipage}[t]{1.253in}\raggedright
Train other creature \end{minipage}} & \multicolumn{1}{p{0.663in}|}{\begin{minipage}[t]{0.663in}\raggedright
2 months\end{minipage}} & \multicolumn{4}{p{1.791in}|}{\begin{minipage}[t]{1.791in}\raggedright
60 + HD of creature \end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{2.095in}|}{\begin{minipage}[t]{2.095in}\raggedright
\textbf{Reduce Teaching/Training to . . . }\end{minipage}} & \multicolumn{1}{p{0.910in}|}{\begin{minipage}[t]{0.910in}\centering
\textbf{DC Modifier}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1 month\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+25\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{2.095in}|}{\begin{minipage}[t]{2.095in}\centering
1 day \end{minipage}} & \multicolumn{1}{p{0.910in}|}{\begin{minipage}[t]{0.910in}\centering
+50\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
1 hour\end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\centering
+75\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{2.095in}|}{\begin{minipage}[t]{2.095in}\centering
1 minute\end{minipage}} & \multicolumn{3}{p{1.049in}|}{\begin{minipage}[t]{1.049in}\centering
+100\end{minipage}}\\
\hline
\end{longtable}

\textbf{Reduce Teaching/Training: }Normally, teaching or training a creature requires 
two months of time. A character can accelerate the process of teaching or training 
a creature, reducing the time required to the listed time, by adding the DC modifier 
to the base DC for teaching or training the creature. A character can't reduce 
the required time to less than 1 minute. 

\vspace{12pt}
\subsection*{Heal }

The character can greatly speed a patient's recovery of hit points. 

\begin{longtable}{|p{1.142in}|p{0.358in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.142in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{0.358in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Quicken recovery\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright 50 
\end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{1.142in}\raggedright Perfect recovery\end{minipage} & \begin{minipage}[t]{0.358in}\raggedright 100 
\end{minipage}\\
\hline
\end{longtable}

\textbf{Quicken Recovery: }The character can allow a character to regain hit points 
in a single hour as if he or she had provided long-term care for a full day (2 
or 3 hit points per level, based on activity). The character can quicken the recovery 
of up to six patients at a time. No character's recovery can be quickened more 
than once per day (even by different healers). 

\textbf{Perfect Recovery:}\textit{ }The character can allow a character to regain 
hit points in a single hour as if he or she had provided long-term care for a full 
week (2 or 3 hit points per level per day, based on activity). The character can 
use perfect recovery on up to six patients at a time. No character's recovery can 
be perfected more than once per day, nor can perfect recovery and quicken recovery 
both be used on the same patient in the same day (even by different healers).

\vspace{12pt}
\subsection*{Hide }

The character can hide others as well as hiding him or herself. 

\begin{longtable}{|p{0.872in}|p{1.087in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.872in}\raggedright \textbf{Task}\end{minipage} & \begin{minipage}[t]{1.087in}\centering \textbf{Check 
Modifier}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\centering Hide another\end{minipage} & \begin{minipage}[t]{0.069in}\centering -30\end{minipage}\\
\hline
\end{longtable}

\textit{\textbf{Hide Another:}}\textit{ }By accepting a -30 penalty on his or her 
Hide check, a character can hide another adjacent creature whose size is no more 
than one category larger than the character's own. Modifiers to the check for the 
size of the creature still apply, as do all other penalties, including those for 
moving faster than half speed. Likewise, a character can only hide another creature 
when it is not under direct observation by a third party. The creature the character 
hides remains hidden until it is spotted or it takes some other action that breaks 
its concealment, as normal. 

\vspace{12pt}
\subsection*{Intimidate }

Intimidate does not possess an epic usage. 

\textbf{Special:} The DC to intimidate any creature whose attitude is fanatic is 
increased by +20. 

\vspace{12pt}
\subsection*{Jump }

Jump does not possess an epic usage. 

\vspace{12pt}
\subsection*{Knowledge}

Knowledge does not possess an epic usage. 

\vspace{12pt}
\subsection*{Listen }

The character can pinpoint the location of an invisible creature, or detect an 
illusion with an auditory component. 

\begin{longtable}{|p{0.351in}|p{2.403in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.351in}\raggedright \textbf{DC }\end{minipage} & \begin{minipage}[t]{2.403in}\raggedright \textbf{Task 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright 80 \end{minipage} & \begin{minipage}[t]{0.069in}\raggedright Defeat 
illusion with auditory component \end{minipage}\\
\hline
\end{longtable}

\textbf{Defeat Illusion:}\textit{ }The character can automatically detect any illusion 
with an auditory component for what it truly is. No Will save is required, and 
the character doesn't have to interact with the illusion (but he or she must be 
able to hear its auditory component). Special: A character can use Listen to notice 
the presence of an invisible creature (generally opposed by a Move Silently check). 
If the character beats the DC by 20 or more, he or she can pinpoint the location 
of the invisible creature, though it still maintains total concealment from the 
character (50\% miss chance). 

\vspace{12pt}
\subsection*{Move Silently }

Move Silently does not possess an epic usage. 

\vspace{12pt}
\subsection*{Open Lock }

The character can open locks more quickly than normal. 

\begin{longtable}{|p{1.473in}|p{0.910in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.473in}\raggedright \textbf{Open lock as . . . }\end{minipage} & \begin{minipage}[t]{0.910in}\raggedright \textbf{DC 
Modifier }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Move-equivalent action \end{minipage} & \begin{minipage}[t]{0.069in}\raggedright +20 
\end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{1.473in}\raggedright Free action \end{minipage} & \begin{minipage}[t]{0.910in}\raggedright +50 
\end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Perform }

The character can sway an audience's attitude with his or her performance.

\begin{longtable}{llllllllllllll}
\hline
% ROW 1
\multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
\textbf{ }\end{minipage}} & \multicolumn{6}{p{3.307in}|}{\begin{minipage}[t]{3.307in}\centering
------------------\textbf{New Attitude ------------------}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
\textbf{Initial Attitude }\end{minipage}} & \multicolumn{6}{p{0.325in}|}{\begin{minipage}[t]{0.325in}\centering
\textbf{Hos}\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
\textbf{Unf}\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
\textbf{Indif}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\centering
\textbf{Friend}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\centering
\textbf{Help}\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
\textbf{Fanatic}\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Hostile \end{minipage}} & \multicolumn{1}{p{0.467in}|}{\begin{minipage}[t]{0.467in}\centering
Less than 20\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
20\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
25\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
35\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
50\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
150\end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Unfriendly \end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Less than 5\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
5\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
15\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
25\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
40\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
120\end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Indifferent \end{minipage}} & \multicolumn{8}{p{0.847in}|}{\begin{minipage}[t]{0.847in}\centering
---\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
15\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
30\end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\raggedright
90\end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
Friendly \end{minipage}} & \multicolumn{1}{p{0.054in}|}{\begin{minipage}[t]{0.054in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
20\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
60\end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{p{0.341in}|}{\begin{minipage}[t]{0.341in}\centering
Helpful \end{minipage}} & \multicolumn{8}{p{0.847in}|}{\begin{minipage}[t]{0.847in}\centering
---\end{minipage}} & \multicolumn{1}{|p{0.814in}|}{\begin{minipage}[t]{0.814in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.665in}|}{\begin{minipage}[t]{0.665in}\raggedright
---\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
Less than 1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
1\end{minipage}} & \multicolumn{1}{p{0.611in}|}{\begin{minipage}[t]{0.611in}\raggedright
50\end{minipage}}\\
\hline
\end{longtable}

\textbf{Hos: }hostile. \textbf{Unf: }unfriendly. \textbf{Indif: }indifferent. \textbf{Friend: 
}friendly. \textbf{Help: }helpful.

\textbf{Fanatic: }The attitude of fanatic is added here. In addition to the obvious 
effects, any NPC whose attitude is fanatic gains a +2 morale bonus to Strength 
and Constitution scores, a +1 morale bonus on Will saves, and a -1 penalty to AC 
whenever fighting for the character or his or her cause. This attitude will remain 
for one day plus one day per point of the character's Charisma bonus, at which 
point the NPC's attitude will revert to its original attitude (or indifferent, 
if no attitude is specified). 

Treat the fanatic attitude as a mind-affecting enchantment effect for purposes 
of immunity, save bonuses, or being detected by the Sense Motive skill. Since it 
is nonmagical, it can't be dispelled; however, any effect that suppresses or counters 
mind-affecting effects will affect it normally. A fanatic NPC's attitude can't 
be further adjusted by the use of skills. 

\begin{longtable}{|p{0.503in}|p{1.251in}|p{2.583in}|p{0.054in}|p{0.054in}|p{0.054in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.503in}\raggedright \textbf{Attitude }\end{minipage} & \begin{minipage}[t]{1.251in}\raggedright \textbf{Means 
}\end{minipage} & \begin{minipage}[t]{2.583in}\raggedright \textbf{Possible Actions 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.054in}\raggedright Fanatic \end{minipage} & \begin{minipage}[t]{0.054in}\raggedright Will 
give life to serve you\end{minipage} & \begin{minipage}[t]{0.054in}\raggedright Fight 
to the death against overwhelming odds, throw self in front of onrushing dragon 
\end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Profession }

Profession does not possess an epic usage. 

\vspace{12pt}
\subsection*{Ride }

The character can stand upon his or her mount in combat. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
\textbf{DC}\end{minipage}} & \multicolumn{1}{p{1.296in}|}{\begin{minipage}[t]{1.296in}\raggedright
\textbf{Task }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
40 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Stand on mount \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
50 \end{minipage}} & \multicolumn{1}{p{1.296in}|}{\begin{minipage}[t]{1.296in}\raggedright
Unconscious control \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Attack from cover \end{minipage}}\\
\hline
\end{longtable}

\textbf{Stand on Mount: }This allows the character to stand on his or her mount's 
back even during movement or combat. The character takes no penalties to actions 
while doing so. 

\textbf{Unconscious Control: }As a free action, the character can attempt to control 
a light horse, pony, or heavy horse while in combat. If the character fails, he 
or she controls the mount as a move-equivalent action. A character does not need 
to roll for warhorses or warponies. 

\textbf{Attack from Cover: }The character can react instantly to drop down and 
hang alongside his or her mount, using it as one-half cover. The character can 
attack and cast spells while using his or her mount as cover without penalty. If 
the character fails, he or she doesn't get the cover benefit. 

\vspace{12pt}
\subsection*{Search }

The character can sense the presence of magic in an area. 

\begin{longtable}{|p{0.849in}|p{0.351in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.849in}\raggedright \textbf{Task }\end{minipage} & \begin{minipage}[t]{0.351in}\raggedright \textbf{DC 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Sense magic \end{minipage} & \begin{minipage}[t]{0.069in}\raggedright 60 
\end{minipage}\\
\hline
\end{longtable}

\textbf{Sense Magic: }The character senses the presence of any active magical effects 
in the area being searched. The character can't determine the number, strength, 
or type of the effects. 

\vspace{12pt}
\subsection*{Sense Motive }

The character can discern a target's alignment and even detect surface thoughts.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.562in}|}{\begin{minipage}[t]{1.562in}\raggedright
\textbf{Task }\end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
\textbf{DC}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Discern partial alignment \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.562in}|}{\begin{minipage}[t]{1.562in}\raggedright
Discern full alignment \end{minipage}} & \multicolumn{1}{p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
80 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Detect surface thoughts \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
100 \end{minipage}}\\
\hline
\end{longtable}

\textbf{Discern Partial Alignment: }This use of the skill lets a character discern 
one component of a target's alignment. When making the check, the character states 
whether he or she is trying to discern the law-chaos or good-evil component. A 
character can't retry the check, and he or she can't use this to discern more than 
one component of the alignment (but see below). The target must be visible and 
within 30 feet of the character. 

\textbf{Discern Full Alignment: }This use of the skill lets a character determine 
both components of a target's alignment. The character can't retry the check. The 
target must be visible and within 30 feet of the character. 

\textbf{Detect Surface Thoughts: }This lets a character read the surface thoughts 
of a single target (as the 3rd-round effect of the \textit{detect thoughts }spell). 
There is no saving throw to resist this effect, though the target can use Bluff 
to disguise his or her surface thoughts (see the Bluff skill description), in which 
case this becomes an opposed check (any result lower than 100 automatically fails). 
The target must be visible and within 30 feet of the character.

\vspace{12pt}
\subsection*{Sleight of Hand }

The character can lift another's weapon and perform major feats of legerdemain. 

\begin{longtable}{|p{0.236in}|p{4.170in}|p{0.047in}|p{0.047in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.236in}\raggedright \textbf{DC}\end{minipage} & \begin{minipage}[t]{4.170in}\raggedright \textbf{ 
Task}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.047in}\raggedright 50 \end{minipage} & \begin{minipage}[t]{0.047in}\raggedright Lift 
a sheathed weapon from another creature and hide it on the character's person, 
if the weapon is no more than one size category larger than the character's own 
size. \end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{0.236in}\raggedright 80\end{minipage} & \begin{minipage}[t]{4.170in}\raggedright Make 
an adjacent, willing creature or object of the character's size or smaller ``disappear'' 
while in plain view. In fact, the willing creature or object is displaced up to 
10 feet away---make a separate Hide check to determine how well the ``disappeared'' 
creature or object is hidden. \end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Spellcraft }

The character can identify properties of a magic item. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.051in}|}{\begin{minipage}[t]{1.051in}\raggedright
\textbf{DC }\end{minipage}} & \multicolumn{1}{p{3.313in}|}{\begin{minipage}[t]{3.313in}\raggedright
\textbf{Task }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
50 + caster level \end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
Identify basic property of magic item \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.051in}|}{\begin{minipage}[t]{1.051in}\raggedright
70 + caster level \end{minipage}} & \multicolumn{1}{p{3.313in}|}{\begin{minipage}[t]{3.313in}\raggedright
Identify all properties of magic item \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
50\end{minipage}} & \multicolumn{1}{p{0.068in}|}{\begin{minipage}[t]{0.068in}\raggedright
Quick identification of alchemical substances and potions\end{minipage}}\\
\hline
\end{longtable}

\textbf{Identify Basic Property of Magic Item:} This use of the skill requires 
one round of inspection, and functions exactly as if the character had cast an 
\textit{identify }spell on the item. A character can't attempt this on the same 
item more than once. 

\textbf{Identify All Properties of Magic Item:}\textit{ }This requires one minute 
of inspection, and reveals all properties of a single magic item (including command 
words and charges remaining). A character can't attempt this on the same item more 
than once. If an item has different caster levels for different properties, use 
the highest caster level. 

\textbf{Quick Identification: }A character can identify a substance or potion in 
the field as a full-round action, without an alchemical lab or any cost. The character 
can't retry this check (or take 20); if he or she fails, the character must identify 
the substance in an alchemical lab, as normal. 

\vspace{12pt}
\subsection*{Spot }

The character can pinpoint the location of an invisible creature, or detect an 
illusion with a visual component. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
\textbf{DC }\end{minipage}} & \multicolumn{1}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
\textbf{Task }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
20 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Notice presence of active invisible creature \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
30 \end{minipage}} & \multicolumn{1}{p{3.317in}|}{\begin{minipage}[t]{3.317in}\raggedright
Notice presence of unmoving, living invisible creature \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
40 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Notice presence of inanimate invisible object \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
40 \end{minipage}} & \multicolumn{3}{p{3.456in}|}{\begin{minipage}[t]{3.456in}\raggedright
Notice presence of unmoving, unliving invisible creature \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
80 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Defeat illusion \end{minipage}}\\
\hline
\end{longtable}

A character can use Spot to notice the presence of an invisible creature\textit{. 
}The relevant DCs are reprinted here. If the character beats the DC by 20 or more, 
he or she can pinpoint the location of the invisible creature, though it still 
maintains total concealment from the character (50\% miss chance). 

\textbf{Defeat Illusion: }The character can automatically detect any illusion with 
a visual component for what it truly is. No Will save is required, and the character 
doesn't have to interact with the illusion (but he or she must be able to see it). 

\subsection*{\textbf{Using Spot to Read Lips }}

\subsection*{\begin{longtable}{|p{2.503in}|p{0.910in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{2.503in}\raggedright \textbf{Task }\end{minipage} & \begin{minipage}[t]{0.910in}\raggedright \textbf{DC 
Modifier }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Read lips while moving at up to full speed\end{minipage} & \begin{minipage}[t]{0.069in}\raggedright +20 
\end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{2.503in}\raggedright Pronounce unfamiliar language \end{minipage} & \begin{minipage}[t]{0.910in}\raggedright +20 
\end{minipage}\\
\hline
\end{longtable}
}

\textbf{Pronounce Unfamiliar Language:}\textit{ }This use of the skill allows a 
character to repeat the speech of an observed creature, potentially allowing a 
comrade to translate the speech. It doesn't grant the character any ability to 
understand the language spoken. 

\vspace{12pt}
\subsection*{Survival}

The character can ignore the effects of terrain on movement and withstand even 
the harshest weather. If the character is capable of tracking, he or she can identify 
the races of creatures being tracked. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
\textbf{DC }\end{minipage}} & \multicolumn{1}{p{4.198in}|}{\begin{minipage}[t]{4.198in}\raggedright
\textbf{Task }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
40 \end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Get along in the wild while moving at full speed. The character can provide food 
and water for one other person for every 2 points by which the check result exceeds 
40. \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{4.198in}|}{\begin{minipage}[t]{4.198in}\raggedright
Automatically succeed on all Fortitude saves against severe weather. The character 
can extend this benefit to one other character for every 2 points by which the 
check result exceeds 60. \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Ignore overland movement penalties of terrain. The character and his or her mount 
can move at full overland speed regardless of terrain. The character can extend 
this benefit to one other character for every 5 points by which the check result 
exceeds 60. \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.217in}|}{\begin{minipage}[t]{0.217in}\raggedright
60 \end{minipage}} & \multicolumn{3}{p{4.283in}|}{\begin{minipage}[t]{4.283in}\raggedright
Identify race/kind of creature(s) by tracks.* \end{minipage}}\\
\hline
\end{longtable}

*Requires the Track feat. 

\vspace{12pt}
Wherever the character is, he or she can determine the direction to a location 
on the same plane. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
\textbf{DC}\end{minipage}} & \multicolumn{1}{p{1.712in}|}{\begin{minipage}[t]{1.712in}\raggedright
\textbf{ Familiarity with Location }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
40 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Very familiar \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{1.712in}|}{\begin{minipage}[t]{1.712in}\raggedright
Studied carefully \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
80 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Seen casually \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
100 \end{minipage}} & \multicolumn{3}{p{1.851in}|}{\begin{minipage}[t]{1.851in}\raggedright
Viewed once \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
120 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Description only \end{minipage}}\\
\hline
\end{longtable}

With a successful check, the character knows the direction to the desired location. 
This merely points the character in the direction of the location; it doesn't provide 
him or her with information on how to get there, nor does it take into account 
any obstacles in the path. ``Very familiar'' represents a place where the character 
has been very often and where he or she feels at home. ``Studied carefully'' represents 
a place the character knows well, either because he or she has been there often 
or has used other means to study the place. ``Seen casually'' is a place that the 
character has viewed more than once, but which he or she has not studied. ``Viewed 
once'' is a place that the character has seen once, possibly using magic. ``Description 
only'' is a place whose location and appearance the character knows through someone 
else's description. 

\vspace{12pt}
\subsection*{Swim }

The character can swim up vertical surfaces, or swim much faster than normal. 

\begin{longtable}{|p{0.351in}|p{1.176in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.351in}\raggedright \textbf{DC }\end{minipage} & \begin{minipage}[t]{1.176in}\raggedright \textbf{Task 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright 80 \end{minipage} & \begin{minipage}[t]{0.069in}\raggedright Swim 
up waterfall \end{minipage}\\
\hline
\end{longtable}

\textbf{Swim up Waterfall: }This use of the skill allows a character to swim an 
angled or vertical surface, as long as he or she remains completely or mostly immersed 
in water. Other examples might include swimming up a whirlpool or an incredibly 
large wave. 

\begin{longtable}{|p{1.111in}|p{0.910in}|p{0.069in}|p{0.069in}|}
\hline
% ROW 1
\begin{minipage}[t]{1.111in}\raggedright \textbf{Circumstance }\end{minipage} & \begin{minipage}[t]{0.910in}\raggedright \textbf{DC 
Modifier }\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.069in}\raggedright Speed swimming \end{minipage} & \begin{minipage}[t]{0.069in}\raggedright -20 
\end{minipage}\\
\hline
\end{longtable}

\textbf{Speed Swimming: }By taking a -20 penalty on the check, a character can 
swim his or her speed as a move-equivalent action, or double his or her speed as 
a full-round action. 

\vspace{12pt}
\subsection*{Tumble }

The character can fall from great heights without taking damage, move greater distances 
with an adjustment, or ``climb'' vertical surfaces with a series of bounces. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
\textbf{DC }\end{minipage}} & \multicolumn{1}{p{3.826in}|}{\begin{minipage}[t]{3.826in}\raggedright
\textbf{Task }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
30 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Treat a fall as if it were 20 feet shorter when determining damage. \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
35 \end{minipage}} & \multicolumn{1}{p{3.826in}|}{\begin{minipage}[t]{3.826in}\raggedright
Free stand. \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
45 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Treat a fall as if it were 30 feet shorter when determining damage. \end{minipage}}\\
\hline
% ROW 5
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
50 \end{minipage}} & \multicolumn{3}{p{3.965in}|}{\begin{minipage}[t]{3.965in}\raggedright
Climb vertical surface. \end{minipage}}\\
\hline
% ROW 6
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Treat a fall as if it were 40 feet shorter when determining damage. \end{minipage}}\\
\hline
% ROW 7
\multicolumn{1}{|p{0.358in}|}{\begin{minipage}[t]{0.358in}\raggedright
100 \end{minipage}} & \multicolumn{3}{p{3.965in}|}{\begin{minipage}[t]{3.965in}\raggedright
Ignore falling damage. \end{minipage}}\\
\hline
\end{longtable}

\textbf{Free Stand: }The character can stand up from prone as a free action (instead 
of as a move-equivalent action). 

\textbf{Climb Vertical Surface: }The character can climb up to 20 feet (as part 
of normal move-ment) by jumping and bouncing off walls, trees, or similar vertical 
surfaces. The character must have at least two vertical surfaces to bounce off, 
and the two must be within 10 feet of each other. 

\textbf{Ignore Falling Damage: }The character can fall from any height and take 
no damage. 

Special: A character with 25 or more ranks in Tumble gains a +5 dodge bonus when 
executing the fight defensively standard or full-round action, instead of a +2 
bonus (or the +3 bonus from having 5 or more ranks). Increase this dodge bonus 
by +1 for every 10 additional ranks above 25 the character has. A character with 
25 or more ranks in Tumble gains a +10 dodge bonus to AC when executing the total 
defense standard action, instead of a +4 bonus (or the +6 bonus from having 5 or 
more ranks). Increase this dodge bonus by +2 for every 10 additional ranks above 
25 the character has. 

\vspace{12pt}
\subsection*{Use Magic Device }

Use Magic Device does not possess an epic usage. 

\vspace{12pt}
\subsection*{Use Rope }

The character can splice ropes together quickly, tie unique knots, and even animate 
a rope he or she holds. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
\textbf{Task}\end{minipage}} & \multicolumn{1}{p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Quick splicing \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
50 \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{1.184in}|}{\begin{minipage}[t]{1.184in}\raggedright
Tie unique knot \end{minipage}} & \multicolumn{1}{p{0.351in}|}{\begin{minipage}[t]{0.351in}\raggedright
60 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Animate held rope \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
80 \end{minipage}}\\
\hline
\end{longtable}

\textbf{Quick Splicing:}\textit{ }The character can splice two ropes together as 
a move-equivalent action. 

\textbf{Tie Unique Knot:}\textit{ }The character can tie a knot that only he or 
she knows how to untie. This doesn't affect any Escape Artist checks made to escape 
these bindings. 

\textbf{Animate Held Rope:} The character can command any rope he or she holds 
as if it had the \textit{animate rope }spell cast upon it (except that using the 
skill in this way doesn't grant any bonus on Use Rope checks made with the animated 
rope). Each command requires a separate Use Rope check. Because the effect isn't 
magical, it can't be dispelled. 

\vspace{24pt}
\subsection*{{\LARGE PSIONIC SKILLS}}

\vspace{12pt}
\subsection*{Autohypnosis }

The character has trained his or her mind to ignore poison, resist mental influence, 
and convince his or her body that he or she is tougher than normal. 

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.675in}|}{\begin{minipage}[t]{0.675in}\raggedright
\textbf{DC}\end{minipage}} & \multicolumn{1}{p{3.738in}|}{\begin{minipage}[t]{3.738in}\raggedright
\textbf{Task}\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
Poison's DC + 5\end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
When poisoned, the character can make an Autohypnosis check on his or her next 
action. A successful check indicates the character does not have to make a saving 
throw against the poison's secondary damage, which he or she instead automatically 
ignores. \end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.675in}|}{\begin{minipage}[t]{0.675in}\raggedright
50 \end{minipage}} & \multicolumn{1}{p{3.738in}|}{\begin{minipage}[t]{3.738in}\raggedright
If a failed saving throw indicates the character is affected by any mind-affecting 
powers, spells, or spell-like effects, a successful Autohypnosis check allows an 
immediate second saving throw to resist the effect. If the mind-affecting effect 
normally does not allow a saving throw, a successful Autohypnosis check allows 
a saving throw. \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
60 \end{minipage}} & \multicolumn{1}{p{0.043in}|}{\begin{minipage}[t]{0.043in}\raggedright
With a successful Autohypnosis check, the character gains temporary hit points 
equal to 10 + his or her Wisdom modifier. The temporary hit points persist until 
lost. A character cannot check for temporary hit points more than once per day. 
Temporary hit points gained through Autohypnosis do not stack with temporary hit 
points gained through any other source \end{minipage}}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{Stabilize Self }

Mortal wounds are less lethal for the character. 

\begin{longtable}{|p{0.217in}|p{4.198in}|p{0.043in}|p{0.043in}|}
\hline
% ROW 1
\begin{minipage}[t]{0.217in}\raggedright \textbf{DC}\end{minipage} & \begin{minipage}[t]{4.198in}\raggedright \textbf{Task 
}\end{minipage}\\
\hline
% ROW 2
\begin{minipage}[t]{0.043in}\raggedright 30\end{minipage} & \begin{minipage}[t]{0.043in}\raggedright If 
reduced to negative hit points but not dead, make a Stabilize Self check. If successful, 
the character does not go unconscious and can continue taking actions until he 
or she bleeds to death or stabilizes (the character can also continue making stabilization 
checks). If healed or stabilized, the character continues to take actions normally. 
\end{minipage}\\
\hline
% ROW 3
\begin{minipage}[t]{0.217in}\raggedright 60 \end{minipage} & \begin{minipage}[t]{4.198in}\raggedright On 
a successful Stabilize Self check, the character gains damage reduction 2/-. The 
damage reduction lasts for 12 hours. The character cannot check for damage reduction 
more than once per day. Damage reduction gained through Stabilize Self does not 
stack with damage reduction gained through any other source. \end{minipage}\\
\hline
\end{longtable}

\vspace{12pt}
\subsection*{{\LARGE Miscellaneous}}

\textit{Scrying} spells

To attempt any of these tasks, the \textit{scrying }spell must be on your class 
spell list (though it need not be among your spells known). If you have any bonuses 
that would apply to the caster level of your \textit{scrying }spell, add these 
to your caster level check.

\begin{longtable}{llll}
\hline
% ROW 1
\multicolumn{1}{|p{0.972in}|}{\begin{minipage}[t]{0.972in}\raggedright
\textbf{Task}\end{minipage}} & \multicolumn{1}{p{1.666in}|}{\begin{minipage}[t]{1.666in}\raggedright
\textbf{DC }\end{minipage}}\\
\hline
% ROW 2
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Learn scryer \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
30\end{minipage}}\\
\hline
% ROW 3
\multicolumn{1}{|p{0.972in}|}{\begin{minipage}[t]{0.972in}\raggedright
Return scrying \end{minipage}} & \multicolumn{1}{p{1.666in}|}{\begin{minipage}[t]{1.666in}\raggedright
50 \end{minipage}}\\
\hline
% ROW 4
\multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Break scrying \end{minipage}} & \multicolumn{1}{p{0.069in}|}{\begin{minipage}[t]{0.069in}\raggedright
Opposed caster level check \end{minipage}}\\
\hline
\end{longtable}

\textbf{Learn Scryer: }If you determine that you're being scried upon, you can 
learn the identity of the scryer with a DC 30 caster level check. If successful, 
you learn the name, race, and location of the scryer. 

\textbf{Return Scrying: }If you determine that you're being scried upon, you can 
look back through the sensor at the scryer with a DC 50 caster level check. This 
allows you to spy on the scrying being as if you had cast a \textit{scrying }spell 
upon that person. This return scrying can be detected by your target as normal.

\textbf{Break Scrying: }If you determine that you're being scried, you can make 
an opposed caster level check with the scryer. (Your caster level must be at least 
21st to attempt this task.) If you are successful, the scrying ends, and the scryer 
may not target you with a Divination (Scrying) spell or effect for a number of 
hours equal to your Intelligence modifier (minimum 1).

\end{document}
