\classname{Lunar Knight} \label{comm:prestige:lunarknight}
\vspace*{-8pt}
\quot{``Agent of love and justice, pretty soldier Lunar Knight! In the name of the moon, I will punish you!''}

\ability{Requirements:}{}
\listprereq
\itemability{BAB:}{+7}
\itemability{Skills:}{Knowledge (the Planes) 10 ranks}
\itemability{Alignment:}{Any Good}
\itemability{Special:}{A Knight of an appropriate order qualifies just by existing.}
\end{list}\vspace*{8pt}


\ability{Hit Die:}{d10}

\ability{Class Skills:}{Whatever you want, since Koumei doesn't believe in cross-class skills.}

\ability{Skill Points at Each Level:}{4 + Int modifier.}

\begin{table}[tbh]
\begin{small}
\begin{tabular}{lp{1.9cm}p{0.7cm}p{0.7cm}p{0.7cm}l}
Level  &Base Attack  Bonus &Fort Save &Ref Save &Will Save &Special\\
1st &+1 &+2 &+2 &+2 &Aura of Moonlight, Flight, Lunar Healing Escalation\\
2nd &+2 &+3 &+3 &+3 &Moon Prism Power, Moon Spiral Heart Attack\\
3rd &+3 &+3 &+3 &+3 &Lunar Gorgeous Meditation, Silver Smite\\
4th &+4 &+4 &+4 &+4 &Cosmic Moon Power, Starlight Honeymoon Therapy Kiss\\
5th &+5 &+4 &+4 &+4 &Silver Moon Crystal Power Kiss, Half Moon Phases\\
\end{tabular}
\end{small}
\end{table}

\smallskip\noindent All of the following are Class Features of the Lunar Knight prestige class.

\ability{Weapon and Armor Proficiency:}{Lunar Knight gain no proficiency with any weapon or armor.}

\ability{Aura of Moonlight:}{The Lunar Knight emits moonlight (like Daylight) out to 20' unless they decide to suppress the ability such as to sleep. Anyone assuming a form other than their own natural one is forced back to their natural form while in the area. Lycanthropes, however, are forced into their half-way form. This is a Supernatural ability.}

\ability{Flight:}{Lunar Knights can fly at a speed of 50' with Perfect maneuverability. This is a Supernatural ability.}

\ability{Lunar Healing Escalation:}{As a Supernatural ability, the Lunar Knight can heal others with a Standard Action at will. This generates a 15' burst around the Knight, and everyone within the area that the Knight designates regains 1d8 HP per class level, plus her Charisma modifier. This sadly does not heal the Knight herself.}

\ability{Moon Prism Power:}{As a Supernatural ability at will, the Lunar Knight may transform, requiring a Standard Action. This is not affected by Aura of Moonlight. While transformed, the Knight gains a Deflection bonus to AC and a Resistance bonus to all saves, equal to her class level, and Fast Healing equal to her Charisma modifier. Also, her Flight speed is doubled. This ability lasts for the encounter - cooling down whenever her adrenaline returns to normal.}

\ability{Moon Spiral Heart Attack:}{The Lunar Knight gains the ability to launch a dazzling light attack as a Supernatural ability, but only when Moon Prism Power is activated. It can be used once per transformation, and requires a Standard Action. This fires a bolt out to Medium Range, requiring a Touch Attack, that deals 1d6 Holy damage per hit die. Additionally, it creates a burst of colour, 15' in radius, centred on the target. All in the area must make a Will save (Charisma-based) or be Fascinated for 1d6 rounds.}

\ability{Lunar Gorgeous Meditation:}{Now, whenever the Lunar Knight transforms, their allies within 30' also gain the Fast Healing.}

\ability{Silver Smite:}{If a Designated Foe is stupid enough not to damage the Knight, then when she in turn hits them for a lot of extra damage, she may declare it a Silver Smite. If the target is [Extraplanar], then at the end of the Knight's turn (assuming she attacked them), they must make a Will Save (Charisma-based) or be Banished. If a [Shapechanger], they instead must make a Fortitude save or be destroyed. Anyone else simply has to make a Will save or spend 1 round Cowering.}

\ability{Cosmic Moon Power:}{Having activated Moon Prism Power, a Lunar Knight may activate Cosmic Moon Power, a Supernatural ability, as a Standard action once per transformation. All enemies within 50' must immediately make a Will save (Charisma-based). If they fail, they are Charmed as per a Charm Monster spell.}

\ability{Starlight Honeymoon Therapy Kiss:}{Having activated Moon Prism Power, a Lunar Knight may end the effect to activate Starlight Honeymoon Therapy Kiss, a Supernatural Ability. This is a Full Round Action that acts as a Mass Heal spell. Additionally, any enemy within 50' may elect to benefit from this spell, but if they do so, they are affected by a Charm Monster effect, even if immune.}

\ability{Silver Moon Crystal Power Kiss:}{Having activated Moon Prism Power, a Lunar Knight may end the effect to unleash the Silver Moon Crystal Power Kiss, their most powerful attack. This is a Supernatural ability that requires a Full Round Action. It creates a 50' cone, and all enemies within the cone immediately take 2d6 Holy damage per hit die of the Knight, with a Will save for half. Furthermore, if they fail the save they become Stunned for 1 minute, and if they fail and are the Designated Foe, they are Destroyed. Any allies caught in the area receive a +5 Sacred bonus to AC for one round.}

\ability{Half Moon Phases:}{When not affected by Moon Prism Power, the Lunar Knight may spend a Standard Action to split into two as a Supernatural Ability. This lasts until they decide to end the effect (causing one to vanish), and must be ended in order to activate Moon Prism Power. They may both attack, flank with each other and so on, but may not use charged or single-use items, and any X per Y abilities used by one count as being used by the other. Also, damage is shared, and 10 Hit Points are lost every round that they are divided. While both may designate different foes, thus allowing for two Designated Opponents, they each count as the original for the purposes of preventing the bonus damage.}
